### 2023-02-25 summary.tex
Add a description of (univalent) n-categories and multicategories

\documentclass{amsart}

\title{Summary of the things that I learned}
\author{Arnoud van der Leer}

\begin{document}
  \maketitle

  \section{Week 08}
  \subsection{Univalent Categories}
  A univalent category is a category in which the univalence axiom holds. I.e., a category $ \mathcal C $ in which, for all $ A, B \in \mathcal C_0 $, the canonical map $ (A =_{\mathcal C} B) \to (A \cong B) $ is an equivalence.

  \subsection{Categories}
  An \textbf{$ n $-category} is a category with $ 0 $-cells (objects), $ 1 $-cells (morphisms), $ 2 $-cells (morphisms between morphisms), up to $ n $-cells and various compositions: $ A \to B \to C $. $ A \xrightarrow{f, g, h} B $, $ f \Rightarrow g \Rightarrow h $. $ A \xrightarrow{f, g} B \xrightarrow{f^\prime, g^\prime} C $, $ \alpha: f \Rightarrow g $, and identities $ \alpha^\prime: f^\prime \Rightarrow g^\prime $ gives $ \alpha^\prime * \alpha: f^\prime \circ f \Rightarrow g^\prime \circ g $. These all need to work together `nicely'. An $ \omega $-category is the same, but all the way up.

  A topological space gives a (weak) $ \omega $-category. $ 0 $-cells are points, $ 1 $-cells are paths, $ 2 $-cells are homotopies etc. Composition is by glueing. It is a `groupoid', in the sense that all homotopies of dimension $ \geq 1 $ are invertible. However, glueing is not associative, so it is a `weak' $ \omega $-category.

  A category with only one object $ \star $ is equivalent to a monoid (with elements being the set $ \mathcal C(\star, \star) $). A $ 2 $-category with only one $ 0 $-cell is the same thing as a monoidal category (objects: the $ 1 $-cells. Morphisms: the $ 2 $-cells). A monoidal category with just one object gives $ 2 $ monoid structures on its set of morphisms. These are the same, and commutative.

  A \textbf{monoid} is a set with a multiplication and a unit. A \textbf{monad} on a category $ \mathcal A $ is a functor $ \mathcal A \to \mathcal A $, together with natural transformations $ \mu : T \circ T \to T $ (satisfying associativity) and $ \eta : 1_{\mathcal A} \to T $ (acting as a two-sided unit).

  A \textbf{presheaf} on a category $ \mathcal A $ is a functor $ \mathcal A^{\mathop{opp}} \to \mathbf{Set} $.

  Given a category $ \mathcal E $ and an object $ E \in \mathcal E_0 $, the \textbf{slice category} $ \mathcal E / E $ with objects being the maps $ D \xrightarrow{p} E $ and morphisms being commutative triangles.

  A \textbf{multicategory}, not necessarily the same as an $ n $-category, is a category in which arrows go from multiple objects to one, instead of from one object to one. I.e. it is a category with a class $ C_0 $ of objects, for all $ n $, and all $ a, a_1, \dots, a_n \in C_0 $, a class $ C(a_1, \dots, a_n; a) $ of `morphisms', and a composition 
  \[ C(a_1, \dots, a_n; a) \times C(a_{1, 1}, \dots, a_{1, k_1}; a_1) \times \dots \times C(a_{n, 1}, \dots, a_{n, k_n}; a_n) \to C(a_{1, 1}, \dots, a_{n, k_n}; a), \]
  written $ (\theta, \theta_1, \dots, \theta_n) \mapsto \theta (\theta_1, \dots, \theta_n) $ and for each $ a \in C_0 $ an identity $ 1_a \in C(a; a) $. It must satisfy associativity
  \[ \theta \circ(\theta_1 \circ(\theta_{1, 1}, \dots, \theta_{1, k_1}), \dots, \theta_n \circ (\theta_{n, 1}, \dots, \theta_{n, k_n})) = (\theta \circ (\theta_1, \dots, \theta_n)) \circ (\theta_{1, 1}, \dots, \theta_{n, k_n}) \]
  and identity
  \[ \theta \circ (1_{a_1}, \dots, 1_{a_n}) = \theta = 1_a \circ \theta. \]

  \subsection{Operads}
  An \textbf{operad} is a multicategory with only one object. More explicitly, an operad has a set $ P(k) $ for every $ k \in \mathbb N $, whose elements can be thought of as $ k $-ary operations. For example, for any vector space $ V $, there is an operad with $ P(k) = V^{\otimes k} \to V $.
\end{document}

### 2023-02-25 summary.tex
Start on a summary of operads

@@
 
+  A \textbf{map of multicategories} is a function $ f_0: C_0 \to C_0^\prime $ and maps $ C(a_1, \dots, a_n; a) \to C(f_0(a_1), \dots, f_0(a_n); f_0(a)) $, preserving composition and identities.
+
+  For $ C $ a multicategory, a \textbf{$ C $-algebra} is a map from $ C $ into the multicategory $ \mathbf{Set} $ (with objects $ \mathrm{Set}_0 $ and maps $ \mathrm{Set}(a_1, \dots, a_n; a) = \mathrm{Set}(a_1 \times \dots \times a_n ; a) $).
+I.e., for each $ a \in C_0 $, a set $ X(a) $, and for each map $ \theta: a_1, \dots, a_n \to a $, a function $ X(\theta): X(a_1) \times X(a_n) \to X(a) $.
+An example is, for a multicategory $ C $, to take $ X(a) = C(; a) $ (maps from the empty sequence into $ a $).
+
   \subsection{Operads}
+  \subsubsection{Definitions}
   An \textbf{operad} is a multicategory with only one object.
 More explicitly, an operad has a set $ P(k) $ for every $ k \in \mathbb N $, whose elements can be thought of as $ k $-ary operations.
-For example, for any vector space $ V $, there is an operad with $ P(k) = V^{\otimes k} \to V $.
+It also has, for all $ n, k_1, \dots, k_n \in \mathbb N $, a \textit{composition} function
+  \[ P(n) \times P(k_1) \times \dots \times P(k_n) \to P(k_1 + \dots + k_n) \]
+  and an element $ 1 = 1_P \in P(1) $ called the \textbf{identity}, satisfying
+  \[ \theta \circ (1, 1, \dots, 1) = \theta = \theta \circ 1 \]
+  for all $ \theta $, and
+  \[ \theta \circ(\theta_1 \circ(\theta_{1, 1}, \dots, \theta_{1, k_1}), \dots, \theta_n \circ (\theta_{n, 1}, \dots, \theta_{n, k_n})) = (\theta \circ (\theta_1, \dots, \theta_n)) \circ (\theta_{1, 1}, \dots, \theta_{n, k_n}) \]
+  for all $ \theta \in P(n) $, $ \theta_1 \in P(k_1) $, \dots, $ \theta_n \in P(k_n) $ and all $ \theta_{1, 1} \dots \theta_{n, k_n} $.
+
+  A \textbf{morphism of operads} is a family
+  \[ f_n : (P(n) \to Q(n))_{n \in \mathbb N} \]
+  of functions, preserving composition and identities.
+
+  A \textbf{$ P $-algebra} for $ P $ an operad, is a set $ X $ and, for each $ n $, and $ \theta \in P(n) $, a function $ \overline{\theta}: X^n \to X $, satisfying the evident axioms (identity is the identity function, the function of a composition is the composition of the functions?).
+
+  \subsubsection{Examples}
+  For any vector space $ V $, there is an operad with $ P(k) = V^{\otimes k} \to V $.
+
+  The terminal operad $ 1 $ has $ P(n) = \{ \star_1 \} $ for all $ n $.
+An algebra for $ 1 $ is a set $ X $ together with a function $ X^n \to X $, denoted as $ (x_1, \dots, x_n) \mapsto (x_1 \cdot \dots \cdot x_n) $, satisfying
+  \[ ((x_{1, 1} \cdot \dots x_{1, k_1}) \cdot \dots \cdot (x_{n, 1} \cdot \dots \cdot x_{n, k_n})) = (x_{1, 1} \cdot \dots \cdot x_{n, k_n}) \]
+  and
+  \[ x = (x). \]
+  The category of $ 1 $-algebras is the category of monoids.
+
+  There exist various sub-operads of $ 1 $. For example, the smallest one has $ P(1) = \{ \star \} $ and $ P(n) = \emptyset $ for $ n \not = 1 $.
+
+  Or the operad with $ P(0) = \emptyset $ and $ P(n) = \{ \star_n \} $ for $ n > 0 $, which has semigroups as its algebras (sets with associative binary operations).
+
+  The suboperad with $ P(n) = \{ \star_n \} $ exactly when $ n \leq 1 $ has as its algebras the pointed sets.
+
 \end{document}

### 2023-02-27 summary.tex
Add examples of operads and theory of T-operads

@@
 \documentclass{amsart}
+
+\usepackage{hyperref}
+\usepackage{tikz-cd}
 
@@
 
+  Of course, there is a concept of \textbf{free multicategory}: Given a set $ X $, and for all $ n \in N $, and $ x, x_1, \dots, x_n \in X $, a set $ X(x_1, \dots, x_n ; x) $, we get a multicategory $ X^\prime $ with $ X^\prime_0 = X_0 $, and $ X^\prime(x_1, \dots, x_n; x) $ given by formal compositions of elements of the $ X(y_1, \dots, y_m; y) $.
+
+  A \textbf{bicategory} consists of a class $ \mathcal B_0 $ of $ 0 $-cells, or objects; For each $ A, B \in \mathcal B_0 $, a category $ \mathcal B(A, B) $ of $ 1 $-cells (objects) and $ 2 $-cells (morphisms); for each $ A, B, C \in \mathcal B_0 $, a functor $ \mathcal B(B, C) \times \mathcal B(A, B) \to \mathcal B(A, C) $ written $ (g, f) \mapsto g \circ f $ on $ 1 $-cells and $ (\delta, \gamma) \mapsto \delta * \gamma $ on $ 2 $-cells; For each $ A \in \mathcal B_0 $ an object $ 1_A \in \mathcal B(A, A) $; isomorphisms representing associativity and identity axioms (e.g.
+$ f \circ 1_A \cong f \in \mathcal B(A, B) $), natural in their arguments, satisfying pentagon and triangle axioms.
+
+  The collection of categories $ \mathrm{Cat} $ forms a bicategory.
+In analogy, we define a monad in a bicategory to be an object $ A $, together with a $ 1 $-cell $ t: A \to A $ and $ 2 $-cells $ \mu: t \circ t \to t $ and $ \eta: 1_A \to t $ satisfying a couple of commutativity axioms (those of 1.1.3 in \cite{higher-operads-higher-categories}).
+
   \subsection{Operads}
@@
 
+  The \textbf{operad of curves} has $ P(n) = \{ \text{smooth maps}\ \mathbb R \to \mathbb R^n \} $.
+
+  Given a monad on $ \mathrm{Set} $, we get a natural operad structure $ T(n)_{n \in \mathbb N} $, with $ T(n) $ the set of words in $ n $ variables and composition given by `substitution'.
+
+  Given a monoid $ M $ (a category with one object), there is a operad given by $ P(n) = M^n $ and composition
+  \[ (\alpha_1, \dots, \alpha_n) \circ ((\alpha_{1, 1}, \dots, \alpha_{1, k_1}), \dots, (\alpha_{n, 1}, \dots, \alpha_{n, k_n})). \]
+
+  The \textbf{Little $ 2 $-disks} operad $ D $ has 
+  \[ D(n) = \{ \text{set of non-overlapping disks contained within the unit disk} \}, \]
+  with composition being geometric "substitution".
+I.e.: scale and move a unit disk and its contained disks to match one of the smaller disks, and replace the smaller disk with the transformed contents of our original unit disk.
+See also: \href{https://upload.wikimedia.org/wikipedia/en/thumb/0/0b/Composition_in_the_little_discs_operad.svg/1920px-Composition_in_the_little_discs_operad.svg.png}{this image that explains a lot}
+
+  Given sets $ X(n) $ for all $ n \in \mathbb N $, the \textbf{free operad} $ X^\prime $ on these is defined exactly by $ X(n) \subseteq X^\prime(n) $, $ 1 \in X^\prime(1) $ and for all $ m, n_1, \dots, n_m \in \mathbb N $ and $ f \in X(m) $ and $ f_i \in X^\prime(n_i) $, we have $ f \circ (f_1, \dots, f_m) \in X^\prime(n_1 + \dots + n_m) $.
+
+  \subsection{\texorpdfstring{$ T $}{T}-operads}
+  \subsubsection{Definitions}
+  A category is \textbf{cartesian} if it has all pullbacks.
+A functor is cartesian if it preserves pullbacks.
+A natural transformation $ \alpha: S \to T $ is cartesian if for all $ f: A \to B $, the naturality diagram
+  \begin{center}
+    \begin{tikzcd}
+      SA \arrow[r, "S f"] \arrow[d, "\alpha_A"] & SB \arrow[d, "\alpha_B"]\\
+      TA \arrow[r, "T f"] & TB
+    \end{tikzcd}
+  \end{center}
+  is a pullback.
+A monad $ (T, \mu, \eta) $ on a category $ \mathcal E $ is cartesian if the category $ \mathcal E $, the functor $ T $ and the natural transformations $ \mu $ and $ \eta $ are cartesian.
+
+  We can represent (the morphism structure of) an ordinary category using diagrams $ C_0 \xleftarrow{\text{domain}} C_1 \xrightarrow{\text{codomain}} C_0 $, $ C_1 \times_{C_0} C_1 \xrightarrow{\text{composition}} C_1 $ and $ C_0 \xrightarrow{\text{id}} C_1 $ together with some axioms.
+For a multicategory, we need to slightly modify this, using a functor $ T: \mathrm{Set} \to \mathrm{Set} $, $ A \mapsto \bigsqcup A^n $, to $ T C_0 \xleftarrow{d} C_1 \xrightarrow{c} C_0 $ and $ C_1 \times_{T C_0} T C_1 \xrightarrow{\circ} C_1 $.
+
+  Given a cartesian monad $ (T, \mu, \eta) $ on a category $ \mathcal E $, we can define a bicategory $ \mathcal E_{(T)} $, with the class of $ 0 $-cells being $ \mathcal E_0 $, the $ 1 $-cells $ E \to E^\prime $ being diagrams $ TE \xleftarrow{d} M \xrightarrow{c} E^\prime $, $ 2 $-cells $ (M, d, c) \to (N, q, p) $ are maps $ M \to N $ such that the diagram with $ E, E^\prime, M, N $ commutes.
+The composite of $ 1 $-cells $ TE \xleftarrow{d} M \xrightarrow{c} E^\prime $ and $ TE \xleftarrow{d^\prime} M^\prime \xrightarrow{c^\prime} E^{\prime\prime} $ is given by
+  \[ T E \xleftarrow{\mu_E} T^2 E \xleftarrow{T d} TM \xleftarrow{} T M \times_{T E^\prime} M^\prime \xrightarrow{} M^\prime \xrightarrow{c^\prime} E^{\prime\prime} \]
+  in which the coproduct in the middle is formed using $ T c $ and $ d $.
+  We can define a $ T $-multicategory to be a monad on $ \mathcal E_{(T)} $.
+Equivalently, we can define it as an object $ C_0 \in \mathcal E $, together with a diagram $ t: T C_0 \xleftarrow{d} C_1 \xrightarrow{c} C_0 $ and maps $ C_1 \circ C_1 := T C_1 \times_{T C_0} C_1 \xrightarrow{\circ} C_1 $ and $ C_0 \xrightarrow{id} C_1 $ satisfying associativity and identity axioms.
+
+  A $ T $-operad is a $ T $-multicategory such that $ C_0 $ is the terminal object of $ \mathcal E $.
+Equivalently, it is an object over $ T 1 $, (so we have a morphism $ P \to T 1 $), together with maps $ P \times_{T 1} T P \to P $ and $ 1 \xrightarrow{id} P $, both over $ T 1 $, satisfying associativity and identity axioms.
+
+  \subsubsection{Examples}
+  For $ T $ the identity monad on $ \mathrm{Set} $, a $ T $-operad is exactly a monoid (or an operad with only unary functions) (since there is always a unique map to $ \{ 1 \} $).
+
+  If $ \mathcal E $ is $ \mathrm{Set} $, the terminal object $ 1 $ will always be $ \{ 1 \} $.
+
+  For the free monoid monad $ T A = \bigsqcup A^n $, the $ T $-operads are precisely the operads that we defined before.
+
+  For the monad $ T A = 1 + A $, we can view $ T A $ as a subset of the free monoid on $ A $, and this gives an operad with $ 0 $-ary and $ 1 $-ary functions.
+
+  \bibliographystyle{alpha}
+  \bibliography{citations}
+
 \end{document}

### 2023-03-01 summary.tex
Add cartesian operads

@@
 \usepackage{tikz-cd}
+
+\newcommand{\Catc}[1]{\mathcal{#1}}
+\newcommand{\BB}{\Catc{B}}
+\newcommand{\CC}{\Catc{C}}
+\newcommand{\EE}{\Catc{E}}
+\newcommand{\Catb}[1]{\mathbf{#1}}
+\newcommand{\SET}{\Catb{Set}}
+\newcommand{\FIN}{\Catb{Fin}}
+\newcommand{\Ob}[1]{{#1}_0}
+\newcommand{\Hom}[3]{{#1}(#2,#3)}
+\newcommand{\op}[1]{\ensuremath{{#1}^\text{op}}}
 
@@
   A univalent category is a category in which the univalence axiom holds.
-I.e., a category $ \mathcal C $ in which, for all $ A, B \in \mathcal C_0 $, the canonical map $ (A =_{\mathcal C} B) \to (A \cong B) $ is an equivalence.
+I.e., a category $ \mathcal C $ in which, for all $ A, B \in \Ob \CC $, the canonical map $ (A =_{\mathcal C} B) \to (A \cong B) $ is an equivalence.
 
@@
 
-  A category with only one object $ \star $ is equivalent to a monoid (with elements being the set $ \mathcal C(\star, \star) $).
+  A category with only one object $ \star $ is equivalent to a monoid (with elements being the set $ \Hom{\CC}{\star}{\star} $).
 A $ 2 $-category with only one $ 0 $-cell is the same thing as a monoidal category (objects: the $ 1 $-cells.
@@
   A \textbf{monoid} is a set with a multiplication and a unit.
-A \textbf{monad} on a category $ \mathcal A $ is a functor $ \mathcal A \to \mathcal A $, together with natural transformations $ \mu : T \circ T \to T $ (satisfying associativity) and $ \eta : 1_{\mathcal A} \to T $ (acting as a two-sided unit).
+A \textbf{monad} on a category $ \CC $ is a functor $ T: \CC \to \CC $, together with natural transformations $ \mu : T \circ T \to T $ (satisfying associativity) and $ \eta : 1_{\mathcal A} \to T $ (acting as a two-sided unit).
 
@@
 
-  Given a category $ \mathcal E $ and an object $ E \in \mathcal E_0 $, the \textbf{slice category} $ \mathcal E / E $ with objects being the maps $ D \xrightarrow{p} E $ and morphisms being commutative triangles.
+  Given a category $ \mathcal E $ and an object $ E \in \Ob \EE $, the \textbf{slice category} $ \mathcal E / E $ with objects being the maps $ D \xrightarrow{p} E $ and morphisms being commutative triangles.
 
@@
 
-  For $ C $ a multicategory, a \textbf{$ C $-algebra} is a map from $ C $ into the multicategory $ \mathbf{Set} $ (with objects $ \mathrm{Set}_0 $ and maps $ \mathrm{Set}(a_1, \dots, a_n; a) = \mathrm{Set}(a_1 \times \dots \times a_n ; a) $).
+  For $ C $ a multicategory, a \textbf{$ C $-algebra} is a map from $ C $ into the multicategory $ \mathbf{Set} $ (with objects $ \SET_0 $ and maps $ \SET(a_1, \dots, a_n; a) = \SET(a_1 \times \dots \times a_n ; a) $).
 I.e., for each $ a \in C_0 $, a set $ X(a) $, and for each map $ \theta: a_1, \dots, a_n \to a $, a function $ X(\theta): X(a_1) \times X(a_n) \to X(a) $.
@@
 
-  Given a monad on $ \mathrm{Set} $, we get a natural operad structure $ T(n)_{n \in \mathbb N} $, with $ T(n) $ the set of words in $ n $ variables and composition given by `substitution'.
+  Given a monad on $ \SET $, we get a natural operad structure $ T(n)_{n \in \mathbb N} $, with $ T(n) $ the set of words in $ n $ variables and composition given by `substitution'.
 
@@
   We can represent (the morphism structure of) an ordinary category using diagrams $ C_0 \xleftarrow{\text{domain}} C_1 \xrightarrow{\text{codomain}} C_0 $, $ C_1 \times_{C_0} C_1 \xrightarrow{\text{composition}} C_1 $ and $ C_0 \xrightarrow{\text{id}} C_1 $ together with some axioms.
-For a multicategory, we need to slightly modify this, using a functor $ T: \mathrm{Set} \to \mathrm{Set} $, $ A \mapsto \bigsqcup A^n $, to $ T C_0 \xleftarrow{d} C_1 \xrightarrow{c} C_0 $ and $ C_1 \times_{T C_0} T C_1 \xrightarrow{\circ} C_1 $.
+For a multicategory, we need to slightly modify this, using a functor $ T: \SET \to \SET $, $ A \mapsto \bigsqcup A^n $, to $ T C_0 \xleftarrow{d} C_1 \xrightarrow{c} C_0 $ and $ C_1 \times_{T C_0} T C_1 \xrightarrow{\circ} C_1 $.
 
@@
   \subsubsection{Examples}
-  For $ T $ the identity monad on $ \mathrm{Set} $, a $ T $-operad is exactly a monoid (or an operad with only unary functions) (since there is always a unique map to $ \{ 1 \} $).
+  For $ T $ the identity monad on $ \SET $, a $ T $-operad is exactly a monoid (or an operad with only unary functions) (since there is always a unique map to $ \{ 1 \} $).
 
-  If $ \mathcal E $ is $ \mathrm{Set} $, the terminal object $ 1 $ will always be $ \{ 1 \} $.
+  If $ \mathcal E $ is $ \SET $, the terminal object $ 1 $ will always be $ \{ 1 \} $.
 
@@
   For the monad $ T A = 1 + A $, we can view $ T A $ as a subset of the free monoid on $ A $, and this gives an operad with $ 0 $-ary and $ 1 $-ary functions.
+The $ 1 $-ary arrows form a monoid, and the $ 0 $-ary arrows are a set, with an action of the monoid.
+
+  \subsection{Cartesian Operads}
+  \subsubsection{Theory}
+  Using \href{https://ncatlab.org/toddtrimble/published/Towards+a+doctrine+of+operads}{Towards a doctrine of operads}.
+
+  NLab uses notation: $ \FIN $ for what we would call a standard skeleton of finite sets (i.e.
+the category of finite sets $ \{ 0, \dots, n - 1 \} $ and maps between them).
+$ A^B $ denotes all morphisms/functors $ B \to A $.
+I.e., the class of functors $ \FIN \to \SET $ is denoted $ \SET^\FIN $.
+
+  Take $ I = \Hom{\FIN}{1}{-}: \SET^\FIN = \FIN \to \SET $.
+
+  Let $ [\SET^\FIN, \SET^\FIN] $ be the category of finite-product-preserving, cocontinuous endofunctors on $ \SET^\FIN $.
+The map $ \mathop{Ev}_I: [\SET^\FIN, \SET^\FIN] \to \SET^\FIN $, given by $ F \mapsto F(I) $ is an equivalence.
+$ [\SET^\FIN, \SET^\FIN] $ has a monoidal product $ \odot $ given by endofunctor composition, and we can transfer this to $ \SET^\FIN $.
+
+  Concretely, we have $ F \odot G = \int^{n \in \FIN} F(n) G^n $.
+
+  \subsubsection{Cartesian operads}
+  A \textbf{cartesian operad} is a monoid in this monoidal category $ (\SET^{\FIN}, \odot, I) $.
+I.e., it is a triple $ (M, \mu, \eta) $, with $ M \in \SET^\FIN $, $ \mu: M \odot M \to M $ and $ \eta: I \to M $.
+
+  More concretely, this is a functor $ M : \FIN \to \SET $, together with maps
+  \[ m_{n, k}: M(n) \times M(k)^n \to M(k), \]
+  natural in $ k $ and dinatural in $ n $, and an element $ e \in M(1) $.
+
+  Dinaturality in $ n $ means the following. Fix $ k \in \FIN $. We have the functors $ \op \FIN \times \FIN \to \SET $ given by 
+  \[ F: (n, n^\prime) \mapsto M(n^\prime) \times M(k)^{n} \quad \text{and} \quad G: (n, n^\prime) \mapsto M(k). \]
+  For all $ n \in \Ob \FIN $, we have a morphism
+  \[ \bullet: F(n, n) = M(n) \times M(k)^n \to M(k) = G(n, n). \]
+  Naturality means that for all $ a: n \to n^\prime $,
+  \[ G(n, a) \circ \bullet \circ F(a, n) = F(a, n^\prime) \circ \bullet \circ G(n^\prime, a). \]
+  i.e., for all $ f \in M(n) $, $ g_1, \dots, g_{n^\prime} \in M(k) $,
+  \[ f \bullet (g_{a(1)}, \dots, g_{a(n)}) = M(a)(f) \bullet (g_1, \dots, g_{n^\prime}). \]
+
+  Now, if we have, in $ \FIN $, a decomposition $ k = k_1 + \dots + k_n $, and we have inclusion maps $ i_j: k_j \hookrightarrow k $, then we have
+  \[ M(n) \times M(k_1) \times \dots \times M(k_n) \xrightarrow{1 \times M(i_1) \times \dots \times M(i_n)} M(n) \times M(k)^n \xrightarrow{m_{n, k}} M(k), \]
+  which gives an operad structure.
+
+  \subsubsection{Clones}
+  In other parts of mathematics, a cartesian operad is called a \textbf{clone}.
+An abstract clone consists of sets $ M(n) $ for all $ n \in \mathbb N $, for all $ n, k \in \mathbb N $ a function $ \bullet: M(n) \times M(k)^n \to M(k) $ and for each $ 1 \leq i \leq n \in \mathbb N $, an element $ \pi_{i, n} \in M(n) $ such that for $ f \in M(i) $, $ g_1, \dots, g_i \in M(j) $ and $ h_1, \dots, h_j \in M(k) $,
+  \[ f \bullet (g_1 \bullet (h_1, \dots, h_j), \dots, g_i \bullet (h_1 \dots, h_j)) = (f \bullet (g_1, \dots, g_i)) \bullet (h_1, \dots, h_j), \]
+  for $ f_1, \dots, f_n \in M(k) $,
+  \[ \pi_{i, n} \bullet (f_1, \dots, f_n) = f_i, \]
+  and for $ f \in M(n) $,
+  \[ f \bullet (\pi_{1, n}, \dots, \pi_{n, n}) = f. \]
+  (It is claimed that this automatically gives naturality)
+
+  Naturality means for all $ a \in \Hom{\FIN}{n}{n^\prime} $, for all $ f \in M(n) $, $ g_1, \dots, g_{n^\prime} \in M(k) $,
+  \[ f \bullet (g_{a(1)}, \dots, g_{a(n)}) = (f \bullet (\pi_{a(1), n^\prime}, \dots, \pi_{a(n), n^\prime})) \bullet (g_1, \dots, g_{n^\prime}). \]
+  However, by associativity and since $ \pi_{i, n} \bullet (f_1, \dots, f_n) $, we have
+  \begin{align*}
+    & (f \bullet (\pi_{a(1), n^\prime}, \dots, \pi_{a(n), n^\prime})) \bullet (g_1, \dots, g_{n^\prime})\\
+    &= (f \bullet (\pi_{a(1), n^\prime} \bullet (g_1, \dots, g_{n^\prime}), \dots, \pi_{a(n), n^\prime} \bullet (g_1, \dots, g_{n^\prime})))\\
+    &= f \bullet (g_{a(1)}, \dots, g_{a(n)}).
+  \end{align*}
+
+  Naturality in $ k $ is as follows. Fix $ n \in \Ob \FIN $. We have functors $ F, G: \FIN \to \SET $, given by
+  \[ F: k \mapsto M(n) \times M(k)^n \quad \text{and} \quad G: k \mapsto M(k). \]
+  For $ a: k \to k^\prime $, we must have
+  \[ G(a) \circ \bullet = \bullet \circ F(a). \]
+  That is, for all $ f \in M(n) $, $ g_1, \dots, g_n \in M(k) $,
+  \[ M(a) (f \bullet (g_1, \dots, g_n)) = f \bullet (M(a)(g_1), \dots, M(a)(g_n)). \]
+  Now, $ M(a) $ is given by 
+  \[ M(a)(f) = f \bullet (\pi_{a(1), k^\prime}, \dots, \pi_{a(k), k^\prime}). \]
+  Therefore, we have
+  \begin{align*}
+    & M(a) (f \bullet (g_1, \dots, g_n))\\
+    &= (f \bullet (g_1, \dots, g_n)) \bullet (\pi_{a(1), k^\prime}, \dots, \pi_{a(k), k^\prime})\\
+    &= f \bullet (g_1 \bullet (\pi_{a(1), k^\prime}, \dots, \pi_{a(k), k^\prime}), \dots, g_n \bullet (\pi_{a(1), k^\prime}, \dots, \pi_{a(k), k^\prime}))\\
+    &= f \bullet (M(a)(g_1), \dots, M(a)(g_n)).
+  \end{align*}
+  So the associativity and projection axioms ensure naturality.
 

### 2023-03-07 summary.tex
Write about adjunctions and about (cartesian) operads

@@
-\documentclass{amsart}
+\documentclass{amsbook}
 
@@
 \newcommand{\CC}{\Catc{C}}
+\newcommand{\DD}{\Catc{D}}
 \newcommand{\EE}{\Catc{E}}
@@
 
-  \section{Week 08}
-  \subsection{Univalent Categories}
+  \chapter{Week 08}
+  \section{Univalent Categories}
   A univalent category is a category in which the univalence axiom holds.
@@
 
-  \subsection{Categories}
+  \section{Categories}
   An \textbf{$ n $-category} is a category with $ 0 $-cells (objects), $ 1 $-cells (morphisms), $ 2 $-cells (morphisms between morphisms), up to $ n $-cells and various compositions: $ A \to B \to C $.
@@
 
-  \subsection{Operads}
-  \subsubsection{Definitions}
+  \section{Operads}
+  \subsection{Definitions}
   An \textbf{operad} is a multicategory with only one object.
@@
 
-  \subsubsection{Examples}
+  \subsection{Examples}
   For any vector space $ V $, there is an operad with $ P(k) = V^{\otimes k} \to V $.
@@
 
-  \subsection{\texorpdfstring{$ T $}{T}-operads}
-  \subsubsection{Definitions}
+  \section{\texorpdfstring{$ T $}{T}-operads}
+  \subsection{Definitions}
   A category is \textbf{cartesian} if it has all pullbacks.
@@
 
-  \subsubsection{Examples}
+  \subsection{Examples}
   For $ T $ the identity monad on $ \SET $, a $ T $-operad is exactly a monoid (or an operad with only unary functions) (since there is always a unique map to $ \{ 1 \} $).
@@
 
-  \subsection{Cartesian Operads}
-  \subsubsection{Theory}
+  \section{Cartesian Operads}
+  \subsection{Theory}
   Using \href{https://ncatlab.org/toddtrimble/published/Towards+a+doctrine+of+operads}{Towards a doctrine of operads}.
@@
 
-  \subsubsection{Cartesian operads}
+  \subsection{Cartesian operads}
   A \textbf{cartesian operad} is a monoid in this monoidal category $ (\SET^{\FIN}, \odot, I) $.
@@
 
-  \subsubsection{Clones}
+  \subsection{Clones}
   In other parts of mathematics, a cartesian operad is called a \textbf{clone}.
@@
 
+  \chapter{Week 09}
+
+  \section{Adjunctions}
+  For three sets $ X, Y, Z $, we have a bijection
+  \[ \Hom \SET {X \times Y} Z \cong \Hom \SET X {Y \to Z} \]
+  that is natural in $ X $ and $ Z $. This is an example of a general notion:
+
+  For functors $ F: \CC \to \DD $ and $ G: \DD \to \CC $, $ F $ is a \textbf{left adjoint} for $ G $ if there is an isomorphism $ \Hom \CC {F X} Y \cong \Hom \DD X {G Y} $ that is dinatural in $ X $ and $ Y $.
+
+  \subsection{Examples}
+  A special case is for $ G: \CC \to \SET $ the forgetful functor: if we have a left adjoint $ F: \SET \to \CC $ to $ G $, we call $ F(X) $ the \textbf{free $ \CC $} of $ X $ (for example: free group, free monoid, free category, etc.).
+That means that $ \Hom \CC {F(X)} Y \cong \Hom \SET X {G(Y)} $, or in other words:
+
+  Adjunctions can be composed: If $ F $ and $ G $ both forget part of the structure of an object, then we can construct the free object `piecewise' using the composition of the left adjoints.
+
+  Let $ G: \Catb{Group} \to \SET $ be the forgetful functor and $ F: \SET \to \Catb{Group} $ be the free group functor.
+For any set $ S $, we have an inclusion $ i: S \hookrightarrow F S $.
+Now, given any group $ Y $ and any morphism of sets from $ S $ to $ Y $ (formally: $ f \in \Hom \SET S {G Y} $).
+Then the fact that $ \Hom \SET {FS} Y \cong \Hom \SET S {G Y} $ is expressed in the fact that $ f $ factors uniquely as $ g \circ i $.
+  \begin{center}
+    \begin{tikzcd}
+      S \arrow[r, "i"] \arrow[rd, "f"] & F(S) \arrow[d, "\exists! g"]\\
+      & Y
+    \end{tikzcd}
+  \end{center}
+
+  In topology, the forgetful functor from topological spaces to sets has a left adjoint that turns a set $ S $ into a space $ F(S) $ with the discrete topology, since it has the smallest topology on $ S $ that still can factor all morphisms $ S \to [0, 1] $ for example.
+
+  In algebra, the inclusion functor from the category of monoids (sets with an associative operation and a unit) to the category of semigroups (sets with an associative operation) has a left adjoint that sends the semigroup $ S $ to the monoid $ S \sqcup \{ \star \} $ and gives it operations such that $ \star $ is the unit.
+
+  In algebra, the inclusion functor from the category of rings to the category of rngs (rings but without an identity) has a left adjoint that sends the rng $ R $ to $ R \times \mathbb Z $ and defines $ (r, x) (s, y) = (rs + xs + ry, xy) $.
+
+  For $ \Catb{Dom_m} $ the category of integral domains with injective morphisms.
+Then the forgetful functor $ \Catb{Fields} \to \Catb{Dom_m} $ has a left adjoint that sends a domain to its field of fractions.
+
+  For $ \rho: R \to S $ a morphism of rings, we can view every $ S $-module as an $ R $-module: we have a functor $ S\Catb{-Mod} \to R\Catb{-Mod} $.
+This has a left adjoint, $ M \mapsto M \otimes_R S $.
+
+  \section{Operads and cartesian operads}
+  \subsection{Recap operads and cartesian operads}
+  In this section, we will represent a cartesian operad $ C $ by a clone:
+  \begin{itemize}
+    \item For all $ n \in \mathbb N $, a set $ C(n) $;
+    \item For all $ 1 \leq i \leq n $ projections $ \pi_{n, i} \in P(n) $;
+    \item For all $ m, n $, a function $ \rho_{m, n}: C(m) \times C(n)^m \to C(n) $.
+  \end{itemize}
+  such that
+  \begin{itemize}
+    \item For $ f \in C(l) $, $ g_1, \dots, g_l \in C(m) $ and $ h_1, \dots, h_m \in C(n) $,
+      \[ \rho(f, (\rho(g_1, (h_1, \dots, h_m)), \dots, \rho(g_l, (h_1, \dots, h_m)))) = \rho(\rho(f, (g_1, \dots, g_l)), (h_1, \dots, h_l)). \]
+    \item for $ f_1, \dots, f_n \in M(n) $ and $ 1 \leq i \leq n $, $ \rho(\pi_{i, n}, (f_1, \dots, f_n)) = f_i $;
+    \item For $ f \in M(n) $, $ \rho(f, (\pi_{1, n}, \dots, \pi_{n, n})) = f $.
+  \end{itemize}
+  and a morphism of cartesian operads $ \varphi: C \to C^\prime $ by componentwise functions $ \varphi_n: C(n) \to C^\prime(n) $ such that
+  \begin{itemize}
+    \item For all $ 1 \leq i \leq n $, $ \varphi_n(\pi_{n, i}) = \pi^\prime_{n, i} $;
+    \item For all $ m, n $, $ f \in C(m) $, $ g_1, \dots, g_m \in C(n) $
+      \[ \rho(\varphi(f), (\varphi(g_1), \dots, \varphi(g_m))) = \varphi(\rho(f, (g_1, \dots, g_m))). \]
+  \end{itemize}
+
+  We will represent an operad $ P $ by
+  \begin{itemize}
+    \item For all $ n \in \mathbb N $, a set $ P(n) $;
+    \item An element $ e \in P(1) $;
+    \item For all $ m, n_1, \dots, n_m \in \mathbb N $, a function
+      \[ \gamma_{m, n_1, \dots, n_m}: C(m) \times C(n_1) \times \dots \times C(n_m) \to C(n_1 + \dots + n_m) \]
+      (we will usually just call this $ \gamma $).
+  \end{itemize}
+  such that
+  \begin{itemize}
+    \item For all $ f \in P(n) $,
+      \[ \gamma(f, (1, \dots, 1)) = f = \gamma(1, f); \]
+    \item For all $ f \in P(l) $, $ g_1 \in P(m_1) $, \dots, $ g_l \in P(m_l) $ and all $ h_{1, 1} \in P(n_{1, 1}) $, \dots, $ h_{l, m_l} \in P(n_{l, m_l}) $,
+      \[ f \circ(g_1 \circ(h_{1, 1}, \dots, h_{1, m_1}), \dots, g_l \circ (h_{l, 1}, \dots, h_{l, m_l})) = (f \circ (g_1, \dots, g_l)) \circ (h_{1, 1}, \dots, h_{l, m_l}). \]
+  \end{itemize}
+  and a morphism of operads $ \psi: P \to P^\prime $ by componentwise functions $ \psi_n: P(n) \to P^\prime(n) $ such that
+  \begin{itemize}
+    \item $ \psi_1(e) = e^\prime $;
+    \item For all $ f \in P(m) $, $ g_1 \in P(n_1) $, \dots, $ g_m \in P(n_m) $,
+      \[ \gamma(\psi(f), (\psi(g_1), \dots, \psi(g_m)))  \psi(\gamma(f, (g_1, \dots, g_m))). \]
+  \end{itemize}
+
+  \subsection{Free operad?}
+  Now, for all $ 1 \leq i \leq m $, we have an injection $ j_i: C(n_i) \to C(n_1 + \dots + n_m) $.
+Intuitively, it maps terms in a context with $ n_i $ variables to terms in a context with $ n_1 + \dots + n_m $ variables, by mapping variable $ 1 \leq k \leq n_1 $ to variable $ n_1 + \dots + n_{i - 1} + k $.
+This gives a morphism
+  \[ \gamma: C(m) \times C(n_1) \times \dots \times C(n_m) \xrightarrow{\mathop{id} \times j_1 \times \dots \times j_m} C(m) \times C(n_1 + \dots + n_m)^m \xrightarrow{\rho} C(n_1 + \dots + n_m), \]
+  which gives an operad structure on the same sets. This gives a functor from cartesian operads to operads.
+
+  Then, the question arises whether this functor has a left adjoint.
+
+  \textbf{Still open}
+
   \bibliographystyle{alpha}

### 2023-03-09 summary.tex
Add a summary ofthe paper

@@
 
+  \section{Cartesian multicategory}
+  Yet another way to think of a cartesian operad is as a one-object cartesian multicategory.
+A \textbf{cartesian multicategory} is a multicategory with an $ S_n $-action on the hom-sets (in other words: we can permute the arguments of the morphsims) and duplication/diagonal/contraction operations
+  \[ \mathrm{Hom}(c_1, \dots, c_k, c_k, \dots, c_n; c) \to \mathrm{Hom}(c_1, \dots, c_k, \dots, c_n; c) \]
+  and deletion/projection/weakening operations
+  \[ \mathrm{Hom}(c_1, \dots, c_k, \dots, c_n; c) \to \mathrm{Hom}(c_1, \dots, c_{k-1}, c_{k+1}, \dots, c_n; c) \]
+
+  \section{The paper}
+  A summary of the results in the paper:
+  \begin{enumerate}
+    \item A definition of the category of algebraic theories (clones).
+    \item A definition of the category of $ T $-algebras (for $ T $ an algebraic theory), the pullback of an algebra, the free algebra, and some properties of these.
+    \item A definition of a presheaf (like an algebra, but with a right action instead of a left one) and some properties of this.
+    \item A sidenote about the more classical approach to algebra.
+    \item A definition for a $ \lambda $-theory and some properties of its constituents.
+    \item A definition for an interpretation of the $ \lambda $-calculus in a $ \lambda $-theory, and some properties.
+    \item The notion that the algebraic theory $ \Lambda $ of all terms of the $ \lambda $-calculus is the initial $ \lambda $-theory.
+    \item The notion that we can add constants to a theory to make sure that it `has enough points'.
+    \item A (new) proof that any $ \lambda $-theory is isomorphic to the endomorphism $ \lambda $-theory of some object.
+    \item A section that concludes an equivalence between the presheaf categories of a Lawvere theory, a $ \lambda $-theory and the category of retracts.
+    \item The definition of $ \Lambda $-algebra and a couple of its properties. In particular, a functor from $ \lambda $-theories to $ \Lambda $-algebras.
+    \item An equivalene between $ \Lambda $-algebras and their presheaves.
+    \item A characterisation of the function space $ U^U $ for $ U \in PA $ the universal.
+    \item An equivalence of categories between the category of $ \Lambda $-algebras and $ \lambda $-theories.
+    \item The Fundamental Theorem of the $ \lambda $-calculus: there is an adjoint equivalence between $ \lambda $-theories and $ \Lambda $-algebras.
+    \item A remark that this is much harder without the category theoretic framework.
+  \end{enumerate}
+
   \bibliographystyle{alpha}

### 2023-03-20 summary.tex
Add a section about the paper "A formalization of Operads in Coq"

@@
 
+  \chapter{Week 11}
+
+  \section{A Formalization of Operads in Coq}
+  A paper was uploaded to the arXiv (see \cite{arxiv-operads}).
+Unfortunately, this paper did not contain any code, which makes it harder to compare their technique to mine.
+The paper is about the formalization of a symmetric multicategory (kind of.
+They do not require $ (\tau \sigma) f = \tau (\sigma f) $ for $ \sigma, \tau \in S_n $ and $ f \in \Hom{\CC}{a_1}{\dots, a_n;a} $)
+
+  The operad data presented in this paper is a bit different (but equivalent) from the data that I have seen so far. Notably: the composition is on one element at a time:
+  \[ \Hom{\CC}{a_1}{\dots, a_n;a} \times \Hom{\CC}{b_1}{\dots, b_m; a_i} \to \Hom{\CC}{a_1}{\dots a_{i-1}, b_1, \dots, b_m, a_{i+1}, \dots, a_n; a}, \]
+  in which $ a_1, \dots a_{i-1}, b_1, \dots, b_m, a_{i+1}, \dots, a_n $ is denoted $ \underline{a} \bullet_{i} \underline{b} $.
+
+  I expect the axioms to become a bit more complicated this way.
+For example, now there are two associativity axioms, and even to state them we need a proof that $ (\underline c \bullet_i \underline a) \bullet_{l - 1 + j} \underline b = (\underline c \bullet_j \underline b) \bullet_i \underline a $.
+
+  Also, their signature of $ \ensuremath{Hom} $ is $ \TYPE \to \mathbf{List}\ \TYPE \to \TYPE $.
+The advantage of using $ \mathbf{List}\ \TYPE $ instead of $ \sum_{n \in \mathbb N} (\mathtt{stn}\ n \to \TYPE) $ is that it sounds simpler.
+The disadvantage is that, for example, to say something about $ c_i $, one needs a function to fetch the $ i $th element of $ \underline c $ and a proof that $ i $ is less than the length of $ \underline{c} $.
+
+  To get elements in the right space, they add a lot of typecasting functions.
+For example, the function $ \mathcal C_{assoc}: \mathcal O((\underline c \bullet_i \underline a) \bullet_{l - 1 + j} \underline b; d) \to \mathcal O((\underline c \bullet_j \underline b) \bullet_i \underline a; d) $ I believe we call such a function a `transport function`.
+The paper claims that if $ A = B $, a typecast function will be the identity.
+The way that it is currently stated, it is not compatible with univalence, I believe.
+
+  I feel like the paper lacks a section explaining the choices that were made and evaluating their results.
+
   \bibliographystyle{alpha}

### 2023-03-20 summary.tex
Start a chapter about the things I would have liked to know when I started with coq

@@
 \newcommand{\SET}{\Catb{Set}}
+\newcommand{\TYPE}{\Catb{Type}}
 \newcommand{\FIN}{\Catb{Fin}}
@@
   \maketitle
+
+  \chapter{Lessons about coq and unimath}
+  When writing coq code, make sure you understand why a proof should work, instead of blindly unfolding and applying Lemmas. That improves the overall quality of the proofs.
+
+  A proof closed with \texttt{Qed} is opaque, whereas a proof that closes with \texttt{Defined} is transparent (i.e. is remembered can be unfolded). Which one is the right one requires some thought.
+
+  Only use \texttt{destruct} in opaque proofs.
+
+  Path induction (or induction on proofs of equality) helps a lot when proving something about a \texttt{transportf}.
+
+  \section{Default API for any \texttt{object}}
+  \begin{itemize}
+    \item \texttt{object\_data}: A definition for the data of the object;
+    \item \texttt{make\_object\_data}: A function to compose the object data out of its parts;
+    \item (Coercions from \texttt{object\_data} to some of its parts;)
+    \item (Explicit functions to access the constituents;)
+    \item \texttt{is\_object}: A definition for the properties of the object;
+    \item \texttt{make\_is\_object}: A function to compose the properties part of the object;
+    \item \texttt{make\_object}: A function to make the object out of its data and property components;
+    \item (A coercion from the object to its data;)
+    \item \texttt{object\_eq}: A lemma about sufficient (and necessary) conditions for two terms of type \texttt{object} to be equal (usually some conditions on the constituents of \texttt{object\_data});
+  \end{itemize}
+
+  \section{Cleaning up code}
+  It is okay to simplify proofs as much as possible. When one wants to step through a proof, they can add \texttt{simpl}s to their own liking.
+
+  \texttt{cbn} is stronger than \texttt{simpl}, so it can be good to try and replace \texttt{cbn}s with \texttt{simpl}s when cleaning up code.
+
+  \section{Things I was not able to find on my own}
+  \texttt{isweq\_iso}
+
+  \texttt{weqdnicoprod}
 

### 2023-03-21 summary.tex
Add one entry to the standard API section

@@
     \item \texttt{object\_data}: A definition for the data of the object;
-    \item \texttt{make\_object\_data}: A function to compose the object data out of its parts;
+    \item \texttt{make\_object\_data}: A function to make the object data out of its parts;
     \item (Coercions from \texttt{object\_data} to some of its parts;)
@@
     \item \texttt{is\_object}: A definition for the properties of the object;
-    \item \texttt{make\_is\_object}: A function to compose the properties part of the object;
+    \item \texttt{make\_is\_object}: A function to make the properties part of the object;
     \item \texttt{make\_object}: A function to make the object out of its data and property components;
     \item (A coercion from the object to its data;)
+    \item A lemma that the properties form a proposition.
     \item \texttt{object\_eq}: A lemma about sufficient (and necessary) conditions for two terms of type \texttt{object} to be equal (usually some conditions on the constituents of \texttt{object\_data});

### 2023-04-19 talks/t01-overview/content.tex
Add two talks, move the summary to a subdirectory

\documentclass{amsart}

\usepackage{stmaryrd}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

\newcommand{\SET}{\ensuremath{SET}}

\begin{document}
  \begin{definition}
    An algebraic theory is a functor $ \mathcal T: F \to \SET $ together with a composition morphism $ \bullet: \mathcal T(m) \times \mathcal T(n)^m \to \mathcal T(n) $ for all $ m, n $ and elements (projections) $ \pi_{n, i} \in \mathcal T(n) $ for all $ 1 \leq i \leq n $. The composition must be associative, unital, compatible with projections and dinatural in $ m $.
  \end{definition}

  This is equivalent to:

  \begin{definition}
    An abstract clone is a function $ C : \mathbb N \to \SET $, together with a composition morphism $ \bullet: C(m) \times C(n)^m \to C(n) $ for all $ m, n $ and elements (projections) $ \pi_{n, i} \in C(n) $ for all $ 1 \leq i \leq n $, such that
    \[ \pi_{n, i} \bullet (f_1, \dots, f_n) = f_i; \]
    \[ f \bullet (\pi_{1, n}, \dots, \pi_{n, n}) = f; \]
    \[ (f \bullet (g_1, \dots, g_m)) \bullet (h_1, \dots, h_n) = f \bullet (g_1 \bullet (h_1, \dots, h_n), \dots, g_m \bullet (h_1, \dots, h_n)). \]
  \end{definition}

  \begin{definition}
    An algebra for an algebraic theory $ \mathcal T $ is a set $ A $ with an associative unital action $ \mathcal T(n) \times A^n \to A $, natural in $ n $.
  \end{definition}

  \begin{definition}
    A $ \lambda $-theory is an algebraic theory $ \mathcal L $ together with retractions $ \mathcal L(n + 1) \triangleleft \mathcal L(n) $ with retraction $ \rho: \mathcal L(n) \to \mathcal L(n + 1) $ and section $ \lambda: \mathcal L(n + 1) \to \mathcal L(n) $ natural in $ n $ and compatible (?) with the actions $ \mathcal L(m) \times \mathcal L(n)^m \to \mathcal L(n) $ and $ \mathcal L(m+1) \times \mathcal L(n)^m \to \mathcal L(n+1) $ (which ``ignores the last variable'').
  \end{definition}

  \begin{definition}
    An algebra for a $ \lambda $-theory $ \mathcal L $ is an algebra $ A $ for the underlying algebraic theory.
  \end{definition}
  For each term $ t(\mathbf x) \in \mathcal L(n) $ and each tuple $ \mathbf a \in A^n $, we get an interpretation $ t(\mathbf a) \in A $.

  Given a $ \lambda $-theory $ \mathcal L $, we can interpret a term $ t $ of the lambda calculus (that has a context $ \Gamma $ of length $ n $) as an element $ \llbracket t \rrbracket \in \mathcal L(n) $.

  \begin{example}
    Take $ T(n) = \{ \star \} $, $ \pi_{n, i} = \star $ and $ \star \bullet \{ \star, \dots, \star \} = \star $.

    This theory is the terminal $ \lambda $-theory.
  \end{example}

  \begin{example}
    The $ \lambda $-calculus $ \Lambda $, in which $ \Lambda(n) $ consists of the terms with $ n $ free variables, $ \pi_{n, i} = \texttt{Var}(i) $ (with De Bruijn indices) and $ \bullet $ is substitution.

    For every theory $ \mathcal T $ the $ \mathcal T(n) $ are algebras, so the $ \Lambda(n) $ are algebras.

    This is a $ \lambda $-theory. According to the paper, it is the initial $ \lambda $-theory.
  \end{example}

  \begin{example}
    We can create abstract clones using algebraic signatures. If we have, for all $ n $, a set of constructors $ \Sigma_n $, and we have a sequence of variables $ x_1, x_2, \dots $. Then we can build the elements iteratively with the rules $ x_i \in T(n) $ if $ i \leq n $, and for $ x_1, \dots, x_m \in T(n) $ and $ \sigma \in \Sigma_m $, $ \sigma(x_1, \dots, x_m) \in T(n) $. Then the $ \pi_{n, i} $ are the $ x_i $, and $ f \bullet (g_1, \dots, g_m) $ substitutes the $ g_i $ for the $ x_i $ in $ f $.

    For example, if we talk about rings, we have $ \Sigma_0 = \{ 0, 1 \} $, $ \Sigma_1 = \{ - \} $ (negation) and $ \Sigma_2 = \{ +, \cdot \} $. Then $ T(n) $ is almost the polynomial ring over $ \mathbb Z $ in $ n $ variables (but not quite, because we distinguish, for example, between $ 0 $, $ 0 + 0 $ and $ x_1 - x_1 $).

    If we have a type $ A $ with for all $ \sigma \in \Sigma_n $, a map $ \llbracket \sigma \rrbracket : A^n \to A $. Then $ A $ is an algebra for this theory.
  \end{example}

  \begin{example}
    Let $ R $ be a ring. Take $ T(n) = R[x_1, \dots, x_n] $ the polynomial ring in $ n $ variables. Take $ \pi_{n, i} = x_i $ and let $ f \bullet (g_1, \dots, g_n) $ substitute the $ g_i $ for the $ x_i $ in $ f $.

    If we have a homomorphism of rings $ R \to S $ and we take $ \mathcal T(n) = R[X_1, \dots, X_n] $, then $ S $ is a $ \mathcal T $-algebra.
  \end{example}

  \begin{example}
    Take $ T(n) = \{ 1, 2, \dots, n \} $, $ \pi_{n, i} = i $ and $ i \bullet (f_1, \dots, f_n) = f_i $.

    Any type $ A $ can be an algebra, with $ i (a_1, \dots, a_n) = a_i $.
  \end{example}

  \begin{example}
    Take a semiring $ R $ with identities $ 0, 1 $ and operations $ +, \cdot $. Take $ T(n) = R^n $, $ \pi_{n, i} = (0, \dots, 0, 1, 0, \dots, 0) $ and take 
    \[ f \bullet (g_1, \dots, g_n) = \begin{pmatrix}
      g_{1, 1} & \dots & g_{n, 1}\\
      \vdots & \ddots & \vdots\\
      g_{1, m} & \dots & g_{n, m}\\
    \end{pmatrix} \begin{pmatrix}
      f_1 \\ \vdots \\ f_n
    \end{pmatrix} := \left( \sum_i f_i \cdot g_{i, 1}, \dots, \sum_i f_i \cdot g_{i, m} \right) \]
    in a matrix multiplication like fashion.

    For example, take $ S $ a set, $ \mathcal T $ a topology on $ S $. Then we can take $ T(n) = \mathcal T^n $, with operations $ \cup $, $ \cap $, and units $ \emptyset $, $ S $. Then we have $ \pi_{n, i} = (\emptyset, \dots, \emptyset, S, \emptyset, \dots, \emptyset) $. For $ U = (U_1, \dots, U_n) $, $ V_i = (V_{i, 1}, \dots, V_{i, m}) $ we have
    \[ U \bullet (V_1, \dots, V_n) = (U_1 \cap V_{1, 1} \cup \dots \cup U_n \cap V_{n, 1}, \dots, U_1 \cap V_{1, m} \cup \dots \cup U_n \cap V_{n, m}). \]

    Or take $ R = \mathbb N $, with operations $ +, \cdot $ and units $ 0, 1 $.
  \end{example}

  Example $ 5 $, and example $ 6 $ with $ R $ a field are special cases of the following:
  \begin{example}
    In any category with finite products, take an object $ X $. Then we can set $ T(n) = (X^n \to X) $. Then $ \pi_{n, i} $ is the $ i $th projection morphism. Also, by the universal property of the product, if we have $ m $ terms of $ (X^n \to X) $, we get a term of $ (X^n \to X^m) $ which we can compose with a term of $ (X^m \to X) $ to get a term of $ (X^n \to X) $.

    If we have a retraction $ r: X \to A $ with section $ s $, then $ A $ is an algebra with $ \varphi \cdot (a_1, \dots, a_n) = r(\varphi(s(a_1), \dots, s(a_n))) $. (?)

    If we have a retraction $ X \to X^X $, the theory that we get is a $ \lambda $-theory.
  \end{example}

  \section{Presheaves}
  Let $ A $ be a $ \Lambda $-algebra.

  \begin{definition}
    We define the monoid $ M_A $ with underlying set $ \{ a \in A \mid \mathbf 1 a = a \} $ and composition $ (a, b) \mapsto a \circ b = \lambda x, a(b x) $ (?).
  \end{definition}

  \begin{definition}
    We define $ PA $ to be the category of presheaves on the category $ M_A $. (I.e. the set of contravariant functors into set). This has `universal object' $ U_A = M_A $ with the obvious right action of $ M_A $.
  \end{definition}

  \begin{lemma}
    For $ U_A $, we have a retraction $ U_A \to U_A^{U_A} $.
  \end{lemma}
  \begin{proof}
    We have $ M_A = \{ a \in A \mid \mathbf 1 a = a \} $. We can identify $ U^U $ with $ \{ a \in A \mid \mathbf 1_2 a = a \} $.

    Composition on the left with $ \mathbf 1 $ gives the retraction.
  \end{proof}

  \begin{definition}
    We take $ \mathcal U_A $ to be the theory of the reflexive universal $ U_A \in P(A) $.
  \end{definition}

  \section{The main theorem}

  We have a map $ \Lambda \to \mathcal L $, which makes $ \mathcal L(0) $ into a $ \Lambda $-algebra.

  Given a $ \Lambda $-algebra $ A $. Take $ \Lambda_A(n) = A + \Lambda(n) $ (which is a coproduct of $ \mathcal T $-algebras, defined using a coend).

  \begin{lemma}
    $ \Lambda_A $ is a $ \lambda $-theory.
  \end{lemma}
  \begin{proof}
    We can identify $ \Lambda_A $ with $ \mathcal U_A $.

    We have a retraction $ U_A \to U_A^{U_A} $. Composition with this gives a retraction $ \mathcal U_A(n) \to \mathcal U_A(n + 1) $. 
  \end{proof}

  \begin{theorem}
    There is an adjoint equivalence $ \mathcal L \mapsto \mathcal L(0) $ and $ A \mapsto \Lambda_A $ between $ \lambda $-theories and  $ \Lambda $-algebras.

    In particular, each $ \lambda $-theory $ \mathcal L $ is isomorphic to the theory of extensions of its initial algebra $ \mathcal L(0) $.
  \end{theorem}

\end{document}

### 2023-04-19 talks/t01-overview/slides.tex
Add two talks, move the summary to a subdirectory

\documentclass[aspectratio=169]{fancyslides} % or beamer/slides

\usepackage{stmaryrd}

% \usetheme{Madrid}

\title{Decorating ``Classical Lambda Calculus in Modern Dress''}

\begin{document}
  \maketitle

  \begin{frame}
    \frametitle{Definitions - Algebraic Theory}

    \begin{definition}
      An algebraic theory consists of
      \begin{itemize}
        \item a functor $ \mathcal T: F \to \mathrm{SET} $,
        \item elements (projections) $ \pi_{n, i} \in \mathcal T(n) $ for all $ 1 \leq i \leq n $,
        \item a composition morphism $ \bullet: \mathcal T(m) \times \mathcal T(n)^m \to \mathcal T(n) $ for all $ m, n $.
      \end{itemize}
      The composition must be
      \begin{itemize}
        \item associative,
        \item unital,
        \item compatible with projections,
        \item dinatural in $ m $.
      \end{itemize}
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{Definitions - Abstract Clone}

    \begin{definition}
      An abstract clone is
      \begin{itemize}
        \item a function $ C : \mathbb N \to \mathrm{SET} $,
        \item a composition morphism $ \bullet: C(m) \times C(n)^m \to C(n) $ for all $ m, n $,
        \item elements (projections) $ \pi_{n, i} \in C(n) $ for all $ 1 \leq i \leq n $.
      \end{itemize}
      The composition must satisfy
      \begin{itemize}
        \item $ \pi_{n, i} \bullet (f_1, \dots, f_n) = f_i $,
        \item $ f \bullet (\pi_{1, n}, \dots, \pi_{n, n}) = f $,
        \item $ (f \bullet (g_1, \dots, g_m)) \bullet (h_1, \dots, h_n) = f \bullet (g_1 \bullet (h_1, \dots, h_n), \dots, g_m \bullet (h_1, \dots, h_n)) $.
      \end{itemize}
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{Definitions - Algebra for an Algebraic Theory}

    \begin{definition}
      An algebra for an algebraic theory $ \mathcal T $ consists of
      \begin{enumerate}
        \item a set $ A $,
        \item an action $ \alpha_n: \mathcal T(n) \times A^n \to A $.
      \end{enumerate}
      Such that $ \alpha_n $ satisfies:
      \begin{enumerate}
        \item naturality in $ n $,
        \item associativity,
        \item unitality.
      \end{enumerate}
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{Definitions - $ \lambda $-theory}

    \begin{definition}
      A $ \lambda $-theory consists of
      \begin{itemize}
        \item an algebraic theory $ \mathcal L $,
        \item a retraction $ \rho: \mathcal L(n) \to \mathcal L(n + 1) $,
        \item a section $ \lambda: \mathcal L(n + 1) \to \mathcal L(n) $.
      \end{itemize}
      Such that
      \begin{itemize}
        \item $ \rho $ and $ \lambda $ are natural in $ n $;
        \item $ \rho $ and $ \lambda $ are compatible (?) with the actions $ \mathcal L(m) \times \mathcal L(n)^m \to \mathcal L(n) $ and $ \mathcal L(m+1) \times \mathcal L(n)^m \to \mathcal L(n+1) $ (which ``ignores the last variable'').
      \end{itemize}
    \end{definition}

    \pause

    \begin{definition}
      An algebra for a $ \lambda $-theory $ \mathcal L $ is an algebra $ A $ for the underlying algebraic theory.
    \end{definition}

    \pause
    \vfill

    For each term $ t(\mathbf x) \in \mathcal L(n) $ and each tuple $ \mathbf a \in A^n $, we get an interpretation $ t(\mathbf a) \in A $.

    \vfill

    Given a $ \lambda $-theory $ \mathcal L $, we can interpret a term $ t $ of the lambda calculus (that has a context $ \Gamma $ of length $ n $) as an element $ \llbracket t \rrbracket \in \mathcal L(n) $.
  \end{frame}

  \begin{frame}
    \frametitle{Examples}

    \begin{definition}
      An abstract clone is
      \begin{itemize}
        \item a function $ C : \mathbb N \to \mathrm{SET} $,
        \item a composition morphism $ \bullet: C(m) \times C(n)^m \to C(n) $ for all $ m, n $,
        \item elements (projections) $ \pi_{n, i} \in C(n) $ for all $ 1 \leq i \leq n $.
      \end{itemize}
      The composition must satisfy
      \begin{itemize}
        \item $ \pi_{n, i} \bullet (f_1, \dots, f_n) = f_i $,
        \item $ f \bullet (\pi_{1, n}, \dots, \pi_{n, n}) = f $,
        \item $ (f \bullet (g_1, \dots, g_m)) \bullet (h_1, \dots, h_n) = f \bullet (g_1 \bullet (h_1, \dots, h_n), \dots, g_m \bullet (h_1, \dots, h_n)) $.
      \end{itemize}
    \end{definition}

    \vfill

    \begin{example}
      Take $ C(n) = \{ \star \} $, $ \pi_{n, i} = \star $ and $ \star \bullet \{ \star, \dots, \star \} = \star $.

      This theory is the terminal $ \lambda $-theory.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Examples}

    The $ \lambda $-calculus $ \Lambda $, in which $ \Lambda(n) $ consists of the terms with $ n $ free variables, $ \pi_{n, i} = \texttt{Var}(i) $ (with De Bruijn indices) and $ \bullet $ is substitution.

    \pause
    \vfill

    For every theory $ \mathcal T $ the $ \mathcal T(n) $ are algebras, so the $ \Lambda(n) $ are algebras.

    \pause
    \vfill

    This is a $ \lambda $-theory. According to the paper, it is the initial $ \lambda $-theory.
  \end{frame}

  \begin{frame}
    \frametitle{Examples}

    More generally, we can create abstract clones using algebraic signatures: Given sets of $ n $-ary constructors $ \Sigma_n $ and a sequence of variables $ x_1, \dots, x_n $, we can build the $ C(n) $ inductively:
    \begin{itemize}
      \item $ x_i : C(n) $ for $ 1 \leq i \leq n $;
      \item $ \sigma(c_1, \dots, c_n) : C(n) $ for $ c_1, \dots, c_n : C(n) $ and $ \sigma: \Sigma_n $.
    \end{itemize}
    Then the $ \pi_{n, i} $ are the $ x_i $, and $ f \bullet (g_1, \dots, g_m) $ substitutes the $ g_i $ for the $ x_i $ in $ f $.

    \pause
    \vfill

    For example, if we talk about rings, we have $ \Sigma_0 = \{ 0, 1 \} $, $ \Sigma_1 = \{ - \} $ (negation) and $ \Sigma_2 = \{ +, \cdot \} $. Then $ C(n) $ is almost the polynomial ring over $ \mathbb Z $ in $ n $ variables (but not quite, because we distinguish, for example, between $ 0 $, $ 0 + 0 $ and $ x_1 - x_1 $).

    \pause
    \vfill

    If we have a type $ A $ and we have for all $ \sigma \in \Sigma_n $, a map $ \llbracket \sigma \rrbracket : A^n \to A $. Then we can make $ A $ into an algebra for this theory.
  \end{frame}

  \begin{frame}
    \frametitle{Examples}
    Let $ R $ be a ring. Take $ T(n) = R[x_1, \dots, x_n] $ the polynomial ring in $ n $ variables. Take $ \pi_{n, i} = x_i $ and let $ f \bullet (g_1, \dots, g_n) $ substitute the $ g_i $ for the $ x_i $ in $ f $.

    \pause
    \vfill

    If we have a homomorphism of rings $ R \to S $ and we take $ \mathcal T(n) = R[X_1, \dots, X_n] $, then $ S $ is a $ \mathcal T $-algebra.
  \end{frame}

  \begin{frame}
    \frametitle{Examples}

    Let $ R $ be a ring. Take $ T(n) = R[x_1, \dots, x_n] $ the polynomial ring in $ n $ variables. Take $ \pi_{n, i} = x_i $ and let $ f \bullet (g_1, \dots, g_n) $ substitute the $ g_i $ for the $ x_i $ in $ f $.

    \pause
    \vfill

    If we have a homomorphism of rings $ R \to S $ and we take $ \mathcal T(n) = R[X_1, \dots, X_n] $, then $ S $ is a $ \mathcal T $-algebra.
  \end{frame}

  \begin{frame}
    \frametitle{Examples}

    Take $ T(n) = \{ 1, 2, \dots, n \} $, $ \pi_{n, i} = i $ and $ i \bullet (f_1, \dots, f_n) = f_i $.

    This is the initial algebraic theory.

    \pause
    \vfill

    Any type $ A $ can be an algebra, with $ i (a_1, \dots, a_n) = a_i $.

    \pause
    \vfill

    I am still pondering whether $ T(n) = \mathbb Z $ could be a $ \lambda $-algebra.
  \end{frame}

  \begin{frame}
    \frametitle{Examples}

    Take a semiring $ R $ with identities $ 0, 1 $ and operations $ +, \cdot $. Take $ T(n) = R^n $, $ \pi_{n, i} = (0, \dots, 0, 1, 0, \dots, 0) $ and take 
    \[ f \bullet (g_1, \dots, g_n) = \begin{pmatrix}
      g_{1, 1} & \dots & g_{n, 1}\\
      \vdots & \ddots & \vdots\\
      g_{1, m} & \dots & g_{n, m}\\
    \end{pmatrix} \begin{pmatrix}
      f_1 \\ \vdots \\ f_n
    \end{pmatrix} := \left( \sum_i f_i \cdot g_{i, 1}, \dots, \sum_i f_i \cdot g_{i, m} \right) \]
    in a matrix multiplication like fashion. ($ T(n) $ is the free $ R $-module on $ n $ generators)

    \pause
    \vfill

    For example, take $ S $ a set, $ \mathcal T $ a topology on $ S $. Then we can take $ T(n) = \mathcal T^n $, with operations $ \cup $, $ \cap $, and units $ \emptyset $, $ S $. Then we have $ \pi_{n, i} = (\emptyset, \dots, \emptyset, S, \emptyset, \dots, \emptyset) $. For $ U = (U_1, \dots, U_n) $, $ V_i = (V_{i, 1}, \dots, V_{i, m}) $ we have
    \[ U \bullet (V_1, \dots, V_n) = (U_1 \cap V_{1, 1} \cup \dots \cup U_n \cap V_{n, 1}, \dots, U_1 \cap V_{1, m} \cup \dots \cup U_n \cap V_{n, m}). \]

    \pause
    \vfill

    Or take $ R = \mathbb N $, with operations $ +, \cdot $ and units $ 0, 1 $.
  \end{frame}

  \begin{frame}
    \frametitle{Examples}

    In any category with finite products, take an object $ X $. Then we can set $ T(n) = (X^n \to X) $. Then $ \pi_{n, i} $ is the $ i $th projection morphism. Also, by the universal property of the product, if we have $ m $ terms of $ (X^n \to X) $, we get a term of $ (X^n \to X^m) $ which we can compose with a term of $ (X^m \to X) $ to get a term of $ (X^n \to X) $.

    \pause
    \vfill

    I believe that if we have a retraction $ r: X \to A $ with section $ s $, then $ A $ is an algebra with $ \varphi \cdot (a_1, \dots, a_n) = r(\varphi(s(a_1), \dots, s(a_n))) $.

    \pause
    \vfill

    If we have a retraction $ X \to X^X $, the theory that we get is a $ \lambda $-theory.
  \end{frame}

  \begin{frame}
    \frametitle{About $ \lambda $-theories}

    Any algebra $ (A, (\alpha_i)_i) $ for a $ \lambda $-theory can be interpreted as a $ \Lambda $-algebra.

    \pause
    \vfill

    Any $ \lambda $-theory $ \mathcal T $ has an element $ e \in \mathcal T(1) $, retractions $ \rho: \mathcal T(n) \to \mathcal T(n + 1) $ and sections $ \sigma: \mathcal T(n + 1) \to \mathcal T(n) $. Define $ app = \rho(e) $. For $ \mathcal T = \Lambda $, we have $ app = xy $.

    \pause

    Then $ \alpha_2(app, (a, -)): A \to A $ gives an interpretation of $ a : A $ as a function.

    \vfill
    \pause

    Take $ \mathbf 1_n = \sigma^{n+1}(\rho^n(e)) $. Note that we can inject this as $ \mathbf 1_n \bullet () $ into any $ \mathcal T(n) $.

    For $ \mathcal T = \Lambda $, this is
    \[ \lambda x, \lambda y_1, \dots, \lambda y_n, x y_1 \dots y_n. \]
    \pause
    For $ n = 1 $, this is
    \[ \lambda x, \lambda y, xy. \]
  \end{frame}

  \begin{frame}
    \frametitle{Preliminaries to the main theorem}

    For a $ \lambda $-theory $ \mathcal L $, $ \mathcal L(0) $ is a $ \mathcal L $-algebra and therefore a $ \Lambda $-algebra.

    \vfill
    \pause

    Given a $ \Lambda $-algebra $ A $. Take $ \Lambda_A(n) = A + \Lambda(n) $, as a coproduct of $ \mathcal T $-algebras, defined using a coend.

    \vfill
    \pause

    \begin{lemma}
      $ \Lambda_A $ is a $ \lambda $-theory.
    \end{lemma}
    \begin{proof}
      We can identify $ \Lambda_A $ with $ \mathcal U_A $.

      We have a retraction $ U_A \to U_A^{U_A} $. Composition with this gives a retraction $ \mathcal U_A(n) \to \mathcal U_A(n + 1) $. 
    \end{proof}
  \end{frame}

  \begin{frame}
    \frametitle{$ \mathcal U_A $}
    Let $ A $ be a $ \Lambda $-algebra.

    \begin{definition}
      We define a monoid $ M_A = (\{ a \in A \mid \mathbf 1 a = a \}, \circ) $ with $ \circ $ being function composition.
    \end{definition}

    \pause
    \vfill

    \begin{definition}
      We define $ P(A) $ to be the category of presheaves on the category $ M_A $. This has `universal object' $ U_A = M_A $ with the obvious right action of $ M_A $.
    \end{definition}

    \pause
    \vfill

    \begin{lemma}
      We have a retraction $ U_A \to U_A^{U_A} $.
    \end{lemma}
    \begin{proof}
      We have $ M_A = \{ a \in A \mid \mathbf 1 a = a \} $. We can identify $ U_A^{U_A} $ with $ \{ a \in A \mid \mathbf 1_2 a = a \} $.

      Composition on the left with $ \mathbf 1 $ gives the retraction.
    \end{proof}

    \pause
    \vfill

    \begin{definition}
      We take $ \mathcal U_A $ to be the endomorphism theory of the reflexive universal $ U_A \in P(A) $.
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{The Main Theorem of the Lambda Calculus}
    \begin{theorem}
      There is an adjoint equivalence $ \mathcal L \mapsto \mathcal L(0) $ and $ A \mapsto \Lambda_A $ between $ \lambda $-theories and  $ \Lambda $-algebras.

      In particular, each $ \lambda $-theory $ \mathcal L $ is isomorphic to the theory of extensions of its initial algebra $ \mathcal L(0) $.
    \end{theorem}
  \end{frame}

\end{document}

### 2023-04-19 talks/t02-readinggroup/slides.tex
Add two talks, move the summary to a subdirectory

\documentclass[aspectratio=169]{fancyslides} % or beamer/slides

\usepackage{stmaryrd}
\usepackage{tikz-cd}

% \usetheme{Madrid}

\newcommand\abstractCloneDefinition{
  \begin{definition}
    An abstract clone is
    \begin{itemize}
      \item a function $ C : \mathbb N \to \mathrm{SET} $,
      \item a composition morphism $ \bullet: C(m) \times C(n)^m \to C(n) $ for all $ m, n $,
      \item elements (projections) $ x_{n, i} \in C(n) $ for all $ 1 \leq i \leq n $.
    \end{itemize}
    The composition must satisfy $ x_{n, i} \bullet (f_1, \dots, f_n) = f_i $ and $ f \bullet (\pi_{1, n}, \dots, \pi_{n, n}) = f $ and
    \[ (f \bullet (g_1, \dots, g_m)) \bullet (h_1, \dots, h_n) = f \bullet (g_1 \bullet (h_1, \dots, h_n), \dots, g_m \bullet (h_1, \dots, h_n)). \]
  \end{definition}
}

\newcommand\algebraDefinition{
  \begin{definition}
    An algebra for an abstract clone $ C $ consists of
    \begin{enumerate}
      \item a set $ A $,
      \item an action $ \alpha_n: C(n) \times A^n \to A $.
    \end{enumerate}
    Such that $ \alpha_n $ satisfies $ \alpha_n(x_{n, i}, a) = a_i $ and $ \alpha_n(f \bullet g, a) = \alpha_m(f, (\alpha_n(g_1, a), \dots, \alpha_n(g_m, a))) $.
  \end{definition}
}

\newcommand\lambdaCloneDefinition{
  \begin{definition}
    A $ \lambda $-clone consists of
    \begin{itemize}
      \item an abstract clone $ \mathcal L $,
      \item functions $ \rho_n: \mathcal L(n) \to \mathcal L(n + 1) $ and $ \lambda_n: \mathcal L(n + 1) \to \mathcal L(n) $.
    \end{itemize}
    Such that
    \[ \rho(f \bullet g) = \rho(f) \bullet (g_1, \dots, g_m, x_{n+1, n+1}) \]
    and
    \[ \lambda(f) \bullet g = \lambda(f \bullet (g_1, \dots, g_m, x_{n+1, n+1})). \]
    Hyland also requires $ (\lambda, \rho) $ to be a section-retraction pair.
  \end{definition}
}

\title{Classical Lambda Calculus in Modern Dress}

\begin{document}
  \maketitle

  \begin{frame}
    \frametitle{Denotational Semantics}

    \texttt{expr = 1 | -<expr> | <expr> + <expr>}\\
    \pause
    For $ t \in \mathtt{expr} $, $ \llbracket t \rrbracket \in \mathbb Z $.
  \end{frame}

  \begin{frame}
    \frametitle{Denotational Semantics}

    \texttt{expr = 1 | x | -<expr> | <expr> + <expr>}\\
    \pause
    For $ t \in \mathtt{expr} $, $ \llbracket t \rrbracket \in \mathbb Z \oplus x \cdot \mathbb Z $.
  \end{frame}

  \begin{frame}
    \frametitle{Denotational Semantics}

    \texttt{expr = 1 | x * <expr> | -<expr> | <expr> + <expr>}\\
    \pause
    For $ t \in \mathtt{expr} $, $ \llbracket t \rrbracket \in \mathbb Z[x] $: polynomials with coefficients in $ \mathbb Z $.
    \pause
    Or $ \llbracket t \rrbracket \in \mathbb Z \to \mathbb Z $. Or maybe $ \llbracket t \rrbracket \in \mathbb R \to \mathbb R $.
  \end{frame}

  \begin{frame}
    \frametitle{Denotational Semantics}

    \texttt{expr = Var(<nat>) | App(<expr>, <expr>) | Abs(Var(<nat>), <expr>)}\\
    \pause
    For $ t \in \mathtt{expr} $, $ \llbracket t \rrbracket \in ? $.\\
  \end{frame}

  \begin{frame}
    \frametitle{Algebraic Theory}

    \begin{definition}
      An algebraic theory consists of
      \begin{itemize}
        \item a functor $ \mathcal T: F \to \mathrm{SET} $,
        \item elements (projections) $ x_{n, i} \in \mathcal T(n) $ for all $ 1 \leq i \leq n $,
        \item a composition morphism $ \bullet: \mathcal T(m) \times \mathcal T(n)^m \to \mathcal T(n) $ for all $ m, n $.
      \end{itemize}
      The composition must be associative, unital, compatible with projections and dinatural in $ m $.
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone}

    \abstractCloneDefinition
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone - Example}

    \abstractCloneDefinition

    \begin{example}
      Take $ C(n) = \{ 1, 2, \dots, n \} $, $ x_{n, i} = i $ and $ i \bullet (f_1, \dots, f_n) = f_i $.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone - Example}

    \abstractCloneDefinition

    \begin{example}
      Take $ C(n) $ the free monoid on $ n $ generators. The $ x_{n, i} $ are the generators and $ f \bullet (g_1, \dots, g_m) $ applies the mapping $ C(m) \to C(n) $ on $ f $, given by sending $ x_{m, i} $ to $ g_i $.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone - Example}

    \abstractCloneDefinition

    \begin{example}
      Let $ X $ be an object in a category with finite products. The endomorphism clone has $ C(n) = (X^n \to X) $. Then $ x_{n, i} $ is the $ i $th projection morphism. The universal property of the product gives $ \bullet $.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone - Example}

    \abstractCloneDefinition

    \begin{example}
      The $ \lambda $-calculus $ \Lambda $, in which $ \Lambda(n) $ consists of the terms with $ n $ free variables, $ x_{n, i} = \texttt{Var}(i) $ (with De Bruijn indices) and $ \bullet $ is substitution.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone Algebra}

    \abstractCloneDefinition
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone Algebra - Example}

    \abstractCloneDefinition

    \begin{example}
      For the clone $ C(n) = \{ 1, \dots, n \} $, any set $ A $ can be an algebra, setting $ \alpha_n(i, a) = a_i $.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone Algebra - Example}

    \abstractCloneDefinition

    \begin{example}
      For the clone with $ C(n) $ the free monoid on $ n $ generators, the algebras are exactly the monoids. Setting $ a \star b := \alpha_2(x_1 \star x_2, (a, b)) $.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Abstract Clone Algebra - Properties}

    \begin{example}
      An algebra $ A $ for the lambda calculus clone $ \Lambda $ gets a lot of structure. For each term $ t \in \Lambda(n) $ and $ a \in A^n $, we have an interpretation $ t(a) \in A $.

      \pause

      $ A $ has function application $ a b := \alpha_2(x_1 x_2, (a, b)) $.

      \pause

      And lambda abstraction $ \lambda x, a x := \alpha_1((\lambda x, x_1 x), (a)) $.

      \pause

      It can inherit beta and eta reduction:
      \begin{align*}
          (\lambda x, a x)(b) &= \alpha_2(x_1 x_2, (\alpha_1((\lambda x, x_1 x), (a)), b))\\
          &= \alpha_2(x_1 x_2, (\alpha_2((\lambda x, x_1 x), (a, b)), \alpha_2(x_2, (a, b))))\\
          &= \alpha_2((x_1 x_2) \bullet ((\lambda x, x_1 x), x_2), (a, b))\\
          &= \alpha_2((\lambda x, x_1 x)(x_2), (a, b))\\
          &= \alpha_2(x_1 x_2, (a, b))\\
          &= a b.\\
      \end{align*}
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{$ \lambda $-clone}

    \lambdaCloneDefinition

    Given a $ \lambda $-clone $ \mathcal L $, we can interpret a term $ t $ of the lambda calculus (that has a context $ \Gamma $ of length $ n $) as an element $ \llbracket t \rrbracket \in \mathcal L(n) $.
  \end{frame}

  \begin{frame}
    \frametitle{$ \lambda $-clone - Example}

    \lambdaCloneDefinition

    \begin{example}
      If we have an object $ X $ in a category with products, and a retraction $ X \to (X \to X) $, the endomorphism clone of $ X $ is a $ \lambda $-clone.
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{$ \lambda $-clone - Example}

    \lambdaCloneDefinition

    \begin{example}
      The lambda calculus clone $ \Lambda $ is a $ \lambda $-clone, with $ \lambda_n f = \lambda x_{n + 1}, f $ and $ \rho_n(f) = f x_{n + 1} $.

      It is the initial $ \lambda $-clone, so any algebra for a $ \lambda $-clone is a "$ \Lambda $-algebra".
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{$ \lambda $-clone - Properties}

    \lambdaCloneDefinition

    Any algebra $ (A, (\alpha_i)_i) $ for a $ \lambda $-theory can be interpreted as a $ \Lambda $-algebra.
  \end{frame}

  \begin{frame}
    work in progress
  \end{frame}

  \begin{frame}
    \frametitle{Preliminaries to the main theorem}

    For a $ \lambda $-theory $ \mathcal L $, $ \mathcal L(0) $ is a $ \mathcal L $-algebra and therefore a $ \Lambda $-algebra.

    \vfill
    \pause

    Given a $ \Lambda $-algebra $ A $. Take $ \Lambda_A(n) = A + \Lambda(n) $, as a coproduct of $ \Lambda $-algebras, defined as a coend of sets
    \[ A + B = \int^{m, n} \mathop{Alg_\Lambda}(\Lambda(m), A) \times \mathop{Alg_\Lambda}(\Lambda(n), B) \times \Lambda (m + n) \]

    \vfill
    \pause

    \begin{lemma}
      $ \Lambda_A $ is a $ \lambda $-theory.
    \end{lemma}
    \begin{proof}
      We can identify $ \Lambda_A $ with $ \mathcal U_A $.

      We have a retraction $ U_A \to U_A^{U_A} $. Composition with this gives a retraction $ \mathcal U_A(n) \to \mathcal U_A(n + 1) $.
    \end{proof}
  \end{frame}

  \begin{frame}
    \frametitle{$ \mathcal U_A $}
    Let $ A $ be a $ \Lambda $-algebra.

    \begin{definition}
      We define a monoid $ M_A = (\{ a \in A \mid \mathbf 1 a = a \}, \circ) $ with $ \mathbf 1 := \lambda x y, x y = \alpha_0((\lambda x y, x y), ()) $ and $ a \circ b := \alpha_2((\lambda x, x_1 (x_2 x)), (a, b)) $.
    \end{definition}

    \pause
    \vfill

    \begin{definition}
      We define $ P(A) $ to be the category of presheaves on the category $ M_A $. This has `universal objec t' $ U_A = M_A $ with the obvious right action of $ M_A $.
    \end{definition}

    \pause
    \vfill

    \begin{lemma}
      We have a retraction $ U_A \to (U_A \to U_A) $.
    \end{lemma}
    \begin{proof}
      We can identify $ U_A \to U_A $ with $ \{ a \in A \mid \mathbf 1_2 a = a \} $ with $ \mathbf 1_2 := \lambda x y_1 y_2, (x y_1) y_2 $.

      Composition on the left with $ \mathbf 1 $ gives the retraction.
    \end{proof}

    \pause
    \vfill

    \begin{definition}
      We take $ \mathcal U_A $ to be the endomorphism theory of the reflexive universal $ U_A \in P(A) $.
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{The Main Theorem of the Lambda Calculus}
    \begin{theorem}
      There is an adjoint equivalence $ \mathcal L \mapsto \mathcal L(0) $ and $ A \mapsto \Lambda_A $ between $ \lambda $-theories and  $ \Lambda $-algebras.

      In particular, each $ \lambda $-theory $ \mathcal L $ is isomorphic to the theory of extensions of its initial algebra $ \mathcal L(0) $.
    \end{theorem}
  \end{frame}

  \begin{frame}
    \frametitle{Conclusion}

    In this framework, we can study the denotations/interpretations/models for the lambda calculus by studying the $ \lambda $-theories.
  \end{frame}

\end{document}

### 2023-04-19 transcript/summary.tex
Add two talks, move the summary to a subdirectory

--- 2023-03-21 summary.tex
@@
     \item \texttt{make\_object}: A function to make the object out of its data and property components;
+    \item \texttt{object}:
     \item (A coercion from the object to its data;)
-    \item A lemma that the properties form a proposition.
+    \item (\texttt{object\_has\_property}: Explicit functions to access the properties;)
+    \item \texttt{is\_object\_isaprop}: A lemma that the properties form a proposition;
     \item \texttt{object\_eq}: A lemma about sufficient (and necessary) conditions for two terms of type \texttt{object} to be equal (usually some conditions on the constituents of \texttt{object\_data});
@@
   \texttt{weqdnicoprod}
+
+  \section{Things I would have liked to know at the start}
+  The fact that if a rewrite does not succeed because a lemma has a slightly different (folded or unfolded) description, we can just force its form like \texttt{rewrite (lemma : form1 = form2)}.
+
+  Setting just one implicit argument like \texttt{action (n := 5)}.
+
+  The fact that instead of finishing a (sub)proof with \texttt{[tactic]. apply idpath.}, one can finish it with \texttt{now [tactic].}.
+
+  \section{Things that I would like to have a standard for}
+  \begin{itemize}
+    \item Naming (of folders, files, terms): what abbreviations are allowed? In what order do words appear? How are words separated? How are names capitalized?
+    \item Documentation headers in files.
+    \item In which cases do we want to use unicode?
+    \item In which cases do we want definitions to be (fully) typed?
+    \item In which cases do we want accessor functions for all data and properties?
+  \end{itemize}
+
+  No lines should have trailing whitespace and all files should have a trailing newline.
 

### 2023-05-02 transcript/summary.tex
Add sections to the summary about displayed categories, field algebraic theories and checklists

@@
   Path induction (or induction on proofs of equality) helps a lot when proving something about a \texttt{transportf}.
+
+  \section{One time checklist}
+  \begin{itemize}
+    \item Check the vscode setting for removing trailing whitespace on save;
+    \item Check the vscode setting for making sure that there is exactly 1 trailing newline on save?
+  \end{itemize}
+
+  \section{Checklist before making a PR}
+  \begin{itemize}
+    \item Make sure that all variables in intros and induction (that are used later) are introduced by name;
+    \item Make sure that \texttt{use} is replaced by \texttt{apply} and \texttt{apply} by \texttt{exact} wherever possible;
+  \end{itemize}
 
@@
 
+  \chapter{Week 17}
+  \section{The applicability of algebraic theories}
+  It turns out that it is very well possible to characterize a family of algebraic constructs using algebraic theories.
+For example, if we take the algebraic theory $ \mathcal T $ with $ \mathcal T(n) $ the monoids on $ n $ generators, there is an equivalence (at least of types, maybe also of categories) between $ \mathcal T $-algebras and monoids.
+We can do the same for groups, rings, ring modules, ring algebras etc.
+The action of certain elements corresponds then to group operation, the ring multiplication, the ring action, etc:
+  \[ a \cdot b := \alpha_2(x_1 \cdot x_2, (a, b)). \]
+  The laws that these operations must obey can also be deduced from the action, by pulling back the equation to the free object. For example, associativity:
+  \begin{align*}
+    a \cdot (b \cdot c) &= \alpha_2(x_1 \cdot x_2, (a, \alpha_2(x_1 \cdot x_2, (b, c))))\\
+    &= \alpha_2(x_1 \cdot x_2, (\alpha_3(x_1, (a, b, c)), \alpha_2(x_1 \cdot x_2, (\alpha_3(x_2, (a, b, c)), \alpha_3(x_3, (a, b, c))))))\\
+    &= \alpha_3(x_1 \cdot (x_2 \cdot x_3), (a, b, c))\\
+    &\dots\\
+    &= (a \cdot b) \cdot c.
+  \end{align*}
+  However, not all algebraic objects can be expressed as algebras for some algebraic theory in this way.
+Consider, for example, fields.
+If we have some algebraic theory $ \mathcal T $ that has the fields as its algebras, we would expect some element $ x_1^{-1} = \frac{1}{x_1} \in \mathcal T(1) $ that expresses the multiplicative inverse.
+However, there is no good way to give a value to $ \alpha_1(x_1^{-1}, (0)) $, since $ 0 $ does not have a multiplicative inverse.
+
+  \section{Using displayed categories}
+  Displayed categories are a way to build categories in a layered fashion.
+I replaced my old definitions for the objects in my library and their categories by the displayed categories version, shaping the definitions of my objects and morphisms in such a way that they are definitionally equal to the objects and morphisms in the (total) displayed categories.
+
+  It turns out that coq has a hard time doing coercions between categories, since there are a lot of implicit coercions between a category and the type of its objects.
+So for a displayed category $ \mathcal C^\prime $ over $ \mathcal C $, and a displayed category $ \mathcal C^{\prime \prime} $ over $ \mathcal C^\prime $, if we have coercions $ \mathcal C^{\prime \prime} \to \mathcal C^\prime $ and $ \mathcal C^\prime \to \mathcal C $, if we have an object of type $ \mathcal C^{\prime \prime} $ (which is actually $ \Ob{\mathcal C^{\prime \prime}} $) and we need an object of type $ \mathcal C $ (actually $ \Ob{\mathcal C} $), then coq will need to make the following chain of coercions:
+  \[ \Ob{\mathcal C^{\prime \prime}} \to \mathcal C^{\prime \prime} \to \mathcal C^\prime \to \mathcal C \to \Ob{\mathcal C} \]
+  and this does not go very well.
+In this case, it worked very well to define separate (definitionally equal) datatypes for the objects and morphisms in each category, define coercions between those, and cast objects in our categories to these analogous datatypes in places where we need these coercions.
+
   \bibliographystyle{alpha}

### 2023-05-02 transcript/summary.tex
Write about how free objects in a category give an algebraic theory with algebras

@@
 
+  In general, given a category $ \CC $, a functor $ F : \CC \to \SET $ with a left adjoint $ G : \SET \to \CC $. Then we can set
+  \[ T(n) = F(G(\{1, \dots, n\})). \]
+  Given $ c \in \Ob{\CC} $, we have a bijection $ \varphi: \Hom{\SET}{\{1, \dots, n\}}{F(c)} \xrightarrow{\sim} \Hom{\CC}{G(\{1, \dots, n\})}{c} $.
+Then, for $ f \in T(m) $, $ g: \{ 1, \dots, m \} \to T(n) $, we can set $ f \bullet g := F(\varphi(g))(f) $.
+We also take $ \pi_{n, i} = \varphi^{-1}(\mathrm{id}_{G(\{1, \dots, n\})})(i) $.
+Then, given any $ A \in \Ob \CC $, we can make $ F(A) $ into an algebra by setting $ \alpha_n(f, a) = F(\varphi(a))(f) $.
+Also, given a morphism $ f \in \Hom{\CC}{A}{B} $, we have a function $ F(f) \in \Hom{\SET}{F(A)}{F(B)} $ (\textbf{TODO: Show that it is an algebra morphism}).
+Of course, $ F $ respects composition and identities, so we have a functor from objects of $ \CC $ to $ T $-algebras.
+
+  However, this functor is not necessarily an equivalence of categories.
+For example, take $ \CC := \SET \times \SET $, with $ F(A, B) = A $, $ G(A) = (A, \emptyset) $ and $ \varphi(f) = (f, \iota_\emptyset) $.
+Then $ T(n) = \{ 1, \dots, n\} $.
+Take $ (A, B) \in \Ob{\SET \times \SET} $.
+Then $ F(A, B) = A $.
+Also, for all $ n $ and all $ a: \{ 1, \dots, n \} \to A $, $ \varphi(a) = (a, \iota_\emptyset) $ and $ F(\varphi(a)) = a $ again.
+Therefore, $ \alpha_n(f, a) = a(f) $, regardless of $ B $, so the functor is not an equivalence of categories.
+
   \section{Using displayed categories}

### 2023-09-01 talks/t03-midterm/slides.tex
Add the midterm talk

\documentclass[aspectratio=169]{fancyslides} % or beamer/slides

\usepackage{stmaryrd}
\usepackage{tikz-cd}

\title{Midterm review}

\begin{document}
  \maketitle

  \begin{frame}
    \frametitle{Classical lambda calculus in modern dress}

    As far as I understand it:
    \begin{itemize}
      \item Paper by Martin Hyland.
      \item Talks about models for the $ \lambda $-calculus.
      \item Scott's representation theorem (1980)
        \begin{quote}
          Any model is isomorphic to the ``endomorphism theory of a reflexive object in a cartesian closed category''.
        \end{quote}
      \item Fundamental theorem of the $ \lambda $-calculus.
        \begin{quote}
          There is an adjoint equivalence between the category of models and the category of semantics for the $ \lambda $-calculus with $ \beta $-equality.
        \end{quote}
    \end{itemize}
  \end{frame}

  \begin{frame}
    \frametitle{Algebraic theories: objects with variables and substitutions}

    \begin{example}
      Polynomial ring: $ \mathbb Z[x_1, ..., x_n] = \{ 1, x_3, x_5 + 7 x_2 - 17 x_3^2 x_5 x_{75}^{371}, \dots \} $.
    \end{example}

    \pause

    \begin{example}
      $ \lambda $-calculus: $ \Lambda(n) = \{ (\lambda x_1, x_1), x_5, (\lambda x_3, x_7) x_{42} \} $.
    \end{example}

    \pause

    \begin{definition}
      An \textit{algebraic theory} $ T $ is a sequence of sets $ T(n) $ with variables $ x_{i, n} \in T(n) $ (for $ 0 \leq i < n $) and a substitution operation $ \bullet : T(m) \times T(n)^m \to T(n) $.
    \end{definition}

    \pause

    \begin{example}
      In $ T(n) = \mathbb Z[x_1, \dots, x_n] $ for $ (m, n) = (2, 1) $:
      \[ (x_1 x_2) \bullet ((\lambda x_2, x_1 x_2), x_1 x_1) = (\lambda x_2, x_1 x_2) (x_1 x_1). \]
    \end{example}
  \end{frame}

  \begin{frame}
    \frametitle{Algebras: semantics}
    We want to interpret terms with free variables as functions from a context to a set

    \begin{example}
      In $ T(n) = \mathbb Z[x_1, \dots, x_n] $, we can take a set $ A = \mathbb Q $ and get
      \[ 2 x_1 + 3 x_1^2 x_2: A^2 \to A, \quad (a_1, a_2) \mapsto 2 \cdot a_1 + 3 \cdot a_1^2 \cdot a_2. \]
    \end{example}

    \pause

    \begin{definition}
      For an algebraic theory $ T $, a \textit{$ T $-algebra} $ A $ is a set $ A $, together with an interpretation function $ T(n) \times A^n \to A $ for all $ n $ (respecting the variables and substitution).
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{$ \lambda $-theory: structure with app and abs}

    To obtain a model for the $ \lambda $-calculus, we want to talk about structures that also have $ \lambda $-abstraction and application.

    \begin{definition}
      A \textit{$ \lambda $-theory} $ L $ is an algebraic theory, together with abstraction functions $ \lambda: L(n + 1) \to L(n) $ and application functions $ \rho: L(n) \to L(n + 1) $ (respecting the substitution).
    \end{definition}

    \pause

    The $ \lambda $-calculus $ \Lambda $ is the initial $ \lambda $-theory.

    \pause

    $ \beta $- and $ \eta $-equality boil down to the requirement that respectively $ \rho \circ \lambda $ and $ \lambda \circ \rho $ are the identity.
  \end{frame}

  \begin{frame}
    \frametitle{Scott's representation theorem (1980)}

    Given an object $ U $ in a cartesian closed category $ C $ such that we have a retraction $ U \xrightarrow{r} U^U $, we get a $ \lambda $-theory with $ \beta $-equality $ \mathcal U $ (the endomorphism theory of $ U $) by setting $ \mathcal U(n) = C(U^n, U) $.

    \pause

    The paper shows that $ \lambda $-theory is the endomorphism theory for some object $ U $.

    \pause

    It does this by explicitly constructing $ U $.
  \end{frame}

  \begin{frame}
    \frametitle{The Fundamental Theorem of the $ \lambda $-Calculus}

    The paper shows that there is an adjoint equivalence between $ \lambda $-theories with $ \beta $-equality and algebras for $ \Lambda $.

    \pause

    The functor one way sends $ L $ to $ L(0) $.

    \pause

    The functor the other way is a bit more complicated. Given a $ \Lambda $-algebra, it
    \begin{itemize}
      \item constructs a monoid $ M_A $;
      \item takes the category of presheaves $ P M_A $;
      \item takes the object $ U = M_A \in P(M_A) $;
      \item takes its endomorphism theory $ \mathcal U(n) $;
      \item notes that $ \Lambda_A $, the algebraic theory of extensions of $ A $, is isomorphic to $ \mathcal U(n) $.
    \end{itemize}
    \pause
    The fundamental theorem then states that $ A \mapsto \Lambda_A $ and $ L \mapsto L(0) $ constitute an adjoint equivalence of these categories.
  \end{frame}

  \begin{frame}
    \frametitle{Progress}
    \begin{itemize}
      \item Definitions and examples for algebraic theories, algebras and $ \lambda $-theories; \pause
      \item Showed equivalence between two definitions for algebraic theories; \pause
      \item Defined their categories as displayed categories; \pause
      \item Showed univalence for all of these categories; \pause
      \item Showed univalence of two standard constructions; \pause
      \item Constructed the $ \Lambda $-calculus with beta and eta equality as a (hypothetical) higher inductive type;
    \end{itemize}
  \end{frame}

  \begin{frame}
    \frametitle{Displayed categories}

    Many categories are based on other categories. They just have `more structure'. We formalized our categories as (towers of) displayed categories, because this matches their mathematical structure more closely, and helps when proving things like univalence. We have the following towers of displayed categories:

    \[ algebraic\_theory \to algebraic\_theory\_data \to pointed\_functor \to [F, HSET]. \]
    \[ algebra \to algebra\_data \to algebraic\_theory \times HSET \to algebraic\_theory;\]
    \[ lambda\_theory \to lambda\_theory\_data \to algebraic\_theory; \]
  \end{frame}

  \begin{frame}
    \frametitle{Univalence of two standard constructions}
    We can view any category $ C $ as a displayed category $ C^\prime $ over the unit category. I showed that $ C^\prime $ is displayed univalent if $ C $ is univalent.

    \pause

    Given displayed categories $ D $ over $ C $ and $ E $ over $ \int_C D $, we have the category $ \sum_D E $, which is displayed over $ C $. If $ D $ and $ E $ are displayed univalent, then $ \sum_D E $ is displayed univalent as well.
  \end{frame}

  \begin{frame}
    \frametitle{The $ \lambda $-calculus as a (hypothetical) higher inductive type}

    Need:
    \begin{itemize}
      \item Sets $ \Lambda(n) $ for all $ n $.
      \item Constructors.
      \item Substitution.
      \item Beta equality.
    \end{itemize}

    \pause

    Solution: Higher inductive type.

    \pause

    Objection: No inductive types in UniMath.

    \pause

    Solution: Hypothetical higher inductive type.
  \end{frame}

  \begin{frame}
    \frametitle{Future work}

    \begin{itemize}
      \item Remainder of the paper;
      \item Verify Hyland's claims about the inefficiency of alternative approaches;
      \item Compare Hyland's approach with the approaches of his predecessors;
      \item Explorations:
        \begin{itemize}
          \item How about the $ \lambda $-calculus with $ \beta $-conversion (as a special relation) instead of $ \beta $-equality?
          \item What if we also have $ \eta $-equality?
          \item What if we don't have $ \beta $-reduction?
        \end{itemize}
    \end{itemize}
  \end{frame}

\end{document}

### 2023-09-01 transcript/summary.tex
Complete the definition of the functor from objects in a category to algebras for the free functor algebraic theory
Add the last couple of weeks to the summary of learned things, up to the construction of a lambda-theory from an algebra

@@
 \usepackage{tikz-cd}
+\usepackage{amssymb}
 
@@
 \newcommand{\Ob}[1]{{#1}_0}
-\newcommand{\Hom}[3]{{#1}(#2,#3)}
+\newcommand{\Hom}[3]{{#1}\left(#2,#3\right)}
 \newcommand{\op}[1]{\ensuremath{{#1}^\text{op}}}
+
+\newtheorem{lemma}{Lemma}
+
+\theoremstyle{definition}
+\newtheorem{remark}{Remark}
 
@@
 
+  \texttt{transportf\_set}
+
   \section{Things I would have liked to know at the start}
@@
   The fact that instead of finishing a (sub)proof with \texttt{[tactic]. apply idpath.}, one can finish it with \texttt{now [tactic].}.
+
+  The pushout of \texttt{exact}, \texttt{apply}, \texttt{refine} and \texttt{use}.
 
@@
     \item In which cases do we want accessor functions for all data and properties?
+    \item What should be documented using comments, and how should they be formatted?
   \end{itemize}
@@
 
-  \chapter{Week 08}
+  \chapter*{Week 08}
   \section{Univalent Categories}
@@
 
-  \chapter{Week 09}
+  \chapter*{Week 09}
 
@@
 
-  \chapter{Week 11}
+  \chapter*{Week 11}
 
@@
 
-  \chapter{Week 17}
+  \chapter*{Week 17}
   \section{The applicability of algebraic theories}
@@
   \[ T(n) = F(G(\{1, \dots, n\})). \]
-  Given $ c \in \Ob{\CC} $, we have a bijection $ \varphi: \Hom{\SET}{\{1, \dots, n\}}{F(c)} \xrightarrow{\sim} \Hom{\CC}{G(\{1, \dots, n\})}{c} $.
+  Given $ c \in \Ob{\CC} $, we have a natural bijection $ \varphi: \Hom{\SET}{\{1, \dots, n\}}{F(c)} \xrightarrow{\sim} \Hom{\CC}{G(\{1, \dots, n\})}{c} $.
 Then, for $ f \in T(m) $, $ g: \{ 1, \dots, m \} \to T(n) $, we can set $ f \bullet g := F(\varphi(g))(f) $.
@@
 Then, given any $ A \in \Ob \CC $, we can make $ F(A) $ into an algebra by setting $ \alpha_n(f, a) = F(\varphi(a))(f) $.
-Also, given a morphism $ f \in \Hom{\CC}{A}{B} $, we have a function $ F(f) \in \Hom{\SET}{F(A)}{F(B)} $ (\textbf{TODO: Show that it is an algebra morphism}).
-Of course, $ F $ respects composition and identities, so we have a functor from objects of $ \CC $ to $ T $-algebras.
+Also, given a morphism $ m \in \Hom{\CC}{A}{B} $, we have a function $ F(m) \in \Hom{\SET}{F(A)}{F(B)} $.
+  are equal. Naturality gives for all $ a: \{1, \dots, n\} \to F(A) $ that
+  \[ m \circ \varphi(a) = \varphi(F(m) \circ a), \]
+  so for $ f: F(G(\{1, \dots, n\})) $,
+  \[ F(m)(\alpha_2(f, a)) = F(m \circ \varphi(a))(f) = F(\varphi(F(m) \circ a))(f) = \alpha_2(f, F(m) \circ a) \]
+  and $ F(m) $ is a morphism of algebras. Of course, $ F $ respects composition and identities, so we have a functor from objects of $ \CC $ to $ T $-algebras.
 
@@
 
+  \chapter*{Week 18}
+
+  \begin{lemma}
+    The lambda calculus $ \Lambda $ is the initial $ \lambda $-theory.
+  \end{lemma}
+  \begin{proof}
+    Given a $ \lambda $-theory $ \mathcal L $, we need a unique morphism $ \varphi : \Lambda \to \mathcal L $.
+
+    Do structural induction on the lambda terms in $ \Lambda(n) $.
+Send \texttt{Var(i)} to $ \pi_{n, i} $, \texttt{Abs(f)} to $ \lambda(\varphi(f)) $ and \texttt{App(f, g)} to $ \rho(\varphi(f)) \bullet (\pi_1, \dots, \pi_n, g) $.
+
+    Show that it preserves $ \bullet $, $ \pi_{i} $, $ \rho $ and $ \lambda $.
+
+    Uniqueness: Again, structural induction on the lambda terms.
+Preservation of the $ \pi_i $ gives the image of \texttt{Var(i)}.
+Preservation of $ \lambda $ gives the image of \texttt{Abs(f)}.
+Preservation of $ \rho $ and $ \bullet $ gives the image of
+    \[ \mathtt{App(f, g)} = \rho(f) \bullet (\pi_1, \dots, \pi_n, g). \]
+  \end{proof}
+
+  Given a $ \lambda $-theory $ \mathcal L $, $ \mathcal L(0) $ is a $ \Lambda $-algebra (by extension of scalars). This gives a functor.
+
+  \begin{lemma}
+    Given a $ \Lambda $-algebra $ A $, we can form the set $ \mathcal U_A $.
+  \end{lemma}
+  \begin{proof}
+
+  \end{proof}
+  \begin{lemma}
+    $ \mathcal U_A $ is a $ \lambda $-theory.
+  \end{lemma}
+
+  \begin{lemma}
+    $ \mathcal U_A $ is functorial in $ A $.
+  \end{lemma}
+  \begin{proof}
+
+  \end{proof}
+
+  These functors form an adjoint equivalence: We have natural isomorphisms $ \mathcal U_{\mathcal L(0)} \cong \mathcal L $ and $ \mathcal U_A(0) \cong A $.
+
+  \chapter*{Week 33}
+  \section{Coends}
+  In a category $ \DD $ with equalizers and products, and given a functor $ F : \op \CC \times \CC \to \DD $, we can define the end $ \int_{c: \Ob \CC} F(c, c) $ to be the equalizer of
+  \[ \prod_{c : \Ob \CC} F(c, c) \rightrightarrows \prod_{\Hom{\CC} c {c^\prime}} F(c, c^\prime). \]
+  For $ \DD = \SET $, an element of this gives, for every element $ c : \Ob \CC $, an element $ f_c : F(c, c) $, such that for all morphisms $ \alpha : \Hom{\CC}{c}{c^\prime} $, we have
+  \[ \#F(c, \alpha)(f_c) =_{F(c, c^\prime)} \#F(\alpha, c^\prime)(f_{c^\prime}). \]
+
+  If we have two functors $ G, G^\prime: \CC \to \CC^\prime $, take $ F(c, c^\prime) = \Hom{\DD^\prime}{G(c)}{G^\prime(c^\prime)} $.
+An element of $ \int_c \Hom{\DD^\prime}{G(c)}{G^\prime(c^\prime)} $ gives, for all $ c: \Ob \CC $ an element $ f_c : \Hom{\SET}{G(c)}{G(c^\prime)} $ such that for all morphisms $ \alpha : \Hom{\CC}{c}{c^\prime} $, we have
+  \[ f_c \cdotp \# G^\prime(\alpha) = \#F(c, \alpha)(f_c) = \#F(\alpha, c^\prime)(f_{c^\prime}) = \#G(\alpha) \cdotp f_{c^\prime}, \]
+  so we have a commutative diagram
+  \begin{center}
+    \begin{tikzcd}
+      G(c) \arrow[r, "\#G(\alpha)"] \arrow[d, "f_c"] & G(c^\prime) \arrow[d, "f_{c^\prime}"]\\
+      G^\prime(c) \arrow[r, "\#G^\prime(\alpha)"] & G^\prime(c)
+    \end{tikzcd}
+  \end{center}
+  Which is exactly the diagram of a natural transformation.
+
+  On the other hand, if $ \DD $ has coproducts, we can define the coend $ \int^{c: \Ob \CC} F(c, c) $ to be the coequalizer of
+  \[ \coprod_{\Hom{\CC} c {c^\prime}} F(c, c^\prime) \rightrightarrows \coprod_{c : \Ob \CC} F(c, c). \]
+  For $ \DD = \SET $, an element of this is an element $ c : \Ob \CC $, together with an element of $ F(c, c) $.
+  For $ c, c^\prime : \Ob \CC $, $ f : F(c^\prime, c) $ and $ \alpha : \Hom{\CC}{c}{c^\prime} $, we identify
+  \[ (c, \#F(\alpha, c)(f)) \]
+  with
+  \[ (c^\prime, \#F(c^\prime, \alpha)(f)). \]
+
+  For $ F(c, c^\prime) = \Hom{\CC^\prime}{G(c)}{G^\prime(c)} $, an element of $ \int^{c: \Ob \CC} $ is an element $ c : \Ob \CC $ with a morphism $ f : \Hom{\CC^\prime}{G(c)}{G^\prime(c)} $ and for a morphism $ \alpha : \Hom{\CC}{c}{c^\prime} $ and morphism $ f : \Hom{\CC^\prime}{G(c^\prime)}{G^\prime(c)} $, we set
+  \[ (c, \#G(\alpha) \cdotp f) = (c, \#F(\alpha, c)(f)) = (c^\prime, \#F(c^\prime, \alpha)(f)) = (c^\prime, f \cdotp \#G^\prime(\alpha)). \]
+
+  \subsection{Wedges}
+  A wedge $ e : w \to F $ is an object $ w $ with, for every object $ c : \Ob \CC $ a morphism $ e_c : w \to F(c, c) $ and for every morphism $ \alpha: c \to c^\prime $ a commutative square
+  \begin{center}
+    \begin{tikzcd}
+      w \arrow[d, "e_c"] \arrow[r, "e_{c^\prime}"] & {F(c^\prime, c^\prime)} \arrow[d, "{\#F(\alpha, c^\prime)}"] \\
+      {F(c, c)} \arrow[r, "{\#F(c, \alpha)}"] & {F(c, c^\prime)}
+    \end{tikzcd}
+  \end{center}
+  The end $ e : \int_{c: \Ob \CC} F(c, c) \to F $ is the universal wedge.
+I.e., given a wedge $ e^\prime : w^\prime \to F $, $ e^\prime $ factors through $ e $ via a unique map $ w^\prime \to \int_{c: \Ob \CC} F(c, c) $.
+
+  Conversely, a cowedge $ e : F \to w $ is an object $ w $ with, for every object $ c : \Ob \CC $ a morphism $ e_c : F(c, c) \to w $ and for every morphism $ \alpha: c \to c^\prime $ a commutative square
+  \begin{center}
+    \begin{tikzcd}
+      {F(c^\prime, c)} \arrow[r, "{\#F(c^\prime, \alpha)}"] \arrow[d, "{\#F(\alpha, c)}"] & {F(c^\prime, c^\prime)} \arrow[d, "e_{c^\prime}"] \\
+      {F(c, c)} \arrow[r, "e_c"] & w
+    \end{tikzcd}
+  \end{center}
+  The coend $ e : F \to \int^{c: \Ob \CC} F(c, c) $ is the universal cowedge.
+I.e., given a cowedge $ e^\prime : F \to w^\prime $, $ e^\prime $ factors through $ e $ via a unique map $ \int_{c: \Ob \CC} F(c, c) \to w^\prime $.
+
+  \subsection{The coproduct of algebras}
+  Now, to the example that we are interested in
+  \[ A + B = \int^{m,n : \Ob F} \mathrm{Alg}_T(T(m), A) \times \mathrm{Alg}_T(T(n), B) \times T(m + n). \]
+  We can identify $ \mathrm{Alg}_T(T(m), A) \cong A^m $:
+  \begin{itemize}
+    \item Send $ f : \mathrm{Alg}_T(T(m), A) $ to $ (f \pi_1, \dots, f \pi_m) : A^m $;
+    \item Send $ (a_1, \dots, a_m) : A^m $ to $ x \mapsto x \bullet (a_1, \dots, a_m) : A $.
+  \end{itemize}
+  Then this becomes
+  \[ A + B = \int^{m,n : \Ob F} A^m \times B^n \times T(m + n). \]
+  An element of this set is a pair
+  \[ ((m, n), ((a_1, \dots, a_m), (b_1, \dots, b_n), f)) \]
+  with $ m, n : \Ob F $, $ a_i : A $, $ b_i : B $ and $ f : T(m + n) $.
+
+  If we have $ m, m^\prime, n, n^\prime : \Ob F $, $ \alpha : \Hom{F}{m}{m^\prime} $, $ \beta : \Hom{F}{n}{n^\prime} $, and an element
+  \[ ((a_i)_i, (b_i)_i, f) : A^{m^\prime} \times B^{n^\prime} \times T(m + n), \]
+  we identify
+  \[ ((m, n), ((a_{\alpha(i)})_i, (b_{\beta(i)})_i, f)) = ((m^\prime, n^\prime), ((a_i)_i, (b_i)_i, \#T(\alpha + \beta)(f))) \]
+
+  Now, we can define the action
+  \[ f \bullet (((m, m^\prime), ((a_{ji})_i, (b_{ji})_i, g_j))_j) := ((m, m^\prime), (f \bullet (a_{ji})_j)_i, (f \bullet (b_{ji})_j)_i, f \bullet (g_j)_j). \]
+  This is associative and projects components because the action on $ A $ and $ B $ is associative and projects components.
+
+  \subsubsection{The universal property}
+  Now, we would just need to show that for all $ C : \Ob{\mathrm{Alg}_T} $ and all $ f_A : A \to C $ and $ f_B : B \to C $, there exists a unique morphism $ g : A + B \to C $.
+
+  Since $ A + B $ is a coend, it would suffice to give $ C $ a $ A^m \times B^n \times T(m + n) $-cowedge structure.
+That is, we need, for all $ m, n: \Ob F $, a morphism $ A^m \times B^n \times T(m + n) \to C $.
+Define
+  \[ f_{A + B}((a_1, \dots, a_m), (b_1, \dots, b_n), f) := f \bullet (f_A(a_1), \dots, f_A(a_m), f_B(b_1), \dots, f_B(b_n)). \]
+  We must show that given $ x: T(l) $ and given, for all $ 1 \leq i \leq l $, $ (a_i, b_i, f_i) : A^m \times B^n \times T(m + n) $, we have
+  \[ x \bullet (f_{A + B}(a_i, b_i, f_i))_i = f_{A + B}((x \bullet (a_i, b_i, f_i))_i). \]
+  But
+  \begin{align*}
+    &x \bullet (f_i \bullet ((f_A(a_{ij}))_j, (f_B(b_{ij}))_j))_i\\
+    &=x \bullet (f_{A + B}(a_i, b_i, f_i))_i\\
+    &= f_{A + B}((x \bullet (a_i, b_i, f_i))_i)\\
+    &= f_{A + B}((x \bullet (a_{ij})_i)_j, (x \bullet (b_{ij})_i)_j, x \bullet f)\\
+    &= (x \bullet f) \bullet ((f_A(x \bullet (a_{ij})_i))_j, (f_B(x \bullet (b_{ij})_i))_j)\\
+    &= (x \bullet f) \bullet ((x \bullet (f_A(a_{ij}))_i)_j, (x \bullet (f_B(b_{ij}))_i)_j)\\
+  \end{align*}
+
+  \chapter*{Week 34}
+  \section{Algebraic Theories as categories}
+  Hyland cites \cite{p13-adamek-rosicky}, which also introduces algebraic theories. There is a correspondence between Hyland's algebraic theories, and ``one-sorted algebraic theories'' in the book.
+
+  The book defines the category $ \mathcal N $, which is the full subcategory of $ \op \SET $, with objects $ n = \{ 0, 1, \dots, n - 1 \} $ for all $ n \in \mathbb N $.
+This category presents $ n $ as $ 1^n $, with projections $ \pi_{n, i} : n \to 1 $.
+
+  \subsection{Algebraic Theories}
+  The book defines a one-sorted algebraic theory to be a category with finite products, whose objects are the natural numbers, together with a functor $ T : \mathcal N \to \mathcal T $ that is the identity on objects.
+
+  Given a one-sorted algebraic theory $ (\mathcal T, T) $, we make Hyland's algebraic theory $ \mathcal T^\prime $ as follows:
+  Take $ \mathcal T^\prime(n) = \mathcal T(n, 1) $. We have $ \mathcal T^\prime(n)^m = \mathcal T(n, 1)^m = \mathcal T(n, m) $. Then composition gives
+  \[ \bullet : \mathcal T^\prime(m) \times \mathcal T^\prime(n)^m = \mathcal T(m, 1) \times \mathcal T(n, m) \to \mathcal T(n, 1) = \mathcal T^\prime(n). \]
+  The projections are given by $ \pi^\prime_{n, i} = \#T(\pi_{n, i}) : \mathcal T(n, 1) = \mathcal T^\prime(n) $.
+
+  Conversely, given Hyland's algebraic theory $ \mathcal T^\prime $, we make a one-sorted algebraic theory $ \mathcal T $ as follows.
+Take $ \Ob{\mathcal T} = \mathbb N $ and $ \Hom{\mathcal T}{m}{n} = \mathcal T^\prime(m)^n $.
+Then $ T $ sends $ f = (\pi_{i_1}, \dots, \pi_{i_n}) = \mathcal N(m, 1)^n = \mathcal N(m, n) $ to $ (\pi^\prime_{i_1}, \dots, \pi^\prime_{i_n}) $.
+Composition is then defined as
+  \[ \mathcal T(l, m) \times \mathcal T(m, 1)^n = \mathcal T(l, m) \times \mathcal T(m, n) \ni (f, (g_1, \dots, g_n)) = (f, g) \mapsto (g_1 \bullet f, \dots, g_n \bullet f) : \mathcal T(l, 1)^n = \mathcal T(l, n).
+\]
+
+  \subsection{Algebraic theory algebras}
+  Given a one-sorted algebraic theory $ (\mathcal T, T) $ and the corresponding Hyland's algebraic theory $ \mathcal T^\prime $.
+
+  An algebra for $ \mathcal T $ is a finite-product-preserving functor $ A: \mathcal T \to \SET $.
+Given such an algebra, we get an algebra $ A^\prime $ for $ \mathcal T^\prime $ by setting $ A^\prime = A(1) $, and for $ f : \mathcal T^\prime(n) = \mathcal T(n, 1) $, we define $ f \bullet - $ to be
+  \[ \#A(f) : (A^\prime)^n = A(1)^n = A(1^n) = A(n) \to A(1) = A^\prime. \]
+  Conversely, given an algebra $ A^\prime $ for $ \mathcal T^\prime $, we define the functor $ A $ to map $ n $ to $ (A^\prime)^n $ on objects, and to send the morphism $ f : \mathcal T(m, n) = \mathcal T(m, 1)^n = (\mathcal T^\prime(m))^n $ to
+  \[ A(m) = (A^\prime)^m \ni a \mapsto (f_1 \bullet a, \dots, f_n \bullet a) (A^\prime)^n = A(n). \]
+  \subsection{Pre(- or post)liminaries}
+  \subsubsection{The Density Theorem}
+  Given an algebraic theory (can be one-sorted) $ \mathcal T $, we have a Yoneda embedding $ Y_{\mathcal T}: \op{\mathcal T} \to [\mathcal T, \SET] $, sending $ X $ to $ \Hom{\mathcal T}{X}{-} $.
+Also, given a $ \mathcal T $-algebra $ A $, we have the category of elements $ \mathop{El} A $, with the objects being dependent pairs $ \sum_{x : \Ob{\mathcal T}}, A x $ and morphisms $ \Hom{\mathrm{El}A}{(X, x)}{(Y, y)} $ being morphisms $ f : \Hom{\mathcal T}{Y}{X} $ with $ \#A(f)(y) = x $.
+Denote $ \Phi_A : \mathop{El} A \to \op{\mathcal T} $ the projection on the first coordinate.
+Then $ A $ is the colimit of the diagram
+  \[ \mathop{El} A \xrightarrow{\Phi_A} \op{\mathcal T} \xrightarrow{Y_{\mathcal T}} [\mathcal T, \SET]. \]
+  I.e. we have, for all $ (x, y) : \mathop{El} A $, a map of functors (i.e. natural transformation)
+  \[ Y_{\mathcal T}(\Phi_A(x, y)) = Y_{\mathcal T}(x) = \Hom{\mathcal T}{x}{-} \Rightarrow A \]
+  That is, for all $ t : \mathcal T $, a map
+  \[ \mathcal T(x, t) \to A(t), f \mapsto \#A(f)(y) \]
+  and for all morphisms $ g : \Hom{\mathcal T}{t}{t^\prime} $ and all $ f: \mathcal T(x, t) $, we have the equality
+  \[ \#A(g)(\#A(f)(y)) = \#A(g \circ f)(y) \]
+  so the map is natural.
+
+  Now, for all $ B : [\mathcal T, \SET] $, we have
+  \begin{align*}
+    \Hom{[\mathcal T, \SET]}{\mathop{colim}_{(x, y) : \mathop{El} A} Y_{\mathcal T}(\Phi_A(x, y))}{B} &\cong \lim_{(x, y) : \mathop{El} A} \Hom{[\mathcal T, \SET]}{Y_{\mathcal T}(\Phi_A(x, y))}{B}\\
+    &\cong \lim_{(x, y) : \mathop{El} A} \Hom{[\mathcal T, \SET]}{Y_{\mathcal T}(x)}{B}\\
+    &\cong \lim_{(x, y) : \mathop{El} A} B(x)\\
+    &\cong \Hom{[\mathop{El} A, \SET]}{\mathrm{pt}}{B}
+  \end{align*}
+  for $ \mathrm{pt} $ the constant functor that sends anything to $ \{ \star \} $.
+Now, given a natural transformation $ \alpha : \Hom{[\mathop{El} A, \SET]}{\mathrm{pt}}{B} $.
+For all $ x : \Ob{\mathcal T} $, we get a map
+  \[ A(x) \to B(x), \quad y \mapsto \alpha_{(x, y)}(\star). \]
+  By naturality of $ \alpha $, this is a natural transformation $ A \Rightarrow B $. This gives an isomorphism
+  \[ \Hom{[\mathop{El} A, \SET]}{\mathrm{pt}}{B} \cong \Hom{[\mathcal T, \SET]}{A}{B}. \]
+  Since this holds for all $ B $, we have
+  \begin{align*}
+    Y_{\op{[\mathcal T, \SET]}}(A)
+    &= \Hom{[\mathcal T, \SET]}{A}{-}\\
+    &\cong \Hom{[\mathcal T, \SET]}{\mathop{colim}_{(x, y) : \mathop{El} A} Y_T(\Phi_A(x, y))}{-}\\
+    &= Y_{\op{[\mathcal T, \SET]}}(\mathop{colim}_{(x, y) : \mathop{El} A} Y_T(\Phi_A(x, y))).
+  \end{align*}
+  By the Yoneda Lemma, this implies that $ \mathop{colim}_{(x, y) : \mathop{El} A} Y_T(\Phi_A(x, y)) \cong A $.
+
+  \subsection{An example}
+  First of all, we need an example.
+Take an algebraic theory (Hyland's kind): $ \mathcal T^\prime(n) = \{\star, 1, 2, 3, \dots, n \} $ with $ \star \bullet g = \star $ and $ i \bullet g = g_i $.
+Take the two-element set $ A^\prime = \{ \bot, \top \} $.
+We can make $ A^\prime $ into an $ \mathcal T^\prime $-algebra by setting $ i \bullet a := a_i $ and $ \star \bullet a = \top $ (or $ \bot $ for that matter, as long as we are consistent).
+
+  Translating this to a one-sorted algebraic theory, we get the category $ \mathcal T $ with $ \Ob{\mathcal T} = \{ 0, 1, 2, \dots \} $ and $ \mathcal T(m, n) = \{ \star, 1, \dots, m \}^n $.
+We also get the algebraic theory (i.e.
+functor) $ A: \mathcal T \to \SET $, given on objects by $ n \mapsto \{ \bot, \top \}^n $ and on morphisms by
+  \[ \mathcal T(m, 1) \ni f \mapsto a \mapsto \left\{ \begin{array}{cc} a_i & f = i\\ \top & f = \star \end{array} \right. \]
+  and extending linearly for $ f \in \mathcal T(m, n) = \mathcal T(m, 1)^n $.
+The category $ \mathrm{El} A $ consists of objects $ (n, a) $ with $ a : \{ \bot, \top \}^n $.
+Its morphisms $ f: \Hom{\mathrm{El} A}{(m, a)}{(n, b)} $ are morphisms $ \Hom{\mathcal T}{n}{m} = \mathcal T^\prime(n)^m $ such that $ A(f)(b) = (f_1 \bullet b, \dots, f_m \bullet b) = a $, so
+  \[ \Hom{\mathrm{El} A}{(m, a)}{(n, b)} \cong \prod_{1 \leq i \leq n} \Hom{\mathrm{El} A}{(1, a_i)}{(n, b)}, \]
+  and
+  \[ (m, a) \cong \coprod_{1 \leq i \leq n} (1, a_i). \]
+  In other words, all objects of $ \mathrm{El} A $ are generated as coproducts by $ (1, \top) $ and $ (1, \bot) $.
+Now, we have $ \Hom{\mathrm{El} A}{(1, a)}{(n, b)} = \{ f : \mathcal T^\prime(n) \mid f \bullet b = a.
+\} $.
+This is the set of $ i $ such that $ b_i = a $, and if $ a = \top $, it contains $ \star $.
+Note that $ \mathcal T(n, 1) \cong \coprod_{a : A^\prime} \Hom{\mathrm{El} A}{(n, c)}{(1, a)} $.
+
+  Now, for an object $ n : \op{\mathcal T} $, the Yoneda embedding sends it to
+  \[ m \mapsto \Hom{\mathcal T}{n}{m} = \mathcal T^\prime(n)^m \]
+  A morphism $ f: \Hom{\op{\mathcal T}}{n}{n^\prime} = \Hom{\mathcal T}{n^\prime}{n} $ is sent to a natural transformation from $ m \mapsto \Hom{\mathcal T}{n}{m} $ to $ \Hom{\mathcal T}{n^\prime}{m} $ by sending $ g : \Hom{\mathcal T}{n}{m} \cong \mathcal T^\prime(n)^m $ to
+  \[ g \circ f = (g_1 \bullet f, \dots, g_n \bullet f) : \Hom{\mathcal T}{n^\prime}{m} \cong T^\prime(n)^m. \]
+
+  We can calculate (co)limits in a functor category pointwise. That means that
+  \[ (\mathop{colim}_{j : J} \mathcal F(j))(x) = \mathop{colim}_{j : J} (\mathcal F(j)(x)) \]
+  We are first and foremost interested in
+  \begin{align*}
+    \left(\mathop{colim}_{(n, a) : \mathrm{El} A} Y_{\mathcal T}(n)\right)(1)
+    &= \mathop{colim}_{(n, a) : \mathrm{El} A} (Y_{\mathcal T}(n)(1))\\
+    &= \mathop{colim}_{(n, a) : \mathrm{El} A} (\mathcal T(n, 1))\\
+    &= \mathop{colim}_{(n, a) : \mathrm{El} A} (\mathcal T^\prime(n))
+  \end{align*}
+  which is the equalizer of
+  \[ \coprod_{f: (m, a) \to (m^\prime, a^\prime)} \mathcal T^\prime(m) \rightrightarrows \coprod_{(n, a) : \mathrm{El} A} \mathcal T^\prime(n) \]
+  for every $ f: (m, a) \to (m^\prime, a^\prime) $ (i.e.
+$ f: \mathcal T^\prime(m^\prime)^m $ such that for all $ i $, $ f_i \bullet a^\prime = a_i $), we identify the $ t : \mathcal T^\prime(m) $ over $ (m, a) $ with the $ t \bullet f : \mathcal T^\prime(m^\prime) $ over $ (m^\prime, a^\prime) $.
+
+  In particular, we identify $ \pi_1 : \mathcal T^\prime(1) $ over $ (1, f \bullet a) $ with $ \pi_1 \bullet f = f : \mathcal T^\prime(m) $ over $ (m, a) $.
+
+  For general $ m $ and $ m^\prime $, we identify $ t \bullet f $ over $ (m^\prime, a) $ with $ t $ over $ (m, (f_1 \bullet a, \dots, f_n \bullet a)) $.
+Since the action on the algebra is associative, we have
+  \[ (t \bullet f) \bullet a = t \bullet (f_1 \bullet a, \dots, f_n \bullet a) \]
+  so the identifications of the $ t $ over $ (m, a) $ with $ \pi_1 $ over $ (1, t \bullet a) $ generate the equivalence relation.
+
+  Now, for the action of $ \mathcal T $ on this colimit. In particular, given $ f: \Hom{\mathcal T}{m}{1} = \mathcal T^\prime(m) $, we want a morphism
+  \[ \Hom{\SET}{\left(\mathop{colim}_{(n, a) : \mathrm{El} A} Y_{\mathcal T}(n)\right)(m)}{\left(\mathop{colim}_{(n, a) : \mathrm{El} A} Y_{\mathcal T}(n)\right)(1)}. \]
+  We get this as
+  \[ \mathop{colim}_{(n, a) : \mathrm{El} A} (t \mapsto f \bullet t): \Hom{\SET}{\mathop{colim}_{(n, a) : \mathrm{El} A} (\mathcal T^\prime(n)^m)}{\mathop{colim}_{(n, a) : \mathrm{El} A} (\mathcal T^\prime(n))}.
+\]
+  Every element can be identified with $ \pi_1 $ over $ (1, a) $ for some $ a $.
+Now, for $ a_1, \dots, a_n: A^\prime $, $ \pi_1 $ over $ (1, a_i) $ is identified with $ \pi_i $ over $ (n, (a_1, \dots, a_n)) $.
+Then the action of $ f $ sends $ (\pi_1, \dots, \pi_n) $ over $ (n, a) $ to $ f \bullet (\pi_1, \dots, \pi_n) = f $ over $ (n, a) $, but this is identified with $ \pi_1 $ over $ (1, f \bullet a) $.
+Therefore, this recovers the action of $ \mathcal T^\prime $ on $ A^\prime $.
+
+  \chapter*{Week 35}
+  \section{The monoid}
+  \textit{Note to self: even though everything is defined by actions of $ \Lambda $, it might be good to define application and abstraction in $ A $.}
+
+  In the lambda calculus theory $ \Lambda $, define
+  \[ \mathbf 1_n := \lambda x_1 \dots x_{n + 1}, x_1 \dots x_{n + 1} : \Lambda(0). \]
+  Specifically, take $ \mathbf 1 := \mathbf 1_1 = \lambda x_1 x_2, x_1 x_2 $. Given a $ \Lambda $-algebra $ A $, we have mappings
+  \begin{align*}
+    APP&: A \times A \to A & (a_1, a_2) &\mapsto (x_1 x_2) \bullet (a_1, a_2)\\
+    ABS&: A \to A & a &\mapsto (\lambda x_2, x_1) \bullet a_1
+  \end{align*}
+  Also, given any constant $ c: \Lambda(0) $, we can inject it as $ c \bullet () : A $. We will identify such an element with $ c $. For example, we have the $ \mathbf 1_n : A $. Now, take the sets
+  \[ A(n) = \{ a: A \mid APP\ \mathbf 1_n\ a = a \}. \]
+  \begin{remark}
+    Note that
+    \begin{align*}
+      APP\ \mathbf 1_n\ a &= (x_1 x_2) \bullet (\lambda x_1 \dots x_{n + 1}, x_1 \dots x_{n + 1} \bullet (), a)\\
+      &= (x_1 x_2) \bullet (\lambda x_2 \dots x_{n + 2}, x_2 \dots x_{n + 2} \bullet a, x_1 \bullet a)\\
+      &= (x_1 x_2) \bullet (\lambda x_2 \dots x_{n + 2}, x_2 \dots x_{n + 2}, x_1) \bullet a\\
+      &= ((\lambda x_2 \dots x_{n + 2}, x_2 \dots x_{n + 2}) x_1) \bullet a\\
+      &= (\lambda x_2 \dots x_{n + 1}, x_1 \dots x_{n + 1}) \bullet a
+    \end{align*}
+    which is equal to
+    \begin{align*}
+      \mathbf 1_{n - 1} \circ a &= (\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_1 \dots x_n, x_1 \dots x_n) \bullet (), a)\\
+      &= (\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_2 \dots x_{n + 1}, x_2 \dots x_{n + 1}) \bullet a, x_1 \bullet a)\\
+      &= ((\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_2 \dots x_{n + 1}, x_2 \dots x_{n + 1}), x_1)) \bullet a\\
+      &= (\lambda x_2, (\lambda x_3 \dots x_{n + 2}, x_3 \dots x_{n + 2}) (x_1 x_2)) \bullet a\\
+      &= (\lambda x_2, (\lambda x_3 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1})) \bullet a.
+    \end{align*}
+  \end{remark}
+
+  \begin{remark}
+    If we have $ \eta $-equality, $ A(1) = A $.
+  \end{remark}
+
+  \begin{remark}
+    Note that we have $ A(n + 1) \subseteq A(n) $, because if
+    \[ a = (\lambda x_2 \dots x_{n + 2}, x_1 \dots x_{n + 2}) \bullet a, \]
+    then
+    \begin{align*}
+      (\lambda x_2 \dots x_{n + 1}, x_1 \dots x_{n + 1}) \bullet a
+      &= (\lambda x_2 \dots x_{n + 1}, x_1 \dots x_{n + 1}) \bullet ((\lambda x_2 \dots x_{n + 2}, x_1 \dots x_{n + 2}) \bullet a)\\
+      &= ((\lambda x_2 \dots x_{n + 1}, x_1 \dots x_{n + 1}) \bullet (\lambda x_2 \dots x_{n + 2}, x_1 \dots x_{n + 2})) \bullet a\\
+      &= (\lambda x_2 \dots x_{n + 1}, (\lambda x_2 \dots x_{n + 2}, x_1 \dots x_{n + 2}) x_2 \dots x_{n + 1}) \bullet a\\
+      &= (\lambda x_2 \dots x_{n + 1}, (\lambda x_{n + 2}, x_1 \dots x_{n + 2})) \bullet a\\
+      &= (\lambda x_2 \dots x_{n + 2}, x_1 \dots x_{n + 2}) \bullet a\\
+      &= a.
+    \end{align*}
+  \end{remark}
+
+  We can then define an operation $ A(1) \times A(1) \to A(1) $, given by
+  \[ (a_1, a_2) \mapsto a_1 \circ a_2 := (\lambda x_3, x_1 (x_2 x_3)) \bullet (a_1, a_2). \]
+  This works because
+  \begin{align*}
+    (\lambda x_2, x_1 x_2) \bullet ((\lambda x_3, x_1 (x_2 x_3)) \bullet (a_1, a_2))
+    &= ((\lambda x_2, x_1 x_2) \bullet (\lambda x_3, x_1 (x_2 x_3))) \bullet (a_1, a_2)\\
+    &= (\lambda x_3, (\lambda x_4, x_1 (x_2 x_4)) x_3) \bullet (a_1, a_2)\\
+    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet (a_1, a_2).
+  \end{align*}
+  This associative since
+  \begin{align*}
+    (a_1 \circ a_2) \circ a_3
+    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_3, x_1 (x_2 x_3)) \bullet (a_1, a_2), a_3)\\
+    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_4, x_1 (x_2 x_4)) \bullet (a_1, a_2, a_3), x_3 \bullet (a_1, a_2, a_3))\\
+    &= ((\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_4, x_1 (x_2 x_4)), x_3)) \bullet (a_1, a_2, a_3)\\
+    &= (\lambda x_4, (\lambda x_5, x_1 (x_2 x_5)) (x_3 x_4)) \bullet (a_1, a_2, a_3)\\
+    &= (\lambda x_4, x_1 (x_2 (x_3 x_4))) \bullet (a_1, a_2, a_3)\\
+    &= (\lambda x_4, x_1 ((\lambda x_5, x_2 (x_3 x_5)) x_4)) \bullet (a_1, a_2, a_3)\\
+    &= ((\lambda x_3, x_1 (x_2 x_3)) \bullet (x_1, (\lambda x_4, x_2 (x_3 x_4)))) \bullet (a_1, a_2, a_3)\\
+    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet (x_1 \bullet (a_1, a_2, a_3), (\lambda x_4, x_2 (x_3 x_4)) \bullet (a_1, a_2, a_3))\\
+    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet (a_1, (\lambda x_3, x_1 (x_2 x_3)) \bullet (a_2, a_3))\\
+    &= a_1 \circ (a_2 \circ a_3).
+  \end{align*}
+  We also have an identity element
+  \[ I = \lambda x_1, x_1 \]
+  since
+  \begin{align*}
+    a \circ I &= \lambda x_1, a (I x_1) & I \circ a &= \lambda x_1, I (a x_1)\\
+    &= \lambda x_1, a x_1&
+    &= \lambda x_1, a x_1\\
+    &= a&
+    &= a.
+  \end{align*}
+  This makes $ A(1) $ into a monoid.
+
+  We can also view this as a one-object category $ M_A $.
+Consider the category $ P A := [\op{M_A}, \SET] $ of presheaves on this category.
+These are sets $ P $, together with a right action $ \alpha: P \times M_A \to P $.
+This category has an object $ U_A $ with underlying set $ A(1) $ and right action
+  \[ (p, a) \mapsto p \circ a. \]
+
+  Now, if we have a map $ f: A \to B $ of $ \Lambda $-algebras, it maps $ A(n) $ to $ B(n) $, since it preserves the image of $ \mathbf 1_n $ and $ APP $.
+This gives a map $ M_f $ of monoids.
+By restriction of scalars, we get a functor $ PB \to PA $.
+It has a left adjoint given by left (or right?) Kan extension.
+
+  \subsection{The function space}
+  \subsubsection{For general monoids}
+  We now study the function space $ U_A \Rightarrow U_A $.
+  In general, for any monoid $ M $, given two presheaves $ X\ Y: PM $, we have a candidate for the function space $ X \Rightarrow Y $.
+We take it to be the set of $ M $-equivariant maps.
+I.e.
+$ \varphi: M \times X \to Y $ such that for all $ m_1\ m_2: M $, $ x: X $,
+  \[ \varphi(m_1 . m_2, x . m_2) = \varphi(m_1, x) . m_2. \]
+  We give this set an $ M $-action:
+  \[ (\varphi . m_3)(m_1, x) = \varphi(m_3 . m_1, x) \]
+  and this is again $ M $-equivariant since
+  \[ (\varphi . m_3)(m_1 . m_2, x . m_2) = \varphi(m_3 . m_1 . m_2, x . m_2) = \varphi(m_3 . m_1, x) . m_2 = (\varphi . m_3)(m_1, x) . m_2 \]
+  This is indeed a right action, since
+  \[ ((\varphi . m_3) . m_4)(m_1, x) = (\varphi . m_3)(m_4 . m_1, x) = \varphi(m_3 . m_4 . m_1, x) = (\varphi . (m_3 . m_4))(m_1, x). \]
+  The evaluation map $ (X \Rightarrow Y) \times X \to Y $ sends $ (\varphi, x) $ to $ \varphi(I, x) $.
+This is universal since if we have a presheaf morphism $ e: Z \times X \to Y $, we can create a presheaf morphism $ u: Z \to (X \Rightarrow Y) $, given by
+  \[ u(z) = (m, x) \mapsto e(z . m, x) \]
+  This is an element of $ (X \Rightarrow Y) $ because
+  \[ u(z)(m_1 . m_2, x . m_2) = e(z . m_1 . m_2, x . m_2) = e(z . m_1, x) . m
+  2 = u(z)(m_1, x) . m_2 \]
+  It is a morphism of presheaves since
+  \[ u(z . m_1)(m_2, x) = e(z . m_1 . m_2, x) = u(z)(m_1 . m_2, x) = (u(z) . m_1)(m_2, x). \]
+  The map is unique since by the universal property and the fact that $ u(z) $ must be a presheaf morphism, we have for all $ z: Z $, $ m: M $ and $ x: X $,
+  \[ u(z)(m, x) = (u(z) . m)(I, x) = u(z . m)(I, x) = e(z . m, x). \]
+
+  \subsubsection{For our monoid}
+  We propose $ A(2) $ as an alternative candidate for the function space $ U_A \Rightarrow U_A $.
+Since $ A(2) $ is characterized by the equation $ a = APP\ \mathbf 1_2\ a $, and that the latter equals $ \mathbf 1 \circ a $, so that $ A(2) $ has a right action of $ A(1) $ (actually a right action of all of $ A $).
+
+  We can create a map from $ A(2) $ to $ U_A \Rightarrow U_A $, which sends an element $ a_1 $ to the map $ \phi(a_1) $ that sends $ (a_2, a_3) \in U_A \times U_A $ to
+  \[ (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a_1, a_2, a_3). \]
+  Note that this is equivariant, since
+  \begin{align*}
+    \phi(a_1)(a_2 \circ a_4, a_3 \circ a_4)
+    &= (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a_1, a_2 \circ a_4, a_3 \circ a_4)\\
+    &= (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a_1, (\lambda x_3, x_1 (x_2 x_3)) \bullet (a_2, a_4), (\lambda x_3, x_1 (x_2 x_3)) \bullet (a_3, a_4))\\
+    &= (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (x_1, (\lambda x_5, x_2 (x_4 x_5)), (\lambda x_5, x_3 (x_4 x_5))) \bullet (a_1, a_2, a_3, a_4)\\
+    &= (\lambda x_5, x_1 ((\lambda x_6, x_2 (x_4 x_6)) x_5) ((\lambda x_6, x_3 (x_4 x_6)) x_5)) \bullet (a_1, a_2, a_3, a_4)\\
+    &= (\lambda x_5, x_1 (x_2 (x_4 x_5)) (x_3 (x_4 x_5))) \bullet (a_1, a_2, a_3, a_4)\\
+    &= (\lambda x_5, (\lambda x_6, x_1 (x_2 x_6) (x_3 x_6)) (x_4 x_5)) \bullet (a_1, a_2, a_3, a_4)\\
+    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_5, x_1 (x_2 x_5) (x_3 x_5)), x_4) \bullet (a_1, a_2, a_3, a_4)\\
+    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a_1, a_2, a_3), a_4)\\
+    &= ((\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a_1, a_2, a_3)) \circ a_4\\
+    &= \phi(a_1)(a_2, a_3) \circ a_4.
+  \end{align*}
+
+  Also,
+  \[ \phi(a_1 \circ a_4) (a_2, a_3) = \lambda x_1, a_1 (a_4 (a_2 x_1)) (a_3 x_1) = u(a_1) (a_4 \circ a_2) (a_3), \]
+  so $ \phi $ is a map of presheaves.
+  \begin{lemma}
+    $ \phi $ is an isomorphism.
+  \end{lemma}
+  \begin{proof}
+    Take $ p = \lambda x_1, x_1 (\lambda x_2 x_3, x_2) $ and $ q = \lambda x_1, x_1 (\lambda x_2 x_3, x_3) $. These are elements of $ A(1) $. Note that for terms $ c_1, c_2 $
+    \begin{align*}
+      p (\lambda x_1, x_1 c_1 c_2)
+      &= (\lambda x_1, x_1 c_1 c_2) (\lambda x_2 x_3, x_2)\\
+      &= (\lambda x_1 x_3, x_2) c_1 c_2\\
+      &= c_1.
+    \end{align*}
+    In the same way, $ q \circ (\lambda x_1 x_2, x_2 c_1 c_2) = c_2 $.
+
+    An inverse is given by
+    \[ \psi: f \mapsto \lambda x_1 x_2, f(p, q)(\lambda x_3, x_3 x_1 x_2). \]
+
+    This is an inverse, because given $ f: U_A \Rightarrow U_A $ and$ (a_1, a_2): U_A \times U_A $, we have
+    \begin{align*}
+      \phi(\psi(f))(a_1, a_2) &= u(\lambda x_1 x_2, f(p, q)(\lambda x_3, x_3 x_1 x_2))(a_1, a_2)\\
+      &= \lambda x_1, (\lambda x_2 x_3, f(p, q)(\lambda x_4, x_4 x_2 x_3)) (a_1 x_1) (a_2 x_1)\\
+      &= \lambda x_1, f(p, q)(\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))\\
+      &= f(p, q) \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)))\\
+      &= f(p \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))), q \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))))\\
+      &= f(\lambda x_1, p (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)), \lambda x_1, q (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)))\\
+      &= f(\lambda x_1, a_1 x_1, \lambda x_1, a_2 x_1)\\
+      &= f(a_1, a_2).
+    \end{align*}
+    The last line is because $ a_i : A(1) $ and therefore $ \lambda x_1, a_i x_1 = a_i $.
+
+    On the other hand, if we have $ a_1: A(2) $, we have
+    \begin{align*}
+      \psi(\phi(a_1)) &= \psi((a_2, a_3) \mapsto \lambda x_1, a_1 (a_2 x_1) (a_3 x_1))\\
+      &= \lambda x_1 x_2, (\lambda x_3, a_1 (p x_3) (q x_3)) (\lambda x_3, x_3 x_1 x_2)\\
+      &= \lambda x_1 x_2, a_1 (p (\lambda x_3, x_3 x_1 x_2)) (q (\lambda x_3, x_3 x_1 x_2))\\
+      &= \lambda x_1 x_2, a_1 x_1 x_2\\
+      &= a_1.
+    \end{align*}
+    The last line is because $ a_1 : A(2) $ and therefore $ \lambda x_1 x_2, a_1 x_1 x_2 = a_1 $.
+
+    Therefore, this map is a bijection and an isomorphism.
+  \end{proof}
+
+  From this identification, we get an evaluation map on $ A(2) $. First of all, an element $ a_1 : A(2) $ is sent to the map
+  \[ (a_3, a_4) \mapsto (\lambda x_1, a_1 (a_3 x_1) (a_4 x_1)) \]
+  which, together with an element $ a_2: A(1) $ is sent to
+  \[ \lambda x_1, a_1 (I x_1) (a_2 x_1) \]
+  for $ I = \lambda x_1, x_1 $ the identity element of the monoid. This results in an evaluation map
+  \[ A(2) \times A(1) \to A(1) \quad (a_1, a_2) \mapsto \lambda x_1, a_1 x_1 (a_2 x_1). \]
+
+  ``In the same way'', we have $ U^n \Rightarrow U \cong A(n + 1) $, with evaluation
+  \[ (a, (b_1, \dots, b_n)) \mapsto \lambda x_1, a x_1 (b_1 x_1) \dots (b_n x_1). \]
+  and since
+  \[ A(n + 1) = \{ a : A \mid \mathbf 1_n \circ a = a \}, \]
+  we have a right action of $ A(1) $ on this set.
+
+  Now, note that for any $ a: A(1) $, if we take $ a^\prime := \mathbf 1 \circ a $, we have
+  \begin{align*}
+    \mathbf 1 \circ a^\prime &= \mathbf 1 \circ \mathbf 1 \circ a\\
+    &= (\lambda x_1 x_2, x_1 x_2) \circ (\lambda x_1 x_2, x_1 x_2) \circ a\\
+    &= \lambda x_1, (\lambda x_2 x_3, x_2 x_3) (\lambda x_2, x_1 x_2) \circ a\\
+    &= \lambda x_1, (\lambda x_2, (\lambda x_3, x_1 x_3) x_2)  \circ a\\
+    &= (\lambda x_1 x_2, x_1 x_2) \circ a\\
+    &= \mathbf 1 \circ a\\
+    &= a^\prime,
+  \end{align*}
+  so we have a mapping $ A(1) \to A(2) $, and an injection $ A(2) \hookrightarrow A(1) $.
+Since for all $ a : A(2) $, $ \mathbf 1 \circ a = a $, we have that composition on the left with $ \mathbf 1 $ gives a retraction from $ A(1) $ onto $ A(2) $ and the endomorphism theory of $ A(1) $ in $ PA $ is a $ \lambda $-theory.
+We call this $ \mathcal U_A $.
+
   \bibliographystyle{alpha}

### 2023-09-11 transcript/summary.tex
Write a summary of my work in week 36

@@
 
+  \chapter{Week 36}
+  \section{The Karoubi envelope}
+  Given a category $ \CC $, define a category $ \overline \CC $, with objects being pairs $ (A, e) $, with $ e: A \to A $ an idempotent.
+A map $ (A, e), (B, f) $ is a map $ v: A \to B $ such that $ f \circ v \circ e = v $.
+The identity on $ (A, e) $ is $ e $, since if $ f \circ v \circ e = v $, then $ v \circ e = f \circ v \circ e \circ e = f \circ v \circ e = v $ (and likewise for $ f \circ v = v $).
+
+  We can embed $ \CC $ into $ \overline \CC $ by sending $ A: \Ob \CC $ to $ (A, \mathop{Id}_A) $, and $ f: \Hom{\CC}{A}{B} $ to $ f $, since $ \mathop{Id}_B \circ f \circ \mathop{Id}_A = f $ is trivial.
+
+  Given an idempotent $ e: \Hom{\CC}{A}{A} $, take $ r = e: \Hom{\overline \CC}{(A, \mathop{Id}_A)}{(A, e)} $ and $ s = e: \Hom{\overline \CC}{(A, e)}{(A, \mathop{Id}_A)} $.
+Then $ r \circ s = e \circ e = e = \mathop{Id}_{(A, e)} $ and $ s \circ r = e \circ e = e $.
+Therefore, $ e $ splits in $ \overline \CC $.
+This also shows that any object $ (A, e) : \Ob{\overline \CC} $ is a retract of (the image of) an object in $ \CC $.
+That is why the paper refers to $ \overline \CC $ as ``the category of retracts''.
+
+  \section{Relatively cartesian closed}
+  Hyland gives a new proof that $ \overline(\mathcal L(1)) $ is cartesian closed (when viewing $ \mathcal L(1) $ as a monoid with operation $ \bullet $, and then as a one-object category), based on the proof in \cite{taylor}.
+
+  For a $ \Lambda $-algebra $ A $, we can take $ A(1) $, the set of functional elements of $ A $.
+This forms a monoid under composition: $ a; b = P a b $ for $ P = \lambda f g x, g(f x) $.
+The Karoubi completion of this category has as objects the terms $ a $ such that $ P a a = a $.
+The morphisms $ a \to b $ are elements $ f: A $ such that $ P a f = f = P f b $.
+
+  Since we view $ \overline{A(1)} $ as a category, we can try to define products and exponentials of elements $ A\ B: \overline{A(1)} $. This is done in \S\S 1.3.5 and 1.3.6.
+
+  Taylor defines a family $ (X_a)_{a: A} $ to be the \textit{display map} $ f: X \to A $ (the $ X_a $ arise as preimages/pullbacks of the $ a: A $).
+We have a category $ \CC^A $, consisting of families over $ A $.
+This is the slice category $ \CC / A $.
+If we have a morphism $ f: A \to B $, we get a functor $ \CC^f: \CC^B \to \CC^A $, which is the pullback along $ f $, and we will call it $ f^* $ or $ \texttt{P} f $.
+For a diagram
+  \begin{center}
+    \begin{tikzcd}
+      Y \arrow[d] & X \arrow[d]\\
+      A \arrow[r, "f"] & B
+    \end{tikzcd}
+  \end{center}
+  there is a natural bijection between morphisms $ Y \xrightarrow{f} X $ over $ f $, and morphisms $ Y \to f^* X $.
+
+  Pullbacks give binary products in $ \CC^A $. That is why these are also called ``fibred products''.
+
+  Now, for indexed products: In $ \SET $, given indexed sets $ (X_a)_{a : A} $, we have the product $ \prod_{a: A} X_a $.
+Its elements are indexed families of elements $ (x_a)_{a: A} $.
+If we have an element $ X: \CC^A $, the elements of $ \prod_{a : A} X_a $ correspond to maps $ \Hom{\CC^a}{A}{X} $, i.e., maps that send $ a $ to an element in $ X_a $.
+
+  The indexed product with a constant set $ \prod_{a: A} B $ is the exponential $ B^A $. Therefore, if a category has indexed products over itself, it is cartesian closed.
+
+  We can also do this in an indexed fasion.
+If we have a family $ B $ indexed over $ A $ (given by a morphism $ f: A \to B $), and for every $ a: A $, a family $ (X_b)_{b : B_a} $ (equivalent to a morphism $ X \to B $), then we can construct the products $ (\prod \alpha X)_a := (\prod_{b: B_a} X_b) $ for all $ a : A $.
+That means that we have the type $ \prod \alpha X $ over $ A $.
+
+  A morphism in $ \CC^A $ from $ C $ to $ (\prod \alpha X) $ is equivalent to a collection of morphisms $ \varphi_a: C_a \to (\prod \alpha X)_a = (\prod_{b: B_a} X_b) $.
+  This is equivalent to a collection of morphisms $ \varphi_{ab}: C_a \to X_b $ for all $ a: A $ and $ b: B_a $.
+  Note that $ a = \alpha b $, so $ C_a = C_{\alpha b} = (\alpha^* C)_b $.
+  So for all $ b: B $, we need a morphism $ (\alpha^* C)_b \to X_b $. However, this is a morphism $ \alpha^* C \to X $ over $ B $.
+  Therefore,
+  \[ \Hom{\CC^A}{C}{\prod \alpha X} \cong \Hom{\CC^B}{\alpha^* C}{X} \]
+  and the functor $ \prod \alpha: \CC^B \to \CC^A $ is a right adjoint to the functor $ \alpha^*: \CC^A \to \CC^B $.
+
+  For a morphism $ B \to A $ and a morphism $ X \to B $, we can take the indexed sums $ (\sum \alpha X)_a := (\sum_{b: B_a} X_b)_a $.
+
+  A morphism $ \sum \alpha X \to C $ in $ \CC^A $ is equivalent to a family of morphisms $ \varphi_a: \sum_{b: B_a} X_b \to C_a $.
+  This is equivalent to, for every $ a: A $ and every $ b: B_a $, a morphism $ \varphi_{ab}: X_b \to C_a = (\alpha^* C)_b $.
+  This is a morphism $ X \to \alpha^* C $ in $ \CC^B $, so $ \sum \alpha \dashv \alpha^* $.
+
+  Therefore, Taylor defines an internal product in an indexed category to be a right adjoint to substitution over a display map, and an internal sum to be a left adjoint.
+
+  \dots
+
+  Hyland's view of this matter is as follows:
+
+  Given a $ \lambda $-theory $ \mathcal L $, the category $ \mathbb R $ is the category of retracts of the idempotent elements of $ \mathcal L(0) $ (I think).
+That is: the objects of $ \mathbb R $ are elements $ a: \mathcal L(0) $, such that $ \lambda x, a (a x) = a $.
+Morphisms between idempotents $ a $ and $ b $ are elements $ f: \mathcal L(0) $ such that $ \lambda x, (b (f (a x))) = f $.
+
+  \section{The Curry Festschrift}
+  The Lambda calculus is a theory of functions.
+It specifies what one can do with functions (in a (concrete) cartesian closed category): One can abstract a function $ A \times B \to C $ to get a function $ A \to (B \to C) $; One can apply a function $ A \to B $ to an element of $ A $ to get an element of $ B $; And one always has the identity function $ x: A \to A $.
+
+  For the typed lambda calculus, the objects in $ \CC $ form the types, and the morphisms (elements of the exponential object) are the lambda terms.
+
+  For the untyped lambda calculus, we can say that all terms have the same domain and codomain $ U \to V $.
+However, since we can compose them with themselves, we must have $ U = V $.
+Also, given two terms $ f\ g: U \to U $, we can apply $ f $ to $ g $, so $ (U \to U) = U^U $ must be inside $ U $.
+Therefore, we want a section $ U^U \to U $ and a retraction $ U \to U^U $.
+
+  \section{Comparing Hyland, Taylor and Curry}
+  \subsection{Taylor}
+  Taylor defines a \textit{Combinatory prealgebra} to be a set $ \Lambda $ with a binary operation $ \bullet $ (``application'') and elements $ K $ ($ \lambda x y, x $) and $ S $ ($ \lambda x y z, x z (y z) $) such that for all $ a\ b\ c: \Lambda $, $ K a b := K \bullet a \bullet b = a $ and $ S a b c = a c (b c) $.
+
+  For $ f: \Lambda $, he defines $ f $ to be \textit{functional} if it has a representation $ f = \lambda x, a $.
+
+  He defines a \textit{Combinatory algebra} to be a prealgebra $ \Lambda $ such that if $ fx = gx $ (in $ \Lambda [x] $, i.e., $ \Lambda $ to which we adjoin an additional element $ x $), then $ f = g $.
+
+  He defines a \textit{model} to be a combinatory algebra $ \Lambda $, such that for all $ f\ g: \Lambda $, if for all $ a: \Lambda $, $ f a = g a $, then $ f = g $.
+
+  He then defines $ \mathbf{Retr}(\Lambda) $ to be the category of retracts of the monoid of functional elements in $ \Lambda $.
+An object is an element $ A: \Lambda $ such that $ P A A = A $, and a morphism $ A \to B $ is an element $ \alpha: \Lambda $ such that $ P A \alpha = \alpha = P \alpha B $.
+
+  % He notes that $ \mathbf{Retr}(\Lambda) $ is concrete iff $ \Lambda $ is a combinatory model (iff the monoid has enough constants).
+  He notes that we can view objects (idempotents) of $ \mathbf{Retr}(\Lambda) $ as types $ \Vert A \Vert = \{ a \mid a = A a \} \subseteq \Lambda $ and morphisms $ \alpha: \mathbf{Retr}(\Lambda)(A, B) $ as maps $ a \mapsto \alpha a: \Vert A \Vert \to \Vert B \Vert $.
+  % Take $ K = \lambda x y, x $ and $ \bot = (\lambda x, x x) (\lambda x, x x) $.
+Take $ T = K \bot = \lambda y, (\lambda x, x x) (\lambda x, x x) $.
+Then $ \Vert T \Vert = \{ \bot \} $ and every type $ A $ has a ``least'' element $ A \bot $.
+
+  At the end of chapter $ 1 $, he shows that $ \mathbf{Retr}(\Lambda) $ is cartesian closed.
+
+  In chapter 4, Taylor introduces a fibration.
+If $ \CC $ is a category and $ D $ is a class of morphisms, we say that $ D $ is a class of \textit{Display Maps} for $ \CC $ if $ D $ is closed under pullbacks along $ \CC $-morphisms, under composition and the maps to the terminal object are in $ D $.
+
+  Then, given any $ A: \mathcal C $, we can construct $ \CC /_{\mathcal D} A $ as a full subcategory of $ \CC / A $, containing as objects only the display maps to $ A $.
+The $ \CC /_{\mathcal D} A $ form a fibration over $ \CC $.
+
+  For $ \alpha: \CC(A, B) $, we have $ \alpha_*: \CC /_{\mathcal D} A \to \CC /_{\mathcal D} B $ ("the substitution functor").
+It has a left adjoint, given by postcomposition, which we will call $ \sum \alpha $.
+If it also has a right adjoint, (which we then call $ \prod \alpha $), we call the category relatively cartesian closed.
+
+  Taylor notes that $ \CC /_{\mathcal D} 1 $, the fiber over the terminal object, consists of all of $ \CC $.
+He also notes that a category that is relatively cartesian closed has cartesian closed fibers.
+
+  \subsection{Hyland}
+  Hyland defines an algebraic theory to be a functor $ \mathcal T: F \rightarrow \SET $, together with variables $ \pi_i : \mathcal T(n) $ for all $ 1 \leq i \leq n $, and an operation (``substitution'') $ \bullet: \mathcal T(m) \times \mathcal T(n)^m \to \mathcal T(n) $ which is associative, unital, dinatural.
+
+  He defines a $ \lambda $-theory to be an algebraic theory $ \mathcal L $, together with retractions $ \rho: \mathcal T(n) \to \mathcal T(n + 1) $, that are compatible with $ \bullet $ (which, on $ \mathcal T(n + 1) $, leaves alone the $ n + 1 $th component).
+
+  He defines $ \Lambda $ to be the $ \lambda $-theory corresponding to the $ \lambda $-calculus, with $ \Lambda(n) $ the set of lambda terms in $ n $ indeterminates.
+
+  Finally, he defines a $ \Lambda $-algebra (one would call this a ``model'') to be a set $ A $, together with an action $ \mathcal \Lambda(n) \times A^n \to A $ for all $ n $ that is associative and unital.
+
+  \subsection{Curry}
+
+  Curry does not give a formal characterization of the $ \lambda $-calculus (he refers to `Lambek's paper').
+However, he notes that there is a correspondence between cartesian closed categories, and `extensional typed $ \lambda $-calculi'.
+
+  This means that a typed $ \lambda $-calculus has at least an identity function $ x_1: A \to A $.
+He also notes that, given a term $ f: A \times B \to C $, we can abstract it to $ \lambda b, f: A \to (B \to C) $.
+Finally, given variables $ u: A \to B $ and $ v: A $, we have $ u (v): (A \to B) \times A \to B $.
+Therefore, we have abstraction and application.
+
+  He also notes that we need extensionality: if $ f = g $, then $ \lambda x, f = \lambda x, g $.
+
+  For the untyped $ \lambda $-calculus, he constructs the terms `in the usual way', by starting with variables $ x_1, \dots $ and then using abstraction and application.
+
+  He then constructs the category $ \mathbb R $ straightforwardly, with as objects the terms $ A $ without free variables, such that $ A = \lambda x, A (A x) $.
+The maps $ f: A \to B $ are terms $ f $ without free variables, for which we can prove $ f = \lambda x, B (f (A x)) $.
+
+  He also constructs products $ A \times B := \lambda u z, z(A(u(\lambda x y, x)))(B(u(\lambda x y, y))) $, with projections
+  \[ p_{AB} := \lambda u, (A \times B)(u)(\lambda xy, x) \quad \text{and} \quad q_{AB} := \lambda u, (A \times B) u (\lambda xy, y), \]
+  with the product of morphisms $ f: C \to A $ and $ g: C \to B $ being $ \langle f, g \rangle := \lambda t z, z(f t)(g t) $.
+
+  Finally, he defines the function space to be
+  \[ A \to B := \lambda f, B \circ f \circ A \]
+  with evaluation
+  \[ \varepsilon_{BC} = \lambda u, C(u(\lambda x y, x))(B(u(\lambda x y, y))) \]
+  and for $ h: A \times B \to C $,
+  \[ \Lambda_{ABC} h = \lambda x y, h (\lambda z, z x y). \]
+  He takes the reflexive object $ U := \lambda x, x $.
+
   \bibliographystyle{alpha}

### 2023-10-16 report/report.tex
Write a first version of the report, up to the representation theorem

\documentclass[a4paper]{amsbook}

\usepackage{hyperref}
\usepackage{tikz-cd}

\title{Semantics for the $ \lambda $-calculus}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\id}[1]{\ensuremath{\text{id}_{#1}}}
\newcommand\TODO{\textbf{(TODO)} }

\begin{document}
  \maketitle

  \tableofcontents

  \chapter{Definitions}

  \section{Algebraic Theories}

  \begin{definition}[algebraic theory]
    We define an algebraic theory $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we usually leave $ n $ implicit), together with a substitution operation
    \[ \_ \bullet \_: T_m \times T_n^m \to T_n \]
    for all $ m, n $, such that
    \begin{align*}
      x_j \bullet g &= g_j\\
      f \bullet (x_{l, i})_i &= f\\
      (f \bullet g) \bullet h &= f \bullet (g_i \bullet h)_i
    \end{align*}
    for all $ 1 \leq j \leq l $, $ f: T_l $, $ g: T_m^l $ and $ h: T_n^m $.
  \end{definition}

  \begin{definition}[algebraic theory morphism]
    A morphism $ F $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ F_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
    \begin{align*}
      F_n(x_j) &= x_j\\
      F_n(f \bullet g) &= F_m(f) \bullet (F_n(g_i))_i
    \end{align*}
    for all $ 1 \leq j \leq n $, $ f: T_m $ and $ g: T_n^m $.
  \end{definition}

  \begin{remark}
    We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
    \[ (f, f^\prime) \bullet (g, g^\prime) = (f \bullet g, f^\prime \bullet g^\prime). \]
    In the same way, the category of algebraic theories has all limits.
  \end{remark}

  \section{Algebras}

  \begin{definition}[algebra]
    An algebra $ A $ for an algebraic theory $ T $ is a set $ A $, together with an action
    \[ \bullet: T_n \times A^n \to A \]
    for all $ n $, such that
    \begin{align*}
      x_j \bullet a &= a_j\\
      (f \bullet g) \bullet a &= f \bullet (g_i \bullet a)_i
    \end{align*}
    for all $ j $, $ f: T_m $, $ g: T_n^m $ and $ a: A^n $.
  \end{definition}

  \begin{definition}[algebra morphism]
    For an algebraic theory $ T $, a morphism $ F $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ F: A \to A $ such that
    \[ F(f \bullet a) = f \bullet (F(a_i))_i \]
    for all $ f: T_n $ and $ a: A^n $.
  \end{definition}

  \begin{remark}
    The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying algebras.
  \end{remark}

  \begin{remark}
    Note that for an algebraic theory $ T $, the $ T_n $ are all algebras for $ T $, with the action given by $ \bullet $.
  \end{remark}

  \section{Presheaves}

  \begin{definition}[presheaf]
    A presheaf $ P $ for an algebraic theory $ T $ is a sequence of sets $ P_n $ indexed over $ \mathbb N $, together with an action
    \[ \bullet: P_m \times T_n^m \to P_n \]
    for all $ m, n $, such that
    \begin{align*}
      t \bullet (x_{l, i})_i &= t\\
      (t \bullet f) \bullet g &= t \bullet (f_i \bullet g)_i
    \end{align*}
    for all $ t: P_l $, $ f: T_m^l $ and $ g: T_n^m $.
  \end{definition}

  \begin{definition}[presheaf morphism]
    For an algebraic theory $ T $, a morphism $ F $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ F_n: P_n \to P^\prime_n $ such that
    \[ F_n(t \bullet f) = F_m(t) \bullet f \]
    for all $ t: P_m $ and $ f: T_n^m $.
  \end{definition}

  We will write $ PT $ for the category of $ T $-presheaves and their morphisms.

  \begin{remark}
    The category of presheaves has all limits. The $ n $th set $ \overline{P}_n $ of a limit $ \overline{P} $ of presheaves $ P_i $ is the limit of the $ n $th sets $ P_{i, n} $ of the presheaves in the limit diagram.
  \end{remark}

  \section{\texorpdfstring{$ \lambda $-}{lambda-}theories}

  \begin{definition}[$ \lambda $-theory]
    A $ \lambda $-theory is an algebraic theory $ L $, together with sequences of functions $ \lambda_n: L_{n + 1} \to L_n $ and $ \rho_n: L_n \to L_{n + 1} $, such that
    \begin{align*}
      \lambda(f) \bullet g &= \lambda(f \bullet (g_1, \dots, g_m, x_{n + 1}))\\
      \rho(f \bullet g) &= \rho(f) \bullet (g_1, \dots, g_m, x_{n + 1})\\
    \end{align*}
    for all $ f: L_m $ and $ g: L_n^m $. (\TODO: Fix)
  \end{definition}

  \begin{definition}[$ \beta $- and $ \eta $-equality]
    We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $. We say that is satisfies $ \eta $-equality if $ \lambda_n \circ \rho_n = \id{L_{n + 1}} $ for all $ n $.
  \end{definition}

  \begin{definition}[$ \lambda $-theory morphism]
    A morphism $ F $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ F $ such that
    \begin{align*}
      F_n(\lambda_n(f)) &= \lambda_n(F_{n + 1}(f))\\
      \rho_n(F_n(g)) &= F_{n + 1}(\rho_n(g))
    \end{align*}
    for all $ f: L_{n + 1} $ and $ g: L_n $.
  \end{definition}

  \begin{remark}
    The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories.
  \end{remark}

  A $ \lambda $-theory algebra or presheaf is a presheaf for the underlying algebraic theory.

  \chapter{Lemmas}

  \section{The endomorphism theory}

  \begin{definition}[Endomorphism theory]
    Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
    The endomorphism theory $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
  \end{definition}

  \begin{lemma}
    $ E(X) $ is indeed an algebraic theory.
  \end{lemma}
  \begin{proof}
    For $ 1 \leq j \leq l $, $ f: E(X)_l $, $ g: {E(X)_m}^l $ and $ h: {E(X)_n}^m $, we have
    \[ x_j \bullet g = x_j \circ \langle g_i \rangle_i = g_j, \]
    \[ f \bullet (x_{l,i})_i = f \circ \langle x_{l, i} \rangle_i = f \circ \id{X^l} = f \]
    and
    \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i. \]
  \end{proof}

  \begin{definition}[Endomorphism $ \lambda $-theory]
    Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $. Let, for $ Y: C $, $ \varphi_Y $ be the isomorphism $ C(X \times Y, X) \xrightarrow{\sim} C(Y, X^X) $.
    We can give $ E(X) $ a $ \lambda $-theory structure by setting, for $ f: E(X)_{n + 1} $ and $ g: E(X)_n $,
    \[ \lambda(f) = abs \circ \varphi_{X^n}(f) \qquad \rho(g) = \varphi_{X^n}^{-1}(app \circ g). \]
  \end{definition}

  \begin{lemma}
    $ E(X) $ is indeed a $ \lambda $-theory.
  \end{lemma}
  \begin{proof}
    Note that $ \varphi: C(- \times X, X) \xrightarrow{\sim} C(-, X^X) $ is a natural isomorphism, so for $ g: {E(X)_n}^m $, the following diagram commutes
    \begin{center}
      \begin{tikzcd}[column sep = 1in]
        C(X^m \times X, X) \arrow[r, "- \circ (\langle g_i \rangle_i \times \id X)"]\arrow[d, "\varphi_{X^m}", bend left] & C(X^n \times X, X^X) \arrow[d, "\varphi_{X^n}", bend left]\\
        C(X^m, X^X) \arrow[r, "- \circ \langle g_i \rangle_i"] \arrow[u, "\varphi_{X^m}^{-1}", bend left] & C(X^n, X^X) \arrow[u, "\varphi_{X^n}^{-1}", bend left]
      \end{tikzcd}
    \end{center}
    and note that $ \langle g_i \rangle_i \times \id X = \langle g_1, \dots, g_m, x_{n + 1} \rangle $. Then we have, for all $ f: E(X)_m $
    \begin{align*}
      \lambda_m(f) \bullet g &= abs \circ \varphi_{X^m}(f) \circ \langle g_i \rangle_i\\
      &= abs \circ \varphi_{X^n}(f \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle)\\
      &= \lambda_n(f \bullet (g_1, \dots, g_m, x_{n + 1}))
    \end{align*}
    and
    \begin{align*}
      \rho_n(f \bullet g) &= \varphi_{X^n}^{-1}(app \circ f \circ \langle g_i \rangle_i)\\
      &= \varphi_{X^m}^{-1}(app \circ f) \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle\\
      &= \rho_m(f) \bullet (g_1, \dots, g_m, x_{n + 1}).
    \end{align*}
  \end{proof}

  \section{The theory presheaf}

  \begin{definition}[The theory presheaf]
    Let $ T $ be an algebraic theory. We can turn $ T $ into an $ T $-presheaf $ \tilde T $ by setting $ \tilde T_n = T_n $ and using the substitution from $ T $:
    \[ \bullet: \tilde T_m \times T_n^m \to \tilde T_n. \]
  \end{definition}

  \begin{lemma}
    $ \tilde T $ is indeed a presheaf.
  \end{lemma}
  \begin{proof}
    For all $ t: \tilde T_l $, $ f: T_m^l $ and $ g: T_n^m $,
    \[ t \bullet (x_{l, i})_i = t \]
    and
    \[ (t \bullet f) \bullet g = t \bullet (f_i \bullet g)_i \]
    because $ T $ is an algebraic theory.
  \end{proof}

  \begin{lemma}
    Given an algebraic theory $ T $ and a $ T $-presheaf $ Q $, we have for all $ n $ a bijection of sets
    \[ \varphi: PT(\tilde T^n, Q) \cong Q_n. \]
  \end{lemma}
  \begin{proof}
    Take $ \varphi(f) = f_n(x_1, \dots, x_n) $.

    Conversely, take $ \varphi^{-1}(q) $ to be the presheaf morphism that sends $ t: T^n_m $ to $ q \bullet t : Q_m $. This is indeed a presheaf morphism, since for all $ t: T^n_l $ and $ f: T^l_m $,
    \[ \varphi^{-1}(q)(t \bullet f) = q \bullet t \bullet f = \varphi^{-1}(q)(t) \bullet f. \]

    Now, for a presheaf morphism $ f: T^n \to Q $ and $ t: T^n_m $, we have
    \[ \varphi^{-1}(\varphi(f))(t) = f_n(x_1, \dots, x_n) \bullet t = f_n((x_1, \dots, x_n) \bullet t) = f_n(t_1, \dots, t_n) = f_n(t). \]

    Conversely, given $ q: Q_n $, we have
    \[ \varphi(\varphi^{-1}(q)) = q \bullet (x_1, \dots, x_n) = q. \]
    which concludes the proof.
  \end{proof}

  \section{The `+l' presheaf}

  Let $ \iota_{m, n} : T_m \to T_{m + n} $ denote the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
  \[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \]
  and
  \[ \iota_{m, n}(f \bullet g) = f \bullet g \bullet (x_i)_i = f \bullet (g_i \bullet (x_j)_j)_i = f \bullet (\iota_{m, n}(g_i))_i. \]

  For tuples $ x : X^m $ and $ y: X^n $, let $ x + y $ denote the tuple $ (x_1, \dots, x_m, y_1, \dots, y_n) : X^{m + n} $.

  \begin{definition}[The `+l' presheaf]
    Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, l) $, given by $ A(Q, l)_n = Q_{n + l} $. Then, for $ q: A(Q, l)_m $ and $ f: T_n^m $, the substitution is given by
    \[ q \bullet_{A(Q, l)} f = q \bullet_Q ((\iota_{n, l} (f_i))_i + (x_{n + i})_i) \]
  \end{definition}
  \begin{lemma}
    The +l presheaf is a presheaf
  \end{lemma}
  \begin{proof}
    We have, for $ q: A(Q, l)_n $,
    \begin{align*}
      q \bullet_{A(Q, l)} (x_i)_i &= q \bullet_Q ((\iota_{n, l}(x_i))_i + (x_{n + i})_i)\\
      &= q \bullet_Q ((x_i)_i + (x_{n + i})_i)\\
      &= q \bullet_Q (x_i)_i\\
      &= q.
    \end{align*}
    We have, for $ q : A(Q, k)_l $, $ f: T_m^l $ and $ g: T_n^m $,
    \begin{align*}
      q \bullet_{A(Q, k)} f \bullet_{A(Q, k)} g &= q \bullet_Q ((\iota_{m, l}(f_i))_i + (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(g_i))_i + (x_{n + i})_i)\\
      &= q \bullet_Q (((\iota_{m, l}(f_i) \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i + (x_{m + i} \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i))\\
      &= q \bullet_Q ((f_i \bullet_T (\iota_{n, l}(g_j))_j)_i + (x_{n + i})_i)\\
      &= q \bullet_Q ((\iota_{n, l}(f_i \bullet_T g))_i + (x_{n + i})_i)\\
      &= q \bullet_{A(Q, k)} (f_i \bullet_T g).
    \end{align*}
  \end{proof}

  \section{Exponentiability of the theory presheaf}

  \begin{lemma}
    For all $ l $, the presheaf $ \tilde T^l $ is exponentiable.
  \end{lemma}
  \begin{proof}
    We will show that $ A(-, l) $ constitutes a right adjoint to the functor $ - \times \tilde T^l $. We will do this using universal arrows (\cite{MacLane}, Chapter IV.1, Theorem 2 (iv)). To that end, we will need for all $ Q: PT $ a universal arrow $ \varphi: A(Q, l) \times \tilde T^l \to Q $.

    For $ q: A(Q, l)_n = Q_{n + l} $ and $ t: \tilde T^l_n $, we take $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $.

    This is a presheaf morphism, since for all $ q: A(Q, l)^l_m $, $ t: \tilde T^l_m $ and $ f: T_n^m $,
    \begin{align*}
      \varphi((q, t) \bullet_{A(Q, l) \times \tilde \tilde T^l} f) &= \varphi(q \bullet_{A(Q, l)} f, t \bullet_{\tilde T^l} f)\\
      &= q \bullet_{A(Q, l)} f \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
      &= q \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i) \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
      &= q \bullet_Q ((\iota_{n, l}(f_i) \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i + (x_{n + i} \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i)\\
      &= q \bullet_Q ((f_i \bullet_T (x_j)_j)_i + ((t \bullet_{\tilde T^l} f)_i)_i)\\
      &= q \bullet_Q ((f_i)_i + (t_i \bullet_{\tilde T} f)_i)\\
      &= q \bullet_Q ((x_i \bullet_T f)_i + (t_i \bullet_T f)_i)\\
      &= q \bullet_Q ((x_i)_i + t) \bullet_Q f\\
      &= \varphi(q, t) \bullet_Q f.
    \end{align*}

    Now, given any presheaf $ Q^\prime : P T $ we need to show that any morphism $ \psi: Q^\prime \times \tilde T^l \to Q $ factors uniquely as $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) $ for some $ \tilde \psi: Q^\prime \to A(Q, l) $.

    So, given such a $ \psi $, and given $ q: Q^\prime_n $, we take $ \tilde \psi(q) = \psi(\iota_{n, l}(q), (x_{n + i})_i) $

    This is a presheaf morphism, since for all $ q: Q^\prime_m $ and $ f : T_n^m $,
    \begin{align*}
      \tilde \psi(q \bullet f) &= \psi(\iota_{n, l}(q \bullet f), (x_{n + i})_i)\\
      &= \psi(q \bullet (\iota_{n, l}(f_i))_i, (x_{n + i})_i)\\
      &= \psi((\iota_{m, l}(q), (x_{m + i})_i) \bullet_{Q^\prime \times \tilde T^l} ((\iota_{n, l}(f_i))_i + (x_{n + i})_i))\\
      &= \psi(\iota_{m, l}(q), (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i)\\
      &= \tilde \psi(q) \bullet_{A(Q, l)} f.
    \end{align*}
    Note that indeed $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) = \psi $:
    \begin{align*}
      \varphi(\tilde \psi(q), t) &= \varphi(\psi(\iota_{n, l}(q), (x_{n + i})_i), t)\\
      &= \psi(\iota_{n, l}(q), (x_{n + i})_i) \bullet ((x_i)_i + t)\\
      &= \psi(\iota_{n, l}(q) \bullet ((x_i)_i + t), (x_{n + i})_i \bullet ((x_i)_i + t))\\
      &= \psi(q \bullet (x_i)_i, (t_i)_i)\\
      &= \psi(q, t).\\
    \end{align*}
    Now, suppose that we have another $ \tilde \psi^\prime : Q^\prime \to A(Q, l) $ such that $ \varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}) = \psi $. Then we have
    \begin{align*}
      \tilde \psi(q) &= \psi(\iota_{n, l}(q), (x_{n + i})_i)\\
      &= (\varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}))(\iota_{n, l}(q), (x_{n + i})_i)\\
      &= \varphi(\tilde \psi^\prime(\iota_{n, l}(q)), (x_{n + i})_i)\\
      &= \tilde \psi^\prime(\iota_{n, l}(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
      &= \iota_{n, l}(\tilde \psi^\prime(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
      &= \tilde \psi^\prime(q) \bullet (x_i)_i\\
      &= \tilde \psi^\prime(q),
    \end{align*}
    so $ \tilde \psi $ is unique, which completes the proof.
  \end{proof}

  Now, this adjunction $ - \times \tilde T^l \dashv A(-, l) $ induces a natural isomorphism
  \[ \varphi: PT(- \times \tilde T^l, \tilde T) \xrightarrow{\sim} PT(-, A(\tilde T, l)) \]
  \begin{lemma}
    For all $ f: PT(\tilde T^n \times \tilde T^l, \tilde T) $,
    \[ \varphi_{\tilde T^n}(f)(q) = f(\iota_{m, l}(q), (x_{m + i})_i) \]
  \end{lemma}
  \begin{proof}
    \TODO
  \end{proof}

  \begin{lemma}
    For all $ f: PT(\tilde T^n, A(\tilde T, l)) $,
    \[ \varphi_{\tilde T^n}^{-1}(f)(q, t) = f(q) \bullet ((x_i)_i + t). \]
  \end{lemma}
  \begin{proof}
    \TODO
  \end{proof}

  \chapter{Theorems}

  \section{Scott's Representation Theorem}
  \begin{theorem}
    Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E(\tilde L) $ of $ \tilde L $ in the presheaf category of $ L $.
  \end{theorem}
  \begin{proof}
    First of all, remember that $ \tilde L $ is indeed exponentiable and that $ \tilde L^{\tilde L} = A(\tilde L, 1) $.
    Now, since $ L $ is a $ \lambda $-theory, we have functions back and forth $ \lambda: A(\tilde L, 1) \to \tilde L $ and $ \rho: \tilde L \to A(\tilde L, 1) $. These are presheaf morphisms because for all $ f: A(\tilde L, 1)_m $ and $ g: \tilde L_m $ and $ t: T_n^m $,
    \[ \lambda(f \bullet_{A(\tilde L, 1)} t) = \lambda(f \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1}))) = \lambda(f) \bullet_{\tilde L} t \]
    and
    \[ \rho(g \bullet_{\tilde L} t) = \rho(g) \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1})) = \rho(g) \bullet_{A(\tilde L, 1)} t. \]
    Therefore, $ E(\tilde L) $ is indeed a $ \lambda $-theory.

    For any presheaf $ Q $ and for any $ n $, we have a bijection $ PL(L^n, Q) \cong Q_n $.
    Then we have $ \varphi: E(\tilde L)_n \cong L_n $.
    This bijection is an isomorphism of $ \lambda $-theories, since it preserves the $ x_i $, $ \bullet $, $ \rho $ and $ \lambda $: for all $ 1 \leq j \leq n $, $ f: E(\tilde L)_m $, $ g: E(\tilde L)_{m + 1} $ and $ h: E(\tilde L)_n^m $.
    \begin{align*}
      \varphi(x_j) &= x_j(x_1, \dots, x_n)\\
      &= x_j;\\
      \varphi(f \bullet h) &= f \circ \langle h_i \rangle_i((x_i)_i)\\
      &= f((h_i((x_j)_j))_i)\\
      &= f((x_i)_i \bullet (h_i((x_j)_j))_i)\\
      &= f((x_i)_i) \bullet (h_i((x_j)_j))_i\\
      &= \varphi(f) \bullet (\varphi(h_i))_i;\\
      \varphi(\rho(f)) &= \rho(f)((x_i)_i)\\
      &= \rho(f((x_i)_i)) \bullet (x_i)_i\\
      &= \rho(f((x_i)_i))\\
      &= \rho(\varphi(f));\\
      \varphi(\lambda(g)) &= \lambda(g)((x_i)_i)\\
      &= \lambda(\varphi_{X^n}(g)((x_i)_i))\\
      &= \lambda(g(\iota_{m, l}((x_i)_i) + (x_{m + 1})))\\
      &= \lambda(g((x_i)_i))\\
      &= \lambda(\varphi(g)).
    \end{align*}
  \end{proof}

  \section{Locally cartesian closedness of the category of retracts}
  \begin{theorem}
    The category of retracts \TODO is locally cartesian closed \TODO.
  \end{theorem}

  \section{The Fundamental Theorem of the \texorpdfstring{$ \lambda $-}{lambda }calculus}
  \begin{theorem}
    There exists an adjoint equivalence between the category of $ \lambda $-theories, and the category of algebras of $ \Lambda $ \TODO.
  \end{theorem}
  \begin{proof}
    In one direction, the proof sends a $ \lambda $-theory $ L $ to the $ L $-algebra $ L(0) $ \TODO. Since $ \Lambda $ is the initial $ \lambda $-theory \TODO, we can give $ L(0) $ a $ \Lambda $-algebra structure \TODO. This constitutes a functor \TODO.

    In the other direction, it sends a $ \Lambda $-algebra $ A $ to the theory of extensions $ \Lambda_A $ \TODO. It is a $ \lambda $-theory because it is isomorphic \TODO to the endomorphism $ \lambda $-theory $ E(A(1)) $ of the object $ A(1) $ in $ PA $ \TODO.

    These constitute an adjoint equivalence. \TODO
  \end{proof}

  \bibliographystyle{alpha}
  \bibliography{citations}

\end{document}

### 2023-10-16 transcript/summary.tex
Write a first version of the report, up to the representation theorem

@@
 \newcommand{\op}[1]{\ensuremath{{#1}^\text{op}}}
+\newcommand{\id}[1]{\ensuremath{\text{id}_{#1}}}
 
@@
   \begin{itemize}
+    \item Make sure that every file is mentioned in \texttt{.package/files} and in \texttt{UniMath/UniMath/CONTENTS.md}.
+    \item Make sure that every file has a comment at the top, explaining what it does.
     \item Make sure that all variables in intros and induction (that are used later) are introduced by name;
-    \item Make sure that \texttt{use} is replaced by \texttt{apply} and \texttt{apply} by \texttt{exact} wherever possible;
   \end{itemize}
@@
 
+  \chapter*{Week 37}
+  \section{The Taylor fibration (continued)}
+  Hyland takes, for $ X \in P(\mathcal L) $, the category $ \mathbb R(X) $ to be the category of retracts of $ \Delta_X(U) = (U \times X \to X) $ in $ P(\mathcal L) / X $, for $ U = \mathcal L $.
+
+  Given an element $ f: \Ob{\mathbb R(X)} $.
+This is an idempotent $ f: \Delta_X(U) \to \Delta_X(U) $.
+I.e., a morphism $ f: U \times X \to U \times X $, such that $ \Delta_X(U) \circ f = \Delta_X(U) $ (so it must respect fibers over $ X $) and $ f \circ f = f $.
+This is equivalent to a morphism $ f: U \times X \to U $ such that $ f \circ \langle f, \pi_r \rangle = f $.
+
+  Then, given any $ \alpha: X^\prime \to X $. For our pullback, set $ \alpha^* f := f \circ (\id U \times \alpha) : U \times X^\prime \to U $. Then
+  \begin{align*}
+    \alpha^* f \circ \langle \alpha^* f, \pi_r \rangle
+    &= f \circ (\id U \times \alpha) \circ \langle f \circ (\id U \times \alpha), \pi_r \rangle\\
+    &= f \circ \langle f \circ (\id U \times \alpha), \alpha \circ \pi_r \rangle\\
+    &= f \circ \langle f \circ (\id U \times \alpha), \pi_r \circ (\id U \times \alpha) \rangle \\
+    &= f \circ \langle f, \pi_r \rangle \circ (\id U \times \alpha)\\
+    &= f \circ (\id U \times \alpha),
+  \end{align*}
+  so $ \alpha^* f $ is an idempotent.
+
+  Now, if we have subsets $ S(n) \subseteq \mathcal L(n) $, such that for all $ f \in S(m) $ and $ g: \mathcal L(n)^m $, $ f \bullet g \in S(n) $, $ S $ is an object in $ P(\mathcal L) $, with action $ \bullet: S(m) \times \mathcal L(n)^m \to S(n) $.
+
+  For example, given $ A: \mathcal L(0) $, we can view $ A $ as an element of $ P(\mathcal L) $ by taking
+  \[ \overline A(n) := \{ a: \mathcal L(n) \mid A a = a \}. \]
+  In that case, for $ a: \overline A(m) $ and $ g: \mathcal L(n)^m $, we have
+  \[ A (a \bullet g)
+    = \rho(A) \bullet a \bullet g
+    = a \bullet g, \]
+  so $ a \bullet g \in \overline A(n) $.
+
+  Hyland claims that the category $ \mathbb R $ of retracts is a subcategory of $ P(\mathcal L) $.
+Note that the objects in the category of retracts are the idempotents of $ \mathcal L(0) $.
+Therefore, they are elements of $ \mathcal L(0) $, and by the above, we can embed them into $ P(\mathcal L) $.
+Also, suppose that we have a morphism $ f: \Hom{\mathbb R}{A}{B} $.
+It is an element $ f: \mathcal L(0) $ such that $ f A = f = B f $.
+Then $ a \mapsto f a $ gives functions $ \overline A(n) \to \overline B(n) $.
+The transformation is natural, and for $ a: \overline A(m) $ and $ g: \mathcal L(n)^m $, we have
+  \[ f (a \bullet g) = \rho(f) \bullet a \bullet g = (f a) \bullet g, \]
+  so it preserves the action of $ \mathcal L $.
+
+  Conversely, given a morphism $ f: \overline A \to \overline B $, to have a full functor, we would want $ f(\rho(A)) $ to be equal to $ \rho(C) $ for some $ C: \mathcal L(0) $ with $ CA = C = BC $.
+
+  Hyland also claims that for some $ X: P(\mathcal L) $, if $ X: \mathbb R $, then $ \mathbb R(X) \subseteq \mathbb R $.
+
+  Suppose that we have an element $ Y: P(\overline A) $ for some idempotent $ A: \mathcal L(0) $.
+Then $ Y $ is an idempotent $ \Delta_{\overline A}(U) \to \Delta_{\overline A}(U) $, so $ Y $ consists of a morphism $ f: \mathcal L \times \overline A \to \mathcal L $, such that for all $ (l, a) $, $ f(f(l, a), a) = f(l, a) $.
+
+  Note that this is equivalent to a morphism $ f: \overline A \to \mathcal L(n + 1) $.
+
+  Note that $ f(l, a) = f(x_1 \bullet (l, a), A x_2 \bullet (l, a)) = f(x_1, A x_2) \bullet (l, a) $.
+
+  So we want to find an idempotent $ B: \mathcal L(0) $ such that $ Y = \overline B $.
+
+  \chapter*{Week 39}
+
+  \section{The coproduct}
+  The coproduct $ A + B $ is defined as the following end
+  \[ \int^{m, n} A^m \times B^n \times \mathcal T(m + n). \]
+  This consists of an algebraic theory $ C $, together with morphisms $ e_{m, n}: A^m \times B^n \times \mathcal T(m + n) \to C $, such that for all $ f: m \to m^\prime $ and $ g: n \to n^\prime $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}[column sep=1.5in]
+      A^{m^\prime} \times B^{n^\prime} \times \mathcal T(m + n) \arrow[r, "{\id{A^{m^\prime} \times B^{n^\prime}} \times \mathcal T(f + g)}"] \arrow[d, "{A^f \times B^g \times \id{\mathcal T(n + m)}}"] & A^{m^\prime} \times B^{n^\prime} \times \mathcal T(m^\prime + n^\prime) \arrow[d, "{e_{m^\prime, n^\prime}}"]\\
+      A^m \times B^n \times \mathcal T(m + n) \arrow[r, "{e_{m, n}}"] & C,\\
+    \end{tikzcd}
+  \end{center}
+  (such a $ C $ is called a co-wedge) and such that for any cowedge $ C^\prime $, i.e., every object $ C^\prime $ with morphisms $ e^\prime_{m, n}: A^m \times B^n \times \mathcal T(m + n) \to C^\prime $ that make the diagram commute, there exists a morphism $ F : C \to C^\prime $ making the following diagram commute.
+  \begin{center}
+    \begin{tikzcd}
+      A^{m^\prime} \times B^{n^\prime} \times \mathcal T(m + n) \arrow[r] \arrow[d] & A^{m^\prime} \times B^{n^\prime} \times \mathcal T(m^\prime + n^\prime) \arrow[d] \arrow[rdd, "{e^\prime_{m^\prime, n^\prime}}", bend left] & \\
+      A^m \times B^n \times \mathcal T(m + n) \arrow[r] \arrow[rrd, "{e^\prime_{m, n}}", bend right] & C \arrow[rd, "\exists! F", dashed] & \\
+      & & C^\prime
+    \end{tikzcd}
+  \end{center}
+  If we interpret this in the category of sets, we only need an action of $ \mathcal T $ to make this into an algebra.
+To this end, note that $ \int^{m, n} A^m \times B^n \times \mathcal T(m + n) $ is a sifted colimit, so it commutes with finite limits:
+  \[ \left( \int^{m, n} A^m \times B^n \times \mathcal T(m + n) \right)^l = \int^{m, n} \left( A^l \right)^m \times \left( B^l \right)^n \times \mathcal T(m + n)^l. \]
+  We will call this cowedge $ e^\prime: \left( A^l \right)^m \times \left( B^l \right)^n \times \mathcal T(m + n)^l \to C^l $.
+Now, given an element $ s: \mathcal T(l) $, we obtain a cowedge structure for $ C^l $ on $ C $, with morphisms
+  \[ e^{\prime\prime}_{m, n}: \left( A^l \right)^m \times \left( B^l \right)^n \times \mathcal T(m + n)^l \to C \]
+  sending $ (a_1, \dots, a_m, b_1, \dots, b_n, t) $ to
+  \[ e_{ml, nl} (a_{11}, \dots, a_{1l}, \dots, a_{ml}, b_{11}, \dots, b_{nl}, s \bullet (t_i \bullet (x_i, x_{l + i}, \dots, x_{(m + n)l + i}))_i). \]
+  We need to check that this forms a cowedge.
+
+  Also, for a monoid, we need $ ((a_1, a_2), (), x_1 x_2) $ and $ ((a_1 a_2), (), x_1) $ to map to the same element in $ A + B $.
+
+  Indeed, given $ f: n \to n^\prime $, $ g: m \to m^\prime $, we have
+  \begin{center}
+    \begin{tikzcd}[column sep=1.3in]
+      \left( A^l \right)^{m^\prime} \times \left( B^l \right)^{n^\prime} \times \mathcal T(m + n)^l
+        \arrow[r, "{\id{\left( A^l \right)^{m^\prime} \times \left( B^l \right)^{n^\prime}} \times \mathcal T(f + g)^l}"]
+        \arrow[d, "{\left( A^l \right)^f \times \left( B^l \right)^g \times \id{\mathcal T(n + m)^l}}"]
+      & \left( A^l \right)^{m^\prime} \times \left( B^l \right)^{n^\prime} \times \mathcal T(m^\prime + n^\prime)^l
+        \arrow[d, "{e^{\prime \prime}_{m^\prime, n^\prime}}"]
+      \\ \left( A^l \right)^m \times \left( B^l \right)^n \times \mathcal T(m + n)^l
+        \arrow[r, "{e^{\prime \prime}_{m, n}}"]
+      & A^m \times B^n \times \mathcal T(m + n) \arrow[d, "{e_{m, n}}"]
+      \\
+      & C\\
+    \end{tikzcd}
+  \end{center}
+  so we obtain a function $ C^l \to C $.
+
   \bibliographystyle{alpha}

### 2023-10-19 report/planning.tex
Add a planning, add half of the proof of the equivalence between lambda algebras and lambda theories

\documentclass{amsart}

\usepackage{a4wide}

\title{Planning}

\begin{document}
  \maketitle

  \section{Global planning}
  \begin{tabular}{l|l|l|l}
    \textbf{Activity} & \textbf{Priority} & \textbf{Duration} & \textbf{Done by}\\\hline
    Prove isomorphism between theories and algebras & High & 2 weeks & November 3\\\hline
    Polish code and do write-up & High & 1 week & November 10\\\hline
    Research and write-up for category of retracts & Middle & 2 weeks & November 24\\\hline
    Formalization of category of retracts & Middle & 2 weeks & December 8\\\hline
    Polish code & Middle & 1 week & December 15\\\hline
    Formalization of isomorphism between $ U_A $ and $ \Lambda_A $ & Middle & 1 week & December 22\\\hline
    Write-up and polishing & Middle & 1 week & December 29\\\hline
    Christmas & High & 2 weeks & January 12\\\hline
    Unforeseen problems & High & 3 weeks & February 2
  \end{tabular}

  \section{Isomorphism}
  \begin{tabular}{r|l}
    1/2 day\phantom{s} & Initiality of $ \Lambda $\\
    1/2 day\phantom{s} & The functor from lambda theories to $ \Lambda $-algebras\\
    1/2 day\phantom{s} & Definition of the presheaf category\\
    1/2 day\phantom{s} & The object $ A(1) $\\
    1/2 day\phantom{s} & Exponentiability of $ A(1) $\\
    1/2 day\phantom{s} & $ A(1)^{A(1)} \cong A(2) $\\
    2 days & Isomorphism between $ L $ and $ E(A(1)) $\\
    1/2 day\phantom{s} & Faithful functor\\
    1/2 day\phantom{s} & Induced functor on presheaf categories\\
    1/2 day\phantom{s} & Preserves products\\
    1/2 day\phantom{s} & Map from $ E(A(1)) $ to $ E(A^\prime(1)) $\\
    1/2 day\phantom{s} & Map equals $ f $, so functor is full\\\hline
    \textbf{7 1/2 days}
  \end{tabular}

\end{document}

### 2023-10-19 report/report.tex
Add a planning, add half of the proof of the equivalence between lambda algebras and lambda theories

@@
 \newcommand{\id}[1]{\ensuremath{\text{id}_{#1}}}
+\newcommand{\op}[1]{\ensuremath{#1^{\text{op}}}}
+\newcommand\SET{\mathbf{SET}}
 \newcommand\TODO{\textbf{(TODO)} }
@@
   \section{Locally cartesian closedness of the category of retracts}
+  \begin{definition}[Category of retracts]
+    The category of retracts for a $ \lambda $-theory $ L $ is the category with objects $ f: L_n $ such that $ f \bullet f = f $ and it has as morphisms $ g: f \to f^\prime $ the terms $ g: L_n $ such that $ f^\prime \bullet g \bullet f = g $.
+The object $ f: L_n $ has identity element $ f $, and we have composition $ g \circ g^\prime = g \bullet g^\prime $.
+These are morphisms \TODO
+  \end{definition}
+
+  \begin{lemma}
+    The category of retracts is indeed a category.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
   \begin{theorem}
-    The category of retracts \TODO is locally cartesian closed \TODO.
+    The category of retracts is locally cartesian closed \TODO.
   \end{theorem}
@@
   \section{The Fundamental Theorem of the \texorpdfstring{$ \lambda $-}{lambda }calculus}
+
+  \begin{definition}[$ \Lambda $]
+    There is a special $ \lambda $-theory, given by the $ \lambda $-calculus itself.
+$ \Lambda_n $ is the set of $ \lambda $-terms with $ n $ free variables, the $ x_i $ are the free variables, and $ \bullet $ is given by substitution.
+$ \lambda $ sends $ f: \Lambda_{n + 1} $ to $ \lambda x_{n + 1}, f $ and $ \rho $ sends $ f: \Lambda_n $ to $ \iota_{n, 1}(f) x_{n + 1} $ in $ \Lambda_n $.
+  \end{definition}
+
+  \begin{lemma}
+    $ \Lambda $ is indeed a $ \lambda $-theory.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{lemma}
+    $ \Lambda $ is the initial $ \lambda $-theory.
+  \end{lemma}
+  \begin{proof}
+    Given a $ \lambda $-theory $ L $, we construct a morphism $ f: \Lambda \to L $ by induction on the $ \lambda $-terms.
+We set $ f(x_i) = x_i $, $ f(\lambda(t)) = \lambda(f(t)) $ and $ f(st) = \rho(f(s)) \bullet ((x_i)_i + (f(t))) $.
+
+    This is a $ \lambda $-theory morphism because \TODO
+
+    It is unique, since \TODO
+  \end{proof}
+
+  \begin{definition}[Pullback of algebras]
+    If we have a morphism of algebraic theories $ f: T^\prime \to T $, we have a functor $ AT \to AT^\prime $.
+
+    On objects, it sends a $ T $-algebra $ A $ to a $ T^\prime $-algebra with set $ A $ and action $ g \bullet_{T^\prime} a = f(g) \bullet_T a $. This is a $ T^\prime $-algebra because \TODO.
+
+    On morphisms, it sends $ \varphi: A \to A $ to $ \varphi: A \to A $. This is a $ T^\prime $-algebra morphism because for all $ g: T^\prime_n $ and $ a: A^n $, we have
+    \[ \varphi(g \bullet_{T^\prime} a) = \varphi(f(g) \bullet_T a) = f(g) \bullet_T \varphi(a) = g \bullet_{T^\prime} \varphi(a). \]
+  \end{definition}
+  \begin{lemma}
+    This is indeed a functor.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{definition}[Term algebra]
+    Given an algebraic theory $ T $, for every $ n $, $ T_n $ together with the action operator $ \bullet: T_m \times T_n^m \to T_n $ gives a $ T $-algebra.
+  \end{definition}
+
+  \begin{lemma}
+    $ T_n $ is indeed a $ T $-algebra.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{definition}
+    For all $ n $, we have a functor from lambda theories to $ \Lambda $-algebras.
+It sends the $ \lambda $-theory $ L $ to the $ L $-algebra $ L_n $ and then turns this into a $ \Lambda $-algebra via the morpism $ \Lambda \to L $.
+
+    It sends morphisms $ f: L \to L^\prime $ to $ f_n : L_n \to L^\prime_n $. This is a $ \Lambda $-algebra morphism because \TODO
+  \end{definition}
+
+  \begin{lemma}
+    This indeed constitutes a functor.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{remark}
+    Note that for a monoid $ M $, if we view $ M $ as a category, the category $ [\op{M}, \SET] $ consists of sets with a right $ M $-action.
+  \end{remark}
+
+  \begin{definition}[The exponential object in the presheaf category]
+    Given a monoid $ M $, if we have two presheaves (sets with right $ M $-actions) $ P $ and $ P^\prime $, we have a set of $ M $-equivariant maps
+    \[ F_{P, P^\prime} = \left\{ f: M \times P \to P^\prime \mid \prod_{p : P, m, m^\prime: M} f(m, p)m^\prime = f(m m^\prime, p m^\prime) \right\} \]
+    with a right $ M $-action, given by $ f m^\prime(m, p) = f(m^\prime m, p) $. This is again $ M $-equivariant because
+    \[ fm^\prime(m, p)m^{\prime \prime} = f(m^\prime m, p)m^{\prime \prime} = f(m^\prime m m^{\prime \prime}, p m^{\prime \prime}) = f m^\prime(m m^{\prime \prime}, p m^{\prime \prime}), \]
+    so $ F_{P, P^\prime} $ is a presheaf.
+
+    Now, to show that $ F_{P, P^\prime} $ is the exponential object $ {P^\prime}^P $, we show that for any $ P $, $ F_{P, -} $ is the left adjoint of $ - \times P $.
+So we need for all $ P^\prime: PT $, a universal arrow $ \varphi: F_{P, P^\prime} \times P \to P^\prime $.
+
+    First of all, we have an evaluation map $ \varphi: F_{P, P^\prime} \times P \to P^\prime $ given by $ (f, p) \mapsto f(I, p) $ for $ I $ the unit of the monoid.
+This map is equivariant because for all $ m $,
+    \[ (f, p) m = (f m, p m) \mapsto f m(I, p m) = f(m, p m) = f(I, p) m. \]
+    Now, given any presheaf $ Q $ and any morphism $ \psi: Q \times P \to P^\prime $, take $ \tilde \psi: Q \to F_{P, P^\prime} $ given by $ \psi(q)(m, p) = \psi(q m, p) $. This is equivariant because
+    \[ \tilde \psi(q)m(m^\prime, p) = \tilde \psi(q)(m m^\prime, p) = \psi(q m m^\prime, p) = \tilde \psi(q m)(m^\prime, p) \]
+    and we have
+    \[ \varphi(\tilde \psi(q), p) = \tilde \psi(q)(I, p) = \psi(q, p). \]
+    Now, suppose that we have $ \tilde \psi^\prime: Q \to F_{P, P^\prime} $ such that $ \varphi \circ (\tilde \psi^\prime \times \id{P}) = \psi $. Then for all $ q : Q $, $ m: M $ and $ p: P $,
+    \[ \tilde \psi(q)(m, p) = \psi(q m, p) = \varphi(\tilde \psi^\prime(q m), p) = \tilde \psi^\prime(q m)(I, p) = \psi^\prime(q) m(I, p) = \psi^\prime(q)(m, p), \]
+    so $ \tilde \psi $ is unique and $ F_{P, P^\prime} $ is an exponential object.
+  \end{definition}
+
+  \begin{definition}[n-functional terms]
+    Let $ A $ be a $ \Lambda $-algebra. We define
+    \[ A(n) = \{ a : A \mid (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 x_3 \dots x_{n + 1}) \bullet a = a \}. \]
+  \end{definition}
+
+  \begin{definition}
+    Take $ \mathbf 1_n = (\lambda x_1 \dots x_n, x_1 \dots x_n) \bullet () : A $.
+  \end{definition}
+
+  \begin{definition}
+    We define composition as $ a \circ b = (\lambda x_3, x_1 (x_2 x_3)) \circ (a, b) $ for $ a, b : A $.
+  \end{definition}
+
+  \begin{lemma}
+    This composition is associative.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{definition}[The monoid of a $ \Lambda $-algebra]
+    Now we make $ A(1) $ into a monoid with unit $ \lambda x_1, x_1 $.
+  \end{definition}
+
+  \begin{lemma}
+    This is indeed a monoid.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  From here on, we will assume that $ \Lambda $ (and therefore, any $ \lambda $-theory) satisfies $ \beta $-equality.
+
+  \begin{lemma}
+    For $ a: A $, $ a $ is in $ A(n) $ iff $ \mathbf 1_n \circ a = a $.
+  \end{lemma}
+  \begin{proof}
+    \begin{align*}
+      \mathbf 1_n \circ a
+      &= (\lambda x_3, x_1 (x_2 x_3)) \bullet (((\lambda x_1 \dots x_n, x_1 \dots x_n) \bullet ()), a)\\
+      &= (\lambda x_3, x_1 (x_2 x_3)) \bullet (((\lambda x_2 \dots x_{n + 1}, x_2 \dots x_{n + 1}) \bullet a), x_1 \bullet a)\\
+      &= ((\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_2 \dots x_{n + 1}, x_2 \dots x_{n + 1}), x_1)) \bullet a\\
+      &= (\lambda x_2, (\lambda x_3 \dots x_{n + 2}, x_3 \dots x_{n + 2}) (x_1 x_2)) \bullet a\\
+      &= (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1}) \bullet a.
+    \end{align*}
+  \end{proof}
+
+  \begin{definition}[The presheaf category of a $ \Lambda $-algebra]
+    Let $ A $ be a $ \Lambda $-algebra. If we view the monoid $ A(1) $ as a one-object category, we define the category $ PA $ to be the category of presheaves $ [\op{A(1)}, \SET] $.
+  \end{definition}
+
+  \begin{definition}[The objects $ A(n) $ in $ PA $]
+    Given $ a: A(n) $ and $ b: A(1) $, we have
+    \[ \mathbf 1_n \circ (a \circ b) = (\mathbf 1_n \circ a) \circ b = a \circ b, \]
+    so $ a \circ b: A(n) $ and we have a right $ A(1) $-action on $ A(n) $, which makes $ A(n) $ into an object in $ PA $.
+  \end{definition}
+
+  \begin{lemma}
+    We have $ A(1)^{A(1)} \cong A(2) $.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{definition}[Endomorphism $ \lambda $-theory of a $ \Lambda $-algebra]
+    $ PA $ borrows products from $ \SET $. Therefore, the algebraic theory $ E(A(1)) $ exists. Now note that $ A(1) $ is exponentiable and $ A(1)^{A(1)} \cong A(2) $.
+    Note that $ A(2) \subseteq A(1) $ and that $ (\lambda x_2 x_3, x_1 x_2 x_3) \bullet - $ gives a function from $ A(1) $ to $ A(2) $. This gives $ E(A(1)) $ a $ \lambda $-theory structure.
+  \end{definition}
+
   \begin{theorem}
-    There exists an adjoint equivalence between the category of $ \lambda $-theories, and the category of algebras of $ \Lambda $ \TODO.
+    There exists an adjoint equivalence between the category of $ \lambda $-theories, and the category of algebras of $ \Lambda $.
   \end{theorem}
   \begin{proof}
-    In one direction, the proof sends a $ \lambda $-theory $ L $ to the $ L $-algebra $ L(0) $ \TODO.
-Since $ \Lambda $ is the initial $ \lambda $-theory \TODO, we can give $ L(0) $ a $ \Lambda $-algebra structure \TODO.
-This constitutes a functor \TODO.
+    We will show that the functor $ L \mapsto L_0 $ is an equivalence of categories.
 
-    In the other direction, it sends a $ \Lambda $-algebra $ A $ to the theory of extensions $ \Lambda_A $ \TODO.
-It is a $ \lambda $-theory because it is isomorphic \TODO to the endomorphism $ \lambda $-theory $ E(A(1)) $ of the object $ A(1) $ in $ PA $ \TODO.
+    It is essentially surjective, because $ L $ is isomorphic \TODO to $ E(A(1)) $.
 
-    These constitute an adjoint equivalence. \TODO
+    Now, given morphisms $ f, f^\prime: L \to L^\prime $. Suppose that $ f_0 = f^\prime_0 $. Suppose that $ L $ and $ L^\prime $ have $ \beta $-equality. Then, given $ l: L_n $, we have
+    \[ f_n(l) = \rho^n(\lambda^n(f_n(l))) = \rho^n(f_0(\lambda^n(l))) = \rho^n(f^\prime_0(\lambda^n(l))) = \rho^n(\lambda^n(f^\prime_n(l))) = f^\prime_n(l), \]
+    so the functor is faithful.
+
+    The functor is full because a $ \Lambda $-algebra morphism $ f: A \to A^\prime $ induces a morphism $ f^*: PA^\prime \to PA $ \TODO, and via left Kan extension we get a left adjoint $ f_*: PA \to PA^\prime $ with $ f_*(A(1)) \cong A^\prime(1) $ \TODO.
+Now, $ f_* $ preserves (finite) products \TODO, so we have maps $ PA(A(1)^n, A(1)) \to PA^\prime(A^\prime(1)^n, A^\prime(1)) $ and so a map $ E(A(1)) \to E(A^\prime(1)) $ \TODO.
+This map, when restricted to a map $ PA(1, A(1)) \to PA^\prime(1, A(1)) $, and transported along the isomorphism $ a \mapsto a I $ \TODO, is equal to $ f $ \TODO.
+  \end{proof}
+
+  \begin{lemma}
+    The category of $ T $-algebras has coproducts.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{definition}[Theory of extensions]
+    Let $ T $ be an algebraic theory and $ A $ a $ T $-algebra.
+We can define an algebraic theory $ T_A $ called `the theory of extensions of $ A $' with $ (T_A)_n = T_n + A $.
+The left injection of the variables $ x_i : T_n $ gives the variables.
+    Now, take $ h: (T_n + A)^m $. Sending $ g: T_m $ to $ \varphi(g) := g \bullet h $ gives a $ T $-algebra morphism $ T_m \to T_n + A $ since
+    \[ \varphi(f \bullet g) = f \bullet g \bullet h = f \bullet (g_i \bullet h) = f \bullet (\varphi(g_i))_i. \]
+    This, together with the injection morphism of $ A $ into $ T_n + A $, gives us a $ T $-algebra morphism from the coproduct: $ T_m + A \to T_n + A $.
+We especially have a function on sets $ (T_m + A) \times (T_n + A)^m \to T_n + A $, which we will define our substitution to be.
+  \end{definition}
+
+  \begin{lemma}
+    $ T_A $ is indeed an algebraic theory.
+  \end{lemma}
+  \begin{proof}
+    \TODO
   \end{proof}

### 2023-11-01 report/report.tex
Update report, write talk for dutchcats

@@
   \begin{proof}
-    \TODO
+    We have a bijection $ \varphi: A(2) \cong F_{A(1), A(1)} $, given by
+    \[ \varphi(a)(b, b^\prime) = (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a, b, b^\prime). \]
+    Note that $ \varphi(d) $ is equivariant because \TODO
+    Now, $ \varphi $ is a presheaf morphism because \TODO
+
+    Take $ p = \lambda x_1, x_1 (\lambda x_2 x_3, x_2) $ and $ q = \lambda x_1, x_1 (\lambda x_2 x_3, x_3) $. These are elements of $ A(1) $. Note that for terms $ c_1, c_2 $
+    \begin{align*}
+      p (\lambda x_1, x_1 c_1 c_2)
+      &= (\lambda x_1, x_1 c_1 c_2) (\lambda x_2 x_3, x_2)\\
+      &= (\lambda x_1 x_3, x_2) c_1 c_2\\
+      &= c_1.
+    \end{align*}
+    In the same way, $ q \circ (\lambda x_1 x_2, x_2 c_1 c_2) = c_2 $.
+
+    An inverse is given by
+    \[ \psi: f \mapsto \lambda x_1 x_2, f(p, q)(\lambda x_3, x_3 x_1 x_2). \]
+    This is a presheaf morphism because \TODO
+
+    This is an inverse, because given $ f: F_{A(1), A(1)} $ and$ (a_1, a_2): A(1) \times A(1) $, we have
+    \begin{align*}
+      \varphi(\psi(f))(a_1, a_2) &= u(\lambda x_1 x_2, f(p, q)(\lambda x_3, x_3 x_1 x_2))(a_1, a_2)\\
+      &= \lambda x_1, (\lambda x_2 x_3, f(p, q)(\lambda x_4, x_4 x_2 x_3)) (a_1 x_1) (a_2 x_1)\\
+      &= \lambda x_1, f(p, q)(\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))\\
+      &= f(p, q) \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)))\\
+      &= f(p \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))), q \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))))\\
+      &= f(\lambda x_1, p (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)), \lambda x_1, q (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)))\\
+      &= f(\lambda x_1, a_1 x_1, \lambda x_1, a_2 x_1)\\
+      &= f(a_1, a_2).
+    \end{align*}
+    The last line is because $ a_i : A(1) $ and therefore $ \lambda x_1, a_i x_1 = a_i $.
+
+    On the other hand, if we have $ a_1: A(2) $, we have
+    \begin{align*}
+      \psi(\varphi(a_1)) &= \psi((a_2, a_3) \mapsto \lambda x_1, a_1 (a_2 x_1) (a_3 x_1))\\
+      &= \lambda x_1 x_2, (\lambda x_3, a_1 (p x_3) (q x_3)) (\lambda x_3, x_3 x_1 x_2)\\
+      &= \lambda x_1 x_2, a_1 (p (\lambda x_3, x_3 x_1 x_2)) (q (\lambda x_3, x_3 x_1 x_2))\\
+      &= \lambda x_1 x_2, a_1 x_1 x_2\\
+      &= a_1.
+    \end{align*}
+    The last line is because $ a_1 : A(2) $ and therefore $ \lambda x_1 x_2, a_1 x_1 x_2 = a_1 $.
+
+    Therefore, this map is a bijection and an isomorphism.
   \end{proof}
@@
   \end{definition}
+
+  \begin{definition}[Pullback functor on presheaves for a $ \Lambda $-algebra]
+    Let $ f: A \to A^\prime $ be a $ \Lambda $-algebra morphism. Then for all $ a: A(n) $,
+    \[ \mathbf 1_n \circ f(a) = f(\mathbf 1_n) \circ f(a) = f(\mathbf 1_n \circ a), \]
+    so we have an induced morphism $ f: A(n) \to A^\prime(n) $.
+
+    Now, given a presheaf $ P: PA^\prime $.
+We can create a presheaf $ f^* P : PA $ by taking the set of $ P $, and, for $ p: P $ and $ a: A $, setting $ pa = p \circ f(a) $.
+This is indeed a presheaf because \TODO
+
+    Now, given a morphism $ g: P \to P^\prime $, we get a morphism by taking the function on the sets of $ P $ and $ P^\prime $. This is a morphism because \TODO
+  \end{definition}
+
+  \begin{lemma}
+    The above indeed constitutes a functor.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  Left Kan extension then gives a left adjoint $ f_*: PA \to PA^\prime $.
+
+  \begin{lemma}
+    We have $ f_*(A(1)) \cong A^\prime(1) $.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{lemma}
+    $ f_* $ preserves finite products.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{definition}
+    Since $ f_* $ preserves finite products, given an element of $ g: E(A(1))(n) = PA(A(1)^n, A(1)) $, we get
+    \[ \# f_*(g): PA^\prime(f(A(1)^n), f(A(1))) \cong PA^\prime(A^\prime(1)^n, A^\prime(1)) = E(A^\prime(1))(n). \]
+  \end{definition}
+
+  \begin{lemma}
+    $ \# f_*: E(A(1)) \to E(A^\prime(1)) $ is a map of $ \lambda $-theories.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{definition}
+    We have an isomorphism $ E(A(1))(0) \cong A $ given by $ a \mapsto a I $.
+  \end{definition}
+
+  \begin{lemma}
+    This is indeed an isomorphism of $ \Lambda $-algebras.
+  \end{lemma}
+  \begin{proof}
+    \TODO
+  \end{proof}
+
+  \begin{lemma}
+    Given $ g: A \to A^\prime $,
+  \end{lemma}
 
@@
 
-    The functor is full because a $ \Lambda $-algebra morphism $ f: A \to A^\prime $ induces a morphism $ f^*: PA^\prime \to PA $ \TODO, and via left Kan extension we get a left adjoint $ f_*: PA \to PA^\prime $ with $ f_*(A(1)) \cong A^\prime(1) $ \TODO.
-Now, $ f_* $ preserves (finite) products \TODO, so we have maps $ PA(A(1)^n, A(1)) \to PA^\prime(A^\prime(1)^n, A^\prime(1)) $ and so a map $ E(A(1)) \to E(A^\prime(1)) $ \TODO.
+    The functor is full because a $ \Lambda $-algebra morphism $ f: A \to A^\prime $ induces a functor $ f^*: PA^\prime \to PA $, and via left Kan extension we get a left adjoint $ f_*: PA \to PA^\prime $ with $ f_*(A(1)) \cong A^\prime(1) $.
+Now, $ f_* $ preserves (finite) products, so we have maps $ PA(A(1)^n, A(1)) \to PA^\prime(A^\prime(1)^n, A^\prime(1)) $ and so a map $ E(A(1)) \to E(A^\prime(1)) $.
 This map, when restricted to a map $ PA(1, A(1)) \to PA^\prime(1, A(1)) $, and transported along the isomorphism $ a \mapsto a I $ \TODO, is equal to $ f $ \TODO.

### 2023-11-01 talks/t04-dutch-cats/outline.tex
Update report, write talk for dutchcats

\documentclass{amsart}

\title{Semantics for the $ \lambda $-calculus}
\author{Arnoud van der Leer\\Delft University of Technology\\\texttt{arnoudvanderleer@gmail.com}}

\begin{document}
  \maketitle

  \section{Intro}

  Hi, it is so good to see you all here. For those who don't know me, I am Arnoud van der Leer, master's student at TU Delft, and am currently working on my master's thesis, supervised by Benedikt and Kobe.

  Today, I am going to talk about the paper `Classical lambda calculus in modern dress'. This is a paper from 2013, written by Cambridge professor Martin Hyland.
  In this paper, he talks about models for the $ \lambda $-calculus, and proves three `big' theorems about them.
  I will also talk a little bit about my thesis, which revolves around this paper. My job is to `annotate' this paper, so to speak.

  \tableofcontents

  So here is the outline of my talk. We are currently in the introduction.
  To prove things about the $ \lambda $-calculus and its models, we first need establish the way in which we will formally talk about the $ \lambda $-calculus. We will also talk a bit about denotational semantics.
  Then we will have a look at the three main theorems.
  The first main theorem is Scotts representation theorem, which shows that every model of the $ \lambda $-calculus can be obtained from some category.
  Hyland calls the second main theorem the fundamental theorem of the $ \lambda $-calculus. This is a somewhat stronger result, which says that there is an equivalence between models and denotations for the $ \lambda $-calculus.
  For me, the last main theorem seems to be the most cryptic one, to me. It states that if we have a model for the $ \lambda $-calculus, then create its `category of retracts', then this category is `relatively cartesian closed'. It basically says: if we have a model for the $ \lambda $-calculus, we can create a category in which we can do some form of dependent type theory.
  Lastly, I will talk a bit about my contribution to this, so annotating the paper, and especially mechanizing it.

  \section{Talking about the $\lambda$-calculus}

  So, first of all, in this talk, I will talk almost exclusively about the \textbf{untyped} $ \lambda $-calculus. The untyped $ \lambda $-calculus essentially is about collections that consist of only functions. With the objects of these collections, (so functions), we can do a couple of things. First of all, we can create new objects, which are just the `variables'. Then, given two of these objects, we can apply one to the other. Lastly, given a function with $ n + 1 $ free variables, we can create a function with $ n $ free variables by abstracting.

  Again, note that everything here is a function.

  We can impose two types of equalities on these terms: $ \beta $-equality and $ \eta $-equality. One is about what happens when you first abstract and then apply. The other is about what happens if you first apply to a variable and then abstract again.

  So a model for the $ \lambda $-calculus is something that exhibits this structure. Something thas has variables, application and abstraction, and maybe $ \beta $ and/or $ \eta $-equality.

  One such collection is the \textit{pure} $ \lambda $-calculus. One can view this as an inductive type, given by these three constructors. We can also create the pure $ \lambda $-calculus with $ \beta $-equality, which arises from this inductive type via a quotient.

  \subsection{Models}

  So, the first stepping stone in talking formally about models are algebraic theories. These are structures with variables and some substitution operation.

  One example of this is the $ \Lambda $-calculus.

  Another example is a polynomial ring. It has variables, you can add and multiply polynomials together. And if you have two polynomials, you can substitute one in the place of a variable in the other to get a new polynomial.

  The formal definition of an algebraic theory is

  \subsection{Semantics}

  \section{The main theorems}

  \subsection{Scott's representation theorem}

  \subsection{The fundamental theorem of the $\lambda$-calculus}

  \subsection{The category of retracts}

  \section{My contribution}

  \subsection{Annotating the paper}

  \subsection{Mechanization}

  \section{Conclusion}

\end{document}

### 2023-11-01 talks/t04-dutch-cats/slides.tex
Update report, write talk for dutchcats

\documentclass[aspectratio=169]{fancyslides} % or beamer/slides

% \usepackage{stmaryrd}
\usepackage{tikz-cd}
\usepackage{datetime2}

\title{Semantics for the \texorpdfstring{$ \lambda $}{lambda}-calculus}
\author{Arnoud van der Leer\\Delft University of Technology\\\texttt{arnoudvanderleer@gmail.com}}

\begin{document}
  \maketitle

  \section{Intro}

  \begin{frame}
    \frametitle{Classical lambda calculus in modern dress}

    \begin{itemize}
      \item Paper by Martin Hyland.
      \item About models for the $ \lambda $-calculus.
      \item Three `big' theorems.
      \item My job: `annotate'.
    \end{itemize}
  \end{frame}

  \frame{\tableofcontents}

  \section{Talking about the \texorpdfstring{$\lambda$}{lambda}-calculus}

  \frame{\tableofcontents[currentsection]}

  \begin{frame}
    \frametitle{The \textbf{untyped} $ \lambda $-calculus}

    Describes a collection consisting of (only) functions.

    \pause

    Has terms, consisting of \textit{variables}, \textit{application} and \textit{abstraction}:
    \[ x_1 \]
    \[ x_1 (x_2 x_1) \]
    \[ \lambda x_1, x_1 \]
    \[ \lambda x_3 x_2 x_1, x_1 (x_2 x_3). \]

    Can have $ \beta $- and $ \eta $-equality:
    \[ (\lambda x_n, f) g = f [x_n := g] \qquad \lambda x_n, (f x_n) = f.\]

    \pause

    The \textit{(pure) $ \lambda $-calculus}: Described exactly by the above.
  \end{frame}

  \subsection{Models}
  \begin{frame}
    \frametitle{Algebraic theories: objects with variables and substitution}

    \begin{example}
      $ \lambda $-calculus: $ \Lambda_n = \{ (\lambda x_1, x_1), x_5, (\lambda x_3, x_7) x_{42} \} $.
    \end{example}

    \pause

    \begin{example}
      Polynomial ring: $ \mathbb Z[x_1, ..., x_n] = \{ 1, x_3, 2048 + 7 x_1^{37} - x_6 x_{13}^{42} x_{17}^{1729}, \dots \} $.
    \end{example}

    \pause

    \begin{definition}
      An \textit{algebraic theory} $ T $ is a sequence of sets $ T_n $ with variables $ x_{i, n} \in T_n $ (for $ 0 \leq i < n $) and a substitution operation $ \bullet : T_m \times T_n^m \to T_n $.
    \end{definition}
  \end{frame}

  \begin{frame}
    \frametitle{$ \lambda $-theory: structure with app and abs}

    \begin{definition}
      A \textit{$ \lambda $-theory} $ L $ is an algebraic theory, together with abstraction functions $ \lambda: L_{n + 1} \to L_n $ and application functions $ \rho: L_n \to L_{n + 1} $ (both compatible with the substitution).
    \end{definition}

    \pause

    The pure $ \lambda $-calculus $ \Lambda $ is the initial $ \lambda $-theory.

    \pause

    $ \beta $- and $ \eta $-equality:
    \[ \rho_n \circ \lambda_n = \mathrm{Id}_{L_{n + 1}} \qquad \lambda_n \circ \rho_n = \mathrm{Id}_{L_n}. \]
  \end{frame}

  \subsection{Semantics}
  \begin{frame}
    \frametitle{Algebras: Interpretations (or denotations)}
    We want to interpret terms with free variables as functions from a context to a set

    \begin{example}
      In $ T(n) = \mathbb Z[x_1, \dots, x_n] $, we can take a set $ A = \mathbb Q $ and get
      \[ 2 x_1 + 3 x_1^2 x_2: A^2 \to A, \quad (a_1, a_2) \mapsto 2 \cdot a_1 + 3 \cdot a_1^2 \cdot a_2. \]
    \end{example}

    \pause

    \begin{definition}
      For an algebraic theory $ T $, a \textit{$ T $-algebra} $ A $ is a set $ A $, together with interpretation functions $ T_n \times A^n \to A $ for all $ n $ (respecting the variables and substitution).
    \end{definition}
  \end{frame}

  \section{The main theorems}

  \frame{\tableofcontents[currentsection]}

  \subsection{Scott's representation theorem}
  \begin{frame}
    \frametitle{Scott's representation theorem (1980)}

    \textit{For every $ \lambda $-theory $ L $, we can find a category $ C $ and an object $ X : C_0 $, such that $ L $ is isomorphic to the \textit{endomorphism theory} of $ X $: the $ \lambda $-theory $ E(X) $ given by $ E(X)_n = X^n \to X $.}

    \pause

    The variables of $ E(X)_n $ are the projections $ \pi_i: X^n \to X $. Also, substituting $ g_1, \dots, g_m : X^n \to X $ into $ f: X^m \to X $ composes $ f $ with $ \langle g_1, \dots, g_m \rangle : X^n \to X^m $.

    \pause

    For $ \lambda: E(X)_{n + 1} \to E(X)_n $, postcomposing with some morphism $ \overline{abs}: (X \to X) \to X $ gives
    \[ \lambda: E(X)_{n + 1} = (X^{n + 1} \to X) \simeq (X^n \to (X \to X)) \xrightarrow{\overline{abs}\ \circ\ -} (X^n \to X) = E(X)_n. \]

    In the same way, we get $ \rho: E(X)_n \to E(X)_{n + 1} $ from a morphism $ \overline{app}: X \to (X \to X) $.
  \end{frame}

  \begin{frame}
    \frametitle{Scott's representation theorem (1980)}

    \textit{For every $ \lambda $-theory $ L $, we can find a category $ C $ and an object $ X : C_0 $, such that $ L $ is isomorphic to the \textit{endomorphism theory} of $ X $: the $ \lambda $-theory $ E(X) $ given by $ E(X)_n = X^n \to X $.}

    $ C $ is the category of sequences of sets $ (P_i)_i $ with a composition $ P_m \times L_n^m \to P_n $ and $ X $ is the sequence $ (L_i)_i $.

    With Hyland's definitions and some lemmas, the representation theorem arises before you know it \textit{(on paper)}.
  \end{frame}

  \subsection{The fundamental theorem of the \texorpdfstring{$\lambda$}{lambda}-calculus}
  \begin{frame}
    \frametitle{``The fundamental theorem of the $ \lambda $-Calculus''}

    There is a functor from $ \lambda $-theories to $ \Lambda $-algebras, sending $ L $ to $ L_0 $: its set of constants.

    \pause

    There is also a functor from $ \Lambda $-algebras to $ \lambda $-theories.

    This functor again uses the endomorphism theory $ E(X) $ for some object $ X $ to construct the $ \lambda $-theory.

    \pause

    Hyland shows that these functors constitute an adjoint equivalence.
  \end{frame}

  \subsection{The category of retracts}
  \begin{frame}
    \frametitle{The category of retracts}

    Given a $ \lambda $-theory $ L $, we can view elements $ f: L_1 $ as one-argument functions, and we can compose them like $ f \circ g := f \bullet g $.

    Now we construct a category $ R $
    \[ R_0 = \{ a : L_1 \mid a \circ a = a \}, \qquad a \to b = \{ f: L_1 \mid b \circ f \circ a = f \}. \]

    \pause

    This category is cartesian closed: it has products, and `exponentials'. So its morphisms constitute a simply typed $ \lambda $-calculus: we can do \textit{type theory} with the morphisms.
  \end{frame}

  \begin{frame}
    \frametitle{Locally cartesian closed}
    This category is cartesian closed: it has products, and `exponentials'. So its morphisms constitute a simply typed $ \lambda $-calculus: we can do \textit{type theory} with the morphisms.

    \pause

    If we want to do \textit{dependent type theory}, we need dependent products and sums.

    For a morphism $ f: A \to B $, we have a pullback functor between slice categories $ f^*: R / B \to R / A $. We have a dependent product and sum along $ f $ if $ f^* $ has a right and a left adjoint.

    If the category is \textit{locally cartesian closed}, we have all dependent products, and so all pullback functors have both adjoints.

    \pause

    But this is too strong a requirement. Not all pullback functors have both adjoints, but some do. $ R $ is \textit{relatively cartesian closed}.

    \pause

    I am still working on understanding the proof.
  \end{frame}

  \section{My contribution}
  \frame{\tableofcontents[currentsection]}

  \subsection{Annotating the paper}
  \begin{frame}
    \frametitle{Annotating the paper}

    \textit{An algebraic theory $ T $ is first a functor $ T : \mathbf{F} \to Sets $: so we have sets $ T(n) $ of $ n $-ary multimaps with variable renamings. In addition, $ T $ is equipped with projections $ pr_1, \dots, pr_n : T(n) $ including as special case the identity $ id \in T(1) $. Finally there are compositions $ T(n) \times T(m)^n \to T(m) $ which are} \textbf{associative, unital, compatible with projections and natural in $ n $ and $ m $}. \textit{A map $ F : S \to T $ of algebraic theories is a natural transformation with components $ F_n : S(n) \to T(n) $ preserving projections and composition.}

    \pause

    \begin{itemize}
      \item Learn the background.
      \item Decode the definitions and theorems.
      \item Find examples.
      \item Formalize.
      \item Mechanize.
    \end{itemize}

  \end{frame}

  \subsection{Mechanization}
  \begin{frame}
    \frametitle{Mechanization}

    \begin{itemize}
      \item Displayed categories:
      \begin{itemize}
        \item Univalence;
        \item Limits (twice);
      \end{itemize}
      \item Higher inductive types;
      \item $ X^{n + 1} = X \times X^n $;
      \item $ X_{n + 1} = X_{1 + n} $;
    \end{itemize}

  \end{frame}

  \section{Conclusion}

  \frame{\tableofcontents[currentsection]}

  \begin{frame}
    \frametitle{Conclusion}

    Algebraic theories, $ \lambda $-theories and their algebras (and `presheaves') seem to be a promising way to work with models for the $ \lambda $-calculus.

    \pause

    3 `big' theorems:
    \begin{itemize}
      \item Every model of the $ \lambda $-calculus arises as the endomorphism theory of some category.
      \item There is an equivalence between models of the $ \lambda $-calculus, and interpretations of the $ \lambda $-calculus as functions on a set.
      \item From a model for the untyped $ \lambda $-calculus, we can create a category in which we can do some form of dependent type theory.
    \end{itemize}

    \pause

    I am slowly processing the paper.

    \pause

    Mechanization is hard.

  \end{frame}

  \begin{frame}
    \frametitle{Do you have questions?}

    \pause

    Because I have one: I am still a bit unsure about the exact `meaning' of relative cartesian closedness. Can someone explain that better to me?

  \end{frame}

\end{document}

### 2023-12-14 report/chapters/category-theory.tex
Start writing the report in earnest

\chapter{Category Theoretic Preliminaries}

I will assume a familiarity with the category-theoretical concepts presented in \cite{CT4P}. These include categories, functors, isomorphisms, natural transformations, adjunctions, equivalences and limits.

\tikzset{%
    symbol/.style={%
        draw=none,
        every to/.append style={%
            edge node={node [sloped, allow upside down, auto=false]{$#1$}}}
    }
}

\section{Adjunctions}
An adjoint equivalence of categories has multiple definitions. The one we will use here is the following:
\begin{definition}
  An adjoint equivalence between categories $ C $ and $ D $ is a pair of adjoint functors
  \begin{center}
    \begin{tikzcd}
      D \arrow[r, bend right, "R"'{name=R}] & C \arrow[l, bend right, "L"'{name=L}]
      \ar[from=L, to=R, symbol=\dashv]
    \end{tikzcd}
  \end{center}
  such that the unit $ \eta: \id{C} \Rightarrow R \circ L $ and counit $ \epsilon: L \circ R \Rightarrow \id{D} $ are isomorphisms of functors.
\end{definition}

\section{Kan Extensions}
One of the most general and abstract concepts in category theory is the concept of \textit{Kan extensions}. In \cite{MacLane}, Section X.7, MacLane notes that
\begin{quote}
  The notion of Kan extensions subsumes all the other fundamental concepts of category theory.
\end{quote}
In this thesis, we will use left Kan extension a handful of times. It comes in handy when we want to extend a functor along another functor in the following way:

Let $ A $, $ B $ and $ C $ be categories and let $ F : A \to B $ be a functor.
\begin{definition}
  Precomposition gives a functor between functor categories $ F_* : [B, C] \to [A, C] $. If $ F_* $ has a left adjoint, we will denote call this adjoint functor the \textit{left Kan extension} along $ F $ and denote it $ \mathrm{Lan}_F : [A, C] \to [B, C] $.

  \begin{center}
    \begin{tikzcd}[column sep=.5cm]
      A \arrow[rr, "F"] \arrow[rd, dashed, "F_* G"'] & & B \arrow[ld, "G"]\\
      & C
    \end{tikzcd} \hspace{2cm} \begin{tikzcd}[column sep=.5cm]
      A \arrow[rr, "F"] \arrow[rd, "G"'] & & B \arrow[ld, dashed, "\Lan F G"]\\
      & C
    \end{tikzcd}
  \end{center}

  Analogously, when $ F_* $ has a right adjoint, one calls this the \textit{right Kan extension} along $ F $ and denote it $ \mathrm{Ran}_F: [A, C] \to [B, C] $.
\end{definition}

If a category has limits (resp. colimits), we can construct the right (resp. left) Kan extension in a `pointwise' fashion (see Theorem X.3.1 in \cite{MacLane} or Theorem 2.3.3 in \cite{Kashiwara}). Below, I will outline the parts of the construction that we will need explicitly in this thesis.
\begin{lemma}
  If $ C $ has colimits, $ \Lan F {} $ exists.
\end{lemma}
\begin{proof}
  First of all, for objects $ b: B $, we take
  \[ \Lan F G(b) := \text{colim} \left( (F \downarrow b) \to A \xrightarrow G C \right). \]

  Here, $ (F \downarrow b) $ denotes the comma category with as objects the morphisms $ B(F(a), b) $ for all $ a: A $, and as morphisms from $ f: B(F(a), b) $ to $ f^\prime: B(F(a^\prime), b) $ the morphisms $ g: A(a, a^\prime) $ that make the diagram commute:
  \begin{center}
    \begin{tikzcd}[column sep=.5cm]
      F(a) \arrow[rr, "F(g)"] \arrow[rd, "f^\prime"'] & & F(a^\prime) \arrow[ld, "f^\prime"]\\
      & b
    \end{tikzcd}
  \end{center}
  and $ (F \downarrow b) \to A $ denotes the projection functor that sends $ f: B(F(a_1), b) $ to $ a_1 $.

  Now, a morphism $ h: B(b, b^\prime) $ gives a morphism of diagrams, sending the $ F(a) $ corresponding to $ f: B(G(a), b) $ to the $ F(a) $ corresponding to $ h \circ f: B(G(a), b^\prime) $. From this, we get a morphism $ \Lan F G(h): C(\Lan F G(b), \Lan F G(b^\prime)) $.

  The unit of the adjunction is a natural transformation $ \eta: \id{[A, C]} \Rightarrow F_* \circ \Lan F {} $. We will define this pointwise, for $ G: [A, C] $ and $ a: A $. Our diagram contains the $ G(a) $ corresponding to $ \id{F(a)}: (F \downarrow F(a)) $ and the colimit cocone gives a morphism
  \[ \eta_G(a) : C(G(a), \Lan F G (F(a))), \]
  the latter being equal to $ (F_* \circ \Lan F {})(G)(a) $.

  The counit of the adjunction is a natural transformation $ \epsilon: \Lan F {} \circ F_* \Rightarrow \id{[B, C]} $. We will also define this pointwise, for $ G: [B, C] $ and $ b: B $. The diagram for $ \Lan F (F_* G)(b) $ consists of $ G(F(a)) $ for all $ f: B(F(a), b) $. Then, by the universal property of the colimit, the morphisms $ G(f): C(G(F(a)), G(b)) $ induce a morphism
  \[ \epsilon_G(b) : C(\Lan F (F_* G)(b), G(b)). \]
\end{proof}

\begin{lemma}
  If $ F : A \to B $ is a fully faithful functor, and $ C $ is a category with colimits, $ \eta $ is a natural isomorphism.
\end{lemma}
\begin{proof}
  To show that $ \eta $ is a natural isomorphism, we have to show that $ \eta_G(a^\prime): G(a^\prime) \Rightarrow \Lan F G(F(a^\prime)) $ is an isomorphism for all $ G: [A, C] $ and $ a^\prime: A $. Since a left adjoint is unique up to natural isomorphism, we can assume that $ \Lan F G(F(a^\prime)) $ is given by
  \[ \text{colim} ((F \downarrow F(a^\prime)) \to A \xrightarrow G C). \]
  Now, the diagram for this colimit consists of $ G(a) $ for each arrow $ f: B(F(a), F(a^\prime)) $. Since $ F $ is fully faithful, we have $ f = F(\overline f) $ for some $ \overline f: A(a, a^\prime) $. If we now take the arrows $ G(\overline f): C(G(a), G(a^\prime)) $, the universal property of the colimit gives an arrow
  \[ \varphi: C(\Lan F G(F(a^\prime)), G(a^\prime)) \]
  which constitutes an inverse to $ \eta_G(a^\prime) $.
\end{proof}

\begin{remark}
  In the same way, if $ C $ has limits, $ \epsilon $ is a natural isomorphism.
\end{remark}

\begin{corollary}
  If $ C $ has limits or colimits, precomposition of functors $ [B, C] $ along a fully faithful functor is (split) essentially surjective.
\end{corollary}
\begin{proof}
  For each $ G: [A, C] $ we take $ \Lan F G: [B, C] $, and we have $ F_*(\Lan F G) \cong G $.
\end{proof}

\begin{corollary}
  If $ C $ has colimits (resp. limits), left (resp. right) Kan extension of functors $ [A, C] $ along a fully faithful functor is fully faithful.
\end{corollary}
\begin{proof}
  Since left Kan extension along $ F $ is the left adjoint to precomposition, we have
  \[ [A, C](\Lan F G, \Lan F G^\prime) \cong [B, C](G, F_*(\Lan F G^\prime)) \cong [B, C](G, G^\prime). \]
\end{proof}

\section{The Karoubi envelope}
Let $ C $ be a category.
\begin{definition}
  We can define another category $ \overline C $. The objects of $ C $ are tuples $ (c, a) $ with $ c: C $, $ a: C(c, c) $ such that $ a \circ a = a $. The morphisms between $ (c, a) $ and $ (d, b) $ are morphisms $ f: C(a, b) $ such that $ b \circ f \circ a = f $. The identity morphism on $ (c, a) $ is given by $ a $ and $ \overline C $ inherits morphism composition from $ C $.
\end{definition}
This category is called the \textit{Karoubi Envelope}, the \textit{idempotent completion}, the \textit{category of retracts}, or the \textit{Cauchy completion} of $ C $.

% \begin{definition}
%   \TODO Karoubi envelope in terms of presheaves
%   Alternatively, one can define $ \overline C $ to be the full subcategory of the presheaf category $ [\op C, \SET] $ that consists of retracts of representable presheaves. That is, the presheaves $ P: \op C $ such that there exists
% \end{definition}

% \begin{definition}
%   Abstract definition: \TODO
% \end{definition}

% \begin{lemma}
%   Equivalence of the definitions
% \end{lemma}

\begin{remark}
  Note that for a morphism $ f: \overline C((c, a), (d, b)) $,
  \[ f \circ a = b \circ f \circ a \circ a = b \circ f \circ a = f \]
  and in the same way, $ b \circ f = f $.
\end{remark}

\begin{definition}
  We have an embedding $ \iota_C: C \to \overline C $, sending $ c: C $ to $ (c, \id{c}) $ and $ f: C(c, d) $ to $ f $.
\end{definition}

\begin{remark}
  Note that the embedding is fully faithful, since
  \[ \overline C((c, \id c), (d, \id d)) = \{ f: C(c, d) \mid \id d \circ f \circ \id c = f \} = C(c, d). \]
\end{remark}

Let $ D $ be a category with colimits.
\begin{lemma}
  We have an adjoint equivalence between $ [C, D] $ and $ [\overline C, D] $.
\end{lemma}
\begin{proof}
  We already have an adjunction $ \Lan {\iota_C} {} \dashv \iota_{C*} $. Also, since $ \iota_C $ is fully faithful, we know that $ \eta $ is a natural isomorphism. Therefore, we only have to show that $ \epsilon $ is a natural isomorphism. That is, we need to show that $ \epsilon_G(c, a): D(\Lan {\iota_C} (\iota_{C*} G) (c, a), G(c, a)) $ is an isomorphism for all $ G: [\overline C, D] $ and $ (c, a): \overline C $.

  One of the components in the diagram of $ \Lan {\iota_C} (\iota_{C*} G) (c, a) $ is the $ \iota_{C*} G(c) = G(c, \id c) $ corresponding to $ a: \iota_C(c) \to (c, a) $. This component has a morphism into our colimit
  \[ \varphi: C(G(\iota_C(c)), \Lan {\iota_C} (\iota_{C*} G) (c, a)). \]
  Note that we can view $ a $ as a morphism $ a: \overline C((c, a), \iota_C(c)) $. This gives us our inverse morphism
  \[ \varphi \circ G(a): C(G(c, a), \Lan {\iota_C} (\iota_{C*} G) (c, a)). \]
\end{proof}

\begin{remark}
  Actually, one does not need the full power of colimits. If one just has coequalizers, one can lift a functor $ G: [C, D] $ to a functor $ \overline G: [\overline C, D] $ by taking $ \overline G(c, a) $ to be the coequalizer of the diagram
  \begin{center}
    \begin{tikzcd}
      G(c) \arrow[r, "G(a)"', shift right] \arrow[r, "\id{G(c)}", shift left] & G(c)
    \end{tikzcd}
  \end{center}
  Alternatively, one could take the equalizer of the diagram, or the right Kan extension along $ \iota_C $.
\end{remark}

\begin{lemma}
  The formation of the opposite category commutes with the formation of the Karoubi envelope.
\end{lemma}
\begin{proof}
  An object in $ \overline{\op C} $ is an object $ c: \op C $ (which is just an object $ c: C $), together with an idempotent morphism $ a: \op C(c, c) = C(c, c) $. This is the same as an object in $ \op{\overline C} $.

  A morphism in $ \overline{\op C}((c, a), (d, b)) $ is a morphism $ f: \op C(c, d) = C(d, c) $ such that
  \[ a \circ_C f \circ_C b = b \circ_{\op C} f \circ_{\op C} a = f \]
  A morphism in $ \op{\overline C}((c, a), (d, b)) = \overline C((d, b), (c, a)) $ is a morphism $ f: C(d, c) $ such that $ a \circ f \circ b = f $.

  Now, in both categories, the identity morphism on $ (c, a) $ is given by $ a $.

  Lastly, $ \overline {\op C} $ inherits morphism composition from $ \op C $, which is the opposite of composition in $ C $. On the other hand, composition in $ \op{\overline C} $ is the opposite of composition in $ \overline C $, which inherits composition from $ C $.
\end{proof}

\begin{corollary}
  As the category $ \SET $ is cocomplete, we have an equivalence between the category of presheaves on $ C $ and the category of presheaves on $ \overline C $.
\end{corollary}

\section{Monoids as categories}
Take a monoid $ M $.
\begin{definition}
  We can construct a category $ C_M $ with $ C_{M0} = \{ \star \} $, $ C_M(\star, \star) = M $. The identity morphism on $ \star $ is the identity $ 1: M $. The composition is given by $ f \circ g = f \cdot g $.
\end{definition}

\begin{definition}
  A \textit{right monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, m^\prime: M $,
  \[ x 1 = x \qquad \text{and} \qquad (x m) m^\prime = x (m \cdot m^\prime). \]
\end{definition}

\begin{definition}
  A \textit{morphism} between sets $ X $ and $ Y $ with a right $ M $- action is an $ M $-equivariant function $ f: X \to Y $: a function such that for all $ x: X $ and $ m: M $, $ f(xm) = f(x)m $.
\end{definition}

\begin{lemma}
  Presheaves on $ C_M $ are equivalent to sets with a right $ M $-action.
\end{lemma}
\begin{proof}
  This correspondence sends a presheaf $ F $ to the set $ F(\star) $, and conversely, the set $ X $ to the presheaf $ F $ given by $ F(\star) := X $. The $ M $-action corresponds to the presheaf acting on morphisms as $ xm = F(m)(x) $. A natural transformation between presheaves $ F \Rightarrow G $ corresponds to a function $ F(\star) \to G(\star) $ that is $ M $-equivariant, so this is exactly a monoid action morphism.
\end{proof}

Monoid monoid action: \TODO\\
Limits: \TODO\\
Exponentials: \TODO\\
Global elements: \TODO\\
Restriction of scalars: \TODO\\
Extension of scalars: \TODO\\
Extension of scalars preserves the monoid action: \TODO\\
Extension of scalars preserves limits: \TODO

### 2023-12-14 talks/t04-dutch-cats/outline.tex
Start writing the report in earnest

@@
 
-  The formal definition of an algebraic theory is
+  The formal definition of an algebraic theory is a sequence of sets $ T_n $, you can think of those as containing the terms in $ n $ free variables, with variables $ x_1, \dots, x_n $ in set $ n $, and a substitution.
+You can view the substitution as taking a term with $ m $ free variables, and $ m $ terms with $ n $ free variables, and substituting the $ g $'s for the free variables in $ f $.
+
+  I have seen structures like algebraic theories in a lot of literature. They are known by different names: Lawvere theories, cartesian operads, abstract clones or algebraic theories.
+
+  Now we are able to start talking formally about models for the $ \lambda $-theory, by extending the notion of algebraic theory.
+A $ \lambda $-theory is an algebraic theory, together with abstraction functions, that take a term with $ n + 1 $ free variables and give a term with $ n $ free variables, and application functions that go the other way around.
+
+  A somewhat important example of a $ \lambda $-theory is the pure $ \lambda $-calculus.
+
+  We can also consider models with $ \beta $- and/or $ \eta $-equality, by saying that $ \lambda $ after $ \rho $ or the other way around must be the identity.
+
+  I feel like $ \lambda $-theories are a lot less known than algebraic theories.
+They were not mentioned in the literature that I saw about algebraic theories, and I have only seen the term in this specific paper.
 
@@
 
+  Now we will talk a bit about semantics, interpretations or denotations, because we want to interpret the terms in our algebraic theories as functions on some set.
+More specifically, we want to interpret the terms in $ n $ variables as functions that take $ n $ elements of a set and give an element of the set again.
+
+  For example, in the case of our polynomial ring, we can take as the set the rational numbers, and a polynomial in $ n $ variables then gives an $ n $-ary function.
+
+  The formal definition is \dots
+
   \section{The main theorems}
 
+  Now we get to the main theorems.
+
   \subsection{Scott's representation theorem}
+
+  The first theorem, Scott's representation theorem, states that (\dots).
 

### 2023-12-14 talks/t04-dutch-cats/slides.tex
Start writing the report in earnest

@@
 
-% \usepackage{stmaryrd}
 \usepackage{tikz-cd}
 \usepackage{datetime2}
+\usepackage{stackengine}
+
+\setlength{\parskip}{.5\baselineskip}
+\setbeamertemplate{footline}[frame number]
 
@@
 
-  \frame{\tableofcontents}
+  \begin{frame}[fragile]
+    \begin{columns}
+      \begin{column}{.5\textwidth}
+        \tableofcontents
+      \end{column}
+      \begin{column}{.5\textwidth}
+        \begin{tikzcd}
+          \Lambda-algebras \arrow[d, harpoon, shift left]           &                                                   \\
+          \lambda-theories \arrow[d] \arrow[u, harpoon, shift left] & \stackanchor{Endomorphism}{theories} \arrow[l, two heads, hook] \\
+          \stackanchor{Relatively\ Cartesian}{Closed\ Categories}   &
+        \end{tikzcd}
+      \end{column}
+    \end{columns}
+  \end{frame}
 
@@
 
-  \frame{\tableofcontents[currentsection]}
+  \begin{frame}[fragile]
+    \begin{columns}
+      \begin{column}{.5\textwidth}
+        \tableofcontents[currentsection]
+      \end{column}
+      \begin{column}{.5\textwidth}
+        \begin{tikzcd}
+          \Lambda-algebras \arrow[d, harpoon, shift left]           &                                                   \\
+          \lambda-theories \arrow[d] \arrow[u, harpoon, shift left] & \stackanchor{Endomorphism}{theories} \arrow[l, two heads, hook] \\
+          \stackanchor{Relatively\ Cartesian}{Closed\ Categories}   &
+        \end{tikzcd}
+      \end{column}
+    \end{columns}
+  \end{frame}
 
@@
 
-  \frame{\tableofcontents[currentsection]}
+  \subsection{Scott's representation theorem}
 
-  \subsection{Scott's representation theorem}
+  \begin{frame}[fragile]
+    \begin{columns}
+      \begin{column}{.5\textwidth}
+        \tableofcontents[currentsubsection]
+      \end{column}
+      \begin{column}{.5\textwidth}
+        \begin{tikzcd}
+          \Lambda-algebras \arrow[d, harpoon, shift left]           &                                                   \\
+          \lambda-theories \arrow[d] \arrow[u, harpoon, shift left] & \stackanchor{Endomorphism}{theories} \arrow[l, two heads, hook] \\
+          \stackanchor{Relatively\ Cartesian}{Closed\ Categories}   &
+        \end{tikzcd}
+      \end{column}
+    \end{columns}
+  \end{frame}
+
   \begin{frame}
@@
 
-    For $ \lambda: E(X)_{n + 1} \to E(X)_n $, postcomposing with some morphism $ \overline{abs}: (X \to X) \to X $ gives
-    \[ \lambda: E(X)_{n + 1} = (X^{n + 1} \to X) \simeq (X^n \to (X \to X)) \xrightarrow{\overline{abs}\ \circ\ -} (X^n \to X) = E(X)_n. \]
-
-    In the same way, we get $ \rho: E(X)_n \to E(X)_{n + 1} $ from a morphism $ \overline{app}: X \to (X \to X) $.
+    We obtain $ \lambda: E(X)_{n + 1} \to E(X)_n $ as
+    \[ \lambda: E(X)_{n + 1} = (X^{n + 1} \to X) \simeq (X^n \to X^X) \xrightarrow{\overline{abs}\ \circ\ -} (X^n \to X) = E(X)_n. \]
+    for some morphism $ \overline{abs}: X^X \to X $. In the same way, we get $ \rho: E(X)_n \to E(X)_{n + 1} $ from a morphism $ \overline{app}: X \to X^X $.
   \end{frame}
@@
 
+    \pause
+
     With Hyland's definitions and some lemmas, the representation theorem arises before you know it \textit{(on paper)}.
@@
   \subsection{The fundamental theorem of the \texorpdfstring{$\lambda$}{lambda}-calculus}
+
+  \begin{frame}[fragile]
+    \begin{columns}
+      \begin{column}{.5\textwidth}
+        \tableofcontents[currentsubsection]
+      \end{column}
+      \begin{column}{.5\textwidth}
+        \begin{tikzcd}
+          \Lambda-algebras \arrow[d, harpoon, shift left]           &                                                   \\
+          \lambda-theories \arrow[d] \arrow[u, harpoon, shift left] & \stackanchor{Endomorphism}{theories} \arrow[l, two heads, hook] \\
+          \stackanchor{Relatively\ Cartesian}{Closed\ Categories}   &
+        \end{tikzcd}
+      \end{column}
+    \end{columns}
+  \end{frame}
   \begin{frame}
@@
     There is also a functor from $ \Lambda $-algebras to $ \lambda $-theories.
-
     This functor again uses the endomorphism theory $ E(X) $ for some object $ X $ to construct the $ \lambda $-theory.
@@
   \subsection{The category of retracts}
+
+  \begin{frame}[fragile]
+    \begin{columns}
+      \begin{column}{.5\textwidth}
+        \tableofcontents[currentsubsection]
+      \end{column}
+      \begin{column}{.5\textwidth}
+        \begin{tikzcd}
+          \Lambda-algebras \arrow[d, harpoon, shift left]           &                                                   \\
+          \lambda-theories \arrow[d] \arrow[u, harpoon, shift left] & \stackanchor{Endomorphism}{theories} \arrow[l, two heads, hook] \\
+          \stackanchor{Relatively\ Cartesian}{Closed\ Categories}   &
+        \end{tikzcd}
+      \end{column}
+    \end{columns}
+  \end{frame}
   \begin{frame}
@@
 
-  \begin{frame}
-    \frametitle{Locally cartesian closed}
+  \begin{frame}[fragile]
+    \frametitle{Relatively cartesian closed}
     This category is cartesian closed: it has products, and `exponentials'. So its morphisms constitute a simply typed $ \lambda $-calculus: we can do \textit{type theory} with the morphisms.
@@
 
-    For a morphism $ f: A \to B $, we have a pullback functor between slice categories $ f^*: R / B \to R / A $.
-We have a dependent product and sum along $ f $ if $ f^* $ has a right and a left adjoint.
+    \begin{center}
+      \begin{tikzcd}
+        R / A \arrow[d, dashed] \arrow[r, "f^*" description] & R / B \arrow[d, dashed] \arrow[l, "\sum_f"', bend right] \arrow[l, "\prod_f", bend left] \\
+        A & B \arrow[l, "f"]
+      \end{tikzcd}
+    \end{center}
 
-    If the category is \textit{locally cartesian closed}, we have all dependent products, and so all pullback functors have both adjoints.
+    \textit{Locally cartesian closed}: all pullback functors have both adjoints.
 
@@
 
-    But this is too strong a requirement. Not all pullback functors have both adjoints, but some do. $ R $ is \textit{relatively cartesian closed}.
+    In $ R $, not all pullback functors have both adjoints, but some do: \textit{relatively cartesian closed}.
 
@@
   \section{My contribution}
-  \frame{\tableofcontents[currentsection]}
+  \begin{frame}[fragile]
+    \begin{columns}
+      \begin{column}{.5\textwidth}
+        \tableofcontents[currentsection]
+      \end{column}
+      \begin{column}{.5\textwidth}
+        \begin{tikzcd}
+          \Lambda-algebras \arrow[d, harpoon, shift left]           &                                                   \\
+          \lambda-theories \arrow[d] \arrow[u, harpoon, shift left] & \stackanchor{Endomorphism}{theories} \arrow[l, two heads, hook] \\
+          \stackanchor{Relatively\ Cartesian}{Closed\ Categories}   &
+        \end{tikzcd}
+      \end{column}
+    \end{columns}
+  \end{frame}
 
@@
       \item Find examples.
-      \item Formalize.
+      \item Formalize (on paper).
       \item Mechanize.

### 2023-12-16 report/chapters/category-theory.tex
Add motivation about the Karoubi envelope to the report

@@
 These include categories, functors, isomorphisms, natural transformations, adjunctions, equivalences and limits.
+
+\section{Notation}
+For an object $ c $ in a category $ C $, I will write $ c: C $.
+
+For a morphism $ f $ between objects $ c $ and $ c^\prime $ in a category $ C $, I will write $ f: C(c, c^\prime) $ or $ f: c \to c^\prime $.
+
+For composition of morphisms $ f: C(c, d) $ and $ g: C(d, e) $, I will write $ f \cdot g $.
+
+For composition of functors $ F: A \to B $ and $ G: B \to C $, I will write $ F \bullet G $.
+
+\section{Adjunctions}
+An adjoint equivalence of categories has multiple definitions. The one we will use here is the following:
 
@@
 
-\section{Adjunctions}
-An adjoint equivalence of categories has multiple definitions. The one we will use here is the following:
 \begin{definition}
@@
   \end{center}
-  such that the unit $ \eta: \id{C} \Rightarrow R \circ L $ and counit $ \epsilon: L \circ R \Rightarrow \id{D} $ are isomorphisms of functors.
+  such that the unit $ \eta: \id{C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{D} $ are isomorphisms of functors.
 \end{definition}
@@
 
-  Now, a morphism $ h: B(b, b^\prime) $ gives a morphism of diagrams, sending the $ F(a) $ corresponding to $ f: B(G(a), b) $ to the $ F(a) $ corresponding to $ h \circ f: B(G(a), b^\prime) $.
+  Now, a morphism $ h: B(b, b^\prime) $ gives a morphism of diagrams, sending the $ F(a) $ corresponding to $ f: B(G(a), b) $ to the $ F(a) $ corresponding to $ f \cdot h: B(G(a), b^\prime) $.
 From this, we get a morphism $ \Lan F G(h): C(\Lan F G(b), \Lan F G(b^\prime)) $.
 
-  The unit of the adjunction is a natural transformation $ \eta: \id{[A, C]} \Rightarrow F_* \circ \Lan F {} $.
+  The unit of the adjunction is a natural transformation $ \eta: \id{[A, C]} \Rightarrow \Lan F {} \bullet F_* $.
 We will define this pointwise, for $ G: [A, C] $ and $ a: A $.
@@
   \[ \eta_G(a) : C(G(a), \Lan F G (F(a))), \]
-  the latter being equal to $ (F_* \circ \Lan F {})(G)(a) $.
+  the latter being equal to $ (\Lan F {} \bullet F_*)(G)(a) $.
 
-  The counit of the adjunction is a natural transformation $ \epsilon: \Lan F {} \circ F_* \Rightarrow \id{[B, C]} $.
+  The counit of the adjunction is a natural transformation $ \epsilon: F_* \bullet \Lan F {} \Rightarrow \id{[B, C]} $.
 We will also define this pointwise, for $ G: [B, C] $ and $ b: B $.
@@
 \section{The Karoubi envelope}
-Let $ C $ be a category.
+Let $ C $ be a category. If we have a retraction-section pair
+\begin{tikzcd}
+  c \arrow[r, shift left, "r"] & d \arrow[l, shift left, "s"]
+\end{tikzcd}
+we have (by definition) $ s \cdot r = \id d $.
+On the other hand, $ s \cdot r: c \to c $ is an idempotent morphism.
+Conversely, we can wonder whether for any idempotent morphism $ a: c \to c $, we can find a retraction-section pair $ r: c \to d $ and $ s: d \to c $ such that $ a = r \cdot s $.
+If this is the case, we say that the idempotent $ a $ \textit{splits}.
+If $ a $ does not split, we can wonder whether we can find an embedding $ \iota_C : C \hookrightarrow \overline C $ such that the idempotent $ \iota_C(a): \iota_C(c) \to \iota_C(c) $ does split.
+
 \begin{definition}
-  We can define another category $ \overline C $.
-The objects of $ C $ are tuples $ (c, a) $ with $ c: C $, $ a: C(c, c) $ such that $ a \circ a = a $.
-The morphisms between $ (c, a) $ and $ (d, b) $ are morphisms $ f: C(a, b) $ such that $ b \circ f \circ a = f $.
+  We define the category $ \overline C $.
+The objects of $ \overline C $ are tuples $ (c, a) $ with $ c: C $, $ a: C(c, c) $ such that $ a \cdot a = a $.
+The morphisms between $ (c, a) $ and $ (d, b) $ are morphisms $ f: C(a, b) $ such that $ a \cdot f \cdot b = f $.
 The identity morphism on $ (c, a) $ is given by $ a $ and $ \overline C $ inherits morphism composition from $ C $.
@@
   Note that for a morphism $ f: \overline C((c, a), (d, b)) $,
-  \[ f \circ a = b \circ f \circ a \circ a = b \circ f \circ a = f \]
-  and in the same way, $ b \circ f = f $.
+  \[ a \cdot f = a \cdot a \cdot f \cdot b = a \cdot f \cdot b = f \]
+  and in the same way, $ f \cdot b = f $.
 \end{remark}
@@
 
+\begin{lemma}
+  Every object $ c: \overline C $ is a retract of $ \iota_C(c_0) $ for some $ c_0: C $.
+\end{lemma}
+\begin{proof}
+  Note that $ c = (c_0, a) $ for some $ c_0: C $ and an idempotent $ a: c \to c $. We have morphisms
+  \begin{tikzcd}
+    \iota_C(c) \arrow[r, shift left, "a_\rightarrow"] & (c, a) \arrow[l, shift left, "a_\leftarrow"]
+  \end{tikzcd}, both given by $ a $. We have $ a_\leftarrow \cdot a_\rightarrow = a = \id{(c, a)} $, so $ (c, a) $ is a retract of $ \iota_C(c) $.
+\end{proof}
+
+\begin{lemma}
+  Every idempotent splits in $ \overline C $.
+\end{lemma}
+\begin{proof}
+  Take an idempotent $ a: C(c, c) $.
+We have an object $ (c, a): \overline C $.
+By the previous lemma, $ (c, a) $ is a retract of $ \iota_C(c) $.
+We have $ \iota_C(a) = a = a_\rightarrow \cdot a_\leftarrow $, so $ a $ splits in $ \overline C $.
+\end{proof}
+
 \begin{remark}
   Note that the embedding is fully faithful, since
-  \[ \overline C((c, \id c), (d, \id d)) = \{ f: C(c, d) \mid \id d \circ f \circ \id c = f \} = C(c, d). \]
+  \[ \overline C((c, \id c), (d, \id d)) = \{ f: C(c, d) \mid \id c \cdot f \cdot \id d = f \} = C(c, d). \]
 \end{remark}
 
-Let $ D $ be a category with colimits.
+\begin{remark}
+  Let $ D $ be a category. Suppose that we have a retraction-section pair in $ D $, given by
+  \begin{tikzcd}
+    d \arrow[r, shift left, "r"] & d^\prime \arrow[l, shift left, "s"]
+  \end{tikzcd}.
+  Now, suppose that we have an object $ c: D $ and a morphism $ f $ with $ (r \cdot s) \cdot f = f $.
+Then we get a morphism $ s \cdot f: d^\prime \to c $ such that $ f $ factors as $ r \cdot (s \cdot f) $.
+Also, for any $ g $ with $ r \cdot g = f $, we have
+  \[ g = s \cdot r \cdot g = s \cdot f. \]
+  \begin{center}
+    \begin{tikzcd}
+      d \arrow[r, left, "r"] \arrow[rd, "f"'] & d^\prime \arrow[r, "s"] \arrow[d, "s \cdot f" description] & d \arrow[ld, "f"]\\
+      & c
+    \end{tikzcd}.
+  \end{center}
+  Therefore, $ d^\prime $ is the equalizer of \begin{tikzcd}
+    d \arrow[r, shift left, "\id d"] \arrow[r, shift right, "r \cdot s"'] & d
+  \end{tikzcd}. In the same way, it is also the coequalizer of this diagram.
+\end{remark}
+
+Since a functor preserves retracts, and since every object of $ \overline C $ is a retract of an object in $ C $, one can lift a functor from $ C $ (to a category with (co)equalizers) to a functor on $ \overline C $.
+
+For convenience, the lemma below works with pointwise left Kan extension using colimits, but one could also prove this using just (co)equalizers (or right Kan extension using limits).
 \begin{lemma}
-  We have an adjoint equivalence between $ [C, D] $ and $ [\overline C, D] $.
+  Let $ D $ be a category with colimits. We have an adjoint equivalence between $ [C, D] $ and $ [\overline C, D] $.
 \end{lemma}
@@
   Note that we can view $ a $ as a morphism $ a: \overline C((c, a), \iota_C(c)) $. This gives us our inverse morphism
-  \[ \varphi \circ G(a): C(G(c, a), \Lan {\iota_C} (\iota_{C*} G) (c, a)). \]
+  \[ G(a) \cdot \varphi: C(G(c, a), \Lan {\iota_C} (\iota_{C*} G) (c, a)). \]
 \end{proof}
-
-\begin{remark}
-  Actually, one does not need the full power of colimits.
-If one just has coequalizers, one can lift a functor $ G: [C, D] $ to a functor $ \overline G: [\overline C, D] $ by taking $ \overline G(c, a) $ to be the coequalizer of the diagram
-  \begin{center}
-    \begin{tikzcd}
-      G(c) \arrow[r, "G(a)"', shift right] \arrow[r, "\id{G(c)}", shift left] & G(c)
-    \end{tikzcd}
-  \end{center}
-  Alternatively, one could take the equalizer of the diagram, or the right Kan extension along $ \iota_C $.
-\end{remark}
 
@@
   A morphism in $ \overline{\op C}((c, a), (d, b)) $ is a morphism $ f: \op C(c, d) = C(d, c) $ such that
-  \[ a \circ_C f \circ_C b = b \circ_{\op C} f \circ_{\op C} a = f \]
-  A morphism in $ \op{\overline C}((c, a), (d, b)) = \overline C((d, b), (c, a)) $ is a morphism $ f: C(d, c) $ such that $ a \circ f \circ b = f $.
+  \[ b \cdot_C f \cdot_C a = a \cdot_{\op C} f \cdot_{\op C} b = f. \]
+  A morphism in $ \op{\overline C}((c, a), (d, b)) = \overline C((d, b), (c, a)) $ is a morphism $ f: C(d, c) $ such that $ b \cdot f \cdot a = f $.
 
@@
 The identity morphism on $ \star $ is the identity $ 1: M $.
-The composition is given by $ f \circ g = f \cdot g $.
+The composition is given by multiplication $ g \cdot_{C_M} f = f \cdot_M g $.
 \end{definition}
@@
 \begin{definition}
-  A \textit{morphism} between sets $ X $ and $ Y $ with a right $ M $- action is an $ M $-equivariant function $ f: X \to Y $: a function such that for all $ x: X $ and $ m: M $, $ f(xm) = f(x)m $.
+  A \textit{morphism} between sets $ X $ and $ Y $ with a right $ M $- action is an $ M $-equivariant function $ f: X \to Y $: a function such that $ f(xm) = f(x)m $ for all $ x: X $ and $ m: M $.
 \end{definition}
@@
 The $ M $-action corresponds to the presheaf acting on morphisms as $ xm = F(m)(x) $.
-A natural transformation between presheaves $ F \Rightarrow G $ corresponds to a function $ F(\star) \to G(\star) $ that is $ M $-equivariant, so this is exactly a monoid action morphism.
+A morphism (natural transformation) between presheaves $ F \Rightarrow G $ corresponds to a function $ F(\star) \to G(\star) $ that is $ M $-equivariant, which is exactly a monoid action morphism.
 \end{proof}
 
-Monoid monoid action: \TODO\\
-Limits: \TODO\\
+\begin{definition}
+  We can view $ M $ as an object $ U_M $ in $ C_M $, with action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
+\end{definition}
+
+\begin{remark}
+  Since the category of sets with an $ M $-action is equivalent to a presheaf category, it has all limits.
+However, we can make this concrete.
+The set of the product $ \prod_i X_i $ is the product of the underlying sets.
+The action is given pointwise by $ (x_i)_i m = (x_i m)_i $.
+\end{remark}
+
+\begin{lemma}
+  The category $ C $ of sets with an $ M $-action has exponentials.
+\end{lemma}
+\begin{proof}
+  Given sets with $ M $-action $ X $ and $ Y $. Consider the set $ C(M \times X, Y) $ with an $ M $-action given by $ \phi m^\prime(m, x) = \phi(m^\prime m, x) $.
+\end{proof}
+
 Exponentials: \TODO\\

### 2023-12-18 report/chapters/category-theory.tex
Add a remark about morphisms between retracts, rework the proof that idempotents split

@@
 \begin{proof}
-  Take an idempotent $ a: C(c, c) $.
-We have an object $ (c, a): \overline C $.
-By the previous lemma, $ (c, a) $ is a retract of $ \iota_C(c) $.
-We have $ \iota_C(a) = a = a_\rightarrow \cdot a_\leftarrow $, so $ a $ splits in $ \overline C $.
+  Take an idempotent $ e: \overline C(c, c) $.
+Note that $ c $ is given by an object $ c_0: C $ and an idempotent $ a: C(c_0, c_0) $.
+Also, $ e $ is given by some idempotent $ e: C(c_0, c_0) $ with $ a \cdot e \cdot a = e $.
+
+  Now, we have $ (c_0, e): \overline C $ and morphisms
+  \begin{tikzcd}
+    (c_0, a) \arrow[r, shift left, "e_\rightarrow"] & (c_0, e) \arrow[l, shift left, "e_\leftarrow"]
+  \end{tikzcd}, both given by $ e $.
+We have $ e_\leftarrow \cdot e_\rightarrow = e = \id{(c_0, e)} $, so $ (c_0, e) $ is a retract of $ (c_0, a) $.
+Also, $ e = e_\rightarrow \cdot e_\leftarrow $, so $ e $ is split.
 \end{proof}
@@
   \end{tikzcd}. In the same way, it is also the coequalizer of this diagram.
+
+  Now, note that if we have a coequalizer $ c^\prime $ of $ \id c $ and $ a $, and an equalizer $ d^\prime $ of $ \id d $ and $ b $, the universal properties of these give an equivalence
+  \[ D(c^\prime, d^\prime) \cong \{ f: D(c, d^\prime) \mid a \cdot f = f \} \cong \{ f: D(c, d) \mid a \cdot f = f = f \cdot b \}. \]
+  \begin{center}
+    \begin{tikzcd}
+      c \arrow[r, shift left, "\id c"] \arrow[r, shift right, "a"'] & c \arrow[r] \arrow[d] \arrow[rd] & c^\prime \arrow[d]\\
+      d & d \arrow[l, shift right, "\id d"'] \arrow[l, shift left, "b"] & d^\prime \arrow[l]
+    \end{tikzcd}
+  \end{center}
 \end{remark}

### 2023-12-18 report/chapters/category-theory.tex
Work out the section on sets with a monoid action

@@
 
+\begin{remark}
+  An isomorphism of monoids gives an (adjoint) equivalence of categories.
+\end{remark}
+
 \begin{definition}
@@
 \begin{definition}
-  We can view $ M $ as an object $ U_M $ in $ C_M $, with action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
+  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
 \end{definition}
@@
 
+\begin{definition}
+  Given an object $ c $ in a category $ C $ with terminal object $ t $. The global elements of $ c $ are the morphisms $ C(t, c) $.
+\end{definition}
+
+Note that the initial set with $ M $-action is $ \{ \star \} $, with action $ \star m = \star $.
+
+\begin{lemma}
+  The global elements of a set with right $ M $-action correspond to the elements that are invariant under the $ M $-action.
+\end{lemma}
+\begin{proof}
+  A global element of $ X $ is a morphism $ \varphi: \{ \star \} \to X $ such that for all $ m: M $, $ \varphi(\star)m = \varphi(\star m) = \varphi(\star) $.
+Therefore, it is given precisely by the element $ \varphi(\star): X $, which must be invariant under the $ M $-action.
+\end{proof}
+
 \begin{lemma}
@@
 \begin{proof}
-  Given sets with $ M $-action $ X $ and $ Y $. Consider the set $ C(M \times X, Y) $ with an $ M $-action given by $ \phi m^\prime(m, x) = \phi(m^\prime m, x) $.
+  Given sets with $ M $-action $ X $ and $ Y $.
+Consider the set $ C(M \times X, Y) $ with an $ M $-action given by $ \phi m^\prime(m, x) = \phi(m^\prime m, x) $.
+This is the exponential object $ X^Y $, with the evaluation morphism $ X \times X^Y \to Y $ given by $ (x, \phi) \mapsto \phi(1, x) $.
 \end{proof}
 
-Exponentials: \TODO\\
-Global elements: \TODO\\
-Restriction of scalars: \TODO\\
-Extension of scalars: \TODO\\
-Extension of scalars preserves the monoid action: \TODO\\
-Extension of scalars preserves limits: \TODO
+\subsection{Extension and restriction of scalars}
+
+Let $ \varphi: M \to M^\prime $ be a morphism of monoids.
+
+\begin{lemma}
+  We get a \textit{restriction of scalars} functor $ \varphi_* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
+\end{lemma}
+\begin{proof}
+  Given a set $ X $ with right $ M^\prime $-action, take the set $ X $ again, and give it a right $ M $-action, sending $ (x, m) $ to $ x \varphi(m) $.
+
+  On morphisms, send an $ M^\prime $-equivariant morphism $ f: X \to X^\prime $ to the $ M $-equivariant morphism $ f: X \to X^\prime $.
+\end{proof}
+
+Since $ \SET $ has colimits, and restriction of scalars corresponds to precomposition of presheaves (on $ C_{M^\prime} $), we can give it a left adjoint.
+This is the (pointwise) left Kan extension, which boils down to:
+
+\begin{lemma}
+  We get an \textit{extension of scalars} functor $ \varphi^* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
+\end{lemma}
+\begin{proof}
+  Given a set $ X $ with right $ M $-action.
+Take $ Y = X \times M^\prime / \sim $ with the relation $ (x m, m^\prime) \sim (x, f(m) \cdot m^\prime) $ for $ m: M $.
+This has a right $ M^\prime $-action given by $ (x, m^\prime)n^\prime = (x, m^\prime n^\prime) $.
+
+  On morphisms, it sends $ f: X \to X^\prime $ to the morphism $ (x, m^\prime) \mapsto (f(x), m^\prime) $.
+\end{proof}
+
+\begin{lemma}
+  For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi^*(U_M) \cong U_{M^\prime} $.
+\end{lemma}
+\begin{proof}
+  The proof relies on the fact that for all $ m: U_M $ and $ m^\prime : M^\prime $, we have
+  \[ (m, m^\prime) \sim (1, \varphi(m) m^\prime). \]
+\end{proof}
+
+Consider the category $ D $ with $ D_0 = M^\prime $ and
+\[ D(m^\prime, \overline m^\prime) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime \}. \]
+
+If a category has an object $ t $, such that there is a morphism to it from every other object in the category, $ t $ is said to be \textit{weakly terminal}.
+
+\begin{lemma}
+  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal set with right $ M $-action, we have $ \varphi^*(I_M) \cong I_{M^\prime} $.
+\end{lemma}
+\begin{proof}
+  If $ D $ has a weakly terminal object, there exists $ \overline m^\prime : M^\prime $ such that for all $ m^\prime: M^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $.
+
+  The proof relies on the fact that every element of $ \varphi^*(I_M) $ is given by some $ (\star, m^\prime) $, but then
+  \[ (\star, m^\prime) = (\star \cdot m, m^\prime) \sim (\star, \varphi(m) \cdot m^\prime) = (\star, \overline{m^\prime}), \]
+  so $ \varphi^*(I_M) $ has exactly $ 1 $ element.
+\end{proof}
+
+\begin{remark}
+  For $ \varphi^* $ to preserve terminal objects, we actually only need $ D $ to be connected.
+The fact that $ \varphi^*(I_M) $ is a quotient by a symmetric and transitive relation then allows us to `walk' from any $ (\star, m^\prime_1) $ to any other $ (\star, m^\prime_2) $ in small steps.
+\end{remark}
+
+For any $ m^\prime_1, m^\prime_2: M^\prime $, consider the category $ D_{m^\prime_1, m^\prime_2} $, given by
+\[ D_{m^\prime_1, m^\prime_2, 0} = \{ (m^\prime, m_1, m_2): M^\prime \times M \times M \mid m_i^\prime = \varphi(m_i) \cdot m^\prime \} \]
+and
+\[ D_{m^\prime_1, m^\prime_2}((m^\prime, m_1, m_2), (\overline m^\prime, \overline m_1, \overline m_2)) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime, m_i = \overline m_i \cdot m \}.
+\]
+
+\begin{lemma}
+  Suppose that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object for all $ m^\prime_1, m^\prime_2: M^\prime $.
+Then for sets $ A $ and $ B $ with right $ M $-action, we have $ \varphi^*(A \times B) \cong \varphi^*(A) \times \varphi^*(B) $.
+\end{lemma}
+\begin{proof}
+  Now, any element in $ \varphi^*(A) \times \varphi^*(B) = (A \times M^\prime / \sim) \times (B \times M^\prime / \sim) $ is given by some $ (a, m^\prime_1, b, m^\prime_2) $.
+
+  The fact that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object means that we have some $ \overline m^\prime: M^\prime $ and $ \overline m_1, \overline m_2: M $ with $ m_i^\prime = \varphi(\overline m_i) \cdot \overline m^\prime $, such that for all $ m^\prime: M^\prime $ and $ m_1, m_2: M $ with $ m_i^\prime = \varphi(m_i) \cdot m^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \cdot m $.
+
+  Therefore,
+  \[ (a, m^\prime_1, b, m^\prime_2) = (a, \varphi(\overline m_1) \cdot \overline m^\prime, b, \varphi(\overline m_2) \cdot \overline m^\prime) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime), \]
+  so this is equivalent to some element in $ \varphi^*(A \times B) = (A \times B \times M^\prime / \sim) $.
+
+  The second part of weak terminality means that this equivalence is actually well-defined: equivalent elements in $ \varphi^*(A) \times \varphi^*(B) $ are sent to equivalent elements in $ \varphi^*(A \times B) $.
+
+  (\TODO Work this out more?)
+\end{proof}

### 2024-01-16 report/chapters/algebraic-structures.tex
Make a rough sketch of the layout of the thesis

--- 2023-10-16 report/report.tex
@@
-\documentclass[a4paper]{amsbook}
+\chapter{Algebraic Structures}
 
-\usepackage{hyperref}
-\usepackage{tikz-cd}
-
-\title{Semantics for the $ \lambda $-calculus}
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}
-
-\newcommand{\id}[1]{\ensuremath{\text{id}_{#1}}}
-\newcommand\TODO{\textbf{(TODO)} }
-
-\begin{document}
-  \maketitle
-
-  \tableofcontents
-
-  \chapter{Definitions}
-
-  \section{Algebraic Theories}
+\section{Algebraic Theories}\label{sec:algebraic-theories}
 
@@
 \begin{remark}
-    The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying algebras.
+  The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying sets.
 \end{remark}
@@
   \begin{align*}
-      \lambda(f) \bullet g &= \lambda(f \bullet (g_1, \dots, g_m, x_{n + 1}))\\
-      \rho(f \bullet g) &= \rho(f) \bullet (g_1, \dots, g_m, x_{n + 1})\\
+    \lambda_m(f) \bullet h &= \lambda_n(f \bullet (h_1 \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), \dots, h_m \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), x_{n + 1, n + 1}))\\
+    \rho_n(g \bullet h) &= \rho_m(g) \bullet (h_1 \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), \dots, h_m \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), x_{n + 1, n + 1})
   \end{align*}
-    for all $ f: L_m $ and $ g: L_n^m $. (\TODO: Fix)
+  for all $ f: L_{m + 1} $, $ g: L_m $ and $ h: L_n^m $.
 \end{definition}
@@
 
-  \chapter{Lemmas}
+\section{Examples}
 
-  \section{The endomorphism theory}
+\subsection{The free algebraic theory on a set}
+\subsection{The free object algebraic theory}
+\subsection{The initial algebraic theory}
 
-  \begin{definition}[Endomorphism theory]
-    Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
-    The endomorphism theory $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
-  \end{definition}
-
-  \begin{lemma}
-    $ E(X) $ is indeed an algebraic theory.
-  \end{lemma}
-  \begin{proof}
-    For $ 1 \leq j \leq l $, $ f: E(X)_l $, $ g: {E(X)_m}^l $ and $ h: {E(X)_n}^m $, we have
-    \[ x_j \bullet g = x_j \circ \langle g_i \rangle_i = g_j, \]
-    \[ f \bullet (x_{l,i})_i = f \circ \langle x_{l, i} \rangle_i = f \circ \id{X^l} = f \]
-    and
-    \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i.
-\]
-  \end{proof}
-
-  \begin{definition}[Endomorphism $ \lambda $-theory]
-    Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $.
-Let, for $ Y: C $, $ \varphi_Y $ be the isomorphism $ C(X \times Y, X) \xrightarrow{\sim} C(Y, X^X) $.
-    We can give $ E(X) $ a $ \lambda $-theory structure by setting, for $ f: E(X)_{n + 1} $ and $ g: E(X)_n $,
-    \[ \lambda(f) = abs \circ \varphi_{X^n}(f) \qquad \rho(g) = \varphi_{X^n}^{-1}(app \circ g). \]
-  \end{definition}
-
-  \begin{lemma}
-    $ E(X) $ is indeed a $ \lambda $-theory.
-  \end{lemma}
-  \begin{proof}
-    Note that $ \varphi: C(- \times X, X) \xrightarrow{\sim} C(-, X^X) $ is a natural isomorphism, so for $ g: {E(X)_n}^m $, the following diagram commutes
-    \begin{center}
-      \begin{tikzcd}[column sep = 1in]
-        C(X^m \times X, X) \arrow[r, "- \circ (\langle g_i \rangle_i \times \id X)"]\arrow[d, "\varphi_{X^m}", bend left] & C(X^n \times X, X^X) \arrow[d, "\varphi_{X^n}", bend left]\\
-        C(X^m, X^X) \arrow[r, "- \circ \langle g_i \rangle_i"] \arrow[u, "\varphi_{X^m}^{-1}", bend left] & C(X^n, X^X) \arrow[u, "\varphi_{X^n}^{-1}", bend left]
-      \end{tikzcd}
-    \end{center}
-    and note that $ \langle g_i \rangle_i \times \id X = \langle g_1, \dots, g_m, x_{n + 1} \rangle $. Then we have, for all $ f: E(X)_m $
-    \begin{align*}
-      \lambda_m(f) \bullet g &= abs \circ \varphi_{X^m}(f) \circ \langle g_i \rangle_i\\
-      &= abs \circ \varphi_{X^n}(f \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle)\\
-      &= \lambda_n(f \bullet (g_1, \dots, g_m, x_{n + 1}))
-    \end{align*}
-    and
-    \begin{align*}
-      \rho_n(f \bullet g) &= \varphi_{X^n}^{-1}(app \circ f \circ \langle g_i \rangle_i)\\
-      &= \varphi_{X^m}^{-1}(app \circ f) \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle\\
-      &= \rho_m(f) \bullet (g_1, \dots, g_m, x_{n + 1}).
-    \end{align*}
-  \end{proof}
-
-  \section{The theory presheaf}
-
-  \begin{definition}[The theory presheaf]
-    Let $ T $ be an algebraic theory. We can turn $ T $ into an $ T $-presheaf $ \tilde T $ by setting $ \tilde T_n = T_n $ and using the substitution from $ T $:
-    \[ \bullet: \tilde T_m \times T_n^m \to \tilde T_n. \]
-  \end{definition}
-
-  \begin{lemma}
-    $ \tilde T $ is indeed a presheaf.
-  \end{lemma}
-  \begin{proof}
-    For all $ t: \tilde T_l $, $ f: T_m^l $ and $ g: T_n^m $,
-    \[ t \bullet (x_{l, i})_i = t \]
-    and
-    \[ (t \bullet f) \bullet g = t \bullet (f_i \bullet g)_i \]
-    because $ T $ is an algebraic theory.
-  \end{proof}
-
-  \begin{lemma}
-    Given an algebraic theory $ T $ and a $ T $-presheaf $ Q $, we have for all $ n $ a bijection of sets
-    \[ \varphi: PT(\tilde T^n, Q) \cong Q_n. \]
-  \end{lemma}
-  \begin{proof}
-    Take $ \varphi(f) = f_n(x_1, \dots, x_n) $.
-
-    Conversely, take $ \varphi^{-1}(q) $ to be the presheaf morphism that sends $ t: T^n_m $ to $ q \bullet t : Q_m $. This is indeed a presheaf morphism, since for all $ t: T^n_l $ and $ f: T^l_m $,
-    \[ \varphi^{-1}(q)(t \bullet f) = q \bullet t \bullet f = \varphi^{-1}(q)(t) \bullet f. \]
-
-    Now, for a presheaf morphism $ f: T^n \to Q $ and $ t: T^n_m $, we have
-    \[ \varphi^{-1}(\varphi(f))(t) = f_n(x_1, \dots, x_n) \bullet t = f_n((x_1, \dots, x_n) \bullet t) = f_n(t_1, \dots, t_n) = f_n(t). \]
-
-    Conversely, given $ q: Q_n $, we have
-    \[ \varphi(\varphi^{-1}(q)) = q \bullet (x_1, \dots, x_n) = q. \]
-    which concludes the proof.
-  \end{proof}
-
-  \section{The `+l' presheaf}
+\subsection{The terminal theory}
+\subsection{The Endomorphism Theory}
+\subsection{The free \texorpdfstring{$ \lambda $}{lambda}-theory}
+\subsection{The \texorpdfstring{$ \lambda $}{lambda}-calculus}
+\subsection{The theory presheaf}
+\subsection{The theory algebra}
+\subsection{The "+l" presheaf}
 
@@
 \end{proof}
-
-  \section{Exponentiability of the theory presheaf}
-
-  \begin{lemma}
-    For all $ l $, the presheaf $ \tilde T^l $ is exponentiable.
-  \end{lemma}
-  \begin{proof}
-    We will show that $ A(-, l) $ constitutes a right adjoint to the functor $ - \times \tilde T^l $.
-We will do this using universal arrows (\cite{MacLane}, Chapter IV.1, Theorem 2 (iv)).
-To that end, we will need for all $ Q: PT $ a universal arrow $ \varphi: A(Q, l) \times \tilde T^l \to Q $.
-
-    For $ q: A(Q, l)_n = Q_{n + l} $ and $ t: \tilde T^l_n $, we take $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $.
-
-    This is a presheaf morphism, since for all $ q: A(Q, l)^l_m $, $ t: \tilde T^l_m $ and $ f: T_n^m $,
-    \begin{align*}
-      \varphi((q, t) \bullet_{A(Q, l) \times \tilde \tilde T^l} f) &= \varphi(q \bullet_{A(Q, l)} f, t \bullet_{\tilde T^l} f)\\
-      &= q \bullet_{A(Q, l)} f \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
-      &= q \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i) \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
-      &= q \bullet_Q ((\iota_{n, l}(f_i) \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i + (x_{n + i} \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i)\\
-      &= q \bullet_Q ((f_i \bullet_T (x_j)_j)_i + ((t \bullet_{\tilde T^l} f)_i)_i)\\
-      &= q \bullet_Q ((f_i)_i + (t_i \bullet_{\tilde T} f)_i)\\
-      &= q \bullet_Q ((x_i \bullet_T f)_i + (t_i \bullet_T f)_i)\\
-      &= q \bullet_Q ((x_i)_i + t) \bullet_Q f\\
-      &= \varphi(q, t) \bullet_Q f.
-    \end{align*}
-
-    Now, given any presheaf $ Q^\prime : P T $ we need to show that any morphism $ \psi: Q^\prime \times \tilde T^l \to Q $ factors uniquely as $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) $ for some $ \tilde \psi: Q^\prime \to A(Q, l) $.
-
-    So, given such a $ \psi $, and given $ q: Q^\prime_n $, we take $ \tilde \psi(q) = \psi(\iota_{n, l}(q), (x_{n + i})_i) $
-
-    This is a presheaf morphism, since for all $ q: Q^\prime_m $ and $ f : T_n^m $,
-    \begin{align*}
-      \tilde \psi(q \bullet f) &= \psi(\iota_{n, l}(q \bullet f), (x_{n + i})_i)\\
-      &= \psi(q \bullet (\iota_{n, l}(f_i))_i, (x_{n + i})_i)\\
-      &= \psi((\iota_{m, l}(q), (x_{m + i})_i) \bullet_{Q^\prime \times \tilde T^l} ((\iota_{n, l}(f_i))_i + (x_{n + i})_i))\\
-      &= \psi(\iota_{m, l}(q), (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i)\\
-      &= \tilde \psi(q) \bullet_{A(Q, l)} f.
-    \end{align*}
-    Note that indeed $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) = \psi $:
-    \begin{align*}
-      \varphi(\tilde \psi(q), t) &= \varphi(\psi(\iota_{n, l}(q), (x_{n + i})_i), t)\\
-      &= \psi(\iota_{n, l}(q), (x_{n + i})_i) \bullet ((x_i)_i + t)\\
-      &= \psi(\iota_{n, l}(q) \bullet ((x_i)_i + t), (x_{n + i})_i \bullet ((x_i)_i + t))\\
-      &= \psi(q \bullet (x_i)_i, (t_i)_i)\\
-      &= \psi(q, t).\\
-    \end{align*}
-    Now, suppose that we have another $ \tilde \psi^\prime : Q^\prime \to A(Q, l) $ such that $ \varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}) = \psi $. Then we have
-    \begin{align*}
-      \tilde \psi(q) &= \psi(\iota_{n, l}(q), (x_{n + i})_i)\\
-      &= (\varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}))(\iota_{n, l}(q), (x_{n + i})_i)\\
-      &= \varphi(\tilde \psi^\prime(\iota_{n, l}(q)), (x_{n + i})_i)\\
-      &= \tilde \psi^\prime(\iota_{n, l}(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
-      &= \iota_{n, l}(\tilde \psi^\prime(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
-      &= \tilde \psi^\prime(q) \bullet (x_i)_i\\
-      &= \tilde \psi^\prime(q),
-    \end{align*}
-    so $ \tilde \psi $ is unique, which completes the proof.
-  \end{proof}
-
-  Now, this adjunction $ - \times \tilde T^l \dashv A(-, l) $ induces a natural isomorphism
-  \[ \varphi: PT(- \times \tilde T^l, \tilde T) \xrightarrow{\sim} PT(-, A(\tilde T, l)) \]
-  \begin{lemma}
-    For all $ f: PT(\tilde T^n \times \tilde T^l, \tilde T) $,
-    \[ \varphi_{\tilde T^n}(f)(q) = f(\iota_{m, l}(q), (x_{m + i})_i) \]
-  \end{lemma}
-  \begin{proof}
-    \TODO
-  \end{proof}
-
-  \begin{lemma}
-    For all $ f: PT(\tilde T^n, A(\tilde T, l)) $,
-    \[ \varphi_{\tilde T^n}^{-1}(f)(q, t) = f(q) \bullet ((x_i)_i + t). \]
-  \end{lemma}
-  \begin{proof}
-    \TODO
-  \end{proof}
-
-  \chapter{Theorems}
-
-  \section{Scott's Representation Theorem}
-  \begin{theorem}
-    Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E(\tilde L) $ of $ \tilde L $ in the presheaf category of $ L $.
-  \end{theorem}
-  \begin{proof}
-    First of all, remember that $ \tilde L $ is indeed exponentiable and that $ \tilde L^{\tilde L} = A(\tilde L, 1) $.
-    Now, since $ L $ is a $ \lambda $-theory, we have functions back and forth $ \lambda: A(\tilde L, 1) \to \tilde L $ and $ \rho: \tilde L \to A(\tilde L, 1) $.
-These are presheaf morphisms because for all $ f: A(\tilde L, 1)_m $ and $ g: \tilde L_m $ and $ t: T_n^m $,
-    \[ \lambda(f \bullet_{A(\tilde L, 1)} t) = \lambda(f \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1}))) = \lambda(f) \bullet_{\tilde L} t \]
-    and
-    \[ \rho(g \bullet_{\tilde L} t) = \rho(g) \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1})) = \rho(g) \bullet_{A(\tilde L, 1)} t. \]
-    Therefore, $ E(\tilde L) $ is indeed a $ \lambda $-theory.
-
-    For any presheaf $ Q $ and for any $ n $, we have a bijection $ PL(L^n, Q) \cong Q_n $.
-    Then we have $ \varphi: E(\tilde L)_n \cong L_n $.
-    This bijection is an isomorphism of $ \lambda $-theories, since it preserves the $ x_i $, $ \bullet $, $ \rho $ and $ \lambda $: for all $ 1 \leq j \leq n $, $ f: E(\tilde L)_m $, $ g: E(\tilde L)_{m + 1} $ and $ h: E(\tilde L)_n^m $.
-    \begin{align*}
-      \varphi(x_j) &= x_j(x_1, \dots, x_n)\\
-      &= x_j;\\
-      \varphi(f \bullet h) &= f \circ \langle h_i \rangle_i((x_i)_i)\\
-      &= f((h_i((x_j)_j))_i)\\
-      &= f((x_i)_i \bullet (h_i((x_j)_j))_i)\\
-      &= f((x_i)_i) \bullet (h_i((x_j)_j))_i\\
-      &= \varphi(f) \bullet (\varphi(h_i))_i;\\
-      \varphi(\rho(f)) &= \rho(f)((x_i)_i)\\
-      &= \rho(f((x_i)_i)) \bullet (x_i)_i\\
-      &= \rho(f((x_i)_i))\\
-      &= \rho(\varphi(f));\\
-      \varphi(\lambda(g)) &= \lambda(g)((x_i)_i)\\
-      &= \lambda(\varphi_{X^n}(g)((x_i)_i))\\
-      &= \lambda(g(\iota_{m, l}((x_i)_i) + (x_{m + 1})))\\
-      &= \lambda(g((x_i)_i))\\
-      &= \lambda(\varphi(g)).
-    \end{align*}
-  \end{proof}
-
-  \section{Locally cartesian closedness of the category of retracts}
-  \begin{theorem}
-    The category of retracts \TODO is locally cartesian closed \TODO.
-  \end{theorem}
-
-  \section{The Fundamental Theorem of the \texorpdfstring{$ \lambda $-}{lambda }calculus}
-  \begin{theorem}
-    There exists an adjoint equivalence between the category of $ \lambda $-theories, and the category of algebras of $ \Lambda $ \TODO.
-  \end{theorem}
-  \begin{proof}
-    In one direction, the proof sends a $ \lambda $-theory $ L $ to the $ L $-algebra $ L(0) $ \TODO.
-Since $ \Lambda $ is the initial $ \lambda $-theory \TODO, we can give $ L(0) $ a $ \Lambda $-algebra structure \TODO.
-This constitutes a functor \TODO.
-
-    In the other direction, it sends a $ \Lambda $-algebra $ A $ to the theory of extensions $ \Lambda_A $ \TODO.
-It is a $ \lambda $-theory because it is isomorphic \TODO to the endomorphism $ \lambda $-theory $ E(A(1)) $ of the object $ A(1) $ in $ PA $ \TODO.
-
-    These constitute an adjoint equivalence. \TODO
-  \end{proof}
-
-  \bibliographystyle{alpha}
-  \bibliography{citations}
-
-\end{document}

### 2024-01-16 report/chapters/alternative-definitions.tex
Make a rough sketch of the layout of the thesis

\chapter{Alternative definitions}
The literature, there are many different but equivalent definitions, carrying many different names, for the objects that called `algebraic theories' in Section \ref{sec:algebraic-theories}. What makes matters even more confusing is the fact that the literature does not provide a consistent bijection between names and definitions. This section will showcase some of the various definitions.

% First of all, let $ \F $ be a skeleton of finite sets: the category with $ \F_0 = \{ 0, 1, \dots \} $ and $ \F(m, n) = \SET(\{1, 2, \dots, m\}, \{1, 2, \dots, n\}) $.

\section{Abstract Clone}
\begin{definition}[abstract clone]
  An algebraic theory as presented in Section \ref{sec:algebraic-theories}, is usually called an \textit{abstract clone}. In this thesis, outside of this specific section, we will call it algebraic theory to be consistent with the names that Hyland attaches to objects.
\end{definition}

\section{Lawvere theory}
\begin{definition}[algebraic theory]
  An \textit{algebraic theory} as presented in \cite{algebaric-theories-2010} is a small category with finite products.
\end{definition}
\begin{definition}[algebraic theory algebra]
  An \textit{algebra} for an algebraic theory $ T $ is a finite-product-preserving functor $ T \to \SET $.
\end{definition}

This definition is more general than the definition of algebraic theory in Section \ref{sec:algebraic-theories}. To make it equivalent, we have to be more specific about the objects of the category:
\begin{definition}[Lawvere theory]
  A \textit{Lawvere theory}, or \textit{one-sorted algebraic theory} is a category $ L $, with $ L_0 = \{ 0, 1, \dots \} $, such that $ n = 1^n $, the $ n $-fold product.
\end{definition}

\subsection{Algebras for Lawvere Theories}

\section{Relative Monad}
\begin{definition}[relative monad]
  Let $ S: C \to D $ be a functor. A \textit{relative monad} on $ S $ is a functor $ T: C \to D $, together with a natural transformation $ \eta: S \Rightarrow T $ and a transformation $ (-)^*: D(S(X), T(Y)) \to D(T(X), T(Y)) $, natural in both $ S $ and $ T $, such that for all $ f: S(X) \to T(Y) $ and $ g: S(Y) \to T(Z) $,
  \[ f = \eta_X \cdot f^*, \qquad \eta_X^* = \id{T X} \qquad \text{and} \qquad (f \cdot g^*)^* = f^* \cdot g^*. \]
\end{definition}

\section{Cartesian Operad}
\begin{definition}[multicategory]
  A \textit{multicategory} $ C $ consists of
  \begin{itemize}
    \item A collection of objects $ C_0 $;
    \item For all $ c_1, \dots, c_n, d: C_0 $, a collection of multimorphisms $ C((c_1, \dots, c_n), d) $;
    \item For all $ c: C_0 $, an identity morphism $ \id c : C(c, c) $;
    \item For all multimorphisms $ f: C((d_1, \dots, d_n), e) $ and $ g_i: C((c_{i,1}, \dots, c_{i,m_i}), d_i) $ for $ 1 \leq n \leq i $, a composite multimorphism
    \[ (g_1, \dots, g_n) \cdot f: C((c_{1,1}, \dots, c_{n, m_n}), e) \]
  \end{itemize}
  such that these satisfy certain identity and associativity axioms (see for example \cite{higher-operads}, page 35).
\end{definition}

Let $ S_n $ be the symmetric group on $ n $ elements (the group consisting of all ways to shuffle the numbers $ (1, \dots, n) $).

\begin{definition}[symmetric multicategory]
  A \textit{symmetric} multicategory is a multicategory $ C $, together with, for each $ \sigma: S_n $ and all $ c_1, \dots, c_n, d $, a bijection
  \[ \overline \sigma: C((c_1, \dots, c_n), d) \to C((c_{\sigma(1)}, \dots, c_{\sigma(n)}), d), \]
  such that for all $ \rho, \sigma: S_n $ and $ \theta: C((c_1, \dots, c_n), d) $,
  \[ \overline \rho(\overline \sigma(\theta)) = \overline{(\sigma \rho)}(\theta) \quad \text{and} \quad \overline {1_{S_n}}(\theta) = \theta, \]
  compatible with multimorphism composition (see \cite{higher-operads}, page 52, equation (2:7)).
\end{definition}
In some sense, for a symmetric multicategory, the order of the objects in the domain of a multimorphism does not matter.

For a collection $ S $ and a tuple $ x = x_1, \dots, x_n: S $ and $ 1 \leq i \leq j \leq n $,
\begin{itemize}
  \item let $ u_i(x): S^{n+i+1-j} $ denote the tuple $ x $, but with the subtuple $ (x_i, \dots, x_j) $ repeated once:
    \[ (x_1, \dots, x_i, \dots, x_j, x_i, \dots, x_j, \dots, x_n). \]
  \item let $ v_i(x): S^{n-i-1+j} $ denote the tuple $ x $, but with the subtuple $ (x_i, \dots, x_j) $ removed:
    \[ (x_1, \dots, x_{i-1}, x_{j+1}, \dots, x_n). \]
\end{itemize}

\begin{definition}[cartesian multicategory]
  A \textit{cartesian multicategory} is a multicategory $ C $, with, for all $ c_1, \dots, c_n, d: C_0 $ and $ 1 \leq i \leq n $
  \begin{itemize}
    \item a \textit{contraction} operation $ \overline{u_i}: C(u_{i, i}(c), d) \to C(c, d) $,
    \item a \textit{deletion} operation $ \overline {v_i}: C(v_{i, i}(c), d) \to C(c, d) $,
  \end{itemize}
  that satisfy some axioms \TODO
\end{definition}

\begin{definition}[cartesian operad]
  A \textit{cartesian operad} is a cartesian multicategory with one object.
\end{definition}

\begin{lemma}
  The following are equivalent:
  \begin{enumerate}[(1)]
    \item An abstract clone.
    \item A Lawvere theory.
    \item A relative monad on the embedding $ \iota: \FinSET \hookrightarrow \SET $.
    \item A cartesian operad.
  \end{enumerate}
\end{lemma}
\begin{proof}
  $ (1) \Rightarrow (2) $: Given an abstract clone $ C $, we construct a Lawvere theory $ L $ as follows: We have objects $ L_0 = \{ 0, 1, \dots \} $ and morphisms $ L(m, n) = C_m^n $. The identity morphism is $ \id n = (x_i)_i : L(n, n) $ and for $ f: L(l, m) $, $ g: L(m, n) $, we have composition
  \[ f \cdot g = (g_i \bullet f)_i: L(l, n). \]
  Lastly, we have product projections $ \pi_{n, i} = x_{n, i}: L(n, 1) $ for all $ 1 \leq i \leq n $.

  $ (2) \Rightarrow (3) $: Given a Lawvere theory $ L $, we construct a relative monad $ (F, \eta) $ as follows: For $ n: \FinSET $, take $ F(n) = L(n, 1) $ and for $ a: \FinSET(m, n) $, let $ F(a): \SET(F(m), F(n)) $ be the morphism given by precomposition with the product morphism
  \[ \langle \pi_{n, a(1)}, \dots, \pi_{n, a(m)} \rangle : L(n, m). \]
  The natural transformation is given by $ \eta_n(i) = \pi_{n, i}: F(n) $ for all $ i: \iota(n) = \{1, \dots, n\} $. Lastly, for $ f: \SET(\iota(m), F(n)) $, let $ f : \SET(F(m), F(n)) $ be given by precomposition with the product morphism
  \[ \langle f(1), \dots, f(m) \rangle : L(n, m) \]

  $ (3) \Rightarrow (4) $: Given a relative monad $ (F, \eta) $, we construct a cartesian operad $ A $ as follows: We take a multicategory with $ A_0: \{ \star \} $. We take as the set of $ n $-fold morphisms $ A((\star)_i, \star) = F(n) $. We take an identity multimorphism $ \id \star = \eta_1(1) : A(\star, star) $.
  For some natural number $ m $, natural numbers $ n_1, \dots, n_m $ and $ i: 1 \leq i \leq m $ let $ \phi_i: \FinSET(n_i, \sum n_i) $ be the standard injections into the coproduct. For $ f: F(m) $ and $ g_i: F(n_i) $, we have $ F(\varphi_i): \SET(F(n_i), F(\sum n_i)) $, so we have $ (F(\varphi_i)(g_i))_i: \SET(\iota(m), F(\sum n_i)) $ and the composition is given by
  \[ f \cdot g = (F(\varphi_i)(g_i))_i^*(f): F\left(\sum n_i\right). \]

  The permutation, contraction and deletion operations given by
  \begin{align*}
    \overline{\sigma} = F(\sigma): A((\star_1, \dots, \star_n), \star) \to A((\star_{\sigma(1)}, \dots, \star_{\sigma(n)}), \star)
  \end{align*}

  Given a cartesian operad $ A $
  \TODO
\end{proof}

### 2024-01-16 report/chapters/category-theory.tex
Make a rough sketch of the layout of the thesis

@@
 
-\section{Adjunctions}
+\section{Quick preliminaries}
+\subsection{Adjunctions}
 An adjoint equivalence of categories has multiple definitions. The one we will use here is the following:
@@
 \end{definition}
+
+\subsection{Exponential objects}
+\TODO
 
@@
 \begin{remark}
+  Actually, we have a functor from the category of monoids to the category of setcategories (categories whose object type is a set).
+
+  A monoid morphism $ f: M \to M^\prime $ is equivalent to a functor $ F_f: C_M \to C_{M^\prime} $.
+Any functor between $ C_M $ and $ C_{M^\prime} $ sends $ \star_M $ to $ \star_{M^\prime} $.
+The monoid morphism manifests as $ F_f(m) = f(m) $ for $ m: C_M(\star, \star) = M $.
+\end{remark}
+
+\begin{lemma}
   An isomorphism of monoids gives an (adjoint) equivalence of categories.
-\end{remark}
+\end{lemma}
+\begin{proof}
+  Given an isomorphism $ f: M \to M^\prime $.
+Then we have functors $ F_f: C_M \to C_{M^\prime} $ and $ F_{f^{-1}}: C_{M^\prime} \to C_M $.
+Take the identity natural transformations $ \eta: \id{C_M} \Rightarrow F_f \bullet F_{f^{-1}} $ and $ \epsilon: F_{f^{-1}} \bullet F_f \Rightarrow \id{C_{M^\prime}} $.
+Of course these are natural isomorphisms.
+\end{proof}
 

### 2024-01-16 report/chapters/formalization.tex
Make a rough sketch of the layout of the thesis

\chapter{The formalization}

\section{Statistics}

\section{Components}

\section{Displayed categories}

\subsection{Defininig objects by their category instead of the other way around}

\subsection{\_ax for categories and their objects}

\subsection{Cartesian vs cartesian'}

\section{Inductive types}

\section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus}
Defining Lambda Calculus in a different way (not as an axiomatized HIT)
  - As set quotient instead of HIT
  - With a signature

\section{Tuples}
$ stn m \to A $ vs vec A

\section{Products}
$ T \times (T \times \dots \times T) $ vs $ T \times T^n vs T^(S n) $
Terminal as product over empty set
over any set with a function to empty.

\section{The \texorpdfstring{$ n + p $}{n + p}-presheaf}
L (S n) (for lambda) vs L (n + 1) (stemming from the naive implementation of the L (n + p) presheaf)

\section{Quotients}
Quotients (by hrel or eqrel) vs coproducts (generalizing to arbitrary category with coproduct) vs a category with some structure

\section{The Karoubi envelope}
KanExtension instead of specific construction at KaroubiEnvelope

\section{Univalence}
Univalence bewijzen via isweqhomot vs direct

### 2024-01-16 report/chapters/paper.tex
Make a rough sketch of the layout of the thesis

--- 2023-11-01 report/report.tex
@@
-\documentclass[a4paper]{amsbook}
-
-\usepackage{hyperref}
-\usepackage{tikz-cd}
-
-\title{Semantics for the $ \lambda $-calculus}
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}
-
-\newcommand{\id}[1]{\ensuremath{\text{id}_{#1}}}
-\newcommand{\op}[1]{\ensuremath{#1^{\text{op}}}}
-\newcommand\SET{\mathbf{SET}}
-\newcommand\TODO{\textbf{(TODO)} }
-
-\begin{document}
-  \maketitle
-
-  \tableofcontents
-
-  \chapter{Definitions}
-
-  \section{Algebraic Theories}
-
-  \begin{definition}[algebraic theory]
-    We define an algebraic theory $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we usually leave $ n $ implicit), together with a substitution operation
-    \[ \_ \bullet \_: T_m \times T_n^m \to T_n \]
-    for all $ m, n $, such that
-    \begin{align*}
-      x_j \bullet g &= g_j\\
-      f \bullet (x_{l, i})_i &= f\\
-      (f \bullet g) \bullet h &= f \bullet (g_i \bullet h)_i
-    \end{align*}
-    for all $ 1 \leq j \leq l $, $ f: T_l $, $ g: T_m^l $ and $ h: T_n^m $.
-  \end{definition}
-
-  \begin{definition}[algebraic theory morphism]
-    A morphism $ F $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ F_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
-    \begin{align*}
-      F_n(x_j) &= x_j\\
-      F_n(f \bullet g) &= F_m(f) \bullet (F_n(g_i))_i
-    \end{align*}
-    for all $ 1 \leq j \leq n $, $ f: T_m $ and $ g: T_n^m $.
-  \end{definition}
-
-  \begin{remark}
-    We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
-    \[ (f, f^\prime) \bullet (g, g^\prime) = (f \bullet g, f^\prime \bullet g^\prime). \]
-    In the same way, the category of algebraic theories has all limits.
-  \end{remark}
-
-  \section{Algebras}
-
-  \begin{definition}[algebra]
-    An algebra $ A $ for an algebraic theory $ T $ is a set $ A $, together with an action
-    \[ \bullet: T_n \times A^n \to A \]
-    for all $ n $, such that
-    \begin{align*}
-      x_j \bullet a &= a_j\\
-      (f \bullet g) \bullet a &= f \bullet (g_i \bullet a)_i
-    \end{align*}
-    for all $ j $, $ f: T_m $, $ g: T_n^m $ and $ a: A^n $.
-  \end{definition}
-
-  \begin{definition}[algebra morphism]
-    For an algebraic theory $ T $, a morphism $ F $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ F: A \to A $ such that
-    \[ F(f \bullet a) = f \bullet (F(a_i))_i \]
-    for all $ f: T_n $ and $ a: A^n $.
-  \end{definition}
-
-  \begin{remark}
-    The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying algebras.
-  \end{remark}
-
-  \begin{remark}
-    Note that for an algebraic theory $ T $, the $ T_n $ are all algebras for $ T $, with the action given by $ \bullet $.
-  \end{remark}
-
-  \section{Presheaves}
-
-  \begin{definition}[presheaf]
-    A presheaf $ P $ for an algebraic theory $ T $ is a sequence of sets $ P_n $ indexed over $ \mathbb N $, together with an action
-    \[ \bullet: P_m \times T_n^m \to P_n \]
-    for all $ m, n $, such that
-    \begin{align*}
-      t \bullet (x_{l, i})_i &= t\\
-      (t \bullet f) \bullet g &= t \bullet (f_i \bullet g)_i
-    \end{align*}
-    for all $ t: P_l $, $ f: T_m^l $ and $ g: T_n^m $.
-  \end{definition}
-
-  \begin{definition}[presheaf morphism]
-    For an algebraic theory $ T $, a morphism $ F $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ F_n: P_n \to P^\prime_n $ such that
-    \[ F_n(t \bullet f) = F_m(t) \bullet f \]
-    for all $ t: P_m $ and $ f: T_n^m $.
-  \end{definition}
-
-  We will write $ PT $ for the category of $ T $-presheaves and their morphisms.
-
-  \begin{remark}
-    The category of presheaves has all limits.
-The $ n $th set $ \overline{P}_n $ of a limit $ \overline{P} $ of presheaves $ P_i $ is the limit of the $ n $th sets $ P_{i, n} $ of the presheaves in the limit diagram.
-  \end{remark}
-
-  \section{\texorpdfstring{$ \lambda $-}{lambda-}theories}
-
-  \begin{definition}[$ \lambda $-theory]
-    A $ \lambda $-theory is an algebraic theory $ L $, together with sequences of functions $ \lambda_n: L_{n + 1} \to L_n $ and $ \rho_n: L_n \to L_{n + 1} $, such that
-    \begin{align*}
-      \lambda(f) \bullet g &= \lambda(f \bullet (g_1, \dots, g_m, x_{n + 1}))\\
-      \rho(f \bullet g) &= \rho(f) \bullet (g_1, \dots, g_m, x_{n + 1})\\
-    \end{align*}
-    for all $ f: L_m $ and $ g: L_n^m $. (\TODO: Fix)
-  \end{definition}
-
-  \begin{definition}[$ \beta $- and $ \eta $-equality]
-    We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $.
-We say that is satisfies $ \eta $-equality if $ \lambda_n \circ \rho_n = \id{L_{n + 1}} $ for all $ n $.
-  \end{definition}
-
-  \begin{definition}[$ \lambda $-theory morphism]
-    A morphism $ F $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ F $ such that
-    \begin{align*}
-      F_n(\lambda_n(f)) &= \lambda_n(F_{n + 1}(f))\\
-      \rho_n(F_n(g)) &= F_{n + 1}(\rho_n(g))
-    \end{align*}
-    for all $ f: L_{n + 1} $ and $ g: L_n $.
-  \end{definition}
-
-  \begin{remark}
-    The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories.
-  \end{remark}
-
-  A $ \lambda $-theory algebra or presheaf is a presheaf for the underlying algebraic theory.
-
-  \chapter{Lemmas}
+\chapter{The paper}
 
@@
   and
-    \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i.
-\]
+  \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i. \]
 \end{proof}
@@
 \section{The `+l' presheaf}
-
-  Let $ \iota_{m, n} : T_m \to T_{m + n} $ denote the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
-  \[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \]
-  and
-  \[ \iota_{m, n}(f \bullet g) = f \bullet g \bullet (x_i)_i = f \bullet (g_i \bullet (x_j)_j)_i = f \bullet (\iota_{m, n}(g_i))_i. \]
-
-  For tuples $ x : X^m $ and $ y: X^n $, let $ x + y $ denote the tuple $ (x_1, \dots, x_m, y_1, \dots, y_n) : X^{m + n} $.
-
-  \begin{definition}[The `+l' presheaf]
-    Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, l) $, given by $ A(Q, l)_n = Q_{n + l} $. Then, for $ q: A(Q, l)_m $ and $ f: T_n^m $, the substitution is given by
-    \[ q \bullet_{A(Q, l)} f = q \bullet_Q ((\iota_{n, l} (f_i))_i + (x_{n + i})_i) \]
-  \end{definition}
-  \begin{lemma}
-    The +l presheaf is a presheaf
-  \end{lemma}
-  \begin{proof}
-    We have, for $ q: A(Q, l)_n $,
-    \begin{align*}
-      q \bullet_{A(Q, l)} (x_i)_i &= q \bullet_Q ((\iota_{n, l}(x_i))_i + (x_{n + i})_i)\\
-      &= q \bullet_Q ((x_i)_i + (x_{n + i})_i)\\
-      &= q \bullet_Q (x_i)_i\\
-      &= q.
-    \end{align*}
-    We have, for $ q : A(Q, k)_l $, $ f: T_m^l $ and $ g: T_n^m $,
-    \begin{align*}
-      q \bullet_{A(Q, k)} f \bullet_{A(Q, k)} g &= q \bullet_Q ((\iota_{m, l}(f_i))_i + (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(g_i))_i + (x_{n + i})_i)\\
-      &= q \bullet_Q (((\iota_{m, l}(f_i) \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i + (x_{m + i} \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i))\\
-      &= q \bullet_Q ((f_i \bullet_T (\iota_{n, l}(g_j))_j)_i + (x_{n + i})_i)\\
-      &= q \bullet_Q ((\iota_{n, l}(f_i \bullet_T g))_i + (x_{n + i})_i)\\
-      &= q \bullet_{A(Q, k)} (f_i \bullet_T g).
-    \end{align*}
-  \end{proof}
-
-  \section{Exponentiability of the theory presheaf}
 
@@
 
-  \chapter{Theorems}
-
 \section{Scott's Representation Theorem}
@@
 \end{theorem}
+
+\section{Equivalences}
 
@@
 
+\section{An alternative proof for the fundamental theorem}
+
+\section{Theory of extensions}
+
 \begin{lemma}
@@
 \end{proof}
-
-  \bibliographystyle{alpha}
-  \bibliography{citations}
-
-\end{document}

### 2024-01-16 report/chapters/previous-work.tex
Make a rough sketch of the layout of the thesis

\chapter{Previous work in categorical semantics}

\section{The correspondence between categories and \texorpdfstring{$ \lambda $}{lambda}-calculi}
In \cite{curry}, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects'). (See page 413).

Types in the $ \lambda $-calculus correspond to objects in the category.

Types $ A \to B $ in the $ \lambda $-calculus correspond to exponential objects $ B^A $ in the category.

Terms in the $ \lambda $-calculus of type $ B $, with free variables $ x_1: A_1, \dots, x_n: A_n $, correspond to morphisms $ A_1 \times \dots \times A_n \to B $.

A free variable $ x_i: A_i $ in a context with free variables $ x_1: A_1, \dots, x_n: A_n $ corresponds to the projection morphism $ \pi_i : A_1 \times \dots \times A_n \to A_i $.

Given a term $ s: B_1 \to B_2 $ and a term $ t: B_1 $, both with free variables $ x_1: A_1, \dots, x_n: A_n $, corresponding to morphisms $ \overline s: A_1 \times \dots \times A_n \to B_2 $ and $ \overline t: A_1 \times \dots \times A_n \to B_1 $, the application $ st: B_2 $ corresponds to the composite of the product morphism with the evaluation morphism $ A_1 \times \dots \times A_n \to B_2^{B_1} \times B_1 \to B_2 $.
\begin{center}
  \begin{tikzcd}
    & A_1 \times \dots \times A_n \arrow[ld, "\overline s"'] \arrow[rd, "\overline t"] \arrow[d, "{\langle \overline s, \overline t \rangle}", dashed] &\\
    B_2^{B_1} & B_2^{B_1} \times B_1 \arrow[l, "\pi_1"] \arrow[r, "\pi_2"'] \arrow[d, "ev"] & B_1\\
    & B_2 &
  \end{tikzcd}
\end{center}

Given a term $ t: B $ with free variables $ x_1: A_1, \dots, x_n: A_n $, the abstraction $ (\lambda x_n, t): A_n \to B $ corresponds to using the adjunction $ - \times A_n \dashv (-)^{A_n} $:
\[ C(A_1 \times \dots \times A_{n-1} \times A_n, B) \simeq C(A_1 \times \dots \times A_{n-1}, B^{A_n}). \]

\TODO
How about the untyped $ \lambda $-calculus?

\section{Scott's Representation Theorem}

\section{The Taylor Fibration}

### 2024-01-16 report/chapters/univalent-foundations.tex
Make a rough sketch of the layout of the thesis

\chapter{Univalent Foundations}

\section{Equality and homotopy}
\section{hProps and hSets}
\section{Transports and transport hell}
\section{The univalence axiom}
\section{Univalent categories}

### 2024-01-16 report/report.tex
Start writing the report in earnest
Make a rough sketch of the layout of the thesis

--- 2023-10-16 report/report.tex
@@
 \usepackage{tikz-cd}
+\usepackage{enumerate}
 
@@
 \newcommand{\id}[1]{\ensuremath{\text{id}_{#1}}}
+\newcommand{\op}[1]{\ensuremath{#1^{\text{op}}}}
+\newcommand{\Lan}[2]{\ensuremath{\text{Lan}_{#1}#2}}
+\newcommand\SET{\mathbf{SET}}
+% \newcommand\F{\mathbf{F}}
+\newcommand\FinSET{\mathbf{FinSET}}
 \newcommand\TODO{\textbf{(TODO)} }
@@
 
+  \setcounter{tocdepth}{4}
   \tableofcontents
 
-  \chapter{Definitions}
-
-  \section{Algebraic Theories}
-
-  \begin{definition}[algebraic theory]
-    We define an algebraic theory $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we usually leave $ n $ implicit), together with a substitution operation
-    \[ \_ \bullet \_: T_m \times T_n^m \to T_n \]
-    for all $ m, n $, such that
-    \begin{align*}
-      x_j \bullet g &= g_j\\
-      f \bullet (x_{l, i})_i &= f\\
-      (f \bullet g) \bullet h &= f \bullet (g_i \bullet h)_i
-    \end{align*}
-    for all $ 1 \leq j \leq l $, $ f: T_l $, $ g: T_m^l $ and $ h: T_n^m $.
-  \end{definition}
-
-  \begin{definition}[algebraic theory morphism]
-    A morphism $ F $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ F_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
-    \begin{align*}
-      F_n(x_j) &= x_j\\
-      F_n(f \bullet g) &= F_m(f) \bullet (F_n(g_i))_i
-    \end{align*}
-    for all $ 1 \leq j \leq n $, $ f: T_m $ and $ g: T_n^m $.
-  \end{definition}
-
-  \begin{remark}
-    We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
-    \[ (f, f^\prime) \bullet (g, g^\prime) = (f \bullet g, f^\prime \bullet g^\prime). \]
-    In the same way, the category of algebraic theories has all limits.
-  \end{remark}
-
-  \section{Algebras}
-
-  \begin{definition}[algebra]
-    An algebra $ A $ for an algebraic theory $ T $ is a set $ A $, together with an action
-    \[ \bullet: T_n \times A^n \to A \]
-    for all $ n $, such that
-    \begin{align*}
-      x_j \bullet a &= a_j\\
-      (f \bullet g) \bullet a &= f \bullet (g_i \bullet a)_i
-    \end{align*}
-    for all $ j $, $ f: T_m $, $ g: T_n^m $ and $ a: A^n $.
-  \end{definition}
-
-  \begin{definition}[algebra morphism]
-    For an algebraic theory $ T $, a morphism $ F $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ F: A \to A $ such that
-    \[ F(f \bullet a) = f \bullet (F(a_i))_i \]
-    for all $ f: T_n $ and $ a: A^n $.
-  \end{definition}
-
-  \begin{remark}
-    The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying algebras.
-  \end{remark}
-
-  \begin{remark}
-    Note that for an algebraic theory $ T $, the $ T_n $ are all algebras for $ T $, with the action given by $ \bullet $.
-  \end{remark}
-
-  \section{Presheaves}
-
-  \begin{definition}[presheaf]
-    A presheaf $ P $ for an algebraic theory $ T $ is a sequence of sets $ P_n $ indexed over $ \mathbb N $, together with an action
-    \[ \bullet: P_m \times T_n^m \to P_n \]
-    for all $ m, n $, such that
-    \begin{align*}
-      t \bullet (x_{l, i})_i &= t\\
-      (t \bullet f) \bullet g &= t \bullet (f_i \bullet g)_i
-    \end{align*}
-    for all $ t: P_l $, $ f: T_m^l $ and $ g: T_n^m $.
-  \end{definition}
-
-  \begin{definition}[presheaf morphism]
-    For an algebraic theory $ T $, a morphism $ F $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ F_n: P_n \to P^\prime_n $ such that
-    \[ F_n(t \bullet f) = F_m(t) \bullet f \]
-    for all $ t: P_m $ and $ f: T_n^m $.
-  \end{definition}
-
-  We will write $ PT $ for the category of $ T $-presheaves and their morphisms.
-
-  \begin{remark}
-    The category of presheaves has all limits.
-The $ n $th set $ \overline{P}_n $ of a limit $ \overline{P} $ of presheaves $ P_i $ is the limit of the $ n $th sets $ P_{i, n} $ of the presheaves in the limit diagram.
-  \end{remark}
-
-  \section{\texorpdfstring{$ \lambda $-}{lambda-}theories}
-
-  \begin{definition}[$ \lambda $-theory]
-    A $ \lambda $-theory is an algebraic theory $ L $, together with sequences of functions $ \lambda_n: L_{n + 1} \to L_n $ and $ \rho_n: L_n \to L_{n + 1} $, such that
-    \begin{align*}
-      \lambda(f) \bullet g &= \lambda(f \bullet (g_1, \dots, g_m, x_{n + 1}))\\
-      \rho(f \bullet g) &= \rho(f) \bullet (g_1, \dots, g_m, x_{n + 1})\\
-    \end{align*}
-    for all $ f: L_m $ and $ g: L_n^m $. (\TODO: Fix)
-  \end{definition}
-
-  \begin{definition}[$ \beta $- and $ \eta $-equality]
-    We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $.
-We say that is satisfies $ \eta $-equality if $ \lambda_n \circ \rho_n = \id{L_{n + 1}} $ for all $ n $.
-  \end{definition}
-
-  \begin{definition}[$ \lambda $-theory morphism]
-    A morphism $ F $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ F $ such that
-    \begin{align*}
-      F_n(\lambda_n(f)) &= \lambda_n(F_{n + 1}(f))\\
-      \rho_n(F_n(g)) &= F_{n + 1}(\rho_n(g))
-    \end{align*}
-    for all $ f: L_{n + 1} $ and $ g: L_n $.
-  \end{definition}
-
-  \begin{remark}
-    The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories.
-  \end{remark}
-
-  A $ \lambda $-theory algebra or presheaf is a presheaf for the underlying algebraic theory.
-
-  \chapter{Lemmas}
-
-  \section{The endomorphism theory}
-
-  \begin{definition}[Endomorphism theory]
-    Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
-    The endomorphism theory $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
-  \end{definition}
-
-  \begin{lemma}
-    $ E(X) $ is indeed an algebraic theory.
-  \end{lemma}
-  \begin{proof}
-    For $ 1 \leq j \leq l $, $ f: E(X)_l $, $ g: {E(X)_m}^l $ and $ h: {E(X)_n}^m $, we have
-    \[ x_j \bullet g = x_j \circ \langle g_i \rangle_i = g_j, \]
-    \[ f \bullet (x_{l,i})_i = f \circ \langle x_{l, i} \rangle_i = f \circ \id{X^l} = f \]
-    and
-    \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i.
-\]
-  \end{proof}
-
-  \begin{definition}[Endomorphism $ \lambda $-theory]
-    Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $.
-Let, for $ Y: C $, $ \varphi_Y $ be the isomorphism $ C(X \times Y, X) \xrightarrow{\sim} C(Y, X^X) $.
-    We can give $ E(X) $ a $ \lambda $-theory structure by setting, for $ f: E(X)_{n + 1} $ and $ g: E(X)_n $,
-    \[ \lambda(f) = abs \circ \varphi_{X^n}(f) \qquad \rho(g) = \varphi_{X^n}^{-1}(app \circ g). \]
-  \end{definition}
-
-  \begin{lemma}
-    $ E(X) $ is indeed a $ \lambda $-theory.
-  \end{lemma}
-  \begin{proof}
-    Note that $ \varphi: C(- \times X, X) \xrightarrow{\sim} C(-, X^X) $ is a natural isomorphism, so for $ g: {E(X)_n}^m $, the following diagram commutes
-    \begin{center}
-      \begin{tikzcd}[column sep = 1in]
-        C(X^m \times X, X) \arrow[r, "- \circ (\langle g_i \rangle_i \times \id X)"]\arrow[d, "\varphi_{X^m}", bend left] & C(X^n \times X, X^X) \arrow[d, "\varphi_{X^n}", bend left]\\
-        C(X^m, X^X) \arrow[r, "- \circ \langle g_i \rangle_i"] \arrow[u, "\varphi_{X^m}^{-1}", bend left] & C(X^n, X^X) \arrow[u, "\varphi_{X^n}^{-1}", bend left]
-      \end{tikzcd}
-    \end{center}
-    and note that $ \langle g_i \rangle_i \times \id X = \langle g_1, \dots, g_m, x_{n + 1} \rangle $. Then we have, for all $ f: E(X)_m $
-    \begin{align*}
-      \lambda_m(f) \bullet g &= abs \circ \varphi_{X^m}(f) \circ \langle g_i \rangle_i\\
-      &= abs \circ \varphi_{X^n}(f \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle)\\
-      &= \lambda_n(f \bullet (g_1, \dots, g_m, x_{n + 1}))
-    \end{align*}
-    and
-    \begin{align*}
-      \rho_n(f \bullet g) &= \varphi_{X^n}^{-1}(app \circ f \circ \langle g_i \rangle_i)\\
-      &= \varphi_{X^m}^{-1}(app \circ f) \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle\\
-      &= \rho_m(f) \bullet (g_1, \dots, g_m, x_{n + 1}).
-    \end{align*}
-  \end{proof}
-
-  \section{The theory presheaf}
-
-  \begin{definition}[The theory presheaf]
-    Let $ T $ be an algebraic theory. We can turn $ T $ into an $ T $-presheaf $ \tilde T $ by setting $ \tilde T_n = T_n $ and using the substitution from $ T $:
-    \[ \bullet: \tilde T_m \times T_n^m \to \tilde T_n. \]
-  \end{definition}
-
-  \begin{lemma}
-    $ \tilde T $ is indeed a presheaf.
-  \end{lemma}
-  \begin{proof}
-    For all $ t: \tilde T_l $, $ f: T_m^l $ and $ g: T_n^m $,
-    \[ t \bullet (x_{l, i})_i = t \]
-    and
-    \[ (t \bullet f) \bullet g = t \bullet (f_i \bullet g)_i \]
-    because $ T $ is an algebraic theory.
-  \end{proof}
-
-  \begin{lemma}
-    Given an algebraic theory $ T $ and a $ T $-presheaf $ Q $, we have for all $ n $ a bijection of sets
-    \[ \varphi: PT(\tilde T^n, Q) \cong Q_n. \]
-  \end{lemma}
-  \begin{proof}
-    Take $ \varphi(f) = f_n(x_1, \dots, x_n) $.
-
-    Conversely, take $ \varphi^{-1}(q) $ to be the presheaf morphism that sends $ t: T^n_m $ to $ q \bullet t : Q_m $. This is indeed a presheaf morphism, since for all $ t: T^n_l $ and $ f: T^l_m $,
-    \[ \varphi^{-1}(q)(t \bullet f) = q \bullet t \bullet f = \varphi^{-1}(q)(t) \bullet f. \]
-
-    Now, for a presheaf morphism $ f: T^n \to Q $ and $ t: T^n_m $, we have
-    \[ \varphi^{-1}(\varphi(f))(t) = f_n(x_1, \dots, x_n) \bullet t = f_n((x_1, \dots, x_n) \bullet t) = f_n(t_1, \dots, t_n) = f_n(t). \]
-
-    Conversely, given $ q: Q_n $, we have
-    \[ \varphi(\varphi^{-1}(q)) = q \bullet (x_1, \dots, x_n) = q. \]
-    which concludes the proof.
-  \end{proof}
-
-  \section{The `+l' presheaf}
-
-  Let $ \iota_{m, n} : T_m \to T_{m + n} $ denote the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
-  \[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \]
-  and
-  \[ \iota_{m, n}(f \bullet g) = f \bullet g \bullet (x_i)_i = f \bullet (g_i \bullet (x_j)_j)_i = f \bullet (\iota_{m, n}(g_i))_i. \]
-
-  For tuples $ x : X^m $ and $ y: X^n $, let $ x + y $ denote the tuple $ (x_1, \dots, x_m, y_1, \dots, y_n) : X^{m + n} $.
-
-  \begin{definition}[The `+l' presheaf]
-    Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, l) $, given by $ A(Q, l)_n = Q_{n + l} $. Then, for $ q: A(Q, l)_m $ and $ f: T_n^m $, the substitution is given by
-    \[ q \bullet_{A(Q, l)} f = q \bullet_Q ((\iota_{n, l} (f_i))_i + (x_{n + i})_i) \]
-  \end{definition}
-  \begin{lemma}
-    The +l presheaf is a presheaf
-  \end{lemma}
-  \begin{proof}
-    We have, for $ q: A(Q, l)_n $,
-    \begin{align*}
-      q \bullet_{A(Q, l)} (x_i)_i &= q \bullet_Q ((\iota_{n, l}(x_i))_i + (x_{n + i})_i)\\
-      &= q \bullet_Q ((x_i)_i + (x_{n + i})_i)\\
-      &= q \bullet_Q (x_i)_i\\
-      &= q.
-    \end{align*}
-    We have, for $ q : A(Q, k)_l $, $ f: T_m^l $ and $ g: T_n^m $,
-    \begin{align*}
-      q \bullet_{A(Q, k)} f \bullet_{A(Q, k)} g &= q \bullet_Q ((\iota_{m, l}(f_i))_i + (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(g_i))_i + (x_{n + i})_i)\\
-      &= q \bullet_Q (((\iota_{m, l}(f_i) \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i + (x_{m + i} \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i))\\
-      &= q \bullet_Q ((f_i \bullet_T (\iota_{n, l}(g_j))_j)_i + (x_{n + i})_i)\\
-      &= q \bullet_Q ((\iota_{n, l}(f_i \bullet_T g))_i + (x_{n + i})_i)\\
-      &= q \bullet_{A(Q, k)} (f_i \bullet_T g).
-    \end{align*}
-  \end{proof}
-
-  \section{Exponentiability of the theory presheaf}
-
-  \begin{lemma}
-    For all $ l $, the presheaf $ \tilde T^l $ is exponentiable.
-  \end{lemma}
-  \begin{proof}
-    We will show that $ A(-, l) $ constitutes a right adjoint to the functor $ - \times \tilde T^l $.
-We will do this using universal arrows (\cite{MacLane}, Chapter IV.1, Theorem 2 (iv)).
-To that end, we will need for all $ Q: PT $ a universal arrow $ \varphi: A(Q, l) \times \tilde T^l \to Q $.
-
-    For $ q: A(Q, l)_n = Q_{n + l} $ and $ t: \tilde T^l_n $, we take $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $.
-
-    This is a presheaf morphism, since for all $ q: A(Q, l)^l_m $, $ t: \tilde T^l_m $ and $ f: T_n^m $,
-    \begin{align*}
-      \varphi((q, t) \bullet_{A(Q, l) \times \tilde \tilde T^l} f) &= \varphi(q \bullet_{A(Q, l)} f, t \bullet_{\tilde T^l} f)\\
-      &= q \bullet_{A(Q, l)} f \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
-      &= q \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i) \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
-      &= q \bullet_Q ((\iota_{n, l}(f_i) \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i + (x_{n + i} \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i)\\
-      &= q \bullet_Q ((f_i \bullet_T (x_j)_j)_i + ((t \bullet_{\tilde T^l} f)_i)_i)\\
-      &= q \bullet_Q ((f_i)_i + (t_i \bullet_{\tilde T} f)_i)\\
-      &= q \bullet_Q ((x_i \bullet_T f)_i + (t_i \bullet_T f)_i)\\
-      &= q \bullet_Q ((x_i)_i + t) \bullet_Q f\\
-      &= \varphi(q, t) \bullet_Q f.
-    \end{align*}
-
-    Now, given any presheaf $ Q^\prime : P T $ we need to show that any morphism $ \psi: Q^\prime \times \tilde T^l \to Q $ factors uniquely as $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) $ for some $ \tilde \psi: Q^\prime \to A(Q, l) $.
-
-    So, given such a $ \psi $, and given $ q: Q^\prime_n $, we take $ \tilde \psi(q) = \psi(\iota_{n, l}(q), (x_{n + i})_i) $
-
-    This is a presheaf morphism, since for all $ q: Q^\prime_m $ and $ f : T_n^m $,
-    \begin{align*}
-      \tilde \psi(q \bullet f) &= \psi(\iota_{n, l}(q \bullet f), (x_{n + i})_i)\\
-      &= \psi(q \bullet (\iota_{n, l}(f_i))_i, (x_{n + i})_i)\\
-      &= \psi((\iota_{m, l}(q), (x_{m + i})_i) \bullet_{Q^\prime \times \tilde T^l} ((\iota_{n, l}(f_i))_i + (x_{n + i})_i))\\
-      &= \psi(\iota_{m, l}(q), (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i)\\
-      &= \tilde \psi(q) \bullet_{A(Q, l)} f.
-    \end{align*}
-    Note that indeed $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) = \psi $:
-    \begin{align*}
-      \varphi(\tilde \psi(q), t) &= \varphi(\psi(\iota_{n, l}(q), (x_{n + i})_i), t)\\
-      &= \psi(\iota_{n, l}(q), (x_{n + i})_i) \bullet ((x_i)_i + t)\\
-      &= \psi(\iota_{n, l}(q) \bullet ((x_i)_i + t), (x_{n + i})_i \bullet ((x_i)_i + t))\\
-      &= \psi(q \bullet (x_i)_i, (t_i)_i)\\
-      &= \psi(q, t).\\
-    \end{align*}
-    Now, suppose that we have another $ \tilde \psi^\prime : Q^\prime \to A(Q, l) $ such that $ \varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}) = \psi $. Then we have
-    \begin{align*}
-      \tilde \psi(q) &= \psi(\iota_{n, l}(q), (x_{n + i})_i)\\
-      &= (\varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}))(\iota_{n, l}(q), (x_{n + i})_i)\\
-      &= \varphi(\tilde \psi^\prime(\iota_{n, l}(q)), (x_{n + i})_i)\\
-      &= \tilde \psi^\prime(\iota_{n, l}(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
-      &= \iota_{n, l}(\tilde \psi^\prime(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
-      &= \tilde \psi^\prime(q) \bullet (x_i)_i\\
-      &= \tilde \psi^\prime(q),
-    \end{align*}
-    so $ \tilde \psi $ is unique, which completes the proof.
-  \end{proof}
-
-  Now, this adjunction $ - \times \tilde T^l \dashv A(-, l) $ induces a natural isomorphism
-  \[ \varphi: PT(- \times \tilde T^l, \tilde T) \xrightarrow{\sim} PT(-, A(\tilde T, l)) \]
-  \begin{lemma}
-    For all $ f: PT(\tilde T^n \times \tilde T^l, \tilde T) $,
-    \[ \varphi_{\tilde T^n}(f)(q) = f(\iota_{m, l}(q), (x_{m + i})_i) \]
-  \end{lemma}
-  \begin{proof}
-    \TODO
-  \end{proof}
-
-  \begin{lemma}
-    For all $ f: PT(\tilde T^n, A(\tilde T, l)) $,
-    \[ \varphi_{\tilde T^n}^{-1}(f)(q, t) = f(q) \bullet ((x_i)_i + t). \]
-  \end{lemma}
-  \begin{proof}
-    \TODO
-  \end{proof}
-
-  \chapter{Theorems}
-
-  \section{Scott's Representation Theorem}
-  \begin{theorem}
-    Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E(\tilde L) $ of $ \tilde L $ in the presheaf category of $ L $.
-  \end{theorem}
-  \begin{proof}
-    First of all, remember that $ \tilde L $ is indeed exponentiable and that $ \tilde L^{\tilde L} = A(\tilde L, 1) $.
-    Now, since $ L $ is a $ \lambda $-theory, we have functions back and forth $ \lambda: A(\tilde L, 1) \to \tilde L $ and $ \rho: \tilde L \to A(\tilde L, 1) $.
-These are presheaf morphisms because for all $ f: A(\tilde L, 1)_m $ and $ g: \tilde L_m $ and $ t: T_n^m $,
-    \[ \lambda(f \bullet_{A(\tilde L, 1)} t) = \lambda(f \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1}))) = \lambda(f) \bullet_{\tilde L} t \]
-    and
-    \[ \rho(g \bullet_{\tilde L} t) = \rho(g) \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1})) = \rho(g) \bullet_{A(\tilde L, 1)} t. \]
-    Therefore, $ E(\tilde L) $ is indeed a $ \lambda $-theory.
-
-    For any presheaf $ Q $ and for any $ n $, we have a bijection $ PL(L^n, Q) \cong Q_n $.
-    Then we have $ \varphi: E(\tilde L)_n \cong L_n $.
-    This bijection is an isomorphism of $ \lambda $-theories, since it preserves the $ x_i $, $ \bullet $, $ \rho $ and $ \lambda $: for all $ 1 \leq j \leq n $, $ f: E(\tilde L)_m $, $ g: E(\tilde L)_{m + 1} $ and $ h: E(\tilde L)_n^m $.
-    \begin{align*}
-      \varphi(x_j) &= x_j(x_1, \dots, x_n)\\
-      &= x_j;\\
-      \varphi(f \bullet h) &= f \circ \langle h_i \rangle_i((x_i)_i)\\
-      &= f((h_i((x_j)_j))_i)\\
-      &= f((x_i)_i \bullet (h_i((x_j)_j))_i)\\
-      &= f((x_i)_i) \bullet (h_i((x_j)_j))_i\\
-      &= \varphi(f) \bullet (\varphi(h_i))_i;\\
-      \varphi(\rho(f)) &= \rho(f)((x_i)_i)\\
-      &= \rho(f((x_i)_i)) \bullet (x_i)_i\\
-      &= \rho(f((x_i)_i))\\
-      &= \rho(\varphi(f));\\
-      \varphi(\lambda(g)) &= \lambda(g)((x_i)_i)\\
-      &= \lambda(\varphi_{X^n}(g)((x_i)_i))\\
-      &= \lambda(g(\iota_{m, l}((x_i)_i) + (x_{m + 1})))\\
-      &= \lambda(g((x_i)_i))\\
-      &= \lambda(\varphi(g)).
-    \end{align*}
-  \end{proof}
-
-  \section{Locally cartesian closedness of the category of retracts}
-  \begin{theorem}
-    The category of retracts \TODO is locally cartesian closed \TODO.
-  \end{theorem}
-
-  \section{The Fundamental Theorem of the \texorpdfstring{$ \lambda $-}{lambda }calculus}
-  \begin{theorem}
-    There exists an adjoint equivalence between the category of $ \lambda $-theories, and the category of algebras of $ \Lambda $ \TODO.
-  \end{theorem}
-  \begin{proof}
-    In one direction, the proof sends a $ \lambda $-theory $ L $ to the $ L $-algebra $ L(0) $ \TODO.
-Since $ \Lambda $ is the initial $ \lambda $-theory \TODO, we can give $ L(0) $ a $ \Lambda $-algebra structure \TODO.
-This constitutes a functor \TODO.
-
-    In the other direction, it sends a $ \Lambda $-algebra $ A $ to the theory of extensions $ \Lambda_A $ \TODO.
-It is a $ \lambda $-theory because it is isomorphic \TODO to the endomorphism $ \lambda $-theory $ E(A(1)) $ of the object $ A(1) $ in $ PA $ \TODO.
-
-    These constitute an adjoint equivalence. \TODO
-  \end{proof}
+  \include{chapters/algebraic-structures}
+  \include{chapters/category-theory}
+  \include{chapters/univalent-foundations}
+  \include{chapters/previous-work}
+  \include{chapters/paper}
+  \include{chapters/formalization}
 
@@
 
+  \appendix
+  \include{chapters/alternative-definitions}
+
 \end{document}

### 2024-01-18 report/chapters/algebraic-structures.tex
Start working on the "examples" section of the report

@@
 
-We will write $ PT $ for the category of $ T $-presheaves and their morphisms.
+We will write $ \Pshf T $ for the category of $ T $-presheaves and their morphisms.
 
@@
 
+There is a lot of different examples of algebraic theories and their algebras. Some of these even turn out to be $ \lambda $-theories. In this section, we will discuss a couple of these.
+
 \subsection{The free algebraic theory on a set}
+\begin{example}
+  Let $ S $ be a set. We can construct an algebraic theory $ F(S) $ by taking $ F(S)_n = S \sqcup \{ 1, \dots, n \} $ with projections $ x_i = i $ and substitution
+  \begin{align*}
+    i \bullet g &= g_i & s \bullet g &= s
+  \end{align*}
+  for $ i : \{ 1, \dots, n \} $ and $ s : S $.
+
+  If we have a function $ f: S \to S^\prime $, we get a morphism $ F(f): F(S) \to F(S^\prime) $ given by
+  \begin{align*}
+    F(f)_n(i) &= i & F(f)_n(s) &= f(s)
+  \end{align*}
+  for $ i : \{ 1, \dots, n \} $ and $ s : S $.
+
+  Also, $ F $ obviously respects the identity and substitution morphisms, so it is a functor.
+\end{example}
+
+Note that we have a forgetful functor $ (\cdot)_0 $ that sends a morphism of algebraic theories $ g: T \to T^\prime $ to the function $ f_0: T_0 \to T^\prime_0 $.
+
+\begin{lemma}
+  The algebraic theory $ F(S) $ defined above, is the free algebraic theory on the set $ S $.
+\end{lemma}
+\begin{proof}
+  Let $ T $ be an algebraic theory. We have an equivalence
+  \[ \AlgTh(F(S), T) \cong \SET(S, T_0), \]
+  sending $ f: \AlgTh(F(S), T) $ to $ f_0: S = S \sqcup \emptyset \to T_0 $ (this is trivially natural in $ S $ and $ T $) and $ f: \SET(S, T_0) $ to the functions $ g_n: F(S)_n \to T_n $ given by
+  \begin{align*}
+    g_n(i) &= x_i & g_n(s) &= f(s) \bullet ().
+  \end{align*}
+\end{proof}
+
+The proofs that $ F(S) $ is an algebraic theory and that $ F(f) $ and $ g $ are algebraic theory morphisms is an easy exercise in case distinction.
+
+\begin{corollary}
+  $ F(\emptyset) $ is the initial algebraic theory.
+\end{corollary}
+\begin{proof}
+  For $ S = \emptyset $, the equivalence of hom-sets becomes
+  \[ \AlgTh(F(\emptyset), T) \cong \SET(\emptyset, T_0) \]
+  and the latter has exactly one element.
+\end{proof}
+
 \subsection{The free object algebraic theory}
-\subsection{The initial algebraic theory}
+
+\begin{example}
+  Take a category $ C $, with a forgetful functor $ G: C \to \SET $ and a free functor $ F: \SET \to C $.
+Let $ \eta: \id \SET \Rightarrow F \bullet G $ be the unit of the adjunction and let $ \varphi: C(F(c), d) \cong \SET(c, G(d)) $ be the natural equivalence of homsets.
+
+  We define an algebraic theory $ T $ with $ T_n = G(F(\{ 1, \dots, n \})) $, projections $ x_{n, i} = \eta_{\{1, \dots, n\}}(i) $.
+For the substitution, note that we take $ t_1, \dots, t_m: T_n $, so we have $ t: \{ 1, \dots, m \} \to G(F(\{ 1, \dots, n \})) $.
+We then take
+  \[ s \bullet t = G(\varphi^{-1}(t))(s). \]
+
+  Now, given an object $ c: C $, we can create a $ T $-algebra $ \alpha(c) $, with set $ G(c) $ and action
+  \[ s \bullet t = G(\varphi^{-1}(t))(s). \]
+  Also, given a morphism $ f: C(c, d) $. This gives a morphism $ G(f): \alpha(c) \to \alpha(d) $. Therefore, $ \alpha: C \to \Alg T $ is a functor.
+\end{example}
+
+The proofs that $ T $ is an algebraic theory, that $ G(c) $ is an algebra and that $ G(f) $ is an algebra morphism mainly rely on the fact that $ \varphi $ is natural.
+
+So we have a functor from $ C $ to the category of $ T $-algebras.
+One can wonder whether there also is a functor the other way, or whether $ \alpha $ is even an equivalence.
+This is hard to characterize precisely, but in algebra, there is a broad class of examples where the functor is an equivalence, so where $ C $ is equivalent to $ \Alg T $.
+That is probably why $ T $ is called an \textit{algebraic theory}.
+
+The idea is that if an object of $ C $ is a set, together with some operations between its elements, one can carefully choose some elements of $ T_0 $, $ T_1 $, $ T_2 $ etc., which act on an algebra like the specified operations.
+
+\begin{example}
+  For $ C $ the category of monoids, $ \alpha: C \to \Alg T $ is an adjoint equivalence.
+
+  Note that $ T_n $ is the free monoid on $ n $ elements.
+Its elements can be viewed as strings $ (x_1 x_5 x_3 x_{18} \dots x_7) $ with the characters $ x_1, \dots, x_n $, with the $ x_i $ the generators of the monoid, acting as the projections of the algebraic theory.
+
+  Let $ A $ be a $ T $-algebra. We can give $ A $ a monoid structure by taking, for $ a, b: A $,
+  \[ a b = (x_1 x_2) \bullet (a, b) \]
+  and unit element
+  \[ 1 = () \bullet (). \]
+  Then the laws like associativity follow from those laws on the monoid and from the fact that the action on the algebra commutes with the substitution:
+  \[ a (b c) = (x_1 (x_2 x_3)) \bullet (a, b, c) = ((x_1 x_2) x_3) \bullet (a, b, c) = (a b) c. \]
+  Note that if we take a monoid, turn it into a $ T $-algebra and then into a monoid again, we still have the same underlying set, and it turns out that the monoid operation and unit element are equal to the original monoid operation and unit element.
+Therefore, $ \alpha $ is essentially surjective.
+It is also fully faithful, since any $ T $-algebra morphism respects the action of $ T $, which makes it into a monoid morphism.
+Therefore, $ \alpha $ is an adjoint equivalence.
+\end{example}
+
+\begin{remark}
+  In the same way, one can characterize groups, rings and $ R $-algebras (for $ R $ a ring) as algebras of some algebraic theory.
+On the other hand, one can not use this method to describe fields as algebras for some theory $ T $, because one would need to describe the inverse $ z \mapsto z^{-1} $ operation as $ t \bullet (z) $ for some $ t: T_1 $, with $ z z^{-1} = 1 $, but since the elements of the algebraic theory act on all (combinations of) elements of the algebra, one would be able to take the inverse $ 0^{-1} = t \bullet (0) $ with $ 0 0^{-1} = 1 $, which would make no sense.
+\end{remark}
 
 \subsection{The terminal theory}
-\subsection{The Endomorphism Theory}
+\begin{example}
+  We can create a (somewhat trivial) algebraic theory $ T $ by taking $ T_n = \{ \star \} $, with projections $ x_i = \star $ and substitution $ \star \bullet \star = \star $.
+Taking $ \lambda(\star) = \star $ and $ \rho(\star) = \star $, we give it a $ \lambda $-theory structure (with $ \beta $ and $ \eta $-equality).
+Checking that this is indeed an algebraic theory and even a $ \lambda $-theory is trivial.
+
+  Now, given any other algebraic theory $ T^\prime $, there exists a unique function $ T^\prime_n \to T_n $ for every $ n $, sending everything to $ \star $.
+These functions actually constitute an algebraic theory morphism $ T^\prime \to T $.
+If $ T^\prime $ is a $ \lambda $-theory, the algebraic theory morphism is actually a $ \lambda $-theory morphism.
+Again, checking this is trivial.
+
+  Therefore, $ T $ is the terminal algebraic theory and $ \lambda $-theory.
+\end{example}
+
+\subsection{The endomorphism theory}
+
+\begin{definition}[Endomorphism theory]
+  Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
+  The endomorphism theory $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
+\end{definition}
+
+\begin{lemma}
+  $ E(X) $ is indeed an algebraic theory.
+\end{lemma}
+\begin{proof}
+  For $ 1 \leq j \leq l $, $ f: E(X)_l $, $ g: {E(X)_m}^l $ and $ h: {E(X)_n}^m $, we have
+  \[ x_j \bullet g = x_j \circ \langle g_i \rangle_i = g_j, \]
+  \[ f \bullet (x_{l,i})_i = f \circ \langle x_{l, i} \rangle_i = f \circ \id{X^l} = f \]
+  and
+  \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i. \]
+\end{proof}
+
+\begin{definition}[Endomorphism $ \lambda $-theory]
+  Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $.
+Let, for $ Y: C $, $ \varphi_Y $ be the isomorphism $ C(X \times Y, X) \xrightarrow{\sim} C(Y, X^X) $.
+  We can give $ E(X) $ a $ \lambda $-theory structure by setting, for $ f: E(X)_{n + 1} $ and $ g: E(X)_n $,
+  \[ \lambda(f) = abs \circ \varphi_{X^n}(f) \qquad \rho(g) = \varphi_{X^n}^{-1}(app \circ g). \]
+\end{definition}
+
+\begin{lemma}
+  $ E(X) $ is indeed a $ \lambda $-theory.
+\end{lemma}
+\begin{proof}
+  Note that $ \varphi: C(- \times X, X) \xrightarrow{\sim} C(-, X^X) $ is a natural isomorphism, so for $ g: {E(X)_n}^m $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}[column sep = 1in]
+      C(X^m \times X, X) \arrow[r, "- \circ (\langle g_i \rangle_i \times \id X)"]\arrow[d, "\varphi_{X^m}", bend left] & C(X^n \times X, X^X) \arrow[d, "\varphi_{X^n}", bend left]\\
+      C(X^m, X^X) \arrow[r, "- \circ \langle g_i \rangle_i"] \arrow[u, "\varphi_{X^m}^{-1}", bend left] & C(X^n, X^X) \arrow[u, "\varphi_{X^n}^{-1}", bend left]
+    \end{tikzcd}
+  \end{center}
+  and note that $ \langle g_i \rangle_i \times \id X = \langle g_1, \dots, g_m, x_{n + 1} \rangle $. Then we have, for all $ f: E(X)_m $
+  \begin{align*}
+    \lambda_m(f) \bullet g &= abs \circ \varphi_{X^m}(f) \circ \langle g_i \rangle_i\\
+    &= abs \circ \varphi_{X^n}(f \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle)\\
+    &= \lambda_n(f \bullet (g_1, \dots, g_m, x_{n + 1}))
+  \end{align*}
+  and
+  \begin{align*}
+    \rho_n(f \bullet g) &= \varphi_{X^n}^{-1}(app \circ f \circ \langle g_i \rangle_i)\\
+    &= \varphi_{X^m}^{-1}(app \circ f) \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle\\
+    &= \rho_m(f) \bullet (g_1, \dots, g_m, x_{n + 1}).
+  \end{align*}
+\end{proof}
+
 \subsection{The free \texorpdfstring{$ \lambda $}{lambda}-theory}
-\subsection{The \texorpdfstring{$ \lambda $}{lambda}-calculus}
+
+Let $ S $ be a set. Consider the sequence of inductive types $ (\Lambda(S)_n)_n $ with the following constructors:
+\begin{align*}
+  \mathtt{Var}_n &: \{ 1, \dots, n \} \to \Lambda(S)_n;\\
+  \mathtt{App}_n &: \Lambda(S)_n \to \Lambda(S)_n \to \Lambda(S)_n;\\
+  \mathtt{Abs}_n &: \Lambda(S)_{n + 1} \to \Lambda(S)_n;\\
+  \mathtt{Con}_n &: S \to \Lambda(S)_n.\\
+\end{align*}
+
+Define a substitution operator $ \bullet: \Lambda(S)_m \times \Lambda(S)_n^m \to \Lambda(S)_n $ by induction on the first argument:
+\begin{align*}
+  \mathtt{Var}_m(i) \bullet g &= g_i;\\
+  \mathtt{App}_m(a, b) \bullet g &= \mathtt{App}_n(a \bullet g, b \bullet g);\\
+  \mathtt{Abs}_m(a) \bullet g &= \mathtt{Abs}_n(a \bullet ((g_i \bullet (x_{n + 1, j})_j)_i + (x_{n + 1})));\\
+  \mathtt{Con}_m(s) \bullet g &= \mathtt{Con}_n(s).
+\end{align*}
+
+And then quotient $ \Lambda(S) $ by the relation generated by
+\[ \mathtt{App}_m(\mathtt{Abs}_m(f), g) \sim f \bullet ((x_{n, i})_i + (g)) \]
+for all $ f: \Lambda(S)_{n + 1} $ and $ g: \Lambda(S)_n $.
+
+% \subsection{The \texorpdfstring{$ \lambda $}{lambda}-calculus}
+
+\subsection{The theory algebra}
+\begin{example}
+  Let $ T $ be an algebraic theory and $ n $ a natural number.
+We can endow the $ T_n $ with a $ T $-algebra structure, by taking the substitution operator of $ T $ as the $ T $-action.
+Since this commutes with the substitution operator and the projections, $ T_n $ is a $ T $-algebra.
+\end{example}
+
 \subsection{The theory presheaf}
-\subsection{The theory algebra}
+\begin{example}
+  Let $ T $ be an algebraic theory.
+We can endow $ T $ with a $ T $-presheaf structure, by taking the substitution operator of $ T $ as the action on $ T $.
+Since this commutes with the substitution operator and the projections, $ T $ is a $ T $-presheaf.
+\end{example}
+
+\begin{lemma}
+  Given an algebraic theory $ T $ and a $ T $-presheaf $ Q $, we have for all $ n $ a bijection of sets
+  \[ \varphi: \Pshf T(T^n, Q) \cong Q_n. \]
+\end{lemma}
+\begin{proof}
+  For $ f: \Pshf T(T^n, Q) $, take $ \varphi(f) = f_n(x_1, \dots, x_n) $.
+
+  Conversely, for all $ q: Q_n $ and all $ t_1, \dots, t_n: T_m^n $ take
+  \[ \varphi^{-1}(q)_m(t_1, \dots, t_n) = q \bullet t. \]
+\end{proof}
+
 \subsection{The "+l" presheaf}
@@
 Let $ \iota_{m, n} : T_m \to T_{m + n} $ denote the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
-\[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \]
-and
-\[ \iota_{m, n}(f \bullet g) = f \bullet g \bullet (x_i)_i = f \bullet (g_i \bullet (x_j)_j)_i = f \bullet (\iota_{m, n}(g_i))_i. \]
+\[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \quad \text{and} \quad \iota_{m, n}(f \bullet g) = f \bullet (\iota_{m, n}(g_i))_i. \]
 
@@
 
-\begin{definition}[The `+l' presheaf]
-  Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, l) $, given by $ A(Q, l)_n = Q_{n + l} $. Then, for $ q: A(Q, l)_m $ and $ f: T_n^m $, the substitution is given by
-  \[ q \bullet_{A(Q, l)} f = q \bullet_Q ((\iota_{n, l} (f_i))_i + (x_{n + i})_i) \]
-\end{definition}
+\begin{example}[The `+l' presheaf]
+  Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, l) $ with $ A(Q, l)_n = Q_{n + l} $ and, for $ q: A(Q, l)_m $ and $ f: T_n^m $, action
+  \[ q \bullet_{A(Q, l)} f = q \bullet_Q ((\iota_{n, l} (f_i))_i + (x_{n + i})_i). \]
+\end{example}
+
 \begin{lemma}
-  The +l presheaf is a presheaf
+  For all $ l $ and $ T $-presheaves $ Q $, $ A(Q, l) $ is the exponential object $ Q^{T^l} $.
 \end{lemma}
 \begin{proof}
-  We have, for $ q: A(Q, l)_n $,
-  \begin{align*}
-    q \bullet_{A(Q, l)} (x_i)_i &= q \bullet_Q ((\iota_{n, l}(x_i))_i + (x_{n + i})_i)\\
-    &= q \bullet_Q ((x_i)_i + (x_{n + i})_i)\\
-    &= q \bullet_Q (x_i)_i\\
-    &= q.
-  \end{align*}
-  We have, for $ q : A(Q, k)_l $, $ f: T_m^l $ and $ g: T_n^m $,
-  \begin{align*}
-    q \bullet_{A(Q, k)} f \bullet_{A(Q, k)} g &= q \bullet_Q ((\iota_{m, l}(f_i))_i + (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(g_i))_i + (x_{n + i})_i)\\
-    &= q \bullet_Q (((\iota_{m, l}(f_i) \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i + (x_{m + i} \bullet_T ((\iota_{n, l}(g_j))_j + (x_{n + j})_j))_i))\\
-    &= q \bullet_Q ((f_i \bullet_T (\iota_{n, l}(g_j))_j)_i + (x_{n + i})_i)\\
-    &= q \bullet_Q ((\iota_{n, l}(f_i \bullet_T g))_i + (x_{n + i})_i)\\
-    &= q \bullet_{A(Q, k)} (f_i \bullet_T g).
-  \end{align*}
+  We will show that $ A(-, l) $ constitutes a right adjoint to the functor $ - \times T^l $. We will do this using universal arrows.
+
+  For $ Q $ a $ T $-presheaf, take the arrow $ \varphi: A(Q, l) \times T^l \to Q $ given by $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $ for $ q: A(Q, l)_n = Q_{n + l} $ and $ t: T^l_n $.
+
+  Now, given a $ T $-presheaf $ Q^\prime $ and a morphism $ \psi: Q^\prime \times T^l \to Q $.
+Define $ \tilde \psi: Q^\prime_n \to A(Q, l)_n $ by $ \tilde \psi(q) = \psi(\iota_{n, l}(q), (x_{n + i})_i) $.
+
+  Then $ \psi $ factors as $ \varphi \circ (\tilde \psi \times \id{T^l}) $.
+Also, some equational reasoning shows that $ \tilde \psi $ is unique, which proves that $ \varphi $ indeed is a universal arrow.
 \end{proof}
+
+Now, this adjunction $ - \times T^l \dashv A(-, l) $ induces a natural isomorphism
+\[ \varphi: \Pshf T(- \times T^l, T) \xrightarrow{\sim} \Pshf T(-, A(T, l)) \]
+\begin{lemma}
+  For all $ f: \Pshf T(T^n \times T^l, T) $,
+  \[ \varphi_{T^n}(f)(q) = f(\iota_{m, l}(q), (x_{m + i})_i) \]
+\end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}
+
+\begin{lemma}
+  For all $ f: \Pshf T(T^n, A(T, l)) $,
+  \[ \varphi_{T^n}^{-1}(f)(q, t) = f(q) \bullet ((x_i)_i + t). \]
+\end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}

### 2024-01-18 report/chapters/paper.tex
Start working on the "examples" section of the report

@@
 \chapter{The paper}
-
-\section{The endomorphism theory}
-
-\begin{definition}[Endomorphism theory]
-  Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
-  The endomorphism theory $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
-\end{definition}
-
-\begin{lemma}
-  $ E(X) $ is indeed an algebraic theory.
-\end{lemma}
-\begin{proof}
-  For $ 1 \leq j \leq l $, $ f: E(X)_l $, $ g: {E(X)_m}^l $ and $ h: {E(X)_n}^m $, we have
-  \[ x_j \bullet g = x_j \circ \langle g_i \rangle_i = g_j, \]
-  \[ f \bullet (x_{l,i})_i = f \circ \langle x_{l, i} \rangle_i = f \circ \id{X^l} = f \]
-  and
-  \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i. \]
-\end{proof}
-
-\begin{definition}[Endomorphism $ \lambda $-theory]
-  Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $.
-Let, for $ Y: C $, $ \varphi_Y $ be the isomorphism $ C(X \times Y, X) \xrightarrow{\sim} C(Y, X^X) $.
-  We can give $ E(X) $ a $ \lambda $-theory structure by setting, for $ f: E(X)_{n + 1} $ and $ g: E(X)_n $,
-  \[ \lambda(f) = abs \circ \varphi_{X^n}(f) \qquad \rho(g) = \varphi_{X^n}^{-1}(app \circ g). \]
-\end{definition}
-
-\begin{lemma}
-  $ E(X) $ is indeed a $ \lambda $-theory.
-\end{lemma}
-\begin{proof}
-  Note that $ \varphi: C(- \times X, X) \xrightarrow{\sim} C(-, X^X) $ is a natural isomorphism, so for $ g: {E(X)_n}^m $, the following diagram commutes
-  \begin{center}
-    \begin{tikzcd}[column sep = 1in]
-      C(X^m \times X, X) \arrow[r, "- \circ (\langle g_i \rangle_i \times \id X)"]\arrow[d, "\varphi_{X^m}", bend left] & C(X^n \times X, X^X) \arrow[d, "\varphi_{X^n}", bend left]\\
-      C(X^m, X^X) \arrow[r, "- \circ \langle g_i \rangle_i"] \arrow[u, "\varphi_{X^m}^{-1}", bend left] & C(X^n, X^X) \arrow[u, "\varphi_{X^n}^{-1}", bend left]
-    \end{tikzcd}
-  \end{center}
-  and note that $ \langle g_i \rangle_i \times \id X = \langle g_1, \dots, g_m, x_{n + 1} \rangle $. Then we have, for all $ f: E(X)_m $
-  \begin{align*}
-    \lambda_m(f) \bullet g &= abs \circ \varphi_{X^m}(f) \circ \langle g_i \rangle_i\\
-    &= abs \circ \varphi_{X^n}(f \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle)\\
-    &= \lambda_n(f \bullet (g_1, \dots, g_m, x_{n + 1}))
-  \end{align*}
-  and
-  \begin{align*}
-    \rho_n(f \bullet g) &= \varphi_{X^n}^{-1}(app \circ f \circ \langle g_i \rangle_i)\\
-    &= \varphi_{X^m}^{-1}(app \circ f) \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle\\
-    &= \rho_m(f) \bullet (g_1, \dots, g_m, x_{n + 1}).
-  \end{align*}
-\end{proof}
-
-\section{The theory presheaf}
-
-\begin{definition}[The theory presheaf]
-  Let $ T $ be an algebraic theory. We can turn $ T $ into an $ T $-presheaf $ \tilde T $ by setting $ \tilde T_n = T_n $ and using the substitution from $ T $:
-  \[ \bullet: \tilde T_m \times T_n^m \to \tilde T_n. \]
-\end{definition}
-
-\begin{lemma}
-  $ \tilde T $ is indeed a presheaf.
-\end{lemma}
-\begin{proof}
-  For all $ t: \tilde T_l $, $ f: T_m^l $ and $ g: T_n^m $,
-  \[ t \bullet (x_{l, i})_i = t \]
-  and
-  \[ (t \bullet f) \bullet g = t \bullet (f_i \bullet g)_i \]
-  because $ T $ is an algebraic theory.
-\end{proof}
-
-\begin{lemma}
-  Given an algebraic theory $ T $ and a $ T $-presheaf $ Q $, we have for all $ n $ a bijection of sets
-  \[ \varphi: PT(\tilde T^n, Q) \cong Q_n. \]
-\end{lemma}
-\begin{proof}
-  Take $ \varphi(f) = f_n(x_1, \dots, x_n) $.
-
-  Conversely, take $ \varphi^{-1}(q) $ to be the presheaf morphism that sends $ t: T^n_m $ to $ q \bullet t : Q_m $. This is indeed a presheaf morphism, since for all $ t: T^n_l $ and $ f: T^l_m $,
-  \[ \varphi^{-1}(q)(t \bullet f) = q \bullet t \bullet f = \varphi^{-1}(q)(t) \bullet f. \]
-
-  Now, for a presheaf morphism $ f: T^n \to Q $ and $ t: T^n_m $, we have
-  \[ \varphi^{-1}(\varphi(f))(t) = f_n(x_1, \dots, x_n) \bullet t = f_n((x_1, \dots, x_n) \bullet t) = f_n(t_1, \dots, t_n) = f_n(t). \]
-
-  Conversely, given $ q: Q_n $, we have
-  \[ \varphi(\varphi^{-1}(q)) = q \bullet (x_1, \dots, x_n) = q. \]
-  which concludes the proof.
-\end{proof}
-
-\section{The `+l' presheaf}
-
-\begin{lemma}
-  For all $ l $, the presheaf $ \tilde T^l $ is exponentiable.
-\end{lemma}
-\begin{proof}
-  We will show that $ A(-, l) $ constitutes a right adjoint to the functor $ - \times \tilde T^l $.
-We will do this using universal arrows (\cite{MacLane}, Chapter IV.1, Theorem 2 (iv)).
-To that end, we will need for all $ Q: PT $ a universal arrow $ \varphi: A(Q, l) \times \tilde T^l \to Q $.
-
-  For $ q: A(Q, l)_n = Q_{n + l} $ and $ t: \tilde T^l_n $, we take $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $.
-
-  This is a presheaf morphism, since for all $ q: A(Q, l)^l_m $, $ t: \tilde T^l_m $ and $ f: T_n^m $,
-  \begin{align*}
-    \varphi((q, t) \bullet_{A(Q, l) \times \tilde \tilde T^l} f) &= \varphi(q \bullet_{A(Q, l)} f, t \bullet_{\tilde T^l} f)\\
-    &= q \bullet_{A(Q, l)} f \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
-    &= q \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i) \bullet_Q ((x_i)_i + (t \bullet_{\tilde T^l} f))\\
-    &= q \bullet_Q ((\iota_{n, l}(f_i) \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i + (x_{n + i} \bullet_T ((x_j)_j + (t \bullet_{\tilde T^l} f)))_i)\\
-    &= q \bullet_Q ((f_i \bullet_T (x_j)_j)_i + ((t \bullet_{\tilde T^l} f)_i)_i)\\
-    &= q \bullet_Q ((f_i)_i + (t_i \bullet_{\tilde T} f)_i)\\
-    &= q \bullet_Q ((x_i \bullet_T f)_i + (t_i \bullet_T f)_i)\\
-    &= q \bullet_Q ((x_i)_i + t) \bullet_Q f\\
-    &= \varphi(q, t) \bullet_Q f.
-  \end{align*}
-
-  Now, given any presheaf $ Q^\prime : P T $ we need to show that any morphism $ \psi: Q^\prime \times \tilde T^l \to Q $ factors uniquely as $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) $ for some $ \tilde \psi: Q^\prime \to A(Q, l) $.
-
-  So, given such a $ \psi $, and given $ q: Q^\prime_n $, we take $ \tilde \psi(q) = \psi(\iota_{n, l}(q), (x_{n + i})_i) $
-
-  This is a presheaf morphism, since for all $ q: Q^\prime_m $ and $ f : T_n^m $,
-  \begin{align*}
-    \tilde \psi(q \bullet f) &= \psi(\iota_{n, l}(q \bullet f), (x_{n + i})_i)\\
-    &= \psi(q \bullet (\iota_{n, l}(f_i))_i, (x_{n + i})_i)\\
-    &= \psi((\iota_{m, l}(q), (x_{m + i})_i) \bullet_{Q^\prime \times \tilde T^l} ((\iota_{n, l}(f_i))_i + (x_{n + i})_i))\\
-    &= \psi(\iota_{m, l}(q), (x_{m + i})_i) \bullet_Q ((\iota_{n, l}(f_i))_i + (x_{n + i})_i)\\
-    &= \tilde \psi(q) \bullet_{A(Q, l)} f.
-  \end{align*}
-  Note that indeed $ \varphi \circ (\tilde \psi \times \id{\tilde T^l}) = \psi $:
-  \begin{align*}
-    \varphi(\tilde \psi(q), t) &= \varphi(\psi(\iota_{n, l}(q), (x_{n + i})_i), t)\\
-    &= \psi(\iota_{n, l}(q), (x_{n + i})_i) \bullet ((x_i)_i + t)\\
-    &= \psi(\iota_{n, l}(q) \bullet ((x_i)_i + t), (x_{n + i})_i \bullet ((x_i)_i + t))\\
-    &= \psi(q \bullet (x_i)_i, (t_i)_i)\\
-    &= \psi(q, t).\\
-  \end{align*}
-  Now, suppose that we have another $ \tilde \psi^\prime : Q^\prime \to A(Q, l) $ such that $ \varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}) = \psi $. Then we have
-  \begin{align*}
-    \tilde \psi(q) &= \psi(\iota_{n, l}(q), (x_{n + i})_i)\\
-    &= (\varphi \circ (\tilde \psi^\prime \times \id{\tilde T^l}))(\iota_{n, l}(q), (x_{n + i})_i)\\
-    &= \varphi(\tilde \psi^\prime(\iota_{n, l}(q)), (x_{n + i})_i)\\
-    &= \tilde \psi^\prime(\iota_{n, l}(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
-    &= \iota_{n, l}(\tilde \psi^\prime(q)) \bullet ((x_i)_i + (x_{n + i})_i)\\
-    &= \tilde \psi^\prime(q) \bullet (x_i)_i\\
-    &= \tilde \psi^\prime(q),
-  \end{align*}
-  so $ \tilde \psi $ is unique, which completes the proof.
-\end{proof}
-
-Now, this adjunction $ - \times \tilde T^l \dashv A(-, l) $ induces a natural isomorphism
-\[ \varphi: PT(- \times \tilde T^l, \tilde T) \xrightarrow{\sim} PT(-, A(\tilde T, l)) \]
-\begin{lemma}
-  For all $ f: PT(\tilde T^n \times \tilde T^l, \tilde T) $,
-  \[ \varphi_{\tilde T^n}(f)(q) = f(\iota_{m, l}(q), (x_{m + i})_i) \]
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{lemma}
-  For all $ f: PT(\tilde T^n, A(\tilde T, l)) $,
-  \[ \varphi_{\tilde T^n}^{-1}(f)(q, t) = f(q) \bullet ((x_i)_i + t). \]
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
 

### 2024-01-19 report/chapters/algebraic-structures.tex
Finish the first version of the examples section

@@
 
+\begin{lemma}
+  The category $ \Alg{F(S)} $ is equivalent to the coslice category (\TODO) $ S \downarrow \SET $.
+\end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}
+
+$ F(\emptyset) $ is, in some sense, the smallest nontrivial algebraic theory. Then $ F(S) $ is the smallest nontrivial algebraic theory that has the elements of $ S $ as constants.
+
+\subsection{The free \texorpdfstring{$ \lambda $}{lambda}-theory on a set}
+
+Like with the free algebraic theory, we will construct the free $ \lambda $-theory as the smallest nontrivial $ \lambda $-theory (which is the $ \lambda $-calculus) with some additional constants.
+
+Let $ S $ be a set. Consider the sequence of inductive types $ (\Lambda(S)_n)_n $ with the following constructors:
+\begin{align*}
+  \mathtt{Var}_n &: \{ 1, \dots, n \} \to \Lambda(S)_n;\\
+  \mathtt{App}_n &: \Lambda(S)_n \to \Lambda(S)_n \to \Lambda(S)_n;\\
+  \mathtt{Abs}_n &: \Lambda(S)_{n + 1} \to \Lambda(S)_n;\\
+  \mathtt{Con}_n &: S \to \Lambda(S)_n.\\
+\end{align*}
+
+Define a substitution operator $ \bullet: \Lambda(S)_m \times \Lambda(S)_n^m \to \Lambda(S)_n $ by induction on the first argument:
+\begin{align*}
+  \mathtt{Var}_m(i) \bullet g &= g_i;\\
+  \mathtt{App}_m(a, b) \bullet g &= \mathtt{App}_n(a \bullet g, b \bullet g);\\
+  \mathtt{Abs}_m(a) \bullet g &= \mathtt{Abs}_n(a \bullet ((g_i \bullet (x_{n + 1, j})_j)_i + (x_{n + 1})));\\
+  \mathtt{Con}_m(s) \bullet g &= \mathtt{Con}_n(s).
+\end{align*}
+
+And then quotient $ \Lambda(S) $ by the relation generated by
+\[ \mathtt{App}_m(\mathtt{Abs}_m(f), g) \sim f \bullet ((x_{n, i})_i + (g)) \]
+for all $ f: \Lambda(S)_{n + 1} $ and $ g: \Lambda(S)_n $.
+
+\begin{example}
+  We can give the sequence of sets $ \Lambda(S) $ an algebraic theory structure with variables $ x_{m, i} = \mathtt{Var}_m(i) $ and the substitution operator $ \bullet $ defined above.
+We can give $ \Lambda(S) $ a $ \lambda $-theory structure with $ \beta $-equality by taking
+  \[ \lambda_n(f) = \mathtt{Abs}_n(f) \quad \text{and} \quad \rho_n(f) = \mathtt{App}_{n + 1}(f \bullet (\mathtt{Var}_{n + 1}(i))_i, \mathtt{Var}_{n + 1}(n + 1)). \]
+
+  Now, given a function $ S \to S^\prime $, we define a morphism $ \LamTh(\Lambda(S), \Lambda(S^\prime)) $ by induction, sending $ \mathtt{Var}(i) $, $ \mathtt{App}(a, b) $ and $ \mathtt{Abs}(a) $ in $ \Lambda(S) $ to their corresponding elements in $ \Lambda(S^\prime) $ and sending $ \mathtt{Con}(s) $ to $ \mathtt{Con}(f(s)) $.
+\end{example}
+
+Note that, like with the previous example, we have a forgetful functor $ (\dot)_0: \LamTh \to \SET $.
+
+\begin{lemma}
+  $ \Lambda(S) $ is the free $ \lambda $-theory on $ S $.
+\end{lemma}
+\begin{proof}
+  Let $ L $ be a $ \lambda $-theory. We have an equivalence
+  \[ \LamTh(\Lambda(S), L) \cong \SET(S, L_0), \]
+  sending $ f: \LamTh(\Lambda(S), L) $ to $ f_0 \vert_S: S \to L_0 $ (again, trivially natural in $ S $ and $ L $) and conversely, $ g: \SET(S, L_0) $ to the inductively defined $ f: \LamTh(\Lambda(S), L) $ given by
+  \begin{align*}
+    f(\mathtt{Var}(i)) &= x_i;\\
+    f(\mathtt{App}(a, b)) &= \rho(f(a)) \bullet ((x_{n, i})_i + (b));\\
+    f(\mathtt{Abs}(a)) &= \lambda(f(a));\\
+    f(\mathtt{Con}(s)) &= g(s) \bullet ().
+  \end{align*}
+\end{proof}
+
+The proofs that $ \Lambda(S) $ is indeed a $ \lambda $-theory and that $ \Lambda(f) $ and $ g $ are $ \lambda $-theory morphisms, mainly work by definition of $ \bullet $, $ \lambda $ and $ \rho $, by induction on the terms of $ \Lambda(S) $ and by invoking the properties of the $ \lambda $-theory $ L $.
+
+\begin{corollary}
+  The `pure' lambda calculus is the initial $ \lambda $-theory.
+\end{corollary}
+\begin{proof}
+  If we take $ S = \emptyset $, $ \Lambda(\emptyset) $ is the lambda calculus, which we will call $ \Lambda $.
+We have, like with the free algebraic theory, that $ \Lambda(\emptyset) $ is the initial $ \lambda $-theory.
+\end{proof}
+
 \subsection{The free object algebraic theory}
@@
 
+\begin{remark}
+  Another counterexample is the category $ \mathbf{Top} $ of topological spaces.
+We have a forgetful functor $ G: \mathbf{Top} \to \SET $ that just forgets the topology.
+On the other hand, we have a free functor $ F: \SET \to \mathbf{Top} $ which endows a set with the discrete topology.
+In this case, one obtains the inital algebraic theory $ T_n = \{ 1, \dots, n \} $, with an algebra action on every topological space $ i \bullet (a_1, \dots, a_n) = a_i $.
+Now, note that we can endow the set $ \{ \top, \bot \} $ with four different, nonisomorphic topologies, which all yield the same $ T $-algebra; the $ T $-algebra structure does not preserve the topological information.
+Therefore, the functor $ \alpha: \mathbf{Top} \to \Alg T $ is not an equivalence.
+\end{remark}
+
 \subsection{The terminal theory}
@@
 
+\begin{lemma}
+  $ \{ \star \} $ is the only algebra of the terminal theory.
+\end{lemma}
+\begin{proof}
+  Let $ A $ be a $ T $-algebra. First of all, we have an element $ \star_A = \star_T \bullet_{0} () $. Secondly, for all elements $ \star, \star^\prime: A $, we have
+  \[ \star = x_1 \bullet (\star, \star^\prime) = \star \bullet (\star, \star^\prime) = x_2 \bullet (\star, \star^\prime) = \star^\prime. \]
+  Therefore, $ A = \{ \star \} $, which allows exactly one possible $ T $-action:
+  \[ \star \bullet (\star, \dots, \star) = \star. \]
+\end{proof}
+
 \subsection{The endomorphism theory}
@@
 \end{definition}
-
-\begin{lemma}
-  $ E(X) $ is indeed an algebraic theory.
-\end{lemma}
-\begin{proof}
-  For $ 1 \leq j \leq l $, $ f: E(X)_l $, $ g: {E(X)_m}^l $ and $ h: {E(X)_n}^m $, we have
-  \[ x_j \bullet g = x_j \circ \langle g_i \rangle_i = g_j, \]
-  \[ f \bullet (x_{l,i})_i = f \circ \langle x_{l, i} \rangle_i = f \circ \id{X^l} = f \]
-  and
-  \[ (f \bullet g) \bullet h = f \circ \langle g_i \rangle_i \circ \langle h_i \rangle_i = f \circ \langle g_i \circ \langle h_{i^\prime} \rangle_{i^\prime} \rangle_i = f \bullet (g_i \bullet h)_i. \]
-\end{proof}
 
@@
 
-\begin{lemma}
-  $ E(X) $ is indeed a $ \lambda $-theory.
-\end{lemma}
-\begin{proof}
-  Note that $ \varphi: C(- \times X, X) \xrightarrow{\sim} C(-, X^X) $ is a natural isomorphism, so for $ g: {E(X)_n}^m $, the following diagram commutes
-  \begin{center}
-    \begin{tikzcd}[column sep = 1in]
-      C(X^m \times X, X) \arrow[r, "- \circ (\langle g_i \rangle_i \times \id X)"]\arrow[d, "\varphi_{X^m}", bend left] & C(X^n \times X, X^X) \arrow[d, "\varphi_{X^n}", bend left]\\
-      C(X^m, X^X) \arrow[r, "- \circ \langle g_i \rangle_i"] \arrow[u, "\varphi_{X^m}^{-1}", bend left] & C(X^n, X^X) \arrow[u, "\varphi_{X^n}^{-1}", bend left]
-    \end{tikzcd}
-  \end{center}
-  and note that $ \langle g_i \rangle_i \times \id X = \langle g_1, \dots, g_m, x_{n + 1} \rangle $. Then we have, for all $ f: E(X)_m $
-  \begin{align*}
-    \lambda_m(f) \bullet g &= abs \circ \varphi_{X^m}(f) \circ \langle g_i \rangle_i\\
-    &= abs \circ \varphi_{X^n}(f \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle)\\
-    &= \lambda_n(f \bullet (g_1, \dots, g_m, x_{n + 1}))
-  \end{align*}
-  and
-  \begin{align*}
-    \rho_n(f \bullet g) &= \varphi_{X^n}^{-1}(app \circ f \circ \langle g_i \rangle_i)\\
-    &= \varphi_{X^m}^{-1}(app \circ f) \circ \langle g_1, \dots, g_m, x_{n + 1} \rangle\\
-    &= \rho_m(f) \bullet (g_1, \dots, g_m, x_{n + 1}).
-  \end{align*}
-\end{proof}
-
-\subsection{The free \texorpdfstring{$ \lambda $}{lambda}-theory}
-
-Let $ S $ be a set. Consider the sequence of inductive types $ (\Lambda(S)_n)_n $ with the following constructors:
-\begin{align*}
-  \mathtt{Var}_n &: \{ 1, \dots, n \} \to \Lambda(S)_n;\\
-  \mathtt{App}_n &: \Lambda(S)_n \to \Lambda(S)_n \to \Lambda(S)_n;\\
-  \mathtt{Abs}_n &: \Lambda(S)_{n + 1} \to \Lambda(S)_n;\\
-  \mathtt{Con}_n &: S \to \Lambda(S)_n.\\
-\end{align*}
-
-Define a substitution operator $ \bullet: \Lambda(S)_m \times \Lambda(S)_n^m \to \Lambda(S)_n $ by induction on the first argument:
-\begin{align*}
-  \mathtt{Var}_m(i) \bullet g &= g_i;\\
-  \mathtt{App}_m(a, b) \bullet g &= \mathtt{App}_n(a \bullet g, b \bullet g);\\
-  \mathtt{Abs}_m(a) \bullet g &= \mathtt{Abs}_n(a \bullet ((g_i \bullet (x_{n + 1, j})_j)_i + (x_{n + 1})));\\
-  \mathtt{Con}_m(s) \bullet g &= \mathtt{Con}_n(s).
-\end{align*}
-
-And then quotient $ \Lambda(S) $ by the relation generated by
-\[ \mathtt{App}_m(\mathtt{Abs}_m(f), g) \sim f \bullet ((x_{n, i})_i + (g)) \]
-for all $ f: \Lambda(S)_{n + 1} $ and $ g: \Lambda(S)_n $.
-
-% \subsection{The \texorpdfstring{$ \lambda $}{lambda}-calculus}
+The proofs that $ E(X) $ is an algebraic theory and a $ \lambda $-theory, use properties of the product, and naturality of the isomorphism $ \varphi_Y $.
 
@@
 \end{proof}
-
-Now, this adjunction $ - \times T^l \dashv A(-, l) $ induces a natural isomorphism
-\[ \varphi: \Pshf T(- \times T^l, T) \xrightarrow{\sim} \Pshf T(-, A(T, l)) \]
-\begin{lemma}
-  For all $ f: \Pshf T(T^n \times T^l, T) $,
-  \[ \varphi_{T^n}(f)(q) = f(\iota_{m, l}(q), (x_{m + i})_i) \]
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{lemma}
-  For all $ f: \Pshf T(T^n, A(T, l)) $,
-  \[ \varphi_{T^n}^{-1}(f)(q, t) = f(q) \bullet ((x_i)_i + t). \]
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}

### 2024-01-19 report/chapters/algebraic-structures.tex
Write about coslices

@@
 
+Let $ \iota_{m, n} : T_m \to T_{m + n} $ be the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
+\[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \quad \text{and} \quad \iota_{m, n}(f \bullet g) = f \bullet (\iota_{m, n}(g_i))_i. \]
+
+For tuples $ x : X^m $ and $ y: X^n $, let $ x + y $ denote the tuple $ (x_1, \dots, x_m, y_1, \dots, y_n) : X^{m + n} $.
+
 \begin{definition}[$ \lambda $-theory]
@@
   \begin{align*}
-    \lambda_m(f) \bullet h &= \lambda_n(f \bullet (h_1 \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), \dots, h_m \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), x_{n + 1, n + 1}))\\
-    \rho_n(g \bullet h) &= \rho_m(g) \bullet (h_1 \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), \dots, h_m \bullet (x_{n + 1, 1}, \dots, x_{n + 1, n}), x_{n + 1, n + 1})
+    \lambda_m(f) \bullet h &= \lambda_n(f \bullet ((\iota_{n, 1}(h_i))_i + (x_{n + 1})))\\
+    \rho_n(g \bullet h) &= \rho_m(g) \bullet ((\iota_{n, 1}(h_i))_i + (x_{n + 1}))
   \end{align*}
@@
 \begin{lemma}
-  The category $ \Alg{F(S)} $ is equivalent to the coslice category (\TODO) $ S \downarrow \SET $.
+  There is an adjoint equivalence between the category $ \Alg{F(S)} $ and the coslice category (\TODO) $ S \downarrow \SET $.
 \end{lemma}
 \begin{proof}
-  \TODO
+  For the equivalence, we send a $ F(S) $-algebra $ A $ to the set $ A $ with morphism $ s \mapsto s \bullet () $.
+An algebra morphism $ f: A \to B $ is sent to the coslice morphism $ f: (S \to A) \to (S \to B) $.
+This constitutes a functor.
+
+  Note that the category of $ F(S) $-algebras is univalent.
+
+  Also, the functor is fully faithful, since one can show that for $ F(S) $-algebras, the coslice morphism $ \varphi: (f: S \to A) \to (f^\prime: S \to B) $ also has the structure of an algebra morphism $ \varphi: A \to B $.
+
+  Lastly, the functor is essentially surjective, since we can lift a coslice $ f: S \to X $ to a $ F(S) $-algebra $ X $, with action
+  \[ i \bullet x = x_i \quad \text{and} \quad s \bullet x = f(s). \]
+
+  Therefore, the functor $ \Alg{F(S)} \to S \downarrow \SET $ is an adjoint equivalence.
+
+  The proofs of these facts work by simple case distinction, and by using the properties of the coslice and algebra morphisms.
 \end{proof}
@@
 
-Let $ \iota_{m, n} : T_m \to T_{m + n} $ denote the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
-\[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \quad \text{and} \quad \iota_{m, n}(f \bullet g) = f \bullet (\iota_{m, n}(g_i))_i. \]
-
-For tuples $ x : X^m $ and $ y: X^n $, let $ x + y $ denote the tuple $ (x_1, \dots, x_m, y_1, \dots, y_n) : X^{m + n} $.
-
 \begin{example}[The `+l' presheaf]

### 2024-01-23 report/chapters/algebraic-structures.tex
Add an index

@@
 
-\begin{definition}[algebraic theory]
-  We define an algebraic theory $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we usually leave $ n $ implicit), together with a substitution operation
+\begin{definition}
+  We define an \iindex{algebraic theory} $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we usually leave $ n $ implicit), together with a substitution operation
   \[ \_ \bullet \_: T_m \times T_n^m \to T_n \]
@@
 
-\begin{definition}[algebraic theory morphism]
-  A morphism $ F $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ F_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
+\begin{definition}
+  A \textit{morphism}\index{algebraic theory!morphism} $ F $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ F_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
   \begin{align*}
@@
 
-\begin{definition}[algebra]
-  An algebra $ A $ for an algebraic theory $ T $ is a set $ A $, together with an action
+\begin{definition}
+  An \iindex{algebra} $ A $ for an algebraic theory $ T $ is a set $ A $, together with an action
   \[ \bullet: T_n \times A^n \to A \]
@@
 
-\begin{definition}[algebra morphism]
-  For an algebraic theory $ T $, a morphism $ F $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ F: A \to A $ such that
+\begin{definition}
+  For an algebraic theory $ T $, a \textit{morphism}\index{algebra!morphism} $ F $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ F: A \to A $ such that
   \[ F(f \bullet a) = f \bullet (F(a_i))_i \]
@@
 
+\begin{lemma}
+  \TODO Fibration
+\end{lemma}
+
 \section{Presheaves}
 
-\begin{definition}[presheaf]
-  A presheaf $ P $ for an algebraic theory $ T $ is a sequence of sets $ P_n $ indexed over $ \mathbb N $, together with an action
+\begin{definition}
+  A \iindex{presheaf} $ P $ for an algebraic theory $ T $ is a sequence of sets $ P_n $ indexed over $ \mathbb N $, together with an action
   \[ \bullet: P_m \times T_n^m \to P_n \]
@@
 
-\begin{definition}[presheaf morphism]
-  For an algebraic theory $ T $, a morphism $ F $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ F_n: P_n \to P^\prime_n $ such that
+\begin{definition}
+  For an algebraic theory $ T $, a \textit{morphism}\index{presheaf!morphism} $ F $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ F_n: P_n \to P^\prime_n $ such that
   \[ F_n(t \bullet f) = F_m(t) \bullet f \]
@@
 
+\begin{lemma}
+  \TODO Fibration
+\end{lemma}
+
 \section{\texorpdfstring{$ \lambda $-}{lambda-}theories}
@@
 \begin{definition}[$ \lambda $-theory]
-  A $ \lambda $-theory is an algebraic theory $ L $, together with sequences of functions $ \lambda_n: L_{n + 1} \to L_n $ and $ \rho_n: L_n \to L_{n + 1} $, such that
+  A \iindex{$ \lambda $-theory} is an algebraic theory $ L $, together with sequences of functions $ \lambda_n: L_{n + 1} \to L_n $ and $ \rho_n: L_n \to L_{n + 1} $, such that
   \begin{align*}
@@
 \begin{definition}[$ \lambda $-theory morphism]
-  A morphism $ F $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ F $ such that
+  A \textit{morphism}\index{$ \lambda $-theory!morphism} $ F $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ F $ such that
   \begin{align*}
@@
 On the other hand, we have a free functor $ F: \SET \to \mathbf{Top} $ which endows a set with the discrete topology.
-In this case, one obtains the inital algebraic theory $ T_n = \{ 1, \dots, n \} $, with an algebra action on every topological space $ i \bullet (a_1, \dots, a_n) = a_i $.
-Now, note that we can endow the set $ \{ \top, \bot \} $ with four different, nonisomorphic topologies, which all yield the same $ T $-algebra; the $ T $-algebra structure does not preserve the topological information.
+The construction above yields the inital algebraic theory $ T_n = \{ 1, \dots, n \} $, with an algebra action on every topological space $ i \bullet (a_1, \dots, a_n) = a_i $.
+Now, note that we can endow the set $ \{ \top, \bot \} $ with four different, nonisomorphic topologies, which all yield the same $ T $-algebra.
+In other words: the $ T $-algebra structure does not preserve the topological information.
 Therefore, the functor $ \alpha: \mathbf{Top} \to \Alg T $ is not an equivalence.
@@
 
-\begin{definition}[Endomorphism theory]
+\begin{definition}
   Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
-  The endomorphism theory $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
+  The \iindex{endomorphism theory} $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
 \end{definition}
 
-\begin{definition}[Endomorphism $ \lambda $-theory]
+\begin{definition}
   Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:presheaf-Yoneda}
   Given an algebraic theory $ T $ and a $ T $-presheaf $ Q $, we have for all $ n $ a bijection of sets

### 2024-01-23 report/chapters/category-theory.tex
Start working on the "examples" section of the report
Finish the first version of the examples section
Move some small category-theoretical definitions to the category theory chapter, perform slight revisions on the text, shorten the section on the representation theorem

@@
 
-\section{Quick preliminaries}
-\subsection{Adjunctions}
-An adjoint equivalence of categories has multiple definitions. The one we will use here is the following:
+\section{Universal Arrows}
+(\cite{MacLane}, Chapter IV.1, Theorem 2 (iv))
+\TODO
 
-\tikzset{%
-    symbol/.style={%
-        draw=none,
-        every to/.append style={%
-            edge node={node [sloped, allow upside down, auto=false]{$#1$}}}
-    }
-}
+\section{Adjunctions}
 
-\begin{definition}
-  An adjoint equivalence between categories $ C $ and $ D $ is a pair of adjoint functors
+Recall that an \iindex{adjunction} $ L \dashv R $ is a pair of functors
 \begin{center}
@@
     D \arrow[r, bend right, "R"'{name=R}] & C \arrow[l, bend right, "L"'{name=L}]
-      \ar[from=L, to=R, symbol=\dashv]
   \end{tikzcd}
 \end{center}
-  such that the unit $ \eta: \id{C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{D} $ are isomorphisms of functors.
+with natural transformations (the unit and counit)
+\[ \eta: \id C \Rightarrow L \bullet R \quad \text{and} \quad \epsilon: R \bullet L \Rightarrow \id D \]
+such that the diagrams
+\begin{center}
+  \begin{tikzcd}[column sep = .5cm]
+    L \arrow[rd, "\eta \bullet L"'] \arrow[rr, "\id L"] & & L\\
+    & L \bullet R \bullet L \arrow[ur, "L \bullet \epsilon"']
+  \end{tikzcd}
+  \qquad
+  \begin{tikzcd}[column sep = .5cm]
+    R \arrow[rd, "R \bullet \eta"'] \arrow[rr, "\id R"] & & R\\
+    & R \bullet L \bullet R \arrow[ur, "\epsilon \bullet R"']
+  \end{tikzcd}
+\end{center}
+commute.
+Here the natural transformation $ \eta \bullet L: L \bullet R \bullet L $ is the natural transformation $ \eta $ whiskered on the right by $ L $, and the other whiskered transformations are similar.
+
+An alternative characterization of an adjunction $ L \dashv R $ is as a natural bijection
+\[ \varphi: D(L(c), d) \xrightarrow{\sim} C(c, R(d)). \]
+Naturality means that for all $ f: C(c^\prime, c) $, $ g: D(d, d^\prime) $ and $ h: D(L(c), d) $,
+\[ \varphi(L(f) \cdot h \cdot g) = f \cdot \varphi(h) \cdot R(g). \]
+
+\subsection{Adjoint equivalences}
+An adjoint equivalence of categories has multiple definitions. The one we will use here is the following:
+
+\begin{definition}
+  An \iindex{adjoint equivalence} between categories $ C $ and $ D $ is a pair of adjoint functors $ L \dashv R $ like above such that the unit $ \eta: \id{C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{D} $ are isomorphisms of functors.
 \end{definition}
@@
 \subsection{Exponential objects}
+Note that in the category of sets, for all $ X, Y: \SET $, we have a set $ (X \to Y) $. Also, for all $ X, Y, Z $, there is a (natural) bijection
+\[ (X \times Y \to Z) \cong (X \to (Y \to Z)) \]
+which we can also write as
+\[ \SET(X \times Y, Z) \cong \SET(X, (Y \to Z)). \]
+In other words, we have functors $ X \mapsto X \times Y $ and $ Z \mapsto (Y \to Z) $, and these two form an adjunction. The following generalizes this
+\begin{definition}
+  A category $ C $ has \textit{exponential objects}\index{exponential objects} (or \textit{exponentials}) if for all $ c: C $, the functor $ c^\prime \mapsto c^\prime \times c $ has a right adjoint, which we denote $ d \mapsto d^c $.
+\end{definition}
+
+\begin{lemma}
+  For $ c, d, d^c : C $, we have a natural bijection
+  \[ C(d^\prime \times c, d) \cong C(d^\prime, d^c) \]
+  iff we have a universal arrow ...
+\end{lemma}
+\begin{proof}
   \TODO
+\end{proof}
+
+\begin{remark}
+  It is actually very well possible that a category does not have all exponentials, but it has some objects $ c, d, d^c: C $ with a natural bijection
+  \[ C(d^\prime \times c, d) \cong C(d^\prime, d^c). \]
+  Then $ d^c $ is still called an exponential object.
+\end{remark}
+
+\section{(Co)slice categories}
+Given an object in a category $ c: C $, the morphisms to and from $ c $ constitute the slice and coslice categories
+\begin{definition}
+  The \iindex{slice category} $ C \downarrow c $ is the category with as objects the morphisms to $ c $:
+  \[ (C \downarrow c)_0 = \sum_{c^\prime: C} C(c^\prime, c). \]
+  The morphisms from $ (c^\prime, f) $ to $ (c^{\prime\prime}, f^\prime) $ are the morphisms $ g: c^\prime \to c^{\prime\prime} $ making the following diagram commute.
+  \begin{center}
+    \begin{tikzcd}[column sep=.5cm]
+      c^\prime \arrow[rr, "g"] \arrow[rd, "f"'] & & c^{\prime\prime} \arrow[ld, "f^\prime"]\\
+      & c
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+The \textit{coslice category}\index{slice category!co-} $ c \downarrow C $ is similar, but with the morphisms from $ c $:
+\[ (c \downarrow C)_0 = \sum_{c^\prime: C} C(c, c^\prime). \]
+
+\section{(Weakly) terminal objects}
+\begin{definition}
+  If a category has an object $ t $, such that there is a (not necessarily unique) morphism to it from every other object in the category, $ t $ is said to be a \iindex{weakly terminal object}.
+\end{definition}
+
+\begin{definition}
+  Given an object $ c $ in a category $ C $ with terminal object $ t $. A \iindex{global element} of $ c $ is a morphism $ C(t, c) $.
+\end{definition}
 
@@
   Precomposition gives a functor between functor categories $ F_* : [B, C] \to [A, C] $.
-If $ F_* $ has a left adjoint, we will denote call this adjoint functor the \textit{left Kan extension} along $ F $ and denote it $ \mathrm{Lan}_F : [A, C] \to [B, C] $.
+If $ F_* $ has a left adjoint, we will denote call this adjoint functor the \textit{left Kan extension}\index{Kan extension!left} along $ F $ and denote it $ \mathrm{Lan}_F : [A, C] \to [B, C] $.
 
@@
 
-  Analogously, when $ F_* $ has a right adjoint, one calls this the \textit{right Kan extension} along $ F $ and denote it $ \mathrm{Ran}_F: [A, C] \to [B, C] $.
+  Analogously, when $ F_* $ has a right adjoint, one calls this the \textit{right Kan extension}\index{Kan extension!right} along $ F $ and denote it $ \mathrm{Ran}_F: [A, C] \to [B, C] $.
 \end{definition}
@@
     \begin{tikzcd}[column sep=.5cm]
-      F(a) \arrow[rr, "F(g)"] \arrow[rd, "f^\prime"'] & & F(a^\prime) \arrow[ld, "f^\prime"]\\
+      F(a) \arrow[rr, "F(g)"] \arrow[rd, "f"'] & & F(a^\prime) \arrow[ld, "f^\prime"]\\
       & b
@@
 \begin{lemma}
-  If $ F : A \to B $ is a fully faithful functor, and $ C $ is a category with colimits, $ \eta $ is a natural isomorphism.
+  If $ F : A \to B $ is a fully faithful functor, and $ C $ is a category with colimits, $ \eta: \id{[A, C]} \Rightarrow \Lan F {} \bullet F_* $ is a natural isomorphism.
 \end{lemma}
@@
   To show that $ \eta $ is a natural isomorphism, we have to show that $ \eta_G(a^\prime): G(a^\prime) \Rightarrow \Lan F G(F(a^\prime)) $ is an isomorphism for all $ G: [A, C] $ and $ a^\prime: A $.
-Since a left adjoint is unique up to natural isomorphism, we can assume that $ \Lan F G(F(a^\prime)) $ is given by
+Since a left adjoint is unique up to natural isomorphism (\cite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(a^\prime)) $ is given by
   \[ \text{colim} ((F \downarrow F(a^\prime)) \to A \xrightarrow G C). \]
@@
   \[ \varphi: C(\Lan F G(F(a^\prime)), G(a^\prime)) \]
-  which constitutes an inverse to $ \eta_G(a^\prime) $.
+  which constitutes an inverse to $ \eta_G(a^\prime) $. The proof of this revolves around properties of the colimit and its (induced) morphisms.
 \end{proof}
@@
 we have (by definition) $ s \cdot r = \id d $.
-On the other hand, $ s \cdot r: c \to c $ is an idempotent morphism.
-Conversely, we can wonder whether for any idempotent morphism $ a: c \to c $, we can find a retraction-section pair $ r: c \to d $ and $ s: d \to c $ such that $ a = r \cdot s $.
-If this is the case, we say that the idempotent $ a $ \textit{splits}.
+On the other hand, $ r \cdot s: c \to c $ is an idempotent morphism, since $ r \cdot s \cdot r \cdot s = r \cdot s $.
+Conversely, we can wonder whether for some idempotent morphism $ a: c \to c $, we can find a retraction-section pair $ (r, s) $ such that $ a = r \cdot s $.
+If this is the case, we say that the idempotent $ a $ \textit{splits}\index{split idempotent}.
 If $ a $ does not split, we can wonder whether we can find an embedding $ \iota_C : C \hookrightarrow \overline C $ such that the idempotent $ \iota_C(a): \iota_C(c) \to \iota_C(c) $ does split.
+This is one way to arrive at the \textit{Karoubi envelope}.
 
@@
 \end{definition}
-This category is called the \textit{Karoubi Envelope}, the \textit{idempotent completion}, the \textit{category of retracts}, or the \textit{Cauchy completion} of $ C $.
-
-% \begin{definition}
-%   \TODO Karoubi envelope in terms of presheaves
-%   Alternatively, one can define $ \overline C $ to be the full subcategory of the presheaf category $ [\op C, \SET] $ that consists of retracts of representable presheaves.
-That is, the presheaves $ P: \op C $ such that there exists
-% \end{definition}
-
-% \begin{definition}
-%   Abstract definition: \TODO
-% \end{definition}
-
-% \begin{lemma}
-%   Equivalence of the definitions
-% \end{lemma}
+This category is called the \iindex{Karoubi envelope}, the \textit{idempotent completion}\index{idempotent completion|see{Karoubi envelope}}, the \textit{category of retracts}\index{category of retracts|see{Karoubi envelope}}, or the \textit{Cauchy completion}\index{Cauchy completion|see{Karoubi envelope}} of $ C $.
 
@@
 \begin{lemma}
-  Every idempotent splits in $ \overline C $.
+  In $ \overline C $, every idempotent splits.
 \end{lemma}
@@
 \begin{corollary}
-  As the category $ \SET $ is cocomplete, we have an equivalence between the category of presheaves on $ C $ and the category of presheaves on $ \overline C $.
+  As the category $ \SET $ is cocomplete, we have an equivalence between the category of presheaves on $ C $ and the category of presheaves on $ \overline C $:
+  \[ [\op C, \SET] \cong [\overline{\op C}, \SET] \cong [\op{\overline C}, \SET]. \]
 \end{corollary}
@@
 \begin{definition}
-  A \textit{right monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, m^\prime: M $,
+  A \textit{right monoid action}\index{monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, m^\prime: M $,
   \[ x 1 = x \qquad \text{and} \qquad (x m) m^\prime = x (m \cdot m^\prime). \]
@@
 \begin{definition}
-  A \textit{morphism} between sets $ X $ and $ Y $ with a right $ M $- action is an $ M $-equivariant function $ f: X \to Y $: a function such that $ f(xm) = f(x)m $ for all $ x: X $ and $ m: M $.
+  A \textit{morphism}\index{monoid action!morphism} between sets $ X $ and $ Y $ with a right $ M $-action is an $ M $-equivariant function $ f: X \to Y $: a function such that $ f(xm) = f(x)m $ for all $ x: X $ and $ m: M $.
 \end{definition}
@@
 
-\begin{definition}
-  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
-\end{definition}
-
 \begin{remark}
@@
 \end{remark}
-
-\begin{definition}
-  Given an object $ c $ in a category $ C $ with terminal object $ t $. The global elements of $ c $ are the morphisms $ C(t, c) $.
-\end{definition}
 
@@
 Consider the set $ C(M \times X, Y) $ with an $ M $-action given by $ \phi m^\prime(m, x) = \phi(m^\prime m, x) $.
-This is the exponential object $ X^Y $, with the evaluation morphism $ X \times X^Y \to Y $ given by $ (x, \phi) \mapsto \phi(1, x) $.
+This is the exponential object $ X^Y $, with the (universal) evaluation morphism $ X \times X^Y \to Y $ given by $ (x, \phi) \mapsto \phi(1, x) $.
 \end{proof}
+
+\begin{definition}
+  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
+\end{definition}
 
@@
 
+Remember that sets with a right monoid action are equivalent to presheaves on the monoid category.
+Also, $ \varphi $ is equivalent to a functor between the monoid categories.
+The following is a specific case of the concepts in the section about Kan extension:
+
 \begin{lemma}
-  We get a \textit{restriction of scalars} functor $ \varphi_* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
+  We get a \iindex{restriction of scalars} functor $ \varphi_* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
 \end{lemma}
@@
 \begin{lemma}
-  We get an \textit{extension of scalars} functor $ \varphi^* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
+  We get an \iindex{extension of scalars} functor $ \varphi^* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
 \end{lemma}
@@
 
-  On morphisms, it sends $ f: X \to X^\prime $ to the morphism $ (x, m^\prime) \mapsto (f(x), m^\prime) $.
+  On morphisms, it sends the $ m $-equivariant $ f: X \to X^\prime $ to the morphism $ (x, m^\prime) \mapsto (f(x), m^\prime) $.
 \end{proof}
@@
 
-If a category has an object $ t $, such that there is a morphism to it from every other object in the category, $ t $ is said to be \textit{weakly terminal}.
-
 \begin{lemma}
-  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal set with right $ M $-action, we have $ \varphi^*(I_M) \cong I_{M^\prime} $.
+  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi^*(I_M) \cong I_{M^\prime} $.
 \end{lemma}
 \begin{proof}
-  If $ D $ has a weakly terminal object, there exists $ \overline m^\prime : M^\prime $ such that for all $ m^\prime: M^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $.
+  If $ D $ has a weakly terminal object, there exists $ m_0 : M^\prime $ such that for all $ m^\prime: M^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = m_0 $.
 
@@
 
-  The fact that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object means that we have some $ \overline m^\prime: M^\prime $ and $ \overline m_1, \overline m_2: M $ with $ m_i^\prime = \varphi(\overline m_i) \cdot \overline m^\prime $, such that for all $ m^\prime: M^\prime $ and $ m_1, m_2: M $ with $ m_i^\prime = \varphi(m_i) \cdot m^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \cdot m $.
-
+  The fact that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object means that we have some $ \overline m^\prime: M^\prime $ and $ \overline m_1, \overline m_2: M $ with $ m_i^\prime = \varphi(\overline m_i) \cdot \overline m^\prime $.
 Therefore,
@@
 
-  The second part of weak terminality means that this equivalence is actually well-defined: equivalent elements in $ \varphi^*(A) \times \varphi^*(B) $ are sent to equivalent elements in $ \varphi^*(A \times B) $.
-
-  (\TODO Work this out more?)
+  The fact that $ (\overline m^\prime, \overline m_1, \overline m_2) $ is weakly terminal also means that for all $ m^\prime: M^\prime $ and $ m_1, m_2: M $ with $ m_i^\prime = \varphi(m_i) \cdot m^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \cdot m $.
+This means that the equivalence that we established is actually well-defined: equivalent elements in $ \varphi^*(A) \times \varphi^*(B) $ are sent to equivalent elements in $ \varphi^*(A \times B) $.
 \end{proof}

### 2024-01-23 report/chapters/paper.tex
Move some small category-theoretical definitions to the category theory chapter, perform slight revisions on the text, shorten the section on the representation theorem

@@
 \begin{theorem}
-  Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E(\tilde L) $ of $ \tilde L $ in the presheaf category of $ L $.
+  Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E(L) $ of $ L: \Pshf L $, which is $ L $, viewed as a presheaf in its own presheaf category.
 \end{theorem}
 \begin{proof}
-  First of all, remember that $ \tilde L $ is indeed exponentiable and that $ \tilde L^{\tilde L} = A(\tilde L, 1) $.
-  Now, since $ L $ is a $ \lambda $-theory, we have functions back and forth $ \lambda: A(\tilde L, 1) \to \tilde L $ and $ \rho: \tilde L \to A(\tilde L, 1) $.
-These are presheaf morphisms because for all $ f: A(\tilde L, 1)_m $ and $ g: \tilde L_m $ and $ t: T_n^m $,
-  \[ \lambda(f \bullet_{A(\tilde L, 1)} t) = \lambda(f \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1}))) = \lambda(f) \bullet_{\tilde L} t \]
-  and
-  \[ \rho(g \bullet_{\tilde L} t) = \rho(g) \bullet_{\tilde L} ((\iota_{m, 1}(t_i))_i + (x_{n + 1})) = \rho(g) \bullet_{A(\tilde L, 1)} t. \]
-  Therefore, $ E(\tilde L) $ is indeed a $ \lambda $-theory.
+  First of all, remember that $ L $ is indeed exponentiable and that $ L^L = A(L, 1) $.
+  Now, since $ L $ is a $ \lambda $-theory, we have sequences of functions back and forth $ \lambda_n: A(L, 1)_n \to L_n $ and $ \rho_n: L_n \to A(L, 1)_n $.
+These commute with the $ L $-actions, so they constitute presheaf morphisms and $ E(L) $ is indeed a $ \lambda $-theory.
 
-  For any presheaf $ Q $ and for any $ n $, we have a bijection $ PL(L^n, Q) \cong Q_n $.
-  Then we have $ \varphi: E(\tilde L)_n \cong L_n $.
-  This bijection is an isomorphism of $ \lambda $-theories, since it preserves the $ x_i $, $ \bullet $, $ \rho $ and $ \lambda $: for all $ 1 \leq j \leq n $, $ f: E(\tilde L)_m $, $ g: E(\tilde L)_{m + 1} $ and $ h: E(\tilde L)_n^m $.
-  \begin{align*}
-    \varphi(x_j) &= x_j(x_1, \dots, x_n)\\
-    &= x_j;\\
-    \varphi(f \bullet h) &= f \circ \langle h_i \rangle_i((x_i)_i)\\
-    &= f((h_i((x_j)_j))_i)\\
-    &= f((x_i)_i \bullet (h_i((x_j)_j))_i)\\
-    &= f((x_i)_i) \bullet (h_i((x_j)_j))_i\\
-    &= \varphi(f) \bullet (\varphi(h_i))_i;\\
-    \varphi(\rho(f)) &= \rho(f)((x_i)_i)\\
-    &= \rho(f((x_i)_i)) \bullet (x_i)_i\\
-    &= \rho(f((x_i)_i))\\
-    &= \rho(\varphi(f));\\
-    \varphi(\lambda(g)) &= \lambda(g)((x_i)_i)\\
-    &= \lambda(\varphi_{X^n}(g)((x_i)_i))\\
-    &= \lambda(g(\iota_{m, l}((x_i)_i) + (x_{m + 1})))\\
-    &= \lambda(g((x_i)_i))\\
-    &= \lambda(\varphi(g)).
-  \end{align*}
+  Lemma \ref{lem:presheaf-Yoneda} gives a sequence of bijections $ \varphi_n : \Pshf L(L^n, L) \cong L_n $ for all $ n $, sending $ F: \Pshf L(L^n, L) $ to $ F(x_1, \dots, x_n) $, and conversely sending $ s: L_n $ to $ ((t_1, \dots, t_n) \mapsto s \bullet (t_1, \dots, t_n)) $.
+It considers $ \lambda $-terms in $ n $ variables as $ n $-ary functions on the $ \lambda $-calculus.
+Therefore, it should come as no surprise that $ \varphi $ preserves the $ x_i $, $ \bullet $, $ \rho $ and $ \lambda $, which makes it into an isomorphism of $ \lambda $-theories and this concludes the proof.
 \end{proof}
@@
 \section{The Fundamental Theorem of the \texorpdfstring{$ \lambda $-}{lambda }calculus}
-
-\begin{definition}[$ \Lambda $]
-  There is a special $ \lambda $-theory, given by the $ \lambda $-calculus itself.
-$ \Lambda_n $ is the set of $ \lambda $-terms with $ n $ free variables, the $ x_i $ are the free variables, and $ \bullet $ is given by substitution.
-$ \lambda $ sends $ f: \Lambda_{n + 1} $ to $ \lambda x_{n + 1}, f $ and $ \rho $ sends $ f: \Lambda_n $ to $ \iota_{n, 1}(f) x_{n + 1} $ in $ \Lambda_n $.
-\end{definition}
-
-\begin{lemma}
-  $ \Lambda $ is indeed a $ \lambda $-theory.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{lemma}
-  $ \Lambda $ is the initial $ \lambda $-theory.
-\end{lemma}
-\begin{proof}
-  Given a $ \lambda $-theory $ L $, we construct a morphism $ f: \Lambda \to L $ by induction on the $ \lambda $-terms.
-We set $ f(x_i) = x_i $, $ f(\lambda(t)) = \lambda(f(t)) $ and $ f(st) = \rho(f(s)) \bullet ((x_i)_i + (f(t))) $.
-
-  This is a $ \lambda $-theory morphism because \TODO
-
-  It is unique, since \TODO
-\end{proof}
 

### 2024-01-27 report/chapters/algebraic-structures.tex
Start working on the fundamental theorem proof

@@
 \end{remark}
+
+\begin{definition}[Pullback of algebras]
+  If we have a morphism of algebraic theories $ f: T^\prime \to T $, we have a functor $ \Alg T \to \Alg T^\prime $.
+It endows $ T^\prime $-algebras with an action from $ T $ given by $ g \bullet_{T^\prime} a = f(g) \bullet_T a $.
+Then $ T^\prime $-algebra morphisms commute with this $ T $-action, so we indeed have a functor.
+\end{definition}
 
@@
 
-\begin{example}
+\begin{example}\label{ex:free-monoid-theory}
   For $ C $ the category of monoids, $ \alpha: C \to \Alg T $ is an adjoint equivalence.

### 2024-01-27 report/chapters/category-theory.tex
Start working on the fundamental theorem proof

@@
 
-\section{Monoids as categories}
+\section{Monoids as categories}\label{sec:monoid-category}
 Take a monoid $ M $.
@@
 \end{definition}
+
+These, together with the identity and composition from $ \SET $, constitute a category $ \RAct M $ of right $ M $-actions.
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:scalar-extension-monoid-monoid-action}
   For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi^*(U_M) \cong U_{M^\prime} $.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:scalar-extension-terminal}
   Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi^*(I_M) \cong I_{M^\prime} $.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:scalar-extension-product}
   Suppose that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object for all $ m^\prime_1, m^\prime_2: M^\prime $.
@@
   \[ (a, m^\prime_1, b, m^\prime_2) = (a, \varphi(\overline m_1) \cdot \overline m^\prime, b, \varphi(\overline m_2) \cdot \overline m^\prime) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime), \]
-  so this is equivalent to some element in $ \varphi^*(A \times B) = (A \times B \times M^\prime / \sim) $.
+  so this is equivalent to some element in $ \varphi^*(A \times B) = (A \times B \times M^\prime / \sim) $. Note that this trivially respects the right $ M^\prime $-action.
 
@@
 This means that the equivalence that we established is actually well-defined: equivalent elements in $ \varphi^*(A) \times \varphi^*(B) $ are sent to equivalent elements in $ \varphi^*(A \times B) $.
+
+  Therefore, we have an isomorphism $ \psi: \varphi^*(A) \times \varphi^*(B) \xrightarrow{\sim} \varphi^*(A \times B) $.
+Now we only need to show that the projections are preserved by this isomorphism.
+To that end, take $ x = (a, m^\prime_1, b, m^\prime_2) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime) : \varphi^*(A) \times \varphi^*(B) $.
+We have
+  \[ \varphi^*(\pi_1)(\psi(x)) = (a \overline m_1, \overline m^\prime) = \pi^\prime_1(x). \]
+  In the same way, $ \varphi^*(\pi_2) \circ \psi = \pi^\prime_2 $ and this concludes the proof.
 \end{proof}

### 2024-01-27 report/chapters/paper.tex
Start working on the fundamental theorem proof

@@
 
+\section{Terms of a \texorpdfstring{$ \Lambda $}{Lambda}-algebra}
+Let $ A $ be an algebra for the initial $ \lambda $-theory $ \Lambda $. We will assume that $ \Lambda $ (and therefore, any $ \lambda $-theory) satisfies $ \beta $-equality.
+
+The $ \Lambda $-algebra structure gives the terms of $ A $ quite a lot of behaviour. For example, we can define `function application' as
+\[ a b = (x_1 x_2) \bullet (a, b) \]
+and composition as
+\[ a \circ b = (x_1 \circ x_2) \bullet (a, b) \]
+for $ a, b : A $, with $ x_1 \circ x_2 = \lambda x_3, x_1 (x_2 x_3) : \Lambda_2 $.
+
+\begin{remark}
+  Recall that in Example \ref{ex:free-monoid-theory}, we constructed an algebraic theory $ T $ with a monoid structure.
+This allowed us to define a monoid operation on $ T $-algebras as well.
+We then were able to transfer associativity of the operation on the $ T_n $ to associativity of the operation on the algebras.
+In exactly the same way, the function composition on $ A $ is associative because composition on $ \Lambda_n $ is associative.
+\end{remark}
+
+\begin{definition}
+  We can consider the sets of elements of $ A $ that behave like functions in $ n $ variables:
+  \[ A_n = \{ a : A \mid (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 x_3 \dots x_{n + 1}) \bullet a = a \}. \]
+\end{definition}
+
+\begin{definition}
+  Take $ \mathbf 1_n = (\lambda x_1 \dots x_n, x_1 \dots x_n) \bullet () : A $.
+\end{definition}
+
+\begin{remark}
+  Some straightforward rewriting, shows that for all $ a : A $,
+  \[ \mathbf 1_n \circ a = (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1}) \bullet a. \]
+  In other words, $ A_n = \{ a : A \mid \mathbf 1_n \circ a = a \} $.
+\end{remark}
+
+\begin{remark}
+  Also note that $ \mathbf 1_n \circ a \circ \mathbf 1_n = \mathbf 1_n \circ a $, so for $ a : A_n $, $ a \circ \mathbf 1_n = a $.
+\end{remark}
+
+\begin{lemma}
+  For $ t: \Lambda_{m + n} $ and $ a_1, \dots, a_m: A $, we have $ (\lambda^n t) \bullet (a_1, \dots, a_m) : A $ and we have
+  \[ \mathbf 1_n \circ ((\lambda^n t) \bullet (a_1, \dots, a_m)) = (\lambda^n t) \bullet (a_1, \dots, a_m), \]
+  so $ (\lambda^n t) \bullet (a_1, \dots, a_m) : A_n $.
+\end{lemma}
+\begin{proof}
+  This follows by straightforward rewriting.
+\end{proof}
+
+\begin{corollary}
+  By the previous remark,
+  \[ ((\lambda^n t) \bullet (a_1, \dots, a_m)) \circ \mathbf 1_n = (\lambda^n t) \bullet (a_1, \dots, a_m). \]
+\end{corollary}
+\begin{corollary}
+  In particular, $ \mathbf 1_m \circ \mathbf 1_n = \mathbf 1_{\max(m, n)} $.
+From this, it follows that $ A_m \subseteq A_n $ for $ m \leq n $.
+It also follows that $ a \mapsto \mathbf 1_n \circ a $ gives a function from $ A $ to $ A_n $ (and also from $ A_m \subseteq A $ to $ A_n $).
+\end{corollary}
+
 \section{The Fundamental Theorem of the \texorpdfstring{$ \lambda $-}{lambda }calculus}
 
-\begin{definition}[Pullback of algebras]
-  If we have a morphism of algebraic theories $ f: T^\prime \to T $, we have a functor $ AT \to AT^\prime $.
+The fundamental theorem states that there is an equivalence of categories
+\[ \LamTh \cong \Alg \Lambda. \]
+We will prove this by showing that there is a fully faithful and essentially surjective functor.
 
-  On objects, it sends a $ T $-algebra $ A $ to a $ T^\prime $-algebra with set $ A $ and action $ g \bullet_{T^\prime} a = f(g) \bullet_T a $. This is a $ T^\prime $-algebra because \TODO.
+\subsection{The functor}
 
-  On morphisms, it sends $ \varphi: A \to A $ to $ \varphi: A \to A $. This is a $ T^\prime $-algebra morphism because for all $ g: T^\prime_n $ and $ a: A^n $, we have
-  \[ \varphi(g \bullet_{T^\prime} a) = \varphi(f(g) \bullet_T a) = f(g) \bullet_T \varphi(a) = g \bullet_{T^\prime} \varphi(a). \]
+\begin{definition}
+  For all $ n $, we have a functor from lambda theories to $ \Lambda $-algebras.
+It sends the $ \lambda $-theory $ L $ to the $ L $-algebra $ L_n $ and then turns this into a $ \Lambda $-algebra via the morpism $ \Lambda \to L $.
+It sends morphisms $ f: L \to L^\prime $ to the algebra morphism $ f_n : L_n \to L^\prime_n $.
 \end{definition}
+
+\subsection{Lifting \texorpdfstring{$ \Lambda $}{Lambda}-algebras}
+
+\begin{definition}[The monoid of a $ \Lambda $-algebra]
+  Now we make $ A_1 $ into a monoid under composition $ \circ $ with unit $ \mathbf 1_1 $. The fact that this is a monoid follows from the remarks in the last section.
+\end{definition}
+
+Recall that we have an equivalence $ [\op{C_{A_1}}, \SET] \cong \RAct{A_1} $.
+
+\begin{definition}
+  Now, composition $ \circ $ gives a right $ A_1 $-action on the $ A_n $, so we have $ A_n : \RAct{A_1} $.
+\end{definition}
+
 \begin{lemma}
-  This is indeed a functor.
+  We have $ A_1^{A_1} \cong A_2 $ in $ \RAct{A_1} $.
 \end{lemma}
 \begin{proof}
+  Recall that $ A_1^{A_1} $ consists of the set of $ A_1 $-equivariant morphisms $ A_1 \times A_1 \to A_1 $.
+
+  We have a bijection $ \varphi: A_2 \xrightarrow{\sim} A_1^{A_1} $, given by
+  \[ \varphi(a)(b, b^\prime) = (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a, b, b^\prime), \]
+  \TODO: relate to product in category of retracts.
+
+  with an inverse given by
+  \[ \varphi^{-1}(f) = \lambda x_1 x_2, f(p_1, p_2)(\lambda x_3, x_3 x_1 x_2) \]
+  for $ p_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $. Note that for terms $ c_1, c_2 $, we have $ p_i (\lambda x_1, x_1 c_1 c_2) = c_i $.
+
+  This is an inverse, because given $ f: A_1^{A_1} $ and $ (a_1, a_2): A_1 \times A_1 $, we have
+  \[ \varphi(\psi(f))(a_1, a_2) = f(p_1, p_2) \circ q = f(p_1 \circ q, p_2 \circ q) = f(a_1, a_2) \]
+  for $ q = \lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)) $.
+In the last step of this proof, we use, among other things, the fact that the $ a_i : A_1 $ and therefore $ \lambda x_1, a_i x_1 = a_i $.
+
+  Some straightforward rewriting shows that for $ a: A_2 $, we have $ \psi(\varphi(a)) = a $.
+In the last step of this proof, we use the fact that $ a : A_2 $ and therefore $ \lambda x_1 x_2, a x_1 x_2 = a $.
+
+  Therefore, $ \varphi $ is a bijection and, as it turns out, an isomorphism.
+\end{proof}
+
+\begin{definition}[Construction of the $ \lambda $-theory]
+  Since $ \RAct{A_1} $ has products, the algebraic theory $ E(A_1) $ exists.
+
+  Recall that $ A_2 \subseteq A_1 $ and that $ a \mapsto \mathbf 1_2 \circ a $ gives a function from $ A_1 $ to $ A_2 $, which is, by definition, the identity on $ A_2 $.
+This gives $ E(A_1) $ a $ \lambda $-theory structure with $ \beta $-equality.
+\end{definition}
+
+\subsection{Lifting algebra morphisms}
+
+\begin{definition}[Pullback functor on presheaves for a $ \Lambda $-algebra]
+  A $ \Lambda $-algebra morphism preserves $ \mathbf 1_n $ and $ \circ $, so it sends elements of $ A_n $ to $ A^\prime_n $. In particular, it gives a monoid morphism $ f: A_1 \to A^\prime_1 $.
+
+  Therefore, as described in Section \ref{sec:monoid-category}, we get pullback and pushforward functors $ f_*: \RAct{A^\prime_1} \to \RAct{A_1} $ and $ f^* : \RAct{A_1} \to \RAct{A^\prime_1} $.
+\end{definition}
+
+\begin{remark}
+  By Lemma \ref{lem:scalar-extension-monoid-monoid-action}, we have $ f^*(U_{A_1}) \cong U_{A^\prime_1} $.
+\end{remark}
+
+\begin{lemma}
+  $ f^* $ preserves finite products.
+\end{lemma}
+\begin{proof}
+  We will show that $ f^* $ preserves binary products and the terminal object.
+
+  We use Lemma \ref{lem:scalar-extension-terminal} to show that $ f^* $ preserves the terminal object. We take
+  \[ a_0 = (\lambda x_1 x_2, x_2) \bullet () : A_1 \quad \text{and} \quad a_0^\prime = (\lambda x_1 x_2, x_2) \bullet () : A^\prime_1 \]
+  and $ a_0^\prime $ is weakly terminal because for all $ a : A_1 $, we have $ f(a_0) \circ a = a_0^\prime $.
+
+  We use Lemma \ref{lem:scalar-extension-product} to show that $ f^* $ also preserves the product. Therefore, given $ a_1, a_2 : A_1 $.
+
+  (\TODO: relate to product)
+  Take $ a = \lambda x_1 x_2, x_2 (a_1 x_1) (a_2 x_1) $ and $ \pi_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{n + 1}) $. We have $ a_i = f(\pi_i) \circ a $.
+
+  Need to show that exists $ (\overline m^\prime, \overline m_1, \overline m_2) : A^\prime_1 \times A_1 \times A_1 $ with $ a_i = f(\overline m_i) \circ \overline m^\prime $ such that for all $ (m^\prime, m_1, m_2) $, there exists $ m : A_1 $ such that $ f(m) = m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \circ m $.
+
   \TODO
@@
 
-\begin{definition}[Term algebra]
-  Given an algebraic theory $ T $, for every $ n $, $ T_n $ together with the action operator $ \bullet: T_m \times T_n^m \to T_n $ gives a $ T $-algebra.
+\begin{definition}
+  Since $ f^* $ preserves finite products, given an element of $ g: E(U_{A_1})_n = \RAct{A}(U_{A_1}^n, U_{A_1}) $, we get
+  \[ \# f^*(g): \RAct{A^\prime}(f(A_1^n), f(A_1)) \cong \RAct{A^\prime}((A^\prime_1)^n, A^\prime_1) = E(A^\prime_1)_n. \]
 \end{definition}
@@
 \begin{lemma}
-  $ T_n $ is indeed a $ T $-algebra.
+  $ \# f^*: E(U_{A_1}) \to E(U_{A^\prime_1}) $ is a map of $ \lambda $-theories.
 \end{lemma}
@@
 \begin{definition}
-  For all $ n $, we have a functor from lambda theories to $ \Lambda $-algebras.
-It sends the $ \lambda $-theory $ L $ to the $ L $-algebra $ L_n $ and then turns this into a $ \Lambda $-algebra via the morpism $ \Lambda \to L $.
-
-  It sends morphisms $ f: L \to L^\prime $ to $ f_n : L_n \to L^\prime_n $. This is a $ \Lambda $-algebra morphism because \TODO
-\end{definition}
-
-\begin{lemma}
-  This indeed constitutes a functor.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{remark}
-  Note that for a monoid $ M $, if we view $ M $ as a category, the category $ [\op{M}, \SET] $ consists of sets with a right $ M $-action.
-\end{remark}
-
-\begin{definition}[The exponential object in the presheaf category]
-  Given a monoid $ M $, if we have two presheaves (sets with right $ M $-actions) $ P $ and $ P^\prime $, we have a set of $ M $-equivariant maps
-  \[ F_{P, P^\prime} = \left\{ f: M \times P \to P^\prime \mid \prod_{p : P, m, m^\prime: M} f(m, p)m^\prime = f(m m^\prime, p m^\prime) \right\} \]
-  with a right $ M $-action, given by $ f m^\prime(m, p) = f(m^\prime m, p) $. This is again $ M $-equivariant because
-  \[ fm^\prime(m, p)m^{\prime \prime} = f(m^\prime m, p)m^{\prime \prime} = f(m^\prime m m^{\prime \prime}, p m^{\prime \prime}) = f m^\prime(m m^{\prime \prime}, p m^{\prime \prime}), \]
-  so $ F_{P, P^\prime} $ is a presheaf.
-
-  Now, to show that $ F_{P, P^\prime} $ is the exponential object $ {P^\prime}^P $, we show that for any $ P $, $ F_{P, -} $ is the left adjoint of $ - \times P $.
-So we need for all $ P^\prime: PT $, a universal arrow $ \varphi: F_{P, P^\prime} \times P \to P^\prime $.
-
-  First of all, we have an evaluation map $ \varphi: F_{P, P^\prime} \times P \to P^\prime $ given by $ (f, p) \mapsto f(I, p) $ for $ I $ the unit of the monoid.
-This map is equivariant because for all $ m $,
-  \[ (f, p) m = (f m, p m) \mapsto f m(I, p m) = f(m, p m) = f(I, p) m. \]
-  Now, given any presheaf $ Q $ and any morphism $ \psi: Q \times P \to P^\prime $, take $ \tilde \psi: Q \to F_{P, P^\prime} $ given by $ \psi(q)(m, p) = \psi(q m, p) $. This is equivariant because
-  \[ \tilde \psi(q)m(m^\prime, p) = \tilde \psi(q)(m m^\prime, p) = \psi(q m m^\prime, p) = \tilde \psi(q m)(m^\prime, p) \]
-  and we have
-  \[ \varphi(\tilde \psi(q), p) = \tilde \psi(q)(I, p) = \psi(q, p). \]
-  Now, suppose that we have $ \tilde \psi^\prime: Q \to F_{P, P^\prime} $ such that $ \varphi \circ (\tilde \psi^\prime \times \id{P}) = \psi $. Then for all $ q : Q $, $ m: M $ and $ p: P $,
-  \[ \tilde \psi(q)(m, p) = \psi(q m, p) = \varphi(\tilde \psi^\prime(q m), p) = \tilde \psi^\prime(q m)(I, p) = \psi^\prime(q) m(I, p) = \psi^\prime(q)(m, p), \]
-  so $ \tilde \psi $ is unique and $ F_{P, P^\prime} $ is an exponential object.
-\end{definition}
-
-\begin{definition}[n-functional terms]
-  Let $ A $ be a $ \Lambda $-algebra. We define
-  \[ A(n) = \{ a : A \mid (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 x_3 \dots x_{n + 1}) \bullet a = a \}. \]
-\end{definition}
-
-\begin{definition}
-  Take $ \mathbf 1_n = (\lambda x_1 \dots x_n, x_1 \dots x_n) \bullet () : A $.
-\end{definition}
-
-\begin{definition}
-  We define composition as $ a \circ b = (\lambda x_3, x_1 (x_2 x_3)) \circ (a, b) $ for $ a, b : A $.
-\end{definition}
-
-\begin{lemma}
-  This composition is associative.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{definition}[The monoid of a $ \Lambda $-algebra]
-  Now we make $ A(1) $ into a monoid with unit $ \lambda x_1, x_1 $.
-\end{definition}
-
-\begin{lemma}
-  This is indeed a monoid.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-From here on, we will assume that $ \Lambda $ (and therefore, any $ \lambda $-theory) satisfies $ \beta $-equality.
-
-\begin{lemma}
-  For $ a: A $, $ a $ is in $ A(n) $ iff $ \mathbf 1_n \circ a = a $.
-\end{lemma}
-\begin{proof}
-  \begin{align*}
-    \mathbf 1_n \circ a
-    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet (((\lambda x_1 \dots x_n, x_1 \dots x_n) \bullet ()), a)\\
-    &= (\lambda x_3, x_1 (x_2 x_3)) \bullet (((\lambda x_2 \dots x_{n + 1}, x_2 \dots x_{n + 1}) \bullet a), x_1 \bullet a)\\
-    &= ((\lambda x_3, x_1 (x_2 x_3)) \bullet ((\lambda x_2 \dots x_{n + 1}, x_2 \dots x_{n + 1}), x_1)) \bullet a\\
-    &= (\lambda x_2, (\lambda x_3 \dots x_{n + 2}, x_3 \dots x_{n + 2}) (x_1 x_2)) \bullet a\\
-    &= (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1}) \bullet a.
-  \end{align*}
-\end{proof}
-
-\begin{definition}[The presheaf category of a $ \Lambda $-algebra]
-  Let $ A $ be a $ \Lambda $-algebra. If we view the monoid $ A(1) $ as a one-object category, we define the category $ PA $ to be the category of presheaves $ [\op{A(1)}, \SET] $.
-\end{definition}
-
-\begin{definition}[The objects $ A(n) $ in $ PA $]
-  Given $ a: A(n) $ and $ b: A(1) $, we have
-  \[ \mathbf 1_n \circ (a \circ b) = (\mathbf 1_n \circ a) \circ b = a \circ b, \]
-  so $ a \circ b: A(n) $ and we have a right $ A(1) $-action on $ A(n) $, which makes $ A(n) $ into an object in $ PA $.
-\end{definition}
-
-\begin{lemma}
-  We have $ A(1)^{A(1)} \cong A(2) $.
-\end{lemma}
-\begin{proof}
-  We have a bijection $ \varphi: A(2) \cong F_{A(1), A(1)} $, given by
-  \[ \varphi(a)(b, b^\prime) = (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a, b, b^\prime). \]
-  Note that $ \varphi(d) $ is equivariant because \TODO
-  Now, $ \varphi $ is a presheaf morphism because \TODO
-
-  Take $ p = \lambda x_1, x_1 (\lambda x_2 x_3, x_2) $ and $ q = \lambda x_1, x_1 (\lambda x_2 x_3, x_3) $. These are elements of $ A(1) $. Note that for terms $ c_1, c_2 $
-  \begin{align*}
-    p (\lambda x_1, x_1 c_1 c_2)
-    &= (\lambda x_1, x_1 c_1 c_2) (\lambda x_2 x_3, x_2)\\
-    &= (\lambda x_1 x_3, x_2) c_1 c_2\\
-    &= c_1.
-  \end{align*}
-  In the same way, $ q \circ (\lambda x_1 x_2, x_2 c_1 c_2) = c_2 $.
-
-  An inverse is given by
-  \[ \psi: f \mapsto \lambda x_1 x_2, f(p, q)(\lambda x_3, x_3 x_1 x_2). \]
-  This is a presheaf morphism because \TODO
-
-  This is an inverse, because given $ f: F_{A(1), A(1)} $ and$ (a_1, a_2): A(1) \times A(1) $, we have
-  \begin{align*}
-    \varphi(\psi(f))(a_1, a_2) &= u(\lambda x_1 x_2, f(p, q)(\lambda x_3, x_3 x_1 x_2))(a_1, a_2)\\
-    &= \lambda x_1, (\lambda x_2 x_3, f(p, q)(\lambda x_4, x_4 x_2 x_3)) (a_1 x_1) (a_2 x_1)\\
-    &= \lambda x_1, f(p, q)(\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))\\
-    &= f(p, q) \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)))\\
-    &= f(p \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))), q \circ (\lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1))))\\
-    &= f(\lambda x_1, p (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)), \lambda x_1, q (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)))\\
-    &= f(\lambda x_1, a_1 x_1, \lambda x_1, a_2 x_1)\\
-    &= f(a_1, a_2).
-  \end{align*}
-  The last line is because $ a_i : A(1) $ and therefore $ \lambda x_1, a_i x_1 = a_i $.
-
-  On the other hand, if we have $ a_1: A(2) $, we have
-  \begin{align*}
-    \psi(\varphi(a_1)) &= \psi((a_2, a_3) \mapsto \lambda x_1, a_1 (a_2 x_1) (a_3 x_1))\\
-    &= \lambda x_1 x_2, (\lambda x_3, a_1 (p x_3) (q x_3)) (\lambda x_3, x_3 x_1 x_2)\\
-    &= \lambda x_1 x_2, a_1 (p (\lambda x_3, x_3 x_1 x_2)) (q (\lambda x_3, x_3 x_1 x_2))\\
-    &= \lambda x_1 x_2, a_1 x_1 x_2\\
-    &= a_1.
-  \end{align*}
-  The last line is because $ a_1 : A(2) $ and therefore $ \lambda x_1 x_2, a_1 x_1 x_2 = a_1 $.
-
-  Therefore, this map is a bijection and an isomorphism.
-\end{proof}
-
-\begin{definition}[Endomorphism $ \lambda $-theory of a $ \Lambda $-algebra]
-  $ PA $ borrows products from $ \SET $. Therefore, the algebraic theory $ E(A(1)) $ exists. Now note that $ A(1) $ is exponentiable and $ A(1)^{A(1)} \cong A(2) $.
-  Note that $ A(2) \subseteq A(1) $ and that $ (\lambda x_2 x_3, x_1 x_2 x_3) \bullet - $ gives a function from $ A(1) $ to $ A(2) $. This gives $ E(A(1)) $ a $ \lambda $-theory structure.
-\end{definition}
-
-\begin{definition}[Pullback functor on presheaves for a $ \Lambda $-algebra]
-  Let $ f: A \to A^\prime $ be a $ \Lambda $-algebra morphism. Then for all $ a: A(n) $,
-  \[ \mathbf 1_n \circ f(a) = f(\mathbf 1_n) \circ f(a) = f(\mathbf 1_n \circ a), \]
-  so we have an induced morphism $ f: A(n) \to A^\prime(n) $.
-
-  Now, given a presheaf $ P: PA^\prime $.
-We can create a presheaf $ f^* P : PA $ by taking the set of $ P $, and, for $ p: P $ and $ a: A $, setting $ pa = p \circ f(a) $.
-This is indeed a presheaf because \TODO
-
-  Now, given a morphism $ g: P \to P^\prime $, we get a morphism by taking the function on the sets of $ P $ and $ P^\prime $. This is a morphism because \TODO
-\end{definition}
-
-\begin{lemma}
-  The above indeed constitutes a functor.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-Left Kan extension then gives a left adjoint $ f_*: PA \to PA^\prime $.
-
-\begin{lemma}
-  We have $ f_*(A(1)) \cong A^\prime(1) $.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{lemma}
-  $ f_* $ preserves finite products.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{definition}
-  Since $ f_* $ preserves finite products, given an element of $ g: E(A(1))(n) = PA(A(1)^n, A(1)) $, we get
-  \[ \# f_*(g): PA^\prime(f(A(1)^n), f(A(1))) \cong PA^\prime(A^\prime(1)^n, A^\prime(1)) = E(A^\prime(1))(n). \]
-\end{definition}
-
-\begin{lemma}
-  $ \# f_*: E(A(1)) \to E(A^\prime(1)) $ is a map of $ \lambda $-theories.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
-\begin{definition}
-  We have an isomorphism $ E(A(1))(0) \cong A $ given by $ a \mapsto a I $.
+  We have an isomorphism $ E(U_{A_1})_0 \cong A $ given by $ a \mapsto a I $.
 \end{definition}
@@
 
-  It is essentially surjective, because $ L $ is isomorphic \TODO to $ E(A(1)) $.
+  It is essentially surjective, because $ L $ is isomorphic \TODO to $ E(U_{A_1}) $.
 
@@
 
-  The functor is full because a $ \Lambda $-algebra morphism $ f: A \to A^\prime $ induces a functor $ f^*: PA^\prime \to PA $, and via left Kan extension we get a left adjoint $ f_*: PA \to PA^\prime $ with $ f_*(A(1)) \cong A^\prime(1) $.
-Now, $ f_* $ preserves (finite) products, so we have maps $ PA(A(1)^n, A(1)) \to PA^\prime(A^\prime(1)^n, A^\prime(1)) $ and so a map $ E(A(1)) \to E(A^\prime(1)) $.
-This map, when restricted to a map $ PA(1, A(1)) \to PA^\prime(1, A(1)) $, and transported along the isomorphism $ a \mapsto a I $ \TODO, is equal to $ f $ \TODO.
+  The functor is full because a $ \Lambda $-algebra morphism $ f: A \to A^\prime $ induces a functor $ f^*: \RAct{A^\prime} \to \RAct{A} $, and via left Kan extension we get a left adjoint $ f^*: \RAct{A} \to \RAct{A^\prime} $ with $ f^*(A_1) \cong A^\prime_1 $.
+Now, $ f^* $ preserves (finite) products, so we have maps $ \RAct{A}(A_1^n, A_1) \to \RAct{A^\prime}((A^\prime_1)^n, A^\prime_1) $ and so a map $ E(U_{A_1}) \to E(U_{A^\prime_1}) $.
+This map, when restricted to a map $ \RAct{A}(1, A_1) \to \RAct{A^\prime}(1, A_1) $, and transported along the isomorphism $ a \mapsto a I $ \TODO, is equal to $ f $ \TODO.
 \end{proof}

### 2024-02-06 report/chapters/alternative-definitions.tex
Add alternative definitions of the algebraic structures

@@
 The literature, there are many different but equivalent definitions, carrying many different names, for the objects that called `algebraic theories' in Section \ref{sec:algebraic-theories}.
-What makes matters even more confusing is the fact that the literature does not provide a consistent bijection between names and definitions.
+Also, many of these different names are attached to differently defined objects in different sources.
 This section will showcase some of the various definitions.
 
-% First of all, let $ \F $ be a skeleton of finite sets: the category with $ \F_0 = \{ 0, 1, \dots \} $ and $ \F(m, n) = \SET(\{1, 2, \dots, m\}, \{1, 2, \dots, n\}) $.
+In this section, we will denote the finite set $ \llbracket n \rrbracket = \{ 1, \dots, n \} $.
 
 \section{Abstract Clone}
-\begin{definition}[abstract clone]
-  An algebraic theory as presented in Section \ref{sec:algebraic-theories}, is usually called an \textit{abstract clone}.
+\begin{definition}
+  An algebraic theory as presented in Section \ref{sec:algebraic-theories}, is usually called an \iindex{abstract clone}.
 In this thesis, outside of this specific section, we will call it algebraic theory to be consistent with the names that Hyland attaches to objects.
@@
 
+\begin{remark}
+  The definition of algebraic theory that Hyland gives is closest to that of an abstract clone.
+However, instead of a sequence of sets $ (T_n)_n $, he requires a functor $ T: F \to \SET $ (with $ F \subseteq \FinSET $ the skeleton category of finite sets $ F_0 = \{ \llbracket 0 \rrbracket, \llbracket 1 \rrbracket, \dots \} $), and he requires $ \bullet: T_m \times T_n^m \to T_n $ to be dinatural in $ n $ and natural in $ m $.
+
+  Using naturality, one can show that with such a functor we have $ x_{n, i} = f(a)(x_{1, 1}) $ for the function $ a(1) = i : \llbracket n \rrbracket $.
+
+  Alternatively, using the same naturality, one can show that this functor sends a morphism $ a: \llbracket m \rrbracket \to \llbracket n \rrbracket $ to the function $ T_m \to T_n $ given by
+  \[ f \mapsto f \bullet (x_{n, a(i)})_i. \]
+  If we take this to be the definition of our functor on morphisms, the (di)naturality in $ m $ and $ n $ can be shown using the associativity and the laws about the interaction between $ \bullet $ and the $ x_i $.
+
+  Since any additional properties mean extra complexity when formalizing, and since the proofs rarely use the functor structure, we decided to reduce the functor $ T: \FinSET \to \SET $ to a sequence of sets $ (T_n)_n $.
+\end{remark}
+
 \section{Lawvere theory}
-\begin{definition}[algebraic theory]
-  An \textit{algebraic theory} as presented in \cite{algebaric-theories-2010} is a small category with finite products.
+\begin{definition}
+  An \iindex{algebraic theory} as presented in \cite{algebaric-theories-2010} is a small category with finite products.
 \end{definition}
-\begin{definition}[algebraic theory algebra]
-  An \textit{algebra} for an algebraic theory $ T $ is a finite-product-preserving functor $ T \to \SET $.
+\begin{definition}
+  An \iindex{algebra} for an algebraic theory $ T $ is a finite-product-preserving functor $ T \to \SET $.
 \end{definition}
@@
 This definition is more general than the definition of algebraic theory in Section \ref{sec:algebraic-theories}. To make it equivalent, we have to be more specific about the objects of the category:
-\begin{definition}[Lawvere theory]
-  A \textit{Lawvere theory}, or \textit{one-sorted algebraic theory} is a category $ L $, with $ L_0 = \{ 0, 1, \dots \} $, such that $ n = 1^n $, the $ n $-fold product.
-\end{definition}
-
-\subsection{Algebras for Lawvere Theories}
-
-\section{Relative Monad}
-\begin{definition}[relative monad]
-  Let $ S: C \to D $ be a functor.
-A \textit{relative monad} on $ S $ is a functor $ T: C \to D $, together with a natural transformation $ \eta: S \Rightarrow T $ and a transformation $ (-)^*: D(S(X), T(Y)) \to D(T(X), T(Y)) $, natural in both $ S $ and $ T $, such that for all $ f: S(X) \to T(Y) $ and $ g: S(Y) \to T(Z) $,
-  \[ f = \eta_X \cdot f^*, \qquad \eta_X^* = \id{T X} \qquad \text{and} \qquad (f \cdot g^*)^* = f^* \cdot g^*. \]
-\end{definition}
-
-\section{Cartesian Operad}
-\begin{definition}[multicategory]
-  A \textit{multicategory} $ C $ consists of
-  \begin{itemize}
-    \item A collection of objects $ C_0 $;
-    \item For all $ c_1, \dots, c_n, d: C_0 $, a collection of multimorphisms $ C((c_1, \dots, c_n), d) $;
-    \item For all $ c: C_0 $, an identity morphism $ \id c : C(c, c) $;
-    \item For all multimorphisms $ f: C((d_1, \dots, d_n), e) $ and $ g_i: C((c_{i,1}, \dots, c_{i,m_i}), d_i) $ for $ 1 \leq n \leq i $, a composite multimorphism
-    \[ (g_1, \dots, g_n) \cdot f: C((c_{1,1}, \dots, c_{n, m_n}), e) \]
-  \end{itemize}
-  such that these satisfy certain identity and associativity axioms (see for example \cite{higher-operads}, page 35).
-\end{definition}
-
-Let $ S_n $ be the symmetric group on $ n $ elements (the group consisting of all ways to shuffle the numbers $ (1, \dots, n) $).
-
-\begin{definition}[symmetric multicategory]
-  A \textit{symmetric} multicategory is a multicategory $ C $, together with, for each $ \sigma: S_n $ and all $ c_1, \dots, c_n, d $, a bijection
-  \[ \overline \sigma: C((c_1, \dots, c_n), d) \to C((c_{\sigma(1)}, \dots, c_{\sigma(n)}), d), \]
-  such that for all $ \rho, \sigma: S_n $ and $ \theta: C((c_1, \dots, c_n), d) $,
-  \[ \overline \rho(\overline \sigma(\theta)) = \overline{(\sigma \rho)}(\theta) \quad \text{and} \quad \overline {1_{S_n}}(\theta) = \theta, \]
-  compatible with multimorphism composition (see \cite{higher-operads}, page 52, equation (2:7)).
-\end{definition}
-In some sense, for a symmetric multicategory, the order of the objects in the domain of a multimorphism does not matter.
-
-For a collection $ S $ and a tuple $ x = x_1, \dots, x_n: S $ and $ 1 \leq i \leq j \leq n $,
-\begin{itemize}
-  \item let $ u_i(x): S^{n+i+1-j} $ denote the tuple $ x $, but with the subtuple $ (x_i, \dots, x_j) $ repeated once:
-    \[ (x_1, \dots, x_i, \dots, x_j, x_i, \dots, x_j, \dots, x_n). \]
-  \item let $ v_i(x): S^{n-i-1+j} $ denote the tuple $ x $, but with the subtuple $ (x_i, \dots, x_j) $ removed:
-    \[ (x_1, \dots, x_{i-1}, x_{j+1}, \dots, x_n). \]
-\end{itemize}
-
-\begin{definition}[cartesian multicategory]
-  A \textit{cartesian multicategory} is a multicategory $ C $, with, for all $ c_1, \dots, c_n, d: C_0 $ and $ 1 \leq i \leq n $
-  \begin{itemize}
-    \item a \textit{contraction} operation $ \overline{u_i}: C(u_{i, i}(c), d) \to C(c, d) $,
-    \item a \textit{deletion} operation $ \overline {v_i}: C(v_{i, i}(c), d) \to C(c, d) $,
-  \end{itemize}
-  that satisfy some axioms \TODO
-\end{definition}
-
-\begin{definition}[cartesian operad]
-  A \textit{cartesian operad} is a cartesian multicategory with one object.
+\begin{definition}
+  A \iindex{Lawvere theory}, or \textit{one-sorted algebraic theory} is a category $ L $, with $ L_0 = \{ 0, 1, \dots \} $, such that $ n = 1^n $, the $ n $-fold product.
 \end{definition}
@@
 \begin{lemma}
-  The following are equivalent:
-  \begin{enumerate}[(1)]
-    \item An abstract clone.
-    \item A Lawvere theory.
-    \item A relative monad on the embedding $ \iota: \FinSET \hookrightarrow \SET $.
-    \item A cartesian operad.
-  \end{enumerate}
+  There is an equivalence between abstract clones and Lawvere theories.
 \end{lemma}
 \begin{proof}
-  $ (1) \Rightarrow (2) $: Given an abstract clone $ C $, we construct a Lawvere theory $ L $ as follows: We have objects $ L_0 = \{ 0, 1, \dots \} $ and morphisms $ L(m, n) = C_m^n $.
+  Let $ C $ be an abstract clone.
+We construct a Lawvere theory $ L $ as follows: We have objects $ L_0 = \{ 0, 1, \dots \} $ and morphisms $ L(m, n) = C_m^n $.
 The identity morphism is $ \id n = (x_i)_i : L(n, n) $ and for $ f: L(l, m) $, $ g: L(m, n) $, we have composition
@@
 
-  $ (2) \Rightarrow (3) $: Given a Lawvere theory $ L $, we construct a relative monad $ (F, \eta) $ as follows: For $ n: \FinSET $, take $ F(n) = L(n, 1) $ and for $ a: \FinSET(m, n) $, let $ F(a): \SET(F(m), F(n)) $ be the morphism given by precomposition with the product morphism
-  \[ \langle \pi_{n, a(1)}, \dots, \pi_{n, a(m)} \rangle : L(n, m). \]
-  The natural transformation is given by $ \eta_n(i) = \pi_{n, i}: F(n) $ for all $ i: \iota(n) = \{1, \dots, n\} $.
-Lastly, for $ f: \SET(\iota(m), F(n)) $, let $ f : \SET(F(m), F(n)) $ be given by precomposition with the product morphism
-  \[ \langle f(1), \dots, f(m) \rangle : L(n, m) \]
+  Conversely, if $ L $ is a Lawvere theory, we construct an abstract clone $ C $ as follows:
+  We take $ C_n = L(n, 1) $.
+We take the $ x_{n, i} $ to be the product projections $ \pi_i : L(n, 1) $ and we define the substitution $ f \bullet g = \langle g_i \rangle_i \cdot f $ the composite of the product morphism $ \langle g_i \rangle_i $ with $ f $.
+\end{proof}
 
-  $ (3) \Rightarrow (4) $: Given a relative monad $ (F, \eta) $, we construct a cartesian operad $ A $ as follows: We take a multicategory with $ A_0: \{ \star \} $.
-We take as the set of $ n $-fold morphisms $ A((\star)_i, \star) = F(n) $.
-We take an identity multimorphism $ \id \star = \eta_1(1) : A(\star, star) $.
-  For some natural number $ m $, natural numbers $ n_1, \dots, n_m $ and $ i: 1 \leq i \leq m $ let $ \phi_i: \FinSET(n_i, \sum n_i) $ be the standard injections into the coproduct.
-For $ f: F(m) $ and $ g_i: F(n_i) $, we have $ F(\varphi_i): \SET(F(n_i), F(\sum n_i)) $, so we have $ (F(\varphi_i)(g_i))_i: \SET(\iota(m), F(\sum n_i)) $ and the composition is given by
-  \[ f \cdot g = (F(\varphi_i)(g_i))_i^*(f): F\left(\sum n_i\right). \]
+\subsection{Algebras for Lawvere Theories}
 
-  The permutation, contraction and deletion operations given by
+\begin{lemma}
+  Let $ C $ be an abstract clone, and $ L $ be its associated Lawvere theory by the equivalence given above. A $ C $-algebra is equivalent to an algebra for $ L $.
+\end{lemma}
+\begin{proof}
+  Let $ A $ be a $ C $-algebra. We will construct a functor $ F: L \to \SET $ as follows: We take $ F(n) = A^n $. We define the action on morphisms as
+  \[ F(f)(a) = (f_i \bullet a)_i \]
+  for $ f: L(m, n) = L(m, 1)^n $ and $ a: A^m $.
+
+  Conversely, let $ F: L \to \SET $ be a functor. We take the $ C $-algebra $ A $, with $ A = F(1) $ and for $ f: C_n = L(n, 1) $ and $ a: A^n $, $ f \bullet a = F(f)(a) $.
+\end{proof}
+
+\section{Cartesian Operad}
+
+\begin{definition}
+  A \iindex{cartesian operad} T is a functor $ T: F \to \SET $, together with an `identity' element $ \id{}: T(1) $ and for all $ m, n_1, \dots, n_m: \mathbb N $, a composition map
+  \[ T(m) \times \prod_i T(n_i) \to T\left(\sum_i n_i\right), \]
+  written $ (f, g_1, \dots, g_m) \mapsto f[g_1, \dots, g_m] $, satisfying some identity, associativity and naturality conditions (see \cite{lambda-monoid}, Definition 2.1, for more details).
+\end{definition}
+
+\begin{remark}
+  One can arrive at this concept as a standalone definition, or one can view a cartesian operad as a \iindex{cartesian multicategory} with one element.
+A multicategory is a category in which morphisms have type $ C((X_1, X_2, \dots, X_n), Y) $ instead of $ C(X, Y) $.
+A cartesian multicategory is a multicategory in which one can permute the $ X_i $ of a morphism and has `contraction' and `weakening' operations:
   \begin{align*}
-    \overline{\sigma} = F(\sigma): A((\star_1, \dots, \star_n), \star) \to A((\star_{\sigma(1)}, \dots, \star_{\sigma(n)}), \star)
+    C((X_1, \dots, X_i, X_i, \dots, X_n), Y) &\to C((X_1, \dots, X_i, \dots, X_n), Y),\\
+    C((X_1, \dots, X_{i - 1}, X_{i + 1}, \dots, X_n), Y) &\to C((X_1, \dots, X_{i - 1}, X_i, X_{i + 1}, \dots, X_n), Y).
   \end{align*}
+\end{remark}
 
-  Given a cartesian operad $ A $
-  \TODO
+\begin{lemma}
+  There is an equivalence between abstract clones and cartesian operads.
+\end{lemma}
+\begin{proof}
+  Let $ C $ be an abstract clone.
+We define a cartesian operad $ T $ with $ T(n) = C_n $ and $ T(f)(t) = t \bullet (x_{f(1)}, \dots, x_{f(m)}) $ for $ f: \llbracket m \rrbracket \to \llbracket n \rrbracket $ and $ t: C_m $.
+The identity element is $ x_{1, 1} $ and the composition $ f[g_1, \dots, g_n] $, for $ f: C_m $ and $ g_i: C_{n_i} $, is given by lifting all terms to $ C_{\sum_i n_i} $ and then substituting:
+  \[ f[g_1, \dots, g_n] = f \bullet (T(\iota_i)(g_i)) \]
+  for $ \iota_i : \llbracket n_i \rrbracket \hookrightarrow \llbracket \sum_i n_i \rrbracket $ the pairwise disjoint injections.
+
+  Conversely, given a cartesian operad $ T $, we construct an abstract clone $ C $ with $ C_n = T(\llbracket n \rrbracket) $.
+The variables are $ x_{n, i} = \iota_{n, i}(\id{}) $, for $ \iota_{n, i}: \llbracket 1 \rrbracket \hookrightarrow \llbracket n \rrbracket $ the morphism that sends $ 1 $ to $ i $.
+The substitution $ f \bullet (g_i)_i $ for $ g_1, \dots, g_m: T(n) $ is given by composing and then identifying some variables:
+  \[ f \bullet (g_i)_i = T(\pi)(f[g_1, \dots, g_m]) \]
+  for $ \pi: \llbracket m n \rrbracket \to \llbracket n \rrbracket $ the function that sends $ i + 1 $ to $ (i \mod n) + 1 $.
 \end{proof}
+
+\section{Relative Monad}
+\begin{definition}
+  Let $ S: C \to D $ be a functor.
+A \iindex{relative monad} on $ S $ is a functor $ T: C \to D $, together with a natural transformation $ \eta: S \Rightarrow T $ and a `kleisli extension' $ (-)^*: D(S(X), T(Y)) \to D(T(X), T(Y)) $, natural in both $ S $ and $ T $, such that for all $ f: D(S(X), T(Y)) $ and $ g: D(S(Y), T(Z)) $,
+  \[ \eta_X^* = \id{T X}, \qquad f = \eta_X \cdot f^* \qquad \text{and} \qquad (f \cdot g^*)^* = f^* \cdot g^*. \]
+\end{definition}
+
+\begin{remark}
+  Note that for an adjunction $ F \dashv G $, $ F \bullet G $ gives a monad.
+In the same way, there exists a notion of \iindex{relative adjunction}, from which we can obtain a relative monad (see \cite{monads-endofunctors}, Theorem 2.10).
+\end{remark}
+
+\begin{remark}
+  Now, there is a result that states: There is an equivalence between abstract clones and relative monads on the embedding $ \iota: \FinSET \hookrightarrow \SET $.
+
+  Note that the objects of $ \FinSET $ are defined to be sets $ X $, together with a proof that there exists some $ n: \mathbb N $ and some bijection $ f: X \xrightarrow{\sim} \llbracket n \rrbracket $.
+This existence of $ n $ and $ f $ is given by the propositional truncation $ \left\Vert \sum_{n: \mathbb N}, X \xrightarrow{\sim} \llbracket n \rrbracket \right\Vert $.
+
+  Classically, this construction starts with ``fix, for all $ X : \FinSET $, a bijection $ f: X \xrightarrow{\sim} \llbracket n \rrbracket $''.
+However, since $ X $ only provides \textit{mere existence} of such a bijection without choosing one (by the propositional truncation), there is no way to obtain $ f $ without using the axiom of choice.
+
+  Now, we can partially circumvent this problem by noting that we have a fully faithful and essentially surjective embedding $ F \to \FinSET $ (for $ F $ a skeleton of finite sets), which induces an adjoint equivalence $ [F, \SET] \xrightarrow{\sim} [\FinSET, \SET] $, so we can lift the functor part of a relative monad on $ F \to \SET $ to $ \FinSET \to \SET $.
+We can also lift the natural transformation using this equivalence.
+However, the kleisli extension cannot be lifted using this and we are stuck.
+
+  Therefore, we will prove a modified statement:
+\end{remark}
+
+\begin{lemma}
+  There is an equivalence between abstract clones and relative monads on the embedding $ \iota: F \hookrightarrow \SET $.
+\end{lemma}
+\begin{proof}
+  Let $ C $ be an abstract clone.
+We define a relative monad $ T $ as follows: We take $ T(\llbracket n \rrbracket) = C_n $.
+For a morphism $ a: F(\llbracket m \rrbracket, \llbracket n \rrbracket) $.
+We take $ T(a)(f) = f \bullet (x_{a(i)})_i $.
+We define $ \eta_{\llbracket n \rrbracket}(i) = x_{n, i} $.
+Finally, for $ g: \SET(\llbracket m \rrbracket, T(\llbracket n \rrbracket)) $, we define $ g^*(f) = f \bullet g $.
+
+  Conversely, let $ (T, \eta, (\cdot)^*) $ be a relative monad on the embedding $ \iota: F \hookrightarrow \SET $.
+We define an abstract clone $ C $ with $ C_n = T(\llbracket n \rrbracket) $.
+Substitution is defined as $ f \bullet g = g^*(f) $ for $ f: C_m $ and $ g: C_n^m $ and we have variables $ x_{n, i} = \eta_{\llbracket n \rrbracket}(i) $.
+\end{proof}
+
+\section{Monoid in a skew-monoidal category}
+For details and a general treatment, see \cite{monads-endofunctors}, Section 3 and specifically Theorem 3.4.
+
+\begin{definition}
+  Consider the category $ [F, \SET] $.
+Note that we have a functor $ \iota: F \hookrightarrow \SET $ and that $ \SET $ has colimits.
+Therefore, we can define a `tensor product' on functors $ [F, \SET] $ as
+  \[ F \otimes G = G \bullet \Lan{\iota}{F}. \]
+  Together with the `unit' $ \iota $, this gives $ [F, \SET] $ a `skew-monoidal category' structure.
+\end{definition}
+
+\begin{definition}
+  Given a (skew-)monoidal category $ (C, \otimes, I) $, a \iindex{monoid} in this category is an object $ T : C $, together with a `multiplication' $ \mu: C(T \otimes T, T) $ and a `unit' morphism $ \eta: C(I, T) $ satisfying a couple of laws (see \cite{MacLane}, Section III.6).
+\end{definition}
+
+\begin{lemma}
+  There exists an equivalence between relative monads on $ \iota: F \hookrightarrow \SET $ and monoids in the skew-monoidal category $ [F, \SET] $.
+\end{lemma}
+\begin{proof}
+  A monoid in $ [F, \SET] $ consists of an object $ T: [F, \SET] $, together with natural transformations $ \mu: T \otimes T \Rightarrow T $ and $ \eta: \iota \Longrightarrow T $.
+We can immediately see the functor $ T $ and natural transformation $ \eta $ of the relative monad pop up here.
+The kleisli extension corresponds to $ \mu $; they are related to each other via the properties of the left Kan extension of $ T $.
+\end{proof}

### 2024-02-13 report/chapters/algebraic-structures.tex
Write a bit about the proof of the fundamental theorem, add some category theory

@@
 
+Together, these form the category of algebraic theories \iindex{$ \AlgTh $}.
+
 \begin{remark}
@@
 \end{definition}
+
+Together, these form the category of $ T $-algebras \iindex{$ \Alg T $}.
 
@@
 
-We will write $ \Pshf T $ for the category of $ T $-presheaves and their morphisms.
+Together, these form the category of $ T $-presheaves \iindex{$ \Pshf T $}.
 
@@
 
+Together, these form the category of $ \lambda $-theories \iindex{$ \LamTh $}.
+
 \begin{definition}[$ \beta $- and $ \eta $-equality]
@@
 
-A $ \lambda $-theory algebra or presheaf is a presheaf for the underlying algebraic theory.
+\begin{definition}
+  A $ \lambda $-theory algebra or presheaf is an algebra or presheaf for the underlying algebraic theory.
+\end{definition}
 
@@
     f(\mathtt{Var}(i)) &= x_i;\\
-    f(\mathtt{App}(a, b)) &= \rho(f(a)) \bullet ((x_{n, i})_i + (b));\\
+    f(\mathtt{App}(a, b)) &= \rho(f(a)) \bullet ((x_{n, i})_i + (f(b)));\\
     f(\mathtt{Abs}(a)) &= \lambda(f(a));\\
@@
 We have, like with the free algebraic theory, that $ \Lambda(\emptyset) $ is the initial $ \lambda $-theory.
+\end{proof}
+
+\subsubsection{About $ \Lambda $-algebra morphisms}
+
+\begin{lemma}\label{lem:make-is-lambda-algebra-morphism}
+  Let $ A $ and $ B $ be $ \Lambda $-algebras and let $ f: \SET(A, B) $ be a function that preserves the application and the $ \Lambda $-definable constants:
+  \[ f((x_1 x_2) \bullet (a, b)) = (x_1 x_2) \bullet (f(a), f(b)) \quad \text{and} \quad f(s \bullet ()) = s \bullet () \]
+  for all $ a, b: A $ and $ s: \Lambda_0 $. Then $ f $ is a $ \Lambda $-algebra morphism.
+\end{lemma}
+\begin{proof}
+  Note that for $ s: \Lambda_{n + 1} $ and $ a: A^{n + 1} $,
+  \[ (x_1 x_2) \bullet (\lambda(s) \bullet (a_i)_i, a_{n + 1}) = s \bullet a. \]
+  By induction, we can express $ s \bullet a $ using a combination of $ (x_1 x_2) \bullet (\cdot, \cdot) $ and $ \lambda^n(s) $:
+  \begin{align*}
+    f(s \bullet a) &= f((x_1 x_2) \bullet (\dots ((x_1 x_2) \bullet (\lambda^n(s) \bullet (), a_1), \dots), a_n))\\
+    &= (x_1 x_2) \bullet (\dots ((x_1 x_2) \bullet (f(\lambda^n(s) \bullet ()), f(a_1)), \dots), f(a_n))\\
+    &= s \bullet (f(a_i))_i,
+  \end{align*}
+  so $ f $ is a $ \Lambda $-algebra morphism.
 \end{proof}

### 2024-02-13 report/chapters/category-theory.tex
Write a bit about the proof of the fundamental theorem, add some category theory

@@
 \section{Universal Arrows}
-(\cite{MacLane}, Chapter IV.1, Theorem 2 (iv))
-\TODO
+
+One concept in category theory that can be used to describe a lot of limits and adjunctions is that of a universal arrow (see for example \cite{MacLane}, Part III)
+\begin{definition}
+  A \iindex{universal arrow} from an object $ c: C $ to a functor $ F: D \to C $ consists of an object $ d: D $ and a morphism $ f: D(c, F(d)) $ such that for every similar pair $ (d^\prime, f^\prime) $, $ f^\prime $ factors uniquely as $ f \cdot F(g) $ for some $ g: C(d, d^\prime) $:
+  \begin{center}
+    \begin{tikzcd}
+      c \arrow[d, "f"'] \arrow[rd, "f^\prime"] &\\
+      F(d) \arrow[r, "F(g)"'] & F(d^\prime)
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+There is also the dual concept of a universal arrow $ (d, f) $ from a functor $ F $ to an object $ c: C $. Its universal property yields the following diagram:
+\begin{center}
+  \begin{tikzcd}
+    F(d^\prime)\arrow[rd, "f^\prime"']  \arrow[r, "F(g)"] & F(d) \arrow[d, "f"]\\
+    & c
+  \end{tikzcd}
+\end{center}
 
@@
 
-An alternative characterization of an adjunction $ L \dashv R $ is as a natural bijection
+An alternative characterization (see \cite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
 \[ \varphi: D(L(c), d) \xrightarrow{\sim} C(c, R(d)). \]
@@
 \[ \varphi(L(f) \cdot h \cdot g) = f \cdot \varphi(h) \cdot R(g). \]
+
+Lastly, one can construct an adjunction using universal arrows. This lends itself particularly well for a formalization, where it is often preferable to have as little `demonstranda' as possible:
+\begin{lemma}
+  One can construct an adjunction $ (F, G, \eta, \epsilon) $ as above from only the functor $ L: C \to D $ and, for each $ c: C $, a universal arrow $ (R(c), \epsilon_c) $ from $ L $ to $ c $.
+\end{lemma}
+\begin{proof}
+  See \cite{MacLane}, Chapter IV.1, Theorem 2 (iv).
+\end{proof}
 
@@
 
-\begin{lemma}
-  For $ c, d, d^c : C $, we have a natural bijection
-  \[ C(d^\prime \times c, d) \cong C(d^\prime, d^c) \]
-  iff we have a universal arrow ...
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
 \begin{remark}
@@
 \end{remark}
+
+\section{Fibrations}
+Let $ P : E \to B $ be a functor. In this case, we will view this as the category $ E $ `lying over' the category $ B $, with for every point $ b: B $, a slice $ E_b = P^{-1}(B) $ lying `above' $ b $.
+
+\begin{definition}
+  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ w: B(P(x), P(y)) $ with $ w \cdot P(f) = P(g) $, there exists $ \bar w: E(x, y) $ such that $ P(\bar w) = w $ and $ \bar w \cdot f = g $, like illustrated in the following diagram from \cite{nlab:grothendieck_fibration}
+  \begin{center}
+    \begin{tikzcd}[row sep = .5in]
+      E \arrow[d, "P"] &x \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar w"'] & y \arrow[r, "f"'] & z\\
+      B & P(x) \arrow[r, "\forall w"'] \arrow[rr, "P(g)", bend left] & P(y) \arrow[r, "P(f)"'] & P(z)
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+\begin{definition}
+  $ P $ is a \iindex{fibration} if for all $ y: E $ and morphisms $ f: B(x, P(y)) $, there exists a cartesian morphism $ \bar f: E(\bar x, y) $ such that $ P(\bar f) = f $.
+\end{definition}
 
@@
 
-These, together with the identity and composition from $ \SET $, constitute a category $ \RAct M $ of right $ M $-actions.
+These, together with the identity and composition from $ \SET $, constitute a category \iindex{$ \RAct M $} of right $ M $-actions.
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:global-action-elements}
   The global elements of a set with right $ M $-action correspond to the elements that are invariant under the $ M $-action.

### 2024-02-13 report/chapters/paper.tex
Write a bit about the proof of the fundamental theorem, add some category theory

@@
 \begin{lemma}
-  We have $ A_1^{A_1} \cong A_2 $ in $ \RAct{A_1} $.
+  We have $ U_{A_1}^{U_{A_1}} \cong A_2 $ in $ \RAct{A_1} $.
 \end{lemma}
 \begin{proof}
-  Recall that $ A_1^{A_1} $ consists of the set of $ A_1 $-equivariant morphisms $ A_1 \times A_1 \to A_1 $.
+  Recall that $ U_{A_1}^{U_{A_1}} $ consists of the set of $ A_1 $-equivariant morphisms $ U_{A_1} \times U_{A_1} \to U_{A_1} $.
 
-  We have a bijection $ \varphi: A_2 \xrightarrow{\sim} A_1^{A_1} $, given by
+  We have a bijection $ \varphi: A_2 \xrightarrow{\sim} U_{A_1}^{U_{A_1}} $, given by
   \[ \varphi(a)(b, b^\prime) = (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a, b, b^\prime), \]
@@
   \[ \varphi^{-1}(f) = \lambda x_1 x_2, f(p_1, p_2)(\lambda x_3, x_3 x_1 x_2) \]
+  \TODO: Make more explicitly that we use $ \bullet $ here.
   for $ p_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $. Note that for terms $ c_1, c_2 $, we have $ p_i (\lambda x_1, x_1 c_1 c_2) = c_i $.
 
-  This is an inverse, because given $ f: A_1^{A_1} $ and $ (a_1, a_2): A_1 \times A_1 $, we have
+  This is an inverse, because given $ f: U_{A_1}^{U_{A_1}} $ and $ (a_1, a_2): U_{A_1} \times U_{A_1} $, we have
   \[ \varphi(\psi(f))(a_1, a_2) = f(p_1, p_2) \circ q = f(p_1 \circ q, p_2 \circ q) = f(a_1, a_2) \]
@@
 \begin{definition}[Construction of the $ \lambda $-theory]
-  Since $ \RAct{A_1} $ has products, the algebraic theory $ E(A_1) $ exists.
+  Since $ \RAct{A_1} $ has products, the algebraic theory $ E(U_{A_1}) $ exists.
 
   Recall that $ A_2 \subseteq A_1 $ and that $ a \mapsto \mathbf 1_2 \circ a $ gives a function from $ A_1 $ to $ A_2 $, which is, by definition, the identity on $ A_2 $.
-This gives $ E(A_1) $ a $ \lambda $-theory structure with $ \beta $-equality.
+This gives $ E(U_{A_1}) $ a $ \lambda $-theory structure with $ \beta $-equality.
 \end{definition}
@@
   (\TODO: relate to product)
-  Take $ a = \lambda x_1 x_2, x_2 (a_1 x_1) (a_2 x_1) $ and $ \pi_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{n + 1}) $. We have $ a_i = f(\pi_i) \circ a $.
 
-  Need to show that exists $ (\overline m^\prime, \overline m_1, \overline m_2) : A^\prime_1 \times A_1 \times A_1 $ with $ a_i = f(\overline m_i) \circ \overline m^\prime $ such that for all $ (m^\prime, m_1, m_2) $, there exists $ m : A_1 $ such that $ f(m) = m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \circ m $.
+  Take $ a = \lambda x_1 x_2, x_2 (a_1 x_1) (a_2 x_1) $ and $ \pi_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $.
+We have $ a_i = f(\pi_i) \circ a $.
+Now, for some $ a^\prime: A^\prime_1 $, $ \pi_1^\prime, \pi_2^\prime: A_1 $ such that $ a_i = f(\pi_i^\prime) \circ a^\prime $, take $ m = \lambda x_1 x_2, x_2 (\pi_1^\prime x_1) (\pi_2^\prime x_1) $.
+Then $ \pi_i \circ m = \pi_i^\prime $ and $ f(m) \circ a^\prime = a $, so $ (a, \pi_1, \pi_2) $ is weakly terminal and $ f^* $ preserves binary products.
 
-  \TODO
+  Since any finite product is (isomorphic to) a construction with a repeated binary product and the terminal object, the fact that $ f^* $ preserves binary products and the terminal object shows that $ f^* $ preserves all finite products.
 \end{proof}
@@
   Since $ f^* $ preserves finite products, given an element of $ g: E(U_{A_1})_n = \RAct{A}(U_{A_1}^n, U_{A_1}) $, we get
-  \[ \# f^*(g): \RAct{A^\prime}(f(A_1^n), f(A_1)) \cong \RAct{A^\prime}((A^\prime_1)^n, A^\prime_1) = E(A^\prime_1)_n. \]
+  \[ f^*(g): \RAct{A^\prime}(f(U_{A_1}^n), f(U_{A_1})) \cong \RAct{A^\prime}((U_{A^\prime_1})^n, U_{A^\prime_1}) = E(U_{A^\prime_1})_n \]
+  so we have a morphism $ f^*: \LamTh(E(U_{A_1}), E(U_{A^\prime_1})) $.
 \end{definition}
 
+\begin{remark}
+  The fact that $ f^* $ preserves the variables and substitution is not very hard, since these are just defined in terms of finite products $ U_{A_1} $ and $ f^* $ preserves finite products and $ U_{A_1} $.
+
+  However, showing that it is a $ \lambda $-theory morphism is really hard. Hyland claims
+  \begin{quote}
+    $ f $ preserves $ \mathbf 1_n $, which determines the function space as a retract of the universal. So $ f^* $ preserves the retract and the result follows.
+  \end{quote}
+  This indeed covers the core of the argument, but actually verifying that it works is much more complicated: We a natural equivalence and isomorphisms
+  \begin{align*}
+    \alpha_A: \RAct{A_1}(X \times Y, Z) &\xrightarrow{\sim} \RAct{A}(X, Z^Y);\\
+    \beta: f^*(U_{A_1}) &\xrightarrow{\sim} U_{A_1^\prime};\\
+    \bar \gamma: f^*(A \times B) &\xrightarrow{\sim} f^*(A) \times f^*(B);\\
+    \gamma_n: f^*(X^n) &\xrightarrow{\sim} f^*(X)^n;\\
+    % \delta: f^*(X^Y) &\xrightarrow{\sim} f^*(X)^{f^*(Y)};\\
+    \delta_A: U_{A_1}^{U_{A_1}} &\xrightarrow{\sim} A_2.
+  \end{align*}
+  with $ \gamma_{n + 1} = \bar{\gamma} \cdot (\gamma_n \times \id X) $.
+  Then, for $ s: E(U_{A_1})_{n + 1} $, we have $ \lambda_A(s) = \alpha_A(s) \cdot \delta_A \cdot \pi_A : \RAct{A_1}(U_{A_1}^n, U_{A_1}) $ for the projection $ \pi_A: A_2 \to U_{A_1} $.
+However, note that $ f^*(\lambda_A(s)): \RAct{A^\prime_1}(f^*(U_{A^\prime_1}^n), f^*(U_{A^\prime_1})) $.
+To compare this to $ \lambda_{A^\prime}(\dots) $, we actually need to take
+  \[ (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\lambda_A(s)) \cdot \beta : \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
+  On the other hand, we also have $ f^*(s): \RAct{A^\prime_1}(f^*(U_{A_1}^{n + 1}), f^*(U_{A_1})) $ and we cannot apply $ \lambda_{A^\prime} $ directly. Instead, the term that we end up with is
+  \[ \lambda_{A^\prime}((\beta^{-1})^{n + 1} \cdot \gamma_{n + 1}^{-1} \cdot f^*(s) \cdot \beta): \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
+  So the equality that we need to prove is (using functoriality of $ f^* $ and naturality of $ \alpha_{A^\prime} $):
+  \begin{align*}
+    &(\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\alpha_A(s)) \cdot f^*(\delta_A \cdot \pi_A) \cdot \beta\\
+    &= (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot \alpha_{A^\prime}((\id X^n \times \beta^{-1}) \cdot \bar{\gamma}^{-1} \cdot f^*(s)) \cdot \beta^{U_{A_1}} \cdot \delta_{A^\prime} \cdot \pi_{A^\prime}.
+  \end{align*}
+  Because of the complicated definition of each of these terms, I was unable to verify the correctness of this statement (and the similar statement about $ \rho: E(U_{A_1})_n \to E(U_{A_1})_{n + 1} $) within a day, even though I am willing to believe Hyland's claim.
+  \TODO
+
+  % Given a morphism $ t: X \times Y \to Z $, $ \alpha_{A_1}(t): X \to (U_{A_1} \times Y \to Z) $ is given by
+  % \[ \alpha(t)(x)(a, y) = t(x a, y) \]
+
+  % Also, $ \beta: f^*(U_{A_1}) \xrightarrow{\sim} U_{A^\prime_1} $ is given, for $ a: A_1 $ and $ a^\prime : A^\prime_1 $, by
+  % \[ \beta(a, a^\prime) = f(a) a^\prime \quad \text{and} \quad \beta^{-1}(a^\prime) = (1, a^\prime). \]
+
+  % Given a morphism $ s: X \to Y $, we have $ f^*(s): f^*(X) \to f^*(Y) $ given by
+  % \[ f^*(s)(x, a^\prime) = (s(x), a^\prime). \]
+
+  % Finally, we have
+  % \[ \delta(s) = \lambda x_1 x_2, s(p_1, p_2)(\lambda x_3, x_3 x_1 x_2) \]
+  % with $ p_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $.
+
+  % For some $ s: U_{A_1}^{n + 1} \to U_{A_1} $, the left hand side sends $ (a, (a^\prime_1, \dots, a^\prime_n)): f^*(U_{A_1}^n) $ to
+  % \begin{align*}
+  %   &\lambda x_1 x_2, f(s((a_i p_1)_i, p_2)) (\lambda x_3, x_3 x_1 x_2) \circ a^\prime\\
+  %   &= \lambda x_1 x_2, f(s((a_i p_1)_i, p_2)) (\lambda x_3, x_3 a^\prime (x_1) x_2)
+  % \end{align*}
+  % and the right hand side sends it to
+  % \begin{align*}
+  %   \lambda x_1 x_2, \lambda x_3, (f(s((a_i p_1)_i, p_2))((\lambda x_4, x_4 (a^\prime p_1 (\lambda x_3, x_3 x_1 x_2)) (p_2 (\lambda x_3, x_3 x_1 x_2)))(x_3)))
+  % \end{align*}
+\end{remark}
+
 \begin{lemma}
-  $ \# f^*: E(U_{A_1}) \to E(U_{A^\prime_1}) $ is a map of $ \lambda $-theories.
+  We have a bijection $ \varphi: E(U_{A_1})_0 \cong A $, sending $ s $ to $ x_1 (\lambda x_2, x_2) \bullet (s(\star)) $.
 \end{lemma}
 \begin{proof}
-  \TODO
+  Using \ref{lem:global-action-elements}, we showed that $ E(U_{A_1})_0 $ corresponds to the set of $ A_1 $-equivariant elements of $ U_{A_1} $, sending $ s $ to $ s(\star) $.
+Now, for an $ A_1 $-equivariant element $ a $,
+  \[ (\lambda x_2, x_1 (\lambda x_3, x_3)) \bullet a = a \circ ((\lambda x_1 x_2, x_2) \bullet ()) = a \]
+  so we can send $ a $ to $ A $ as $ (x_1 (\lambda x_2, x_2)) \bullet a $ and it has (two-sided) inverse $ (\lambda x_2, x_1) \bullet a $.
 \end{proof}
 
-\begin{definition}
-  We have an isomorphism $ E(U_{A_1})_0 \cong A $ given by $ a \mapsto a I $.
-\end{definition}
+We want to show that $ \varphi $ is an isomorphism of $ \Lambda $-algebras.
+We use Lemma \ref{lem:make-is-lambda-algebra-morphism} for this, so we need to show that it preserves the application and the $ \Lambda $-definable constants.
 
 \begin{lemma}
-  This is indeed an isomorphism of $ \Lambda $-algebras.
+  For $ \varphi $ as above, we have for all $ a, b: E(U_{A_1})_0 $, we have
+  \[ \varphi((x_1 x_2) \bullet (a, b)) = (x_1 x_2) \bullet (\varphi(a), \varphi(b)). \]
+\end{lemma}
+\begin{proof}
+  For $ a, b: E(U_{A_1})_0 $, we have, for the isomorphism $ \delta: \RAct{A_1}(U_{A_1}^{U_{A_1}}, A_2) $,
+  \begin{align*}
+    \varphi((x_{2, 1} x_{2, 2}) \bullet (a, b)) &= \varphi(\rho(x_{1, 1}) \bullet (a, b))\\
+    &= (x_1 (\lambda x_2, x_2)) \bullet (\langle a, b \rangle \cdot ((s, t) \mapsto (\delta^{-1}(\mathbf 1_2 \circ s)) (1, t)))(\star)\\
+    &= (x_1 (\lambda x_2, x_2)) \bullet (\lambda x_3, x_1 x_3 (x_2 x_3)) \bullet (a(\star), b(\star))\\
+    &= (x_1 (\lambda x_3, x_3) (x_2 (\lambda x_3, x_3))) \bullet (a(\star), b(\star))\\
+    &= (x_1 x_2) \bullet (\varphi(a), \varphi(b))
+  \end{align*}
+  and this concludes the proof.
+\end{proof}
+
+\begin{lemma}
+  For $ \varphi $ as above, we have for all $ s: \Lambda_0 $,
+  \[ \varphi(s \bullet ()) = s \bullet (). \]
 \end{lemma}
@@
 \begin{lemma}
-  Given $ g: A \to A^\prime $,
+  We have an isomorphism $ U_{L_0} \cong L $.
 \end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}
+
+\begin{lemma}
+  This is indeed an isomorphism of $ \lambda $-theories.
+\end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}
 

### 2024-02-14 report/chapters/algebraic-structures.tex
Update the definition of fibration, write about the algebra and presheaf fibrations

@@
 
-\begin{definition}[Pullback of algebras]
+\begin{definition}[Pullback of algebras]\label{def:algebra-pullback}
   If we have a morphism of algebraic theories $ f: T^\prime \to T $, we have a functor $ \Alg T \to \Alg T^\prime $.
@@
 
-\begin{lemma}
-  \TODO Fibration
+We can also consider the category of `all' algebraic theory algebras together.
+That is, the category $ C $ with $ C_0 = \sum_{T : \AlgTh}, \Alg T $ and $ C((T, A), (T^\prime, A^\prime)) $ consisting of pairs $ (f, f^\prime): \AlgTh(T, T^\prime) \times \SET(A, A^\prime) $ such that for all $ t: T_n $ and $ a: A^n $,
+\[ f^\prime(t \bullet a) = f(t) \bullet (f^\prime(a_i))_i. \]
+We then have a functor $ P: C \to \AlgTh $, projecting onto the first coordinate.
+
+\begin{lemma}\label{lem:algebra-fibration}
+  $ P $ is a fibration.
 \end{lemma}
+\begin{proof}
+  Given an algebraic theory morphism $ f: \AlgTh(S, T) $ and a $ T $-algebra $ A_T $, Definition \ref{def:algebra-pullback} gives an $ S $-algebra $ A_S $ with underlying set $ A_T $.
+The cartesian morphism is $ (f, \id{A_T}): C((S, A_S), (T, A_T)) $.
+
+  It is cartesian because for $ (R, A_R): C $ and $ (g, g^\prime): C((R, A_R), (T, A_T)) $ and $ h: \AlgTh(R, S) $ with $ h \cdot f = g $, the required morphism $ C((R, A_R), (S, A_S)) $ is given by $ g^\prime: \SET(A_R, A_S) $.
+\end{proof}
 
@@
 
-\begin{lemma}
-  \TODO Fibration
-\end{lemma}
+An analogue to Lemma \ref{lem:algebra-fibration} shows that, like with algebras, the total category of presheaves is fibered over the category of algebraic theories.
 
@@
 \begin{lemma}
-  There is an adjoint equivalence between the category $ \Alg{F(S)} $ and the coslice category (\TODO) $ S \downarrow \SET $.
+  There is an adjoint equivalence between the category $ \Alg{F(S)} $ and the coslice category $ S \downarrow \SET $.
 \end{lemma}

### 2024-02-14 report/chapters/category-theory.tex
Update the definition of fibration, write about the algebra and presheaf fibrations

@@
       c \arrow[d, "f"'] \arrow[rd, "f^\prime"] &\\
-      F(d) \arrow[r, "F(g)"'] & F(d^\prime)
+      F(d) \arrow[r, "F(g)"', dashed] & F(d^\prime)
     \end{tikzcd}
@@
   \begin{tikzcd}
-    F(d^\prime)\arrow[rd, "f^\prime"']  \arrow[r, "F(g)"] & F(d) \arrow[d, "f"]\\
+    F(d^\prime)\arrow[rd, "f^\prime"']  \arrow[r, "F(g)", dashed] & F(d) \arrow[d, "f"]\\
     & c
@@
 \begin{definition}
-  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ w: B(P(x), P(y)) $ with $ w \cdot P(f) = P(g) $, there exists $ \bar w: E(x, y) $ such that $ P(\bar w) = w $ and $ \bar w \cdot f = g $, like illustrated in the following diagram from \cite{nlab:grothendieck_fibration}
+  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ h: B(P(x), P(y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(x, y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \cite{nlab:grothendieck_fibration}
   \begin{center}
     \begin{tikzcd}[row sep = .5in]
-      E \arrow[d, "P"] &x \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar w"'] & y \arrow[r, "f"'] & z\\
-      B & P(x) \arrow[r, "\forall w"'] \arrow[rr, "P(g)", bend left] & P(y) \arrow[r, "P(f)"'] & P(z)
+      E \arrow[d, "P"] &x \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar h"', dashed] & y \arrow[r, "f"'] & z\\
+      B & P(x) \arrow[r, "\forall h"'] \arrow[rr, "P(g)", bend left] & P(y) \arrow[r, "P(f)"'] & P(z)
     \end{tikzcd}
@@
 \begin{definition}
-  $ P $ is a \iindex{fibration} if for all $ y: E $ and morphisms $ f: B(x, P(y)) $, there exists a cartesian morphism $ \bar f: E(\bar x, y) $ such that $ P(\bar f) = f $.
+  $ P $ is a \iindex{fibration} if for all $ y: E $ and morphisms $ f: B(x, P(y)) $, there exist an object $ \bar x: E $ and a cartesian morphism $ \bar f: E(\bar x, y) $ such that $ P(\bar x) = x $ and $ P(\bar f) = f $:
+  \begin{center}
+    \begin{tikzcd}
+      E \arrow[d, "P"] & \bar x \arrow[r, "\exists \bar f", dashed] & y\\
+      B & x \arrow[r, "\forall f"] & P(y)
+    \end{tikzcd}
+  \end{center}
 \end{definition}
@@
 \end{definition}
-The \textit{coslice category}\index{slice category!co-} $ c \downarrow C $ is similar, but with the morphisms from $ c $:
+The \textit{coslice category}\index{slice category!co-} $ c \downarrow C $ is similar, but with the morphisms \textit{from} $ c $ instead of \textit{to} $ c $:
 \[ (c \downarrow C)_0 = \sum_{c^\prime: C} C(c, c^\prime). \]
@@
 \begin{definition}
-  Given an object $ c $ in a category $ C $ with terminal object $ t $. A \iindex{global element} of $ c $ is a morphism $ C(t, c) $.
+  Let $ C $ be a category with terminal object $ t $. For an object $ c: C $, a \iindex{global element} of $ c $ is a morphism $ f: C(t, c) $.
 \end{definition}

### 2024-02-29 report/chapters/algebraic-structures.tex
Write down Scott's representation theorem, and define relatively cartesian closedness

@@
 
-\begin{definition}
+\begin{definition}\label{def:endomorphism-theory}
   Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.

### 2024-02-29 report/chapters/category-theory.tex
Write down Scott's representation theorem, and define relatively cartesian closedness

@@
 \[ (c \downarrow C)_0 = \sum_{c^\prime: C} C(c, c^\prime). \]
+
+\section{Dependent products and sums}\label{sec:dependent-products}
+
+Take a category $ C $ (for example, $ \mathbb R $, $ \SET $ or $ \TYPE $).
+To talk about dependent sums $ \sum_{a: A} X_a $ and products $ \prod_{a: A} X_a $ in $ C $, we first need some way to construct the family of objects $ (X_a)_a $.
+Of course, we can do this \textit{externally} using a set $ A $, and picking an object $ X_a : C $ for every element $ a : A $.
+However, there is also an \textit{internal} representation, as a morphism $ X \to A $.
+
+Note that in $ \SET $, the external and internal ways of indexing are equivalent, because given a family $ (X_a)_a $ we can construct a morphism $ f: \sum_{a : A} X_a \to A $ and conversely, we can recover the family $ (X_a)_a $ as $ (f^{-1}(a))_a $.
+
+In $ \SET $, given a family $ (X_a)_a $ over $ A $ and a morphism $ \alpha: B \to A $, we get a family $ X_{\alpha(b)} $ over $ B $.
+It turns out that in the internal representation this arises as the pullback
+\begin{center}
+  \begin{tikzcd}
+    \sum_{b : B} X_{\alpha(b)} \arrow[r] \arrow[d, "\alpha^* f"] \arrow[dr, phantom, "\lrcorner", very near start] & \sum_{a : A} X_a \arrow[d, "f"]\\
+    B \arrow[r, "\alpha"] & A
+  \end{tikzcd}
+\end{center}
+This can be turned into a pullback or `substitution' functor $ \alpha^* $, which Taylor calls $ \mathtt{P}\alpha $.
+We can construct $ \alpha^* : (C \downarrow A) \to (C \downarrow B) $ for any category $ C $ with pullbacks and any morphism $ \alpha: C(B, A) $.
+
+Now, in $ \SET $, for a family $ (X_a)_a $, consider the dependent product $ \prod_{a : A} X_a $.
+Its elements $ (x_a)_a $ can be identified with morphisms from the terminal set: $ \{ \star \} \to \prod_{a : A} X_a $, sending $ \star $ to $ (x_a)_a $.
+However, they can also be identified with the morphisms $ \varphi: A \to \sum_{a : A} X_a $ that make the following diagram commute, sending $ a $ to $ x_a $:
+\begin{center}
+  \begin{tikzcd}
+    A \arrow[rd, "\id A"] \arrow[rr, " \varphi "] & & \sum_{a : A} X_a \arrow[ld, "f"]\\
+    & A
+  \end{tikzcd}
+\end{center}
+These are morphisms in $ (\SET \downarrow A) $ from $ (A, \id A) $ to $ (\sum_{a : A} X_a, f) $.
+Note that for the terminal morphism $ \alpha: A \to \{ \star \} $, we have $ \id A = \alpha^*(\id{\{\star\}}) $.
+To summarize, we have an equivalence
+\[ (\SET \downarrow A)(\alpha^*(\id{\{\star\}}), f) \simeq (\SET \downarrow {\{\star\}})( \id{\{ \star \}}, \prod_{a : A} X_a). \]
+Now, given a family of families $ ((X_b)_{b : B_a})_{a : A} $, we can wonder whether we can construct the family of dependent products $ (\prod_{b : B_a} X_b)_a $.
+In $ \SET $, this is definitely possible, and from this, we get an equivalence again
+\[ (\SET \downarrow (\sum_{a : A} B_a))(\alpha^*(\id A), f) \simeq (\SET \downarrow A)(\id A, (\prod_{b : B_a} X_b)_a). \]
+These equivalences suggest an adjunction $ \alpha^* \dashv \prod_{\dots} $. We can use this to define in general
+\begin{definition}
+  For a category $ C $ and a morphism $ \alpha: B \to A $, the \iindex{dependent product} along $ \alpha $ is, if it exists, the right adjoint to the pullback functor:
+  \begin{center}
+    \begin{tikzcd}
+      (C \downarrow A) \arrow[r, shift left=2, "\alpha^*"{name=A}] &
+      (C \downarrow B) \arrow[l, shift left=2, "\prod_\alpha"{name=B}]
+      \ar[from=A, to=B, symbol=\dashv]
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+\begin{remark}
+  As argued above, we can recover the familiar dependent product $ \prod_{a : A} X_a $ of a family $ (X_a)_a $ as the dependent product $ \prod_\alpha f $ along the terminal morphism $ \alpha: A \to I $, with $ f: \sum_a X_a \to A $ the internal representation of the family.
+Here we use the equivalence between $ (C \downarrow I) $ and $ C $.
+\end{remark}
+
+Now we turn our attention to dependent sums.
+In $ \SET $, let $ (X_a)_a $ and $ (B_a)_a $ be two families over $ A $ and let $ ((Y_b)_{b : B_a})_{a : A} $ be a family of families.
+Let $ \alpha: \sum_{a : A} B_a \to A $ be the internal representation of $ (B_a)_a $.
+A family of maps $ f_a : (\sum_{b : B_a} Y_b)_a \to X_a $ consists of maps $ Y_b \to X_a $ for all $ b : B_a $, so these are maps $ f_b : Y_b \to X_{\alpha(b)} $.
+This gives an equivalence
+\[ (\SET \downarrow A)((\sum_{b : B_a} Y_b)_a, (X_a)_a) \simeq (\SET \downarrow (\sum_{a : A} B_a))((Y_b)_b, \alpha^*((X_a)_a)). \]
+This, again, suggests an adjunction which we will use as a definition.
+\begin{definition}
+  For a category $ C $ and a morphism $ \alpha: B \to A $, the \iindex{dependent sum} along $ \alpha $ is, if it exists, the left adjoint to the pullback functor:
+  \begin{center}
+    \begin{tikzcd}
+      (C \downarrow A) \arrow[r, shift right=2, "\alpha^*"'{name=B}] &
+      (C \downarrow B) \arrow[l, shift right=2, "\sum_\alpha"'{name=A}]
+      \ar[from=A, to=B, symbol=\dashv]
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+However, note that the conversion from an external to an internal representation in $ \SET $ already contained a dependent sum, which is no coincidence.
+It turns out that in practice, we will never have a hard time obtaining dependent sums:
+\begin{lemma}
+  Let $ \alpha : C(B, A) $ be a morphism in a category.
+If the pullback functor $ \alpha^*: (C \downarrow A) \to (C \downarrow B) $ exists, it has a left adjoint given by postcomposition with $ \alpha $.
+\end{lemma}
+\begin{proof}
+  For morphisms $ f: X \to A $, $ g: Y \to B $, the universal property of the pullback, with the following diagram
+  \begin{center}
+    \begin{tikzcd}
+      Y \arrow[r, "\varphi"'] \arrow[rr, "\psi", bend left] \arrow[dr, "g"'] & \alpha^* X \arrow[d, "\alpha^* f"'] \arrow[r] \arrow[rd, phantom, "\lrcorner", very near start] & X \arrow[d, "f"]\\
+      & B \arrow[r, "\alpha"'] & A
+    \end{tikzcd}
+  \end{center}
+  gives an equivalence between morphisms $ \varphi: Y \to \alpha^* X $ that commute with $ g $ and $ \alpha^* f $, and morphisms $ \psi: Y \to X $ that commute with $ g $, $ f $ and $ \alpha $.
+In other words:
+  \[ (C \downarrow A)(g \cdot \alpha, f) \simeq (C \downarrow B)(g, \alpha^*(f)), \]
+  which shows the adjunction.
+\end{proof}
+
+Now, let $ f : X \to A $ be the internal representation of an indexed family $ (X_a)_a $ and let $ \alpha : A \to I $ be the terminal projection.
+We have $ \sum_{a : A} X_a = f \circ \alpha : X \to I $.
+By the equivalence between $ (C \downarrow I) $ and $ C $, we see that the dependent sum of the family $ (X_a)_a $ is exactly $ X $.
+Therefore, our attention is mainly focused on the dependent product.
+
+We will close this section with a name for a category that has all dependent products:
+
+\begin{definition}
+  A \index{cartesian closed!locally}\textit{locally cartesian closed} category is a category $ C $ with pullbacks such that each pullback functor $ \alpha^* $ has a right adjoint.
+\end{definition}
 

### 2024-02-29 report/chapters/previous-work.tex
Write down Scott's representation theorem, and define relatively cartesian closedness

@@
 
-\section{The correspondence between categories and \texorpdfstring{$ \lambda $}{lambda}-calculi}
-In \cite{curry}, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
-(See page 413).
+\section{The correspondence between categories and typed \texorpdfstring{$ \lambda $}{lambda}-calculi}
+In \cite{curry}, page 413, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
 
@@
 
-Given a term $ t: B $ with free variables $ x_1: A_1, \dots, x_n: A_n $, the abstraction $ (\lambda x_n, t): A_n \to B $ corresponds to using the adjunction $ - \times A_n \dashv (-)^{A_n} $:
+Given a term $ t: B $ with free variables $ x_1: A_1, \dots, x_n: A_n $, the abstraction $ (\lambda x_n, t): A_n \to B $ corresponds to using the adjunction corresponding to the exponential object of $ A_n $:
 \[ C(A_1 \times \dots \times A_{n-1} \times A_n, B) \simeq C(A_1 \times \dots \times A_{n-1}, B^{A_n}). \]
 
-\TODO
-How about the untyped $ \lambda $-calculus?
+\section{Scott's Representation Theorem}
+The correspondence above for a simply-typed $ \lambda $-calculus raises a question whether such a correspondence also exists for an untyped $ \lambda $-calculus.
+As Definition \ref{def:endomorphism-theory} shows that in fairly general circumstances we can take one object $ c $ in a category $ C $ and consider the morphisms $ t: C(c^n, c) $ as terms in an untyped $ \lambda $-calculus.
+Hyland calls this the `endomorphism theory' of $ c $.
 
-\section{Scott's Representation Theorem}
+\TODO Remark upon the significance of having a reflexive object
+
+We can then wonder whether this construction is part of a correspondence between untyped $ \lambda $-calculi and some class of categories.
+This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \cite{curry}, page 418).
+\begin{lemma}
+  We can obtain every untyped $ \lambda $-calculus as the endomorphism theory of some object in some category.
+\end{lemma}
+\begin{proof}
+  Let $ L $ be a $ \lambda $-theory. First of all, for $ a_1, a_2: L_0 $, we define
+  \begin{align*}
+    a_1 \circ a_2 &= \lambda x_1, a_1 (a_2 x_1);\\
+    (a_1, a_2) &= \lambda x_1, x_1 a_1 a_2;\\
+    \langle a_1, a_2 \rangle &= \lambda x_1, (a_1 x_1, a_2 x_1);\\
+    \pi_i &= \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}).
+  \end{align*}
+  Although, actually, since every one of these starts with a $ \lambda $-abstraction, we would need to lift the constants $ a_i $ to $ \iota_{0, 1}(a_i): L_1 $ to make the definitions above typecheck.
+
+  Note that $ \pi_i (a_1, a_2) = a_i $ and $ \pi_i \circ \langle a_1, a_2 \rangle = \lambda x_1, a_i x_1 $.
+
+  Also, note that by replacing the $ x_i $ by $ x_{n + i} $ and the $ \iota_{0, 1}(a_i) $ by $ \iota_{n, 1}(a_i) $, we obtain definitions not only for $ n = 0 $, but for all $ n \geq 0 $.
+
+  For our category, we take the category $ \mathbb R $ which Hyland calls the `category of retracts'.
+It is the Karoubi envelope of the monoid of the terms without free variables under composition.
+That is, we consider the category of idempotent functions:
+  \[ \mathbb R_0 = \{ A : L_0 \mid A \circ A = A \} \quad \text{and} \quad \mathbb R(A, B) = \{ f: L_0 \mid B \circ f \circ A = f \}, \]
+  with $ \id A = A $ and composition given by $ \circ $.
+
+  This category has a terminal object $ I = \lambda x_1 x_2, x_2 : \mathbb R $.
+
+  The category has binary products with projections and product morphisms
+  \[ A_1 \times A_2 = \langle p_1, p_2 \rangle, \quad p_i = A_i \circ \pi_i \quad \text{and} \quad \langle f, g \rangle. \]
+
+  The category also has exponential objects
+  \[ C^B = \lambda x_1, B \circ x_1 \circ C \]
+  with evaluation morphism $ \epsilon_{BC}: C^B \times B \to C $ given by
+  \[ \epsilon_{BC} = \lambda x_1, C(\pi_1 x_1 (B (\pi_2 x_1))), \]
+  which is universal because we can lift a morphism $ f: \mathbb R(A \times B, C) $ to a morphism $ \varphi(f): \mathbb R(A, C^B) $ given by
+  \[ \varphi(f) = \lambda x_1 x_2, f (x_1, x_2). \]
+  Note that for $ g: \mathbb R(A, C^B) $, the inverse $ \varphi^{-1}(g) $ is given by
+  \[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle: \mathbb R(A \times B, C). \]
+
+  Now, consider the object $ U = \lambda x_1, x_1 : \mathbb R $.
+Note that for all $ A: \mathbb R $, we have morphisms $ A: \mathbb R(U, A) $ and $ A: \mathbb R(A, U) $, which exhibit $ A $ as a retract of $ U $.
+In particular, $ U^U $ is a retract of $ U $, so $ U $ is a reflexive object.
+
+  Therefore, $ E(U) $, the endomorphism theory of $ U $, has a $ \lambda $-theory structure.
+Note that the finite powers of $ U $ in $ \mathbb R $ are given by $ U^0 = I $ and $ U^{n + 1} = U^n \times U $.
+
+  We have $ E(U)_n = \mathbb R(U^n, U) = \{ f: L_0 \mid U \circ f \circ U^n = f \} $. The variables of $ E(U) $ are the projections of $ U^n $:
+  \[ q_{n, i} = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i}. \]
+  The substitution is given by composition with the product morphism:
+  \[ f \bullet g = f \circ \langle \langle \langle I, g_1 \rangle, \dots \rangle, g_n \rangle. \]
+  We have $ U^U = \lambda f, U \circ f \circ U = \lambda x_1 x_2, x_1 x_2 $.
+Using the equivalence $ \mathbb R(U^n \times U, U) \simeq \mathbb R(U^n, U^U) $ and the retraction $ U^U: U \to U^U $, the abstraction and application $ \lambda $ and $ \rho $ are given by
+  \[ \lambda(f) = \lambda x_1 x_2, \iota_{0, 2}(f)(x_1, x_2), \quad \rho(g) = \lambda x_1, \iota_{0, 1}(g) (\pi_1 x_1) (\pi_2 x_1). \]
+  for $ f: \mathbb R(U^{n + 1}, U) $ and $ g: \mathbb R(U^n, U) $.
+
+  Now, we have bijections $ \psi_0: E(U)_0 \xrightarrow{\sim} L_0 $, given by
+  \[ \psi_0(f) = f (\lambda x_1, x_1) \quad \text{and} \quad \psi_0^{-1}(g) = \lambda x_1, \iota_{0, 1}(g). \]
+  We can extend this to any $ n $, by reducing any term to a constant by repeatedly using $ \lambda $, then applying the bijection, and then lifting it again using $ \rho $. Explicitly, we obtain
+  \[ \psi_n(f) = \iota_{0, n}(f) ((((\lambda x_{n+1}, x_{n+1}), x_1), \dots), x_n), \quad \text{and} \quad \psi^{-1}_n(g) = \lambda x_1, g \bullet (q_i x_1)_i. \]
+  It is not hard to verify that this is indeed a bijection, using at one point the fact that $ f: \mathbb R(U^n, U) $ is defined by $ f \circ U^n = f $, for
+  \[ U^n = \lambda x_1, (((\lambda x_2, x_2), q_{n, 1} x_1 ), \dots, q_{n, n} x_1 ). \]
+  It is also pretty straightforward to check that
+  \begin{align*}
+    \psi(q_{n, i}) &= x_i, & \psi(f) \bullet (\psi(g_i))_i &= \psi(f \bullet g),\\
+    \psi(\lambda(h)) &= \lambda(\psi(h)), & \psi(\rho(h^\prime)) &= \rho(\psi(h^\prime))
+  \end{align*}
+  for $ f: E(U)_m $, $ g: E(U)_n^m $, $ h: E(U)_{n + 1} $ and $ h^\prime : E(U)_n $. Therefore, $ \psi $ is an isomorphism of $ \lambda $-theories.
+\end{proof}
 
 \section{The Taylor Fibration}
+
+In his dissertation, Paul Taylor shows that $ \mathbb R $ is not only cartesian closed, but also \iindex{relatively cartesian closed}.
+
+In Section \ref{sec:dependent-products}, we studied internal and external representations of families of objects in a category and how they behaved under substitutions (pullbacks).
+This was to arrive at a definition for dependent products and sums, as the right and left adjoints to the pullback (or substitution) functor $ \alpha^*: (C \downarrow A) \to (C \downarrow B) $ along some morphism $ \alpha : C(B, A) $.
+
+Now, some categories are not locally cartesian closed.
+That is: not all substitution functors $ \alpha^* $ exist or have a right adjoint.
+One way to look at this, is that not all morphisms $ X \to A $ represent an family.
+In these categories, we can carefully choose a subset of the morphisms to represent our indexed families.
+We will call a morphism representing an indexed family a \iindex{display map}.
+In most cases, we have quite a bit of choice which maps we want to take as our display maps.
+However, to make sure that indexed families are well-behaved, a class of display maps needs to have some properties:
+\begin{enumerate}
+  \item The pullback of a display map along any morphism exists and is a display map.
+  \item The composite of two display maps is a display map.
+  \item $ C $ has a terminal object and any terminal projection is a display map.
+\end{enumerate}
+\begin{remark}
+  A maximal example of a class of display maps is, for example, in the category $ \SET $, where we can take our class of display maps to equal the class of all morphisms of $ C $.
+\end{remark}
+\begin{remark}
+  A `minimal' example of a class of display maps is the class of (maps isomorphic to) product projections in a category with finite products.
+In this case, all indexed families are constant, and then dependent sums and products become binary products and exponential objects.
+\end{remark}
+
+Now, let $ C $ be a category with a class of display maps.
+For any $ A : C $, we get a category $ C^A $ as a full subcategory of the slice category $ C \downarrow A $, with as objects the display maps $ f: X \to A $.
+A morphisms from in $ f: X \to A $ to $ g: Y \to A $ is a morphism $ \varphi: X \to Y $ such that the following diagram commutes.
+\begin{center}
+  \begin{tikzcd}
+    X \arrow[rd, "f"'] \arrow[rr, "\varphi"] & & Y \arrow[ld, "g"]\\
+    & A &
+  \end{tikzcd}
+\end{center}
+Note that for the terminal object $ I : C $, $ C^I $ is still equivalent to $ C $.
+
+Also note that since display maps are closed under pullbacks, we can construct the pullback functor $ \alpha^*: (C \downarrow A) \to (C \downarrow B) $ for all $ \alpha: C(B, A) $.
+
+Note that since composing two display maps gives a display map again, and since the dependent sum is given by postcomposition, the pullback functor $ \alpha^* $ has a left adjoint for all display maps $ \alpha $.
+That is: the fiber categories $ C^A $ have dependent sums over display maps.
+
+The question whether the fiber categories $ C^A $ also have dependent products over display maps, brings us to the definition of relative cartesian closedness.
+\begin{definition}
+  A category $ C $ is \index{cartesian closed!relatively}\textit{cartesian closed relative} to a class of display maps $ D $, if the substitution functors $ \alpha^* $ along display maps have right adjoints.
+\end{definition}

### 2024-03-05 report/chapters/previous-work.tex
Remark upon the importance of a reflexive object

@@
 
-\TODO Remark upon the significance of having a reflexive object
+\begin{remark}
+  To construct a \textit{simply typed} $ \lambda $-calculus from a category, we just need a cartesian closed category.
+In a simply typed $ \lambda $-calculus, there is a lot of restriction on which terms we can apply to each other.
+A term of type $ A \to B $ can only be applied to a term of type $ A $, which gives a term of type $ B $.
+In particular, a term can be applied only finitely many times to other terms, and every time, the result has a different type.
 
-We can then wonder whether this construction is part of a correspondence between untyped $ \lambda $-calculi and some class of categories.
+  On the other hand, for an \textit{untyped} $ \lambda $-calculus, we need a cartesian closed category with a `reflexive object'.
+This is because in the untyped $ \lambda $-calculus, we can apply arbitrary terms to each other.
+For example, we can apply the term $ (\lambda x_1, x_1 x_1) $ to itself, which would not be typable in the simply typed $ \lambda $-calculus.
+Suppose that we have a category $ C $ and an object $ U $ such that the morphisms $ C(U^n, U) $ give the untype $ \lambda $-terms in $ n $ free variables, for all $ n $.
+Now, given two terms $ f, g : C(U^n, U) $, for the application $ f g $, we need to consider $ f $ as a morphism in $ C(U^n, U^U) $.
+We can do this by postcomposing with a morphism $ \varphi: C(U, U^U) $.
+On the other hand, if $ n > 0 $, then $ (\lambda x_n, f) $ is a morphism in $ C(U^{n - 1}, U^U) $, but it is a term in $ n - 1 $ free variables, so it should be in $ C(U^{n - 1}, U) $.
+For this, we postcompose with a morphism $ \psi: C(U^U, U) $.
+Now, for our untyped $ \lambda $-calculus to have $ \beta $-equality, we need $ \psi \cdot \varphi = \id{U^U} $, which means that the exponential $ U^U $ of $ U $ is a retract of $ U $.
+This is exactly what it means for $ U $ to be a \iindex{reflexive object}: an object $ U $ in a cartesian closed category, that has a retraction onto its `function space' $ U^U $.
+Note that if we want our $ \lambda $-theory to also have $ \eta $-equality, the retraction must be an isomorphism.
+
+  Note that $ \SET $ is a cartesian closed category, but that for sets $ X $ and $ Y $, the function space $ X^Y $ has cardinality $ \vert X \vert^{\vert Y \vert} $, and therefore $ U^U $ cannot be a retract of $ U $, unless $ U = \{ \star \} $, in which case we have a very trivial $ \lambda $-calculus: $ \SET(U^n, U) = \{ \star \} $.
+
+  During the 1960s, computer scientists sought for nontrivial examples of reflexive objects, there is a quote by Dana Scott that ``Lambda-calculus has no mathematical models!''\cite{strachey}.
+However, in 1969, the same Dana Scott discovered that the category of (continuous) lattices with (Scott-)continuous functions between them has a nontrivial reflexive object, with the retraction onto the function spaces being even an isomorphism.
+Such a reflexive object $ D_\infty $ is obtained by starting with an arbitrary lattice $ D_0 $, iteratively taking $ D_{n + 1} = D_n^{D_n} $, with a retraction (in the `wrong' direction) $ r: D_n^{D_n} \to D_n $, and then passing to the limit $ D_\infty = \lim_{\leftarrow} D_n $ (for the main result, see Theorem 4.4 in \cite{scott-continuous}, page 127).
+\end{remark}
+
+Since Lambek showed an equivalence between simply typed $ \lambda $-calculi and cartesian closed categories, and since we have a construction for an untyped $ \lambda $-calculus from a cartesian closed category with a reflexive object, we can wonder whether this construction constitutes contitutes an equivalence between untyped $ \lambda $-calculi and some class of categories.
 This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \cite{curry}, page 418).

### 2024-03-05 report/chapters/category-theory.tex
Write about the significance of local/relative cartesian closedness

@@
 \section{Dependent products and sums}\label{sec:dependent-products}
+The following is based loosely on Section 4.1 of \cite{taylor}.
 
@@
     \begin{tikzcd}
-      Y \arrow[r, "\varphi"'] \arrow[rr, "\psi", bend left] \arrow[dr, "g"'] & \alpha^* X \arrow[d, "\alpha^* f"'] \arrow[r] \arrow[rd, phantom, "\lrcorner", very near start] & X \arrow[d, "f"]\\
+      Y \arrow[r, dashed, "\varphi"'] \arrow[rr, "\psi", bend left] \arrow[dr, "g"'] & \alpha^* X \arrow[d, "\alpha^* f"'] \arrow[r] \arrow[rd, phantom, "\lrcorner", very near start] & X \arrow[d, "f"]\\
       & B \arrow[r, "\alpha"'] & A
@@
 \end{definition}
+
+Apart from having dependent sums and products, there also is the following theorem that shows the significance locally cartesian closedness:
+\begin{lemma}\label{lem:locally-cartesian-closed}
+  A category $ C $ is locally cartesian closed iff $ (C \downarrow A) $ is cartesian closed for each $ A : C $.
+\end{lemma}
+\begin{proof}
+  See the end of Section 1.3 of \cite{freyd}.
+\end{proof}
 

### 2024-03-05 report/chapters/previous-work.tex
Write about the significance of local/relative cartesian closedness

@@
   The category also has exponential objects
-  \[ C^B = \lambda x_1, B \circ x_1 \circ C \]
-  with evaluation morphism $ \epsilon_{BC}: C^B \times B \to C $ given by
+  \[ (C \downarrow_D B) = \lambda x_1, B \circ x_1 \circ C \]
+  with evaluation morphism $ \epsilon_{BC}: (C \downarrow_D B) \times B \to C $ given by
   \[ \epsilon_{BC} = \lambda x_1, C(\pi_1 x_1 (B (\pi_2 x_1))), \]
-  which is universal because we can lift a morphism $ f: \mathbb R(A \times B, C) $ to a morphism $ \varphi(f): \mathbb R(A, C^B) $ given by
+  which is universal because we can lift a morphism $ f: \mathbb R(A \times B, C) $ to a morphism $ \varphi(f): \mathbb R(A, (C \downarrow_D B)) $ given by
   \[ \varphi(f) = \lambda x_1 x_2, f (x_1, x_2). \]
-  Note that for $ g: \mathbb R(A, C^B) $, the inverse $ \varphi^{-1}(g) $ is given by
+  Note that for $ g: \mathbb R(A, (C \downarrow_D B)) $, the inverse $ \varphi^{-1}(g) $ is given by
   \[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle: \mathbb R(A \times B, C). \]
@@
 That is: not all substitution functors $ \alpha^* $ exist or have a right adjoint.
-One way to look at this, is that not all morphisms $ X \to A $ represent an family.
+One way to look at this, is that not all morphisms $ X \to A $ represent a family of objects.
 In these categories, we can carefully choose a subset of the morphisms to represent our indexed families.
@@
 \begin{remark}
-  A maximal example of a class of display maps is, for example, in the category $ \SET $, where we can take our class of display maps to equal the class of all morphisms of $ C $.
+  A `maximal' example of a class of display maps is, for example, in the category $ \SET $, where we can take our class of display maps to equal the class of all morphisms of $ C $.
 \end{remark}
@@
 
-Now, let $ C $ be a category with a class of display maps.
-For any $ A : C $, we get a category $ C^A $ as a full subcategory of the slice category $ C \downarrow A $, with as objects the display maps $ f: X \to A $.
-A morphisms from in $ f: X \to A $ to $ g: Y \to A $ is a morphism $ \varphi: X \to Y $ such that the following diagram commutes.
+Now, let $ C $ be a category with a class of display maps $ D $.
+We will denote the class of display maps from $ X $ to $ A $ with $ D(X, A) \subseteq C(X, A) $.
+For any $ A : C $, we get a category $ (C \downarrow_D A) $ as a full subcategory of the slice category $ (C \downarrow A) $, with as objects the display maps $ f: D(X, A) $.
+A morphism from $ f: D(X, A) $ to $ g: D(Y, A) $ is a morphism $ \varphi: C(X, Y) $ such that the following diagram commutes.
 \begin{center}
@@
 \end{center}
-Note that for the terminal object $ I : C $, $ C^I $ is still equivalent to $ C $.
+Note that for the terminal object $ I : C $, $ (C \downarrow_D I) $ is still equivalent to $ C $, since every terminal projection is a display map.
 
-Also note that since display maps are closed under pullbacks, we can construct the pullback functor $ \alpha^*: (C \downarrow A) \to (C \downarrow B) $ for all $ \alpha: C(B, A) $.
+Also note that since display maps are closed under pullbacks, the pullback functor $ (C \downarrow A) \to (C \downarrow B) $ for $ \alpha: C(B, A) $ restricts to a pullback functor $ \alpha^*: (C \downarrow_D A) \to (C \downarrow_D B) $.
 
-Note that since composing two display maps gives a display map again, and since the dependent sum is given by postcomposition, the pullback functor $ \alpha^* $ has a left adjoint for all display maps $ \alpha $.
-That is: the fiber categories $ C^A $ have dependent sums over display maps.
+Note that since composing two display maps gives a display map again, and since the dependent sum is given by postcomposition, $ \alpha^* $ has a left adjoint for all display maps $ \alpha $.
+That is: the fiber categories $ (C \downarrow_D A) $ have dependent sums over display maps.
 
-The question whether the fiber categories $ C^A $ also have dependent products over display maps, brings us to the definition of relative cartesian closedness.
+The question whether the fiber categories $ (C \downarrow_D A) $ also have dependent products over display maps, brings us to the definition of relative cartesian closedness.
 \begin{definition}
@@
 \end{definition}
+
+Now, analogously to \ref{lem:locally-cartesian-closed}, Taylor shows:
+\begin{lemma}
+  If a category $ C $ is cartesian closed relative to a class of display maps $ D $, then the fiber categories $ (C \downarrow_D A) $ are cartesian closed and the substitution functors $ \alpha^* $ preserve this structure.
+\end{lemma}
+\begin{proof}
+  The proofs leading up to \S 4.3.7 in \cite{taylor}.
+\end{proof}

### 2024-03-07 report/chapters/algebraic-structures.tex
Do the setup of the Taylor fibration, move content about R to a separete section, show some properties of R

@@
 \end{remark}
+
+Later on, we will see an example of a trivial algebraic theory (the terminal theory) $ T $, in which every $ T_n $ only contains one element.
+However, we can say a bit about nontrivial algebraic theories.
+\begin{lemma}\label{lem:nontrivial-algebraic-theory}
+  Let $ T $ be an algebraic theory, such that $ T_n $ has at least two distinct elements for some $ n $. Then for all $ 1 \leq i, j \leq m $ with $ i \not = j $, we have $ x_{m, i} \not = x_{m, j} $.
+\end{lemma}
+\begin{proof}
+  We can also formulate the statement as: If there exist $ 1 \leq i, j \leq m $ with $ i \not = j $ such that $ x_{m, i} = x_{m, j} $, then all $ L_n $ contain at most one distinct element.
+
+  So, suppose that $ x_{m, i} = x_{m, j} $ for some $ i \not = j $. For $ a, b : L_n $, we define $ v : L_n^m $ as
+  \[ v_k = \left\{\begin{array}{ll} a & k = i\\ b & k \not = i \end{array}\right., \]
+  so in particular, $ v_j = b $. Then we have
+  \[ a = v_i = x_{m, i} \bullet v = x_{m, j} \bullet v = v_j = b, \]
+  so $ L_n $ contains at most one distinct element.
+\end{proof}
 

### 2024-03-07 report/chapters/previous-work.tex
Do the setup of the Taylor fibration, move content about R to a separete section, show some properties of R

@@
 
-\section{The correspondence between categories and typed \texorpdfstring{$ \lambda $}{lambda}-calculi}
+\section{The correspondence between categories and typed \texorpdfstring{$ \lambda $}{lambda}-calculi}\label{sec:lambek-correspondence}
 In \cite{curry}, page 413, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
@@
 
+\section{The category of retracts}
+
+The next sections make extensive use of a category called $ \R $, which Hyland calls the `category of retracts'. In this section, we will define the category, and show some properties about it.
+
+Let $ L $ be a $ \lambda $-theory. First of all, for $ a_1, a_2: L_0 $, we define
+\begin{align*}
+  a_1 \circ a_2 &= \lambda x_1, a_1 (a_2 x_1);\\
+  (a_1, a_2) &= \lambda x_1, x_1 a_1 a_2;\\
+  \langle a_1, a_2 \rangle &= \lambda x_1, (a_1 x_1, a_2 x_1);\\
+  \pi_i &= \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}).
+\end{align*}
+Although, actually, since every one of these starts with a $ \lambda $-abstraction, we need to lift the constants $ a_i $ to $ \iota_{0, 1}(a_i): L_1 $ to make the definitions above typecheck.
+
+Note that $ \pi_i (a_1, a_2) = a_i $ and $ \pi_i \circ \langle a_1, a_2 \rangle = \lambda x_1, a_i x_1 $, which is exactly what we would expect of a projection.
+
+Also, note that by replacing the $ x_i $ by $ x_{n + i} $ and the $ \iota_{0, 1}(a_i) $ by $ \iota_{n, 1}(a_i) $, we obtain definitions not only for elements of $ L_0 $, but for all $ L_n $.
+
+\begin{definition}
+  We define the category \index{R}$ \R $ as the Karoubi envelope of the monoid of the $ \lambda $-terms without free variables under composition. That is, the category of idempotent functions:
+  \[ \R_0 = \{ A : L_0 \mid A \circ A = A \} \quad \text{and} \quad \R(A, B) = \{ f: L_0 \mid B \circ f \circ A = f \}, \]
+  with $ \id A = A $ and composition given by $ \circ $.
+\end{definition}
+
+Now, to give a bit more intuition for the objects of $ \R $, we can pretend that an object $ A : \R $ consists of the set of elements that satisfy $ A a = a $.
+Then a morphism $ f : \R(A, B) $ gives $ B (f a) = (B \circ f) a = f a $.
+This actually constitutes a functor from $ R $ to $ \Pshf L $:
+
+\begin{definition}\label{def:retracts-embedding}
+  We define a functor $ \varphi: \R \to \Pshf L $ by taking
+  \[ \varphi(A)_n = \{ a : L_n \mid \iota_{0, n}(A) a = a \} \quad \text{and} \quad \varphi(f)_n(a) = \iota_{0, n}(f) a \]
+  for $ A, B : \R $, $ f: \R(A, B) $ and $ a : A $. The presheaf action on $ \varphi(A) $ is given by the substitution of $ L $:
+  \[ (a, f) \mapsto a \bullet f \]
+  for $ f : L_n^m $ and $ a : L_m $ such that $ \iota_{0, m}(A) a = a $.
+\end{definition}
+
+It turns out that this embeds $ \R $ as a full subcategory of $ \Pshf L $:
+\begin{lemma}
+  This functor $ \varphi $ is fully faithful.
+\end{lemma}
+\begin{proof}
+  Take $ A, B : \R $. We need to show that $ f \mapsto \varphi(f) $ is an equivalence between $ \R(A, B) $ and $ \Pshf L(\varphi(A), \varphi(B)) $. We have a function
+  \[ \psi: \Pshf L(\varphi(A), \varphi(B)) \to \R(A, B), \quad g \mapsto (\lambda x_1, g_1(\iota_1(A) x_1)) \]
+  which gives us the inverse. To see that this even typechecks, note that we have
+  \[ \iota_1(A) x_1 : \varphi(A)_1 \quad \text{and} \quad g_1(\iota_1(A) x_1) : \varphi(B)_1 \subseteq L_1. \]
+  Using the fact that $ g $ is a presheaf morphism, we can show that
+  \[ B \circ \psi(g) \circ A = \psi(g), \]
+  and that $ \varphi $ and $ \psi $ are inverses.
+\end{proof}
+
+\begin{remark}
+  Note that if $ L $ is a nontrivial $ \lambda $-theory, $ \R $ is not a univalent category.
+To see this, note, for example, that we have an object $ X := \langle \pi_1, \pi_2 \rangle : \R $ (corresponding to the type of `pairs' of $ \lambda $-terms).
+Since $ L_0 $ is a set, $ X = X $ is a proposition.
+However, $ X $ has (at least) two automorphisms:
+  \[ \langle \pi_1, \pi_2 \rangle \quad \text{and} \quad \langle \pi_2, \pi_1 \rangle. \]
+  These are the identity, and the automorphism (of order 2) that swaps the elements of the pair.
+To see that these are indeed different morphisms, note that applying them (or their lifted versions) to $ (x_{2, 1}, x_{2, 2}) $ gives respectively $ x_{2, 1} $ and $ x_{2, 2} $, which are distinct elements by Lemma \ref{lem:nontrivial-algebraic-theory}.
+\end{remark}
+
 \section{Scott's Representation Theorem}
-The correspondence above for a simply-typed $ \lambda $-calculus raises a question whether such a correspondence also exists for an untyped $ \lambda $-calculus.
-As Definition \ref{def:endomorphism-theory} shows that in fairly general circumstances we can take one object $ c $ in a category $ C $ and consider the morphisms $ t: C(c^n, c) $ as terms in an untyped $ \lambda $-calculus.
+The correspondence in Section \ref{sec:lambek-correspondence} between simply-typed $ \lambda $-calculi and cartesian closed categories raises a question whether such a correspondence also exists for untyped $ \lambda $-calculi.
+Definition \ref{def:endomorphism-theory} shows that in fairly general circumstances we can take one object $ c $ in a category $ C $ and consider the morphisms $ t: C(c^n, c) $ as terms in an untyped $ \lambda $-calculus.
 Hyland calls this the `endomorphism theory' of $ c $.
@@
 \begin{proof}
-  Let $ L $ be a $ \lambda $-theory. First of all, for $ a_1, a_2: L_0 $, we define
-  \begin{align*}
-    a_1 \circ a_2 &= \lambda x_1, a_1 (a_2 x_1);\\
-    (a_1, a_2) &= \lambda x_1, x_1 a_1 a_2;\\
-    \langle a_1, a_2 \rangle &= \lambda x_1, (a_1 x_1, a_2 x_1);\\
-    \pi_i &= \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}).
-  \end{align*}
-  Although, actually, since every one of these starts with a $ \lambda $-abstraction, we would need to lift the constants $ a_i $ to $ \iota_{0, 1}(a_i): L_1 $ to make the definitions above typecheck.
+  Let $ L $ be a $ \lambda $-theory. Scott considers the category $ \R $.
 
-  Note that $ \pi_i (a_1, a_2) = a_i $ and $ \pi_i \circ \langle a_1, a_2 \rangle = \lambda x_1, a_i x_1 $.
-
-  Also, note that by replacing the $ x_i $ by $ x_{n + i} $ and the $ \iota_{0, 1}(a_i) $ by $ \iota_{n, 1}(a_i) $, we obtain definitions not only for $ n = 0 $, but for all $ n \geq 0 $.
-
-  For our category, we take the category $ \mathbb R $ which Hyland calls the `category of retracts'.
-It is the Karoubi envelope of the monoid of the terms without free variables under composition.
-That is, we consider the category of idempotent functions:
-  \[ \mathbb R_0 = \{ A : L_0 \mid A \circ A = A \} \quad \text{and} \quad \mathbb R(A, B) = \{ f: L_0 \mid B \circ f \circ A = f \}, \]
-  with $ \id A = A $ and composition given by $ \circ $.
-
-  This category has a terminal object $ I = \lambda x_1 x_2, x_2 : \mathbb R $.
+  This category has a terminal object $ I = \lambda x_1 x_2, x_2 : \R $.
 
@@
   \[ \epsilon_{BC} = \lambda x_1, C(\pi_1 x_1 (B (\pi_2 x_1))), \]
-  which is universal because we can lift a morphism $ f: \mathbb R(A \times B, C) $ to a morphism $ \varphi(f): \mathbb R(A, (C \downarrow_D B)) $ given by
+  which is universal because we can lift a morphism $ f: \R(A \times B, C) $ to a morphism $ \varphi(f): \R(A, (C \downarrow_D B)) $ given by
   \[ \varphi(f) = \lambda x_1 x_2, f (x_1, x_2). \]
-  Note that for $ g: \mathbb R(A, (C \downarrow_D B)) $, the inverse $ \varphi^{-1}(g) $ is given by
-  \[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle: \mathbb R(A \times B, C). \]
+  Note that for $ g: \R(A, (C \downarrow_D B)) $, the inverse $ \varphi^{-1}(g) $ is given by
+  \[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle: \R(A \times B, C). \]
 
-  Now, consider the object $ U = \lambda x_1, x_1 : \mathbb R $.
-Note that for all $ A: \mathbb R $, we have morphisms $ A: \mathbb R(U, A) $ and $ A: \mathbb R(A, U) $, which exhibit $ A $ as a retract of $ U $.
+  Now, consider the object $ U = \lambda x_1, x_1 : \R $.
+Note that for all $ A: \R $, we have morphisms $ A: \R(U, A) $ and $ A: \R(A, U) $, which exhibit $ A $ as a retract of $ U $.
 In particular, $ U^U $ is a retract of $ U $, so $ U $ is a reflexive object.
 
-  Therefore, $ E(U) $, the endomorphism theory of $ U $, has a $ \lambda $-theory structure.
-Note that the finite powers of $ U $ in $ \mathbb R $ are given by $ U^0 = I $ and $ U^{n + 1} = U^n \times U $.
+  Therefore, $ E(U) $, the endomorphism theory of $ U $, has a $ \lambda $-theory structure. Note that the finite powers of $ U $ in $ \R $ are given by $ U^0 = I $ and $ U^{n + 1} = U^n \times U $.
 
-  We have $ E(U)_n = \mathbb R(U^n, U) = \{ f: L_0 \mid U \circ f \circ U^n = f \} $. The variables of $ E(U) $ are the projections of $ U^n $:
+  We have $ E(U)_n = \R(U^n, U) = \{ f: L_0 \mid U \circ f \circ U^n = f \} $. The variables of $ E(U) $ are the projections of $ U^n $:
   \[ q_{n, i} = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i}. \]
@@
   We have $ U^U = \lambda f, U \circ f \circ U = \lambda x_1 x_2, x_1 x_2 $.
-Using the equivalence $ \mathbb R(U^n \times U, U) \simeq \mathbb R(U^n, U^U) $ and the retraction $ U^U: U \to U^U $, the abstraction and application $ \lambda $ and $ \rho $ are given by
+Using the equivalence $ \R(U^n \times U, U) \simeq \R(U^n, U^U) $ and the retraction $ U^U: U \to U^U $, the abstraction and application $ \lambda $ and $ \rho $ are given by
   \[ \lambda(f) = \lambda x_1 x_2, \iota_{0, 2}(f)(x_1, x_2), \quad \rho(g) = \lambda x_1, \iota_{0, 1}(g) (\pi_1 x_1) (\pi_2 x_1). \]
-  for $ f: \mathbb R(U^{n + 1}, U) $ and $ g: \mathbb R(U^n, U) $.
+  for $ f: \R(U^{n + 1}, U) $ and $ g: \R(U^n, U) $.
 
@@
   \[ \psi_n(f) = \iota_{0, n}(f) ((((\lambda x_{n+1}, x_{n+1}), x_1), \dots), x_n), \quad \text{and} \quad \psi^{-1}_n(g) = \lambda x_1, g \bullet (q_i x_1)_i. \]
-  It is not hard to verify that this is indeed a bijection, using at one point the fact that $ f: \mathbb R(U^n, U) $ is defined by $ f \circ U^n = f $, for
+  It is not hard to verify that this is indeed a bijection, using at one point the fact that $ f: \R(U^n, U) $ is defined by $ f \circ U^n = f $, for
   \[ U^n = \lambda x_1, (((\lambda x_2, x_2), q_{n, 1} x_1 ), \dots, q_{n, n} x_1 ). \]
@@
 
-In his dissertation, Paul Taylor shows that $ \mathbb R $ is not only cartesian closed, but also \iindex{relatively cartesian closed}.
+In his dissertation, Paul Taylor shows that $ \R $ is not only cartesian closed, but also \iindex{relatively cartesian closed}.
 
@@
 \begin{proof}
-  The proofs leading up to \S 4.3.7 in \cite{taylor}.
+  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \cite{taylor}.
 \end{proof}
+
+\TODO Displayed category?
+
+\subsection{Taylor's proof}
+
+First of all, Taylor considers `functions' $ X: A \to \R_0 $ for some $ A : \R_0 $.
+He characterizes these functions as the $ \lambda $-terms that satisfy $ X \circ A = X $ and $ \lambda x_1, (X x_1) \circ (X x_1) = X $.
+Taylor then constructs global dependent sums as
+\[ \sum_A X = \lambda x_1, (A (\pi_1 x_1), X (\pi_1 x_1) (\pi_2 x_1)). \]
+Note that with the embedding in Definition \ref{def:retracts-embedding}, we can consider this as consisting of pairs $ (a, x) $ with $ a : A $ and $ x : X a $, which is exactly what we would expect from a dependent sum.
+
+\begin{definition}
+  For $ \R $, we will take a morphism $ f: X \to A $ to be a display map if we have some $ Y : A \to R_0 $ like above, and some isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ such that $ f = g \cdot p_1 $ with $ p_1 : \sum_A Y \to A $ given by $ \lambda x_1, A (\pi_1 x_1) $.
+\end{definition}
+
+\begin{remark}
+  Hyland actually gives a different characterization of Taylor's display maps.
+He claims that Taylor takes the display maps $ X \to A $ to be the retracts in $ (C \downarrow A) $ of $ p_1: A \times U \to A $,
+  the projection onto the first coordinate. The two characterizations are equivalent:
+
+  Given $ Y: A \to \R_0 $, $ Y a $ is a retract of $ U $ for all $ a $.
+Concretely, both morphisms $ r : A \times U \to \sum_A Y $ and $ s : \sum_A Y \to A \times U $ are given by $ \sum_A Y $ and these commute with the projection to $ A $.
+Therefore, if we have an isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ in $ (C \downarrow A) $, then $ \sum_A Y \cdot g^{-1} $ and $ g \cdot \sum_A Y $ make $ X $ into a retract of $ A \times U $.
+
+  Conversely, given a retraction $ r : A \times U \to X $ and section $ s : X \to A \times U $ in $ (C \downarrow A) $, the term
+  \[ \lambda x_1 x_2, \pi_2 (s (r (x_1, x_2))) \]
+  gives a function $ Y : A \to \R_0 $.
+Using the properties of $ r $ and $ s $ and the definition of $ \sum_A Y $, one can show that $ r $ gives a morphism $ \sum_A Y \to X $ and $ s $ gives a morphism $ X \to \sum_A Y $, and that $ r \circ s = \id{\sum_A Y} $.
+Combined with the fact that $ s \circ r = \id X $, this shows that $ X $ is isomorphic to $ \sum_A Y $.
+\end{remark}
+
+\begin{remark}
+  Recall that if $ L $ is nontrivial, $ \R $ is not univalent, and the existence of $ Y: A \to \R_0 $ with the isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ is not a proposition.
+Take, for example, $ Y : I \to \R_0 $ given by $ (\lambda x_1, U \times U) $ for $ I $ the terminal object.
+Recall that $ (C \downarrow I) $ is equivalent to $ C $.
+Under this equivalence $ \sum_I Y $ is equivalent to $ U \times U $.
+As mentioned before, $ \sum_I Y $ has (at least) two distinct isomorphisms to itself: the identity and the isomorphism that swaps both sides of the product.
+
+  In a similar way, being a retract of $ A \times U $ is not a proposition.
+Therefore, if we want the class of display maps to really be a subclass of the class of morphisms, we need the existence of $ Y: A \to \R_0 $ and the isomorphism $ g : X \to \sum_A Y $, or the existence of the retraction $ A \times U \to X $, to mean \textit{mere existence} in this case.
+\end{remark}
+
+Now, in the spirit of Scott, Taylor gives a very syntactical proof that $ \R $ is cartesian closed, relative to some class of display maps:
+
+\TODO

### 2024-03-21 report/chapters/category-theory.tex
Do the setup of the Taylor fibration, move content about R to a separete section, show some properties of R
Write about univalent foundations, the univalence axiom, univalent categories, and a bit about hSets

@@
 \subsection{Adjoint equivalences}
-An adjoint equivalence of categories has multiple definitions. The one we will use here is the following:
+An (adjoint) equivalence of categories has multiple definitions. The one we will use here is the following:
 
-\begin{definition}
+\begin{definition}\label{def:equivalence-of-categories}
   An \iindex{adjoint equivalence} between categories $ C $ and $ D $ is a pair of adjoint functors $ L \dashv R $ like above such that the unit $ \eta: \id{C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{D} $ are isomorphisms of functors.
@@
 
-Take a category $ C $ (for example, $ \mathbb R $, $ \SET $ or $ \TYPE $).
+Take a category $ C $.
 To talk about dependent sums $ \sum_{a: A} X_a $ and products $ \prod_{a: A} X_a $ in $ C $, we first need some way to construct the family of objects $ (X_a)_a $.

### 2024-03-21 report/chapters/previous-work.tex
Write about univalent foundations, the univalence axiom, univalent categories, and a bit about hSets

@@
 This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \cite{curry}, page 418).
-\begin{lemma}
+\begin{theorem}
   We can obtain every untyped $ \lambda $-calculus as the endomorphism theory of some object in some category.
-\end{lemma}
+\end{theorem}
 \begin{proof}
@@
   The category also has exponential objects
-  \[ (C \downarrow_D B) = \lambda x_1, B \circ x_1 \circ C \]
-  with evaluation morphism $ \epsilon_{BC}: (C \downarrow_D B) \times B \to C $ given by
+  \[ C^B = \lambda x_1, B \circ x_1 \circ C \]
+  with evaluation morphism $ \epsilon_{BC}: C^B \times B \to C $ given by
   \[ \epsilon_{BC} = \lambda x_1, C(\pi_1 x_1 (B (\pi_2 x_1))), \]
-  which is universal because we can lift a morphism $ f: \R(A \times B, C) $ to a morphism $ \varphi(f): \R(A, (C \downarrow_D B)) $ given by
+  which is universal because we can lift a morphism $ f: \R(A \times B, C) $ to a morphism $ \varphi(f): \R(A, C^B) $ given by
   \[ \varphi(f) = \lambda x_1 x_2, f (x_1, x_2). \]
-  Note that for $ g: \R(A, (C \downarrow_D B)) $, the inverse $ \varphi^{-1}(g) $ is given by
-  \[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle: \R(A \times B, C). \]
+  Note that for $ g: \R(A, C^B) $, the inverse $ \varphi^{-1}(g) $ is given by
+  \[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle = \lambda x_1, g (\pi_1 x_1) (\pi_2 x_1): \R(A \times B, C). \]
 
@@
 \begin{proof}
-  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \cite{taylor}.
+  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \cite{taylor}. It is also proved as Proposition 6 of \cite{theory-of-constructions}.
 \end{proof}
@@
 
-Now, in the spirit of Scott, Taylor gives a very syntactical proof that $ \R $ is cartesian closed, relative to some class of display maps:
+This brings us to Taylor's theorem about $ \R $:
+\begin{theorem}
+  $ \R $ is cartesian closed, relative to this class of display maps.
+\end{theorem}
+\begin{proof}
+  In the spirit of Scott, Taylor gives a very syntactical proof.
+\end{proof}
 
-\TODO
+\TODO Relate indexed types and fibrations.

### 2024-03-21 report/chapters/univalent-foundations.tex
Write down Scott's representation theorem, and define relatively cartesian closedness
Do the setup of the Taylor fibration, move content about R to a separete section, show some properties of R
Write about univalent foundations, the univalence axiom, univalent categories, and a bit about hSets

@@
 
+\section{The univalence principle}
+\begin{quote}
+  \textit{Isomorphic objects are equivalent.}
+\end{quote}
+This principle is visible in most of mathematics: Sets with a bijection have the same number of elements, isomorphic groups have the same properties, and since the universal property of limits makes them ``unique up to unique isomorphism'', we can talk about `the' limit of some diagram in a category.
+
+Now, the \iindex{univalence principle} takes this a step further. It states that
+\begin{quote}
+  \textit{Isomorphic objects are equal.}
+\end{quote}
+Univalent foundations seeks to be a foundation for mathematics that is in line with this principle.
+This is often done within the framework of `Martin-Löf dependent type theory', a type theory constructed by Per Martin-Löf \cite{martin-lof-type-theory}.
+This type theory has types which depend on values of (other) types (like \texttt{array(T, n)}, the type of arrays of length $ n $, with elements of type $ T $).
+It is a constructive type theory, so it does not automatically assume the law of excluded middle (which states that "not (not x)" implies "x") or the axiom of choice (stating that for every indexed family $ (S_i)_{i : I} $ with the $ S_i $ nonempty, there exists $ f: \prod_i S_i $), although it is compatible with these axioms, so one can still assume these alongside its usual axioms.
+
+It is important to note that Martin-Löf type theory has \textit{identity types}: given a type $ T $ and elements $ x, y: T $, we have a type $ \mathrm{Id}_T(x, y) $ (note that this is a dependent type), which we will usually denote with $ x = y $.
+An element $ p: x = y $ is a proof that $ x $ is `equal' to $ y $.
+This type comes with an interesting induction principle called \iindex{path induction}: we can show any statement about paths $ p: x = y $ for generic $ x $ and $ y $, if we can show it about the `trivial' path $ \mathrm{refl}: x = x $ for generic $ x $.
+For example, symmetry of the equality boils down to a function $ \prod_{x y : T} x = y \to y = x $.
+We construct this using path induction with the function that sends $ \mathrm{refl}: x = x $ to itself.
+For more information, see \cite{hottbook}, Section 1.12.1.
+
+In set-theoretic mathematics, there is the concept of a `bijection' $ S \simeq T $ of sets (or an isomorphism in the category $ \SET $), which is often treated as an equivalence.
+It consists of functions $ f: S \to T $ and $ g: T \to S $ with $ f \cdot g = \id S $ and $ g \cdot f = \id T $.
+In type theory, we have a similar concept, which is called `equivalence' (of types) $ S \simeq T $.
+Since bijections are not well-behaved for types that are not sets (see \ref{sec:homotopy-props-sets}), because in those cases, a function $ f: S \to T $ can have multiple distinct inverses.
+Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ (see \cite{hottbook}, Equation 2.4.10).
+However, intuitively we can still think of these as bijections.
+
+Using the identity type, we can make our statement of the univalence principle more precise (and a bit stronger). For types, we can construct a function
+\[ \mathrm{idtoequiv}: \prod_{S, T: \TYPE} (S = T) \to (S \simeq T). \]
+We construct this function using path induction with the identity bijection $ \prod_S \id S: (S \simeq S) $.
+In fact, this is a specific case of the following: for a category $ C $, if we denote the type of isomorphisms between objects $ c $ and $ d $ with $ c \cong d $, we can construct a function
+\[ \mathrm{idtoiso}: \prod_{c, d: C} (c = d) \to (c \cong d), \]
+using path induction with the identity isomorphism $ \prod_{c: C} \id c: (c \cong c) $. We can then formulate the univalence principle for categories as
+\begin{quote}
+  For all $ c, d : C $, $ \mathrm{idtoiso}_{c, d}: (c = d) \to (c \cong d) $ is an equivalence.
+\end{quote}
+A category that adheres to the univalence principle is called a \iindex{univalent category}.
+
+\section{The univalence axiom}
+Now, even for a basic category, like the category of types, it seems impossible to prove that the univalence principle holds.
+However, this is no surprise: it turns out that it is independent of the axioms of Martin-Löf type theory (\TODO \textbf{Is this true?
+I need a reference for this, but could not find one}).
+That is: it cannot be proven, but assuming it as an axiom does not yield contradictions.
+
+As mentioned before, univalent foundations attempts to develop as much of mathematics as possible along the univalence principle. Therefore, we assume as our first axiom the \iindex{univalence axiom}:
+\begin{axiom}
+  For all $ S, T: \TYPE $, the function $ \mathrm{idtoequiv}_{S, T}: (S = T) \to (S \simeq T) $ is an equivalence.
+\end{axiom}
+In other words:
+\begin{axiom}
+  $ \TYPE $ is univalent.
+\end{axiom}
+
+\begin{remark}
+  One consequence of the independence of the univalence axiom is that equivalent objects are `indiscernible'.
+That is: even if we do not yet assume the univalence axiom, we cannot formulate a property that is satisfied by some type, but not by another, equivalent type.
+This is because such a property would yield a contradiction when we would assume the univalence axiom.
+\end{remark}
+
+Now, the question arises: how about the univalence axiom for categories other than $ \TYPE $?
+Do we need to keep assuming an additional axiom for every category that we want to be univalent?
+It turns out that this is not necessary.
+In practice, most categories consist of `sets (or types) with additional structure'.
+For example: topological spaces, groups, $ \lambda $-theories and algebraic theory algebras.
+In such categories, we can leverage the univalence of $ \TYPE $ to show that for isomorphic objects, their underlying types are equal.
+Also morphisms are usually defined in such a way that they `preserve' the `additional structure', which is what we need to show that the category is univalent.
+
+Also, Theorem 4.5 in \cite{univalent-categories} shows that if a category $ B $ is univalent (in the paper, categories are called `precategories` and univalent categories are just called `categories'), then the functor category $ A \rightarrow B $ is also univalent.
+In particular, the category of (pre)sheaves $ A \to \SET $ is univalent.
+
+Therefore, the univalence axiom is a very powerful axiom, and we usually do not need to assume additional axioms to show that more categories satisfy the univalence principle.
+
+The last structure in this section for which we want to consider the univalence axiom, is the 2-category $ \Cat $ of categories.
+In general, we cannot show that this satisfies the univalence principle.
+However, we will restrict our attention to the sub-2-category of univalent categories, which are the categories that we want to study.
+Then Theorem 6.8 in \cite{univalent-categories} shows that for univalent categories $ C $ and $ D $, there is an equivalence between $ C = D $ and $ C \simeq D $, where $ C \simeq D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
+
+Lastly, a result about univalent categories that we will use a couple of times in this thesis:
+\begin{lemma}
+  For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is fully faithful and essentially surjective' are equivalent propositions (see \ref{sec:homotopy-props-sets}).
+\end{lemma}
+\begin{proof}
+  See \cite{univalent-categories}, Lemma 6.8.
+\end{proof}
+
 \section{Equality and homotopy}
-\section{hProps and hSets}
+\TODO
+
+\section{hProps and hSets}\label{sec:homotopy-props-sets}
+If we have a type $ T $ and objects $ x $ and $ y $, we can wonder how many elements $ x = y $ has.
+In set-based mathematics, this would be a nonsensical question: two elements of a set are either equal or not equal.
+Therefore, we can expect the answer to be that $ x = y $ has at most one element.
+And indeed, if we do not assume the univalence axiom, we can assume the axiom `uniqueness of identity proofs', which states that for $ p, q: x = y $, we have a proof of equality $ h: p = q $.
+
+On the other hand, suppose that we do assume the univalence axiom. Consider the type $ T = \{ -1, 1 \} $. We can construct two equivalences $ \id T, \sigma: T \simeq T $:
+\[ \id T(x) = x \quad \text{and} \quad \sigma(x) = -x. \]
+By the univalence axiom, we must have that $ T = T $ has (at least) two distinct elements, corresponding to $ \id T $ and $ \sigma $.
+Therefore, the univalence axiom is not compatible with uniqueness of identity proofs, and we see that in a univalent setting, some identity types have more than one element.
+
+This means that types in general have too little structure to serve as a foundation for mathematics that was originally set-based.
+For example, suppose that we want to define monoids, based on general types.
+We define these as types $ T $, together with a monoid operation $ \circ: T \times T \to T $ and a unit $ u: T $ which satisfies some axioms (for example, $ h_1: \prod_{f: M} f \circ u = f $).
+Now, suppose that we want to show that two of these monoids $ ((M, \circ, u), (h_1^\prime, \dots)) $ and $ ((M^\prime, \circ^\prime, u^\prime), (h_1, \dots)) $ are equal.
+We would start by showing that $ M = M^\prime $, that $ \circ = \circ^\prime $ and that $ u = u^\prime $ (actually, for the last two, we would need to transport).
+However, then we still need to show that $ (h_1, \dots) = (h_1^\prime, \dots) $, so we need to show that $ h_1 = h_1^\prime $ (both showing that $ f \circ u = f $ for all $ f $).
+This quickly becomes very unwieldy and painful.
+To prevent this, we base our definitions of structures such as groups on homotopy sets:
+\begin{definition}
+  A \iindex{mere proposition} is a type $ T $ such that for all $ x, y: T $, $ x = y $.
+\end{definition}
+
+\begin{definition}
+  A \iindex{homotopy set} is a type $ T $ such that for all $ x, y: T $, $ x = y $ is a mere proposition.
+\end{definition}
+
+\TODO
+
+\subsection{(mere) existence}
+\index{mere existence}
+\TODO
+
 \section{Transports and transport hell}
-\section{The univalence axiom}
-\section{Univalent categories}
+\TODO

### 2024-03-25 report/chapters/univalent-foundations.tex
Add a section about dependent type theory, one about homotopy and one about transports

@@
 \chapter{Univalent Foundations}
+
+\section{Dependent type theory}
+Univalent foundations takes place in a framework of type theory. In this section, we will quickly introduce some topics that we will need in subsequent sections.
+
+First of all, \iindex{type theory} is the study of types.
+A type is much like a set in set theory, it has elements (for example,$ \mathrm{true}: \mathrm{Bool} $ or $ 1: \mathbb N $), but there are important differences.
+First of all, in type theory, elements are declared together with their type, whereas in set theory, something can be an element of multiple sets, like $ 5 \in \mathbb N $ and $ 5 \in \mathbb R $.
+Secondly, equality in type theory can work a bit differently than in classical mathematics, but will cover this in the next section.
+
+One notable class of types is given by the \textit{function types}.
+For types $ A $ and $ B $, we may have the type $ A \to B $.
+An element $ f $ of this type can be combined with an element $ a $ of $ A $ to give an element $ f(b) $ of $ B $.
+
+Now, in type theory, we can assume the existence of all kinds of constructs.
+One of these constructs is \index{dependent type}\textit{dependent types}.
+A dependent type is a type which depends on values of other types.
+For example, $ \mathtt{array}(T, n) $, the type of arrays of length $ n $, with elements of type $ T $.
+If a type theory has dependent types, we talk about \iindex{dependent type theory}.
+
+Suppose that we have a type $ A $, and a dependent type which we will write $ B: A \to \TYPE $.
+
+One of the constructs which may or may not exist, is a type $ \sum_{a: A} B(a) $ called the \textit{dependent sum}, consisting of all pairs $ (a, b) $ with $ a : A $ and $ b: B(a) $.
+So every element of $ \sum_{a: A} B(a) $ consists of exactly one element $ a: A $ with a corresponding element of $ B(a) $.
+
+Another construct which may exist, is a type $ \prod_{a: A} B(a) $, consisting of all `functions' $ f $ which map elements $ a: A $ to elements $ f(a): B(a) $.
+Every element of $ \prod_{a: A} B(a) $ contains therefore elements of $ B(a) $ for all the $ a $ simultaneously.
+
+Lastly, there is a very strong connection between logic and type theory.
+This is called the \iindex{Curry-Howard correspondence} or sometimes referred to as \iindex{products as types}.
+We can view a type $ T $ as the proposition ``$ T $ has an element''.
+An element of $ T $ is then a `proof' or `witness' of this proposition.
+If the type theory is strong enough, it allows us to do mathematics in it, where:
+\begin{itemize}
+  \item A function $ f: A \to B $ that takes an argument of type $ A $ and yields a result of type $ B $ corresponds to the proof of $ B $ under the hypothesis that $ A $ holds: ``suppose that $ A $, then $ B $''.
+  \item The empty type $ \mathbf 0 $ corresponds to `false'. Note that for all types $ A $, we can construct a function $ \mathbf 0 \to A $. In other words, we can prove everything from `false'.
+  \item The unit type $ \mathbf 1 $ corresponds to `true'.
+  \item The negation of $ T $ is the function type $ T \to \mathbf 0 $.
+  \item The conjuction ``$ A $ and $ B $'' is given as the product type $ A \times B $.
+  \item The statement ``For all $ a: A $, $ B(a) $ holds'', for some dependent type $ B $ (i.e. predicate) over $ A $, is given as the dependent product $ \prod_{a: A} B(a) $.
+\end{itemize}
 
@@
 Univalent foundations seeks to be a foundation for mathematics that is in line with this principle.
-This is often done within the framework of `Martin-Löf dependent type theory', a type theory constructed by Per Martin-Löf \cite{martin-lof-type-theory}.
-This type theory has types which depend on values of (other) types (like \texttt{array(T, n)}, the type of arrays of length $ n $, with elements of type $ T $).
+This is often done within the framework of `Martin-Löf dependent type theory', a type theory developed by Per Martin-Löf \cite{martin-lof-type-theory}.
 It is a constructive type theory, so it does not automatically assume the law of excluded middle (which states that "not (not x)" implies "x") or the axiom of choice (stating that for every indexed family $ (S_i)_{i : I} $ with the $ S_i $ nonempty, there exists $ f: \prod_i S_i $), although it is compatible with these axioms, so one can still assume these alongside its usual axioms.
@@
 
-\section{Equality and homotopy}
-\TODO
-
 \section{hProps and hSets}\label{sec:homotopy-props-sets}
@@
 Therefore, we can expect the answer to be that $ x = y $ has at most one element.
-And indeed, if we do not assume the univalence axiom, we can assume the axiom `uniqueness of identity proofs', which states that for $ p, q: x = y $, we have a proof of equality $ h: p = q $.
+And indeed, if we do not assume the univalence axiom, we can assume another axiom, called `uniqueness of identity proofs', which states that for $ p, q: x = y $, we have a proof of equality $ h: p = q $.
 
-On the other hand, suppose that we do assume the univalence axiom. Consider the type $ T = \{ -1, 1 \} $. We can construct two equivalences $ \id T, \sigma: T \simeq T $:
+On the other hand, suppose that we do assume the univalence axiom. Consider the two-element type $ T = \{ -1, 1 \} $. We can construct two different equivalences $ \id T, \sigma: T \simeq T $:
 \[ \id T(x) = x \quad \text{and} \quad \sigma(x) = -x. \]
-By the univalence axiom, we must have that $ T = T $ has (at least) two distinct elements, corresponding to $ \id T $ and $ \sigma $.
+By the univalence axiom, we must have that the identity type $ (T = T) $ has (at least) two distinct elements, corresponding to $ \id T $ and $ \sigma $.
 Therefore, the univalence axiom is not compatible with uniqueness of identity proofs, and we see that in a univalent setting, some identity types have more than one element.
 
-This means that types in general have too little structure to serve as a foundation for mathematics that was originally set-based.
-For example, suppose that we want to define monoids, based on general types.
-We define these as types $ T $, together with a monoid operation $ \circ: T \times T \to T $ and a unit $ u: T $ which satisfies some axioms (for example, $ h_1: \prod_{f: M} f \circ u = f $).
-Now, suppose that we want to show that two of these monoids $ ((M, \circ, u), (h_1^\prime, \dots)) $ and $ ((M^\prime, \circ^\prime, u^\prime), (h_1, \dots)) $ are equal.
-We would start by showing that $ M = M^\prime $, that $ \circ = \circ^\prime $ and that $ u = u^\prime $ (actually, for the last two, we would need to transport).
-However, then we still need to show that $ (h_1, \dots) = (h_1^\prime, \dots) $, so we need to show that $ h_1 = h_1^\prime $ (both showing that $ f \circ u = f $ for all $ f $).
-This quickly becomes very unwieldy and painful.
-To prevent this, we base our definitions of structures such as groups on homotopy sets:
+A consequence of this is that types in general have too little structure to serve as a foundation for mathematics that was originally set-based.
+For example, suppose that we want to formalize the theory of groups.
+A group homomorphism $ f: \mathbf{Grp}(H, G) $ is defined as a function on the underlying types $ f_1: H \to G $, together with a proof that it commutes with the group operations: $ f_2: \prod_{x, y: H} f_1(x \circ y) = f_1(x) \circ f_1(y) $.
+Now, normally in group theory, to show that two homomorphisms $ f, g: \mathbf{Grp}(H, G) $ are equal, we show that $ \prod_{x: H} f_1(x) = g_1(x) $, the `data' is equal.
+However, if we are working with types instead of sets, we also need to show that the proofs of the `properties' are equal: $ f_2 = g_2 $ (note that we actually would need to transport $ f_2 $ here, for this equality to typecheck).
+This makes showing equality of morphisms much more complicated for concrete groups, and sometimes outright impossible for generic groups.
+
+To deal with this, we need the concepts of mere propositions and (homotopy) sets:
+
 \begin{definition}
@@
 
-\TODO
+Since the identity types for a homotopy set are mere propositions, a homotopy set mimicks a set in set theory, where equality between elements `is' or `is not'.
+If we restrict the underlying type of a group to be a homotopy set, it can be shown that $ \prod_{x, y: H} f_1(x \circ y) = f_1(x) \circ f_1(y) $ is a mere proposition, so $ f_2 = g_2 $ trivially.
+This is often true when translating definitions from set theory to univalent foundations: if we base our objects on homotopy sets instead of types, we only have to worry about equality of `data', the equality of `properties' follows automatically.
 
-\subsection{(mere) existence}
-\index{mere existence}
-\TODO
+For similar reasons, we restrict the hom-types $ C(c, d) $ of categories to be sets.
+Note that $ \TYPE $ is not a category under this definition (it is a `precategory', for some definition of precategory), because in general, the type of functions between sets $ S \to T $ is not a set.
 
-\section{Transports and transport hell}
-\TODO
+\section{truncation and (mere) existence}
+As mentioned before, if we want to do mathematics in a dependent type theory, we can `encode' propositions as types.
+The elements of the type correspond to the proofs that the proposition is true, see for example the identity types.
+However, we need to be careful here about the distinction between types in general and mere propositions:
+
+A proof that a type $ T $ is nonempty usually consists of giving an element $ t : T $.
+If we encode the statement ``$ T $ is nonempty'' as $ T $, and if $ T $ is not a mere proposition, then ``$ T $ is nonempty'' is not a mere proposition, so it has multiple distinct proofs.
+In some cases, this is exactly what we want, because we want to retrieve the chosen element of $ T $.
+However, in some cases, we want the fact that a set is nonempty (or any statement in general) to be a mere proposition, to avoid having to carry around a specific element and having to prove equality of two specific elements.
+For such cases, we have the `propositional truncation':
+
+\begin{definition}
+  For a type $ T $, a type $ \Vert T \Vert $ exists (\cite{hottbook}, Section 3.7) with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
+It has a recursion principle stating that for a mere proposition $ B $, a function $ f: A \to B $ induces a function $ \vert f \vert: \Vert T \Vert \to B $ that commutes with $ \vert \cdot \vert $.
+This object is called the \index{truncation!propositional}\textit{propositional truncation}.
+\end{definition}
+The propositional truncation forgets the details about a type, and only keeps the information about whether it is inhabited or not.
+The recursion principle means that if we are trying to prove a mere proposition based on some element $ \vert t \vert: \Vert T \Vert $, we can pretend that we do have a concrete element $ t: T $.
+
+There also is the concept of higher order truncations.
+For example, the \index{truncation!set}\textit{set truncation} $ \Vert A \Vert_0 $, which is a homotopy set and has an equivalence $ (\Vert A \Vert_0 \to B) \simeq (A \to B) $ for any set $ B $.
+However, these higher truncation types become increasingly harder to construct, and in this thesis, we will only need to consider the propositional truncation.
+
+Often, when we prove a theorem or lemma that ``there exists some $ x: X $ such that $ Y(x) $'', what we actually mean is that we can construct an element $ x: X $ and then an element $ y : Y(x) $ of the dependent type $ Y $ over $ X $.
+This is equivalent to having an element of $ \sum_{x: X} Y(x) $.
+However, this is in general of course not a mere proposition.
+If we want to express that the set of such $ x $ is nonempty as a mere proposition, we talk about \iindex{mere existence}:
+\begin{definition}
+  Given a dependent type $ Y $ over $ X $, if we say that there \textit{merely exists} an element $ x: X $ such that $ Y(x) $, we mean that we have an element of the propositional truncation
+  \[ h: \left(\exists x: Y(x)\right) := \left\Vert \sum_{x: X} Y(x) \right\Vert. \]
+\end{definition}
+
+For example, if we have objects in a category $ c, d: C $ and we want to talk about a retraction $ f $ of $ c $ onto $ d $, we commonly define this as ``a morphism $ f_1: C(c, d) $, such that there exists a `section': a morphism $ f_2: C(d, c) $ with $ f_2 \cdot f_1 = \id d $''.
+Now, we commonly consider $ f_1 $ to be the `data' of the retraction; we consider retractions $ f $ and $ f^\prime $ to be the same retraction if $ f_1 = f^\prime_1 $.
+This means that being a retraction is about the `mere existence' of a section.
+Note, however, that in this case, we cannot use the section in constructions, except when we are trying to prove mere propositions.
+
+\section{Equality and homotopy}
+Univalent Foundations is often mentioned together with Homotopy Type Theory, because they are related but distinct concepts. Therefore, we will mention it here.
+
+As we saw before, if we do not assume uniqueness of identity proofs, given two elements $ x, y: T $, we can have multiple distinct proofs that $ x = y $, which is counterintuitive.
+One way to think about this, is the perspective of homotopy type theory.
+In homotopy type theory, one considers a type $ T $ to be a `space', intuitively similar to a topological space, but without an explicit topology.
+The elements $ t : T $ are then the points of the space.
+Elements of the identity type $ (s = t) $ are interpreted as `paths' from $ s $ to $ t $.
+That is why the induction principle of $ (s = t) $ is called `path induction'.
+Of course, we can go higher: for $ p, q : x = y $, the elements $ (p = q) $ are `paths between paths', (path) `homotopies', `sheets' or `1-cells', for homotopies $ h, h^\prime: p = q $, the elements of $ h = h^\prime $ are paths between paths between paths, `volumes' or `2-cells' etc.
+
+If we have a `geometric' interpretation of our type theory, we can investigate the `shape' of a (nonempty) type $ T $, given by the structure of the (higher) identity types.
+
+\begin{figure}
+  \begin{subfigure}{.3\textwidth}
+    \includesvg[pretex=\tiny, width=\columnwidth]{images/homotopy-plane}
+    \caption{}
+    \label{fig:homotopy-plane}
+  \end{subfigure}
+  \begin{subfigure}{.3\textwidth}
+    \includesvg[pretex=\tiny, width=\columnwidth]{images/homotopy-cylinder}
+    \caption{}
+    \label{fig:homotopy-cylinder}
+  \end{subfigure}
+  \begin{subfigure}{.3\textwidth}
+    \includesvg[pretex=\tiny, width=\columnwidth]{images/homotopy-sphere}
+    \caption{}
+    \label{fig:homotopy-sphere}
+  \end{subfigure}
+  \caption{Different possible homotopy structures}
+\end{figure}
+
+First of all, if we have $ x, y : T $ for which $ x = y $ does not have an inhabitant, $ x $ and $ y $ lie in different `connected components'. Now, we focus on a connected type:
+
+For example, are all elements $ x, y: T $ of the type equal to each other, and are all elements $ p, q: x = y $ of all the (higher) identity types also equal in a unique way?
+Then we have a \iindex{contractible type}, which intuitively looks somewhat like a plane (Figure \ref{fig:homotopy-plane}).
+
+It is also possible that any two elements $ x, y : T $ are equal, but that there are distinct paths $ p, q: x = y $, with no homotopy between them.
+Then intuitively $ T $ looks like a circle or a tube or a projective space, or something more complicated (Figure \ref{fig:homotopy-cylinder}).
+
+\begin{remark}
+  Note that we can give the type of paths $ x = x $ a group structure and $ x = y $ is a `torsor' for this group.
+If $ x = y $ has exactly two distinct elements, the group $ x = x $ looks like $ \mathbb Z / 2 \mathbb Z $, which suggests some projective plane-like structure.
+
+  For something to look like a circle or tube, we need this group $ x = x $ to be isomorphic to $ \mathbb Z $. For an example, see \cite{circle-fundamental-group}.
+\end{remark}
+
+As a third example, consider a type $ T $ in which any two elements $ x, y : T $ are equal, and any two paths $ p, q: x = y $ have two distinct homotopies $ h, h^\prime: p = q $ between them.
+Then we can imagine the type to look somewhat like a sphere (Figure \ref{fig:homotopy-sphere}) or something more complicated.
+
+This is the lens through which homotopy type theory studies types.
+
+\section{Transport}
+
+\begin{figure}
+  \begin{subfigure}{.45\textwidth}
+    \includesvg[pretex=\tiny, width=.7\columnwidth]{images/fibration}
+    \caption{}
+    \label{fig:fibration}
+  \end{subfigure}
+  \begin{subfigure}{.45\textwidth}
+    \includesvg[pretex=\tiny, width=.7\columnwidth]{images/transport}
+    \caption{}
+    \label{fig:transport}
+  \end{subfigure}
+  \caption{A fibration with a path in the base space, giving rise to transport in the fibration}
+\end{figure}
+
+Suppose that we have a dependent type $ B: A \to UU $.
+Intuitively, $ B $ is a collection of spaces, lying over the points of $ A $ (Figure \ref{fig:fibration}).
+Now, if we have a path $ p: a = a^\prime $ in $ A $, we can use path induction to get a function $ \mathrm{transport}_p: B(a) \to B(a^\prime) $ (Figure \ref{fig:transport}).
+
+For example, this allows us to transfer an element from $ \mathtt{array}(T, n + n) $ to $ \mathtt{array}(T, 2 \cdot n) $ with transport over the path $ n + n = 2 \cdot n $.
+Also, if we assume the univalence axiom, and we have, for example, an isomorphism of groups $ f: G \cong G^\prime $ and a proof $ h $ that $ G $ is semisimple, we can transport $ h $ along the equality given by $ f $ to a proof that $ G^\prime $ is semisimple.
+
+\begin{example}\label{ex:transport-array}
+  In addition, consider the following example.
+We take $ A $ to be a type universe, and let $ B: T \mapsto \mathtt{array}(T, 3) $.
+Consider the types $ a = \{ \top, \bot \} $ and $ a^\prime = \{ 0, 1 \} $.
+We have equivalences $ \overline p $ and $ \overline q $ between $ a $ and $ a^\prime $:
+  \[ \overline p(\top) = 1, \overline p(\bot) = 0 \quad \text{and} \quad \overline q(\top) = 0, \overline q(\bot) = 1. \]
+  That means that we have distinct equalities $ p, q: a = a^\prime $.
+Now, suppose that we have an array $ x = [\top, \top, \bot]: B(a) $.
+Since $ a = a^\prime $, we would want to treat $ x $ as an element of $ B(a^\prime) $, but then we need to make a choice whether we treat it as $ [1, 1, 0] $ or $ [0, 0, 1] $ (or something else altogether).
+This is exactly the question whether we transport along $ p $ or $ q $, and therefore, when our base type is not a set, it is important to be aware that we are transporting a property along an equality, and we need to be careful which equality it is that we transport along.
+\end{example}
+
+Another place where transports occur frequently is when proving equality $ (x, y) = (x^\prime, y^\prime) $ of elements of a dependent sum $ \sum_{a: A} B(a) $.
+We can start componentwise by proving $ p: x = x^\prime $, but after this, we cannot directly prove $ q: y = y^\prime $, because these two live in different types: $ B(x) $ and $ B(x^\prime) $ respectively.
+Therefore, we need to transport, and then prove
+\[ \mathrm{transport}_p(y) = y^\prime: B(x^\prime). \]
+
+\subsection{Caution: `transport hell'}
+Now, it seems that we can transport all properties and data along equalities. And of course, that is true, but some caution needs to be taken with this when working with a proof assistant.
+
+For example, consider the situation in Example \ref{ex:transport-array}.
+As mentioned, we can transport $ x $ to get an element $ y := \mathrm{transport}_p(x) $, which is an element of $ B(a^\prime) $, but now suppose that we want to compute something using its first coefficient $ y_1 $.
+Of course, on paper it quickly becomes clear that $ y_1 = 1 $, but in practice, it takes quite some work to convince a proof assistant of that fact.
+Of course, we could write a lemma which states that for any array $ x $, any equivalence $ \overline p $ with corresponding equality $ p $, and any index $ i $,
+\[ \mathrm{transport}_p(x)_i = \overline p(x_i). \]
+However, at that point, we have more or less constructed our own function between $ B(a) $ and $ B(a^\prime) $, which is much easier to work with than $ \mathrm{transport}_p $.
+
+Experience teaches that in general, it is fine to transport properties $ b: B(a) $ of which we will never need the value, only the fact that it (merely) exists.
+On the other hand, for properties and constructions of which we might later want to use the actual value, it is much better to transfer them `by hand'.
+Often, but not always, this criterion coincides with $ B(a) $ being a mere proposition.
+
+Another case where unwanted transports often occur is when showing the equality of two complicated elements of a type.
+For example, $ ((x_1, x_2), (x_3, x_4)) = ((x^\prime_1, x^\prime_2), (x^\prime_3, x^\prime_4)) $, both elements of
+\[ \sum_{(x_1, x_2): \sum_{a: A} B(a)} \sum_{x_3 : C(x_1)} D(x_1, x_2, x_3). \]
+This example involves proofs:
+\begin{itemize}
+  \item $ p : x_1 = x^\prime_1 $;
+  \item $ q : \mathrm{transport}_p(x_2) = x^\prime_2 $;
+  \item $ r : \mathrm{transport}_{(p, q)}(x_3) = x^\prime_3 $, which can be simplified to $ \mathrm{transportf}_p(x_3) = x^\prime_3 $, since $ x_3 $ does not depend on $ x_2 $
+  \item and finally $ s: \mathrm{transport}_{((p, q), r)}(x_4) = x^\prime_4 $.
+\end{itemize}
+In general, these latter proofs $ r $ and $ s $ are very challenging and best avoided whenever possible.
+The situation in which one has to work with such complicated transports, which make a proof (seemingly unnecesarily) complicated is called \iindex{transport hell}.
+Some mathematical tools have been developed (see for example \ref{sec:displayed-categories} about displayed categories) that help avoid transport hell in some cases.
+Additionally, the structure or `strategy' of a proof can sometimes be changed in order to avoid the worst of the transports.
+However, it is often not possible to avoid transports altogether, and this is one of the reasons why proving something in a proof assistant takes a lot more work than proving it on paper.

### 2024-03-26 report/chapters/univalent-foundations.tex
Add a short piece about type systems

@@
 
-First of all, \iindex{type theory} is the study of types.
-A type is much like a set in set theory, it has elements (for example,$ \mathrm{true}: \mathrm{Bool} $ or $ 1: \mathbb N $), but there are important differences.
+First of all, \iindex{type theory} is the study of `type systems'.
+A \iindex{type system} is a collection of terms or elements, each of which has a corresponding type.
+A type is much like a set in set theory in that it has elements (for example, $ \mathrm{true}: \mathrm{Bool} $ or $ 1: \mathbb N $), but there are important differences.
 First of all, in type theory, elements are declared together with their type, whereas in set theory, something can be an element of multiple sets, like $ 5 \in \mathbb N $ and $ 5 \in \mathbb R $.
@@
 One notable class of types is given by the \textit{function types}.
-For types $ A $ and $ B $, we may have the type $ A \to B $.
+For types $ A $ and $ B $, our type system might have the type $ A \to B $.
 An element $ f $ of this type can be combined with an element $ a $ of $ A $ to give an element $ f(b) $ of $ B $.
+Of course, the elements of this type are thought of (and usually are) functions from $ A $ to $ B $.
 
-Now, in type theory, we can assume the existence of all kinds of constructs.
+Now, a type system may or may not have all kinds of constructs.
 One of these constructs is \index{dependent type}\textit{dependent types}.
@@
 For example, $ \mathtt{array}(T, n) $, the type of arrays of length $ n $, with elements of type $ T $.
-If a type theory has dependent types, we talk about \iindex{dependent type theory}.
+The study of type systems that have such dependent types is called \iindex{dependent type theory}.
 
@@
 
-One of the constructs which may or may not exist, is a type $ \sum_{a: A} B(a) $ called the \textit{dependent sum}, consisting of all pairs $ (a, b) $ with $ a : A $ and $ b: B(a) $.
-So every element of $ \sum_{a: A} B(a) $ consists of exactly one element $ a: A $ with a corresponding element of $ B(a) $.
+One of the possible constructs in a type system is a type $ \sum_{a: A} B(a) $ called the \textit{dependent sum}, consisting of all pairs $ (a, b) $ with $ a : A $ and $ b: B(a) $.
+So every element of $ \sum_{a: A} B(a) $ gives an element of one $ B(a) $ (for some $ a : A $).
+Note that for the constant dependent type $ B(a) = B $, $ \sum_{a: A} B $ is the product type $ A \times B $.
 
 Another construct which may exist, is a type $ \prod_{a: A} B(a) $, consisting of all `functions' $ f $ which map elements $ a: A $ to elements $ f(a): B(a) $.
-Every element of $ \prod_{a: A} B(a) $ contains therefore elements of $ B(a) $ for all the $ a $ simultaneously.
+Every element of $ \prod_{a: A} B(a) $ gives therefore elements of all the $ B(a) $ simultaneously.
+Note that $ \prod_{a: A} B $ is the function type $ A \to B $.
 
@@
 An element of $ T $ is then a `proof' or `witness' of this proposition.
-If the type theory is strong enough, it allows us to do mathematics in it, where:
+If the type system is strong enough, it allows us to do mathematics in it, where:
 \begin{itemize}
   \item A function $ f: A \to B $ that takes an argument of type $ A $ and yields a result of type $ B $ corresponds to the proof of $ B $ under the hypothesis that $ A $ holds: ``suppose that $ A $, then $ B $''.
+Note that the notation $ A \to B $ also makes sense if we think of $ A $ and $ B $ propositions.
   \item The empty type $ \mathbf 0 $ corresponds to `false'. Note that for all types $ A $, we can construct a function $ \mathbf 0 \to A $. In other words, we can prove everything from `false'.
@@
   \item The conjuction ``$ A $ and $ B $'' is given as the product type $ A \times B $.
+  \item The disjunction ``$ A $ or $ B $'' is given as the propositional truncation of the coproduct, union or sum type $ A \sqcup B $.
   \item The statement ``For all $ a: A $, $ B(a) $ holds'', for some dependent type $ B $ (i.e. predicate) over $ A $, is given as the dependent product $ \prod_{a: A} B(a) $.
+\end{itemize}
+If we think of types as propositions, the question whether some axiom is assumed or not becomes the question whether some (family of) type(s) is inhabited.
+Note that most of the axioms that we list here require the notion of mere propositions, propositional truncation and mere existence, which we will cover from Section \ref{sec:homotopy-props-sets} onwards.
+\begin{itemize}
+  \item If for all mere propositions $ A $, the type $ \Vert A \lor (A \to \mathbf 0) \Vert $ is inhabited, we say that the type system assumes the \iindex{axiom of excluded middle}: ``Either $ A $ is true, or $ A $ is not true''.
+This is axiom allows us to prove $ A $ from `not not $ A $'.
+  \item If for all dependent types $ C $ over $ A $ and $ B $, the type
+    \[ \left(\prod_{a: A} \exists (b: B), C(a, b) \right) \to \exists (f: A \to B), \prod_{a: A} C(a, f(a)) \]
+    is inhabited, we say that the type system assumes the \index{axiom of choice!propositional}\textit{propositional axiom of choice}: ``The product of a family of nonempty sets is nonempty''.
+  \item In any type theory which has the required constructs, the following holds: For all dependent types $ C $ over $ A $ and $ B $, the type
+    \[ \left(\prod_{a: A} \sum_{b: B} C(a, b) \right) \to \sum_{f: A \to B} \prod_{a: A} C(a, f(a)) \]
+    is inhabited. This axiom (or actually more of a theorem) is called the \index{axiom of choice!type theoretic}\textit{type theoretic axiom of choice}.
 \end{itemize}
@@
 This is often done within the framework of `Martin-Löf dependent type theory', a type theory developed by Per Martin-Löf \cite{martin-lof-type-theory}.
-It is a constructive type theory, so it does not automatically assume the law of excluded middle (which states that "not (not x)" implies "x") or the axiom of choice (stating that for every indexed family $ (S_i)_{i : I} $ with the $ S_i $ nonempty, there exists $ f: \prod_i S_i $), although it is compatible with these axioms, so one can still assume these alongside its usual axioms.
+It is a family of dependent type systems with dependent products, dependent sums, an empty type, a unit type and union types.
+It is a constructive type theory, so it does not automatically assume the axiom of excluded middle or the propositional axiom of choice.
+It is however compatible with these axioms, so one can still assume these alongside its usual axioms.
 
@@
 
+Note that for the Curry-Howard correspondence, the product or conjunction $ A \land B = A \times B $ of two mere propositions is again a mere proposition.
+However, the union $ A \sqcup B $ is not necessarily a mere proposition.
+To make it into a mere proposition, we need to take the propositional truncation $ A \lor B = \Vert A \sqcup B \Vert $.
+
 \section{Equality and homotopy}

### 2024-03-26 report/chapters/univalent-foundations.tex
Write about universe levels

@@
 Secondly, equality in type theory can work a bit differently than in classical mathematics, but will cover this in the next section.
+
+So if we have types and elements, are types also elements of some type?
+This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system (see \cite{girard}).
+This is just like having a `set of all sets', which results in problematic questions like ``does its subset, containing only the sets which do not contain itself, contain itself?'' This is usually solved by either stating that types do not themselves have a type, or by assuming the existence of \textit{type universes} $ U_1, U_2, \dots $, such that every type is an element of some $ U_i $.
+Note that universes are allowed to be inclusive or not: we may have $ U_n \subseteq U_{n + 1} $.
+In this thesis, we will not explicitly mention particular universes.
+We will just write $ \TYPE $ to denote some type universe (or its category of types and functions).
+This is called \textit{typical ambiguity}, meaning that every theorem holds for all (suitable) assignments of universes to these instances of $ \TYPE $.
 

### 2024-03-28 report/chapters/previous-work.tex
Add more properties about R, show that it is not locally cartesian closed

@@
 
+In the next chapter, the `universal object' $ U : \R $, given by the identity $ \lambda x_1, x_1 $, plays a major role. Note that $ \varphi(U) = L $.
+
+Note that this category has many (isomorphic, but not equal for nontrivial $ L $) terminal objects, given by $ I_c := \lambda x_1, \iota_{0, 1}(c) : \R $ for any $ c: L_0 $.
+These are terminal because for $ f: A \to I_c $, we have $ f = I_c \circ f = I_c $.
+Note that $ \varphi(I_c)_n = \{ \iota_{0, n}(c) \} $.
+We will choose $ I = \lambda x_1 x_2, x_2 : \R $ as our main example of the terminal object.
+
+We might wonder whether the category also has an initial object $ O $. However, for any $ c: L_0 $, we would have a morphism (with the same term as the terminal object)
+\[ \lambda x_1, \iota_{0, 1}(c) : A \to U, \]
+so if $ L $ is nontrivial, $ \R $ has no initial object.
+
+The category has binary products with projections and product morphisms
+\[ A_1 \times A_2 = \langle p_1, p_2 \rangle, \quad p_i = A_i \circ \pi_i \quad \text{and} \quad \langle f, g \rangle. \]
+Recall that for any object $ A $, we have $ A = \id A $, which for $ A_1 \times A_2 $ is $ \langle p_1, p_2 \rangle $ by the universal property of the product, which explains why the product is of this form.
+
+The category also has exponential objects
+\[ C^B = \lambda x_1, C \circ x_1 \circ B \]
+with evaluation morphism $ \epsilon_{BC}: C^B \times B \to C $ given by
+\[ \epsilon_{BC} = \lambda x_1, C(\pi_1 x_1 (B (\pi_2 x_1))), \]
+which is universal because we can lift a morphism $ f: \R(A \times B, C) $ to a morphism $ \psi(f): \R(A, C^B) $ given by
+\[ \psi(f) = \lambda x_1 x_2, f (x_1, x_2). \]
+Note that for $ g: \R(A, C^B) $, the inverse $ \psi^{-1}(g) $ is given by
+\[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle = \lambda x_1, g (\pi_1 x_1) (\pi_2 x_1): \R(A \times B, C). \]
+Also note that
+\[ \lambda x_1, C \circ x_1 \circ B = C^B = \id{C^B} = \psi(\epsilon_{BC}). \]
+The first representation shows that $ \varphi(C^B)_0 = \R(B, C) $, as we would expect.
+
+Now, we might wonder whether there exists some $ A: \R $ such that $ \varphi(A)_0 = \emptyset $. However, for any $ c : L_0 $, we have $ A c : \varphi(A)_0 $, because
+\[ A c = (A \circ A) c = A (A c). \]
+Note that we can lift constants from $ \varphi(A)_0 $ to any $ \varphi(A)_n $, so they are all nonempty.
+
+Combining this with the embedding of $ \R \hookrightarrow \Pshf L $, we would expect $ \R $ to not have all pullbacks.
+This is because in $ \Pshf L $, for a cospan $ B \xrightarrow f A \xleftarrow g C $ with $ f_n(B_n) \cap g_n(C_n) = \emptyset $, we would have $ Q_n = \emptyset $, which could never happen with an object coming from $ \R $.
+Note, however, that this can not be made rigorous, because a fully faithful embedding reflects limits, but does not preserve them.
+
+However, it is true that $ \R $ does not have all pullbacks (if $ L $ is nontrivial). Consider for example the following cospan:
+\[ I \xrightarrow f U \xleftarrow g I \]
+for different $ f, g: \R(I, U) $.
+For example, $ f = (\lambda x_1, \iota_{0, 1}(\pi_1)) $ and $ g = (\lambda x_1, \iota_{0, 1}(\pi_2)) $.
+Now, take any object $ Q: \R $.
+Note that we have a unique morphism $ I: \R(Q, I) $.
+Then we have the following diagram:
+\begin{center}
+  \begin{tikzcd}
+    Q \arrow[r, "I"] \arrow[d, "I"] & I \arrow[d, "g"]\\
+    I \arrow[r, "f"] & U
+  \end{tikzcd}
+\end{center}
+with
+\[ f \circ I = f \not = g = g \circ I, \]
+so the diagram does not commute, and $ Q $ is not a pullback of this cospan.
+
 \section{Scott's Representation Theorem}
@@
 
-  This category has a terminal object $ I = \lambda x_1 x_2, x_2 : \R $.
-
-  The category has binary products with projections and product morphisms
-  \[ A_1 \times A_2 = \langle p_1, p_2 \rangle, \quad p_i = A_i \circ \pi_i \quad \text{and} \quad \langle f, g \rangle. \]
-
-  The category also has exponential objects
-  \[ C^B = \lambda x_1, B \circ x_1 \circ C \]
-  with evaluation morphism $ \epsilon_{BC}: C^B \times B \to C $ given by
-  \[ \epsilon_{BC} = \lambda x_1, C(\pi_1 x_1 (B (\pi_2 x_1))), \]
-  which is universal because we can lift a morphism $ f: \R(A \times B, C) $ to a morphism $ \varphi(f): \R(A, C^B) $ given by
-  \[ \varphi(f) = \lambda x_1 x_2, f (x_1, x_2). \]
-  Note that for $ g: \R(A, C^B) $, the inverse $ \varphi^{-1}(g) $ is given by
-  \[ \epsilon \circ \langle g \circ \pi_1, B \circ \pi_2 \rangle = \lambda x_1, g (\pi_1 x_1) (\pi_2 x_1): \R(A \times B, C). \]
-
-  Now, consider the object $ U = \lambda x_1, x_1 : \R $.
   Note that for all $ A: \R $, we have morphisms $ A: \R(U, A) $ and $ A: \R(A, U) $, which exhibit $ A $ as a retract of $ U $.
@@
 Now, some categories are not locally cartesian closed.
-That is: not all substitution functors $ \alpha^* $ exist or have a right adjoint.
-One way to look at this, is that not all morphisms $ X \to A $ represent a family of objects.
-In these categories, we can carefully choose a subset of the morphisms to represent our indexed families.
-We will call a morphism representing an indexed family a \iindex{display map}.
-In most cases, we have quite a bit of choice which maps we want to take as our display maps.
+That is: not all pullback/substitution functors $ \alpha^* $ exist or have a right adjoint.
+For example, $ \R $ does not have all pullbacks, so the substitution functors do not always exist.
+One way to look at this, is that in such a category not every morphism $ X \to A $ represents a family of objects.
+In such a category, we can carefully choose a subset of the morphisms to represent our indexed families.
+We will call a morphism that we choose to represent an indexed family a \iindex{display map}.
+In most cases, we have quite a bit of choice how big we want our class of display maps to be.
 However, to make sure that indexed families are well-behaved, a class of display maps needs to have some properties:

### 2024-04-08 report/chapters/previous-work.tex
Show that R does not have coproducts

@@
 \chapter{Previous work in categorical semantics}
+
+\begin{tabular}{|c|c|c|}\hline
+  $ K $ & $ \lambda xy.x $ & constant \\\hline
+  $ S $ & $ \lambda xyz.xz(yz) $ & \\\hline
+  $ I $ & $ \lambda x.x = SKK $ & identity \\\hline
+  $ Y $ & $ \lambda f.(\lambda x.f (xx))(\lambda x.f (xx)) $ & ﬁxpoint \\\hline
+  $ \bot $ & $ (\lambda x.xx)(\lambda x.xx) = (SII)(SII) = YI $ & bottom \\\hline
+  $ P $ & $ \lambda f gx.g(f x) = S(K(S(S(KS)K)))K $ & composition \\\hline
+  $ Q $ & $ \lambda f gax.ga(f ax) $ & ﬁbred composition \\\hline
+  $ \langle \rangle $ & $ \lambda xyz.zxy $ & pairing \\\hline
+  $ 0 $ & $ \lambda xy.x = K $ & left projection \\\hline
+  $ 1 $ & $ \lambda xy.y = KI $ & right projection \\\hline
+\end{tabular}
 
@@
 
-Note that this category has many (isomorphic, but not equal for nontrivial $ L $) terminal objects, given by $ I_c := \lambda x_1, \iota_{0, 1}(c) : \R $ for any $ c: L_0 $.
+Note that $ \R $ has many (isomorphic, but not equal for nontrivial $ L $) terminal objects, given by $ I_c := \lambda x_1, \iota_{0, 1}(c) : \R $ for any $ c: L_0 $.
 These are terminal because for $ f: A \to I_c $, we have $ f = I_c \circ f = I_c $.
@@
 
-We might wonder whether the category also has an initial object $ O $. However, for any $ c: L_0 $, we would have a morphism (with the same term as the terminal object)
+We might wonder whether $ \R $ also has an initial object $ O $. However, for any $ c: L_0 $, we would have a morphism (with the same term as the terminal object)
 \[ \lambda x_1, \iota_{0, 1}(c) : A \to U, \]
@@
 
-The category has binary products with projections and product morphisms
+$ \R $ has binary products with projections and product morphisms
 \[ A_1 \times A_2 = \langle p_1, p_2 \rangle, \quad p_i = A_i \circ \pi_i \quad \text{and} \quad \langle f, g \rangle. \]
@@
 
-The category also has exponential objects
+$ \R $ also has exponential objects
 \[ C^B = \lambda x_1, C \circ x_1 \circ B \]
@@
 so the diagram does not commute, and $ Q $ is not a pullback of this cospan.
+
+Taylor notes (\cite{taylor}, Section 1.5) that the objects in $ \R $ have very strong properties with respect to fixpoints.
+One of the properties also arises via Lawvere's fixed point theorem (\cite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint.
+That is, there exists $ s: I \to B $ such that $ f \circ s = s $.
+Working out the proof even yields an explicit term:
+\[ s = \lambda i, (\lambda x, f (x x)) (\lambda x, f (x x)). \]
+Indeed, $ s = \lambda i, f ((\lambda x, f (x x)) (\lambda x, f (x x))) = f \circ s $, and $ B \circ s = B \circ f \circ s = s = s \circ I $, so $ s : \R(I, B) $.
+
+From this, Taylor deduces (\cite{taylor}, \S 1.5.12) that $ \R $ does not have all coproducts if $ L $ is nontrivial, because suppose that $ \R $ has all coproducts.
+Then $ B = I + I $ is a `boolean algebra object': We define $ \bot, \top: I \to B $ to be the injections on the left and right components.
+Since $ \R $ is cartesian closed, binary products distribute over binary coproducts, so we have $ B \times B \cong ((I \times I) + (I \times I)) + ((I \times I) + (I \times I)) $, and note that $ I \times I \cong I $.
+Using the universal property of the coproduct, we can define $ \lnot: B \to B $ componentwise as $ \lnot = [\top, \bot] $, the coproduct arrow
+\begin{center}
+  \begin{tikzcd}[row sep = .3in]
+    I \arrow[r, "\bot"] \arrow[rd, "\top"'] & I + I \arrow[d, dashed, "{[\top, \bot]}"description] & I \arrow[l, "\top"'] \arrow[ld, "\bot"]\\
+    & I + I &
+  \end{tikzcd}
+  % \begin{tikzcd}[row sep = .3in]
+  %   I \arrow[rrrd, "\bot"'] \arrow[r, "\bot"] & I + I \arrow[rrd, "{[\bot, \bot]}" description, dashed] \arrow[rr, bend left] & I \arrow[rd, "\bot"] \arrow[l, "\top"'] & I + I + I + I \arrow[d, dashed, "{[[\bot, \bot], [\bot, \top]]}" description] & I \arrow[ld, "\bot"'] \arrow[r, "\bot"] & I + I \arrow[lld, "{[\bot, \top]}" description, dashed] \arrow[ll, bend right] & I \arrow[llld, "\top"] \arrow[l, "\top"'] \\
+  %   & & & I + I & & &
+  % \end{tikzcd}
+\end{center}
+Note that by the definition of $ \lnot $, $ \lnot \circ \bot = \top $.
+Similarly, we define $ \land, \lor : B \times B \to B $ as $ \land = [[\bot, \bot], [\bot, \top]] $ and $ \lor = [[\bot, \top], [\top, \top]] $.
+Using the same universal property, we can also verify some properties of $ \bot, \top, \land $ and $ \lnot $, like the fact that the following diagrams commute:
+\begin{center}
+  \begin{tikzcd}[column sep = .5in]
+    B \arrow[rd, "{\id B}"] \arrow[r, "{\langle \id B, \id B \rangle}"] & B \times B \arrow[d, "\land"]\\
+    & B
+  \end{tikzcd}
+  \begin{tikzcd}[column sep = .5in]
+    B \arrow[d, "!"] \arrow[r, "{\langle \lnot, \id B \rangle}"] & B \times B \arrow[d, "\land"]\\
+    I \arrow[r, "\bot"] & B
+  \end{tikzcd}
+\end{center}
+for $ !: B \to I $ the terminal projection.
+We do this by checking, for example, that $ \id B \circ \top = \land \circ \langle \id B, \id B \rangle \circ \top $ and $ \id B \circ \bot = \land \circ \langle \id B, \id B \rangle \circ \bot $.
+Now, as mentioned above, every endomorphism has a fixed point.
+In particular, we have some $ \star: I \to B $ such that $ \lnot \circ \star = \star $.
+Now, note that
+\[ \star = \land \circ \langle \id B, \id B \rangle \circ \star = \land \circ \langle \star, \star \rangle = \land \circ \langle \star, \lnot \circ \star \rangle = \land \circ \langle \id B, \lnot \rangle \circ \star = \bot \circ !
+\circ \star = \bot \]
+and then
+\[ \bot = \star = \lnot \circ \star = \lnot \circ \bot = \top. \]
+Now, for any object $ A: \R $ and any two global elements $ f, g: I \to A $, we have the following diagram:
+\begin{center}
+  \begin{tikzcd}
+    I \arrow[r, shift left, "\bot"] \arrow[r, shift right, "\top"'] \arrow[rr, bend left, "f"] \arrow[rr, bend right, "g"'] & I + I \arrow[r, "{[f, g]}"] & A
+  \end{tikzcd}
+\end{center}
+and we have
+\[ f = [f, g] \circ \bot = [f, g] \circ \top = g. \]
+In particular, for any two objects $ A, A^\prime: \R $,
+\[ \R(A^\prime, A) \simeq \R(I \times A^\prime, A) \simeq \R(I, A^{A^\prime}) \simeq \{ \star \}, \]
+so $ \R $ the trivial category and $ L $ is trivial.
 

### 2024-04-10 report/chapters/category-theory.tex
Add fibrations, write about the extend of the equivalence R^A <-> R / A

@@
 Of course, we can do this \textit{externally} using a set $ A $, and picking an object $ X_a : C $ for every element $ a : A $.
+We then have a category of such families $ C^A $, with objects $ (X_a)_a $ and morphisms $ (f_a)_a: C^A((X_a)_a, (Y_a)_a) $, with $ f_a: X_a \to Y_a $.
+We write $ C^A $ because we can view this as just the $ A $-fold power of $ C $.
+Now, this assignment of categories $ A \mapsto C^A $ can be turned into a contravariant (pseudo)functor of $ 2 $-categories $ \op \SET \to \Cat $.
+It sends a morphism $ f: A \to B $ to the `relabeling' or `substitution' functor $ C^B \to C^A $, $ (X_b)_b \mapsto (X_{f(a)})_a $.
+
 However, there is also an \textit{internal} representation, as a morphism $ X \to A $.
+We can turn the collection of these morphisms over all the $ A : C $ simultaneously into a category $ C^2 $ (abusing notation a bit, writing $ 2 $ for the two-point category $ \bullet \to \bullet $).
+Then taking codomains $ (X \to A) \mapsto A $ gives a functor $ C^2 \to C $.
+The fiber of this functor above $ A $ is the slice category $ (C \downarrow A) $.
 
-Note that in $ \SET $, the external and internal ways of indexing are equivalent, because given a family $ (X_a)_a $ we can construct a morphism $ f: \sum_{a : A} X_a \to A $ and conversely, we can recover the family $ (X_a)_a $ as $ (f^{-1}(a))_a $.
+In $ \SET $, the external and internal ways of indexing are actually equivalent, because given a family $ (X_a)_a $ we can construct a morphism $ f: \sum_{a : A} X_a \to A $ and conversely, we can recover the family $ (X_a)_a $ as $ (f^{-1}(a))_a $.
 
-In $ \SET $, given a family $ (X_a)_a $ over $ A $ and a morphism $ \alpha: B \to A $, we get a family $ X_{\alpha(b)} $ over $ B $.
+Also note that for $ \SET $, if we consider an indexed family $ (X_a)_a $ as some function $ X: A \to \SET $, then substitution over $ \alpha: B \to A $ is just given by postcomposition $ X \circ \alpha: B \to \SET $.
 It turns out that in the internal representation this arises as the pullback
@@
 This can be turned into a pullback or `substitution' functor $ \alpha^* $, which Taylor calls $ \mathtt{P}\alpha $.
+This turns the functor $ \SET^2 \to \SET $ into a fibration.
 We can construct $ \alpha^* : (C \downarrow A) \to (C \downarrow B) $ for any category $ C $ with pullbacks and any morphism $ \alpha: C(B, A) $.
+The existence of this pullback makes the functor $ C^2 \to C $ into a fibration.
 
@@
 
-Apart from having dependent sums and products, there also is the following theorem that shows the significance locally cartesian closedness:
+Apart from having dependent sums and products, there also is the following theorem that shows the significance of locally cartesian closedness:
 \begin{lemma}\label{lem:locally-cartesian-closed}

### 2024-04-10 report/chapters/previous-work.tex
Add fibrations, write about the extend of the equivalence R^A <-> R / A

@@
 
-In the next chapter, the `universal object' $ U : \R $, given by the identity $ \lambda x_1, x_1 $, plays a major role. Note that $ \varphi(U) = L $.
+In the next chapter, the `universal object' $ U : \R $, given by the identity $ \lambda x_1, x_1 $, plays a major role.
+Note that for all $ A: \R $, we have morphisms $ A: \R(U, A) $ and $ A: \R(A, U) $, which exhibit $ A $ as a retract of $ U $.
+Also note that $ \varphi(U) = L $.
 
@@
 \[ \R(A^\prime, A) \simeq \R(I \times A^\prime, A) \simeq \R(I, A^{A^\prime}) \simeq \{ \star \}, \]
-so $ \R $ the trivial category and $ L $ is trivial.
+so $ \R $ is the trivial category and $ L $ is trivial.
 
@@
 \begin{proof}
-  Let $ L $ be a $ \lambda $-theory. Scott considers the category $ \R $.
+  Let $ L $ be a $ \lambda $-theory. Scott considers its category of retracts $ \R $, with `universal object' $ U $.
 
-  Note that for all $ A: \R $, we have morphisms $ A: \R(U, A) $ and $ A: \R(A, U) $, which exhibit $ A $ as a retract of $ U $.
-In particular, $ U^U $ is a retract of $ U $, so $ U $ is a reflexive object.
+  Note that $ U^U $ is a retract of $ U $, so $ U $ is a reflexive object.
 
@@
 For example, $ \R $ does not have all pullbacks, so the substitution functors do not always exist.
+In such a category $ C $, the functor $ C^2 \to C $ is not a fibration.
 One way to look at this, is that in such a category not every morphism $ X \to A $ represents a family of objects.
@@
 We will call a morphism that we choose to represent an indexed family a \iindex{display map}.
-In most cases, we have quite a bit of choice how big we want our class of display maps to be.
-However, to make sure that indexed families are well-behaved, a class of display maps needs to have some properties:
+In most cases, we have quite a bit of choice how big we want our subtype of display maps to be.
+However, to make sure that indexed families are well-behaved, the subtype of display maps needs to have some properties:
 \begin{enumerate}
@@
 \begin{remark}
-  A `maximal' example of a class of display maps is, for example, in the category $ \SET $, where we can take our class of display maps to equal the class of all morphisms of $ C $.
+  A `maximal' example of a subtype of display maps is, for example, in the category $ \SET $, where we can take our subtype of display maps to equal the full type of all morphisms of $ C $.
 \end{remark}
 \begin{remark}
-  A `minimal' example of a class of display maps is the class of (maps isomorphic to) product projections in a category with finite products.
+  A `minimal' example of a subtype of display maps is the subtype of (maps isomorphic to) product projections in a category with finite products.
 In this case, all indexed families are constant, and then dependent sums and products become binary products and exponential objects.
@@
 
-Now, let $ C $ be a category with a class of display maps $ D $.
-We will denote the class of display maps from $ X $ to $ A $ with $ D(X, A) \subseteq C(X, A) $.
+Now, let $ C $ be a category with a subtype of display maps $ D \subseteq C $.
+We will denote the subtype of display maps from $ X $ to $ A $ with $ D(X, A) \subseteq C(X, A) $.
 For any $ A : C $, we get a category $ (C \downarrow_D A) $ as a full subcategory of the slice category $ (C \downarrow A) $, with as objects the display maps $ f: D(X, A) $.
@@
 
-First of all, Taylor considers `functions' $ X: A \to \R_0 $ for some $ A : \R_0 $.
-He characterizes these functions as the $ \lambda $-terms that satisfy $ X \circ A = X $ and $ \lambda x_1, (X x_1) \circ (X x_1) = X $.
-Taylor then constructs global dependent sums as
-\[ \sum_A X = \lambda x_1, (A (\pi_1 x_1), X (\pi_1 x_1) (\pi_2 x_1)). \]
-Note that with the embedding in Definition \ref{def:retracts-embedding}, we can consider this as consisting of pairs $ (a, x) $ with $ a : A $ and $ x : X a $, which is exactly what we would expect from a dependent sum.
+Taylor starts out with a kind of `external' representation of indexed families $ (X_a)_a $ in $ \R $. He denotes these as `functions' $ A \to \R_0 $. They are the elements $ X: L_0 $ with
+\[ X \circ A = X \quad \text{and} \quad (\lambda x_1, (X x_1) \circ (X x_1)) = X. \]
+These $ X $ form a category $ \R^A $, with the morphisms in $ \R^A(X, Y) $ given by $ f: L_0 $ with $ f \circ A = f $ and $ (\lambda x_1, (Y x_1) \circ (f x_1) \circ (X x_1)) = f $.
+The identity on $ X $ is given by $ X $, and the composition is given by $ f \cdot g = \lambda x_1, g x_1 \circ f x_1 $.
+
+Taylor shows that these categories $ \R^A $ are cartesian closed.
+He notes that assigning these categories $ \R^A $ to objects $ A: \R $ again constitutes a contravariant (pseudo)functor $ \op \R \to \Cat $, sending morphisms $ A \to B $ to precomposition functors $ \R^B \to \R^A $.
+
+For $ A: \SET $, we have an equivalence between the elements of $ \SET^A $ and the elements of the fiber $ (\SET \downarrow A) $ of the fibration $ \SET^2 \to \SET $.
+Now, in the case of some $ A: \R $, we can construct a `global dependent sum' functor $ \sum_A : \R^A \to (\R \downarrow A) $, which sends $ X: \R^A $ to
+\[ \sum_A X = \lambda x_1, (A (\pi_1 x_1), X (\pi_1 x_1) (\pi_2 x_1)), \]
+together with a projection morphism $ p_X: \sum_A X \to A $ given by $ \lambda x_1, A(\pi_1 x_1) $.
+Note that with the embedding in Definition \ref{def:retracts-embedding} into $ \Pshf L $, we can consider $ \sum_A X $ as consisting of pairs $ (a, x) $ with $ a : A $ and $ x : X a $, which is exactly what we would expect from a dependent sum.
+$ \sum_A $ sends a morphism $ f: X \to Y $ to
+\[ \sum_A f = \lambda x_1, ( A (\pi_1 x_1), f (\pi_1 x_1) (\pi_2 x_1) ) : \R\left(\sum_A X, \sum_A Y\right) \]
+
+Now, this is fully faithful: given a morphism $ g: \R\left(\sum_A X, \sum_A Y\right) $, we take
+\[ \psi(g) = \lambda x_1 x_2, \pi_2 (g (x_1, x_2)). \]
+For verifying that $ \psi(g) $ is indeed a morphism in $ \R^A(X, Y) $, it helps to recall that $ g \circ \sum_A X = g = \sum_A Y \circ g $ and $ p_Y \circ g = p_X $.
+Since $ \psi(\sum_A f) = f $ for all $ f: \R^A(X, Y) $ and $ \sum_A \psi(g) = g $ for all $ g: \R(\sum_A X, \sum_A Y) $, $ \sum_A $ is indeed fully faithful.
+
+On the other hand, $ \sum_A $ is generally not surjective.
+To mitigate this somewhat, we can choose our subtype $ D $ of display maps in such a way that the restriction $ \R^A \to (C \downarrow_D A) $ becomes essentially surjective.
 
 \begin{definition}
-  For $ \R $, we will take a morphism $ f: X \to A $ to be a display map if we have some $ Y : A \to R_0 $ like above, and some isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ such that $ f = g \cdot p_1 $ with $ p_1 : \sum_A Y \to A $ given by $ \lambda x_1, A (\pi_1 x_1) $.
+  For $ \R $, we will consider a morphism $ f: X \to A $ to be a display map if we have some $ Y : \R^A $ like above, and some isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ such that $ f = g \cdot p_Y $:
+  \begin{center}
+    \begin{tikzcd}
+      X \arrow[rd, "f"] \arrow[rr, "g"] & & \sum_A Y \arrow[ld, "p_1"]\\
+      & A
+    \end{tikzcd}
+  \end{center}
 \end{definition}
@@
   Hyland actually gives a different characterization of Taylor's display maps.
-He claims that Taylor takes the display maps $ X \to A $ to be the retracts in $ (C \downarrow A) $ of $ p_1: A \times U \to A $,
+He claims that Taylor takes the display maps $ X \to A $ to be the retracts in $ (\R \downarrow A) $ of $ p_1: A \times U \to A $,
   the projection onto the first coordinate. The two characterizations are equivalent:
 
-  Given $ Y: A \to \R_0 $, $ Y a $ is a retract of $ U $ for all $ a $.
+  Given $ Y: \R^A $, intuitively $ Y a $ is a retract of $ U $ for all $ a $.
 Concretely, both morphisms $ r : A \times U \to \sum_A Y $ and $ s : \sum_A Y \to A \times U $ are given by $ \sum_A Y $ and these commute with the projection to $ A $.
-Therefore, if we have an isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ in $ (C \downarrow A) $, then $ \sum_A Y \cdot g^{-1} $ and $ g \cdot \sum_A Y $ make $ X $ into a retract of $ A \times U $.
+Therefore, if we have an isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ in $ (\R \downarrow A) $, then $ \sum_A Y \cdot g^{-1} $ and $ g \cdot \sum_A Y $ make $ X $ into a retract of $ A \times U $.
 
-  Conversely, given a retraction $ r : A \times U \to X $ and section $ s : X \to A \times U $ in $ (C \downarrow A) $, the term
-  \[ \lambda x_1 x_2, \pi_2 (s (r (x_1, x_2))) \]
-  gives a function $ Y : A \to \R_0 $.
+  Conversely, given a retraction $ r : A \times U \to X $ and section $ s : X \to A \times U $ in $ (\R \downarrow A) $, we have
+  \[ Y = \lambda x_1 x_2, \pi_2 (s (r (x_1, x_2))) : \R^A. \]
   Using the properties of $ r $ and $ s $ and the definition of $ \sum_A Y $, one can show that $ r $ gives a morphism $ \sum_A Y \to X $ and $ s $ gives a morphism $ X \to \sum_A Y $, and that $ r \circ s = \id{\sum_A Y} $.
@@
 \begin{remark}
-  Recall that if $ L $ is nontrivial, $ \R $ is not univalent, and the existence of $ Y: A \to \R_0 $ with the isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ is not a proposition.
-Take, for example, $ Y : I \to \R_0 $ given by $ (\lambda x_1, U \times U) $ for $ I $ the terminal object.
-Recall that $ (C \downarrow I) $ is equivalent to $ C $.
+  Recall that if $ L $ is nontrivial, $ \R $ is not univalent, and the existence of $ Y: \R^A $ with the isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ is not a proposition.
+Take, for example, $ Y : \R^I $ given by $ (\lambda x_1, U \times U) $.
+Recall that $ (\R \downarrow I) $ is equivalent to $ \R $.
 Under this equivalence $ \sum_I Y $ is equivalent to $ U \times U $.
@@
   In a similar way, being a retract of $ A \times U $ is not a proposition.
-Therefore, if we want the class of display maps to really be a subclass of the class of morphisms, we need the existence of $ Y: A \to \R_0 $ and the isomorphism $ g : X \to \sum_A Y $, or the existence of the retraction $ A \times U \to X $, to mean \textit{mere existence} in this case.
+Therefore, if we want the class of display maps to really be a subclass of the class of morphisms, we need the existence of $ Y: \R^A $ and the isomorphism $ g : X \xrightarrow \sim \sum_A Y $, or the existence of the retraction $ A \times U \to X $, to mean \textit{mere existence} in this case.
+This means that we cannot use these in constructions, except for mere propositions.
 \end{remark}

### 2024-04-10 report/chapters/univalent-foundations.tex
Add fibrations, write about the extend of the equivalence R^A <-> R / A

@@
 
-\section{truncation and (mere) existence}
+\section{Truncation and (mere) existence}
 As mentioned before, if we want to do mathematics in a dependent type theory, we can `encode' propositions as types.

### 2024-04-12 report/chapters/previous-work.tex
Show that we always have morphisms

@@
 \begin{remark}
+  Note that for all $ A : \R $, we can `reduce' any $ x: L_n $ to
+  \[ \iota_{0, n}(A) x : \varphi(A)_n \]
+  and in the same way, for all $ A, B: \R $, we can turn any $ f: L_0 $ into a morphism $ B \circ f \circ A : \R(A, B) $. In particular, we have $ B \circ A : \R(A, B) $.
+  Of course, all elements of $ \varphi(A)_n $ and all elements of $ \R(A, B) $ arise this way.
+\end{remark}
+
+\begin{remark}
   Note that if $ L $ is a nontrivial $ \lambda $-theory, $ \R $ is not a univalent category.
@@
 
-We might wonder whether $ \R $ also has an initial object $ O $. However, for any $ c: L_0 $, we would have a morphism (with the same term as the terminal object)
-\[ \lambda x_1, \iota_{0, 1}(c) : A \to U, \]
+We might wonder whether $ \R $ also has an initial object $ O $. However, for any $ c: L_0 $, we would have a constant morphism
+\[ I_c = \lambda x_1, \iota_{0, 1}(c) : \R(A, U), \]
 so if $ L $ is nontrivial, $ \R $ has no initial object.
@@
 Combining this with the embedding of $ \R \hookrightarrow \Pshf L $, we would expect $ \R $ to not have all pullbacks.
-This is because in $ \Pshf L $, for a cospan $ B \xrightarrow f A \xleftarrow g C $ with $ f_n(B_n) \cap g_n(C_n) = \emptyset $, we would have $ Q_n = \emptyset $, which could never happen with an object coming from $ \R $.
-Note, however, that this can not be made rigorous, because a fully faithful embedding reflects limits, but does not preserve them.
+This is because in $ \Pshf L $, for a cospan $ B \xrightarrow f A \xleftarrow g C $ with $ f_n(B_n) \cap g_n(C_n) = \emptyset $ for some $ n $, the pullback $ Q $ would have $ Q_n = \emptyset $, which could never happen with an object coming from $ \R $.
+Note, however, that this can not be made rigorous, because a fully faithful embedding reflects limits, but does not necessarily preserve them.
 
@@
 \[ f = [f, g] \circ \bot = [f, g] \circ \top = g. \]
-In particular, for any two objects $ A, A^\prime: \R $,
+In particular, for any two objects $ A, A^\prime: \R $, since we have $ A \circ A^\prime : \R(A^\prime, A) $, so $ \R(A^\prime, A) $ is nonempty, we have
 \[ \R(A^\prime, A) \simeq \R(I \times A^\prime, A) \simeq \R(I, A^{A^\prime}) \simeq \{ \star \}, \]
@@
 On the other hand, $ \sum_A $ is generally not surjective.
-To mitigate this somewhat, we can choose our subtype $ D $ of display maps in such a way that the restriction $ \R^A \to (C \downarrow_D A) $ becomes essentially surjective.
+However, we can choose our subtype $ D $ of display maps in such a way that the restriction $ \R^A \to (C \downarrow_D A) $ becomes essentially surjective.
 
 \begin{definition}
-  For $ \R $, we will consider a morphism $ f: X \to A $ to be a display map if we have some $ Y : \R^A $ like above, and some isomorphism $ g: X \xrightarrow{\sim} \sum_A Y $ such that $ f = g \cdot p_Y $:
-  \begin{center}
-    \begin{tikzcd}
-      X \arrow[rd, "f"] \arrow[rr, "g"] & & \sum_A Y \arrow[ld, "p_1"]\\
-      & A
-    \end{tikzcd}
-  \end{center}
+  For $ \R $, we will consider a morphism $ f: X \to A $ to be a display map if we have some $ Y : \R^A $ like above, and some isomorphism $ g: (X, f) \xrightarrow{\sim} (\sum_A Y, p_Y) $ in $ (\R \downarrow A) $.
 \end{definition}
@@
 
+Taylor shows that these display maps are well-defined, in the sense that they satisfy the three properties mentioned above.
+\begin{enumerate}
+  \item Given a display map $ (X, f): (\R \downarrow_D A) $ and a morphism $ \alpha: \R(B, A) $.
+Recall that this means that there merely exists a $ Y: \R^A $ and an isomorphism $ X \xrightarrow \sim \sum_A Y $ in $ (\R \downarrow A) $.
+Therefore, we have mere existence of a pullback $ \sum_B (Y \circ \alpha) $ of $ \sum_A Y $ along $ \alpha $.
+For all $ C: \R $ with $ \beta: \R(C, B) $ and $ \gamma: \R(C, \sum_A Y) $ that make the square commute, we have the morphism $ \lambda x_1, (\beta x_1, \pi_2 (\gamma x_1)): \R(C, \sum_B (Y \circ \alpha)) $.
+    \begin{center}
+      \begin{tikzcd}[column sep = .5in]
+        C \arrow[rrrd, bend left, "\gamma"] \arrow[dd, bend right=90, "\beta"'] \arrow[d, dashed, "{\lambda x_1, (\beta x_1, \pi_2 (\gamma x_1))}"] \\
+        \sum_B (Y \circ \alpha) \arrow[rrr, "{\lambda x_1, (\alpha (\pi_1 x_1), Y (\alpha (\pi_1 x_1)) (\pi_2 x_1))}"] \arrow[d, "p_{(Y \circ \alpha)}"] &&& \sum_A Y \arrow[d, "p_Y"] & X \arrow[l, "g"] \arrow[ld, "f"]\\
+        B \arrow[rrr, "\alpha"] &&& A
+      \end{tikzcd}
+    \end{center}
+    By the isomorphism between $ X $ and $ \sum_A Y $, $ \sum_B (Y \circ \alpha) $ is also a pullback of $ X $: by postcomposing with $ g $ and its inverse, we see that morphisms from $ \sum_B (Y \circ A) $ and $ C $ to $ X $ are equivalent to morphisms to $ \sum_A Y $.
+
+    \TODO: Verify that these morphisms are indeed morphisms.
+  \item
+  \item Let $ B \to I $ be a terminal projection. Consider $ Y = (\lambda x_1, B) : \R^I $. We have
+    \[ \sum_I Y = \lambda x_1, ((\lambda x_2, x_2), B (\pi_2 x_1)) = \langle I \circ \pi_1, B \circ \pi_2 \rangle = I \times B, \]
+    which is isomorphic to $ B $.
+\end{enumerate}
+
 This brings us to Taylor's theorem about $ \R $:

### 2024-04-15 report/chapters/previous-work.tex
Verify that display maps are well-defined

@@
 We will denote the subtype of display maps from $ X $ to $ A $ with $ D(X, A) \subseteq C(X, A) $.
-For any $ A : C $, we get a category $ (C \downarrow_D A) $ as a full subcategory of the slice category $ (C \downarrow A) $, with as objects the display maps $ f: D(X, A) $.
-A morphism from $ f: D(X, A) $ to $ g: D(Y, A) $ is a morphism $ \varphi: C(X, Y) $ such that the following diagram commutes.
-\begin{center}
-  \begin{tikzcd}
-    X \arrow[rd, "f"'] \arrow[rr, "\varphi"] & & Y \arrow[ld, "g"]\\
-    & A &
-  \end{tikzcd}
-\end{center}
+For any $ A : C $, we define the category $ (C \downarrow_D A) $ as a full subcategory of the slice category $ (C \downarrow A) $, with as objects the display maps $ f: D(X, A) $.
+The morphisms between two objects of $ (C \downarrow_D A) $ are still all the morphisms of $ (C \downarrow A) $ (i.e.
+the morphisms of $ C $ that commute with the display maps).
+
 Note that for the terminal object $ I : C $, $ (C \downarrow_D I) $ is still equivalent to $ C $, since every terminal projection is a display map.
 
-Also note that since display maps are closed under pullbacks, the pullback functor $ (C \downarrow A) \to (C \downarrow B) $ for $ \alpha: C(B, A) $ restricts to a pullback functor $ \alpha^*: (C \downarrow_D A) \to (C \downarrow_D B) $.
+Also note that since the pullback of display maps against any map exist (and are display maps again), we get a pullback functor $ \alpha^*: (C \downarrow_D A) \to (C \downarrow_D B) $.
+This is the restriction of the pullback functor $ \alpha^*: (C \downarrow A) \to (C \downarrow B) $, if it exists.
 
@@
 \end{proof}
-
-\TODO Displayed category?
 
@@
 
-Taylor shows that these display maps are well-defined, in the sense that they satisfy the three properties mentioned above.
+Taylor shows that these display maps indeed satisfy the three properties mentioned above. However, in univalent foundations, there are some subtleties in the case of pullbacks:
 \begin{enumerate}
@@
     By the isomorphism between $ X $ and $ \sum_A Y $, $ \sum_B (Y \circ \alpha) $ is also a pullback of $ X $: by postcomposing with $ g $ and its inverse, we see that morphisms from $ \sum_B (Y \circ A) $ and $ C $ to $ X $ are equivalent to morphisms to $ \sum_A Y $.
+  \item Given display maps $ f: B \to A $ and $ g: C \to B $.
+We have $ X : \R^A $ and $ Y: \R^B $ with isomorphisms $ s: B \xrightarrow \sim \sum_A X $ and $ t: C \xrightarrow \sim \sum_B Y $.
+We need to show that $ f \circ g: C \to A $ is also a display map.
+    \begin{center}
+      \begin{tikzcd}
+        C \arrow[d, "g"] \arrow[r, "\sim", "t"'] & \sum_B Y \arrow[ld, "p_Y"] \arrow[r, "u"', "\sim"] & \sum_A Z \arrow[ldld, bend left, "p_Z"]\\
+        B \arrow[d, "f"] \arrow[r, "\sim", "s"'] & \sum_A X \arrow[ld, "p_X"]\\
+        A
+      \end{tikzcd}
+    \end{center}
+    Intuitively, $ \sum_B Y \cong \sum_A Z $ represents
+    \[ \sum_{b: \sum_{a: A} X a} Y b \cong \sum_{a: A} \sum_{x: X a} Y(a, x), \]
+    by the isomorphism that relates $ ((a, x), y) $ to $ (a, (x, y)) $. Therefore, consider
+    \[ Z = \lambda x_1 x_2, (X x_1 (\pi_1 x_2), Y (s^{-1} (x_1, \pi_1 x_2)) (\pi_2 x_2)): \R^A. \]
+    we have an isomorphism $ u: \sum_B Y \xrightarrow \sim \sum_A Z $ given by:
+    \[ u = \lambda x_1, (A a, (X a x, Y b y)) \]
+    with
+    \[ b = \pi_1 x_1;\quad a = \pi_1 (s b); \quad x = \pi_2 (s b); \quad y = \pi_2 x_1, \]
+    and
+    \[ u^{-1} = \lambda x_1, (s^{-1}(A a, X a x), Y b y) \]
+    with
+    \[ a = \pi_1 x_1; \quad x = \pi_1 (\pi_2 x_1); \quad b = s^{-1}(a, x); \quad y = \pi_2 (\pi_2 x_1) \]
+    and then $ u \circ t $ is an isomorphism in $ (\R \downarrow A) $ between $ (C, f \circ g) $ and $ (\sum_A Z, p_Z) $.
 
-    \TODO: Verify that these morphisms are indeed morphisms.
-  \item
+    % \TODO: Verify that
+    % \begin{itemize}
+    %   \item $ Z: \R^A $
+    %     \begin{align*}
+    %       &Z x_1 (Z x_1 x_2)\\
+    %       &= (X x_1 (X x_1 (\pi_1 x_2)), Y (s^{-1} (x_1, (X x_1 (\pi_1 x_2)))) (Y (s^{-1} (x_1, (\pi_1 x_2))) (\pi_2 x_2)))\\
+    %       &= (X x_1 (\pi_1 x_2), Y (s^{-1} (x_1, \pi_1 x_2)) (\pi_2 x_2))\\
+    %       &= Z x_1 x_2.
+    %     \end{align*}
+    %   \item $ u $ is a morphism
+    %     \begin{align*}
+    %       \sum_A Z (u (\sum_B Y x_1))
+    %       &= \sum_A Z (u (B (\pi_1 x_1), Y (\pi_1 x_1) (\pi_2 x_1)))\\
+    %       &= \sum_A Z (\pi_1 (s (\pi_1 x_1)), (\pi_2 (s (\pi_1 x_1)), Y (\pi_1 x_1) (\pi_2 x_1)))\\
+    %       &= (A (\pi_1 (s (\pi_1 x_1))), (X (\pi_1 (s (\pi_1 x_1))) ((\pi_2 (s (\pi_1 x_1)))), Y (\pi_1 x_1) (\pi_2 x_1)))\\
+    %       &= u x_1.
+    %     \end{align*}
+    %   \item $ u^{-1} $ is a morphism
+    %     \begin{align*}
+    %       \sum_B Y (u^{-1} (\sum_A Z x_1))
+    %       &= \sum_B Y (u^{-1} (A (\pi_1 x_1), (X (\pi_1 x_1) (\pi_1 (\pi_2 x_1)), Y (s^{-1} ((\pi_1 x_1), \pi_1 (\pi_2 x_1))) (\pi_2 (\pi_2 x_1)))))\\
+    %       &= \sum_B Y (s^{-1}(\pi_1 x_1, \pi_1 (\pi_2 x_1)), Y (s^{-1} (\pi_1 x_1, \pi_1 (\pi_2 x_1))) (\pi_2 (\pi_2 x_1)))\\
+    %       &= (s^{-1}(\pi_1 x_1, \pi_1 (\pi_2 x_1)), Y (s^{-1} (\pi_1 x_1, \pi_1 (\pi_2 x_1))) (\pi_2 (\pi_2 x_1)))\\
+    %       &= u^{-1} x_1
+    %     \end{align*}
+    %   \item $ u \circ u^{-1} = \id{\sum_A Z} $
+    %     \begin{align*}
+    %       u(u^{-1} x_1)
+    %       &= u(s^{-1} (\pi_1 x_1, \pi_1 (\pi_2 x_1)), Y (s^{-1} (\pi_1 x_1, \pi_1 (\pi_2 x_1))) (\pi_2 (\pi_2 x_1)))\\
+    %       &= (A (\pi_1 x_1), (X (\pi_1 x_1) (\pi_1 (\pi_2 x_1)), Y (s^{-1} (\pi_1 x_1, \pi_1 (\pi_2 x_1))) (\pi_2 (\pi_2 x_1))))\\
+    %       &= \sum_A Z x_1
+    %     \end{align*}
+    %   \item $ u^{-1} \circ u = \id{\sum_B Y} $.
+    %     \begin{align*}
+    %       u^{-1} (u x_1)
+    %       &= u^{-1}(\pi_1 (s (\pi_1 x_1)), (\pi_2 (s (\pi_1 x_1)), Y (\pi_1 x_1) (\pi_2 x_1)))\\
+    %       &= (B (\pi_1 x_1), Y (\pi_1 x_1) (\pi_2 x_1))
+    %       &= \sum_B Y x_1.
+    %     \end{align*}
+    %   \item $ p_Z \circ u = g \circ p_Y $.
+    %     \begin{align*}
+    %       p_Z (u x_1)
+    %       &= p_Z (\pi_1 (s (\pi_1 x_1)), (\pi_2 (s (\pi_1 x_1)), Y (\pi_1 x_1) (\pi_2 x_1)))\\
+    %       &= A (\pi_1 (s (\pi_1 x_1)))\\
+    %       &= A (\pi_1 (s (B (\pi_1 x_1))))\\
+    %       &= p_X (s (p_Y x_1))\\
+    %       g (p_Y x_1).
+    %     \end{align*}
+    % \end{itemize}
   \item Let $ B \to I $ be a terminal projection. Consider $ Y = (\lambda x_1, B) : \R^I $. We have
@@
 \end{enumerate}
+\begin{remark}
+  There is an awful lot of properties to verify here (e.g.
+that some terms are elements of some $ \R^A $, that others are morphisms in some $ \R(\sum_A X, \sum_B Y) $, that some diagrams commute), but most of it boils down to writing down the equations that should hold, reducing them via $ \beta $-equality, and then using the facts that objects $ A: \R $ are idempotent, that morphisms $ f: \R(A, B) $ equal $ B \circ f \circ A $ and that objects $ X: \R^A $ satisfy $ X \circ A = X $ and $ X a (X a x) = X a x $ for all $ a $ and $ x $.
+Note that for a morphism $ f: \sum_A X \to B $,
+  \[ f(A x_1, x_2) = f(x_1, x_2) = f(x_1, X x_1 x_2), \]
+  so $ f $ `absorbs' such instances of $ A $ and $ X $, so to speak.
+\end{remark}
 
@@
 \end{proof}
-
-\TODO Relate indexed types and fibrations.

### 2024-04-18 report/chapters/category-theory.tex
Finish "previous work"

@@
 
-There is also the dual concept of a universal arrow $ (d, f) $ from a functor $ F $ to an object $ c: C $. Its universal property yields the following diagram:
+There is also the dual concept of a universal arrow $ (d, f) $ from a functor $ F $ to an object $ c: C $. Its universal property can be summarized in the following diagram:
 \begin{center}
@@
 \begin{lemma}
-  One can construct an adjunction $ (F, G, \eta, \epsilon) $ as above from only the functor $ L: C \to D $ and, for each $ c: C $, a universal arrow $ (R(c), \epsilon_c) $ from $ L $ to $ c $.
+  One can construct an adjunction $ (L, R, \eta, \epsilon) $ as above from only the functor $ L: C \to D $ and, for each $ c: C $, a universal arrow $ (R(c), \epsilon_c) $ from $ L $ to $ c $.
 \end{lemma}

### 2024-04-18 report/chapters/previous-work.tex
Finish "previous work"

@@
 
-Taylor starts out with a kind of `external' representation of indexed families $ (X_a)_a $ in $ \R $. He denotes these as `functions' $ A \to \R_0 $. They are the elements $ X: L_0 $ with
+As Hyland remarks, Taylor shows that $ \R $ is relatively cartesian closed using a very syntactical argument, in the spirit of Scott.
+
+He starts out with a kind of `external' representation of indexed families $ (X_a)_a $ in $ \R $. He denotes these as `functions' $ A \to \R_0 $. They are the elements $ X: L_0 $ with
 \[ X \circ A = X \quad \text{and} \quad (\lambda x_1, (X x_1) \circ (X x_1)) = X. \]
@@
 
+For $ A: \R $, we introduce the combinator
+\[ \sum_A = \lambda x_1 x_2, (A (\pi_1 x_2), x_1 (\pi_1 x_2) (\pi_2 x_2)). \]
+
 For $ A: \SET $, we have an equivalence between the elements of $ \SET^A $ and the elements of the fiber $ (\SET \downarrow A) $ of the fibration $ \SET^2 \to \SET $.
-Now, in the case of some $ A: \R $, we can construct a `global dependent sum' functor $ \sum_A : \R^A \to (\R \downarrow A) $, which sends $ X: \R^A $ to
-\[ \sum_A X = \lambda x_1, (A (\pi_1 x_1), X (\pi_1 x_1) (\pi_2 x_1)), \]
-together with a projection morphism $ p_X: \sum_A X \to A $ given by $ \lambda x_1, A(\pi_1 x_1) $.
+Now, for $ A: \R $, $ \sum_A $ gives a functor from $ \R^A $ to $ (\R \downarrow A) $.
+Note that it sends objects $ X: \R^A $ to $ \sum_A X $, together with a projection morphism $ p_X = A \circ \pi_1: \sum_A X \to A $.
 Note that with the embedding in Definition \ref{def:retracts-embedding} into $ \Pshf L $, we can consider $ \sum_A X $ as consisting of pairs $ (a, x) $ with $ a : A $ and $ x : X a $, which is exactly what we would expect from a dependent sum.
-$ \sum_A $ sends a morphism $ f: X \to Y $ to
-\[ \sum_A f = \lambda x_1, ( A (\pi_1 x_1), f (\pi_1 x_1) (\pi_2 x_1) ) : \R\left(\sum_A X, \sum_A Y\right) \]
 
-Now, this is fully faithful: given a morphism $ g: \R\left(\sum_A X, \sum_A Y\right) $, we take
+Now, $ \sum_A $ is fully faithful: given a morphism $ g: \R\left(\sum_A X, \sum_A Y\right) $, we take
 \[ \psi(g) = \lambda x_1 x_2, \pi_2 (g (x_1, x_2)). \]
@@
 \end{enumerate}
+
 \begin{remark}
@@
 
-This brings us to Taylor's theorem about $ \R $:
+\begin{remark}
+  To talk about `relatively cartesian closed', we need a pullback functor $ \alpha^* : (\R \downarrow_D A) \to (\R \downarrow_D B) $ for all (display maps) $ \alpha: B \to A $.
+However, as remarked before, since the definition of display maps involves a propositional truncation, we only have mere existence of pullbacks, and to pass from the statement ``for all $ f $, there exists a pullback $ \alpha^* f $'' to the statement ``there exists a function that sends every morphism $ f : (\R \downarrow_D A) $ to its pullback $ \alpha^* f : (\R \downarrow_D B) $'', we need to assume the axiom of choice.
+
+  However, note that we have a weak equivalence (an essentially surjective and fully faithful functor) between strict categories (categories in which the type of objects is a homotopy set) $ \sum_A: \R^A \xrightarrow \sim (\R \downarrow_D A) $.
+If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (\cite{univalent-categories}, introduction, page 2 \TODO: maybe find a better reference for this) and then our pullback functor is given by
+  \[ \sum_A^{-1} \bullet (\alpha \cdot -) \bullet \sum_B, \]
+  where $ (\alpha \cdot -): \R^A \to \R^B $ denotes the functor given by precomposition with $ \alpha $.
+\end{remark}
+
+This brings us to the main theorem of this section (\cite{taylor}, 5.1.8).
 \begin{theorem}
-  $ \R $ is cartesian closed, relative to this class of display maps.
+  If we assume the axiom of choice, $ \R $ is cartesian closed, relative to the given class of display maps.
 \end{theorem}
 \begin{proof}
-  In the spirit of Scott, Taylor gives a very syntactical proof.
+  Let $ \alpha: B \to A $ be a display map.
+We have mere existence of some $ X: \R^A $ and an isomorphism $ g: (X, \alpha) \xrightarrow \sim (\sum B, p_X) $.
+We need to show that there is a right adjoint to the pullback functor $ \alpha^* $.
+Since under assumption of the axiom of choice, $ \alpha^* $ is defined as a composition of a precomposition functor with two equivalences of categories, this is equivalent to showing that there is a right adjoint to the precomposition functor $ (\alpha \cdot -): \R^A \to \R^B $ (note that $ \alpha \cdot - $ sends $ f $ to $ f \circ \alpha $).
+
+  Now, intuitively, any $ Y: \R^B $ denotes an indexed family $ ((Y (a, b))_{b: X a})_{a: A} $.
+We want the right adjoint $ \alpha_* Y $ to be the indexed family of dependent products $ (\prod_{b: B_a} Y (a, b))_a $.
+An element $ f $ of the dependent product $ \alpha_* Y a $ is then a function from $ X a $, that satisfies $ f b : Y (a, b) $ for all $ b : X a $.
+Therefore, for all $ a : A $ and all $ f : L_0 $, we want $ (\alpha_* Y a) f = f $ to mean ``$ f \circ X a = f $ and, $ f b : Y (a, b) $ for all $ b: X a $''.
+We encode these two parts as
+  \[ \lambda x_1, x_1 \circ X a \quad \text{and} \quad \lambda x_1 x_2, Y (g^{-1} (a, x_2)) (x_1 x_2). \]
+  It turns out that these are idempotents and they commute, so we can compose them into one object
+  \[ \alpha_* Y a = \lambda x_1 x_2, Y (g^{-1} (a, x_2)) (x_1 (X a x_2)) : \R \]
+  and we define the combinator
+  \[ \alpha_* = \lambda x_1 x_2 x_3 x_4, x_1 (g^{-1} (x_2, x_4)) (x_3 (X x_2 x_4)). \]
+  Now, applying $ \alpha_* $ to both objects and morphisms in $ \R^A $ gives a functor $ \alpha_* : \R^B \to \R^A $.
+
+  Note that for all $ Y : \R^B $ and all $ b $, we have a morphism $ (\lambda x_1, x_1 (\pi_2 (g b))) : \R(\alpha_* Y (\alpha b), Y b) $. Making this parametric in $ b $ gives us a counit
+  \[ \epsilon_Y = \lambda x_1 x_2, Y x_1 (x_2 (\pi_2 (g x_1))) : \R^B((\alpha_* Y) \circ \alpha, Y). \]
+
+  % First of all, $ \epsilon_Y \circ B = \epsilon_Y $, also
+  % \begin{align*}
+  %   (Y x_1 \circ \epsilon_Y x_1 \circ (\alpha_* Y \circ \alpha) x_1) x_2
+  %   &= Y x_1 (\epsilon_Y x_1 (\alpha_* Y (\alpha x_1) x_2))\\
+  %   &= Y x_1 ((\lambda f, Y x_1 (f (X (\alpha x_1) (\pi_2 (g x_1))))) (\lambda x_3, Y (g^{-1} (\alpha x_1, x_3)) (x_2 (X (\alpha x_1) x_3))))\\
+  %   &= Y x_1 (((\lambda x_3, Y (g^{-1} (\alpha x_1, x_3)) (x_2 (X (\alpha x_1) x_3)))) (X (\alpha x_1) (\pi_2 (g x_1))))\\
+  %   &= Y x_1 (Y (g^{-1} (\alpha x_1, (\pi_2 (g x_1)))) (x_2 (X (\alpha x_1) (X (\alpha x_1) (\pi_2 (g x_1))))))\\
+  %   &= Y x_1 (Y x_1 (x_2 (X (\alpha x_1) (X (\alpha x_1) (\pi_2 (g x_1))))))\\
+  %   &= Y x_1 (x_2 (X (\alpha x_1) (\pi_2 (g x_1))))\\
+  %   &= \epsilon_Y x_1 x_2.
+  % \end{align*}
+
+  To show that $ (\alpha \cdot -) \dashv \alpha_* $, we need to show that for all $ Y : \R^B $, $ (\alpha_* Y, \epsilon_Y) $ is a universal arrow from $ (\alpha \cdot -) $ to $ Y $.
+Recall the following diagram:
+  \begin{center}
+    \begin{tikzcd}
+      Z \circ \alpha \arrow[rd, "f"'] \arrow[r, "{\hat f \circ \alpha}", dashed] & (\alpha_* Y) \circ \alpha \arrow[d, "{\epsilon_Y}"]\\
+      & Y
+    \end{tikzcd}
+  \end{center}
+  Now, suppose that we have some $ Z : \R^A $ and some $ f: \R^B(Z \circ \alpha, Y) $. We define
+  \[ \hat f = \lambda x_1 x_2 x_3, f(g^{-1}(x_1, x_3)) (Z x_1 x_2): \R^A(Z, \alpha_* Y) \]
+  and we have $ ((\hat f) \circ \alpha) \cdot \epsilon_Y = f $.
+  % \begin{align*}
+  %   (((\alpha \cdot -) \hat f) \cdot \epsilon_Y) b z
+  %   &= \epsilon_Y b ((\hat f (\alpha b)) z)\\
+  %   &= \epsilon_Y b (\lambda x_3, f (g^{-1} ((\alpha b), x_3)) (Z (\alpha b) z))\\
+  %   &= Y b ((\lambda x_3, f (g^{-1} ((\alpha b), x_3)) (Z (\alpha b) z)) (\pi_2 (g b)))\\
+  %   &= Y b (f (g^{-1} ((\alpha b), \pi_2 (g b))) (Z (\alpha b) z))\\
+  %   &= Y b (f (g^{-1} (g b)) (Z (\alpha b) z))\\
+  %   &= f b z.
+  % \end{align*}
+  Now, suppose that we have some (other) $ \hat f^\prime : \R^A(Z, \alpha_*(Y)) $ such that $ (\hat f^\prime \circ \alpha) \cdot \epsilon_Y = f $.
+Then substituting $ (\hat f^\prime \circ \alpha) \cdot \epsilon_Y $ for $ f $ in $ \hat f $ yields
+  \[ \hat f = \lambda x_1, (\alpha_* Y x_1) \circ (\hat f^\prime x_1) = \hat f^\prime, \]
+  so $ \hat f $ is unique and $ (\alpha_* Y, \epsilon_Y) $ is a universal arrow, which concludes the proof that $ (\alpha \cdot -) \dashv \alpha_* $.
+  % \begin{align*}
+  %   \hat f
+  %   &= \lambda x_1 x_2 x_3, f (g^{-1} (x_1, x_3))(Z x_1 x_2)\\
+  %   &= \lambda x_1 x_2 x_3, ((\epsilon_Y (g^{-1} (x_1, x_3))) \circ ((\hat f^\prime \circ \alpha) (g^{-1} (x_1, x_3)))) (Z x_1 x_2)\\
+  %   &= \lambda x_1 x_2 x_3, (\epsilon_Y (g^{-1} (x_1, x_3))) (\hat f^\prime (\alpha (g^{-1} (x_1, x_3))) (Z x_1 x_2))\\
+  %   &= \lambda x_1 x_2 x_3, (\epsilon_Y (g^{-1} (x_1, x_3))) (\hat f^\prime x_1 x_2)\\
+  %   &= \lambda x_1 x_2 x_3, Y (g^{-1} (x_1, x_3)) (\hat f^\prime x_1 x_2 (\pi_2 (g (g^{-1} (x_1, x_3)))))\\
+  %   &= \lambda x_1 x_2 x_3, Y (g^{-1} (x_1, x_3)) (\hat f^\prime x_1 x_2 (X x_1 x_3))\\
+  %   &= \lambda x_1 x_2, \alpha_* Y x_1 (\hat f^\prime x_1 (Z x_1 x_2))\\
+  %   &= \hat f^\prime
+  % \end{align*}
 \end{proof}
+
+\begin{remark}
+  Recall that in the definition of $ \alpha_* $, we composed commuting idempotents
+  \[ \lambda x_1 x_2, x_1 (X a x_2) \quad \text{and} \quad \lambda x_1 x_2, Y (a, x_2) (x_1 x_2). \]
+  In his PhD thesis, Taylor instead composes the idempotents
+  \[ \lambda x_1, x_1 (X a x_2) \quad \text{and} \quad \lambda x_1 x_2, Y x_2 (x_1 x_2). \]
+  Note that in the first term, $ x_2 $ plays the role of an element of $ X a $, whereas in the second term, it plays the role of an element of $ B $.
+Of course, if we worked in $ \SET $, we would indeed have $ X a \subseteq \bigsqcup_{a : A} X_a \cong B $.
+However, in $ \R $, the `terms' of $ B \cong \sum_A X $ look like pairs $ (a, x) $ with $ a : A $ and $ x : X a $, so we cannot consider terms of $ X a $ to be terms of $ B $.
+
+  Therefore, the idempotents that he uses do not commute, and the resulting term
+  \[ \lambda x_1 x_2, Y (B x_2) (x_1 (X a x_2)) \]
+  (notice the redundant usage of $ B $) is not idempotent.
+\end{remark}

### 2024-04-25 report/chapters/alternative-definitions.tex
Show equivalence of the presheaf categories

@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:lawvere-clone}
   There is an equivalence between abstract clones and Lawvere theories.
@@
   Conversely, let $ F: L \to \SET $ be a functor. We take the $ C $-algebra $ A $, with $ A = F(1) $ and for $ f: C_n = L(n, 1) $ and $ a: A^n $, $ f \bullet a = F(f)(a) $.
+\end{proof}
+
+\subsection{Presheaves for Lawvere Theories}
+
+\begin{lemma}\label{lem:lawvere-presheaf}
+  Let $ C $ be an abstract clone, and $ L $ be its associated Lawvere theory by the equivalence given above. A $ C $-presheaf is equivalent to a presheaf over $ L $.
+\end{lemma}
+\begin{proof}
+  The correspondence between $ C $-presheaves $ P $ and presheaves $ Q $ over $ L $ is as follows:
+
+  The sets $ P_n $ correspond to the action of $ Q $ on objects $ Q(n) $.
+
+  The $ P $-action $ P_m \times C_n^m \to P_n $ corresponds to the action of $ Q $ on morphisms $ L(n, m) \times Q(m) \to Q(n) $.
 \end{proof}

### 2024-04-25 report/chapters/category-theory.tex
Show equivalence of the presheaf categories

@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:lan-precomp-iso}
   If $ F : A \to B $ is a fully faithful functor, and $ C $ is a category with colimits, $ \eta: \id{[A, C]} \Rightarrow \Lan F {} \bullet F_* $ is a natural isomorphism.
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:surjective-precomposition}
   If $ C $ has limits or colimits, precomposition of functors $ [B, C] $ along a fully faithful functor is (split) essentially surjective.
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:karoubi-presheaf}
   As the category $ \SET $ is cocomplete, we have an equivalence between the category of presheaves on $ C $ and the category of presheaves on $ \overline C $:

### 2024-04-25 report/chapters/paper.tex
Write about the significance of local/relative cartesian closedness
Show equivalence of the presheaf categories

@@
-\chapter{The paper}
+\chapter{Hyland's paper}
 
@@
 
-\section{Locally cartesian closedness of the category of retracts}
-\begin{definition}[Category of retracts]
-  The category of retracts for a $ \lambda $-theory $ L $ is the category with objects $ f: L_n $ such that $ f \bullet f = f $ and it has as morphisms $ g: f \to f^\prime $ the terms $ g: L_n $ such that $ f^\prime \bullet g \bullet f = g $.
-The object $ f: L_n $ has identity element $ f $, and we have composition $ g \circ g^\prime = g \bullet g^\prime $.
-These are morphisms \TODO
-\end{definition}
+\section{Relations between the categories}
+
+As mentioned before, we have a fully faithful embedding of $ \R $ into $ \Pshf L $.
+
+Also, we have a functor from the Lawvere Theory $ \mathbf{L} $ (see Lemma \ref{lem:lawvere-clone}) associated to $ L $ into $ \R $, sending $ n : \mathbf L $ to $ U^n : \R $.
+By Scott's representation theorem, this functor can map morphisms as follows:
+\[ \mathbf L(m, n) = L_m^n \cong \R(U^m, U)^n \cong \R(U^m, U^n), \]
+which immediately shows that this functor is a fully faithful embedding.
+
+Note that if we consider $ L_1 $ as a monoid, with operation $ \bullet $ and unit $ x_1 $, and if we consider this monoid as a category, we can embed this (fully faithfully) into $ \mathbf L $.
+This gives the following sequence of embeddings:
+\begin{center}
+  \begin{tikzcd}
+    L_1 \arrow[r, hookrightarrow] & \mathbf L \arrow[r, hookrightarrow] & \R \arrow[r, hookrightarrow] & \Pshf L
+  \end{tikzcd}
+\end{center}
+Note that the composition of the first two morphisms sends the object of the category $ L_1 $ to $ (\lambda x_1, x_1) : \R $, which is exactly the usual embedding of $ L_1 $ into its Karoubi envelope.
+
+Write $ i: \op{L_1} \hookrightarrow \op{\mathbf L} $ and $ j: \op{\mathbf L} \hookrightarrow \op \R $ for the embeddings on the opposite categories.
+By Corollary \ref{cor:surjective-precomposition}, the first three categories in this sequence yield the following sequence of essentially surjective functors on the presheaf categories:
+\begin{center}
+  \begin{tikzcd}
+    & \Pshf L \arrow[d, "\sim"]\\
+    P \R \arrow[r, twoheadrightarrow, "j_*"] \arrow[rr, bend right, "\sim"] & P \mathbf L \arrow[r, twoheadrightarrow, "i_*"] & P L_1
+  \end{tikzcd}
+\end{center}
+The two equivalences in this diagram are due to Lemma \ref{lem:lawvere-presheaf} and Corollary \ref{cor:karoubi-presheaf}.
 
 \begin{lemma}
-  The category of retracts is indeed a category.
+  The precomposition functors $ i_* $ and $ j_* $ are adjoint equivalences.
 \end{lemma}
 \begin{proof}
-  \TODO
+  We will show that $ j_* $ is an adjoint equivalence. From the `two out of three' property, it follows then that $ i_* $ is also an adjoint equivalence.
+
+  Lemma \ref{lem:lan-precomp-iso} shows that $ \eta: \id{P \mathbf L} \Rightarrow \Lan j {} \bullet j_* $ is a natural isomorphism.
+To complete the proof that $ j_* $ is an adjoint equivalence, we just have to show that $ \epsilon: j_* \bullet \Lan j {} \Rightarrow \id{P \mathbf L} $ is a natural isomorphism as well.
+
+  To this end, take $ F : P \R $. By Lemma \ref{lem:lan-precomp-iso}, we have the isomorphism
+  \[ \eta^{-1}_{j_* F}: j_* (\Lan j (j_* F)) \cong j_* F. \]
+  Since functors preserve isomorphisms, we have $ i_* (j_* (\Lan j (j_* F))) \cong i_* (j_* F) $.
+However, since $ j_* \bullet i_* $ is an equivalence and in particular fully faithful, this corresponds to an isomorphism
+  \[ \Lan j (j_* F) \cong F. \]
+  Now we only need to prove that its morphism is equal to $ \epsilon_F $.
+Equivalently, we need to prove that $ i_* (j_* \epsilon) $ is equal to the morphism $ i_* \eta_{j_* F}^{-1} $, or that $ j_* \epsilon $ equals $ \eta^{-1}_{j_* F} $.
+
+  Take $ n : \mathbf L $.
+We need to show that $ \epsilon_F (j(n)) = \eta_{j_* F}^{-1}(n) $ as functions from $ (\Lan j {} (j_* F)) (j(n)) $ to $ F(j(n)) $.
+Note that the diagram for $ (\Lan j {} (j_* F)) (j(n)) $ consists of $ F(j(m)) $ for all $ f: \R(j(m), j(n)) $.
+Now, as it turns out, both $ \epsilon_F (j(n)) $ and $ \eta_{j_* F}^{-1}(n) $ are defined as the colimit arrow of $ F(f) : \SET(F(j(m)), F(j(n))) $ for all $ f: \R(j(m), j(n)) $, which concludes the proof.
 \end{proof}
+
+\section{Locally cartesian closedness of the category of retracts}
 
@@
 \end{theorem}
-
-\section{Equivalences}
 

### 2024-04-25 report/chapters/previous-work.tex
Show equivalence of the presheaf categories

@@
 \end{definition}
+
+\begin{remark}
+  Hyland instead defines $ \R $ as
+  \[ \R_0 = \{ A : L_1 \mid A \bullet A = A \} \quad \text{and} \R(A, B) = \{ f : L_1 \mid B \bullet f \bullet A = f \}, \]
+  writing $ s \bullet t $ instead of $ s \bullet (t) $ for $ s, t : L_1 $. Note that the following diagram commutes:
+  \begin{center}
+    \begin{tikzcd}
+      L_1 \times L_1 \arrow[r, "\bullet"] \arrow[d, "{(s, t) \mapsto ((\lambda x_1, s), (\lambda x_1, t))}"'] & L_1 \arrow[d, "{s \mapsto (\lambda x_1, s)}"]\\
+      L_0 \times L_0 \arrow[r, "\circ"] & L_0
+    \end{tikzcd}
+  \end{center}
+  Now, since for $ A : \R $, $ A = \lambda x_1, \iota_{0, 1}(A) (\iota_{0, 1}(A) x_1) $, we have $ \lambda x_1, \iota_{0, 1}(A) x_1 = A $.
+This shows that $ s \mapsto \lambda x_1, s $ and $ t \mapsto \iota_{0, 1}(t) x_1 $ (both on objects and morphisms) constitute an equivalence between Hyland's category of retracts and Scott's category of retracts.
+\end{remark}
 
@@
   \[ \hat f = \lambda x_1, (\alpha_* Y x_1) \circ (\hat f^\prime x_1) = \hat f^\prime, \]
-  so $ \hat f $ is unique and $ (\alpha_* Y, \epsilon_Y) $ is a universal arrow, which concludes the proof that $ (\alpha \cdot -) \dashv \alpha_* $.
+  so $ \hat f $ is unique and $ (\alpha_* Y, \epsilon_Y) $ is a universal arrow, which concludes the proof that $ (\alpha \cdot -) \dashv \alpha_* $ and we see that $ \R $ is cartesian closed relative to the given class of display maps.
   % \begin{align*}

### 2024-04-30 report/chapters/category-theory.tex
Show that hat R is the Rezk completion of R

@@
 For composition of functors $ F: A \to B $ and $ G: B \to C $, I will write $ F \bullet G $.
+
+\section{Yoneda}
+We can embed a category $ C $ into the functor category $ P C = [\op C, \SET] $ as follows (see \cite{Kashiwara}, Section 1.4):
+\begin{definition}
+  The \iindex{Yoneda embedding} $ Y : C \hookrightarrow P C $ is given on objects by $ Y(c) = C(-, c) $:
+  \[ Y(c)(d) = C(d, c) \quad \text{and} \quad Y(c)(f)(g) = f \cdot g \]
+  for $ d: C $, $ f: C(d, d^\prime) $ and $ g: C(d^\prime, c) $. It sends a morphism $ f: C(c, c^\prime) $ to the natural transformation $ Y(f): C(-, c) \Rightarrow C(-, c^\prime) $ given by
+  \[ Y(f)(d)(g) = g \cdot f \]
+  for $ d: C $ and $ g: C(d, c) $.
+\end{definition}
+
+For a functor between categories $ f: C \to D $, given the Yoneda embeddings $ Y_C : C \to P C $ and $ Y_D : D \to P D $ (we will often omit the subscript $ C $ and $ D $), we can create a diagram
+\begin{center}
+  \begin{tikzcd}
+    C \arrow[r, "f"] \arrow[d, hookrightarrow, "Y"] & D \arrow[d, hookrightarrow, "Y"]\\
+    P C & P D \arrow[l, "\op f_*"]
+  \end{tikzcd}
+\end{center}
+Note that the arrows in this diagram are functors, so objects in a category, instead of elements of a set.
+Therefore, it does not make sense to talk about `equality' of the morphisms along the different paths, but we rather talk about isomorphism in the functor category $ [C, P C] $.
+If we have such an isomorphism, we say the diagram `2-commutes':
+\begin{lemma}\label{lem:Yoneda-restriction-commutes}
+  If $ f: C \to D $ is a fully faithful functor, the diagram above 2-commutes.
+\end{lemma}
+\begin{proof}
+  For $ c, d : C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
+  \[ Y(c)(d) = C(d, c) \xrightarrow[f_{d, c}]{\sim} D(f(d), f(c)) = \op f_*(Y(f(c)))(d). \]
+  Also, for $ g: C(d^\prime, d) $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}
+      Y(c)(d) \arrow[d, "g \cdot -"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "f_{d^\prime, d}(g) \cdot -"]\\
+      Y(c)(d^\prime) \arrow[r, "f_{d^\prime, c}"] & \op f_*(Y(f(c)))(d^\prime)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ d $ and we have $ Y(c) \cong \op f_*(Y(f(c))) $ in $ P C $. Lastly, for $ g: C(c, c^\prime) $ and $ d: C $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}
+      Y(c)(d) \arrow[d, "- \cdot g"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "- \cdot f_{c, c^\prime}(g)"]\\
+      Y(c^\prime)(d) \arrow[r, "f_{d, c^\prime}"] & \op f_*(Y(f(c^\prime)))(d)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ c $ and we have $ Y \cong f \bullet Y \bullet \op f_* $ in $ [C, P C] $.
+\end{proof}
 
@@
 
-\section{Adjunctions}
+\section{Adjunctions and equivalences}
 
@@
   An \iindex{adjoint equivalence} between categories $ C $ and $ D $ is a pair of adjoint functors $ L \dashv R $ like above such that the unit $ \eta: \id{C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{D} $ are isomorphisms of functors.
+\end{definition}
+
+\subsection{Weak equivalences}
+There is also the notion of `weak equivalence'. In some cases, this is equivalent to an adjoint equivalence (for example, when its domain is univalent).
+\begin{definition}
+  A functor $ F: C \to D $ is called a \iindex{weak equivalence} if it is essentially surjective and fully faithful.
 \end{definition}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:karoubi-is-retract}
   Every object $ c: \overline C $ is a retract of $ \iota_C(c_0) $ for some $ c_0: C $.
@@
 
-\begin{remark}
+\begin{remark}\label{rem:retract-coequalizer}
   Let $ D $ be a category. Suppose that we have a retraction-section pair in $ D $, given by
@@
 \end{corollary}
+
+Now, there is also another (classically equivalent) definition of the category of retracts:
+\begin{definition}
+  Let $ Y: C \to P C $ be the Yoneda embedding of $ C $ into its category of presheaves.
+We define the category $ \hat \R $ as the full subcategory of $ P C $ consisting of objects $ F : P C $ such that there exists an object $ c: C $ and a retraction of $ Y(c) $ onto $ F $.
+Note that the existence of $ c $ and the retraction is \textit{mere existence} (see the chapter on Univalent Foundations) because we need this to be a subcategory of $ P C $.
+\end{definition}
+
+\begin{lemma}
+  $ \hat \R $ is the Rezk completion of $ \R $.
+\end{lemma}
+\begin{proof}
+  First of all, note that $ \hat \R $ is univalent, since it is a presheaf category (see Theorem 4.5 in \cite{univalent-categories}).
+So we must show that we have a weak equivalence from $ \R $ to $ \hat \R $.
+
+  Secondly, by Corollary \ref{cor:karoubi-presheaf} we have an adjoint equivalence $ {\op{\iota_C}}_*: P \R \xrightarrow \sim P C $ and by Lemma \ref{lem:Yoneda-restriction-commutes}, the following diagram 2-commutes:
+  \begin{center}
+    \begin{tikzcd}
+      C \arrow[r, "\iota_C"] \arrow[d, "Y"] & \R \arrow[d, "Y"]\\
+      P C & P \R \arrow[l, "\sim"', "{\op{\iota_C}}_*"]
+    \end{tikzcd}
+  \end{center}
+
+  By Lemma \ref{lem:karoubi-is-retract}, every object of $ \R $ is a retract of some object in $ c $.
+Therefore, every object in the image of $ \R $ inside $ P C $ is a retract of some object in the image of $ C $, so we can turn $ Y \bullet {\op{\iota_C}}_* : \R \to P C $ into a fully faithful embedding into $ \hat \R $.
+
+  Now, to show that it is essentially surjective, take an object $ F : \hat \R $.
+That is, take a retract \begin{tikzcd} F \arrow[r, shift left, "s"] & Y(c) \arrow[l, shift left, "r"] \end{tikzcd}.
+Note that $ r \cdot s $ is an idempotent on $ Y(c) $.
+Since $ Y $ is a fully faithful embedding, it gives an equivalence on the hom-sets, so we have an element $ e : C(c, c) $ that maps to $ r \cdot s : P C (Y(c), Y(c)) $.
+We will show that $ (c, e) $ is our preimage in $ \R $ of $ F $.
+
+  Also, $ (c, e) $ is a retract of $ \iota_C(c) $ with section and retraction $ e $.
+Therefore, $ \op{\iota_C} \bullet Y(c, e) $ is a retract of $ \op{\iota_C} \bullet Y (\iota_C (c)) $ with section and retraction $ \op{\iota_C} \bullet Y(e) $.
+Composing these gives an idempotent
+  \[ \op{\iota_C} \bullet Y(e): d \mapsto f \mapsto f \cdot e \]
+  on $ \op{\iota_C} \bullet Y (\iota_C (c)) $. Transporting this along the isomorphism with $ Y(c) $, we get an idempotent
+  \[ d \mapsto f \mapsto \iota_C^{-1}(\iota_C(f) \cdot e) \]
+  on $ Y(c) $. Note that we can view $ e $ both as an idempotent on $ c $ and on $ \iota_C(e) $, and that $ \iota_C(e) = e $, so $ \iota_C^{-1}(\iota_C(f) \cdot e) = f \cdot e $.
+
+  Therefore, the idempotent on $ Y(c) $ is exactly $ Y(e) = r \cdot s $.
+By Remark \ref{rem:retract-coequalizer}, $ \op{\iota_C} \bullet Y(c, e) $ is the equalizer of $ \id{Y(c)} $ and $ r \cdot s $.
+Note that by the same remark, $ F $ is the equalizer of $ \id{Y(c)} $ and $ r \cdot s $ as well.
+Since the equalizer is unique up to unique isomorphism, we have an isomorphism $ F \cong \op{\iota_C} \bullet Y(c, e) $ and we see that $ Y \bullet {\op{\iota_C}}_* $ is essentially surjective.
+\end{proof}
+
+\begin{remark}
+  As shown above, $ \R $ and $ \hat \R $ have a very strong relation.
+In classical mathematics, they are even equivalent.
+However, since $ \R $ is not univalent, we do not have a full equivalence in univalent foundations and our choice of definition will have consequences.
+One one hand, $ \hat \R $ is univalent.
+On the other hand, the objects of $ \R $ are uniquely associated with one idempotent morphism in $ C $.
+
+  In this thesis, I will choose to interpret the `category of retracts' to mean $ \R $.
+This is because Dana Scott and Paul Taylor perform most of their constructions explicitly using the (idempotent) morphisms of $ C $, which is closest to working in $ \R $.
+
+  It is however very well possible that most of the proofs can be made to work in $ \hat \R $ as well.
+For future research, it would be interesting to see what the differences are between working in $ \R $ and $ \hat \R $ for these proofs.
+\end{remark}
 

### 2024-04-30 report/chapters/paper.tex
Show that hat R is the Rezk completion of R

@@
 \end{center}
+
 Note that the composition of the first two morphisms sends the object of the category $ L_1 $ to $ (\lambda x_1, x_1) : \R $, which is exactly the usual embedding of $ L_1 $ into its Karoubi envelope.
@@
 Write $ i: \op{L_1} \hookrightarrow \op{\mathbf L} $ and $ j: \op{\mathbf L} \hookrightarrow \op \R $ for the embeddings on the opposite categories.
-By Corollary \ref{cor:surjective-precomposition}, the first three categories in this sequence yield the following sequence of essentially surjective functors on the presheaf categories:
+By Corollary \ref{cor:surjective-precomposition}, the first two morphisms in this sequence yield the following sequence of essentially surjective functors on the presheaf categories:
 \begin{center}
   \begin{tikzcd}
-    & \Pshf L \arrow[d, "\sim"]\\
+    \mathbf R \arrow[r, hookrightarrow] \arrow[d, hookrightarrow, "Y"] & \Pshf L \arrow[d, "\sim"]\\
     P \R \arrow[r, twoheadrightarrow, "j_*"] \arrow[rr, bend right, "\sim"] & P \mathbf L \arrow[r, twoheadrightarrow, "i_*"] & P L_1
@@
 
+\begin{lemma}
+  We have a natural isomorphism between the two functors from $ \R $ to $ P \mathbf L $ in the diagram above.
+\end{lemma}
+\begin{proof}
+  Note:
+  \[ (Y \bullet j_*)(A)(n) = (j \bullet (Y(A)))(n) = Y(A)(j(n)) = \R(U^n, A) \]
+  \[ (\iota \bullet \sim)(A)(n) = \{ a : L_n \mid A a = a \} \]
+
+  By Scott's representation theorem, we have $ \mathbb R(U^n, U) \cong L_n, $ via
+  \[ f \mapsto \iota_{0, n}(f) ((((c, x_1), x_2), \dots), x_n). \]
+  Restricting this equivalence to the morphisms to $ A $ yields
+  \[ \R(U^n, A) \cong \{ a : L_n \mid A a = a \}. \]
+  \TODO: Check coherence.
+\end{proof}
+
 \section{Locally cartesian closedness of the category of retracts}
+
+Recall that Paul Taylor constructed a class of display maps for $ \R $.
 
@@
 
-The fundamental theorem states that there is an equivalence of categories
+The fundamental theorem states that there is an adjoint equivalence
 \[ \LamTh \cong \Alg \Lambda. \]
-We will prove this by showing that there is a fully faithful and essentially surjective functor.
+We will prove this by showing that there is a weak equivalence.
 

### 2024-04-30 report/chapters/previous-work.tex
Show that hat R is the Rezk completion of R

@@
 
-  However, note that we have a weak equivalence (an essentially surjective and fully faithful functor) between strict categories (categories in which the type of objects is a homotopy set) $ \sum_A: \R^A \xrightarrow \sim (\R \downarrow_D A) $.
+  However, note that we have a weak equivalence between strict categories (categories in which the type of objects is a homotopy set) $ \sum_A: \R^A \xrightarrow \sim (\R \downarrow_D A) $.
 If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (\cite{univalent-categories}, introduction, page 2 \TODO: maybe find a better reference for this) and then our pullback functor is given by

### 2024-04-30 report/chapters/univalent-foundations.tex
Show that hat R is the Rezk completion of R

@@
 
+Note that if $ B $ is a univalent category and $ A $ is any cateory, the functor category $ [A, B] = B^A $ is univalent as well.
+In particular, the presheaf category $ P A = [\op A, \SET] $ is univalent.
+
+\begin{lemma}
+  For every category $ C $, there exists a univalent category $ \hat C $ with a weak equivalence
+  \[ \iota: C \hookrightarrow \hat C. \]
+\end{lemma}
+\begin{proof}
+  See \cite{univalent-categories}, Theorem 8.5.
+\end{proof}
+We call this univalent category the \iindex{Rezk completion}.
+\TODO: Uniqueness?
+
 \section{The univalence axiom}
@@
 \begin{lemma}
-  For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is fully faithful and essentially surjective' are equivalent propositions (see \ref{sec:homotopy-props-sets}).
+  For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is a weak equivalence' are equivalent propositions (see \ref{sec:homotopy-props-sets}).
 \end{lemma}

### 2024-05-01 report/chapters/algebraic-structures.tex
Start working on Hyland's Taylor fibration

@@
 
+\subsection{The initial presheaf}
+\begin{example}
+  Let $ T $ be an algebraic theory. We can construct a $ T $-presheaf $ P $, with $ P_n = \emptyset $. Then $ \bullet : P_m \times T_n^m \to P_m $ is trivial, and the presheaf laws hold trivially.
+\end{example}
+
+\begin{lemma}
+  This is indeed the initial presheaf.
+\end{lemma}
+\begin{proof}
+  Let $ Q $ be a $ T $-presheaf.
+For all $ n $, since $ P_n $ is empty, there is only one possible function $ P_n \to Q_n $.
+These functions trivially satisfy the presheaf morphism laws, so they constitute the unique presheaf morphism $ P \to Q $.
+\end{proof}
+
 \subsection{The theory presheaf}

### 2024-05-01 report/chapters/category-theory.tex
Start working on Hyland's Taylor fibration

@@
 Now, there is also another (classically equivalent) definition of the category of retracts:
-\begin{definition}
+\begin{definition}\label{def:karoubi'}
   Let $ Y: C \to P C $ be the Yoneda embedding of $ C $ into its category of presheaves.
-We define the category $ \hat \R $ as the full subcategory of $ P C $ consisting of objects $ F : P C $ such that there exists an object $ c: C $ and a retraction of $ Y(c) $ onto $ F $.
+We define the category $ \hat C $ as the full subcategory of $ P C $ consisting of objects $ F : P C $ such that there exists an object $ c: C $ and a retraction of $ Y(c) $ onto $ F $.
 Note that the existence of $ c $ and the retraction is \textit{mere existence} (see the chapter on Univalent Foundations) because we need this to be a subcategory of $ P C $.
@@
 
-\begin{lemma}
-  $ \hat \R $ is the Rezk completion of $ \R $.
+\begin{lemma}\label{lem:retracts-rezk}
+  $ \hat C $ is the Rezk completion of $ \overline C $.
 \end{lemma}
 \begin{proof}
-  First of all, note that $ \hat \R $ is univalent, since it is a presheaf category (see Theorem 4.5 in \cite{univalent-categories}).
-So we must show that we have a weak equivalence from $ \R $ to $ \hat \R $.
+  First of all, note that $ \hat C $ is univalent, since it is a presheaf category (see Theorem 4.5 in \cite{univalent-categories}).
+So we must show that we have a weak equivalence from $ \overline C $ to $ \hat C $.
 
-  Secondly, by Corollary \ref{cor:karoubi-presheaf} we have an adjoint equivalence $ {\op{\iota_C}}_*: P \R \xrightarrow \sim P C $ and by Lemma \ref{lem:Yoneda-restriction-commutes}, the following diagram 2-commutes:
+  Secondly, by Corollary \ref{cor:karoubi-presheaf} we have an adjoint equivalence $ {\op{\iota_C}}_*: P \overline C \xrightarrow \sim P C $ and by Lemma \ref{lem:Yoneda-restriction-commutes}, the following diagram 2-commutes:
   \begin{center}
     \begin{tikzcd}
-      C \arrow[r, "\iota_C"] \arrow[d, "Y"] & \R \arrow[d, "Y"]\\
-      P C & P \R \arrow[l, "\sim"', "{\op{\iota_C}}_*"]
+      C \arrow[r, "\iota_C"] \arrow[d, "Y"] & \overline C \arrow[d, "Y"]\\
+      P C & P \overline C \arrow[l, "\sim"', "{\op{\iota_C}}_*"]
     \end{tikzcd}
@@
 
-  By Lemma \ref{lem:karoubi-is-retract}, every object of $ \R $ is a retract of some object in $ c $.
-Therefore, every object in the image of $ \R $ inside $ P C $ is a retract of some object in the image of $ C $, so we can turn $ Y \bullet {\op{\iota_C}}_* : \R \to P C $ into a fully faithful embedding into $ \hat \R $.
+  By Lemma \ref{lem:karoubi-is-retract}, every object of $ \overline C $ is a retract of some object in $ c $.
+Therefore, every object in the image of $ \overline C $ inside $ P C $ is a retract of some object in the image of $ C $, so we can turn $ Y \bullet {\op{\iota_C}}_* : \overline C \to P C $ into a fully faithful embedding into $ \hat C $.
 
-  Now, to show that it is essentially surjective, take an object $ F : \hat \R $.
+  Now, to show that it is essentially surjective, take an object $ F : \hat C $.
 That is, take a retract \begin{tikzcd} F \arrow[r, shift left, "s"] & Y(c) \arrow[l, shift left, "r"] \end{tikzcd}.
@@
 Since $ Y $ is a fully faithful embedding, it gives an equivalence on the hom-sets, so we have an element $ e : C(c, c) $ that maps to $ r \cdot s : P C (Y(c), Y(c)) $.
-We will show that $ (c, e) $ is our preimage in $ \R $ of $ F $.
+We will show that $ (c, e) $ is our preimage in $ \overline C $ of $ F $.
 
@@
 \begin{remark}
-  As shown above, $ \R $ and $ \hat \R $ have a very strong relation.
+  As shown above, $ \overline C $ and $ \hat C $ have a very strong relation.
 In classical mathematics, they are even equivalent.
-However, since $ \R $ is not univalent, we do not have a full equivalence in univalent foundations and our choice of definition will have consequences.
-One one hand, $ \hat \R $ is univalent.
-On the other hand, the objects of $ \R $ are uniquely associated with one idempotent morphism in $ C $.
+However, since $ \overline C $ is not univalent, we do not have a full equivalence in univalent foundations and our choice of definition will have consequences.
+One one hand, $ \hat C $ is univalent.
+On the other hand, every object of $ \overline C $ is uniquely associated with one idempotent morphism in $ C $.
 
-  In this thesis, I will choose to interpret the `category of retracts' to mean $ \R $.
-This is because Dana Scott and Paul Taylor perform most of their constructions explicitly using the (idempotent) morphisms of $ C $, which is closest to working in $ \R $.
+  In this thesis, I will choose to interpret the `category of retracts' to mean $ \overline C $.
+This is because Dana Scott and Paul Taylor perform most of their constructions explicitly using the (idempotent) morphisms of $ C $, which is closest to working in $ \overline C $.
 
-  It is however very well possible that most of the proofs can be made to work in $ \hat \R $ as well.
-For future research, it would be interesting to see what the differences are between working in $ \R $ and $ \hat \R $ for these proofs.
+  It is however very well possible that most of the proofs can be made to work in $ \hat C $ as well.
+For future research, it would be interesting to see what the differences are between working in $ \overline C $ and $ \hat C $ for these proofs.
 \end{remark}

### 2024-05-01 report/chapters/paper.tex
Start working on Hyland's Taylor fibration

@@
 \begin{lemma}
-  We have a natural isomorphism between the two functors from $ \R $ to $ P \mathbf L $ in the diagram above.
+  The square in the diagram above 2-commutes.
 \end{lemma}
@@
   \[ \R(U^n, A) \cong \{ a : L_n \mid A a = a \}. \]
-  \TODO: Check coherence.
+  Of course, this is natural in $ A $, since for $ g: \R(A, B) $, postcomposing elements of $ \R(U^n, A) $ by $ g $ is equivalent to applying $ g $ to the elements of $ \{ a : L_n \mid A a = a \} $.
+
+  \TODO: Check naturality in $ n $.
 \end{proof}
@@
 
-Recall that Paul Taylor constructed a class of display maps for $ \R $.
+Recall that Paul Taylor constructed a category of `dependent retracts' $ \R^A $, and then defined a class of display maps for $ \R $ in such a way that it gives a weak equivalence $ \sum_A : \R^A \xrightarrow{\sim} (\R \downarrow_D A) $.
+I.e., a map $ f: \R(X, A) $ is defined to be a display map if it is isomorphic to something in the image of the functor $ \sum_A $.
+We saw that these display maps can also be characterized as the retracts of $ p_1: A \times U \to A $ in $ (\R \downarrow A) $.
+
+Now, noticing that we can embed $ \R $ as a full subcategory in $ \Pshf L $, Hyland attempts to do a similar thing for $ \Pshf L $.
+Noting that the universal object $ U : \R $ is embedded as the theory presheaf $ L : \Pshf L $, he defines a full subcategory $ \R(A) \subseteq (\Pshf L \downarrow A) $, consisting precisely of the retracts of $ p_1: A \times L \to A $ in $ (\Pshf L \downarrow A) $.
+
+\begin{remark}
+  Again, being a retract of $ p_1 $ is not a mere proposition. For example, consider $ \id L : D(L, L) $:
+  \begin{center}
+    \begin{tikzcd}
+      L \arrow[rr, shift left, "s"] \arrow[rd, "\id L"'] & & L \times L \arrow[ll, shift left, "r"] \arrow[ld, "p_1"]\\
+      & L
+    \end{tikzcd}
+  \end{center}
+  There are multiple possible retraction-section pairs $ (r, s) $ that make the diagram commute.
+For example, we can take $ s $ to be the diagonal embedding $ \Delta : L \to L \times L $ (sending $ l $ to $ (l, l) $).
+Then we can take $ r = p_1 $ or $ r = p_2 $.
+We can also take $ r = \pi_1 $ and $ s = \langle \id L, g \rangle $ the product morphism of $ \id L $ and any (possibly constant) endomorphism $ g: L \to L $.
+
+  Therefore, we need to take the propositional truncation of the existence of $ r $ and $ s $.
+\end{remark}
+
+\begin{remark}
+  Taylor would write $ (\Pshf L \downarrow_D A) $ instead of $ \R(A) $, with $ D(X, A) $ the retracts $ f: X \to A $ of $ p_1 : L \times A \to A $.
+However, note that $ D $ is not a class of display maps.
+For example, for $ D $ to be a class of display maps, all terminal projections $ !
+: X \to T $ need to be in $ D $.
+Since for any category $ C $ with terminal object $ T $, we have an equivalence $ (C \downarrow T) \cong C $, having all terminal projections in $ D $ is equivalent to every object in $ \Pshf L $ being a retract of $ L $.
+
+  However, if we take $ X $ to be the empty (initial) presheaf, we see that there are no morphisms $ L \to X $, because the $ L_n $ are nonempty and the $ X_n $ are empty.
+
+  There also is a more category-theoretical argument: Suppose that every object of $ \Pshf L $ is a retract of $ L $.
+Via the equivalence $ \Pshf L \cong L_1 $, we see that every object of $ P L_1 $ is a retract of $ Y(\star) $.
+However then the embedding of $ \hat \R $ (Definition \ref{def:karoubi'}) into $ P L_1 $ is an adjoint equivalence.
+Since $ Y_{\R} \bullet {\op{\iota_{L_1}}}_* : \R \to \hat \R $ and $ {\op{\iota_{L_1}}}_* : P \R \to P L_1 $ are weak equivalences, (Lemma \ref{lem:retracts-rezk}, Corollary \ref{cor:karoubi-presheaf}), $ Y_\R : \R \to P \R $ is a weak equivalence as well, but the Yoneda embedding is never essentially surjective.
+For example, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = Y(c)(c) $, so $ Y(c) $ is not isomorphic to $ E $.
+\end{remark}
 

### 2024-05-01 transcript/summary.tex
Start working on Hyland's Taylor fibration

@@
   Yet another way to think of a cartesian operad is as a one-object cartesian multicategory.
-A \textbf{cartesian multicategory} is a multicategory with an $ S_n $-action on the hom-sets (in other words: we can permute the arguments of the morphsims) and duplication/diagonal/contraction operations
+A \textbf{cartesian multicategory} is a multicategory with an $ S_n $-action on the hom-sets (in other words: we can permute the arguments of the morphisms) and duplication/diagonal/contraction operations
   \[ \mathrm{Hom}(c_1, \dots, c_k, c_k, \dots, c_n; c) \to \mathrm{Hom}(c_1, \dots, c_k, \dots, c_n; c) \]

### 2024-05-07 report/chapters/category-theory.tex
Show that the dependent product and sum send R(Y) to R(X)

@@
 
+% Now, if we have an object in a slice category, we can again look at the slice of the slice category over that object. However, this gives us nothing new:
+% \begin{lemma}
+%   Let $ (d, f) $ be an object in the slice category $ (C \downarrow c) $. The slice category $ ((C \downarrow c) \downarrow (d, f)) $ is equivalent to $ (C \downarrow d) $.
+% \end{lemma}
+% \begin{proof}
+%   An object of $ ((e, g), \alpha) : ((C \downarrow c) \downarrow (d, f)) $ is equivalent to an object $ (e, g) : (C \downarrow c) $, together with a morphism $ \alpha: (C \downarrow c)((e, g), (d, f)) $.
+That is, a morphism $ \alpha: C(e, d) $ such that the obvious triangle commutes (shown in the diagram below on the far left).
+
+%   Then a morphism between $ ((e, g), \alpha) $ and $ ((e^\prime, g^\prime), \alpha^\prime) $ is a morphism $ \beta $ between $ (e, g) $ and $ (e^\prime, g^\prime) $ that commutes with $ \alpha $ and $ \alpha^\prime $.
+Note that a morphism between $ (e, g) $ and $ (e^\prime, g^\prime) $ is a morphism between $ e $ and $ e^\prime $ that commutes with $ g $ and $ g^\prime $.
+%   \begin{center}
+%     \begin{tikzcd}
+%       e \arrow[rdd, "g"'] \arrow[rd, "\alpha"] \arrow[rr, "\beta"] && e^\prime \arrow[ldd, "g^\prime"] \arrow[ld, "\alpha^\prime"']\\
+%       & d \arrow[d, "f" description]\\
+%       & c
+%     \end{tikzcd}
+%     $ \Leftrightarrow $
+%     \begin{tikzcd}
+%       e \arrow[rd, "\alpha"] \arrow[rr, "\beta"] && e^\prime \arrow[ld, "\alpha^\prime"']\\
+%       & d
+%     \end{tikzcd}
+%   \end{center}
+
+%   Now, note that $ g $ and $ g^\prime $ are completely determined by $ g = \alpha \cdot f $ and $ g^\prime = \alpha^\prime \cdot f $.
+Also, if $ \beta $ commutes with $ \alpha $ and $ \alpha^\prime $, it automatically also commutes with $ g $ and $ g^\prime $.
+Therefore, as shown above, we have a correspondence between objects and morphisms
+%   \[ \beta: ((e, g), \alpha) \to ((e^\prime, g^\prime), \alpha^\prime) \Leftrightarrow \beta: (e, \alpha), (e^\prime, \alpha^\prime). \]
+% \end{proof}
+
+% Also, it turns out that we can derive some structure of the slice categories from the original category:
+% \begin{lemma}
+%   For $ (d, f), (d^\prime, f^\prime) : (C \downarrow c) $, their product in the slice category is given by their pullback / fibered product $ d \times_c d^\prime $, together with the induced morphism $ g: d \times_c d^\prime \dasharrow c $.
+% \end{lemma}
+% \begin{proof}
+%   Consider the diagram below.
+The fibered product gives `projections' $ h $ and $ h^\prime $.
+Also, if we have some $ (e, \alpha) : (C \downarrow c) $, together with morphisms $ \beta : (e, \alpha) \to (d, f) $ and $ \beta^\prime : (e, \alpha) \to (d^\prime, f^\prime) $.
+Then $ \beta $ and $ \beta^\prime $ commute with $ f $ and $ f^\prime $, so by the universal property of the fibred product, there exists a unique morphism $ \gamma : e \to d \times_c d^\prime $ that makes the triangles with $ \beta $ and $ h $, and with $ \beta^\prime $ and $ h^\prime $ commute.
+Then $ \gamma $ commutes with $ \alpha $ and $ g $ as well, so it is a morphism in $ (C \downarrow c) $.
+This shows that $ (d \times_c d^\prime, g) $ has the universal property of the product in $ (C \downarrow c) $.
+%   \begin{center}
+%     \begin{tikzcd}
+%       e \arrow[rd, "\beta"] \arrow[rr, "\beta^\prime", bend left] \arrow[rrd, "\alpha"', bend right=49, shift right] \arrow[r, dashed, "\gamma"] & d \times_c d^\prime \arrow[r, "h^\prime"'] \arrow[d, "h"] \arrow[rd, dashed, "g"] & d^\prime \arrow[d, "f^\prime"] \\
+%       & d \arrow[r, "f"] & c
+%     \end{tikzcd}
+%   \end{center}
+% \end{proof}
+
 \section{Dependent products and sums}\label{sec:dependent-products}
@@
 It turns out that in practice, we will never have a hard time obtaining dependent sums:
-\begin{lemma}
+\begin{lemma}\label{lem:sum-postcomposition}
   Let $ \alpha : C(B, A) $ be a morphism in a category.
@@
 
-Now, there is also another (classically equivalent) definition of the category of retracts:
+Now, there is also another (classically equivalent) definition of the Karoubi envelope:
 \begin{definition}\label{def:karoubi'}
@@
 
-  In this thesis, I will choose to interpret the `category of retracts' to mean $ \overline C $.
+  In this thesis, I will choose to interpret the `category of retracts' or `Karoubi envelope' to mean $ \overline C $.
 This is because Dana Scott and Paul Taylor perform most of their constructions explicitly using the (idempotent) morphisms of $ C $, which is closest to working in $ \overline C $.

### 2024-05-07 report/chapters/paper.tex
Show that the dependent product and sum send R(Y) to R(X)

@@
 \section{Scott's Representation Theorem}
-\begin{theorem}
+\begin{theorem}\label{thm:representation-theorem}
   Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E(L) $ of $ L: \Pshf L $, which is $ L $, viewed as a presheaf in its own presheaf category.
@@
 I.e., a map $ f: \R(X, A) $ is defined to be a display map if it is isomorphic to something in the image of the functor $ \sum_A $.
-We saw that these display maps can also be characterized as the retracts of $ p_1: A \times U \to A $ in $ (\R \downarrow A) $.
+We saw that these display maps can also be characterized as the retracts of the projection $ p_1: A \times U \to A $ in $ (\R \downarrow A) $.
+
+For a category $ C $ with products, Hyland introduces the notation $ \Delta_X Y $ for the element $ (X \times Y, p_1) : (C \downarrow X) $, and we will follow his example in this.
 
 Now, noticing that we can embed $ \R $ as a full subcategory in $ \Pshf L $, Hyland attempts to do a similar thing for $ \Pshf L $.
-Noting that the universal object $ U : \R $ is embedded as the theory presheaf $ L : \Pshf L $, he defines a full subcategory $ \R(A) \subseteq (\Pshf L \downarrow A) $, consisting precisely of the retracts of $ p_1: A \times L \to A $ in $ (\Pshf L \downarrow A) $.
+Noting that the universal object $ U : \R $ is embedded as the theory presheaf $ L : \Pshf L $, he defines a full subcategory $ \R(A) \subseteq (\Pshf L \downarrow A) $, consisting precisely of the retracts of $ \Delta_A L $ in $ (\Pshf L \downarrow A) $.
 
 \begin{remark}
-  Again, being a retract of $ p_1 $ is not a mere proposition. For example, consider $ \id L : D(L, L) $:
+  Again, being a retract of $ \Delta_A L $ is not a mere proposition. For example, consider $ \id L : D(L, L) $:
   \begin{center}
@@
 \begin{remark}
-  Taylor would write $ (\Pshf L \downarrow_D A) $ instead of $ \R(A) $, with $ D(X, A) $ the retracts $ f: X \to A $ of $ p_1 : L \times A \to A $.
+  Taylor would write $ (\Pshf L \downarrow_D A) $ instead of $ \R(A) $, with $ D(X, A) $ the retracts $ f: X \to A $ of $ \Delta_A L $.
 However, note that $ D $ is not a class of display maps.
@@
 
-  However, if we take $ X $ to be the empty (initial) presheaf, we see that there are no morphisms $ L \to X $, because the $ L_n $ are nonempty and the $ X_n $ are empty.
+  However, if we take $ X $ to be the initial (empty) presheaf, we see that there are no morphisms $ L \to X $, because the $ L_n $ are nonempty and the $ X_n $ are empty.
 
@@
 Since $ Y_{\R} \bullet {\op{\iota_{L_1}}}_* : \R \to \hat \R $ and $ {\op{\iota_{L_1}}}_* : P \R \to P L_1 $ are weak equivalences, (Lemma \ref{lem:retracts-rezk}, Corollary \ref{cor:karoubi-presheaf}), $ Y_\R : \R \to P \R $ is a weak equivalence as well, but the Yoneda embedding is never essentially surjective.
-For example, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = Y(c)(c) $, so $ Y(c) $ is not isomorphic to $ E $.
+For any category $ C $, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = Y(c)(c) $, so $ Y(c) $ is not isomorphic to $ E $.
 \end{remark}
 
-\begin{theorem}
-  The category of retracts is locally cartesian closed \TODO.
-\end{theorem}
+Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \cite{borceux-3}).
+Therefore, for a morphism $ f: \Pshf L(Y, X) $, we have adjunctions
+\begin{center}
+  \begin{tikzcd}
+    (\Pshf L \downarrow X) \arrow[r, "f^*"' description, ""{name=B}] & (\Pshf L \downarrow Y) \arrow[l, bend right, "{\sum_f = - \cdot f}"'{name=A}] \arrow[l, bend left, "\prod_f"{name=C}]
+    \arrow[from=A, to=B, symbol=\dashv]
+    \arrow[from=B, to=C, symbol=\dashv]
+  \end{tikzcd}
+\end{center}
+
+\begin{remark}\label{rem:pullback-of-projection}
+  Note that for $ X, Y, Z : C $ and $ f: C(Y, X) $, the following diagram shows that $ f^* \Delta_X Z \cong \Delta_Y Z $:
+  \begin{center}
+    \begin{tikzcd}
+      Y \times Z \arrow[d, "p_1"] \arrow[r, "f \times \id Z"] & X \times Z \arrow[d, "p_1"] \arrow[r, "p_2"] & Z \arrow[d, "!"]\\
+      Y \arrow[r, "f"] & X \arrow [r, "!"] & T
+    \end{tikzcd}
+  \end{center}
+\end{remark}
+
+In fact, $ \Delta_X : C \to C / X $ is a functor, with $ \Delta_X(f) = \id X \times f $ for $ f: C(Y, Y^\prime) $. This functor preserves the terminal object, products and pullbacks:
+\begin{lemma}\label{lem:delta-limits}
+  $ \Delta_X $ preserves all limits.
+\end{lemma}
+\begin{proof}
+  Take a diagram $ ((A_i)_i, (f_j)_j) $ in $ C $.
+Suppose that this has a limit $ (L, (g_i)_i) : C $.
+Now, consider an object $ (B, q) : (C \downarrow X) $, together with morphisms $ h_i : (C \downarrow X)((B, q), \Delta_X A_i) $, that commute with the $ \Delta_X f_j $:
+  \begin{center}
+    \begin{tikzcd}
+      & B \arrow[ldd, "h_{m_j}"'] \arrow[rdd, "h_{n_j}"]\\
+      & X \times L \arrow[ld, "\Delta_X g_{m_j}"] \arrow[rd, "\Delta_X g_{n_j}"']\\
+      X \times A_{m_j} \arrow[rr, "\Delta_X f_j"'] & & X \times A_{n_j}
+    \end{tikzcd}
+  \end{center}
+  Then the morphisms in $ (C \downarrow X)((B, q), \Delta_X L) $, commuting with the $ \Delta_X g_j $ and $ h_j $ are the morphisms in $ C(B, X \times L) \cong C(B, X) \times C(B, L) $ that commute with the projections to $ X $ and the $ \id X \times g_j $ and $ h_j $.
+Since the morphisms in $ C(B, X) $ commuting with $ q $ and $ \id X $ are exactly $ q $, we can forget about this component, and the morphisms we are looking for correspond to the morphisms in $ C(B, L) $ that commute with the $ g_j $ and $ h_j \cdot p_1 $.
+Since $ (L, (g_j)_j) $ is a limit, this is a unique morphism.
+\end{proof}
+
+\begin{lemma}\label{lem:delta-exponentials}
+  $ \Delta_X $ preserves exponential objects:
+\end{lemma}
+\begin{proof}
+  See \cite{borceux-3}, Lemma 5.8.2. This lemma shows this via the following equivalences:
+  \begin{align*}
+    (C \downarrow X)((A, f), \Delta_X Y^Z) &\cong C(A, Y^Z)\\
+    &\cong C(A \times Z, Y)\\
+    &\cong (C \downarrow X)((A \times X \times Z, \langle f, p_1 \rangle), \Delta_X Y)\\
+    &\cong (C \downarrow X)((A, f) \times \Delta_X Z, \Delta_X Y)\\
+  \end{align*}
+\end{proof}
+
+\begin{lemma}\label{lem:constant-dependent-product}
+  For $ W, X, Z : C $ and $ p_1 : X \times Z \to X $,
+  \[ \prod_{p_1} \Delta_{X \times Z} W = \Delta_X W^Z \]
+\end{lemma}
+\begin{proof}
+  First of all, note that $ (C \downarrow X \times Z) \cong ((C \downarrow X) \downarrow \Delta_X Z) $.
+Also note that the composite morphism $ (X \times Z) \times W \xrightarrow{p_1} X \times Z \xrightarrow{p_1} X $ is the element $ \Delta_X (W \times Z) : (C \downarrow X) $.
+
+  By Proposition 1.34 in \cite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
+  \begin{center}
+    \begin{tikzcd}
+      \prod_{p_1} \Delta_{X \times Z} W \arrow[r] \arrow[d] & (\Delta_X Z \times W)^{\Delta_X Z} \arrow[d, "(\Delta_X p_1)^{\Delta_X Z}"]\\
+      X \arrow[r] & (\Delta_X Z)^{\Delta_X Z}
+    \end{tikzcd}
+  \end{center}
+
+  By Lemma \ref{lem:delta-exponentials}, $ \Delta_X $ preserves exponential objects, so the morphism on the right is $ \Delta_X p_1^Z : (C \downarrow X)(\Delta_X (Z \times W)^Z, \Delta_X Z^Z) $.
+However, we have an isomorphism $ (Z \times W)^Z \xrightarrow \sim Z^Z \times Z^W $, and then the morphism on the right becomes
+  \[ \Delta_X p_1 : (C \downarrow X)(\Delta_X(Z^Z \times Z^W), \Delta_X Z^Z) \]
+  We also have an isomorphism $ X \cong \Delta_X T $. Then by Lemma \ref{lem:delta-limits} and Remark \ref{rem:pullback-of-projection}, the pullback of this diagram is $ \Delta_X W^Z $:
+  \begin{center}
+    \begin{tikzcd}
+      \Delta_X W^Z \arrow[r] \arrow[d] & \Delta_X (Z^Z \times W^Z) \arrow[d, "p_1"]\\
+      \Delta_X T \arrow[r] & \Delta_X Z^Z
+    \end{tikzcd}
+  \end{center}
+\end{proof}
+
+Now, Hyland shows the following:
+\begin{lemma}
+  For $ (Y, f) : \R(X) $, we can restrict $ \sum_f $ and $ \prod_f $ to functors from $ \R(Y) $ to $ \R(X) $.
+\end{lemma}
+\begin{proof}
+  This proof proceeds by reducing, step by step, to a known case.
+
+  We take $ (Z, g) : \R(Y) $.
+Since functors preserve retraction-section pairs, $ \prod_f(Z, g) $ is a retract of $ \prod_f \Delta_Y L $.
+Now, if this is a retract of $ \Delta_X L $, then $ \prod_f(Z, g) $ is a retract of $ \Delta_X L $ as well: We can just compose retractions and sections.
+Therefore, to show that the image of $ \R(Y) $ under $ \prod_f $ lies within $ \R(X) $, we just need to show that $ \prod_f \Delta_Y L $ lies in $ \R(X) $.
+In the same way, for $ \sum_f $ we just need to show that $ \sum_f \Delta_Y L $ lies in $ \R(X) $.
+
+  By the definition of $ \R(X) $, $ (Y, f) $ is a retract:
+  \begin{center}
+    \begin{tikzcd}
+      Y \arrow[rd, "f"'] \arrow[r, "s"] & X \times L \arrow[d, "p_1"] \arrow[r, "r"] & Y \arrow[ld, "f"]\\
+      & X
+    \end{tikzcd}
+  \end{center}
+
+  The counits of the adjunctions $ r_* \vdash \prod_r $ and $ s_* \vdash \prod_s $, give maps
+  \[
+    \prod_f \Delta_Y L \xrightarrow{\prod_f \eta_r}
+    \prod_f \prod_r r^* \Delta_Y L \xrightarrow{\prod_f \prod_r \eta_s}
+    \prod_f \prod_r \prod_s s^* r^* \Delta_Y L
+  \]
+  Their composite is $ \prod_f \eta_{s \cdot r} $. However, note that $ r \cdot s = \id Y $, so we have an isomorphism of functors
+  \[ (s \cdot r)^* \cong \id{\Pshf L \downarrow Y} \quad \text{and} \quad \prod_{s \cdot r} \cong \id{\Pshf L \downarrow Y} \]
+  and transporting $ \eta_{s \cdot r} $ along these isomorphisms, we get the identity natural transformation $ \id{\Pshf L \downarrow Y} \Rightarrow \id{\Pshf L \downarrow Y} $.
+
+  Secondly, note that $ r \cdot f = p_1 $, so we have $ \prod_r \bullet \prod_f \cong \prod_{p_1} $.
+
+  Lastly, by Remark \ref{rem:pullback-of-projection}, $ r^* \Delta_Y L \cong \Delta_{X \times L} L $.
+
+  Therefore, we have the following diagram, showing that $ \prod_f \Delta_Y L $ is a retraction of $ \prod_{p_1} \Delta_{X \times L} L $:
+  \begin{center}
+    \begin{tikzcd}
+      & \prod_{p_1} \Delta_{X \times L} L\\
+      \prod_f \Delta_Y L
+        \arrow[r, "\prod_f \eta_r"]
+        \arrow[rr, bend right, "\prod_f \eta_{s \cdot r}"]
+        \arrow[rrr, bend right, "\id {\Pshf L \downarrow X}"] &
+      \prod_f \prod_r r^* \Delta_Y L \arrow[r, "\prod_f \prod_r \eta_s"] \arrow[u, "\sim"] &
+      \prod_f \prod_r \prod_s s^* r^* \Delta_Y L \arrow[r, "\sim"] &
+      \prod_f \Delta_Y L
+    \end{tikzcd}
+  \end{center}
+  In a similar way, $ \sum_f \Delta_Y L $ is a retract of $ \sum_{p_1} \Delta_{X \times L} L $:
+  \begin{center}
+    \begin{tikzcd}
+      & & \sum_{p_1} \Delta_{X \times L} L \\
+      \sum_f \Delta_Y L
+        \arrow[r, "\sim"]
+        \arrow[rrr, bend right, "\id {\Pshf L \downarrow X}"] &
+      \sum_f \sum_r \sum_s s^* r^* \Delta_Y L
+        \arrow[r, "\sum_f \sum_r \epsilon_s"]
+        \arrow[rr, bend right, "\sum_f \epsilon_{s \cdot r}"] &
+      \sum_f \sum_r r^* \Delta_Y L
+        \arrow[u, "\sim"]
+        \arrow[r, "\sum_f \epsilon_r"] &
+      \sum_f \Delta_Y L
+    \end{tikzcd}
+  \end{center}
+  So again, by the transitivity of retracts, we only have to show that $ \prod_{p_1} \Delta_{X \times L} L $ and $ \sum_{p_1} \Delta_{X \times L} L $ are retracts of $ \Delta_X L $.
+By Lemma \ref{lem:constant-dependent-product}, we have $ \prod_{p_1} \Delta_{X \times L} L \cong \Delta_X L^L $.
+By Lemma \ref{lem:sum-postcomposition}, the functor $ \sum_{p_1} $ is given by postcomposition, so $ \sum_{p_1} \Delta_{X \times L} L \cong \Delta_X (L \times L) $.
+
+  Since $ \Delta_X $ is a functor, and in particular, preserves retracts, we only have to show that $ L \times L $ and $ L^L $ are retracts of $ L $.
+
+  But we already saw in Theorem \ref{thm:representation-theorem} that $ L^L \cong A(L, 1) $ is a retract of $ L $.
+
+  Also, the (pairing and splitting) morphisms $ s: \Pshf L(L \times L, L) $ and $ r: \Pshf L(L, L \times L) $ given by
+  \[ s_n(a, b) = \lambda x_{n + 1}, x_{n + 1} a b \quad \text{and} \quad r_n(a) = (a (\lambda x_{n + 1} x_{n + 2}, x_{n + 1}), a (\lambda x_{n + 1} x_{n + 2}, x_{n + 2})) \]
+  exhibit $ L \times L $ as a retract of $ L $.
+\end{proof}
+
+% \begin{remark}
+%   Now, recall that according to Hyland, Taylor endows the category of retracts $ \R $ with a class of display maps $ D $, such that $ (\R \downarrow_D X) $ consists exactly of the retracts of $ \Delta_X U $.
+
+%   Hyland then claims that the fact that $ \R $ is cartesian closed relative to this class of display maps (which Taylor shows in his PhD thesis) follows from the theorem above.
+
+%   The proof of this recalls that $ \R $ is a full subcategory of $ \Pshf L $, and that for $ X : \R $, all elements of $ \R(X) $ (i.e.
+all $ X $-retracts of $ X \times L $) are also elements of $ \R $.
+This uses Definition \ref{def:karoubi'}, the alternative definition of the category $ \hat \R $ of retracts as the full subcategory of $ P L(1) $ consisting of the retracts of all $ Y(c) : P L(1) $ for $ c: L(1) $.
+
+%   And indeed, we have a weak equivalence $ \R \hookrightarrow \hat R $.
+One could imagine similar weak equivalences $ (\R \downarrow_D X) \hookrightarrow \R(X) $.
+One could then attempt, for some $ f: \R(X) $, to pre- and postcompose the functors $ \sum_f $, $ f^* $ and $ \prod_f $ with this equivalence, to get these functors on the relative slices of $ \R $.
+%   \begin{center}
+%     \begin{tikzcd}
+
+%     \end{tikzcd}
+%   \end{center}
+
+%   and its right adjoint $ \R(X) \to \R(Y) $ with these equivalences to get .
+
+%   However, for every $ \hat Y : \hat R $, we only have mere existence of a preimage $ Y : \R $.
+% \end{remark}
+% we can find an object $  $.
+
+% the definition of $ \hat \R $ as a full subcategory of $ P L(1) \cong \Pshf L $.
+
+% , and $ \iota: \R \hookrightarrow \Pshf L $ the embedding, $ \R(\iota(X)) $ is equivalent to $ (\R \downarrow_D X) $.
+This uses Definition \ref{def:karoubi'} of $ \hat \R $.
+By Lemma \ref{lem:retracts-rezk}, $ \R $ and $ \hat \R $ are weakly equivalent.
+% \begin{corollary}
+% \end{corollary}
+% \begin{proof}
+
+%   This stems from the idea that $ \Pshf L \cong P \R $, and that $ \R $ consists exactly of the retracts of $  $.
+%   However, without the axiom of choice, it is only equivalent to $ (\hat \R \downarrow_D X) $.
+% \end{proof}
 

### 2024-05-13 report/chapters/paper.tex
Write about Hyland's proof of relative cartesian closedness

@@
 Now, Hyland shows the following:
-\begin{lemma}
+\begin{theorem}\label{thm:restrict-sum-product}
   For $ (Y, f) : \R(X) $, we can restrict $ \sum_f $ and $ \prod_f $ to functors from $ \R(Y) $ to $ \R(X) $.
-\end{lemma}
+\end{theorem}
 \begin{proof}
@@
 
-% \begin{remark}
-%   Now, recall that according to Hyland, Taylor endows the category of retracts $ \R $ with a class of display maps $ D $, such that $ (\R \downarrow_D X) $ consists exactly of the retracts of $ \Delta_X U $.
+\begin{remark}
+  Now, recall that according to Hyland, Taylor endows the category of retracts $ \R $ with a class of display maps $ D $, such that $ (\R \downarrow_D X) $ consists exactly of the retracts of $ \Delta_X U $.
 
-%   Hyland then claims that the fact that $ \R $ is cartesian closed relative to this class of display maps (which Taylor shows in his PhD thesis) follows from the theorem above.
+  Hyland then claims that the fact that $ \R $ is cartesian closed relative to this class of display maps follows from the theorem above.
+Recall that Taylor already shows relative cartesian closedness directly, which still works in univalent foundations if we assume the axiom of choice.
 
-%   The proof of this recalls that $ \R $ is a full subcategory of $ \Pshf L $, and that for $ X : \R $, all elements of $ \R(X) $ (i.e.
-all $ X $-retracts of $ X \times L $) are also elements of $ \R $.
-This uses Definition \ref{def:karoubi'}, the alternative definition of the category $ \hat \R $ of retracts as the full subcategory of $ P L(1) $ consisting of the retracts of all $ Y(c) : P L(1) $ for $ c: L(1) $.
+  Recall that we have a weak equivalence $ \varphi : \R \xrightarrow \sim \hat \R $ (Lemma \ref{lem:retracts-rezk}) and one can imagine that we can extend this to weak equivalences $ \psi_X : (\R \downarrow_D X) \xrightarrow \sim (\hat \R \downarrow_D \varphi(X)) $.
+Hyland notes that for $ X : \hat \R $, $ \R(\varphi(X)) $ is equivalent to $ (\hat \R \downarrow_D \varphi(X)) $.
+Implicitly, for $ f: \R(X, Y) $, he wants to lift the functors $ \sum_f $, $ f^* $ and $ \prod_f $ along the equivalences $ \psi $:
+  \begin{center}
+    \begin{tikzcd}[column sep = .5in, row sep = .5in]
+      (\R \downarrow_D X)
+        \arrow[d, "\psi_X"]
+        \arrow[r, dashed, bend left, "\sum_f"']
+        \arrow[r, dashed, bend right, "\prod_f"]
+      & (\R \downarrow_D Y)
+        \arrow[d, "\psi_Y"]
+        \arrow[l, dashed, "f^*" description]\\
+      \R(\varphi(X))
+        \arrow[r, bend left, "\sum_{\varphi(f)}"']
+        \arrow[r, bend right, "\prod_{\varphi(f)}"]
+      & \R(\varphi(Y))
+        \arrow[l, "\varphi(f)^*" description]\\
+    \end{tikzcd}
+  \end{center}
+  For this to work, we need to turn the weak equivalences $ \psi_X $ into adjoint equivalences.
+In particular, we know that for every object $ A : \R(\varphi(X)) $, there merely exists a preimage $ \bar A : (\R \downarrow_D X) $ such that $ \psi_X(\bar A) \cong A $, and we need to construct a functor $ \psi_X^{-1}: \R(\varphi(X)) \to (\R \downarrow_D X) $.
 
-%   And indeed, we have a weak equivalence $ \R \hookrightarrow \hat R $.
-One could imagine similar weak equivalences $ (\R \downarrow_D X) \hookrightarrow \R(X) $.
-One could then attempt, for some $ f: \R(X) $, to pre- and postcompose the functors $ \sum_f $, $ f^* $ and $ \prod_f $ with this equivalence, to get these functors on the relative slices of $ \R $.
-%   \begin{center}
-%     \begin{tikzcd}
+  For Taylor's proof, we did a similar thing when we knew that for every object $ X : (\R \downarrow_D A) $, there existed some $ Y : \R^A $, and we needed to construct a pullback functor $ f^* : (\R \downarrow_D A) \to (\R \downarrow_D B) $.
+We could use the axiom of choice here because the objects of $ \R $ (and therefore also the objects of the relative slices $ (\R \downarrow_D A) $) form a set.
 
-%     \end{tikzcd}
-%   \end{center}
+  However, as mentioned in \cite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \cite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
 
-%   and its right adjoint $ \R(X) \to \R(Y) $ with these equivalences to get .
-
-%   However, for every $ \hat Y : \hat R $, we only have mere existence of a preimage $ Y : \R $.
-% \end{remark}
-% we can find an object $  $.
-
-% the definition of $ \hat \R $ as a full subcategory of $ P L(1) \cong \Pshf L $.
-
-% , and $ \iota: \R \hookrightarrow \Pshf L $ the embedding, $ \R(\iota(X)) $ is equivalent to $ (\R \downarrow_D X) $.
-This uses Definition \ref{def:karoubi'} of $ \hat \R $.
-By Lemma \ref{lem:retracts-rezk}, $ \R $ and $ \hat \R $ are weakly equivalent.
-% \begin{corollary}
-% \end{corollary}
-% \begin{proof}
-
-%   This stems from the idea that $ \Pshf L \cong P \R $, and that $ \R $ consists exactly of the retracts of $  $.
-%   However, without the axiom of choice, it is only equivalent to $ (\hat \R \downarrow_D X) $.
-% \end{proof}
+  Therefore, in univalent foundations, the relative cartesian closedness is not a corollary of Theorem \ref{thm:restrict-sum-product}.
+\end{remark}
 

### 2024-05-16 report/chapters/category-theory.tex
Write about the karoubi envelope of a Lambda-algebra

--- 2024-05-01 report/chapters/category-theory.tex
@@
 
+Now, if we have an object in a slice category, we can again look at the slice of the slice category over that object. However, this gives us nothing new:
+\begin{lemma}
+  Let $ (d, f) $ be an object in the slice category $ (C \downarrow c) $. The slice category $ ((C \downarrow c) \downarrow (d, f)) $ is equivalent to $ (C \downarrow d) $.
+\end{lemma}
+\begin{proof}
+  An object of $ ((e, g), \alpha) : ((C \downarrow c) \downarrow (d, f)) $ is an object $ (e, g) : (C \downarrow c) $, together with a morphism $ \alpha: (C \downarrow c)((e, g), (d, f)) $.
+That is, a morphism $ \alpha: C(e, d) $ such that the obvious triangle commutes (shown in the diagram below on the far left).
+
+  Then a morphism between $ ((e, g), \alpha) $ and $ ((e^\prime, g^\prime), \alpha^\prime) $ is a morphism $ \beta $ between $ (e, g) $ and $ (e^\prime, g^\prime) $ that commutes with $ \alpha $ and $ \alpha^\prime $.
+Note that a morphism between $ (e, g) $ and $ (e^\prime, g^\prime) $ is a morphism between $ e $ and $ e^\prime $ that commutes with $ g $ and $ g^\prime $.
+  \begin{center}
+    \begin{tikzcd}
+      e \arrow[rdd, "g"'] \arrow[rd, "\alpha"] \arrow[rr, "\beta"] && e^\prime \arrow[ldd, "g^\prime"] \arrow[ld, "\alpha^\prime"']\\
+      & d \arrow[d, "f" description]\\
+      & c
+    \end{tikzcd}
+    $ \Leftrightarrow $
+    \begin{tikzcd}
+      e \arrow[rd, "\alpha"] \arrow[rr, "\beta"] && e^\prime \arrow[ld, "\alpha^\prime"']\\
+      & d
+    \end{tikzcd}
+  \end{center}
+
+  Now, note that $ g $ and $ g^\prime $ are completely determined by $ g = \alpha \cdot f $ and $ g^\prime = \alpha^\prime \cdot f $, so we can leave them out.
+Also, if $ \beta $ commutes with $ \alpha $ and $ \alpha^\prime $, it automatically also commutes with $ g $ and $ g^\prime $.
+Therefore, as shown above, we have a correspondence between objects and morphisms
+  \[ \beta: ((e, g), \alpha) \to ((e^\prime, g^\prime), \alpha^\prime) \Leftrightarrow \beta: (e, \alpha) \to (e^\prime, \alpha^\prime). \]
+\end{proof}
+
+Also, it turns out that we can derive some structure of the slice categories from the original category:
+\begin{lemma}
+  For $ (d, f), (d^\prime, f^\prime) : (C \downarrow c) $, their product in the slice category is given by their pullback / fibered product $ d \times_c d^\prime $, together with the induced morphism $ g: d \times_c d^\prime \dasharrow c $.
+\end{lemma}
+\begin{proof}
+  Consider the diagram below.
+The fibered product gives `projections' $ h $ and $ h^\prime $.
+Also, if we have some $ (e, \alpha) : (C \downarrow c) $, together with morphisms $ \beta : (e, \alpha) \to (d, f) $ and $ \beta^\prime : (e, \alpha) \to (d^\prime, f^\prime) $.
+Then $ \beta $ and $ \beta^\prime $ commute with $ f $ and $ f^\prime $, so by the universal property of the fibred product, there exists a unique morphism $ \gamma : e \to d \times_c d^\prime $ that makes the triangles with $ \beta $ and $ h $, and with $ \beta^\prime $ and $ h^\prime $ commute.
+Then $ \gamma $ commutes with $ \alpha $ and $ g $ as well, so it is a morphism in $ (C \downarrow c) $.
+This shows that $ (d \times_c d^\prime, g) $ has the universal property of the product in $ (C \downarrow c) $.
+  \begin{center}
+    \begin{tikzcd}
+      e \arrow[rd, "\beta"] \arrow[rr, "\beta^\prime", bend left] \arrow[rrd, "\alpha"', bend right=49, shift right] \arrow[r, dashed, "\gamma"] & d \times_c d^\prime \arrow[r, "h^\prime"'] \arrow[d, "h"] \arrow[rd, dashed, "g"] & d^\prime \arrow[d, "f^\prime"] \\
+      & d \arrow[r, "f"] & c
+    \end{tikzcd}
+  \end{center}
+\end{proof}
+
+For a category $ C $ with products, Hyland introduces the notation $ \Delta_X Y $ for the element $ (X \times Y, p_1) : (C \downarrow X) $, and we will follow his example in this.
+
+In fact, $ \Delta_X : C \to C / X $ is a functor, with $ \Delta_X(f) = \id X \times f $ for $ f: C(Y, Y^\prime) $. This functor preserves the terminal object, products and pullbacks:
+\begin{lemma}\label{lem:delta-limits}
+  $ \Delta_X $ preserves all limits.
+\end{lemma}
+\begin{proof}
+  Take a diagram $ ((A_i)_i, (f_j)_j) $ in $ C $.
+Suppose that this has a limit $ (L, (g_i)_i) : C $.
+Now, consider an object $ (B, q) : (C \downarrow X) $, together with morphisms $ h_i : (C \downarrow X)((B, q), \Delta_X A_i) $, that commute with the $ \Delta_X f_j $:
+  \begin{center}
+    \begin{tikzcd}
+      & B \arrow[ldd, "h_{m_j}"'] \arrow[rdd, "h_{n_j}"]\\
+      & X \times L \arrow[ld, "\Delta_X g_{m_j}"] \arrow[rd, "\Delta_X g_{n_j}"']\\
+      X \times A_{m_j} \arrow[rr, "\Delta_X f_j"'] & & X \times A_{n_j}
+    \end{tikzcd}
+  \end{center}
+  Then the morphisms in $ (C \downarrow X)((B, q), \Delta_X L) $, commuting with the $ \Delta_X g_j $ and $ h_j $ are the morphisms in $ C(B, X \times L) \cong C(B, X) \times C(B, L) $ that commute with the projections to $ X $ and the $ \id X \times g_j $ and $ h_j $.
+Since the morphisms in $ C(B, X) $ commuting with $ q $ and $ \id X $ are exactly $ q $, we can forget about this component, and the morphisms we are looking for correspond to the morphisms in $ C(B, L) $ that commute with the $ g_j $ and $ h_j \cdot p_1 $.
+Since $ (L, (g_j)_j) $ is a limit, this is a unique morphism.
+\end{proof}
+
+\begin{lemma}\label{lem:delta-exponentials}
+  $ \Delta_X $ preserves exponential objects:
+\end{lemma}
+\begin{proof}
+  See \cite{borceux-3}, Lemma 5.8.2. This lemma shows this via the following equivalences:
+  \begin{align*}
+    (C \downarrow X)((A, f), \Delta_X Y^Z) &\cong C(A, Y^Z)\\
+    &\cong C(A \times Z, Y)\\
+    &\cong (C \downarrow X)((A \times X \times Z, \langle f, p_1 \rangle), \Delta_X Y)\\
+    &\cong (C \downarrow X)((A, f) \times \Delta_X Z, \Delta_X Y)\\
+  \end{align*}
+\end{proof}
+
 \section{Dependent products and sums}\label{sec:dependent-products}
@@
   See the end of Section 1.3 of \cite{freyd}.
+\end{proof}
+
+\begin{remark}\label{rem:pullback-of-projection}
+  Note that for $ X, Y, Z : C $ and $ f: C(Y, X) $, the following diagram shows that $ f^* \Delta_X Z \cong \Delta_Y Z $:
+  \begin{center}
+    \begin{tikzcd}
+      Y \times Z \arrow[d, "p_1"] \arrow[r, "f \times \id Z"] & X \times Z \arrow[d, "p_1"] \arrow[r, "p_2"] & Z \arrow[d, "!"]\\
+      Y \arrow[r, "f"] & X \arrow [r, "!"] & T
+    \end{tikzcd}
+  \end{center}
+\end{remark}
+
+\begin{lemma}\label{lem:constant-dependent-product}
+  For $ W, X, Z : C $ and $ p_1 : X \times Z \to X $,
+  \[ \prod_{p_1} \Delta_{X \times Z} W \cong \Delta_X W^Z \]
+\end{lemma}
+\begin{proof}
+  First of all, note that $ (C \downarrow X \times Z) \cong ((C \downarrow X) \downarrow \Delta_X Z) $.
+Also note that the composite morphism $ (X \times Z) \times W \xrightarrow{p_1} X \times Z \xrightarrow{p_1} X $ is the element $ \Delta_X (W \times Z) : (C \downarrow X) $.
+
+  By Proposition 1.34 in \cite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
+  \begin{center}
+    \begin{tikzcd}
+      \prod_{p_1} \Delta_{X \times Z} W \arrow[r] \arrow[d] & (\Delta_X Z \times W)^{\Delta_X Z} \arrow[d, "(\Delta_X p_1)^{\Delta_X Z}"]\\
+      X \arrow[r] & (\Delta_X Z)^{\Delta_X Z}
+    \end{tikzcd}
+  \end{center}
+
+  By Lemma \ref{lem:delta-exponentials}, $ \Delta_X $ preserves exponential objects, so the morphism on the right is $ \Delta_X p_1^Z : (C \downarrow X)(\Delta_X (Z \times W)^Z, \Delta_X Z^Z) $.
+However, we have an isomorphism $ (Z \times W)^Z \cong Z^Z \times Z^W $, and then the morphism on the right becomes
+  \[ \Delta_X p_1 : (C \downarrow X)(\Delta_X(Z^Z \times Z^W), \Delta_X Z^Z) \]
+  We also have an isomorphism $ X \cong \Delta_X T $. Then by Lemma \ref{lem:delta-limits} and Remark \ref{rem:pullback-of-projection}, the pullback of this diagram is $ \Delta_X W^Z $:
+  \begin{center}
+    \begin{tikzcd}
+      \Delta_X W^Z \arrow[r] \arrow[d] & \Delta_X (Z^Z \times W^Z) \arrow[d, "\Delta_X p_1"]\\
+      \Delta_X T \arrow[r] & \Delta_X Z^Z
+    \end{tikzcd}
+  \end{center}
 \end{proof}

### 2024-05-16 report/chapters/paper.tex
Write about the karoubi envelope of a Lambda-algebra

@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:equivalent-presheaf-cats}
   The precomposition functors $ i_* $ and $ j_* $ are adjoint equivalences.
@@
   \[ (Y \bullet j_*)(A)(n) = (j \bullet (Y(A)))(n) = Y(A)(j(n)) = \R(U^n, A) \]
-  \[ (\iota \bullet \sim)(A)(n) = \{ a : L_n \mid A a = a \} \]
+  \[ (\iota \bullet \sim)(A)(n) = \{ a : L_n \mid \iota_{0, n}(A) a = a \} \]
 
-  By Scott's representation theorem, we have $ \mathbb R(U^n, U) \cong L_n, $ via
-  \[ f \mapsto \iota_{0, n}(f) ((((c, x_1), x_2), \dots), x_n). \]
+  By Scott's representation theorem, we have $ \varphi_n: \R(U^n, U) \xrightarrow \sim L_n, $ given by
+  \[ \varphi_n(f) = \iota_{0, n}(f) ((((c, x_1), x_2), \dots), x_n). \]
   Restricting this equivalence to the morphisms to $ A $ yields
@@
 
-  \TODO: Check naturality in $ n $.
+  Lastly, for $ f : L_m^n $, the presheaf actions
+  \[ (Y \bullet j_*)(A)(f) : \R(U^n, A) \to \R(U^m, A) \]
+  and
+  \[ (\iota \bullet \sim)(A)(f) : \{ a : L_n \mid \iota_{0, n}(A) a = a \} \to \{ a : L_m \mid \iota_{0, n}(A) a = a \} \]
+  are in fact given by the substitution operations $ \bullet $ in $ E(U) $ and $ L $.
+Since Scott's representation theorem shows that $ E(U) $ is isomorphic to $ L $ as a $ \lambda $-theory, these substitutions are compatible with the $ \varphi_n $, which shows naturality in $ n $.
 \end{proof}
@@
 We saw that these display maps can also be characterized as the retracts of the projection $ p_1: A \times U \to A $ in $ (\R \downarrow A) $.
-
-For a category $ C $ with products, Hyland introduces the notation $ \Delta_X Y $ for the element $ (X \times Y, p_1) : (C \downarrow X) $, and we will follow his example in this.
 
@@
 \end{center}
-
-\begin{remark}\label{rem:pullback-of-projection}
-  Note that for $ X, Y, Z : C $ and $ f: C(Y, X) $, the following diagram shows that $ f^* \Delta_X Z \cong \Delta_Y Z $:
-  \begin{center}
-    \begin{tikzcd}
-      Y \times Z \arrow[d, "p_1"] \arrow[r, "f \times \id Z"] & X \times Z \arrow[d, "p_1"] \arrow[r, "p_2"] & Z \arrow[d, "!"]\\
-      Y \arrow[r, "f"] & X \arrow [r, "!"] & T
-    \end{tikzcd}
-  \end{center}
-\end{remark}
-
-In fact, $ \Delta_X : C \to C / X $ is a functor, with $ \Delta_X(f) = \id X \times f $ for $ f: C(Y, Y^\prime) $. This functor preserves the terminal object, products and pullbacks:
-\begin{lemma}\label{lem:delta-limits}
-  $ \Delta_X $ preserves all limits.
-\end{lemma}
-\begin{proof}
-  Take a diagram $ ((A_i)_i, (f_j)_j) $ in $ C $.
-Suppose that this has a limit $ (L, (g_i)_i) : C $.
-Now, consider an object $ (B, q) : (C \downarrow X) $, together with morphisms $ h_i : (C \downarrow X)((B, q), \Delta_X A_i) $, that commute with the $ \Delta_X f_j $:
-  \begin{center}
-    \begin{tikzcd}
-      & B \arrow[ldd, "h_{m_j}"'] \arrow[rdd, "h_{n_j}"]\\
-      & X \times L \arrow[ld, "\Delta_X g_{m_j}"] \arrow[rd, "\Delta_X g_{n_j}"']\\
-      X \times A_{m_j} \arrow[rr, "\Delta_X f_j"'] & & X \times A_{n_j}
-    \end{tikzcd}
-  \end{center}
-  Then the morphisms in $ (C \downarrow X)((B, q), \Delta_X L) $, commuting with the $ \Delta_X g_j $ and $ h_j $ are the morphisms in $ C(B, X \times L) \cong C(B, X) \times C(B, L) $ that commute with the projections to $ X $ and the $ \id X \times g_j $ and $ h_j $.
-Since the morphisms in $ C(B, X) $ commuting with $ q $ and $ \id X $ are exactly $ q $, we can forget about this component, and the morphisms we are looking for correspond to the morphisms in $ C(B, L) $ that commute with the $ g_j $ and $ h_j \cdot p_1 $.
-Since $ (L, (g_j)_j) $ is a limit, this is a unique morphism.
-\end{proof}
-
-\begin{lemma}\label{lem:delta-exponentials}
-  $ \Delta_X $ preserves exponential objects:
-\end{lemma}
-\begin{proof}
-  See \cite{borceux-3}, Lemma 5.8.2. This lemma shows this via the following equivalences:
-  \begin{align*}
-    (C \downarrow X)((A, f), \Delta_X Y^Z) &\cong C(A, Y^Z)\\
-    &\cong C(A \times Z, Y)\\
-    &\cong (C \downarrow X)((A \times X \times Z, \langle f, p_1 \rangle), \Delta_X Y)\\
-    &\cong (C \downarrow X)((A, f) \times \Delta_X Z, \Delta_X Y)\\
-  \end{align*}
-\end{proof}
-
-\begin{lemma}\label{lem:constant-dependent-product}
-  For $ W, X, Z : C $ and $ p_1 : X \times Z \to X $,
-  \[ \prod_{p_1} \Delta_{X \times Z} W = \Delta_X W^Z \]
-\end{lemma}
-\begin{proof}
-  First of all, note that $ (C \downarrow X \times Z) \cong ((C \downarrow X) \downarrow \Delta_X Z) $.
-Also note that the composite morphism $ (X \times Z) \times W \xrightarrow{p_1} X \times Z \xrightarrow{p_1} X $ is the element $ \Delta_X (W \times Z) : (C \downarrow X) $.
-
-  By Proposition 1.34 in \cite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
-  \begin{center}
-    \begin{tikzcd}
-      \prod_{p_1} \Delta_{X \times Z} W \arrow[r] \arrow[d] & (\Delta_X Z \times W)^{\Delta_X Z} \arrow[d, "(\Delta_X p_1)^{\Delta_X Z}"]\\
-      X \arrow[r] & (\Delta_X Z)^{\Delta_X Z}
-    \end{tikzcd}
-  \end{center}
-
-  By Lemma \ref{lem:delta-exponentials}, $ \Delta_X $ preserves exponential objects, so the morphism on the right is $ \Delta_X p_1^Z : (C \downarrow X)(\Delta_X (Z \times W)^Z, \Delta_X Z^Z) $.
-However, we have an isomorphism $ (Z \times W)^Z \xrightarrow \sim Z^Z \times Z^W $, and then the morphism on the right becomes
-  \[ \Delta_X p_1 : (C \downarrow X)(\Delta_X(Z^Z \times Z^W), \Delta_X Z^Z) \]
-  We also have an isomorphism $ X \cong \Delta_X T $. Then by Lemma \ref{lem:delta-limits} and Remark \ref{rem:pullback-of-projection}, the pullback of this diagram is $ \Delta_X W^Z $:
-  \begin{center}
-    \begin{tikzcd}
-      \Delta_X W^Z \arrow[r] \arrow[d] & \Delta_X (Z^Z \times W^Z) \arrow[d, "p_1"]\\
-      \Delta_X T \arrow[r] & \Delta_X Z^Z
-    \end{tikzcd}
-  \end{center}
-\end{proof}
 
@@
 \[ a \circ b = (x_1 \circ x_2) \bullet (a, b) \]
-for $ a, b : A $, with $ x_1 \circ x_2 = \lambda x_3, x_1 (x_2 x_3) : \Lambda_2 $.
+and the same for the other constructions at the start of Section \ref{sec:retracts-category}.
 
@@
 \[ \LamTh \cong \Alg \Lambda. \]
-We will prove this by showing that there is a weak equivalence.
+We will prove this by showing that there is a weak equivalence. Using the fact that $ \LamTh $ is
 
@@
 
+Here, we are mostly interested in the case $ n = 0 $.
+
 \subsection{Lifting \texorpdfstring{$ \Lambda $}{Lambda}-algebras}
@@
 \begin{definition}[The monoid of a $ \Lambda $-algebra]
-  Now we make $ A_1 $ into a monoid under composition $ \circ $ with unit $ \mathbf 1_1 $. The fact that this is a monoid follows from the remarks in the last section.
+  We make $ A_1 $, the `functional elements' of $ A $, into a monoid under composition $ \circ $ with unit $ \mathbf 1_1 $. The fact that this is a monoid follows from the remarks in the last section.
 \end{definition}
@@
 
+\begin{remark}
+  Note that, like in the last chapter, we can take the Karoubi envelope $ \R_A $ of $ C_{A_1} $, which yields the following diagram:
+  \begin{center}
+    \begin{tikzcd}
+      & C_{A_1} \arrow[d, hookrightarrow, "Y"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "Y"]\\
+      \RAct{A_1} & P C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
+    \end{tikzcd}
+  \end{center}
+  Explicitly, this gives the embedding $ \R_A(U, -): \R_A \hookrightarrow \RAct{A_1} $ given by
+  \[ X \mapsto \R_A(U, X) = \{ x : A \mid X \circ x = x \}. \]
+  Actually, we can repeat almost the entirety of Section \ref{sec:retracts-category} for $ \R_A $. In particular, $ \R_A $ has products
+  \[ A \times B = \langle x_1 \circ \pi_1, x_2 \circ \pi_2 \rangle \bullet (A, B) \]
+  and exponential objects
+  \[ B^A = (\lambda x_3, x_1 \circ x_3 \circ x_2) \bullet (B, A) \]
+  with isomorphism
+  \[ \psi: \R_A(C \times A, B) \xrightarrow \sim \R_A(C, B^A) \]
+  given by
+  \[ \psi(f) = (\lambda x_2, x_1 (\pi_1 x_2) (\pi_2 x_2)) \bullet f \quad \text{and} \quad \psi^{-1}(f) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet f. \]
+\end{remark}
+
+\begin{remark}
+  Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $.
+From Lemma \ref{lem:equivalent-presheaf-cats}, it follows that $ \RAct{A_1} $ is equivalent to $ \Pshf L $.
+This might motivate some of the following constructions.
+\end{remark}
+
 \begin{definition}
-  Now, composition $ \circ $ gives a right $ A_1 $-action on the $ A_n $, so we have $ A_n : \RAct{A_1} $.
+  Now, composition $ \circ $ gives a right $ A_1 $-action on the $ A_n $, so we have $ A_n : \RAct{A_1} $ (note that this is the image of $ \mathbf 1_n : \R_A $ under the embeddding into $ \RAct{A_1} $).
 \end{definition}
@@
 \begin{lemma}
-  We have $ U_{A_1}^{U_{A_1}} \cong A_2 $ in $ \RAct{A_1} $.
+  $ A_2 $ is the exponential object $ A_1^{A_1} $ in $ \RAct{A_1} $.
 \end{lemma}
 \begin{proof}
-  Recall that $ U_{A_1}^{U_{A_1}} $ consists of the set of $ A_1 $-equivariant morphisms $ U_{A_1} \times U_{A_1} \to U_{A_1} $.
-
-  We have a bijection $ \varphi: A_2 \xrightarrow{\sim} U_{A_1}^{U_{A_1}} $, given by
-  \[ \varphi(a)(b, b^\prime) = (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (a, b, b^\prime), \]
-  \TODO: relate to product in category of retracts.
-
-  with an inverse given by
-  \[ \varphi^{-1}(f) = \lambda x_1 x_2, f(p_1, p_2)(\lambda x_3, x_3 x_1 x_2) \]
-  \TODO: Make more explicitly that we use $ \bullet $ here.
-  for $ p_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $. Note that for terms $ c_1, c_2 $, we have $ p_i (\lambda x_1, x_1 c_1 c_2) = c_i $.
-
-  This is an inverse, because given $ f: U_{A_1}^{U_{A_1}} $ and $ (a_1, a_2): U_{A_1} \times U_{A_1} $, we have
-  \[ \varphi(\psi(f))(a_1, a_2) = f(p_1, p_2) \circ q = f(p_1 \circ q, p_2 \circ q) = f(a_1, a_2) \]
-  for $ q = \lambda x_1, (\lambda x_2, x_2 (a_1 x_1) (a_2 x_1)) $.
-In the last step of this proof, we use, among other things, the fact that the $ a_i : A_1 $ and therefore $ \lambda x_1, a_i x_1 = a_i $.
-
-  Some straightforward rewriting shows that for $ a: A_2 $, we have $ \psi(\varphi(a)) = a $.
-In the last step of this proof, we use the fact that $ a : A_2 $ and therefore $ \lambda x_1 x_2, a x_1 x_2 = a $.
-
-  Therefore, $ \varphi $ is a bijection and, as it turns out, an isomorphism.
+  Note that the embedding $ \R_A \hookrightarrow \RAct{A_1} $ is the composition of a Yoneda embedding and two adjoint equivalences.
+These all preserve exponential objects (\TODO: Citation needed).
+Since $ A_1 $ is the image of $ \mathbf 1_1 : \R_A $, the exponential $ A_1^{A_1} $ is $ A_2 $, the image of $ \mathbf 1_1^{\mathbf 1_1} = \lambda x_1 x_2, x_1 x_2 $.
 \end{proof}
 
+\begin{remark}
+  Hyland shows this by explicitly constructing an isomorphism $ \psi $ between $ A_2 $ and the `familiar' exponential object in $ \RAct{A_1} $ (the set of $ A_1 $-equivariant morphisms $ U_{A_1} \times U_{A_1} \to U_{A_1} $), given by
+  \[ \varphi(f) = (b, b^\prime) \mapsto (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (f, b, b^\prime), \]
+  treating $ f : A_2 $ as a function in two elements, and simultaneously composing it with the functions $ b, b^\prime : A_1 $ in one argument. It has an inverse
+  \[ \varphi^{-1}(g) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet (g(\pi_1, \pi_2)). \]
+  Note that the first pair $ (x_2, x_3) $ is a $ \lambda $-term, whereas the second pair $ (\pi_1, \pi_2) $ is a pair in $ U_{A_1} \times U_{A_1} $.
+\end{remark}
+
 \begin{definition}[Construction of the $ \lambda $-theory]
-  Since $ \RAct{A_1} $ has products, the algebraic theory $ E(U_{A_1}) $ exists.
+  Now, note that, like before, $ \mathbf 1_1 $ is a retract of $ \mathbf 1_2 $ in $ \R_A $.
+The embedding into $ \RAct{A_1} $ turns this into the embedding as a subset $ A_2 \subseteq A_1 $ and a retraction $ r: A_1 \to A_2 $, given by precomposition with $ \mathbf 1_2 $.
 
-  Recall that $ A_2 \subseteq A_1 $ and that $ a \mapsto \mathbf 1_2 \circ a $ gives a function from $ A_1 $ to $ A_2 $, which is, by definition, the identity on $ A_2 $.
-This gives $ E(U_{A_1}) $ a $ \lambda $-theory structure with $ \beta $-equality.
+  Therefore, $ U_{A_1} $ is a reflexive object in $ \RAct{A_1} $, and we get an $ \lambda $-theory $ E(U_{A_1}) $.
 \end{definition}

### 2024-05-16 report/chapters/previous-work.tex
Write about the karoubi envelope of a Lambda-algebra

@@
 
-\begin{tabular}{|c|c|c|}\hline
-  $ K $ & $ \lambda xy.x $ & constant \\\hline
-  $ S $ & $ \lambda xyz.xz(yz) $ & \\\hline
-  $ I $ & $ \lambda x.x = SKK $ & identity \\\hline
-  $ Y $ & $ \lambda f.(\lambda x.f (xx))(\lambda x.f (xx)) $ & ﬁxpoint \\\hline
-  $ \bot $ & $ (\lambda x.xx)(\lambda x.xx) = (SII)(SII) = YI $ & bottom \\\hline
-  $ P $ & $ \lambda f gx.g(f x) = S(K(S(S(KS)K)))K $ & composition \\\hline
-  $ Q $ & $ \lambda f gax.ga(f ax) $ & ﬁbred composition \\\hline
-  $ \langle \rangle $ & $ \lambda xyz.zxy $ & pairing \\\hline
-  $ 0 $ & $ \lambda xy.x = K $ & left projection \\\hline
-  $ 1 $ & $ \lambda xy.y = KI $ & right projection \\\hline
-\end{tabular}
+% \begin{tabular}{|c|c|c|}\hline
+%   $ K $ & $ \lambda xy.x $ & constant \\\hline
+%   $ S $ & $ \lambda xyz.xz(yz) $ & \\\hline
+%   $ I $ & $ \lambda x.x = SKK $ & identity \\\hline
+%   $ Y $ & $ \lambda f.(\lambda x.f (xx))(\lambda x.f (xx)) $ & ﬁxpoint \\\hline
+%   $ \bot $ & $ (\lambda x.xx)(\lambda x.xx) = (SII)(SII) = YI $ & bottom \\\hline
+%   $ P $ & $ \lambda f gx.g(f x) = S(K(S(S(KS)K)))K $ & composition \\\hline
+%   $ Q $ & $ \lambda f gax.ga(f ax) $ & ﬁbred composition \\\hline
+%   $ \langle \rangle $ & $ \lambda xyz.zxy $ & pairing \\\hline
+%   $ 0 $ & $ \lambda xy.x = K $ & left projection \\\hline
+%   $ 1 $ & $ \lambda xy.y = KI $ & right projection \\\hline
+% \end{tabular}
 
@@
 
-\section{The category of retracts}
+\section{The category of retracts}\label{sec:retracts-category}
 
@@
   Hyland instead defines $ \R $ as
-  \[ \R_0 = \{ A : L_1 \mid A \bullet A = A \} \quad \text{and} \R(A, B) = \{ f : L_1 \mid B \bullet f \bullet A = f \}, \]
+  \[ \R_0 = \{ A : L_1 \mid A \bullet A = A \} \quad \text{and} \quad \R(A, B) = \{ f : L_1 \mid B \bullet f \bullet A = f \}, \]
   writing $ s \bullet t $ instead of $ s \bullet (t) $ for $ s, t : L_1 $. Note that the following diagram commutes:
@@
 We might wonder whether $ \R $ also has an initial object $ O $. However, for any $ c: L_0 $, we would have a constant morphism
-\[ I_c = \lambda x_1, \iota_{0, 1}(c) : \R(A, U), \]
+\[ I_c = \lambda x_1, \iota_{0, 1}(c) : \R(O, U), \]
 so if $ L $ is nontrivial, $ \R $ has no initial object.
@@
 Also note that
-\[ \lambda x_1, C \circ x_1 \circ B = C^B = \id{C^B} = \psi(\epsilon_{BC}). \]
-The first representation shows that $ \varphi(C^B)_0 = \R(B, C) $, as we would expect.
+\[ \psi(\epsilon_{BC}) = \lambda x_1, C \circ x_1 \circ B = C^B = \id{C^B}. \]
+Note that $ \varphi(C^B)_0 = \R(B, C) $, as we would expect.
 

### 2024-05-20 report/chapters/category-theory.tex
Write about essential surjectiviy

@@
 \begin{lemma}
-  We get a \iindex{restriction of scalars} functor $ \varphi_* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
+  We get a \iindex{restriction of scalars} functor $ \varphi^* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
 \end{lemma}
@@
 Since $ \SET $ has colimits, and restriction of scalars corresponds to precomposition of presheaves (on $ C_{M^\prime} $), we can give it a left adjoint.
-This is the (pointwise) left Kan extension, which boils down to:
+This is the (pointwise) left Kan extension, which boils down to a very concrete definition, reminiscent of a tensor product:
 
-\begin{lemma}
-  We get an \iindex{extension of scalars} functor $ \varphi^* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
+\begin{lemma}\label{lem:scalar-extension}
+  We get an \iindex{extension of scalars} functor $ \varphi_* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
 \end{lemma}
@@
 \begin{lemma}\label{lem:scalar-extension-monoid-monoid-action}
-  For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi^*(U_M) \cong U_{M^\prime} $.
+  For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi_*(U_M) \cong U_{M^\prime} $.
 \end{lemma}
@@
 \begin{lemma}\label{lem:scalar-extension-terminal}
-  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi^*(I_M) \cong I_{M^\prime} $.
+  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi_*(I_M) \cong I_{M^\prime} $.
 \end{lemma}
@@
 
-  The proof relies on the fact that every element of $ \varphi^*(I_M) $ is given by some $ (\star, m^\prime) $, but then
+  The proof relies on the fact that every element of $ \varphi_*(I_M) $ is given by some $ (\star, m^\prime) $, but then
   \[ (\star, m^\prime) = (\star \cdot m, m^\prime) \sim (\star, \varphi(m) \cdot m^\prime) = (\star, \overline{m^\prime}), \]
-  so $ \varphi^*(I_M) $ has exactly $ 1 $ element.
+  so $ \varphi_*(I_M) $ has exactly $ 1 $ element.
 \end{proof}
@@
 \begin{remark}
-  For $ \varphi^* $ to preserve terminal objects, we actually only need $ D $ to be connected.
-The fact that $ \varphi^*(I_M) $ is a quotient by a symmetric and transitive relation then allows us to `walk' from any $ (\star, m^\prime_1) $ to any other $ (\star, m^\prime_2) $ in small steps.
+  For $ \varphi_* $ to preserve terminal objects, we actually only need $ D $ to be connected.
+The fact that $ \varphi_*(I_M) $ is a quotient by a symmetric and transitive relation then allows us to `walk' from any $ (\star, m^\prime_1) $ to any other $ (\star, m^\prime_2) $ in small steps.
 \end{remark}
@@
   Suppose that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object for all $ m^\prime_1, m^\prime_2: M^\prime $.
-Then for sets $ A $ and $ B $ with right $ M $-action, we have $ \varphi^*(A \times B) \cong \varphi^*(A) \times \varphi^*(B) $.
+Then for sets $ A $ and $ B $ with right $ M $-action, we have $ \varphi_*(A \times B) \cong \varphi_*(A) \times \varphi_*(B) $.
 \end{lemma}
 \begin{proof}
-  Now, any element in $ \varphi^*(A) \times \varphi^*(B) = (A \times M^\prime / \sim) \times (B \times M^\prime / \sim) $ is given by some $ (a, m^\prime_1, b, m^\prime_2) $.
+  Now, any element in $ \varphi_*(A) \times \varphi_*(B) = (A \times M^\prime / \sim) \times (B \times M^\prime / \sim) $ is given by some $ (a, m^\prime_1, b, m^\prime_2) $.
 
@@
   \[ (a, m^\prime_1, b, m^\prime_2) = (a, \varphi(\overline m_1) \cdot \overline m^\prime, b, \varphi(\overline m_2) \cdot \overline m^\prime) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime), \]
-  so this is equivalent to some element in $ \varphi^*(A \times B) = (A \times B \times M^\prime / \sim) $. Note that this trivially respects the right $ M^\prime $-action.
+  so this is equivalent to some element in $ \varphi_*(A \times B) = (A \times B \times M^\prime / \sim) $. Note that this trivially respects the right $ M^\prime $-action.
 
   The fact that $ (\overline m^\prime, \overline m_1, \overline m_2) $ is weakly terminal also means that for all $ m^\prime: M^\prime $ and $ m_1, m_2: M $ with $ m_i^\prime = \varphi(m_i) \cdot m^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \cdot m $.
-This means that the equivalence that we established is actually well-defined: equivalent elements in $ \varphi^*(A) \times \varphi^*(B) $ are sent to equivalent elements in $ \varphi^*(A \times B) $.
+This means that the equivalence that we established is actually well-defined: equivalent elements in $ \varphi_*(A) \times \varphi_*(B) $ are sent to equivalent elements in $ \varphi_*(A \times B) $.
 

### 2024-05-20 report/chapters/paper.tex
Write about essential surjectiviy

@@
   \end{center}
-  Explicitly, this gives the embedding $ \R_A(U, -): \R_A \hookrightarrow \RAct{A_1} $ given by
-  \[ X \mapsto \R_A(U, X) = \{ x : A \mid X \circ x = x \}. \]
-  Actually, we can repeat almost the entirety of Section \ref{sec:retracts-category} for $ \R_A $. In particular, $ \R_A $ has products
+  Explicitly, this gives the embedding $ \R_A(\mathbf 1_1, -): \R_A \hookrightarrow \RAct{A_1} $ given by
+  \[ X \mapsto \R_A(\mathbf 1_1, X) = \{ x : A \mid X \circ x = x \}. \]
+  Now, we can repeat almost the entirety of Section \ref{sec:retracts-category} for $ \R_A $. In particular, $ \R_A $ has "universal object"
+  \[ U = \mathbf 1_1, \]
+  products
   \[ A \times B = \langle x_1 \circ \pi_1, x_2 \circ \pi_2 \rangle \bullet (A, B) \]
@@
   \[ B^A = (\lambda x_3, x_1 \circ x_3 \circ x_2) \bullet (B, A) \]
-  with isomorphism
-  \[ \psi: \R_A(C \times A, B) \xrightarrow \sim \R_A(C, B^A) \]
+  with the isomorphism $ \psi: \R_A(C \times A, B) \xrightarrow \sim \R_A(C, B^A) $
   given by
-  \[ \psi(f) = (\lambda x_2, x_1 (\pi_1 x_2) (\pi_2 x_2)) \bullet f \quad \text{and} \quad \psi^{-1}(f) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet f. \]
+  \[ \psi(f) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet f \quad \text{and} \quad \psi^{-1}(f) = (\lambda x_2, x_1 (\pi_1 x_2) (\pi_2 x_2)) \bullet f. \]
 \end{remark}
@@
 \begin{definition}
-  Now, composition $ \circ $ gives a right $ A_1 $-action on the $ A_n $, so we have $ A_n : \RAct{A_1} $ (note that this is the image of $ \mathbf 1_n : \R_A $ under the embeddding into $ \RAct{A_1} $).
+  Composition $ \circ $ gives a right $ A_1 $-action on the $ A_n $, so we have $ A_n : \RAct{A_1} $ (note that this is the image of $ \mathbf 1_n : \R_A $ under the embeddding into $ \RAct{A_1} $).
 \end{definition}
@@
   Hyland shows this by explicitly constructing an isomorphism $ \psi $ between $ A_2 $ and the `familiar' exponential object in $ \RAct{A_1} $ (the set of $ A_1 $-equivariant morphisms $ U_{A_1} \times U_{A_1} \to U_{A_1} $), given by
-  \[ \varphi(f) = (b, b^\prime) \mapsto (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (f, b, b^\prime), \]
-  treating $ f : A_2 $ as a function in two elements, and simultaneously composing it with the functions $ b, b^\prime : A_1 $ in one argument. It has an inverse
-  \[ \varphi^{-1}(g) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet (g(\pi_1, \pi_2)). \]
+  \[ \psi(f) = (b, b^\prime) \mapsto (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (f, b, b^\prime), \]
+  treating $ f : A_2 $ as a function in two variables, and simultaneously composing it with the functions $ b, b^\prime : A_1 $. It has an inverse
+  \[ \psi^{-1}(g) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet (g(\pi_1, \pi_2)). \]
   Note that the first pair $ (x_2, x_3) $ is a $ \lambda $-term, whereas the second pair $ (\pi_1, \pi_2) $ is a pair in $ U_{A_1} \times U_{A_1} $.
@@
   Now, note that, like before, $ \mathbf 1_1 $ is a retract of $ \mathbf 1_2 $ in $ \R_A $.
-The embedding into $ \RAct{A_1} $ turns this into the embedding as a subset $ A_2 \subseteq A_1 $ and a retraction $ r: A_1 \to A_2 $, given by precomposition with $ \mathbf 1_2 $.
+When we embed these into $ \RAct{A_1} $, we see that we have a subset $ A_2 \subseteq A_1 $ and a retraction $ r: A_1 \to A_2 $, given by precomposition with $ \mathbf 1_2 $.
 
-  Therefore, $ U_{A_1} $ is a reflexive object in $ \RAct{A_1} $, and we get an $ \lambda $-theory $ E(U_{A_1}) $.
+  Therefore, $ \mathbf 1_1 $ and $ U_{A_1} $ are reflexive objects in $ \R_A $ and $ \RAct{A_1} $, and we get isomorphic $ \lambda $-theories $ E(\mathbf 1_1) $ and $ E(U_{A_1}) $.
 \end{definition}
 
-\subsection{Lifting algebra morphisms}
-
-\begin{definition}[Pullback functor on presheaves for a $ \Lambda $-algebra]
-  A $ \Lambda $-algebra morphism preserves $ \mathbf 1_n $ and $ \circ $, so it sends elements of $ A_n $ to $ A^\prime_n $. In particular, it gives a monoid morphism $ f: A_1 \to A^\prime_1 $.
-
-  Therefore, as described in Section \ref{sec:monoid-category}, we get pullback and pushforward functors $ f_*: \RAct{A^\prime_1} \to \RAct{A_1} $ and $ f^* : \RAct{A_1} \to \RAct{A^\prime_1} $.
-\end{definition}
-
-\begin{remark}
-  By Lemma \ref{lem:scalar-extension-monoid-monoid-action}, we have $ f^*(U_{A_1}) \cong U_{A^\prime_1} $.
-\end{remark}
-
 \begin{lemma}
-  $ f^* $ preserves finite products.
+  We have an isomorphism of $ \Lambda $-algebras $ \varphi: E(\mathbf 1_1)_0 \xrightarrow A $.
 \end{lemma}
 \begin{proof}
-  We will show that $ f^* $ preserves binary products and the terminal object.
-
-  We use Lemma \ref{lem:scalar-extension-terminal} to show that $ f^* $ preserves the terminal object. We take
-  \[ a_0 = (\lambda x_1 x_2, x_2) \bullet () : A_1 \quad \text{and} \quad a_0^\prime = (\lambda x_1 x_2, x_2) \bullet () : A^\prime_1 \]
-  and $ a_0^\prime $ is weakly terminal because for all $ a : A_1 $, we have $ f(a_0) \circ a = a_0^\prime $.
-
-  We use Lemma \ref{lem:scalar-extension-product} to show that $ f^* $ also preserves the product. Therefore, given $ a_1, a_2 : A_1 $.
-
-  (\TODO: relate to product)
-
-  Take $ a = \lambda x_1 x_2, x_2 (a_1 x_1) (a_2 x_1) $ and $ \pi_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $.
-We have $ a_i = f(\pi_i) \circ a $.
-Now, for some $ a^\prime: A^\prime_1 $, $ \pi_1^\prime, \pi_2^\prime: A_1 $ such that $ a_i = f(\pi_i^\prime) \circ a^\prime $, take $ m = \lambda x_1 x_2, x_2 (\pi_1^\prime x_1) (\pi_2^\prime x_1) $.
-Then $ \pi_i \circ m = \pi_i^\prime $ and $ f(m) \circ a^\prime = a $, so $ (a, \pi_1, \pi_2) $ is weakly terminal and $ f^* $ preserves binary products.
-
-  Since any finite product is (isomorphic to) a construction with a repeated binary product and the terminal object, the fact that $ f^* $ preserves binary products and the terminal object shows that $ f^* $ preserves all finite products.
+  Take $ c_n = (\lambda x_{n + 1}, x_{n + 1}): \Lambda_n $.
+Note that $ E(\mathbf 1_1)_0 $ is given by $ \{ a : A \mid (\lambda x_2, x_1 c_3) \bullet a = a \} $.
+Therefore, we have a bijection given by
+  \[ \varphi(a) = (x_1 c_2) \bullet a \quad \text{and} \quad \varphi^{-1}(a) = (\lambda x_2, x_1) \bullet a. \]
+  Now, to show that this is an isomorphism of $ \Lambda $-algebras, recall that $ \bullet: \R_A(U^n, U) \times \R_A(I, U)^n \to \R_A(U) $ is given by precomposition with the product morphism and that the $ \Lambda $-algebra structure on $ E(\mathbf 1_1)_0 $ is given by the embedding $ f \mapsto \iota_\Lambda(f) \bullet_A () $ of $ \Lambda $ into $ E(\mathbf 1_1)_0 $.
+We have for all $ f: \Lambda_n $, and all $ a : E(\mathbf 1_1)_0^n $,
+  \begin{align*}
+    \varphi(f \bullet_{E(\mathbf 1_1)} a)
+    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_1, \dots, a_n \rangle)(c_n)\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1 c_n), x_2 c_n), \dots), x_n c_n)) \bullet_A a\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1), x_2), \dots), x_n)) \bullet_A (\varphi(a_i))_i,
+  \end{align*}
+  writing $ \bar x_n $ for $ ((\dots((c_n, x_1), x_2), \dots), x_n) $, and leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $,
+  \[ \iota_\Lambda(f) \bar x_n = f. \]
+  We will do this by structural induction on $ f $.
+  \begin{itemize}
+    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i} $, and
+      \[ (\pi_2 \circ \pi_1 \circ \dots \circ \pi_1) \bar x_n = x_{n, i}. \]
+    \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
+      \[ \iota_\Lambda(f) = (\lambda x_1 x_2, \iota_{0, 2}(\iota_\Lambda(g)) (x_1, x_2)), \]
+      and if the induction hypothesis holds for $ g $, then
+      \begin{align*}
+        \iota_\Lambda(f) \bar x_n
+        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) \bar x_n\\
+        &= \lambda x_{n + 1}, \iota_\Lambda(g) (\bar x_n, x_{n + 1})\\
+        &= \lambda x_{n + 1}, g.
+      \end{align*}
+    \item If $ f = g_1 g_2 $ for $ g_1, g_2 : \Lambda_{n + 1} $, we have
+      \[
+        \iota_\Lambda(f)
+        = (\lambda x_1, \iota_\Lambda(g_1) (\pi_1 x_1) (\pi_2 x_1)) \circ \langle \id{U^n}, \iota_\Lambda(g_2) \rangle
+        = \lambda x_1, \iota_\Lambda(g_1) x_1 (\iota_\Lambda(g_2) x_1),
+      \]
+      and if the induction hypothesis holds for $ g_1 $ and $ g_2 $, then
+      \begin{align*}
+        \iota_\Lambda(f) \bar x_n
+        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) \bar x_n\\
+        &= \iota_\Lambda(g_1) \bar x_n (\iota_\Lambda(g_2) \bar x_n)\\
+        &= g_1 g_2.
+      \end{align*}
+  \end{itemize}
 \end{proof}
-
-\begin{definition}
-  Since $ f^* $ preserves finite products, given an element of $ g: E(U_{A_1})_n = \RAct{A}(U_{A_1}^n, U_{A_1}) $, we get
-  \[ f^*(g): \RAct{A^\prime}(f(U_{A_1}^n), f(U_{A_1})) \cong \RAct{A^\prime}((U_{A^\prime_1})^n, U_{A^\prime_1}) = E(U_{A^\prime_1})_n \]
-  so we have a morphism $ f^*: \LamTh(E(U_{A_1}), E(U_{A^\prime_1})) $.
-\end{definition}
-
-\begin{remark}
-  The fact that $ f^* $ preserves the variables and substitution is not very hard, since these are just defined in terms of finite products $ U_{A_1} $ and $ f^* $ preserves finite products and $ U_{A_1} $.
-
-  However, showing that it is a $ \lambda $-theory morphism is really hard. Hyland claims
-  \begin{quote}
-    $ f $ preserves $ \mathbf 1_n $, which determines the function space as a retract of the universal. So $ f^* $ preserves the retract and the result follows.
-  \end{quote}
-  This indeed covers the core of the argument, but actually verifying that it works is much more complicated: We a natural equivalence and isomorphisms
-  \begin{align*}
-    \alpha_A: \RAct{A_1}(X \times Y, Z) &\xrightarrow{\sim} \RAct{A}(X, Z^Y);\\
-    \beta: f^*(U_{A_1}) &\xrightarrow{\sim} U_{A_1^\prime};\\
-    \bar \gamma: f^*(A \times B) &\xrightarrow{\sim} f^*(A) \times f^*(B);\\
-    \gamma_n: f^*(X^n) &\xrightarrow{\sim} f^*(X)^n;\\
-    % \delta: f^*(X^Y) &\xrightarrow{\sim} f^*(X)^{f^*(Y)};\\
-    \delta_A: U_{A_1}^{U_{A_1}} &\xrightarrow{\sim} A_2.
-  \end{align*}
-  with $ \gamma_{n + 1} = \bar{\gamma} \cdot (\gamma_n \times \id X) $.
-  Then, for $ s: E(U_{A_1})_{n + 1} $, we have $ \lambda_A(s) = \alpha_A(s) \cdot \delta_A \cdot \pi_A : \RAct{A_1}(U_{A_1}^n, U_{A_1}) $ for the projection $ \pi_A: A_2 \to U_{A_1} $.
-However, note that $ f^*(\lambda_A(s)): \RAct{A^\prime_1}(f^*(U_{A^\prime_1}^n), f^*(U_{A^\prime_1})) $.
-To compare this to $ \lambda_{A^\prime}(\dots) $, we actually need to take
-  \[ (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\lambda_A(s)) \cdot \beta : \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
-  On the other hand, we also have $ f^*(s): \RAct{A^\prime_1}(f^*(U_{A_1}^{n + 1}), f^*(U_{A_1})) $ and we cannot apply $ \lambda_{A^\prime} $ directly. Instead, the term that we end up with is
-  \[ \lambda_{A^\prime}((\beta^{-1})^{n + 1} \cdot \gamma_{n + 1}^{-1} \cdot f^*(s) \cdot \beta): \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
-  So the equality that we need to prove is (using functoriality of $ f^* $ and naturality of $ \alpha_{A^\prime} $):
-  \begin{align*}
-    &(\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\alpha_A(s)) \cdot f^*(\delta_A \cdot \pi_A) \cdot \beta\\
-    &= (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot \alpha_{A^\prime}((\id X^n \times \beta^{-1}) \cdot \bar{\gamma}^{-1} \cdot f^*(s)) \cdot \beta^{U_{A_1}} \cdot \delta_{A^\prime} \cdot \pi_{A^\prime}.
-  \end{align*}
-  Because of the complicated definition of each of these terms, I was unable to verify the correctness of this statement (and the similar statement about $ \rho: E(U_{A_1})_n \to E(U_{A_1})_{n + 1} $) within a day, even though I am willing to believe Hyland's claim.
-  \TODO
-
-  % Given a morphism $ t: X \times Y \to Z $, $ \alpha_{A_1}(t): X \to (U_{A_1} \times Y \to Z) $ is given by
-  % \[ \alpha(t)(x)(a, y) = t(x a, y) \]
-
-  % Also, $ \beta: f^*(U_{A_1}) \xrightarrow{\sim} U_{A^\prime_1} $ is given, for $ a: A_1 $ and $ a^\prime : A^\prime_1 $, by
-  % \[ \beta(a, a^\prime) = f(a) a^\prime \quad \text{and} \quad \beta^{-1}(a^\prime) = (1, a^\prime). \]
-
-  % Given a morphism $ s: X \to Y $, we have $ f^*(s): f^*(X) \to f^*(Y) $ given by
-  % \[ f^*(s)(x, a^\prime) = (s(x), a^\prime). \]
-
-  % Finally, we have
-  % \[ \delta(s) = \lambda x_1 x_2, s(p_1, p_2)(\lambda x_3, x_3 x_1 x_2) \]
-  % with $ p_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $.
-
-  % For some $ s: U_{A_1}^{n + 1} \to U_{A_1} $, the left hand side sends $ (a, (a^\prime_1, \dots, a^\prime_n)): f^*(U_{A_1}^n) $ to
-  % \begin{align*}
-  %   &\lambda x_1 x_2, f(s((a_i p_1)_i, p_2)) (\lambda x_3, x_3 x_1 x_2) \circ a^\prime\\
-  %   &= \lambda x_1 x_2, f(s((a_i p_1)_i, p_2)) (\lambda x_3, x_3 a^\prime (x_1) x_2)
-  % \end{align*}
-  % and the right hand side sends it to
-  % \begin{align*}
-  %   \lambda x_1 x_2, \lambda x_3, (f(s((a_i p_1)_i, p_2))((\lambda x_4, x_4 (a^\prime p_1 (\lambda x_3, x_3 x_1 x_2)) (p_2 (\lambda x_3, x_3 x_1 x_2)))(x_3)))
-  % \end{align*}
-\end{remark}
 
@@
 \end{proof}
+
+\subsection{Lifting algebra morphisms}
+
+Now, take a morphism $ F: \Alg{\Lambda}(A, B) $.
+Recall that $ \circ $, the structure on $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given by $ f \bullet (a_1, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $.
+Since we have $ F(f \bullet (a_1, \dots, a_n)) = f \bullet (F(a_1), \dots, F(a_n)) $, $ F $ gives a functor $ F: \R_A \to \R_B $ that preserves the terminal object, the object $ \mathbf 1_1 $, the products, their projections, the exponential objects and the natural isomorphisms $ \R_A(C, B^A) \cong \R_A(C \times A, B) $.
+This induces a $ \lambda $-theory morphism $ E(\mathbf 1_1) \to E(\mathbf 1_1) $ between the endomorphism theories of $ \mathbf 1_1 : A $ and $ \mathbf 1_1 : B $.
+
+\begin{remark}
+  Instead of in $ \R_A $ and $ \R_B $, Hyland tries to do the above in the `presheaf' categories $ \RAct{A_1} $ and $ \RAct{B_1} $.
+$ F $ induces a monoid morphism $ A_1 \to B_1 $, which gives a functor $ C_{A_1} \to C_{B_1} $.
+Precomposing with this, we get a functor $ \RAct{B_1} \to \RAct{A_1} $, and we only get the functor $ \RAct{A_1} \to \RAct{B_1} $ in the right direction after taking a Left Kan extension (the "tensor product": see Lemma \ref{lem:scalar-extension}).
+\end{remark}
+
+\begin{lemma}
+  The functors on $ \R_A $ and $ \RAct{A_1} $ induced by $ F $ commute with the embedding of $ \R_A $ and $ \R_B $ into $ \RAct{A_1} $ and $ \RAct{B_1} $.
+In other words, the diagram below $ 2 $-commutes:
+  \begin{center}
+    \begin{tikzcd}
+      \R_A \arrow[r, "F"] \arrow[d, "{\R_A(\mathbf 1_1, -)}"] & \R_B \arrow[d, "{\R_B(\mathbf 1_1, -)}"]\\
+      \RAct{A_1} \arrow[r, "F^*"] & \RAct{B_1}
+    \end{tikzcd}
+  \end{center}
+\end{lemma}
+\begin{proof}
+  Given $ X : \R_A $, we need to show that we have a natural isomorphism of sets with a right $ B_1 $-action $ \psi: \R_B(\mathbf 1_1, F(X)) \xrightarrow \sim F^*(\R_A(\mathbf 1_1, X)) $, that is, we need
+  \[ \psi: \{ f : B \mid F(X) \circ f = f \} \xrightarrow \sim \{ f : A \mid X \circ f = f \} \times B_1 / \sim \]
+  with the equivalence relation on the latter given by $ (f, F(a) \circ b) \sim (f \circ a, b) $ for all $ f : \R_A(\mathbf 1_1, X) $, $ b : B_1 $ and $ a : A_1 $. We can take $ \psi $ to be
+  \[ \psi(f) = (X, f) \quad \text{and} \quad \psi^{-1}(f, b) = F(f) \circ b, \]
+  which is $ B_1 $-equivariant and natural in $ X $.
+  % We have
+  % \[ \psi^{-1}(\psi(f)) = \psi^{-1}(X, f) = F(X) \circ f = f \]
+  % \[ \psi(\psi^{-1}(f, b)) = \psi(F(f) \circ b) = (X, F(f) \circ b) = (X \circ f, b) = (f, b) \]
+  % We need to show that this is natural in $ X $.
+Therefore, take $ g : \R_A(X, Y) $.
+Then $ \R_B(\mathbf 1_1, F(g)) $ is given by postcomposition with $ F(g) $.
+Also, $ F^*(\R_A(\mathbf 1_1, g)) $ is given by postcomposing with $ g $ on the component $ \R_A(\mathbf 1_1, g) $.
+Then
+  % \[ \psi(F(g) \circ f) = (Y, F(g) \circ f) = (Y \circ g, f) = (g \circ X, f) \]
+\end{proof}
+
+For completeness' sake, the rest of this section will describe Hyland's reasoning a bit more:
+\begin{lemma}
+  The extension of scalars $ F^* $ sends $ U_{A_1} $ to $ U_{B_1} $ and preserves finite products.
+\end{lemma}
+\begin{proof}
+  By Lemma \ref{lem:scalar-extension-monoid-monoid-action}, we have $ F^*(U_{A_1}) \cong U_{B_1} $.
+
+  We will show that $ F^* $ preserves binary products and the terminal object.
+
+  We use Lemma \ref{lem:scalar-extension-terminal} to show that $ F^* $ preserves the terminal object. We take (very similar to the terminal object in $ \R $):
+  \[ a_0 = (\lambda x_1 x_2, x_2) \bullet () : A_1 \quad \text{and} \quad b_0 = (\lambda x_1 x_2, x_2) \bullet () : B_1 \]
+  and $ a_0 $ is weakly terminal because for all $ a : A_1 $, we have $ F(a_0) \circ a = b_0 $.
+
+  We use Lemma \ref{lem:scalar-extension-product} to show that $ F^* $ also preserves the product.
+Therefore, given $ a_1, a_2 : B_1 $.
+Take $ b = \langle x_1, x_2 \rangle \bullet (a_1, a_2) $, together with the familiar projections $ \pi_i \bullet () : A_1 $.
+We have $ a_i = F(\pi_i) \circ a $.
+
+  Now, for some $ b^\prime: B_1 $ and $ \pi_1^\prime, \pi_2^\prime: A_1 $ such that $ a_i = F(\pi_i^\prime) \circ b^\prime $, take $ m = \langle \pi_1^\prime, \pi_2^\prime \rangle $.
+Then $ \pi_i \circ m = \pi_i^\prime $ and $ F(m) \circ a^\prime = a $, so $ (a, \pi_1, \pi_2) $ is weakly terminal and $ F^* $ preserves binary products.
+
+  Since any finite product is (isomorphic to) a construction with a repeated binary product and the terminal object, the fact that $ F^* $ preserves binary products and the terminal object shows that $ F^* $ preserves all finite products.
+\end{proof}
+
+Now, we can start defining our lift of $ F $:
+\begin{definition}
+  We can send an element $ g: E(U_{A_1})_n = \RAct{A}(U_{A_1}^n, U_{A_1}) $ to
+  \[ F^*(g): \RAct{A^\prime}(f(U_{A_1}^n), f(U_{A_1})) \cong \RAct{A^\prime}((U_{A^\prime_1})^n, U_{A^\prime_1}) = E(U_{A^\prime_1})_n \]
+  so we have a morphism $ \bar F: \LamTh(E(U_{A_1}), E(U_{A^\prime_1})) $.
+\end{definition}
+
+\begin{remark}
+  The fact that $ \bar F $ preserves the variables and substitution is not very hard, since these are just defined in terms of finite products of $ U_{A_1} $ and $ \bar F $ preserves finite products and $ U_{A_1} $.
+
+  However, showing that it is a $ \lambda $-theory morphism is a different matter. Hyland claims
+  \begin{quote}
+    $ F $ preserves $ \mathbf 1_n $, which determines the function space as a retract of the universal. So $ \bar F $ preserves the retract and the result follows.
+  \end{quote}
+  Although this covers the core of the argument, it is very complicated to actually verify that this works, because we need to pass through a lot of isomorphisms, and check that they work nicely together:
+  \begin{align*}
+    \alpha_A: \RAct{A_1}(X \times Y, Z) &\xrightarrow{\sim} \RAct{A}(X, Z^Y);\\
+    \beta: F^*(U_{A_1}) &\xrightarrow{\sim} U_{A_1^\prime};\\
+    \bar \gamma: F^*(A \times B) &\xrightarrow{\sim} F^*(A) \times F^*(B);\\
+    \gamma_n: F^*(X^n) &\xrightarrow{\sim} F^*(X)^n;\\
+    % \delta: F^*(X^Y) &\xrightarrow{\sim} F^*(X)^{F^*(Y)};\\
+    \delta_A: U_{A_1}^{U_{A_1}} &\xrightarrow{\sim} A_2.
+  \end{align*}
+  % with $ \gamma_{n + 1} = \bar{\gamma} \cdot (\gamma_n \times \id X) $.
+  % Then, for $ s: E(U_{A_1})_{n + 1} $, we have $ \lambda_A(s) = \alpha_A(s) \cdot \delta_A \cdot \pi_A : \RAct{A_1}(U_{A_1}^n, U_{A_1}) $ for the projection $ \pi_A: A_2 \to U_{A_1} $.
+However, note that $ f^*(\lambda_A(s)): \RAct{A^\prime_1}(f^*(U_{A^\prime_1}^n), f^*(U_{A^\prime_1})) $.
+To compare this to $ \lambda_{A^\prime}(\dots) $, we actually need to take
+  % \[ (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\lambda_A(s)) \cdot \beta : \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
+  % On the other hand, we also have $ f^*(s): \RAct{A^\prime_1}(f^*(U_{A_1}^{n + 1}), f^*(U_{A_1})) $ and we cannot apply $ \lambda_{A^\prime} $ directly. Instead, the term that we end up with is
+  % \[ \lambda_{A^\prime}((\beta^{-1})^{n + 1} \cdot \gamma_{n + 1}^{-1} \cdot f^*(s) \cdot \beta): \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
+  % So the equality that we need to prove is (using functoriality of $ f^* $ and naturality of $ \alpha_{A^\prime} $):
+  % \begin{align*}
+  %   &(\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\alpha_A(s)) \cdot f^*(\delta_A \cdot \pi_A) \cdot \beta\\
+  %   &= (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot \alpha_{A^\prime}((\id X^n \times \beta^{-1}) \cdot \bar{\gamma}^{-1} \cdot f^*(s)) \cdot \beta^{U_{A_1}} \cdot \delta_{A^\prime} \cdot \pi_{A^\prime}.
+  % \end{align*}
+  % Because of the complicated definition of each of these terms, I was unable to verify the correctness of this statement (and the similar statement about $ \rho: E(U_{A_1})_n \to E(U_{A_1})_{n + 1} $) within a day, even though I am willing to believe Hyland's claim.
+  % \TODO
+
+  % Given a morphism $ t: X \times Y \to Z $, $ \alpha_{A_1}(t): X \to (U_{A_1} \times Y \to Z) $ is given by
+  % \[ \alpha(t)(x)(a, y) = t(x a, y) \]
+
+  % Also, $ \beta: f^*(U_{A_1}) \xrightarrow{\sim} U_{A^\prime_1} $ is given, for $ a: A_1 $ and $ a^\prime : A^\prime_1 $, by
+  % \[ \beta(a, a^\prime) = f(a) a^\prime \quad \text{and} \quad \beta^{-1}(a^\prime) = (1, a^\prime). \]
+
+  % Given a morphism $ s: X \to Y $, we have $ f^*(s): f^*(X) \to f^*(Y) $ given by
+  % \[ f^*(s)(x, a^\prime) = (s(x), a^\prime). \]
+
+  % Finally, we have
+  % \[ \delta(s) = \lambda x_1 x_2, s(p_1, p_2)(\lambda x_3, x_3 x_1 x_2) \]
+  % with $ p_i = \lambda x_1, x_1 (\lambda x_2 x_3, x_{i + 1}) $.
+
+  % For some $ s: U_{A_1}^{n + 1} \to U_{A_1} $, the left hand side sends $ (a, (a^\prime_1, \dots, a^\prime_n)): f^*(U_{A_1}^n) $ to
+  % \begin{align*}
+  %   &\lambda x_1 x_2, f(s((a_i p_1)_i, p_2)) (\lambda x_3, x_3 x_1 x_2) \circ a^\prime\\
+  %   &= \lambda x_1 x_2, f(s((a_i p_1)_i, p_2)) (\lambda x_3, x_3 a^\prime (x_1) x_2)
+  % \end{align*}
+  % and the right hand side sends it to
+  % \begin{align*}
+  %   \lambda x_1 x_2, \lambda x_3, (f(s((a_i p_1)_i, p_2))((\lambda x_4, x_4 (a^\prime p_1 (\lambda x_3, x_3 x_1 x_2)) (p_2 (\lambda x_3, x_3 x_1 x_2)))(x_3)))
+  % \end{align*}
+\end{remark}
 

### 2024-05-22 report/chapters/category-theory.tex
Show that the functor is essentially surjective

@@
 For composition of functors $ F: A \to B $ and $ G: B \to C $, I will write $ F \bullet G $.
-
-\section{Yoneda}
-We can embed a category $ C $ into the functor category $ P C = [\op C, \SET] $ as follows (see \cite{Kashiwara}, Section 1.4):
-\begin{definition}
-  The \iindex{Yoneda embedding} $ Y : C \hookrightarrow P C $ is given on objects by $ Y(c) = C(-, c) $:
-  \[ Y(c)(d) = C(d, c) \quad \text{and} \quad Y(c)(f)(g) = f \cdot g \]
-  for $ d: C $, $ f: C(d, d^\prime) $ and $ g: C(d^\prime, c) $. It sends a morphism $ f: C(c, c^\prime) $ to the natural transformation $ Y(f): C(-, c) \Rightarrow C(-, c^\prime) $ given by
-  \[ Y(f)(d)(g) = g \cdot f \]
-  for $ d: C $ and $ g: C(d, c) $.
-\end{definition}
-
-For a functor between categories $ f: C \to D $, given the Yoneda embeddings $ Y_C : C \to P C $ and $ Y_D : D \to P D $ (we will often omit the subscript $ C $ and $ D $), we can create a diagram
-\begin{center}
-  \begin{tikzcd}
-    C \arrow[r, "f"] \arrow[d, hookrightarrow, "Y"] & D \arrow[d, hookrightarrow, "Y"]\\
-    P C & P D \arrow[l, "\op f_*"]
-  \end{tikzcd}
-\end{center}
-Note that the arrows in this diagram are functors, so objects in a category, instead of elements of a set.
-Therefore, it does not make sense to talk about `equality' of the morphisms along the different paths, but we rather talk about isomorphism in the functor category $ [C, P C] $.
-If we have such an isomorphism, we say the diagram `2-commutes':
-\begin{lemma}\label{lem:Yoneda-restriction-commutes}
-  If $ f: C \to D $ is a fully faithful functor, the diagram above 2-commutes.
-\end{lemma}
-\begin{proof}
-  For $ c, d : C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
-  \[ Y(c)(d) = C(d, c) \xrightarrow[f_{d, c}]{\sim} D(f(d), f(c)) = \op f_*(Y(f(c)))(d). \]
-  Also, for $ g: C(d^\prime, d) $, the following diagram commutes
-  \begin{center}
-    \begin{tikzcd}
-      Y(c)(d) \arrow[d, "g \cdot -"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "f_{d^\prime, d}(g) \cdot -"]\\
-      Y(c)(d^\prime) \arrow[r, "f_{d^\prime, c}"] & \op f_*(Y(f(c)))(d^\prime)
-    \end{tikzcd}
-  \end{center}
-  so the isomorphism is natural in $ d $ and we have $ Y(c) \cong \op f_*(Y(f(c))) $ in $ P C $. Lastly, for $ g: C(c, c^\prime) $ and $ d: C $, the following diagram commutes
-  \begin{center}
-    \begin{tikzcd}
-      Y(c)(d) \arrow[d, "- \cdot g"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "- \cdot f_{c, c^\prime}(g)"]\\
-      Y(c^\prime)(d) \arrow[r, "f_{d, c^\prime}"] & \op f_*(Y(f(c^\prime)))(d)
-    \end{tikzcd}
-  \end{center}
-  so the isomorphism is natural in $ c $ and we have $ Y \cong f \bullet Y \bullet \op f_* $ in $ [C, P C] $.
-\end{proof}
 
@@
 \end{remark}
+
+\section{Yoneda}
+We can embed a category $ C $ fully faithfully into the functor category $ P C = [\op C, \SET] $ as follows (see \cite{Kashiwara}, Section 1.4):
+\begin{definition}
+  The \iindex{Yoneda embedding} $ Y : C \hookrightarrow P C $ is given on objects by $ Y(c) = C(-, c) $:
+  \[ Y(c)(d) = C(d, c) \quad \text{and} \quad Y(c)(f)(g) = f \cdot g \]
+  for $ d: C $, $ f: C(d, d^\prime) $ and $ g: C(d^\prime, c) $. It sends a morphism $ f: C(c, c^\prime) $ to the natural transformation $ Y(f): C(-, c) \Rightarrow C(-, c^\prime) $ given by
+  \[ Y(f)(d)(g) = g \cdot f \]
+  for $ d: C $ and $ g: C(d, c) $.
+\end{definition}
+
+Now, this embedding has a couple of properties:
+\begin{lemma}
+  For any $ c: C $ and $ F : PC $, we have an equivalence $ PC(Y(c), F) \simeq F(c) $, and this equivalence is natural in $ c $ and $ F $.
+\end{lemma}
+\begin{proof}
+  See \cite{Kashiwara}, Proposition 1.4.3.
+\end{proof}
+
+\begin{lemma}
+  The Yoneda embedding functor preserves limits.
+\end{lemma}
+\begin{proof}
+  See \cite{borceux}, Volume 1, Proposition 2.15.5.
+\end{proof}
+
+\begin{lemma}
+  The Yoneda embedding functor preserves exponential objects (\cite{stackexchange:yoneda-exponentials}).
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+
+For a functor between categories $ f: C \to D $, given the Yoneda embeddings $ Y_C : C \to P C $ and $ Y_D : D \to P D $ (we will often omit the subscript $ C $ and $ D $), we can create a diagram
+\begin{center}
+  \begin{tikzcd}
+    C \arrow[r, "f"] \arrow[d, hookrightarrow, "Y"] & D \arrow[d, hookrightarrow, "Y"]\\
+    P C & P D \arrow[l, "\op f_*"]
+  \end{tikzcd}
+\end{center}
+Note that the arrows in this diagram are functors, so objects in a category, instead of elements of a set.
+Therefore, it does not make sense to talk about `equality' of the morphisms along the different paths, but we rather talk about isomorphism in the functor category $ [C, P C] $.
+If we have such an isomorphism, we say the diagram `2-commutes':
+\begin{lemma}\label{lem:Yoneda-restriction-commutes}
+  If $ f: C \to D $ is a fully faithful functor, the diagram above 2-commutes.
+\end{lemma}
+\begin{proof}
+  For $ c, d : C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
+  \[ Y(c)(d) = C(d, c) \xrightarrow[f_{d, c}]{\sim} D(f(d), f(c)) = \op f_*(Y(f(c)))(d). \]
+  Also, for $ g: C(d^\prime, d) $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}
+      Y(c)(d) \arrow[d, "g \cdot -"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "f_{d^\prime, d}(g) \cdot -"]\\
+      Y(c)(d^\prime) \arrow[r, "f_{d^\prime, c}"] & \op f_*(Y(f(c)))(d^\prime)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ d $ and we have $ Y(c) \cong \op f_*(Y(f(c))) $ in $ P C $. Lastly, for $ g: C(c, c^\prime) $ and $ d: C $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}
+      Y(c)(d) \arrow[d, "- \cdot g"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "- \cdot f_{c, c^\prime}(g)"]\\
+      Y(c^\prime)(d) \arrow[r, "f_{d, c^\prime}"] & \op f_*(Y(f(c^\prime)))(d)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ c $ and we have $ Y \cong f \bullet Y \bullet \op f_* $ in $ [C, P C] $.
+\end{proof}
 
@@
 \begin{proof}
-  See \cite{borceux-3}, Lemma 5.8.2. This lemma shows this via the following equivalences:
+  See \cite{borceux}, Volume 3, Lemma 5.8.2. This lemma shows this via the following equivalences:
   \begin{align*}
@@
   The proof relies on the fact that every element of $ \varphi_*(I_M) $ is given by some $ (\star, m^\prime) $, but then
-  \[ (\star, m^\prime) = (\star \cdot m, m^\prime) \sim (\star, \varphi(m) \cdot m^\prime) = (\star, \overline{m^\prime}), \]
+  \[ (\star, m^\prime) = (\star \cdot m, m^\prime) \sim (\star, \varphi(m) \cdot m^\prime) = (\star, m_0), \]
   so $ \varphi_*(I_M) $ has exactly $ 1 $ element.

### 2024-05-22 report/chapters/paper.tex
Show that the functor is essentially surjective

@@
     \mathbf R \arrow[r, hookrightarrow] \arrow[d, hookrightarrow, "Y"] & \Pshf L \arrow[d, "\sim"]\\
-    P \R \arrow[r, twoheadrightarrow, "j_*"] \arrow[rr, bend right, "\sim"] & P \mathbf L \arrow[r, twoheadrightarrow, "i_*"] & P L_1
+    P \R \arrow[r, twoheadrightarrow, "j_*"] \arrow[rr, bend right, "\sim"] & P \mathbf L \arrow[r, twoheadrightarrow, "i_*"] & P C_{L_1}
   \end{tikzcd}
@@
   There also is a more category-theoretical argument: Suppose that every object of $ \Pshf L $ is a retract of $ L $.
-Via the equivalence $ \Pshf L \cong L_1 $, we see that every object of $ P L_1 $ is a retract of $ Y(\star) $.
-However then the embedding of $ \hat \R $ (Definition \ref{def:karoubi'}) into $ P L_1 $ is an adjoint equivalence.
-Since $ Y_{\R} \bullet {\op{\iota_{L_1}}}_* : \R \to \hat \R $ and $ {\op{\iota_{L_1}}}_* : P \R \to P L_1 $ are weak equivalences, (Lemma \ref{lem:retracts-rezk}, Corollary \ref{cor:karoubi-presheaf}), $ Y_\R : \R \to P \R $ is a weak equivalence as well, but the Yoneda embedding is never essentially surjective.
+Via the equivalence $ \Pshf L \cong L_1 $, we see that every object of $ P C_{L_1} $ is a retract of $ Y(\star) $.
+However then the embedding of $ \hat \R $ (Definition \ref{def:karoubi'}) into $ P C_{L_1} $ is an adjoint equivalence.
+Since $ Y_{\R} \bullet {\op{\iota_{L_1}}}_* : \R \to \hat \R $ and $ {\op{\iota_{L_1}}}_* : P \R \to P C_{L_1} $ are weak equivalences, (Lemma \ref{lem:retracts-rezk}, Corollary \ref{cor:karoubi-presheaf}), $ Y_\R : \R \to P \R $ is a weak equivalence as well, but the Yoneda embedding is never essentially surjective.
 For any category $ C $, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = Y(c)(c) $, so $ Y(c) $ is not isomorphic to $ E $.
@@
 
-Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \cite{borceux-3}).
+Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \cite{borceux}, Volume 3).
 Therefore, for a morphism $ f: \Pshf L(Y, X) $, we have adjunctions
@@
 
+In particular, we have a set with right $ A_1 $-action, given by $ A_1 $ itself. We will call this set with right $ A_1 $-action $ U_A $.
+
 \begin{remark}
@@
 
-\begin{remark}
+\begin{remark}\label{rem:ract-presheaf-equivalence}
   Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $.
@@
 \begin{remark}
-  Hyland shows this by explicitly constructing an isomorphism $ \psi $ between $ A_2 $ and the `familiar' exponential object in $ \RAct{A_1} $ (the set of $ A_1 $-equivariant morphisms $ U_{A_1} \times U_{A_1} \to U_{A_1} $), given by
+  Hyland shows this by explicitly constructing an isomorphism $ \psi $ between $ A_2 $ and the `familiar' exponential object in $ \RAct{A_1} $ (the set of $ A_1 $-equivariant morphisms $ U_A \times U_A \to U_A $), given by
   \[ \psi(f) = (b, b^\prime) \mapsto (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (f, b, b^\prime), \]
@@
   \[ \psi^{-1}(g) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet (g(\pi_1, \pi_2)). \]
-  Note that the first pair $ (x_2, x_3) $ is a $ \lambda $-term, whereas the second pair $ (\pi_1, \pi_2) $ is a pair in $ U_{A_1} \times U_{A_1} $.
+  Note that the first pair $ (x_2, x_3) $ is a $ \lambda $-term, whereas the second pair $ (\pi_1, \pi_2) $ is a pair in $ U_A \times U_A $.
 \end{remark}
@@
 
-  Therefore, $ \mathbf 1_1 $ and $ U_{A_1} $ are reflexive objects in $ \R_A $ and $ \RAct{A_1} $, and we get isomorphic $ \lambda $-theories $ E(\mathbf 1_1) $ and $ E(U_{A_1}) $.
+  Therefore, $ \mathbf 1_1 $ and $ U_A $ are reflexive objects in $ \R_A $ and $ \RAct{A_1} $, and we get isomorphic $ \lambda $-theories $ E(\mathbf 1_1) $ and $ E(U_A) $.
 \end{definition}
-
-\begin{lemma}
-  We have an isomorphism of $ \Lambda $-algebras $ \varphi: E(\mathbf 1_1)_0 \xrightarrow A $.
-\end{lemma}
-\begin{proof}
-  Take $ c_n = (\lambda x_{n + 1}, x_{n + 1}): \Lambda_n $.
-Note that $ E(\mathbf 1_1)_0 $ is given by $ \{ a : A \mid (\lambda x_2, x_1 c_3) \bullet a = a \} $.
-Therefore, we have a bijection given by
-  \[ \varphi(a) = (x_1 c_2) \bullet a \quad \text{and} \quad \varphi^{-1}(a) = (\lambda x_2, x_1) \bullet a. \]
-  Now, to show that this is an isomorphism of $ \Lambda $-algebras, recall that $ \bullet: \R_A(U^n, U) \times \R_A(I, U)^n \to \R_A(U) $ is given by precomposition with the product morphism and that the $ \Lambda $-algebra structure on $ E(\mathbf 1_1)_0 $ is given by the embedding $ f \mapsto \iota_\Lambda(f) \bullet_A () $ of $ \Lambda $ into $ E(\mathbf 1_1)_0 $.
-We have for all $ f: \Lambda_n $, and all $ a : E(\mathbf 1_1)_0^n $,
-  \begin{align*}
-    \varphi(f \bullet_{E(\mathbf 1_1)} a)
-    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_1, \dots, a_n \rangle)(c_n)\\
-    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1 c_n), x_2 c_n), \dots), x_n c_n)) \bullet_A a\\
-    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1), x_2), \dots), x_n)) \bullet_A (\varphi(a_i))_i,
-  \end{align*}
-  writing $ \bar x_n $ for $ ((\dots((c_n, x_1), x_2), \dots), x_n) $, and leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $,
-  \[ \iota_\Lambda(f) \bar x_n = f. \]
-  We will do this by structural induction on $ f $.
-  \begin{itemize}
-    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i} $, and
-      \[ (\pi_2 \circ \pi_1 \circ \dots \circ \pi_1) \bar x_n = x_{n, i}. \]
-    \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
-      \[ \iota_\Lambda(f) = (\lambda x_1 x_2, \iota_{0, 2}(\iota_\Lambda(g)) (x_1, x_2)), \]
-      and if the induction hypothesis holds for $ g $, then
-      \begin{align*}
-        \iota_\Lambda(f) \bar x_n
-        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) \bar x_n\\
-        &= \lambda x_{n + 1}, \iota_\Lambda(g) (\bar x_n, x_{n + 1})\\
-        &= \lambda x_{n + 1}, g.
-      \end{align*}
-    \item If $ f = g_1 g_2 $ for $ g_1, g_2 : \Lambda_{n + 1} $, we have
-      \[
-        \iota_\Lambda(f)
-        = (\lambda x_1, \iota_\Lambda(g_1) (\pi_1 x_1) (\pi_2 x_1)) \circ \langle \id{U^n}, \iota_\Lambda(g_2) \rangle
-        = \lambda x_1, \iota_\Lambda(g_1) x_1 (\iota_\Lambda(g_2) x_1),
-      \]
-      and if the induction hypothesis holds for $ g_1 $ and $ g_2 $, then
-      \begin{align*}
-        \iota_\Lambda(f) \bar x_n
-        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) \bar x_n\\
-        &= \iota_\Lambda(g_1) \bar x_n (\iota_\Lambda(g_2) \bar x_n)\\
-        &= g_1 g_2.
-      \end{align*}
-  \end{itemize}
-\end{proof}
-
-\begin{lemma}
-  We have a bijection $ \varphi: E(U_{A_1})_0 \cong A $, sending $ s $ to $ x_1 (\lambda x_2, x_2) \bullet (s(\star)) $.
-\end{lemma}
-\begin{proof}
-  Using \ref{lem:global-action-elements}, we showed that $ E(U_{A_1})_0 $ corresponds to the set of $ A_1 $-equivariant elements of $ U_{A_1} $, sending $ s $ to $ s(\star) $.
-Now, for an $ A_1 $-equivariant element $ a $,
-  \[ (\lambda x_2, x_1 (\lambda x_3, x_3)) \bullet a = a \circ ((\lambda x_1 x_2, x_2) \bullet ()) = a \]
-  so we can send $ a $ to $ A $ as $ (x_1 (\lambda x_2, x_2)) \bullet a $ and it has (two-sided) inverse $ (\lambda x_2, x_1) \bullet a $.
-\end{proof}
-
-We want to show that $ \varphi $ is an isomorphism of $ \Lambda $-algebras.
-We use Lemma \ref{lem:make-is-lambda-algebra-morphism} for this, so we need to show that it preserves the application and the $ \Lambda $-definable constants.
-
-\begin{lemma}
-  For $ \varphi $ as above, we have for all $ a, b: E(U_{A_1})_0 $, we have
-  \[ \varphi((x_1 x_2) \bullet (a, b)) = (x_1 x_2) \bullet (\varphi(a), \varphi(b)). \]
-\end{lemma}
-\begin{proof}
-  For $ a, b: E(U_{A_1})_0 $, we have, for the isomorphism $ \delta: \RAct{A_1}(U_{A_1}^{U_{A_1}}, A_2) $,
-  \begin{align*}
-    \varphi((x_{2, 1} x_{2, 2}) \bullet (a, b)) &= \varphi(\rho(x_{1, 1}) \bullet (a, b))\\
-    &= (x_1 (\lambda x_2, x_2)) \bullet (\langle a, b \rangle \cdot ((s, t) \mapsto (\delta^{-1}(\mathbf 1_2 \circ s)) (1, t)))(\star)\\
-    &= (x_1 (\lambda x_2, x_2)) \bullet (\lambda x_3, x_1 x_3 (x_2 x_3)) \bullet (a(\star), b(\star))\\
-    &= (x_1 (\lambda x_3, x_3) (x_2 (\lambda x_3, x_3))) \bullet (a(\star), b(\star))\\
-    &= (x_1 x_2) \bullet (\varphi(a), \varphi(b))
-  \end{align*}
-  and this concludes the proof.
-\end{proof}
-
-\begin{lemma}
-  For $ \varphi $ as above, we have for all $ s: \Lambda_0 $,
-  \[ \varphi(s \bullet ()) = s \bullet (). \]
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
 
@@
       \R_A \arrow[r, "F"] \arrow[d, "{\R_A(\mathbf 1_1, -)}"] & \R_B \arrow[d, "{\R_B(\mathbf 1_1, -)}"]\\
-      \RAct{A_1} \arrow[r, "F^*"] & \RAct{B_1}
+      \RAct{A_1} \arrow[r, "F_*"] & \RAct{B_1}
     \end{tikzcd}
@@
 \begin{proof}
-  Given $ X : \R_A $, we need to show that we have a natural isomorphism of sets with a right $ B_1 $-action $ \psi: \R_B(\mathbf 1_1, F(X)) \xrightarrow \sim F^*(\R_A(\mathbf 1_1, X)) $, that is, we need
+  Given $ X : \R_A $, we need to show that we have a natural isomorphism of sets with a right $ B_1 $-action $ \psi: \R_B(\mathbf 1_1, F(X)) \xrightarrow \sim F_*(\R_A(\mathbf 1_1, X)) $, that is, we need
   \[ \psi: \{ f : B \mid F(X) \circ f = f \} \xrightarrow \sim \{ f : A \mid X \circ f = f \} \times B_1 / \sim \]
@@
 Then $ \R_B(\mathbf 1_1, F(g)) $ is given by postcomposition with $ F(g) $.
-Also, $ F^*(\R_A(\mathbf 1_1, g)) $ is given by postcomposing with $ g $ on the component $ \R_A(\mathbf 1_1, g) $.
+Also, $ F_*(\R_A(\mathbf 1_1, g)) $ is given by postcomposing with $ g $ on the component $ \R_A(\mathbf 1_1, g) $.
 Then
@@
 \begin{lemma}
-  The extension of scalars $ F^* $ sends $ U_{A_1} $ to $ U_{B_1} $ and preserves finite products.
+  The extension of scalars $ F_* $ sends $ U_A $ to $ U_A $ and preserves finite products.
 \end{lemma}
 \begin{proof}
-  By Lemma \ref{lem:scalar-extension-monoid-monoid-action}, we have $ F^*(U_{A_1}) \cong U_{B_1} $.
+  By Lemma \ref{lem:scalar-extension-monoid-monoid-action}, we have $ F_*(U_A) \cong U_A $.
 
-  We will show that $ F^* $ preserves binary products and the terminal object.
+  We will show that $ F_* $ preserves binary products and the terminal object.
 
-  We use Lemma \ref{lem:scalar-extension-terminal} to show that $ F^* $ preserves the terminal object. We take (very similar to the terminal object in $ \R $):
+  We use Lemma \ref{lem:scalar-extension-terminal} to show that $ F_* $ preserves the terminal object. We take (very similar to the terminal object in $ \R $):
   \[ a_0 = (\lambda x_1 x_2, x_2) \bullet () : A_1 \quad \text{and} \quad b_0 = (\lambda x_1 x_2, x_2) \bullet () : B_1 \]
-  and $ a_0 $ is weakly terminal because for all $ a : A_1 $, we have $ F(a_0) \circ a = b_0 $.
+  and $ a_0 $ is weakly terminal because for all $ a : B_1 $, we have $ F(a_0) \circ a = b_0 $.
 
-  We use Lemma \ref{lem:scalar-extension-product} to show that $ F^* $ also preserves the product.
+  We use Lemma \ref{lem:scalar-extension-product} to show that $ F_* $ also preserves the product.
 Therefore, given $ a_1, a_2 : B_1 $.
@@
   Now, for some $ b^\prime: B_1 $ and $ \pi_1^\prime, \pi_2^\prime: A_1 $ such that $ a_i = F(\pi_i^\prime) \circ b^\prime $, take $ m = \langle \pi_1^\prime, \pi_2^\prime \rangle $.
-Then $ \pi_i \circ m = \pi_i^\prime $ and $ F(m) \circ a^\prime = a $, so $ (a, \pi_1, \pi_2) $ is weakly terminal and $ F^* $ preserves binary products.
+Then $ \pi_i \circ m = \pi_i^\prime $ and $ F(m) \circ a^\prime = a $, so $ (a, \pi_1, \pi_2) $ is weakly terminal and $ F_* $ preserves binary products.
 
-  Since any finite product is (isomorphic to) a construction with a repeated binary product and the terminal object, the fact that $ F^* $ preserves binary products and the terminal object shows that $ F^* $ preserves all finite products.
+  Since any finite product is (isomorphic to) a construction with a repeated binary product and the terminal object, the fact that $ F_* $ preserves binary products and the terminal object shows that $ F_* $ preserves all finite products.
 \end{proof}
@@
 \begin{definition}
-  We can send an element $ g: E(U_{A_1})_n = \RAct{A}(U_{A_1}^n, U_{A_1}) $ to
-  \[ F^*(g): \RAct{A^\prime}(f(U_{A_1}^n), f(U_{A_1})) \cong \RAct{A^\prime}((U_{A^\prime_1})^n, U_{A^\prime_1}) = E(U_{A^\prime_1})_n \]
-  so we have a morphism $ \bar F: \LamTh(E(U_{A_1}), E(U_{A^\prime_1})) $.
+  We can send an element $ g: E(U_A)_n = \RAct{A}(U_A^n, U_A) $ to
+  \[ F_*(g): \RAct{A^\prime}(f(U_A^n), f(U_A)) \cong \RAct{A^\prime}((U_{A^\prime})^n, U_{A^\prime}) = E(U_{A^\prime})_n \]
+  so we have a morphism $ \bar F: \LamTh(E(U_A), E(U_{A^\prime})) $.
 \end{definition}
@@
 \begin{remark}
-  The fact that $ \bar F $ preserves the variables and substitution is not very hard, since these are just defined in terms of finite products of $ U_{A_1} $ and $ \bar F $ preserves finite products and $ U_{A_1} $.
+  The fact that $ \bar F $ preserves the variables and substitution is not very hard, since these are just defined in terms of finite products of $ U_A $ and $ \bar F $ preserves finite products and $ U_A $.
 
@@
     \alpha_A: \RAct{A_1}(X \times Y, Z) &\xrightarrow{\sim} \RAct{A}(X, Z^Y);\\
-    \beta: F^*(U_{A_1}) &\xrightarrow{\sim} U_{A_1^\prime};\\
-    \bar \gamma: F^*(A \times B) &\xrightarrow{\sim} F^*(A) \times F^*(B);\\
-    \gamma_n: F^*(X^n) &\xrightarrow{\sim} F^*(X)^n;\\
-    % \delta: F^*(X^Y) &\xrightarrow{\sim} F^*(X)^{F^*(Y)};\\
-    \delta_A: U_{A_1}^{U_{A_1}} &\xrightarrow{\sim} A_2.
+    \beta: F_*(U_A) &\xrightarrow{\sim} U_{A^\prime};\\
+    \bar \gamma: F_*(A \times B) &\xrightarrow{\sim} F_*(A) \times F_*(B);\\
+    \gamma_n: F_*(X^n) &\xrightarrow{\sim} F_*(X)^n;\\
+    % \delta: F_*(X^Y) &\xrightarrow{\sim} F_*(X)^{F_*(Y)};\\
+    \delta_A: U_A^{U_A} &\xrightarrow{\sim} A_2.
   \end{align*}
   % with $ \gamma_{n + 1} = \bar{\gamma} \cdot (\gamma_n \times \id X) $.
-  % Then, for $ s: E(U_{A_1})_{n + 1} $, we have $ \lambda_A(s) = \alpha_A(s) \cdot \delta_A \cdot \pi_A : \RAct{A_1}(U_{A_1}^n, U_{A_1}) $ for the projection $ \pi_A: A_2 \to U_{A_1} $.
-However, note that $ f^*(\lambda_A(s)): \RAct{A^\prime_1}(f^*(U_{A^\prime_1}^n), f^*(U_{A^\prime_1})) $.
+  % Then, for $ s: E(U_A)_{n + 1} $, we have $ \lambda_A(s) = \alpha_A(s) \cdot \delta_A \cdot \pi_A : \RAct{A_1}(U_A^n, U_A) $ for the projection $ \pi_A: A_2 \to U_A $.
+However, note that $ f^*(\lambda_A(s)): \RAct{A^\prime_1}(f^*(U_{A^\prime}^n), f^*(U_{A^\prime})) $.
 To compare this to $ \lambda_{A^\prime}(\dots) $, we actually need to take
-  % \[ (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\lambda_A(s)) \cdot \beta : \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
-  % On the other hand, we also have $ f^*(s): \RAct{A^\prime_1}(f^*(U_{A_1}^{n + 1}), f^*(U_{A_1})) $ and we cannot apply $ \lambda_{A^\prime} $ directly. Instead, the term that we end up with is
-  % \[ \lambda_{A^\prime}((\beta^{-1})^{n + 1} \cdot \gamma_{n + 1}^{-1} \cdot f^*(s) \cdot \beta): \RAct{A^\prime_1}(U_{A_1}^n, U_{A_1}). \]
+  % \[ (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\lambda_A(s)) \cdot \beta : \RAct{A^\prime_1}(U_A^n, U_A). \]
+  % On the other hand, we also have $ f^*(s): \RAct{A^\prime_1}(f^*(U_A^{n + 1}), f^*(U_A)) $ and we cannot apply $ \lambda_{A^\prime} $ directly. Instead, the term that we end up with is
+  % \[ \lambda_{A^\prime}((\beta^{-1})^{n + 1} \cdot \gamma_{n + 1}^{-1} \cdot f^*(s) \cdot \beta): \RAct{A^\prime_1}(U_A^n, U_A). \]
   % So the equality that we need to prove is (using functoriality of $ f^* $ and naturality of $ \alpha_{A^\prime} $):
@@
   %   &(\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\alpha_A(s)) \cdot f^*(\delta_A \cdot \pi_A) \cdot \beta\\
-  %   &= (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot \alpha_{A^\prime}((\id X^n \times \beta^{-1}) \cdot \bar{\gamma}^{-1} \cdot f^*(s)) \cdot \beta^{U_{A_1}} \cdot \delta_{A^\prime} \cdot \pi_{A^\prime}.
+  %   &= (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot \alpha_{A^\prime}((\id X^n \times \beta^{-1}) \cdot \bar{\gamma}^{-1} \cdot f^*(s)) \cdot \beta^{U_A} \cdot \delta_{A^\prime} \cdot \pi_{A^\prime}.
   % \end{align*}
-  % Because of the complicated definition of each of these terms, I was unable to verify the correctness of this statement (and the similar statement about $ \rho: E(U_{A_1})_n \to E(U_{A_1})_{n + 1} $) within a day, even though I am willing to believe Hyland's claim.
+  % Because of the complicated definition of each of these terms, I was unable to verify the correctness of this statement (and the similar statement about $ \rho: E(U_A)_n \to E(U_A)_{n + 1} $) within a day, even though I am willing to believe Hyland's claim.
   % \TODO
 
-  % Given a morphism $ t: X \times Y \to Z $, $ \alpha_{A_1}(t): X \to (U_{A_1} \times Y \to Z) $ is given by
+  % Given a morphism $ t: X \times Y \to Z $, $ \alpha_{A_1}(t): X \to (U_A \times Y \to Z) $ is given by
   % \[ \alpha(t)(x)(a, y) = t(x a, y) \]
 
-  % Also, $ \beta: f^*(U_{A_1}) \xrightarrow{\sim} U_{A^\prime_1} $ is given, for $ a: A_1 $ and $ a^\prime : A^\prime_1 $, by
+  % Also, $ \beta: f^*(U_A) \xrightarrow{\sim} U_{A^\prime} $ is given, for $ a: A_1 $ and $ a^\prime : A^\prime_1 $, by
   % \[ \beta(a, a^\prime) = f(a) a^\prime \quad \text{and} \quad \beta^{-1}(a^\prime) = (1, a^\prime). \]
@@
 
-  % For some $ s: U_{A_1}^{n + 1} \to U_{A_1} $, the left hand side sends $ (a, (a^\prime_1, \dots, a^\prime_n)): f^*(U_{A_1}^n) $ to
+  % For some $ s: U_A^{n + 1} \to U_A $, the left hand side sends $ (a, (a^\prime_1, \dots, a^\prime_n)): f^*(U_A^n) $ to
   % \begin{align*}
@@
 
+\subsection{Essentially surjective}
+
 \begin{lemma}
-  We have an isomorphism $ U_{L_0} \cong L $.
+  We have an isomorphism of $ \Lambda $-algebras $ \epsilon: E(\mathbf 1_1)_0 \xrightarrow \sim A $.
 \end{lemma}
 \begin{proof}
-  \TODO
+  Take $ c_n = (\lambda x_{n + 1}, x_{n + 1}): \Lambda_n $.
+Note that $ E(\mathbf 1_1)_0 $ is given by $ \{ a : A \mid (\lambda x_2, x_1 c_2) \bullet a = a \} $.
+Therefore, we have a bijection given by
+  \[ \epsilon(a) = (x_1 c_1) \bullet a \quad \text{and} \quad \epsilon^{-1}(a) = (\lambda x_2, x_1) \bullet a. \]
+  Now, to show that this is an isomorphism of $ \Lambda $-algebras, recall that $ \bullet: \R_A(U^n, U) \times \R_A(I, U)^n \to \R_A(U) $ is given by precomposition with the product morphism and that the $ \Lambda $-algebra structure on $ E(\mathbf 1_1)_0 $ is given by the embedding $ f \mapsto \iota_\Lambda(f) \bullet_A () $ of $ \Lambda $ into $ E(\mathbf 1_1)_0 $.
+We have for all $ f: \Lambda_n $, and all $ a : E(\mathbf 1_1)_0^n $,
+  \begin{align*}
+    \epsilon(f \bullet_{E(\mathbf 1_1)} a)
+    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_1, \dots, a_n \rangle)(c_n)\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1 c_n), x_2 c_n), \dots), x_n c_n)) \bullet_A a\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1), x_2), \dots), x_n)) \bullet_A (\epsilon(a_i))_i,
+  \end{align*}
+  writing $ \bar x_n $ for $ ((\dots((c_n, x_1), x_2), \dots), x_n) $, and leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $,
+  \[ \iota_\Lambda(f) \bar x_n = f. \]
+  We will do this by structural induction on $ f $.
+  \begin{itemize}
+    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i} $, and
+      \[ (\pi_2 \circ \pi_1 \circ \dots \circ \pi_1) \bar x_n = x_{n, i}. \]
+    \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
+      \[ \iota_\Lambda(f) = (\lambda x_1 x_2, \iota_{0, 2}(\iota_\Lambda(g)) (x_1, x_2)), \]
+      and if the induction hypothesis holds for $ g $, then
+      \begin{align*}
+        \iota_\Lambda(f) \bar x_n
+        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) \bar x_n\\
+        &= \lambda x_{n + 1}, \iota_\Lambda(g) (\bar x_n, x_{n + 1})\\
+        &= \lambda x_{n + 1}, g.
+      \end{align*}
+    \item Recall that application in a $ \lambda $-theory is given by $ g_1 g_2 = \rho(g_1) \bullet (x_1, \dots, x_n, g_2) $. Now, if $ f = g_1 g_2 $ for $ g_1, g_2 : \Lambda_{n + 1} $, we have
+      \[
+        \iota_\Lambda(f)
+        = (\lambda x_1, \iota_\Lambda(g_1) (\pi_1 x_1) (\pi_2 x_1)) \circ \langle \id{U^n}, \iota_\Lambda(g_2) \rangle
+        = \lambda x_1, \iota_\Lambda(g_1) x_1 (\iota_\Lambda(g_2) x_1),
+      \]
+      and if the induction hypothesis holds for $ g_1 $ and $ g_2 $, then
+      \begin{align*}
+        \iota_\Lambda(f) \bar x_n
+        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) \bar x_n\\
+        &= \iota_\Lambda(g_1) \bar x_n (\iota_\Lambda(g_2) \bar x_n)\\
+        &= g_1 g_2.
+      \end{align*}
+  \end{itemize}
+\end{proof}
+
+Hyland shows the same fact in a slightly higher-level way.
+
+For his proof, we already need the unit of the adjunction. The quest for this counit boils down to a version of Scott's representation theorem.
+\begin{lemma}
+  For a $ \lambda $-theory $ L $, we can define an (iso)morphism
+  \[ \eta: \LamTh(L, E(U_{L_0})). \]
+\end{lemma}
+\begin{proof}
+  Note that for $ \R $ the category of retracts of $ L $,
+  \[ \mathbf R \xrightarrow \sim \mathbf R_{L_0} \xrightarrow{Y} P \R_{L_0} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1} \]
+  is a fully faithful functor that preserves finite products and exponential objects, and that $ U_{L_0} $ is the image of $ U = (\lambda x_1, x_1) $ under this embedding, so we have an isomorphism $ E(U) \cong E(U_{L_0}) $.
+Then $ \eta $ arises by composing this with the isomorphism from Scott's representation theorem (Theorem \ref{thm:Scott})
+  \[ \eta: L \xrightarrow \sim E(U) \xrightarrow \sim E(U_{L_0}). \]
+  Note that on the terms without free variables, this becomes
+  \[ \eta_0:
+    L_0
+      \xrightarrow{f \mapsto (\lambda x_1, \iota_{0, 1}(f))}
+    \R(I, U)
+      \xrightarrow{f \mapsto (I \mapsto f)}
+    \RAct{(L_0)_1}(\{I\}, (L_0)_1),
+  \]
+  so $ \eta_0(f) = (I \mapsto (\lambda x_1, \iota_{0, 1}(f))) $.
+\end{proof}
+
+Alternatively, we can use Hyland's version of the representation theorem:
+\begin{lemma}
+  For a $ \lambda $-theory $ L $, we can define an (iso)morphism
+  \[ \eta: \LamTh(L, E(U_{L_0})). \]
+\end{lemma}
+\begin{proof}
+  Note that we have a chain of equivalences (Lemma \ref{lem:equivalent-presheaf-cats} and Remark \ref{rem:ract-presheaf-equivalence})
+  \[ \Pshf L \xrightarrow \sim P \mathbf L \xrightarrow \sim P C_{L_1} \xrightarrow \sim \RAct{L_1} \xrightarrow \sim \RAct{{L_0}_1} \]
+  and $ U_{L_0} $ is isomorphic to the image of the theory presheaf $ L $ under this equivalence.
+Then $ \eta $ arises by combining this with the isomorphism from Scott's representation theorem (Theorem \ref{thm:representation-theorem})
+  \[ \eta: L \xrightarrow \sim E(L) \xrightarrow \sim E(U_{L_0}). \]
+  Note that on the terms without free variables, this becomes
+  \[ \eta_0:
+    L_0
+      \xrightarrow{f \mapsto (\star \mapsto \iota_{0, n}(f))_n}
+    \Pshf L(I, L)
+      \xrightarrow{F \mapsto (\star \mapsto (\lambda x_1, F_1(\star)))}
+    \RAct{(L_0)_1}(\{\star\}, (L_0)_1),
+  \]
+  so $ \eta_0(f) = (\star \mapsto (\lambda x_1, \iota_{0, 1}(f))) $, which luckily coincides with the $ \eta_0 $ given above.
 \end{proof}
@@
 \begin{lemma}
-  This is indeed an isomorphism of $ \lambda $-theories.
+  We have a bijection $ \epsilon_A : E(U_A)_0 \cong A $, sending $ s $ to $ x_1 (\lambda x_2, x_2) \bullet (s(\star)) $.
 \end{lemma}
 \begin{proof}
+  In Lemma \ref{lem:global-action-elements}, we showed that $ E(U_A)_0 $ corresponds to the set of $ A_1 $-equivariant elements of $ U_A $, sending $ s $ to $ s(\star) $.
+Now, for an $ A_1 $-equivariant element $ a $,
+  \[ (\lambda x_2, x_1 (\lambda x_3, x_3)) \bullet a = a \circ ((\lambda x_1 x_2, x_2) \bullet ()) = a \]
+  so we can send $ a $ to $ A $ as $ (x_1 (\lambda x_2, x_2)) \bullet a $ and it has (two-sided) inverse $ (\lambda x_2, x_1) \bullet a $.
+\end{proof}
+
+We want to show that $ \epsilon_A $ is an isomorphism of $ \Lambda $-algebras.
+We use Lemma \ref{lem:make-is-lambda-algebra-morphism} for this, so we need to show that it preserves the application and the $ \Lambda $-definable constants.
+
+\begin{lemma}
+  For $ \epsilon_A $ as above, we have for all $ a, b: E(U_A)_0 $, we have
+  \[ \epsilon_A((x_1 x_2) \bullet (a, b)) = (x_1 x_2) \bullet (\epsilon_A(a), \epsilon_A(b)). \]
+\end{lemma}
+\begin{proof}
+  For $ a, b: E(U_A)_0 $, we have, for the isomorphism $ \delta: \RAct{A_1}(U_A^{U_A}, A_2) $,
+  \begin{align*}
+    \epsilon_A((x_1 x_2) \bullet (a, b)) &= (x_1 (\lambda x_3, x_3) (x_2 (\lambda x_3, x_3))) \bullet (a(\star), b(\star))\\
+    &= (x_1 x_2) \bullet (\epsilon_A(a), \epsilon_A(b))
+  \end{align*}
+  and this concludes the proof.
+\end{proof}
+
+\begin{lemma}\label{lem:counit-natural}
+  Let $ F: A \to B $ be a $ \Lambda $-algebra morphism. Then the following diagram commutes:
+  \begin{center}
+    \begin{tikzcd}
+      E(U_A)_0 \arrow[d, "\epsilon_A"] \arrow[r, "\bar F_0"] & E(U_B)_0 \arrow[d, "\epsilon_A"]\\
+      A \arrow[r, "f"] & B
+    \end{tikzcd}
+  \end{center}
+\end{lemma}
+\begin{proof}
+  The functor $ F_* : \RAct{A_1} \to \RAct{B_1} $ sends $ X : \RAct{A_1} $ to $ X \times B_1 / \sim : \RAct{B_1} $. We have isomorphisms
+  \[ \beta: F_*(U_A) \xrightarrow \sim U_B \quad \text{and} \quad \gamma: F_*(I) \xrightarrow \sim I, \]
+  with
+  \[ \beta(a, b) = F(a) \circ b \quad \text{and} \quad \gamma^{-1}(\star) = (\star, (\lambda x_1 x_2, x_2) \bullet ()). \]
+  Then $ \bar F: \RAct{A_1}(I, U_A) \to \RAct{B_1}(I, U_B) $ is given by
+  \[
+    \bar F(s)(\star)
+    = \gamma^{-1} \cdot (s \times \id{B_1}) \cdot \beta
+    = (\lambda x_2, x_1 (\lambda x_3, x_3)) \bullet F(s(\star)),
+  \]
+  so
+  \[
+    (\bar F \cdot \epsilon_B)(s)
+    = (x_1 (\lambda x_2, x_2)) \bullet F(s(\star))
+    = (\epsilon_A \cdot F)(s),
+  \]
+  which concludes the proof.
+\end{proof}
+
+\begin{lemma}
+  For $ \epsilon_A $ as above, we have for all $ s: \Lambda_0 $,
+  \[ \epsilon_A(s \bullet ()) = s \bullet (). \]
+\end{lemma}
+\begin{proof}
+  Consider the following diagram, with $ F: \Alg \Lambda(\Lambda_0, A) $ given by $ s \mapsto s \bullet () $:
+  \begin{center}
+    \begin{tikzcd}
+      E(U_{\Lambda_0})_0
+        \arrow[r, "(\bar F)_0"]
+        \arrow[d, "\epsilon_{\Lambda_0}"]
+      & E(U_A)_0
+        \arrow[d, "\epsilon_A"]\\
+      \Lambda_0
+        \arrow[r, "F"]
+        \arrow[u, bend left, "\eta_0"]
+      & A
+    \end{tikzcd}
+  \end{center}
+  By Lemma \ref{lem:counit-natural}, the square commutes. Also, note that $ \eta_0 \cdot \epsilon_{\Lambda_0} $ sends $ s : \Lambda_0 $ to
+  \[ (x_1 (\lambda x_2, x_2)) \bullet (\lambda x_1, \iota_{0, 1}(s)) = s. \]
+  Recall that there exists a unique morphism $ \iota_\Lambda: \LamTh(\Lambda, E(U_A)) $, and that for all $ s: \Lambda_0 $, $ s \bullet () = \iota_\Lambda(s) \bullet () = \iota_\Lambda(s) $.
+Since we have $ \eta \cdot \bar F : \LamTh(\Lambda, E(U_A)) $, we must have $ \iota_\Lambda = \eta \cdot \bar F $ and
+  \begin{align*}
+    \epsilon_A(s \bullet_{E(U_A)} ())
+    &= \epsilon_A(\bar{F_0}(\eta_0(s)))\\
+    &= F(\epsilon_{\Lambda_0}(\eta_0(s)))\\
+    &= F(s)\\
+    &= s \bullet_A (),
+  \end{align*}
+  which concludes the proof.
+\end{proof}
+
+\subsection{Fully faithful}
+
 \TODO
-\end{proof}
+
+\subsection{Adjoint equivalence}
 
@@
 
-  It is essentially surjective, because $ L $ is isomorphic \TODO to $ E(U_{A_1}) $.
+  It is essentially surjective, because $ L $ is isomorphic \TODO to $ E(U_A) $.
 
@@
   The functor is full because a $ \Lambda $-algebra morphism $ f: A \to A^\prime $ induces a functor $ f^*: \RAct{A^\prime} \to \RAct{A} $, and via left Kan extension we get a left adjoint $ f^*: \RAct{A} \to \RAct{A^\prime} $ with $ f^*(A_1) \cong A^\prime_1 $.
-Now, $ f^* $ preserves (finite) products, so we have maps $ \RAct{A}(A_1^n, A_1) \to \RAct{A^\prime}((A^\prime_1)^n, A^\prime_1) $ and so a map $ E(U_{A_1}) \to E(U_{A^\prime_1}) $.
+Now, $ f^* $ preserves (finite) products, so we have maps $ \RAct{A}(A_1^n, A_1) \to \RAct{A^\prime}((A^\prime_1)^n, A^\prime_1) $ and so a map $ E(U_A) \to E(U_{A^\prime}) $.
 This map, when restricted to a map $ \RAct{A}(1, A_1) \to \RAct{A^\prime}(1, A_1) $, and transported along the isomorphism $ a \mapsto a I $ \TODO, is equal to $ f $ \TODO.

### 2024-05-24 report/chapters/paper.tex
Write almost the full proof of Hyland

@@
 Write $ i: \op{L_1} \hookrightarrow \op{\mathbf L} $ and $ j: \op{\mathbf L} \hookrightarrow \op \R $ for the embeddings on the opposite categories.
-By Corollary \ref{cor:surjective-precomposition}, the first two morphisms in this sequence yield the following sequence of essentially surjective functors on the presheaf categories:
+By Corollary \ref{cor:surjective-precomposition}, the first two functors in this sequence essentially yield surjective functors on the presheaf categories:
 \begin{center}
   \begin{tikzcd}
-    \mathbf R \arrow[r, hookrightarrow] \arrow[d, hookrightarrow, "Y"] & \Pshf L \arrow[d, "\sim"]\\
-    P \R \arrow[r, twoheadrightarrow, "j_*"] \arrow[rr, bend right, "\sim"] & P \mathbf L \arrow[r, twoheadrightarrow, "i_*"] & P C_{L_1}
+    C_{L_1} \arrow[d, "Y", hook] &
+    \mathbf L \arrow[l, "\op i"'] \arrow[d, "Y", hook] &
+    \mathbf R \arrow[rd, hook] \arrow[d, "Y", hook] \arrow[l, "\op j"']\\
+    P C_{L_1} &
+    P \mathbf L \arrow[l, "i_*"', two heads] &
+    P \R \arrow[l, "j_*"', two heads] \arrow[ll, "\sim"', bend left] &
+    \Pshf L \arrow[ll, "\sim", bend left]
   \end{tikzcd}
@@
 \begin{lemma}
-  The square in the diagram above 2-commutes.
+  The embeddings of $ \R $ into $ \Pshf L $ and $ P \R $ commute with the equivalence between these categories.
 \end{lemma}
@@
 
-\section{Terms of a \texorpdfstring{$ \Lambda $}{Lambda}-algebra}
-Let $ A $ be an algebra for the initial $ \lambda $-theory $ \Lambda $. We will assume that $ \Lambda $ (and therefore, any $ \lambda $-theory) satisfies $ \beta $-equality.
+\section{The `Fundamental Theorem' of the \texorpdfstring{$ \lambda $}{lambda}-calculus}
 
-The $ \Lambda $-algebra structure gives the terms of $ A $ quite a lot of behaviour. For example, we can define `function application' as
-\[ a b = (x_1 x_2) \bullet (a, b) \]
-and composition as
-\[ a \circ b = (x_1 \circ x_2) \bullet (a, b) \]
+The final theorem that Hyland works towards in his paper constructs an equivalence between $ \lambda $-calculi and $ \Lambda $-algebras.
+First, we will give an elementary version of Hyland's proof.
+Then we will provide an expanded version of Hyland's proof.
+And afterwards we will show it in a third, somewhat unrelated way.
+
+We will assume that $ \Lambda $ (and therefore, any $ \lambda $-theory) satisfies $ \beta $-equality.
+
+In both cases, one part of the equivalence is very easy:
+\begin{definition}
+  For all $ n $, we have a functor from lambda theories to $ \Lambda $-algebras.
+It sends the $ \lambda $-theory $ L $ to the $ L $-algebra $ L_n $ and then turns this into a $ \Lambda $-algebra via the morpism $ \Lambda \to L $.
+It sends morphisms $ f: L \to L^\prime $ to the algebra morphism $ f_n : L_n \to L^\prime_n $.
+\end{definition}
+Here we are only interested in the case $ n = 0 $.
+
+\subsection{An elementary version of Hyland's proof}
+We will use Lemma \ref{lem:univalen-category-equivalence}, by showing that $ L \mapsto L_0 $ is a weak equivalence.
+
+First of all, let $ A $ be an algebra for the initial $ \lambda $-theory $ \Lambda $.
+
+The $ \Lambda $-algebra structure gives the terms of $ A $ quite a lot of interesting behaviour. For example, we can define `function application' and composition as
+\[ a b = (x_1 x_2) \bullet (a, b) \quad \text{and} \quad a \circ b = (x_1 \circ x_2) \bullet (a, b), \]
 and the same for the other constructions at the start of Section \ref{sec:retracts-category}.
@@
 \begin{remark}
-  Recall that in Example \ref{ex:free-monoid-theory}, we constructed an algebraic theory $ T $ with a monoid structure.
+  Recall that in Example \ref{ex:free-monoid-theory}, we constructed an algebraic theory $ T $ encapsulating the structure of a monoid.
 This allowed us to define a monoid operation on $ T $-algebras as well.
@@
 In exactly the same way, the function composition on $ A $ is associative because composition on $ \Lambda_n $ is associative.
+Similarly, we can show that $ \pi_1 (a, b) = a $, that $ \pi_2 \circ \langle a, b \rangle = (\lambda x_2, x_1 x_2) \bullet b $ etc.
 \end{remark}
 
+In fact, we can repeat almost the entirety of Section \ref{sec:retracts-category} for $ A $ instead of for $ L_0 $:
 \begin{definition}
-  We can consider the sets of elements of $ A $ that behave like functions in $ n $ variables:
-  \[ A_n = \{ a : A \mid (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 x_3 \dots x_{n + 1}) \bullet a = a \}. \]
+  We define the `category of retracts' of $ A $ as the category $ \R_A $ given by
+  \[ (\R_A)_0 = \{ X : A \mid X \circ X = X \} \quad \text{and} \quad \R_A(X, Y) = \{ f : A \mid Y \circ f \circ X = f \}. \]
 \end{definition}
+Just like in Section \ref{sec:retracts-category}, $ \R_A $ has `universal object' and terminal object
+\[ U = (\lambda x_1, x_1) \bullet () \quad \text{and} \quad I = (\lambda x_1, c_1), \]
+products
+\[ A \times B = \langle A \circ \pi_1, B \circ \pi_2 \rangle \]
+and exponential objects
+\[ B^A = (\lambda x_3, x_1 \circ x_3 \circ x_2) \bullet (B, A) \]
+with the isomorphism $ \psi: \R_A(C \times A, B) \xrightarrow \sim \R_A(C, B^A) $
+given by
+\[ \psi(f) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet f \quad \text{and} \quad \psi^{-1}(f) = (\lambda x_2, x_1 (\pi_1 x_2) (\pi_2 x_2)) \bullet f. \]
+
+Therefore, we have a $ \lambda $-theory $ E_{\R_A}(U) $.
+
+\begin{remark}
+  Note that if $ A = L_0 $, then the construction of $ \R_A $ and $ \R $ coincide, so we have an almost trivial equivalence $ \R_A \cong \R $, and an isomorphism $ E_{\R}(U) \cong E_{\R_A}(U) $.
+\end{remark}
+
+The following lemma shows that our functor is essentially surjective:
+
+\begin{lemma}\label{lem:elementary-essentially-surjective}
+  We have a $ \Lambda $-algebra isomorphism $ \epsilon_A : E_{\R_A}(U)_0 \xrightarrow \sim A $.
+\end{lemma}
+\begin{proof}
+  Take $ c_n = (\lambda x_{n + 1}, x_{n + 1}): \Lambda_n $. Note that
+  \[ E(U)_0 = \{ f : A \mid (\lambda x_2, x_1 c_2) \bullet f = f \}. \]
+  Therefore, we have a bijection given by
+  \[ \epsilon(a) = (x_1 c_1) \bullet a \quad \text{and} \quad \epsilon^{-1}(a) = (\lambda x_2, x_1) \bullet a. \]
+  Now, to show that this is an isomorphism of $ \Lambda $-algebras, recall that $ \bullet: \R_A(U^n, U) \times \R_A(I, U)^n \to \R_A(U) $ is given by precomposition with the product morphism and that the $ \Lambda $-algebra structure on $ E(U)_0 $ is given by the embedding of $ \Lambda $ into $ E(U)_0 $, given by $ f \mapsto {\iota_\Lambda}_n(f) \bullet_A () $ for some collection $ ({\iota_\Lambda}_n: \Lambda_n \to \Lambda_0)_n $ (from now on, we will drop the $ n $ and just write $ \iota_\Lambda $).
+We have for all $ f: \Lambda_n $, and all $ a : E(U)_0^n $,
+  \begin{align*}
+    \epsilon(f \bullet_{E(U)} a)
+    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_1, \dots, a_n \rangle)(c_n)\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1 c_n), x_2 c_n), \dots), x_n c_n)) \bullet_A a\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1), x_2), \dots), x_n)) \bullet_A (\epsilon(a_i))_i,
+  \end{align*}
+  and we want this to equal $ f \bullet_A (\epsilon(a_i))_i $.
+Writing $ \bar x_n $ for $ ((\dots((c_n, x_1), x_2), \dots), x_n) $, and leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $, we have $ \iota_\Lambda(f) \bar x_n = f $.
+We will do this by structural induction on $ f $.
+  \begin{itemize}
+    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i} $, and
+      \[ \iota_\Lambda(f) \bar x_n = (\pi_2 \circ \pi_1 \circ \dots \circ \pi_1) \bar x_n = x_{n, i}. \]
+    \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
+      \[ \iota_\Lambda(f) = (\lambda x_1 x_2, \iota_{0, 2}(\iota_\Lambda(g)) (x_1, x_2)), \]
+      and if the induction hypothesis holds for $ g $, then
+      \begin{align*}
+        \iota_\Lambda(f) \bar x_n
+        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) \bar x_n\\
+        &= \lambda x_{n + 1}, \iota_\Lambda(g) (\bar x_n, x_{n + 1})\\
+        &= \lambda x_{n + 1}, g.
+      \end{align*}
+    \item Recall that application in a $ \lambda $-theory is given by $ g_1 g_2 = \rho(g_1) \bullet (x_1, \dots, x_n, g_2) $. Now, if $ f = g_1 g_2 $ for $ g_1, g_2 : \Lambda_{n + 1} $, we have
+      \[
+        \iota_\Lambda(f)
+        = (\lambda x_1, \iota_\Lambda(g_1) (\pi_1 x_1) (\pi_2 x_1)) \circ \langle \id{U^n}, \iota_\Lambda(g_2) \rangle
+        = \lambda x_1, \iota_\Lambda(g_1) x_1 (\iota_\Lambda(g_2) x_1),
+      \]
+      and if the induction hypothesis holds for $ g_1 $ and $ g_2 $, then
+      \begin{align*}
+        \iota_\Lambda(f) \bar x_n
+        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) \bar x_n\\
+        &= \iota_\Lambda(g_1) \bar x_n (\iota_\Lambda(g_2) \bar x_n)\\
+        &= g_1 g_2.
+      \end{align*}
+  \end{itemize}
+\end{proof}
+
+Now, take a morphism $ F: \Alg{\Lambda}(A, B) $.
+Recall that $ \circ $, the categories $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given using $ f \bullet (a_1, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $.
+Since we have $ F(f \bullet (a_1, \dots, a_n)) = f \bullet (F(a_1), \dots, F(a_n)) $, $ F $ gives a functor $ F: \R_A \to \R_B $, such that
+\[ F(I) = I, F(U) = U, F(A \times B) = F(A) \times F(B) \quad \text{and} \quad F(A^B) = F(A)^{F(B)}, \]
+and the same for the product projections and the the natural isomorphisms $ \R_A(C, B^A) \cong \R_A(C \times A, B) $. In particular, we have for all $ f: \R_A(U^n, U) $,
+\[ F(f) : \R_B(F(U^n), F(U)) = \R_B(U^n, U). \]
+Therefore, $ F $ gives a $ \Lambda $-theory morphism between the endomorphism theories of $ U: \R_A $ and $ U: \R_B $. This allows us to show:
+\begin{lemma}\label{lem:elementary-full}
+  The functor is full.
+\end{lemma}
+\begin{proof}
+  For any $ \lambda $-theory $ L $, Theorem \ref{thm:Scott} gives an isomorphism of $ \lambda $-theories $ \eta_L: L \xrightarrow \sim E_{\R_{L_0}}(U) $, with
+  \[ {\eta_L}_0(f) = \lambda x_1, \iota_{0, 1}(f) \quad \text{and} \quad {\eta_L^{-1}}_0(g) = g(\lambda x_1, x_1). \]
+
+  Now, for $ L, L^\prime: \LamTh $ and $ F: \Alg{\Lambda}(L_0, L^\prime_0) $, we have
+  \[ \eta_L \cdot F \cdot \eta_{L^\prime}^{-1} : \LamTh(L, L^\prime), \]
+  and we have for all $ s : L_0 $,
+  \[ ({\eta_L}_0 \cdot F \cdot {\eta_{L^\prime}^{-1}}_0)(s) = (\lambda x_1, \iota_{0, 1}(F(s))) (\lambda x_1, x_1) = F(s), \]
+  which shows that the functor is full.
+\end{proof}
+
+Now, we only have to show:
+\begin{lemma}\label{lem:elementary-faithful}
+  The functor is faithful.
+\end{lemma}
+\begin{proof}
+  Take morphisms $ F, G: \LamTh(L, L^\prime) $. Suppose that $ F_0 = G_0 $. Then, for all $ s: L_n $, we have
+  \[ F_n(s) = \rho^n(F_0(\lambda^n(s))) = \rho^n(G_0(\lambda^n(s))) = G_n(s), \]
+  so $ F = G $.
+\end{proof}
+
+Summarizing,
+\begin{theorem}
+  The functor that sends $ L : \LamTh $ to $ L_0 : \Alg{\Lambda} $, is an adjoint equivalence.
+\end{theorem}
+\begin{proof}
+  By Lemma \ref{lem:elementary-full} and Lemma \ref{lem:elementary-faithful}, the functor is fully faithful.
+By Lemma \ref{lem:elementary-essentially-surjective}, it is essentially surjective, so it is a weak equivalence.
+Since $ \LamTh $ and $ \Alg{\Lambda} $ are univalent categories, Lemma \ref{lem:univalen-category-equivalence} shows that $ F $ is an adjoint equivalence.
+\end{proof}
+
+\subsection{Hyland's proof}
+
+\subsubsection{Terms of a \texorpdfstring{$ \Lambda $}{Lambda}-algebra}
 
@@
 \begin{remark}
-  Some straightforward rewriting, shows that for all $ a : A $,
-  \[ \mathbf 1_n \circ a = (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1}) \bullet a. \]
-  In other words, $ A_n = \{ a : A \mid \mathbf 1_n \circ a = a \} $.
+  Note that we have $ \mathbf 1_1 = U : \R_A $.
+\end{remark}
+
+\begin{definition}
+  In this section, we consider sets of elements of $ A $ that behave like functions in $ n $ variables:
+  \[ A_n = \{ a : A \mid (\lambda x_2 x_3 \dots x_{n + 1}, x_1 x_2 x_3 \dots x_{n + 1}) \bullet a = a \}. \]
+\end{definition}
+
+\begin{remark}
+  Some straightforward rewriting, shows that
+  \[ A_n = \{ a : A \mid \mathbf 1_n \circ a = a \}. \]
 \end{remark}
@@
 
+The following shows that `functions in $ n $ variables' are indeed all in $ A_n $:
 \begin{lemma}
@@
 
-\section{The Fundamental Theorem of the \texorpdfstring{$ \lambda $-}{lambda }calculus}
-
-The fundamental theorem states that there is an adjoint equivalence
-\[ \LamTh \cong \Alg \Lambda. \]
-We will prove this by showing that there is a weak equivalence. Using the fact that $ \LamTh $ is
-
-\subsection{The functor}
-
-\begin{definition}
-  For all $ n $, we have a functor from lambda theories to $ \Lambda $-algebras.
-It sends the $ \lambda $-theory $ L $ to the $ L $-algebra $ L_n $ and then turns this into a $ \Lambda $-algebra via the morpism $ \Lambda \to L $.
-It sends morphisms $ f: L \to L^\prime $ to the algebra morphism $ f_n : L_n \to L^\prime_n $.
-\end{definition}
-
-Here, we are mostly interested in the case $ n = 0 $.
-
-\subsection{Lifting \texorpdfstring{$ \Lambda $}{Lambda}-algebras}
-
 \begin{definition}[The monoid of a $ \Lambda $-algebra]
-  We make $ A_1 $, the `functional elements' of $ A $, into a monoid under composition $ \circ $ with unit $ \mathbf 1_1 $. The fact that this is a monoid follows from the remarks in the last section.
+  We make $ A_1 $, the `functional elements' of $ A $, into a monoid under composition $ \circ $ with unit $ \mathbf 1_1 $. The fact that this is a monoid follows from the remarks above.
 \end{definition}
@@
 
-In particular, we have a set with right $ A_1 $-action, given by $ A_1 $ itself. We will call this set with right $ A_1 $-action $ U_A $.
-
-\begin{remark}
-  Note that, like in the last chapter, we can take the Karoubi envelope $ \R_A $ of $ C_{A_1} $, which yields the following diagram:
+\begin{remark}\label{rem:ract-presheaf-equivalence}
+  Note that, like in the last chapter, $ \R_A $ pops up as the Karoubi envelope of the monoid category $ C_{A_1} $, and fits into the following diagram:
   \begin{center}
@@
   \[ X \mapsto \R_A(\mathbf 1_1, X) = \{ x : A \mid X \circ x = x \}. \]
-  Now, we can repeat almost the entirety of Section \ref{sec:retracts-category} for $ \R_A $. In particular, $ \R_A $ has "universal object"
-  \[ U = \mathbf 1_1, \]
-  products
-  \[ A \times B = \langle x_1 \circ \pi_1, x_2 \circ \pi_2 \rangle \bullet (A, B) \]
-  and exponential objects
-  \[ B^A = (\lambda x_3, x_1 \circ x_3 \circ x_2) \bullet (B, A) \]
-  with the isomorphism $ \psi: \R_A(C \times A, B) \xrightarrow \sim \R_A(C, B^A) $
-  given by
-  \[ \psi(f) = (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet f \quad \text{and} \quad \psi^{-1}(f) = (\lambda x_2, x_1 (\pi_1 x_2) (\pi_2 x_2)) \bullet f. \]
+  Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $.
+Using \ref{lem:equivalent-presheaf-cats}, we have the following 2-commutative diagram:
+  \begin{center}
+    \begin{tikzcd}
+      &
+      C_{{L_0}_1} \arrow[dd, "Y" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "Y" description, hook] \arrow[rd, "\sim" description, no head] & & \\
+      &
+      & C_{L_1} \arrow[dd, "Y" description, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "Y" description, hook] & & \mathbf R \arrow[dd, "Y" description, hook] \arrow[rdd, hook] & \\
+      \RAct{{L_0}_1} &
+      P C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] & & & P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] & & \\
+      &
+      & P C_{L_1} & P \mathbf L \arrow[l, "\sim" description] & & P \R \arrow[ll, "\sim" description] & \Pshf L \arrow[lll, "\sim" description, bend left]
+    \end{tikzcd}
+  \end{center}
 \end{remark}
 
-\begin{remark}\label{rem:ract-presheaf-equivalence}
-  Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $.
-From Lemma \ref{lem:equivalent-presheaf-cats}, it follows that $ \RAct{A_1} $ is equivalent to $ \Pshf L $.
-This might motivate some of the following constructions.
-\end{remark}
+\subsubsection{Constructing a theory from an algebra}
 
 \begin{definition}
-  Composition $ \circ $ gives a right $ A_1 $-action on the $ A_n $, so we have $ A_n : \RAct{A_1} $ (note that this is the image of $ \mathbf 1_n : \R_A $ under the embeddding into $ \RAct{A_1} $).
+  Composition $ \circ $ gives a right $ A_1 $-action on the $ A_n $, so we have $ A_n : \RAct{A_1} $.
+In particular, $ A_1 $ acts on itself, and we will call this set with right $ A_1 $-action $ U_A $.
 \end{definition}
@@
 \begin{lemma}
-  $ A_2 $ is the exponential object $ A_1^{A_1} $ in $ \RAct{A_1} $.
+  $ A_2 $ is isomorphic to the exponential object $ U_A^{U_A} $ in $ \RAct{A_1} $.
 \end{lemma}
 \begin{proof}
-  Note that the embedding $ \R_A \hookrightarrow \RAct{A_1} $ is the composition of a Yoneda embedding and two adjoint equivalences.
-These all preserve exponential objects (\TODO: Citation needed).
-Since $ A_1 $ is the image of $ \mathbf 1_1 : \R_A $, the exponential $ A_1^{A_1} $ is $ A_2 $, the image of $ \mathbf 1_1^{\mathbf 1_1} = \lambda x_1 x_2, x_1 x_2 $.
-\end{proof}
-
-\begin{remark}
-  Hyland shows this by explicitly constructing an isomorphism $ \psi $ between $ A_2 $ and the `familiar' exponential object in $ \RAct{A_1} $ (the set of $ A_1 $-equivariant morphisms $ U_A \times U_A \to U_A $), given by
+  Recall that $ U_A^{U_A} $ is the set of $ A_1 $-equivariant morphisms $ U_A \times U_A \to U_A $. We have an isomorphism $ \psi: A_2 \xrightarrow \sim U_A^{U_A} $, given by
   \[ \psi(f) = (b, b^\prime) \mapsto (\lambda x_4, x_1 (x_2 x_4) (x_3 x_4)) \bullet (f, b, b^\prime), \]
@@
   Note that the first pair $ (x_2, x_3) $ is a $ \lambda $-term, whereas the second pair $ (\pi_1, \pi_2) $ is a pair in $ U_A \times U_A $.
+
+  For $ f: U_A^{U_A} $ and $ (a_1, a_2): U_A \times U_A $, we have
+  \[
+    \psi(\psi^{-1}(f))(a_1, a_2)
+    = f(\pi_1, \pi_2) \circ \langle a_1, a_2 \rangle
+    = f(\pi_1 \circ \langle a_1, a_2 \rangle, \pi_2 \circ \langle a_1, a_2 \rangle)
+    = f(a_1, a_2).
+  \]
+  Here we use the $ A_1 $-equivariance of $ f $. In the last step of this proof, we use, among other things, the fact that the $ a_i : A_1 $ and therefore $ \lambda x_1, a_i x_1 = a_i $.
+
+  Some straightforward rewriting shows that for $ a: A_2 $, we have $ \psi^{-1}(\psi(a)) = a $.
+In the last step of this proof, we use the fact that $ a : A_2 $ and therefore $ \lambda x_1 x_2, a x_1 x_2 = a $.
+
+  Therefore, $ \psi $ is a bijection and, as it turns out, an isomorphism.
+\end{proof}
+
+\begin{remark}
+  Recall that the embedding $ \R_A \hookrightarrow \RAct{A_1} $ is the composition of a Yoneda embedding and two adjoint equivalences.
+These all preserve exponential objects (\TODO: Citation needed).
+Now, note that $ A_1 $ is the image of $ U : \R_A $, so the exponential $ U_A^{U_A} $ is $ A_2 $, the image of $ U^U = \lambda x_1 x_2, x_1 x_2 = \mathbf 1_2 $.
 \end{remark}
@@
 \begin{definition}[Construction of the $ \lambda $-theory]
-  Now, note that, like before, $ \mathbf 1_1 $ is a retract of $ \mathbf 1_2 $ in $ \R_A $.
-When we embed these into $ \RAct{A_1} $, we see that we have a subset $ A_2 \subseteq A_1 $ and a retraction $ r: A_1 \to A_2 $, given by precomposition with $ \mathbf 1_2 $.
+  Recall that $ A_2 \subseteq U_A $, and that we have a retraction $ a \mapsto \mathbf 1_2 \circ a : U_A \to A_2 $.
 
-  Therefore, $ \mathbf 1_1 $ and $ U_A $ are reflexive objects in $ \R_A $ and $ \RAct{A_1} $, and we get isomorphic $ \lambda $-theories $ E(\mathbf 1_1) $ and $ E(U_A) $.
+  Therefore, $ U_A $ is a reflexive object in $ \RAct{A_1} $, and we get a $ \lambda $-theory $ E(U_A) $.
 \end{definition}
 
-\subsection{Lifting algebra morphisms}
-
-Now, take a morphism $ F: \Alg{\Lambda}(A, B) $.
-Recall that $ \circ $, the structure on $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given by $ f \bullet (a_1, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $.
-Since we have $ F(f \bullet (a_1, \dots, a_n)) = f \bullet (F(a_1), \dots, F(a_n)) $, $ F $ gives a functor $ F: \R_A \to \R_B $ that preserves the terminal object, the object $ \mathbf 1_1 $, the products, their projections, the exponential objects and the natural isomorphisms $ \R_A(C, B^A) \cong \R_A(C \times A, B) $.
-This induces a $ \lambda $-theory morphism $ E(\mathbf 1_1) \to E(\mathbf 1_1) $ between the endomorphism theories of $ \mathbf 1_1 : A $ and $ \mathbf 1_1 : B $.
-
 \begin{remark}
-  Instead of in $ \R_A $ and $ \R_B $, Hyland tries to do the above in the `presheaf' categories $ \RAct{A_1} $ and $ \RAct{B_1} $.
-$ F $ induces a monoid morphism $ A_1 \to B_1 $, which gives a functor $ C_{A_1} \to C_{B_1} $.
-Precomposing with this, we get a functor $ \RAct{B_1} \to \RAct{A_1} $, and we only get the functor $ \RAct{A_1} \to \RAct{B_1} $ in the right direction after taking a Left Kan extension (the "tensor product": see Lemma \ref{lem:scalar-extension}).
+  The cartesian closed embedding of $ \R_A $ into $ \RAct{A_1} $ sends $ U $ to $ U_A $.
+It sends the retraction $ U^U: \R_A(U, U^U) $ exactly to the retraction $ a \mapsto \mathbf 1_2 \circ a: \RAct{A_1}(U_A, A_2) $.
+Therefore, we have a $ \lambda $-theory isomorphism $ E_{\R_A}(U) \cong E_{\RAct{A_1}}(U_A) $.
 \end{remark}
 
-\begin{lemma}
-  The functors on $ \R_A $ and $ \RAct{A_1} $ induced by $ F $ commute with the embedding of $ \R_A $ and $ \R_B $ into $ \RAct{A_1} $ and $ \RAct{B_1} $.
-In other words, the diagram below $ 2 $-commutes:
-  \begin{center}
-    \begin{tikzcd}
-      \R_A \arrow[r, "F"] \arrow[d, "{\R_A(\mathbf 1_1, -)}"] & \R_B \arrow[d, "{\R_B(\mathbf 1_1, -)}"]\\
-      \RAct{A_1} \arrow[r, "F_*"] & \RAct{B_1}
-    \end{tikzcd}
-  \end{center}
-\end{lemma}
-\begin{proof}
-  Given $ X : \R_A $, we need to show that we have a natural isomorphism of sets with a right $ B_1 $-action $ \psi: \R_B(\mathbf 1_1, F(X)) \xrightarrow \sim F_*(\R_A(\mathbf 1_1, X)) $, that is, we need
-  \[ \psi: \{ f : B \mid F(X) \circ f = f \} \xrightarrow \sim \{ f : A \mid X \circ f = f \} \times B_1 / \sim \]
-  with the equivalence relation on the latter given by $ (f, F(a) \circ b) \sim (f \circ a, b) $ for all $ f : \R_A(\mathbf 1_1, X) $, $ b : B_1 $ and $ a : A_1 $. We can take $ \psi $ to be
-  \[ \psi(f) = (X, f) \quad \text{and} \quad \psi^{-1}(f, b) = F(f) \circ b, \]
-  which is $ B_1 $-equivariant and natural in $ X $.
-  % We have
-  % \[ \psi^{-1}(\psi(f)) = \psi^{-1}(X, f) = F(X) \circ f = f \]
-  % \[ \psi(\psi^{-1}(f, b)) = \psi(F(f) \circ b) = (X, F(f) \circ b) = (X \circ f, b) = (f, b) \]
-  % We need to show that this is natural in $ X $.
-Therefore, take $ g : \R_A(X, Y) $.
-Then $ \R_B(\mathbf 1_1, F(g)) $ is given by postcomposition with $ F(g) $.
-Also, $ F_*(\R_A(\mathbf 1_1, g)) $ is given by postcomposing with $ g $ on the component $ \R_A(\mathbf 1_1, g) $.
-Then
-  % \[ \psi(F(g) \circ f) = (Y, F(g) \circ f) = (Y \circ g, f) = (g \circ X, f) \]
-\end{proof}
+\subsubsection{Constructing a theory morphism from an algebra morphism}
 
-For completeness' sake, the rest of this section will describe Hyland's reasoning a bit more:
+Take a morphism $ F: \Alg{\Lambda}(A, B) $.
+Note that $ F $ preserves $ \circ $ and the $ \mathbf 1_n $.
+Therefore, it induces a monoid morphism $ A_1 \to B_1 $, which gives a functor $ C_{A_1} \to C_{B_1} $.
+Precomposing with this, we get a functor $ \RAct{B_1} \to \RAct{A_1} $.
+
+To get a morphism $ E_{\RAct{A_1}}(U_A) \to E_{\RAct{B_1}}(U_B) $ however, we need a functor $ \RAct{A_1} \to \RAct{B_1} $, which we obtain by Left Kan extension: see Lemma \ref{lem:scalar-extension} (the ``tensor product'').
+
+Hyland gives a very high-level argument why $ F_* $ induces a morphism $ \bar F : \LamTh(E_{\RAct{A_1}}(U_A), E_{\RAct{B_1}}(U_B)) $, which we will discuss a bit more here.
+
 \begin{lemma}
@@
 
-  We will show that $ F_* $ preserves binary products and the terminal object.
+  We will show that $ F_* $ preserves binary products and the terminal object, because from this it follows that $ F_* $ preserves all finite products.
 
@@
 Therefore, given $ a_1, a_2 : B_1 $.
-Take $ b = \langle x_1, x_2 \rangle \bullet (a_1, a_2) $, together with the familiar projections $ \pi_i \bullet () : A_1 $.
+Take $ b = \langle a_1, a_2 \rangle $, together with the familiar projections $ \pi_i : A_1 $.
 We have $ a_i = F(\pi_i) \circ a $.
@@
   \begin{align*}
-    \alpha_A: \RAct{A_1}(X \times Y, Z) &\xrightarrow{\sim} \RAct{A}(X, Z^Y);\\
+    \alpha_A: \RAct{A_1}(X \times Y, Z) &\xrightarrow{\sim} \RAct{A_1}(X, Z^Y);\\
     \beta: F_*(U_A) &\xrightarrow{\sim} U_{A^\prime};\\
@@
   \end{align*}
+  Since we already motivated this in a different way, we will leave it as an exercise for the enthousiastic reader.
   % with $ \gamma_{n + 1} = \bar{\gamma} \cdot (\gamma_n \times \id X) $.
@@
   % Because of the complicated definition of each of these terms, I was unable to verify the correctness of this statement (and the similar statement about $ \rho: E(U_A)_n \to E(U_A)_{n + 1} $) within a day, even though I am willing to believe Hyland's claim.
-  % \TODO
 
@@
 
-\subsection{Essentially surjective}
-
 \begin{lemma}
-  We have an isomorphism of $ \Lambda $-algebras $ \epsilon: E(\mathbf 1_1)_0 \xrightarrow \sim A $.
+  For $ F = \id A $, we have $ \bar F = \id{E(U_A)} $.
 \end{lemma}
 \begin{proof}
-  Take $ c_n = (\lambda x_{n + 1}, x_{n + 1}): \Lambda_n $.
-Note that $ E(\mathbf 1_1)_0 $ is given by $ \{ a : A \mid (\lambda x_2, x_1 c_2) \bullet a = a \} $.
-Therefore, we have a bijection given by
-  \[ \epsilon(a) = (x_1 c_1) \bullet a \quad \text{and} \quad \epsilon^{-1}(a) = (\lambda x_2, x_1) \bullet a. \]
-  Now, to show that this is an isomorphism of $ \Lambda $-algebras, recall that $ \bullet: \R_A(U^n, U) \times \R_A(I, U)^n \to \R_A(U) $ is given by precomposition with the product morphism and that the $ \Lambda $-algebra structure on $ E(\mathbf 1_1)_0 $ is given by the embedding $ f \mapsto \iota_\Lambda(f) \bullet_A () $ of $ \Lambda $ into $ E(\mathbf 1_1)_0 $.
-We have for all $ f: \Lambda_n $, and all $ a : E(\mathbf 1_1)_0^n $,
-  \begin{align*}
-    \epsilon(f \bullet_{E(\mathbf 1_1)} a)
-    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_1, \dots, a_n \rangle)(c_n)\\
-    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1 c_n), x_2 c_n), \dots), x_n c_n)) \bullet_A a\\
-    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1), x_2), \dots), x_n)) \bullet_A (\epsilon(a_i))_i,
-  \end{align*}
-  writing $ \bar x_n $ for $ ((\dots((c_n, x_1), x_2), \dots), x_n) $, and leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $,
-  \[ \iota_\Lambda(f) \bar x_n = f. \]
-  We will do this by structural induction on $ f $.
-  \begin{itemize}
-    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i} $, and
-      \[ (\pi_2 \circ \pi_1 \circ \dots \circ \pi_1) \bar x_n = x_{n, i}. \]
-    \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
-      \[ \iota_\Lambda(f) = (\lambda x_1 x_2, \iota_{0, 2}(\iota_\Lambda(g)) (x_1, x_2)), \]
-      and if the induction hypothesis holds for $ g $, then
-      \begin{align*}
-        \iota_\Lambda(f) \bar x_n
-        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) \bar x_n\\
-        &= \lambda x_{n + 1}, \iota_\Lambda(g) (\bar x_n, x_{n + 1})\\
-        &= \lambda x_{n + 1}, g.
-      \end{align*}
-    \item Recall that application in a $ \lambda $-theory is given by $ g_1 g_2 = \rho(g_1) \bullet (x_1, \dots, x_n, g_2) $. Now, if $ f = g_1 g_2 $ for $ g_1, g_2 : \Lambda_{n + 1} $, we have
+  By the reasoning set forth in Lemma \ref{lem:elementary-faithful}, we only need to check $ \bar F_0 $. Given $ s : \RAct{A_1}(I, U_A) $, we have
+  \[ \bar F_0(s) = \gamma^{-1} \cdot F_*(s) \cdot \beta: \RAct{A_1}(I, U_A) \]
+  for $ \gamma: F_*(I) \cong I $ and $ \beta: F_*(U_A) \cong U_A $. Then
   \[
-        \iota_\Lambda(f)
-        = (\lambda x_1, \iota_\Lambda(g_1) (\pi_1 x_1) (\pi_2 x_1)) \circ \langle \id{U^n}, \iota_\Lambda(g_2) \rangle
-        = \lambda x_1, \iota_\Lambda(g_1) x_1 (\iota_\Lambda(g_2) x_1),
+    \bar{\id A}(s)(\star) = s(\star) \circ ((\lambda x_1 x_2, x_2) \bullet ()) = s(\star \circ ((\lambda x_1 x_2, x_2) \bullet ())),
   \]
-      and if the induction hypothesis holds for $ g_1 $ and $ g_2 $, then
-      \begin{align*}
-        \iota_\Lambda(f) \bar x_n
-        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) \bar x_n\\
-        &= \iota_\Lambda(g_1) \bar x_n (\iota_\Lambda(g_2) \bar x_n)\\
-        &= g_1 g_2.
-      \end{align*}
-  \end{itemize}
-\end{proof}
-
-Hyland shows the same fact in a slightly higher-level way.
-
-For his proof, we already need the unit of the adjunction. The quest for this counit boils down to a version of Scott's representation theorem.
-\begin{lemma}
-  For a $ \lambda $-theory $ L $, we can define an (iso)morphism
-  \[ \eta: \LamTh(L, E(U_{L_0})). \]
-\end{lemma}
-\begin{proof}
-  Note that for $ \R $ the category of retracts of $ L $,
-  \[ \mathbf R \xrightarrow \sim \mathbf R_{L_0} \xrightarrow{Y} P \R_{L_0} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1} \]
-  is a fully faithful functor that preserves finite products and exponential objects, and that $ U_{L_0} $ is the image of $ U = (\lambda x_1, x_1) $ under this embedding, so we have an isomorphism $ E(U) \cong E(U_{L_0}) $.
-Then $ \eta $ arises by composing this with the isomorphism from Scott's representation theorem (Theorem \ref{thm:Scott})
-  \[ \eta: L \xrightarrow \sim E(U) \xrightarrow \sim E(U_{L_0}). \]
-  Note that on the terms without free variables, this becomes
-  \[ \eta_0:
-    L_0
-      \xrightarrow{f \mapsto (\lambda x_1, \iota_{0, 1}(f))}
-    \R(I, U)
-      \xrightarrow{f \mapsto (I \mapsto f)}
-    \RAct{(L_0)_1}(\{I\}, (L_0)_1),
-  \]
-  so $ \eta_0(f) = (I \mapsto (\lambda x_1, \iota_{0, 1}(f))) $.
-\end{proof}
-
-Alternatively, we can use Hyland's version of the representation theorem:
-\begin{lemma}
-  For a $ \lambda $-theory $ L $, we can define an (iso)morphism
-  \[ \eta: \LamTh(L, E(U_{L_0})). \]
-\end{lemma}
-\begin{proof}
-  Note that we have a chain of equivalences (Lemma \ref{lem:equivalent-presheaf-cats} and Remark \ref{rem:ract-presheaf-equivalence})
-  \[ \Pshf L \xrightarrow \sim P \mathbf L \xrightarrow \sim P C_{L_1} \xrightarrow \sim \RAct{L_1} \xrightarrow \sim \RAct{{L_0}_1} \]
-  and $ U_{L_0} $ is isomorphic to the image of the theory presheaf $ L $ under this equivalence.
-Then $ \eta $ arises by combining this with the isomorphism from Scott's representation theorem (Theorem \ref{thm:representation-theorem})
-  \[ \eta: L \xrightarrow \sim E(L) \xrightarrow \sim E(U_{L_0}). \]
-  Note that on the terms without free variables, this becomes
-  \[ \eta_0:
-    L_0
-      \xrightarrow{f \mapsto (\star \mapsto \iota_{0, n}(f))_n}
-    \Pshf L(I, L)
-      \xrightarrow{F \mapsto (\star \mapsto (\lambda x_1, F_1(\star)))}
-    \RAct{(L_0)_1}(\{\star\}, (L_0)_1),
-  \]
-  so $ \eta_0(f) = (\star \mapsto (\lambda x_1, \iota_{0, 1}(f))) $, which luckily coincides with the $ \eta_0 $ given above.
+  so $ \bar{\id A}_0(s) = s $ and we can conclude that $ \bar{\id A} = \id{E(U_A)} $.
 \end{proof}
@@
 \begin{lemma}
-  We have a bijection $ \epsilon_A : E(U_A)_0 \cong A $, sending $ s $ to $ x_1 (\lambda x_2, x_2) \bullet (s(\star)) $.
+  For $ F : \Alg{\Lambda}(A, B) $ and $ G: \Alg{\Lambda}(B, C) $, we have $ \bar F \cdot \bar G = \overline{F \cdot G} $.
 \end{lemma}
 \begin{proof}
-  In Lemma \ref{lem:global-action-elements}, we showed that $ E(U_A)_0 $ corresponds to the set of $ A_1 $-equivariant elements of $ U_A $, sending $ s $ to $ s(\star) $.
-Now, for an $ A_1 $-equivariant element $ a $,
-  \[ (\lambda x_2, x_1 (\lambda x_3, x_3)) \bullet a = a \circ ((\lambda x_1 x_2, x_2) \bullet ()) = a \]
-  so we can send $ a $ to $ A $ as $ (x_1 (\lambda x_2, x_2)) \bullet a $ and it has (two-sided) inverse $ (\lambda x_2, x_1) \bullet a $.
+  Again, we only have to check at the terms without free variables. Given $ s : \RAct{A_1}(I, U_A) $, we have
+  \[ (\bar F \cdot \bar G)(s) = \gamma_G^{-1} \cdot G_*(\gamma_F^{-1} \cdot F_*(s) \cdot \beta_F) \cdot \beta_G: \RAct{C_1}(I, U_C) \]
+  for $ \gamma: F_*(I) \cong I $ and $ \beta: F_*(U_A) \cong U_A $. Then
+  \begin{align*}
+    (\bar F \cdot \bar G)(s)(\star)
+    &= G(F(s(\star)) \circ ((\lambda x_1 x_2, x_2) \bullet_B ())) \circ ((\lambda x_1 x_2, x_2) \bullet_C ())\\
+    &= G(F(s(\star \circ ((\lambda x_1 x_2, x_2) \bullet_A ()) \circ ((\lambda x_1 x_2, x_2) \bullet_A ()))))\\
+    &= G(F(s(\star)))\\
+    &= (F \cdot G)^{-1}(s(\star \circ ((\lambda x_1 x_2, x_2) \bullet_A ())))\\
+    &= \overline(F \cdot G)(s)(\star)
+  \end{align*}
+  so $ (\bar F \cdot \bar G)_0(s) = (\overline{F \cdot G})_0(s) $ and we can conclude that $ \bar F \cdot \bar G = \overline{F \cdot G} $.
 \end{proof}
+
+\begin{definition}
+  We get a functor from $ \Alg{\Lambda} $ to $ \LamTh $, sending objects $ A $ to $ E_{\RAct{A_1}}(U_A) $ and morphisms $ F: \Alg{\Lambda}(A, B) $ to $ \bar F: E(U_A) \to E(U_B) $.
+\end{definition}
+
+\begin{remark}
+  Note that for $ X : \R_A $, we have a natural isomorphism of sets with a right $ B_1 $-action
+  \[ \psi: \{ f : B \mid F(X) \circ f = f \} \xrightarrow \sim \{ f : A \mid X \circ f = f \} \times B_1 / \sim \]
+  given by
+  \[ \psi(f) = (X, f) \quad \text{and} \quad \psi^{-1}(f, b) = F(f) \circ b. \]
+  % which is $ B_1 $-equivariant and natural in $ X $.
+  % We have
+  % \[ \psi^{-1}(\psi(f)) = \psi^{-1}(X, f) = F(X) \circ f = f \]
+  % \[ \psi(\psi^{-1}(f, b)) = \psi(F(f) \circ b) = (X, F(f) \circ b) = (X \circ f, b) = (f, b) \]
+  % We need to show that this is natural in $ X $.
+Therefore, take $ g : \R_A(X, Y) $.
+Then $ \R_B(\mathbf 1_1, F(g)) $ is given by postcomposition with $ F(g) $.
+Also, $ F_*(\R_A(\mathbf 1_1, g)) $ is given by postcomposing with $ g $ on the component $ \R_A(\mathbf 1_1, g) $.
+Then
+  % \[ \psi(F(g) \circ f) = (Y, F(g) \circ f) = (Y \circ g, f) = (g \circ X, f) \]
+
+  Therefore, the following diagram $ 2 $-commutes:
+  \begin{center}
+    \begin{tikzcd}
+      \R_A \arrow[r, "F"] \arrow[d, "{\R_A(\mathbf 1_1, -)}"] & \R_B \arrow[d, "{\R_B(\mathbf 1_1, -)}"]\\
+      \RAct{A_1} \arrow[r, "F_*"] & \RAct{B_1}
+    \end{tikzcd}
+  \end{center}
+  Since $ F $ preserves all the structure of $ \R_A $, as do the embeddings of $ \R_A $ and $ \R_B $ into $ \RAct{A_1} $ and $ \RAct{B_1} $, one would expect $ F_* $ to preserves the structure of the full subcategory $ \R_A $ of $ \RAct{A_1} $, including $ U_A $, its finite products and their exponentials.
+This is another way to argue that $ \bar F $ is indeed a morphism of $ \lambda $-theories.
+\end{remark}
+
+\subsubsection{The unit}
+
+Definining the unit of the adjunction boils down to a version of Scott's representation theorem.
+
+\begin{lemma}
+  For a $ \lambda $-theory $ L $, we can define a $ \lambda $-theory isomorphism
+  \[ \eta: L \xrightarrow{\sim} E(U_{L_0}). \]
+\end{lemma}
+\begin{proof}
+  Recall from Remark \ref{rem:ract-presheaf-equivalence} that we have a chain of equivalences
+  \[ \Pshf L \xrightarrow \sim P \mathbf L \xrightarrow \sim P C_{L_1} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}. \]
+  It sends the presheaf $ L^n $ to the set $ L_1^n $ with a right action sending $ s: L_1^n $ and $ t: (L_0)_1 $ to $ (s_i \bullet_L \rho(t))_i : L_1^n $.
+We have an isomorphism $ s \mapsto (\lambda(s_i))_i: (L_1)^n \to U_{L_0} $, with inverse $ (\rho_i)_i : s \mapsto (\rho(s_i))_i $.
+
+  Then $ \eta $ arises by combining this with the isomorphism from Scott's representation theorem (Theorem \ref{thm:representation-theorem})
+  \[ \eta: L \xrightarrow \sim E_{\Pshf L}(L) \xrightarrow \sim E_{\RAct{{L_0}_1}}(U_{L_0}). \]
+  It is quite easy to work out that we can make this explicit as
+  \[ \eta_n:
+    L_n
+      \xrightarrow{f \mapsto ((s : \Pshf{L_m^n}) \mapsto f \bullet s)_m}
+    \Pshf L(L^n, L)
+      \xrightarrow{f \mapsto f_1}
+    \RAct{(L_0)_1}(L_1^n, L_1),
+      \xrightarrow{\lambda \circ - \circ (\rho_i)_i}
+    \RAct{(L_0)_1}(U_{L_0}^n, U_{L_0}),
+  \]
+  so $ \eta_n(f)(s) = \lambda(f \bullet (\rho(s_i))_i) $ for $ f: L_n $ and $ s: U_{L_0}^n $.
+\end{proof}
+
+\begin{remark}
+  Note that we can do the same with Scott's version of his representation theorem, using the chain of equivalences and an embedding
+  \[ \mathbf R \xrightarrow \sim \mathbf R_{L_0} \xrightarrow{Y} P \R_{L_0} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}, \]
+  Here, it is a bit harder to get an explicit formula for $ \eta $, because we need to do a bit more conversion between $ U_A^n $ and the image of $ U^n $ after the embedding $ \varphi: \mathbb R \hookrightarrow \RAct{{L_0}_1} $.
+If we quickly define $ \lambda $-terms
+  \[ \langle x_i \rangle_i = \langle x_1, \dots, x_n \rangle = \langle \langle \dots \langle (\lambda x_{n + 1} x_{n + 2}, x_{n + 2}), x_1 \rangle, \dots\rangle, x_n \rangle \]
+  and corresponding tuples $ (x_i)_i $ and projections $ \pi_i $, we have
+  \[ L_n \xrightarrow{f \mapsto \lambda(f \bullet (\pi_i x_1)_i)} \mathbb R(U^n, U) \xrightarrow{f \mapsto f \circ -} \RAct{{L_0}_1}(\varphi(U^n), U_{L_0}) \xrightarrow{(s \mapsto \langle s_i \rangle_i) \circ -} \RAct{{L_0}_1}(U_{L_0}^n, U_{L_0}).
+\]
+  and in the end, we obtain the very same explicit formula
+  \[ \eta_n(f)(s) = \iota_{0, n}(f)(x_i)_i \circ (\langle s_i \rangle_i) = \lambda(f \bullet (\rho(s_i))_i). \]
+\end{remark}
+
+\begin{lemma}
+  $ \eta $ is natural in $ L $.
+\end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}
+
+\subsubsection{The counit}
+
+\begin{definition}
+  For $ A : \Alg \Lambda $, we define a bijection $ \epsilon_A : E_{\RAct{A_1}}(U_A)_0 \cong A $ as
+  \[ \epsilon_A(s) = x_1 (\lambda x_2, x_2) \bullet (s(\star)) \quad \text{and} \quad \epsilon_A^{-1}(a)(\star) = (\lambda x_2, x_1) \bullet a. \]
+  These are inverses because $ s(\star) $ is $ A_1 $-equivariant (Lemma \ref{lem:global-action-elements}), and then
+  \[ (\lambda x_2, x_1 (\lambda x_3, x_3)) \bullet s(\star) = s(\star) \circ ((\lambda x_1 x_2, x_2) \bullet ()) = s(\star). \]
+\end{definition}
 
@@
 \begin{lemma}
-  For $ \epsilon_A $ as above, we have for all $ a, b: E(U_A)_0 $, we have
+  We have for all $ a, b: E(U_A)_0 $,
   \[ \epsilon_A((x_1 x_2) \bullet (a, b)) = (x_1 x_2) \bullet (\epsilon_A(a), \epsilon_A(b)). \]
@@
 \begin{proof}
-  For $ a, b: E(U_A)_0 $, we have, for the isomorphism $ \delta: \RAct{A_1}(U_A^{U_A}, A_2) $,
+  For $ a, b: E(U_A)_0 $, we have, using at some point the isomorphism $ \delta: \RAct{A_1}(U_A^{U_A}, A_2) $,
   \begin{align*}
@@
 \begin{lemma}\label{lem:counit-natural}
-  Let $ F: A \to B $ be a $ \Lambda $-algebra morphism. Then the following diagram commutes:
+  $ \epsilon $ is a natural transformation. I.e., for all $ F: \Alg{\Lambda}(A, B) $, the following diagram commutes:
   \begin{center}
     \begin{tikzcd}
-      E(U_A)_0 \arrow[d, "\epsilon_A"] \arrow[r, "\bar F_0"] & E(U_B)_0 \arrow[d, "\epsilon_A"]\\
-      A \arrow[r, "f"] & B
+      E(U_A)_0 \arrow[d, "\epsilon_A"] \arrow[r, "\bar F_0"] & E(U_B)_0 \arrow[d, "\epsilon_B"]\\
+      A \arrow[r, "F"] & B
     \end{tikzcd}
@@
 \begin{lemma}
-  For $ \epsilon_A $ as above, we have for all $ s: \Lambda_0 $,
+  We have for all $ s: \Lambda_0 $,
   \[ \epsilon_A(s \bullet ()) = s \bullet (). \]
@@
 \begin{proof}
-  Consider the following diagram, with $ F: \Alg \Lambda(\Lambda_0, A) $ given by $ s \mapsto s \bullet () $:
+  Consider the following diagram, with $ F: \Alg \Lambda(\Lambda_0, A) $ given by $ F(s) = s \bullet () $:
   \begin{center}
@@
       E(U_{\Lambda_0})_0
-        \arrow[r, "(\bar F)_0"]
+        \arrow[r, "\bar F_0"]
         \arrow[d, "\epsilon_{\Lambda_0}"]
@@
   \[ (x_1 (\lambda x_2, x_2)) \bullet (\lambda x_1, \iota_{0, 1}(s)) = s. \]
-  Recall that there exists a unique morphism $ \iota_\Lambda: \LamTh(\Lambda, E(U_A)) $, and that for all $ s: \Lambda_0 $, $ s \bullet () = \iota_\Lambda(s) \bullet () = \iota_\Lambda(s) $.
+  Recall that there exists a unique morphism $ \iota_\Lambda: \LamTh(\Lambda, E(U_A)) $, and that for all $ s: \Lambda_0 $, by definition $ s \bullet_{E(U_A)_0} () = \iota_\Lambda(s) \bullet_{E(U_A)} () = \iota_\Lambda(s) $.
 Since we have $ \eta \cdot \bar F : \LamTh(\Lambda, E(U_A)) $, we must have $ \iota_\Lambda = \eta \cdot \bar F $ and
@@
 
-\subsection{Fully faithful}
+\subsubsection{The equivalence}
 
-\TODO
+Now, Hyland leaves the following implicit:
+\begin{lemma}
+  $ \epsilon $ and $ \eta $ satisfy the zigzag identities.
+\end{lemma}
+\begin{proof}
 
-\subsection{Adjoint equivalence}
+\end{proof}
 
+Finally, we can state the fundamental theorem of the $ \lambda $-calculus:
 \begin{theorem}
-  There exists an adjoint equivalence between the category of $ \lambda $-theories, and the category of algebras of $ \Lambda $.
+  There is an adjoint equivalence $ \LamTh \cong \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
 \end{theorem}
-\begin{proof}
-  We will show that the functor $ L \mapsto L_0 $ is an equivalence of categories.
-
-  It is essentially surjective, because $ L $ is isomorphic \TODO to $ E(U_A) $.
-
-  Now, given morphisms $ f, f^\prime: L \to L^\prime $. Suppose that $ f_0 = f^\prime_0 $. Suppose that $ L $ and $ L^\prime $ have $ \beta $-equality. Then, given $ l: L_n $, we have
-  \[ f_n(l) = \rho^n(\lambda^n(f_n(l))) = \rho^n(f_0(\lambda^n(l))) = \rho^n(f^\prime_0(\lambda^n(l))) = \rho^n(\lambda^n(f^\prime_n(l))) = f^\prime_n(l), \]
-  so the functor is faithful.
-
-  The functor is full because a $ \Lambda $-algebra morphism $ f: A \to A^\prime $ induces a functor $ f^*: \RAct{A^\prime} \to \RAct{A} $, and via left Kan extension we get a left adjoint $ f^*: \RAct{A} \to \RAct{A^\prime} $ with $ f^*(A_1) \cong A^\prime_1 $.
-Now, $ f^* $ preserves (finite) products, so we have maps $ \RAct{A}(A_1^n, A_1) \to \RAct{A^\prime}((A^\prime_1)^n, A^\prime_1) $ and so a map $ E(U_A) \to E(U_{A^\prime}) $.
-This map, when restricted to a map $ \RAct{A}(1, A_1) \to \RAct{A^\prime}(1, A_1) $, and transported along the isomorphism $ a \mapsto a I $ \TODO, is equal to $ f $ \TODO.
-\end{proof}
 

### 2024-05-24 report/chapters/univalent-foundations.tex
Write almost the full proof of Hyland

@@
 Lastly, a result about univalent categories that we will use a couple of times in this thesis:
-\begin{lemma}
+\begin{lemma}\label{lem:univalen-category-equivalence}
   For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is a weak equivalence' are equivalent propositions (see \ref{sec:homotopy-props-sets}).

### 2024-05-24 report/chapters/paper.tex
Show the zigzag identity

@@
   For a $ \lambda $-theory $ L $, we can define a $ \lambda $-theory isomorphism
-  \[ \eta: L \xrightarrow{\sim} E(U_{L_0}). \]
+  \[ \eta_L: L \xrightarrow{\sim} E(U_{L_0}). \]
 \end{lemma}
@@
 
-  Then $ \eta $ arises by combining this with the isomorphism from Scott's representation theorem (Theorem \ref{thm:representation-theorem})
-  \[ \eta: L \xrightarrow \sim E_{\Pshf L}(L) \xrightarrow \sim E_{\RAct{{L_0}_1}}(U_{L_0}). \]
-  It is quite easy to work out that we can make this explicit as
+  Then $ \eta_L $ arises by combining this with the isomorphism from Scott's representation theorem (Theorem \ref{thm:representation-theorem})
+  \[ \eta_L: L \xrightarrow \sim E_{\Pshf L}(L) \xrightarrow \sim E_{\RAct{{L_0}_1}}(U_{L_0}). \]
+  It is quite easy to work out that we can make this explicit as (dropping the $ L $ and just writing $ \eta_L $)
   \[ \eta_n:
@@
 \begin{lemma}
-  $ \eta $ is natural in $ L $.
+  $ \eta $ is natural in $ L $. That is, for all $ F: \LamTh(L, L^\prime) $, the following diagram commutes:
+  \begin{center}
+    \begin{tikzcd}
+      L \arrow[r, "F"] \arrow[d, "\eta_L"] & L^\prime \arrow[d, "\eta_{L^\prime}"]\\
+      E_{\RAct{{L_0}_1}}(U_{L_0}) \arrow[r, "\bar{F_0}"] & E_{\RAct{{L^\prime_0}_1}}(U_{L^\prime_0})
+    \end{tikzcd}
+  \end{center}
 \end{lemma}
 \begin{proof}
-  \TODO
+  We must show
+  \[ \eta_L \cdot \bar{F_0} = F \cdot \eta_{L^\prime}. \]
+  Note that for all $ s : L_0 $,
+  \begin{align*}
+    \bar{F_0}_0(\eta_L(s))
+    &= \gamma_{F_0}^{-1} \cdot {F_0}_*(\star \mapsto (\lambda x_1, \iota_{0, 1}(s))) \cdot \beta_F\\
+    &= \star \mapsto F_0(\lambda x_1, \iota_{0, 1}(s)) \circ ((\lambda x_1 x_2, x_2) \bullet ())\\
+    &= \star \mapsto (\lambda x_1, \iota_{0, 1}(F_0(s)))\\
+    &= \eta_{L^\prime}(F_0(s))
+  \end{align*}
+  and by Lemma \ref{lem:elementary-full}, this concludes the proof.
 \end{proof}
@@
 
+To show that $ \epsilon $ preserves the $ \Lambda $-definable constants, we first need to show two properties of $ \epsilon $ and $ \eta $:
 \begin{lemma}\label{lem:counit-natural}
-  $ \epsilon $ is a natural transformation. I.e., for all $ F: \Alg{\Lambda}(A, B) $, the following diagram commutes:
+  $ \epsilon $ is natural in $ A $. That is, for all $ F: \Alg{\Lambda}(A, B) $, the following diagram commutes:
   \begin{center}
@@
 
+\begin{lemma}\label{lem:zigzag}
+  $ \epsilon $ and $ \eta $ satisfy one of the zigzag identities.
+\end{lemma}
+\begin{proof}
+  In this case, the zigzag identity on $ L \mapsto L_0 $ boils down to the following diagram commuting for all $ L : \LamTh $:
+  \begin{center}
+    \begin{tikzcd}
+      L_0 \arrow[rr, "\id{L_0}"] \arrow[rd, "{\eta_L}_0"] & & L\\
+      & E(U_{L_0})_0 \arrow[ru, "\epsilon_{L_0}"]
+    \end{tikzcd}
+  \end{center}
+  Now, note that for all $ f : L_0 $,
+  \[
+    ({\eta_L}_0 \cdot \epsilon_{L_0})(f)
+    = (x_1 (\lambda x_2, x_2)) \bullet (\lambda x_1, \iota_{0, 1}(f))
+    = f,
+  \]
+  which shows that the diagram commutes.
+\end{proof}
+
+Now, finally, we are ready to show that $ \epsilon $ is an isomorphism of $ \Lambda $-algebras:
 \begin{lemma}
@@
   \end{center}
-  By Lemma \ref{lem:counit-natural}, the square commutes. Also, note that $ \eta_0 \cdot \epsilon_{\Lambda_0} $ sends $ s : \Lambda_0 $ to
-  \[ (x_1 (\lambda x_2, x_2)) \bullet (\lambda x_1, \iota_{0, 1}(s)) = s. \]
+  By Lemma \ref{lem:counit-natural}, the square commutes and by Lemma \ref{lem:zigzag}, we have $ \eta_0 \cdot \epsilon_{\Lambda_0} = \id{\Lambda_0} $.
+
   Recall that there exists a unique morphism $ \iota_\Lambda: \LamTh(\Lambda, E(U_A)) $, and that for all $ s: \Lambda_0 $, by definition $ s \bullet_{E(U_A)_0} () = \iota_\Lambda(s) \bullet_{E(U_A)} () = \iota_\Lambda(s) $.
@@
 
-Now, Hyland leaves the following implicit:
-\begin{lemma}
-  $ \epsilon $ and $ \eta $ satisfy the zigzag identities.
-\end{lemma}
-\begin{proof}
-
-\end{proof}
-
-Finally, we can state the fundamental theorem of the $ \lambda $-calculus:
+By Lemma 3.2 in \cite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
 \begin{theorem}

### 2024-05-27 report/chapters/paper.tex
Give an alternative proof of the representation theorem

@@
 
-\section{The `Fundamental Theorem' of the \texorpdfstring{$ \lambda $}{lambda}-calculus}
+\section{An elementary proof of the `Fundamental Theorem'}
 
 The final theorem that Hyland works towards in his paper constructs an equivalence between $ \lambda $-calculi and $ \Lambda $-algebras.
-First, we will give an elementary version of Hyland's proof.
-Then we will provide an expanded version of Hyland's proof.
-And afterwards we will show it in a third, somewhat unrelated way.
+In this section, we will provide an elementary proof of this theorem.
 
@@
 
-\subsection{An elementary version of Hyland's proof}
 We will use Lemma \ref{lem:univalen-category-equivalence}, by showing that $ L \mapsto L_0 $ is a weak equivalence.
@@
 
-\subsection{Hyland's proof}
+\section{Hyland's proof}
 
-\subsubsection{Terms of a \texorpdfstring{$ \Lambda $}{Lambda}-algebra}
+Hyland gives a more category theoretical proof. That means that there is more high-level intuition why things work the way they work, but on the flip side, there is a lot more details to check.
+
+\subsection{Terms of a \texorpdfstring{$ \Lambda $}{Lambda}-algebra}
 
@@
 
-\subsubsection{Constructing a theory from an algebra}
+\subsection{Constructing a theory from an algebra}
 
@@
 
-\subsubsection{Constructing a theory morphism from an algebra morphism}
+\subsection{Constructing a theory morphism from an algebra morphism}
 
@@
 
-\subsubsection{The unit}
+\subsection{The unit}
 
@@
 
-\subsubsection{The counit}
+\subsection{The counit}
 
@@
 
-\subsubsection{The equivalence}
+\subsection{The equivalence}
 
@@
 
-\section{An alternative proof for the fundamental theorem}
+\begin{remark}
+  Hyland remarks that the isomorphism $ U_A^{U_A} \cong A_2 $ can be generalized to isomorphisms $ U_A^{U_A^n} \cong A_{n + 1} $.
+  \begin{align*}
+    \RAct{A_1}(U_A^n, U_A)
+    &\cong \RAct{A_1}(I, U_A^{U_A^n})\\
+    &\cong \RAct{A_1}(I, A_{n + 1})\\
+    &\cong \{ f : A_{n + 1} \mid \forall a : A_1, f \circ a = f \}\\
+    &\cong A_n.
+  \end{align*}
+  % In particular, we can pick $ a = \lambda x_1, x_1 (\lambda x_2, x_2) $. Then we have an isomorphism from this subset of $ A_{n + 1} $ to $ A_n $, given by
+  % \[ f \mapsto (x_1 (\lambda x_2, x_2)) \bullet f \quad \text{and} \quad g \mapsto (\lambda x_2, x_1) \bullet g. \]
+  Explicitly, we get an isomorphism $ \psi: \RAct{A_1}(U_A^n, U_A) \xrightarrow \sim A_n $, given by
+  \[ \psi(f) = (\lambda x_2 \dots x_{n + 1}, x_1 (x_2, \dots, x_{n + 1})) \bullet (f (\pi_1, \dots, \pi_n)) \]
+  and
+  \[ \psi^{-1}(g)(a_1, \dots, a_n) = (\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}) \dots (x_{n + 1} x_{n + 2})) \bullet (g, a_1, \dots, a_n). \]
+  Note that to show this, we need to use the $ A_1 $-equivariance of $ f $ at some point:
+  \begin{align*}
+    &f(\pi_2, \dots, \pi_{n + 1})((\lambda x_{n + 1}, x_{n + 1}), x_1, \dots, x_n)\\
+    &= (f(\pi_1, \dots, \pi_n) \circ \langle \pi_2, \dots, \pi_{n + 1} \rangle) ((\lambda x_{n + 2}, x_{n + 2}), x_1, \dots, x_n)\\
+    &= f(\pi_1, \dots, \pi_n) (x_1, \dots, x_n).\\
+  \end{align*}
+  This gives a $ \lambda $-theory structure on $ (A_n)_n $, with
+  \begin{align*}
+    y_{n, i} &= (\lambda x_1 \dots x_n, x_{n, i}) \bullet ();\\
+    f \bullet g &= (\lambda x_{m + 2} \dots x_{m + n + 1}, x_1 (x_2 x_{m + 2} \dots x_{m + n + 1}) \dots (x_{m + 1} x_{m + 2} \dots x_{m + n + 1})) \bullet (f, g_1, \dots, g_m);\\
+    \rho(f) &= \mathbf 1_m \circ f;\\
+    \lambda(h) &= f.
+  \end{align*}
+  for $ f: A_m $, $ g: A_n^m $ and $ h: A_{m + 1} $.
+
+  Then any $ F: \Alg \Lambda(A, B) $ gives functions $ F: A_n \to B_n $, and these give a $ \lambda $-theory morphism in $ \LamTh((A_n)_n, (B_n)_n) $.
+
+  The natural isomorphism $ \epsilon_A: A_0 \to A $ is just $ \id A $.
+Also, $ {\eta_L}_n : L_n \to (L_0)_n $ is given by $ \lambda^n $, with $ \rho^n $ as its inverse.
+The zigzag identities are trivial, so this gives another, very elemental proof of the fundamental theorem.
+  % \begin{align*}
+  %   \psi^{-1}(\psi(f))(b)
+  %   &= (\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}) \dots (x_{n + 1} x_{n + 2})) \bullet (\psi(f), b_1, \dots, b_n)\\
+  %   &= (\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}, \dots, x_{n + 1} x_{n + 2})) \bullet (f (\pi_1, \dots, \pi_n), b_1, \dots, b_n)\\
+  %   &= (x_1 \circ \langle x_2, \dots, x_{n + 1} \rangle) \bullet (f (\pi_1, \dots, \pi_n), b_1, \dots, b_n)\\
+  %   &= f (\pi_1, \dots, \pi_n) \circ \langle b_1, \dots, b_n \rangle\\
+  %   &= f (\pi_1 \circ \langle b_1, \dots, b_n \rangle, \dots, \pi_n \circ \langle b_1, \dots, b_n \rangle)\\
+  %   &= f (b_1, \dots, b_n).
+  % \end{align*}
+  % \begin{align*}
+  %   \psi(\psi^{-1}(g))
+  %   &= (\lambda x_2 \dots x_{n + 1}, x_1 (x_2, \dots, x_{n + 1})) \bullet ((\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}) \dots (x_{n + 1} x_{n + 2})) \bullet (g, \pi_1, \dots, \pi_n))\\
+  %   &= (\lambda x_2 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1}) \bullet g\\
+  %   &= g.
+  % \end{align*}
+\end{remark}
 

### 2024-05-28 report/src/alternative-definitions.tex
Change to the TU Delft PL template

--- 2024-04-25 report/chapters/alternative-definitions.tex
@@
 \begin{definition}
-  An \iindex{algebraic theory} as presented in \cite{algebaric-theories-2010} is a small category with finite products.
+  An \iindex{algebraic theory} as presented in \textcite{algebaric-theories-2010} is a small category with finite products.
 \end{definition}
@@
   \[ T(m) \times \prod_i T(n_i) \to T\left(\sum_i n_i\right), \]
-  written $ (f, g_1, \dots, g_m) \mapsto f[g_1, \dots, g_m] $, satisfying some identity, associativity and naturality conditions (see \cite{lambda-monoid}, Definition 2.1, for more details).
+  written $ (f, g_1, \dots, g_m) \mapsto f[g_1, \dots, g_m] $, satisfying some identity, associativity and naturality conditions (see \textcite{lambda-monoid}, Definition 2.1, for more details).
 \end{definition}
@@
   Note that for an adjunction $ F \dashv G $, $ F \bullet G $ gives a monad.
-In the same way, there exists a notion of \iindex{relative adjunction}, from which we can obtain a relative monad (see \cite{monads-endofunctors}, Theorem 2.10).
+In the same way, there exists a notion of \iindex{relative adjunction}, from which we can obtain a relative monad (see \textcite{monads-endofunctors}, Theorem 2.10).
 \end{remark}
@@
 \section{Monoid in a skew-monoidal category}
-For details and a general treatment, see \cite{monads-endofunctors}, Section 3 and specifically Theorem 3.4.
+For details and a general treatment, see \textcite{monads-endofunctors}, Section 3 and specifically Theorem 3.4.
 
@@
 \begin{definition}
-  Given a (skew-)monoidal category $ (C, \otimes, I) $, a \iindex{monoid} in this category is an object $ T : C $, together with a `multiplication' $ \mu: C(T \otimes T, T) $ and a `unit' morphism $ \eta: C(I, T) $ satisfying a couple of laws (see \cite{MacLane}, Section III.6).
+  Given a (skew-)monoidal category $ (C, \otimes, I) $, a \iindex{monoid} in this category is an object $ T : C $, together with a `multiplication' $ \mu: C(T \otimes T, T) $ and a `unit' morphism $ \eta: C(I, T) $ satisfying a couple of laws (see \textcite{MacLane}, Section III.6).
 \end{definition}

### 2024-05-28 report/src/category-theory.tex
Change to the TU Delft PL template

--- 2024-05-22 report/chapters/category-theory.tex
@@
 
-I will assume a familiarity with the category-theoretical concepts presented in \cite{CT4P}.
+I will assume a familiarity with the category-theoretical concepts presented in \textcite{CT4P}.
 These include categories, functors, isomorphisms, natural transformations, adjunctions, equivalences and limits.
@@
 
-One concept in category theory that can be used to describe a lot of limits and adjunctions is that of a universal arrow (see for example \cite{MacLane}, Part III)
+One concept in category theory that can be used to describe a lot of limits and adjunctions is that of a universal arrow (see for example \textcite{MacLane}, Part III)
 \begin{definition}
@@
 \begin{center}
-  \begin{tikzcd}[column sep = .5cm]
+  \begin{tikzcd}
     L \arrow[rd, "\eta \bullet L"'] \arrow[rr, "\id L"] & & L\\
@@
   \qquad
-  \begin{tikzcd}[column sep = .5cm]
+  \begin{tikzcd}
     R \arrow[rd, "R \bullet \eta"'] \arrow[rr, "\id R"] & & R\\
@@
 \end{center}
-commute.
+commute (these are called the \iindex{triangle identities} or \iindex{zigzag identities}).
 Here the natural transformation $ \eta \bullet L: L \bullet R \bullet L $ is the natural transformation $ \eta $ whiskered on the right by $ L $, and the other whiskered transformations are similar.
 
-An alternative characterization (see \cite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
+An alternative characterization (see \textcite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
 \[ \varphi: D(L(c), d) \xrightarrow{\sim} C(c, R(d)). \]
@@
 \begin{proof}
-  See \cite{MacLane}, Chapter IV.1, Theorem 2 (iv).
+  See \textcite{MacLane}, Chapter IV.1, Theorem 2 (iv).
 \end{proof}
@@
 \section{Yoneda}
-We can embed a category $ C $ fully faithfully into the functor category $ P C = [\op C, \SET] $ as follows (see \cite{Kashiwara}, Section 1.4):
+We can embed a category $ C $ fully faithfully into the functor category $ P C = [\op C, \SET] $ as follows (see \textcite{Kashiwara}, Section 1.4):
 \begin{definition}
@@
 \begin{proof}
-  See \cite{Kashiwara}, Proposition 1.4.3.
+  See \textcite{Kashiwara}, Proposition 1.4.3.
 \end{proof}
@@
 \begin{proof}
-  See \cite{borceux}, Volume 1, Proposition 2.15.5.
+  See \textcite{borceux}, Volume 1, Proposition 2.15.5.
 \end{proof}
@@
 \begin{lemma}
-  The Yoneda embedding functor preserves exponential objects (\cite{stackexchange:yoneda-exponentials}).
+  The Yoneda embedding functor preserves exponential objects (\textcite{stackexchange:yoneda-exponentials}).
 \end{lemma}
@@
 \begin{definition}
-  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ h: B(P(x), P(y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(x, y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \cite{nlab:grothendieck_fibration}
+  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ h: B(P(x), P(y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(x, y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \textcite{nlab:grothendieck_fibration}
   \begin{center}
-    \begin{tikzcd}[row sep = .5in]
+    \begin{tikzcd}[sep=large]
       E \arrow[d, "P"] &x \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar h"', dashed] & y \arrow[r, "f"'] & z\\
@@
   \begin{center}
-    \begin{tikzcd}[column sep=.5cm]
+    \begin{tikzcd}
       c^\prime \arrow[rr, "g"] \arrow[rd, "f"'] & & c^{\prime\prime} \arrow[ld, "f^\prime"]\\
@@
 \begin{proof}
-  See \cite{borceux}, Volume 3, Lemma 5.8.2. This lemma shows this via the following equivalences:
+  See \textcite{borceux}, Volume 3, Lemma 5.8.2. This lemma shows this via the following equivalences:
   \begin{align*}
@@
 \section{Dependent products and sums}\label{sec:dependent-products}
-The following is based loosely on Section 4.1 of \cite{taylor}.
+The following is based loosely on Section 4.1 of \textcite{taylor}.
 
@@
 \begin{proof}
-  See the end of Section 1.3 of \cite{freyd}.
+  See the end of Section 1.3 of \textcite{freyd}.
 \end{proof}
@@
 
-  By Proposition 1.34 in \cite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
+  By Proposition 1.34 in \textcite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
   \begin{center}
@@
 \section{Kan Extensions}
-One of the most general and abstract concepts in category theory is the concept of \textit{Kan extensions}. In \cite{MacLane}, Section X.7, MacLane notes that
+One of the most general and abstract concepts in category theory is the concept of \textit{Kan extensions}. In \textcite{MacLane}, Section X.7, MacLane notes that
 \begin{quote}
@@
   \begin{center}
-    \begin{tikzcd}[column sep=.5cm]
+    \begin{tikzcd}
       A \arrow[rr, "F"] \arrow[rd, dashed, "F_* G"'] & & B \arrow[ld, "G"]\\
       & C
-    \end{tikzcd} \hspace{2cm} \begin{tikzcd}[column sep=.5cm]
+    \end{tikzcd}
+    \qquad
+    \begin{tikzcd}
       A \arrow[rr, "F"] \arrow[rd, "G"'] & & B \arrow[ld, dashed, "\Lan F G"]\\
@@
 colimits), we can construct the right (resp.
-left) Kan extension in a `pointwise' fashion (see Theorem X.3.1 in \cite{MacLane} or Theorem 2.3.3 in \cite{Kashiwara}).
+left) Kan extension in a `pointwise' fashion (see Theorem X.3.1 in \textcite{MacLane} or Theorem 2.3.3 in \textcite{Kashiwara}).
 Below, I will outline the parts of the construction that we will need explicitly in this thesis.
@@
   \begin{center}
-    \begin{tikzcd}[column sep=.5cm]
+    \begin{tikzcd}
       F(a) \arrow[rr, "F(g)"] \arrow[rd, "f"'] & & F(a^\prime) \arrow[ld, "f^\prime"]\\
@@
   To show that $ \eta $ is a natural isomorphism, we have to show that $ \eta_G(a^\prime): G(a^\prime) \Rightarrow \Lan F G(F(a^\prime)) $ is an isomorphism for all $ G: [A, C] $ and $ a^\prime: A $.
-Since a left adjoint is unique up to natural isomorphism (\cite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(a^\prime)) $ is given by
+Since a left adjoint is unique up to natural isomorphism (\textcite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(a^\prime)) $ is given by
   \[ \text{colim} ((F \downarrow F(a^\prime)) \to A \xrightarrow G C). \]
@@
 \begin{proof}
-  First of all, note that $ \hat C $ is univalent, since it is a presheaf category (see Theorem 4.5 in \cite{univalent-categories}).
+  First of all, note that $ \hat C $ is univalent, since it is a presheaf category (see Theorem 4.5 in \textcite{univalent-categories}).
 So we must show that we have a weak equivalence from $ \overline C $ to $ \hat C $.
@@
 This is the exponential object $ X^Y $, with the (universal) evaluation morphism $ X \times X^Y \to Y $ given by $ (x, \phi) \mapsto \phi(1, x) $.
+Explicitly, we get a natural isomorphism $ \psi: \RAct M(Z \times Y, X) \xrightarrow \sim \RAct M(Z, X^Y) $ given by
+  \[ \psi(f)(z)(m, y) = f(z m, y) \quad \text{and} \quad \psi^{-1}(g)(z, y) = g(z)(1, y). \]
 \end{proof}

### 2024-05-28 report/src/metadata.tex
Change to the TU Delft PL template

% !TEX root = document.tex

\title{Universal algebra and the \texorpdfstring{$ \lambda $}{lambda}-calculus}
\subtitle{Version of \today}
%\subtitle{Master's Thesis}
\author{Arnoud van der Leer}
\authoremail{\url{a.a.vanderleer@student.tudelft.nl}}
\birthplace{Leiderdorp, the Netherlands}
\studentid{4485890}
\coverpicture{
  \centerline{
    \Large
    \begin{tikzcd}[
      ampersand replacement=\&,
      sep=scriptsize
    ]
      \&
      C_{{L_0}_1} \arrow[dd, "Y" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] \& \& \& \R_{L_0} \arrow[dd, "Y" description, hook] \arrow[rd, "\sim" description, no head] \& \& \\
      \&
      \& C_{L_1} \arrow[dd, "Y" description, hook] \arrow[r, hook] \& \mathbf L \arrow[rr, hook] \arrow[dd, "Y" description, hook] \& \& \mathbf R \arrow[dd, "Y" description, hook] \arrow[rdd, hook] \& \\
      \RAct{{L_0}_1} \&
      P C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] \& \& \& P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] \& \& \\
      \&
      \& P C_{L_1} \& P \mathbf L \arrow[l, "\sim" description] \& \& P \R \arrow[ll, "\sim" description] \& \Pshf L \arrow[lll, "\sim" description, bend left]
    \end{tikzcd}
  }
}
\colophon{\noindent
  \copyright{} \the\year{} \: \theauthor. \\[1em]
  Cover picture: A 2-commutative diagram featuring categories that appear in this thesis.
}

### 2024-05-28 report/src/paper.tex
Change to the TU Delft PL template

--- 2024-05-27 report/chapters/paper.tex
@@
   By Scott's representation theorem, we have $ \varphi_n: \R(U^n, U) \xrightarrow \sim L_n, $ given by
-  \[ \varphi_n(f) = \iota_{0, n}(f) ((((c, x_1), x_2), \dots), x_n). \]
+  \[ \varphi_n(f) = \iota_{0, n}(f) (x_i)_i. \]
   Restricting this equivalence to the morphisms to $ A $ yields
@@
 
-Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \cite{borceux}, Volume 3).
+Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \textcite{borceux}, Volume 3).
 Therefore, for a morphism $ f: \Pshf L(Y, X) $, we have adjunctions
@@
   \begin{center}
-    \begin{tikzcd}[column sep = .5in, row sep = .5in]
+    \begin{tikzcd}[sep=large]
       (\R \downarrow_D X)
@@
 
-  However, as mentioned in \cite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \cite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
+  However, as mentioned in \textcite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \textcite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
 
@@
     \epsilon(f \bullet_{E(U)} a)
-    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_1, \dots, a_n \rangle)(c_n)\\
-    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1 c_n), x_2 c_n), \dots), x_n c_n)) \bullet_A a\\
-    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1), x_2), \dots), x_n)) \bullet_A (\epsilon(a_i))_i,
+    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_i \rangle_i)(c_n)\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) (x_i c_n)_i) \bullet_A a\\
+    &= (\iota_{0, n}(\iota_\Lambda(f)) (x_i)_i) \bullet_A (\epsilon(a_i))_i,
   \end{align*}
   and we want this to equal $ f \bullet_A (\epsilon(a_i))_i $.
-Writing $ \bar x_n $ for $ ((\dots((c_n, x_1), x_2), \dots), x_n) $, and leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $, we have $ \iota_\Lambda(f) \bar x_n = f $.
+Leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $, we have $ \iota_\Lambda(f) (x_i)_i = f $.
 We will do this by structural induction on $ f $.
   \begin{itemize}
-    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i} $, and
-      \[ \iota_\Lambda(f) \bar x_n = (\pi_2 \circ \pi_1 \circ \dots \circ \pi_1) \bar x_n = x_{n, i}. \]
+    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_{n, i} $, and
+      \[ \iota_\Lambda(f) (x_i)_i = \pi_{n, i} (x_{n, i})_i = x_{n, i}. \]
     \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
@@
       \begin{align*}
-        \iota_\Lambda(f) \bar x_n
-        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) \bar x_n\\
-        &= \lambda x_{n + 1}, \iota_\Lambda(g) (\bar x_n, x_{n + 1})\\
+        \iota_\Lambda(f) (x_i)_i
+        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) (x_i)_i\\
+        &= \lambda x_{n + 1}, \iota_\Lambda(g) ((x_i)_i, x_{n + 1})\\
         &= \lambda x_{n + 1}, g.
@@
       \begin{align*}
-        \iota_\Lambda(f) \bar x_n
-        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) \bar x_n\\
-        &= \iota_\Lambda(g_1) \bar x_n (\iota_\Lambda(g_2) \bar x_n)\\
+        \iota_\Lambda(f) (x_i)_i
+        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) (x_i)_i\\
+        &= \iota_\Lambda(g_1) (x_i)_i (\iota_\Lambda(g_2) (x_i)_i)\\
         &= g_1 g_2.
@@
 Recall that $ \circ $, the categories $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given using $ f \bullet (a_1, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $.
-Since we have $ F(f \bullet (a_1, \dots, a_n)) = f \bullet (F(a_1), \dots, F(a_n)) $, $ F $ gives a functor $ F: \R_A \to \R_B $, such that
+Since we have $ F(f \bullet (a_i)_i) = f \bullet (F(a_i)) $, $ F $ gives a functor $ F: \R_A \to \R_B $, such that
 \[ F(I) = I, F(U) = U, F(A \times B) = F(A) \times F(B) \quad \text{and} \quad F(A^B) = F(A)^{F(B)}, \]
@@
 
-By Lemma 3.2 in \cite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
+By Lemma 3.2 in \textcite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
 \begin{theorem}
@@
   The natural isomorphism $ \epsilon_A: A_0 \to A $ is just $ \id A $.
+Note that, even though $ A_0 = A $ as sets, their $ \Lambda $-algebra structures are defined differently, so it takes some work to show that $ \epsilon_A $ is a $ \Lambda $-algebra morphism.
 Also, $ {\eta_L}_n : L_n \to (L_0)_n $ is given by $ \lambda^n $, with $ \rho^n $ as its inverse.

### 2024-05-28 report/src/previous-work.tex
Change to the TU Delft PL template

--- 2024-05-16 report/chapters/previous-work.tex
@@
 \section{The correspondence between categories and typed \texorpdfstring{$ \lambda $}{lambda}-calculi}\label{sec:lambek-correspondence}
-In \cite{curry}, page 413, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
+In \textcite{curry}, page 413, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
 
@@
 Also, note that by replacing the $ x_i $ by $ x_{n + i} $ and the $ \iota_{0, 1}(a_i) $ by $ \iota_{n, 1}(a_i) $, we obtain definitions not only for elements of $ L_0 $, but for all $ L_n $.
+
+Later on, we will need not only pairs and their projects, but also $ n $-tuples with projections. Therefore, we define
+\begin{align*}
+  (a_i)_i = (a_1, \dots, a_n) &= ((\dots((c, a_1), a_2), \dots), a_n);\\
+  \langle a_i \rangle_i = \langle a_1, \dots, a_n \rangle &= \langle\langle\dots\langle\langle c, a_1\rangle, a_2\rangle, \dots\rangle, a_n\rangle;\\
+  \pi_{n, i} &= \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i}
+\end{align*}
+for some constant $ c $, which usually is someting like $ \lambda x_{n + 1}, x_{n + 1} $.
 
@@
 
-Taylor notes (\cite{taylor}, Section 1.5) that the objects in $ \R $ have very strong properties with respect to fixpoints.
-One of the properties also arises via Lawvere's fixed point theorem (\cite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint.
+Taylor notes (\textcite{taylor}, Section 1.5) that the objects in $ \R $ have very strong properties with respect to fixpoints.
+One of the properties also arises via Lawvere's fixed point theorem (\textcite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint.
 That is, there exists $ s: I \to B $ such that $ f \circ s = s $.
@@
 
-From this, Taylor deduces (\cite{taylor}, \S 1.5.12) that $ \R $ does not have all coproducts if $ L $ is nontrivial, because suppose that $ \R $ has all coproducts.
+From this, Taylor deduces (\textcite{taylor}, \S 1.5.12) that $ \R $ does not have all coproducts if $ L $ is nontrivial, because suppose that $ \R $ has all coproducts.
 Then $ B = I + I $ is a `boolean algebra object': We define $ \bot, \top: I \to B $ to be the injections on the left and right components.
@@
 \begin{center}
-  \begin{tikzcd}[row sep = .3in]
+  \begin{tikzcd}[sep=large]
     I \arrow[r, "\bot"] \arrow[rd, "\top"'] & I + I \arrow[d, dashed, "{[\top, \bot]}"description] & I \arrow[l, "\top"'] \arrow[ld, "\bot"]\\
@@
   \end{tikzcd}
-  % \begin{tikzcd}[row sep = .3in]
+  % \begin{tikzcd}[sep=large]
   %   I \arrow[rrrd, "\bot"'] \arrow[r, "\bot"] & I + I \arrow[rrd, "{[\bot, \bot]}" description, dashed] \arrow[rr, bend left] & I \arrow[rd, "\bot"] \arrow[l, "\top"'] & I + I + I + I \arrow[d, dashed, "{[[\bot, \bot], [\bot, \top]]}" description] & I \arrow[ld, "\bot"'] \arrow[r, "\bot"] & I + I \arrow[lld, "{[\bot, \top]}" description, dashed] \arrow[ll, bend right] & I \arrow[llld, "\top"] \arrow[l, "\top"'] \\
@@
 \begin{center}
-  \begin{tikzcd}[column sep = .5in]
+  \begin{tikzcd}[sep=large]
     B \arrow[rd, "{\id B}"] \arrow[r, "{\langle \id B, \id B \rangle}"] & B \times B \arrow[d, "\land"]\\
@@
   \end{tikzcd}
-  \begin{tikzcd}[column sep = .5in]
+  \begin{tikzcd}[sep=large]
     B \arrow[d, "!"] \arrow[r, "{\langle \lnot, \id B \rangle}"] & B \times B \arrow[d, "\land"]\\
@@
 
-  During the 1960s, computer scientists sought for nontrivial examples of reflexive objects, there is a quote by Dana Scott that ``Lambda-calculus has no mathematical models!''\cite{strachey}.
+  During the 1960s, computer scientists sought for nontrivial examples of reflexive objects, there is a quote by Dana Scott that ``Lambda-calculus has no mathematical models!''\textcite{strachey}.
 However, in 1969, the same Dana Scott discovered that the category of (continuous) lattices with (Scott-)continuous functions between them has a nontrivial reflexive object, with the retraction onto the function spaces being even an isomorphism.
-Such a reflexive object $ D_\infty $ is obtained by starting with an arbitrary lattice $ D_0 $, iteratively taking $ D_{n + 1} = D_n^{D_n} $, with a retraction (in the `wrong' direction) $ r: D_n^{D_n} \to D_n $, and then passing to the limit $ D_\infty = \lim_{\leftarrow} D_n $ (for the main result, see Theorem 4.4 in \cite{scott-continuous}, page 127).
+Such a reflexive object $ D_\infty $ is obtained by starting with an arbitrary lattice $ D_0 $, iteratively taking $ D_{n + 1} = D_n^{D_n} $, with a retraction (in the `wrong' direction) $ r: D_n^{D_n} \to D_n $, and then passing to the limit $ D_\infty = \lim_{\leftarrow} D_n $ (for the main result, see Theorem 4.4 in \textcite{scott-continuous}, page 127).
 \end{remark}
@@
 Since Lambek showed an equivalence between simply typed $ \lambda $-calculi and cartesian closed categories, and since we have a construction for an untyped $ \lambda $-calculus from a cartesian closed category with a reflexive object, we can wonder whether this construction constitutes contitutes an equivalence between untyped $ \lambda $-calculi and some class of categories.
-This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \cite{curry}, page 418).
-\begin{theorem}
+This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \textcite{curry}, page 418).
+\begin{theorem}\label{thm:Scott}
   We can obtain every untyped $ \lambda $-calculus as the endomorphism theory of some object in some category.
@@
 
-  We have $ E(U)_n = \R(U^n, U) = \{ f: L_0 \mid U \circ f \circ U^n = f \} $. The variables of $ E(U) $ are the projections of $ U^n $:
-  \[ q_{n, i} = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i}. \]
+  We have $ E(U)_n = \R(U^n, U) = \{ f: L_0 \mid U \circ f \circ U^n = f \} $.
+The variables of $ E(U) $ are the projections $ \pi_{n, i} $ of $ U^n $.
 The substitution is given by composition with the product morphism:
@@
   We can extend this to any $ n $, by reducing any term to a constant by repeatedly using $ \lambda $, then applying the bijection, and then lifting it again using $ \rho $. Explicitly, we obtain
-  \[ \psi_n(f) = \iota_{0, n}(f) ((((\lambda x_{n+1}, x_{n+1}), x_1), \dots), x_n), \quad \text{and} \quad \psi^{-1}_n(g) = \lambda x_1, g \bullet (q_i x_1)_i. \]
+  \[ \psi_n(f) = \iota_{0, n}(f)(x_i)_i, \quad \text{and} \quad \psi^{-1}_n(g) = \lambda x_1, g \bullet (\pi_{n, i} x_1)_i. \]
   It is not hard to verify that this is indeed a bijection, using at one point the fact that $ f: \R(U^n, U) $ is defined by $ f \circ U^n = f $, for
-  \[ U^n = \lambda x_1, (((\lambda x_2, x_2), q_{n, 1} x_1 ), \dots, q_{n, n} x_1 ). \]
+  \[ U^n = \langle \pi_{n, i} \rangle_i. \]
   It is also pretty straightforward to check that
   \begin{align*}
-    \psi(q_{n, i}) &= x_i, & \psi(f) \bullet (\psi(g_i))_i &= \psi(f \bullet g),\\
+    \psi(\pi_{n, i}) &= x_i, & \psi(f) \bullet (\psi(g_i))_i &= \psi(f \bullet g),\\
     \psi(\lambda(h)) &= \lambda(\psi(h)), & \psi(\rho(h^\prime)) &= \rho(\psi(h^\prime))
@@
 \begin{proof}
-  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \cite{taylor}. It is also proved as Proposition 6 of \cite{theory-of-constructions}.
+  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \textcite{taylor}. It is also proved as Proposition 6 of \textcite{theory-of-constructions}.
 \end{proof}
@@
     \begin{center}
-      \begin{tikzcd}[column sep = .5in]
+      \begin{tikzcd}[sep=large]
         C \arrow[rrrd, bend left, "\gamma"] \arrow[dd, bend right=90, "\beta"'] \arrow[d, dashed, "{\lambda x_1, (\beta x_1, \pi_2 (\gamma x_1))}"] \\
@@
   However, note that we have a weak equivalence between strict categories (categories in which the type of objects is a homotopy set) $ \sum_A: \R^A \xrightarrow \sim (\R \downarrow_D A) $.
-If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (\cite{univalent-categories}, introduction, page 2 \TODO: maybe find a better reference for this) and then our pullback functor is given by
+If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (\textcite{univalent-categories}, introduction, page 2 \TODO: maybe find a better reference for this) and then our pullback functor is given by
   \[ \sum_A^{-1} \bullet (\alpha \cdot -) \bullet \sum_B, \]
@@
 
-This brings us to the main theorem of this section (\cite{taylor}, 5.1.8).
+This brings us to the main theorem of this section (\textcite{taylor}, 5.1.8).
 \begin{theorem}

### 2024-05-28 report/src/univalent-foundations.tex
Change to the TU Delft PL template

--- 2024-05-24 report/chapters/univalent-foundations.tex
@@
 So if we have types and elements, are types also elements of some type?
-This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system (see \cite{girard}).
+This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system (see \textcite{girard}).
 This is just like having a `set of all sets', which results in problematic questions like ``does its subset, containing only the sets which do not contain itself, contain itself?'' This is usually solved by either stating that types do not themselves have a type, or by assuming the existence of \textit{type universes} $ U_1, U_2, \dots $, such that every type is an element of some $ U_i $.
@@
 Univalent foundations seeks to be a foundation for mathematics that is in line with this principle.
-This is often done within the framework of `Martin-Löf dependent type theory', a type theory developed by Per Martin-Löf \cite{martin-lof-type-theory}.
+This is often done within the framework of `Martin-Löf dependent type theory', a type theory developed by Per Martin-Löf \textcite{martin-lof-type-theory}.
 It is a family of dependent type systems with dependent products, dependent sums, an empty type, a unit type and union types.
@@
 We construct this using path induction with the function that sends $ \mathrm{refl}: x = x $ to itself.
-For more information, see \cite{hottbook}, Section 1.12.1.
+For more information, see \textcite{hottbook}, Section 1.12.1.
 
@@
 Since bijections are not well-behaved for types that are not sets (see \ref{sec:homotopy-props-sets}), because in those cases, a function $ f: S \to T $ can have multiple distinct inverses.
-Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ (see \cite{hottbook}, Equation 2.4.10).
+Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ (see \textcite{hottbook}, Equation 2.4.10).
 However, intuitively we can still think of these as bijections.
@@
 \begin{proof}
-  See \cite{univalent-categories}, Theorem 8.5.
+  See \textcite{univalent-categories}, Theorem 8.5.
 \end{proof}
@@
 
-Also, Theorem 4.5 in \cite{univalent-categories} shows that if a category $ B $ is univalent (in the paper, categories are called `precategories` and univalent categories are just called `categories'), then the functor category $ A \rightarrow B $ is also univalent.
+Also, Theorem 4.5 in \textcite{univalent-categories} shows that if a category $ B $ is univalent (in the paper, categories are called `precategories` and univalent categories are just called `categories'), then the functor category $ A \rightarrow B $ is also univalent.
 In particular, the category of (pre)sheaves $ A \to \SET $ is univalent.
@@
 However, we will restrict our attention to the sub-2-category of univalent categories, which are the categories that we want to study.
-Then Theorem 6.8 in \cite{univalent-categories} shows that for univalent categories $ C $ and $ D $, there is an equivalence between $ C = D $ and $ C \simeq D $, where $ C \simeq D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
+Then Theorem 6.8 in \textcite{univalent-categories} shows that for univalent categories $ C $ and $ D $, there is an equivalence between $ C = D $ and $ C \simeq D $, where $ C \simeq D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
 
@@
 \begin{proof}
-  See \cite{univalent-categories}, Lemma 6.8.
+  See \textcite{univalent-categories}, Lemma 6.8.
 \end{proof}
@@
 \begin{definition}
-  For a type $ T $, a type $ \Vert T \Vert $ exists (\cite{hottbook}, Section 3.7) with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
+  For a type $ T $, a type $ \Vert T \Vert $ exists (\textcite{hottbook}, Section 3.7) with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
 It has a recursion principle stating that for a mere proposition $ B $, a function $ f: A \to B $ induces a function $ \vert f \vert: \Vert T \Vert \to B $ that commutes with $ \vert \cdot \vert $.
@@
   \begin{subfigure}{.3\textwidth}
-    \includesvg[pretex=\tiny, width=\columnwidth]{images/homotopy-plane}
+    \includesvg[pretex=\tiny, width=\columnwidth]{img/homotopy-plane}
     \caption{}
@@
   \begin{subfigure}{.3\textwidth}
-    \includesvg[pretex=\tiny, width=\columnwidth]{images/homotopy-cylinder}
+    \includesvg[pretex=\tiny, width=\columnwidth]{img/homotopy-cylinder}
     \caption{}
@@
   \begin{subfigure}{.3\textwidth}
-    \includesvg[pretex=\tiny, width=\columnwidth]{images/homotopy-sphere}
+    \includesvg[pretex=\tiny, width=\columnwidth]{img/homotopy-sphere}
     \caption{}
@@
 
-  For something to look like a circle or tube, we need this group $ x = x $ to be isomorphic to $ \mathbb Z $. For an example, see \cite{circle-fundamental-group}.
+  For something to look like a circle or tube, we need this group $ x = x $ to be isomorphic to $ \mathbb Z $. For an example, see \textcite{circle-fundamental-group}.
 \end{remark}
@@
   \begin{subfigure}{.45\textwidth}
-    \includesvg[pretex=\tiny, width=.7\columnwidth]{images/fibration}
+    \includesvg[pretex=\tiny, width=.7\columnwidth]{img/fibration}
     \caption{}
@@
   \begin{subfigure}{.45\textwidth}
-    \includesvg[pretex=\tiny, width=.7\columnwidth]{images/transport}
+    \includesvg[pretex=\tiny, width=.7\columnwidth]{img/transport}
     \caption{}

### 2024-05-28 report/src/alternative-definitions.tex
Improve citations, quotes, move dependencies and definitions to style file

--- 2024-04-25 report/chapters/alternative-definitions.tex
@@
 \begin{definition}
-  An \iindex{algebraic theory} as presented in \cite{algebaric-theories-2010} is a small category with finite products.
+  An \iindex{algebraic theory} as presented in \autocite{algebaric-theories-2010} is a small category with finite products.
 \end{definition}
@@
   \[ T(m) \times \prod_i T(n_i) \to T\left(\sum_i n_i\right), \]
-  written $ (f, g_1, \dots, g_m) \mapsto f[g_1, \dots, g_m] $, satisfying some identity, associativity and naturality conditions (see \cite{lambda-monoid}, Definition 2.1, for more details).
+  written $ (f, g_1, \dots, g_m) \mapsto f[g_1, \dots, g_m] $, satisfying some identity, associativity and naturality conditions (see \autocite{lambda-monoid}, Definition 2.1, for more details).
 \end{definition}
@@
   Note that for an adjunction $ F \dashv G $, $ F \bullet G $ gives a monad.
-In the same way, there exists a notion of \iindex{relative adjunction}, from which we can obtain a relative monad (see \cite{monads-endofunctors}, Theorem 2.10).
+In the same way, there exists a notion of \iindex{relative adjunction}, from which we can obtain a relative monad (see \autocite{monads-endofunctors}, Theorem 2.10).
 \end{remark}
@@
 \section{Monoid in a skew-monoidal category}
-For details and a general treatment, see \cite{monads-endofunctors}, Section 3 and specifically Theorem 3.4.
+For details and a general treatment, see \autocite{monads-endofunctors}, Section 3 and specifically Theorem 3.4.
 
@@
 \begin{definition}
-  Given a (skew-)monoidal category $ (C, \otimes, I) $, a \iindex{monoid} in this category is an object $ T : C $, together with a `multiplication' $ \mu: C(T \otimes T, T) $ and a `unit' morphism $ \eta: C(I, T) $ satisfying a couple of laws (see \cite{MacLane}, Section III.6).
+  Given a (skew-)monoidal category $ (C, \otimes, I) $, a \iindex{monoid} in this category is an object $ T : C $, together with a `multiplication' $ \mu: C(T \otimes T, T) $ and a `unit' morphism $ \eta: C(I, T) $ satisfying a couple of laws (see \autocite{MacLane}, Section III.6).
 \end{definition}

### 2024-05-28 report/src/category-theory.tex
Improve citations, quotes, move dependencies and definitions to style file

@@
 
-I will assume a familiarity with the category-theoretical concepts presented in \textcite{CT4P}.
+I will assume a familiarity with the category-theoretical concepts presented in \autocite{CT4P}.
 These include categories, functors, isomorphisms, natural transformations, adjunctions, equivalences and limits.
@@
 
-One concept in category theory that can be used to describe a lot of limits and adjunctions is that of a universal arrow (see for example \textcite{MacLane}, Part III)
+One concept in category theory that can be used to describe a lot of limits and adjunctions is that of a universal arrow (see for example \autocite{MacLane}, Part III)
 \begin{definition}
@@
 
-An alternative characterization (see \textcite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
+An alternative characterization (see \autocite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
 \[ \varphi: D(L(c), d) \xrightarrow{\sim} C(c, R(d)). \]
@@
 \begin{proof}
-  See \textcite{MacLane}, Chapter IV.1, Theorem 2 (iv).
+  See \autocite{MacLane}, Chapter IV.1, Theorem 2 (iv).
 \end{proof}
@@
 \section{Yoneda}
-We can embed a category $ C $ fully faithfully into the functor category $ P C = [\op C, \SET] $ as follows (see \textcite{Kashiwara}, Section 1.4):
+We can embed a category $ C $ fully faithfully into the functor category $ P C = [\op C, \SET] $ as follows (see \autocite{Kashiwara}, Section 1.4):
 \begin{definition}
@@
 \begin{proof}
-  See \textcite{Kashiwara}, Proposition 1.4.3.
+  See \autocite{Kashiwara}, Proposition 1.4.3.
 \end{proof}
@@
 \begin{proof}
-  See \textcite{borceux}, Volume 1, Proposition 2.15.5.
+  See \autocite{borceux}, Volume 1, Proposition 2.15.5.
 \end{proof}
@@
 \begin{lemma}
-  The Yoneda embedding functor preserves exponential objects (\textcite{stackexchange:yoneda-exponentials}).
+  The Yoneda embedding functor preserves exponential objects (\autocite{stackexchange:yoneda-exponentials}).
 \end{lemma}
@@
 \begin{definition}
-  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ h: B(P(x), P(y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(x, y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \textcite{nlab:grothendieck_fibration}
+  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ h: B(P(x), P(y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(x, y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \autocite{nlab:grothendieck_fibration}
   \begin{center}
@@
 \begin{proof}
-  See \textcite{borceux}, Volume 3, Lemma 5.8.2. This lemma shows this via the following equivalences:
+  See \autocite{borceux}, Volume 3, Lemma 5.8.2. This lemma shows this via the following equivalences:
   \begin{align*}
@@
 \section{Dependent products and sums}\label{sec:dependent-products}
-The following is based loosely on Section 4.1 of \textcite{taylor}.
+The following is based loosely on Section 4.1 of \autocite{taylor}.
 
@@
 \begin{proof}
-  See the end of Section 1.3 of \textcite{freyd}.
+  See the end of Section 1.3 of \autocite{freyd}.
 \end{proof}
@@
 
-  By Proposition 1.34 in \textcite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
+  By Proposition 1.34 in \autocite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
   \begin{center}
@@
 \section{Kan Extensions}
-One of the most general and abstract concepts in category theory is the concept of \textit{Kan extensions}. In \textcite{MacLane}, Section X.7, MacLane notes that
-\begin{quote}
-  The notion of Kan extensions subsumes all the other fundamental concepts of category theory.
-\end{quote}
+One of the most general and abstract concepts in category theory is the concept of \textit{Kan extensions}. In \autocite{MacLane}, Section X.7, MacLane notes that
+
+\enquote{The notion of Kan extensions subsumes all the other fundamental concepts of category theory.}
+
 In this thesis, we will use left Kan extension a handful of times. It comes in handy when we want to extend a functor along another functor in the following way:
@@
 colimits), we can construct the right (resp.
-left) Kan extension in a `pointwise' fashion (see Theorem X.3.1 in \textcite{MacLane} or Theorem 2.3.3 in \textcite{Kashiwara}).
+left) Kan extension in a `pointwise' fashion (see Theorem X.3.1 in \autocite{MacLane} or Theorem 2.3.3 in \autocite{Kashiwara}).
 Below, I will outline the parts of the construction that we will need explicitly in this thesis.
@@
   To show that $ \eta $ is a natural isomorphism, we have to show that $ \eta_G(a^\prime): G(a^\prime) \Rightarrow \Lan F G(F(a^\prime)) $ is an isomorphism for all $ G: [A, C] $ and $ a^\prime: A $.
-Since a left adjoint is unique up to natural isomorphism (\textcite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(a^\prime)) $ is given by
+Since a left adjoint is unique up to natural isomorphism (\autocite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(a^\prime)) $ is given by
   \[ \text{colim} ((F \downarrow F(a^\prime)) \to A \xrightarrow G C). \]
@@
 \begin{proof}
-  First of all, note that $ \hat C $ is univalent, since it is a presheaf category (see Theorem 4.5 in \textcite{univalent-categories}).
+  First of all, note that $ \hat C $ is univalent, since it is a presheaf category (see Theorem 4.5 in \autocite{univalent-categories}).
 So we must show that we have a weak equivalence from $ \overline C $ to $ \hat C $.

### 2024-05-28 report/src/paper.tex
Improve citations, quotes, move dependencies and definitions to style file

@@
 
-Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \textcite{borceux}, Volume 3).
+Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \autocite{borceux}, Volume 3).
 Therefore, for a morphism $ f: \Pshf L(Y, X) $, we have adjunctions
@@
 
-  However, as mentioned in \textcite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \textcite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
+  However, as mentioned in \autocite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \autocite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
 
@@
   However, showing that it is a $ \lambda $-theory morphism is a different matter. Hyland claims
-  \begin{quote}
-    $ F $ preserves $ \mathbf 1_n $, which determines the function space as a retract of the universal. So $ \bar F $ preserves the retract and the result follows.
-  \end{quote}
+
+  \enquote{$ F $ preserves $ \mathbf 1_n $, which determines the function space as a retract of the universal. So $ \bar F $ preserves the retract and the result follows.}
+
   Although this covers the core of the argument, it is very complicated to actually verify that this works, because we need to pass through a lot of isomorphisms, and check that they work nicely together:
@@
 
-By Lemma 3.2 in \textcite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
+By Lemma 3.2 in \autocite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
 \begin{theorem}

### 2024-05-28 report/src/previous-work.tex
Improve citations, quotes, move dependencies and definitions to style file

@@
 \section{The correspondence between categories and typed \texorpdfstring{$ \lambda $}{lambda}-calculi}\label{sec:lambek-correspondence}
-In \textcite{curry}, page 413, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
+In \autocite{curry}, page 413, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
 
@@
 
-Taylor notes (\textcite{taylor}, Section 1.5) that the objects in $ \R $ have very strong properties with respect to fixpoints.
-One of the properties also arises via Lawvere's fixed point theorem (\textcite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint.
+Taylor notes (\autocite{taylor}, Section 1.5) that the objects in $ \R $ have very strong properties with respect to fixpoints.
+One of the properties also arises via Lawvere's fixed point theorem (\autocite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint.
 That is, there exists $ s: I \to B $ such that $ f \circ s = s $.
@@
 
-From this, Taylor deduces (\textcite{taylor}, \S 1.5.12) that $ \R $ does not have all coproducts if $ L $ is nontrivial, because suppose that $ \R $ has all coproducts.
+From this, Taylor deduces (\autocite{taylor}, \S 1.5.12) that $ \R $ does not have all coproducts if $ L $ is nontrivial, because suppose that $ \R $ has all coproducts.
 Then $ B = I + I $ is a `boolean algebra object': We define $ \bot, \top: I \to B $ to be the injections on the left and right components.
@@
 
-  During the 1960s, computer scientists sought for nontrivial examples of reflexive objects, there is a quote by Dana Scott that ``Lambda-calculus has no mathematical models!''\textcite{strachey}.
+  During the 1960s, computer scientists sought for nontrivial examples of reflexive objects, there is a quote by Dana Scott that ``Lambda-calculus has no mathematical models!''\autocite{strachey}.
 However, in 1969, the same Dana Scott discovered that the category of (continuous) lattices with (Scott-)continuous functions between them has a nontrivial reflexive object, with the retraction onto the function spaces being even an isomorphism.
-Such a reflexive object $ D_\infty $ is obtained by starting with an arbitrary lattice $ D_0 $, iteratively taking $ D_{n + 1} = D_n^{D_n} $, with a retraction (in the `wrong' direction) $ r: D_n^{D_n} \to D_n $, and then passing to the limit $ D_\infty = \lim_{\leftarrow} D_n $ (for the main result, see Theorem 4.4 in \textcite{scott-continuous}, page 127).
+Such a reflexive object $ D_\infty $ is obtained by starting with an arbitrary lattice $ D_0 $, iteratively taking $ D_{n + 1} = D_n^{D_n} $, with a retraction (in the `wrong' direction) $ r: D_n^{D_n} \to D_n $, and then passing to the limit $ D_\infty = \lim_{\leftarrow} D_n $ (for the main result, see Theorem 4.4 in \autocite{scott-continuous}, page 127).
 \end{remark}
@@
 Since Lambek showed an equivalence between simply typed $ \lambda $-calculi and cartesian closed categories, and since we have a construction for an untyped $ \lambda $-calculus from a cartesian closed category with a reflexive object, we can wonder whether this construction constitutes contitutes an equivalence between untyped $ \lambda $-calculi and some class of categories.
-This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \textcite{curry}, page 418).
+This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \autocite{curry}, page 418).
 \begin{theorem}\label{thm:Scott}
@@
 \begin{proof}
-  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \textcite{taylor}. It is also proved as Proposition 6 of \textcite{theory-of-constructions}.
+  Taylor proves this in a series of lemmas leading up to \S 4.3.7 in \autocite{taylor}. It is also proved as Proposition 6 of \autocite{theory-of-constructions}.
 \end{proof}
@@
   However, note that we have a weak equivalence between strict categories (categories in which the type of objects is a homotopy set) $ \sum_A: \R^A \xrightarrow \sim (\R \downarrow_D A) $.
-If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (\textcite{univalent-categories}, introduction, page 2 \TODO: maybe find a better reference for this) and then our pullback functor is given by
+If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (\autocite{univalent-categories}, introduction, page 2 \TODO: maybe find a better reference for this) and then our pullback functor is given by
   \[ \sum_A^{-1} \bullet (\alpha \cdot -) \bullet \sum_B, \]
@@
 
-This brings us to the main theorem of this section (\textcite{taylor}, 5.1.8).
+This brings us to the main theorem of this section (\autocite{taylor}, 5.1.8).
 \begin{theorem}

### 2024-05-28 report/src/univalent-foundations.tex
Improve citations, quotes, move dependencies and definitions to style file

@@
 So if we have types and elements, are types also elements of some type?
-This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system (see \textcite{girard}).
+This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system (see \autocite{girard}).
 This is just like having a `set of all sets', which results in problematic questions like ``does its subset, containing only the sets which do not contain itself, contain itself?'' This is usually solved by either stating that types do not themselves have a type, or by assuming the existence of \textit{type universes} $ U_1, U_2, \dots $, such that every type is an element of some $ U_i $.
@@
 \section{The univalence principle}
-\begin{quote}
-  \textit{Isomorphic objects are equivalent.}
-\end{quote}
+\enquote{\textit{Isomorphic objects are equivalent.}}
+
 This principle is visible in most of mathematics: Sets with a bijection have the same number of elements, isomorphic groups have the same properties, and since the universal property of limits makes them ``unique up to unique isomorphism'', we can talk about `the' limit of some diagram in a category.
@@
 Now, the \iindex{univalence principle} takes this a step further. It states that
-\begin{quote}
-  \textit{Isomorphic objects are equal.}
-\end{quote}
+
+\enquote{\textit{Isomorphic objects are equal.}}
+
 Univalent foundations seeks to be a foundation for mathematics that is in line with this principle.
-This is often done within the framework of `Martin-Löf dependent type theory', a type theory developed by Per Martin-Löf \textcite{martin-lof-type-theory}.
+This is often done within the framework of `Martin-Löf dependent type theory', a type theory developed by Per Martin-Löf \autocite{martin-lof-type-theory}.
 It is a family of dependent type systems with dependent products, dependent sums, an empty type, a unit type and union types.
@@
 We construct this using path induction with the function that sends $ \mathrm{refl}: x = x $ to itself.
-For more information, see \textcite{hottbook}, Section 1.12.1.
+For more information, see \autocite{hottbook}, Section 1.12.1.
 
@@
 Since bijections are not well-behaved for types that are not sets (see \ref{sec:homotopy-props-sets}), because in those cases, a function $ f: S \to T $ can have multiple distinct inverses.
-Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ (see \textcite{hottbook}, Equation 2.4.10).
+Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ (see \autocite{hottbook}, Equation 2.4.10).
 However, intuitively we can still think of these as bijections.
@@
 using path induction with the identity isomorphism $ \prod_{c: C} \id c: (c \cong c) $. We can then formulate the univalence principle for categories as
-\begin{quote}
-  For all $ c, d : C $, $ \mathrm{idtoiso}_{c, d}: (c = d) \to (c \cong d) $ is an equivalence.
-\end{quote}
+
+\enquote{For all $ c, d : C $, $ \mathrm{idtoiso}_{c, d}: (c = d) \to (c \cong d) $ is an equivalence.}
+
 A category that adheres to the univalence principle is called a \iindex{univalent category}.
@@
 \begin{proof}
-  See \textcite{univalent-categories}, Theorem 8.5.
+  See \autocite{univalent-categories}, Theorem 8.5.
 \end{proof}
@@
 
-Also, Theorem 4.5 in \textcite{univalent-categories} shows that if a category $ B $ is univalent (in the paper, categories are called `precategories` and univalent categories are just called `categories'), then the functor category $ A \rightarrow B $ is also univalent.
+Also, Theorem 4.5 in \autocite{univalent-categories} shows that if a category $ B $ is univalent (in the paper, categories are called `precategories` and univalent categories are just called `categories'), then the functor category $ A \rightarrow B $ is also univalent.
 In particular, the category of (pre)sheaves $ A \to \SET $ is univalent.
@@
 However, we will restrict our attention to the sub-2-category of univalent categories, which are the categories that we want to study.
-Then Theorem 6.8 in \textcite{univalent-categories} shows that for univalent categories $ C $ and $ D $, there is an equivalence between $ C = D $ and $ C \simeq D $, where $ C \simeq D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
+Then Theorem 6.8 in \autocite{univalent-categories} shows that for univalent categories $ C $ and $ D $, there is an equivalence between $ C = D $ and $ C \simeq D $, where $ C \simeq D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
 
@@
 \begin{proof}
-  See \textcite{univalent-categories}, Lemma 6.8.
+  See \autocite{univalent-categories}, Lemma 6.8.
 \end{proof}
@@
 \begin{definition}
-  For a type $ T $, a type $ \Vert T \Vert $ exists (\textcite{hottbook}, Section 3.7) with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
+  For a type $ T $, a type $ \Vert T \Vert $ exists (\autocite{hottbook}, Section 3.7) with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
 It has a recursion principle stating that for a mere proposition $ B $, a function $ f: A \to B $ induces a function $ \vert f \vert: \Vert T \Vert \to B $ that commutes with $ \vert \cdot \vert $.
@@
 
-  For something to look like a circle or tube, we need this group $ x = x $ to be isomorphic to $ \mathbb Z $. For an example, see \textcite{circle-fundamental-group}.
+  For something to look like a circle or tube, we need this group $ x = x $ to be isomorphic to $ \mathbb Z $. For an example, see \autocite{circle-fundamental-group}.
 \end{remark}

### 2024-05-29 report/src/category-theory.tex
Define the theory of extensions

@@
 
+\section{Coends}\label{sec:coends}
+This section is based on Section 1.2 of \autocite{riehl}.
+
+In this thesis, we will encounter co-ends a couple of times, so we will introduce them here.
+\begin{definition}
+  Let $ C, D $ be categories and $ F : \op C \times C \to D $ a functor. We define the \iindex{coend} $ \int^{c : C} F(c, c) $ to be the colimit
+  \begin{center}
+    \begin{tikzcd}
+      \displaystyle\coprod_{\substack{f : C(a, b)}} F(b, a)
+        \arrow[r, shift left, "{F(f, \id b)}"]
+        \arrow[r, shift right, "{F(\id a, f)}"'] &
+      \displaystyle\coprod_{c : C} F(c, c)
+        \arrow[r, dashed] &
+      \int^C F
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+\begin{remark}
+  An alternative way to phrase this, is that $ \int^C F : D $ is an object, equipped with arrows $ F(c, c) \to \int^C F $ such that for all $ f: C(a, b) $, the following diagram must commute
+  \begin{center}
+    \begin{tikzcd}
+      F(b, a) \arrow[r, "{F(f, \id a)}"] \arrow[d, "{F(\id b, f)}"] & F(a, a) \arrow[d]\\
+      F(b, b) \arrow[r] & \int^C F
+    \end{tikzcd}
+  \end{center}
+  and such that for any other $ G : D $ with the same properties, we have a unique morphism $ \int_C F \to G $, making the triangles commute
+  \begin{center}
+    \begin{tikzcd}
+      F(c, c) \arrow[r] \arrow[rd] & \int_C F \arrow[d]\\
+      & G
+    \end{tikzcd}
+  \end{center}
+\end{remark}
+
+\begin{remark}
+  Of course, a co-end is actually the dual notion of an end, which can be defined as the equalizer of the diagram above, but with the arrows reversed.
+\end{remark}
+
+\begin{remark}
+  Left Kan extension can be expressed as a coend:
+  \[ \Lan F G(b) = \int^{a : A} D(F a, b) \cdot G a \]
+  where $ S \cdot X $ for $ S $ a set and $ X : C $ denotes the `copower'. In most cases, we will have
+  \[ S \cdot X = \coprod_{s : S} X. \]
+\end{remark}
+
 \section{The Karoubi envelope}

### 2024-05-29 report/src/paper.tex
Define the theory of extensions

@@
 
+The fundamental theorem of the $ \lambda $-calculus that Hyland shows is actually not of the form shown above.
+To get there, we first need to show that the category of $ T $-algebras for an algebraic theory $ T $ has coproducts, and define the `theory of extensions'.
+
+Let $ \llbracket n \rrbracket $ denote the finite set $ \{ 1, 2, \dots, n \} $.
+Let \index{$ \F $}$ \F \subseteq \FinSET $ be the full subcategory with $ \F_0 = \{ \llbracket 0 \rrbracket, \llbracket 1 \rrbracket, \dots \} $.
+
 \begin{lemma}
-  The category of $ T $-algebras has coproducts.
+  Let $ T $ be an algebraic theory. The category of $ T $-algebras has coproducts.
 \end{lemma}
 \begin{proof}
-  \TODO
+  This is shown in \autocite{algebaric-theories-2010}, in the lemmas leading up to Theorem 4.5.
+
+  Explicitly, we can express the coproduct of algebras, and especially its set, as the following coend (\autocite{Hyland}, Proposition 2.5) (see also Section \ref{sec:coends} for more on coends)
+  \[ A + B = \int^{(m, n) : \F \times \F} A^m \times B^n \times T_{m^\prime + n^\prime}, \]
+  considering $ T $ as a functor $ T : \F \to \SET $ as a functor (see Remark \ref{rem:abstract-clone-functor}).
+Note that we do not need the exact definition of $ A + B $ for the rest of this section.
+Nonetheless, it is interesting to see how it is defined and why this definition works.
+
+  One can think of $ A + B $ consisting of elements $ t \bullet (a + b) $ for $ t: T_{m + n} $, $ a : A^m $ and $ b: B^n $ (writing $ (a + b) $ for $ (a_1, \dots, a_m, b_1, \dots, b_n) $), `substituting' the $ a_i $ and $ b_j $ for the $ x_i $ and $ x_{m + j} $ in $ t $.
+
+  The relations then give `associativity' of this substitution and also assure that reordering or duplicating $ x_i $ and their corresponding $ a_i $ and $ b_j $ do not yield different elements: associating the images on the left and right of
+  \[ A^{m^\prime} \times B^{n^\prime} \times T_{m^\prime + n^\prime} \leftarrow A^{m^\prime} \times B^{n^\prime} \times T_{m + n} \rightarrow A^m \times B^n \times T_{m + n} \]
+  gives
+  \[ (t \bullet ((x_{f(i)})_i + (x_{m + g(j)})_j)) \bullet a + b = t \bullet ((a_{f(i)})_i + (b_{g(j)})_j) \]
+  for $ f: \llbracket m \rrbracket \to \llbracket m^\prime \rrbracket $, $ g: \llbracket n \rrbracket \to \llbracket n^\prime \rrbracket $, $ t : T_{m + n} $, $ a : A^{m^\prime} $ and $ b : B^{n^\prime} $.
+
+  Then it becomes clear what the action of $ T $ will be on $ A + B $, although the precise definition has quite a combinatorial nature.
+For $ s : T_l $, $ t_i : T_{m_i + n_i} $, $ a_i : A^{m_i} $ and $ b_i : B^{n_i} $, define the disjoint embeddings
+  \[ d_i : \left\llbracket m_i + n_i \right\rrbracket \cong \left\llbracket m_i \right\rrbracket \sqcup \left\llbracket n_i \right\rrbracket \hookrightarrow \left\llbracket \sum_j m_j \right\rrbracket \sqcup \left\llbracket \sum_j n_j \right\rrbracket \cong \left\llbracket \sum_j m_j + \sum_j n_j \right\rrbracket, \]
+  which we will use to make sure that the $ x_j $ in the different $ t_i $ are mapped to distinct variables. Then we can define
+  \[ s \bullet (t_i \bullet a_i + b_i) = (s \bullet (t_i \bullet (x_{d_i(j)})_j)_i) \bullet (a_1 + b_1 + \dots + a_l + b_l). \]
+  More formally (using the coend injections $ A^{\sum_k m_k} \times B^{\sum_k n_k} \times T_{\sum_k m_k + \sum_k n_k} \to A + B $), this gives functions
+  \[ T_l \to (A^{m_1} \times B^{n_1} \times T_{m_1 + n_1} \to (\dots \to (A^{m_l} \times B^{n_l} \times T_{m_l + n_l} \to A + B) \dots )), \]
+  commuting with the relations between the different $ (A^m \times B^n \times T_{m + n}) $, which, by repeatedly using the universal property of the coend, then correspond to functions
+  \[ T_l \to (A + B \to (\dots \to (A + B \to A + B) \dots )), \]
+  or, equivalently, a function
+  \[ T_l \times (A + B)^l \to A + B. \]
+
+  We have left and right injections $ A \to A + B $ and $ B \to A + B $, given respectively by the maps $ A^1 \times B^0 \times T_{1 + 0} \to A + B $ and $ A^0 \times B^1 \times T_{0 + 1} \to A + B $:
+  \[ a \mapsto x_1 \bullet a \quad \text{and} \quad b \mapsto x_1 \bullet b \]
+  and every element $ A + B $ arises by the action of $ t $ on combinations of these embedded elements:
+  \[ t \bullet (a + b) = t \bullet ((x_1 \bullet a_i)_i + (x_1 \bullet b_j)_j), \]
+  which ultimately can be used to show that $ A + B $ indeed has the universal property of the coproduct.
 \end{proof}
@@
 The left injection of the variables $ x_i : T_n $ gives the variables.
-  Now, take $ h: (T_n + A)^m $. Sending $ g: T_m $ to $ \varphi(g) := g \bullet h $ gives a $ T $-algebra morphism $ T_m \to T_n + A $ since
-  \[ \varphi(f \bullet g) = f \bullet g \bullet h = f \bullet (g_i \bullet h) = f \bullet (\varphi(g_i))_i. \]
-  This, together with the injection morphism of $ A $ into $ T_n + A $, gives us a $ T $-algebra morphism from the coproduct: $ T_m + A \to T_n + A $.
-We especially have a function on sets $ (T_m + A) \times (T_n + A)^m \to T_n + A $, which we will define our substitution to be.
+  Now, take $ h: (T_n + A)^m $.
+Sending $ g: T_m $ to $ g \bullet h $ gives a $ T $-algebra morphism $ T_m \to T_n + A $.
+Together with the right injection morphism of $ A $ into $ T_n + A $, this gives us a $ T $-algebra morphism from the coproduct: $ T_m + A \to T_n + A $.
+In particular, we have a function on sets $ (T_m + A) \times (T_n + A)^m \to T_n + A $, which we will define our substitution to be.
 \end{definition}
-
-\begin{lemma}
-  $ T_A $ is indeed an algebraic theory.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}

### 2024-06-07 report/src/algebraic-structures.tex
Set up for the final form of the fundamental theorem

--- 2024-05-01 report/chapters/algebraic-structures.tex
@@
 \end{definition}
+
+\begin{remark}
+  \TODO Say something about universal algebra
+  For equivalent definitions of different kinds, see Chapter \ref{ch:alternative-definitions}.
+\end{remark}
 
@@
 \begin{remark}
-  Note that for an algebraic theory $ T $, the $ T_n $ are all algebras for $ T $, with the action given by $ \bullet $.
+  Note that for an algebraic theory $ T $, the $ T_n $ are algebras for $ T $, with the action given by $ \bullet $.
 \end{remark}
 
-\begin{definition}[Pullback of algebras]\label{def:algebra-pullback}
-  If we have a morphism of algebraic theories $ f: T^\prime \to T $, we have a functor $ \Alg T \to \Alg T^\prime $.
-It endows $ T^\prime $-algebras with an action from $ T $ given by $ g \bullet_{T^\prime} a = f(g) \bullet_T a $.
-Then $ T^\prime $-algebra morphisms commute with this $ T $-action, so we indeed have a functor.
+\begin{definition}\label{def:algebra-pullback}
+  If we have a morphism of algebraic theories $ f: T^\prime \to T $, we have a \textit{pullback functor of algebras}\index{pullback functor!of algebras} $ f^* : \Alg T \to \Alg {T^\prime} $.
+It endows $ T $-algebras with an action from $ T^\prime $ given by $ g \bullet_{T^\prime} a = f(g) \bullet_T a $.
+Then $ T $-algebra morphisms commute with this $ T^\prime $-action, so we indeed have a functor.
 \end{definition}
+
+\begin{remark}
+  Note that by Lemma \ref{lem:lawvere-algebra}, algebras for $ T $ are equivalent to finite-product-preserving functors from its Lawvere theory to $ \SET $.
+Then $ f: T^\prime \to T $ corresponds to a functor on the Lawvere theories $ \mathbf L_f: \mathbf L_{T^\prime} \to \mathbf L_T $, and $ f^*: \Alg T \to \Alg{T^\prime} $ corresponds to precomposition with $ \mathbf L_f $:
+  \begin{center}
+    \begin{tikzcd}
+      \mathbf L_{T^\prime} \arrow[r, "{\mathbf L_f}"] \arrow[rd, dashed] & \mathbf L_T \arrow[d]\\
+      & \SET
+    \end{tikzcd}
+  \end{center}
+\end{remark}
+
+Actually, we can recover some information about the algebraic theory morphism from this pullback functor. For example,
+\begin{lemma}\label{lem:algebra-pullback-equivalence}
+  If $ F^* $ is an equivalence of categories, $ F $ is an isomorphism.
+\end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}
 
@@
 
+\begin{remark}
+  Recall from \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $.
+Now, recall from (\TODO) that we can embed any category inside its category of $ \SET $-valued functors.
+This embeds $ n: \mathbf L $ as the theory algebra $ T_n $.
+Then the Yoneda Lemma gives a bijection
+  \[ \Alg T(T_n, A) \cong A^n = \SET(\{ 1, \dots, n \}, A) \]
+  natural in $ n $ and $ A $.
+Explicitly, it sends $ F: \Alg T(T_n, A) $ to $ i \mapsto F(x_i) $ and $ (a_i)_i : A^n $ to $ f \mapsto f \bullet a $.
+The natural equivalence immediately shows that $ T_n $ is the free $ T $-algebra on $ n $ elements.
+\end{remark}
+
 \subsection{The initial presheaf}
@@
 
-\begin{lemma}\label{lem:presheaf-Yoneda}
-  Given an algebraic theory $ T $ and a $ T $-presheaf $ Q $, we have for all $ n $ a bijection of sets
-  \[ \varphi: \Pshf T(T^n, Q) \cong Q_n. \]
-\end{lemma}
-\begin{proof}
-  For $ f: \Pshf T(T^n, Q) $, take $ \varphi(f) = f_n(x_1, \dots, x_n) $.
-
-  Conversely, for all $ q: Q_n $ and all $ t_1, \dots, t_n: T_m^n $ take
-  \[ \varphi^{-1}(q)_m(t_1, \dots, t_n) = q \bullet t. \]
-\end{proof}
+\begin{remark}\label{rem:presheaf-Yoneda}
+  Recall from \ref{lem:lawvere-presheaf} that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $.
+Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category inside its own category of presheaves.
+This embeds $ n: \mathbf L $ as the power $ T^n = (T_m^n)_m $ of the theory presheaf.
+Then the Yoneda Lemma gives a bijection
+  \[ \Pshf T(T^n, Q) \cong Q_n \]
+  natural in $ n $ and $ Q $. Explicitly, it sends $ f: \Pshf T(T^n, Q) $ to $ f_n(x_1, \dots, x_n) $ and $ q: Q_n $ to $ (t_i)_i \mapsto q \bullet t $.
+\end{remark}
 

### 2024-06-07 report/src/alternative-definitions.tex
Define the theory of extensions
Set up for the final form of the fundamental theorem

@@
-\chapter{Alternative definitions}
+\chapter{Alternative definitions}\label{ch:alternative-definitions}
 The literature, there are many different but equivalent definitions, carrying many different names, for the objects that called `algebraic theories' in Section \ref{sec:algebraic-theories}.
@@
 
-\begin{remark}
+\begin{remark}\label{rem:abstract-clone-functor}
   The definition of algebraic theory that Hyland gives is closest to that of an abstract clone.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:lawvere-algebra}
   Let $ C $ be an abstract clone, and $ L $ be its associated Lawvere theory by the equivalence given above. A $ C $-algebra is equivalent to an algebra for $ L $.

### 2024-06-07 report/src/category-theory.tex
Set up for the final form of the fundamental theorem

@@
 \end{definition}
+
+Alternatively, we can characterize universal arrows by their action on hom-sets:
+\begin{lemma}
+  Let $ F: C \to D $ be a functor and $ d: D $ an object. An object $ c: C $ and an arrow $ f: D(d, F(c)) $ form a universal arrow from $ d $ to $ F $ if and only if the function
+  \[ (g \mapsto f \cdot F(g)) : C(c, x) \cong D(d, F(x)) \]
+  is a bijection.
+
+  Conversely, for all $ c: C $ and $ d: D $, every bijection
+  \[ C(c, x) \cong D(d, F(x)) \]
+  that is natural in $ x $ arises in this way from some universal arrow $ f: D(d, F(c)) $.
+\end{lemma}
+\begin{proof}
+  See \autocite{MacLane}, Chapter III.2, Proposition 1.
+\end{proof}
 
@@
 
+\subsection{Forgetful functors and free objects}
+
+In mathematics, we often deal with objects that are `based on' other objects.
+For example, a ring is a set with some additional structure.
+Often, this is a relation between the respective categories (for example, in the case of a displayed category, see Section \ref{sec:displayed-categories}), and such a relation gives rise to a \iindex{forgetful functor}, that `forgets' about the additional structure.
+In the examples of rings and sets, the forgetful functor sends a ring to its underlying set, and a ring morphism to the function between the sets.
+However, note that there is no formal definition of forgetful functors.
+The name is more of a way to talk about the perceived relation between the categories.
+
+\begin{definition}
+  Given a forgetful functor $ F: C \to D $, we define the \textit{free functor}\index{free!functor} associated to $ F $ to be the left adjoint to $ F $, if it exists.
+\end{definition}
+
+\begin{example}
+  Consider the forgetful functor from the category of commutative rings to the category of sets, sending a ring to its underlying set.
+This has a left adjoint, sending the set $ \{ 1, 2, \dots, n \} $ to the polynomial ring $ \mathbb Z[X_1, \dots, X_n] $, and more generally, sending $ S $ to the polynomial ring $ \mathbb Z[X_s]_{s : S} $.
+This ring is then called `the free commutative ring on $ S $'.
+If $ S $ is finite of size $ n $, the ring is also called `the free commutative ring on $ n $ generators'.
+
+  The free functor sends a function $ f: S \to T $ to the ring morphism $ \mathbb Z[X_s]_{s: S} \to \mathbb Z[X_t]_{t: T} $ that sends $ X_s $ to $ X_{f(s)} $.
+
+  The natural bijection
+  \[ \mathbf{Rng}(\mathbb Z[X_s]_{s : S}, R) \cong \SET(S, R) \]
+  then sends $ f: \mathbf{Rng}(\mathbb Z[X_s]_{s : S}, R) $ to $ s \mapsto f(X_s) $ and $ g: \SET(S, R) $ to the morphism that sends $ X_s $ to $ g(s) $.
+\end{example}
+
+However, sometimes, we have a forgetful functor $ F: C \to D $, but we cannot give a free functor on the entire category $ D $. In such a case, we might still talk about free `objects':
+\begin{definition}
+  Let $ F: C \to D $ be a forgetful functor. Given $ d: D $, the \textit{free object}\index{free!object} on $ d $ is a universal arrow $ (c, f) $ from $ d $ to $ F $.
+\end{definition}
+
+\begin{remark}
+  By \autocite{MacLane}, Chapter IV.1, Theorem 2 (ii), if we have a free object on every $ d: D $, we can piece these together to get a free functor associated to $ F $.
+\end{remark}
+
 \section{Yoneda}
 We can embed a category $ C $ fully faithfully into the functor category $ P C = [\op C, \SET] $ as follows (see \autocite{Kashiwara}, Section 1.4):
-\begin{definition}
+\begin{definition}\label{def:Yoneda-embedding}
   The \iindex{Yoneda embedding} $ Y : C \hookrightarrow P C $ is given on objects by $ Y(c) = C(-, c) $:
@@
 \begin{lemma}
-  The Yoneda embedding functor preserves exponential objects (\autocite{stackexchange:yoneda-exponentials}).
+  The Yoneda embedding functor is \iindex{cartesian}. That is, not only does it preserve binary products, but it also preserves exponential objects (\autocite{stackexchange:yoneda-exponentials}).
 \end{lemma}
 \begin{proof}
-
+  \TODO
 \end{proof}

### 2024-06-07 report/src/paper.tex
Set up for the final form of the fundamental theorem

@@
 
-  Lemma \ref{lem:presheaf-Yoneda} gives a sequence of bijections $ \varphi_n : \Pshf L(L^n, L) \cong L_n $ for all $ n $, sending $ F: \Pshf L(L^n, L) $ to $ F(x_1, \dots, x_n) $, and conversely sending $ s: L_n $ to $ ((t_1, \dots, t_n) \mapsto s \bullet (t_1, \dots, t_n)) $.
+  Remark \ref{rem:presheaf-Yoneda} gives a sequence of bijections $ \varphi_n : \Pshf L(L^n, L) \cong L_n $ for all $ n $, sending $ F: \Pshf L(L^n, L) $ to $ F(x_1, \dots, x_n) $, and conversely sending $ s: L_n $ to $ ((t_1, \dots, t_n) \mapsto s \bullet (t_1, \dots, t_n)) $.
 It considers $ \lambda $-terms in $ n $ variables as $ n $-ary functions on the $ \lambda $-calculus.
@@
 
-Let $ \llbracket n \rrbracket $ denote the finite set $ \{ 1, 2, \dots, n \} $.
-Let \index{$ \F $}$ \F \subseteq \FinSET $ be the full subcategory with $ \F_0 = \{ \llbracket 0 \rrbracket, \llbracket 1 \rrbracket, \dots \} $.
+Let $ \llbracket n \rrbracket $ denote the finite set $ \{ 1, 2, \dots, n \} $. For $ T $ an algebraic theory, let $ \mathbf L $ be its corresponding Lawvere theory (Lemma \ref{lem:lawvere-clone}).
+
+\TODO: Move the coproducts and theory of extensions to chapter 3?
 
@@
   Explicitly, we can express the coproduct of algebras, and especially its set, as the following coend (\autocite{Hyland}, Proposition 2.5) (see also Section \ref{sec:coends} for more on coends)
-  \[ A + B = \int^{(m, n) : \F \times \F} A^m \times B^n \times T_{m^\prime + n^\prime}, \]
-  considering $ T $ as a functor $ T : \F \to \SET $ as a functor (see Remark \ref{rem:abstract-clone-functor}).
-Note that we do not need the exact definition of $ A + B $ for the rest of this section.
-Nonetheless, it is interesting to see how it is defined and why this definition works.
+  \[ A + B = \int^{(m, n) : \mathbf L \times \mathbf L} T_{m^\prime + n^\prime} \times A^m \times B^n, \]
+  considering $ A $ as a covariant functor on $ \mathbf L $ (see Lemma \ref{lem:lawvere-algebra}) and the theory presheaf $ T $ as a presheaf (see Lemma \ref{lem:lawvere-presheaf}).
+
+  Note that we do not need the exact definition of $ A + B $ for the rest of this section. Nonetheless, it is interesting to see how it is defined and why this definition works.
 
@@
 
-  The relations then give `associativity' of this substitution and also assure that reordering or duplicating $ x_i $ and their corresponding $ a_i $ and $ b_j $ do not yield different elements: associating the images on the left and right of
-  \[ A^{m^\prime} \times B^{n^\prime} \times T_{m^\prime + n^\prime} \leftarrow A^{m^\prime} \times B^{n^\prime} \times T_{m + n} \rightarrow A^m \times B^n \times T_{m + n} \]
+  However, the coend is a quotient of $ \coprod T_{m + n} \times A^m \times B^n $ along some relations.
+These relations then give `associativity' of this substitution $ t \bullet (a + b) $.
+In particular, they assure that reordering or duplicating $ x_i $ and their corresponding $ a_i $ and $ b_j $ do not yield different elements.
+For $ f: \mathbf L(m, m^\prime) = T_m^{m^\prime} $, $ g: \mathbf L(n, n^\prime) = T_n^{n^\prime} $, associating the images on the left and right of
+  \[ T_{m^\prime + n^\prime} \times A^{m^\prime} \times B^{n^\prime} \leftarrow T_{m^\prime + n^\prime} \times A^m \times B^n \rightarrow T_{m + n} \times A^m \times B^n \]
   gives
-  \[ (t \bullet ((x_{f(i)})_i + (x_{m + g(j)})_j)) \bullet a + b = t \bullet ((a_{f(i)})_i + (b_{g(j)})_j) \]
-  for $ f: \llbracket m \rrbracket \to \llbracket m^\prime \rrbracket $, $ g: \llbracket n \rrbracket \to \llbracket n^\prime \rrbracket $, $ t : T_{m + n} $, $ a : A^{m^\prime} $ and $ b : B^{n^\prime} $.
-
-  Then it becomes clear what the action of $ T $ will be on $ A + B $, although the precise definition has quite a combinatorial nature.
+  \[ t \bullet ((f_i \bullet a)_i + (g_j \bullet b)_j) = (t \bullet ((f_i \bullet (x_{m + n, j})_j)_i + (g_i \bullet (x_{m + n, m + j})_j)_i)) \bullet (a + b) \]
+  for $ t : T_{m^\prime + n^\prime} $, $ a : A^m $ and $ b : B^n $.
+
+  Then it becomes clear what the action of $ T $ will be on $ A + B $, although the precise definition looks a bit complex because we have to juggle a bit with the variables in the different $ T_{m + n} $.
 For $ s : T_l $, $ t_i : T_{m_i + n_i} $, $ a_i : A^{m_i} $ and $ b_i : B^{n_i} $, define the disjoint embeddings
@@
   Let $ T $ be an algebraic theory and $ A $ a $ T $-algebra.
-We can define an algebraic theory $ T_A $ called `the theory of extensions of $ A $' with $ (T_A)_n = T_n + A $.
-The left injection of the variables $ x_i : T_n $ gives the variables.
-  Now, take $ h: (T_n + A)^m $.
-Sending $ g: T_m $ to $ g \bullet h $ gives a $ T $-algebra morphism $ T_m \to T_n + A $.
+We can define an algebraic theory $ T_A $ called the \iindex{theory of extensions} of $ A $' with $ (T_A)_n = A + T_n $.
+The right injection of the variables $ x_i : T_n $ gives the variables.
+
+  For $ h: (A + T_n)^m $, sending $ g: T_m $ to $ g \bullet h $ gives a $ T $-algebra morphism $ T_m \to T_n + A $.
 Together with the right injection morphism of $ A $ into $ T_n + A $, this gives us a $ T $-algebra morphism from the coproduct: $ T_m + A \to T_n + A $.
-In particular, we have a function on sets $ (T_m + A) \times (T_n + A)^m \to T_n + A $, which we will define our substitution to be.
+Doing this for every $ h: (A + T_n)^m $ gives us the substitution $ (T_m + A) \times (T_n + A)^m \to T_n + A $.
+
+  Showing that this is indeed an algebraic theory involves invoking the universal property of the coproduct and using properties of $ T $-algebras and $ T $-algebra morphisms.
 \end{definition}
+
+\begin{remark}
+  Note that for a $ T $-algebra morphism $ f: A \to B $, we have morphisms $ f: A + T_n \xrightarrow{f + \id{T_n}} B + T_n $.
+\end{remark}
+
+\begin{remark}
+  Note that the right embeddings $ r_n : T_n \to A + T_n $ give an algebraic theory morphism $ (r_n)_n : T \to T_A $, so we can think of $ T $ as lying inside $ T_A $.
+\end{remark}
+
+The following result explains why we are interested in the theory of extensions:
+\begin{lemma}\label{lem:extensions-algebra-coslice}
+  For $ T $ an algebraic theory and $ A $ a $ T $-algebra, we have an adjoint equivalence $ \Alg{T_A} \cong (A \downarrow \Alg T) $ between algebras for $ T_A $ and the coslice category over $ A $.
+\end{lemma}
+\begin{proof}
+  Let $ B $ be a $ T_A $-algebra. Pullback along the embedding $ (r_n)_n : T \to T_A $ gives $ (r_n)_n^*(B) : \Alg T $. Also, we have a $ T $-algebra morphism $ A \to B $ given by the composition
+  \[ A \to (T_A)_0 \xrightarrow{f \mapsto f \bullet ()} B. \]
+
+  Conversely, take $ f: \Alg T(A, B) $.
+For $ b: B^n $, we have a $ T $-algebra morphism $ T_n \to B $ given by $ f \mapsto f \bullet b $.
+This, together with $ f $, gives a morphism from the coproduct $ A + T_n \to B $, and doing this for every $ b: B^n $ gives a $ T_A $-action on $ B $ as functions $ (A + T_n) \times B^n \to B $.
+
+  Now, showing that the function $ A \to (T_A)_0 \to B $ defined above is indeed a $ T $-algebra morphism and that the other $ B $, together with the given $ T_A $-action is indeed a $ T_A $-algebra, and furthermore showing that these extend to functors that together form an adjoint equivalence, involves checking a lot of details.
+One can indeed check that all of this holds, using the properties of algebraic theories, algebras, algebra morphisms and coproducts, as well as the fact that for all $ b : B^n $, $ f \mapsto f \bullet b $ is a morphism in $ \Alg T(A + T_n, (r_n)_n^*(B)) $.
+However, for the sake of brevity, we will omit these and point to the formalization for the details.
+\end{proof}
+
+\begin{example}
+  Take $ T_n = Z[X_1, \dots, X_n] $, the polynomial rings in $ n $ variables.
+$ T $-algebras correspond to commutative rings, so we can call $ T $ `the theory of commutative rings'.
+Now, for a commutative ring $ R $, $ \Alg{T_R} $ is equivalent to the coslice category $ (R \downarrow \Alg T) $, which is the category of $ R $-algebras.
+Therefore, the theory of extensions $ T_R $ can be considered to be the theory of $ R $-algebras.
+\end{example}
+
+\begin{lemma}\label{lem:factor-through-extensions}
+  Any algebraic theory morphism $ f: \AlgTh(S, T) $ factorizes through the embedding of $ S $ into the theory of extensions of the pullback of the algebra $ T_0 $:
+  \begin{center}
+    \begin{tikzcd}
+      S \arrow[r] \arrow[rr, bend right, "f"'] & S_{f^*(T_0)} \arrow[r] & T
+    \end{tikzcd}
+  \end{center}
+\end{lemma}
+\begin{proof}
+  For any $ n $, we have a map of $ S $-algebras $ [t \mapsto t \bullet (), f_n] : f^*(T_0) + S_n \to f^*(T_n) $, given on $ f^*(T_0) $ by $ t \mapsto t \bullet () $ and on $ S_n $ by $ f_n $.
+By the universal property of the coproduct, the following diagram commutes for all $ n $:
+  \begin{center}
+    \begin{tikzcd}[sep = large]
+      S_n \arrow[r, "r_n"] \arrow[rr, bend right, "f_n"'] & f^*(T_0) + S_n \arrow[r, "{[t \mapsto t \bullet (), f_n]}"] & T
+    \end{tikzcd}
+  \end{center}
+  which shows that $ (r_n)_n \cdot [f \mapsto f \bullet (), f_n]_n = f $.
+
+  Now, to show that $ [f \mapsto f \bullet (), f_n]_n $ indeed constitutes an algebraic theory morphism is a bit more work.
+It involves using the universal property of the coproduct a couple of times, as well as showing that for all $ g : S_{f^*(T_0)}^n $,
+  \[ s \mapsto ([t \mapsto t \bullet (), f_m] x) \bullet_T ([t \mapsto t \bullet (), f_n] g_i)_i \]
+  is a morphism in $ \Alg S(f^*(T_0) + T_m, f^*(T_n)) $. For more details, we again point to the formalization.
+\end{proof}
+
+Now, given a $ \Lambda $-algebra $ A $, applying the above to the initial morphism $ \iota_\Lambda : \Lambda \to E(U_A) $, we get the following diagram:
+\begin{center}
+  \begin{tikzcd}[sep = large]
+    \Lambda \arrow[r] & \Lambda_{E(U_A)_0} \arrow[r, "{[t \mapsto t \bullet (), \iota_{\Lambda_n}]_n}"] \arrow[d, "\Lambda_{\epsilon_A}"] & E(U_A)\\
+    & \Lambda_A
+  \end{tikzcd}
+\end{center}
+For the final form of the fundamental theorem, we need to show that
+\[ \Lambda_{\epsilon_A}^{-1} \cdot [t \mapsto t \bullet (), \iota_{\Lambda_n}]_n = [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \]
+is an isomorphism.
+By Lemma \ref{lem:factor-through-extensions}, this is equivalent to its pullback $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* : \Alg{E(U_A)} \to \Alg{\Lambda_A} $ being an equivalence of categories.
+
+\begin{lemma}
+  $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* $ is essentially surjective.
+\end{lemma}
+\begin{proof}
+  Take $ B : \Alg{\Lambda_A} $.
+By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a coslice $ h: \Alg{\Lambda}(A, B) $.
+By the equivalence of categories we established earlier, $ h $ induces a morphism $ \bar h: \AlgTh(E(U_A), E(U_B)) $.
+Pulling the $ E(U_B) $-algebra $ E(U_B)_0 $ back along this morphism, gives a $ E(U_A) $-algebra $ \bar h^*(E(U_B)_0) $.
+\end{proof}
+
+\begin{lemma}
+  $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* $ is fully faithful.
+\end{lemma}
+\begin{proof}
+  \TODO
+\end{proof}
+
+\begin{lemma}
+  $ \Lambda_A $ is isomorphic to $ E(U_A) $ as an algebraic theory.
+\end{lemma}
+\begin{proof}
+  By the previous two lemmas, the pullback functor $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* $ is a weak equivalence.
+Since algebra categories are univalent, this means that the pullback functor is an equivalence of categories.
+Then, by Lemma \ref{lem:algebra-pullback-equivalence}, $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n : \AlgTh(\Lambda_A, E(U_A)) $ is an isomorphism.
+\end{proof}
+
+The final form of Hyland's representation theorem is the following:
+\begin{theorem}
+  The functor that sends a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $ and the functor that sends a $ \Lambda $-algebra $ A $ to the theory of extensions $ \Lambda_A $ form an adjoint equivalence
+  \[ \LamTh \cong \Alg \Lambda. \]
+\end{theorem}

### 2024-06-07 report/src/previous-work.tex
Set up for the final form of the fundamental theorem

@@
 
-    % \TODO: Verify that
     % \begin{itemize}
@@
   However, note that we have a weak equivalence between strict categories (categories in which the type of objects is a homotopy set) $ \sum_A: \R^A \xrightarrow \sim (\R \downarrow_D A) $.
-If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (\autocite{univalent-categories}, introduction, page 2 \TODO: maybe find a better reference for this) and then our pullback functor is given by
+If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (see bullet (ii) in the introduction of Chapter 9 of \autocite{hottbook}) and then our pullback functor is given by
   \[ \sum_A^{-1} \bullet (\alpha \cdot -) \bullet \sum_B, \]

### 2024-06-07 report/src/univalent-foundations.tex
Set up for the final form of the fundamental theorem

@@
 First of all, \iindex{type theory} is the study of `type systems'.
-A \iindex{type system} is a collection of terms or elements, each of which has a corresponding type.
+A \iindex{type system} is a collection of \textit{terms} or \textit{elements}, each of which has a corresponding type.
 A type is much like a set in set theory in that it has elements (for example, $ \mathrm{true}: \mathrm{Bool} $ or $ 1: \mathbb N $), but there are important differences.
-First of all, in type theory, elements are declared together with their type, whereas in set theory, something can be an element of multiple sets, like $ 5 \in \mathbb N $ and $ 5 \in \mathbb R $.
-Secondly, equality in type theory can work a bit differently than in classical mathematics, but will cover this in the next section.
+First of all, in type theory, terms are declared together with their type, so every term has exactly one type, whereas in set theory, something can be an element of multiple sets, like $ 5 \in \mathbb N $ and $ 5 \in \mathbb R $.
+Secondly, equality in type theory can work a bit differently than in set-based mathematics, but I will cover this in the next section.
+
+Of course, in computer science, we are very familiar with type systems.
+In most programming languages, values explicitly (e.g.
+in Java) or implicitly (e.g.
+in Python) have a type associated to them.
+For example, \texttt{"Hello, World"} is of type \textit{string}, \texttt{true} and \texttt{false} are of type \textit{boolean}, \texttt{1} is of type \textit{integer} and \texttt{-5.8} is of type \textit{floating point number}.
+And here, already, we see some subtleties: due to their different internal representations, many programming languages distinguish between integers and floating point numbers, even though every integer can be considered to be a floating point number.
+Usually, programming languages resolve this by offering methods (sometimes in the form of \textit{coercions}) to convert between the two types (discarding what comes after the decimal point when converting a floating point number to an integer).
+Another coercion that occurs sometimes is the conversion of a \textit{character} like \texttt{a}, \texttt{1} or \texttt{\&} to an integer and back.
 

### 2024-06-07 report/src/paper.tex
Show that the pullback is essentially surjective

@@
 \begin{lemma}\label{lem:extensions-algebra-coslice}
-  For $ T $ an algebraic theory and $ A $ a $ T $-algebra, we have an adjoint equivalence $ \Alg{T_A} \cong (A \downarrow \Alg T) $ between algebras for $ T_A $ and the coslice category over $ A $.
+  For $ T $ an algebraic theory and $ A $ a $ T $-algebra, we have an adjoint equivalence $ \Alg{T_A} \cong (A \downarrow \Alg T) $ between algebras for $ T_A $ and the coslice category under $ A $.
 \end{lemma}
@@
   Take $ B : \Alg{\Lambda_A} $.
-By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a coslice $ h: \Alg{\Lambda}(A, B) $.
-By the equivalence of categories we established earlier, $ h $ induces a morphism $ \bar h: \AlgTh(E(U_A), E(U_B)) $.
-Pulling the $ E(U_B) $-algebra $ E(U_B)_0 $ back along this morphism, gives a $ E(U_A) $-algebra $ \bar h^*(E(U_B)_0) $.
+By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a object in the coslice category $ h : \Alg{\Lambda}(A, B) $.
+As shown earlier in this chapter, $ h $ induces a morphism $ \bar h: \AlgTh(E(U_A), E(U_B)) $.
+We then have a $ E(U_A) $-algebra $ \bar h^*(E(U_B)_0) $.
+Now we need to prove that we have an isomorphism of $ \Lambda_A $-algebras
+  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot \bar h)^*(E(U_B)_0) \cong B. \]
+  Under the equivalence in Lemma \ref{lem:extensions-algebra-coslice}, this pullback of $ E(U_B)_0 $ corresponds to some $ (B^\prime, h^\prime) : (A \downarrow \Alg \Lambda) $.
+The set of $ B^\prime $ is $ \RAct{B_1}(I, U_B) $, its $ \Lambda $-action is given by
+  \[ (f, b) \mapsto \bar h_n(\iota_{\Lambda_n}(f)) \bullet_{E(U_B)} b, \]
+  and the morphism $ h^\prime $ is given by $ h^\prime(a) = \bar h(\epsilon_A^{-1}(a)) $. Note that by initiality of $ \Lambda $, the following diagram of algebraic theories commutes
+  \begin{center}
+    \begin{tikzcd}
+      & \Lambda \arrow[ld, "\iota_\Lambda"'] \arrow[rd, "\iota_\Lambda"]\\
+      E(U_A) \arrow[rr, "\bar h"] && E(U_B)
+    \end{tikzcd}
+  \end{center}
+  Therefore, $ \bar h_n(\iota_{\Lambda_n}(f)) = \iota_{\Lambda_n}(f) $, so the $ \Lambda $-action on $ B^\prime $ coincides with the action on $ \iota_\Lambda^*(E(U_B)_0) $ and $ B^\prime = \iota_\Lambda^*(E(U_B)_0) $.
+We have the following diagram in $ \Alg \Lambda $:
+  \begin{center}
+    \begin{tikzcd}[sep = large]
+      & A \arrow[ld, "a \mapsto \bar h(\epsilon_A^{-1}(a))"'] \arrow[rd, "h"]\\
+      E(U_B)_0 \arrow[rr, "\epsilon_B"] & & B
+    \end{tikzcd}
+  \end{center}
+  By Lemma \ref{lem:counit-natural}, the diagram commutes, which shows that $ \epsilon_B $ is an isomorphism in the coslice category under $ A $.
+Pulling this isomorphism back along the equivalence from Lemma \ref{lem:extensions-algebra-coslice} gives an isomorphism of $ \Lambda_A $-algebras
+  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot \bar h)^*(E(U_B)_0) \cong B \]
+  and this concludes the proof.
 \end{proof}

### 2024-06-13 report/src/paper.tex
Make (a sketch of) the fundamental theorem work using R_A instead of RAct_{A_1}

--- 2024-06-07 report/src/paper.tex
@@
 
-\section{An elementary proof of the `Fundamental Theorem'}
-
+\section{An elementary proof of the `Fundamental Theorem'}\label{sec:elementary-fundamental-theorem}
 The final theorem that Hyland works towards in his paper constructs an equivalence between $ \lambda $-calculi and $ \Lambda $-algebras.
@@
 Now, take a morphism $ F: \Alg{\Lambda}(A, B) $.
-Recall that $ \circ $, the categories $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given using $ f \bullet (a_1, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $.
+Recall that $ \circ $, the categories $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given using $ f \bullet (a_2, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $.
 Since we have $ F(f \bullet (a_i)_i) = f \bullet (F(a_i)) $, $ F $ gives a functor $ F: \R_A \to \R_B $, such that
@@
 
-Now, given a $ \Lambda $-algebra $ A $, applying the above to the initial morphism $ \iota_\Lambda : \Lambda \to E(U_A) $, we get the following diagram:
+Now, given a $ \Lambda $-algebra $ A $, applying the above to the initial morphism $ \iota_\Lambda : \Lambda \to E_{\R_A}(U) $, we get the following diagram:
 \begin{center}
   \begin{tikzcd}[sep = large]
-    \Lambda \arrow[r] & \Lambda_{E(U_A)_0} \arrow[r, "{[t \mapsto t \bullet (), \iota_{\Lambda_n}]_n}"] \arrow[d, "\Lambda_{\epsilon_A}"] & E(U_A)\\
+    \Lambda \arrow[r] & \Lambda_{E_{\R_A}(U)_0} \arrow[r, "{[t \mapsto t \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n}"] \arrow[d, "\Lambda_{\epsilon_A}"] & E_{\R_A}(U)\\
     & \Lambda_A
@@
 For the final form of the fundamental theorem, we need to show that
-\[ \Lambda_{\epsilon_A}^{-1} \cdot [t \mapsto t \bullet (), \iota_{\Lambda_n}]_n = [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \]
-is an isomorphism.
-By Lemma \ref{lem:factor-through-extensions}, this is equivalent to its pullback $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* : \Alg{E(U_A)} \to \Alg{\Lambda_A} $ being an equivalence of categories.
-
-\begin{lemma}
-  $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* $ is essentially surjective.
+\[ \Lambda_{\epsilon_A^{-1}} \cdot [t \mapsto t \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n = [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n \]
+is an isomorphism of algebraic theories. By Lemma \ref{lem:factor-through-extensions}, this is equivalent to its pullback
+\[ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n^* : \Alg{E_{\R_A}(U)} \to \Alg{\Lambda_A} \]
+being an equivalence of categories.
+
+\begin{lemma}
+  The pullback functor
+  \[ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n^* \]
+  is essentially surjective.
 \end{lemma}
@@
   Take $ B : \Alg{\Lambda_A} $.
-By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a coslice $ h: \Alg{\Lambda}(A, B) $.
-By the equivalence of categories we established earlier, $ h $ induces a morphism $ \bar h: \AlgTh(E(U_A), E(U_B)) $.
-Pulling the $ E(U_B) $-algebra $ E(U_B)_0 $ back along this morphism, gives a $ E(U_A) $-algebra $ \bar h^*(E(U_B)_0) $.
-\end{proof}
+By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a object in the coslice category $ h : \Alg{\Lambda}(A, B) $.
+As shown in Section \ref{sec:elementary-fundamental-theorem}, $ h $ sends elements in $ \R_A(U^n, U) $ to elements in $ \R_B(U^n, U) $, so we can regard it as a morphism $ h: \AlgTh(E_{\R_A}(U), E_{\R_B}(U)) $.
+We then have a $ E_{\R_A}(U) $-algebra $ h^*(E_{\R_B}(U)_0) $.
+Now we need to prove that we have an isomorphism of $ \Lambda_A $-algebras
+  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot h)^*(E_{\R_B}(U)_0) \cong B. \]
+  Under the equivalence in Lemma \ref{lem:extensions-algebra-coslice}, this pullback of $ E_{\R_B}(U)_0 $ corresponds to some $ (B^\prime, h^\prime) : (A \downarrow \Alg \Lambda) $.
+The set of $ B^\prime $ is $ \R_B(I, U) $, its $ \Lambda $-action is given by
+  \[ (f, b) \mapsto h(\iota_{\Lambda_n}(f)) \bullet_{E_{\R_B}(U)} b, \]
+  and the morphism $ h^\prime $ is given by $ h^\prime(a) = h(\epsilon_A^{-1}(a)) $. Note that by initiality of $ \Lambda $, the following diagram of algebraic theories commutes
+  \begin{center}
+    \begin{tikzcd}
+      & \Lambda \arrow[ld, "\iota_\Lambda"'] \arrow[rd, "\iota_\Lambda"]\\
+      E_{\R_A}(U) \arrow[rr, "h"] && E_{\R_B}(U)
+    \end{tikzcd}
+  \end{center}
+  Therefore, $ h_n(\iota_{\Lambda_n}(f)) = \iota_{\Lambda_n}(f) $, so $ B^\prime = \iota_\Lambda^*(E_{\R_B}(U)_0) $. We have the following diagram in $ \Alg \Lambda $:
+  \begin{center}
+    \begin{tikzcd}[sep = large]
+      & A \arrow[ld, "a \mapsto h(\epsilon_A^{-1}(a))"'] \arrow[rd, "h"]\\
+      E_{\R_B}(U)_0 \arrow[rr, "\epsilon_B"] & & B
+    \end{tikzcd}
+  \end{center}
+  \TODO: Show commutativity
+
+  which shows that $ \epsilon_B $ is an isomorphism in the coslice category under $ A $.
+Pulling this isomorphism back along the equivalence from Lemma \ref{lem:extensions-algebra-coslice} gives an isomorphism of $ \Lambda_A $-algebras
+  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot h)^*(E_{\R_B}(U)_0) \cong B \]
+  and this concludes the proof.
+\end{proof}
+
+\begin{lemma}
+  For $ \iota_\Lambda: \LamTh(\Lambda, E_{\R_A}(U)) $ and $ s_i : \Lambda_n $, we have
+  \[ \iota_\Lambda((s_i)_i) = \langle x_i \rangle_i \bullet_A (\iota_\Lambda(s_i))_i, \]
+  and we will call the latter $ \langle \iota_\Lambda(s_i) \rangle_i $.
+\end{lemma}
+\begin{proof}
+  By the recursive nature of the definitions of $ (s_i)_i $ and $ \langle a_i \rangle_i $, it suffices to show that for $ a, b : \Lambda_n $, $ \iota_\Lambda((a, b)) = \langle \iota_\Lambda(a), \iota_\Lambda(b) \rangle $ and that $ \iota_\Lambda(c_n) = I_c $.
+Since $ \iota_\Lambda $ is defined via structural induction, this is just a matter of straightforward but tedious unfolding and rewriting, at some point using the fact that $ \iota_\Lambda(a) \circ U^n = \iota_\Lambda(a) $:
+  \begin{align*}
+    \iota_\Lambda((a, b))
+    &= \iota_\Lambda(\lambda x_{n + 1}, x_{n + 1} \iota_{n, n + 1}(a) \iota_{n, n + 1}(b))\\
+    &= (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet_A \iota_\Lambda(x_{n + 1} \iota_{n, n + 1}(a) \iota_{n, n + 1}(b))\\
+    &= (\lambda x_4 x_5, (\lambda x_6, x_1 x_6 (x_2 x_6) (x_3 x_6)) (x_4, x_5)) \bullet_A (\iota_\Lambda(x_{n + 1}), \iota_\Lambda(a \bullet_\Lambda (x_{n + 1, i})_i), \iota_\Lambda(b \bullet_\Lambda (x_{n + 1, i})_i))\\
+    &= (\lambda x_3 x_4, \pi_{n + 1, n + 1} (x_3, x_4) ((x_1 \circ \langle \pi_{n + 1, i} \rangle)_i (x_3, x_4)) ((x_2 \circ \langle \pi_{n + 1, i} \rangle)_i (x_3, x_4))) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
+    &= (\lambda x_3 x_4, x_4 ((x_1 \circ \langle \pi_{n, i} \rangle_i) x_3) ((x_2 \circ \langle \pi_{n, i} \rangle_i) x_3)) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
+    &= (\lambda x_3 x_4, x_4 (x_1 x_3) (x_2 x_3)) \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))\\
+    &= \langle x_1, x_2 \rangle \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b))
+  \end{align*}
+  and
+  \begin{align*}
+    \iota_\Lambda(c_n)
+    &= \iota_\Lambda(\lambda x_{n + 1}, x_{n + 1})\\
+    &= (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet_A \iota_\Lambda(x_{n + 1})\\
+    &= \lambda x_1 x_2, \pi_{n + 1, n + 1} (x_1, x_2)\\
+    &= \lambda x_1 x_2, x_2\\
+    &= I_c.
+  \end{align*}
+\end{proof}
+
+\begin{remark}\label{rem:endomorphism-theory-algebra-to-endomorphism-theory-algebra}
+  Note that for any $ E_{\R_A}(U) $-algebra $ B $, we can view the pullback $ \Lambda_A $-algebra $ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]^* B $ as an object in the coslice category under $ A $, given by
+  \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B () : \Alg \Lambda(A, \iota_\Lambda^* B). \]
+  Functoriality of the endomorphism theory construction of the respective categories of retracts, gives a $ \lambda $-theory morphism
+  \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B (): \LamTh(E_{\R_A}(U), E_{\R_{\iota_\Lambda^* B}}(U)). \]
+  Then, we can pull back the theory algebra along this morphism, to get, again a $ E_{\R_A}(U) $-algebra
+  \[ (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0). \]
+\end{remark}
+
+\begin{lemma}
+  For $ B : \Alg {E_{\R_A}(U)} $, we have an isomorphism of $ E_{\R_A}(U) $-algebras given by
+  \[ \epsilon_{\iota_\Lambda^* B} : (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0) \xrightarrow \sim B. \]
+\end{lemma}
+\begin{proof}
+  Note that the underlying set of $ (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0) $ is $ \R_{\iota_\Lambda^* B}(I, U) $, and that $ \epsilon_{\iota_\Lambda^* B} $ is a bijection between this set and $ B $.
+Now we only need to show that it is a morphism of $ E_{\R_A}(U) $-algebras.
+Take $ s: E_{\R_A}(U)_n $ and all $ b : E_{\R_{\iota_\Lambda^* B}}(U)_0^n $.
+We have
+  \begin{align*}
+    \epsilon_{\iota_\Lambda^* B}(s \bullet_{(a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* E_{\R_{\iota_\Lambda^* B}}(U)_0} b)
+    &= \iota_\Lambda(x_1 c_1) \bullet_B (s \bullet_{(a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* E_{\R_{\iota_\Lambda^* B}}(U)_0} b)\\
+    &= \iota_\Lambda(x_1 c_1) \bullet_B ((\epsilon_A^{-1}(s) \bullet_B ()) \bullet_{E_{\R_{\iota_\Lambda^* B}}(U)_0} b)\\
+    &= \iota_\Lambda(x_1 c_1) \bullet_B (\iota_\Lambda(x_1 \circ \langle x_2, \dots, x_{n + 1} \rangle) \bullet_B (\epsilon_A^{-1}(s) \bullet_B (), b_1, \dots, b_n))\\
+    &= \iota_\Lambda(x_1 c_1) \bullet_B ((\iota_\Lambda(x_1 \circ \langle x_{i + 1} \rangle_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b)\\
+    &= (\iota_\Lambda(x_1 c_1) \bullet_{E_{\R_A}(U)} (\iota_\Lambda(x_1 \circ \langle x_{i + 1} \rangle_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n)))) \bullet_B b\\
+    &= (\iota_\Lambda(x_1 (x_{i + 1} c_{n + 1})_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b\\
+    &= (\iota_\Lambda(x_1 (x_{i + 1} c_{n + 1})_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b\\
+    &= (\epsilon_A^{-1}(s) (x_i c_n)_i) \bullet_B b\\
+    &= (\epsilon_A^{-1}(s) (x_i)_i \bullet \iota_\Lambda(x_i c_n)_i) \bullet_B b.
+  \end{align*}
+  Also,
+  \begin{align*}
+    s \bullet_B (\epsilon_B(b_i))_i
+    &= s \bullet_B (\iota_\Lambda(x_1 c_1) \bullet_B b_i)_i\\
+    &= s \bullet_B (\iota_\Lambda(x_i c_n) \bullet_B (b_j)_j)_i\\
+    &= (s \bullet_{E_{\R_A}(U)} (\iota_\Lambda(x_i c_n))_i) \bullet_B b.
+  \end{align*}
+  Then the result follows from the fact that
+  \begin{align*}
+    ((\epsilon_A^{-1}(s)) \bullet_{E_{\R_A}(U)} ()) (x_i)_i
+    &= ((\lambda x_2, x_1) \bullet_A s) (x_i)_i\\
+    &= (\lambda x_3, x_1 x_3 x_2 x_3) \bullet_A ((\lambda x_2, x_1) \bullet_A s, \iota_\Lambda((x_i)_i))\\
+    &= (\lambda x_3, x_1 x_2 x_3) \bullet_A (s, \langle \iota_\Lambda(x_i) \rangle_i)\\
+    &= (x_1 \circ x_2) \bullet_A (s, U^n)\\
+    &= s.
+  \end{align*}
+\end{proof}
+
+\TODO show functoriality of pullback in coslice category.
 
@@
 \begin{proof}
-  \TODO
-\end{proof}
-
-\begin{lemma}
-  $ \Lambda_A $ is isomorphic to $ E(U_A) $ as an algebraic theory.
+  First of all, note that the pullback functor is always faithful, since it preserves all the `data' (i.e. the functions) of the algebra morphisms.
+
+  Now, to show that it is full, take $ B, C: \Alg{E_{\R_A}(U)} $. Also, take a morphism
+  \[ h : \Alg{\Lambda_A}([a \mapsto \epsilon_A^{-1}(a) \bullet_B (), \iota_{\Lambda_n}]_n^* B, [a \mapsto \epsilon_A^{-1}(a) \bullet_C (), \iota_{\Lambda_n}]_n^* C). \]
+  By Remark \ref{rem:endomorphism-theory-algebra-to-endomorphism-theory-algebra}, and by functoriality of the endomorphism theory construction, we get a commutative diagram
+  \begin{center}
+    \begin{tikzcd}
+      & E_{\R_A}(U) \arrow[ld, "a \mapsto \epsilon_A^{-1}(a) \bullet_B ()"'] \arrow[rd, "a \mapsto \epsilon_A^{-1}(a) \bullet_C ()"]\\
+      E_{\R_{\iota_{\Lambda}^* B}}(U) \arrow[rr, "h"] & & E_{\R_{\iota_{\Lambda}^* C}}(U)
+    \end{tikzcd}
+  \end{center}
+  Now, using functoriality of the pullback of the theory algebras in the coslice category $ (E_{\R_A}(U) \downarrow \AlgTh) $, and using the previous lemma, we get the following diagram of $ E_{\R_A}(U) $-algebras, which gives us the lift $ \bar h : \Alg{E_{\R_A}(U)}(B, C) $:
+  \begin{center}
+    \begin{tikzcd}[sep = large]
+      (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0)
+        \arrow[r, "(a \mapsto \epsilon_A^{-1}(a) \bullet ())^* h_0"]
+        \arrow[d, "\epsilon_{\iota_\Lambda^* B}", "\sim"'] &
+      (a \mapsto \epsilon_A^{-1}(a) \bullet_C ())^* (E_{\R_{\iota_\Lambda^* C}}(U)_0)
+        \arrow[d, "\epsilon_{\iota_\Lambda^* C}", "\sim"']\\
+      B \arrow[r, dashed, "\bar h"] & C
+    \end{tikzcd}
+  \end{center}
+
+  \TODO: Show that $ \bar h $ restricts to $ h $.
+\end{proof}
+
+\begin{lemma}
+  $ \Lambda_A $ is isomorphic to $ E_{\R_A}(U) $ as an algebraic theory.
 \end{lemma}
@@
 Since algebra categories are univalent, this means that the pullback functor is an equivalence of categories.
-Then, by Lemma \ref{lem:algebra-pullback-equivalence}, $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n : \AlgTh(\Lambda_A, E(U_A)) $ is an isomorphism.
+Then, by Lemma \ref{lem:algebra-pullback-equivalence}, $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n : \AlgTh(\Lambda_A, E_{\R_A}(U)) $ is an isomorphism.
 \end{proof}

### 2024-06-14 report/src/paper.tex
Prettify the proofs that the pullback is full, and that epsilon_B is an isomorphism of E_{R_A}(U)-algebras

@@
 \begin{lemma}
+  The isomorphisms $ \epsilon_A : E_{\R_A}(U)_0 \xrightarrow \sim A $ form a natural transformation. That is, for all $ h: \Alg \Lambda(A, B) $, the following diagram commutes:
+  \begin{center}
+    \begin{tikzcd}
+      E_{\R_A}(U)_0 \arrow[r, "h"] \arrow[d, "\epsilon_A"] & E_{\R_B}(U)_0 \arrow[d, "\epsilon_B"]\\
+      A \arrow[r, "h"] & B
+    \end{tikzcd}
+  \end{center}
+\end{lemma}
+\begin{proof}
+  This follows from simple unfolding and using the property of algebra morphisms: For all $ f: E_{\R_A}(U)_0 = \{ f : A \mid (x_1 \circ I_c) \bullet_A f = f \} $,
+  \begin{align*}
+    \epsilon_B(h(f))
+    &= (x_1 c_1) \bullet_B h(f)\\
+    &= h((x_1 c_1) \bullet_A f)\\
+    &= h(\epsilon_A(f)).
+  \end{align*}
+\end{proof}
+
+\begin{lemma}
   The pullback functor
@@
 By Lemma \ref{lem:extensions-algebra-coslice} we can consider $ B $ to be a object in the coslice category $ h : \Alg{\Lambda}(A, B) $.
-As shown in Section \ref{sec:elementary-fundamental-theorem}, $ h $ sends elements in $ \R_A(U^n, U) $ to elements in $ \R_B(U^n, U) $, so we can regard it as a morphism $ h: \AlgTh(E_{\R_A}(U), E_{\R_B}(U)) $.
-We then have a $ E_{\R_A}(U) $-algebra $ h^*(E_{\R_B}(U)_0) $.
+As shown in Section \ref{sec:elementary-fundamental-theorem}, $ h $ sends elements in $ \R_A(U^n, U) $ to elements in $ \R_B(U^n, U) $, so we can regard it as a morphism $ (h)_n: \AlgTh(E_{\R_A}(U), E_{\R_B}(U)) $.
+We then have a $ E_{\R_A}(U) $-algebra $ (h)_n^*(E_{\R_B}(U)_0) $.
 Now we need to prove that we have an isomorphism of $ \Lambda_A $-algebras
-  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot h)^*(E_{\R_B}(U)_0) \cong B. \]
+  \[ ([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n \cdot (h)_n)^*(E_{\R_B}(U)_0) \cong B. \]
   Under the equivalence in Lemma \ref{lem:extensions-algebra-coslice}, this pullback of $ E_{\R_B}(U)_0 $ corresponds to some $ (B^\prime, h^\prime) : (A \downarrow \Alg \Lambda) $.
@@
       & \Lambda \arrow[ld, "\iota_\Lambda"'] \arrow[rd, "\iota_\Lambda"]\\
-      E_{\R_A}(U) \arrow[rr, "h"] && E_{\R_B}(U)
-    \end{tikzcd}
-  \end{center}
-  Therefore, $ h_n(\iota_{\Lambda_n}(f)) = \iota_{\Lambda_n}(f) $, so $ B^\prime = \iota_\Lambda^*(E_{\R_B}(U)_0) $. We have the following diagram in $ \Alg \Lambda $:
+      E_{\R_A}(U) \arrow[rr, "(h)_n"] && E_{\R_B}(U)
+    \end{tikzcd}
+  \end{center}
+  Therefore, $ h(\iota_{\Lambda_n}(f)) = \iota_{\Lambda_n}(f) $, so the $ \Lambda $-action on $ B^\prime $ is exactly the action on $ \iota_\Lambda^*(E_{\R_B}(U)_0) $, which means that $ B^\prime = \iota_\Lambda^*(E_{\R_B}(U)_0) $.
+We have the following diagram in $ \Alg \Lambda $:
   \begin{center}
@@
       & A \arrow[ld, "a \mapsto h(\epsilon_A^{-1}(a))"'] \arrow[rd, "h"]\\
-      E_{\R_B}(U)_0 \arrow[rr, "\epsilon_B"] & & B
-    \end{tikzcd}
-  \end{center}
-  \TODO: Show commutativity
-
-  which shows that $ \epsilon_B $ is an isomorphism in the coslice category under $ A $.
+      E_{\R_B}(U)_0 \arrow[rr, "\epsilon_B", "\sim"'] & & B
+    \end{tikzcd}
+  \end{center}
+  By naturality of $ \epsilon $, this diagram commutes, which shows that $ \epsilon_B $ is an isomorphism in the coslice category under $ A $.
 Pulling this isomorphism back along the equivalence from Lemma \ref{lem:extensions-algebra-coslice} gives an isomorphism of $ \Lambda_A $-algebras
@@
   For $ \iota_\Lambda: \LamTh(\Lambda, E_{\R_A}(U)) $ and $ s_i : \Lambda_n $, we have
-  \[ \iota_\Lambda((s_i)_i) = \langle x_i \rangle_i \bullet_A (\iota_\Lambda(s_i))_i, \]
-  and we will call the latter $ \langle \iota_\Lambda(s_i) \rangle_i $.
-\end{lemma}
-\begin{proof}
-  By the recursive nature of the definitions of $ (s_i)_i $ and $ \langle a_i \rangle_i $, it suffices to show that for $ a, b : \Lambda_n $, $ \iota_\Lambda((a, b)) = \langle \iota_\Lambda(a), \iota_\Lambda(b) \rangle $ and that $ \iota_\Lambda(c_n) = I_c $.
-Since $ \iota_\Lambda $ is defined via structural induction, this is just a matter of straightforward but tedious unfolding and rewriting, at some point using the fact that $ \iota_\Lambda(a) \circ U^n = \iota_\Lambda(a) $:
+  \[ \iota_\Lambda((s_i)_i) = \langle x_i \rangle_i \bullet_A (\iota_\Lambda(s_i))_i. \]
+\end{lemma}
+\begin{proof}
+  By the recursive nature of the definitions of $ (s_i)_i $ and $ \langle x_i \rangle_i $, it suffices to show that for $ a, b : \Lambda_n $, $ \iota_\Lambda((a, b)) = \langle x_1, x_2 \rangle \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b)) $ and that $ \iota_\Lambda(c_n) = I_c \bullet () $.
+Since $ \iota_\Lambda $ is defined via structural induction, this is just a matter of straightforward but tedious unfolding and rewriting, at some point using the fact that $ (x_1 \circ U^n) \bullet_A \iota_\Lambda(a) = \iota_\Lambda(a) $:
   \begin{align*}
@@
     &= (\lambda x_2 x_3, x_1 (x_2, x_3)) \bullet_A \iota_\Lambda(x_{n + 1})\\
-    &= \lambda x_1 x_2, \pi_{n + 1, n + 1} (x_1, x_2)\\
-    &= \lambda x_1 x_2, x_2\\
-    &= I_c.
+    &= (\lambda x_1 x_2, \pi_{n + 1, n + 1} (x_1, x_2)) \bullet_A ()\\
+    &= (\lambda x_1 x_2, x_2) \bullet_A ()\\
+    &= I_c \bullet_A ().
   \end{align*}
@@
   \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B () : \Alg \Lambda(A, \iota_\Lambda^* B). \]
-  Functoriality of the endomorphism theory construction of the respective categories of retracts, gives a $ \lambda $-theory morphism
+  Functoriality of the endomorphism theory construction of $ U : \R_A $ and $ U : \R_{\iota_\Lambda^* B} $, gives a $ \lambda $-theory morphism
   \[ a \mapsto \epsilon_A^{-1}(a) \bullet_B (): \LamTh(E_{\R_A}(U), E_{\R_{\iota_\Lambda^* B}}(U)). \]
@@
   \begin{align*}
-    \epsilon_{\iota_\Lambda^* B}(s \bullet_{(a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* E_{\R_{\iota_\Lambda^* B}}(U)_0} b)
-    &= \iota_\Lambda(x_1 c_1) \bullet_B (s \bullet_{(a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* E_{\R_{\iota_\Lambda^* B}}(U)_0} b)\\
+    \epsilon_{\iota_\Lambda^* B}(s \bullet b)
     &= \iota_\Lambda(x_1 c_1) \bullet_B ((\epsilon_A^{-1}(s) \bullet_B ()) \bullet_{E_{\R_{\iota_\Lambda^* B}}(U)_0} b)\\
@@
     &= (\iota_\Lambda(x_1 (x_{i + 1} c_{n + 1})_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b\\
-    &= (\iota_\Lambda(x_1 (x_{i + 1} c_{n + 1})_i) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda(x_1), \dots, \iota_\Lambda(x_n))) \bullet_B b\\
-    &= (\epsilon_A^{-1}(s) (x_i c_n)_i) \bullet_B b\\
-    &= (\epsilon_A^{-1}(s) (x_i)_i \bullet \iota_\Lambda(x_i c_n)_i) \bullet_B b.
+    &= (\iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda((x_i c_n)_i))) \bullet_B b\\
+    &= ((\iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda((x_i)_i))) \bullet_{E_{\R_A}(U)} (x_i c_n)_i) \bullet_B b\\
   \end{align*}
@@
   \begin{align*}
-    ((\epsilon_A^{-1}(s)) \bullet_{E_{\R_A}(U)} ()) (x_i)_i
-    &= ((\lambda x_2, x_1) \bullet_A s) (x_i)_i\\
-    &= (\lambda x_3, x_1 x_3 x_2 x_3) \bullet_A ((\lambda x_2, x_1) \bullet_A s, \iota_\Lambda((x_i)_i))\\
-    &= (\lambda x_3, x_1 x_2 x_3) \bullet_A (s, \langle \iota_\Lambda(x_i) \rangle_i)\\
-    &= (x_1 \circ x_2) \bullet_A (s, U^n)\\
+    \iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} (\epsilon_A^{-1}(s), \iota_\Lambda((x_i)_i))
+    &= \iota_\Lambda(x_1 x_2) \bullet_{E_{\R_A}(U)} ((\lambda x_2, x_1) \bullet_A s, \langle x_i \rangle_i \bullet_A (\iota_\Lambda(x_i))_i)\\
+    &= (\lambda x_3, x_1 x_3 x_2 x_3) \bullet_A ((\lambda x_2, x_1) \bullet_A s, \langle x_i \rangle_i \bullet_A (\pi_{n, i} \bullet_A ())_i)\\
+    &= (\lambda x_3, x_1 x_2 x_3) \bullet_A (s, \langle \pi_{n, i} \rangle_i \bullet_A ())\\
+    &= (x_1 \circ x_2) \bullet_A (s, U^n \bullet_A ())\\
     &= s.

### 2024-06-17 report/src/paper.tex
Finish the main proof of the fundamental theorem

@@
 By Lemma 3.2 in \autocite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
-\begin{theorem}
+\begin{theorem}\label{thm:Hyland-fundamental-theorem}
   There is an adjoint equivalence $ \LamTh \cong \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
@@
 
-\TODO: Move the coproducts and theory of extensions to chapter 3?
+\TODO Move the coproducts and theory of extensions to chapter 3?
 
@@
 \begin{remark}
+  We can turn the map $ A \mapsto T_A $ into a functor $ T_- : \Alg T \to \AlgTh $. For a morphism $ f: \Alg T(A, B) $, we get maps
+  \[ f + \id{T_n} : \Alg T(A + T_n, B + T_n). \]
+  We can combine these into a morphism $ T_f = (f + \id{T_n})_n $, and this makes $ T_- $ into a functor from $ \Alg T $ to $ \AlgTh $.
+
+  To actually show that $ T_f $ is a morphism and that $ T_- $ is a functor, we use the properties of the coproduct a couple of times, as well as the fact that $ f + \id{T_n} : \Alg T(A + T_n, B + T_n) $ preserves the $ T $-action.
+\end{remark}
+
+\begin{remark}
   Note that for a $ T $-algebra morphism $ f: A \to B $, we have morphisms $ f: A + T_n \xrightarrow{f + \id{T_n}} B + T_n $.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:pullback-essentially-surjective}
   The pullback functor
@@
 \begin{proof}
-  By the recursive nature of the definitions of $ (s_i)_i $ and $ \langle x_i \rangle_i $, it suffices to show that for $ a, b : \Lambda_n $, $ \iota_\Lambda((a, b)) = \langle x_1, x_2 \rangle \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b)) $ and that $ \iota_\Lambda(c_n) = I_c \bullet () $.
+  By the recursive nature of the definitions of $ (s_i)_i $ and $ \langle x_i \rangle_i $, it suffices to show that for $ a, b : \Lambda_n $, $ \iota_\Lambda((a, b)) = \langle x_1, x_2 \rangle \bullet_A (\iota_\Lambda(a), \iota_\Lambda(b)) $ and that $ \iota_\Lambda(c_n) = I_c \bullet_A () $.
 Since $ \iota_\Lambda $ is defined via structural induction, this is just a matter of straightforward but tedious unfolding and rewriting, at some point using the fact that $ (x_1 \circ U^n) \bullet_A \iota_\Lambda(a) = \iota_\Lambda(a) $:
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:pullback-fully-faithful}
   $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* $ is fully faithful.
@@
       & E_{\R_A}(U) \arrow[ld, "a \mapsto \epsilon_A^{-1}(a) \bullet_B ()"'] \arrow[rd, "a \mapsto \epsilon_A^{-1}(a) \bullet_C ()"]\\
-      E_{\R_{\iota_{\Lambda}^* B}}(U) \arrow[rr, "h"] & & E_{\R_{\iota_{\Lambda}^* C}}(U)
-    \end{tikzcd}
-  \end{center}
-  Now, using functoriality of the pullback of the theory algebras in the coslice category $ (E_{\R_A}(U) \downarrow \AlgTh) $, and using the previous lemma, we get the following diagram of $ E_{\R_A}(U) $-algebras, which gives us the lift $ \bar h : \Alg{E_{\R_A}(U)}(B, C) $:
+      E_{\R_{\iota_{\Lambda}^* B}}(U) \arrow[rr, "(h)_n"] & & E_{\R_{\iota_{\Lambda}^* C}}(U)
+    \end{tikzcd}
+  \end{center}
+  Now, using functoriality of the pullback of the theory algebras in the coslice category $ (E_{\R_A}(U) \downarrow \AlgTh) $, and using the previous lemma, we get the following diagram of $ E_{\R_A}(U) $-algebras:
   \begin{center}
@@
       (a \mapsto \epsilon_A^{-1}(a) \bullet_B ())^* (E_{\R_{\iota_\Lambda^* B}}(U)_0)
-        \arrow[r, "(a \mapsto \epsilon_A^{-1}(a) \bullet ())^* h_0"]
+        \arrow[r, "(a \mapsto \epsilon_A^{-1}(a) \bullet ())^* h"]
         \arrow[d, "\epsilon_{\iota_\Lambda^* B}", "\sim"'] &
@@
   \end{center}
-
-  \TODO: Show that $ \bar h $ restricts to $ h $.
+  This gives us the lift
+  \[ \bar h = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot (a \mapsto \epsilon_A^{-1}(a) \bullet ())^* h \cdot \epsilon_{\iota_\Lambda^* C} : \Alg{E_{\R_A}(U)}(B, C) \]
+
+  Now, when we again pull back this map to
+  \[ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* \bar h : \Alg{\Lambda_A}([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* B, [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* C).
+\]
+  Note that by naturality of $ \epsilon $, we have
+  \[ \bar h = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot h \cdot \epsilon_{\iota_\Lambda^* C} = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot \epsilon_{\iota_\Lambda^* B} \cdot h = h \]
+  as functions, and therefore $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* \bar h = h $, so the pullback is full.
 \end{proof}
@@
 \begin{proof}
-  By the previous two lemmas, the pullback functor $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* $ is a weak equivalence.
+  By Lemmas \ref{lem:pullback-essentially-surjective} and  \ref{lem:pullback-fully-faithful}, the pullback functor $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* $ is a weak equivalence.
 Since algebra categories are univalent, this means that the pullback functor is an equivalence of categories.
@@
 \end{proof}
+
+Now, to show that we can replace the functor $ A \mapsto E_{\R_A}(U) $ by $ A \mapsto \Lambda_A $, we can show that the functors are isomorphic:
+
+\begin{lemma}
+  The isomorphisms $ [a \mapsto \epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} (), \iota_{\Lambda_n}]_n : \AlgTh(\Lambda_A, E_{\R_A}(U)) $ form a natural isomorphism between the functors
+  \[ A \mapsto E_{\R_A}(U), \quad h \mapsto (h)_n \quad \text{and} \quad A \mapsto \Lambda_A, \quad h \mapsto \Lambda_h. \]
+\end{lemma}
+\begin{proof}
+  We must show that for all $ h: \Alg \Lambda(A, B) $ and for all $ n $, the following diagram of $ \Lambda $-algebras commutes:
+  \begin{center}
+    \begin{tikzcd}[sep = large]
+      A + \Lambda_n
+        \arrow[d, "h + \id{\Lambda_n}"']
+        \arrow[rr, "{[a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]}"]
+      && \iota_\Lambda^*(E_{\R_A}(U)_n)
+        \arrow[d, "h"]
+      \\ B + \Lambda_n
+        \arrow[rr, "{[a \mapsto \epsilon_B^{-1}(a) \bullet (), \iota_{\Lambda_n}]}"']
+      && \iota_\Lambda^*(E_{\R_B}(U)_n)
+    \end{tikzcd}
+  \end{center}
+  Now, by the universal property of the coproduct $ A + \Lambda_n $, it suffices to check that for all $ a : A $ and $ t : \Lambda_n $,
+  \[ h(\epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} ()) = \epsilon_B^{-1}(h(a)) \bullet_{E_{\R_B}(U)} () \quad \text{and} \quad h(\iota_{\Lambda_n}(a)) = \iota_{\Lambda_n}(a). \]
+  The former follows from the fact that $ (h)_n : \LamTh(E_{\R_A}(U), E_{\R_B}(U)) $ respects the substitution and from the naturality of $ \epsilon^{-1} $:
+  \[ h(\epsilon_A^{-1}(a) \bullet_{E_{\R_A}(U)} ())
+    = h(\epsilon_A^{-1}(a)) \bullet_{E_{\R_B}(U)} ()
+    = \epsilon_B^{-1}(h(a)) \bullet_{E_{\R_B}(U)} (), \]
+  whereas the latter follows from the initiality of $ \Lambda $, and the fact that $ (h)_n : E_{\R_A}(U) \to E_{\R_B}(U) $ is a $ \lambda $-theory morphism.
+\end{proof}
+
+\begin{remark}
+  Now, note that for any $ \Lambda $-algebra $ A $, $ \Lambda_A $ is an algebraic theory.
+However, for our equivalence of categories, we need a functor to the category of $ \lambda $-theories.
+By the natural isomorphism above (which respects the algebraic theory structures), we see that the objects and morphisms in the images of $ E_{\R_-}(U) $ and $ \Lambda_- $ have `the same' algebraic theory structures, and we can transfer the additional $ \lambda $-theory structures from $ E_{\R_-}(U) $ to $ \Lambda_- $.
+With some abuse of notation, this yields a functor $ \Lambda_- : \Alg \Lambda \to \LamTh $.
+\end{remark}
 
@@
 \end{theorem}
+\begin{proof}
+  By \ref{thm:Hyland-fundamental-theorem}, we have an adjoint equivalence given by
+  \[ L \mapsto L_0 \quad \text{and} \quad A \mapsto E_{\R_A}(U). \]
+  By the previous lemma, the second functor is isomorphic to $ \Lambda_-: \Alg \Lambda \to \LamTh $. Therefore, we can replace one by the other.
+
+  There are two ways to see this: We may notice that we can transfer the unit, the counit and the two zigzag identities of the adjunction along the natural isomorphism and show that this all works together.
+As an alternative, we can also notice that the category of $ \lambda $-theories is univalent, so the functor category $ \Alg \Lambda \to \LamTh $ is univalent and the natural isomorphism between the functors is an equality, and we can replace one by the other.
+\end{proof}

### 2024-06-17 report/src/algebraic-structures.tex
Show that the pullback is essentially surjective
Show that the algebra pullback is functorial in the

@@
 \begin{definition}
-  A \textit{morphism}\index{algebraic theory!morphism} $ F $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ F_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
+  A \textit{morphism}\index{algebraic theory!morphism} $ f $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ f_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
   \begin{align*}
-    F_n(x_j) &= x_j\\
-    F_n(f \bullet g) &= F_m(f) \bullet (F_n(g_i))_i
+    f_n(x_j) &= x_j\\
+    f_n(f \bullet g) &= f_m(f) \bullet (f_n(g_i))_i
   \end{align*}
@@
 \begin{definition}
-  For an algebraic theory $ T $, a \textit{morphism}\index{algebra!morphism} $ F $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ F: A \to A $ such that
-  \[ F(f \bullet a) = f \bullet (F(a_i))_i \]
-  for all $ f: T_n $ and $ a: A^n $.
+  For an algebraic theory $ T $, a \textit{morphism}\index{algebra!morphism} $ f $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ f: A \to A $ such that
+  \[ f(t \bullet a) = f \bullet (f(a_i))_i \]
+  for all $ t: T_n $ and $ a: A^n $.
 \end{definition}
@@
 \begin{lemma}\label{lem:algebra-pullback-equivalence}
-  If $ F^* $ is an equivalence of categories, $ F $ is an isomorphism.
+  If $ f^* $ is an equivalence of categories, $ f $ is an isomorphism.
 \end{lemma}
@@
 \begin{definition}
-  For an algebraic theory $ T $, a \textit{morphism}\index{presheaf!morphism} $ F $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ F_n: P_n \to P^\prime_n $ such that
-  \[ F_n(t \bullet f) = F_m(t) \bullet f \]
+  For an algebraic theory $ T $, a \textit{morphism}\index{presheaf!morphism} $ f $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ f_n: P_n \to P^\prime_n $ such that
+  \[ f_n(t \bullet f) = f_m(t) \bullet f \]
   for all $ t: P_m $ and $ f: T_n^m $.
@@
 \begin{definition}[$ \lambda $-theory morphism]
-  A \textit{morphism}\index{$ \lambda $-theory!morphism} $ F $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ F $ such that
+  A \textit{morphism}\index{$ \lambda $-theory!morphism} $ f $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ f $ such that
   \begin{align*}
-    F_n(\lambda_n(f)) &= \lambda_n(F_{n + 1}(f))\\
-    \rho_n(F_n(g)) &= F_{n + 1}(\rho_n(g))
+    f_n(\lambda_n(s)) &= \lambda_n(f_{n + 1}(s))\\
+    \rho_n(f_n(t)) &= f_{n + 1}(\rho_n(t))
   \end{align*}
-  for all $ f: L_{n + 1} $ and $ g: L_n $.
+  for all $ s: L_{n + 1} $ and $ t: L_n $.
 \end{definition}
@@
 
-  Lastly, the functor is essentially surjective, since we can lift a coslice $ f: S \to X $ to a $ F(S) $-algebra $ X $, with action
+  Lastly, the functor is essentially surjective, since we can lift an object $ f: S \to X $ to a $ F(S) $-algebra $ X $, with action
   \[ i \bullet x = x_i \quad \text{and} \quad s \bullet x = f(s). \]
@@
 
+\begin{remark}
   $ F(\emptyset) $ is, in some sense, the smallest nontrivial algebraic theory. Then $ F(S) $ is the smallest nontrivial algebraic theory that has the elements of $ S $ as constants.
+\end{remark}
+
+\begin{remark}
+  Note that the category of $ F(\emptyset) $-algebras is equivalent to the coslice-category $ (\emptyset \downarrow \SET) $, which, since $ \emptyset $ is the initial set, is just equivalent to $ \SET $.
+\end{remark}
 
@@
   natural in $ n $ and $ A $.
-Explicitly, it sends $ F: \Alg T(T_n, A) $ to $ i \mapsto F(x_i) $ and $ (a_i)_i : A^n $ to $ f \mapsto f \bullet a $.
+Explicitly, it sends $ f: \Alg T(T_n, A) $ to $ i \mapsto f(x_i) $ and $ (a_i)_i : A^n $ to $ f \mapsto f \bullet a $.
 The natural equivalence immediately shows that $ T_n $ is the free $ T $-algebra on $ n $ elements.
 \end{remark}
+
+Using some additional machinery, we can combine this with the algebra pullback functor to get another functor:
+\begin{definition}\label{def:theory-algebra-pullback-functor}
+  Take a nonnegative integer $ n $.
+Take an object $ S : \AlgTh $.
+For every object $ T : \AlgTh $, we can take the $ T $-algebra $ T_n $.
+Then every morphism $ f: \AlgTh(S, T) $ gives an $ S $-algebra $ f^* T_n $.
+In fact, this is a functor from $ (S \downarrow \AlgTh) $ to $ \Alg S $: We send a morphism $ g: (S \downarrow \AlgTh)((T, f), (T^\prime, f^\prime)) $ to
+  \[ g_n: f^* T_n \to (f^\prime)^* T^\prime_n. \]
+  This is an algebra morphism because it commutes with $ f $, $ f^\prime $ and the substitution of $ T $ and $ T^\prime $: For $ s: S_m $ and $ t: (f^* T_n)^m $, we have
+  \[
+      g_n(s \bullet_{f^* T_n} t)
+    = g_m(f_m(s)) \bullet_{T^\prime} (g_n(t_i))_i
+    = s \bullet_{(f^\prime)^* T^\prime_n} (g_n(t_i))_i.
+  \]
+  The functor obviously preserves the identity morphisms and composition of morphisms, so it is indeed a functor.
+\end{definition}
 

### 2024-06-17 report/src/paper.tex
Show that the algebra pullback is functorial in the

@@
 In this section, we will provide an elementary proof of this theorem.
+Then, in the next section, we will give Hyland's original proof, which uses more high-level categorical reasoning.
 
@@
 
-In both cases, one part of the equivalence is very easy:
-\begin{definition}
-  For all $ n $, we have a functor from lambda theories to $ \Lambda $-algebras.
-It sends the $ \lambda $-theory $ L $ to the $ L $-algebra $ L_n $ and then turns this into a $ \Lambda $-algebra via the morpism $ \Lambda \to L $.
-It sends morphisms $ f: L \to L^\prime $ to the algebra morphism $ f_n : L_n \to L^\prime_n $.
-\end{definition}
+In both cases, one part of the equivalence is very easy.
+Recall that the pure $ \lambda $-calculus, the $ \lambda $-theory $ \Lambda $, is the initial object of $ \LamTh $.
+That means that $ \LamTh $ is equivalent to $ (\Lambda \downarrow \LamTh) $.
+Now, using Definition \ref{def:theory-algebra-pullback-functor}, for any $ n $ we get a functor
+\[ -_n : \LamTh \to \Alg \Lambda. \]
 Here we are only interested in the case $ n = 0 $.
 
-We will use Lemma \ref{lem:univalen-category-equivalence}, by showing that $ L \mapsto L_0 $ is a weak equivalence.
+We will use Lemma \ref{lem:univalen-category-equivalence}, by showing that $ -_0 $ is a weak equivalence.
 
@@
 
-\TODO show functoriality of pullback in coslice category.
-
 \begin{lemma}\label{lem:pullback-fully-faithful}
@@
   \end{center}
-  Now, using functoriality of the pullback of the theory algebras in the coslice category $ (E_{\R_A}(U) \downarrow \AlgTh) $, and using the previous lemma, we get the following diagram of $ E_{\R_A}(U) $-algebras:
+  Now, using Definition \ref{def:theory-algebra-pullback-functor} for the coslice category $ (E_{\R_A}(U) \downarrow \AlgTh) $, and using the previous lemma, we get the following diagram of $ E_{\R_A}(U) $-algebras:
   \begin{center}

### 2024-06-25 report/src/algebraic-structures.tex
Start writing about semi cartesian closed categories

@@
 
+\subsection{The $ \lambda $-calculus operations}\label{subsec:lambda-calculus-operations}
+Now, for a $ \lambda $-theory $ L $, we have variables $ x_{n, i} : L_n $ and $ \lambda $-abstraction $ f \mapsto \lambda(f) $.
+We will sometimes denote $ \lambda(f) $ as $ \lambda x_{n + 1}, f $ for $ f: L_{n + 1} $.
+Now, consider the element $ \rho(x_{1, 1}) : L_2 $.
+\begin{definition}
+  Using the substitution, we have binary operations on the $ L_n $, sending $ (f, g) : L_n \times L_n $ to $ \rho(x_{1, 1}) \bullet (f, g) : L_n $.
+\end{definition}
+We will denote $ \rho(x_{1, 1}) \bullet (f, g) $ as $ f g $, and this gives us our application operation, so we can interpret all three operations of the $ \lambda $-calculus in $ L $.
+
+\begin{remark}
+  Note that if $ L $ has $ \beta $-equality, we have
+  \[ \lambda(f) g = \rho(\lambda(f)) \bullet (x_1, \dots, x_n, g) = f \bullet (x_1, \dots, x_n, g), \]
+  so we have the usual $ \beta $ equality. In the same way $ \eta $-equality in $ L $ gives
+  \[ \lambda(\iota_{n, 1}(f) x_{n + 1}) = \lambda(\rho(f)) = f. \]
+\end{remark}
+\begin{remark}
+  Also that for $ f: L_n $,
+  \[ \rho(f) = \rho(x_1 \bullet f) = \iota_{n, 1}(f) x_{n + 1}. \]
+  Therefore, we can also think of the application as being the primary operation, from which we derive $ \rho $. In the same way, we have
+  \[ \rho^m(f) = \iota_{n, m}(f) x_{n + 1} \dots x_{n + m}. \]
+\end{remark}
+\begin{remark}
+  Note that for $ f, g : L_n $,
+  \[
+    \rho(f) \bullet (x_1, \dots, x_n, g)
+    = \rho(x_1) \bullet (\iota_{n, 1}(f), x_{n + 1}) \bullet (x_1, \dots, x_n, g)
+    = \rho(x_1) \bullet (\iota_{n, 1}(f), g),
+  \]
+  so we could also define the application as $ f g = \rho(f) \bullet (x_1, \dots, x_n, g) $, although that is more complicated.
+\end{remark}
+
 \section{Examples}
@@
 
+In this subsection, we will use the $ \lambda $-calculus operations defined in Subsection \ref{subsec:lambda-calculus-operations}.
+
 Like with the free algebraic theory, we will construct the free $ \lambda $-theory as the smallest nontrivial $ \lambda $-theory (which is the $ \lambda $-calculus) with some additional constants.
@@
     f(\mathtt{Var}(i)) &= x_i;\\
-    f(\mathtt{App}(a, b)) &= \rho(f(a)) \bullet ((x_{n, i})_i + (f(b)));\\
-    f(\mathtt{Abs}(a)) &= \lambda(f(a));\\
+    f(\mathtt{App}(a, b)) &= f(a) f(b);\\
+    f(\mathtt{Abs}(a)) &= \lambda x_{n + 1}, f(a);\\
     f(\mathtt{Con}(s)) &= g(s) \bullet ().
@@
 \end{proof}
+
+\begin{remark}
+  One can also consider this lemma a proof that we can `interpret' the $ \lambda $-calculus with some constants inside any $ \lambda $-theory $ L $ if we give an interpretation of the constants as terms in $ L_0 $.
+\end{remark}
 

### 2024-06-25 report/src/weak-cartesian-closed.tex
Start writing about semi cartesian closed categories

\chapter{Weak Cartesian Closed Categories}
In Definition \ref{def:endomorphism-theory}, we defined the endomorphism $ \lambda $-theory of a reflexive object in a cartesian closed category. However, as it turns out, we do not need all of the properties of a cartesian closed category. It suffices to consider a \textit{weak} cartesian closed category. In fact, even a `semi cartesian closed category' will suffice, but in this section, we will restrict ourselves to a weak cartesian closed category, as this notion suits our purposes well enough.

It seems that semi cartesian closed categories were first defined in \cite{hayashi-1985-semifunctors} and then \cite{hoofman-1993-semi-cartesian-closed} gave a slightly different definition, as well as the very related definition of a weak cartesian closed category. The latter paper also contains the construction of the endomorphism $ \lambda $-theory.

\begin{definition}
  Let $ C $ be a category with binary products (we will call the projections $ \pi_1 $ and $ \pi_2 $), and take $ A, B : C $. A \iindex{semi-exponential object} is an object $ A^B : C $, with a morphism $ \mathrm{ev}: C(A^B \times B \to A) $ and a hayashi-1985-semifunctorsfunction
  \[ \mathrm{cur}_X: C(X \times B \to A) \to C(X, A^B) \]
  for all $ X $, such that
  \[ \langle g \cdot \mathrm{cur}_X(f), h \rangle \cdot \mathrm{ev} = \langle g, h \rangle \cdot f \quad \text{and} \quad \mathrm{cur}_Y((g \times \id B) \cdot f) = g \cdot \mathrm{cur}_X(f) \]
  for all $ f: C(X \times B, A) $, $ g : C(Y, X) $ and $ h : C(Y, B) $.
\end{definition}

\begin{definition}
  A \textit{weak cartesian closed category}\index{cartesian closed category!weak} is a category $ C $ with a terminal object and binary products, together with a choice for a semi-exponential object $ A^B $ for all $ A, B : C $.
\end{definition}

\begin{definition}
  Let $ C $ a weak cartesian closed category. A \iindex{reflexive object} in $ C $ is an object $ U $ with morphisms $ f $ and $ g $, forming the following commutative diagram:
  \begin{center}
    \begin{tikzcd}
      U^U \arrow[dd, "\mathrm{cur}_{U^U}(\mathrm{ev})"'] \arrow[rd, "f"]\\
      & U \arrow[ld, "g"]\\
      U^U
    \end{tikzcd}
  \end{center}
\end{definition}

\begin{definition}
  If we have a reflexive object $ (U, f, g) $ in a weak cartesian closed category $ C $, we can endow the endomorphism algebraic theory $ E_C(U) $ (Definition \ref{def:endomorphism-theory}) with a $ \lambda $-theory structure with $ \beta $-equality, with
  \[ \rho(s) = ((s \cdot g) \times \id U) \cdot \mathrm{ev} : C(U^{n + 1}, U) \]
  and
  \[ \lambda(t) = \mathrm{cur}_{U^n}(t) \cdot f : C(U^n, U) \]
  for $ s: E(U)_n $ and $ t: E(U)_{n + 1} $.
\end{definition}

\begin{lemma}
  The definition above indeed yields a $ \lambda $-theory with $ \beta $-equality.
\end{lemma}
\begin{proof}
  We have
  \begin{align*}
    \rho(s \bullet t)
    &= ((\langle t_i \rangle_i \cdot (s \cdot g)) \times \id U) \cdot \mathrm{ev}\\
    &= (\langle t_i \rangle_i \times \id U) \cdot ((s \cdot g) \times \id U) \cdot \mathrm{ev}\\
    &= \rho(s) \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1, n + 1})),
  \end{align*}
  \begin{align*}
    \lambda(s) \bullet t
    &= \langle t_i \rangle_i \cdot \mathrm{cur}(t) \cdot f\\
    &= \mathrm{cur}_{U^n}((\langle t_i \rangle_i \times \id U) \cdot t) \cdot f\\
    &= \lambda(s \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1, n + 1})))
  \end{align*}
  and
  \begin{align*}
    \rho(\lambda(s))
    &= \langle \pi_1 \cdot \mathrm{cur}_{U^n}(t) \cdot \mathrm{cur}_{U^U}(\mathrm{ev}), \pi_2 \rangle \cdot \mathrm{ev}\\
    &= \langle \pi_1 \cdot \mathrm{cur}_{U^n}(t), \pi_2 \rangle \cdot \mathrm{ev}\\
    &= t.
  \end{align*}
\end{proof}

Now, we will show that the semi-exponential objects satisfy some properties that justify the use of the exponential notation. These properties allow us to construct semi-exponentials on products, from the semi-exponentials of their components.

\begin{lemma}
  Take $ A, A^\prime, B : C $. If $ A^B $ and $ {A^\prime}^B $ are semi-exponential objects, then $ A^B \times (A^\prime)^B $ is the semi-exponential object $ (A \times A^\prime)^B $.
\end{lemma}
\begin{proof}
  We have
  \begin{align*}
    \mathrm{ev} : C(A^B \times B \to A) \quad &\text{and} \quad \mathrm{ev}^\prime : C({A^\prime}^B \times B \to A^\prime),\\
    \mathrm{cur}_X: C(X \times B, A) \to C(X, A^B) \quad &\text{and} \quad \mathrm{cur}^\prime_X: C(X \times B, A^\prime) \to C(X, {A^\prime}^B).
  \end{align*}
  Define
  \[ \mathrm{ev}^{\prime \prime} = \langle \langle \pi_1 \cdot \pi_1, \pi_2 \rangle \cdot \mathrm{ev}, \langle \pi_1 \cdot \pi_2, \pi_2 \rangle \cdot \mathrm{ev} \rangle : C(A^B \times {A^\prime}^B, A \times A^\prime) \]
  and for $ f: C(X \times B, A \times A^\prime) $,
  \[ \mathrm{cur}^{\prime \prime}_X(f) = \langle \mathrm{cur}_X(f \cdot \pi_1), \mathrm{cur}_X(f \cdot \pi_2) \rangle : C(X, A^B \times A^{B^\prime}). \]
  These satisfy the required equations.
\end{proof}

\begin{lemma}
  Take $ A, B, B^\prime : C $. If $ A^B $ and $ (A^B)^{B^\prime} $ are semi-exponential objects, then $ (A^B)^{B^\prime} $ is the semi-exponential object $ A^{B \times B^\prime} $.
\end{lemma}
\begin{proof}
  We have
  \begin{align*}
    \mathrm{ev} : C(A^B \times B \to A) \quad &\text{and} \quad \mathrm{ev}^\prime : : C((A^B)^{B^\prime} \times B^\prime \to A^B),\\
    \mathrm{cur}_X: C(X \times B, A) \to C(X, A^B) \quad &\text{and} \quad \mathrm{cur}^\prime_X: C(X \times B^\prime, A^B) \to C(X, (A^B)^{B^\prime}).
  \end{align*}
  Define
  \[ \mathrm{ev}^{\prime \prime} = \langle (\id {(A^B)^{B^\prime}} \times \pi_2) \cdot \mathrm{ev}^\prime, \pi_2 \cdot \pi_1 \rangle \cdot \mathrm{ev} : C((A^B)^{B^\prime} \times (B \times B^\prime), A) \]
  and for $ f: C(X \times (B \times B^\prime), A) $,
  \[ \mathrm{cur}^{\prime \prime}_X(f) = \mathrm{cur}^\prime_X(\mathrm{cur}_{X \times B^\prime}(\langle \pi_1 \cdot \pi_1, \langle \pi_2, \pi_1 \cdot \pi_2 \rangle \rangle \cdot f)) : C(X, (A^B)^{B^\prime}). \]
  Then, for $ f: C(X \times (B \times B^\prime), A) $, $ g: C(Y, X) $ and $ h: C(Y, B \times B^\prime) $,
  \begin{align*}
    \langle g \cdot \mathrm{cur}^{\prime \prime}_X(f), h \rangle \cdot \mathrm{ev}^{\prime \prime}
    &= \langle \langle g \cdot \mathrm{cur}^\prime_X(\mathrm{cur}_{X \times B^\prime}(\langle \pi_1 \cdot \pi_1, \langle \pi_2, \pi_1 \cdot \pi_2 \rangle \rangle \cdot f)), h \cdot \pi_2 \rangle \cdot \mathrm{ev}^\prime, h \cdot \pi_1 \rangle \cdot \mathrm{ev}\\
    &= \langle \langle \langle g, h \cdot \pi_2 \rangle, h \cdot \pi_1 \rangle \cdot \pi_1 \cdot \pi_1, \langle \langle \langle g, h \cdot \pi_2 \rangle, h \cdot \pi_1 \rangle \cdot \pi_2, \langle \langle g, h \cdot \pi_2 \rangle, h \cdot \pi_1 \rangle \cdot \pi_1 \cdot \pi_2 \rangle \rangle \cdot f\\
    &= \langle g, h \rangle \cdot f
  \end{align*}
  and
  \begin{align*}
    \mathrm{cur}^{\prime \prime}_Y((g \times \id B) \cdot f)
    &= \mathrm{cur}^\prime_Y(\mathrm{cur}_{Y \times B^\prime}(((g \times \id{B^\prime}) \times \id B) \cdot \langle \pi_1 \cdot \pi_1, \langle \pi_2, \pi_1 \cdot \pi_2 \rangle \rangle \cdot f))\\
    &= \mathrm{cur}^\prime_Y((g \times \id{B^\prime}) \cdot \mathrm{cur}_{X \times B^\prime}(\langle \pi_1 \cdot \pi_1, \langle \pi_2, \pi_1 \cdot \pi_2 \rangle \rangle \cdot f))\\
    &= g \cdot \mathrm{cur}^\prime_X(\mathrm{cur}_{X \times B^\prime}(\langle \pi_1 \cdot \pi_1, \langle \pi_2, \pi_1 \cdot \pi_2 \rangle \rangle \cdot f)),\\
  \end{align*}
  which concludes the proof.
\end{proof}

Now, we can show that giving an algebraic theory a $ \lambda $-theory structure amounts to endowing its corresponding Lawvere theory (Lemma \ref{lem:lawvere-clone}) with a weak cartesian closed structure.
\begin{lemma}
  Let $ L $ be an algebraic theory. A weak cartesian closed category structure on its associated Lawvere theory gives a $ \lambda $-theory structure on $ L $.
\end{lemma}
\begin{proof}
  \TODO
\end{proof}

\begin{lemma}
  Let $ L $ be a $ \lambda $-theory. Then its corresponding Lawvere theory $ C $ is a weak cartesian closed category.
\end{lemma}
\begin{proof}
  Note that by definition of a Lawvere theory, every $ n: C $ is the $ n $-fold product of $ 1 $. Therefore, binary products are given by addition on the natural numbers, and $ 0 $ is the terminal object.

  \TODO
\end{proof}

### 2024-06-26 report/src/algebraic-structures.tex
Write about semi-closed structure

@@
 \end{definition}
+
+\begin{remark}
+  Hyland claims that `a $ \lambda $-theory is an algebraic theory $ L $ equipped with semi-closed structure'.
+By `semi-closed structure', he probably means the structure of a semi cartesian closed category on the Lawvere theory associated to $ L $ (Lemma \ref{lem:lawvere-clone}).
+Because a Lawvere theory has finite products, we even would have a weak cartesian closed category.
+For more information about weak cartesian closed categories, see Appendix \ref{ch:weak-cartesian-closed-categories}.
+
+  In the appendix, we see that a $ \lambda $-theory structure on an algebraic theory $ L $ gives its associated Lawvere theory $ C $ a weak cartesian closed structure with the exponential object $ 1^1 $ equal to $ 1 $.
+Conversely, we can give $ L $ a $ \lambda $-theory structure from a weak cartesian closed structure on $ C $ where $ 1 $ is a reflexive object.
+Note that we really need $ 1 $ to be a reflexive object to make the construction work.
+
+  However, note that a weak cartesian closed structure on $ C $ with $ 1 $ a reflexive object contains more information than a $ \lambda $-theory structure on $ L $: If we have a $ \lambda $-theory structure on $ L $, then construct from this a weak cartesian closed category structure with $ 1^1 = 1 $ on $ C $ and derive from this again a $ \lambda $-theory structure on $ L $, we get the same $ \lambda $-theory structure that we started out with.
+If, on the other hand, we go from a weak cartesian closed structure where $ 1 $ is a reflexive object to a $ \lambda $-theory structure and then to a weak cartesian closed structure again, we might end up with a different structure than the one that we started out with.
+This is because a weak cartesian closed structure is not necessarily unique up to isomorphism.
+In particular, we construct semi-exponential objects $ m^n $ which are equal to $ m $ for all $ m, n : C $, and derive their data, $ \mathrm{ev} $ and $ \mathrm{cur} $, from just the data of $ 1^1 $ in the original weak cartesian closed structure.
+Therefore, there are enough ways in which the resulting weak cartesian closed structure can differ from the original one.
+
+  Note that here, we really need a choice for the exponential objects.
+It is not enough to just ask for the mere existence of semi-exponential objects.
+This is because we need the information contained in $ \mathrm{ev}: L_2 $ and $ \mathrm{cur} : L_{n + 1} \to L_n $ to define $ \lambda $ and $ \rho $.
+\end{remark}
 

### 2024-06-26 report/src/weak-cartesian-closed.tex
Write about semi-closed structure

@@
-\chapter{Weak Cartesian Closed Categories}
+\chapter{Weak Cartesian Closed Categories}\label{ch:weak-cartesian-closed-categories}
 In Definition \ref{def:endomorphism-theory}, we defined the endomorphism $ \lambda $-theory of a reflexive object in a cartesian closed category.
@@
 
+\begin{remark}
+  Since the requirements for semi-exponential objects do not involve the usual universal properties, a weak cartesian closed structure (or a semi-exponential object) is not unique up to isomorphism.
+For example, see example 2.1 and 2.2 in \cite{hoofman-1993-semi-cartesian-closed} for two distinct weak cartesian closed structures on a category.
+\end{remark}
+
 \begin{definition}
-  Let $ C $ a weak cartesian closed category. A \iindex{reflexive object} in $ C $ is an object $ U $ with morphisms $ f $ and $ g $, forming the following commutative diagram:
+  A \iindex{reflexive object} in a category $ C $ with binary products is an object $ U $ with an exponential $ U^U $ and morphisms $ f $ and $ g $, forming the following commutative diagram:
   \begin{center}
@@
 \begin{definition}
-  If we have a reflexive object $ (U, f, g) $ in a weak cartesian closed category $ C $, we can endow the endomorphism algebraic theory $ E_C(U) $ (Definition \ref{def:endomorphism-theory}) with a $ \lambda $-theory structure with $ \beta $-equality, with
+  If we have a reflexive object $ (U, f, g) $ in a category $ C $ with finite products, we can endow the endomorphism algebraic theory $ E_C(U) $ (Definition \ref{def:endomorphism-theory}) with a $ \lambda $-theory structure with $ \beta $-equality, with
   \[ \rho(s) = ((s \cdot g) \times \id U) \cdot \mathrm{ev} : C(U^{n + 1}, U) \]
@@
 \begin{proof}
-  We have
+  Note that for morphisms $ f: C(U^{m + 1}, U) $ and $ g: C(U^n, U)^m $,
+  \[ (\langle g_i \rangle_i \times \id U) \cdot f = f \bullet (\iota_{n, 1}(g_1), \dots, \iota_{n, 1}(g_m), x_{n + 1}). \]
+  Then
   \begin{align*}
     \rho(s \bullet t)
-    &= ((\langle t_i \rangle_i \cdot (s \cdot g)) \times \id U) \cdot \mathrm{ev}\\
+    &= ((\langle t_i \rangle_i \cdot s \cdot g) \times \id U) \cdot \mathrm{ev}\\
     &= (\langle t_i \rangle_i \times \id U) \cdot ((s \cdot g) \times \id U) \cdot \mathrm{ev}\\
-    &= \rho(s) \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1, n + 1})),
+    &= \rho(s) \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1})),
   \end{align*}
@@
     &= \mathrm{cur}_{U^n}((\langle t_i \rangle_i \times \id U) \cdot t) \cdot f\\
-    &= \lambda(s \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1, n + 1})))
+    &= \lambda(s \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1}))),
   \end{align*}
-  and
+  where we use the property of $ \mathrm{cur} $, and
   \begin{align*}
@@
     &= \langle \pi_1 \cdot \mathrm{cur}_{U^n}(t), \pi_2 \rangle \cdot \mathrm{ev}\\
-    &= t.
+    &= t
   \end{align*}
+  where we use the property of $ \mathrm{ev} $ twice.
 \end{proof}
 
+We get the following as a special case, in which $ U^U $ is not only a retract of $ U $, but actually equal to $ U $.
+\begin{corollary}
+  Let $ L $ be an algebraic theory.
+Suppose that its associated Lawvere theory $ C $ is a weak cartesian closed category and suppose that for $ 1 : C $, we have $ 1^1 = 1 $.
+Then we can give $ L $ a $ \lambda $-theory structure with $ \beta $ equality, given by
+  \[ \lambda_n(s) = \mathrm{cur}_n(s) \quad \text{and} \quad \rho(t) = \mathrm{ev} \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1})). \]
+\end{corollary}
+
 Now, we will show that the semi-exponential objects satisfy some properties that justify the use of the exponential notation.
-These properties allow us to construct semi-exponentials on products, from the semi-exponentials of their components.
+These properties allow us to construct semi-exponentials on products from the semi-exponentials of their components.
+\begin{remark}
+  Note that in a category $ C $ with a terminal object $ I $, we have exponential objects
+  \[ A^I = A \quad \text{and} \quad I^A = I \]
+  for all objects $ A $. Therefore, we get semi-exponential objects for free if we have a terminal object.
+\end{remark}
 
@@
 
-Now, we can show that giving an algebraic theory a $ \lambda $-theory structure amounts to endowing its corresponding Lawvere theory (Lemma \ref{lem:lawvere-clone}) with a weak cartesian closed structure.
-\begin{lemma}
-  Let $ L $ be an algebraic theory. A weak cartesian closed category structure on its associated Lawvere theory gives a $ \lambda $-theory structure on $ L $.
-\end{lemma}
-\begin{proof}
-  \TODO
-\end{proof}
-
+Now, we can show that giving an algebraic theory a $ \lambda $-theory structure gives its corresponding Lawvere theory (Lemma \ref{lem:lawvere-clone}) a weak cartesian closed structure.
 \begin{lemma}
@@
 
-  \TODO
+  Now, we define $ 1^1 = 1 $, with
+  \[ \mathrm{ev} = \rho(x_1) : C(2, 1) \quad \text{and} \quad \mathrm{cur}_n(f) = \lambda(f) : C(n, 1) \]
+  for $ f: C(n + 1, 1) $. The following shows that this is indeed a semi-exponential object:
+  \[
+    \rho(x_1) \bullet (\lambda(f) \bullet g, h) = \rho(x_1 \bullet \lambda(f)) \bullet (g + (h)) = f \bullet (g + (h)) \]
+  and
+  \[ \lambda(f \bullet ((\iota_{n, 1}(g_i))_i + (x_{n + 1, n + 1}))) = \lambda(f) \bullet g \]
+  Now, by the remark and the lemmas above, we have for $ m, n: C $ (both nonzero),
+  \[ m^n = (1 \times \dots \times 1)^n = 1^n \times \dots \times 1^n \]
+  and
+  \[ 1^n = 1^{1 \times \dots \times 1} = ((1^1)^1\dots)^1 = 1 \]
+  so $ C $ has semi-exponential objects and it is a weak cartesian closed category.
 \end{proof}

### 2024-06-26 report/src/algebraic-structures.tex
Write about the original representation theorem, write about cartesian closedness when L has both beta and eta equality

--- 2024-06-25 report/src/algebraic-structures.tex
@@
 
-Together, these form the category of $ \lambda $-theories \iindex{$ \LamTh $}.
+\begin{remark}
+  Hyland claims that `a $ \lambda $-theory is an algebraic theory $ L $ equipped with semi-closed structure'.
+By `semi-closed structure', he probably means the structure of a semi cartesian closed category on the Lawvere theory associated to $ L $ (Lemma \ref{lem:lawvere-clone}).
+Because a Lawvere theory has finite products, we even would have a weak cartesian closed category.
+For more information about weak cartesian closed categories, see Appendix \ref{ch:weak-cartesian-closed-categories}.
+
+  In the appendix, we see that a $ \lambda $-theory structure with $ \beta $-equality on an algebraic theory $ L $ gives its associated Lawvere theory $ C $ a weak cartesian closed structure with the exponential object $ 1^1 $ equal to $ 1 $.
+Conversely, we can give $ L $ a $ \lambda $-theory structure with $ \beta $-equality from a weak cartesian closed structure on $ C $ where $ 1 $ is a reflexive object.
+Note that we really need $ 1 $ to be a reflexive object to make the construction work.
+
+  However, note that a weak cartesian closed structure on $ C $ with $ 1 $ a reflexive object contains more information than a $ \lambda $-theory structure with $ \beta $-equality on $ L $: If we have a $ \lambda $-theory structure with $ \beta $-equality on $ L $, then construct from this a weak cartesian closed category structure with $ 1^1 = 1 $ on $ C $ and derive from this again a $ \lambda $-theory structure on $ L $, we get the same $ \lambda $-theory structure that we started out with.
+If, on the other hand, we go from a weak cartesian closed structure where $ 1 $ is a reflexive object to a $ \lambda $-theory structure with $ \beta $-equality and then to a weak cartesian closed structure again, we might end up with a different structure than the one that we started out with.
+This is because a weak cartesian closed structure is not necessarily unique up to isomorphism.
+In particular, we construct semi-exponential objects $ m^n $ which are equal to $ m $ for all $ m, n : C $, and derive their data ($ \mathrm{ev} $ and $ \mathrm{cur} $) from just the data of $ 1^1 $ in the original weak cartesian closed structure.
+Therefore, there are enough ways in which the resulting weak cartesian closed structure can differ from the original one.
+
+  Note that here, we really need a choice for the exponential objects.
+It is not enough to just ask for the mere existence of semi-exponential objects.
+This is because we need the information contained in $ \mathrm{ev}: L_2 $ and $ \mathrm{cur} : L_{n + 1} \to L_n $ to define $ \lambda $ and $ \rho $.
+
+  Lastly, if $ L $ has both $ \beta $- and $ \eta $-equality, the weak cartesian closed structure becomes a cartesian closed structure, which is unique, so in that case, giving an algebraic theory $ L $ a $ \lambda $-theory structure with $ \beta $- and $ \eta $-equality is the same as giving its associated Lawvere theory a cartesian closed category structure.
+\end{remark}
 
@@
 
+Together, these form the category of $ \lambda $-theories \iindex{$ \LamTh $}.
+
 \begin{remark}
@@
   Using the substitution, we have binary operations on the $ L_n $, sending $ (f, g) : L_n \times L_n $ to $ \rho(x_{1, 1}) \bullet (f, g) : L_n $.
+We will denote $ \rho(x_{1, 1}) \bullet (f, g) $ as $ f g $, and this gives us our application operation.
 \end{definition}
-We will denote $ \rho(x_{1, 1}) \bullet (f, g) $ as $ f g $, and this gives us our application operation, so we can interpret all three operations of the $ \lambda $-calculus in $ L $.
+This means that we can interpret all three operations of the $ \lambda $-calculus in $ L $.
 
@@
   \[ \lambda(f) g = \rho(\lambda(f)) \bullet (x_1, \dots, x_n, g) = f \bullet (x_1, \dots, x_n, g), \]
-  so we have the usual $ \beta $ equality. In the same way $ \eta $-equality in $ L $ gives
+  so we have the usual $ \beta $-equality. In the same way $ \eta $-equality of $ L $ gives
   \[ \lambda(\iota_{n, 1}(f) x_{n + 1}) = \lambda(\rho(f)) = f. \]
@@
 \begin{remark}
-  Also that for $ f: L_n $,
+  Also note that for $ f: L_n $,
   \[ \rho(f) = \rho(x_1 \bullet f) = \iota_{n, 1}(f) x_{n + 1}. \]

### 2024-06-26 report/src/paper.tex
Write about the original representation theorem, write about cartesian closedness when L has both beta and eta equality

@@
 \end{proof}
+
+\begin{remark}
+  Actually, in this thesis we stumbled upon another category with a reflexive object that exhibits $ L $ as its endomorphism theory, provided that $ L $ has $ \beta $-equality: In Appendix \ref{ch:weak-cartesian-closed-categories}, we see that the Lawvere theory $ C $ associated to $ L $ is a weak cartesian closed category, in which $ 1^1 = 1 $.
+It is then easy to see that the endomorphism theory that we obtain from this reflexive object $ 1 $ is exactly equal to $ L $.
+
+  Note, however, that this is technically not an answer to Scott's original theorem, because the original formulation asks for a cartesian closed category with a reflexive object, whereas here we only have a reflexive object in a weak cartesian closed category.
+Even so, it is an answer to the core of the question, which is about whether we can represent any $ \lambda $-theory as the sets of morphisms $ C(U^n, U) $ for some $ U : C $.
+\end{remark}
 

### 2024-06-26 report/src/weak-cartesian-closed.tex
Write about the original representation theorem, write about cartesian closedness when L has both beta and eta equality

@@
 Suppose that its associated Lawvere theory $ C $ is a weak cartesian closed category and suppose that for $ 1 : C $, we have $ 1^1 = 1 $.
-Then we can give $ L $ a $ \lambda $-theory structure with $ \beta $ equality, given by
+Then we can give $ L $ a $ \lambda $-theory structure with $ \beta $-equality, given by
   \[ \lambda_n(s) = \mathrm{cur}_n(s) \quad \text{and} \quad \rho(t) = \mathrm{ev} \bullet ((\iota_{n, 1}(t_i))_i + (x_{n + 1})). \]
@@
 \begin{lemma}
-  Let $ L $ be a $ \lambda $-theory. Then its corresponding Lawvere theory $ C $ is a weak cartesian closed category.
+  Let $ L $ be a $ \lambda $-theory with $ \beta $-equality. Its corresponding Lawvere theory $ C $ is a weak cartesian closed category.
 \end{lemma}
@@
   for $ f: C(n + 1, 1) $. The following shows that this is indeed a semi-exponential object:
-  \[
-    \rho(x_1) \bullet (\lambda(f) \bullet g, h) = \rho(x_1 \bullet \lambda(f)) \bullet (g + (h)) = f \bullet (g + (h)) \]
+  \[ \rho(x_1) \bullet (\lambda(f) \bullet g, h) = \rho(x_1 \bullet \lambda(f)) \bullet (g + (h)) = f \bullet (g + (h)) \]
   and
@@
 \end{proof}
+
+\begin{remark}
+  Note that if $ L $ has both $ \beta $- and $ \eta $-equality, then for $ 1^1 $,
+  \[ \mathrm{cur}: C(n + 1, 1) \to C(n, 1), \]
+  which is given by $ \lambda $, has an inverse given by $ \rho $.
+Furthermore, since $ \lambda $ and $ \rho $ respect substitution, these constitute a natural isomorphism between $ C(- + 1, 1) $ and $ C(-, 1) $, so the semi-exponential object $ 1^1 = 1 $ is in fact an exponential object.
+Then we have for all $ m $ and $ n $, an exponential object
+  \[ m^n = (1 \times \dots \times 1)^{1 \times \dots \times 1} = 1^{1 \times \dots \times 1} \times \dots \times 1^{1 \times \dots \times 1} = 1 \times \dots \times 1 = m, \]
+  so $ C $ is cartesian closed.
+\end{remark}

### 2024-06-26 report/src/paper.tex
Write about the Yoneda lemma

@@
 \section{Scott's Representation Theorem}
+
+Now, Scott's representation theorem, which asks whether we can represent any $ \lambda $-theory as the endomorphism theory of some reflexive object in some cartesian closed category, can be answered using the presheaf category.
 \begin{theorem}\label{thm:representation-theorem}
-  Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E(L) $ of $ L: \Pshf L $, which is $ L $, viewed as a presheaf in its own presheaf category.
+  Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E_{\Pshf L}(L) $, with $ L $ viewed as a presheaf.
 \end{theorem}
@@
 \end{proof}
+So Hyland shows that the representation theorem follows largely from the fact that the functions from $ L_n $ to itself can be represented by $ L_{n + 1} $, together with the Yoneda lemma for the Lawvere theory associated to $ L $ (Remark \ref{rem:presheaf-Yoneda}).
+
+This proof is particularly nice, because it does not require $ \beta $- or $ \eta $-equality, but if $ L $ has $ \beta $- or $ \eta $-equality, then we can immediately see (even without the isomorphism from the theorem) that the endomorphism theory also has this property.
 

### 2024-07-23 report/src/algebraic-structures.tex
Write about universal algebra

@@
   The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying sets.
+\end{remark}
+
+\begin{remark}
+  The notions of algebraic theories and their algebras stem from the field of \iindex{universal algebra}.
+In universal algebra, one studies the `collections of algebraic structures'.
+For example, the collection of monoids: a monoid is a set with an associative binary operation and an identity element.
+Other examples of collections are those of abelian monoids, (abelian) groups or (commutative) rings.
+As we will see in Example \ref{ex:free-monoid-theory}, one can construct an algebraic theory $ T $ such that the category of monoids is equivalent to $ \Alg T $, and we can do very similar things for the other structures mentioned.
+Therefore, one could say that universal algebra studies algebraic theories and their algebras (or `models').
+
+  Any category that is equivalent to $ \Alg T $ for some algebraic theory $ T $ is called \iindex{algebraic}.
+For example, in Remark \ref{rem:free-theory-algebra-set}, we will see that $ \SET $ is algebraic.
+By the remark above, an algebraic category has all limits.
+It turns out that it also has all colimits (see Lemma \ref{lem:algebra-coproducts} for binary coproducts, or \autocite{algebraic-theories-2010}, Part 1, Theorem 4.5 for general colimits).
+Note, however, that this proof is a lot more complicated than the proof about limits, just like colimits of algebraic objects usually are more complicated than limits.
+For example, consider (binary) coproducts of groups.
 \end{remark}
@@
 
+\begin{remark}
+  Now, there are two ways to study $ \lambda $-calculus-like structures using the tools given here.
+We can study $ \lambda $-theories, which by the reasoning above have a $ \lambda $-calculus structure.
+Alternatively, we can try to study the $ \lambda $-calculus-like structures as algebras for some algebraic theory $ \Lambda $.
+However, it is not clear beforehand that this will succeed, because there is no reason why this category should be algebraic.
+In particular, $ \lambda $-abstraction causes problems, because it is not an algebraic operation.
+Of course, we can still do exactly the same as in Example \ref{ex:free-monoid-theory}: We can let $ \Lambda_n $ be the set of $ \Lambda $-terms with constants $ x_1, \dots, x_n $, which we can also regard as free variables (see Definition \ref{def:pure-lambda-calculus}), and study the category $ \Alg \Lambda $.
+
+  Later on, we will see that these two ways of studying $ \lambda $-calculus-like structures do coincide: we will see that the category $ \LamTh $ is indeed algebraic, and moreover, that the objects of $ \Alg \Lambda $ are equivalent to $ \lambda $-theories.
+\end{remark}
+
 \section{Examples}
@@
 
-\begin{remark}
+\begin{remark}\label{rem:free-theory-algebra-set}
   Note that the category of $ F(\emptyset) $-algebras is equivalent to the coslice-category $ (\emptyset \downarrow \SET) $, which, since $ \emptyset $ is the initial set, is just equivalent to $ \SET $.
@@
 
+\begin{definition}\label{def:pure-lambda-calculus}
+  We define the `pure' $ \lambda $-calculus $ \Lambda $ to be $ \Lambda(\emptyset) $.
+\end{definition}
+
 \begin{corollary}
-  The `pure' lambda calculus is the initial $ \lambda $-theory.
+  $ \Lambda $ is the initial $ \lambda $-theory.
 \end{corollary}
-\begin{proof}
-  If we take $ S = \emptyset $, $ \Lambda(\emptyset) $ is the lambda calculus, which we will call $ \Lambda $.
-We have, like with the free algebraic theory, that $ \Lambda(\emptyset) $ is the initial $ \lambda $-theory.
-\end{proof}
 

### 2024-07-23 report/src/paper.tex
Write about universal algebra

@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:algebra-coproducts}
   Let $ T $ be an algebraic theory. The category of $ T $-algebras has coproducts.
@@
 \begin{proof}
-  This is shown in \autocite{algebaric-theories-2010}, in the lemmas leading up to Theorem 4.5.
+  This is shown in \autocite{algebraic-theories-2010}, in the lemmas leading up to Theorem 4.5.
 

### 2024-07-26 report/src/algebraic-structures.tex
Show that f is an isomorphism if its pullback functor is an equivalence

@@
 \begin{remark}
-  \TODO Say something about universal algebra
   For equivalent definitions of different kinds, see Chapter \ref{ch:alternative-definitions}.
@@
 \begin{proof}
-  \TODO
+  \TODO Move to after the theory algebra, because we need that.
+
+  Note that to show that $ f $ is an isomorphism, we only need to show that the $ f_n $ are bijections.
+From the fact that we have inverse functions $ g_n : \SET(T, T^\prime) $ for the $ f_n $, and the fact that $ f $ is an algebraic theory morphism, we know that $ (g_n)_n $ is an algebraic theory morphism as well, and that it is the inverse of $ f $.
+
+  First of all, note that for all $ n : \mathbb N $ and $ B : \Alg T $, the following diagram in $ \SET $ commutes:
+  \begin{center}
+    \begin{tikzcd}
+      \Alg T(T_n, B) \arrow[r, "f^*"] \arrow[d, "\sim"] & \Alg{T^\prime}(f^* T_n, f^* B) \arrow[d, "\bar f_n \cdot -"]\\
+      B^n \arrow[r, "\sim"] & \Alg{T^\prime}(T^\prime_n, f^* B)
+    \end{tikzcd}
+  \end{center}
+  % \[ (g : T_n \to B) \mapsto (g: T_n \to B) \mapsto (f \cdot g : T^\prime_n \to B) \]
+  % \[ (g : T_n \to B) \mapsto ((g x_i)_i : B^n) \mapsto (s \mapsto s \bullet_{f^* B} (g x_i)_i) \]
+  % \[
+  %   s \bullet_{f^* B} (g x_i)_i
+  %   = f(s) \bullet (g x_i)_i
+  %   = g(f(s) \bullet (x_i)_i)
+  %   = g(f(s))
+  % \]
+  with $ \bar f_n: T^\prime_n \to f^* T_n $ the $ T^\prime $-algebra morphism with underlying function $ f_n $.
+Note that $ f^* $ is fully faithful, so the function at the top is a bijection, and so precomposition by $ \bar f_n $ is a bijection as well.
+Since $ f^* $ is essentially surjective, we have for all $ A : \Alg T^\prime $, some $ B : \Alg T $ and an isomorphism $ h: f^* B \xrightarrow \sim A $, which gives the following commutative diagram:
+  \begin{center}
+    \begin{tikzcd}
+      \Alg{T^\prime}(f^* T_n, f^* B) \arrow[d, "\bar f_n \cdot -", "\sim"'] \arrow[r, "- \cdot h"', "\sim"] & \Alg{T^\prime}(f^* T_n, A) \arrow[d, "\bar f_n \cdot -"]\\
+      \Alg{T^\prime}(T^\prime_n, f^* B) \arrow[r, "- \cdot h"', "\sim"] & \Alg{T^\prime}(T^\prime_n, A)
+    \end{tikzcd}
+  \end{center}
+  so the arrow on the right is an equivalence as well.
+Taking $ A = T^\prime_n $, there exists some $ g: \Alg{T^\prime}(f^* T_n, T^\prime_n) $ such that $ \bar f_n \cdot g = \id{T^\prime_n} $.
+Also, note that
+  \[ \bar f_n \cdot g \cdot \bar f_n = \bar f_n \cdot \id{f^* T_n} \]
+  so taking $ A = f^* T_n $, we see that
+  \[ g \cdot \bar f_n = \id{f^* T_n}, \]
+  so $ f_n $, the underlying function of $ \bar f_n $, is a bijection, with inverse $ g $.
 \end{proof}
+
+\begin{remark}
+  Hyland's proof of this fact is almost the same, but in the last part, he uses some category theory. Instead of explicitly constructing the inverse, he notices that the bijection
+  \[ \Alg{T^\prime}(f^* T_n, A) \xrightarrow[\bar f_n \cdot -] \sim \Alg{T^\prime}(T^\prime_n, A) \]
+  is in fact the image of $ \bar f_n $ under the (covariant) Yoneda embedding of $ \Alg{T^\prime} $ into the functor category $ \Alg{T^\prime} \to \SET $:
+  \[ \hat Y(\bar f_n): \hat Y(f^* T_n) \to \hat Y(T^\prime_n). \]
+  Since the Yoneda embedding is fully faithful, this shows that $ \bar f_n $ is an isomorphism of $ T^\prime $-algebras, so in particular, it is a bijection.
+\end{remark}
 
@@
 
-\begin{remark}
+\begin{remark}\label{rem:lambda-theory-or-algebra}
   Now, there are two ways to study $ \lambda $-calculus-like structures using the tools given here.
@@
 
-\begin{example}
+\begin{example}\label{ex:free-lambda-theory}
   We can give the sequence of sets $ \Lambda(S) $ an algebraic theory structure with variables $ x_{m, i} = \mathtt{Var}_m(i) $ and the substitution operator $ \bullet $ defined above.

### 2024-08-24 report/src/category-theory.tex
Show that the Yoneda embedding preserves binary products and exponential objects

@@
 \begin{lemma}
-  For any $ c: C $ and $ F : PC $, we have an equivalence $ PC(Y(c), F) \simeq F(c) $, and this equivalence is natural in $ c $ and $ F $.
-\end{lemma}
-\begin{proof}
-  See \autocite{Kashiwara}, Proposition 1.4.3.
-\end{proof}
-
-\begin{lemma}
-  The Yoneda embedding functor preserves limits.
-\end{lemma}
-\begin{proof}
-  See \autocite{borceux}, Volume 1, Proposition 2.15.5.
-\end{proof}
-
-\begin{lemma}
-  The Yoneda embedding functor is \iindex{cartesian}. That is, not only does it preserve binary products, but it also preserves exponential objects (\autocite{stackexchange:yoneda-exponentials}).
-\end{lemma}
-\begin{proof}
-  \TODO
+  For any $ A: C $ and $ F : P C $, we have an equivalence $ P C(Y(A), F) \simeq F(A) $, and this equivalence is natural in $ c $ and $ F $.
+\end{lemma}
+\begin{proof}
+  It sends a natural transformation $ \alpha: P C(Y(A), F) $ to the element $ \alpha_A(\id A) $.
+Conversely, it sends an element $ x : P(A) $ to the natural transformation $ \alpha $ given by $ \alpha_B(f) = P(f)(x) $ for all $ f: Y(A)(B) = C(B, A) $.
+For more details, see \autocite{Kashiwara}, Proposition 1.4.3.
+\end{proof}
+
+\begin{remark}
+  For any category $ D $, the category $ [C, D] $ has (co)limits of some kind (terminal or initial object, (co)products, (co)equalizers) iff $ D $ does.
+These (co)limits are computed pointwise: for example, for binary products, $ (F \times G)(X) = F(X) \times G(X) $.
+In particular $ P C $ has all limits and colimits because $ \SET $ has all limits and colimits.
+\end{remark}
+
+\begin{remark}
+  Also, for any small category $ C $ (small means that the collection of objects is a type in our type universe.
+For example: $ \TYPE $ or $ \SET $ are not small categories, because a type cannot contain itself), the presheaf category $ P C $ has exponential objects, given by
+  \[ (F^G)(X) = \hom{PC}(Y(X) \times G, F) \]
+  the natural transformations from the product functor of the Yoneda embedding of $ X $ and $ G $, to $ F $ (see \autocite{MacLane-Moerdijk}, Section I.6, Proposition 1).
+\end{remark}
+
+\begin{definition}
+  Suppose that we have a functor $ F: C \to D $, and $ C $ and $ D $ both have binary products.
+Then for $ A, B : C $, we have morphisms $ \pi_1: A \times B \to A $ and $ \pi_2 : A \times B \to B $ and applying $ F $ to these yields morphisms from $ F(A \times B) $ to $ F(A) $ and $ F(B) $.
+We then have a product morphism
+  \[ \langle F(\pi_1), F(\pi_2) \rangle: F(A \times B) \to F(A) \times F(B). \]
+  Now, if this morphism is an isomorphism for all $ A, B : C $, we say that $ F $ \index{preservation of binary products}\textit{preserves binary products}.
+
+  One can imagine that there exists a similar definition of preservation of limits in general, in which the limit morphism of $ F $ applied to the projections from the limit is an isomorphism for any limit in $ C $.
+\end{definition}
+
+\begin{definition}\label{def:exponentials-preservation}
+  Suppose that we have a functor $ F: C \to D $ that preserves binary products, and $ C $ and $ D $ have exponential objects. Then for $ A, B : C $, we have natural bijections
+  \[ \varphi: C(A^B \times B, A) \xrightarrow \sim C(A^B, A^B) \quad \text{and} \quad \psi: D(F(A^B) \times F(B), F(A)) \xrightarrow \sim D(F(A^B), F(A)^{F(B)}) \]
+  This gives a morphism $ F(\varphi^{-1}(\id{A^B})) : D(F(A^B \times B), F(A)) $.
+Precomposing with the inverse of the isomorphism $ f: F(A^B \times B) \xrightarrow \sim F(A^B) \times F(B) $ and applying $ \psi $ gives
+  \[ \psi(f^{-1} \cdot \varphi^{-1}(\id{A^B})) : D(F(A^B), F(A)^{F(B)}). \]
+  We say that $ F $ \index{preservation of exponentials}\textit{preserves exponentials} if this morphism is an isomorphism for all $ A, B : C $.
+A name for a functor that preserves exponentials is a\iindex{cartesian functor}.
+\end{definition}
+
+\begin{lemma}
+  The Yoneda embedding preserves limits.
+\end{lemma}
+\begin{proof}
+  See \autocite{borceux}, Volume 1, Proposition 2.15.5 for the full proof, but note that for binary products, we have bijections
+  \[ Y(A \times B)(X) \xrightarrow \sim Y(A)(X) \times Y(B)(X) \]
+  sending $ f : C(X, A \times B) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(X, A) \times Y(X, B) $ to the product morphism $ \langle g_1, g_2 \rangle : Y(X, A \times B) $.
+This idea is the core of the proof about all limits.
+\end{proof}
+
+\begin{lemma}
+  The Yoneda embedding preserves exponentials.
+\end{lemma}
+\begin{proof}
+  First of all, note that for $ A, B, X : C $, we have a sequence of isomorphisms  (\autocite{stackexchange:yoneda-exponentials})
+  \begin{align*}
+    Y(A^B)(X) &\cong P C(Y(X), Y(A^B))\\
+    &\cong C(X, A^B)\\
+    &\cong C(X \times B, A)\\
+    &\cong P C(Y(X \times B), Y(A))\\
+    &\cong P C(Y(X) \times Y(B), Y(A))\\
+    &\cong P C(Y(X), Y(A)^Y(B))\\
+    &\cong (Y(A)^Y(B))(X)
+  \end{align*}
+  using (once or twice) the Yoneda lemma, fully faithfulness of the Yoneda embedding, the property of the exponential object, and the fact that the Yoneda embedding preserves binary products.
+
+  Some calculating shows that when applying this isomorphism to some $ f: Y(A^B)(X) $, we get the natural transformation $ h: P C(Y(X) \times Y(B), Y(A)) $ given by
+  \[ h_Z(g_1, g_2) = \langle g_1, g_2 \rangle \cdot \varphi^{-1}(f) \]
+  for all $ Z: C $ and $ (g_1, g_2) : Y(X)(Z) \times Y(B)(Z) $ and with the natural bijection
+  \[ \varphi: C(X \times B, A) \xrightarrow \sim C(X, A^B). \]
+
+  It turns out that when we apply the morphism in Definition \ref{def:exponentials-preservation} to $ f $, we get exactly the same natural transformation.
+Therefore, the morphism in Definition \ref{def:exponentials-preservation} is the isomorphism defined here and we conclude that $ Y $ preserves exponentials.
 \end{proof}

### 2024-09-02 talks/t05-categories-of-retracts/presentation.tex
Add a 5-page document about Hyland's proof of Taylor's fibration

\documentclass{amsart}

\usepackage{tikz-cd}
\usepackage{tabularx}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\renewcommand{\tabularxcolumn}[1]{m{#1}}

\DeclareFontFamily{U}{dmjhira}{}
\DeclareFontShape{U}{dmjhira}{m}{n}{ <-> dmjhira }{}

\DeclareRobustCommand{\yo}{\text{\usefont{U}{dmjhira}{m}{n}\symbol{"48}}}

\DeclareMathOperator\Psh{Psh}
\DeclareMathOperator\id{id}

\title{The categories of retracts}

\begin{document}
  \maketitle

  \section*{Locally cartesian closed}

  Let $ C $ be any category, and take $ f: C(B, A) $.
  \begin{center}
    \begin{tikzcd}
      C \downarrow A \arrow[r, "f^*", description] & C \downarrow B \arrow[l, "\sum_f"', bend right] \arrow[l, "\prod_f", bend left]
    \end{tikzcd}
  \end{center}

  \section*{Relatively cartesian closed}
  Some categories do not have $ f^* $ or $ \prod_f $ for all $ f $. But sometimes we can choose full subcategories of `display maps' (or `fibrations') $ C \downarrow_H B \subseteq C \downarrow B $ such that
  \begin{itemize}
    \item Composition of display maps is a display map;
    \item Terminal projections are display maps (so $ C \downarrow_H T = C \downarrow T \simeq C $);
    \item Pullbacks of display maps along any map exist.
  \end{itemize}
  \begin{center}
    \begin{tikzcd}
      C \downarrow_H A \arrow[r, "f^*" description] & C \downarrow_H B \arrow[l, "\sum_f"', bend right] \arrow[l, "\prod_f", bend left]
    \end{tikzcd}
  \end{center}
  Cartesian closed relative to $ H $ if $ f^* $ has a right adjoint.

  \newpage

  Let $ A $ be a category. Let $ \yo: A \hookrightarrow \Psh A $ be the Yoneda embedding. Let $ B, C, D $ be the categories given by:

  \section*{Scott's version}

  \[ B_0 = \sum_{X : A}\ \sum_{f : A(X, X)} f \cdot f = f \]
  \[ B((X_1, f_1), (X_2, f_2)) = \{ g: A(X_1, X_2) \mid f_1 \cdot g \cdot f_2 = g \}: \]
  \begin{center}
    \begin{tikzcd}
      X_1
        \arrow["f_1"', loop, distance=2em, in=-150, out=150]
        \arrow[r, "g"] &
      X_2
        \arrow["f_2"', loop, distance=2em, in=30, out=-30]
    \end{tikzcd}
  \end{center}

  \section*{First interpretation of the equivalent notion}

  \[ C_0 = \sum_{P : \Psh A}\ \sum_{X : A}\ \sum_{s: A(P, \yo(X))}\ \sum_{r: A(\yo(X), P)} s \cdot r = \id \]
  \[ C((P_1, X_1, r_1, s_1), (P_2, X_2, r_2, s_2)) = \Psh A(P_1, P_2): \]
  \begin{center}
    \begin{tikzcd}
      \yo(X_1) \arrow[r, "r_1", bend left] &
      P_1 \arrow[r, "g"] \arrow[l, "s_1", bend left] &
      P_2 \arrow[r, "s_2", bend left] &
      \yo(X_2) \arrow[l, "r_2", bend left]
    \end{tikzcd}
  \end{center}

  \section*{Second interpretation of the equivalent notion}

  \[ D_0 = \sum_{P : \Psh A} \left\Vert \sum_{X : A}\ \sum_{s: A(P, \yo(X))}\ \sum_{r: A(\yo(X), P)} s \cdot r = \id \right\Vert \]
  \[ D((P_1, X_1, r_1, s_1), (P_2, X_2, r_2, s_2)) = \Psh A(P_1, P_2): \]
  \begin{center}
    \begin{tikzcd}
      \mathit{\yo(X_1)} \arrow[r, "r_1", bend left, dashed] &
      P_1 \arrow[l, "s_1", bend left, dashed] \arrow[r, "g"] &
      P_2 \arrow[r, "s_2", bend left, dashed] &
      \mathit{\yo(X_2)} \arrow[l, "r_2", bend left, dashed]
    \end{tikzcd}
  \end{center}

  \newpage

  \begin{center}
    \begin{tabularx}{.7\textwidth}{c >{\centering\arraybackslash}X}
      B &
      \begin{tikzcd}[ampersand replacement = \&]
        X_1
          \arrow["f_1"', loop, distance=2em, in=-150, out=150]
          \arrow[r, "g"] \&
        X_2
          \arrow["f_2"', loop, distance=2em, in=30, out=-30]
      \end{tikzcd}\\
      C &
      \begin{tikzcd}[ampersand replacement = \&]
        \yo(X_1) \arrow[r, "r_1", bend left] \&
        P_1 \arrow[r, "g"] \arrow[l, "s_1", bend left] \&
        P_2 \arrow[r, "s_2", bend left] \&
        \yo(X_2) \arrow[l, "r_2", bend left]
      \end{tikzcd}\\
      D &
      \begin{tikzcd}[ampersand replacement = \&]
        \mathit{\yo(X_1)} \arrow[r, "r_1", bend left, dashed] \&
        P_1 \arrow[l, "s_1", bend left, dashed] \arrow[r, "g"] \&
        P_2 \arrow[r, "s_2", bend left, dashed] \&
        \mathit{\yo(X_2)} \arrow[l, "r_2", bend left, dashed]
      \end{tikzcd}
    \end{tabularx}
  \end{center}

  \section*{Properties}

  \begin{center}
    \begin{tabularx}{.8\textwidth}{l| *3{>{\centering\arraybackslash}X}}
      & B & C & D\\\hline
      Embeds fully faithfully into $ \Psh A $ & \cmark & \cmark & \cmark\\
      Subcategory of $ \Psh A $ & \xmark & \xmark & \cmark\\
      Univalent & \xmark & \xmark & \cmark\\
      Scott's construction & \cmark & \xmark & \xmark\\
      Taylor's construction & \cmark & \xmark & \xmark\\
    \end{tabularx}
  \end{center}

  \begin{center}
    \begin{tikzcd}
      B \arrow[r, "\sim"] & C \arrow[r, hook, two heads] & D \arrow[r, phantom, "\subseteq"] & \Psh A
    \end{tikzcd}
  \end{center}

  \newpage

  \section*{Taylor}
  Taylor works in Scott's category of retracts $ B $ of a category $ A $ that is based on a monoid:

  \begin{center}
    \begin{tikzcd}
      *
        \arrow["f_1"', loop, distance=2em, in=-150, out=150]
        \arrow[r, "g"] &
      *
        \arrow["f_2"', loop, distance=2em, in=30, out=-30]
    \end{tikzcd}
  \end{center}

  For $ X : B $, Taylor constructs a category of `indexed types' $ B^X $ (which behaves like functions $ X \to B $) with a fully faithful embedding
  \[ \sum_X : B^X \hookrightarrow B \downarrow X. \]
  He chooses $ D $ such that $ i $ is essentially surjective onto $ B \downarrow_H X $ and shows that we have an adjunction
  \begin{center}
    \begin{tikzcd}[row sep=large]
      B^X \arrow[d, hook, two heads, "\sum_X"] \arrow[r, "f^*" description] & B^Y \arrow[d, hook, two heads, "\sum_Y"] \arrow[l, bend left, "\prod_f"]\\
      B \downarrow_H X & B \downarrow_H Y
    \end{tikzcd}
  \end{center}
  In this case, $ B $ is a setcategory, so the functors $ \sum $ become equivalences under the axiom of choice and we can lift $ f^* \dashv \prod_f $ to $ B \downarrow_H X $ and $ B \downarrow_H Y $.
  In fact we have mere existence of pullbacks and to turn this into the mere existence of a pullback functor already requires the axiom of choice.

  Note that if we try to do a similar thing in $ C $, we would expect to have easy candidates for $ \prod_f $ and $ \sum_f $, but again we only have mere existence of pullbacks and now that is an even bigger problem because $ C $ is not a setcategory.
  \begin{center}
    \begin{tikzcd}
      \yo(*) \arrow[r, "r_1", bend left] &
      P_1 \arrow[r, "g"] \arrow[l, "s_1", bend left] &
      P_2 \arrow[r, "s_2", bend left] &
      \yo(*) \arrow[l, "r_2", bend left]
    \end{tikzcd}
  \end{center}

  \newpage

  \section*{Hyland}
  For $ X : \Psh A $, Hyland considers `the category of retracts' $ \mathbb R(X) $ of
  \[ \pi_1: X \times \yo(*) \to X \]
  in $ \Psh A \downarrow X $. He proceeds to construct retractions of $ (Y \times \yo(*), \pi_1) $ onto $ \prod_f(X, g) $ and $ \sum_f(X, g) $ for $ f: Y \to X $ in $ \mathbb R(X) $ and for a retraction of $ (X \times \yo(*), \pi_1) $ onto $ (X, g) $. That is,
  \[ \prod_f, \sum_f : \Psh A \downarrow X \to \Psh A \downarrow Y \]
  send objects in $ \mathbb R(X) $ to $ \mathbb R(Y) $.

  Furthermore, he claims that
  \begin{itemize}
    \item Scott's category of retracts $ B $ ($ = \mathbb R(\yo(*)) $) is a subcategory of $ \Psh A $.
    \item For $ X \in B $ and $ Y \in \mathbb R(X) $, $ Y \in B $.
    \item From this, Taylor's theorem follows.
  \end{itemize}

  This suggests that Hyland attempts to lift $ \prod_f $ and $ \sum_f $ along the weak equivalences
  \begin{center}
    \begin{tikzcd}[sep=huge]
      (\mathbb R \downarrow_H X)
        \arrow[d, hook, two heads, "\psi_X"]
        \arrow[r, dashed, bend left, "\sum_f"']
        \arrow[r, dashed, bend right, "\prod_f"]
      & (\mathbb R \downarrow_H Y)
        \arrow[d, hook, two heads, "\psi_Y"]
        \arrow[l, dashed, "f^*" description]\\
      \mathbb R(\varphi(X))
        \arrow[r, bend left, "\sum_{\varphi(f)}"']
        \arrow[r, bend right, "\prod_{\varphi(f)}"]
      & \mathbb R(\varphi(Y))
        \arrow[l, "\varphi(f)^*" description]\\
    \end{tikzcd}
  \end{center}

  But since we are working with presheaf categories here, a weak equivalence does not give an adjoint equivalence.

  \section*{The solution}
  If we abandon the need to replicate Taylor's proof, we can actually do a lot better:
  We will work in $ D $, the Rezk completion of $ B $ and $ C $:
  \begin{center}
    \begin{tikzcd}
      \mathit{\yo(X_1)} \arrow[r, "r_1", bend left, dashed] &
      P_1 \arrow[l, "s_1", bend left, dashed] \arrow[r, "g"] &
      P_2 \arrow[r, "s_2", bend left, dashed] &
      \mathit{\yo(X_2)} \arrow[l, "r_2", bend left, dashed]
    \end{tikzcd}
  \end{center}

  We take $ (Y, f) : D \downarrow_H X $ if there merely exists a retraction from $ \pi_1 : X \times \yo(*) \to X $ onto $ (Y, f) $. We can show that this forms a class of display maps, and using Hyland's proof, we can show that $ \prod_f $ restricts to the relative slices, so $ D $ is cartesian closed relative to $ H $.
\end{document}

### 2024-09-03 report/src/category-theory.tex
Write about the three Karoubi envelopes

@@
         \arrow[r, dashed] &
-      \int^C F
+      \displaystyle\int^C F
     \end{tikzcd}
@@
   \[ \Lan F G(b) = \int^{a : A} D(F a, b) \cdot G a \]
-  where $ S \cdot X $ for $ S $ a set and $ X : C $ denotes the `copower'. In most cases, we will have
+  where $ S \cdot X $ for $ S $ a set and $ X : C $ denotes the `copower', which in most cases can be defined as
   \[ S \cdot X = \coprod_{s : S} X. \]
@@
 
+\section{Monoids as categories}\label{sec:monoid-category}
+Take a monoid $ M $.
+\begin{definition}
+  We can construct a category $ C_M $ with $ C_{M0} = \{ \star \} $, $ C_M(\star, \star) = M $.
+The identity morphism on $ \star $ is the identity $ 1: M $.
+The composition is given by multiplication $ g \cdot_{C_M} f = f \cdot_M g $.
+\end{definition}
+
+\begin{remark}
+  Actually, we have a functor from the category of monoids to the category of setcategories (categories whose object type is a set).
+
+  A monoid morphism $ f: M \to M^\prime $ is equivalent to a functor $ F_f: C_M \to C_{M^\prime} $.
+Any functor between $ C_M $ and $ C_{M^\prime} $ sends $ \star_M $ to $ \star_{M^\prime} $.
+The monoid morphism manifests as $ F_f(m) = f(m) $ for $ m: C_M(\star, \star) = M $.
+\end{remark}
+
+\begin{lemma}
+  An isomorphism of monoids gives an (adjoint) equivalence of categories.
+\end{lemma}
+\begin{proof}
+  Given an isomorphism $ f: M \to M^\prime $.
+Then we have functors $ F_f: C_M \to C_{M^\prime} $ and $ F_{f^{-1}}: C_{M^\prime} \to C_M $.
+Take the identity natural transformations $ \eta: \id{C_M} \Rightarrow F_f \bullet F_{f^{-1}} $ and $ \epsilon: F_{f^{-1}} \bullet F_f \Rightarrow \id{C_{M^\prime}} $.
+Of course these are natural isomorphisms.
+\end{proof}
+
+\begin{definition}
+  A \textit{right monoid action}\index{monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, m^\prime: M $,
+  \[ x 1 = x \qquad \text{and} \qquad (x m) m^\prime = x (m \cdot m^\prime). \]
+\end{definition}
+
+\begin{definition}
+  A \textit{morphism}\index{monoid action!morphism} between sets $ X $ and $ Y $ with a right $ M $-action is an $ M $-equivariant function $ f: X \to Y $: a function such that $ f(xm) = f(x)m $ for all $ x: X $ and $ m: M $.
+\end{definition}
+
+These, together with the identity and composition from $ \SET $, constitute a category \iindex{$ \RAct M $} of right $ M $-actions.
+
+\begin{lemma}
+  Presheaves on $ C_M $ are equivalent to sets with a right $ M $-action.
+\end{lemma}
+\begin{proof}
+  This correspondence sends a presheaf $ F $ to the set $ F(\star) $, and conversely, the set $ X $ to the presheaf $ F $ given by $ F(\star) := X $.
+The $ M $-action corresponds to the presheaf acting on morphisms as $ xm = F(m)(x) $.
+A morphism (natural transformation) between presheaves $ F \Rightarrow G $ corresponds to a function $ F(\star) \to G(\star) $ that is $ M $-equivariant, which is exactly a monoid action morphism.
+\end{proof}
+
+\begin{remark}
+  Since the category of sets with an $ M $-action is equivalent to a presheaf category, it has all limits.
+However, we can make this concrete.
+The set of the product $ \prod_i X_i $ is the product of the underlying sets.
+The action is given pointwise by $ (x_i)_i m = (x_i m)_i $.
+\end{remark}
+
+Note that the initial set with $ M $-action is $ \{ \star \} $, with action $ \star m = \star $.
+
+\begin{lemma}\label{lem:global-action-elements}
+  The global elements of a set with right $ M $-action correspond to the elements that are invariant under the $ M $-action.
+\end{lemma}
+\begin{proof}
+  A global element of $ X $ is a morphism $ \varphi: \{ \star \} \to X $ such that for all $ m: M $, $ \varphi(\star)m = \varphi(\star m) = \varphi(\star) $.
+Therefore, it is given precisely by the element $ \varphi(\star): X $, which must be invariant under the $ M $-action.
+\end{proof}
+
+\begin{lemma}
+  The category $ C $ of sets with an $ M $-action has exponentials.
+\end{lemma}
+\begin{proof}
+  Given sets with $ M $-action $ X $ and $ Y $.
+Consider the set $ C(M \times X, Y) $ with an $ M $-action given by $ \phi m^\prime(m, x) = \phi(m^\prime m, x) $.
+This is the exponential object $ X^Y $, with the (universal) evaluation morphism $ X \times X^Y \to Y $ given by $ (x, \phi) \mapsto \phi(1, x) $.
+Explicitly, we get a natural isomorphism $ \psi: \RAct M(Z \times Y, X) \xrightarrow \sim \RAct M(Z, X^Y) $ given by
+  \[ \psi(f)(z)(m, y) = f(z m, y) \quad \text{and} \quad \psi^{-1}(g)(z, y) = g(z)(1, y). \]
+\end{proof}
+
+\begin{definition}
+  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
+\end{definition}
+
+\subsection{Extension and restriction of scalars}
+
+Let $ \varphi: M \to M^\prime $ be a morphism of monoids.
+
+Remember that sets with a right monoid action are equivalent to presheaves on the monoid category.
+Also, $ \varphi $ is equivalent to a functor between the monoid categories.
+The following is a specific case of the concepts in the section about Kan extension:
+
+\begin{lemma}
+  We get a \iindex{restriction of scalars} functor $ \varphi^* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
+\end{lemma}
+\begin{proof}
+  Given a set $ X $ with right $ M^\prime $-action, take the set $ X $ again, and give it a right $ M $-action, sending $ (x, m) $ to $ x \varphi(m) $.
+
+  On morphisms, send an $ M^\prime $-equivariant morphism $ f: X \to X^\prime $ to the $ M $-equivariant morphism $ f: X \to X^\prime $.
+\end{proof}
+
+Since $ \SET $ has colimits, and restriction of scalars corresponds to precomposition of presheaves (on $ C_{M^\prime} $), we can give it a left adjoint.
+This is the (pointwise) left Kan extension, which boils down to a very concrete definition, reminiscent of a tensor product:
+
+\begin{lemma}\label{lem:scalar-extension}
+  We get an \iindex{extension of scalars} functor $ \varphi_* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
+\end{lemma}
+\begin{proof}
+  Given a set $ X $ with right $ M $-action.
+Take $ Y = X \times M^\prime / \sim $ with the relation $ (x m, m^\prime) \sim (x, f(m) \cdot m^\prime) $ for $ m: M $.
+This has a right $ M^\prime $-action given by $ (x, m^\prime)n^\prime = (x, m^\prime n^\prime) $.
+
+  On morphisms, it sends the $ m $-equivariant $ f: X \to X^\prime $ to the morphism $ (x, m^\prime) \mapsto (f(x), m^\prime) $.
+\end{proof}
+
+\begin{lemma}\label{lem:scalar-extension-monoid-monoid-action}
+  For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi_*(U_M) \cong U_{M^\prime} $.
+\end{lemma}
+\begin{proof}
+  The proof relies on the fact that for all $ m: U_M $ and $ m^\prime : M^\prime $, we have
+  \[ (m, m^\prime) \sim (1, \varphi(m) m^\prime). \]
+\end{proof}
+
+Consider the category $ D $ with $ D_0 = M^\prime $ and
+\[ D(m^\prime, \overline m^\prime) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime \}. \]
+
+\begin{lemma}\label{lem:scalar-extension-terminal}
+  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi_*(I_M) \cong I_{M^\prime} $.
+\end{lemma}
+\begin{proof}
+  If $ D $ has a weakly terminal object, there exists $ m_0 : M^\prime $ such that for all $ m^\prime: M^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = m_0 $.
+
+  The proof relies on the fact that every element of $ \varphi_*(I_M) $ is given by some $ (\star, m^\prime) $, but then
+  \[ (\star, m^\prime) = (\star \cdot m, m^\prime) \sim (\star, \varphi(m) \cdot m^\prime) = (\star, m_0), \]
+  so $ \varphi_*(I_M) $ has exactly $ 1 $ element.
+\end{proof}
+
+\begin{remark}
+  For $ \varphi_* $ to preserve terminal objects, we actually only need $ D $ to be connected.
+The fact that $ \varphi_*(I_M) $ is a quotient by a symmetric and transitive relation then allows us to `walk' from any $ (\star, m^\prime_1) $ to any other $ (\star, m^\prime_2) $ in small steps.
+\end{remark}
+
+For any $ m^\prime_1, m^\prime_2: M^\prime $, consider the category $ D_{m^\prime_1, m^\prime_2} $, given by
+\[ D_{m^\prime_1, m^\prime_2, 0} = \{ (m^\prime, m_1, m_2): M^\prime \times M \times M \mid m_i^\prime = \varphi(m_i) \cdot m^\prime \} \]
+and
+\[ D_{m^\prime_1, m^\prime_2}((m^\prime, m_1, m_2), (\overline m^\prime, \overline m_1, \overline m_2)) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime, m_i = \overline m_i \cdot m \}.
+\]
+
+\begin{lemma}\label{lem:scalar-extension-product}
+  Suppose that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object for all $ m^\prime_1, m^\prime_2: M^\prime $.
+Then for sets $ A $ and $ B $ with right $ M $-action, we have $ \varphi_*(A \times B) \cong \varphi_*(A) \times \varphi_*(B) $.
+\end{lemma}
+\begin{proof}
+  Now, any element in $ \varphi_*(A) \times \varphi_*(B) = (A \times M^\prime / \sim) \times (B \times M^\prime / \sim) $ is given by some $ (a, m^\prime_1, b, m^\prime_2) $.
+
+  The fact that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object means that we have some $ \overline m^\prime: M^\prime $ and $ \overline m_1, \overline m_2: M $ with $ m_i^\prime = \varphi(\overline m_i) \cdot \overline m^\prime $.
+Therefore,
+  \[ (a, m^\prime_1, b, m^\prime_2) = (a, \varphi(\overline m_1) \cdot \overline m^\prime, b, \varphi(\overline m_2) \cdot \overline m^\prime) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime), \]
+  so this is equivalent to some element in $ \varphi_*(A \times B) = (A \times B \times M^\prime / \sim) $. Note that this trivially respects the right $ M^\prime $-action.
+
+  The fact that $ (\overline m^\prime, \overline m_1, \overline m_2) $ is weakly terminal also means that for all $ m^\prime: M^\prime $ and $ m_1, m_2: M $ with $ m_i^\prime = \varphi(m_i) \cdot m^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \cdot m $.
+This means that the equivalence that we established is actually well-defined: equivalent elements in $ \varphi_*(A) \times \varphi_*(B) $ are sent to equivalent elements in $ \varphi_*(A \times B) $.
+
+  Therefore, we have an isomorphism $ \psi: \varphi^*(A) \times \varphi^*(B) \xrightarrow{\sim} \varphi^*(A \times B) $.
+Now we only need to show that the projections are preserved by this isomorphism.
+To that end, take $ x = (a, m^\prime_1, b, m^\prime_2) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime) : \varphi^*(A) \times \varphi^*(B) $.
+We have
+  \[ \varphi^*(\pi_1)(\psi(x)) = (a \overline m_1, \overline m^\prime) = \pi^\prime_1(x). \]
+  In the same way, $ \varphi^*(\pi_2) \circ \psi = \pi^\prime_2 $ and this concludes the proof.
+\end{proof}
+
 \section{The Karoubi envelope}
-Let $ C $ be a category. If we have a retraction-section pair
-\begin{tikzcd}
-  c \arrow[r, shift left, "r"] & d \arrow[l, shift left, "s"]
-\end{tikzcd}
-we have (by definition) $ s \cdot r = \id d $.
-On the other hand, $ r \cdot s: c \to c $ is an idempotent morphism, since $ r \cdot s \cdot r \cdot s = r \cdot s $.
-Conversely, we can wonder whether for some idempotent morphism $ a: c \to c $, we can find a retraction-section pair $ (r, s) $ such that $ a = r \cdot s $.
-If this is the case, we say that the idempotent $ a $ \textit{splits}\index{split idempotent}.
-If $ a $ does not split, we can wonder whether we can find an embedding $ \iota_C : C \hookrightarrow \overline C $ such that the idempotent $ \iota_C(a): \iota_C(c) \to \iota_C(c) $ does split.
-This is one way to arrive at the \textit{Karoubi envelope}.
+Let $ C $ be a category and $ X, Y : C $ objects. We will denote the type of section-retraction pairs of $ Y $ onto $ X $ with
+\[ X \triangleleft Y := \sum_{r : C(Y, X)} \sum_{s : C(X, Y)} s \cdot r = \id X. \]
+Now, note that for $ (r, s) : X \triangleleft Y $, $ r \cdot s: C(Y, Y) $ is an idempotent morphism, since $ r \cdot s \cdot r \cdot s = r \cdot s $.
+We can also wonder whether for an idempotent morphism $ f: C(X, X) $, we can find some $ Y : C $ and some $ (r, s) : X \triangleleft Y $ such that $ f = r \cdot s $.
+If this is the case, we say that the idempotent $ f $ \textit{splits}\index{split idempotent}.
+If $ f $ does not split, we can wonder whether we can find an embedding $ \iota_C : C \hookrightarrow \overline C $ into some category $ \overline C $ such that the idempotent $ \iota_C(f): \overline C(\iota_C(X), \iota_C(X)) $ does split.
+This is one way to arrive at the \textit{Karoubi envelope}:
 
@@
   We define the category $ \overline C $.
-The objects of $ \overline C $ are tuples $ (c, a) $ with $ c: C $, $ a: C(c, c) $ such that $ a \cdot a = a $.
-The morphisms between $ (c, a) $ and $ (d, b) $ are morphisms $ f: C(a, b) $ such that $ a \cdot f \cdot b = f $.
-The identity morphism on $ (c, a) $ is given by $ a $ and $ \overline C $ inherits morphism composition from $ C $.
+The objects of $ \overline C $ are tuples $ (X, f) $ with $ X: C $, $ f: C(X, X) $ such that $ f \cdot f = f $.
+The morphisms between $ (X_1, f_1) $ and $ (X_2, f_2) $ are morphisms $ g: C(X_1, X_2) $ such that $ f_1 \cdot g \cdot f_2 = g $.
+This can be summarized in the following diagram:
+  \begin{center}
+    \begin{tikzcd}
+      X_1
+        \arrow["f_1"', loop, distance=2em, in=-150, out=150]
+        \arrow[r, "g"] &
+      X_2
+        \arrow["f_2"', loop, distance=2em, in=30, out=-30]
+    \end{tikzcd}
+  \end{center}
+  The identity morphism on $ (X, f) $ is given by $ f $ and $ \overline C $ inherits morphism composition from $ C $.
 \end{definition}
@@
 
-Since a functor preserves retracts, and since every object of $ \overline C $ is a retract of an object in $ C $, one can lift a functor from $ C $ (to a category with (co)equalizers) to a functor on $ \overline C $.
-
-For convenience, the lemma below works with pointwise left Kan extension using colimits, but one could also prove this using just (co)equalizers (or right Kan extension using limits).
+There is also another (classically equivalent) definition of the Karoubi envelope.
+An object in this alternative category is a presheaf $ F : PC $ that is a retract of the Yoneda embedding $ \yo(X) $ of an object $ X : C $.
+Note that there are two different ways to translate this to univalent foundations.
+We can either interpret the existence of the object $ X $ and the retraction $ (r, s) : F \triangleleft \yo(X) $ as additional \textit{structure} on $ F $, or we can treat it as a \textit{property} and ask for \textit{mere existence} of $ X $, $ r $ and $ s $.
+This gives rise to two different categories:
+
+\begin{definition}\label{def:karoubi'}
+  We define the category $ \tilde C $ in which every object is a presheaf $ F : P C $, together with an object $ X : C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo (X) $.
+The morphisms from $ (F_1, X_1, r_1, s_1) $ to $ (F_2, X_2, r_2, s_2) $ are just the presheaf morphisms $ f: PC(F_1, F_2) $.
+This can be summarized in the following diagram:
+  \begin{center}
+    \begin{tikzcd}
+      \yo(X_1) \arrow[r, "r_1", bend left] &
+      F_1 \arrow[r, "g"] \arrow[l, "s_1", bend left] &
+      F_2 \arrow[r, "s_2", bend left] &
+      \yo(X_2) \arrow[l, "r_2", bend left]
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+\begin{definition}\label{def:karoubi''}
+  We define the category $ \hat C $ as the full subcategory of $ P C $ consisting of objects $ F : P C $ such that there merely exist an object $ X: C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo(X) $, summarized in the following diagram:
+  \begin{center}
+    \begin{tikzcd}
+      \mathit{\yo(X_1)} \arrow[r, "r_1", bend left, dashed] &
+      F_1 \arrow[l, "s_1", bend left, dashed] \arrow[r, "g"] &
+      F_2 \arrow[r, "s_2", bend left, dashed] &
+      \mathit{\yo(X_2)} \arrow[l, "r_2", bend left, dashed]
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+This gives us what we need to translate the classical equivalence between the two notions of Karoubi envelope to type theory:
+\begin{lemma}\label{lem:karoubi-equivalence}
+  We have an adjoint equivalence $ \overline C \xrightarrow \sim \tilde C $.
+\end{lemma}
+\begin{proof}
+  As shown in Remark \ref{rem:retract-coequalizer}, an object $ (X, f) : \overline C $ is the equalizer of $ \id X $ and $ f $. Therefore, we send it to the equalizer
+  \begin{center}
+    \begin{tikzcd}
+      F \arrow[r, "s"] & \yo(X) \arrow[r, shift left, "\id{\yo X}"] \arrow[r, shift right, "\yo(f)"'] & \yo(X)
+    \end{tikzcd}
+  \end{center}
+  Note that for $ \yo(f) $, we have $ \yo(f) \cdot \yo(f) = \yo(f) \cdot \id{\yo X} $, so the universal property of the equalizer gives a morphism $ r: PC(\yo(X), F) $ such that $ r \cdot s = \yo(f) $.
+Using this same universal property, we can show that $ s \cdot r = \id F $.
+  We send a morphism $ g: \overline C((X_1, f_1), (X_2, f_2)) $ to
+  \[ s_1 \cdot \yo(g) \cdot r_2 : PC(F_1, F_2). \]
+  Note that this is an equivalence on the morphisms: For any morphism $ \bar g : PC(F_1, F_2) $, we have
+  \[ r_1 \cdot \bar g \cdot s_2 : PC(\yo(X_1), \yo(X_2)). \]
+  By the fully faithfulness of the Yoneda lemma, this corresponds to a morphism $ g : C(X_1, X_2) $ and we can show that these two maps between $ C((X_1, f_1), (X_2, f_2)) $ and $ \overline C(F_1, F_2) $ are inverses of each other.
+  \begin{center}
+    \begin{tikzcd}
+      F_1 \arrow[r, shift left, "s_1"] \arrow[d, "\bar g"] & \yo(X_1) \arrow[l, shift left, "r_1"] \arrow[r, shift left, "\id{\yo X_1}"] \arrow[r, shift right, "\yo(f_1)"'] \arrow[d, "\yo(g)"] & \yo(X_1)\\
+      F_2 \arrow[r, shift left, "s_2"] & \yo(X_2) \arrow[l, shift left, "r_2"] \arrow[r, shift left, "\id{\yo X_2}"] \arrow[r, shift right, "\yo(f_2)"'] & \yo(X_2)\\
+    \end{tikzcd}
+  \end{center}
+
+  Now, note that this map is also split essentially surjective.
+For some $ (F, X, r, s) : \tilde C $, $ r \cdot s $ is an idempotent morphism on $ \yo(X) $, and by fully faithfulness of the Yoneda Lemma, it corresponds to an idempotent morphism $ f $ on $ X $.
+We send $ (F, X, r, s) $ to $ (X, f) $.
+Note that both $ F $ is the equalizer of $ \id{\yo X} $ and $ r \cdot s $.
+Therefore, it is isomorphic to the image of $ (X, f) $.
+
+  The fact that a fully faithful and split essentially surjective functor is an adjoint equivalence concludes the proof.
+\end{proof}
+
+\begin{remark}
+  Note that since the morphism types of $ \tilde C $ and $ \hat C $ are the same, and since the objects of $ \hat C $ are just truncated versions of the objects in $ \tilde C $, we have a fully faithful embedding
+  \[ \tilde C \hookrightarrow \hat C, \]
+  which just forgets the choices for $ X $, $ r $ and $ s $ on the objects.
+Note that this is also essentially surjective: by definition, for any $ (F, H) : \hat C $, there merely exist $ X $, $ r $ and $ s $ such that $ (X, r, s) $ truncates to $ H $.
+  Therefore, we have a weak equivalence from $ tilde C $ to $ \hat C $. However, as we will see, $ \tilde C $ is usually not univalent, so this does not give an adjoint equivalence of categories.
+\end{remark}
+
+\begin{remark}
+  The fully faithful embedding $ i_C : C \hookrightarrow \overline C $ induces equivalences $ (X \cong Y) \simeq (\iota_C(X) \cong \iota_C(Y)) $.
+We also have an equivalence $ (X = Y) \simeq (\iota_C(X) = \iota_C(Y)) $, because, as it turns out, any equality between $ X $ and $ Y $ also preserves the identity of $ X $.
+Therefore, if $ \overline C $ is univalent, we have a chain of equivalences
+  \[ (X = Y) \simeq (\iota_C(X) = \iota_C(Y)) \simeq (\iota_C(X) \cong \iota_C(Y)) \simeq (X \cong Y), \]
+  which shows that $ C $ is univalent as well.
+\end{remark}
+
+\begin{remark}
+  Note that the converse does not necessarily hold. Consider the commutative monoid consisting of the three matrices
+  \[
+    a = \begin{pmatrix}
+      1 & 0\\0 & 1
+    \end{pmatrix}, \quad
+    b = \begin{pmatrix}
+      1 & 0\\0 & 0
+    \end{pmatrix} \quad \text{and} \quad
+    c = \begin{pmatrix}
+      -1 & 0\\0 & 0
+    \end{pmatrix}
+  \]
+  under matrix multiplication.
+As we saw in Section \ref{sec:monoid-category}, we can turn this into a category $ C_M $ with one object $ \star $, and the three morphisms $ a $, $ b $ and $ c $.
+Only $ a $ is an isomorphism and since $ \star = \star $ has exactly one inhabitant, $ C_M $ is univalent.
+
+  When we construct the Karoubi envelope $ \overline C_M $, we get a category with objects $ a $ and $ b $.
+Now, note that since $ M $ is a set, $ b = b $ still has one inhabitant.
+Of course, $ b \cong b $ contains the identity automorphism.
+However, since
+  \[ b \cdot c = c \quad \text{and} \quad c \cdot c = b, \]
+  $ c $ is also an automorphism of $ b $. Therefore, $ \overline C_M $ is not univalent.
+
+  In a somewhat more complicated way, we can show that $ \tilde C_M $ is not univalent either: the counterpart of $ b $ in that category has two automorphisms, corresponding to $ b $ and $ c $, but only one equality, which is the identity.
+This is because isomorphisms only have to respect the presheaf structure, whereas equalities also have to respect the section (and retraction).
+Note that presheaves are univalent, so equality of presheaves is equivalent to isomorphism of presheaves.
+
+  Therefore, $ \overline C $ and $ \tilde C $ are usually more pathological than $ C $ itself. On the other hand, since $ \hat C $ is a full subcategory of $ PC $, it is univalent.
+\end{remark}
+
+This all leads up to:
+\begin{corollary}
+  We have three candidates for the category of retracts, which are related to each other and to $ C $ and $ PC $ as follows:
+  \begin{center}
+    \begin{tikzcd}
+      C \arrow[r, hook, "\iota_C"] & \overline C \arrow[r, "\sim"] & \tilde C \arrow[r, hook, two heads] & \hat C \arrow[r, phantom, "\subseteq"] & PC
+    \end{tikzcd}
+  \end{center}
+  The fact that $ \hat C $ is univalent, and has weak equivalences from $ \overline C $ and $ \tilde C $ exhibits $ \hat C $ as the Rezk completion of $ \overline C $ and $ \tilde C $.
+\end{corollary}
+
+\begin{remark}
+  Our choice of definition will have consequences.
+One one hand, $ \hat C $ is univalent, but very abstract.
+In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism.
+On the other hand, $ \overline C $ and $ \tilde C $ are very elementary and concrete, but not univalent, which makes working with them also hard.
+\end{remark}
+
+The remainder of this section works towards the adjoint equivalence between $ PC $ and $ P \overline C $.
+
+Since a functor preserves retracts, and since every object of $ \overline C $ is a retract of an object in $ C $, we can generalize the construction of the functor that we do in Lemma \ref{lem:karoubi-equivalence} for the functor $ \yo: C \to PC $, to general functors $ F: C \to D $ for categories $ D $ with (co)equalizers.
+
+For convenience, the lemma below works very abstractly with pointwise left Kan extension using colimits, but one could also prove this using just (co)equalizers (or right Kan extension using limits).
 \begin{lemma}
@@
 \end{corollary}
-
-Now, there is also another (classically equivalent) definition of the Karoubi envelope:
-\begin{definition}\label{def:karoubi'}
-  Let $ Y: C \to P C $ be the Yoneda embedding of $ C $ into its category of presheaves.
-We define the category $ \hat C $ as the full subcategory of $ P C $ consisting of objects $ F : P C $ such that there exists an object $ c: C $ and a retraction of $ Y(c) $ onto $ F $.
-Note that the existence of $ c $ and the retraction is \textit{mere existence} (see the chapter on Univalent Foundations) because we need this to be a subcategory of $ P C $.
-\end{definition}
-
-\begin{lemma}\label{lem:retracts-rezk}
-  $ \hat C $ is the Rezk completion of $ \overline C $.
-\end{lemma}
-\begin{proof}
-  First of all, note that $ \hat C $ is univalent, since it is a presheaf category (see Theorem 4.5 in \autocite{univalent-categories}).
-So we must show that we have a weak equivalence from $ \overline C $ to $ \hat C $.
-
-  Secondly, by Corollary \ref{cor:karoubi-presheaf} we have an adjoint equivalence $ {\op{\iota_C}}_*: P \overline C \xrightarrow \sim P C $ and by Lemma \ref{lem:Yoneda-restriction-commutes}, the following diagram 2-commutes:
-  \begin{center}
-    \begin{tikzcd}
-      C \arrow[r, "\iota_C"] \arrow[d, "Y"] & \overline C \arrow[d, "Y"]\\
-      P C & P \overline C \arrow[l, "\sim"', "{\op{\iota_C}}_*"]
-    \end{tikzcd}
-  \end{center}
-
-  By Lemma \ref{lem:karoubi-is-retract}, every object of $ \overline C $ is a retract of some object in $ c $.
-Therefore, every object in the image of $ \overline C $ inside $ P C $ is a retract of some object in the image of $ C $, so we can turn $ Y \bullet {\op{\iota_C}}_* : \overline C \to P C $ into a fully faithful embedding into $ \hat C $.
-
-  Now, to show that it is essentially surjective, take an object $ F : \hat C $.
-That is, take a retract \begin{tikzcd} F \arrow[r, shift left, "s"] & Y(c) \arrow[l, shift left, "r"] \end{tikzcd}.
-Note that $ r \cdot s $ is an idempotent on $ Y(c) $.
-Since $ Y $ is a fully faithful embedding, it gives an equivalence on the hom-sets, so we have an element $ e : C(c, c) $ that maps to $ r \cdot s : P C (Y(c), Y(c)) $.
-We will show that $ (c, e) $ is our preimage in $ \overline C $ of $ F $.
-
-  Also, $ (c, e) $ is a retract of $ \iota_C(c) $ with section and retraction $ e $.
-Therefore, $ \op{\iota_C} \bullet Y(c, e) $ is a retract of $ \op{\iota_C} \bullet Y (\iota_C (c)) $ with section and retraction $ \op{\iota_C} \bullet Y(e) $.
-Composing these gives an idempotent
-  \[ \op{\iota_C} \bullet Y(e): d \mapsto f \mapsto f \cdot e \]
-  on $ \op{\iota_C} \bullet Y (\iota_C (c)) $. Transporting this along the isomorphism with $ Y(c) $, we get an idempotent
-  \[ d \mapsto f \mapsto \iota_C^{-1}(\iota_C(f) \cdot e) \]
-  on $ Y(c) $. Note that we can view $ e $ both as an idempotent on $ c $ and on $ \iota_C(e) $, and that $ \iota_C(e) = e $, so $ \iota_C^{-1}(\iota_C(f) \cdot e) = f \cdot e $.
-
-  Therefore, the idempotent on $ Y(c) $ is exactly $ Y(e) = r \cdot s $.
-By Remark \ref{rem:retract-coequalizer}, $ \op{\iota_C} \bullet Y(c, e) $ is the equalizer of $ \id{Y(c)} $ and $ r \cdot s $.
-Note that by the same remark, $ F $ is the equalizer of $ \id{Y(c)} $ and $ r \cdot s $ as well.
-Since the equalizer is unique up to unique isomorphism, we have an isomorphism $ F \cong \op{\iota_C} \bullet Y(c, e) $ and we see that $ Y \bullet {\op{\iota_C}}_* $ is essentially surjective.
-\end{proof}
-
-\begin{remark}
-  As shown above, $ \overline C $ and $ \hat C $ have a very strong relation.
-In classical mathematics, they are even equivalent.
-However, since $ \overline C $ is not univalent, we do not have a full equivalence in univalent foundations and our choice of definition will have consequences.
-One one hand, $ \hat C $ is univalent.
-On the other hand, every object of $ \overline C $ is uniquely associated with one idempotent morphism in $ C $.
-
-  In this thesis, I will choose to interpret the `category of retracts' or `Karoubi envelope' to mean $ \overline C $.
-This is because Dana Scott and Paul Taylor perform most of their constructions explicitly using the (idempotent) morphisms of $ C $, which is closest to working in $ \overline C $.
-
-  It is however very well possible that most of the proofs can be made to work in $ \hat C $ as well.
-For future research, it would be interesting to see what the differences are between working in $ \overline C $ and $ \hat C $ for these proofs.
-\end{remark}
-
-\section{Monoids as categories}\label{sec:monoid-category}
-Take a monoid $ M $.
-\begin{definition}
-  We can construct a category $ C_M $ with $ C_{M0} = \{ \star \} $, $ C_M(\star, \star) = M $.
-The identity morphism on $ \star $ is the identity $ 1: M $.
-The composition is given by multiplication $ g \cdot_{C_M} f = f \cdot_M g $.
-\end{definition}
-
-\begin{remark}
-  Actually, we have a functor from the category of monoids to the category of setcategories (categories whose object type is a set).
-
-  A monoid morphism $ f: M \to M^\prime $ is equivalent to a functor $ F_f: C_M \to C_{M^\prime} $.
-Any functor between $ C_M $ and $ C_{M^\prime} $ sends $ \star_M $ to $ \star_{M^\prime} $.
-The monoid morphism manifests as $ F_f(m) = f(m) $ for $ m: C_M(\star, \star) = M $.
-\end{remark}
-
-\begin{lemma}
-  An isomorphism of monoids gives an (adjoint) equivalence of categories.
-\end{lemma}
-\begin{proof}
-  Given an isomorphism $ f: M \to M^\prime $.
-Then we have functors $ F_f: C_M \to C_{M^\prime} $ and $ F_{f^{-1}}: C_{M^\prime} \to C_M $.
-Take the identity natural transformations $ \eta: \id{C_M} \Rightarrow F_f \bullet F_{f^{-1}} $ and $ \epsilon: F_{f^{-1}} \bullet F_f \Rightarrow \id{C_{M^\prime}} $.
-Of course these are natural isomorphisms.
-\end{proof}
-
-\begin{definition}
-  A \textit{right monoid action}\index{monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, m^\prime: M $,
-  \[ x 1 = x \qquad \text{and} \qquad (x m) m^\prime = x (m \cdot m^\prime). \]
-\end{definition}
-
-\begin{definition}
-  A \textit{morphism}\index{monoid action!morphism} between sets $ X $ and $ Y $ with a right $ M $-action is an $ M $-equivariant function $ f: X \to Y $: a function such that $ f(xm) = f(x)m $ for all $ x: X $ and $ m: M $.
-\end{definition}
-
-These, together with the identity and composition from $ \SET $, constitute a category \iindex{$ \RAct M $} of right $ M $-actions.
-
-\begin{lemma}
-  Presheaves on $ C_M $ are equivalent to sets with a right $ M $-action.
-\end{lemma}
-\begin{proof}
-  This correspondence sends a presheaf $ F $ to the set $ F(\star) $, and conversely, the set $ X $ to the presheaf $ F $ given by $ F(\star) := X $.
-The $ M $-action corresponds to the presheaf acting on morphisms as $ xm = F(m)(x) $.
-A morphism (natural transformation) between presheaves $ F \Rightarrow G $ corresponds to a function $ F(\star) \to G(\star) $ that is $ M $-equivariant, which is exactly a monoid action morphism.
-\end{proof}
-
-\begin{remark}
-  Since the category of sets with an $ M $-action is equivalent to a presheaf category, it has all limits.
-However, we can make this concrete.
-The set of the product $ \prod_i X_i $ is the product of the underlying sets.
-The action is given pointwise by $ (x_i)_i m = (x_i m)_i $.
-\end{remark}
-
-Note that the initial set with $ M $-action is $ \{ \star \} $, with action $ \star m = \star $.
-
-\begin{lemma}\label{lem:global-action-elements}
-  The global elements of a set with right $ M $-action correspond to the elements that are invariant under the $ M $-action.
-\end{lemma}
-\begin{proof}
-  A global element of $ X $ is a morphism $ \varphi: \{ \star \} \to X $ such that for all $ m: M $, $ \varphi(\star)m = \varphi(\star m) = \varphi(\star) $.
-Therefore, it is given precisely by the element $ \varphi(\star): X $, which must be invariant under the $ M $-action.
-\end{proof}
-
-\begin{lemma}
-  The category $ C $ of sets with an $ M $-action has exponentials.
-\end{lemma}
-\begin{proof}
-  Given sets with $ M $-action $ X $ and $ Y $.
-Consider the set $ C(M \times X, Y) $ with an $ M $-action given by $ \phi m^\prime(m, x) = \phi(m^\prime m, x) $.
-This is the exponential object $ X^Y $, with the (universal) evaluation morphism $ X \times X^Y \to Y $ given by $ (x, \phi) \mapsto \phi(1, x) $.
-Explicitly, we get a natural isomorphism $ \psi: \RAct M(Z \times Y, X) \xrightarrow \sim \RAct M(Z, X^Y) $ given by
-  \[ \psi(f)(z)(m, y) = f(z m, y) \quad \text{and} \quad \psi^{-1}(g)(z, y) = g(z)(1, y). \]
-\end{proof}
-
-\begin{definition}
-  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
-\end{definition}
-
-\subsection{Extension and restriction of scalars}
-
-Let $ \varphi: M \to M^\prime $ be a morphism of monoids.
-
-Remember that sets with a right monoid action are equivalent to presheaves on the monoid category.
-Also, $ \varphi $ is equivalent to a functor between the monoid categories.
-The following is a specific case of the concepts in the section about Kan extension:
-
-\begin{lemma}
-  We get a \iindex{restriction of scalars} functor $ \varphi^* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
-\end{lemma}
-\begin{proof}
-  Given a set $ X $ with right $ M^\prime $-action, take the set $ X $ again, and give it a right $ M $-action, sending $ (x, m) $ to $ x \varphi(m) $.
-
-  On morphisms, send an $ M^\prime $-equivariant morphism $ f: X \to X^\prime $ to the $ M $-equivariant morphism $ f: X \to X^\prime $.
-\end{proof}
-
-Since $ \SET $ has colimits, and restriction of scalars corresponds to precomposition of presheaves (on $ C_{M^\prime} $), we can give it a left adjoint.
-This is the (pointwise) left Kan extension, which boils down to a very concrete definition, reminiscent of a tensor product:
-
-\begin{lemma}\label{lem:scalar-extension}
-  We get an \iindex{extension of scalars} functor $ \varphi_* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
-\end{lemma}
-\begin{proof}
-  Given a set $ X $ with right $ M $-action.
-Take $ Y = X \times M^\prime / \sim $ with the relation $ (x m, m^\prime) \sim (x, f(m) \cdot m^\prime) $ for $ m: M $.
-This has a right $ M^\prime $-action given by $ (x, m^\prime)n^\prime = (x, m^\prime n^\prime) $.
-
-  On morphisms, it sends the $ m $-equivariant $ f: X \to X^\prime $ to the morphism $ (x, m^\prime) \mapsto (f(x), m^\prime) $.
-\end{proof}
-
-\begin{lemma}\label{lem:scalar-extension-monoid-monoid-action}
-  For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi_*(U_M) \cong U_{M^\prime} $.
-\end{lemma}
-\begin{proof}
-  The proof relies on the fact that for all $ m: U_M $ and $ m^\prime : M^\prime $, we have
-  \[ (m, m^\prime) \sim (1, \varphi(m) m^\prime). \]
-\end{proof}
-
-Consider the category $ D $ with $ D_0 = M^\prime $ and
-\[ D(m^\prime, \overline m^\prime) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime \}. \]
-
-\begin{lemma}\label{lem:scalar-extension-terminal}
-  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi_*(I_M) \cong I_{M^\prime} $.
-\end{lemma}
-\begin{proof}
-  If $ D $ has a weakly terminal object, there exists $ m_0 : M^\prime $ such that for all $ m^\prime: M^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = m_0 $.
-
-  The proof relies on the fact that every element of $ \varphi_*(I_M) $ is given by some $ (\star, m^\prime) $, but then
-  \[ (\star, m^\prime) = (\star \cdot m, m^\prime) \sim (\star, \varphi(m) \cdot m^\prime) = (\star, m_0), \]
-  so $ \varphi_*(I_M) $ has exactly $ 1 $ element.
-\end{proof}
-
-\begin{remark}
-  For $ \varphi_* $ to preserve terminal objects, we actually only need $ D $ to be connected.
-The fact that $ \varphi_*(I_M) $ is a quotient by a symmetric and transitive relation then allows us to `walk' from any $ (\star, m^\prime_1) $ to any other $ (\star, m^\prime_2) $ in small steps.
-\end{remark}
-
-For any $ m^\prime_1, m^\prime_2: M^\prime $, consider the category $ D_{m^\prime_1, m^\prime_2} $, given by
-\[ D_{m^\prime_1, m^\prime_2, 0} = \{ (m^\prime, m_1, m_2): M^\prime \times M \times M \mid m_i^\prime = \varphi(m_i) \cdot m^\prime \} \]
-and
-\[ D_{m^\prime_1, m^\prime_2}((m^\prime, m_1, m_2), (\overline m^\prime, \overline m_1, \overline m_2)) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime, m_i = \overline m_i \cdot m \}.
-\]
-
-\begin{lemma}\label{lem:scalar-extension-product}
-  Suppose that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object for all $ m^\prime_1, m^\prime_2: M^\prime $.
-Then for sets $ A $ and $ B $ with right $ M $-action, we have $ \varphi_*(A \times B) \cong \varphi_*(A) \times \varphi_*(B) $.
-\end{lemma}
-\begin{proof}
-  Now, any element in $ \varphi_*(A) \times \varphi_*(B) = (A \times M^\prime / \sim) \times (B \times M^\prime / \sim) $ is given by some $ (a, m^\prime_1, b, m^\prime_2) $.
-
-  The fact that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object means that we have some $ \overline m^\prime: M^\prime $ and $ \overline m_1, \overline m_2: M $ with $ m_i^\prime = \varphi(\overline m_i) \cdot \overline m^\prime $.
-Therefore,
-  \[ (a, m^\prime_1, b, m^\prime_2) = (a, \varphi(\overline m_1) \cdot \overline m^\prime, b, \varphi(\overline m_2) \cdot \overline m^\prime) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime), \]
-  so this is equivalent to some element in $ \varphi_*(A \times B) = (A \times B \times M^\prime / \sim) $. Note that this trivially respects the right $ M^\prime $-action.
-
-  The fact that $ (\overline m^\prime, \overline m_1, \overline m_2) $ is weakly terminal also means that for all $ m^\prime: M^\prime $ and $ m_1, m_2: M $ with $ m_i^\prime = \varphi(m_i) \cdot m^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \cdot m $.
-This means that the equivalence that we established is actually well-defined: equivalent elements in $ \varphi_*(A) \times \varphi_*(B) $ are sent to equivalent elements in $ \varphi_*(A \times B) $.
-
-  Therefore, we have an isomorphism $ \psi: \varphi^*(A) \times \varphi^*(B) \xrightarrow{\sim} \varphi^*(A \times B) $.
-Now we only need to show that the projections are preserved by this isomorphism.
-To that end, take $ x = (a, m^\prime_1, b, m^\prime_2) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime) : \varphi^*(A) \times \varphi^*(B) $.
-We have
-  \[ \varphi^*(\pi_1)(\psi(x)) = (a \overline m_1, \overline m^\prime) = \pi^\prime_1(x). \]
-  In the same way, $ \varphi^*(\pi_2) \circ \psi = \pi^\prime_2 $ and this concludes the proof.
-\end{proof}

### 2024-09-06 report/src/algebraic-structures.tex
Fix a couple of TODO's, write about Selinger

@@
 \begin{proof}
-  \TODO Move to after the theory algebra, because we need that.
+  This proof uses the theory algebra, which will be properly defined in Example \ref{ex:theory-algebra}.
 
@@
 \subsection{The theory algebra}
-\begin{example}
+\begin{example}\label{ex:theory-algebra}
   Let $ T $ be an algebraic theory and $ n $ a natural number.
@@
   Recall from \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $.
-Now, recall from (\TODO) that we can embed any category inside its category of $ \SET $-valued functors.
+Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category $ C $ as $ \op C $ inside its category of $ \SET $-valued functors.
 This embeds $ n: \mathbf L $ as the theory algebra $ T_n $.
@@
   natural in $ n $ and $ A $.
-Explicitly, it sends $ f: \Alg T(T_n, A) $ to $ i \mapsto f(x_i) $ and $ (a_i)_i : A^n $ to $ f \mapsto f \bullet a $.
+Explicitly, it sends $ f: \Alg T(T_n, A) $ to $ (f(x_i))_i $ and $ (a_i)_i : A^n $ to $ f \mapsto f \bullet a $.
 The natural equivalence immediately shows that $ T_n $ is the free $ T $-algebra on $ n $ elements.

### 2024-09-06 report/src/category-theory.tex
Fix a couple of TODO's, write about Selinger

@@
 \subsection{Weak equivalences}
-There is also the notion of `weak equivalence'. In some cases, this is equivalent to an adjoint equivalence (for example, when its domain is univalent).
+There is also the notion of `weak equivalence'. In some cases, this is equivalent to an adjoint equivalence (for example, when its domain is univalent, see Section \ref{sec:univalence-principle}).
 \begin{definition}
@@
 \begin{definition}\label{def:Yoneda-embedding}
-  The \iindex{Yoneda embedding} $ Y : C \hookrightarrow P C $ is given on objects by $ Y(c) = C(-, c) $:
-  \[ Y(c)(d) = C(d, c) \quad \text{and} \quad Y(c)(f)(g) = f \cdot g \]
-  for $ d: C $, $ f: C(d, d^\prime) $ and $ g: C(d^\prime, c) $. It sends a morphism $ f: C(c, c^\prime) $ to the natural transformation $ Y(f): C(-, c) \Rightarrow C(-, c^\prime) $ given by
-  \[ Y(f)(d)(g) = g \cdot f \]
+  The \iindex{Yoneda embedding} $ \yo : C \hookrightarrow P C $ is given on objects by $ \yo(c) = C(-, c) $:
+  \[ \yo(c)(d) = C(d, c) \quad \text{and} \quad \yo(c)(f)(g) = f \cdot g \]
+  for $ d: C $, $ f: C(d, d^\prime) $ and $ g: C(d^\prime, c) $. It sends a morphism $ f: C(c, c^\prime) $ to the natural transformation $ \yo(f): C(-, c) \Rightarrow C(-, c^\prime) $ given by
+  \[ \yo(f)(d)(g) = g \cdot f \]
   for $ d: C $ and $ g: C(d, c) $.
@@
 \begin{lemma}
-  For any $ A: C $ and $ F : P C $, we have an equivalence $ P C(Y(A), F) \simeq F(A) $, and this equivalence is natural in $ c $ and $ F $.
-\end{lemma}
-\begin{proof}
-  It sends a natural transformation $ \alpha: P C(Y(A), F) $ to the element $ \alpha_A(\id A) $.
-Conversely, it sends an element $ x : P(A) $ to the natural transformation $ \alpha $ given by $ \alpha_B(f) = P(f)(x) $ for all $ f: Y(A)(B) = C(B, A) $.
+  For any $ A: C $ and $ F : P C $, we have an equivalence $ P C(\yo(A), F) \simeq F(A) $, and this equivalence is natural in $ c $ and $ F $.
+\end{lemma}
+\begin{proof}
+  It sends a natural transformation $ \alpha: P C(\yo(A), F) $ to the element $ \alpha_A(\id A) $.
+Conversely, it sends an element $ x : P(A) $ to the natural transformation $ \alpha $ given by $ \alpha_B(f) = P(f)(x) $ for all $ f: \yo(A)(B) = C(B, A) $.
 For more details, see \autocite{Kashiwara}, Proposition 1.4.3.
@@
   Also, for any small category $ C $ (small means that the collection of objects is a type in our type universe.
-For example: $ \TYPE $ or $ \SET $ are not small categories, because a type cannot contain itself), the presheaf category $ P C $ has exponential objects, given by
-  \[ (F^G)(X) = \hom{PC}(Y(X) \times G, F) \]
+For example: for a fixed universe of types, $ \TYPE $ or $ \SET $ are not small categories, the universe of types is not contained in itself), the presheaf category $ P C $ has exponential objects, given by
+  \[ (F^G)(X) = \hom{PC}(\yo(X) \times G, F) \]
   the natural transformations from the product functor of the Yoneda embedding of $ X $ and $ G $, to $ F $ (see \autocite{MacLane-Moerdijk}, Section I.6, Proposition 1).
@@
   See \autocite{borceux}, Volume 1, Proposition 2.15.5 for the full proof, but note that for binary products, we have bijections
-  \[ Y(A \times B)(X) \xrightarrow \sim Y(A)(X) \times Y(B)(X) \]
-  sending $ f : C(X, A \times B) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(X, A) \times Y(X, B) $ to the product morphism $ \langle g_1, g_2 \rangle : Y(X, A \times B) $.
+  \[ \yo(A \times B)(X) \xrightarrow \sim \yo(A)(X) \times \yo(B)(X) \]
+  sending $ f : C(X, A \times B) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(X, A) \times C(X, B) $ to the product morphism $ \langle g_1, g_2 \rangle : Y(X, A \times B) $.
 This idea is the core of the proof about all limits.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:Yoneda-preserves-exponentials}
   The Yoneda embedding preserves exponentials.
@@
   \begin{align*}
-    Y(A^B)(X) &\cong P C(Y(X), Y(A^B))\\
+    \yo(A^B)(X) &\cong P C(\yo(X), \yo(A^B))\\
     &\cong C(X, A^B)\\
     &\cong C(X \times B, A)\\
-    &\cong P C(Y(X \times B), Y(A))\\
-    &\cong P C(Y(X) \times Y(B), Y(A))\\
-    &\cong P C(Y(X), Y(A)^Y(B))\\
-    &\cong (Y(A)^Y(B))(X)
+    &\cong P C(\yo(X \times B), \yo(A))\\
+    &\cong P C(\yo(X) \times \yo(B), \yo(A))\\
+    &\cong P C(\yo(X), \yo(A)^\yo(B))\\
+    &\cong (\yo(A)^\yo(B))(X)
   \end{align*}
@@
 
-  Some calculating shows that when applying this isomorphism to some $ f: Y(A^B)(X) $, we get the natural transformation $ h: P C(Y(X) \times Y(B), Y(A)) $ given by
+  Some calculating shows that when applying this isomorphism to some $ f: \yo(A^B)(X) $, we get the natural transformation $ h: P C(\yo(X) \times \yo(B), \yo(A)) $ given by
   \[ h_Z(g_1, g_2) = \langle g_1, g_2 \rangle \cdot \varphi^{-1}(f) \]
-  for all $ Z: C $ and $ (g_1, g_2) : Y(X)(Z) \times Y(B)(Z) $ and with the natural bijection
+  for all $ Z: C $ and $ (g_1, g_2) : \yo(X)(Z) \times \yo(B)(Z) $ and with the natural bijection
   \[ \varphi: C(X \times B, A) \xrightarrow \sim C(X, A^B). \]
@@
   It turns out that when we apply the morphism in Definition \ref{def:exponentials-preservation} to $ f $, we get exactly the same natural transformation.
-Therefore, the morphism in Definition \ref{def:exponentials-preservation} is the isomorphism defined here and we conclude that $ Y $ preserves exponentials.
-\end{proof}
-
-For a functor between categories $ f: C \to D $, given the Yoneda embeddings $ Y_C : C \to P C $ and $ Y_D : D \to P D $ (we will often omit the subscript $ C $ and $ D $), we can create a diagram
-\begin{center}
-  \begin{tikzcd}
-    C \arrow[r, "f"] \arrow[d, hookrightarrow, "Y"] & D \arrow[d, hookrightarrow, "Y"]\\
+Therefore, the morphism in Definition \ref{def:exponentials-preservation} is the isomorphism defined here and we conclude that $ \yo $ preserves exponentials.
+\end{proof}
+
+For a functor between categories $ f: C \to D $, given the Yoneda embeddings $ \yo_C : C \to P C $ and $ \yo_D : D \to P D $ (we will often omit the subscript $ C $ and $ D $), we can create a diagram
+\begin{center}
+  \begin{tikzcd}
+    C \arrow[r, "f"] \arrow[d, hookrightarrow, "\yo"] & D \arrow[d, hookrightarrow, "\yo"]\\
     P C & P D \arrow[l, "\op f_*"]
@@
   For $ c, d : C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
-  \[ Y(c)(d) = C(d, c) \xrightarrow[f_{d, c}]{\sim} D(f(d), f(c)) = \op f_*(Y(f(c)))(d). \]
+  \[ \yo(c)(d) = C(d, c) \xrightarrow[f_{d, c}]{\sim} D(f(d), f(c)) = \op f_*(\yo(f(c)))(d). \]
   Also, for $ g: C(d^\prime, d) $, the following diagram commutes
@@
     \begin{tikzcd}
-      Y(c)(d) \arrow[d, "g \cdot -"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "f_{d^\prime, d}(g) \cdot -"]\\
-      Y(c)(d^\prime) \arrow[r, "f_{d^\prime, c}"] & \op f_*(Y(f(c)))(d^\prime)
-    \end{tikzcd}
-  \end{center}
-  so the isomorphism is natural in $ d $ and we have $ Y(c) \cong \op f_*(Y(f(c))) $ in $ P C $. Lastly, for $ g: C(c, c^\prime) $ and $ d: C $, the following diagram commutes
-  \begin{center}
-    \begin{tikzcd}
-      Y(c)(d) \arrow[d, "- \cdot g"] \arrow[r, "f_{d, c}"] & \op f_*(Y(f(c)))(d) \arrow[d, "- \cdot f_{c, c^\prime}(g)"]\\
-      Y(c^\prime)(d) \arrow[r, "f_{d, c^\prime}"] & \op f_*(Y(f(c^\prime)))(d)
-    \end{tikzcd}
-  \end{center}
-  so the isomorphism is natural in $ c $ and we have $ Y \cong f \bullet Y \bullet \op f_* $ in $ [C, P C] $.
+      \yo(c)(d) \arrow[d, "g \cdot -"] \arrow[r, "f_{d, c}"] & \op f_*(\yo(f(c)))(d) \arrow[d, "f_{d^\prime, d}(g) \cdot -"]\\
+      \yo(c)(d^\prime) \arrow[r, "f_{d^\prime, c}"] & \op f_*(\yo(f(c)))(d^\prime)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ d $ and we have $ \yo(c) \cong \op f_*(\yo(f(c))) $ in $ P C $. Lastly, for $ g: C(c, c^\prime) $ and $ d: C $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}
+      \yo(c)(d) \arrow[d, "- \cdot g"] \arrow[r, "f_{d, c}"] & \op f_*(\yo(f(c)))(d) \arrow[d, "- \cdot f_{c, c^\prime}(g)"]\\
+      \yo(c^\prime)(d) \arrow[r, "f_{d, c^\prime}"] & \op f_*(\yo(f(c^\prime)))(d)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ c $ and we have $ \yo \cong f \bullet \yo \bullet \op f_* $ in $ [C, P C] $.
 \end{proof}
@@
 Note that there are two different ways to translate this to univalent foundations.
-We can either interpret the existence of the object $ X $ and the retraction $ (r, s) : F \triangleleft \yo(X) $ as additional \textit{structure} on $ F $, or we can treat it as a \textit{property} and ask for \textit{mere existence} of $ X $, $ r $ and $ s $.
+We can either interpret the existence of the object $ X $ and the retraction $ (r, s) : F \triangleleft \yo(X) $ as additional \textit{structure} on $ F $, or we can treat it as a \textit{property} and ask for \textit{mere existence} (see Definition \ref{def:mere-existence}) of $ X $, $ r $ and $ s $.
 This gives rise to two different categories:
@@
 \end{remark}
+
+Even though univalence and the Rezk completion in general will be covered in Section \ref{sec:univalence-principle}, we will study univalence of the Karoubi envelope here:
 

### 2024-09-06 report/src/paper.tex
Fix a couple of TODO's, write about Selinger

@@
 
-  Therefore, we have the following diagram, showing that $ \prod_f \Delta_Y L $ is a retraction of $ \prod_{p_1} \Delta_{X \times L} L $:
+  Therefore, we have the following diagram, showing that $ \prod_f \Delta_Y L $ is a retract of $ \prod_{p_1} \Delta_{X \times L} L $:
   \begin{center}
@@
   Recall that the embedding $ \R_A \hookrightarrow \RAct{A_1} $ is the composition of a Yoneda embedding and two adjoint equivalences.
-These all preserve exponential objects (\TODO: Citation needed).
+These all preserve exponential objects (see Lemma \ref{lem:Yoneda-preserves-exponentials}).
 Now, note that $ A_1 $ is the image of $ U : \R_A $, so the exponential $ U_A^{U_A} $ is $ A_2 $, the image of $ U^U = \lambda x_1 x_2, x_1 x_2 = \mathbf 1_2 $.
@@
 
-\TODO Move the coproducts and theory of extensions to chapter 3?
+(\TODO Is it maybe a good idea to move the coproducts and theory of extensions to chapter 3?)
 

### 2024-09-06 report/src/univalent-foundations.tex
Fix a couple of TODO's, write about Selinger

@@
 
-\section{The univalence principle}
+\section{The univalence principle}\label{sec:univalence-principle}
 \enquote{\textit{Isomorphic objects are equivalent.}}
@@
 
+Also, if $ A $ is univalent, any full subcategory $ B \subseteq A $ is also univalent, because isomorphisms and equalities of objects in $ B $ can be shown to be the `the same' as their isomorphisms and equalities in $ A $.
+
 \begin{lemma}
-  For every category $ C $, there exists a univalent category $ \hat C $ with a weak equivalence
-  \[ \iota: C \hookrightarrow \hat C. \]
+  For every category $ C $, there exists a univalent category $ D $ with a weak equivalence
+  \[ \iota: C \hookrightarrow D. \]
 \end{lemma}
 \begin{proof}
+  One construction takes $ D $ to be the full subcategory of the presheaf category $ PC $ of objects that are isomorphic (there \textit{merely exists} an isomorphism) to the Yoneda embedding $ \yo(X) $ of some object $ X : C $.
 See \autocite{univalent-categories}, Theorem 8.5.
 \end{proof}
-We call this univalent category the \iindex{Rezk completion}.
-\TODO: Uniqueness?
+We call such a univalent category a \iindex{Rezk completion} of $ C $.
+
+\begin{remark}
+  We can call it \textit{the} Rezk completion, since it is unique: Precomposition with the weak equivalence $ \iota: C \hookrightarrow D $ gives an adjoint equivalence on the functor categories $ [D, E] \simeq [C, E] $ for any univalent category $ E $.
+From this, it follows that $ \iota $ is the ``initial functor'' from $ C $: any functor from $ C $ to a univalent category factors uniquely through $ \iota $.
+
+  Now, two initial functors $ F : C \to D $ and $ F^\prime : C \to D^\prime $ factor uniquely through each other:
+  \[ F^\prime = F \bullet G \quad \text{and} \quad F = F^\prime \bullet G^\prime \]
+  for some functors $ G $ and $ G^\prime $ and we can show that
+  \[ G \bullet G^\prime = \id D \quad \text{and} \quad G^\prime \bullet G = \id{D^\prime}. \]
+  From this, we can construct an equivalence $ D \cong D^\prime $.
+Since $ D $ and $ D^\prime $ are univalent, this equivalence gives an equality of categories, and because $ F \bullet G = F^\prime $, we have an equality of pairs
+  \[ (D, F) = (D^\prime, F^\prime). \]
+\end{remark}
 
@@
 If we want to express that the set of such $ x $ is nonempty as a mere proposition, we talk about \iindex{mere existence}:
-\begin{definition}
+\begin{definition}\label{def:mere-existence}
   Given a dependent type $ Y $ over $ X $, if we say that there \textit{merely exists} an element $ x: X $ such that $ Y(x) $, we mean that we have an element of the propositional truncation

### 2024-09-09 report/src/algebraic-structures.tex
Update some notation for the Yoneda lemma

@@
   \[ \Alg{T^\prime}(f^* T_n, A) \xrightarrow[\bar f_n \cdot -] \sim \Alg{T^\prime}(T^\prime_n, A) \]
-  is in fact the image of $ \bar f_n $ under the (covariant) Yoneda embedding of $ \Alg{T^\prime} $ into the functor category $ \Alg{T^\prime} \to \SET $:
-  \[ \hat Y(\bar f_n): \hat Y(f^* T_n) \to \hat Y(T^\prime_n). \]
+  is in fact the image of $ \op{\bar f_n} $ under the Yoneda embedding of $ \op{\Alg{T^\prime}} $ (or of $ \bar f_n $ under the covariant Yoneda embedding of $ \Alg{T^\prime} $) into the functor category $ \Alg{T^\prime} \to \SET $:
+  \[ \yo(\bar f_n): \yo(f^* T_n) \to \yo(T^\prime_n). \]
   Since the Yoneda embedding is fully faithful, this shows that $ \bar f_n $ is an isomorphism of $ T^\prime $-algebras, so in particular, it is a bijection.
@@
 
-We can also consider the category of `all' algebraic theory algebras together.
+Note that besides the categories $ \Alg T $, we can also consider the category of `all' algebraic theory algebras together.
 That is, the category $ C $ with $ C_0 = \sum_{T : \AlgTh}, \Alg T $ and $ C((T, A), (T^\prime, A^\prime)) $ consisting of pairs $ (f, f^\prime): \AlgTh(T, T^\prime) \times \SET(A, A^\prime) $ such that for all $ t: T_n $ and $ a: A^n $,

### 2024-09-09 report/src/category-theory.tex
Update some notation for the Yoneda lemma

@@
   \[ \yo(A \times B)(X) \xrightarrow \sim \yo(A)(X) \times \yo(B)(X) \]
-  sending $ f : C(X, A \times B) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(X, A) \times C(X, B) $ to the product morphism $ \langle g_1, g_2 \rangle : Y(X, A \times B) $.
-This idea is the core of the proof about all limits.
+  sending $ f : C(X, A \times B) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(X, A) \times C(X, B) $ to the product morphism $ \langle g_1, g_2 \rangle : \yo(X, A \times B) $.
+This idea is also the core of the proof about general limits.
 \end{proof}
@@
 \begin{proof}
-  Note that $ c = (c_0, a) $ for some $ c_0: C $ and an idempotent $ a: c \to c $. We have morphisms
-  \begin{tikzcd}
-    \iota_C(c) \arrow[r, shift left, "a_\rightarrow"] & (c, a) \arrow[l, shift left, "a_\leftarrow"]
-  \end{tikzcd}, both given by $ a $. We have $ a_\leftarrow \cdot a_\rightarrow = a = \id{(c, a)} $, so $ (c, a) $ is a retract of $ \iota_C(c) $.
+  Note that $ c = (c_0, a) $ for some $ c_0: C $ and an idempotent $ a: c \to c $. We have
+  \[ (a, a) : (c, a) \triangleleft \iota_C(c), \]
+  since $ a \cdot a = a = \id{(c, a)} $, so $ (c, a) $ is a retract of $ \iota_C(c) $.
 \end{proof}
@@
 
-  Now, we have $ (c_0, e): \overline C $ and morphisms
-  \begin{tikzcd}
-    (c_0, a) \arrow[r, shift left, "e_\rightarrow"] & (c_0, e) \arrow[l, shift left, "e_\leftarrow"]
-  \end{tikzcd}, both given by $ e $.
-We have $ e_\leftarrow \cdot e_\rightarrow = e = \id{(c_0, e)} $, so $ (c_0, e) $ is a retract of $ (c_0, a) $.
-Also, $ e = e_\rightarrow \cdot e_\leftarrow $, so $ e $ is split.
-\end{proof}
-
-\begin{remark}
-  Note that the embedding is fully faithful, since
+  Now, we have $ (c_0, e): \overline C $ and
+  \[ (e, e) : (c_0, e) \triangleleft (c_0, a), \]
+  because $ e \cdot e = e = \id{(c_0, e)} $. Also, $ e = e \cdot e $, so $ e $ is split.
+\end{proof}
+
+\begin{remark}
+  Note that $ \iota_C $ is fully faithful, since
   \[ \overline C((c, \id c), (d, \id d)) = \{ f: C(c, d) \mid \id c \cdot f \cdot \id d = f \} = C(c, d). \]
@@
 \begin{remark}\label{rem:retract-coequalizer}
-  Let $ D $ be a category. Suppose that we have a retraction-section pair in $ D $, given by
-  \begin{tikzcd}
-    d \arrow[r, shift left, "r"] & d^\prime \arrow[l, shift left, "s"]
-  \end{tikzcd}.
-  Now, suppose that we have an object $ c: D $ and a morphism $ f $ with $ (r \cdot s) \cdot f = f $.
-Then we get a morphism $ s \cdot f: d^\prime \to c $ such that $ f $ factors as $ r \cdot (s \cdot f) $.
-Also, for any $ g $ with $ r \cdot g = f $, we have
-  \[ g = s \cdot r \cdot g = s \cdot f. \]
+  Let $ D $ be a category and suppose that we have two objects $ d, d^\prime : D $ and a retraction
+  \[ (r, s) : d^\prime \triangleleft d. \]
+  Then $ d^\prime $ is the equalizer of \begin{tikzcd}
+    d \arrow[r, shift left, "\id d"] \arrow[r, shift right, "r \cdot s"'] & d \end{tikzcd} in the following way:
+
+  Suppose that we have an object $ c: D $ and a morphism $ f $ with $ (r \cdot s) \cdot f = f $.
+Then we get a morphism $ s \cdot f: D(d^\prime, c) $ such that $ f $ factors as $ r \cdot (s \cdot f) $.
+Also, for any $ g: D(d^\prime, c) $ with $ r \cdot g = f $, we have $ g = s \cdot r \cdot g = s \cdot f $:
   \begin{center}
@@
   \end{center}
-  Therefore, $ d^\prime $ is the equalizer of \begin{tikzcd}
-    d \arrow[r, shift left, "\id d"] \arrow[r, shift right, "r \cdot s"'] & d
-  \end{tikzcd}. In the same way, it is also the coequalizer of this diagram.
+
+  In a similar way, $ d^\prime $ is also the coequalizer of the given diagram.
 
@@
 
-There is also another (classically equivalent) definition of the Karoubi envelope.
+Besides $ \overline C $, there is also another (classically equivalent) definition of the Karoubi envelope.
 An object in this alternative category is a presheaf $ F : PC $ that is a retract of the Yoneda embedding $ \yo(X) $ of an object $ X : C $.
@@
 We send $ (F, X, r, s) $ to $ (X, f) $.
-Note that both $ F $ is the equalizer of $ \id{\yo X} $ and $ r \cdot s $.
-Therefore, it is isomorphic to the image of $ (X, f) $.
+Note that both $ F $ and the image of $ (X, f) $ are equalizers of $ \id{\yo X} $ and $ r \cdot s $, so they are isomorphic.
 
@@
 Note that this is also essentially surjective: by definition, for any $ (F, H) : \hat C $, there merely exist $ X $, $ r $ and $ s $ such that $ (X, r, s) $ truncates to $ H $.
-  Therefore, we have a weak equivalence from $ tilde C $ to $ \hat C $. However, as we will see, $ \tilde C $ is usually not univalent, so this does not give an adjoint equivalence of categories.
-\end{remark}
+  Therefore, we have a weak equivalence from $ \tilde C $ to $ \hat C $. However, as we will see, $ \tilde C $ is usually not univalent, so this does not give an adjoint equivalence of categories.
+\end{remark}
+
+This all leads up to:
+\begin{corollary}
+  We have three candidates for the category of retracts, which are related to each other and to $ C $ and $ PC $ as follows:
+  \begin{center}
+    \begin{tikzcd}
+      C \arrow[r, hook, "\iota_C"] & \overline C \arrow[r, "\sim"] & \tilde C \arrow[r, hook, two heads] & \hat C \arrow[r, phantom, "\subseteq"] & PC
+    \end{tikzcd}
+  \end{center}
+  The fact that $ \hat C $ is univalent, and has weak equivalences from $ \overline C $ and $ \tilde C $ exhibits $ \hat C $ as the Rezk completion of $ \overline C $ and $ \tilde C $.
+\end{corollary}
 
@@
 
-This all leads up to:
-\begin{corollary}
-  We have three candidates for the category of retracts, which are related to each other and to $ C $ and $ PC $ as follows:
-  \begin{center}
-    \begin{tikzcd}
-      C \arrow[r, hook, "\iota_C"] & \overline C \arrow[r, "\sim"] & \tilde C \arrow[r, hook, two heads] & \hat C \arrow[r, phantom, "\subseteq"] & PC
-    \end{tikzcd}
-  \end{center}
-  The fact that $ \hat C $ is univalent, and has weak equivalences from $ \overline C $ and $ \tilde C $ exhibits $ \hat C $ as the Rezk completion of $ \overline C $ and $ \tilde C $.
-\end{corollary}
-
-\begin{remark}
-  Our choice of definition will have consequences.
+\begin{remark}
+  As we saw in this section, there are multiple candidates for the `Karoubi envelope'.
+Two of these candidates are equivalent to each other, but the third is not.
+Therefore, we need to be careful which definition we choose, because this choice has consequences.
 One one hand, $ \hat C $ is univalent, but very abstract.
-In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism.
-On the other hand, $ \overline C $ and $ \tilde C $ are very elementary and concrete, but not univalent, which makes working with them also hard.
+In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \hat C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism.
+On the other hand, $ \overline C $ and $ \tilde C $ are very elementary and concrete, which sometimes helps when doing constructions.
+However, they are not univalent, which makes working with them complicated in a different way.
 \end{remark}

### 2024-09-09 report/src/metadata.tex
Update some notation for the Yoneda lemma

@@
       \&
-      C_{{L_0}_1} \arrow[dd, "Y" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] \& \& \& \R_{L_0} \arrow[dd, "Y" description, hook] \arrow[rd, "\sim" description, no head] \& \& \\
+      C_{{L_0}_1} \arrow[dd, "\yo" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] \& \& \& \R_{L_0} \arrow[dd, "\yo" description, hook] \arrow[rd, "\sim" description, no head] \& \& \\
       \&
-      \& C_{L_1} \arrow[dd, "Y" description, hook] \arrow[r, hook] \& \mathbf L \arrow[rr, hook] \arrow[dd, "Y" description, hook] \& \& \mathbf R \arrow[dd, "Y" description, hook] \arrow[rdd, hook] \& \\
+      \& C_{L_1} \arrow[dd, "\yo" description, hook] \arrow[r, hook] \& \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, hook] \& \& \mathbf R \arrow[dd, "\yo" description, hook] \arrow[rdd, hook] \& \\
       \RAct{{L_0}_1} \&

### 2024-09-09 report/src/paper.tex
Update some notation for the Yoneda lemma

@@
   \begin{tikzcd}
-    C_{L_1} \arrow[d, "Y", hook] &
-    \mathbf L \arrow[l, "\op i"'] \arrow[d, "Y", hook] &
-    \mathbf R \arrow[rd, hook] \arrow[d, "Y", hook] \arrow[l, "\op j"']\\
+    C_{L_1} \arrow[d, "\yo", hook] &
+    \mathbf L \arrow[l, "\op i"'] \arrow[d, "yo", hook] &
+    \mathbf R \arrow[rd, hook] \arrow[d, "\yo", hook] \arrow[l, "\op j"']\\
     P C_{L_1} &
@@
   Note:
-  \[ (Y \bullet j_*)(A)(n) = (j \bullet (Y(A)))(n) = Y(A)(j(n)) = \R(U^n, A) \]
+  \[ (\yo \bullet j_*)(A)(n) = (j \bullet (\yo(A)))(n) = \yo(A)(j(n)) = \R(U^n, A) \]
   \[ (\iota \bullet \sim)(A)(n) = \{ a : L_n \mid \iota_{0, n}(A) a = a \} \]
@@
   Lastly, for $ f : L_m^n $, the presheaf actions
-  \[ (Y \bullet j_*)(A)(f) : \R(U^n, A) \to \R(U^m, A) \]
+  \[ (\yo \bullet j_*)(A)(f) : \R(U^n, A) \to \R(U^m, A) \]
   and
@@
   There also is a more category-theoretical argument: Suppose that every object of $ \Pshf L $ is a retract of $ L $.
-Via the equivalence $ \Pshf L \cong L_1 $, we see that every object of $ P C_{L_1} $ is a retract of $ Y(\star) $.
+Via the equivalence $ \Pshf L \cong L_1 $, we see that every object of $ P C_{L_1} $ is a retract of $ \yo(\star) $.
 However then the embedding of $ \hat \R $ (Definition \ref{def:karoubi'}) into $ P C_{L_1} $ is an adjoint equivalence.
-Since $ Y_{\R} \bullet {\op{\iota_{L_1}}}_* : \R \to \hat \R $ and $ {\op{\iota_{L_1}}}_* : P \R \to P C_{L_1} $ are weak equivalences, (Lemma \ref{lem:retracts-rezk}, Corollary \ref{cor:karoubi-presheaf}), $ Y_\R : \R \to P \R $ is a weak equivalence as well, but the Yoneda embedding is never essentially surjective.
-For any category $ C $, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = Y(c)(c) $, so $ Y(c) $ is not isomorphic to $ E $.
+Since $ \yo_{\R} \bullet {\op{\iota_{L_1}}}_* : \R \to \hat \R $ and $ {\op{\iota_{L_1}}}_* : P \R \to P C_{L_1} $ are weak equivalences, (Lemma \ref{lem:retracts-rezk}, Corollary \ref{cor:karoubi-presheaf}), $ \yo_\R : \R \to P \R $ is a weak equivalence as well, but the Yoneda embedding is never essentially surjective.
+For any category $ C $, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = \yo(c)(c) $, so $ \yo(c) $ is not isomorphic to $ E $.
 \end{remark}
@@
     \begin{tikzcd}
-      & C_{A_1} \arrow[d, hookrightarrow, "Y"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "Y"]\\
+      & C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
       \RAct{A_1} & P C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
@@
       &
-      C_{{L_0}_1} \arrow[dd, "Y" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "Y" description, hook] \arrow[rd, "\sim" description, no head] & & \\
+      C_{{L_0}_1} \arrow[dd, "\yo" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, hook] \arrow[rd, "\sim" description, no head] & & \\
       &
-      & C_{L_1} \arrow[dd, "Y" description, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "Y" description, hook] & & \mathbf R \arrow[dd, "Y" description, hook] \arrow[rdd, hook] & \\
+      & C_{L_1} \arrow[dd, "\yo" description, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, hook] & & \mathbf R \arrow[dd, "\yo" description, hook] \arrow[rdd, hook] & \\
       \RAct{{L_0}_1} &
@@
   \[ \eta_L: L \xrightarrow \sim E_{\Pshf L}(L) \xrightarrow \sim E_{\RAct{{L_0}_1}}(U_{L_0}). \]
-  It is quite easy to work out that we can make this explicit as (dropping the $ L $ and just writing $ \eta_L $)
+  It is quite easy to work out that we can make this explicit as (dropping the $ n $ and just writing $ \eta_L $)
   \[ \eta_n:
@@
   Note that we can do the same with Scott's version of his representation theorem, using the chain of equivalences and an embedding
-  \[ \mathbf R \xrightarrow \sim \mathbf R_{L_0} \xrightarrow{Y} P \R_{L_0} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}, \]
+  \[ \mathbf R \xrightarrow \sim \mathbf R_{L_0} \xrightarrow{\yo} P \R_{L_0} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}, \]
   Here, it is a bit harder to get an explicit formula for $ \eta $, because we need to do a bit more conversion between $ U_A^n $ and the image of $ U^n $ after the embedding $ \varphi: \mathbb R \hookrightarrow \RAct{{L_0}_1} $.

### 2024-09-10 report/src/category-theory.tex
Start rewriting the account of the relavite cartesian closedness

@@
-\chapter{Category Theoretic Preliminaries}
+\chapter{Category Theoretic Preliminaries}\label{ch:category-theory}
 
@@
 This all leads up to:
-\begin{corollary}
+\begin{corollary}\label{cor:karoubi-candidates}
   We have three candidates for the category of retracts, which are related to each other and to $ C $ and $ PC $ as follows:

### 2024-09-10 report/src/paper.tex
Start rewriting the account of the relavite cartesian closedness

@@
 
-Recall that Paul Taylor constructed a category of `dependent retracts' $ \R^A $, and then defined a class of display maps for $ \R $ in such a way that it gives a weak equivalence $ \sum_A : \R^A \xrightarrow{\sim} (\R \downarrow_D A) $.
-I.e., a map $ f: \R(X, A) $ is defined to be a display map if it is isomorphic to something in the image of the functor $ \sum_A $.
-We saw that these display maps can also be characterized as the retracts of the projection $ p_1: A \times U \to A $ in $ (\R \downarrow A) $.
-
-Now, noticing that we can embed $ \R $ as a full subcategory in $ \Pshf L $, Hyland attempts to do a similar thing for $ \Pshf L $.
-Noting that the universal object $ U : \R $ is embedded as the theory presheaf $ L : \Pshf L $, he defines a full subcategory $ \R(A) \subseteq (\Pshf L \downarrow A) $, consisting precisely of the retracts of $ \Delta_A L $ in $ (\Pshf L \downarrow A) $.
-
-\begin{remark}
-  Again, being a retract of $ \Delta_A L $ is not a mere proposition. For example, consider $ \id L : D(L, L) $:
-  \begin{center}
-    \begin{tikzcd}
-      L \arrow[rr, shift left, "s"] \arrow[rd, "\id L"'] & & L \times L \arrow[ll, shift left, "r"] \arrow[ld, "p_1"]\\
-      & L
-    \end{tikzcd}
-  \end{center}
-  There are multiple possible retraction-section pairs $ (r, s) $ that make the diagram commute.
-For example, we can take $ s $ to be the diagonal embedding $ \Delta : L \to L \times L $ (sending $ l $ to $ (l, l) $).
-Then we can take $ r = p_1 $ or $ r = p_2 $.
-We can also take $ r = \pi_1 $ and $ s = \langle \id L, g \rangle $ the product morphism of $ \id L $ and any (possibly constant) endomorphism $ g: L \to L $.
-
-  Therefore, we need to take the propositional truncation of the existence of $ r $ and $ s $.
-\end{remark}
-
-\begin{remark}
-  Taylor would write $ (\Pshf L \downarrow_D A) $ instead of $ \R(A) $, with $ D(X, A) $ the retracts $ f: X \to A $ of $ \Delta_A L $.
+Recall that in the last chapter, we saw that Paul Taylor shows that the category of retracts $ \R $, studied by Scott, is not only cartesian closed, but also `relatively cartesian closed'.
+To make his proof work in univalent foundations, we need the axiom of choice.
+The category in question is the Karoubi envelope of the category $ C_{L_0} $ associated to the monoid $ (L_0, \circ) $.
+
+Now, recall from Chapter \ref{ch:category-theory}, that in univalent foundations there are three different definitions that we can take for the Karoubi envelope, denoted $ \overline C_{L_0} $, $ \tilde C_{L_0} $ and $ \hat C_{L_0} $.
+There is three of them because in classical category theory there are two definitions that are equivalent, and because for one of the definitions we have to choose whether we interpret the `existence' of a retraction as additional structure (the retraction is given explicitly) or as a property (where we demand `mere existence').
+This gives the following diagram (Corollary \ref{cor:karoubi-candidates}):
+\begin{center}
+  \begin{tikzcd}
+    C \arrow[r, hook, "\iota_C"] & \overline C \arrow[r, "\sim"] & \tilde C \arrow[r, hook, two heads] & \hat C \arrow[r, phantom, "\subseteq"] & PC
+  \end{tikzcd}
+\end{center}
+where $ \overline C_{L_0} $ and $ \tilde C_{L_0} $ are equivalent to each other, but usually not to $ \hat C_{L_0} $.
+We saw that $ \hat C_{L_0} $ is the Rezk completion of $ \overline C_{L_0} $ and $ \tilde C_{L_0} $.
+
+This is a fine example of a situation where notions that are equivalent in classical mathematics actually diverge in univalent foundations.
+We might say that this is annoying, because we have to be more careful which definition we pick.
+On the other hand, this gives `more detail' in some sense: it is interesting to study which proofs work in which context, and this tells us something about the nature of the proofs.
+
+The proofs of Scott and Taylor are about $ \overline C_{L_0} $, because they work explicitly with idempotents.
+The question whether it is possible to lift the proofs to $ \tilde C_{L_0} $ or $ \hat C_{L_0} $, is left for future research.
+On the other hand, as we will see, Hyland works with presheaves and in this way, he shows that $ \hat C_{L_0} $ is relatively cartesian closed.
+
+Now, officially, $ \hat C_{L_0} $ is the full subcategory of $ P C_{L_0} $, consisting of all objects $ X : P C_{L_0} $ such that there merely exists $ (r, s) : X \triangleleft \yo(\star) $.
+However, recall from the previous section that $ P C_{L_0} \cong P C_{L_1} \cong \Pshf L $.
+Under this equivalence, $ \yo(\star) $ is embedded as the theory presheaf $ L $, and we will work in the full subcategory $ \hat \R \subseteq \Pshf L $ of the objects $ X : \Pshf L $ such that there merely exists $ (r, s) : X \triangleleft L $.
+Of course, then $ \hat R $ is equivalent to $ \hat C_{L_0} $.
+
+\begin{remark}
+  There is a couple of tricks that we will use in this section.
+First of all, note that retractions can be composed.
+That is, given $ (r, s) : X \triangleleft Y $ and $ (r^\prime, s^\prime) : Y \triangleleft Z $, we have
+  \[ (r^\prime \cdot r, s \cdot s^\prime) : X \triangleleft Z. \]
+  Therefore, if we need to show that $ X $ is a retract of $ Z $, and we know that $ X $ is a retract of $ Y $, it remains to show that $ Y $ is a retract of $ Z $.
+
+  Also, functors preserve retractions, so if we have a functor $ F : C \to D $ and we have $ (r, s) : X \triangleleft Y $, then we have
+  \[ (F(r), F(s)) : F(X) \triangleleft F(Y). \]
+
+  Now, recall that in $ \R $, everything is a retract of $ U = \lambda x_1, x_1 $.
+Therefore, by the above, everything in the image of the embedding of $ \R $ into $ \Pshf L $ is a retract of $ L $, and therefore in $ \hat \R $.
+
+  Lastly, if we want to show that we can do some construction on some $ X : \hat \R $, we can often borrow the construction from $ \Pshf L $ to get some object $ Y : \Pshf L $.
+For this part, we cannot use the $ (r, s) : X \triangleleft L $.
+To show that $ Y $ is indeed in $ \hat \R $, we must show that there merely exist $ (r^\prime, s^\prime) : Y \triangleleft L $.
+By the recursion principle of the propositional truncation, we can pretend that we have a concrete $ (r, s) : X \triangleleft L $ to construct $ r^\prime $ and $ s^\prime $.
+\end{remark}
+
+Recall that Paul Taylor's display maps for $ \R $ can be characterized as the retracts of $ \Delta_X U $ (the projection $ p_1: X \times U \to X $) in $ (\R \downarrow X) $.
+This idea also works for $ \hat \R $, and Hyland defines $ D(Y, X) \subseteq \hat \R(Y, X) $ to consist of the retracts of $ \Delta_X L $ in $ (\hat \R \downarrow X) $.
+Note that, because $ \hat \R $ is a full subcategory of $ \Pshf L $, $ (\hat \R \downarrow X) $ is equivalent to $ (\Pshf L \downarrow X) $ for $ X : \hat \R $.
+
+\begin{remark}
+  Again, being a retract of $ \Delta_X L $ is usually not a mere proposition. For example, consider the ways in which $ \Delta_X L $ is a retract of itself:
+  \begin{center}
+    \begin{tikzcd}
+      X \times L \arrow[rr, shift left, "s"] \arrow[rd, "p_1"'] & & X \times L \arrow[ll, shift left, "r"] \arrow[ld, "p_1"]\\
+      & X
+    \end{tikzcd}
+  \end{center}
+  In this particular case, the fact that $ r $ and $ s $ are morphisms in the slice category requires that $ r \cdot p_1 = p_1 $ and $ s \cdot p_1 = p_1 $, but then we can take
+  \[ r = p_1 \times f \quad \text{and} \quad s = p_1 \times g  \]
+  (or more generally $ \langle p_1, f^\prime \rangle $ and $ \langle p_1, g^\prime \rangle $) for any $ f $ and $ g $ that satisfy $ g \cdot f = \id L $. Two options are
+  \[ f = g = \id L \quad \text{or} \quad f_n(t) = t (\lambda x_{n + 1}, x_{n + 1}), \quad g_n(t) = \lambda x_{n + 1}, \iota_{n, 1}(t), \]
+  and these options are distinct if $ L $ is nontrivial.
+
+  Therefore, if we want $ D(Y, X) $ to be a subset of $ \hat \R(Y, X) $, we need to take the propositional truncation of the existence of $ r $ and $ s $.
+\end{remark}
+
+% \begin{remark}
+%   Taylor would write $ (\Pshf L \downarrow_D A) $ instead of $ \R(A) $, with $ D(X, A) $ the retracts $ f: X \to A $ of $ \Delta_A L $.
 However, note that $ D $ is not a class of display maps.
@@
 
-  However, if we take $ X $ to be the initial (empty) presheaf, we see that there are no morphisms $ L \to X $, because the $ L_n $ are nonempty and the $ X_n $ are empty.
-
-  There also is a more category-theoretical argument: Suppose that every object of $ \Pshf L $ is a retract of $ L $.
+%   However, if we take $ X $ to be the initial (empty) presheaf, we see that there are no morphisms $ L \to X $, because the $ L_n $ are nonempty and the $ X_n $ are empty.
+
+%   There also is a more category-theoretical argument: Suppose that every object of $ \Pshf L $ is a retract of $ L $.
 Via the equivalence $ \Pshf L \cong L_1 $, we see that every object of $ P C_{L_1} $ is a retract of $ \yo(\star) $.
@@
 For any category $ C $, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = \yo(c)(c) $, so $ \yo(c) $ is not isomorphic to $ E $.
-\end{remark}
-
-Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \autocite{borceux}, Volume 3).
+% \end{remark}
+
+Note that $ D $ is indeed a class of display maps:
+\begin{enumerate}
+  \item Take $ f : D(Y, X) $ and $ g: \hat \R(Z, X) $.
+We can borrow the pullback from $ \Pshf L $ to get $ Y \times_X Z : \Pshf L $.
+We now must show that we have $ (r^\prime, s^\prime) : Y \times_X Z \triangleleft L $, and in this part, we can pretend that all the `merely exists' properties actually give us concrete elements.
+
+    Now, note that taking pullbacks gives a functor $ g^* : (\Pshf L \downarrow X) \to (\Pshf L \downarrow Z) $.
+Because $ Y $ is a retract of $ X \times L $, $ Y \times_X Z $ is a retract of $ X \times L \times_X Z $, which is isomorphic to $ Z \times L $.
+Since $ Z $ is a retract of $ L $ (and since $ - \times L $ is a functor), $ Z \times L $ is a retract of $ L \times L $.
+But this is (isomorphic to) the image of $ U \times U : \R $, so this is is a retract of $ L $, and we can compose this to a retraction
+    \[ Y \times_X Z \triangleleft Z \times L \triangleleft L \times L \triangleleft L. \]
+    Because $ \hat \R $ is a full subcategory of $ \Pshf L $ and $ Y \times_X Z $ is the pullback of $ f $ and $ g $ in $ \Pshf L $, we have that $ Y \times_X Z $ is also the pullback of $ f $ and $ g $ in $ \hat \R $.
+
+  \item Take $ f: D(Z, Y) $ and $ g: D(Y, X) $.
+    \TODO : Composite
+
+  \item Note that $ \Pshf L $ has a terminal presheaf $ I_n = \{ \star \} $.
+Under the embedding of $ \R $ into $ \Pshf L $, this is (isomorphic to) the image of $ \lambda x_1 x_2, x_2 : \R $, and therefore, it is a retract of $ L $.
+Now, given $ Y : \hat \R $, note that any morphisms between $ Y $ and $ I \times L $ trivially commute with the terminal projections.
+Since $ Y : \hat \R $, there merely exists $ (r, s) : Y \triangleleft L $, and since $ L \cong I \times L $, this means that the terminal projection is indeed in $ D(Y, I) $:
+    \begin{center}
+      \begin{tikzcd}
+        Y \arrow[rd, "!"'] \arrow[rr, dashed, shift left, "s"] & & I \times L \arrow[ld, "!"] \arrow[ll, dashed, shift left, "r"]\\
+        & I
+      \end{tikzcd}
+    \end{center}
+\end{enumerate}
+
+Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos and it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \autocite{borceux}, Volume 3).
 Therefore, for a morphism $ f: \Pshf L(Y, X) $, we have adjunctions
@@
 \begin{theorem}\label{thm:restrict-sum-product}
-  For $ (Y, f) : \R(X) $, we can restrict $ \sum_f $ and $ \prod_f $ to functors from $ \R(Y) $ to $ \R(X) $.
+  For $ f : D(Y, X) $, we can restrict $ \sum_f $ and $ \prod_f $ to functors from $ (\hat \R \downarrow_D Y) $ to $ (\hat \R \downarrow_D X) $.
 \end{theorem}

### 2024-09-10 report/src/univalent-foundations.tex
Update some notation for the Yoneda lemma
Start rewriting the account of the relavite cartesian closedness

@@
   For a type $ T $, a type $ \Vert T \Vert $ exists (\autocite{hottbook}, Section 3.7) with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
-It has a recursion principle stating that for a mere proposition $ B $, a function $ f: A \to B $ induces a function $ \vert f \vert: \Vert T \Vert \to B $ that commutes with $ \vert \cdot \vert $.
+It has a recursion principle stating that for a mere proposition $ B $, a function $ f: T \to B $ induces a function $ \vert f \vert: \Vert T \Vert \to B $ that commutes with $ \vert \cdot \vert $.
 This object is called the \index{truncation!propositional}\textit{propositional truncation}.
@@
 Often, when we prove a theorem or lemma that ``there exists some $ x: X $ such that $ Y(x) $'', what we actually mean is that we can construct an element $ x: X $ and then an element $ y : Y(x) $ of the dependent type $ Y $ over $ X $.
-This is equivalent to having an element of $ \sum_{x: X} Y(x) $.
-However, this is in general of course not a mere proposition.
+This is equivalent to constructing an element of $ \sum_{x: X} Y(x) $.
+However, this is in general not a mere proposition.
 If we want to express that the set of such $ x $ is nonempty as a mere proposition, we talk about \iindex{mere existence}:

### 2024-09-11 report/src/paper.tex
Write about where Hyland's proof about where relative cartesian closedness lives

@@
 
-Now, officially, $ \hat C_{L_0} $ is the full subcategory of $ P C_{L_0} $, consisting of all objects $ X : P C_{L_0} $ such that there merely exists $ (r, s) : X \triangleleft \yo(\star) $.
+Recall that in this thesis, we use the notation $ \Delta_X $ for the functor $ C \to (C \downarrow X) $, sending $ Y $ to $ p_1 : X \times Y \to X $.
+Also, we use the notation $ X \triangleleft Y $ to denote the type of retraction-section pairs $ r: Y \to X $ and $ s: X \to Y $.
+We will sometimes not name $ (r, s) : X \triangleleft Y $ explicitly, but just mention that we have $ X \triangleleft Y $, meaning that we have such $ r $ and $ s $.
+
+Now, officially, $ \hat C_{L_0} $ is the full subcategory of $ P C_{L_0} $, consisting of all objects $ X : P C_{L_0} $ such that there merely exists $ X \triangleleft \yo(\star) $.
 However, recall from the previous section that $ P C_{L_0} \cong P C_{L_1} \cong \Pshf L $.
-Under this equivalence, $ \yo(\star) $ is embedded as the theory presheaf $ L $, and we will work in the full subcategory $ \hat \R \subseteq \Pshf L $ of the objects $ X : \Pshf L $ such that there merely exists $ (r, s) : X \triangleleft L $.
-Of course, then $ \hat R $ is equivalent to $ \hat C_{L_0} $.
+Under this equivalence, $ \yo(\star) $ is embedded as the theory presheaf $ L $, and we will work in the full subcategory $ \hat \R \subseteq \Pshf L $ of the objects $ X : \Pshf L $ such that there merely exists $ X \triangleleft L $.
+Of course, then $ \hat \R $ is equivalent to $ \hat C_{L_0} $.
 
@@
 
-  Now, recall that in $ \R $, everything is a retract of $ U = \lambda x_1, x_1 $.
-Therefore, by the above, everything in the image of the embedding of $ \R $ into $ \Pshf L $ is a retract of $ L $, and therefore in $ \hat \R $.
-
   Lastly, if we want to show that we can do some construction on some $ X : \hat \R $, we can often borrow the construction from $ \Pshf L $ to get some object $ Y : \Pshf L $.
@@
 To show that $ Y $ is indeed in $ \hat \R $, we must show that there merely exist $ (r^\prime, s^\prime) : Y \triangleleft L $.
-By the recursion principle of the propositional truncation, we can pretend that we have a concrete $ (r, s) : X \triangleleft L $ to construct $ r^\prime $ and $ s^\prime $.
+By the recursion principle of the propositional truncation, we can assume that we have a concrete $ (r, s) : X \triangleleft L $ to construct $ r^\prime $ and $ s^\prime $.
 \end{remark}
@@
   Therefore, if we want $ D(Y, X) $ to be a subset of $ \hat \R(Y, X) $, we need to take the propositional truncation of the existence of $ r $ and $ s $.
+\end{remark}
+
+\begin{remark}
+  Recall that for all $ X : \R $, we have $ X \triangleleft U = \lambda x_1, x_1 $, so by the above, for all $ Y $ in the image of the embedding of $ \R $ into $ \Pshf L $, we have $ Y \triangleleft L $.
+In particular, $ Y $ is in $ \hat \R $.
+Actually, we already knew this, because this essentially describes the embedding of $ \R $ into its Rezk completion $ \hat \R $.
+
+  An important example is $ U \times U : \R $, which maps to something isomorphic to $ L \times L $ (because the Yoneda embedding and any adjoint equivalence preserves limits).
+The retraction $ (r, s) : L \times L \triangleleft L $ is given explicitly by the (pairing and splitting) morphisms
+  \[ s_n(a, b) = \lambda x_{n + 1}, x_{n + 1} a b \quad \text{and} \quad r_n(a) = (a (\lambda x_{n + 1} x_{n + 2}, x_{n + 1}), a (\lambda x_{n + 1} x_{n + 2}, x_{n + 2})). \]
+  Now, for any $ X, Y : \Pshf L $ and $ f : \Pshf L(Y, X) $, if we have $ (Y, f) \triangleleft \Delta_X L $ in $ \Pshf L $, we have in particular $ Y \triangleleft X \times L $.
+If we also have $ X \triangleleft L $, we also have $ X \times L \triangleleft L \times L $ because $ - \times L $ is a functor.
+Then we have
+  \[ Y \triangleleft X \times L \triangleleft L \times L \triangleleft L. \]
+  In particular, for any $ X : \hat \R $, if some $ (Y, f) : (\Pshf L \downarrow X) $ is a retract of $ \Delta_X L $, we know that $ Y $ is in $ \hat \R $.
 \end{remark}
@@
   \item Take $ f : D(Y, X) $ and $ g: \hat \R(Z, X) $.
-We can borrow the pullback from $ \Pshf L $ to get $ Y \times_X Z : \Pshf L $.
-We now must show that we have $ (r^\prime, s^\prime) : Y \times_X Z \triangleleft L $, and in this part, we can pretend that all the `merely exists' properties actually give us concrete elements.
+We can borrow the pullback from $ \Pshf L $ to get $ g^*(Y, f) : (\Pshf L \downarrow Z) $.
+We now must show that there merely exists $ g^* (Y, f) \triangleleft \Delta_Z L $ and in this part, we can assume that the mere existences of retractions are actually given by concrete retraction-section pairs.
 
     Now, note that taking pullbacks gives a functor $ g^* : (\Pshf L \downarrow X) \to (\Pshf L \downarrow Z) $.
-Because $ Y $ is a retract of $ X \times L $, $ Y \times_X Z $ is a retract of $ X \times L \times_X Z $, which is isomorphic to $ Z \times L $.
-Since $ Z $ is a retract of $ L $ (and since $ - \times L $ is a functor), $ Z \times L $ is a retract of $ L \times L $.
-But this is (isomorphic to) the image of $ U \times U : \R $, so this is is a retract of $ L $, and we can compose this to a retraction
-    \[ Y \times_X Z \triangleleft Z \times L \triangleleft L \times L \triangleleft L. \]
-    Because $ \hat \R $ is a full subcategory of $ \Pshf L $ and $ Y \times_X Z $ is the pullback of $ f $ and $ g $ in $ \Pshf L $, we have that $ Y \times_X Z $ is also the pullback of $ f $ and $ g $ in $ \hat \R $.
-
-  \item Take $ f: D(Z, Y) $ and $ g: D(Y, X) $.
-    \TODO : Composite
+Now, $ (Y, f) \triangleleft \Delta_X L $, gives $ (g^*Y, g^*f) \triangleleft g^*(\Delta_X L) $:
+    \begin{center}
+      \begin{tikzcd}
+        g^* Y
+          \arrow[rd, "g^*s", shift left]
+          \arrow[dd, "g^* f"]
+          \arrow[rr] &&
+        Y
+          \arrow[rd, "s", shift left]
+          \arrow[dd, "f"] & \\
+        & g^* (X \times L)
+          \arrow[lu, "g^*r", shift left]
+          \arrow[ld, "g^* p_1"]
+          \arrow[rr] & &
+        X \times L
+          \arrow[ld, "p_1"]
+          \arrow[lu, "r", shift left] \\
+        Z
+          \arrow[rr, "g"] & &
+        X &
+      \end{tikzcd}
+    \end{center}
+    The isomorphism between $ g^*(\Delta_X L) $ and $ \Delta_Z L $ (Remark \ref{rem:pullback-of-projection}) shows that we have $ (g^*Y, g^*f) \triangleleft \Delta_Z L $.
+From this, it also follows that $ g^* Y $ is in $ \hat \R $.
+
+    Now, $ g^*Y $ is the pullback of $ f $ and $ g $ in $ \Pshf L $, and $ \hat \R $ is a full subcategory of $ \Pshf L $, so $ g^* Y $ is also the pullback of $ f $ and $ g $ in $ \hat \R $.
+
+  \item Take $ f: D(Z, Y) $ and $ g: D(Y, X) $. We have to show that there merely exists $ (Z, f \cdot g) \triangleleft \Delta_X L $. Because this is a proposition, we can assume that we have
+  \[ (r_Z, s_Z) : (Z, f) \triangleleft \Delta_Y L \quad \text{and} \quad (r_Y, s_Y) : (Y, g) \triangleleft \Delta_X L. \]
+  Then the following diagram gives $ (Z, f \cdot g) \triangleleft \Delta_X (L \times L) $:
+    \begin{center}
+      \begin{tikzcd}
+        Z \arrow[rd, "f"'] \arrow[rr, "s_Z", shift left] & & Y \times L \arrow[ld, "p_1"] \arrow[ll, shift left, "r_Z"] \arrow[rr, shift left, "s_Y \times \id L"] && X \times L \times L \arrow[ll, shift left, "r_Y \times \id L"] \arrow[ld, "p_1"]\\
+        & Y \arrow[rd, "g"'] \arrow[rr, "s_Y", shift left] & & X \times L \arrow[ld, "p_1"] \arrow[ll, shift left, "r_Y"]\\
+        && X
+      \end{tikzcd}
+    \end{center}
+    Now, as we saw earlier, $ \Delta_X $ is a functor and $ L \times L $ is a retract of $ L $.
+Therefore, we have $ \Delta_X (L \times L) \triangleleft \Delta_X L $ and $ f \cdot g $ is in $ D(Z, X) $.
+
+    % \begin{align*}
+    %   (r_Y \times \id L) \cdot r_Z \cdot f \cdot g
+    %   &= (r_Y \times \id L) \cdot p_1 \cdot g\\
+    %   &= p_1 \cdot r_Y \cdot g\\
+    %   &= p_1 \cdot p_1\\
+    % \end{align*}
+
+    % \begin{align*}
+    %   s_Z \cdot (s_1 \times \id L) \cdot p_1 \cdot p_1
+    %   &= s_Z \cdot p_1 \cdot s_1 \cdot p_1\\
+    %   &= f \cdot g\\
+    % \end{align*}
 
   \item Note that $ \Pshf L $ has a terminal presheaf $ I_n = \{ \star \} $.
-Under the embedding of $ \R $ into $ \Pshf L $, this is (isomorphic to) the image of $ \lambda x_1 x_2, x_2 : \R $, and therefore, it is a retract of $ L $.
-Now, given $ Y : \hat \R $, note that any morphisms between $ Y $ and $ I \times L $ trivially commute with the terminal projections.
-Since $ Y : \hat \R $, there merely exists $ (r, s) : Y \triangleleft L $, and since $ L \cong I \times L $, this means that the terminal projection is indeed in $ D(Y, I) $:
-    \begin{center}
-      \begin{tikzcd}
-        Y \arrow[rd, "!"'] \arrow[rr, dashed, shift left, "s"] & & I \times L \arrow[ld, "!"] \arrow[ll, dashed, shift left, "r"]\\
+Under the embedding of $ \R $ into $ \Pshf L $, this is (isomorphic to) the image of $ \lambda x_1 x_2, x_2 : \R $, and therefore, it is in $ \hat \R $.
+Now, given $ Y : \hat \R $, we need to show that the terminal projection $ !
+$ is in $ D(Y, I) $.
+Note that any morphism trivially commutes with the terminal projections.
+Since $ Y : \hat \R $, we have $ (r, s) : Y \triangleleft L $, and since $ L \cong I \times L $, this means that the terminal projection is indeed in $ D(Y, I) $:
+    \begin{center}
+      \begin{tikzcd}
+        Y \arrow[rd, "!"'] \arrow[r, shift left, "s"] & L \arrow[d, "!"] \arrow[l, shift left, "r"] \arrow[r, "\sim"] & I \times L \arrow[ld, "!"]\\
         & I
@@
 \begin{proof}
-  This proof proceeds by reducing, step by step, to a known case.
-
-  We take $ (Z, g) : \R(Y) $.
-Since functors preserve retraction-section pairs, $ \prod_f(Z, g) $ is a retract of $ \prod_f \Delta_Y L $.
-Now, if this is a retract of $ \Delta_X L $, then $ \prod_f(Z, g) $ is a retract of $ \Delta_X L $ as well: We can just compose retractions and sections.
-Therefore, to show that the image of $ \R(Y) $ under $ \prod_f $ lies within $ \R(X) $, we just need to show that $ \prod_f \Delta_Y L $ lies in $ \R(X) $.
-In the same way, for $ \sum_f $ we just need to show that $ \sum_f \Delta_Y L $ lies in $ \R(X) $.
-
-  By the definition of $ \R(X) $, $ (Y, f) $ is a retract:
+  Given $ (Z, g) : (\Pshf L \downarrow Y) $, for $ \prod_F $ we only have to show that if we have $ (Z, g) \triangleleft \Delta_Y L $, then we have $ \prod_f(Z, g) \triangleleft \Delta_X L $.
+Note that since $ X $ is in $ \hat \R $, this also shows that $ \prod_f Z $ is in $ \hat \R $.
+Because functors preserve retractions, it suffices to show that we have $ \prod_f \Delta_Y L \triangleleft \Delta_X L $.
+
+  Since $ f : D(Y, X) $, we have a retraction
   \begin{center}
@@
   \end{center}
-  In a similar way, $ \sum_f \Delta_Y L $ is a retract of $ \sum_{p_1} \Delta_{X \times L} L $:
+  So it suffices to show that $ \prod_{p_1} \Delta_{X \times L} L $ is a retract of $ \Delta_X L $.
+By Lemma \ref{lem:constant-dependent-product}, we have $ \prod_{p_1} \Delta_{X \times L} L \cong \Delta_X L^L $.
+By functoriality of $ \Delta_X $, it suffices to show that $ L^L $ is a retract of $ L $.
+But we already saw in Theorem \ref{thm:representation-theorem} that $ L^L \cong A(L, 1) $ is a retract of $ L $.
+This shows that $ \prod_f $ indeed restricts to a functor from $ (\hat \R \downarrow_D Y) $ to $ (\hat \R \downarrow_D X) $.
+
+  The proof for $ \sum_f $ is very similar. $ \sum_f \Delta_Y L $ is a retract of $ \sum_{p_1} \Delta_{X \times L} L $:
   \begin{center}
@@
   \end{center}
-  So again, by the transitivity of retracts, we only have to show that $ \prod_{p_1} \Delta_{X \times L} L $ and $ \sum_{p_1} \Delta_{X \times L} L $ are retracts of $ \Delta_X L $.
-By Lemma \ref{lem:constant-dependent-product}, we have $ \prod_{p_1} \Delta_{X \times L} L \cong \Delta_X L^L $.
   By Lemma \ref{lem:sum-postcomposition}, the functor $ \sum_{p_1} $ is given by postcomposition, so $ \sum_{p_1} \Delta_{X \times L} L \cong \Delta_X (L \times L) $.
-
-  Since $ \Delta_X $ is a functor, and in particular, preserves retracts, we only have to show that $ L \times L $ and $ L^L $ are retracts of $ L $.
-
-  But we already saw in Theorem \ref{thm:representation-theorem} that $ L^L \cong A(L, 1) $ is a retract of $ L $.
-
-  Also, the (pairing and splitting) morphisms $ s: \Pshf L(L \times L, L) $ and $ r: \Pshf L(L, L \times L) $ given by
-  \[ s_n(a, b) = \lambda x_{n + 1}, x_{n + 1} a b \quad \text{and} \quad r_n(a) = (a (\lambda x_{n + 1} x_{n + 2}, x_{n + 1}), a (\lambda x_{n + 1} x_{n + 2}, x_{n + 2})) \]
-  exhibit $ L \times L $ as a retract of $ L $.
-\end{proof}
-
-\begin{remark}
-  Now, recall that according to Hyland, Taylor endows the category of retracts $ \R $ with a class of display maps $ D $, such that $ (\R \downarrow_D X) $ consists exactly of the retracts of $ \Delta_X U $.
-
-  Hyland then claims that the fact that $ \R $ is cartesian closed relative to this class of display maps follows from the theorem above.
+As we saw earlier, we have $ L \triangleleft L \times L $, which completes the proof that $ \sum_f $ restricts to a functor from $ (\hat \R \downarrow_D Y) $ to $ (\hat \R \downarrow_D X) $.
+\end{proof}
+
+\begin{corollary}
+  Since the $ (\hat \R \downarrow_D X) $ are full subcategories of the $ (\Pshf L \downarrow X) $, so we can restrict the adjunction $ f^* \dashv \prod_f $ to an adjunction $ \bar f^* \dashv \bar \prod_f $ between $ (\hat \R \downarrow_D X) $ and $ (\hat \R \downarrow_D Y) $, which shows that $ \hat \R $ is cartesian closed relative to the class $ D $ of display maps.
+\end{corollary}
+
+\begin{remark}
+  It is a nice feature of Hyland's approach that in univalent foundations, the proofs that $ D $ is a class of display maps and that we can restrict $ \prod_f $ and $ \sum_f $ work without the axiom of choice.
+\end{remark}
+
+\begin{remark}
+  Recall that to make sure that $ D(Y, X) $ is a subset of $ \hat \R(Y, X) $, we had no choice but to take the propositional truncation of the $ (Y, f) \triangleleft \Delta_X L $.
+Coincidentally, for $ \hat \R $ we also took the propositional truncation of the $ X \triangleleft L $.
+
+  In the proofs that $ D $ is a class of display maps, and that we can restrict $ \prod_f $, this worked out great.
+A couple of times, we first did a construction on the presheaves, ignoring the mere existence of the retractions, and then we showed mere existence of one or two retractions, for which we were allowed to assume that we actually had concrete retractions from $ L $ or $ \Delta_X L $.
+
+  Therefore, this only works in $ \hat \R \cong \hat C_{L_0} $.
+Suppose that we tried to do this in $ \tilde C_{L_0} $.
+Note that this category is equivalent to the category with as objects $ X : \Pshf L $, together with some $ (r, s) : X \triangleleft L $.
+Trying to define the pullback functor would already cause problems.
+To define a pullback, we would need to explicitly construct some retraction $ g^* Y \triangleleft L $, for which we would need a retraction $ Z \triangleleft L $.
+However, we have only mere existence of this retraction, so we would only be able to show mere existence of pullbacks, like in Taylor's proof.
+In Taylor's case, we were able to use the axiom of choice because the objects of $ \R $ form a set.
+However, the objects of $ \tilde \R $ do not form a set, and so we cannot use the axiom of choice here (Lemma 3.8.5 in \autocite{hottbook} shows why the axiom of choice only works for sets).
+
+  Since we have an adjoint equivalence between $ \tilde C_{L_0} $ and $ \overline C_{L_0} = \R $, and since any reasoning about $ \R $ using presheaves would use this equivalence, we would run into the same problems if we tried try to apply Hyland's approach to $ \R $.
+However, note that there we might be able to use the axiom of choice to show mere existence of a pullback functor, like in Taylor's proof.
+\end{remark}
+
+% \begin{remark}
+%   Now, recall that according to Hyland, Taylor endows the category of retracts $ \R $ with a class of display maps $ D $, such that $ (\R \downarrow_D X) $ consists exactly of the retracts of $ \Delta_X U $.
+
+%   Hyland then claims that the fact that $ \R $ is cartesian closed relative to this class of display maps follows from the theorem above.
 Recall that Taylor already shows relative cartesian closedness directly, which still works in univalent foundations if we assume the axiom of choice.
 
-  Recall that we have a weak equivalence $ \varphi : \R \xrightarrow \sim \hat \R $ (Lemma \ref{lem:retracts-rezk}) and one can imagine that we can extend this to weak equivalences $ \psi_X : (\R \downarrow_D X) \xrightarrow \sim (\hat \R \downarrow_D \varphi(X)) $.
+%   Recall that we have a weak equivalence $ \varphi : \R \xrightarrow \sim \hat \R $ (Lemma \ref{lem:retracts-rezk}) and one can imagine that we can extend this to weak equivalences $ \psi_X : (\R \downarrow_D X) \xrightarrow \sim (\hat \R \downarrow_D \varphi(X)) $.
 Hyland notes that for $ X : \hat \R $, $ \R(\varphi(X)) $ is equivalent to $ (\hat \R \downarrow_D \varphi(X)) $.
 Implicitly, for $ f: \R(X, Y) $, he wants to lift the functors $ \sum_f $, $ f^* $ and $ \prod_f $ along the equivalences $ \psi $:
-  \begin{center}
-    \begin{tikzcd}[sep=large]
-      (\R \downarrow_D X)
-        \arrow[d, "\psi_X"]
-        \arrow[r, dashed, bend left, "\sum_f"']
-        \arrow[r, dashed, bend right, "\prod_f"]
-      & (\R \downarrow_D Y)
-        \arrow[d, "\psi_Y"]
-        \arrow[l, dashed, "f^*" description]\\
-      \R(\varphi(X))
-        \arrow[r, bend left, "\sum_{\varphi(f)}"']
-        \arrow[r, bend right, "\prod_{\varphi(f)}"]
-      & \R(\varphi(Y))
-        \arrow[l, "\varphi(f)^*" description]\\
-    \end{tikzcd}
-  \end{center}
-  For this to work, we need to turn the weak equivalences $ \psi_X $ into adjoint equivalences.
+%   \begin{center}
+%     \begin{tikzcd}[sep=large]
+%       (\R \downarrow_D X)
+%         \arrow[d, "\psi_X"]
+%         \arrow[r, dashed, bend left, "\sum_f"']
+%         \arrow[r, dashed, bend right, "\prod_f"]
+%       & (\R \downarrow_D Y)
+%         \arrow[d, "\psi_Y"]
+%         \arrow[l, dashed, "f^*" description]\\
+%       \R(\varphi(X))
+%         \arrow[r, bend left, "\sum_{\varphi(f)}"']
+%         \arrow[r, bend right, "\prod_{\varphi(f)}"]
+%       & \R(\varphi(Y))
+%         \arrow[l, "\varphi(f)^*" description]\\
+%     \end{tikzcd}
+%   \end{center}
+%   For this to work, we need to turn the weak equivalences $ \psi_X $ into adjoint equivalences.
 In particular, we know that for every object $ A : \R(\varphi(X)) $, there merely exists a preimage $ \bar A : (\R \downarrow_D X) $ such that $ \psi_X(\bar A) \cong A $, and we need to construct a functor $ \psi_X^{-1}: \R(\varphi(X)) \to (\R \downarrow_D X) $.
 
-  For Taylor's proof, we did a similar thing when we knew that for every object $ X : (\R \downarrow_D A) $, there existed some $ Y : \R^A $, and we needed to construct a pullback functor $ f^* : (\R \downarrow_D A) \to (\R \downarrow_D B) $.
+%   For Taylor's proof, we did a similar thing when we knew that for every object $ X : (\R \downarrow_D A) $, there existed some $ Y : \R^A $, and we needed to construct a pullback functor $ f^* : (\R \downarrow_D A) \to (\R \downarrow_D B) $.
 We could use the axiom of choice here because the objects of $ \R $ (and therefore also the objects of the relative slices $ (\R \downarrow_D A) $) form a set.
 
-  However, as mentioned in \autocite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \autocite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
-
-  Therefore, in univalent foundations, the relative cartesian closedness is not a corollary of Theorem \ref{thm:restrict-sum-product}.
-\end{remark}
+%   However, as mentioned in \autocite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \autocite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
+
+%   Therefore, in univalent foundations, the relative cartesian closedness is not a corollary of Theorem \ref{thm:restrict-sum-product}.
+% \end{remark}
 
 \section{An elementary proof of the `Fundamental Theorem'}\label{sec:elementary-fundamental-theorem}
-The final theorem that Hyland works towards in his paper constructs an equivalence between $ \lambda $-calculi and $ \Lambda $-algebras.
+The final theorem that Hyland works towards in his paper constructs an equivalence between two ways to reason about the $ \lambda $-calculus using these tools from universal algebra: $ \lambda $-theories and $ \Lambda $-algebras.
 In this section, we will provide an elementary proof of this theorem.

### 2024-09-11 report/src/univalent-foundations.tex
Write about where Hyland's proof about where relative cartesian closedness lives

@@
 \end{itemize}
-If we think of types as propositions, the question whether some axiom is assumed or not becomes the question whether some (family of) type(s) is inhabited.
+If we think of types as propositions, the question whether some axiom is assumed or not becomes the question whether we assume some (family of) type(s) to be inhabited.
 Note that most of the axioms that we list here require the notion of mere propositions, propositional truncation and mere existence, which we will cover from Section \ref{sec:homotopy-props-sets} onwards.
@@
 This is axiom allows us to prove $ A $ from `not not $ A $'.
-  \item If for all dependent types $ C $ over $ A $ and $ B $, the type
+  \item If for all (homotopy) sets $ A $, dependent sets $ B(a) $ and dependent propositions $ C(a, b) $, the type
     \[ \left(\prod_{a: A} \exists (b: B), C(a, b) \right) \to \exists (f: A \to B), \prod_{a: A} C(a, f(a)) \]

### 2024-09-19 report/src/formalization.tex
Write about part of the formalization

% 996 0
% 447 37
% 1383 1017
% 26 26
% 6313 889
% 2562 2332
% 1255 326
% 3015 1
% 4206 1668
% 940 48
% 9 5
% 508 4
% 1701 1267
% Total: 23361 7620

% 434 292
% 1144 58
% 96 0
% 469 113
% 145 42
% 495 90
% 508 221
% Total: 3291 816

\chapter{The formalization}
In addition to the reading, investigating and writing mathematics that lead up to the previous chapters, this thesis project also had a formalization component. Parts of Hyland's paper were carefully written out in detail in a proof assistant and added to a library of formalized mathematics with the univalent point of view, called \textit{UniMath}.

This chapter will give an overview of what was formalized, as well as point out and evaluate a couple of design decisions that were made.

\section{Statistics}

The code for this project was written over the course of about 18 months, spread over \href{https://github.com/UniMath/UniMath/pulls?q=is%3Apr+author%3Aarnoudvanderleer+is%3Aclosed}{20 pull requests}: 13 with content about Hyland's paper, adding 23.361 and removing 7.620 lines of code, and 7 with only some missing category theoretical preliminaries, adding 3.291 and removing 816 lines.

\section{Components}

\subsection{Hyland's paper}
The formalized parts of Hyland's paper were collected in a package in the library called \textit{algebraic theories}. This package now consists of a little more than 10.000 lines of code.
\begin{itemize}
  \item Defines algebraic theories, $ \lambda $-theories, algebras and presheaves of algebraic theories, together with their morphisms and their categories. Shows that the categories are univalent and shows for the categories of algebraic theories, $ \lambda $-theories and presheaves that they have limits.
  \item Examples: the terminal algebraic theory, the initial algebraic theory, the $ \lambda $-theory $ \Lambda $.
  \item The `free object' algebraic theory with a functor from $ C $ to it's algebras. Also the equivalence between the `free monoid' algebraic theory $ T $, together with a proof that the functor from monoids to $ T $-algebras is an equivalence.
  \item The construction of the endomorphism theory of an object $ X $ in a category $ C $.
  \item Exponential objects in the category of presheaves.
  \item The original version of Scott's representation theorem.
  \item Hyland's version of Scott's representation theorem.
  \item The construction of a Lawvere theory from an algebraic theory, and the equivalence between
\end{itemize}

\subsection{Category theoretic preliminaries}
Since Hyland's paper uses a lot of general category theory, formalizing it meant adding a lot of missing category theory to the library. Among these are:
\begin{itemize}
  \item Univalence of the Sigma displayed category.
  \item The Sigma displayed category creates limits.
  \item Two definitions for the Karoubi envelope and their preliminaries.
  \item The contents of Section \ref{sec:monoid-category}: The construction of a one-object category from a monoid, the equivalence between it's presheaves and sets with a right monoid action, properties of the category of sets with a monoid action and restriction and extension of scalars.
  \item The Yoneda embedding preserves exponential objects.
  \item The uniqueness of the Rezk completion.
  \item A precomposition functor is equivalent if ...
\end{itemize}

\section{Equality, Isomorphisms and Equivalences}
One of the lessons during this project was that for formalizing, it is always important to choose te right equality for the job. For example, for two categories $ C $ and $ C^\prime $, one can aim to prove either that $ C = C^\prime $ or that we have a functor $ F : C \to C^\prime $ that has a right and left inverse, or that we have a functor $ F : C \to C^\prime $ that is an adjoint equivalence. Even though for univalent categories, these three notions all coincide, in practice it is really hard to show equality of categories directly: To show $ C = C^\prime $, we would need to show that we have an equality $ H : C_0 = C_0^\prime $, and then that for all $ c, c^\prime : C $
\[ (C(\mathrm{transport}_H(c), \mathrm{transport}_H(c^\prime))) = C^\prime(c, c^\prime). \]
It is usually much easier to show that there exists a functor $ F $ with an inverse, because then we don't have to show these equalities of types, but can suffice with maps between the types and equalities of the objects and morphisms that are mapped. However, for the morphisms we still have transports.

The easiest option is usually to show that we have an adjoint equivalence. That way, we don't have to show equality of objects, but only isomorphism (even though in a univalent category, that is of course the same). Then we only have to show equality of morphisms, and this is usually very doable.

An example of this is the proof that for the algebraic $ T $ where $ T_n $ is the free monoid on $ \{ x_1, \dots, x_n \} $, the $ T $-algebras are equivalent to monoids. Initially, this was a proof about (weak) equivalence (so under univalence, equality) of the object types, but of course, this says nothing about morphisms, so it is incomplete. However, it was possible to remove parts of the proof, and use the rest to construct an adjoint equivalence.

In general, the formalization is the cleanest and the easiest when we use equality for elements of homotopy sets (morphisms, for example), isomorphisms for objects in a category and adjoint equivalences for categories themselves.

\section{Displayed categories}\label{sec:displayed-categories}

\index{displayed category}\textit{Displayed categories} (introduced in \autocite{displayed-categories}) are a mathematical idea which provides a great tool in formalizing categories. One of the motivations behind displayed categories is the fact that mathematicians often define a category in terms of another: a monoid is a set together with a binary operation, a group is a monoid in which every element has an inverse, a topological space is a set together with a chosen collection of subsets.

Traditionally, one would say in such a case that we have a `forgetful functor' $ F : C^\prime \to C $. However, working with displayed categories has some advantages over this older approach, both conceptually and practically.

A displayed category $ D $ over a category $ C $ firstly consists of a type $ D_c $ for every $ c : C $ (corresponding to the type of objects $ F^{-1}(c) $) and a type $ d \to_f d^\prime $ for all $ d: D_c $, $ d^\prime : D_{c^\prime} $ and $ f : C(c, c^\prime) $ (corresponding to $ C^\prime((c, d), (c^\prime, d^\prime)) $). A displayed category also consists of an identity `morphism' $ d \to_{\id c} d $ for all $ d : D_c $, and compositions $ \bar f \cdot \bar g : d \to_{f \cdot g} d^{\prime \prime} $ for $ \bar f : d \to_f d^\prime $ and $ \bar g : d^\prime \to_g d^{\prime \prime} $.

When we have a displayed category $ D $ over $ C $, we can define two categories. First of all, we can form the \iindex{total category} $ \int_C D $ (which corresponds to the category $ C^\prime $ in the forgetful functor example), consisting of pairs $ (c, d) $ with $ d : D_c $. Then the forgetful functor is given by $ \pi_1 : \int_C D \to C $. Also, for every $ c : C $, we can form the \iindex{fiber category} over $ c $, which we will also denote as $ D c $. The objects here are the displayed objects over $ c $, and the morphisms are the displayed morphisms over $ \id c $. In the forgetful functor example, this is the preimage category $ F^{-1}(c) $. Lastly, note that if we have a displayed category $ D $ over $ C $, and a displayed category $ E $ over $ \int_C D $, then we can form the \iindex{sigma displayed category} $ \sum_D E $ over $ C $, where $ (\sum_D E)_c $ consists of pairs $ (d, e) $ with $ d : D_c $ and $ e : E_{(c, d)} $. Of course, the total categories are equivalent: $ \int_{\int_C D} E \cong \int_C (\sum_D E) $, which boils down to rebracketing $ ((c, d), e) $ to $ (c, (d, e)) $.

One of the reasons why displayed categories are so useful when formalizing, is the fact that for every next category, only the `new' parts have to be defined. If we define a category that consists of `functors with some additional data', we do not again have to show what the identity and composition functors are, but instead it suffices to construct the additional data for those functors. Also, displayed categories come in handy because some properties of $ \int D $ that are hard to prove directly, can be derived from properties of $ C $ and the fiber categories $ D_c $. For example, we can show that the category of groups is univalent, by noting that $ \SET $ is univalent, and by furthermore showing that the fibers of the displayed category of monoids over $ \SET $ and the fibers of the displayed category of groups over the category of monoids, are univalent.

\subsection{The categories in question}\label{subsec:formalized-categories}

Here is a diagram of the displayed structure of the categories of algebraic theories, $ \lambda $-theories, algebraic theory algebras and algebraic theory presheaves, every arrow denotes that a category is displayed over the total category of the next one.
\begin{center}
  \begin{tikzcd}
    \text{algebra} \arrow[d] & \lambda\text{-theory} \arrow[d] & \text{presheaf} \arrow[d] \\
    \text{algebra data} \arrow[d] & \lambda \text{-theory data} \arrow[d] & \text{presheaf data} \arrow[d] \\
    {\text{(algebraic theory, set)}} \arrow[r] & \text{algebraic theory} \arrow[d] & {\text{(algebraic theory, indexed set)}} \arrow[l] \\
    & \text{algebraic theory data}\arrow[d] &\\
    & \text{indexed set} &
  \end{tikzcd}
\end{center}
In the end, they all derive from the category of indexed sets over the natural numbers, which is the category with as objects all sequences $ T = (T_n)_n $ where the $ T_n $ are sets, and as morphisms from $ T $ to $ S $ all sequences of functions $ (f_n)_n $, with $ f_n : T_n \to S_n $.

Every category of interest is constructed in two stages: in the first step, the displayed objects give the structure (the algebraic theory variables and substitution, the algebra action or the presheaf action) of the objects in question, and the displayed morphisms preserve this structure. In the second step, we take the full subcategory, consisting of the objects that satisfy the right properties. For algebraic theories, these properties are the axioms about interplay between the substitution and the variables.

Note that the algebra data and presheaf data categories are displayed over a product category, which is displayed over the category of algebraic theories (see Subsection \ref{sec:displayed-product}).

The reason why we first construct the category of all algebraic theory algebras together, is because we need we need it to show that that algebras are fibered over algebraic theories (see Subsection \ref{subsec:fibrations}). In fact, we need the category of algebras as a displayed category over the category of algebraic theories. Since in the construction given above, it is displayed over the category of algebra data, we use the sigma construction twice, to bundle all the algebra information in a displayed category of one layer over algebraic theories. Then the category of $ T $-algebras can be defined as the fiber over $ T $ of this displayed category. For presheaves, it is the same story.

Even though the approach of first defining the categories of all algebras or presheaves and then taking a fiber of this, is necessary to talk about fibrations, there is a drawback to this approach. Morphisms in any fiber category are the displayed morphsims over $ \id T $. Therefore, naively composing two morphisms in our fiber gives a displayed morphism over $ \id T \cdot \id T $ and we need to transport over the equality $ \id T \cdot \id T = \id T $ to get morphisms in our fiber category again. So even though we can prove that, as expected, $ (f \cdot g)(a) = g(f(a)) $ for $ f: \Alg T(A, B) $, $ g: \Alg T(B, C) $ and $ a : A $, this is no longer a definitional equality.

\subsection{Univalence}
All of the categories in the diagram above are univalent. The proofs of this proceed by reducing to know or easy cases. For example, we know that a full subcategory of a univalent category is again univalent because it inherits isomorphisms and equalities. Also, we know that a product of univalent categories is univalent again, since its isomorphisms and equalities are equivalent to pairs of isomorphisms and equalities of its factors. We already knew that $ \SET $ is univalent, and in this project, the category of sets, indexed over a type, was constructed and shown to be univalent.

The most interesting proofs are for the `... data' categories. These proofs reduce to univalence of the underlying category (so we prove univalence layer by layer) and univalence of the fiber categories, so for example the fiber of all algebraic theory data structures on one indexed set $ (T_n)_n $. Showing that this fiber is univalent, means showing that for any two choices of substitution functions $ f_n, g_n: T_m \times T_n^m \to T_n $ and variables $ x_{i, n}, y_{i, n} : T_n $, there is an equivalence between `$ (f_n)_n = (g_n)_n $ and $ (x_{i, n})_{i, n} = (y_{i, n})_{i, n} $' and `the identity on $ T_n $ commutes with $ f_n $ and $ g_n $, and with the $ x_{i, n} $ and $ y_{i, n} $'. Since these are propositions and they imply each other, we indeed have this equivalence.

\subsection{Fibrations}\label{subsec:fibrations}

One of the places where displayed categories are conceptually better to work with than forgetful functors, is in the case of fibrations. Recall that a functor $ P: C^\prime \to C $ is a fibration if for every $ Y : C^\prime $ and $ f : C(X, P(Y)) $, there exists $ \bar X : C^\prime $ with $ P(\bar X) = X $ (and a cartesian morphism $ \bar f : C^\prime(\bar X, Y) $ with $ P(\bar f) = f $). The equality $ P(\bar X) = X $ is on objects in the category, and this violates the \textit{principle of equivalence}: `if something is true for $ A $, and $ A $ is isomorphic to $ B $, then it should also hold for $ B $'. Of course, if the category is univalent, isomorphism and equality are the same, but definitions that use equality on objects still give a bit of conceptual friction.

However, we can also define this using displayed categories. The definition becomes
\begin{definition}
  A displayed category $ D $ over $ C $ is a fibration if for every $ \bar Y : D Y $ and $ f: C(X, Y) $, we have $ \bar X : D X $ and a cartesian morphism $ \bar f : \bar X \to_f \bar Y $.
\end{definition}
This avoids using equality on objects, because we can just talk about `the objects above $ X $'. Therefore, in UniMath fibrations are defined in this way and the AlgebraicTheories package used this definition to show that the displayed category of algebraic theory algebras, over the category of algebraic theories, is a fibration. However, during a refactoring round, this proof was removed because this particular proof was too much work to adapt to the changes.

\subsection{What comes first: the category or its object?}
The formalization started with definitions for the objects and morphisms in question: algebraic theories and algebras. Using these, the categories were defined directly. However, since showing univalence is much easier when working with displayed categories, the definitions of the categories were decoupled from the definitions of the objects and morphisms, and instead were constructed as displayed categories. This meant that of every definition, a part was duplicated: once for the object (and morphism) types, and once for the objects and morphisms in the displayed categories. This meant that it was in theory possible to get a mismatch between, for example, the definition of algebraic theories and their category.

Of course, it was possible to get rid of the objects altogether, and just define things in terms of the objects and the morphisms of the categories. However, in practice this causes problems because of \textit{coercions}. For example, if $ X $ is an algebraic theory, mathematicians like to use the name $ X $ also to denote the sequence of sets $ X_n $. Under the hood, this uses a coercion, which allows one to use the same symbol to denote both the entire object, or a part of it, depending on the context. However, when working with displayed categories, the category of algebraic theories is displayed over the category of algebraic theory data, which is displayed over the category of sequences of sets. It turns out that in coq, coercions on categories do not compose very well: If $ X $ is an algebraic theory, and we have coercions from algebraic theories to algebraic theory data, and from algebraic theory data to sequences of sets, we can still only use $ X $ to denote the algebraic theory data, and not the sequence of sets.

In the end, the solution was to first define the category, and then the object and morphism types as the objects and morphisms of the category. The coercions can then be defined on the standalone object and morphism types, which works very well.

\subsection{A product of categories}\label{subsec:displayed-product}
Given two categories $ C $ and $ C^\prime $, their product $ C \times C^\prime $ can be viewed as a displayed category over $ C $ (or $ C^\prime $), where the objects over any object are the objects of $ C^\prime $, and the displayed morphisms $ g: c \to_f c^\prime $ are the morphisms $ g: C^\prime(c, c^\prime) $. There are two ways to formalize this.

The first approach uses \textit{reindexing}, by taking the unique functor to the unit category $ F : C \to \{ \star \} $, and considering $ C^\prime $ as a displayed category $ D $ over $ \{ \star \} $. Then we have the reindexed (pullback) displayed category $ F^* D $, with $ (F^* D)_c = D_{F(c)} $, with $ \int (F^* D) \cong C \times C^\prime $. The advantage of this approach is that it uses fairly simple general machinery. The disadvantage is that for the general construction of $ (F^* D) $, we need to transport over the equalities
\[ \id{F(X)} = F(\id X) \quad \text{and} \quad F(f) \cdot F(g) = F(f \cdot g) \]
in the definitions of, respectively, the displayed identity and composition. In practice, this adds friction to the formalization.

The second approach is by constructing the displayed category $ D $ directly, setting $ D_c = C^\prime $ and $ c \to_f c^\prime = C^\prime(c, c^\prime) $. This is slightly more work, because we do it in an elementary way instead of using category theoretical machinery. Even so, in practice, this approach gives cleaner definitions for the identity and composition morphisms of the total category. Therefore, halfway during the project, a switch was made from the first to the second approach.

\subsection{Limits}

\subsubsection{Limits in a fibered category}

\section{Duplication in definitions}
One of the adages in software engineering is `DRY': ``Don't Repeat Yourself'': Long expressions and blocks of code that occur multiple times throughout the program should usually be abstracted into a separate function. One of the reasons for this is that it is easier to change code in this function, than to change every instance of the repeated expression or block of code. When writing mathematics, such functions are usually called `lemmas'. However, in this project there was also another example of duplication, which occurred in statements of definitions and lemmas. For example, in the definition of the displayed category of algebraic theories, the displayed object type over a sequence of sets $ T_n $ is
\[ \left(\prod_n \prod_{i : \{ 1, \dots, n \}} T_n \right) \times \left( \prod_{m, n} T_m \times T_n^m \to T_n \right), \]
corresponding to the variables and the substitution. Then, the constructor of an algebraic theory takes arguments
\[ v : \prod_n \prod_{i : \{ 1, \dots, n \}} T_n \quad \text{and} \quad s : \prod_{m, n} T_m \times T_n^m \to T_n. \]
Also, given an algebraic theory, we have accessors:
\[ x_{n, i} : T_n \quad \text{and} \quad \bullet_{m, n} : (\prod_{m, n} T_m \times T_n^m \to T_n) \]
Lastly, when we define a new algebraic theory, we need to provide terms of these types again.

Therefore, in this project, the type of every one of these components is given a name, ending in \texttt{\_ax}, for `axiom'. For example, there are \texttt{var\_ax} and \texttt{subst\_ax} for algebraic theories, \texttt{mor\_var\_ax} and \texttt{mor\_subst\_ax} for their morphisms, \texttt{action\_ax} for algebras and \texttt{app\_ax} and \texttt{abs\_ax} for $ \lambda $-theories. The definition of the displayed categories, the constructors, the accessors and the definitions of new objects can then refer back to this.

This indeed reduces the amount of duplication in the code, and makes it slightly easier to write some definitions, because one does not have to remember and type the exact formulation of every axiom. However, there is no free lunch here: The axioms are not immediately unfolded when they occur. Therefore, if one uses the constructor for an algebraic theory, the goals become \texttt{var\_ax} and \texttt{subst\_ax}, and these have to be unfolded to see what they mean. Also, when coq is asked to state the property of an algebra morphism, it responds with \texttt{mor\_action\_ax}, which is not very informative. This is not a big problem, per se, but it adds some friction when formalizing. This friction could be reduced a lot if coq would have some sort of macros, which would immediately be unfolded upon use, and would never be printed.

Another drawback of this approach is that for algebras and presheaves, there are in fact two different axioms. This is because their categories are displayed over the categories of algebraic theories, and the category of $ T $-algebras and $ T $-presheaves are fibers of the full displayed category. Therefore, the morphisms of $ T $-algebras are given by displayed morphisms over $ \id T $, so the axiom of an algebra morphism $ g $ is
\[ \mathtt{mor\_action\_ax}: \prod_n \prod_{t : T_n} \prod_{a : A^n} g (t \bullet a) = \id T(t) \bullet (g (a_i))_i, \]
and in practice, this makes it harder to work with them. There was an instance where one conversion from $ \id T(t) $ to $ t $ added multiple seconds to the compilation time. Therefore, for the algebras and presheaves, some of these axioms have to be stated twice: once to define the displayed category, and once for most of the other occurrences.

\section{Inductive types}

\section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus}
Defining Lambda Calculus in a different way (not as an axiomatized HIT)
  - As set quotient instead of HIT
  - With a signature

\section{Tuples}

A lot of the mathematics in the paper requires us to work with `tuples': terms that bundle a certain number of terms of some type. A tuple type already occurs already as $ T_m^n $ in the definition of the substitution operation of algebraic theories:
\[ \bullet: T_m \times T_n^m \to T_n. \]
Now, there are two common ways to formalize such tuples, both with their advantages and disadvantages.

The first option is to say that the type $ A^n $ just denotes the $ n $-fold cartesian product
\[ A \times (\dots \times (A \times A) \dots). \]
There are multiple advantages to this approach. First of all, this approach allows us to easily construct `literals', like $ (5, -12) : \mathbb Z^2 $ or $ (\bot, \top, \top) : \mathrm{bool}^3 $. It is also very easy to extend an $ n $-tuple $ a $ with another element $ x $, because this just gives the pair $ (x, a) $. Because of the clear relation between the extended tuple and the original one, this approach also allows for a nice induction principle: a way to prove things about general $ a : A^n $ by proving it for $ () : A^0 $ and by showing that if it holds for any $ a : A^m $, it also holds for $ (x, a) : A^{m + 1} $ for all $ x $ (note that this is a version of \texttt{fold} for lists).

The other approach is to view $ A^n $ as the type of functions from $ \{ 1, \dots, n \} $ to $ A $. An advantage of this is that it becomes trivial to extend a function $ f $ on $ A $ to a function on its tuples, sending $ a $ to $ f \circ a $ (which would be called $ (f(a_i))_i $ in this thesis). Also, this approach makes it very easy to define $ n $-tuples of arbitrary size. For example, $ (x_i)_i : T_n $ (in one of the axioms of an algebraic theory) is just the function that sends $ i $ to the variable $ x_i $. These tuples of arbitrary size have very good computational behaviour, since the value of $ (x_i)_i $ at $ j $ is, by definition, $ x_j $.

Very early on in the project, a choice was made to use the second approach. Since many definitions require extending a mapping to a tuple, and since we don't very often need to extend tuples or do induction on a tuple, this proved to be the right choice.

The main place where we need to be able to extend tuples, is when working with $ \lambda $-theories, for example in the axioms about the relation between substitution and $ \lambda $-abstraction and -application. To accomplish this, we use the equivalence between $ \{ 1, \dots, n + 1 \} $ and $ \{ 1, \dots, n \} \sqcup \{ \star \} $.

Also, when working with a $ \Lambda $-algebra $ A $ (or an algebra) for the free monoid theory, we often want to define an operation, for example $ \circ $, on $ A $ by sending $ a $ and $ b $ to $ (x_1 \circ x_2) \bullet (a, b) $. Since constructing the literal tuple $ (a, b) $ directly as a function quickly becomes a mess, we use the equivalence between $ A \times \dots \times A $ and $ \{ 1, \dots, n \} \to A $ to define literal tuples via the cartesian product, and then transform them to functions.

Using some lemmas about the behaviour of extended tuples and literals defined this way, this slightly mixed approach works fine. However, it would be worth investigating whether it is possible to have a tuple type in the library with all of the operations of both the function and the cartesian product approaches, so that it is no longer necessary to choose between them.

\section{Products}
$ T \times (T \times \dots \times T) $ vs $ T \times T^n vs T^(S n) $
Terminal as product over empty set
over any set with a function to empty.

\section{The \texorpdfstring{$ n + p $}{n + p}-presheaf}
L (S n) (for lambda) vs L (n + 1) (stemming from the naive implementation of the L (n + p) presheaf)

\section{Quotients}
Quotients (by hrel or eqrel) vs coproducts (generalizing to arbitrary category with coproduct) vs a category with some structure

\section{The Karoubi envelope}
KanExtension instead of specific construction at KaroubiEnvelope

\section{Univalence}
Univalence bewijzen via isweqhomot vs direct

\section{The learning curve}

### 2024-09-20 report/src/algebraic-structures.tex
Expand the list of formalized files, write about limits

@@
 
-\begin{remark}
+\begin{remark}\label{rem:algebraic-theory-limits}
   We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution

### 2024-09-20 report/src/formalization.tex
Expand the list of formalized files, write about limits

@@
 
-\section{Components}
+\section{Overview of the formalized material}
+The material that was formalized can be subdivided into material that is introduced or described in Hyland's paper, and category theoretical preliminaries that are necessary to make the proofs in Hyland's paper work.
 
-\subsection{Hyland's paper}
-The formalized parts of Hyland's paper were collected in a package in the library called \textit{algebraic theories}. This package now consists of a little more than 10.000 lines of code.
+The formalized parts of Hyland's paper are collected in a package in the library called \textit{algebraic theories}. This package now consists of over 14.000 lines of code, and contains
 \begin{itemize}
-  \item Defines algebraic theories, $ \lambda $-theories, algebras and presheaves of algebraic theories, together with their morphisms and their categories.
-Shows that the categories are univalent and shows for the categories of algebraic theories, $ \lambda $-theories and presheaves that they have limits.
-  \item Examples: the terminal algebraic theory, the initial algebraic theory, the $ \lambda $-theory $ \Lambda $.
-  \item The `free object' algebraic theory with a functor from $ C $ to it's algebras.
+% AlgebraicTheoryCategory.v AlgebraicTheoryCategoryCore.v AlgebraicTheories.v AlgebraicTheoryMorphisms.v
+% LambdaTheories.v LambdaTheoryCategory.v LambdaTheoryCategoryCore.v LambdaTheoryMorphisms.v
+% AlgebraCategory.v AlgebraCategoryCore.v Algebras.v AlgebraMorphisms.v
+% PresheafCategory.v PresheafCategoryCore.v PresheafMorphisms.v Presheaves.v
+  \item Definitions for algebraic theories, $ \lambda $-theories, algebras and presheaves of algebraic theories, together with their morphisms and their categories.
+Proofs that the categories are univalent, that the categories of algebraic theories, $ \lambda $-theories and presheaves have limits and that the categories of algebras and presheaves are fibered over the category of algebraic theories.
+% FreeTheory.v LambdaCalculus.v OnePointTheory.v ProjectionsTheory.v TheoryAlgebra.v
+  \item The terminal algebraic theory, the free algebraic theory on a set, with as a special case the initial algebraic theory, the $ \lambda $-theory $ \Lambda $, the $ T $-presheaf structure on $ T $ and the $ T $-algebra structure on $ T_n $.
+% FreeMonoidTheory.v FreeObjectTheory.v
+  \item The `free object' algebraic theory with a functor from $ C $ to its algebras.
 Also the equivalence between the `free monoid' algebraic theory $ T $, together with a proof that the functor from monoids to $ T $-algebras is an equivalence.
-  \item The construction of the endomorphism theory of an object $ X $ in a category $ C $.
-  \item Exponential objects in the category of presheaves.
+% EndomorphismTheory.v
+  \item The construction of the endomorphism theory $ E(X) $ for some object $ X : C $ in a category $ C $ with finite products.
+% Combinators.v CategoryOfRetracts.v OriginalRepresentationTheorem.v
   \item The original version of Scott's representation theorem.
-  \item Hyland's version of Scott's representation theorem.
-  \item The construction of a Lawvere theory from an algebraic theory, and the equivalence between
+% Plus1Presheaf.v RepresentationTheorem.v
+  \item Hyland's version of Scott's representation theorem, including the construction of the presheaf $ A(P, 1) $ and the proof that it is the exponential object $ P^T $.
+% AlgebraToTheory.v
+  \item The construction of a $ \lambda $-theory from a $ \Lambda $-algebra $ A $ as the endomorphism theory $ E_{\RAct{A_1}}(U_A) $ (Definition \ref{def:lambda-algebra-to-lambda-theory}).
+% AlgebraicTheoryToLawvereTheory.v
+  \item The construction of a Lawvere theory $ L $ from an algebraic theory $ T $, and the equivalence between the presheaf category $ PL $ and the presheaf category $ \Pshf T $.
+% ExtensionsTheory.v LambdaCalculus.v
+  \item The theory of extensions $ T_A $ of a $ T $-algebra.
+  \item An axiomatic definition of the pure $ \lambda $-calculus (see Section \ref{sec:axiomatic-lambda-calculus}).
 \end{itemize}
 
-\subsection{Category theoretic preliminaries}
-Since Hyland's paper uses a lot of general category theory, formalizing it meant adding a lot of missing category theory to the library. Among these are:
+Since Hyland's paper uses a lot of general category theory, formalizing it entailed adding the preliminaries that had not yet been formalized to the library. Among these are:
 \begin{itemize}
@@
   \item The Sigma displayed category creates limits.
-  \item Two definitions for the Karoubi envelope and their preliminaries.
+  \item The definitions $ \overline C $ and $ \hat C $ for the Karoubi envelope and their preliminaries.
   \item The contents of Section \ref{sec:monoid-category}: The construction of a one-object category from a monoid, the equivalence between it's presheaves and sets with a right monoid action, properties of the category of sets with a monoid action and restriction and extension of scalars.
@@
   \item The uniqueness of the Rezk completion.
+% FundamentalTheorem/SurjectivePrecomposition.v
   \item A precomposition functor is equivalent if ...
+% FiniteSetSkeleton.v
+  \item The skeleton category $ F $ of finite sets, with
+  \[ F_0 = \{ 0, 1, \dots \} \quad \text{and} \quad F(m, n) = \SET(\{ 1, \dots, n \}, \{ 1, \dots, m \}). \]
+% IndexedSetCategory.v
+  \item The univalent category $ \SET^A $ of indexed sets $ (X_a)_a $ over a type $ A $, which can be defined formally as
+  \[ \SET^A_0 = (A \to \SET) \quad \text{and} \quad \SET^A(X, Y) = \prod_a X_a \to Y_a. \]
 \end{itemize}
@@
 \end{center}
-In the end, they all derive from the category of indexed sets over the natural numbers, which is the category with as objects all sequences $ T = (T_n)_n $ where the $ T_n $ are sets, and as morphisms from $ T $ to $ S $ all sequences of functions $ (f_n)_n $, with $ f_n : T_n \to S_n $.
+In the end, they all derive from the category of indexed sets over the natural numbers (or equivalently, the category of sequences of sets).
 
-Every category of interest is constructed in two stages: in the first step, the displayed objects give the structure (the algebraic theory variables and substitution, the algebra action or the presheaf action) of the objects in question, and the displayed morphisms preserve this structure.
+Note that every `relevant' category is constructed in two stages: in the first step, in a category called `\dots data', the displayed objects give the structure (the algebraic theory variables and substitution, the algebra action or the presheaf action) of the objects in question, and the displayed morphisms preserve this structure.
 In the second step, we take the full subcategory, consisting of the objects that satisfy the right properties.
@@
 
-Note that the algebra data and presheaf data categories are displayed over a product category, which is displayed over the category of algebraic theories (see Subsection \ref{sec:displayed-product}).
+Note that the algebra data and presheaf data categories are displayed over a product category, which is displayed over the category of algebraic theories (see Subsection \ref{subsec:displayed-product}).
 
@@
 All of the categories in the diagram above are univalent.
-The proofs of this proceed by reducing to know or easy cases.
+The proofs of this proceed by reducing to known or easy cases.
 For example, we know that a full subcategory of a univalent category is again univalent because it inherits isomorphisms and equalities.
@@
 
-The most interesting proofs are for the `...
-data' categories.
+The most interesting proofs are for the `\dots data' categories.
 These proofs reduce to univalence of the underlying category (so we prove univalence layer by layer) and univalence of the fiber categories, so for example the fiber of all algebraic theory data structures on one indexed set $ (T_n)_n $.
 Showing that this fiber is univalent, means showing that for any two choices of substitution functions $ f_n, g_n: T_m \times T_n^m \to T_n $ and variables $ x_{i, n}, y_{i, n} : T_n $, there is an equivalence between `$ (f_n)_n = (g_n)_n $ and $ (x_{i, n})_{i, n} = (y_{i, n})_{i, n} $' and `the identity on $ T_n $ commutes with $ f_n $ and $ g_n $, and with the $ x_{i, n} $ and $ y_{i, n} $'.
-Since these are propositions and they imply each other, we indeed have this equivalence.
+Since these are mere propositions and they imply each other, we indeed have this equivalence.
 
@@
 
-However, we can also define this using displayed categories. The definition becomes
+However, we can also define this in the language of displayed categories. The definition becomes
 \begin{definition}
@@
 This avoids using equality on objects, because we can just talk about `the objects above $ X $'.
-Therefore, in UniMath fibrations are defined in this way and the AlgebraicTheories package used this definition to show that the displayed category of algebraic theory algebras, over the category of algebraic theories, is a fibration.
-However, during a refactoring round, this proof was removed because this particular proof was too much work to adapt to the changes.
+Therefore, in UniMath fibrations are defined in this way and the algebraic theories package uses this definition to show that the displayed categories of algebraic theory algebras and presheaves, over the category of algebraic theories, are fibrations.
+
+\subsection{Limits}
+In this subsection, we will mainly treat binary products, as they are somewhat simpler to understand than limits in general.
+However, it is not too hard to generalize the material presented here to limits in general, and the formalized proofs treat limits in general, instead of binary products.
+
+Recall from Remark \ref{rem:algebraic-theory-limits} that algebraic theories have all limits, and that given a diagram, the underlying set of the limit is the limit of the underlying sets.
+Compare this to group or ring theory: for rings $ R $ and $ S $, the set $ R \times S $ can again be given a ring structure, which is the binary product of $ R $ and $ S $ in the category of rings.
+
+This is all very reminiscent of the way that displayed categories `borrow' information from their base category.
+Now if a category $ C $ has binary products, we say that a displayed category $ D $ over $ C $ \textit{creates binary products}, if for all $ \bar X : D_X $, $ \bar Y : D_Y $, we can `lift' their product.
+That is, if we can find
+\[ \overline{X \times Y} : D_{X \times Y}, \quad \bar{\pi_1} : \overline{X \times Y} \to_{\pi_1} \bar X \quad \text{and} \quad \bar{\pi_2} : \overline{X \times Y} \to_{\pi_2} \bar Y \]
+and if $ (X \times Y, \overline{X \times Y}) $ with the projections $ (\pi_1, \bar{\pi_1}) $ and $ (\pi_2, \bar{\pi_2}) $ is the product of $ (X, \bar X) $ and $ (Y, \bar Y) $ in $ \int_C D $.
+By definition, if $ D $ creates binary products, then $ \int_C D $ has binary products.
+
+In itself, this is not a very revolutionary idea.
+However, when formalizing, this allows us to work layer by layer, every time adding a little bit of new information, and reusing the rest from the layer below to show that every category that we construct has binary products.
+Also, in the rest of this section we will see that very often, it suffices to formalize a lot less than the full construction of a binary product, and that when we do constructions on displayed categories, like the sigma displayed category or taking a fiber category, we often immediately deduce that the resulting (displayed) category still has (or creates) binary products.
+
+During this project, a small lemma was added to the library, showing that for a full subcategory $ \int_C D \subseteq C $, where $ D_c $ is a mere proposition for all $ c : C $, if for all $ (X, \bar X), (Y, \bar Y) : \int D $, we have $ D_{X \times Y} $ (the $ C $-product of two objects in $ \int D $ is again in $ \int D $), then $ D $ creates binary products.
+Also, a lemma was added that shows that if a displayed category $ D $ over $ C $, and a displayed category $ E $ over $ D $, both create binary products, then $ \sigma_D E $ also creates binary products.
+
+Note that for many categories, the displayed morphisms are mere propositions.
+In particular, this holds for the `\dots data' categories of this project.
+For example, an algebra morphism is a function that `respects the operation', and respecting the operation is a mere proposition.
+In these categories, it is not necessary to give a full proof that the object $ (X \times Y, \overline{X \times Y}) $ and the morphisms $ (\pi_i, \overline{\pi_i}) $ form a binary product, because it suffices to show that for all $ C, \bar C, f, g $ and all $ \bar f : \bar C \to_f \bar A $ and $ \bar g : \bar C \to_g \bar B $, we can lift the product morphism to
+\[ \overline{\langle f, g \rangle} : \bar C \to_{\langle f, g \rangle} \overline{A \times B} \]
+For example, if the function $ f $ commutes with the algebra actions on $ \bar C $ and $ \bar A $, and $ g $ commutes with the actions on $ \bar C $ and $ \bar B $, then we need to show that the product morphism $ \langle f, g \rangle $ commutes with the actions on $ \bar C $ and $ \overline{A \times B} $.
+A lemma showing that it suffices to show that we can lift the product morphism was added to the library, and used to show that the `\dots data' displayed categories create binary products.
+
+Now, recall that the categories of $ T $-algebras and $ T $-presheaves are a fiber of a displayed category.
+Now, if we want a binary product of $ X, Y : \Alg T $ and we take the product of $ (T, X) $ and $ (T, Y) $ in the category of all algebras, we end up with $ (T \times T, X \times Y) $, or $ X \times Y : \Alg {T \times T} $, even though we would like to have $ (T, X) $ for some $ X : \Alg T $.
+It turns out that here we need the fact that algebras and presheaves are fibered over algebraic theories, and adding the following lemma to the library gave the final brick for showing show that all categories discussed here have limits:
+\begin{lemma}
+  For a displayed category $ D $ over a category $ C $, suppose that $ C $ has binary products, that $ D $ creates binary products, and that $ D $ is a fibration.
+Then the fiber categories $ D_X $ have binary products.
+\end{lemma}
+\begin{proof}
+  Take $ \bar X_1, \bar X_2 : D_X $.
+We have a product $ \bar X_1 \times \bar X_2 : D_{X \times X} $ with projections $ \bar \pi_i : \bar X_1 \times \bar X_2 \to_{\pi_i} \bar X_i $.
+For the diagonal morphism on $ X $, the fibration gives an object $ \bar Y $ and a a cartesian lift:
+  \[ \bar f : \bar Y \to_{\langle \id X, \id X \rangle} \bar X_1 \times \bar X_2, \]
+  so we have projections
+  \[ \bar p_i = \bar f \cdot \bar \pi_i : \bar Y \to_{\id X} \bar X_i. \]
+  In the diagram below, the first row is the fiber $ D_X $ and the second row is the fiber $ D_{X \times X} $.
+  \begin{center}
+    \begin{tikzcd}
+      \bar X_i & \bar Y \arrow[d, "\bar f" description] \arrow[l, "\bar p_i"] & \bar Z \arrow[ll, "\bar g_i"', bend right] \arrow[l, "\bar h"] \arrow[ld, "{\langle \bar g_1, \bar g_2 \rangle}"] \\
+      & \bar X_1 \times \bar X_2 \arrow[lu, "\bar \pi_i"] &
+    \end{tikzcd}
+  \end{center}
+  Now, given some $ \bar g_1: \bar Z \to_{g_1} \bar X_1 $ and $ \bar g_2: \bar Z \to_{g_2} \bar X_2 $, we have
+  \[ \langle \bar g_1, \bar g_2 \rangle : \bar Z \to_{\langle g_1, g_2 \rangle} \bar X_1 \times \bar X_2. \]
+  Because $ \bar f $ is cartesian, we have a unique
+  \[ \bar h: \bar Z \to_{\id X} \bar Y, \]
+  such that
+  \[ \bar h \cdot \bar f = \langle \bar g_1, \bar g_2 \rangle. \]
+  Therefore,
+  \[ \bar h \cdot \bar p_i = \bar h \cdot \bar f \cdot \bar \pi_i = \langle \bar g_1, \bar g_2 \rangle \cdot \bar \pi_i = \bar g_i, \]
+  which shows that $ \bar Y $ is the product of $ \bar X_1 $ and $ \bar X_2 $ in $ D_X $.
+\end{proof}
 
@@
 Therefore, halfway during the project, a switch was made from the first to the second approach.
-
-\subsection{Limits}
-
-\subsubsection{Limits in a fibered category}
 
@@
 
-\section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus}
+\section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus} \label{sec:axiomatic-lambda-calculus}
 Defining Lambda Calculus in a different way (not as an axiomatized HIT)
@@
 
-\section{Univalence}
-Univalence bewijzen via isweqhomot vs direct
+\section{Constructing equivalences}
+Via isweqhomot or directly
 

### 2024-09-20 report/src/paper.tex
Expand the list of formalized files, write about limits

@@
 
-\begin{definition}[Construction of the $ \lambda $-theory]
+\begin{definition}[Construction of the $ \lambda $-theory]\label{def:lambda-algebra-to-lambda-theory}
   Recall that $ A_2 \subseteq U_A $, and that we have a retraction $ a \mapsto \mathbf 1_2 \circ a : U_A \to A_2 $.

### 2024-09-23 report/src/formalization.tex
Write about the +p presheaf

@@
-% 996 0
-% 447 37
-% 1383 1017
-% 26 26
-% 6313 889
-% 2562 2332
-% 1255 326
-% 3015 1
-% 4206 1668
-% 940 48
-% 9 5
-% 508 4
-% 1701 1267
-% Total: 23361 7620
-
-% 434 292
-% 1144 58
-% 96 0
-% 469 113
-% 145 42
-% 495 90
-% 508 221
-% Total: 3291 816
-
+% 996 0; 447 37; 1383 1017; 26 26; 6313 889; 2562 2332; 1255 326; 3015 1; 4206 1668; 940 48; 9 5; 508 4; 1701 1267; Total: 23361 7620
+% 434 292; 1144 58; 96 0; 469 113; 145 42; 495 90; 508 221; Total: 3291 816
 \chapter{The formalization}
@@
 
-\section{Statistics}
-
+\section{Some numbers}
 The code for this project was written over the course of about 18 months, spread over \href{https://github.com/UniMath/UniMath/pulls?q=is%3Apr+author%3Aarnoudvanderleer+is%3Aclosed}{20 pull requests}: 13 with content about Hyland's paper, adding 23.361 and removing 7.620 lines of code, and 7 with only some missing category theoretical preliminaries, adding 3.291 and removing 816 lines.
@@
 % FundamentalTheorem/SurjectivePrecomposition.v
-  \item A precomposition functor is equivalent if ...
+  \item If $ F : C \to C^\prime $ is a fully faithful functor, and $ D $ is a category with colimits, then the precomposition functor $ F \bullet - : [C^\prime, D] \to [C, D] $ is split essentially surjective.
+  A precomposition functor is equivalent if ...
+  \item A proof of a generalized version of Lemma \ref{lem:equivalent-presheaf-cats}, showing that if $ F : C \to C^\prime $ is a functor, if $ F^\prime : C^\prime \to C^{\prime \prime} $ is a fully faithful functor, if $ D $ is a category with colimits and if the precomposition $ (F \bullet F^\prime) \bullet - : [C^{\prime \prime}, D] \to [C, D] $ is an adjoint equivalence, then $ F^\prime \bullet - $ and $ F^\prime \bullet - $ are adjoint equivalences too.
 % FiniteSetSkeleton.v
@@
 
-In general, the formalization is the cleanest and the easiest when we use equality for elements of homotopy sets (morphisms, for example), isomorphisms for objects in a category and adjoint equivalences for categories themselves.
+In general, the formalization is the cleanest and the easiest when we use equality for elements of homotopy sets (morphisms, or terms in an algebraic theory, for example), isomorphisms for objects in a category and adjoint equivalences for categories themselves.
 
@@
 This is slightly more work, because we do it in an elementary way instead of using category theoretical machinery.
-Even so, in practice, this approach gives cleaner definitions for the identity and composition morphisms of the total category.
+In return, this approach gives cleaner definitions in practice for the identity and composition morphisms of the total category.
 Therefore, halfway during the project, a switch was made from the first to the second approach.
@@
 
-\section{Inductive types}
-
 \section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus} \label{sec:axiomatic-lambda-calculus}
@@
   - With a signature
+
+\subsection{\texorpdfstring{$ \beta $}{beta}-reduction in proofs}
 
@@
 \section{Products}
-$ T \times (T \times \dots \times T) $ vs $ T \times T^n vs T^(S n) $
-Terminal as product over empty set
-over any set with a function to empty.
+A very similar problem pops up in the proof of the representation theorem, where the definition of the endomorphism theory $ E_{\Pshf L}(L) $ meets the isomorphism $ \Pshf L(L^n, L) \cong L_n $ of the Yoneda lemma for presheaves.
+First of all, recall that the function $ \lambda_n $ of $ E(L) $ is defined via the following chain of morphisms
+\[ \Pshf L(L^{n + 1}, L) = \Pshf(L^n \times L, L) \cong \Pshf L(L^n, L^L) \xrightarrow{- \cdot \text{abs}} \Pshf L(L^n, L). \]
+To make this easy, we would like to have $ L^{n + 1} = L^n \times L $, and this would give a definition $ L^n = ( \dots (I \times L) \times \dots) \times L $ where $ I $ is the terminal object.
+
+On the other hand, recall that inverse morphism of $ \Pshf L(L^n, L) \cong L_n $ sends $ s: L_n $ to the presheaf morphism that sends $ (t_i)_i : L^n_m $ to $ s \bullet t : L_m $.
+Here, we would like the sets of $ L^n $ to match the tuple types in the definition of the substitution $ \bullet : L_n \times L_m^n \to L_m $.
+However, these two are incompatible, since elements of the repeated product are nested pairs, whereas the tuples in $ L_m^n $ are functions from $ \{ 1, \dots, n \} $ to $ L_m $.
+
+In this case, somewhat of a compromise was made.
+The endomorphism theory was indeed defined using a repeated binary product, and the construction of finite powers from the terminal object and binary products\footnote{Unfortunately, defininig the product of a tuple of objects was much harder than defining the finite power of one object.
+When generalizing the approach to tuples of objects, some terms suddenly do not have the `correct' type, which has something to do with some equalities like $ ((x_1, \dots, x_n) + (y))_{n + 1} = y $ that do not hold definitionally.
+Even though this specific problem can be solved using transports, the rest of the proof becomes then much harder because the transports get in the way}.
+On the other hand, the Yoneda lemma for $ L $-presheaves does indeed use the `usual' notion of products $ L^n $ where the sets are tuple types.
+Luckily, the library contains a proof that two products are isomorphic, so where the definitions clash, we use the isomorphisms to translate between them.
+Even though this adds friction, in the end it is pretty straightforward.
+
+Also, this project added a lemma to the library stating that in any category $ C $, $ \prod_{i : \emptyset} X_i $ (for $ X : \emptyset \to T $ a family of objects) is given by the terminal object.
+However, the repeated binary product construction needed $ \prod_{i : \{ i \mid 1 \leq i \leq 0 \}} X_i $, and $ \emptyset $ is not definitionally equal to $ \{ i \mid 1 \leq i \leq 0 \} $.
+Initially, this was solved by transporting along the equality $ \emptyset = \{ i \mid 1 \leq i \leq 0 \} $.
+However, much further down the line, some proof involved an element of this product over $ \{ i \mid 1 \leq i \leq 0 \} $, and because of the transport, coq was not able to see that this product was just $ \{ \star \} $.
+Therefore, the statement of the lemma about the empty product was changed to ``For a type $ I $ and a family $ X : I \to C $, if we have a function $ f : I \to \emptyset $, the terminal object gives the product $ \prod_{i : I} X_i $''.
+Note that having the function $ f $ is equivalent to $ I $ being equivalent (and therefore equal) to the empty type.
+This change in the statement did provide the right amount of generality to make computation down the line much smoother.
 
 \section{The \texorpdfstring{$ n + p $}{n + p}-presheaf}
-L (S n) (for lambda) vs L (n + 1) (stemming from the naive implementation of the L (n + p) presheaf)
+Now, the definition of the endomorphism $ \lambda $-theory $ E_{\Pshf L}(L) $ requires that the theory presheaf $ L $ is exponentiable.
+As shown before, $ P^L $ is given by $ A(P, 1) $, the `plus 1' presheaf, where the last variable is ignored in the $ L $-action.
+In fact, one can show that $ P^{L^n} $ is given by $ A(P, n) $ and this was the level of generality at which the statement was formalized.
+To obtain the action
+\[ \bullet : A(P, p)_m \times L_n^m \to A(P, p)_n, \]
+the equivalence
+\[ \{ 1, \dots, n + p \} \simeq \{ 1, \dots, n \} \sqcup \{ 1, \dots, p \} \]
+was used, which indeed sends the first $ n $ elements to the first set, and the last $ p $ elements to the second.
+After this, it was time to construct the presheaf morphisms for $ \rho $ and $ \lambda $ between $ L $ and $ A(L, 1) $, but this turned out to be much harder than expected, because $ A(L, 1)_n = L_{n + 1} $, whereas $ \rho $ and $ \lambda $ are functions between $ L_n $ and $ L_{S n} $, where $ S n = 1 + n $.
+Unfortunately, $ 1 + n $ is not definitionally equal to $ n + 1 $, and even though we might transport along a proof $ h: 1 + n = n + 1 $, this will give problems down the road.
+
+In this case, the cleanest solution was to only do the construction for the special case $ p = 1 $, and formulate it like $ A(P, 1)_n = P_{S n} $. This can use the equivalence
+\[ s_m: \{ 1, \dots, n + 1 \} \simeq \{ 1, \dots, n \} \sqcup \{ \star \}, \]
+with
+\[ s_m(i) = \left\{ \begin{array}{cc}
+    i & i < m\\
+    \star & i = m\\
+    i - 1 & i > m
+\end{array}\right. .  \]
 

### 2024-09-24 report/src/formalization.tex
Write about quotients

@@
 \subsection{\texorpdfstring{$ \beta $}{beta}-reduction in proofs}
+Tactic
 
@@
 \[ \{ 1, \dots, n + p \} \simeq \{ 1, \dots, n \} \sqcup \{ 1, \dots, p \} \]
-was used, which indeed sends the first $ n $ elements to the first set, and the last $ p $ elements to the second.
+from the library was used, which sends the first $ n $ elements to the first set, and the last $ p $ elements to the second, so this could indeed be used to construct elements of tuples $ A^{n + p} $, separating them into first a tuple of $ n $ and then a tuple of $ p $.
 After this, it was time to construct the presheaf morphisms for $ \rho $ and $ \lambda $ between $ L $ and $ A(L, 1) $, but this turned out to be much harder than expected, because $ A(L, 1)_n = L_{n + 1} $, whereas $ \rho $ and $ \lambda $ are functions between $ L_n $ and $ L_{S n} $, where $ S n = 1 + n $.
@@
 
-In this case, the cleanest solution was to only do the construction for the special case $ p = 1 $, and formulate it like $ A(P, 1)_n = P_{S n} $. This can use the equivalence
+In this case, the cleanest solution was to only do the construction for the special case $ p = 1 $ and take $ A(P, 1)_n = P_{S n} $, using the equivalence from the library
 \[ s_m: \{ 1, \dots, n + 1 \} \simeq \{ 1, \dots, n \} \sqcup \{ \star \}, \]
@@
     i - 1 & i > m
-\end{array}\right. .  \]
+\end{array}\right. ,  \]
+taking $ m = n $ in this case.
+
+It is possible that constructing a new equivalence
+\[ \{ 1, \dots, p + n \} \simeq \{1, \dots, n\} \sqcup \{1, \dots, p\}, \]
+makes it possible to generalize the result to general $ p $ again.
+However, this equivalence would be somewhat weird, because the order of $ n $ and $ p $ are reversed.
+Also, proving things about these standard finite sets is quite hard, and outside the scope of this project, so this was not attempted in this project, but potentially left for future work.
 
 \section{Quotients}
-Quotients (by hrel or eqrel) vs coproducts (generalizing to arbitrary category with coproduct) vs a category with some structure
+This project used quotients twice, once explicitly and once implicitly.
+The first occurrence of quotients was the construction of the `extension of scalars' functor $ f_*: \RAct N \to \RAct M $ from Lemma \ref{lem:scalar-extension}.
+Here, the formalization worked directly with quotients over a relation.
+However, the relation given by $ R : (x n, m) \sim (x, f(n) \cdot m) $ for all $ a $, is reflexive and transitive, but not necessarily symmetric.
+Therefore, first the `equivalence closure' $ \bar R $ of $ R $ is taken: the smallest transitive and symmetric relation that contains $ R $.
+This is then used for the quotient.
+To construct functions from this, like, the right action of the monoid $ M^\prime $, we use the universal property of the quotient: a function from $ X \times M^\prime $ that sends `related' elements $ (x_1, m_1) $ and $ (x_2, m_2) $ to the same element.
+However, the quotient is taken over $ \bar R $ instead of $ R $, so it is no longer possible to assume that $ x_2 = x_1 n $ and $ m_1 = f(n) \cdot m_2 $ for some $ n $.
+In the case of the right $ M^\prime $-action, it sufficed to add the following lemma to the library
+\begin{lemma}
+  For a relation $ S $ on a set $ A $ and a relation $ T $ on a set $ B $, if for $ f: A \to B $, we have that $ S(a_1, a_2) $ implies $ T(f(a_1), f(a_2)) $ for all $ a_1, a_2 : A $, then $ \bar S(a_1, a_2) $ implies $ \bar T(f(a_1), f(a_2)) $ for all $ a_1, a_2 $.
+\end{lemma}
+However, overall, working with these quotients in an elementary way was quite a hassle.
 
-\section{The Karoubi envelope}
-KanExtension instead of specific construction at KaroubiEnvelope
+The second occurrence of quotients was in the proof of Corollary \ref{cor:karoubi-presheaf}, or the lemma that it is based on.
+Initially, the statement of the lemma was only about $ \SET $, stating that $ \iota_C \bullet - : [\bar C, \SET] \to [C, \SET] $ was an adjoint equivalence.
+The proof used coequalizers of functors, like in Lemma \ref{lem:karoubi-equivalence}.
+Note that coequalizers of set-valued functions are given pointwise by coequalizers in $ \SET $, which are formalized using quotients.
+Because of this, when simplifying, coq usually reduced the goal to elementary statements about quotients, which somewhat obfuscated the relatively simple nature of the construction.
+Luckily, the construction could be made agnostic to the specific implementation of coequalizers, by introducing a variable
+\[ \mathtt{H : Coequalizers HSET} \]
+and using this instead of our known implementation.
+Since the proofs did not use any elements of the sets in question, it was then trivial to generalize to any category with coequalizers.
+It turned out that the construction was a special version of left Kan extension, which uses general colimits, and using the existing definition of Kan extension, the proof was made considerably shorter.
+
+In hindsight, it may have been better to replace the quotient $ Y := X \times M / \sim $ by a coequalizer
+\begin{center}
+  \begin{tikzcd}[sep = huge]
+    N \times X \times M \arrow[r, shift left, "{(n, x, m) \mapsto (x n, m)}"] \arrow[r, shift right, "{(n, x, m) \mapsto (x, f(n) \cdot m)}"'] & X \times M \arrow[r, dashed] & Y
+  \end{tikzcd},
+\end{center}
+which is closer to the way this relation is defined.
+Under the hood, this still takes a quotient over the equivalence closure, but now it is less visible.
+Here, the universal property of the coequalizer can be used to define functions out of $ Y $, which may be easier to work with than the universal property of the quotient.
+
+The generalization from $ \SET $ to an arbitrary category with coequalizers, which we saw in the case of Karoubi envelopes, can also be done here, but it would take considerably more effort.
+The problem is that the definitions of monoids and sets with a monoid action really do use the elements of their underlying sets.
+For example, a monoid $ M $ has a unit $ u $ and multiplication $ \cdot $, such that $ u \cdot m = m = m \cdot u $ and $ m \cdot (n \cdot l) = (m \cdot n) \cdot l $ for all $ m, n, l : M $.
+The generalization for an object $ M $ in some category $ C $, turns the unit into a function $ u : I \to M $ from the terminal object and the multiplication into a function $ \mu : M \times M $ from the binary product\footnote{Note that one does not need the full power of binary products to define internal monoids.
+A category with a product-like structure $ \otimes $ and a terminal-like object $ I $ that one needs to define internal monoids, is called a \index{category!monoidal}\textit{monoidal category}.}, such that the following diagrams commute:
+\begin{center}
+  \begin{tikzcd}
+    M \times (M \times M) \arrow[rr, "{\sim}"] \arrow[d, "{\id M \times \mu}"'] & & (M \times M) \times M \arrow[d, "{\mu \times \id M}"]\\
+    M \times M \arrow[rd, "{\mu}"'] & & M \times M \arrow[ld, "{\mu}"]\\
+    & M
+  \end{tikzcd}
+  \begin{tikzcd}
+    I \times M \arrow[r, "u \times \id M"] \arrow[rd, "\sim"'] & M \times M \arrow[d, "\mu"] & M \times I \arrow[l, "\id M \times u"'] \arrow[ld, "\sim"]\\
+    & M
+  \end{tikzcd}
+\end{center}
+Such a generalization of a monoid to a general category is called an \index{monoid!internal}\textit{internal monoid}.
+In a similar way, sets with a monoid action can be generalized.
+However, this all would be a lot of work, and elementary reasoning about internal monoids of $ \SET $ is still much more cumbersome than for the ordinary set-based monoids.
+Also, for the fundamental theorem we only need the ordinary set-based monoids.
+Therefore, this generalization was not pursued any further.
 

### 2024-09-24 report/src/formalization.tex
Write about the lambda calculus

@@
 
-\subsection{What comes first: the category or its object?}
+\subsection{Chicken or egg?}
 The formalization started with definitions for the objects and morphisms in question: algebraic theories and algebras.
@@
 Therefore, for the algebras and presheaves, some of these axioms have to be stated twice: once to define the displayed category, and once for most of the other occurrences.
-
-\section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus} \label{sec:axiomatic-lambda-calculus}
-Defining Lambda Calculus in a different way (not as an axiomatized HIT)
-  - As set quotient instead of HIT
-  - With a signature
-
-\subsection{\texorpdfstring{$ \beta $}{beta}-reduction in proofs}
-Tactic
 
@@
 
-\section{Quotients}
+\section{Quotients}\label{sec:quotients}
 This project used quotients twice, once explicitly and once implicitly.
@@
 For example, a monoid $ M $ has a unit $ u $ and multiplication $ \cdot $, such that $ u \cdot m = m = m \cdot u $ and $ m \cdot (n \cdot l) = (m \cdot n) \cdot l $ for all $ m, n, l : M $.
-The generalization for an object $ M $ in some category $ C $, turns the unit into a function $ u : I \to M $ from the terminal object and the multiplication into a function $ \mu : M \times M $ from the binary product\footnote{Note that one does not need the full power of binary products to define internal monoids.
-A category with a product-like structure $ \otimes $ and a terminal-like object $ I $ that one needs to define internal monoids, is called a \index{category!monoidal}\textit{monoidal category}.}, such that the following diagrams commute:
+The generalization for an object $ M $ in some category $ C $, turns the unit into a function $ u : I \to M $ from the terminal object and the multiplication into a function $ \mu : M \times M $ from the binary product
+\footnote{Note that one does not need the full power of binary products or terminal objects to define internal monoids.
+A category with the product-like structure $ \otimes $ and terminal-like object $ I $ that one needs to define internal monoids, is called a \index{category!monoidal}\textit{monoidal category}.},
+such that the following diagrams commute:
 \begin{center}
@@
 
-\section{Constructing equivalences}
-Via isweqhomot or directly
+\section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus} \label{sec:axiomatic-lambda-calculus}
+One of the important classes of objects in this thesis is the class of $ \Lambda $-algebras: algebras for the initial $ \lambda $-theory $ \Lambda $, corresponding to the `pure' $ \lambda $-calculus.
+Therefore, much of this project required the pure $ \lambda $-calculus to be formalized.
+Now, in this thesis, it is defined as a quotient of an inductive type.
+However, in the UniMath library, the use of inductive types (other than a handful of basic ones like \texttt{empty}, \texttt{bool}, \texttt{nat} and \texttt{coprod}) is prohibited
+\footnote{This is because allowing inductive types requires a much larger trusted codebase of the proof assistant, and because most of mathematics can be formalized with $ \sum $-types or using initial algebras of functors, instead of inductive and record types.}.
+Also, as we saw in section \ref{sec:quotients}, working with quotients can be somewhat complicated.
+
+The inductive type approach has a variation, which instead of a quotient uses a higher inductive type to force the required elements to be equal.
+Unfortunately, even if the use of inductive types was allowed, coq does not support higher inductive types.
+
+Instead, a different, more axiomatic approach was taken.
+A class in group theory often starts with laying out a couple of axioms, like: ``We have a set $ G $, with a binary operation $ b $, a unary operation $ u $ and an element $ e $.
+$ b $ is associative, $ u $ is a left and right inverse for $ b $ and $ e $ is a unit for $ b $.'' Afterwards, this structure is usually bundled into the declaration ``Let $ G $ be a group.'' In the same spirit, every section in the formalization that needs the pure $ \lambda $-calculus, starts with ``Let $ L $ be the pure $ \lambda $-calculus with $ \beta $-equality.'' To this end, there is a definition \texttt{lambda\_calculus}, consisting of
+\begin{itemize}
+  \item A sequence of sets $ (L_n)_n $;
+  \item Variables, app, abs, subst:
+    \[ \mathtt{var}_{n, i} : L_n, \quad \mathtt{app}_n: L_n \times L_n \to L_n, \quad \mathtt{abs}_n : L_{S n} \to L_n \quad \text{and} \quad \mathtt{subst}_{m, n}: L_m \times L_n^m \to L_n; \]
+  \item A couple of identities about the interactions between the constructors. In particular, $ \beta $-equality:
+    \[
+      \mathtt{subst}(\mathtt{var}_i, t) = t_i, \quad
+      \dots, \quad
+      \mathtt{app}(\mathtt{abs}(s), t) = \mathtt{subst}(s, (\mathtt{var}_i)_i + (t));
+    \]
+  \item The induction principle, which coincides with the induction principle that a higher inductive type would have: Given, for all $ t : L_n $, a type $ A_{n, t} $, it is possible to construct, for every $ t : L_n $, an element $ f(t) : A_{n, t} $ by just giving elements and functions, corresponding to the constructors
+    \begin{align*}
+      f_{\mathtt{var}(n, i)} &:A_{\mathtt{var}_{n, i}}\\
+      f_{\mathtt{app}(s, t)} &:A_s \times A_t \to A_{\mathtt{app}(s, t)}\\
+      f_{\mathtt{abs}(t)} &:A_t \to A_{\mathtt{abs}(t)}\\
+      f_{\mathtt{subst}(s, t)} &:A_s \times A_{t_1} \times \dots \times A_{t_n} \to A_{\mathtt{subst}(s, t)}\\
+    \end{align*}
+    and by showing that they are compatible with the identities on $ L $. For example, for $ \beta $-equality, this is equality between
+    \[ f_{\mathtt{app}}(f_{\mathtt{abs}}(s), t): A_{\mathtt{app}(\mathtt{abs}(s), t)} \quad \text{and} \quad f_{\mathtt{subst}}(s, f_{\mathtt{var}_1}, \dots, f_{\mathtt{var}_n}, t): A_{\mathtt{subst}(s, (\mathtt{var}_i)_i + (t))}.
+\]
+    Note that the left and right hand side live in different types, so the equality can only be stated using a transport over $ \beta $-equality.
+  \item A couple of identities about the interaction between induction and the constructors: if $ f $ is defined using the induction principle as above,
+  \begin{align*}
+    f(\mathtt{var}_i) &= f_{\mathtt{var}_i}\\
+    f(\mathtt{app}(s, t)) &= f_{\mathtt{app}(s, t)}(f(s), f(t))\\
+    f(\mathtt{abs}(t)) &= f_{\mathtt{abs}(t)}(f(t))\\
+    f(\mathtt{subst}(s, t)) &= f_{\mathtt{subst}(s, t)}(f(s), (f(t_i))_i).
+  \end{align*}
+\end{itemize}
+
+\begin{remark}
+  Note that the first three bullets just give $ L $ a $ \lambda $-theory structure. Only by the induction principle, it becomes clear that $ L $ is the (unique) pure $ \lambda $-calculus.
+\end{remark}
+
+\begin{remark}
+  The induction principle has two common uses: $ A_{n, t} $ can be taken to be a constant type $ A $ (or potentially $ A_n $), in which case induction results in functions $ L_n \to A $.
+The $ A_{n, t} $ can also be taken to be mere propositions, in which case induction `proves' something about all $ t : L_n $.
+
+  In both cases, the rules about respecting the identities like $ \beta $-equality become simpler: in the first case, the transports disappear, and in the second case, the rules are satisfied automatically.
+\end{remark}
+
+\begin{remark}
+  Often, the pure $ \lambda $-calculus is defined using just the constructors $ \mathtt{var} $, $ \mathtt{app} $ and $ \mathtt{abs} $.
+$ \mathtt{subst} $ is usually defined using induction, which gives the identities about the interaction between $ \mathtt{subst} $ and the others for free.
+However, since this is a definition of the $ \lambda $-calculus with $ \beta $-equality, the induction principle must include a rule about compatibility with the $ \beta $-equality.
+Since the definition of $ \beta $-equality already uses $ \mathtt{subst} $, it is not possible to define $ \mathtt{subst} $ using induction.
+This is why it is added as an additional constructor, along with requirements about its interaction with the other constructors.
+This approach is called \iindex{explicit substitution}.
+\end{remark}
+
+\subsection{Propagation of substitution}
+Once the pure $ \lambda $-calculus is defined, it is not very hard to give it a $ \lambda $-theory structure, using the induction principle a couple of times to show that some identities are satisfied.
+
+Now, as mentioned in Subsection \ref{subsec:lambda-calculus-operations}, any $ \lambda $-theory allows the operations $ \mathtt{var} $, $ \mathtt{app} $, $ \mathtt{abs} $ and $ \mathtt{subst} $ with the same interaction as for the pure $ \lambda $-calculus.
+Therefore, given any $ \lambda $-calculus, it is possible to start defining more complicated structures like the $ a \circ b $, $ \langle a, b \rangle $ and $ A \times B $ from Section \ref{sec:retracts-category}, which is indeed done in the original proof of Scott's representation theorem.
+However the equalities about the interaction between $ \mathtt{subst} $ and the other operations are not definitional, even for the pure $ \lambda $-calculus.
+Consider the following term (using concatenation for application):
+\[ \lambda x_5, x_5 (x_1 x_2 (x_4 x_3)) \bullet (x_1, x_2, x_3, x_1) : L_3. \]
+It is not hard to see that this results in $ \lambda x_4, x_4 (x_1 x_2 (x_1 x_3)) $.
+However, it takes a lot of steps to rewrite this: moving the substitution past the $ \lambda $-abstraction, then into 4 instances of application, and lastly using 5 instances of the interaction between variables and substitution, resulting in a total of 10 rewrites for a seemingly trivial term.
+It is not unheard of to have 40 of these rewrites consecutively in a proof, and since there is a lot of things to prove, this quickly becomes tedious.
+
+Therefore, a tactic was added to the project. A first version of this tactic was a variation of
+\begin{lstlisting}
+Ltac reduce_lambda := (
+  rewrite subst_var +
+  rewrite subst_l_var +
+  ...
+  rewrite beta_equality
+).
+\end{lstlisting}
+attempting to rewrite (once) with at least one, but possible multiple of the equalities.
+The statement \texttt{repeat reduce\_lambda} sometimes took a couple of seconds, but this saved a lot of manual work.
+Still, there was much room for improvement.
+
+Therefore, along with the original proof of Scott's representation theorem, a new version of the tactic, called \texttt{propagate\_subst} has been added.
+It recursively traverses the $ \lambda $-term in the left-hand side of the goal, checking whether the term matches a form that can be rewritten into something else.
+It performs the possible rewrites, and also prints these rewrite statements which can replace it.
+For example, if the goal is
+\begin{lstlisting}
+(λ'm, (inflate a (inflate b var (stnweq (inr tt))))) • c =
+(λ'n, (inflate (a • c) (inflate (b • c) var (stnweq (inr tt)))))
+\end{lstlisting}
+a call to \texttt{repeat reduce\_lambda} would take about a second, but a call to \texttt{propagate\_subst ()} runs in about $ \frac 1 3 $ of a second and prints
+\begin{lstlisting}
+refine '(subst_abs _ _ _ @ _).
+refine '(_ @ !maponpaths (λ x, (abs (app x _))) (inflate_subst _ _ _)).
+refine '(_ @ !maponpaths (λ x, (abs (app _ (app x _)))) (inflate_subst _ _ _)).
+refine '(maponpaths (λ x, (abs x)) (subst_app _ _ _ _) @ _).
+refine '(maponpaths (λ x, (abs (app x _))) (subst_inflate _ _ _) @ _).
+refine '(maponpaths (λ x, (abs (app _ x))) (subst_app _ _ _ _) @ _).
+refine '(maponpaths (λ x, (abs (app _ (app x _)))) (subst_inflate _ _ _) @ _).
+refine '(maponpaths (λ x, (abs (app _ (app _ x)))) (var_subst _ _ _) @ _).
+refine '(maponpaths (λ x, (abs (app _ (app _ x)))) (extend_tuple_inr _ _ _) @ _).
+\end{lstlisting}
+Replacing the call to \texttt{propagate\_subst} by these statements, results in the same rewrites, but these only take $ \frac{1}{25} $ of a second.
+
+Now, on top of the speedup, the new tactic is modular and extensible.
+It is modular, in the sense that some of its parts are also tactics themselves, and can be used for other tactics as well.
+For example, the \texttt{traverse} tactic, which traverses a $ \lambda $-term in the goal and executes something for every subterm, is also used in a new tactic that is called \texttt{generate\_refine}, which takes a pattern, and for every subterm that matches it, prints a
+\begin{lstlisting}
+refine '(maponpaths (λ x, ... x ...) _ @ _).
+\end{lstlisting}
+statement, which can be used to quickly generate statements that very precisely rewrite one subterm.
+The \texttt{propagate\_subst} tactic is also extensible, in the sense that the patterns for both the subterm traversal and the rewrites are kept in a list, which can be extended when new combinators are defined.
+For example, at the point where the tactics are defined, the traversal only works for the constructors $ \mathtt{var} $, $ \mathtt{app} $, $ \mathtt{abs} $ and $ \mathtt{subst} $, and the rewrites only work for the interactions between these operations.
+Using this, composition $ a \circ b $ is defined, and so a pattern to branch into $ a $ and $ b $ is added to the traversals, and a rewrite with
+\[ (a \circ b) \bullet t = (a \bullet t) \circ (b \bullet t) \]
+is added.
+Progressing through the file, the same is done for combinators like the pair $ (a, b) $, the projection $ \pi_1 $ (including a rewrite $ \pi_1 \langle a, b \rangle = a $), $ \mathtt{curry} $ and $ \mathtt{n\_tuple} $ (consisting of nested pairs).
+
+It would be interesting to see whether parts of these tactics can be generalized.
+For example, whether it is possible to create an extensible tactic which shows that some type is a homotopy set, or a mere proposition, and prints the coq statements that can replace the tactic call.
+Or whether it would be possible to generalize \texttt{generate\_refine} to very qukickly generate very fast and precise rewrite statements for large and complicated goals.
 
 \section{The learning curve}
+% \section{The direct approach}
+% Via isweqhomot or directly

### 2024-09-25 report/src/700-formalization.tex
Reorganize repository

--- 2024-09-24 report/src/formalization.tex
@@
 \section{The learning curve}
-% \section{The direct approach}
-% Via isweqhomot or directly
+Let me conclude this chapter with a more personal note about formalization.
+In the past fifteen years, I have worked with a plethora of different programming languages, and I would like to think that in all this time, I have learned a great deal about programming.
+When I start working with a new language, it takes me a couple of minutes to figure things out, and within an hour, I can probably get a small program up and running, with some help from google.
+However, when I started working with coq and UniMath, I kind of had to start from scratch again.
+As it turns out, the naive or direct approach is often not the right one when working with a proof assistant, and of the code that I wrote in the first months, almost nothing remains.
+Even though every programming language has some sort of learning curve, formalizing in a proof assistant is especially unforgiving: You often have to change an old definition, or start over when you are halfway through a proof, because your current approach gets bogged down further and further with, for example, unintelligible transports.
+For every line of code that ends up in a pull request, many lines are written and erased again.
+
+For example, if we want to show that two types $ X $ and $ Y $ are equivalent, we need to construct an equivalence, which has the following type:
+\[ X \simeq Y := \{ f : X \to Y \mid \forall y, \mathtt{is\_contractible}(\{ x \mid f(x) = y \}) \}. \]
+One can view this as having an `isomorphism'
+\[ f: X \to Y, \quad g : Y \to X, \quad h_1(x): g(f(x)) = x \quad \text{and} \quad h_2(y) : f(g(y)) = y, \]
+but then together with a proof $ h_3 $, showing that applying $ f $ to $ h_1(x) $ is the same as taking $ h_2(f(x)) $.
+This last part is to ensure that `$ f $ is a weak equivalence' is a mere proposition, even if $ X $ and $ Y $ are not sets: if $ X $ and $ Y $ are not sets, there can be multiple paths $ h_1 $ and $ h_2 $, so $ f $ can be an isomorphism `in multiple ways'.
+It can be tempting to just close our eyes and start constructing this equivalence part by part.
+When we then get to defining $ h_3 $, however, it is easy to get stuck, because reasoning about paths is complicated.
+Luckily, there is a surjection
+\[ \mathtt{isweq\_iso} : \mathtt{is\_iso}(f) \twoheadrightarrow \mathtt{isweq}(f), \]
+which allows us to construct an isomorphism and then get an equivalence (with $ h_3 $) for free.
+
+Another example: When we want to define a category, usually we start by defining what the objects and morphisms in the category look like, and then constructing a category from that.
+Since we work in univalent foundations here, we want to show that the category is univalent, so that $ \mathrm{idtoiso}: (a = b) \to (a \cong b) $ is an equivalence.
+However, if we try to show this directly, the proof quickly accumulates piles of transports, that are very hard to resolve.
+Instead, there are two common `indirect' approaches:
+\begin{itemize}
+  \item Either we first construct multiple smaller equivalences, ignoring $ \mathrm{idtoiso} $ for the time being:
+    \begin{align*}
+      (a = b) &\simeq \{ \text{componentwise equalities between $ a $ and $ b $} \}\\
+      &\simeq \{ \text{componentwise isomorphisms between $ a $ and $ b $} \}\\
+      &\simeq (a \cong b),
+    \end{align*}
+    and then use a proof that if we have an equivalence $ f: X \simeq Y $, and we have some $ g : X \to Y $ with $ f(x) = g(x) $ for all $ x : X $, we know that $ g $ is an equivalence as well.
+  \item We transform the category into a stack of displayed categories, derive definitions for our objects from this displayed category, and then do the easy proofs that the fibers of every layer are univalent.
+\end{itemize}
+Both of these approaches are not what we would think of in the first place, but they are the approaches that turn out to work very well.
+In short, there is a very steep learning curve for working with a proof assistant and it takes a lot of experience to formalize mathematics.
+Not only to know what kind of tactics are available, but also to get a feeling for the theorems, lemmas and constructions that work well for proving or constructing something.

### 2024-09-25 500-previous-work.tex
Re-focus the repository on the report

--- 2024-06-07 report/src/previous-work.tex
@@
 \begin{definition}
-  We define the category \index{R}$ \R $ as the Karoubi envelope of the monoid of the $ \lambda $-terms without free variables under composition. That is, the category of idempotent functions:
+  We define the category \index{R}$ \R $ as the Karoubi envelope $ \overline C_{L_0} $ of the one-point category based on the monoid of the $ \lambda $-terms without free variables under composition.
+In this case, we choose to interpret the Karoubi envelope as the very syntactical construction using idempotents, because Scott reasons about them in this way:
   \[ \R_0 = \{ A : L_0 \mid A \circ A = A \} \quad \text{and} \quad \R(A, B) = \{ f: L_0 \mid B \circ f \circ A = f \}, \]
@@
 \begin{remark}
-  Hyland instead defines $ \R $ as
+  Hyland instead defines $ \R $ as the Karoubi envelope $ \overline C_{L_1} $ (again, the construction using the idempotents) of the monoid $ (L_1, - \bullet (-)) $ with identity element $ x_{1, 1} $:
   \[ \R_0 = \{ A : L_1 \mid A \bullet A = A \} \quad \text{and} \quad \R(A, B) = \{ f : L_1 \mid B \bullet f \bullet A = f \}, \]
-  writing $ s \bullet t $ instead of $ s \bullet (t) $ for $ s, t : L_1 $. Note that the following diagram commutes:
+  writing $ s \bullet t $ instead of $ s \bullet (t) $ for $ s, t : L_1 $. Note that we have a monoid morphism:
   \begin{center}
@@
   \end{center}
-  Now, since for $ A : \R $, $ A = \lambda x_1, \iota_{0, 1}(A) (\iota_{0, 1}(A) x_1) $, we have $ \lambda x_1, \iota_{0, 1}(A) x_1 = A $.
+  and since for $ A : \R $, $ A = \lambda x_1, \iota_{0, 1}(A) (\iota_{0, 1}(A) x_1) $, we have $ \lambda x_1, \iota_{0, 1}(A) x_1 = A $.
 This shows that $ s \mapsto \lambda x_1, s $ and $ t \mapsto \iota_{0, 1}(t) x_1 $ (both on objects and morphisms) constitute an equivalence between Hyland's category of retracts and Scott's category of retracts.
@@
 In his dissertation, Paul Taylor shows that $ \R $ is not only cartesian closed, but also \iindex{relatively cartesian closed}.
+Recall we have chosen to interpret $ \R $ as the category $ \overline C_{L_0} $, constructed using idempotents, because both Scott's and Taylor's proof are very syntactical in nature.
 
@@
 \end{remark}
+
+\section{The \texorpdfstring{$ \lambda $}{lambda}-calculus is algebraic}
+As we mentioned in Remark \ref{rem:lambda-theory-or-algebra}, using tools from universal algebra, there are two approaches to study $ \lambda $-calculus-like structures.
+One can either study $ \lambda $-theories or algebras for the algebraic theory $ \Lambda $.
+We will see that Hyland shows that these are equivalent.
+
+In his proof, he refers to the 2002 paper `The lambda calculus is algebraic' by Peter Selinger (\autocite{selinger-lambda-calculus-algebraic}).
+We will not study this paper in detail, but it is interesting to have a quick look at it, because it seems that Hyland took some inspiration from it.
+
+Selinger studies two kinds of objects which he calls $ \lambda $-algebras and $ \lambda $-theories:
+\begin{definition}
+  A \textit{combinatory algebra} is a set $ A $, together with a binary (application) operation $ (a_1, a_2) \mapsto a_1 a_2 $, and distinguished elements $ k, s : A $ such that for all $ a_1, a_2, a_3 : A $,
+  \[ k a_1 a_2 = a_1 \quad \text{and} \quad s a_1 a_2 a_3 = a_1 a_3 (a_2 a_3). \]
+  A \textit{$ \lambda $-algebra} is a combinatory algebra which `behaves nicely' in some sense\footnote{We can interpret terms of combinatory algebra (abstract terms involving just application, the constants $ S $ and $ K $, constants from $ A $ and some variables) as functions on $ A $.
+We can also interpret them as $ \lambda $-terms with constants in $ A $, by sending $ S $ and $ K $ to the $ S $ and $ K $ combinators.
+Then `behaving nicely' means that if the $ \lambda $-terms of two such terms are equal, then their functions on $ A $ are equal as well.}.
+\end{definition}
+
+For a set $ C $ and a countable set $ V $, we define $ \Lambda_C $ to be the inductive type with constructors
+\[ \mathtt{Var}(x), \quad \mathtt{App}(f, g), \quad \mathtt{Abs}(x, f) \quad \text{and} \quad \mathtt{Con}(c) \]
+for $ x : V $, $ f, g : \Lambda_C $ and $ c : C $.
+\begin{definition}
+  A \textit{$ \lambda $-theory} is an equivalence relation `$ = $' on $ \Lambda_C $ for some $ C $, containing $ \alpha $- and $ \beta $-equality and closed under application and abstraction.
+\end{definition}
+
+Selinger shows in his paper that the categories of $ \lambda $-algebras and $ \lambda $-theories are equivalent.
+As we will see in the next chapter, Hyland shows that his own notions of $ \Lambda $-algebras and $ \lambda $-theories are equivalent.
+
+Now, it is not hard to show that Hyland's and Selinger's notions of $ \lambda $-theory are equivalent: If we have one of Selinger's $ \lambda $-theories with a countable set of variables, enumerate the variables as $ x_1, x_2, \dots $ and let $ L_n $ be the set of terms with only the free variables $ x_1, \dots, x_n $.
+Then, if we quotient by the equivalence relation, we get one of Hyland's $ \lambda $-theories.
+Conversely, if we start with one of Hyland's $ \lambda $-theories $ L $, we can consider $ L_n $ as a subset of $ L_{n + 1} $ by sending $ x_{n, i} $ to $ x_{n + 1, i} $.
+If we take the union $ \bar L = \bigcup_n L_n $ (officially, this is a directed limit), we have a function $ f: \Lambda_{\bar L} \to \bar L $, because the constants of $ \Lambda_{\bar L} $ are exactly the terms of $ \bar L $ and because $ \lambda $-theories in Hyland's sense support the operations of the $ \lambda $-calculus (see subsection \ref{subsec:lambda-calculus-operations}).
+This gives an equivalence relation on $ \Lambda_{\bar L} $ by taking $ a\ `='\ b $ if $ f(a) = f(b) $.
+
+Note, however, that is very hard to show that Hyland's notion of $ \Lambda $-algebra and Selinger's notion of $ \lambda $-algebra are equivalent.
+If we start with a $ \Lambda $-algebra $ A $, this is already a combinatory algebra, because $ \Lambda $ contains the $ S $ and $ K $ combinators and their image are the designated elements $ s $ and $ k $.
+However, if we start with a $ \lambda $-algebra and want to turn this into a $ \Lambda $-algebra, we need to give a $ t $-action for every $ t : \Lambda $, not just for $ S $ and $ K $.
+Therefore, we need to show that any $ \Lambda $-term can be expressed in terms of $ K $, $ S $ and application.
+However, at that point we are already halfway through a proof that any $ \Lambda $-algebra can be given a $ \lambda $-theory structure.

### 2024-09-25 300-univalent-foundations.tex
Add a reference about independence of the univalence axiom

--- 2024-09-11 report/src/univalent-foundations.tex
@@
 Now, even for a basic category, like the category of types, it seems impossible to prove that the univalence principle holds.
-However, this is no surprise: it turns out that it is independent of the axioms of Martin-Löf type theory (\TODO \textbf{Is this true?
-I need a reference for this, but could not find one}).
-That is: it cannot be proven, but assuming it as an axiom does not yield contradictions.
+However, this is no surprise: It turns out that there is a model in set theory for Martin-Löf type theory with univalence (\autocite{simplicial-set-model}), but also for Martin-Löf type theory with proof irrelevance (\autocite{proof-irrelevant-model}).
+In the latter, the type $ x = y $ has at most one element for all $ x, y : T $ and all types $ T $, which contradicts univalence.
+Therefore, univalence is independent of the axioms of Martin-Löf type theory: both univalence or its negation cannot be proved, but either can be assumed as an axiom.
 

### 2024-09-25 500-previous-work.tex
Add a reference about independence of the univalence axiom

@@
 Since Lambek showed an equivalence between simply typed $ \lambda $-calculi and cartesian closed categories, and since we have a construction for an untyped $ \lambda $-calculus from a cartesian closed category with a reflexive object, we can wonder whether this construction constitutes contitutes an equivalence between untyped $ \lambda $-calculi and some class of categories.
-This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \autocite{curry}, page 418).
+This question finds a partial answer in the following theorem, originally proved in a very syntactical way by Dana Scott (see \autocite{curry}, page 418).
 \begin{theorem}\label{thm:Scott}

### 2024-09-25 100-introduction.tex
Write an introduction

\chapter{Introduction}

The $ \lambda $-calculus is an abstract tool that is used in an area where mathematics meets computer science, to study algorithms, programming languages and even category theory. It was conceived by Alonzo Church, primarily as a foundation for mathematics instead of set theory or type theory (\autocite{church-lambda-calculus}). A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such a function could not exist (\autocite{church-number-theory}). A year later, Alan Turing showed, using previous work of Kleene (\autocite{kleene-lambda}), that a function is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine (\autocite{turing-lambda}), solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.

Later, all kinds of different flavours and extensions of the $ \lambda $-calculus were put forth, with colorful names like `simply typed $ \lambda $-calculus', `System T' and `PCF'. Even though the $ \lambda $-calculus was originally a very abstract tool, it was also the inspiration for function programming languages, and traces of it can be seen in imperative programming languages, where unnamed functions are commonly called `lambda functions' and are sometimes even written like \texttt{lambda x y : (x - y) * (x + y)}.

Even so, the theoretical study of the $ \lambda $-calculus and its extensions continues to this day. For example, in 2013, a paper by Martin Hyland was published, named `classical lambda calculus in modern dress' (\autocite{Hyland}). In this paper, Hyland approaches the $ \lambda $-calculus from the viewpoint of universal algebra, using algebraic theories, and more generally category theory, to study it. This way, he obtains two new proofs for old theorems. The paper also contains a theorem that shows that two different ways to study the $ \lambda $-calculus using universal algebra are equivalent.

In this thesis, we study the paper through the lens of univalent foundations, a foundation of mathematics based on type theory set forth by Vladimir Voevodsky. We work out the details of the proofs from the paper, see where subtleties arise when converting from set theory to univalent foundations and discuss the formalization of part of the material. Of particular interest is the discussion of Hyland's proof of the locally cartesian closedness of a category of retracts (or Karoubi envelope) in Section \ref{sec:locally-cartesian-closed}, which was proved earlier by Paul Taylor in a different way. It turns out that in the translation from set theory to univalent foundations, the definition of the category of retracts `branches' into two nonequivalent definitions, and that Taylor's proof is about one definition, whereas Hyland's proof is about the other.

% 600-paper.tex
Now, most of this thesis works towards Chapter \ref{ch:the-paper}, about Hyland's paper.
% 500-previous-work.tex
He builds upon work of other authors, though, and understanding their work, exposited in Chapter \ref{ch:previous-work}, helps to understand Hyland's paper.
% 200-category-theory.tex
Since both Hyland and the other authors use a lot of category theory, Chapter \ref{ch:category-theory} establishes most of the preliminary knowledge regarding category theory. It is probably wise to skim this chapter, and sporadically come back to it to better understand the material in the other chapters.
% 300-univalent-foundations.tex
Because this thesis works from a univalent standpoint, Chapter \ref{ch:univalent-foundations} introduces univalent foundations and builds the preliminary knowledge in that area for the rest of the paper.
% 400-algebraic-structures.tex
Then Chapter \ref{ch:algebraic-structures} introduces the main objects that are studied by Hyland, namely $ \lambda $-theories and $ \Lambda $-algebras, together with related notions and examples.
% 700-formalization.tex
Lastly, the formalization of part of the material is discussed in Chapter \ref{ch:the-formalization}.

### 2024-09-25 700-formalization.tex
Write an introduction

--- 2024-09-25 report/src/700-formalization.tex
@@
 % 434 292; 1144 58; 96 0; 469 113; 145 42; 495 90; 508 221; Total: 3291 816
-\chapter{The formalization}
+\chapter{The formalization}\label{ch:the-formalization}
 In addition to the reading, investigating and writing mathematics that lead up to the previous chapters, this thesis project also had a formalization component.

### 2024-09-26 100-introduction.tex
Write a conclusion

@@
 It was conceived by Alonzo Church, primarily as a foundation for mathematics instead of set theory or type theory (\autocite{church-lambda-calculus}).
-A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such a function could not exist (\autocite{church-number-theory}).
-A year later, Alan Turing showed, using previous work of Kleene (\autocite{kleene-lambda}), that a function is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine (\autocite{turing-lambda}), solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.
+A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such an algorithm could not exist (\autocite{church-number-theory}).
+A year later, Alan Turing showed, using previous work of Kleene (\autocite{kleene-lambda}), that an algorithm is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine (\autocite{turing-lambda}), solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.
 

### 2024-09-26 800-conclusion.tex
Write a conclusion

\chapter{Conclusion}
In this thesis, we have seen how Dana Scott showed in an elementary way that any $ \lambda $-theory arises as the endomorphism theory of a reflexive object in its category of retracts. We saw Martin Hyland's proof that any $ \lambda $-theory arises as the endomorphism theory in the presheaf category of its Lawvere theory, using the Yoneda lemma in a very elegant way.

We also saw how Paul Taylor shows that Scott's category of retracts is cartesian closed, relative to some class of display maps, and that Hyland gives an interesting new proof of this, using the pre-established fact that the presheaf is locally cartesian closed. Here it was interesting to note that Taylor's and Hyland's proofs are about the same category in classical mathematics, but that these categories become nonequivalent in univalent foundations, one being the Rezk completion of the other.

As we saw, there are two ways to study the $ \lambda $-calculus using tools from universal algebra: both via $ \lambda $-theories and $ \Lambda $-algebras. We saw that Hyland gives an equivalence between these two in his Fundamental Theorem of the $ \lambda $-calculus, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, and sending a $ \Lambda $-algebra $ A $ to its theory of extensions $ \Lambda_A $. We also showed a couple of variations on the proof of this fundamental theorem, exhibiting multiple equivalent ways to construct a $ \lambda $-theory from a $ \Lambda $-algebra.

Lastly, we saw how part of the material in this thesis was formalized, and evaluated the choices that were made in the formalization. Unfortunately, due to the very time-consuming nature of formalization, not all of the material could be formalized. In future work, it would be interesting to see which version of Hyland's fundamental theorem would lend itself best to formalization. Personally, I would guess it is the most elementary one, exhibited in Section \ref{sec:elementary-fundamental-theorem}.

Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \bar C $ and $ \hat C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \bar C $, can be made to work on its Rezk completion $ \hat C $.

### 2024-09-26 100-introduction.tex
Clean up symbol names, add a link to the UniMath repository

@@
 Lastly, the formalization of part of the material is discussed in Chapter \ref{ch:the-formalization}.
+
+Note that throughout this document, links are included to \href{https://arnoudvanderleer.github.io/cs-masters-thesis/toc.html}{documentation} of the corresponding formalized material, formalized either by me or by someone else.
+It refers to the state of \href{https://github.com/UniMath/UniMath/tree/5eb5c8958c4dddd4219f895bf7bc51547395522d}{the UniMath repository} at commit number \texttt{5eb5c8958c4dddd4219f895bf7bc51547395522d}.

### 2024-09-26 200-category-theory.tex
Clean up symbol names, add a link to the UniMath repository

--- 2024-09-10 report/src/category-theory.tex
@@
 \section{Notation}
-For an object $ c $ in a category $ C $, I will write $ c: C $.
-
-For a morphism $ f $ between objects $ c $ and $ c^\prime $ in a category $ C $, I will write $ f: C(c, c^\prime) $ or $ f: c \to c^\prime $.
-
-For composition of morphisms $ f: C(c, d) $ and $ g: C(d, e) $, I will write $ f \cdot g $.
-
-For composition of functors $ F: A \to B $ and $ G: B \to C $, I will write $ F \bullet G $.
+Throughout this thesis, an object $ X $ in a category $ C $ will be denoted by $ X : C $.
+A morphism $ f $ between objects $ X $ and $ Y $ in a category $ C $ will be denoted by $ f: C(X, Y) $ or sometimes $ f: X \to Y $.
+Composition of morphisms $ f: C(X, Y) $ and $ g: C(Y, Z) $ will be denoted by $ f \cdot g $.
+And composition of functors $ F: A \to B $ and $ G: B \to C $ will be denoted by $ F \bullet G $.
 
@@
 \begin{definition}
-  A \iindex{universal arrow} from an object $ c: C $ to a functor $ F: D \to C $ consists of an object $ d: D $ and a morphism $ f: D(c, F(d)) $ such that for every similar pair $ (d^\prime, f^\prime) $, $ f^\prime $ factors uniquely as $ f \cdot F(g) $ for some $ g: C(d, d^\prime) $:
-  \begin{center}
-    \begin{tikzcd}
-      c \arrow[d, "f"'] \arrow[rd, "f^\prime"] &\\
-      F(d) \arrow[r, "F(g)"', dashed] & F(d^\prime)
+  A \iindex{universal arrow} from an object $ X: D $ to a functor $ F: C \to D $ consists of an object $ Y: C $ and a morphism $ f: D(X, F(Y)) $ such that for every similar pair $ (Y^\prime, f^\prime) $, $ f^\prime $ factors uniquely as $ f \cdot F(g) $ for some $ g: C(Y, Y^\prime) $:
+  \begin{center}
+    \begin{tikzcd}
+      X \arrow[d, "f"'] \arrow[rd, "f^\prime"] &\\
+      F(Y) \arrow[r, "F(g)"', dashed] & F(Y^\prime)
     \end{tikzcd}
@@
 \begin{lemma}
-  Let $ F: C \to D $ be a functor and $ d: D $ an object. An object $ c: C $ and an arrow $ f: D(d, F(c)) $ form a universal arrow from $ d $ to $ F $ if and only if the function
-  \[ (g \mapsto f \cdot F(g)) : C(c, x) \cong D(d, F(x)) \]
+  Let $ F: C \to D $ be a functor and $ X: D $ an object. An object $ Y: C $ and an arrow $ f: D(X, F(Y)) $ form a universal arrow from $ X $ to $ F $ if and only if the function
+  \[ (g \mapsto f \cdot F(g)) : C(Y, x) \cong D(X, F(x)) \]
   is a bijection.
 
-  Conversely, for all $ c: C $ and $ d: D $, every bijection
-  \[ C(c, x) \cong D(d, F(x)) \]
-  that is natural in $ x $ arises in this way from some universal arrow $ f: D(d, F(c)) $.
+  Conversely, for all $ Y: C $ and $ X: D $, every bijection
+  \[ C(Y, Z) \cong D(X, F(Z)) \]
+  that is natural in $ Z $ arises in this way from some universal arrow $ f: D(X, F(Y)) $.
 \end{lemma}
@@
 
-There is also the dual concept of a universal arrow $ (d, f) $ from a functor $ F $ to an object $ c: C $. Its universal property can be summarized in the following diagram:
-\begin{center}
-  \begin{tikzcd}
-    F(d^\prime)\arrow[rd, "f^\prime"']  \arrow[r, "F(g)", dashed] & F(d) \arrow[d, "f"]\\
-    & c
+There is also the dual concept of a universal arrow $ (X, f) $ from a functor $ F $ to an object $ Y: C $. Its universal property can be summarized in the following diagram:
+\begin{center}
+  \begin{tikzcd}
+    F(X^\prime)\arrow[rd, "f^\prime"']  \arrow[r, "F(g)", dashed] & F(X) \arrow[d, "f"]\\
+    & Y
   \end{tikzcd}
@@
 An alternative characterization (see \autocite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
-\[ \varphi: D(L(c), d) \xrightarrow{\sim} C(c, R(d)). \]
-Naturality means that for all $ f: C(c^\prime, c) $, $ g: D(d, d^\prime) $ and $ h: D(L(c), d) $,
+\[ \varphi: D(L(X), Y) \xrightarrow{\sim} C(X, R(Y)). \]
+Naturality means that for all $ f: C(X^\prime, X) $, $ g: D(Y, Y^\prime) $ and $ h: D(L(X), Y) $,
 \[ \varphi(L(f) \cdot h \cdot g) = f \cdot \varphi(h) \cdot R(g). \]
 
-Lastly, one can construct an adjunction using universal arrows. This lends itself particularly well for a formalization, where it is often preferable to have as little `demonstranda' as possible:
-\begin{lemma}
-  One can construct an adjunction $ (L, R, \eta, \epsilon) $ as above from only the functor $ L: C \to D $ and, for each $ c: C $, a universal arrow $ (R(c), \epsilon_c) $ from $ L $ to $ c $.
+Lastly, one can construct an adjunction using universal arrows. This lends itself particularly well for a formalization, where it is often preferable to have as few `demonstranda' as possible:
+\begin{lemma}
+  One can construct an adjunction $ (L, R, \eta, \epsilon) $ as above from only the functor $ L: C \to D $ and, for each $ X: C $, a universal arrow $ (R(X), \epsilon_X) $ from $ L $ to $ X $.
 \end{lemma}
@@
 \subsection{Exponential objects}
-Note that in the category of sets, for all $ X, Y: \SET $, we have a set $ (X \to Y) $. Also, for all $ X, Y, Z $, there is a (natural) bijection
+Note that in the category of sets, for all $ X, Y: \SET $, we have a set of functions $ (X \to Y) $. Also, for all $ X, Y, Z $, there is a (natural) bijection
 \[ (X \times Y \to Z) \cong (X \to (Y \to Z)) \]
@@
 \begin{definition}
-  A category $ C $ has \textit{exponential objects}\index{exponential objects} (or \textit{exponentials}) if for all $ c: C $, the functor $ c^\prime \mapsto c^\prime \times c $ has a right adjoint, which we denote $ d \mapsto d^c $.
-\end{definition}
-
-\begin{remark}
-  It is actually very well possible that a category does not have all exponentials, but it has some objects $ c, d, d^c: C $ with a natural bijection
-  \[ C(d^\prime \times c, d) \cong C(d^\prime, d^c). \]
-  Then $ d^c $ is still called an exponential object.
+  A category $ C $ has \textit{exponential objects}\index{exponential objects} (or \textit{exponentials}) if for all $ X: C $, the functor $ X^\prime \mapsto X^\prime \times X $ has a right adjoint, which we denote $ Y \mapsto Y^X $.
+\end{definition}
+
+\begin{remark}
+  It is actually very well possible that a category does not have all exponentials, but it has some objects $ X, Y, Y^X: C $ with a bijection
+  \[ C(X^\prime \times X, Y) \cong C(X^\prime, Y^X) \]
+  that is natural in $ X^\prime $. Then $ Y^X $ is still called an exponential object.
 \end{remark}
@@
 This ring is then called `the free commutative ring on $ S $'.
-If $ S $ is finite of size $ n $, the ring is also called `the free commutative ring on $ n $ generators'.
+If $ S $ has $ n $ elements, the ring is also called `the free commutative ring on $ n $ generators'.
 
@@
 
-However, sometimes, we have a forgetful functor $ F: C \to D $, but we cannot give a free functor on the entire category $ D $. In such a case, we might still talk about free `objects':
-\begin{definition}
-  Let $ F: C \to D $ be a forgetful functor. Given $ d: D $, the \textit{free object}\index{free!object} on $ d $ is a universal arrow $ (c, f) $ from $ d $ to $ F $.
-\end{definition}
-
-\begin{remark}
-  By \autocite{MacLane}, Chapter IV.1, Theorem 2 (ii), if we have a free object on every $ d: D $, we can piece these together to get a free functor associated to $ F $.
+However, as with exponential object, sometimes we have a forgetful functor $ F: C \to D $, but we cannot give a free functor on the entire category $ D $.
+In such a case, we might still talk about free `objects':
+\begin{definition}
+  Let $ F: C \to D $ be a forgetful functor. Given $ X: D $, the \textit{free object}\index{free!object} on $ X $ is a universal arrow $ (Y, f) $ from $ X $ to $ F $.
+\end{definition}
+
+\begin{remark}
+  By \autocite{MacLane}, Chapter IV.1, Theorem 2 (ii), if we have a free object on every $ X: D $, we can piece these together to get a free functor associated to $ F $.
 \end{remark}
@@
 \begin{definition}\label{def:Yoneda-embedding}
-  The \iindex{Yoneda embedding} $ \yo : C \hookrightarrow P C $ is given on objects by $ \yo(c) = C(-, c) $:
-  \[ \yo(c)(d) = C(d, c) \quad \text{and} \quad \yo(c)(f)(g) = f \cdot g \]
-  for $ d: C $, $ f: C(d, d^\prime) $ and $ g: C(d^\prime, c) $. It sends a morphism $ f: C(c, c^\prime) $ to the natural transformation $ \yo(f): C(-, c) \Rightarrow C(-, c^\prime) $ given by
-  \[ \yo(f)(d)(g) = g \cdot f \]
-  for $ d: C $ and $ g: C(d, c) $.
+  The \iindex{Yoneda embedding} $ \yo : C \hookrightarrow P C $ is given on objects by $ \yo(Y) = C(-, Y) $:
+  \[ \yo(Y)(X) = C(X, Y) \quad \text{and} \quad \yo(Y)(f)(g) = f \cdot g \]
+  for $ X: C $, $ f: C(X, X^\prime) $ and $ g: C(X^\prime, Y) $. It sends a morphism $ f: C(Y, Y^\prime) $ to the natural transformation $ \yo(f): C(-, Y) \Rightarrow C(-, Y^\prime) $ given by
+  \[ \yo(f)(X)(g) = g \cdot f \]
+  for $ X: C $ and $ g: C(X, Y) $.
 \end{definition}
@@
 \begin{lemma}
-  For any $ A: C $ and $ F : P C $, we have an equivalence $ P C(\yo(A), F) \simeq F(A) $, and this equivalence is natural in $ c $ and $ F $.
-\end{lemma}
-\begin{proof}
-  It sends a natural transformation $ \alpha: P C(\yo(A), F) $ to the element $ \alpha_A(\id A) $.
-Conversely, it sends an element $ x : P(A) $ to the natural transformation $ \alpha $ given by $ \alpha_B(f) = P(f)(x) $ for all $ f: \yo(A)(B) = C(B, A) $.
+  For any $ Y: C $ and $ F : P C $, we have an equivalence $ P C(\yo(Y), F) \simeq F(Y) $, and this equivalence is natural in $ Y $ and $ F $.
+\end{lemma}
+\begin{proof}
+  It sends a natural transformation $ \alpha: P C(\yo(Y), F) $ to the element $ \alpha_Y(\id Y) $.
+Conversely, it sends an element $ X : P(Y) $ to the natural transformation $ \alpha $ given by $ \alpha_X(f) = P(f)(X) $ for all $ f: \yo(Y)(X) = C(X, Y) $.
 For more details, see \autocite{Kashiwara}, Proposition 1.4.3.
@@
 For example: for a fixed universe of types, $ \TYPE $ or $ \SET $ are not small categories, the universe of types is not contained in itself), the presheaf category $ P C $ has exponential objects, given by
-  \[ (F^G)(X) = \hom{PC}(\yo(X) \times G, F) \]
+  \[ (F^G)(X) = PC(\yo(X) \times G, F), \]
   the natural transformations from the product functor of the Yoneda embedding of $ X $ and $ G $, to $ F $ (see \autocite{MacLane-Moerdijk}, Section I.6, Proposition 1).
@@
   Suppose that we have a functor $ F: C \to D $, and $ C $ and $ D $ both have binary products.
-Then for $ A, B : C $, we have morphisms $ \pi_1: A \times B \to A $ and $ \pi_2 : A \times B \to B $ and applying $ F $ to these yields morphisms from $ F(A \times B) $ to $ F(A) $ and $ F(B) $.
+Then for $ X, Y : C $, we have morphisms $ \pi_1: X \times Y \to X $ and $ \pi_2 : X \times Y \to Y $ and applying $ F $ to these yields morphisms from $ F(X \times Y) $ to $ F(X) $ and $ F(Y) $.
 We then have a product morphism
-  \[ \langle F(\pi_1), F(\pi_2) \rangle: F(A \times B) \to F(A) \times F(B). \]
-  Now, if this morphism is an isomorphism for all $ A, B : C $, we say that $ F $ \index{preservation of binary products}\textit{preserves binary products}.
-
-  One can imagine that there exists a similar definition of preservation of limits in general, in which the limit morphism of $ F $ applied to the projections from the limit is an isomorphism for any limit in $ C $.
+  \[ \langle F(\pi_1), F(\pi_2) \rangle: F(X \times Y) \to F(X) \times F(Y). \]
+  Now, if this morphism is an isomorphism for all $ X, Y : C $, we say that $ F $ \index{preservation of binary products}\textit{preserves binary products}.
+
+  One can imagine that there exists a similar definition of preservation of limits in general, in which the limit morphism of `$ F $ applied to the projections from the limit' is an isomorphism, for any limit in $ C $.
 \end{definition}
@@
 \begin{definition}\label{def:exponentials-preservation}
-  Suppose that we have a functor $ F: C \to D $ that preserves binary products, and $ C $ and $ D $ have exponential objects. Then for $ A, B : C $, we have natural bijections
-  \[ \varphi: C(A^B \times B, A) \xrightarrow \sim C(A^B, A^B) \quad \text{and} \quad \psi: D(F(A^B) \times F(B), F(A)) \xrightarrow \sim D(F(A^B), F(A)^{F(B)}) \]
-  This gives a morphism $ F(\varphi^{-1}(\id{A^B})) : D(F(A^B \times B), F(A)) $.
-Precomposing with the inverse of the isomorphism $ f: F(A^B \times B) \xrightarrow \sim F(A^B) \times F(B) $ and applying $ \psi $ gives
-  \[ \psi(f^{-1} \cdot \varphi^{-1}(\id{A^B})) : D(F(A^B), F(A)^{F(B)}). \]
-  We say that $ F $ \index{preservation of exponentials}\textit{preserves exponentials} if this morphism is an isomorphism for all $ A, B : C $.
-A name for a functor that preserves exponentials is a\iindex{cartesian functor}.
+  Suppose that we have a functor $ F: C \to D $ that preserves binary products, and $ C $ and $ D $ have exponential objects. Then for $ X, Y : C $, we have natural bijections
+  \[ \varphi: C(X^Y \times Y, X) \xrightarrow \sim C(X^Y, X^Y) \quad \text{and} \quad \psi: D(F(X^Y) \times F(Y), F(X)) \xrightarrow \sim D(F(X^Y), F(X)^{F(Y)}) \]
+  This gives a morphism $ F(\varphi^{-1}(\id{X^Y})) : D(F(X^Y \times Y), F(X)) $.
+Precomposing with the inverse of the isomorphism $ f: F(X^Y \times Y) \xrightarrow \sim F(X^Y) \times F(Y) $ and applying $ \psi $ gives
+  \[ \psi(f^{-1} \cdot \varphi^{-1}(\id{X^Y})) : D(F(X^Y), F(X)^{F(Y)}). \]
+  We say that $ F $ \index{preservation of exponentials}\textit{preserves exponentials} if this morphism is an isomorphism for all $ X, Y : C $.
+A name for a functor that preserves exponentials is a \iindex{cartesian functor}.
 \end{definition}
@@
   See \autocite{borceux}, Volume 1, Proposition 2.15.5 for the full proof, but note that for binary products, we have bijections
-  \[ \yo(A \times B)(X) \xrightarrow \sim \yo(A)(X) \times \yo(B)(X) \]
-  sending $ f : C(X, A \times B) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(X, A) \times C(X, B) $ to the product morphism $ \langle g_1, g_2 \rangle : \yo(X, A \times B) $.
+  \[ \yo(X \times Y)(Z) \xrightarrow \sim \yo(X)(Z) \times \yo(Y)(Z) \]
+  sending $ f : C(Z, X \times Y) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(Z, X) \times C(Z, Y) $ to the product morphism $ \langle g_1, g_2 \rangle : \yo(Z, X \times Y) $.
 This idea is also the core of the proof about general limits.
@@
 \begin{proof}
-  First of all, note that for $ A, B, X : C $, we have a sequence of isomorphisms  (\autocite{stackexchange:yoneda-exponentials})
+  First of all, note that for $ X, Y, Z : C $, we have a sequence of isomorphisms  (\autocite{stackexchange:yoneda-exponentials})
   \begin{align*}
-    \yo(A^B)(X) &\cong P C(\yo(X), \yo(A^B))\\
-    &\cong C(X, A^B)\\
-    &\cong C(X \times B, A)\\
-    &\cong P C(\yo(X \times B), \yo(A))\\
-    &\cong P C(\yo(X) \times \yo(B), \yo(A))\\
-    &\cong P C(\yo(X), \yo(A)^\yo(B))\\
-    &\cong (\yo(A)^\yo(B))(X)
+    \yo(X^Y)(Z) &\cong P C(\yo(Z), \yo(X^Y))\\
+    &\cong C(Z, X^Y)\\
+    &\cong C(Z \times Y, X)\\
+    &\cong P C(\yo(Z \times Y), \yo(X))\\
+    &\cong P C(\yo(Z) \times \yo(Y), \yo(X))\\
+    &\cong P C(\yo(Z), \yo(X)^\yo(Y))\\
+    &\cong (\yo(X)^\yo(Y))(Z)
   \end{align*}
@@
 
-  Some calculating shows that when applying this isomorphism to some $ f: \yo(A^B)(X) $, we get the natural transformation $ h: P C(\yo(X) \times \yo(B), \yo(A)) $ given by
+  Some calculating shows that when applying this isomorphism to some $ f: \yo(X^Y)(Z) $, we get the natural transformation $ h: P C(\yo(Z) \times \yo(Y), \yo(X)) $ given by
   \[ h_Z(g_1, g_2) = \langle g_1, g_2 \rangle \cdot \varphi^{-1}(f) \]
-  for all $ Z: C $ and $ (g_1, g_2) : \yo(X)(Z) \times \yo(B)(Z) $ and with the natural bijection
-  \[ \varphi: C(X \times B, A) \xrightarrow \sim C(X, A^B). \]
+  for all $ Z: C $ and $ (g_1, g_2) : \yo(Z)(Z) \times \yo(Y)(Z) $ and with the natural bijection
+  \[ \varphi: C(Z \times Y, X) \xrightarrow \sim C(Z, X^Y). \]
 
@@
 Note that the arrows in this diagram are functors, so objects in a category, instead of elements of a set.
-Therefore, it does not make sense to talk about `equality' of the morphisms along the different paths, but we rather talk about isomorphism in the functor category $ [C, P C] $.
+Therefore, it often does not make a lot of sense to talk about `equality' of the functors along the different paths, but we rather talk about isomorphism in the functor category $ [C, P C] $.
 If we have such an isomorphism, we say the diagram `2-commutes':
@@
 \begin{proof}
-  For $ c, d : C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
-  \[ \yo(c)(d) = C(d, c) \xrightarrow[f_{d, c}]{\sim} D(f(d), f(c)) = \op f_*(\yo(f(c)))(d). \]
-  Also, for $ g: C(d^\prime, d) $, the following diagram commutes
-  \begin{center}
-    \begin{tikzcd}
-      \yo(c)(d) \arrow[d, "g \cdot -"] \arrow[r, "f_{d, c}"] & \op f_*(\yo(f(c)))(d) \arrow[d, "f_{d^\prime, d}(g) \cdot -"]\\
-      \yo(c)(d^\prime) \arrow[r, "f_{d^\prime, c}"] & \op f_*(\yo(f(c)))(d^\prime)
-    \end{tikzcd}
-  \end{center}
-  so the isomorphism is natural in $ d $ and we have $ \yo(c) \cong \op f_*(\yo(f(c))) $ in $ P C $. Lastly, for $ g: C(c, c^\prime) $ and $ d: C $, the following diagram commutes
-  \begin{center}
-    \begin{tikzcd}
-      \yo(c)(d) \arrow[d, "- \cdot g"] \arrow[r, "f_{d, c}"] & \op f_*(\yo(f(c)))(d) \arrow[d, "- \cdot f_{c, c^\prime}(g)"]\\
-      \yo(c^\prime)(d) \arrow[r, "f_{d, c^\prime}"] & \op f_*(\yo(f(c^\prime)))(d)
-    \end{tikzcd}
-  \end{center}
-  so the isomorphism is natural in $ c $ and we have $ \yo \cong f \bullet \yo \bullet \op f_* $ in $ [C, P C] $.
+  For $ Y, X : C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
+  \[ \yo(Y)(X) = C(X, Y) \xrightarrow[f_{X, Y}]{\sim} D(f(X), f(Y)) = \op f_*(\yo(f(Y)))(X). \]
+  Also, for $ g: C(X^\prime, X) $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}
+      \yo(Y)(X) \arrow[d, "g \cdot -"] \arrow[r, "f_{X, Y}"] & \op f_*(\yo(f(Y)))(X) \arrow[d, "f_{X^\prime, X}(g) \cdot -"]\\
+      \yo(Y)(X^\prime) \arrow[r, "f_{X^\prime, Y}"] & \op f_*(\yo(f(Y)))(X^\prime)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ X $ and we have $ \yo(Y) \cong \op f_*(\yo(f(Y))) $ in $ P C $. Lastly, for $ g: C(Y, Y^\prime) $ and $ X: C $, the following diagram commutes
+  \begin{center}
+    \begin{tikzcd}
+      \yo(Y)(X) \arrow[d, "- \cdot g"] \arrow[r, "f_{X, Y}"] & \op f_*(\yo(f(Y)))(X) \arrow[d, "- \cdot f_{Y, Y^\prime}(g)"]\\
+      \yo(Y^\prime)(X) \arrow[r, "f_{X, Y^\prime}"] & \op f_*(\yo(f(Y^\prime)))(X)
+    \end{tikzcd}
+  \end{center}
+  so the isomorphism is natural in $ Y $ and we have $ \yo \cong f \bullet \yo \bullet \op f_* $ in $ [C, P C] $.
 \end{proof}
@@
 \section{Fibrations}
-Let $ P : E \to B $ be a functor. In this case, we will view this as the category $ E $ `lying over' the category $ B $, with for every point $ b: B $, a slice $ E_b = P^{-1}(B) $ lying `above' $ b $.
-
-\begin{definition}
-  A morphism $ f: E(y, z) $ is called \iindex{cartesian} if for all $ g: E(x, z) $ and $ h: B(P(x), P(y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(x, y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \autocite{nlab:grothendieck_fibration}
+Let $ P : E \to B $ be a functor. In this case, we will view this as the category $ E $ `lying over' the category $ B $, with for every point $ X: B $, a slice $ E_X = P^{-1}(B) $ lying `above' $ X $.
+
+\begin{definition}
+  A morphism $ f: E(Y, Z) $ is called \iindex{cartesian} if for all $ g: E(X, Z) $ and $ h: B(P(X), P(Y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(X, Y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \autocite{nlab:grothendieck_fibration}
   \begin{center}
     \begin{tikzcd}[sep=large]
-      E \arrow[d, "P"] &x \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar h"', dashed] & y \arrow[r, "f"'] & z\\
-      B & P(x) \arrow[r, "\forall h"'] \arrow[rr, "P(g)", bend left] & P(y) \arrow[r, "P(f)"'] & P(z)
-    \end{tikzcd}
-  \end{center}
-\end{definition}
-
-\begin{definition}
-  $ P $ is a \iindex{fibration} if for all $ y: E $ and morphisms $ f: B(x, P(y)) $, there exist an object $ \bar x: E $ and a cartesian morphism $ \bar f: E(\bar x, y) $ such that $ P(\bar x) = x $ and $ P(\bar f) = f $:
-  \begin{center}
-    \begin{tikzcd}
-      E \arrow[d, "P"] & \bar x \arrow[r, "\exists \bar f", dashed] & y\\
-      B & x \arrow[r, "\forall f"] & P(y)
+      E \arrow[d, "P"] &X \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar h"', dashed] & Y \arrow[r, "f"'] & Z\\
+      B & P(X) \arrow[r, "\forall h"'] \arrow[rr, "P(g)", bend left] & P(Y) \arrow[r, "P(f)"'] & P(Z)
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+\begin{definition}
+  $ P $ is a \iindex{fibration} if for all $ Y: E $ and morphisms $ f: B(X, P(Y)) $, there exist an object $ \bar X: E $ and a cartesian morphism $ \bar f: E(\bar X, Y) $ such that $ P(\bar X) = X $ and $ P(\bar f) = f $:
+  \begin{center}
+    \begin{tikzcd}
+      E \arrow[d, "P"] & \bar X \arrow[r, "\exists \bar f", dashed] & Y\\
+      B & X \arrow[r, "\forall f"] & P(Y)
     \end{tikzcd}
@@
 \section{(Co)slice categories}
-Given an object in a category $ c: C $, the morphisms to and from $ c $ constitute the slice and coslice categories
-\begin{definition}
-  The \iindex{slice category} $ C \downarrow c $ is the category with as objects the morphisms to $ c $:
-  \[ (C \downarrow c)_0 = \sum_{c^\prime: C} C(c^\prime, c). \]
-  The morphisms from $ (c^\prime, f) $ to $ (c^{\prime\prime}, f^\prime) $ are the morphisms $ g: c^\prime \to c^{\prime\prime} $ making the following diagram commute.
-  \begin{center}
-    \begin{tikzcd}
-      c^\prime \arrow[rr, "g"] \arrow[rd, "f"'] & & c^{\prime\prime} \arrow[ld, "f^\prime"]\\
-      & c
-    \end{tikzcd}
-  \end{center}
-\end{definition}
-The \textit{coslice category}\index{slice category!co-} $ c \downarrow C $ is similar, but with the morphisms \textit{from} $ c $ instead of \textit{to} $ c $:
-\[ (c \downarrow C)_0 = \sum_{c^\prime: C} C(c, c^\prime). \]
+Given an object in a category $ X: C $, the morphisms to and from $ X $ constitute the slice and coslice categories
+\begin{definition}
+  The \iindex{slice category} $ C \downarrow X $ is the category with as objects the morphisms to $ X $:
+  \[ (C \downarrow X)_0 = \sum_{Y: C} C(Y, X). \]
+  The morphisms from $ (Y_1, f_1) $ to $ (Y_2, f_2) $ are the morphisms $ g: Y_1 \to Y_2 $ making the following diagram commute.
+  \begin{center}
+    \begin{tikzcd}
+      Y_1 \arrow[rr, "g"] \arrow[rd, "f_1"'] & & Y_2 \arrow[ld, "f_2"]\\
+      & X
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+The \textit{coslice category}\index{slice category!co-} $ X \downarrow C $ is similar, but with the morphisms \textit{from} $ X $ instead of \textit{to} $ X $:
+\[ (X \downarrow C)_0 = \sum_{Y: C} C(X, Y). \]
 
@@
 \begin{lemma}
-  Let $ (d, f) $ be an object in the slice category $ (C \downarrow c) $. The slice category $ ((C \downarrow c) \downarrow (d, f)) $ is equivalent to $ (C \downarrow d) $.
-\end{lemma}
-\begin{proof}
-  An object of $ ((e, g), \alpha) : ((C \downarrow c) \downarrow (d, f)) $ is an object $ (e, g) : (C \downarrow c) $, together with a morphism $ \alpha: (C \downarrow c)((e, g), (d, f)) $.
-That is, a morphism $ \alpha: C(e, d) $ such that the obvious triangle commutes (shown in the diagram below on the far left).
-
-  Then a morphism between $ ((e, g), \alpha) $ and $ ((e^\prime, g^\prime), \alpha^\prime) $ is a morphism $ \beta $ between $ (e, g) $ and $ (e^\prime, g^\prime) $ that commutes with $ \alpha $ and $ \alpha^\prime $.
-Note that a morphism between $ (e, g) $ and $ (e^\prime, g^\prime) $ is a morphism between $ e $ and $ e^\prime $ that commutes with $ g $ and $ g^\prime $.
-  \begin{center}
-    \begin{tikzcd}
-      e \arrow[rdd, "g"'] \arrow[rd, "\alpha"] \arrow[rr, "\beta"] && e^\prime \arrow[ldd, "g^\prime"] \arrow[ld, "\alpha^\prime"']\\
-      & d \arrow[d, "f" description]\\
-      & c
+  Let $ (Y, f) $ be an object in the slice category $ (C \downarrow X) $. The slice category $ ((C \downarrow X) \downarrow (Y, f)) $ is equivalent to $ (C \downarrow Y) $.
+\end{lemma}
+\begin{proof}
+  An object of $ ((Z, g), \alpha) : ((C \downarrow X) \downarrow (Y, f)) $ is an object $ (Z, g) : (C \downarrow X) $, together with a morphism $ \alpha: (C \downarrow X)((Z, g), (Y, f)) $.
+That is, a morphism $ \alpha: C(Z, Y) $ such that the obvious triangle commutes (shown in the diagram below on the far left).
+
+  Then a morphism between $ ((Z_1, g_1), \alpha_1) $ and $ ((Z_2, g_2), \alpha_2) $ is a morphism $ \beta $ between $ (Z_1, g_1) $ and $ (Z_2, g_2) $ that commutes with $ \alpha_1 $ and $ \alpha_2 $.
+Note that a morphism between $ (Z_1, g_1) $ and $ (Z_2, g_2) $ is a morphism between $ Z_1 $ and $ Z_2 $ that commutes with $ g_1 $ and $ g_2 $.
+  \begin{center}
+    \begin{tikzcd}
+      Z_1 \arrow[rdd, "g_1"'] \arrow[rd, "\alpha_1"] \arrow[rr, "\beta"] && Z_2 \arrow[ldd, "g_2"] \arrow[ld, "\alpha_2"']\\
+      & Y \arrow[d, "f" description]\\
+      & X
     \end{tikzcd}
@@
     \begin{tikzcd}
-      e \arrow[rd, "\alpha"] \arrow[rr, "\beta"] && e^\prime \arrow[ld, "\alpha^\prime"']\\
-      & d
-    \end{tikzcd}
-  \end{center}
-
-  Now, note that $ g $ and $ g^\prime $ are completely determined by $ g = \alpha \cdot f $ and $ g^\prime = \alpha^\prime \cdot f $, so we can leave them out.
-Also, if $ \beta $ commutes with $ \alpha $ and $ \alpha^\prime $, it automatically also commutes with $ g $ and $ g^\prime $.
+      Z_1 \arrow[rd, "\alpha_1"] \arrow[rr, "\beta"] && Z_2 \arrow[ld, "\alpha_2"']\\
+      & Y
+    \end{tikzcd}
+  \end{center}
+
+  Now, note that $ g_1 $ and $ g_2 $ are completely determined by $ g_i = \alpha_i \cdot f $, so we can leave them out.
+Also, if $ \beta $ commutes with $ \alpha_1 $ and $ \alpha_2 $, it automatically also commutes with $ g_1 $ and $ g_2 $.
 Therefore, as shown above, we have a correspondence between objects and morphisms
-  \[ \beta: ((e, g), \alpha) \to ((e^\prime, g^\prime), \alpha^\prime) \Leftrightarrow \beta: (e, \alpha) \to (e^\prime, \alpha^\prime). \]
-\end{proof}
-
-Also, it turns out that we can derive some structure of the slice categories from the original category:
-\begin{lemma}
-  For $ (d, f), (d^\prime, f^\prime) : (C \downarrow c) $, their product in the slice category is given by their pullback / fibered product $ d \times_c d^\prime $, together with the induced morphism $ g: d \times_c d^\prime \dasharrow c $.
+  \[ \beta: ((Z_1, g_1), \alpha_1) \to ((Z_2, g_2), \alpha_2) \Leftrightarrow \beta: (Z_1, \alpha_1) \to (Z_2, \alpha_2). \]
+\end{proof}
+
+Now, the slice categories inherit some structure from the original category:
+\begin{lemma}
+  For $ (Y_1, f_1), (Y_2, f_2) : (C \downarrow X) $, their product in the slice category is given by their pullback, or fibered product, $ Y_1 \times_X Y_2 $, together with the induced morphism $ g: Y_1 \times_X Y_2 \dasharrow X $.
 \end{lemma}
@@
   Consider the diagram below.
-The fibered product gives `projections' $ h $ and $ h^\prime $.
-Also, if we have some $ (e, \alpha) : (C \downarrow c) $, together with morphisms $ \beta : (e, \alpha) \to (d, f) $ and $ \beta^\prime : (e, \alpha) \to (d^\prime, f^\prime) $.
-Then $ \beta $ and $ \beta^\prime $ commute with $ f $ and $ f^\prime $, so by the universal property of the fibred product, there exists a unique morphism $ \gamma : e \to d \times_c d^\prime $ that makes the triangles with $ \beta $ and $ h $, and with $ \beta^\prime $ and $ h^\prime $ commute.
-Then $ \gamma $ commutes with $ \alpha $ and $ g $ as well, so it is a morphism in $ (C \downarrow c) $.
-This shows that $ (d \times_c d^\prime, g) $ has the universal property of the product in $ (C \downarrow c) $.
-  \begin{center}
-    \begin{tikzcd}
-      e \arrow[rd, "\beta"] \arrow[rr, "\beta^\prime", bend left] \arrow[rrd, "\alpha"', bend right=49, shift right] \arrow[r, dashed, "\gamma"] & d \times_c d^\prime \arrow[r, "h^\prime"'] \arrow[d, "h"] \arrow[rd, dashed, "g"] & d^\prime \arrow[d, "f^\prime"] \\
-      & d \arrow[r, "f"] & c
+The fibered product gives `projections' $ h_1 $ and $ h_2 $.
+Also, if we have some $ (Z, \alpha) : (C \downarrow X) $, together with morphisms $ \beta_1 : (Z, \alpha) \to (Y_1, f_1) $ and $ \beta_2 : (Z, \alpha) \to (Y_2, f_2) $.
+Then $ \beta_1 $ and $ \beta_2 $ commute with $ f_1 $ and $ f_2 $, so by the universal property of the fibred product, there exists a unique morphism $ \gamma : Z \to Y_1 \times_X Y_2 $ that makes the triangles with $ \beta_1 $ and $ h_1 $, and with $ \beta_2 $ and $ h_2 $ commute.
+Then $ \gamma $ commutes with $ \alpha $ and $ g $ as well, so it is a morphism in $ (C \downarrow X) $.
+This shows that $ (Y_1 \times_X Y_2, g) $ has the universal property of the product in $ (C \downarrow X) $.
+  \begin{center}
+    \begin{tikzcd}
+      Z \arrow[rd, "\beta_1"] \arrow[rr, "\beta_2", bend left] \arrow[rrd, "\alpha"', bend right=49, shift right] \arrow[r, dashed, "\gamma"] & Y_1 \times_X Y_2 \arrow[r, "h_2"'] \arrow[d, "h_1"] \arrow[rd, dashed, "g"] & Y_2 \arrow[d, "f_2"] \\
+      & Y_1 \arrow[r, "f_1"] & X
     \end{tikzcd}
@@
 \begin{proof}
-  Take a diagram $ ((A_i)_i, (f_j)_j) $ in $ C $.
-Suppose that this has a limit $ (L, (g_i)_i) : C $.
-Now, consider an object $ (B, q) : (C \downarrow X) $, together with morphisms $ h_i : (C \downarrow X)((B, q), \Delta_X A_i) $, that commute with the $ \Delta_X f_j $:
-  \begin{center}
-    \begin{tikzcd}
-      & B \arrow[ldd, "h_{m_j}"'] \arrow[rdd, "h_{n_j}"]\\
+  Take a diagram $ ((Y_i)_i, (f_j)_j) $ in $ C $.
+Suppose that this has a limit $ L : C $ with projections $ g_i : C(L, Y_i) $.
+Now, consider an object $ (Z, q) : (C \downarrow X) $, together with morphisms $ h_i : (C \downarrow X)((Z, q), \Delta_X Y_i) $, that commute with the $ \Delta_X f_j $:
+  \begin{center}
+    \begin{tikzcd}
+      & Z \arrow[ldd, "h_{m_j}"'] \arrow[rdd, "h_{n_j}"]\\
       & X \times L \arrow[ld, "\Delta_X g_{m_j}"] \arrow[rd, "\Delta_X g_{n_j}"']\\
-      X \times A_{m_j} \arrow[rr, "\Delta_X f_j"'] & & X \times A_{n_j}
-    \end{tikzcd}
-  \end{center}
-  Then the morphisms in $ (C \downarrow X)((B, q), \Delta_X L) $, commuting with the $ \Delta_X g_j $ and $ h_j $ are the morphisms in $ C(B, X \times L) \cong C(B, X) \times C(B, L) $ that commute with the projections to $ X $ and the $ \id X \times g_j $ and $ h_j $.
-Since the morphisms in $ C(B, X) $ commuting with $ q $ and $ \id X $ are exactly $ q $, we can forget about this component, and the morphisms we are looking for correspond to the morphisms in $ C(B, L) $ that commute with the $ g_j $ and $ h_j \cdot p_1 $.
+      X \times Y_{m_j} \arrow[rr, "\Delta_X f_j"'] & & X \times Y_{n_j}
+    \end{tikzcd}
+  \end{center}
+  Then the morphisms in $ (C \downarrow X)((Z, q), \Delta_X L) $, commuting with the $ \Delta_X g_j $ and $ h_j $ are the morphisms in $ C(Z, X \times L) \cong C(Z, X) \times C(Z, L) $ that commute with the projections to $ X $ and the $ \id X \times g_j $ and $ h_j $.
+Since the morphisms in $ C(Z, X) $ commuting with $ q $ and $ \id X $ are exactly $ q $, we can forget about this component, and the morphisms we are looking for correspond to the morphisms in $ C(Z, L) $ that commute with the $ g_j $ and $ h_j \cdot p_1 $.
 Since $ (L, (g_j)_j) $ is a limit, this is a unique morphism.
@@
   \begin{align*}
-    (C \downarrow X)((A, f), \Delta_X Y^Z) &\cong C(A, Y^Z)\\
-    &\cong C(A \times Z, Y)\\
-    &\cong (C \downarrow X)((A \times X \times Z, \langle f, p_1 \rangle), \Delta_X Y)\\
-    &\cong (C \downarrow X)((A, f) \times \Delta_X Z, \Delta_X Y)\\
+    (C \downarrow X)((W, f), \Delta_X Y^Z) &\cong C(W, Y^Z)\\
+    &\cong C(W \times Z, Y)\\
+    &\cong (C \downarrow X)((W \times (X \times Z), \langle f, p_1 \rangle), \Delta_X Y)\\
+    &\cong (C \downarrow X)((W, f) \times \Delta_X Z, \Delta_X Y)\\
   \end{align*}
@@
 Take a category $ C $.
-To talk about dependent sums $ \sum_{a: A} X_a $ and products $ \prod_{a: A} X_a $ in $ C $, we first need some way to construct the family of objects $ (X_a)_a $.
-Of course, we can do this \textit{externally} using a set $ A $, and picking an object $ X_a : C $ for every element $ a : A $.
-We then have a category of such families $ C^A $, with objects $ (X_a)_a $ and morphisms $ (f_a)_a: C^A((X_a)_a, (Y_a)_a) $, with $ f_a: X_a \to Y_a $.
-We write $ C^A $ because we can view this as just the $ A $-fold power of $ C $.
-Now, this assignment of categories $ A \mapsto C^A $ can be turned into a contravariant (pseudo)functor of $ 2 $-categories $ \op \SET \to \Cat $.
-It sends a morphism $ f: A \to B $ to the `relabeling' or `substitution' functor $ C^B \to C^A $, $ (X_b)_b \mapsto (X_{f(a)})_a $.
-
-However, there is also an \textit{internal} representation, as a morphism $ X \to A $.
-We can turn the collection of these morphisms over all the $ A : C $ simultaneously into a category $ C^2 $ (abusing notation a bit, writing $ 2 $ for the two-point category $ \bullet \to \bullet $).
-Then taking codomains $ (X \to A) \mapsto A $ gives a functor $ C^2 \to C $.
-The fiber of this functor above $ A $ is the slice category $ (C \downarrow A) $.
-
-In $ \SET $, the external and internal ways of indexing are actually equivalent, because given a family $ (X_a)_a $ we can construct a morphism $ f: \sum_{a : A} X_a \to A $ and conversely, we can recover the family $ (X_a)_a $ as $ (f^{-1}(a))_a $.
-
-Also note that for $ \SET $, if we consider an indexed family $ (X_a)_a $ as some function $ X: A \to \SET $, then substitution over $ \alpha: B \to A $ is just given by postcomposition $ X \circ \alpha: B \to \SET $.
-It turns out that in the internal representation this arises as the pullback
-\begin{center}
-  \begin{tikzcd}
-    \sum_{b : B} X_{\alpha(b)} \arrow[r] \arrow[d, "\alpha^* f"] \arrow[dr, phantom, "\lrcorner", very near start] & \sum_{a : A} X_a \arrow[d, "f"]\\
-    B \arrow[r, "\alpha"] & A
-  \end{tikzcd}
-\end{center}
-This can be turned into a pullback or `substitution' functor $ \alpha^* $, which Taylor calls $ \mathtt{P}\alpha $.
+To talk about dependent sums $ \sum_{x: X} Y_x $ and products $ \prod_{x: X} Y_x $ in $ C $, we first need some way to construct the family of objects $ (Y_x)_x $.
+Of course, we can do this \textit{externally} using a set $ X $, and picking an object $ Y_x : C $ for every element $ x : X $.
+We then have a category of such families $ C^X $, with objects $ (Y_x)_x $ and morphisms $ (f_x)_x: C^X((Y_x)_x, (Z_x)_x) $, with $ f_x: Y_x \to Z_x $.
+We write $ C^X $ because we can view this as just the $ X $-fold power of $ C $.
+Now, this assignment of categories $ X \mapsto C^X $ can be turned into a contravariant (pseudo)functor of $ 2 $-categories $ \op \SET \to \Cat $.
+It sends a morphism $ f: X_1 \to X_2 $ to the `relabeling' or `substitution' functor $ C^{X_2} \to C^{X_1} $, $ (Y_x)_x \mapsto (Y_{f(x)})_x $.
+
+However, there is also an \textit{internal} representation, as a morphism $ Y \to X $.
+We can turn the collection of these morphisms over all the $ X : C $ simultaneously into a category $ C^2 $ (abusing notation a bit, writing $ 2 $ for the two-point category $ \bullet \to \bullet $).
+Then taking codomains $ (Y \to X) \mapsto X $ gives a functor $ C^2 \to C $.
+The fiber of this functor above $ X $ is the slice category $ (C \downarrow X) $.
+
+In $ \SET $, the external and internal ways of indexing are actually equivalent, because given a family $ (Y_x)_x $ we can construct a morphism $ f = \pi_1: \sum_{x : X} Y_x \to X $ and conversely, we can recover the family $ (Y_x)_x $ as $ (f^{-1}(x))_x $.
+
+Also note that for $ \SET $, if we consider an indexed family $ (Z_y)_y $ as some function $ Z: Y \to \SET $, then substitution over $ f: X \to Y $ is just given by postcomposition $ Z \circ f: X \to \SET $.
+It turns out that in the internal representation this is a pullback
+\begin{center}
+  \begin{tikzcd}
+    \sum_{x : X} Z_{f(x)} \arrow[r] \arrow[d, "\pi_1"] \arrow[dr, phantom, "\lrcorner", very near start] & \sum_{y : Y} Z_y \arrow[d, "\pi_1"]\\
+    X \arrow[r, "f"] & Y
+  \end{tikzcd}
+\end{center}
+This can be extended to a pullback or `substitution' functor $ f^* : (\SET \downarrow Y) \to (\SET \downarrow X) $, which Taylor calls $ \mathtt{P} f $.
 This turns the functor $ \SET^2 \to \SET $ into a fibration.
-We can construct $ \alpha^* : (C \downarrow A) \to (C \downarrow B) $ for any category $ C $ with pullbacks and any morphism $ \alpha: C(B, A) $.
-The existence of this pullback makes the functor $ C^2 \to C $ into a fibration.
-
-Now, in $ \SET $, for a family $ (X_a)_a $, consider the dependent product $ \prod_{a : A} X_a $.
-Its elements $ (x_a)_a $ can be identified with morphisms from the terminal set: $ \{ \star \} \to \prod_{a : A} X_a $, sending $ \star $ to $ (x_a)_a $.
-However, they can also be identified with the morphisms $ \varphi: A \to \sum_{a : A} X_a $ that make the following diagram commute, sending $ a $ to $ x_a $:
-\begin{center}
-  \begin{tikzcd}
-    A \arrow[rd, "\id A"] \arrow[rr, " \varphi "] & & \sum_{a : A} X_a \arrow[ld, "f"]\\
-    & A
-  \end{tikzcd}
-\end{center}
-These are morphisms in $ (\SET \downarrow A) $ from $ (A, \id A) $ to $ (\sum_{a : A} X_a, f) $.
-Note that for the terminal morphism $ \alpha: A \to \{ \star \} $, we have $ \id A = \alpha^*(\id{\{\star\}}) $.
+We can construct such a functor $ f^* $ for any category $ C $ with pullbacks and any morphism $ f: C(X, Y) $, and this makes the functor $ C^2 \to C $ into a fibration.
+
+Now, in $ \SET $, for a family $ (Y_x)_x $, consider the dependent product $ \prod_{x : X} Y_x $.
+Its elements $ (y_x)_x $ can be identified with morphisms from the terminal set: $ \{ \star \} \to \prod_{x : X} Y_x $, sending $ \star $ to $ (y_x)_x $.
+However, they can also be identified with the morphisms $ f: X \to \sum_{x : X} Y_x $ that make the following diagram commute, sending $ x $ to $ y_x $:
+\begin{center}
+  \begin{tikzcd}
+    X \arrow[rd, "\id X"'] \arrow[rr, "f"] & & \sum_{x : X} Y_x \arrow[ld, "\pi_1"]\\
+    & X
+  \end{tikzcd}
+\end{center}
+These are morphisms in $ (\SET \downarrow X) $ from $ (X, \id X) $ to $ (\sum_{x : X} Y_x, \pi_1) $.
+Note that for the terminal morphism $ f: X \to \{ \star \} $, we have $ (X, \id X) = f^*(\{\star\}, \id{\{\star\}}) $.
 To summarize, we have an equivalence
-\[ (\SET \downarrow A)(\alpha^*(\id{\{\star\}}), f) \simeq (\SET \downarrow {\{\star\}})( \id{\{ \star \}}, \prod_{a : A} X_a). \]
-Now, given a family of families $ ((X_b)_{b : B_a})_{a : A} $, we can wonder whether we can construct the family of dependent products $ (\prod_{b : B_a} X_b)_a $.
+\[ (\SET \downarrow X)\left(f^*(\{ \star \}, \id{\{\star\}}), \left(\sum_{x : X} Y_x, \pi_1 \right) \right) \simeq (\SET \downarrow {\{\star\}})\left( (\{\star\}, \id{\{ \star \}}), \left( \prod_{x : X} Y_x, !
+\right) \right) \]
+for $ !
+$ the terminal morphism.
+Now, for an internal indexed family $ f : Y \to X $ and given a family of families $ ((Z_y)_{y : Y_x})_{x : X} $, we can wonder whether we can construct the family of dependent products $ (\prod_{y : Y_x} Z_y)_x $.
 In $ \SET $, this is definitely possible, and from this, we get an equivalence again
-\[ (\SET \downarrow (\sum_{a : A} B_a))(\alpha^*(\id A), f) \simeq (\SET \downarrow A)(\id A, (\prod_{b : B_a} X_b)_a). \]
-These equivalences suggest an adjunction $ \alpha^* \dashv \prod_{\dots} $. We can use this to define in general
-\begin{definition}
-  For a category $ C $ and a morphism $ \alpha: B \to A $, the \iindex{dependent product} along $ \alpha $ is, if it exists, the right adjoint to the pullback functor:
-  \begin{center}
-    \begin{tikzcd}
-      (C \downarrow A) \arrow[r, shift left=2, "\alpha^*"{name=A}] &
-      (C \downarrow B) \arrow[l, shift left=2, "\prod_\alpha"{name=B}]
+\[ \left(\SET \downarrow \sum_{x : X} Y_x \right)\left(f^*(X, \id X), (\sum_{x : X} \sum_{y : Y_x} Z_y, p) \right) \simeq (\SET \downarrow A)\left((X, \id X), \left(\sum_{x : X} \prod_{y : Y_x} Z_y, \pi_1\right)\right).
+\]
+with $ p : \sum_{x : X} \sum_{y : Y_x} Z_y \to \sum_{x : X} Y_x $ defined as $ p(x, y, z) = (x, y) $.
+These equivalences suggest an adjunction $ f^* \dashv \prod_{\dots} $.
+We can use this to define in general
+\begin{definition}
+  For a category $ C $ and a morphism $ f: Y \to X $, the \iindex{dependent product} along $ f $ is, if it exists, the right adjoint to the pullback functor:
+  \begin{center}
+    \begin{tikzcd}
+      (C \downarrow A) \arrow[r, shift left=2, "f^*"{name=A}] &
+      (C \downarrow B) \arrow[l, shift left=2, "\prod_f"{name=B}]
       \ar[from=A, to=B, symbol=\dashv]
@@
 \begin{remark}
-  As argued above, we can recover the familiar dependent product $ \prod_{a : A} X_a $ of a family $ (X_a)_a $ as the dependent product $ \prod_\alpha f $ along the terminal morphism $ \alpha: A \to I $, with $ f: \sum_a X_a \to A $ the internal representation of the family.
+  As argued above, we can recover the familiar dependent product $ \prod_{x : X} Y_x $ of a family $ (Y_x)_x $ as the dependent product $ \prod_f (\sum_x Y_x, \pi_1) $ along the terminal morphism $ f: X \to I $.
 Here we use the equivalence between $ (C \downarrow I) $ and $ C $.
@@
   Given a set $ X $ with right $ M $-action.
-Take $ Y = X \times M^\prime / \sim $ with the relation $ (x m, m^\prime) \sim (x, f(m) \cdot m^\prime) $ for $ m: M $.
+Take $ Y = X \times M^\prime / \sim $ with the relation $ (x m, m^\prime) \sim (x, \varphi(m) \cdot m^\prime) $ for $ m: M $.
 This has a right $ M^\prime $-action given by $ (x, m^\prime)n^\prime = (x, m^\prime n^\prime) $.

### 2024-09-27 400-algebraic-structures.tex
Write an introduction
Add code references to chapter 4

--- 2024-09-09 report/src/algebraic-structures.tex
@@
-\chapter{Algebraic Structures}
+\chapter{Algebraic Structures}\label{ch:algebraic-structures}
 
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.AlgebraicTheories}{algebraic_theory}]
   We define an \iindex{algebraic theory} $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we usually leave $ n $ implicit), together with a substitution operation
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.AlgebraicTheoryMorphism}{algebraic_theory_morphism}]
   A \textit{morphism}\index{algebraic theory!morphism} $ f $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ f_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
@@
 
-Together, these form the category of algebraic theories \iindex{$ \AlgTh $}.
+Together, these form the category of algebraic theories \iindex{$ \AlgTh $} (\coqident{AlgebraicTheories.AlgebraicTheoryCategoryCore}{algebraic_theory_cat}).
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{limits_algebraic_theory_cat}]\label{rem:algebraic-theory-limits}
   We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.Algebras}{algebra}]
   An \iindex{algebra} $ A $ for an algebraic theory $ T $ is a set $ A $, together with an action
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.AlgebraMorphisms}{algebra_morphism}]
   For an algebraic theory $ T $, a \textit{morphism}\index{algebra!morphism} $ f $ between $ T $-algebras $ A $ and $ A^\prime $ is a function $ f: A \to A $ such that
@@
 
-Together, these form the category of $ T $-algebras \iindex{$ \Alg T $}.
+Together, these form the category of $ T $-algebras \iindex{$ \Alg T $} (\coqident{AlgebraicTheories.AlgebraCategoryCore}{algebra_cat}).
 
@@
 It turns out that it also has all colimits (see Lemma \ref{lem:algebra-coproducts} for binary coproducts, or \autocite{algebraic-theories-2010}, Part 1, Theorem 4.5 for general colimits).
-Note, however, that this proof is a lot more complicated than the proof about limits, just like colimits of algebraic objects usually are more complicated than limits.
-For example, consider (binary) coproducts of groups.
+Note, however, that the proof for colimits is a lot more complicated than the proof for limits, just like colimits of algebraic objects usually are more complicated than limits.
+For example, consider (binary) products and coproducts of groups.
 \end{remark}
 
-\begin{remark}
-  Note that for an algebraic theory $ T $, the $ T_n $ are algebras for $ T $, with the action given by $ \bullet $.
-\end{remark}
-
-\begin{definition}\label{def:algebra-pullback}
+\begin{definition}[\coqident{AlgebraicTheories.AlgebraCategory}{algebra_pullback}]\label{def:algebra-pullback}
   If we have a morphism of algebraic theories $ f: T^\prime \to T $, we have a \textit{pullback functor of algebras}\index{pullback functor!of algebras} $ f^* : \Alg T \to \Alg {T^\prime} $.
@@
 
-Note that besides the categories $ \Alg T $, we can also consider the category of `all' algebraic theory algebras together.
+Note that besides the categories $ \Alg T $, we can also consider the category of `all' algebraic theory algebras together (\coqident{AlgebraicTheories.AlgebraCategoryCore}{algebra_full_cat}).
 That is, the category $ C $ with $ C_0 = \sum_{T : \AlgTh}, \Alg T $ and $ C((T, A), (T^\prime, A^\prime)) $ consisting of pairs $ (f, f^\prime): \AlgTh(T, T^\prime) \times \SET(A, A^\prime) $ such that for all $ t: T_n $ and $ a: A^n $,
@@
 
-\begin{lemma}\label{lem:algebra-fibration}
+\begin{lemma}[\coqident{AlgebraicTheories.AlgebraCategory}{algebra_fibration}]\label{lem:algebra-fibration}
   $ P $ is a fibration.
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.Presheaves}{presheaf}]
   A \iindex{presheaf} $ P $ for an algebraic theory $ T $ is a sequence of sets $ P_n $ indexed over $ \mathbb N $, together with an action
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.PresheafMorphisms}{presheaf_morphism}]
   For an algebraic theory $ T $, a \textit{morphism}\index{presheaf!morphism} $ f $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ f_n: P_n \to P^\prime_n $ such that
@@
 
-Together, these form the category of $ T $-presheaves \iindex{$ \Pshf T $}.
+Together, these form the category of $ T $-presheaves \iindex{$ \Pshf T $} (\coqident{AlgebraicTheories.PresheafCategoryCore}{presheaf_cat}).
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.PresheafCategory}{limits_presheaf_cat}]
   The category of presheaves has all limits.
@@
 
-An analogue to Lemma \ref{lem:algebra-fibration} shows that, like with algebras, the total category of presheaves is fibered over the category of algebraic theories.
+An analogue to Lemma \ref{lem:algebra-fibration} shows that, like with algebras, the total category of presheaves is fibered over the category of algebraic theories (\coqident{AlgebraicTheories.PresheafCategory}{presheaf_fibration}).
 
@@
 
-Let $ \iota_{m, n} : T_m \to T_{m + n} $ be the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
+Let \index{$ \iota_{m, n} $}$ \iota_{m, n} : T_m \to T_{m + n} $ be the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
 \[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \quad \text{and} \quad \iota_{m, n}(f \bullet g) = f \bullet (\iota_{m, n}(g_i))_i. \]
@@
 
-\begin{definition}[$ \lambda $-theory]
+\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{lambda_theory}]
   A \iindex{$ \lambda $-theory} is an algebraic theory $ L $, together with sequences of functions $ \lambda_n: L_{n + 1} \to L_n $ and $ \rho_n: L_n \to L_{n + 1} $, such that
@@
 
-\begin{definition}[$ \beta $- and $ \eta $-equality]
+\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{has_β}]
   We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $.
@@
 
-\begin{definition}[$ \lambda $-theory morphism]
-  A \textit{morphism}\index{$ \lambda $-theory!morphism} $ f $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ f $ such that
+\begin{definition}[\coqident{AlgebraicTheories.LambdaTheoryMorphisms}{lambda_theory_morphism}] \textit{morphism}\index{$ \lambda $-theory!morphism} $ f $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ f $ such that
   \begin{align*}
@@
 
-Together, these form the category of $ \lambda $-theories \iindex{$ \LamTh $}.
+Together, these form the category of $ \lambda $-theories \iindex{$ \LamTh $} (\coqident{AlgebraicTheories.LambdaTheoryCategoryCore}{lambda_theory_cat}).
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{limits_lambda_theory_cat}]
   The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories.
@@
 Now, consider the element $ \rho(x_{1, 1}) : L_2 $.
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{app'}]
   Using the substitution, we have binary operations on the $ L_n $, sending $ (f, g) : L_n \times L_n $ to $ \rho(x_{1, 1}) \bullet (f, g) : L_n $.
@@
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{beta_equality}]
   Note that if $ L $ has $ \beta $-equality, we have
@@
 \end{remark}
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app_from_app'}]
   Also note that for $ f: L_n $,
@@
 \end{remark}
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app}]
   Note that for $ f, g : L_n $,
@@
 \subsection{The free algebraic theory on a set}
-\begin{example}
+\begin{example}[\coqident{AlgebraicTheories.Examples.FreeTheory}{free_functor}]
   Let $ S $ be a set. We can construct an algebraic theory $ F(S) $ by taking $ F(S)_n = S \sqcup \{ 1, \dots, n \} $ with projections $ x_i = i $ and substitution
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.Examples.FreeTheory}{free_functor_is_free}]
   The algebraic theory $ F(S) $ defined above, is the free algebraic theory on the set $ S $.
@@
 
-\begin{corollary}
+\begin{corollary}[\coqident{AlgebraicTheories.Examples.ProjectionsTheory}{projections_theory}]
   $ F(\emptyset) $ is the initial algebraic theory.
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.Examples.ProjectionsTheory}{algebra_coslice_equivalence}]
   There is an adjoint equivalence between the category $ \Alg{F(S)} $ and the coslice category $ S \downarrow \SET $.
@@
 
-\begin{definition}\label{def:pure-lambda-calculus}
+\begin{definition}[\coqident{AlgebraicTheories.Examples.LambdaCalculus}{lambda_calculus_lambda_theory}]\label{def:pure-lambda-calculus}
   We define the `pure' $ \lambda $-calculus $ \Lambda $ to be $ \Lambda(\emptyset) $.
@@
 
-\begin{example}
+\begin{example}[\coqident{AlgebraicTheories.Examples.FreeObjectTheory}{free_object_theory}, \coqident{AlgebraicTheories.Examples.FreeObjectTheory}{free_object_algebra_functor}]
   Take a category $ C $, with a forgetful functor $ G: C \to \SET $ and a free functor $ F: \SET \to C $.
@@
 One can wonder whether there also is a functor the other way, or whether $ \alpha $ is even an equivalence.
-This is hard to characterize precisely, but in algebra, there is a broad class of examples where the functor is an equivalence, so where $ C $ is equivalent to $ \Alg T $.
-That is probably why $ T $ is called an \textit{algebraic theory}.
+If $ \alpha $ is an equivalence, $ C $ is trivially an algebraic category, but the question for which algebraic categories $ \alpha $ is an equivalence is harder to answer.
 
-The idea is that if an object of $ C $ is a set, together with some operations between its elements, one can carefully choose some elements of $ T_0 $, $ T_1 $, $ T_2 $ etc., which act on an algebra like the specified operations.
+Of course, for many common categories in algebra, where an object of $ C $ is a set with some operations between its elements, one can carefully choose some elements of $ T_0 $, $ T_1 $, $ T_2 $ etc., which act on an algebra like the specified operations, which turns $ \alpha $ into an equivalence.
 
-\begin{example}\label{ex:free-monoid-theory}
+\begin{example}[\coqident{AlgebraicTheories.Examples.FreeMonoidTheory}{monoid_algebra_equivalence}]\label{ex:free-monoid-theory}
   For $ C $ the category of monoids, $ \alpha: C \to \Alg T $ is an adjoint equivalence.
@@
 \subsection{The terminal theory}
-\begin{example}
+\begin{example}[\coqident{AlgebraicTheories.Examples.OnePointTheory}{one_point_theory}]
   We can create a (somewhat trivial) algebraic theory $ T $ by taking $ T_n = \{ \star \} $, with projections $ x_i = \star $ and substitution $ \star \bullet \star = \star $.
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.Examples.OnePointTheory}{one_point_theory_algebra_is_trivial}]
   $ \{ \star \} $ is the only algebra of the terminal theory.
@@
 
-\begin{definition}\label{def:endomorphism-theory}
+\begin{definition}[\coqident{AlgebraicTheories.Examples.EndomorphismTheory}{endomorphism_algebraic_theory}]\label{def:endomorphism-theory}
   Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.Examples.EndomorphismTheory}{endomorphism_lambda_theory}]
   Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $.
@@
 \subsection{The theory algebra}
-\begin{example}\label{ex:theory-algebra}
+\begin{example}[\coqident{AlgebraicTheories.Examples.TheoryAlgebra}{theory_algebra}]\label{ex:theory-algebra}
   Let $ T $ be an algebraic theory and $ n $ a natural number.
@@
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.Examples.TheoryAlgebra}{theory_algebra_free}]
   Recall from \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $.
@@
 \subsection{The theory presheaf}
-\begin{example}
+\begin{example}[\coqident{AlgebraicTheories.Presheaves}{theory_presheaf}]
   Let $ T $ be an algebraic theory.
@@
 
-\begin{remark}\label{rem:presheaf-Yoneda}
+\begin{remark}[\coqident{AlgebraicTheories.RepresentationTheorem}{presheaf_to_L}]\label{rem:presheaf-Yoneda}
   Recall from \ref{lem:lawvere-presheaf} that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $.
@@
 
-\begin{example}[The `+l' presheaf]
+\begin{example}[\coqident{AlgebraicTheories.Examples.Plus1Presheaf}{plus_1_presheaf}][The `+l' presheaf]
   Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, l) $ with $ A(Q, l)_n = Q_{n + l} $ and, for $ q: A(Q, l)_m $ and $ f: T_n^m $, action
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.RepresentationTheorem}{theory_presheaf_exponentiable}]
   For all $ l $ and $ T $-presheaves $ Q $, $ A(Q, l) $ is the exponential object $ Q^{T^l} $.

### 2024-09-27 500-previous-work.tex
Write an introduction
Add code links to Chapter 5

@@
-\chapter{Previous work in categorical semantics}
+\chapter{Previous work in categorical semantics}\label{ch:previous-work}
 
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.CategoryOfRetracts}{R}]
   We define the category \index{R}$ \R $ as the Karoubi envelope $ \overline C_{L_0} $ of the one-point category based on the monoid of the $ \lambda $-terms without free variables under composition.
@@
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.CategoryOfRetracts}{R_ob_weq_R'}]
   Hyland instead defines $ \R $ as the Karoubi envelope $ \overline C_{L_1} $ (again, the construction using the idempotents) of the monoid $ (L_1, - \bullet (-)) $ with identity element $ x_{1, 1} $:
@@
 
-It turns out that this embeds $ \R $ as a full subcategory of $ \Pshf L $:
+It turns out that this is an embedding:
 \begin{lemma}
@@
 
-In the next chapter, the `universal object' $ U : \R $, given by the identity $ \lambda x_1, x_1 $, plays a major role.
-Note that for all $ A: \R $, we have morphisms $ A: \R(U, A) $ and $ A: \R(A, U) $, which exhibit $ A $ as a retract of $ U $.
+In the next chapter, the `universal object' $ U : \R $, given by the identity $ \lambda x_1, x_1 $ (\coqident{AlgebraicTheories.CategoryOfRetracts}{U}), plays a major role.
+Note that for all $ A: \R $, we have morphisms $ A: \R(U, A) $ and $ A: \R(A, U) $, which exhibit $ A $ as a retract of $ U $ (\coqident{AlgebraicTheories.CategoryOfRetracts}{R_retraction_is_retraction}).
 Also note that $ \varphi(U) = L $.
 
-Note that $ \R $ has many (isomorphic, but not equal for nontrivial $ L $) terminal objects, given by $ I_c := \lambda x_1, \iota_{0, 1}(c) : \R $ for any $ c: L_0 $.
+Note that $ \R $ has many (isomorphic, but not equal for nontrivial $ L $) terminal objects, given by $ I_c := \lambda x_1, \iota_{0, 1}(c) : \R $ for any $ c: L_0 $ (\coqident{AlgebraicTheories.CategoryOfRetracts}{R_terminal}).
 These are terminal because for $ f: A \to I_c $, we have $ f = I_c \circ f = I_c $.
@@
 
-We might wonder whether $ \R $ also has an initial object $ O $. However, for any $ c: L_0 $, we would have a constant morphism
-\[ I_c = \lambda x_1, \iota_{0, 1}(c) : \R(O, U), \]
+We might wonder whether $ \R $ also has an initial object $ O $. However, for all $ c: L_0 $, we would have a constant morphism to the universal object
+\[ \lambda x_1, \iota_{0, 1}(c) : \R(O, U), \]
 so if $ L $ is nontrivial, $ \R $ has no initial object.
 
-$ \R $ has binary products with projections and product morphisms
+$ \R $ has binary products with projections and product morphisms (\coqident{AlgebraicTheories.CategoryOfRetracts}{R_binproducts})
 \[ A_1 \times A_2 = \langle p_1, p_2 \rangle, \quad p_i = A_i \circ \pi_i \quad \text{and} \quad \langle f, g \rangle. \]
@@
 
-$ \R $ also has exponential objects
+$ \R $ also has exponential objects (\coqident{AlgebraicTheories.CategoryOfRetracts}{R_exponentials})
 \[ C^B = \lambda x_1, C \circ x_1 \circ B \]
@@
 Taylor notes (\autocite{taylor}, Section 1.5) that the objects in $ \R $ have very strong properties with respect to fixpoints.
-One of the properties also arises via Lawvere's fixed point theorem (\autocite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint.
+One of the properties also arises via Lawvere's fixed point theorem (\autocite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint (\coqident{AlgebraicTheories.CategoryOfRetracts}{fixpoint_is_fixpoint}).
 That is, there exists $ s: I \to B $ such that $ f \circ s = s $.
@@
 This question finds a partial answer in the following theorem, originally proved in a very syntactical way by Dana Scott (see \autocite{curry}, page 418).
-\begin{theorem}\label{thm:Scott}
+\begin{theorem}[\coqident{AlgebraicTheories.OriginalRepresentationTheorem}{representation_theorem_iso}]\label{thm:Scott}
   We can obtain every untyped $ \lambda $-calculus as the endomorphism theory of some object in some category.

### 2024-09-27 200-category-theory.tex
Make notation in category-theory more consistent

@@
 To summarize, we have an equivalence
-\[ (\SET \downarrow X)\left(f^*(\{ \star \}, \id{\{\star\}}), \left(\sum_{x : X} Y_x, \pi_1 \right) \right) \simeq (\SET \downarrow {\{\star\}})\left( (\{\star\}, \id{\{ \star \}}), \left( \prod_{x : X} Y_x, !
-\right) \right) \]
+\[ (\SET \downarrow X)\left(f^*(\{ \star \}, \id{\{\star\}}), (Y_x)_x \right) \simeq (\SET \downarrow {\{\star\}})\left( (\{\star\}, \id{\{ \star \}}), \left( \prod_{x : X} Y_x, ! \right) \right) \]
 for $ !
@@
 In $ \SET $, this is definitely possible, and from this, we get an equivalence again
-\[ \left(\SET \downarrow \sum_{x : X} Y_x \right)\left(f^*(X, \id X), (\sum_{x : X} \sum_{y : Y_x} Z_y, p) \right) \simeq (\SET \downarrow A)\left((X, \id X), \left(\sum_{x : X} \prod_{y : Y_x} Z_y, \pi_1\right)\right).
-\]
+\[ \left(\SET \downarrow \sum_{x : X} Y_x \right)\left(f^*(X, \id X), (Z_y)_{x, y} \right) \simeq (\SET \downarrow X)\left((X, \id X), \left(\prod_{y : Y_x} Z_y\right)_x\right). \]
 with $ p : \sum_{x : X} \sum_{y : Y_x} Z_y \to \sum_{x : X} Y_x $ defined as $ p(x, y, z) = (x, y) $.
@@
 Now we turn our attention to dependent sums.
-In $ \SET $, let $ (X_a)_a $ and $ (B_a)_a $ be two families over $ A $ and let $ ((Y_b)_{b : B_a})_{a : A} $ be a family of families.
-Let $ \alpha: \sum_{a : A} B_a \to A $ be the internal representation of $ (B_a)_a $.
-A family of maps $ f_a : (\sum_{b : B_a} Y_b)_a \to X_a $ consists of maps $ Y_b \to X_a $ for all $ b : B_a $, so these are maps $ f_b : Y_b \to X_{\alpha(b)} $.
+In $ \SET $, let $ (Y_x)_x $ and $ (Y^\prime_x)_x $ be two families over $ X $ and let $ ((Z_y)_{y : Y_x})_{x : X} $ be a family of families.
+Let $ f: \sum_{x : X} Y_x \to X $ be the internal representation of $ (Y_x)_x $.
+A family of maps $ g_x : (\sum_{y : Y_x} Z_y)_x \to Y^\prime_x $ consists of maps $ Z_y \to Y^\prime_x $ for all $ y : Y_x $, so these are maps $ g_y : Z_y \to Y^\prime_{f(y)} $.
 This gives an equivalence
-\[ (\SET \downarrow A)((\sum_{b : B_a} Y_b)_a, (X_a)_a) \simeq (\SET \downarrow (\sum_{a : A} B_a))((Y_b)_b, \alpha^*((X_a)_a)). \]
+\[ (\SET \downarrow X)\left(\left( \sum_{y : Y_x} Z_y \right)_x, (Y^\prime_x)_x \right) \simeq \left(\SET \downarrow \left(\sum_{x : X} Y_x \right) \right)((Z_y)_y, f^*((Y^\prime_x)_x)). \]
 This, again, suggests an adjunction which we will use as a definition.
 \begin{definition}
-  For a category $ C $ and a morphism $ \alpha: B \to A $, the \iindex{dependent sum} along $ \alpha $ is, if it exists, the left adjoint to the pullback functor:
-  \begin{center}
-    \begin{tikzcd}
-      (C \downarrow A) \arrow[r, shift right=2, "\alpha^*"'{name=B}] &
-      (C \downarrow B) \arrow[l, shift right=2, "\sum_\alpha"'{name=A}]
+  For a category $ C $ and a morphism $ f: Y \to X $, the \iindex{dependent sum} along $ f $ is, if it exists, the left adjoint to the pullback functor:
+  \begin{center}
+    \begin{tikzcd}
+      (C \downarrow X) \arrow[r, shift right=2, "f^*"'{name=B}] &
+      (C \downarrow Y) \arrow[l, shift right=2, "\sum_f"'{name=A}]
       \ar[from=A, to=B, symbol=\dashv]
@@
 \begin{lemma}\label{lem:sum-postcomposition}
-  Let $ \alpha : C(B, A) $ be a morphism in a category.
-If the pullback functor $ \alpha^*: (C \downarrow A) \to (C \downarrow B) $ exists, it has a left adjoint given by postcomposition with $ \alpha $.
-\end{lemma}
-\begin{proof}
-  For morphisms $ f: X \to A $, $ g: Y \to B $, the universal property of the pullback, with the following diagram
-  \begin{center}
-    \begin{tikzcd}
-      Y \arrow[r, dashed, "\varphi"'] \arrow[rr, "\psi", bend left] \arrow[dr, "g"'] & \alpha^* X \arrow[d, "\alpha^* f"'] \arrow[r] \arrow[rd, phantom, "\lrcorner", very near start] & X \arrow[d, "f"]\\
-      & B \arrow[r, "\alpha"'] & A
-    \end{tikzcd}
-  \end{center}
-  gives an equivalence between morphisms $ \varphi: Y \to \alpha^* X $ that commute with $ g $ and $ \alpha^* f $, and morphisms $ \psi: Y \to X $ that commute with $ g $, $ f $ and $ \alpha $.
-In other words:
-  \[ (C \downarrow A)(g \cdot \alpha, f) \simeq (C \downarrow B)(g, \alpha^*(f)), \]
+  Let $ f : C(Y, X) $ be a morphism in a category. If the pullback functor $ f^*: (C \downarrow X) \to (C \downarrow Y) $ exists, it has a left adjoint given by postcomposition with $ f $.
+\end{lemma}
+\begin{proof}
+  For morphisms $ g: Z \to X $, $ h: W \to Y $, the universal property of the pullback, with the following diagram
+  \begin{center}
+    \begin{tikzcd}
+      W \arrow[r, dashed, "\varphi"'] \arrow[rr, "\psi", bend left] \arrow[dr, "h"'] & f^* Z \arrow[d, "f^* g"'] \arrow[r] \arrow[rd, phantom, "\lrcorner", very near start] & Z \arrow[d, "g"]\\
+      & Y \arrow[r, "f"'] & X
+    \end{tikzcd}
+  \end{center}
+  gives an equivalence between morphisms $ \varphi: W \to f^* Z $ that commute with $ h $ and $ f^* g $, and morphisms $ \psi: W \to Z $ that commute with $ h $, $ g $ and $ f $. In other words:
+  \[ (C \downarrow X)(h \cdot f, g) \simeq (C \downarrow Y)(h, f^*(g)), \]
   which shows the adjunction.
@@
 
-Now, let $ f : X \to A $ be the internal representation of an indexed family $ (X_a)_a $ and let $ \alpha : A \to I $ be the terminal projection.
-We have $ \sum_{a : A} X_a = f \circ \alpha : X \to I $.
-By the equivalence between $ (C \downarrow I) $ and $ C $, we see that the dependent sum of the family $ (X_a)_a $ is exactly $ X $.
+Now, let $ g : Y \to X $ be the internal representation of an indexed family $ (Y_x)_x $ and let $ f : X \to I $ be the terminal projection.
+We have $ \sum_{x : X} Y_x = g \cdot f : Y \to I $.
+By the equivalence between $ (C \downarrow I) $ and $ C $, we see that the dependent sum of the family $ (Y_x)_x $ is exactly $ Y $.
 Therefore, our attention is mainly focused on the dependent product.
@@
 \begin{definition}
-  A \index{cartesian closed!locally}\textit{locally cartesian closed} category is a category $ C $ with pullbacks such that each pullback functor $ \alpha^* $ has a right adjoint.
+  A \index{cartesian closed!locally}\textit{locally cartesian closed} category is a category $ C $ with pullbacks such that each pullback functor $ f^* $ has a right adjoint.
 \end{definition}
@@
 \begin{lemma}\label{lem:locally-cartesian-closed}
-  A category $ C $ is locally cartesian closed iff $ (C \downarrow A) $ is cartesian closed for each $ A : C $.
+  A category $ C $ is locally cartesian closed iff $ (C \downarrow X) $ is cartesian closed for each $ X : C $.
 \end{lemma}
@@
       Y \times Z \arrow[d, "p_1"] \arrow[r, "f \times \id Z"] & X \times Z \arrow[d, "p_1"] \arrow[r, "p_2"] & Z \arrow[d, "!"]\\
-      Y \arrow[r, "f"] & X \arrow [r, "!"] & T
+      Y \arrow[r, "f"] & X \arrow [r, "!"] & I
     \end{tikzcd}
@@
 \begin{lemma}\label{lem:constant-dependent-product}
-  For $ W, X, Z : C $ and $ p_1 : X \times Z \to X $,
-  \[ \prod_{p_1} \Delta_{X \times Z} W \cong \Delta_X W^Z \]
-\end{lemma}
-\begin{proof}
-  First of all, note that $ (C \downarrow X \times Z) \cong ((C \downarrow X) \downarrow \Delta_X Z) $.
-Also note that the composite morphism $ (X \times Z) \times W \xrightarrow{p_1} X \times Z \xrightarrow{p_1} X $ is the element $ \Delta_X (W \times Z) : (C \downarrow X) $.
-
-  By Proposition 1.34 in \autocite{freyd}, $ \prod_{p_1} \Delta_{X \times Z} W $ is given as the following pullback:
-  \begin{center}
-    \begin{tikzcd}
-      \prod_{p_1} \Delta_{X \times Z} W \arrow[r] \arrow[d] & (\Delta_X Z \times W)^{\Delta_X Z} \arrow[d, "(\Delta_X p_1)^{\Delta_X Z}"]\\
-      X \arrow[r] & (\Delta_X Z)^{\Delta_X Z}
-    \end{tikzcd}
-  \end{center}
-
-  By Lemma \ref{lem:delta-exponentials}, $ \Delta_X $ preserves exponential objects, so the morphism on the right is $ \Delta_X p_1^Z : (C \downarrow X)(\Delta_X (Z \times W)^Z, \Delta_X Z^Z) $.
-However, we have an isomorphism $ (Z \times W)^Z \cong Z^Z \times Z^W $, and then the morphism on the right becomes
-  \[ \Delta_X p_1 : (C \downarrow X)(\Delta_X(Z^Z \times Z^W), \Delta_X Z^Z) \]
-  We also have an isomorphism $ X \cong \Delta_X T $. Then by Lemma \ref{lem:delta-limits} and Remark \ref{rem:pullback-of-projection}, the pullback of this diagram is $ \Delta_X W^Z $:
-  \begin{center}
-    \begin{tikzcd}
-      \Delta_X W^Z \arrow[r] \arrow[d] & \Delta_X (Z^Z \times W^Z) \arrow[d, "\Delta_X p_1"]\\
-      \Delta_X T \arrow[r] & \Delta_X Z^Z
+  For $ Z, X, Y : C $ and $ p_1 : X \times Y \to X $,
+  \[ \prod_{p_1} \Delta_{X \times Y} Z \cong \Delta_X Z^Y \]
+\end{lemma}
+\begin{proof}
+  First of all, note that $ (C \downarrow X \times Y) \cong ((C \downarrow X) \downarrow \Delta_X Y) $.
+Also note that the composite morphism $ (X \times Y) \times Z \xrightarrow{p_1} X \times Y \xrightarrow{p_1} X $ is the element $ \Delta_X (Z \times Y) : (C \downarrow X) $.
+
+  By Proposition 1.34 in \autocite{freyd}, $ \prod_{p_1} \Delta_{X \times Y} Z $ is given as the following pullback:
+  \begin{center}
+    \begin{tikzcd}
+      \prod_{p_1} \Delta_{X \times Y} Z \arrow[r] \arrow[d] & (\Delta_X Y \times Z)^{\Delta_X Y} \arrow[d, "(\Delta_X p_1)^{\Delta_X Y}"]\\
+      X \arrow[r] & (\Delta_X Y)^{\Delta_X Y}
+    \end{tikzcd}
+  \end{center}
+
+  By Lemma \ref{lem:delta-exponentials}, $ \Delta_X $ preserves exponential objects, so the morphism on the right is $ \Delta_X p_1^Y : (C \downarrow X)(\Delta_X (Y \times Z)^Y, \Delta_X Y^Y) $.
+However, we have an isomorphism $ (Y \times Z)^Y \cong Y^Y \times Y^Z $, and then the morphism on the right becomes
+  \[ \Delta_X p_1 : (C \downarrow X)(\Delta_X(Y^Y \times Y^Z), \Delta_X Y^Y) \]
+  We also have an isomorphism $ X \cong \Delta_X I $. Then by Lemma \ref{lem:delta-limits} and Remark \ref{rem:pullback-of-projection}, the pullback of this diagram is $ \Delta_X Z^Y $:
+  \begin{center}
+    \begin{tikzcd}
+      \Delta_X Z^Y \arrow[r] \arrow[d] & \Delta_X (Y^Y \times Z^Y) \arrow[d, "\Delta_X p_1"]\\
+      \Delta_X I \arrow[r] & \Delta_X Y^Y
     \end{tikzcd}
@@
 \begin{definition}
-  If a category has an object $ t $, such that there is a (not necessarily unique) morphism to it from every other object in the category, $ t $ is said to be a \iindex{weakly terminal object}.
-\end{definition}
-
-\begin{definition}
-  Let $ C $ be a category with terminal object $ t $. For an object $ c: C $, a \iindex{global element} of $ c $ is a morphism $ f: C(t, c) $.
+  If a category has an object $ I $, such that there is a (not necessarily unique) morphism to it from every other object in the category, $ I $ is said to be a \iindex{weakly terminal object}.
+\end{definition}
+
+\begin{definition}
+  Let $ C $ be a category with terminal object $ I $. For an object $ X: C $, a \iindex{global element} of $ X $ is a morphism $ f: C(I, X) $.
 \end{definition}

### 2024-09-28 100-introduction.tex
Add a lot of references to the code

--- 2024-09-26 100-introduction.tex
@@
 Lastly, the formalization of part of the material is discussed in Chapter \ref{ch:the-formalization}.
+
+Note that throughout this document, links are included to \href{https://arnoudvanderleer.github.io/cs-masters-thesis/toc.html}{\nolinkurl{documentation}} of the corresponding formalized material.
+The documentation refers to the state of \href{https://github.com/UniMath/UniMath/tree/5eb5c8958c4dddd4219f895bf7bc51547395522d}{\nolinkurl{the UniMath repository}} at commit number \texttt{5eb5c8958c4dddd4219f895bf7bc51547395522d}.

### 2024-09-28 200-category-theory.tex
Add a lot of references to the code

@@
 
-There is also the dual concept of a universal arrow $ (X, f) $ from a functor $ F $ to an object $ Y: C $. Its universal property can be summarized in the following diagram:
+There is also the dual concept: a universal arrow $ (X, f) $ from a functor $ F $ to an object $ Y: C $. Its universal property can be summarized in the following diagram:
 \begin{center}
@@
 
-\begin{lemma}\label{lem:Yoneda-preserves-exponentials}
+\begin{lemma}[\coqident{CategoryTheory.YonedaExponentials}{yoneda_preserves_exponentials}]\label{lem:Yoneda-preserves-exponentials}
   The Yoneda embedding preserves exponentials.
@@
 
-\begin{lemma}\label{lem:lan-precomp-iso}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.SurjectivePrecomposition}{pre_comp_split_essentially_surjective}]\label{lem:lan-precomp-iso}
   If $ F : A \to B $ is a fully faithful functor, and $ C $ is a category with colimits, $ \eta: \id{[A, C]} \Rightarrow \Lan F {} \bullet F_* $ is a natural isomorphism.
@@
 Take a monoid $ M $.
-\begin{definition}
+\begin{definition}[\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_to_category_ob}]
   We can construct a category $ C_M $ with $ C_{M0} = \{ \star \} $, $ C_M(\star, \star) = M $.
@@
 
-\begin{remark}
+\begin{remark}[\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_to_category}]
   Actually, we have a functor from the category of monoids to the category of setcategories (categories whose object type is a set).
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_action}]
   A \textit{right monoid action}\index{monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, m^\prime: M $,
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_action_morphism}]
   A \textit{morphism}\index{monoid action!morphism} between sets $ X $ and $ Y $ with a right $ M $-action is an $ M $-equivariant function $ f: X \to Y $: a function such that $ f(xm) = f(x)m $ for all $ x: X $ and $ m: M $.
@@
 
-These, together with the identity and composition from $ \SET $, constitute a category \iindex{$ \RAct M $} of right $ M $-actions.
-
-\begin{lemma}
+These, together with the identity and composition from $ \SET $, constitute a category \iindex{$ \RAct M $} of right $ M $-actions (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_action_cat}).
+
+\begin{lemma}[\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_presheaf_action_equivalence}]
   Presheaves on $ C_M $ are equivalent to sets with a right $ M $-action.
@@
 
-Note that the initial set with $ M $-action is $ \{ \star \} $, with action $ \star m = \star $.
-
-\begin{lemma}\label{lem:global-action-elements}
+Note that the terminal set with $ M $-action is $ \{ \star \} $, with action $ \star m = \star $ (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{terminal_monoid_action}).
+
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_action_global_element_fixpoint_iso}]\label{lem:global-action-elements}
   The global elements of a set with right $ M $-action correspond to the elements that are invariant under the $ M $-action.
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{is_exponentiable_monoid_action}]
   The category $ C $ of sets with an $ M $-action has exponentials.
@@
 
-\begin{definition}
-  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot_M n $ for $ m: U_M $ and $ n: M $.
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_monoid_action}]
+  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot n $ for $ m: U_M $ and $ n: M $. Note that this is the Yoneda embedding of the object $ \star : C_M $.
 \end{definition}
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_restriction_functor}]
   We get a \iindex{restriction of scalars} functor $ \varphi^* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
@@
 
-\begin{lemma}\label{lem:scalar-extension}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_functor}]\label{lem:scalar-extension}
   We get an \iindex{extension of scalars} functor $ \varphi_* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
@@
 
-\begin{lemma}\label{lem:scalar-extension-monoid-monoid-action}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_preserves_monoid_monoid_action}]\label{lem:scalar-extension-monoid-monoid-action}
   For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi_*(U_M) \cong U_{M^\prime} $.
@@
 
-\begin{lemma}\label{lem:scalar-extension-terminal}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_preserves_terminal}]\label{lem:scalar-extension-terminal}
   Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi_*(I_M) \cong I_{M^\prime} $.
@@
 
-\begin{lemma}\label{lem:scalar-extension-product}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_preserves_binproducts}]\label{lem:scalar-extension-product}
   Suppose that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object for all $ m^\prime_1, m^\prime_2: M^\prime $.
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}]
   We define the category $ \overline C $.
@@
 
-\begin{definition}
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_inclusion}]
   We have an embedding $ \iota_C: C \to \overline C $, sending $ c: C $ to $ (c, \id{c}) $ and $ f: C(c, d) $ to $ f $.
@@
 
-\begin{lemma}\label{lem:karoubi-is-retract}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_is_retract}]\label{lem:karoubi-is-retract}
   Every object $ c: \overline C $ is a retract of $ \iota_C(c_0) $ for some $ c_0: C $.
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_idempotent_splits}]
   In $ \overline C $, every idempotent splits.
@@
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_inclusion_fully_faithful}]
   Note that $ \iota_C $ is fully faithful, since
@@
 
-\begin{remark}\label{rem:retract-coequalizer}
+\begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_equalizer}, \coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_coequalizer}]\label{rem:retract-coequalizer}
   Let $ D $ be a category and suppose that we have two objects $ d, d^\prime : D $ and a retraction
@@
 
-\begin{definition}\label{def:karoubi'}
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope'}]\label{def:karoubi'}
   We define the category $ \tilde C $ in which every object is a presheaf $ F : P C $, together with an object $ X : C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo (X) $.
@@
 This gives us what we need to translate the classical equivalence between the two notions of Karoubi envelope to type theory:
-\begin{lemma}\label{lem:karoubi-equivalence}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_is_retract}]\label{lem:karoubi-equivalence}
   We have an adjoint equivalence $ \overline C \xrightarrow \sim \tilde C $.
@@
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_univalence}]
   The fully faithful embedding $ i_C : C \hookrightarrow \overline C $ induces equivalences $ (X \cong Y) \simeq (\iota_C(X) \cong \iota_C(Y)) $.
@@
 For convenience, the lemma below works very abstractly with pointwise left Kan extension using colimits, but one could also prove this using just (co)equalizers (or right Kan extension using limits).
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_pullback_equivalence}]
   Let $ D $ be a category with colimits. We have an adjoint equivalence between $ [C, D] $ and $ [\overline C, D] $.
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{opp_karoubi}]
   The formation of the opposite category commutes with the formation of the Karoubi envelope.

### 2024-09-28 300-univalent-foundations.tex
Write an introduction
Add a lot of references to the code

@@
-\chapter{Univalent Foundations}
+\chapter{Univalent Foundations}\label{ch:univalent-foundations}
 
@@
 
-\begin{remark}
+\begin{remark}[\coqident{Bicategories.RezkCompletions.Uniqueness}{rezk_completion_unique}]
   We can call it \textit{the} Rezk completion, since it is unique: Precomposition with the weak equivalence $ \iota: C \hookrightarrow D $ gives an adjoint equivalence on the functor categories $ [D, E] \simeq [C, E] $ for any univalent category $ E $.

### 2024-09-28 400-algebraic-structures.tex
Add a lot of references to the code

@@
   In the same way, the category of algebraic theories has all limits.
+\end{remark}
+
+\begin{remark}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{is_univalent_algebraic_theory_cat}]
+  Since an isomorphism of algebraic theories $ S \simeq T $ consists of pointwise isomorphisms $ f_n: S_n \simeq T_n $ that respect the variables and substitution, the category of algebraic theories is univalent.
 \end{remark}
@@
   The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying sets.
+\end{remark}
+
+\begin{remark}[\coqident{AlgebraicTheories.AlgebraCategory}{is_univalent_algebra_cat}]
+  Note that just like with algebraic theories, the category of $ T $-algebras is univalent because its (iso)morphisms preserve $ \bullet $.
 \end{remark}
@@
 
+\begin{remark}[\coqident{AlgebraicTheories.AlgebraCategory}{is_univalent_algebra_cat}]
+  Note that just like with algebraic theories and algebras, the category of $ T $-presheaves is univalent because its (iso)morphisms preserve $ \bullet $.
+\end{remark}
+
 An analogue to Lemma \ref{lem:algebra-fibration} shows that, like with algebras, the total category of presheaves is fibered over the category of algebraic theories (\coqident{AlgebraicTheories.PresheafCategory}{presheaf_fibration}).
@@
   The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories.
+\end{remark}
+
+\begin{remark}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{is_univalent_lambda_theory_cat}]
+  Note that just like with algebraic theories, the category of $ \lambda $-theories is univalent because its (iso)morphisms preserve $ \rho $ and $ \lambda $.
 \end{remark}

### 2024-09-28 600-paper.tex
Write an introduction
Add a lot of references to the code

--- 2024-09-11 report/src/paper.tex
@@
-\chapter{Hyland's paper}
+\chapter{Hyland's paper}\label{ch:the-paper}
 
@@
 Now, Scott's representation theorem, which asks whether we can represent any $ \lambda $-theory as the endomorphism theory of some reflexive object in some cartesian closed category, can be answered using the presheaf category.
-\begin{theorem}\label{thm:representation-theorem}
+\begin{theorem}[\coqident{AlgebraicTheories.RepresentationTheorem}{representation_theorem_iso}]\label{thm:representation-theorem}
   Any $ \lambda $-theory $ L $ is isomorphic to the endomorphism $ \lambda $-theory $ E_{\Pshf L}(L) $, with $ L $ viewed as a presheaf.
@@
 
-\begin{lemma}\label{lem:equivalent-presheaf-cats}
+\begin{lemma}[\coqident{CategoryTheory.Equivalences.EquivalenceFromComp}{adjoint_equivalence_1_from_comp}]\label{lem:equivalent-presheaf-cats}
   The precomposition functors $ i_* $ and $ j_* $ are adjoint equivalences.
@@
 
-\section{Locally cartesian closedness of the category of retracts}
+\section{Locally cartesian closedness of the category of retracts}\label{sec:locally-cartesian-closed}
 
@@
 
-\begin{definition}[The monoid of a $ \Lambda $-algebra]
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.AlgebraToTheory}{lambda_algebra_monoid}]
   We make $ A_1 $, the `functional elements' of $ A $, into a monoid under composition $ \circ $ with unit $ \mathbf 1_1 $. The fact that this is a monoid follows from the remarks above.
@@
 
-\begin{lemma}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.AlgebraToTheory}{universal_monoid_exponential_iso}]
   $ A_2 $ is isomorphic to the exponential object $ U_A^{U_A} $ in $ \RAct{A_1} $.
@@
 
-\begin{definition}[Construction of the $ \lambda $-theory]
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.AlgebraToTheory}{lambda_algebra_theory}]\label{def:lambda-algebra-to-lambda-theory}
   Recall that $ A_2 \subseteq U_A $, and that we have a retraction $ a \mapsto \mathbf 1_2 \circ a : U_A \to A_2 $.
@@
 
-(\TODO Is it maybe a good idea to move the coproducts and theory of extensions to chapter 3?)
-
 \begin{lemma}\label{lem:algebra-coproducts}
@@
 
-  Then it becomes clear what the action of $ T $ will be on $ A + B $, although the precise definition looks a bit complex because we have to juggle a bit with the variables in the different $ T_{m + n} $.
+  Then it becomes clear what the action of $ T $ will be on $ A + B $, although the precise definition looks complicated because we have to juggle a bit with the variables in the different $ T_{m + n} $.
 For $ s : T_l $, $ t_i : T_{m_i + n_i} $, $ a_i : A^{m_i} $ and $ b_i : B^{n_i} $, define the disjoint embeddings
@@
 
-\begin{definition}[Theory of extensions]
+\begin{definition}
   Let $ T $ be an algebraic theory and $ A $ a $ T $-algebra.
@@
 
-\begin{remark}
+\begin{remark}[\coqident{AlgebraicTheories.Examples.ExtensionsTheory}{extensions_theory}]
   We can turn the map $ A \mapsto T_A $ into a functor $ T_- : \Alg T \to \AlgTh $. For a morphism $ f: \Alg T(A, B) $, we get maps
@@
 The following result explains why we are interested in the theory of extensions:
-\begin{lemma}\label{lem:extensions-algebra-coslice}
+\begin{lemma}[\coqident{AlgebraicTheories.Examples.ExtensionsTheory}{algebra_coslice_equivalence}]\label{lem:extensions-algebra-coslice}
   For $ T $ an algebraic theory and $ A $ a $ T $-algebra, we have an adjoint equivalence $ \Alg{T_A} \cong (A \downarrow \Alg T) $ between algebras for $ T_A $ and the coslice category under $ A $.
@@
 \begin{example}
-  Take $ T_n = Z[X_1, \dots, X_n] $, the polynomial rings in $ n $ variables.
-$ T $-algebras correspond to commutative rings, so we can call $ T $ `the theory of commutative rings'.
+  Take $ T_n = Z[X_1, \dots, X_n] $, the polynomial ring (the free commutative ring) in $ n $ variables.
+$ T $-algebras are equivalent to commutative rings, so we can call $ T $ `the theory of commutative rings'.
 Now, for a commutative ring $ R $, $ \Alg{T_R} $ is equivalent to the coslice category $ (R \downarrow \Alg T) $, which is the category of $ R $-algebras.
@@
 
-\begin{lemma}\label{lem:factor-through-extensions}
-  Any algebraic theory morphism $ f: \AlgTh(S, T) $ factorizes through the embedding of $ S $ into the theory of extensions of the pullback of the algebra $ T_0 $:
+\begin{lemma}[\coqident{AlgebraicTheories.Examples.ExtensionsTheory}{factorization}]\label{lem:factor-through-extensions}
+  Any algebraic theory morphism $ f: \AlgTh(S, T) $ factors through the embedding of $ S $ into the theory of extensions of the pullback of the algebra $ T_0 $:
   \begin{center}

### 2024-09-28 700-formalization.tex
Add a lot of references to the code

@@
 % FreeMonoidTheory.v FreeObjectTheory.v
-  \item The `free object' algebraic theory with a functor from $ C $ to its algebras.
-Also the equivalence between the `free monoid' algebraic theory $ T $, together with a proof that the functor from monoids to $ T $-algebras is an equivalence.
+  \item The `free object' algebraic theory $ T $ with a functor from $ C $ to $ \Alg T $.
+Also, for the special case where $ C $ is the category of monoids, a proof that this functor $ C \to \Alg T $ is an equivalence.
 % EndomorphismTheory.v
@@
 \begin{itemize}
-  \item Univalence of the Sigma displayed category.
-  \item The Sigma displayed category creates limits.
+  \item Univalence of the Sigma displayed category (\coqident{CategoryTheory.DisplayedCats.Examples.Sigma}{is_univalent_sigma_disp}).
+  \item The Sigma displayed category creates limits (\coqident{CategoryTheory.DisplayedCats.Examples.Sigma}{creates_limits_sigma_disp_cat}).
   \item The definitions $ \overline C $ and $ \hat C $ for the Karoubi envelope and their preliminaries.
@@
   \item If $ F : C \to C^\prime $ is a fully faithful functor, and $ D $ is a category with colimits, then the precomposition functor $ F \bullet - : [C^\prime, D] \to [C, D] $ is split essentially surjective.
-  A precomposition functor is equivalent if ...
   \item A proof of a generalized version of Lemma \ref{lem:equivalent-presheaf-cats}, showing that if $ F : C \to C^\prime $ is a functor, if $ F^\prime : C^\prime \to C^{\prime \prime} $ is a fully faithful functor, if $ D $ is a category with colimits and if the precomposition $ (F \bullet F^\prime) \bullet - : [C^{\prime \prime}, D] \to [C, D] $ is an adjoint equivalence, then $ F^\prime \bullet - $ and $ F^\prime \bullet - $ are adjoint equivalences too.
@@
 % IndexedSetCategory.v
-  \item The univalent category $ \SET^A $ of indexed sets $ (X_a)_a $ over a type $ A $, which can be defined formally as
+  \item The univalent category $ \SET^A $ of indexed sets $ (X_a)_a $ over a type $ A $ (\coqident{AlgebraicTheories.IndexedSetCategory}{is_univalent_indexed_set_cat}, \coqident{AlgebraicTheories.IndexedSetCategory}{limits_indexed_set_cat}), which can be defined formally as
   \[ \SET^A_0 = (A \to \SET) \quad \text{and} \quad \SET^A(X, Y) = \prod_a X_a \to Y_a. \]

### 2024-09-28 800-conclusion.tex
Add a lot of references to the code

@@
 
-We also saw how Paul Taylor shows that Scott's category of retracts is cartesian closed, relative to some class of display maps, and that Hyland gives an interesting new proof of this, using the pre-established fact that the presheaf is locally cartesian closed.
+We also saw how Paul Taylor shows that Scott's category of retracts is cartesian closed, relative to some class of display maps, and that Hyland gives an interesting new proof of this, using the pre-established fact that the presheaf category is locally cartesian closed.
 Here it was interesting to note that Taylor's and Hyland's proofs are about the same category in classical mathematics, but that these categories become nonequivalent in univalent foundations, one being the Rezk completion of the other.
@@
 As we saw, there are two ways to study the $ \lambda $-calculus using tools from universal algebra: both via $ \lambda $-theories and $ \Lambda $-algebras.
-We saw that Hyland gives an equivalence between these two in his Fundamental Theorem of the $ \lambda $-calculus, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, and sending a $ \Lambda $-algebra $ A $ to its theory of extensions $ \Lambda_A $.
-We also showed a couple of variations on the proof of this fundamental theorem, exhibiting multiple equivalent ways to construct a $ \lambda $-theory from a $ \Lambda $-algebra.
+We saw that Hyland gives an equivalence between these two in his Fundamental Theorem of the $ \lambda $-calculus, where part of his construction again uses a presheaf category, $ \RAct{A_1} $, parallel to his proof of Scott's representation theorem.
+The equivalence sends a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $ and sends a $ \Lambda $-algebra $ A $ to its theory of extensions $ \Lambda_A $.
+We also saw a couple of variations on the proof of this fundamental theorem, exhibiting multiple equivalent ways to construct a $ \lambda $-theory from a $ \Lambda $-algebra.
 

### 2024-09-28 910-alternative-definitions.tex
Add a lot of references to the code

--- 2024-06-07 report/src/alternative-definitions.tex
@@
 \begin{definition}
-  An \iindex{algebraic theory} as presented in \autocite{algebaric-theories-2010} is a small category with finite products.
+  An \iindex{algebraic theory} as presented in \autocite{algebraic-theories-2010} is a small category with finite products.
 \end{definition}
@@
 
-\begin{lemma}\label{lem:lawvere-clone}
+\begin{lemma}[One direction: \coqident{AlgebraicTheories.AlgebraicTheoryToLawvereTheory}{algebraic_theory_to_lawvere}]\label{lem:lawvere-clone}
   There is an equivalence between abstract clones and Lawvere theories.
@@
 
-\begin{lemma}\label{lem:lawvere-presheaf}
+\begin{lemma}[\coqident{AlgebraicTheories.AlgebraicTheoryToLawvereTheory}{algebraic_presheaf_weq_lawere_presheaf}]\label{lem:lawvere-presheaf}
   Let $ C $ be an abstract clone, and $ L $ be its associated Lawvere theory by the equivalence given above. A $ C $-presheaf is equivalent to a presheaf over $ L $.

### 2024-09-28 200-category-theory.tex
Improve notation in Chapter 2

@@
 \section{Notation}
-Throughout this thesis, an object $ X $ in a category $ C $ will be denoted by $ X : C $.
-A morphism $ f $ between objects $ X $ and $ Y $ in a category $ C $ will be denoted by $ f: C(X, Y) $ or sometimes $ f: X \to Y $.
-Composition of morphisms $ f: C(X, Y) $ and $ g: C(Y, Z) $ will be denoted by $ f \cdot g $.
-And composition of functors $ F: A \to B $ and $ G: B \to C $ will be denoted by $ F \bullet G $.
+Throughout this thesis, objects of a homotopy set, for example morphisms, will usually be denoted with lowercase letters like $ f, g, h $ and sometimes with greek letters like $ \epsilon, \eta, \varphi, \psi $.
+Objects of a homotopy $ 1 $-type, like objects in a category, will usually be denoted with capital letters like $ X, Y, Z $.
+Lastly, (displayed) (bi)categories themselves will usually be denoted with boldface capital letters like $ \SET $ or $ \D $.
+
+Throughout this thesis, an object $ X $ in a category $ \C $ will be denoted by $ X : \C $.
+A morphism $ f $ between objects $ X $ and $ Y $ in a category $ \C $ will be denoted by $ f: \C(X, Y) $ or sometimes $ f: X \to Y $.
+Composition of morphisms $ f: \C(X, Y) $ and $ g: \C(Y, Z) $ will be denoted by $ f \cdot g $.
+And composition of functors $ F: \A \to \B $ and $ G: \B \to \C $ will be denoted by $ F \bullet G $.
 
@@
 \begin{definition}
-  A \iindex{universal arrow} from an object $ X: D $ to a functor $ F: C \to D $ consists of an object $ Y: C $ and a morphism $ f: D(X, F(Y)) $ such that for every similar pair $ (Y^\prime, f^\prime) $, $ f^\prime $ factors uniquely as $ f \cdot F(g) $ for some $ g: C(Y, Y^\prime) $:
+  A \iindex{universal arrow} from an object $ X: \D $ to a functor $ F: \C \to \D $ consists of an object $ Y: \C $ and a morphism $ f: \D(X, F(Y)) $ such that for every similar pair $ (Y^\prime, f^\prime) $, $ f^\prime $ factors uniquely as $ f \cdot F(g) $ for some $ g: \C(Y, Y^\prime) $:
   \begin{center}
@@
 \begin{lemma}
-  Let $ F: C \to D $ be a functor and $ X: D $ an object. An object $ Y: C $ and an arrow $ f: D(X, F(Y)) $ form a universal arrow from $ X $ to $ F $ if and only if the function
-  \[ (g \mapsto f \cdot F(g)) : C(Y, x) \cong D(X, F(x)) \]
+  Let $ F: \C \to \D $ be a functor and $ X: \D $ an object. An object $ Y: \C $ and an arrow $ f: \D(X, F(Y)) $ form a universal arrow from $ X $ to $ F $ if and only if the function
+  \[ (g \mapsto f \cdot F(g)) : \C(Y, x) \cong \D(X, F(x)) \]
   is a bijection.
 
-  Conversely, for all $ Y: C $ and $ X: D $, every bijection
-  \[ C(Y, Z) \cong D(X, F(Z)) \]
-  that is natural in $ Z $ arises in this way from some universal arrow $ f: D(X, F(Y)) $.
+  Conversely, for all $ Y: \C $ and $ X: \D $, every bijection
+  \[ \C(Y, Z) \cong \D(X, F(Z)) \]
+  that is natural in $ Z $ arises in this way from some universal arrow $ f: \D(X, F(Y)) $.
 \end{lemma}
@@
 
-There is also the dual concept: a universal arrow $ (X, f) $ from a functor $ F $ to an object $ Y: C $. Its universal property can be summarized in the following diagram:
+There is also the dual concept: a universal arrow $ (X, f) $ from a functor $ F $ to an object $ Y: \C $. Its universal property can be summarized in the following diagram:
 \begin{center}
@@
   \begin{tikzcd}
-    D \arrow[r, bend right, "R"'{name=R}] & C \arrow[l, bend right, "L"'{name=L}]
+    \D \arrow[r, bend right, "R"'{name=R}] & \C \arrow[l, bend right, "L"'{name=L}]
   \end{tikzcd}
@@
 with natural transformations (the unit and counit)
-\[ \eta: \id C \Rightarrow L \bullet R \quad \text{and} \quad \epsilon: R \bullet L \Rightarrow \id D \]
+\[ \eta: \id \C \Rightarrow L \bullet R \quad \text{and} \quad \epsilon: R \bullet L \Rightarrow \id \D \]
 such that the diagrams
@@
 An alternative characterization (see \autocite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
-\[ \varphi: D(L(X), Y) \xrightarrow{\sim} C(X, R(Y)). \]
-Naturality means that for all $ f: C(X^\prime, X) $, $ g: D(Y, Y^\prime) $ and $ h: D(L(X), Y) $,
+\[ \varphi: \D(L(X), Y) \xrightarrow{\sim} \C(X, R(Y)). \]
+Naturality means that for all $ f: \C(X^\prime, X) $, $ g: \D(Y, Y^\prime) $ and $ h: \D(L(X), Y) $,
 \[ \varphi(L(f) \cdot h \cdot g) = f \cdot \varphi(h) \cdot R(g). \]
@@
 \begin{lemma}
-  One can construct an adjunction $ (L, R, \eta, \epsilon) $ as above from only the functor $ L: C \to D $ and, for each $ X: C $, a universal arrow $ (R(X), \epsilon_X) $ from $ L $ to $ X $.
+  One can construct an adjunction $ (L, R, \eta, \epsilon) $ as above from only the functor $ L: \C \to \D $ and, for each $ X: \C $, a universal arrow $ (R(X), \epsilon_X) $ from $ L $ to $ X $.
 \end{lemma}
@@
 \begin{definition}\label{def:equivalence-of-categories}
-  An \iindex{adjoint equivalence} between categories $ C $ and $ D $ is a pair of adjoint functors $ L \dashv R $ like above such that the unit $ \eta: \id{C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{D} $ are isomorphisms of functors.
+  An \iindex{adjoint equivalence} between categories $ \C $ and $ \D $ is a pair of adjoint functors $ L \dashv R $ like above such that the unit $ \eta: \id{\C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{\D} $ are isomorphisms of functors.
 \end{definition}
@@
 \begin{definition}
-  A functor $ F: C \to D $ is called a \iindex{weak equivalence} if it is essentially surjective and fully faithful.
+  A functor $ F: \C \to \D $ is called a \iindex{weak equivalence} if it is essentially surjective and fully faithful.
 \end{definition}
@@
 \begin{definition}
-  A category $ C $ has \textit{exponential objects}\index{exponential objects} (or \textit{exponentials}) if for all $ X: C $, the functor $ X^\prime \mapsto X^\prime \times X $ has a right adjoint, which we denote $ Y \mapsto Y^X $.
-\end{definition}
-
-\begin{remark}
-  It is actually very well possible that a category does not have all exponentials, but it has some objects $ X, Y, Y^X: C $ with a bijection
-  \[ C(X^\prime \times X, Y) \cong C(X^\prime, Y^X) \]
+  A category $ \C $ has \textit{exponential objects}\index{exponential objects} (or \textit{exponentials}) if for all $ X: \C $, the functor $ X^\prime \mapsto X^\prime \times X $ has a right adjoint, which we denote $ Y \mapsto Y^X $.
+\end{definition}
+
+\begin{remark}
+  It is actually very well possible that a category does not have all exponentials, but it has some objects $ X, Y, Y^X: \C $ with a bijection
+  \[ \C(X^\prime \times X, Y) \cong \C(X^\prime, Y^X) \]
   that is natural in $ X^\prime $. Then $ Y^X $ is still called an exponential object.
@@
 \begin{definition}
-  Given a forgetful functor $ F: C \to D $, we define the \textit{free functor}\index{free!functor} associated to $ F $ to be the left adjoint to $ F $, if it exists.
+  Given a forgetful functor $ F: \C \to \D $, we define the \textit{free functor}\index{free!functor} associated to $ F $ to be the left adjoint to $ F $, if it exists.
 \end{definition}
@@
 
-However, as with exponential object, sometimes we have a forgetful functor $ F: C \to D $, but we cannot give a free functor on the entire category $ D $.
+However, as with exponential object, sometimes we have a forgetful functor $ F: \C \to \D $, but we cannot give a free functor on the entire category $ \D $.
 In such a case, we might still talk about free `objects':
 \begin{definition}
-  Let $ F: C \to D $ be a forgetful functor. Given $ X: D $, the \textit{free object}\index{free!object} on $ X $ is a universal arrow $ (Y, f) $ from $ X $ to $ F $.
-\end{definition}
-
-\begin{remark}
-  By \autocite{MacLane}, Chapter IV.1, Theorem 2 (ii), if we have a free object on every $ X: D $, we can piece these together to get a free functor associated to $ F $.
+  Let $ F: \C \to \D $ be a forgetful functor. Given $ X: \D $, the \textit{free object}\index{free!object} on $ X $ is a universal arrow $ (Y, f) $ from $ X $ to $ F $.
+\end{definition}
+
+\begin{remark}
+  By \autocite{MacLane}, Chapter IV.1, Theorem 2 (ii), if we have a free object on every $ X: \D $, we can piece these together to get a free functor associated to $ F $.
 \end{remark}
@@
 \section{Yoneda}
-We can embed a category $ C $ fully faithfully into the functor category $ P C = [\op C, \SET] $ as follows (see \autocite{Kashiwara}, Section 1.4):
+We can embed a category $ \C $ fully faithfully into the functor category $ P \C = [\op \C, \SET] $ as follows (see \autocite{Kashiwara}, Section 1.4):
 \begin{definition}\label{def:Yoneda-embedding}
-  The \iindex{Yoneda embedding} $ \yo : C \hookrightarrow P C $ is given on objects by $ \yo(Y) = C(-, Y) $:
-  \[ \yo(Y)(X) = C(X, Y) \quad \text{and} \quad \yo(Y)(f)(g) = f \cdot g \]
-  for $ X: C $, $ f: C(X, X^\prime) $ and $ g: C(X^\prime, Y) $. It sends a morphism $ f: C(Y, Y^\prime) $ to the natural transformation $ \yo(f): C(-, Y) \Rightarrow C(-, Y^\prime) $ given by
+  The \iindex{Yoneda embedding} $ \yo : \C \hookrightarrow P \C $ is given on objects by $ \yo(Y) = \C(-, Y) $:
+  \[ \yo(Y)(X) = \C(X, Y) \quad \text{and} \quad \yo(Y)(f)(g) = f \cdot g \]
+  for $ X: \C $, $ f: \C(X, X^\prime) $ and $ g: \C(X^\prime, Y) $. It sends a morphism $ f: \C(Y, Y^\prime) $ to the natural transformation $ \yo(f): \C(-, Y) \Rightarrow \C(-, Y^\prime) $ given by
   \[ \yo(f)(X)(g) = g \cdot f \]
-  for $ X: C $ and $ g: C(X, Y) $.
+  for $ X: \C $ and $ g: \C(X, Y) $.
 \end{definition}
@@
 \begin{lemma}
-  For any $ Y: C $ and $ F : P C $, we have an equivalence $ P C(\yo(Y), F) \simeq F(Y) $, and this equivalence is natural in $ Y $ and $ F $.
-\end{lemma}
-\begin{proof}
-  It sends a natural transformation $ \alpha: P C(\yo(Y), F) $ to the element $ \alpha_Y(\id Y) $.
-Conversely, it sends an element $ X : P(Y) $ to the natural transformation $ \alpha $ given by $ \alpha_X(f) = P(f)(X) $ for all $ f: \yo(Y)(X) = C(X, Y) $.
+  For any $ Y: \C $ and $ F : P \C $, we have an equivalence $ P \C(\yo(Y), F) \simeq F(Y) $, and this equivalence is natural in $ Y $ and $ F $.
+\end{lemma}
+\begin{proof}
+  It sends a natural transformation $ a: P \C(\yo(Y), F) $ to the element $ a_Y(\id Y) $.
+Conversely, it sends an element $ X : P(Y) $ to the natural transformation $ a $ given by $ a_X(f) = P(f)(X) $ for all $ f: \yo(Y)(X) = \C(X, Y) $.
 For more details, see \autocite{Kashiwara}, Proposition 1.4.3.
@@
 \begin{remark}
-  For any category $ D $, the category $ [C, D] $ has (co)limits of some kind (terminal or initial object, (co)products, (co)equalizers) iff $ D $ does.
+  For any category $ \D $, the category $ [\C, \D] $ has (co)limits of some kind (terminal or initial object, (co)products, (co)equalizers) iff $ \D $ does.
 These (co)limits are computed pointwise: for example, for binary products, $ (F \times G)(X) = F(X) \times G(X) $.
-In particular $ P C $ has all limits and colimits because $ \SET $ has all limits and colimits.
-\end{remark}
-
-\begin{remark}
-  Also, for any small category $ C $ (small means that the collection of objects is a type in our type universe.
-For example: for a fixed universe of types, $ \TYPE $ or $ \SET $ are not small categories, the universe of types is not contained in itself), the presheaf category $ P C $ has exponential objects, given by
-  \[ (F^G)(X) = PC(\yo(X) \times G, F), \]
+In particular $ P \C $ has all limits and colimits because $ \SET $ has all limits and colimits.
+\end{remark}
+
+\begin{remark}
+  Also, for any small category $ \C $ (small means that the collection of objects is a type in our type universe.
+For example: for a fixed universe of types, $ \TYPE $ or $ \SET $ are not small categories, the universe of types is not contained in itself), the presheaf category $ P \C $ has exponential objects, given by
+  \[ (F^G)(X) = P\C(\yo(X) \times G, F), \]
   the natural transformations from the product functor of the Yoneda embedding of $ X $ and $ G $, to $ F $ (see \autocite{MacLane-Moerdijk}, Section I.6, Proposition 1).
@@
 \begin{definition}
-  Suppose that we have a functor $ F: C \to D $, and $ C $ and $ D $ both have binary products.
-Then for $ X, Y : C $, we have morphisms $ \pi_1: X \times Y \to X $ and $ \pi_2 : X \times Y \to Y $ and applying $ F $ to these yields morphisms from $ F(X \times Y) $ to $ F(X) $ and $ F(Y) $.
+  Suppose that we have a functor $ F: \C \to \D $, and $ \C $ and $ \D $ both have binary products.
+Then for $ X, Y : \C $, we have morphisms $ \pi_1: X \times Y \to X $ and $ \pi_2 : X \times Y \to Y $ and applying $ F $ to these yields morphisms from $ F(X \times Y) $ to $ F(X) $ and $ F(Y) $.
 We then have a product morphism
   \[ \langle F(\pi_1), F(\pi_2) \rangle: F(X \times Y) \to F(X) \times F(Y). \]
-  Now, if this morphism is an isomorphism for all $ X, Y : C $, we say that $ F $ \index{preservation of binary products}\textit{preserves binary products}.
-
-  One can imagine that there exists a similar definition of preservation of limits in general, in which the limit morphism of `$ F $ applied to the projections from the limit' is an isomorphism, for any limit in $ C $.
+  Now, if this morphism is an isomorphism for all $ X, Y : \C $, we say that $ F $ \index{preservation of binary products}\textit{preserves binary products}.
+
+  One can imagine that there exists a similar definition of preservation of limits in general, in which the limit morphism of `$ F $ applied to the projections from the limit' is an isomorphism, for any limit in $ \C $.
 \end{definition}
@@
 \begin{definition}\label{def:exponentials-preservation}
-  Suppose that we have a functor $ F: C \to D $ that preserves binary products, and $ C $ and $ D $ have exponential objects. Then for $ X, Y : C $, we have natural bijections
-  \[ \varphi: C(X^Y \times Y, X) \xrightarrow \sim C(X^Y, X^Y) \quad \text{and} \quad \psi: D(F(X^Y) \times F(Y), F(X)) \xrightarrow \sim D(F(X^Y), F(X)^{F(Y)}) \]
-  This gives a morphism $ F(\varphi^{-1}(\id{X^Y})) : D(F(X^Y \times Y), F(X)) $.
+  Suppose that we have a functor $ F: \C \to \D $ that preserves binary products, and $ \C $ and $ \D $ have exponential objects. Then for $ X, Y : \C $, we have natural bijections
+  \[ \varphi: \C(X^Y \times Y, X) \xrightarrow \sim \C(X^Y, X^Y) \quad \text{and} \quad \psi: \D(F(X^Y) \times F(Y), F(X)) \xrightarrow \sim \D(F(X^Y), F(X)^{F(Y)}) \]
+  This gives a morphism $ F(\varphi^{-1}(\id{X^Y})) : \D(F(X^Y \times Y), F(X)) $.
 Precomposing with the inverse of the isomorphism $ f: F(X^Y \times Y) \xrightarrow \sim F(X^Y) \times F(Y) $ and applying $ \psi $ gives
-  \[ \psi(f^{-1} \cdot \varphi^{-1}(\id{X^Y})) : D(F(X^Y), F(X)^{F(Y)}). \]
-  We say that $ F $ \index{preservation of exponentials}\textit{preserves exponentials} if this morphism is an isomorphism for all $ X, Y : C $.
+  \[ \psi(f^{-1} \cdot \varphi^{-1}(\id{X^Y})) : \D(F(X^Y), F(X)^{F(Y)}). \]
+  We say that $ F $ \index{preservation of exponentials}\textit{preserves exponentials} if this morphism is an isomorphism for all $ X, Y : \C $.
 A name for a functor that preserves exponentials is a \iindex{cartesian functor}.
@@
   \[ \yo(X \times Y)(Z) \xrightarrow \sim \yo(X)(Z) \times \yo(Y)(Z) \]
-  sending $ f : C(Z, X \times Y) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : C(Z, X) \times C(Z, Y) $ to the product morphism $ \langle g_1, g_2 \rangle : \yo(Z, X \times Y) $.
+  sending $ f : \C(Z, X \times Y) $ to the pair $ (f \cdot \pi_1, f \cdot \pi_2) $ and conversely, sending a pair $ (g_1, g_2) : \C(Z, X) \times \C(Z, Y) $ to the product morphism $ \langle g_1, g_2 \rangle : \yo(Z, X \times Y) $.
 This idea is also the core of the proof about general limits.
@@
 \begin{proof}
-  First of all, note that for $ X, Y, Z : C $, we have a sequence of isomorphisms  (\autocite{stackexchange:yoneda-exponentials})
+  First of all, note that for $ X, Y, Z : \C $, we have a sequence of isomorphisms  (\autocite{stackexchange:yoneda-exponentials})
   \begin{align*}
-    \yo(X^Y)(Z) &\cong P C(\yo(Z), \yo(X^Y))\\
-    &\cong C(Z, X^Y)\\
-    &\cong C(Z \times Y, X)\\
-    &\cong P C(\yo(Z \times Y), \yo(X))\\
-    &\cong P C(\yo(Z) \times \yo(Y), \yo(X))\\
-    &\cong P C(\yo(Z), \yo(X)^\yo(Y))\\
+    \yo(X^Y)(Z) &\cong P \C(\yo(Z), \yo(X^Y))\\
+    &\cong \C(Z, X^Y)\\
+    &\cong \C(Z \times Y, X)\\
+    &\cong P \C(\yo(Z \times Y), \yo(X))\\
+    &\cong P \C(\yo(Z) \times \yo(Y), \yo(X))\\
+    &\cong P \C(\yo(Z), \yo(X)^\yo(Y))\\
     &\cong (\yo(X)^\yo(Y))(Z)
@@
 
-  Some calculating shows that when applying this isomorphism to some $ f: \yo(X^Y)(Z) $, we get the natural transformation $ h: P C(\yo(Z) \times \yo(Y), \yo(X)) $ given by
+  Some calculating shows that when applying this isomorphism to some $ f: \yo(X^Y)(Z) $, we get the natural transformation $ h: P \C(\yo(Z) \times \yo(Y), \yo(X)) $ given by
   \[ h_Z(g_1, g_2) = \langle g_1, g_2 \rangle \cdot \varphi^{-1}(f) \]
-  for all $ Z: C $ and $ (g_1, g_2) : \yo(Z)(Z) \times \yo(Y)(Z) $ and with the natural bijection
-  \[ \varphi: C(Z \times Y, X) \xrightarrow \sim C(Z, X^Y). \]
+  for all $ Z: \C $ and $ (g_1, g_2) : \yo(Z)(Z) \times \yo(Y)(Z) $ and with the natural bijection
+  \[ \varphi: \C(Z \times Y, X) \xrightarrow \sim \C(Z, X^Y). \]
 
@@
 
-For a functor between categories $ f: C \to D $, given the Yoneda embeddings $ \yo_C : C \to P C $ and $ \yo_D : D \to P D $ (we will often omit the subscript $ C $ and $ D $), we can create a diagram
-\begin{center}
-  \begin{tikzcd}
-    C \arrow[r, "f"] \arrow[d, hookrightarrow, "\yo"] & D \arrow[d, hookrightarrow, "\yo"]\\
-    P C & P D \arrow[l, "\op f_*"]
+For a functor between categories $ f: \C \to \D $, given the Yoneda embeddings $ \yo_\C : \C \to P \C $ and $ \yo_\D : \D \to P \D $ (we will often omit the subscript $ \C $ and $ \D $), we can create a diagram
+\begin{center}
+  \begin{tikzcd}
+    \C \arrow[r, "f"] \arrow[d, hookrightarrow, "\yo"] & \D \arrow[d, hookrightarrow, "\yo"]\\
+    P \C & P \D \arrow[l, "\op f_*"]
   \end{tikzcd}
@@
 Note that the arrows in this diagram are functors, so objects in a category, instead of elements of a set.
-Therefore, it often does not make a lot of sense to talk about `equality' of the functors along the different paths, but we rather talk about isomorphism in the functor category $ [C, P C] $.
+Therefore, it often does not make a lot of sense to talk about `equality' of the functors along the different paths, but we rather talk about isomorphism in the functor category $ [\C, P \C] $.
 If we have such an isomorphism, we say the diagram `2-commutes':
 \begin{lemma}\label{lem:Yoneda-restriction-commutes}
-  If $ f: C \to D $ is a fully faithful functor, the diagram above 2-commutes.
-\end{lemma}
-\begin{proof}
-  For $ Y, X : C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
-  \[ \yo(Y)(X) = C(X, Y) \xrightarrow[f_{X, Y}]{\sim} D(f(X), f(Y)) = \op f_*(\yo(f(Y)))(X). \]
-  Also, for $ g: C(X^\prime, X) $, the following diagram commutes
+  If $ f: \C \to \D $ is a fully faithful functor, the diagram above 2-commutes.
+\end{lemma}
+\begin{proof}
+  For $ Y, X : \C $, since $ f $ is fully faithful, we have isomorphisms of sets, given by
+  \[ \yo(Y)(X) = \C(X, Y) \xrightarrow[f_{X, Y}]{\sim} \D(f(X), f(Y)) = \op f_*(\yo(f(Y)))(X). \]
+  Also, for $ g: \C(X^\prime, X) $, the following diagram commutes
   \begin{center}
@@
   \end{center}
-  so the isomorphism is natural in $ X $ and we have $ \yo(Y) \cong \op f_*(\yo(f(Y))) $ in $ P C $. Lastly, for $ g: C(Y, Y^\prime) $ and $ X: C $, the following diagram commutes
+  so the isomorphism is natural in $ X $ and we have $ \yo(Y) \cong \op f_*(\yo(f(Y))) $ in $ P \C $. Lastly, for $ g: \C(Y, Y^\prime) $ and $ X: \C $, the following diagram commutes
   \begin{center}
@@
   \end{center}
-  so the isomorphism is natural in $ Y $ and we have $ \yo \cong f \bullet \yo \bullet \op f_* $ in $ [C, P C] $.
+  so the isomorphism is natural in $ Y $ and we have $ \yo \cong f \bullet \yo \bullet \op f_* $ in $ [\C, P \C] $.
 \end{proof}
@@
 \section{Fibrations}
-Let $ P : E \to B $ be a functor. In this case, we will view this as the category $ E $ `lying over' the category $ B $, with for every point $ X: B $, a slice $ E_X = P^{-1}(B) $ lying `above' $ X $.
-
-\begin{definition}
-  A morphism $ f: E(Y, Z) $ is called \iindex{cartesian} if for all $ g: E(X, Z) $ and $ h: B(P(X), P(Y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: E(X, Y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \autocite{nlab:grothendieck_fibration}
+Let $ P : \E \to \B $ be a functor.
+In this case, we will view this as the category $ \E $ `lying over' the category $ \B $, with for every point $ X: \B $, a slice $ \E_X = P^{-1}(\B) $ lying `above' $ X $.
+
+\begin{definition}
+  A morphism $ f: \E(Y, Z) $ is called \iindex{cartesian} if for all $ g: \E(X, Z) $ and $ h: \B(P(X), P(Y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: \E(X, Y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \autocite{nlab:grothendieck_fibration}
   \begin{center}
     \begin{tikzcd}[sep=large]
-      E \arrow[d, "P"] &X \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar h"', dashed] & Y \arrow[r, "f"'] & Z\\
-      B & P(X) \arrow[r, "\forall h"'] \arrow[rr, "P(g)", bend left] & P(Y) \arrow[r, "P(f)"'] & P(Z)
-    \end{tikzcd}
-  \end{center}
-\end{definition}
-
-\begin{definition}
-  $ P $ is a \iindex{fibration} if for all $ Y: E $ and morphisms $ f: B(X, P(Y)) $, there exist an object $ \bar X: E $ and a cartesian morphism $ \bar f: E(\bar X, Y) $ such that $ P(\bar X) = X $ and $ P(\bar f) = f $:
-  \begin{center}
-    \begin{tikzcd}
-      E \arrow[d, "P"] & \bar X \arrow[r, "\exists \bar f", dashed] & Y\\
-      B & X \arrow[r, "\forall f"] & P(Y)
+      \E \arrow[d, "P"] &X \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar h"', dashed] & Y \arrow[r, "f"'] & Z\\
+      \B & P(X) \arrow[r, "\forall h"'] \arrow[rr, "P(g)", bend left] & P(Y) \arrow[r, "P(f)"'] & P(Z)
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+\begin{definition}
+  $ P $ is a \iindex{fibration} if for all $ Y: \E $ and morphisms $ f: \B(X, P(Y)) $, there exist an object $ \bar X: \E $ and a cartesian morphism $ \bar f: \E(\bar X, Y) $ such that $ P(\bar X) = X $ and $ P(\bar f) = f $:
+  \begin{center}
+    \begin{tikzcd}
+      \E \arrow[d, "P"] & \bar X \arrow[r, "\exists \bar f", dashed] & Y\\
+      \B & X \arrow[r, "\forall f"] & P(Y)
     \end{tikzcd}
@@
 \section{(Co)slice categories}
-Given an object in a category $ X: C $, the morphisms to and from $ X $ constitute the slice and coslice categories
-\begin{definition}
-  The \iindex{slice category} $ C \downarrow X $ is the category with as objects the morphisms to $ X $:
-  \[ (C \downarrow X)_0 = \sum_{Y: C} C(Y, X). \]
+Given an object in a category $ X: \C $, the morphisms to and from $ X $ constitute the slice and coslice categories
+\begin{definition}
+  The \iindex{slice category} $ \C \downarrow X $ is the category with as objects the morphisms to $ X $:
+  \[ (\C \downarrow X)_0 = \sum_{Y: \C} \C(Y, X). \]
   The morphisms from $ (Y_1, f_1) $ to $ (Y_2, f_2) $ are the morphisms $ g: Y_1 \to Y_2 $ making the following diagram commute.
@@
 \end{definition}
-The \textit{coslice category}\index{slice category!co-} $ X \downarrow C $ is similar, but with the morphisms \textit{from} $ X $ instead of \textit{to} $ X $:
-\[ (X \downarrow C)_0 = \sum_{Y: C} C(X, Y). \]
+The \textit{coslice category}\index{slice category!co-} $ X \downarrow \C $ is similar, but with the morphisms \textit{from} $ X $ instead of \textit{to} $ X $:
+\[ (X \downarrow \C)_0 = \sum_{Y: \C} \C(X, Y). \]
 
@@
 \begin{lemma}
-  Let $ (Y, f) $ be an object in the slice category $ (C \downarrow X) $. The slice category $ ((C \downarrow X) \downarrow (Y, f)) $ is equivalent to $ (C \downarrow Y) $.
-\end{lemma}
-\begin{proof}
-  An object of $ ((Z, g), \alpha) : ((C \downarrow X) \downarrow (Y, f)) $ is an object $ (Z, g) : (C \downarrow X) $, together with a morphism $ \alpha: (C \downarrow X)((Z, g), (Y, f)) $.
-That is, a morphism $ \alpha: C(Z, Y) $ such that the obvious triangle commutes (shown in the diagram below on the far left).
-
-  Then a morphism between $ ((Z_1, g_1), \alpha_1) $ and $ ((Z_2, g_2), \alpha_2) $ is a morphism $ \beta $ between $ (Z_1, g_1) $ and $ (Z_2, g_2) $ that commutes with $ \alpha_1 $ and $ \alpha_2 $.
+  Let $ (Y, f) $ be an object in the slice category $ (\C \downarrow X) $. The slice category $ ((\C \downarrow X) \downarrow (Y, f)) $ is equivalent to $ (\C \downarrow Y) $.
+\end{lemma}
+\begin{proof}
+  An object of $ ((Z, g), a) : ((\C \downarrow X) \downarrow (Y, f)) $ is an object $ (Z, g) : (\C \downarrow X) $, together with a morphism $ a: (\C \downarrow X)((Z, g), (Y, f)) $.
+That is, a morphism $ a: \C(Z, Y) $ such that the obvious triangle commutes (shown in the diagram below on the far left).
+
+  Then a morphism between $ ((Z_1, g_1), a_1) $ and $ ((Z_2, g_2), a_2) $ is a morphism $ b $ between $ (Z_1, g_1) $ and $ (Z_2, g_2) $ that commutes with $ a_1 $ and $ a_2 $.
 Note that a morphism between $ (Z_1, g_1) $ and $ (Z_2, g_2) $ is a morphism between $ Z_1 $ and $ Z_2 $ that commutes with $ g_1 $ and $ g_2 $.
@@
     \begin{tikzcd}
-      Z_1 \arrow[rdd, "g_1"'] \arrow[rd, "\alpha_1"] \arrow[rr, "\beta"] && Z_2 \arrow[ldd, "g_2"] \arrow[ld, "\alpha_2"']\\
+      Z_1 \arrow[rdd, "g_1"'] \arrow[rd, "a_1"] \arrow[rr, "b"] && Z_2 \arrow[ldd, "g_2"] \arrow[ld, "a_2"']\\
       & Y \arrow[d, "f" description]\\
@@
     \begin{tikzcd}
-      Z_1 \arrow[rd, "\alpha_1"] \arrow[rr, "\beta"] && Z_2 \arrow[ld, "\alpha_2"']\\
+      Z_1 \arrow[rd, "a_1"] \arrow[rr, "b"] && Z_2 \arrow[ld, "a_2"']\\
       & Y
@@
 
-  Now, note that $ g_1 $ and $ g_2 $ are completely determined by $ g_i = \alpha_i \cdot f $, so we can leave them out.
-Also, if $ \beta $ commutes with $ \alpha_1 $ and $ \alpha_2 $, it automatically also commutes with $ g_1 $ and $ g_2 $.
+  Now, note that $ g_1 $ and $ g_2 $ are completely determined by $ g_i = a_i \cdot f $, so we can leave them out.
+Also, if $ b $ commutes with $ a_1 $ and $ a_2 $, it automatically also commutes with $ g_1 $ and $ g_2 $.
 Therefore, as shown above, we have a correspondence between objects and morphisms
-  \[ \beta: ((Z_1, g_1), \alpha_1) \to ((Z_2, g_2), \alpha_2) \Leftrightarrow \beta: (Z_1, \alpha_1) \to (Z_2, \alpha_2). \]
+  \[ b: ((Z_1, g_1), a_1) \to ((Z_2, g_2), a_2) \Leftrightarrow b: (Z_1, a_1) \to (Z_2, a_2). \]
 \end{proof}
@@
 \begin{lemma}
-  For $ (Y_1, f_1), (Y_2, f_2) : (C \downarrow X) $, their product in the slice category is given by their pullback, or fibered product, $ Y_1 \times_X Y_2 $, together with the induced morphism $ g: Y_1 \times_X Y_2 \dasharrow X $.
+  For $ (Y_1, f_1), (Y_2, f_2) : (\C \downarrow X) $, their product in the slice category is given by their pullback, or fibered product, $ Y_1 \times_X Y_2 $, together with the induced morphism $ g: Y_1 \times_X Y_2 \dasharrow X $.
 \end{lemma}
@@
 The fibered product gives `projections' $ h_1 $ and $ h_2 $.
-Also, if we have some $ (Z, \alpha) : (C \downarrow X) $, together with morphisms $ \beta_1 : (Z, \alpha) \to (Y_1, f_1) $ and $ \beta_2 : (Z, \alpha) \to (Y_2, f_2) $.
-Then $ \beta_1 $ and $ \beta_2 $ commute with $ f_1 $ and $ f_2 $, so by the universal property of the fibred product, there exists a unique morphism $ \gamma : Z \to Y_1 \times_X Y_2 $ that makes the triangles with $ \beta_1 $ and $ h_1 $, and with $ \beta_2 $ and $ h_2 $ commute.
-Then $ \gamma $ commutes with $ \alpha $ and $ g $ as well, so it is a morphism in $ (C \downarrow X) $.
-This shows that $ (Y_1 \times_X Y_2, g) $ has the universal property of the product in $ (C \downarrow X) $.
-  \begin{center}
-    \begin{tikzcd}
-      Z \arrow[rd, "\beta_1"] \arrow[rr, "\beta_2", bend left] \arrow[rrd, "\alpha"', bend right=49, shift right] \arrow[r, dashed, "\gamma"] & Y_1 \times_X Y_2 \arrow[r, "h_2"'] \arrow[d, "h_1"] \arrow[rd, dashed, "g"] & Y_2 \arrow[d, "f_2"] \\
+Also, if we have some $ (Z, a) : (\C \downarrow X) $, together with morphisms $ b_1 : (Z, a) \to (Y_1, f_1) $ and $ b_2 : (Z, a) \to (Y_2, f_2) $.
+Then $ b_1 $ and $ b_2 $ commute with $ f_1 $ and $ f_2 $, so by the universal property of the fibred product, there exists a unique morphism $ \gamma : Z \to Y_1 \times_X Y_2 $ that makes the triangles with $ b_1 $ and $ h_1 $, and with $ b_2 $ and $ h_2 $ commute.
+Then $ \gamma $ commutes with $ a $ and $ g $ as well, so it is a morphism in $ (\C \downarrow X) $.
+This shows that $ (Y_1 \times_X Y_2, g) $ has the universal property of the product in $ (\C \downarrow X) $.
+  \begin{center}
+    \begin{tikzcd}
+      Z \arrow[rd, "b_1"] \arrow[rr, "b_2", bend left] \arrow[rrd, "a"', bend right=49, shift right] \arrow[r, dashed, "\gamma"] & Y_1 \times_X Y_2 \arrow[r, "h_2"'] \arrow[d, "h_1"] \arrow[rd, dashed, "g"] & Y_2 \arrow[d, "f_2"] \\
       & Y_1 \arrow[r, "f_1"] & X
@@
 
-For a category $ C $ with products, Hyland introduces the notation $ \Delta_X Y $ for the element $ (X \times Y, p_1) : (C \downarrow X) $, and we will follow his example in this.
-
-In fact, $ \Delta_X : C \to C / X $ is a functor, with $ \Delta_X(f) = \id X \times f $ for $ f: C(Y, Y^\prime) $. This functor preserves the terminal object, products and pullbacks:
+For a category $ \C $ with products, Hyland introduces the notation $ \Delta_X Y $ for the element $ (X \times Y, p_1) : (\C \downarrow X) $, and we will follow his example in this.
+
+In fact, $ \Delta_X : \C \to (\C \downarrow X) $ is a functor, with $ \Delta_X(f) = \id X \times f $ for $ f: \C(Y, Y^\prime) $. This functor preserves the terminal object, products and pullbacks:
 \begin{lemma}\label{lem:delta-limits}
@@
 \begin{proof}
-  Take a diagram $ ((Y_i)_i, (f_j)_j) $ in $ C $.
-Suppose that this has a limit $ L : C $ with projections $ g_i : C(L, Y_i) $.
-Now, consider an object $ (Z, q) : (C \downarrow X) $, together with morphisms $ h_i : (C \downarrow X)((Z, q), \Delta_X Y_i) $, that commute with the $ \Delta_X f_j $:
+  Take a diagram $ ((Y_i)_i, (f_j)_j) $ in $ \C $.
+Suppose that this has a limit $ L : \C $ with projections $ g_i : \C(L, Y_i) $.
+Now, consider an object $ (Z, q) : (\C \downarrow X) $, together with morphisms $ h_i : (\C \downarrow X)((Z, q), \Delta_X Y_i) $, that commute with the $ \Delta_X f_j $:
   \begin{center}
@@
   \end{center}
-  Then the morphisms in $ (C \downarrow X)((Z, q), \Delta_X L) $, commuting with the $ \Delta_X g_j $ and $ h_j $ are the morphisms in $ C(Z, X \times L) \cong C(Z, X) \times C(Z, L) $ that commute with the projections to $ X $ and the $ \id X \times g_j $ and $ h_j $.
-Since the morphisms in $ C(Z, X) $ commuting with $ q $ and $ \id X $ are exactly $ q $, we can forget about this component, and the morphisms we are looking for correspond to the morphisms in $ C(Z, L) $ that commute with the $ g_j $ and $ h_j \cdot p_1 $.
+  Then the morphisms in $ (\C \downarrow X)((Z, q), \Delta_X L) $, commuting with the $ \Delta_X g_j $ and $ h_j $ are the morphisms in $ \C(Z, X \times L) \cong \C(Z, X) \times \C(Z, L) $ that commute with the projections to $ X $ and the $ \id X \times g_j $ and $ h_j $.
+Since the morphisms in $ \C(Z, X) $ commuting with $ q $ and $ \id X $ are exactly $ q $, we can forget about this component, and the morphisms we are looking for correspond to the morphisms in $ \C(Z, L) $ that commute with the $ g_j $ and $ h_j \cdot p_1 $.
 Since $ (L, (g_j)_j) $ is a limit, this is a unique morphism.
@@
   \begin{align*}
-    (C \downarrow X)((W, f), \Delta_X Y^Z) &\cong C(W, Y^Z)\\
-    &\cong C(W \times Z, Y)\\
-    &\cong (C \downarrow X)((W \times (X \times Z), \langle f, p_1 \rangle), \Delta_X Y)\\
-    &\cong (C \downarrow X)((W, f) \times \Delta_X Z, \Delta_X Y)\\
+    (\C \downarrow X)((W, f), \Delta_X Y^Z) &\cong \C(W, Y^Z)\\
+    &\cong \C(W \times Z, Y)\\
+    &\cong (\C \downarrow X)((W \times (X \times Z), \langle f, p_1 \rangle), \Delta_X Y)\\
+    &\cong (\C \downarrow X)((W, f) \times \Delta_X Z, \Delta_X Y)\\
   \end{align*}
@@
 
-Take a category $ C $.
-To talk about dependent sums $ \sum_{x: X} Y_x $ and products $ \prod_{x: X} Y_x $ in $ C $, we first need some way to construct the family of objects $ (Y_x)_x $.
-Of course, we can do this \textit{externally} using a set $ X $, and picking an object $ Y_x : C $ for every element $ x : X $.
-We then have a category of such families $ C^X $, with objects $ (Y_x)_x $ and morphisms $ (f_x)_x: C^X((Y_x)_x, (Z_x)_x) $, with $ f_x: Y_x \to Z_x $.
-We write $ C^X $ because we can view this as just the $ X $-fold power of $ C $.
-Now, this assignment of categories $ X \mapsto C^X $ can be turned into a contravariant (pseudo)functor of $ 2 $-categories $ \op \SET \to \Cat $.
-It sends a morphism $ f: X_1 \to X_2 $ to the `relabeling' or `substitution' functor $ C^{X_2} \to C^{X_1} $, $ (Y_x)_x \mapsto (Y_{f(x)})_x $.
+Take a category $ \C $.
+To talk about dependent sums $ \sum_{x: X} Y_x $ and products $ \prod_{x: X} Y_x $ in $ \C $, we first need some way to construct the family of objects $ (Y_x)_x $.
+Of course, we can do this \textit{externally} using a set $ X $, and picking an object $ Y_x : \C $ for every element $ x : X $.
+We then have a category of such families $ \C^X $, with objects $ (Y_x)_x $ and morphisms $ (f_x)_x: \C^X((Y_x)_x, (Z_x)_x) $, with $ f_x: Y_x \to Z_x $.
+We write $ \C^X $ because we can view this as just the $ X $-fold power of $ \C $.
+Now, this assignment of categories $ X \mapsto \C^X $ can be turned into a contravariant (pseudo)functor of $ 2 $-categories $ \op \SET \to \Cat $.
+It sends a morphism $ f: X_1 \to X_2 $ to the `relabeling' or `substitution' functor $ \C^{X_2} \to \C^{X_1} $, $ (Y_x)_x \mapsto (Y_{f(x)})_x $.
 
 However, there is also an \textit{internal} representation, as a morphism $ Y \to X $.
-We can turn the collection of these morphisms over all the $ X : C $ simultaneously into a category $ C^2 $ (abusing notation a bit, writing $ 2 $ for the two-point category $ \bullet \to \bullet $).
-Then taking codomains $ (Y \to X) \mapsto X $ gives a functor $ C^2 \to C $.
-The fiber of this functor above $ X $ is the slice category $ (C \downarrow X) $.
+We can turn the collection of these morphisms over all the $ X : \C $ simultaneously into a category $ \C^2 $ (abusing notation a bit, writing $ 2 $ for the two-point category $ \bullet \to \bullet $).
+Then taking codomains $ (Y \to X) \mapsto X $ gives a functor $ \C^2 \to \C $.
+The fiber of this functor above $ X $ is the slice category $ (\C \downarrow X) $.
 
@@
 This turns the functor $ \SET^2 \to \SET $ into a fibration.
-We can construct such a functor $ f^* $ for any category $ C $ with pullbacks and any morphism $ f: C(X, Y) $, and this makes the functor $ C^2 \to C $ into a fibration.
+We can construct such a functor $ f^* $ for any category $ \C $ with pullbacks and any morphism $ f: \C(X, Y) $, and this makes the functor $ \C^2 \to \C $ into a fibration.
 
@@
 \begin{definition}
-  For a category $ C $ and a morphism $ f: Y \to X $, the \iindex{dependent product} along $ f $ is, if it exists, the right adjoint to the pullback functor:
-  \begin{center}
-    \begin{tikzcd}
-      (C \downarrow A) \arrow[r, shift left=2, "f^*"{name=A}] &
-      (C \downarrow B) \arrow[l, shift left=2, "\prod_f"{name=B}]
+  For a category $ \C $ and a morphism $ f: Y \to X $, the \iindex{dependent product} along $ f $ is, if it exists, the right adjoint to the pullback functor:
+  \begin{center}
+    \begin{tikzcd}
+      (\C \downarrow X) \arrow[r, shift left=2, "f^*"{name=A}] &
+      (\C \downarrow Y) \arrow[l, shift left=2, "\prod_f"{name=B}]
       \ar[from=A, to=B, symbol=\dashv]
@@
   As argued above, we can recover the familiar dependent product $ \prod_{x : X} Y_x $ of a family $ (Y_x)_x $ as the dependent product $ \prod_f (\sum_x Y_x, \pi_1) $ along the terminal morphism $ f: X \to I $.
-Here we use the equivalence between $ (C \downarrow I) $ and $ C $.
+Here we use the equivalence between $ (\C \downarrow I) $ and $ \C $.
 \end{remark}
@@
 \begin{definition}
-  For a category $ C $ and a morphism $ f: Y \to X $, the \iindex{dependent sum} along $ f $ is, if it exists, the left adjoint to the pullback functor:
-  \begin{center}
-    \begin{tikzcd}
-      (C \downarrow X) \arrow[r, shift right=2, "f^*"'{name=B}] &
-      (C \downarrow Y) \arrow[l, shift right=2, "\sum_f"'{name=A}]
+  For a category $ \C $ and a morphism $ f: Y \to X $, the \iindex{dependent sum} along $ f $ is, if it exists, the left adjoint to the pullback functor:
+  \begin{center}
+    \begin{tikzcd}
+      (\C \downarrow X) \arrow[r, shift right=2, "f^*"'{name=B}] &
+      (\C \downarrow Y) \arrow[l, shift right=2, "\sum_f"'{name=A}]
       \ar[from=A, to=B, symbol=\dashv]
@@
 \begin{lemma}\label{lem:sum-postcomposition}
-  Let $ f : C(Y, X) $ be a morphism in a category. If the pullback functor $ f^*: (C \downarrow X) \to (C \downarrow Y) $ exists, it has a left adjoint given by postcomposition with $ f $.
+  Let $ f : \C(Y, X) $ be a morphism in a category. If the pullback functor $ f^*: (\C \downarrow X) \to (\C \downarrow Y) $ exists, it has a left adjoint given by postcomposition with $ f $.
 \end{lemma}
@@
   gives an equivalence between morphisms $ \varphi: W \to f^* Z $ that commute with $ h $ and $ f^* g $, and morphisms $ \psi: W \to Z $ that commute with $ h $, $ g $ and $ f $. In other words:
-  \[ (C \downarrow X)(h \cdot f, g) \simeq (C \downarrow Y)(h, f^*(g)), \]
+  \[ (\C \downarrow X)(h \cdot f, g) \simeq (\C \downarrow Y)(h, f^*(g)), \]
   which shows the adjunction.
@@
 We have $ \sum_{x : X} Y_x = g \cdot f : Y \to I $.
-By the equivalence between $ (C \downarrow I) $ and $ C $, we see that the dependent sum of the family $ (Y_x)_x $ is exactly $ Y $.
+By the equivalence between $ (\C \downarrow I) $ and $ \C $, we see that the dependent sum of the family $ (Y_x)_x $ is exactly $ Y $.
 Therefore, our attention is mainly focused on the dependent product.
@@
 \begin{definition}
-  A \index{cartesian closed!locally}\textit{locally cartesian closed} category is a category $ C $ with pullbacks such that each pullback functor $ f^* $ has a right adjoint.
+  A \index{cartesian closed!locally}\textit{locally cartesian closed} category is a category $ \C $ with pullbacks such that each pullback functor $ f^* $ has a right adjoint.
 \end{definition}
@@
 \begin{lemma}\label{lem:locally-cartesian-closed}
-  A category $ C $ is locally cartesian closed iff $ (C \downarrow X) $ is cartesian closed for each $ X : C $.
+  A category $ \C $ is locally cartesian closed iff $ (\C \downarrow X) $ is cartesian closed for each $ X : \C $.
 \end{lemma}
@@
 \begin{remark}\label{rem:pullback-of-projection}
-  Note that for $ X, Y, Z : C $ and $ f: C(Y, X) $, the following diagram shows that $ f^* \Delta_X Z \cong \Delta_Y Z $:
+  Note that for $ X, Y, Z : \C $ and $ f: \C(Y, X) $, the following diagram shows that $ f^* \Delta_X Z \cong \Delta_Y Z $:
   \begin{center}
@@
 \begin{lemma}\label{lem:constant-dependent-product}
-  For $ Z, X, Y : C $ and $ p_1 : X \times Y \to X $,
+  For $ Z, X, Y : \C $ and $ p_1 : X \times Y \to X $,
   \[ \prod_{p_1} \Delta_{X \times Y} Z \cong \Delta_X Z^Y \]
@@
 \begin{proof}
-  First of all, note that $ (C \downarrow X \times Y) \cong ((C \downarrow X) \downarrow \Delta_X Y) $.
-Also note that the composite morphism $ (X \times Y) \times Z \xrightarrow{p_1} X \times Y \xrightarrow{p_1} X $ is the element $ \Delta_X (Z \times Y) : (C \downarrow X) $.
+  First of all, note that $ (\C \downarrow X \times Y) \cong ((\C \downarrow X) \downarrow \Delta_X Y) $.
+Also note that the composite morphism $ (X \times Y) \times Z \xrightarrow{p_1} X \times Y \xrightarrow{p_1} X $ is the element $ \Delta_X (Z \times Y) : (\C \downarrow X) $.
 
@@
 
-  By Lemma \ref{lem:delta-exponentials}, $ \Delta_X $ preserves exponential objects, so the morphism on the right is $ \Delta_X p_1^Y : (C \downarrow X)(\Delta_X (Y \times Z)^Y, \Delta_X Y^Y) $.
+  By Lemma \ref{lem:delta-exponentials}, $ \Delta_X $ preserves exponential objects, so the morphism on the right is $ \Delta_X p_1^Y : (\C \downarrow X)(\Delta_X (Y \times Z)^Y, \Delta_X Y^Y) $.
 However, we have an isomorphism $ (Y \times Z)^Y \cong Y^Y \times Y^Z $, and then the morphism on the right becomes
-  \[ \Delta_X p_1 : (C \downarrow X)(\Delta_X(Y^Y \times Y^Z), \Delta_X Y^Y) \]
+  \[ \Delta_X p_1 : (\C \downarrow X)(\Delta_X(Y^Y \times Y^Z), \Delta_X Y^Y) \]
   We also have an isomorphism $ X \cong \Delta_X I $. Then by Lemma \ref{lem:delta-limits} and Remark \ref{rem:pullback-of-projection}, the pullback of this diagram is $ \Delta_X Z^Y $:
@@
 \begin{definition}
-  Let $ C $ be a category with terminal object $ I $. For an object $ X: C $, a \iindex{global element} of $ X $ is a morphism $ f: C(I, X) $.
+  Let $ \C $ be a category with terminal object $ I $. For an object $ X: \C $, a \iindex{global element} of $ X $ is a morphism $ f: \C(I, X) $.
 \end{definition}
@@
 
-Let $ A $, $ B $ and $ C $ be categories and let $ F : A \to B $ be a functor.
-\begin{definition}
-  Precomposition gives a functor between functor categories $ F_* : [B, C] \to [A, C] $.
-If $ F_* $ has a left adjoint, we will denote call this adjoint functor the \textit{left Kan extension}\index{Kan extension!left} along $ F $ and denote it $ \mathrm{Lan}_F : [A, C] \to [B, C] $.
-
-  \begin{center}
-    \begin{tikzcd}
-      A \arrow[rr, "F"] \arrow[rd, dashed, "F_* G"'] & & B \arrow[ld, "G"]\\
-      & C
+Let $ \A $, $ \B $ and $ \C $ be categories and let $ F : \A \to \B $ be a functor.
+\begin{definition}
+  Precomposition gives a functor between functor categories $ F_* : [\B, \C] \to [\A, \C] $.
+If $ F_* $ has a left adjoint, we will denote call this adjoint functor the \textit{left Kan extension}\index{Kan extension!left} along $ F $ and denote it $ \mathrm{Lan}_F : [\A, \C] \to [\B, \C] $.
+
+  \begin{center}
+    \begin{tikzcd}
+      \A \arrow[rr, "F"] \arrow[rd, dashed, "F_* G"'] & & \B \arrow[ld, "G"]\\
+      & \C
     \end{tikzcd}
@@
     \begin{tikzcd}
-      A \arrow[rr, "F"] \arrow[rd, "G"'] & & B \arrow[ld, dashed, "\Lan F G"]\\
-      & C
-    \end{tikzcd}
-  \end{center}
-
-  Analogously, when $ F_* $ has a right adjoint, one calls this the \textit{right Kan extension}\index{Kan extension!right} along $ F $ and denote it $ \mathrm{Ran}_F: [A, C] \to [B, C] $.
+      \A \arrow[rr, "F"] \arrow[rd, "G"'] & & \B \arrow[ld, dashed, "\Lan F G"]\\
+      & \C
+    \end{tikzcd}
+  \end{center}
+
+  Analogously, when $ F_* $ has a right adjoint, one calls this the \textit{right Kan extension}\index{Kan extension!right} along $ F $ and denote it $ \mathrm{Ran}_F: [\A, \C] \to [\B, \C] $.
 \end{definition}
@@
 \begin{lemma}
-  If $ C $ has colimits, $ \Lan F {} $ exists.
-\end{lemma}
-\begin{proof}
-  First of all, for objects $ b: B $, we take
-  \[ \Lan F G(b) := \text{colim} \left( (F \downarrow b) \to A \xrightarrow G C \right). \]
-
-  Here, $ (F \downarrow b) $ denotes the comma category with as objects the morphisms $ B(F(a), b) $ for all $ a: A $, and as morphisms from $ f: B(F(a), b) $ to $ f^\prime: B(F(a^\prime), b) $ the morphisms $ g: A(a, a^\prime) $ that make the diagram commute:
-  \begin{center}
-    \begin{tikzcd}
-      F(a) \arrow[rr, "F(g)"] \arrow[rd, "f"'] & & F(a^\prime) \arrow[ld, "f^\prime"]\\
-      & b
-    \end{tikzcd}
-  \end{center}
-  and $ (F \downarrow b) \to A $ denotes the projection functor that sends $ f: B(F(a_1), b) $ to $ a_1 $.
-
-  Now, a morphism $ h: B(b, b^\prime) $ gives a morphism of diagrams, sending the $ F(a) $ corresponding to $ f: B(G(a), b) $ to the $ F(a) $ corresponding to $ f \cdot h: B(G(a), b^\prime) $.
-From this, we get a morphism $ \Lan F G(h): C(\Lan F G(b), \Lan F G(b^\prime)) $.
-
-  The unit of the adjunction is a natural transformation $ \eta: \id{[A, C]} \Rightarrow \Lan F {} \bullet F_* $.
-We will define this pointwise, for $ G: [A, C] $ and $ a: A $.
-Our diagram contains the $ G(a) $ corresponding to $ \id{F(a)}: (F \downarrow F(a)) $ and the colimit cocone gives a morphism
-  \[ \eta_G(a) : C(G(a), \Lan F G (F(a))), \]
-  the latter being equal to $ (\Lan F {} \bullet F_*)(G)(a) $.
-
-  The counit of the adjunction is a natural transformation $ \epsilon: F_* \bullet \Lan F {} \Rightarrow \id{[B, C]} $.
-We will also define this pointwise, for $ G: [B, C] $ and $ b: B $.
-The diagram for $ \Lan F (F_* G)(b) $ consists of $ G(F(a)) $ for all $ f: B(F(a), b) $.
-Then, by the universal property of the colimit, the morphisms $ G(f): C(G(F(a)), G(b)) $ induce a morphism
-  \[ \epsilon_G(b) : C(\Lan F (F_* G)(b), G(b)). \]
+  If $ \C $ has colimits, $ \Lan F {} $ exists.
+\end{lemma}
+\begin{proof}
+  First of all, for objects $ X: \B $, we take
+  \[ (\Lan F G)(X) := \text{colim} \left( (F \downarrow X) \to \A \xrightarrow G \C \right). \]
+
+  Here, $ (F \downarrow X) $ denotes the comma category with as objects the morphisms $ \B(F(Y), X) $ for all $ Y: \A $, and as morphisms from $ f_1: \B(F(Y_1), X) $ to $ f_2: \B(F(Y_2), X) $ the morphisms $ g: \A(Y_1, Y_2) $ that make the diagram commute:
+  \begin{center}
+    \begin{tikzcd}
+      F(Y_1) \arrow[rr, "F(g)"] \arrow[rd, "f_1"'] & & F(Y_2) \arrow[ld, "f_2"]\\
+      & X
+    \end{tikzcd}
+  \end{center}
+  and $ (F \downarrow X) \to \A $ denotes the projection functor that sends $ f: \B(F(Y), X) $ to $ Y $.
+
+  Now, a morphism $ h: \B(X_1, X_2) $ gives a morphism of diagrams, sending the $ G(Y) $ corresponding to $ f: \B(F(Y), X_1) $ to the $ G(Y) $ corresponding to $ f \cdot h: \B(F(Y), X_2) $.
+From this, we get a morphism $ (\Lan F G)(h): \C((\Lan F G)(X_1), (\Lan F G)(X_2)) $.
+
+  The unit of the adjunction is a natural transformation $ \eta: \id{[\A, \C]} \Rightarrow \Lan F {} \bullet F_* $.
+We will define this pointwise, for $ G: [\A, \C] $ and $ Y: \A $.
+Our diagram contains the $ G(Y) $ corresponding to $ \id{F(Y)}: (F \downarrow F(Y)) $ and the colimit cocone gives a morphism
+  \[ \eta_G(Y) : \C(G(Y), \Lan F G (F(Y))), \]
+  the latter being equal to $ (\Lan F {} \bullet F_*)(G)(Y) $.
+
+  The counit of the adjunction is a natural transformation $ \epsilon: F_* \bullet \Lan F {} \Rightarrow \id{[\B, \C]} $.
+We will also define this pointwise, for $ G: [\B, \C] $ and $ X: \B $.
+The diagram for $ \Lan F (F_* G)(X) $ consists of $ G(F(Y)) $ for all $ f: \B(F(Y), X) $.
+Then, by the universal property of the colimit, the morphisms $ G(f): \C(G(F(Y)), G(X)) $ induce a morphism
+  \[ \epsilon_G(X) : \C(\Lan F (F_* G)(X), G(X)). \]
 \end{proof}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.SurjectivePrecomposition}{pre_comp_split_essentially_surjective}]\label{lem:lan-precomp-iso}
-  If $ F : A \to B $ is a fully faithful functor, and $ C $ is a category with colimits, $ \eta: \id{[A, C]} \Rightarrow \Lan F {} \bullet F_* $ is a natural isomorphism.
-\end{lemma}
-\begin{proof}
-  To show that $ \eta $ is a natural isomorphism, we have to show that $ \eta_G(a^\prime): G(a^\prime) \Rightarrow \Lan F G(F(a^\prime)) $ is an isomorphism for all $ G: [A, C] $ and $ a^\prime: A $.
-Since a left adjoint is unique up to natural isomorphism (\autocite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(a^\prime)) $ is given by
-  \[ \text{colim} ((F \downarrow F(a^\prime)) \to A \xrightarrow G C). \]
-  Now, the diagram for this colimit consists of $ G(a) $ for each arrow $ f: B(F(a), F(a^\prime)) $.
-Since $ F $ is fully faithful, we have $ f = F(\overline f) $ for some $ \overline f: A(a, a^\prime) $.
-If we now take the arrows $ G(\overline f): C(G(a), G(a^\prime)) $, the universal property of the colimit gives an arrow
-  \[ \varphi: C(\Lan F G(F(a^\prime)), G(a^\prime)) \]
-  which constitutes an inverse to $ \eta_G(a^\prime) $. The proof of this revolves around properties of the colimit and its (induced) morphisms.
-\end{proof}
-
-\begin{remark}
-  In the same way, if $ C $ has limits, $ \epsilon $ is a natural isomorphism.
+  If $ F : \A \to \B $ is a fully faithful functor, and $ \C $ is a category with colimits, $ \eta: \id{[\A, \C]} \Rightarrow \Lan F {} \bullet F_* $ is a natural isomorphism.
+\end{lemma}
+\begin{proof}
+  To show that $ \eta $ is a natural isomorphism, we have to show that $ \eta_G(Y): G(Y) \Rightarrow \Lan F G(F(Y)) $ is an isomorphism for all $ G: [\A, \C] $ and $ Y: \A $.
+Since a left adjoint is unique up to natural isomorphism (\autocite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(Y)) $ is given by
+  \[ \text{colim} ((F \downarrow F(Y)) \to \A \xrightarrow G \C). \]
+  Now, the diagram for this colimit consists of $ G(X) $ for each arrow $ f: \B(F(X), F(Y)) $.
+Since $ F $ is fully faithful, we have $ f = F(\overline f) $ for some $ \overline f: \A(X, Y) $.
+If we now take the arrows $ G(\overline f): \C(G(X), G(Y)) $, the universal property of the colimit gives an arrow
+  \[ \varphi: \C(\Lan F G(F(Y)), G(Y)) \]
+  which constitutes an inverse to $ \eta_G(Y) $. The proof of this revolves around properties of the colimit and its (induced) morphisms.
+\end{proof}
+
+\begin{remark}
+  In the same way, if $ \C $ has limits, $ \epsilon $ is a natural isomorphism.
 \end{remark}
@@
 \begin{corollary}\label{cor:surjective-precomposition}
-  If $ C $ has limits or colimits, precomposition of functors $ [B, C] $ along a fully faithful functor is (split) essentially surjective.
+  If $ \C $ has limits or colimits, precomposition of functors $ [\B, \C] $ along a fully faithful functor is (split) essentially surjective.
 \end{corollary}
 \begin{proof}
-  For each $ G: [A, C] $ we take $ \Lan F G: [B, C] $, and we have $ F_*(\Lan F G) \cong G $.
+  For each $ G: [\A, \C] $ we take $ \Lan F G: [\B, \C] $, and we have $ F_*(\Lan F G) \cong G $.
 \end{proof}
@@
 \begin{corollary}
-  If $ C $ has colimits (resp. limits), left (resp. right) Kan extension of functors $ [A, C] $ along a fully faithful functor is fully faithful.
+  If $ \C $ has colimits (resp. limits), left (resp. right) Kan extension of functors $ [\A, \C] $ along a fully faithful functor is fully faithful.
 \end{corollary}
@@
   Since left Kan extension along $ F $ is the left adjoint to precomposition, we have
-  \[ [A, C](\Lan F G, \Lan F G^\prime) \cong [B, C](G, F_*(\Lan F G^\prime)) \cong [B, C](G, G^\prime). \]
+  \[ [\A, \C](\Lan F G, \Lan F G^\prime) \cong [\B, \C](G, F_*(\Lan F G^\prime)) \cong [\B, \C](G, G^\prime). \]
 \end{proof}
@@
 \begin{definition}
-  Let $ C, D $ be categories and $ F : \op C \times C \to D $ a functor. We define the \iindex{coend} $ \int^{c : C} F(c, c) $ to be the colimit
-  \begin{center}
-    \begin{tikzcd}
-      \displaystyle\coprod_{\substack{f : C(a, b)}} F(b, a)
-        \arrow[r, shift left, "{F(f, \id b)}"]
-        \arrow[r, shift right, "{F(\id a, f)}"'] &
-      \displaystyle\coprod_{c : C} F(c, c)
+  Let $ \C, \D $ be categories and $ F : \op \C \times \C \to \D $ a functor. We define the \iindex{coend} $ \int^{X : \C} F(X, X) $ to be the colimit
+  \begin{center}
+    \begin{tikzcd}
+      \displaystyle\coprod_{f : \C(Y, Z)} F(Z, Y)
+        \arrow[r, shift left, "{F(f, \id Z)}"]
+        \arrow[r, shift right, "{F(\id Y, f)}"'] &
+      \displaystyle\coprod_{X : \C} F(X, X)
         \arrow[r, dashed] &
-      \displaystyle\int^C F
-    \end{tikzcd}
-  \end{center}
-\end{definition}
-
-\begin{remark}
-  An alternative way to phrase this, is that $ \int^C F : D $ is an object, equipped with arrows $ F(c, c) \to \int^C F $ such that for all $ f: C(a, b) $, the following diagram must commute
-  \begin{center}
-    \begin{tikzcd}
-      F(b, a) \arrow[r, "{F(f, \id a)}"] \arrow[d, "{F(\id b, f)}"] & F(a, a) \arrow[d]\\
-      F(b, b) \arrow[r] & \int^C F
-    \end{tikzcd}
-  \end{center}
-  and such that for any other $ G : D $ with the same properties, we have a unique morphism $ \int_C F \to G $, making the triangles commute
-  \begin{center}
-    \begin{tikzcd}
-      F(c, c) \arrow[r] \arrow[rd] & \int_C F \arrow[d]\\
+      \displaystyle\int^\C F
+    \end{tikzcd}
+  \end{center}
+\end{definition}
+
+\begin{remark}
+  An alternative way to phrase this, is that $ \int^\C F : \D $ is an object, equipped with arrows $ F(X, X) \to \int^\C F $ such that for all $ f: \C(Y, Z) $, the following diagram must commute
+  \begin{center}
+    \begin{tikzcd}
+      F(Z, Y) \arrow[r, "{F(f, \id Y)}"] \arrow[d, "{F(\id Z, f)}"] & F(Y, Y) \arrow[d]\\
+      F(Z, Z) \arrow[r] & \int^\C F
+    \end{tikzcd}
+  \end{center}
+  and such that for any other $ G : \D $ with the same properties, we have a unique morphism $ \int_\C F \to G $, making the triangles commute
+  \begin{center}
+    \begin{tikzcd}
+      F(X, X) \arrow[r] \arrow[rd] & \int_\C F \arrow[d]\\
       & G
@@
   Left Kan extension can be expressed as a coend:
-  \[ \Lan F G(b) = \int^{a : A} D(F a, b) \cdot G a \]
-  where $ S \cdot X $ for $ S $ a set and $ X : C $ denotes the `copower', which in most cases can be defined as
-  \[ S \cdot X = \coprod_{s : S} X. \]
+  \[ \Lan F G(Y) = \int^{X : \A} \D(F a, Y) \cdot G X \]
+  where $ S \cdot Z $ for $ S $ a set and $ Z : \C $ denotes the `copower', which intuitively acts as the $ S $-fold coproduct:
+  \[ S \cdot Z = \coprod_{s : S} Z. \]
 \end{remark}
@@
 \begin{definition}[\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_to_category_ob}]
-  We can construct a category $ C_M $ with $ C_{M0} = \{ \star \} $, $ C_M(\star, \star) = M $.
+  We can construct a category $ \C_M $ with $ \C_{M0} = \{ \star \} $, $ \C_M(\star, \star) = M $.
 The identity morphism on $ \star $ is the identity $ 1: M $.
-The composition is given by multiplication $ g \cdot_{C_M} f = f \cdot_M g $.
+The composition is given by multiplication $ g \cdot_{\C_M} f = f \cdot_M g $.
 \end{definition}
@@
 
-  A monoid morphism $ f: M \to M^\prime $ is equivalent to a functor $ F_f: C_M \to C_{M^\prime} $.
-Any functor between $ C_M $ and $ C_{M^\prime} $ sends $ \star_M $ to $ \star_{M^\prime} $.
-The monoid morphism manifests as $ F_f(m) = f(m) $ for $ m: C_M(\star, \star) = M $.
+  A monoid morphism $ f: M \to N $ is equivalent to a functor $ F_f: \C_M \to \C_N $.
+Any functor $ F_f : \C_M \to \C_N $ sends $ \star_M $ to $ \star_N $ and corresponds to the monoid morphism as $ F_f(m) = f(m) $ for $ m: \C_M(\star, \star) = M $.
 \end{remark}
@@
 \begin{proof}
-  Given an isomorphism $ f: M \to M^\prime $.
-Then we have functors $ F_f: C_M \to C_{M^\prime} $ and $ F_{f^{-1}}: C_{M^\prime} \to C_M $.
-Take the identity natural transformations $ \eta: \id{C_M} \Rightarrow F_f \bullet F_{f^{-1}} $ and $ \epsilon: F_{f^{-1}} \bullet F_f \Rightarrow \id{C_{M^\prime}} $.
+  Given an isomorphism $ f: M \xrightarrow \sim N $, we have functors $ F_f: \C_M \to \C_N $ and $ F_{f^{-1}}: \C_N \to \C_M $.
+Take the identity natural transformations $ \eta: \id{\C_M} \Rightarrow F_f \bullet F_{f^{-1}} $ and $ \epsilon: F_{f^{-1}} \bullet F_f \Rightarrow \id{\C_N} $.
 Of course these are natural isomorphisms.
@@
 \begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_action}]
-  A \textit{right monoid action}\index{monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, m^\prime: M $,
-  \[ x 1 = x \qquad \text{and} \qquad (x m) m^\prime = x (m \cdot m^\prime). \]
+  A \textit{right monoid action}\index{monoid action} of $ M $ on a set $ X $ is a function $ X \times M \to X $ such that for all $ x: X $, $ m, n: M $,
+  \[ x 1 = x \qquad \text{and} \qquad (x m) n = x (m \cdot n). \]
 \end{definition}
@@
 \begin{lemma}[\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_presheaf_action_equivalence}]
-  Presheaves on $ C_M $ are equivalent to sets with a right $ M $-action.
+  There is an adjoint equivalence between the presheaf category $ P \C_M $ and $ \RAct M $.
 \end{lemma}
@@
 \begin{remark}
-  Since the category of sets with an $ M $-action is equivalent to a presheaf category, it has all limits.
+  Since $ \RAct M $ is equivalent to a presheaf category, it has all limits.
 However, we can make this concrete.
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_action_global_element_fixpoint_iso}]\label{lem:global-action-elements}
-  The global elements of a set with right $ M $-action correspond to the elements that are invariant under the $ M $-action.
-\end{lemma}
-\begin{proof}
-  A global element of $ X $ is a morphism $ \varphi: \{ \star \} \to X $ such that for all $ m: M $, $ \varphi(\star)m = \varphi(\star m) = \varphi(\star) $.
-Therefore, it is given precisely by the element $ \varphi(\star): X $, which must be invariant under the $ M $-action.
+  The global elements of $ X : \RAct M $ correspond to $ x : X $ that are invariant under the $ M $-action.
+\end{lemma}
+\begin{proof}
+  A global element of $ X $ is a morphism $ f: \{ \star \} \to X $ such that for all $ m: M $, $ f(\star)m = f(\star m) = f(\star) $.
+Therefore, it is given precisely by the element $ f(\star): X $, which must be invariant under the $ M $-action.
 \end{proof}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{is_exponentiable_monoid_action}]
-  The category $ C $ of sets with an $ M $-action has exponentials.
-\end{lemma}
-\begin{proof}
-  Given sets with $ M $-action $ X $ and $ Y $.
-Consider the set $ C(M \times X, Y) $ with an $ M $-action given by $ \phi m^\prime(m, x) = \phi(m^\prime m, x) $.
-This is the exponential object $ X^Y $, with the (universal) evaluation morphism $ X \times X^Y \to Y $ given by $ (x, \phi) \mapsto \phi(1, x) $.
+  The category $ \RAct M $ has exponentials.
+\end{lemma}
+\begin{proof}
+  Given $ X, Y : \RAct M $.
+Consider the set $ \C(M \times X, Y) $ with an $ M $-action given by $ (f m^\prime)(m, x) = f(m^\prime m, x) $ for $ f : \C(M \times X, Y) $.
+This is the exponential object $ X^Y $, with the (universal) evaluation morphism $ X \times X^Y \to Y $ given by $ (x, f) \mapsto f(1, x) $.
 Explicitly, we get a natural isomorphism $ \psi: \RAct M(Z \times Y, X) \xrightarrow \sim \RAct M(Z, X^Y) $ given by
@@
 \begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{monoid_monoid_action}]
-  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot n $ for $ m: U_M $ and $ n: M $. Note that this is the Yoneda embedding of the object $ \star : C_M $.
+  We can view $ M $ as a set $ U_M $ with right $ M $-action $ m n = m \cdot n $ for $ m: U_M $ and $ n: M $. Note that $ U_M $ is the Yoneda embedding of the object $ \star : \C_M $.
 \end{definition}
@@
 
-Let $ \varphi: M \to M^\prime $ be a morphism of monoids.
-
-Remember that sets with a right monoid action are equivalent to presheaves on the monoid category.
-Also, $ \varphi $ is equivalent to a functor between the monoid categories.
+Let $ f: M \to N $ be a morphism of monoids.
+
+Remember that $ \RAct M $ is equivalent to the functor category $ P \C_M $.
+Also, $ f $ is equivalent to a functor $ F_f : \C_M \to \C_N $.
 The following is a specific case of the concepts in the section about Kan extension:
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_restriction_functor}]
-  We get a \iindex{restriction of scalars} functor $ \varphi^* $ from sets with a right $ M^\prime $-action to sets with a right $ M $-action.
-\end{lemma}
-\begin{proof}
-  Given a set $ X $ with right $ M^\prime $-action, take the set $ X $ again, and give it a right $ M $-action, sending $ (x, m) $ to $ x \varphi(m) $.
-
-  On morphisms, send an $ M^\prime $-equivariant morphism $ f: X \to X^\prime $ to the $ M $-equivariant morphism $ f: X \to X^\prime $.
-\end{proof}
-
-Since $ \SET $ has colimits, and restriction of scalars corresponds to precomposition of presheaves (on $ C_{M^\prime} $), we can give it a left adjoint.
+  We get a \iindex{restriction of scalars} functor $ f^* : \RAct N \to \RAct M $.
+\end{lemma}
+\begin{proof}
+  Given a set $ X $ with right $ N $-action, take the set $ X $ again, and give it a right $ M $-action, sending $ (x, m) $ to $ x f(m) $.
+
+  On morphisms, send an $ N $-equivariant morphism $ f: X \to Y $ to the $ M $-equivariant morphism $ f: X \to Y $.
+\end{proof}
+
+Since $ \SET $ has colimits, and restriction of scalars corresponds to precomposition of $ \C_{N} $-presheaves, we can give it a left adjoint.
 This is the (pointwise) left Kan extension, which boils down to a very concrete definition, reminiscent of a tensor product:
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_functor}]\label{lem:scalar-extension}
-  We get an \iindex{extension of scalars} functor $ \varphi_* $ from sets with a right $ M $-action to sets with a right $ M^\prime $-action.
-\end{lemma}
-\begin{proof}
-  Given a set $ X $ with right $ M $-action.
-Take $ Y = X \times M^\prime / \sim $ with the relation $ (x m, m^\prime) \sim (x, \varphi(m) \cdot m^\prime) $ for $ m: M $.
-This has a right $ M^\prime $-action given by $ (x, m^\prime)n^\prime = (x, m^\prime n^\prime) $.
-
-  On morphisms, it sends the $ m $-equivariant $ f: X \to X^\prime $ to the morphism $ (x, m^\prime) \mapsto (f(x), m^\prime) $.
+  We get an \iindex{extension of scalars} functor $ f_* : \RAct M \to \RAct N $.
+\end{lemma}
+\begin{proof}
+  Given $ X : \RAct M $, take $ Y = X \times N / \sim $ with the relation $ (x m, n) \sim (x, f(m) \cdot n) $ for $ m: M $. This has a right $ N $-action given by $ (x, n_1)n_2 = (x, n_1 n_2) $.
+
+  On morphisms, it sends the $ m $-equivariant $ f: X \to X^\prime $ to the morphism $ (x, n) \mapsto (f(x), n) $.
 \end{proof}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_preserves_monoid_monoid_action}]\label{lem:scalar-extension-monoid-monoid-action}
-  For $ U_M $ the set $ M $ with right $ M $-action, we have $ \varphi_*(U_M) \cong U_{M^\prime} $.
-\end{lemma}
-\begin{proof}
-  The proof relies on the fact that for all $ m: U_M $ and $ m^\prime : M^\prime $, we have
-  \[ (m, m^\prime) \sim (1, \varphi(m) m^\prime). \]
-\end{proof}
-
-Consider the category $ D $ with $ D_0 = M^\prime $ and
-\[ D(m^\prime, \overline m^\prime) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime \}. \]
+  For $ U_M $ the set $ M $ with right $ M $-action, we have $ f_*(U_M) \cong U_{N} $.
+\end{lemma}
+\begin{proof}
+  The proof relies on the fact that for all $ m: U_M $ and $ n : N $, we have
+  \[ (m, n) \sim (1, f(m) n). \]
+\end{proof}
+
+Consider the category $ \D $ with $ \D_0 = N $ and
+\[ \D(n_1, n_2) = \{ m: M \mid f(m) \cdot n_1 = n_2 \}. \]
 
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_preserves_terminal}]\label{lem:scalar-extension-terminal}
-  Suppose that $ D $ has a weakly terminal element. Then for $ I_M $ the terminal object in the category of sets with a right $ M $-action, we have $ \varphi_*(I_M) \cong I_{M^\prime} $.
-\end{lemma}
-\begin{proof}
-  If $ D $ has a weakly terminal object, there exists $ m_0 : M^\prime $ such that for all $ m^\prime: M^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = m_0 $.
-
-  The proof relies on the fact that every element of $ \varphi_*(I_M) $ is given by some $ (\star, m^\prime) $, but then
-  \[ (\star, m^\prime) = (\star \cdot m, m^\prime) \sim (\star, \varphi(m) \cdot m^\prime) = (\star, m_0), \]
-  so $ \varphi_*(I_M) $ has exactly $ 1 $ element.
-\end{proof}
-
-\begin{remark}
-  For $ \varphi_* $ to preserve terminal objects, we actually only need $ D $ to be connected.
-The fact that $ \varphi_*(I_M) $ is a quotient by a symmetric and transitive relation then allows us to `walk' from any $ (\star, m^\prime_1) $ to any other $ (\star, m^\prime_2) $ in small steps.
-\end{remark}
-
-For any $ m^\prime_1, m^\prime_2: M^\prime $, consider the category $ D_{m^\prime_1, m^\prime_2} $, given by
-\[ D_{m^\prime_1, m^\prime_2, 0} = \{ (m^\prime, m_1, m_2): M^\prime \times M \times M \mid m_i^\prime = \varphi(m_i) \cdot m^\prime \} \]
+  Suppose that $ \D $ has a weakly terminal element. Then for $ I_M : \RAct M $ the terminal object, we have $ f_*(I_M) \cong I_{N} $.
+\end{lemma}
+\begin{proof}
+  If $ \D $ has a weakly terminal object, there exists $ n_0 : N $ such that for all $ n: N $, there exists $ m: M $ such that $ f(m) \cdot n = n_0 $.
+
+  The proof then relies on the fact that every element of $ f_*(I_M) $ is given by some $ (\star, n) $, but then there exists some $ m : M $ such that
+  \[ (\star, n) = (\star \cdot m, n) \sim (\star, f(m) \cdot n) = (\star, n_0), \]
+  so $ f_*(I_M) $ has exactly $ 1 $ element.
+\end{proof}
+
+\begin{remark}
+  For $ f_* $ to preserve terminal objects, we actually only need $ \D $ to be connected.
+The fact that $ f_*(I_M) $ is a quotient by a symmetric and transitive relation then allows us to `walk' from any $ (\star, n_1) $ to any other $ (\star, n_2) $ in small steps.
+\end{remark}
+
+For any $ n_1, n_2: N $, consider the category $ \D_{n_1, n_2} $, given by
+\[ \D_{n_1, n_2, 0} = \{ (n, m_1, m_2): N \times M \times M \mid n_i = f(m_i) \cdot n \} \]
 and
-\[ D_{m^\prime_1, m^\prime_2}((m^\prime, m_1, m_2), (\overline m^\prime, \overline m_1, \overline m_2)) = \{ m: M \mid \varphi(m) \cdot m^\prime = \overline m^\prime, m_i = \overline m_i \cdot m \}.
-\]
+\[ \D_{n_1, n_2}((n, m_1, m_2), (\overline n, \overline m_1, \overline m_2)) = \{ m: M \mid f(m) \cdot n = \overline n, m_i = \overline m_i \cdot m \}. \]
 
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_preserves_binproducts}]\label{lem:scalar-extension-product}
-  Suppose that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object for all $ m^\prime_1, m^\prime_2: M^\prime $.
-Then for sets $ A $ and $ B $ with right $ M $-action, we have $ \varphi_*(A \times B) \cong \varphi_*(A) \times \varphi_*(B) $.
-\end{lemma}
-\begin{proof}
-  Now, any element in $ \varphi_*(A) \times \varphi_*(B) = (A \times M^\prime / \sim) \times (B \times M^\prime / \sim) $ is given by some $ (a, m^\prime_1, b, m^\prime_2) $.
-
-  The fact that $ D_{m^\prime_1, m^\prime_2} $ has a weakly terminal object means that we have some $ \overline m^\prime: M^\prime $ and $ \overline m_1, \overline m_2: M $ with $ m_i^\prime = \varphi(\overline m_i) \cdot \overline m^\prime $.
+  Suppose that $ \D_{n_1, n_2} $ has a weakly terminal object for all $ n_1, n_2: N $. Then for $ X, Y : \RAct M $, we have $ f_*(X \times Y) \cong f_*(X) \times f_*(Y) $.
+\end{lemma}
+\begin{proof}
+  Now, any element in $ f_*(X) \times f_*(Y) = (X \times N / \sim) \times (Y \times N / \sim) $ is given by some $ (a, n_1, b, n_2) $.
+
+  The fact that $ \D_{n_1, n_2} $ has a weakly terminal object means that we have some $ \overline n: N $ and $ \overline m_1, \overline m_2: M $ with $ n_i = f(\overline m_i) \cdot \overline n $.
 Therefore,
-  \[ (a, m^\prime_1, b, m^\prime_2) = (a, \varphi(\overline m_1) \cdot \overline m^\prime, b, \varphi(\overline m_2) \cdot \overline m^\prime) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime), \]
-  so this is equivalent to some element in $ \varphi_*(A \times B) = (A \times B \times M^\prime / \sim) $. Note that this trivially respects the right $ M^\prime $-action.
-
-  The fact that $ (\overline m^\prime, \overline m_1, \overline m_2) $ is weakly terminal also means that for all $ m^\prime: M^\prime $ and $ m_1, m_2: M $ with $ m_i^\prime = \varphi(m_i) \cdot m^\prime $, there exists $ m: M $ such that $ \varphi(m) \cdot m^\prime = \overline m^\prime $ and $ m_i = \overline m_i \cdot m $.
-This means that the equivalence that we established is actually well-defined: equivalent elements in $ \varphi_*(A) \times \varphi_*(B) $ are sent to equivalent elements in $ \varphi_*(A \times B) $.
-
-  Therefore, we have an isomorphism $ \psi: \varphi^*(A) \times \varphi^*(B) \xrightarrow{\sim} \varphi^*(A \times B) $.
+  \[ (a, n_1, b, n_2) = (a, f(\overline m_1) \cdot \overline n, b, f(\overline m_2) \cdot \overline n) \sim (a \overline m_1, \overline n, b \overline m_2, \overline n), \]
+  so this is equivalent to $ (a \overline m_1, b \overline m_2, \overline n) : f_*(X \times Y) $. Note that this trivially respects the right $ N $-action.
+
+  The fact that $ (\overline n, \overline m_1, \overline m_2) $ is weakly terminal also means that for all $ n: N $ and $ m_1, m_2: M $ with $ n_i = f(m_i) \cdot n $, there exists $ m: M $ such that $ f(m) \cdot n = \overline n $ and $ m_i = \overline m_i \cdot m $.
+This means that the equivalence that we established is actually well-defined: equivalent elements in $ f_*(X) \times f_*(Y) $ are sent to equivalent elements in $ f_*(X \times Y) $.
+
+  Therefore, we have an isomorphism $ \psi: f^*(X) \times f^*(Y) \xrightarrow{\sim} f^*(X \times Y) $.
 Now we only need to show that the projections are preserved by this isomorphism.
-To that end, take $ x = (a, m^\prime_1, b, m^\prime_2) \sim (a \overline m_1, \overline m^\prime, b \overline m_2, \overline m^\prime) : \varphi^*(A) \times \varphi^*(B) $.
+To that end, take $ x = (a, n_1, b, n_2) \sim (a \overline m_1, \overline n, b \overline m_2, \overline n) : f^*(X) \times f^*(Y) $.
 We have
-  \[ \varphi^*(\pi_1)(\psi(x)) = (a \overline m_1, \overline m^\prime) = \pi^\prime_1(x). \]
-  In the same way, $ \varphi^*(\pi_2) \circ \psi = \pi^\prime_2 $ and this concludes the proof.
+  \[ f^*(\pi_1)(\psi(x)) = (a \overline m_1, \overline n) = \pi^\prime_1(x). \]
+  In the same way, $ f^*(\pi_2) \circ \psi = \pi^\prime_2 $ and this concludes the proof.
 \end{proof}
@@
 \section{The Karoubi envelope}
-Let $ C $ be a category and $ X, Y : C $ objects. We will denote the type of section-retraction pairs of $ Y $ onto $ X $ with
-\[ X \triangleleft Y := \sum_{r : C(Y, X)} \sum_{s : C(X, Y)} s \cdot r = \id X. \]
-Now, note that for $ (r, s) : X \triangleleft Y $, $ r \cdot s: C(Y, Y) $ is an idempotent morphism, since $ r \cdot s \cdot r \cdot s = r \cdot s $.
-We can also wonder whether for an idempotent morphism $ f: C(X, X) $, we can find some $ Y : C $ and some $ (r, s) : X \triangleleft Y $ such that $ f = r \cdot s $.
+Let $ \C $ be a category and $ X, Y : \C $ objects. We will denote the type of section-retraction pairs of $ Y $ onto $ X $ with
+\[ X \triangleleft Y := \sum_{r : \C(Y, X)} \sum_{s : \C(X, Y)} s \cdot r = \id X. \]
+Now, note that for $ (r, s) : X \triangleleft Y $, $ r \cdot s: \C(Y, Y) $ is an idempotent morphism, since $ r \cdot s \cdot r \cdot s = r \cdot s $.
+We can also wonder whether for an idempotent morphism $ f: \C(X, X) $, we can find some $ Y : \C $ and some $ (r, s) : X \triangleleft Y $ such that $ f = r \cdot s $.
 If this is the case, we say that the idempotent $ f $ \textit{splits}\index{split idempotent}.
-If $ f $ does not split, we can wonder whether we can find an embedding $ \iota_C : C \hookrightarrow \overline C $ into some category $ \overline C $ such that the idempotent $ \iota_C(f): \overline C(\iota_C(X), \iota_C(X)) $ does split.
+If $ f $ does not split, we can wonder whether we can find an embedding $ \iota_\C : \C \hookrightarrow \overline \C $ into some category $ \overline \C $ such that the idempotent $ \iota_\C(f): \overline \C(\iota_\C(X), \iota_\C(X)) $ does split.
 This is one way to arrive at the \textit{Karoubi envelope}:
@@
 \begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}]
-  We define the category $ \overline C $.
-The objects of $ \overline C $ are tuples $ (X, f) $ with $ X: C $, $ f: C(X, X) $ such that $ f \cdot f = f $.
-The morphisms between $ (X_1, f_1) $ and $ (X_2, f_2) $ are morphisms $ g: C(X_1, X_2) $ such that $ f_1 \cdot g \cdot f_2 = g $.
+  We define the category $ \overline \C $.
+The objects of $ \overline \C $ are tuples $ (X, f) $ with $ X: \C $, $ f: \C(X, X) $ such that $ f \cdot f = f $.
+The morphisms between $ (X_1, f_1) $ and $ (X_2, f_2) $ are morphisms $ g: \C(X_1, X_2) $ such that $ f_1 \cdot g \cdot f_2 = g $.
 This can be summarized in the following diagram:
@@
   \end{center}
-  The identity morphism on $ (X, f) $ is given by $ f $ and $ \overline C $ inherits morphism composition from $ C $.
-\end{definition}
-This category is called the \iindex{Karoubi envelope}, the \textit{idempotent completion}\index{idempotent completion|see{Karoubi envelope}}, the \textit{category of retracts}\index{category of retracts|see{Karoubi envelope}}, or the \textit{Cauchy completion}\index{Cauchy completion|see{Karoubi envelope}} of $ C $.
-
-\begin{remark}
-  Note that for a morphism $ f: \overline C((c, a), (d, b)) $,
+  The identity morphism on $ (X, f) $ is given by $ f $ and $ \overline \C $ inherits morphism composition from $ \C $.
+\end{definition}
+This category is called the \iindex{Karoubi envelope}, the \textit{idempotent completion}\index{idempotent completion|see{Karoubi envelope}}, the \textit{category of retracts}\index{category of retracts|see{Karoubi envelope}}, or the \textit{Cauchy completion}\index{Cauchy completion|see{Karoubi envelope}} of $ \C $.
+
+\begin{remark}
+  Note that for a morphism $ f: \overline \C((X, a), (Y, b)) $,
   \[ a \cdot f = a \cdot a \cdot f \cdot b = a \cdot f \cdot b = f \]
@@
 \begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_inclusion}]
-  We have an embedding $ \iota_C: C \to \overline C $, sending $ c: C $ to $ (c, \id{c}) $ and $ f: C(c, d) $ to $ f $.
+  We have an embedding $ \iota_\C: \C \to \overline \C $, sending $ X: \C $ to $ (X, \id{X}) $ and $ f: \C(X, Y) $ to $ f $.
 \end{definition}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_is_retract}]\label{lem:karoubi-is-retract}
-  Every object $ c: \overline C $ is a retract of $ \iota_C(c_0) $ for some $ c_0: C $.
-\end{lemma}
-\begin{proof}
-  Note that $ c = (c_0, a) $ for some $ c_0: C $ and an idempotent $ a: c \to c $. We have
-  \[ (a, a) : (c, a) \triangleleft \iota_C(c), \]
-  since $ a \cdot a = a = \id{(c, a)} $, so $ (c, a) $ is a retract of $ \iota_C(c) $.
+  Every object $ X: \overline \C $ is a retract of $ \iota_\C(Y) $ for some $ Y: \C $.
+\end{lemma}
+\begin{proof}
+  Note that $ X = (Y, a) $ for some $ Y: \C $ and an idempotent $ a: Y \to Y $. We have
+  \[ (a, a) : (Y, a) \triangleleft \iota_\C(Y), \]
+  since $ a \cdot a = a = \id{X} $, so $ X $ is a retract of $ \iota_\C(Y) $.
 \end{proof}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_idempotent_splits}]
-  In $ \overline C $, every idempotent splits.
-\end{lemma}
-\begin{proof}
-  Take an idempotent $ e: \overline C(c, c) $.
-Note that $ c $ is given by an object $ c_0: C $ and an idempotent $ a: C(c_0, c_0) $.
-Also, $ e $ is given by some idempotent $ e: C(c_0, c_0) $ with $ a \cdot e \cdot a = e $.
-
-  Now, we have $ (c_0, e): \overline C $ and
-  \[ (e, e) : (c_0, e) \triangleleft (c_0, a), \]
-  because $ e \cdot e = e = \id{(c_0, e)} $. Also, $ e = e \cdot e $, so $ e $ is split.
+  In $ \overline \C $, every idempotent splits.
+\end{lemma}
+\begin{proof}
+  Take an idempotent $ f: \overline \C(X, X) $.
+Note that $ X $ is given by an object $ Y: \C $ and an idempotent $ a: \C(Y, Y) $.
+Also, $ f $ is given by some idempotent $ f: \C(Y, Y) $ with $ a \cdot f \cdot a = f $.
+
+  Now, we have $ (Y, f): \overline \C $ and
+  \[ (f, f) : (Y, f) \triangleleft X, \]
+  because $ f \cdot f = f = \id{(Y, f)} $. Also, $ f = f \cdot f $, so $ f $ is split.
 \end{proof}
@@
 \begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_inclusion_fully_faithful}]
-  Note that $ \iota_C $ is fully faithful, since
-  \[ \overline C((c, \id c), (d, \id d)) = \{ f: C(c, d) \mid \id c \cdot f \cdot \id d = f \} = C(c, d). \]
+  Note that $ \iota_\C $ is fully faithful, since
+  \[ \overline \C((X, \id X), (Y, \id Y)) = \{ f: \C(X, Y) \mid \id X \cdot f \cdot \id Y = f \} = \C(X, Y). \]
 \end{remark}
@@
 \begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_equalizer}, \coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_coequalizer}]\label{rem:retract-coequalizer}
-  Let $ D $ be a category and suppose that we have two objects $ d, d^\prime : D $ and a retraction
-  \[ (r, s) : d^\prime \triangleleft d. \]
-  Then $ d^\prime $ is the equalizer of \begin{tikzcd}
-    d \arrow[r, shift left, "\id d"] \arrow[r, shift right, "r \cdot s"'] & d \end{tikzcd} in the following way:
-
-  Suppose that we have an object $ c: D $ and a morphism $ f $ with $ (r \cdot s) \cdot f = f $.
-Then we get a morphism $ s \cdot f: D(d^\prime, c) $ such that $ f $ factors as $ r \cdot (s \cdot f) $.
-Also, for any $ g: D(d^\prime, c) $ with $ r \cdot g = f $, we have $ g = s \cdot r \cdot g = s \cdot f $:
-  \begin{center}
-    \begin{tikzcd}
-      d \arrow[r, left, "r"] \arrow[rd, "f"'] & d^\prime \arrow[r, "s"] \arrow[d, "s \cdot f" description] & d \arrow[ld, "f"]\\
-      & c
+  Let $ \D $ be a category and suppose that we have two objects $ X, Y : \D $ and a retraction
+  \[ (r, s) : Y \triangleleft X. \]
+  Then $ Y $ is the equalizer of \begin{tikzcd}
+    X \arrow[r, shift left, "\id X"] \arrow[r, shift right, "r \cdot s"'] & X \end{tikzcd} in the following way:
+
+  Suppose that we have an object $ Z: \D $ and a morphism $ f $ with $ (r \cdot s) \cdot f = f $.
+Then $ f $ factors as $ r \cdot (s \cdot f) $.
+Also, for any $ g: \D(Y, Z) $ with $ r \cdot g = f $, we have $ g = s \cdot r \cdot g = s \cdot f $:
+  \begin{center}
+    \begin{tikzcd}
+      X \arrow[r, left, "r"] \arrow[rd, "f"'] & Y \arrow[r, "s"] \arrow[d, "s \cdot f" description] & X \arrow[ld, "f"]\\
+      & Z
     \end{tikzcd}.
@@
 
-  In a similar way, $ d^\prime $ is also the coequalizer of the given diagram.
-
-  Now, note that if we have a coequalizer $ c^\prime $ of $ \id c $ and $ a $, and an equalizer $ d^\prime $ of $ \id d $ and $ b $, the universal properties of these give an equivalence
-  \[ D(c^\prime, d^\prime) \cong \{ f: D(c, d^\prime) \mid a \cdot f = f \} \cong \{ f: D(c, d) \mid a \cdot f = f = f \cdot b \}. \]
-  \begin{center}
-    \begin{tikzcd}
-      c \arrow[r, shift left, "\id c"] \arrow[r, shift right, "a"'] & c \arrow[r] \arrow[d] \arrow[rd] & c^\prime \arrow[d]\\
-      d & d \arrow[l, shift right, "\id d"'] \arrow[l, shift left, "b"] & d^\prime \arrow[l]
-    \end{tikzcd}
-  \end{center}
-\end{remark}
-
-Besides $ \overline C $, there is also another (classically equivalent) definition of the Karoubi envelope.
-An object in this alternative category is a presheaf $ F : PC $ that is a retract of the Yoneda embedding $ \yo(X) $ of an object $ X : C $.
+  In a similar way, $ Y $ is also the coequalizer of the given diagram.
+
+  Now, note that if we have a coequalizer $ W $ of $ \id Z $ and $ a $, and an equalizer $ Y $ of $ \id X $ and $ b $ (in particular, if $ W $ and $ Y $ are retracts), the universal properties of these give an equivalence
+  \[ \D(W, Y) \cong \{ f: \D(Z, Y) \mid a \cdot f = f \} \cong \{ f: \D(Z, X) \mid a \cdot f = f = f \cdot b \}. \]
+  \begin{center}
+    \begin{tikzcd}
+      Z \arrow[r, shift left, "\id Z"] \arrow[r, shift right, "a"'] & Z \arrow[r] \arrow[d] \arrow[rd] & W \arrow[d]\\
+      X & X \arrow[l, shift left, "\id X"] \arrow[l, shift right, "b"'] & Y \arrow[l]
+    \end{tikzcd}
+  \end{center}
+\end{remark}
+
+Besides $ \overline \C $, there is also another (classically equivalent) definition of the Karoubi envelope.
+An object in this alternative category is a presheaf $ F : P\C $ that is a retract of the Yoneda embedding $ \yo(X) $ of an object $ X : \C $.
 Note that there are two different ways to translate this to univalent foundations.
@@
 \begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope'}]\label{def:karoubi'}
-  We define the category $ \tilde C $ in which every object is a presheaf $ F : P C $, together with an object $ X : C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo (X) $.
-The morphisms from $ (F_1, X_1, r_1, s_1) $ to $ (F_2, X_2, r_2, s_2) $ are just the presheaf morphisms $ f: PC(F_1, F_2) $.
+  We define the category $ \tilde \C $ in which every object is a presheaf $ F : P \C $, together with an object $ X : \C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo (X) $.
+The morphisms from $ (F_1, X_1, r_1, s_1) $ to $ (F_2, X_2, r_2, s_2) $ are just the presheaf morphisms $ f: P\C(F_1, F_2) $.
 This can be summarized in the following diagram:
@@
 \begin{definition}\label{def:karoubi''}
-  We define the category $ \hat C $ as the full subcategory of $ P C $ consisting of objects $ F : P C $ such that there merely exist an object $ X: C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo(X) $, summarized in the following diagram:
+  We define the category $ \hat \C $ as the full subcategory of $ P \C $ consisting of objects $ F : P \C $ such that there merely exist an object $ X: \C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo(X) $, summarized in the following diagram:
   \begin{center}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_is_retract}]\label{lem:karoubi-equivalence}
-  We have an adjoint equivalence $ \overline C \xrightarrow \sim \tilde C $.
-\end{lemma}
-\begin{proof}
-  As shown in Remark \ref{rem:retract-coequalizer}, an object $ (X, f) : \overline C $ is the equalizer of $ \id X $ and $ f $. Therefore, we send it to the equalizer
-  \begin{center}
-    \begin{tikzcd}
-      F \arrow[r, "s"] & \yo(X) \arrow[r, shift left, "\id{\yo X}"] \arrow[r, shift right, "\yo(f)"'] & \yo(X)
-    \end{tikzcd}
-  \end{center}
-  Note that for $ \yo(f) $, we have $ \yo(f) \cdot \yo(f) = \yo(f) \cdot \id{\yo X} $, so the universal property of the equalizer gives a morphism $ r: PC(\yo(X), F) $ such that $ r \cdot s = \yo(f) $.
+  We have an adjoint equivalence $ \overline \C \xrightarrow \sim \tilde \C $.
+\end{lemma}
+\begin{proof}
+  As shown in Remark \ref{rem:retract-coequalizer}, an object $ (X, f) : \overline \C $ is the equalizer of $ \id X $ and $ f $. Therefore, we send it to the equalizer
+  \begin{center}
+    \begin{tikzcd}
+      F \arrow[r, "s"] & \yo(X) \arrow[r, shift left, "\id{\yo(X)}"] \arrow[r, shift right, "\yo(f)"'] & \yo(X)
+    \end{tikzcd}
+  \end{center}
+  Note that for $ \yo(f) $, we have $ \yo(f) \cdot \yo(f) = \yo(f) \cdot \id{\yo(X)} $, so the universal property of the equalizer gives a morphism $ r: P\C(\yo(X), F) $ such that $ r \cdot s = \yo(f) $.
 Using this same universal property, we can show that $ s \cdot r = \id F $.
-  We send a morphism $ g: \overline C((X_1, f_1), (X_2, f_2)) $ to
-  \[ s_1 \cdot \yo(g) \cdot r_2 : PC(F_1, F_2). \]
-  Note that this is an equivalence on the morphisms: For any morphism $ \bar g : PC(F_1, F_2) $, we have
-  \[ r_1 \cdot \bar g \cdot s_2 : PC(\yo(X_1), \yo(X_2)). \]
-  By the fully faithfulness of the Yoneda lemma, this corresponds to a morphism $ g : C(X_1, X_2) $ and we can show that these two maps between $ C((X_1, f_1), (X_2, f_2)) $ and $ \overline C(F_1, F_2) $ are inverses of each other.
-  \begin{center}
-    \begin{tikzcd}
-      F_1 \arrow[r, shift left, "s_1"] \arrow[d, "\bar g"] & \yo(X_1) \arrow[l, shift left, "r_1"] \arrow[r, shift left, "\id{\yo X_1}"] \arrow[r, shift right, "\yo(f_1)"'] \arrow[d, "\yo(g)"] & \yo(X_1)\\
-      F_2 \arrow[r, shift left, "s_2"] & \yo(X_2) \arrow[l, shift left, "r_2"] \arrow[r, shift left, "\id{\yo X_2}"] \arrow[r, shift right, "\yo(f_2)"'] & \yo(X_2)\\
+  We send a morphism $ g: \overline \C((X_1, f_1), (X_2, f_2)) $ to
+  \[ s_1 \cdot \yo(g) \cdot r_2 : P\C(F_1, F_2). \]
+  Note that this is an equivalence on the morphisms: For any morphism $ \bar g : P\C(F_1, F_2) $, we have
+  \[ r_1 \cdot \bar g \cdot s_2 : P\C(\yo(X_1), \yo(X_2)). \]
+  By the fully faithfulness of the Yoneda lemma, this corresponds to a morphism $ g : \C(X_1, X_2) $ and we can show that these two maps between $ \C((X_1, f_1), (X_2, f_2)) $ and $ \overline \C(F_1, F_2) $ are inverses of each other.
+  \begin{center}
+    \begin{tikzcd}
+      F_1 \arrow[r, shift left, "s_1"] \arrow[d, "\bar g"] & \yo(X_1) \arrow[l, shift left, "r_1"] \arrow[r, shift left, "\id{\yo(X_1)}"] \arrow[r, shift right, "\yo(f_1)"'] \arrow[d, "\yo(g)"] & \yo(X_1)\\
+      F_2 \arrow[r, shift left, "s_2"] & \yo(X_2) \arrow[l, shift left, "r_2"] \arrow[r, shift left, "\id{\yo(X_2)}"] \arrow[r, shift right, "\yo(f_2)"'] & \yo(X_2)\\
     \end{tikzcd}
@@
   Now, note that this map is also split essentially surjective.
-For some $ (F, X, r, s) : \tilde C $, $ r \cdot s $ is an idempotent morphism on $ \yo(X) $, and by fully faithfulness of the Yoneda Lemma, it corresponds to an idempotent morphism $ f $ on $ X $.
+For some $ (F, X, r, s) : \tilde \C $, $ r \cdot s $ is an idempotent morphism on $ \yo(X) $, and by fully faithfulness of the Yoneda Lemma, it corresponds to an idempotent morphism $ f $ on $ X $.
 We send $ (F, X, r, s) $ to $ (X, f) $.
-Note that both $ F $ and the image of $ (X, f) $ are equalizers of $ \id{\yo X} $ and $ r \cdot s $, so they are isomorphic.
+Note that both $ F $ and the image of $ (X, f) $ are equalizers of $ \id{\yo(X)} $ and $ r \cdot s $, so they are isomorphic.
 
@@
 \begin{remark}
-  Note that since the morphism types of $ \tilde C $ and $ \hat C $ are the same, and since the objects of $ \hat C $ are just truncated versions of the objects in $ \tilde C $, we have a fully faithful embedding
-  \[ \tilde C \hookrightarrow \hat C, \]
+  Note that since the morphism types of $ \tilde \C $ and $ \hat \C $ are the same, and since the objects of $ \hat \C $ are just truncated versions of the objects in $ \tilde \C $, we have a fully faithful embedding
+  \[ \tilde \C \hookrightarrow \hat \C, \]
   which just forgets the choices for $ X $, $ r $ and $ s $ on the objects.
-Note that this is also essentially surjective: by definition, for any $ (F, H) : \hat C $, there merely exist $ X $, $ r $ and $ s $ such that $ (X, r, s) $ truncates to $ H $.
-  Therefore, we have a weak equivalence from $ \tilde C $ to $ \hat C $. However, as we will see, $ \tilde C $ is usually not univalent, so this does not give an adjoint equivalence of categories.
+Note that this is also essentially surjective: by definition, for any $ (F, H) : \hat \C $, there merely exist $ X $, $ r $ and $ s $ such that $ (X, r, s) $ truncates to $ H $.
+  Therefore, we have a weak equivalence from $ \tilde \C $ to $ \hat \C $. However, as we will see, $ \tilde \C $ is usually not univalent, so this does not give an adjoint equivalence of categories.
 \end{remark}
@@
 \begin{corollary}\label{cor:karoubi-candidates}
-  We have three candidates for the category of retracts, which are related to each other and to $ C $ and $ PC $ as follows:
-  \begin{center}
-    \begin{tikzcd}
-      C \arrow[r, hook, "\iota_C"] & \overline C \arrow[r, "\sim"] & \tilde C \arrow[r, hook, two heads] & \hat C \arrow[r, phantom, "\subseteq"] & PC
-    \end{tikzcd}
-  \end{center}
-  The fact that $ \hat C $ is univalent, and has weak equivalences from $ \overline C $ and $ \tilde C $ exhibits $ \hat C $ as the Rezk completion of $ \overline C $ and $ \tilde C $.
+  We have three candidates for the category of retracts, which are related to each other and to $ \C $ and $ P\C $ as follows:
+  \begin{center}
+    \begin{tikzcd}
+      \C \arrow[r, hook, "\iota_\C"] & \overline \C \arrow[r, "\sim"] & \tilde \C \arrow[r, hook, two heads] & \hat \C \arrow[r, phantom, "\subseteq"] & P\C
+    \end{tikzcd}
+  \end{center}
+  The fact that $ \hat \C $ is univalent, and has weak equivalences from $ \overline \C $ and $ \tilde \C $ exhibits $ \hat \C $ as the Rezk completion of $ \overline \C $ and $ \tilde \C $.
 \end{corollary}
@@
 \begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_univalence}]
-  The fully faithful embedding $ i_C : C \hookrightarrow \overline C $ induces equivalences $ (X \cong Y) \simeq (\iota_C(X) \cong \iota_C(Y)) $.
-We also have an equivalence $ (X = Y) \simeq (\iota_C(X) = \iota_C(Y)) $, because, as it turns out, any equality between $ X $ and $ Y $ also preserves the identity of $ X $.
-Therefore, if $ \overline C $ is univalent, we have a chain of equivalences
-  \[ (X = Y) \simeq (\iota_C(X) = \iota_C(Y)) \simeq (\iota_C(X) \cong \iota_C(Y)) \simeq (X \cong Y), \]
-  which shows that $ C $ is univalent as well.
+  The fully faithful embedding $ \iota_\C : \C \hookrightarrow \overline \C $ induces equivalences $ (X \cong Y) \simeq (\iota_\C(X) \cong \iota_\C(Y)) $.
+We also have an equivalence $ (X = Y) \simeq (\iota_\C(X) = \iota_\C(Y)) $, because, as it turns out, any equality between $ X $ and $ Y $ also preserves the identity of $ X $.
+Therefore, if $ \overline \C $ is univalent, we have a chain of equivalences
+  \[ (X = Y) \simeq (\iota_\C(X) = \iota_\C(Y)) \simeq (\iota_\C(X) \cong \iota_\C(Y)) \simeq (X \cong Y), \]
+  which shows that $ \C $ is univalent as well.
 \end{remark}
@@
   under matrix multiplication.
-As we saw in Section \ref{sec:monoid-category}, we can turn this into a category $ C_M $ with one object $ \star $, and the three morphisms $ a $, $ b $ and $ c $.
-Only $ a $ is an isomorphism and since $ \star = \star $ has exactly one inhabitant, $ C_M $ is univalent.
-
-  When we construct the Karoubi envelope $ \overline C_M $, we get a category with objects $ a $ and $ b $.
+As we saw in Section \ref{sec:monoid-category}, we can turn this into a category $ \C_M $ with one object $ \star $, and the three morphisms $ a $, $ b $ and $ c $.
+Only $ a $ is an isomorphism and since $ \star = \star $ has exactly one inhabitant, $ \C_M $ is univalent.
+
+  When we construct the Karoubi envelope $ \overline \C_M $, we get a category with objects $ a $ and $ b $.
 Now, note that since $ M $ is a set, $ b = b $ still has one inhabitant.
@@
   \[ b \cdot c = c \quad \text{and} \quad c \cdot c = b, \]
-  $ c $ is also an automorphism of $ b $. Therefore, $ \overline C_M $ is not univalent.
-
-  In a somewhat more complicated way, we can show that $ \tilde C_M $ is not univalent either: the counterpart of $ b $ in that category has two automorphisms, corresponding to $ b $ and $ c $, but only one equality, which is the identity.
+  $ c $ is also an automorphism of $ b $. Therefore, $ \overline \C_M $ is not univalent.
+
+  In a somewhat more complicated way, we can show that $ \tilde \C_M $ is not univalent either: the counterpart of $ b $ in that category has two automorphisms, corresponding to $ b $ and $ c $, but only one equality, which is the identity.
 This is because isomorphisms only have to respect the presheaf structure, whereas equalities also have to respect the section (and retraction).
@@
 
-  Therefore, $ \overline C $ and $ \tilde C $ are usually more pathological than $ C $ itself. On the other hand, since $ \hat C $ is a full subcategory of $ PC $, it is univalent.
+  Therefore, $ \overline \C $ and $ \tilde \C $ are usually more pathological than $ \C $ itself. On the other hand, since $ \hat \C $ is a full subcategory of $ P\C $, it is univalent.
 \end{remark}
@@
 Therefore, we need to be careful which definition we choose, because this choice has consequences.
-One one hand, $ \hat C $ is univalent, but very abstract.
-In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \hat C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism.
-On the other hand, $ \overline C $ and $ \tilde C $ are very elementary and concrete, which sometimes helps when doing constructions.
+On one hand, $ \hat \C $ is univalent, but very abstract.
+In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \hat \C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism.
+On the other hand, $ \overline \C $ and $ \tilde \C $ are very elementary and concrete, which sometimes helps when doing constructions.
 However, they are not univalent, which makes working with them complicated in a different way.
@@
 
-The remainder of this section works towards the adjoint equivalence between $ PC $ and $ P \overline C $.
-
-Since a functor preserves retracts, and since every object of $ \overline C $ is a retract of an object in $ C $, we can generalize the construction of the functor that we do in Lemma \ref{lem:karoubi-equivalence} for the functor $ \yo: C \to PC $, to general functors $ F: C \to D $ for categories $ D $ with (co)equalizers.
+The remainder of this section works towards the adjoint equivalence between $ P\C $ and $ P \overline \C $.
+
+Since a functor preserves retracts, and since every object of $ \overline \C $ is a retract of an object in $ \C $, we can generalize the construction of the functor that we do in Lemma \ref{lem:karoubi-equivalence} for the functor $ \yo: \C \to P\C $, to general functors $ F: \C \to \D $, if $ \D $ has (co)equalizers.
 
@@
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_pullback_equivalence}]
-  Let $ D $ be a category with colimits. We have an adjoint equivalence between $ [C, D] $ and $ [\overline C, D] $.
-\end{lemma}
-\begin{proof}
-  We already have an adjunction $ \Lan {\iota_C} {} \dashv \iota_{C*} $.
-Also, since $ \iota_C $ is fully faithful, we know that $ \eta $ is a natural isomorphism.
+  Let $ \D $ be a category with colimits. We have an adjoint equivalence between $ [\C, \D] $ and $ [\overline \C, \D] $.
+\end{lemma}
+\begin{proof}
+  We already have an adjunction $ \Lan {\iota_\C} {} \dashv \iota_{\C*} $.
+Also, since $ \iota_\C $ is fully faithful, we know that $ \eta $ is a natural isomorphism.
 Therefore, we only have to show that $ \epsilon $ is a natural isomorphism.
-That is, we need to show that $ \epsilon_G(c, a): D(\Lan {\iota_C} (\iota_{C*} G) (c, a), G(c, a)) $ is an isomorphism for all $ G: [\overline C, D] $ and $ (c, a): \overline C $.
-
-  One of the components in the diagram of $ \Lan {\iota_C} (\iota_{C*} G) (c, a) $ is the $ \iota_{C*} G(c) = G(c, \id c) $ corresponding to $ a: \iota_C(c) \to (c, a) $.
+That is, we need to show that $ \epsilon_G(X, a): \D(\Lan {\iota_\C} (\iota_{\C*} G) (X, a), G(X, a)) $ is an isomorphism for all $ G: [\overline \C, \D] $ and $ (X, a): \overline \C $.
+
+  One of the components in the diagram of $ \Lan {\iota_\C} (\iota_{\C*} G) (X, a) $ is the $ G(\iota_\C(X)) $ corresponding to $ a: \overline \C(\iota_\C(X), (X, a)) $.
 This component has a morphism into our colimit
-  \[ \varphi: C(G(\iota_C(c)), \Lan {\iota_C} (\iota_{C*} G) (c, a)). \]
-  Note that we can view $ a $ as a morphism $ a: \overline C((c, a), \iota_C(c)) $. This gives us our inverse morphism
-  \[ G(a) \cdot \varphi: C(G(c, a), \Lan {\iota_C} (\iota_{C*} G) (c, a)). \]
+  \[ \varphi: \C(G(\iota_\C(X)), \Lan {\iota_\C} (\iota_{\C*} G) (X, a)). \]
+  Note that we can also view $ a $ as a morphism $ a: \overline \C((X, a), \iota_\C(X)) $. This gives us our inverse morphism
+  \[ G(a) \cdot \varphi: \C(G(X, a), \Lan {\iota_\C} (\iota_{\C*} G) (X, a)). \]
 \end{proof}
@@
 \begin{proof}
-  An object in $ \overline{\op C} $ is an object $ c: \op C $ (which is just an object $ c: C $), together with an idempotent morphism $ a: \op C(c, c) = C(c, c) $.
-This is the same as an object in $ \op{\overline C} $.
-
-  A morphism in $ \overline{\op C}((c, a), (d, b)) $ is a morphism $ f: \op C(c, d) = C(d, c) $ such that
-  \[ b \cdot_C f \cdot_C a = a \cdot_{\op C} f \cdot_{\op C} b = f. \]
-  A morphism in $ \op{\overline C}((c, a), (d, b)) = \overline C((d, b), (c, a)) $ is a morphism $ f: C(d, c) $ such that $ b \cdot f \cdot a = f $.
-
-  Now, in both categories, the identity morphism on $ (c, a) $ is given by $ a $.
-
-  Lastly, $ \overline {\op C} $ inherits morphism composition from $ \op C $, which is the opposite of composition in $ C $.
-On the other hand, composition in $ \op{\overline C} $ is the opposite of composition in $ \overline C $, which inherits composition from $ C $.
+  An object in $ \overline{\op \C} $ is an object $ X: \op \C $ (which is just an object $ X: \C $), together with an idempotent morphism $ a: \op \C(X, X) = \C(X, X) $.
+This is the same as an object in $ \op{\overline \C} $.
+
+  A morphism in $ \overline{\op \C}((X, a), (Y, b)) $ is a morphism $ f: \op \C(X, Y) = \C(Y, X) $ such that
+  \[ b \cdot_\C f \cdot_\C a = a \cdot_{\op \C} f \cdot_{\op \C} b = f. \]
+  A morphism in $ \op{\overline \C}((X, a), (Y, b)) = \overline \C((Y, b), (X, a)) $ is a morphism $ f: \C(Y, X) $ such that $ b \cdot f \cdot a = f $.
+
+  Now, in both categories, the identity morphism on $ (X, a) $ is given by $ a $.
+
+  Lastly, $ \overline {\op \C} $ inherits morphism composition from $ \op \C $, which is the opposite of composition in $ \C $.
+On the other hand, composition in $ \op{\overline \C} $ is the opposite of composition in $ \overline \C $, which inherits composition from $ \C $.
 \end{proof}
@@
 \begin{corollary}\label{cor:karoubi-presheaf}
-  As the category $ \SET $ is cocomplete, we have an equivalence between the category of presheaves on $ C $ and the category of presheaves on $ \overline C $:
-  \[ [\op C, \SET] \cong [\overline{\op C}, \SET] \cong [\op{\overline C}, \SET]. \]
+  As the category $ \SET $ is cocomplete, we have an equivalence between the category of presheaves on $ \C $ and the category of presheaves on $ \overline \C $:
+  \[ [\op \C, \SET] \cong [\overline{\op \C}, \SET] \cong [\op{\overline \C}, \SET]. \]
 \end{corollary}

### 2024-10-07 100-introduction.tex
Process most of Maarten's feedback

--- 2024-09-26 100-introduction.tex
@@
 The $ \lambda $-calculus is an abstract tool that is used in an area where mathematics meets computer science, to study algorithms, programming languages and even category theory.
-It was conceived by Alonzo Church, primarily as a foundation for mathematics instead of set theory or type theory (\autocite{church-lambda-calculus}).
-A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such an algorithm could not exist (\autocite{church-number-theory}).
-A year later, Alan Turing showed, using previous work of Kleene (\autocite{kleene-lambda}), that an algorithm is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine (\autocite{turing-lambda}), solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.
+It was conceived by Alonzo Church, primarily as a foundation for mathematics instead of set theory or type theory \autocite{church-lambda-calculus}.
+A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such an algorithm could not exist \autocite{church-number-theory}.
+A year later, Alan Turing showed, using previous work of Kleene \autocite{kleene-lambda}, that an algorithm is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine \autocite{turing-lambda}, solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.
 
 Later, all kinds of different flavours and extensions of the $ \lambda $-calculus were put forth, with colorful names like `simply typed $ \lambda $-calculus', `System T' and `PCF'.
-Even though the $ \lambda $-calculus was originally a very abstract tool, it was also the inspiration for function programming languages, and traces of it can be seen in imperative programming languages, where unnamed functions are commonly called `lambda functions' and are sometimes even written like \texttt{lambda x y : (x - y) * (x + y)}.
+Even though the $ \lambda $-calculus was originally a very abstract tool, it was also the inspiration for function programming languages, and traces of it can be seen in imperative programming languages, where unnamed functions are commonly called `lambda expressions' \autocite{java-lambdas} and are sometimes even written like \texttt{lambda x y : (x - y) * (x + y)} \autocite{python-expressions}.
 
 Even so, the theoretical study of the $ \lambda $-calculus and its extensions continues to this day.
-For example, in 2013, a paper by Martin Hyland was published, named `classical lambda calculus in modern dress' (\autocite{Hyland}).
+For example, in 2017, a paper by Martin Hyland was published\footnote{Note that the paper has been around since 2012, when it was first published as a preprint on arXiv.}, named `classical lambda calculus in modern dress' \autocite{Hyland}.
 In this paper, Hyland approaches the $ \lambda $-calculus from the viewpoint of universal algebra, using algebraic theories, and more generally category theory, to study it.
@@
 
-In this thesis, we study the paper through the lens of univalent foundations, a foundation of mathematics based on type theory set forth by Vladimir Voevodsky.
-We work out the details of the proofs from the paper, see where subtleties arise when converting from set theory to univalent foundations and discuss the formalization of part of the material.
-Of particular interest is the discussion of Hyland's proof of the locally cartesian closedness of a category of retracts (or Karoubi envelope) in Section \ref{sec:locally-cartesian-closed}, which was proved earlier by Paul Taylor in a different way.
+In this thesis, we study the paper through the lens of univalent foundations, a foundation of mathematics based on type theory set forth by Vladimir Voevodsky \autocite{voevodsky-univalent-foundations}.
+We work out the details of the proofs from the paper, see where subtleties arise when converting from set theory to univalent foundations and discuss the formalization of part of the material in the computer proof assistant coq.
+
+The major contributions of this thesis are
+\begin{itemize}
+  \item Of particular interest is the discussion of Hyland's proof of the locally cartesian closedness of a category of retracts (or Karoubi envelope) in Section \ref{sec:locally-cartesian-closed}, which was proved earlier by Paul Taylor in a different way.
 It turns out that in the translation from set theory to univalent foundations, the definition of the category of retracts `branches' into two nonequivalent definitions, and that Taylor's proof is about one definition, whereas Hyland's proof is about the other.
+  \item \TODO
+\end{itemize}
 
@@
 % 300-univalent-foundations.tex
-Because this thesis works from a univalent standpoint, Chapter \ref{ch:univalent-foundations} introduces univalent foundations and builds the preliminary knowledge in that area for the rest of the paper.
+Because this thesis works from a univalent point of view, Chapter \ref{ch:univalent-foundations} introduces univalent foundations and builds the preliminary knowledge in that area for the rest of the paper.
 % 400-algebraic-structures.tex
-Then Chapter \ref{ch:algebraic-structures} introduces the main objects that are studied by Hyland, namely $ \lambda $-theories and $ \Lambda $-algebras, together with related notions and examples.
+Then, Chapter \ref{ch:algebraic-structures} introduces the main objects that are studied by Hyland, namely $ \lambda $-theories and $ \Lambda $-algebras, together with related notions and examples.
 % 700-formalization.tex
 Lastly, the formalization of part of the material is discussed in Chapter \ref{ch:the-formalization}.
+
+Note that throughout this document, links are included to \href{https://arnoudvanderleer.github.io/cs-masters-thesis/toc.html}{\nolinkurl{documentation}} of the corresponding formalized material.
+The documentation refers to the state of \href{https://github.com/UniMath/UniMath/tree/5eb5c8958c4dddd4219f895bf7bc51547395522d}{\nolinkurl{the UniMath repository}} at commit \texttt{5eb5c8958c4dddd4219f895bf7bc51547395522d}.

### 2024-10-07 300-univalent-foundations.tex
Process most of Maarten's feedback

@@
 Now, even for a basic category, like the category of types, it seems impossible to prove that the univalence principle holds.
-However, this is no surprise: It turns out that there is a model in set theory for Martin-Löf type theory with univalence (\autocite{simplicial-set-model}), but also for Martin-Löf type theory with proof irrelevance (\autocite{proof-irrelevant-model}).
+However, this is no surprise: It turns out that there is a model in set theory for Martin-Löf type theory with univalence \autocite{simplicial-set-model}, but also for Martin-Löf type theory with proof irrelevance \autocite{proof-irrelevant-model}.
 In the latter, the type $ x = y $ has at most one element for all $ x, y : T $ and all types $ T $, which contradicts univalence.

### 2024-10-07 100-introduction.tex
Fix title case

@@
 \begin{itemize}
-  \item Of particular interest is the discussion of Hyland's proof of the locally cartesian closedness of a category of retracts (or Karoubi envelope) in Section \ref{sec:locally-cartesian-closed}, which was proved earlier by Paul Taylor in a different way.
+  \item Of particular interest is the discussion of Hyland's proof of the relative cartesian closedness of a category of retracts (or Karoubi envelope) in Section \ref{sec:relatively-cartesian-closed}, which was proved earlier by Paul Taylor in a different way.
 It turns out that in the translation from set theory to univalent foundations, the definition of the category of retracts `branches' into two nonequivalent definitions, and that Taylor's proof is about one definition, whereas Hyland's proof is about the other.

### 2024-10-07 200-category-theory.tex
Process most of Maarten's feedback
Fix title case

@@
 
-\section{Adjunctions and equivalences}
+\section{Adjunctions and Equivalences}
 
@@
 \begin{proof}
-  First of all, note that for $ X, Y, Z : \C $, we have a sequence of isomorphisms  (\autocite{stackexchange:yoneda-exponentials})
+  First of all, note that for $ X, Y, Z : \C $, we have a sequence of isomorphisms \autocite{stackexchange:yoneda-exponentials}
   \begin{align*}
@@
 
-\section{(Co)slice categories}
+\section{(Co)slice Categories}
 Given an object in a category $ X: \C $, the morphisms to and from $ X $ constitute the slice and coslice categories
@@
 
-\section{Dependent products and sums}\label{sec:dependent-products}
+\section{Dependent Products and Sums}\label{sec:dependent-products}
 The following is based loosely on Section 4.1 of \autocite{taylor}.
@@
 
-\section{(Weakly) terminal objects}
+\section{(Weakly) Terminal Objects}
 \begin{definition}
@@
 
-\section{Monoids as categories}\label{sec:monoid-category}
+\section{Monoids as Categories}\label{sec:monoid-category}
 Take a monoid $ M $.
@@
 
-\section{The Karoubi envelope}
+\section{The Karoubi Envelope}
 Let $ \C $ be a category and $ X, Y : \C $ objects. We will denote the type of section-retraction pairs of $ Y $ onto $ X $ with

### 2024-10-07 300-univalent-foundations.tex
Fix title case

@@
 
-\section{Dependent type theory}
+\section{Dependent Type Theory}
 Univalent foundations takes place in a framework of type theory. In this section, we will quickly introduce some topics that we will need in subsequent sections.
@@
 
-\section{The univalence principle}\label{sec:univalence-principle}
+\section{The Univalence Principle}\label{sec:univalence-principle}
 \enquote{\textit{Isomorphic objects are equivalent.}}
@@
 
-\section{The univalence axiom}
+\section{The Univalence Axiom}
 Now, even for a basic category, like the category of types, it seems impossible to prove that the univalence principle holds.
@@
 
-\section{hProps and hSets}\label{sec:homotopy-props-sets}
+\section{Propositions and Sets}\label{sec:homotopy-props-sets}
 If we have a type $ T $ and objects $ x $ and $ y $, we can wonder how many elements $ x = y $ has.
@@
 
-\section{Truncation and (mere) existence}
+\section{Truncation and (Mere) Existence}
 As mentioned before, if we want to do mathematics in a dependent type theory, we can `encode' propositions as types.
@@
 
-\section{Equality and homotopy}
+\section{Equality and Homotopy}
 Univalent Foundations is often mentioned together with Homotopy Type Theory, because they are related but distinct concepts. Therefore, we will mention it here.

### 2024-10-07 500-previous-work.tex
Process most of Maarten's feedback
Fix title case

@@
-\chapter{Previous work in categorical semantics}\label{ch:previous-work}
+\chapter{Previous Work in Categorical Semantics}\label{ch:previous-work}
 
@@
 
-\section{The correspondence between categories and typed \texorpdfstring{$ \lambda $}{lambda}-calculi}\label{sec:lambek-correspondence}
+\section{The Correspondence Between Categories and Typed \texorpdfstring{$ \lambda $}{lambda}-calculi}\label{sec:lambek-correspondence}
 In \autocite{curry}, page 413, Scott and Lambek argue that there is a correspondence between simply typed $ \lambda $-calculi and cartesian closed categories (categories with products and `function objects').
@@
 
-\section{The category of retracts}\label{sec:retracts-category}
+\section{The Category of Retracts}\label{sec:retracts-category}
 
@@
 
-\section{The \texorpdfstring{$ \lambda $}{lambda}-calculus is algebraic}
+\section{The \texorpdfstring{$ \lambda $}{lambda}-calculus is Algebraic}
 As we mentioned in Remark \ref{rem:lambda-theory-or-algebra}, using tools from universal algebra, there are two approaches to study $ \lambda $-calculus-like structures.
@@
 
-In his proof, he refers to the 2002 paper `The lambda calculus is algebraic' by Peter Selinger (\autocite{selinger-lambda-calculus-algebraic}).
+In his proof, he refers to the 2002 paper `The lambda calculus is algebraic' by Peter Selinger \autocite{selinger-lambda-calculus-algebraic}.
 We will not study this paper in detail, but it is interesting to have a quick look at it, because it seems that Hyland took some inspiration from it.

### 2024-10-07 600-paper.tex
Fix title case

@@
-\chapter{Hyland's paper}\label{ch:the-paper}
+\chapter{Hyland's Paper}\label{ch:the-paper}
 
@@
 
-\section{Relations between the categories}
+\section{Relations Between the Categories}
 
@@
 
-\section{Locally cartesian closedness of the category of retracts}\label{sec:locally-cartesian-closed}
+\section{Relative Cartesian Closedness of the Category of Retracts}\label{sec:relatively-cartesian-closed}
 
@@
 
-\section{An elementary proof of the `Fundamental Theorem'}\label{sec:elementary-fundamental-theorem}
+\section{An Elementary Proof of the `Fundamental Theorem'}\label{sec:elementary-fundamental-theorem}
+
 The final theorem that Hyland works towards in his paper constructs an equivalence between two ways to reason about the $ \lambda $-calculus using these tools from universal algebra: $ \lambda $-theories and $ \Lambda $-algebras.
@@
 
-\section{Hyland's proof}
+\section{Hyland's Proof}
 
@@
 
-\section{Theory of extensions}
+\section{The Theory of Extensions}
 

### 2024-10-07 700-formalization.tex
Fix title case

@@
 % 434 292; 1144 58; 96 0; 469 113; 145 42; 495 90; 508 221; Total: 3291 816
-\chapter{The formalization}\label{ch:the-formalization}
+\chapter{The Formalization}\label{ch:the-formalization}
+
 In addition to the reading, investigating and writing mathematics that lead up to the previous chapters, this thesis project also had a formalization component.
@@
 
-\section{Some numbers}
+\section{Some Numbers}
 The code for this project was written over the course of about 18 months, spread over \href{https://github.com/UniMath/UniMath/pulls?q=is%3Apr+author%3Aarnoudvanderleer+is%3Aclosed}{20 pull requests}: 13 with content about Hyland's paper, adding 23.361 and removing 7.620 lines of code, and 7 with only some missing category theoretical preliminaries, adding 3.291 and removing 816 lines.
 
-\section{Overview of the formalized material}
+\section{Overview of the Formalized Material}
 The material that was formalized can be subdivided into material that is introduced or described in Hyland's paper, and category theoretical preliminaries that are necessary to make the proofs in Hyland's paper work.
@@
 
-\section{Displayed categories}\label{sec:displayed-categories}
+\section{Displayed Categories}\label{sec:displayed-categories}
 
@@
 
-\section{Duplication in definitions}
+\section{Duplication in Definitions}
 One of the adages in software engineering is `DRY': ``Don't Repeat Yourself'': Long expressions and blocks of code that occur multiple times throughout the program should usually be abstracted into a separate function.
@@
 
-\section{The formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus} \label{sec:axiomatic-lambda-calculus}
+\section{The Formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus} \label{sec:axiomatic-lambda-calculus}
 One of the important classes of objects in this thesis is the class of $ \Lambda $-algebras: algebras for the initial $ \lambda $-theory $ \Lambda $, corresponding to the `pure' $ \lambda $-calculus.
@@
 
-\section{The learning curve}
+\section{The Learning Curve}
 Let me conclude this chapter with a more personal note about formalization.

### 2024-10-07 910-alternative-definitions.tex
Fix title case

@@
 
-\section{Lawvere theory}
+\section{Lawvere Theory}
 \begin{definition}
@@
 
-\section{Monoid in a skew-monoidal category}
+\section{Monoid in a Skew-Monoidal Category}
 For details and a general treatment, see \autocite{monads-endofunctors}, Section 3 and specifically Theorem 3.4.

### 2024-10-08 100-introduction.tex
Address a lot of feedback, do a spellcheck

@@
 Note that throughout this document, links are included to \href{https://arnoudvanderleer.github.io/cs-masters-thesis/toc.html}{\nolinkurl{documentation}} of the corresponding formalized material.
-The documentation refers to the state of \href{https://github.com/UniMath/UniMath/tree/5eb5c8958c4dddd4219f895bf7bc51547395522d}{\nolinkurl{the UniMath repository}} at commit \texttt{5eb5c8958c4dddd4219f895bf7bc51547395522d}.
+The documentation refers to the state of \href{https://github.com/UniMath/UniMath/tree/5eb5c8958c4dddd4219f895bf7bc51547395522d}{\texttt{the UniMath repository}} at commit \texttt{5eb5c8958c4dddd4219f895bf7bc51547395522d}.

### 2024-10-08 200-category-theory.tex
Address a lot of feedback, do a spellcheck

@@
 \section{Notation}
-Throughout this thesis, objects of a homotopy set, for example morphisms, will usually be denoted with lowercase letters like $ f, g, h $ and sometimes with greek letters like $ \epsilon, \eta, \varphi, \psi $.
+Throughout this thesis, objects of a homotopy set, for example morphisms, will usually be denoted with lowercase letters like $ f, g, h $ and sometimes with Greek letters like $ \epsilon, \eta, \varphi, \psi $.
 Objects of a homotopy $ 1 $-type, like objects in a category, will usually be denoted with capital letters like $ X, Y, Z $.
@@
 \end{center}
-with natural transformations (the unit and counit)
+with natural transformations (the unit and co-unit)
 \[ \eta: \id \C \Rightarrow L \bullet R \quad \text{and} \quad \epsilon: R \bullet L \Rightarrow \id \D \]
@@
 \subsection{Adjoint equivalences}
-An (adjoint) equivalence of categories has multiple definitions. The one we will use here is the following:
-
+An (adjoint) equivalence of categories has two equivalent definitions, that only differ in which notion they take as the base. In this case, we will use the definition that is based on adjunctions:
 \begin{definition}\label{def:equivalence-of-categories}
-  An \iindex{adjoint equivalence} between categories $ \C $ and $ \D $ is a pair of adjoint functors $ L \dashv R $ like above such that the unit $ \eta: \id{\C} \Rightarrow L \bullet R $ and counit $ \epsilon: R \bullet L \Rightarrow \id{\D} $ are isomorphisms of functors.
-\end{definition}
+  An \iindex{adjoint equivalence} between categories $ \C $ and $ \D $ is a pair of adjoint functors $ L \dashv R $ like above such that the unit $ \eta: \id{\C} \Rightarrow L \bullet R $ and co-unit $ \epsilon: R \bullet L \Rightarrow \id{\D} $ are isomorphisms of functors.
+\end{definition}
+
+The alternative is to define an adjoint equivalence as an equivalence of categories (a tuple $ (L, R, \eta, \epsilon) $ of two functors and two natural transformations, where $ \eta $ and $ \epsilon $ are isomorphisms of functors) that additionally satisfies the zigzag identities.
 
@@
 \section{Yoneda}
-We can embed a category $ \C $ fully faithfully into the functor category $ P \C = [\op \C, \SET] $ as follows (see \autocite{Kashiwara}, Section 1.4):
+Let $ \C $ be a category.
+One of the categories that is often important in the study of $ \C $ is its \iindex{presheaf category} $ P \C = [\op \C, \SET] $.
+Its objects are the functors from $ \op C $ to $ \SET $ and its morphisms are the natural transformations between the functors.
+
+We can embed $ \C $ fully faithfully into $ P \C $ as follows (see \autocite{Kashiwara}, Section 1.4):
 \begin{definition}\label{def:Yoneda-embedding}
@@
 \begin{remark}
-  For any category $ \D $, the category $ [\C, \D] $ has (co)limits of some kind (terminal or initial object, (co)products, (co)equalizers) iff $ \D $ does.
+  For any category $ \D $, the category $ [\C, \D] $ has (co)limits of some kind (terminal or initial object, (co)products, (co)equalizers) if and only if $ \D $ does.
 These (co)limits are computed pointwise: for example, for binary products, $ (F \times G)(X) = F(X) \times G(X) $.
@@
 \begin{lemma}\label{lem:locally-cartesian-closed}
-  A category $ \C $ is locally cartesian closed iff $ (\C \downarrow X) $ is cartesian closed for each $ X : \C $.
+  A category $ \C $ is locally cartesian closed if and only if $ (\C \downarrow X) $ is cartesian closed for each $ X : \C $.
 \end{lemma}
@@
 
-  The counit of the adjunction is a natural transformation $ \epsilon: F_* \bullet \Lan F {} \Rightarrow \id{[\B, \C]} $.
+  The co-unit of the adjunction is a natural transformation $ \epsilon: F_* \bullet \Lan F {} \Rightarrow \id{[\B, \C]} $.
 We will also define this pointwise, for $ G: [\B, \C] $ and $ X: \B $.
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_inclusion_fully_faithful}]
-  Note that $ \iota_\C $ is fully faithful, since
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_inclusion_fully_faithful}]
+  $ \iota_\C $ is fully faithful.
+\end{lemma}
+\begin{proof}
+  This follows immediately from the fact that
   \[ \overline \C((X, \id X), (Y, \id Y)) = \{ f: \C(X, Y) \mid \id X \cdot f \cdot \id Y = f \} = \C(X, Y). \]
-\end{remark}
-
-\begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_equalizer}, \coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_coequalizer}]\label{rem:retract-coequalizer}
+\end{proof}
+
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_equalizer}, \coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{retract_functor_is_coequalizer}]\label{rem:retract-coequalizer}
   Let $ \D $ be a category and suppose that we have two objects $ X, Y : \D $ and a retraction
@@
   Then $ Y $ is the equalizer of \begin{tikzcd}
-    X \arrow[r, shift left, "\id X"] \arrow[r, shift right, "r \cdot s"'] & X \end{tikzcd} in the following way:
-
+    X \arrow[r, shift left, "\id X"] \arrow[r, shift right, "r \cdot s"'] & X \end{tikzcd}.
+\end{lemma}
+\begin{proof}
   Suppose that we have an object $ Z: \D $ and a morphism $ f $ with $ (r \cdot s) \cdot f = f $.
@@
   \end{center}
-\end{remark}
+\end{proof}
 
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_univalence}]
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_univalence}]
+  If $ \overline \C $ is univalent, $ \C $ is univalent as well.
+\end{lemma}
+\begin{proof}
   The fully faithful embedding $ \iota_\C : \C \hookrightarrow \overline \C $ induces equivalences $ (X \cong Y) \simeq (\iota_\C(X) \cong \iota_\C(Y)) $.
@@
   which shows that $ \C $ is univalent as well.
-\end{remark}
+\end{proof}
 

### 2024-10-08 300-univalent-foundations.tex
Address a lot of feedback, do a spellcheck

@@
 In type theory, we have a similar concept, which is called `equivalence' (of types) $ S \simeq T $.
-Since bijections are not well-behaved for types that are not sets (see \ref{sec:homotopy-props-sets}), because in those cases, a function $ f: S \to T $ can have multiple distinct inverses.
+Since bijections are not well-behaved for types that are not sets (see Section \ref{sec:homotopy-props-sets}), because in those cases, a function $ f: S \to T $ can have multiple distinct inverses.
 Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ (see \autocite{hottbook}, Equation 2.4.10).
@@
 
-Note that if $ B $ is a univalent category and $ A $ is any cateory, the functor category $ [A, B] = B^A $ is univalent as well.
+Note that if $ B $ is a univalent category and $ A $ is any category, the functor category $ [A, B] = B^A $ is univalent as well.
 In particular, the presheaf category $ P A = [\op A, \SET] $ is univalent.
@@
 \end{proof}
-We call such a univalent category a \iindex{Rezk completion} of $ C $.
-
-\begin{remark}[\coqident{Bicategories.RezkCompletions.Uniqueness}{rezk_completion_unique}]
-  We can call it \textit{the} Rezk completion, since it is unique: Precomposition with the weak equivalence $ \iota: C \hookrightarrow D $ gives an adjoint equivalence on the functor categories $ [D, E] \simeq [C, E] $ for any univalent category $ E $.
+We call such a univalent category a \iindex{Rezk completion} of $ C $. Actually, we can call it \textit{the} Rezk completion:
+\begin{lemma}[\coqident{Bicategories.RezkCompletions.Uniqueness}{rezk_completion_unique}]
+  A Rezk completion is unique.
+\end{lemma}
+\begin{proof}
+  Precomposition with the weak equivalence $ \iota: C \hookrightarrow D $ gives an adjoint equivalence on the functor categories $ [D, E] \simeq [C, E] $ for any univalent category $ E $.
 From this, it follows that $ \iota $ is the ``initial functor'' from $ C $: any functor from $ C $ to a univalent category factors uniquely through $ \iota $.
@@
   \[ F^\prime = F \bullet G \quad \text{and} \quad F = F^\prime \bullet G^\prime \]
-  for some functors $ G $ and $ G^\prime $ and we can show that
+  for two functors $ G $ and $ G^\prime $ and since $ F $ and $ F^\prime $ also factor uniquely through themselves, we have
   \[ G \bullet G^\prime = \id D \quad \text{and} \quad G^\prime \bullet G = \id{D^\prime}. \]
@@
   \[ (D, F) = (D^\prime, F^\prime). \]
-\end{remark}
+\end{proof}
 
@@
 \begin{lemma}\label{lem:univalen-category-equivalence}
-  For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is a weak equivalence' are equivalent propositions (see \ref{sec:homotopy-props-sets}).
+  For a functor between univalent categories $ F: A \to B $, the types `$ F $ is an adjoint equivalence' and `$ F $ is a weak equivalence' are equivalent propositions (see Section \ref{sec:homotopy-props-sets}).
 \end{lemma}
@@
 
-Since the identity types for a homotopy set are mere propositions, a homotopy set mimicks a set in set theory, where equality between elements `is' or `is not'.
+Since the identity types for a homotopy set are mere propositions, a homotopy set mimics a set in set theory, where equality between elements `is' or `is not'.
 If we restrict the underlying type of a group to be a homotopy set, it can be shown that $ \prod_{x, y: H} f_1(x \circ y) = f_1(x) \circ f_1(y) $ is a mere proposition, so $ f_2 = g_2 $ trivially.
@@
 The situation in which one has to work with such complicated transports, which make a proof (seemingly unnecesarily) complicated is called \iindex{transport hell}.
-Some mathematical tools have been developed (see for example \ref{sec:displayed-categories} about displayed categories) that help avoid transport hell in some cases.
+Some mathematical tools have been developed (see for example Section \ref{sec:displayed-categories} about displayed categories) that help avoid transport hell in some cases.
 Additionally, the structure or `strategy' of a proof can sometimes be changed in order to avoid the worst of the transports.

### 2024-10-08 400-algebraic-structures.tex
Address a lot of feedback, do a spellcheck

--- 2024-09-27 400-algebraic-structures.tex
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{limits_algebraic_theory_cat}]\label{rem:algebraic-theory-limits}
+\begin{lemma}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{limits_algebraic_theory_cat}]\label{rem:algebraic-theory-limits}
   We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
@@
   In the same way, the category of algebraic theories has all limits.
-\end{remark}
+
+  Note that the forgetful functor $ F: \AlgTh \to \SET^{\mathbb N} $ creates limits, since any diagram $ d $ has a limit and the underlying set of the limit of $ d $ is the limit of the underlying sets of the objects in $ d $.
+\end{lemma}
+
+\begin{lemma}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{is_univalent_algebraic_theory_cat}]
+  Since an isomorphism of algebraic theories $ S \simeq T $ consists of pointwise isomorphisms $ f_n: S_n \simeq T_n $ that respect the variables and substitution, the category of algebraic theories is univalent.
+\end{lemma}
 
@@
 \begin{remark}
-  The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying sets.
+  The category of algebras has all limits. The set of a limit of algebras is the limit of the underlying sets, so the forgetful functor to the category of sets creates limits.
 \end{remark}
+
+\begin{lemma}[\coqident{AlgebraicTheories.AlgebraCategory}{is_univalent_algebra_cat}]
+  Note that just like with algebraic theories, the category of $ T $-algebras is univalent because its (iso)morphisms preserve $ \bullet $.
+\end{lemma}
 
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.PresheafCategory}{limits_presheaf_cat}]
+\begin{lemma}[\coqident{AlgebraicTheories.PresheafCategory}{limits_presheaf_cat}]
   The category of presheaves has all limits.
 The $ n $th set $ \overline{P}_n $ of a limit $ \overline{P} $ of presheaves $ P_i $ is the limit of the $ n $th sets $ P_{i, n} $ of the presheaves in the limit diagram.
-\end{remark}
+So just like with algebraic theories and algebras, the forgetful functor from the category of presheaves to the category of indexed sets creates limits.
+\end{lemma}
+
+\begin{lemma}[\coqident{AlgebraicTheories.AlgebraCategory}{is_univalent_algebra_cat}]
+  Note that just like with algebraic theories and algebras, the category of $ T $-presheaves is univalent because its (iso)morphisms preserve $ \bullet $.
+\end{lemma}
 
@@
 
-\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{has_β}]
+\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{has_β} \coqident{AlgebraicTheories.LambdaTheories}{has_η}]\label{def:beta-equality}
   We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $.
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{limits_lambda_theory_cat}]
+\begin{lemma}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{limits_lambda_theory_cat}]
   The category of lambda theories has all limits, with the underlying algebraic theory of a limit being the limit of the underlying algebraic theories.
-\end{remark}
+Therefore, the forgetful functor to the category of algebraic theories creates limits.
+\end{lemma}
+
+\begin{lemma}[\coqident{AlgebraicTheories.LambdaTheoryCategory}{is_univalent_lambda_theory_cat}]
+  Note that just like with algebraic theories, the category of $ \lambda $-theories is univalent because its (iso)morphisms preserve $ \rho $ and $ \lambda $.
+\end{lemma}
 
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{beta_equality}]
-  Note that if $ L $ has $ \beta $-equality, we have
+\begin{lemma}[\coqident{AlgebraicTheories.LambdaTheories}{beta_equality}]
+  The definitions for $ \beta $- and $ \eta $-equality in Definition \ref{def:beta-equality} correspond to the usual notions.
+\end{lemma}
+\begin{proof}
+  If $ L $ has $ \beta $-equality, we have
   \[ \lambda(f) g = \rho(\lambda(f)) \bullet (x_1, \dots, x_n, g) = f \bullet (x_1, \dots, x_n, g), \]
@@
   \[ \lambda(\iota_{n, 1}(f) x_{n + 1}) = \lambda(\rho(f)) = f. \]
-\end{remark}
+\end{proof}
+
 \begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app_from_app'}]
@@
 \end{remark}
+
 \begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app}]
@@
 On the other hand, we have a free functor $ F: \SET \to \mathbf{Top} $ which endows a set with the discrete topology.
-The construction above yields the inital algebraic theory $ T_n = \{ 1, \dots, n \} $, with an algebra action on every topological space $ i \bullet (a_1, \dots, a_n) = a_i $.
+The construction above yields the initial algebraic theory $ T_n = \{ 1, \dots, n \} $, with an algebra action on every topological space $ i \bullet (a_1, \dots, a_n) = a_i $.
 Now, note that we can endow the set $ \{ \top, \bot \} $ with four different, nonisomorphic topologies, which all yield the same $ T $-algebra.
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.Examples.TheoryAlgebra}{theory_algebra_free}]
-  Recall from \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $.
-Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category $ C $ as $ \op C $ inside its category of $ \SET $-valued functors.
+\begin{lemma}[\coqident{AlgebraicTheories.Examples.TheoryAlgebra}{theory_algebra_free}]
+  $ T_n $ is the free $ T $-algebra on $ n $ generators.
+\end{lemma}
+\begin{proof}
+  Recall from Lemma \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $.
+Now, recall from Definition \ref{def:Yoneda-embedding} for any category $ C $, we can embed $ \op C $ inside $ [C, \SET] $, the category of $ \SET $-valued functors on $ C $.
 This embeds $ n: \mathbf L $ as the theory algebra $ T_n $.
@@
 The natural equivalence immediately shows that $ T_n $ is the free $ T $-algebra on $ n $ elements.
-\end{remark}
+\end{proof}
 
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.RepresentationTheorem}{presheaf_to_L}]\label{rem:presheaf-Yoneda}
-  Recall from \ref{lem:lawvere-presheaf} that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $.
+\begin{lemma}[\coqident{AlgebraicTheories.RepresentationTheorem}{presheaf_to_L}]\label{rem:presheaf-Yoneda}
+  We have natural bijections
+  \[ \Pshf T(T^n, Q) \cong Q_n \]
+  for $ Q : \Pshf T $.
+\end{lemma}
+\begin{proof}
+  Recall from Lemma \ref{lem:lawvere-presheaf} that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $.
 Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category inside its own category of presheaves.
@@
   natural in $ n $ and $ Q $. Explicitly, it sends $ f: \Pshf T(T^n, Q) $ to $ f_n(x_1, \dots, x_n) $ and $ q: Q_n $ to $ (t_i)_i \mapsto q \bullet t $.
-\end{remark}
+\end{proof}
 

### 2024-10-08 500-previous-work.tex
Address a lot of feedback, do a spellcheck

@@
 \end{align*}
-for some constant $ c $, which usually is someting like $ \lambda x_{n + 1}, x_{n + 1} $.
+for some constant $ c $, which usually is something like $ \lambda x_{n + 1}, x_{n + 1} $.
+
+Recall from Section \ref{sec:monoid-category} that we can view any monoid $ M $ as a one-object category $ C_M $, where the morphisms are the elements of $ M $.
 
 \begin{definition}[\coqident{AlgebraicTheories.CategoryOfRetracts}{R}]
-  We define the category \index{R}$ \R $ as the Karoubi envelope $ \overline C_{L_0} $ of the one-point category based on the monoid of the $ \lambda $-terms without free variables under composition.
-In this case, we choose to interpret the Karoubi envelope as the very syntactical construction using idempotents, because Scott reasons about them in this way:
+  Note that the set of $ \lambda $-terms without free variables $ L_0 $ has a monoid structure under the composition defined above.
+The category \index{R}$ \R $ is defined as the Karoubi envelope $ \overline C_{L_0} $ of the category $ C_{L_0} $ of this monoid.
+
+  We choose to implement the Karoubi envelope using a slightly different (but equivalent) very syntactical construction using idempotents, because Scott reasons about them in this way:
   \[ \R_0 = \{ A : L_0 \mid A \circ A = A \} \quad \text{and} \quad \R(A, B) = \{ f: L_0 \mid B \circ f \circ A = f \}, \]
@@
 For example, we can apply the term $ (\lambda x_1, x_1 x_1) $ to itself, which would not be typable in the simply typed $ \lambda $-calculus.
-Suppose that we have a category $ C $ and an object $ U $ such that the morphisms $ C(U^n, U) $ give the untype $ \lambda $-terms in $ n $ free variables, for all $ n $.
+Suppose that we have a category $ C $ and an object $ U $ such that the morphisms $ C(U^n, U) $ give the untyped $ \lambda $-terms in $ n $ free variables, for all $ n $.
 Now, given two terms $ f, g : C(U^n, U) $, for the application $ f g $, we need to consider $ f $ as a morphism in $ C(U^n, U^U) $.
@@
 
-Now, analogously to \ref{lem:locally-cartesian-closed}, Taylor shows:
+Now, analogously to Lemma \ref{lem:locally-cartesian-closed}, Taylor shows:
 \begin{lemma}
@@
 Conversely, if we start with one of Hyland's $ \lambda $-theories $ L $, we can consider $ L_n $ as a subset of $ L_{n + 1} $ by sending $ x_{n, i} $ to $ x_{n + 1, i} $.
-If we take the union $ \bar L = \bigcup_n L_n $ (officially, this is a directed limit), we have a function $ f: \Lambda_{\bar L} \to \bar L $, because the constants of $ \Lambda_{\bar L} $ are exactly the terms of $ \bar L $ and because $ \lambda $-theories in Hyland's sense support the operations of the $ \lambda $-calculus (see subsection \ref{subsec:lambda-calculus-operations}).
+If we take the union $ \bar L = \bigcup_n L_n $ (officially, this is a directed limit), we have a function $ f: \Lambda_{\bar L} \to \bar L $, because the constants of $ \Lambda_{\bar L} $ are exactly the terms of $ \bar L $ and because $ \lambda $-theories in Hyland's sense support the operations of the $ \lambda $-calculus (see Subsection \ref{subsec:lambda-calculus-operations}).
 This gives an equivalence relation on $ \Lambda_{\bar L} $ by taking $ a\ `='\ b $ if $ f(a) = f(b) $.

### 2024-10-08 600-paper.tex
Address a lot of feedback, do a spellcheck

@@
 
-The $ \Lambda $-algebra structure gives the terms of $ A $ quite a lot of interesting behaviour. For example, we can define `function application' and composition as
+The $ \Lambda $-algebra structure gives the terms of $ A $ a lot of interesting behaviour. For example, we can define `function application' and composition as
 \[ a b = (x_1 x_2) \bullet (a, b) \quad \text{and} \quad a \circ b = (x_1 \circ x_2) \bullet (a, b), \]
@@
   Also, note that if $ A = L_0 $ for some $ \lambda $-theory $ L $, then the monoid $ A_1 $ is equivalent to the monoid $ L_1 $, and $ \R_A $ is equivalent to our familiar category of retracts $ \R $.
-Using \ref{lem:equivalent-presheaf-cats}, we have the following 2-commutative diagram:
+Using Lemma \ref{lem:equivalent-presheaf-cats}, we have the following 2-commutative diagram:
   \begin{center}
@@
       &
-      C_{{L_0}_1} \arrow[dd, "\yo" description, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, hook] \arrow[rd, "\sim" description, no head] & & \\
+      C_{{L_0}_1} \arrow[dd, "\yo" description, near start, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, near start, hook] \arrow[rd, "\sim" description, no head] & & \\
       &
-      & C_{L_1} \arrow[dd, "\yo" description, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, hook] & & \mathbf R \arrow[dd, "\yo" description, hook] \arrow[rdd, hook] & \\
+      & C_{L_1} \arrow[dd, "\yo" description, near start, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, near start, hook] & & \mathbf R \arrow[dd, "\yo" description, near start, hook] \arrow[rdd, hook] & \\
       \RAct{{L_0}_1} &
@@
 
-By Lemma 3.2 in \autocite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
+By Lemma 3.2 in \autocite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigzag identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
 \begin{theorem}\label{thm:Hyland-fundamental-theorem}

### 2024-10-08 700-formalization.tex
Address a lot of feedback, do a spellcheck

@@
 \[ (C(\mathrm{transport}_H(c), \mathrm{transport}_H(c^\prime))) = C^\prime(c, c^\prime). \]
-It is usually much easier to show that there exists a functor $ F $ with an inverse, because then we don't have to show these equalities of types, but can suffice with maps between the types and equalities of the objects and morphisms that are mapped.
+It is usually much easier to show that there exists a functor $ F $ with an inverse, because then we do not have to show these equalities of types, but can suffice with maps between the types and equalities of the objects and morphisms that are mapped.
 However, for the morphisms we still have transports.
@@
 The easiest option is usually to show that we have an adjoint equivalence.
-That way, we don't have to show equality of objects, but only isomorphism (even though in a univalent category, that is of course the same).
+That way, we do not have to show equality of objects, but only isomorphism (even though in a univalent category, that is of course the same).
 Then we only have to show equality of morphisms, and this is usually very doable.
@@
 Even though the approach of first defining the categories of all algebras or presheaves and then taking a fiber of this, is necessary to talk about fibrations, there is a drawback to this approach.
-Morphisms in any fiber category are the displayed morphsims over $ \id T $.
+Morphisms in any fiber category are the displayed morphisms over $ \id T $.
 Therefore, naively composing two morphisms in our fiber gives a displayed morphism over $ \id T \cdot \id T $ and we need to transport over the equality $ \id T \cdot \id T = \id T $ to get morphisms in our fiber category again.
@@
 Very early on in the project, a choice was made to use the second approach.
-Since many definitions require extending a mapping to a tuple, and since we don't very often need to extend tuples or do induction on a tuple, this proved to be the right choice.
+Since many definitions require extending a mapping to a tuple, and since we do not very often need to extend tuples or do induction on a tuple, this proved to be the right choice.
 
@@
 In this case, somewhat of a compromise was made.
-The endomorphism theory was indeed defined using a repeated binary product, and the construction of finite powers from the terminal object and binary products\footnote{Unfortunately, defininig the product of a tuple of objects was much harder than defining the finite power of one object.
+The endomorphism theory was indeed defined using a repeated binary product, and the construction of finite powers from the terminal object and binary products\footnote{Unfortunately, defining the product of a tuple of objects was much harder than defining the finite power of one object.
 When generalizing the approach to tuples of objects, some terms suddenly do not have the `correct' type, which has something to do with some equalities like $ ((x_1, \dots, x_n) + (y))_{n + 1} = y $ that do not hold definitionally.
@@
 For example, whether it is possible to create an extensible tactic which shows that some type is a homotopy set, or a mere proposition, and prints the coq statements that can replace the tactic call.
-Or whether it would be possible to generalize \texttt{generate\_refine} to very qukickly generate very fast and precise rewrite statements for large and complicated goals.
+Or whether it would be possible to generalize \texttt{generate\_refine} to very quickly generate very fast and precise rewrite statements for large and complicated goals.
 

### 2024-10-08 920-weak-cartesian-closed.tex
Address a lot of feedback, do a spellcheck

--- 2024-06-26 report/src/weak-cartesian-closed.tex
@@
 
-It seems that semi cartesian closed categories were first defined in \cite{hayashi-1985-semifunctors} and then \cite{hoofman-1993-semi-cartesian-closed} gave a slightly different definition, as well as the very related definition of a weak cartesian closed category.
+It seems that semi cartesian closed categories were first defined in \autocite{hayashi-1985-semifunctors} and then \autocite{hoofman-1993-semi-cartesian-closed} gave a slightly different definition, as well as the very related definition of a weak cartesian closed category.
 The latter paper also contains the construction of the endomorphism $ \lambda $-theory.
@@
   Let $ C $ be a category with binary products (we will call the projections $ \pi_1 $ and $ \pi_2 $), and take $ A, B : C $.
-A \iindex{semi-exponential object} is an object $ A^B : C $, with a morphism $ \mathrm{ev}: C(A^B \times B \to A) $ and a hayashi-1985-semifunctorsfunction
+A \iindex{semi-exponential object} is an object $ A^B : C $, with a morphism $ \mathrm{ev}: C(A^B \times B \to A) $ and a function
   \[ \mathrm{cur}_X: C(X \times B \to A) \to C(X, A^B) \]
@@
   Since the requirements for semi-exponential objects do not involve the usual universal properties, a weak cartesian closed structure (or a semi-exponential object) is not unique up to isomorphism.
-For example, see example 2.1 and 2.2 in \cite{hoofman-1993-semi-cartesian-closed} for two distinct weak cartesian closed structures on a category.
+For example, see example 2.1 and 2.2 in \autocite{hoofman-1993-semi-cartesian-closed} for two distinct weak cartesian closed structures on a category.
 \end{remark}

### 2024-10-09 700-formalization.tex
Add links to the formalization in chapter 7

@@
 % PresheafCategory.v PresheafCategoryCore.v PresheafMorphisms.v Presheaves.v
-  \item Definitions for algebraic theories, $ \lambda $-theories, algebras and presheaves of algebraic theories, together with their morphisms and their categories.
+  \item Definitions for algebraic theories (\coqident{AlgebraicTheories.AlgebraicTheories}{algebraic_theory}), $ \lambda $-theories (\coqident{AlgebraicTheories.LambdaTheories}{lambda_theory}), algebras (\coqident{AlgebraicTheories.Algebras}{algebra}) and presheaves (\coqident{AlgebraicTheories.Presheaves}{presheaf}) of algebraic theories, together with their morphisms and their categories.
 Proofs that the categories are univalent, that the categories of algebraic theories, $ \lambda $-theories and presheaves have limits and that the categories of algebras and presheaves are fibered over the category of algebraic theories.
 % FreeTheory.v LambdaCalculus.v OnePointTheory.v ProjectionsTheory.v TheoryAlgebra.v
-  \item The terminal algebraic theory, the free algebraic theory on a set, with as a special case the initial algebraic theory, the $ \lambda $-theory $ \Lambda $, the $ T $-presheaf structure on $ T $ and the $ T $-algebra structure on $ T_n $.
+  \item The terminal algebraic theory (\coqident{AlgebraicTheories.Examples.OnePointTheory}{one_point_theory}), the free algebraic theory on a set (\coqident{AlgebraicTheories.Examples.FreeTheory}{free_functor}), with as a special case the initial algebraic theory (\coqident{AlgebraicTheories.Examples.ProjectionsTheory}{projections_theory}), the $ \lambda $-theory $ \Lambda $ (\coqident{AlgebraicTheories.Examples.LambdaCalculus}{lambda_calculus_lambda_theory}), the $ T $-presheaf structure on $ T $ and the $ T $-algebra structure on $ T_n $.
 % FreeMonoidTheory.v FreeObjectTheory.v
-  \item The `free object' algebraic theory $ T $ with a functor from $ C $ to $ \Alg T $.
-Also, for the special case where $ C $ is the category of monoids, a proof that this functor $ C \to \Alg T $ is an equivalence.
+  \item The `free object' algebraic theory $ T $ (\coqident{AlgebraicTheories.Examples.FreeObjectTheory}{free_object_theory}) with a functor from $ \C $ to $ \Alg T $ (\coqident{AlgebraicTheories.Examples.FreeObjectTheory}{free_object_algebra_functor}).
+Also, for the special case where $ \C $ is the category of monoids, a proof that this functor $ \C \to \Alg T $ is an equivalence (\coqident{AlgebraicTheories.Examples.FreeMonoidTheory}{monoid_algebra_equivalence}).
 % EndomorphismTheory.v
-  \item The construction of the endomorphism theory $ E(X) $ for some object $ X : C $ in a category $ C $ with finite products.
+  \item The construction of the endomorphism theory $ E(X) $ for some object $ X : \C $ in a category $ \C $ with finite products (\coqident{AlgebraicTheories.Examples.EndomorphismTheory}{endomorphism_lambda_theory}).
 % Combinators.v CategoryOfRetracts.v OriginalRepresentationTheorem.v
-  \item The original version of Scott's representation theorem.
+  \item The original version of Scott's representation theorem (\coqident{AlgebraicTheories.OriginalRepresentationTheorem}{representation_theorem_iso}).
 % Plus1Presheaf.v RepresentationTheorem.v
-  \item Hyland's version of Scott's representation theorem, including the construction of the presheaf $ A(P, 1) $ and the proof that it is the exponential object $ P^T $.
+  \item Hyland's version of Scott's representation theorem (\coqident{AlgebraicTheories.RepresentationTheorem}{presheaf_lambda_theory_iso}), including the construction of the presheaf $ A(P, 1) $ (\coqident{AlgebraicTheories.Examples.Plus1Presheaf}{plus_1_presheaf}) and the proof that it is the exponential object $ P^T $ (\coqident{AlgebraicTheories.RepresentationTheorem}{theory_presheaf_exponentiable}).
 % AlgebraToTheory.v
-  \item The construction of a $ \lambda $-theory from a $ \Lambda $-algebra $ A $ as the endomorphism theory $ E_{\RAct{A_1}}(U_A) $ (Definition \ref{def:lambda-algebra-to-lambda-theory}).
+  \item The construction of a $ \lambda $-theory from a $ \Lambda $-algebra $ A $ as the endomorphism theory $ E_{\RAct{A_1}}(U_A) $, as discussed in Definition \ref{def:lambda-algebra-to-lambda-theory} (\coqident{AlgebraicTheories.FundamentalTheorem.AlgebraToTheory}{lambda_algebra_theory}).
 % AlgebraicTheoryToLawvereTheory.v
-  \item The construction of a Lawvere theory $ L $ from an algebraic theory $ T $, and the equivalence between the presheaf category $ PL $ and the presheaf category $ \Pshf T $.
-% ExtensionsTheory.v LambdaCalculus.v
-  \item The theory of extensions $ T_A $ of a $ T $-algebra.
-  \item An axiomatic definition of the pure $ \lambda $-calculus (see Section \ref{sec:axiomatic-lambda-calculus}).
+  \item The construction of a Lawvere theory $ \cat L $ from an algebraic theory $ T $ (\coqident{AlgebraicTheories.AlgebraicTheoryToLawvereTheory}{algebraic_theory_to_lawvere}), and the equivalence between the presheaf category $ PL $ and the presheaf category $ \Pshf T $ (\coqident{AlgebraicTheories.AlgebraicTheoryToLawvereTheory}{algebraic_presheaf_weq_lawere_presheaf}).
+% ExtensionsTheory.v
+  \item The theory of extensions $ T_A $ of a $ T $-algebra (\coqident{AlgebraicTheories.Examples.ExtensionsTheory}{extensions_theory}), the equivalence between $ \Alg {T_A} $ and $ A \downarrow \Alg T $ (\coqident{AlgebraicTheories.Examples.ExtensionsTheory}{algebra_coslice_equivalence}) and the factorization of every theory morphism $ f: S \to T $ through $ S_{f^*(T_0)} $ (\coqident{AlgebraicTheories.Examples.ExtensionsTheory}{factorization}).
+% LambdaCalculus.v
+  \item An axiomatic definition of the pure $ \lambda $-calculus as discussed in Section \ref{sec:axiomatic-lambda-calculus} (\coqident{AlgebraicTheories.LambdaCalculus}{lambda_calculus}).
 \end{itemize}
@@
   \item The Sigma displayed category creates limits (\coqident{CategoryTheory.DisplayedCats.Examples.Sigma}{creates_limits_sigma_disp_cat}).
-  \item The definitions $ \overline C $ and $ \hat C $ for the Karoubi envelope and their preliminaries.
-  \item The contents of Section \ref{sec:monoid-category}: The construction of a one-object category from a monoid, the equivalence between it's presheaves and sets with a right monoid action, properties of the category of sets with a monoid action and restriction and extension of scalars.
-  \item The Yoneda embedding preserves exponential objects.
-  \item The uniqueness of the Rezk completion.
+  \item The definitions $ \overline \C $ (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}) and $ \tilde \C $ (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope'}) for the Karoubi envelope, together with some properties and their equivalence (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_equivalence}).
+  \item The contents of Section \ref{sec:monoid-category}: The functorial construction of a one-object category from a monoid (\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_to_category}), the equivalence between it's presheaves and sets with a right monoid action (\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_presheaf_action_equivalence}), properties of the category of sets with a monoid action and restriction and extension of scalars (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_restriction_functor}, \coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_functor}).
+  \item The Yoneda embedding preserves exponential objects (\coqident{CategoryTheory.YonedaExponentials}{yoneda_preserves_exponentials}).
+  \item The uniqueness of the Rezk completion (\coqident{Bicategories.RezkCompletions.Uniqueness}{rezk_completion_unique}).
 % FundamentalTheorem/SurjectivePrecomposition.v
-  \item If $ F : C \to C^\prime $ is a fully faithful functor, and $ D $ is a category with colimits, then the precomposition functor $ F \bullet - : [C^\prime, D] \to [C, D] $ is split essentially surjective.
-  \item A proof of a generalized version of Lemma \ref{lem:equivalent-presheaf-cats}, showing that if $ F : C \to C^\prime $ is a functor, if $ F^\prime : C^\prime \to C^{\prime \prime} $ is a fully faithful functor, if $ D $ is a category with colimits and if the precomposition $ (F \bullet F^\prime) \bullet - : [C^{\prime \prime}, D] \to [C, D] $ is an adjoint equivalence, then $ F^\prime \bullet - $ and $ F^\prime \bullet - $ are adjoint equivalences too.
-% FiniteSetSkeleton.v
-  \item The skeleton category $ F $ of finite sets, with
-  \[ F_0 = \{ 0, 1, \dots \} \quad \text{and} \quad F(m, n) = \SET(\{ 1, \dots, n \}, \{ 1, \dots, m \}). \]
+  \item If $ F : \C_1 \to \C_2 $ is a fully faithful functor, and $ \D $ is a category with colimits, then the precomposition functor $ F \bullet - : [\C_2, \D] \to [\C_1, \D] $ is split essentially surjective (\coqident{AlgebraicTheories.FundamentalTheorem.SurjectivePrecomposition}{pre_comp_split_essentially_surjective}).
+  \item A proof of a generalized version of Lemma \ref{lem:equivalent-presheaf-cats}, showing that if $ F_1 : \C_1 \to \C_2 $ is a functor, if $ F_2 : \C_2 \to \C_3 $ is a fully faithful functor, if $ \D $ is a category with colimits and if the precomposition $ (F_1 \bullet F_2) \bullet - : [\C_3, \D] \to [\C_1, \D] $ is an adjoint equivalence, then $ F_1 \bullet - $ and $ F_2 \bullet - $ are adjoint equivalences too (\coqident{CategoryTheory.Equivalences.EquivalenceFromComp}{adjoint_equivalence_1_from_comp}).
 % IndexedSetCategory.v
-  \item The univalent category $ \SET^A $ of indexed sets $ (X_a)_a $ over a type $ A $ (\coqident{AlgebraicTheories.IndexedSetCategory}{is_univalent_indexed_set_cat}, \coqident{AlgebraicTheories.IndexedSetCategory}{limits_indexed_set_cat}), which can be defined formally as
-  \[ \SET^A_0 = (A \to \SET) \quad \text{and} \quad \SET^A(X, Y) = \prod_a X_a \to Y_a. \]
+  \item The univalent category $ \SET^A $ of indexed sets $ (X_a)_a $ over a type $ A $ (\coqident{AlgebraicTheories.IndexedSetCategory}{indexed_set_cat}), which can be defined formally as
+  \[ \SET^A_0 = (A \to \SET) \quad \text{and} \quad \SET^A(X, Y) = \prod_a X_a \to Y_a \]
+  that is univalent (\coqident{AlgebraicTheories.IndexedSetCategory}{is_univalent_indexed_set_cat}) and has limits (\coqident{AlgebraicTheories.IndexedSetCategory}{limits_indexed_set_cat}).
 \end{itemize}
@@
 One of the lessons during this project was that for formalizing, it is always important to choose te right equality for the job.
-For example, for two categories $ C $ and $ C^\prime $, one can aim to prove either that $ C = C^\prime $ or that we have a functor $ F : C \to C^\prime $ that has a right and left inverse, or that we have a functor $ F : C \to C^\prime $ that is an adjoint equivalence.
-Even though for univalent categories, these three notions all coincide, in practice it is really hard to show equality of categories directly: To show $ C = C^\prime $, we would need to show that we have an equality $ H : C_0 = C_0^\prime $, and then that for all $ c, c^\prime : C $
-\[ (C(\mathrm{transport}_H(c), \mathrm{transport}_H(c^\prime))) = C^\prime(c, c^\prime). \]
+For example, for two categories $ \C $ and $ \D $, one can aim to prove either that $ \C = \D $ or that we have a functor $ F : \C \to \D $ that has a right and left inverse, or that we have a functor $ F : \C \to \D $ that is an adjoint equivalence.
+Even though for univalent categories, these three notions all coincide, in practice it is really hard to show equality of categories directly: To show $ \C = \D $, we would need to show that we have an equality $ H : \C_0 = \C_0^\prime $, and then that for all $ c, c^\prime : \C $
+\[ (\C(\mathrm{transport}_H(c), \mathrm{transport}_H(c^\prime))) = \D(c, c^\prime). \]
 It is usually much easier to show that there exists a functor $ F $ with an inverse, because then we do not have to show these equalities of types, but can suffice with maps between the types and equalities of the objects and morphisms that are mapped.
@@
 However, it was possible to remove parts of the proof, and use the rest to construct an adjoint equivalence.
+Since the category in question is univalent, this adjoint equivalence gives us an equivalence of the object types for free.
 
-In general, the formalization is the cleanest and the easiest when we use equality for elements of homotopy sets (morphisms, or terms in an algebraic theory, for example), isomorphisms for objects in a category and adjoint equivalences for categories themselves.
+In general, the formalization is the cleanest and the easiest when we use equality for elements of homotopy sets (morphisms, or terms in an algebraic theory for example), isomorphisms for objects in a category and adjoint equivalences for categories themselves.
 

### 2024-10-09 600-paper.tex
Add links back from the conclusion

@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:relatively-cartesian-closed}
   Since the $ (\hat \R \downarrow_D X) $ are full subcategories of the $ (\Pshf L \downarrow X) $, so we can restrict the adjunction $ f^* \dashv \prod_f $ to an adjunction $ \bar f^* \dashv \bar \prod_f $ between $ (\hat \R \downarrow_D X) $ and $ (\hat \R \downarrow_D Y) $, which shows that $ \hat \R $ is cartesian closed relative to the class $ D $ of display maps.
@@
 
-\begin{remark}
+\begin{remark}\label{rem:difference-Taylor-Hyland}
   Recall that to make sure that $ D(Y, X) $ is a subset of $ \hat \R(Y, X) $, we had no choice but to take the propositional truncation of the $ (Y, f) \triangleleft \Delta_X L $.
@@
 Summarizing,
-\begin{theorem}
+\begin{theorem}\label{thm:elementary-fundamental-theorem}
   The functor that sends $ L : \LamTh $ to $ L_0 : \Alg{\Lambda} $, is an adjoint equivalence.
@@
 
-\begin{remark}
+\begin{remark}\label{rem:alternative-algebra-to-theory}
   Hyland remarks that the isomorphism $ U_A^{U_A} \cong A_2 $ can be generalized to isomorphisms $ U_A^{U_A^n} \cong A_{n + 1} $.
@@
 The final form of Hyland's representation theorem is the following:
-\begin{theorem}
+\begin{theorem}\label{thm:final-fundamental-theorem}
   The functor that sends a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $ and the functor that sends a $ \Lambda $-algebra $ A $ to the theory of extensions $ \Lambda_A $ form an adjoint equivalence

### 2024-10-09 700-formalization.tex
Add links back from the conclusion

@@
 \begin{center}
-  \begin{tikzcd}
-    \text{algebra} \arrow[d] & \lambda\text{-theory} \arrow[d] & \text{presheaf} \arrow[d] \\
-    \text{algebra data} \arrow[d] & \lambda \text{-theory data} \arrow[d] & \text{presheaf data} \arrow[d] \\
-    {\text{(algebraic theory, set)}} \arrow[r] & \text{algebraic theory} \arrow[d] & {\text{(algebraic theory, indexed set)}} \arrow[l] \\
-    & \text{algebraic theory data}\arrow[d] &\\
-    & \text{indexed set} &
+  \begin{tikzcd}[math mode=false]
+    \coqident{AlgebraicTheories.AlgebraCategoryCore}{algebra_cat} \arrow[d]
+    & \coqident{AlgebraicTheories.LambdaTheoryCategoryCore}{lambda_theory_cat} \arrow[d]
+    & \coqident{AlgebraicTheories.PresheafCategoryCore}{presheaf_cat} \arrow[d]
+    \\ \coqident{AlgebraicTheories.AlgebraCategoryCore}{algebra_data_full_cat} \arrow[d]
+    & \coqident{AlgebraicTheories.LambdaTheoryCategoryCore}{lambda_theory_data_cat} \arrow[d]
+    & \coqident{AlgebraicTheories.PresheafCategoryCore}{presheaf_data_cat} \arrow[d]
+    \\ \begin{tabular}{c}\coqident{AlgebraicTheories.AlgebraicTheoryCategoryCore}{algebraic_theory_cat} \\ $ \times $ \coqident{CategoryTheory.Categories.HSET.Core}{hset_category} \end{tabular} \arrow[r]
+    & \coqident{AlgebraicTheories.AlgebraicTheoryCategoryCore}{algebraic_theory_cat} \arrow[d]
+    & \begin{tabular}{c}\coqident{AlgebraicTheories.AlgebraicTheoryCategoryCore}{algebraic_theory_cat} \\ $ \times $ \coqident{AlgebraicTheories.IndexedSetCategory}{indexed_set_cat} \end{tabular} \arrow[l]
+    \\ & \coqident{AlgebraicTheories.AlgebraicTheoryCategoryCore}{algebraic_theory_data_cat} \arrow[d] &
+    \\ & \coqident{AlgebraicTheories.IndexedSetCategory}{indexed_set_cat} &
   \end{tikzcd}
@@
 
-Note that every `relevant' category is constructed in two stages: in the first step, in a category called `\dots data', the displayed objects give the structure (the algebraic theory variables and substitution, the algebra action or the presheaf action) of the objects in question, and the displayed morphisms preserve this structure.
+Note that every category here is constructed in two layers: in the first layer the `data category', the displayed objects give the structure (the algebraic theory variables and substitution, the algebra action or the presheaf action) of the objects in question, and the displayed morphisms preserve this structure.
 In the second step, we take the full subcategory, consisting of the objects that satisfy the right properties.
-For algebraic theories, these properties are the axioms about interplay between the substitution and the variables.
+For algebraic theories, these properties are the axioms about the interaction between the substitution and the variables.
 

### 2024-10-09 800-conclusion.tex
Add links back from the conclusion

@@
 \chapter{Conclusion}
-In this thesis, we have seen how Dana Scott showed in an elementary way that any $ \lambda $-theory arises as the endomorphism theory of a reflexive object in its category of retracts.
-We saw Martin Hyland's proof that any $ \lambda $-theory arises as the endomorphism theory in the presheaf category of its Lawvere theory, using the Yoneda lemma in a very elegant way.
+In this thesis, we have seen how Dana Scott showed in an elementary way that any $ \lambda $-theory arises as the endomorphism theory of a reflexive object in its category of retracts (Theorem \ref{thm:Scott}).
+We saw Martin Hyland's proof that any $ \lambda $-theory arises as the endomorphism theory in the presheaf category of its Lawvere theory, using the Yoneda lemma in a very elegant way (Theorem \ref{thm:representation-theorem}).
 
-We also saw how Paul Taylor shows that Scott's category of retracts is cartesian closed, relative to some class of display maps, and that Hyland gives an interesting new proof of this, using the pre-established fact that the presheaf category is locally cartesian closed.
-Here it was interesting to note that Taylor's and Hyland's proofs are about the same category in classical mathematics, but that these categories become nonequivalent in univalent foundations, one being the Rezk completion of the other.
+We also saw how Paul Taylor shows that Scott's category of retracts is relatively cartesian closed (Theorem \ref{thm:Taylor}), and that Hyland gives an interesting new proof of this (Corollary \ref{cor:relatively-cartesian-closed}), using the pre-established fact that the presheaf category is locally cartesian closed.
+Here it was interesting to note that Taylor's and Hyland's proofs are about the same category in classical mathematics, but that these categories become nonequivalent in univalent foundations (Remark \ref{rem:difference-Taylor-Hyland}), one being the Rezk completion of the other (Corollary \ref{cor:karoubi-candidates}).
 
 As we saw, there are two ways to study the $ \lambda $-calculus using tools from universal algebra: both via $ \lambda $-theories and $ \Lambda $-algebras.
-We saw that Hyland gives an equivalence between these two in his Fundamental Theorem of the $ \lambda $-calculus, where part of his construction again uses a presheaf category, $ \RAct{A_1} $, parallel to his proof of Scott's representation theorem.
+We saw that Hyland gives an equivalence between these two in his Fundamental Theorem of the $ \lambda $-calculus (Theorem \ref{thm:final-fundamental-theorem}), where part of his construction again uses a presheaf category, $ \RAct{A_1} $ (Theorem \ref{thm:Hyland-fundamental-theorem}), parallel to his proof of Scott's representation theorem.
 The equivalence sends a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $ and sends a $ \Lambda $-algebra $ A $ to its theory of extensions $ \Lambda_A $.
-We also saw a couple of variations on the proof of this fundamental theorem, exhibiting multiple equivalent ways to construct a $ \lambda $-theory from a $ \Lambda $-algebra.
+We also saw a couple of variations on the proof of this fundamental theorem (Theorem \ref{thm:elementary-fundamental-theorem} and Remark \ref{rem:alternative-algebra-to-theory}), exhibiting multiple equivalent ways to construct a $ \lambda $-theory from a $ \Lambda $-algebra.
 
-Lastly, we saw how part of the material in this thesis was formalized, and evaluated the choices that were made in the formalization.
+Lastly, we saw how part of the material in this thesis was formalized, and we evaluated the choices that were made in the formalization (Chapter \ref{ch:the-formalization}).
 Unfortunately, due to the very time-consuming nature of formalization, not all of the material could be formalized.
@@
 
-Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \bar C $ and $ \hat C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \bar C $, can be made to work on its Rezk completion $ \hat C $.
+Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \bar \C $ and $ \hat \C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \bar \C $, can be made to work on its Rezk completion $ \hat \C $.

### 2024-10-09 800-conclusion.tex
Expand "future work" section

@@
 Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \bar \C $ and $ \hat \C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \bar \C $, can be made to work on its Rezk completion $ \hat \C $.
+More generally, note that the Karoubi envelope is not specific to the material in this thesis.
+For example, the Karoubi envelope of a `semi cartesian closed category' is a cartesian closed category, and the cartesian closed structure on $ \R $ in Scott's representation theorem can be viewed as a special case of this \autocite{hayashi-1985-semifunctors}.
+In another direction, the category of smooth manifolds can be constructed as the Karoubi envelope of the category $ \C $ of the open subsets of all Euclidean spaces, with smooth maps between them (see \autocite{Lawvere-Karoubi}, page 267).
+For such classical results about the Karoubi envelope, it would be interesting to study how they hold up in univalent foundations for the different choices $ \overline \C $ and $ \hat \C $ of `the Karoubi envelope'.

### 2024-10-11 100-introduction.tex
Add links to the formalization in chapter 7
Write about proof assistants

@@
 Even so, the theoretical study of the $ \lambda $-calculus and its extensions continues to this day.
-For example, in 2017, a paper by Martin Hyland was published\footnote{Note that the paper has been around since 2012, when it was first published as a preprint on arXiv.}, named `classical lambda calculus in modern dress' \autocite{Hyland}.
+For example, in 2017\footnote{Note that the paper has been around since 2012, when it was first published as a preprint on arXiv.}, a paper by Martin Hyland was published, named `classical lambda calculus in modern dress' \autocite{Hyland}.
 In this paper, Hyland approaches the $ \lambda $-calculus from the viewpoint of universal algebra, using algebraic theories, and more generally category theory, to study it.
 This way, he obtains two new proofs for old theorems.
-The paper also contains a theorem that shows that two different ways to study the $ \lambda $-calculus using universal algebra are equivalent.
+The paper also contains a new theorem that shows that two different ways to study the $ \lambda $-calculus using universal algebra are equivalent.
 
-In this thesis, we study the paper through the lens of univalent foundations, a foundation of mathematics based on type theory set forth by Vladimir Voevodsky \autocite{voevodsky-univalent-foundations}.
-We work out the details of the proofs from the paper, see where subtleties arise when converting from set theory to univalent foundations and discuss the formalization of part of the material in the computer proof assistant coq.
+Now, in the last century, mathematics has changed a lot.
+Of course, new theorems have been proved, new conjectures have been made and new areas of mathematics have come into existence.
+However, as in many professions, the arrival of the computer has affected the way that work is done.
+All kinds of tools have been created that aid mathematicians in their job.
+Some of these tools help with quick calculations, for formulating or disproving new conjectures.
+Other tools help in structurally verifying ideas.
+There even have been some `proofs by computer', which consists of a proof on paper that the theorem can be reduced to a finite, but very large, computation, and a computer program that then executes this computation.
+For example, the first proofs of the four color theorem \autocite{four-color-theorem} or the Kepler conjecture \autocite{Kepler-conjecture} were done this way.
+
+However, because the computation part of such a proof involves a lot of code, and computer code tends to contain bugs, accepting a proof by computer involves a certain amount of trust.
+Therefore, both of the theorems mentioned have subsequently also been proved using `computer proof assistants'\autocite{formalized-four-color-theorem}\autocite{formalized-Kepler-conjecture}.
+Such proof assistants, like `rocq', `lean' and `Agda', are computer programs with only a very small `trusted codebase'\footnote{Trusted codebase means the part of the codebase of which we hope that it is correct.
+The rest of the codebase is checked using this trusted core, so if the trusted core is correct, the rest is too.}, that can verify mathematical reasoning.
+In this way, if we trust the small core of such a proof assistant, and the proof assistant says that a proof is correct, then we can trust that indeed, the proof is correct.
+
+However, the way that these programs reason about mathematics is very formal and rigid.
+This means that `formalizing', proving something using a proof assistant, usually involves a great amount of effort, usually much more than doing a pen-and-paper proof.
+However, talking about a choice between doing pen-and-paper proofs and working with proof assistants would be too simplistic.
+Often, doing a pen-and-paper proof can help one to develop an intuition and get new ideas, whereas formalizing those can then help to get a better view of the intricacies of a proof and to sharpen the understanding of why the proof works.
+Therefore, there is a lot of ongoing research into tools and best practices to make the process of formalizing as smooth as possible; to make these programs, which sometimes are experienced as `proof obstructors', really into `proof assistants'.
+
+% <Under construction>
+
+[Univalent foundations]
+, a foundation of mathematics based on type theory set forth by Vladimir Voevodsky \autocite{voevodsky-univalent-foundations}.
+
+In this thesis, we study Hyland's paper through the lens of univalent foundations.
+We work out the details of the proofs from the paper, see where subtleties arise when converting from set theory to univalent foundations and discuss the formalization of part of the material in the proof assistant `rocq'.
 
@@
 \begin{itemize}
+  \item An analysis of the Karoubi envelope in Univalent foundations.
   \item Of particular interest is the discussion of Hyland's proof of the relative cartesian closedness of a category of retracts (or Karoubi envelope) in Section \ref{sec:relatively-cartesian-closed}, which was proved earlier by Paul Taylor in a different way.
 It turns out that in the translation from set theory to univalent foundations, the definition of the category of retracts `branches' into two nonequivalent definitions, and that Taylor's proof is about one definition, whereas Hyland's proof is about the other.
-  \item \TODO
+  \item Analysis of Hyland's work in it's historical context
+  \item Alternative proof of the fundamental theorem
+  \item Formalization
 \end{itemize}
+% </Under construction>
 

### 2024-10-11 400-algebraic-structures.tex
Write about proof assistants

@@
 Later on, we will see an example of a trivial algebraic theory (the terminal theory) $ T $, in which every $ T_n $ only contains one element.
-However, we can say a bit about nontrivial algebraic theories.
+Now, there are many different nontrivial algebraic theories, and it is not easy to find properties that every algebraic theory must satisfy.
+However, we can show that their variables are distinct, and so every $ T_n $ has at least $ n $ distinct elements, so no nontrivial algebraic theory is `almost trivial', if almost trivial means having some $ N $ such that every $ T_n $ has at most $ N $ elements.
 \begin{lemma}\label{lem:nontrivial-algebraic-theory}
@@
 \begin{proof}
-  We can also formulate the statement as: If there exist $ 1 \leq i, j \leq m $ with $ i \not = j $ such that $ x_{m, i} = x_{m, j} $, then all $ L_n $ contain at most one distinct element.
+  We can also formulate the statement as: If there exist $ 1 \leq i, j \leq m $ with $ i \not = j $ such that $ x_{m, i} = x_{m, j} $, then all $ T_n $ contain at most one distinct element.
 
@@
   \[ a = v_i = x_{m, i} \bullet v = x_{m, j} \bullet v = v_j = b, \]
-  so $ L_n $ contains at most one distinct element.
+  so every $ T_n $ contains exactly one element, and $ T $ is trivial.
 \end{proof}

### 2024-10-11 800-conclusion.tex
Write about proof assistants

@@
 More generally, note that the Karoubi envelope is not specific to the material in this thesis.
-For example, the Karoubi envelope of a `semi cartesian closed category' is a cartesian closed category, and the cartesian closed structure on $ \R $ in Scott's representation theorem can be viewed as a special case of this \autocite{hayashi-1985-semifunctors}.
+For example, one way to construct a cartesian closed category is by taking the Karoubi envelope of a `semi cartesian closed category', and the cartesian closed structure on $ \R $ in Scott's representation theorem can be viewed as a special case of this \autocite{hayashi-1985-semifunctors}.
 In another direction, the category of smooth manifolds can be constructed as the Karoubi envelope of the category $ \C $ of the open subsets of all Euclidean spaces, with smooth maps between them (see \autocite{Lawvere-Karoubi}, page 267).

### 2024-10-11 100-introduction.tex
Rewrite the introduction, list main contributions

@@
 A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such an algorithm could not exist \autocite{church-number-theory}.
-A year later, Alan Turing showed, using previous work of Kleene \autocite{kleene-lambda}, that an algorithm is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine \autocite{turing-lambda}, solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.
+A year later, Alan Turing showed, using previous work of Kleene \autocite{kleene-lambda}, that an algorithm is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine \autocite{turing-lambda}, solidifying the position of both the $ \lambda $-calculus and Turing machines as ways to talk about algorithms.
 
 Later, all kinds of different flavours and extensions of the $ \lambda $-calculus were put forth, with colorful names like `simply typed $ \lambda $-calculus', `System T' and `PCF'.
-Even though the $ \lambda $-calculus was originally a very abstract tool, it was also the inspiration for function programming languages, and traces of it can be seen in imperative programming languages, where unnamed functions are commonly called `lambda expressions' \autocite{java-lambdas} and are sometimes even written like \texttt{lambda x y : (x - y) * (x + y)} \autocite{python-expressions}.
+Even though the $ \lambda $-calculus was originally a very theoretical tool, it was also the inspiration for function programming languages, and traces of it can be seen in imperative programming languages, where unnamed functions are commonly called `lambda expressions' \autocite{java-lambdas} and are sometimes even written like \texttt{lambda x y : (x - y) * (x + y)} \autocite{python-expressions}.
 
 Even so, the theoretical study of the $ \lambda $-calculus and its extensions continues to this day.
-For example, in 2017\footnote{Note that the paper has been around since 2012, when it was first published as a preprint on arXiv.}, a paper by Martin Hyland was published, named `classical lambda calculus in modern dress' \autocite{Hyland}.
+For example, in 2017\footnote{Note that the paper has been around since 2012, when it was first published as a preprint on arXiv.}, a paper by Martin Hyland was published with the title `classical lambda calculus in modern dress' \autocite{Hyland}.
 In this paper, Hyland approaches the $ \lambda $-calculus from the viewpoint of universal algebra, using algebraic theories, and more generally category theory, to study it.
@@
 Now, in the last century, mathematics has changed a lot.
-Of course, new theorems have been proved, new conjectures have been made and new areas of mathematics have come into existence.
-However, as in many professions, the arrival of the computer has affected the way that work is done.
+Of course, new theorems have been proved, new conjectures have been made and entire new areas of mathematics have come into existence.
+However, as in many professions, the arrival of the computer has affected the way that work is done in mathematics.
 All kinds of tools have been created that aid mathematicians in their job.
@@
 Other tools help in structurally verifying ideas.
-There even have been some `proofs by computer', which consists of a proof on paper that the theorem can be reduced to a finite, but very large, computation, and a computer program that then executes this computation.
-For example, the first proofs of the four color theorem \autocite{four-color-theorem} or the Kepler conjecture \autocite{Kepler-conjecture} were done this way.
+There even have been some `proofs by computer', which consist of a proof on paper that a theorem can be reduced to a finite, but very large, computation, and a computer program that then executes this computation.
+For example, the first proofs of the four color theorem \autocite{four-color-theorem} and the Kepler conjecture \autocite{Kepler-conjecture} were done this way.
 
@@
 
-However, the way that these programs reason about mathematics is very formal and rigid.
+This sounds great in theory, but in practice, the way that these programs reason about mathematics is very formal and rigid.
 This means that `formalizing', proving something using a proof assistant, usually involves a great amount of effort, usually much more than doing a pen-and-paper proof.
-However, talking about a choice between doing pen-and-paper proofs and working with proof assistants would be too simplistic.
-Often, doing a pen-and-paper proof can help one to develop an intuition and get new ideas, whereas formalizing those can then help to get a better view of the intricacies of a proof and to sharpen the understanding of why the proof works.
+However, representing this as a choice between doing pen-and-paper proofs and working with proof assistants would be too simplistic.
+Often, doing a pen-and-paper proof can help one to develop an intuition and get new ideas, whereas formalizing those ideas can then help to get a better view of the subtleties of a proof and to sharpen the understanding of why the proof works.
 Therefore, there is a lot of ongoing research into tools and best practices to make the process of formalizing as smooth as possible; to make these programs, which sometimes are experienced as `proof obstructors', really into `proof assistants'.
 
-% <Under construction>
+Now, much of contemporary mathematics is built on the foundation of set theory, which we will often refer to as \iindex{classical mathematics}.
+Usually, `set theory' refers to ZFC: Zermelo Fraenkel set theory with the axiom of choice, developed in the early 1900s.
+On the other hand, most of the formalization in proof assistants is built on the foundation of type theory.
+This is because computers can reason better with types than with sets, as evidenced by the many typed programming languages that are around nowadays.
+However, type theory has been around longer than computers have: it was initially developed by Bertrand Russell in the early 1900s, to create a foundation of mathematics that avoided Russell's paradox\footnote{``Consider the set of all sets that do not contain themself.
+Does this set contain itself?''}.
 
-[Univalent foundations]
-, a foundation of mathematics based on type theory set forth by Vladimir Voevodsky \autocite{voevodsky-univalent-foundations}.
+Nowadays, there are many flavours of type theory around.
+The proof assistant rocq is based on the `calculus of constructions' whereas the proof assistant Agda works with the `unified theory of dependent types'.
+Every flavour has its advantages and disadvantages, but in this thesis we will work with `univalent foundations', set forth by Vladimir Voevodsky \autocite{voevodsky-univalent-foundations}.
+In univalent foundations, the common mathematical principle that `things with a similar structure\footnote{For example, two sets with a bijection between them have a similar structure.
+Also, two graphs $ G $ and $ H $ have a similar structure when there is a bijection $ f $ between their sets of vertices, such that for every two vertices $ v, w : G $, we have a bijection between the set of edges from $ v $ to $ w $, and the set of edges from $ f(v) $ to $ f(w) $.}, are the same' is made explicit.
+The principle is used often in modern mathematics, and making this explicit in the type theory that we work with, allows us to use the principle when formalizing.
 
-In this thesis, we study Hyland's paper through the lens of univalent foundations.
-We work out the details of the proofs from the paper, see where subtleties arise when converting from set theory to univalent foundations and discuss the formalization of part of the material in the proof assistant `rocq'.
+However, note that two objects can often have a similar structure in more than one way.
+For example, the set $ \{ \top, \bot \} $ has two bijections to the set $ \{ 0, 1 \} $.
+To accomodate for this, in univalent foundations, two things can sometimes `be the same' in more way than one.
+For example, we have two equalities between $ \{ \top, \bot \} $ and $ \{ 0, 1 \} $.
+This means that the concept of `sameness' is more intricate to work with in univalent foundations than it is in set theory.
+This is one of the reasons that there are subtleties involved in transferring definitions and proofs from set theory to univalent foundations.
+It is therefore still a topic of ongoing research how well different parts of set-based mathematics can be transferred to univalent foundations and what subtleties pop up when material from set-based mathematics is transferred to univalent foundations.
+For example, often in set-based mathematics, two definitions are equivalent if we assume the axiom of choice.
+However, sometimes in univalent foundations, the axiom of choice is not sufficient to make two such definitions equivalent, and then we have two different definitions.
+It is then interesting to explore the behaviour of these two different definitions in univalent foundations.
 
-The major contributions of this thesis are
+In this thesis, we study the paper `classical lambda calculus in modern dress' through the lens of univalent foundations, work out the details of the proofs and formalize part of the paper and its preliminaries.
+The major contributions are
 \begin{itemize}
-  \item An analysis of the Karoubi envelope in Univalent foundations.
-  \item Of particular interest is the discussion of Hyland's proof of the relative cartesian closedness of a category of retracts (or Karoubi envelope) in Section \ref{sec:relatively-cartesian-closed}, which was proved earlier by Paul Taylor in a different way.
-It turns out that in the translation from set theory to univalent foundations, the definition of the category of retracts `branches' into two nonequivalent definitions, and that Taylor's proof is about one definition, whereas Hyland's proof is about the other.
-  \item Analysis of Hyland's work in it's historical context
-  \item Alternative proof of the fundamental theorem
-  \item Formalization
+  \item The category theoretical preliminaries needed to understand the paper (Chapter \ref{ch:category-theory}), as well as the work of Hyland's predecessors that he expands upon (Chapter \ref{ch:previous-work}), and more detailed versions of his definitions and proofs, complemented with some examples (Chapters \ref{ch:algebraic-structures} and \ref{ch:the-paper}).
+This makes Hyland's paper more accessible to computer scientists.
+  \item The translation of Hyland's paper and the work of his predecessors to univalent foundations (Chapter \ref{ch:the-paper}).
+This shows that his work can be translated to univalent foundations, and contributes to the knowledge about translating classical mathematics to univalent foundations in general.
+  \item A formalization of part of the paper in rocq (Chapter \ref{ch:the-formalization}). This contributes to the knowledge about formalization in general.
+  \item A new proof for the fundamental theorem of the $ \lambda $-calculus (Section \ref{sec:elementary-fundamental-theorem}).
+This version is easier to read and verify, because it is more elementary and uses less category theory than Hyland's proof.
+  \item An analysis of the behaviour of the Karoubi envelope in univalent foundations in general (Section \ref{sec:karoubi-envelope}), and in the specific case of Paul Taylor's and Martin Hyland's work (Remark \ref{rem:difference-Taylor-Hyland}).
+Here we see an example of two definitions that are equivalent in classical mathematics, but become different in univalent foundations.
+It is interesting to see the differences between the behaviour of the two definitions in univalent foundations.
 \end{itemize}
-% </Under construction>
 
 % 600-paper.tex
-Now, most of this thesis works towards Chapter \ref{ch:the-paper}, about Hyland's paper.
-% 500-previous-work.tex
-He builds upon work of other authors, though, and understanding their work, exposited in Chapter \ref{ch:previous-work}, helps to understand Hyland's paper.
-% 200-category-theory.tex
-Since both Hyland and the other authors use a lot of category theory, Chapter \ref{ch:category-theory} establishes most of the preliminary knowledge regarding category theory.
-It is probably wise to skim this chapter, and sporadically come back to it to better understand the material in the other chapters.
+Now, most of this thesis works towards Chapter \ref{ch:the-paper}, about the three main proofs of Hyland's paper.
 % 300-univalent-foundations.tex
 Because this thesis works from a univalent point of view, Chapter \ref{ch:univalent-foundations} introduces univalent foundations and builds the preliminary knowledge in that area for the rest of the paper.
+% 500-previous-work.tex
+As mentioned before, the work of Hyland's predecessors that is covered in Chapter \ref{ch:previous-work} helps to understand his paper.
+% 200-category-theory.tex
+The category theoretical preliminaries for understanding Hyland's paper are covered in Chapter \ref{ch:category-theory}.
+It is probably wise to skim this chapter, and periodically come back to it to better understand the material in the other chapters.
 % 400-algebraic-structures.tex
-Then, Chapter \ref{ch:algebraic-structures} introduces the main objects that are studied by Hyland, namely $ \lambda $-theories and $ \Lambda $-algebras, together with related notions and examples.
+Hyland's three main theorems deal with a couple of objects that he introduces. These objects, together with some properties and examples, are introduced in Chapter \ref{ch:algebraic-structures}.
 % 700-formalization.tex
@@
 
-Note that throughout this document, links are included to \href{https://arnoudvanderleer.github.io/cs-masters-thesis/toc.html}{\nolinkurl{documentation}} of the corresponding formalized material.
+Throughout this document, links are included to \href{https://arnoudvanderleer.github.io/cs-masters-thesis/toc.html}{\nolinkurl{documentation}} of the corresponding formalized material.
 The documentation refers to the state of \href{https://github.com/UniMath/UniMath/tree/5eb5c8958c4dddd4219f895bf7bc51547395522d}{\texttt{the UniMath repository}} at commit \texttt{5eb5c8958c4dddd4219f895bf7bc51547395522d}.

### 2024-10-14 200-category-theory.tex
Rewrite the introduction, list main contributions
Slightly clean up chapter 4

@@
 And composition of functors $ F: \A \to \B $ and $ G: \B \to \C $ will be denoted by $ F \bullet G $.
+
+In this thesis, we will often work with `tuples': elements of $ S^n $ for some set $ S $ and some natural number $ n $. We will denote
+\[ (s_i)_i = (s_1, s_2, \dots, s_n) \quad \text{and} \quad s + t = (s_1, \dots, s_n, t_1, \dots, t_m) : S^{n + m} \]
+for $ s : S^n $ and $ t : S^m $.
 
@@
 
-\section{The Karoubi Envelope}
+\section{The Karoubi Envelope}\label{sec:karoubi-envelope}
 Let $ \C $ be a category and $ X, Y : \C $ objects. We will denote the type of section-retraction pairs of $ Y $ onto $ X $ with

### 2024-10-14 400-algebraic-structures.tex
Slightly clean up chapter 4

--- 2024-10-08 400-algebraic-structures.tex
@@
 \begin{definition}[\coqident{AlgebraicTheories.AlgebraicTheories}{algebraic_theory}]
-  We define an \iindex{algebraic theory} $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we usually leave $ n $ implicit), together with a substitution operation
+  We define an \iindex{algebraic theory} $ T $ to be a sequence of sets $ T_n $ indexed over $ \mathbb N $ with for all $ 1 \leq i \leq n $ elements ("variables" or "projections") $ x_{n, i}: T_n $ (we often leave $ n $ implicit and write $ x_i $), together with a substitution operation
   \[ \_ \bullet \_: T_m \times T_n^m \to T_n \]
-  for all $ m, n $, such that
+  for all $ m $ and $ n $, such that
   \begin{align*}
@@
 \begin{definition}[\coqident{AlgebraicTheories.AlgebraicTheoryMorphism}{algebraic_theory_morphism}]
-  A \textit{morphism}\index{algebraic theory!morphism} $ f $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ f_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit) such that
+  A \textit{morphism}\index{algebraic theory!morphism} $ f $ between algebraic theories $ T $ and $ T^\prime $ is a sequence of functions $ f_n: T_n \to T^\prime_n $ (we usually leave the $ n $ implicit and just write $ f $ if the context is clear) such that
   \begin{align*}
     f_n(x_j) &= x_j\\
-    f_n(f \bullet g) &= f_m(f) \bullet (f_n(g_i))_i
+    f_n(s \bullet t) &= f_m(s) \bullet (f_n(t_i))_i
   \end{align*}
-  for all $ 1 \leq j \leq n $, $ f: T_m $ and $ g: T_n^m $.
+  for all $ 1 \leq j \leq n $, $ s: T_m $ and $ t: T_n^m $.
 \end{definition}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{limits_algebraic_theory_cat}]\label{rem:algebraic-theory-limits}
-  We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x_i) $ and substitution
+  We can construct binary products of algebraic theories, with sets $ (T \times T^\prime)_n = T_n \times T^\prime_n $, variables $ (x_i, x^\prime_i) $ and substitution
   \[ (f, f^\prime) \bullet (g, g^\prime) = (f \bullet g, f^\prime \bullet g^\prime). \]
@@
 
-  Note that the forgetful functor $ F: \AlgTh \to \SET^{\mathbb N} $ creates limits, since any diagram $ d $ has a limit and the underlying set of the limit of $ d $ is the limit of the underlying sets of the objects in $ d $.
+  Note that the forgetful functor $ F: \AlgTh \to \SET^{\mathbb N} $ (where $ \SET^{\mathbb N} $ is the category of `sequences of sets' $ (T_n)_n $) creates limits, since any diagram $ D $ has a limit and the underlying set of the limit of $ D $ is the limit of the underlying sets of the objects in $ D $.
 \end{lemma}
@@
 Later on, we will see an example of a trivial algebraic theory (the terminal theory) $ T $, in which every $ T_n $ only contains one element.
-However, we can say a bit about nontrivial algebraic theories.
+Now, there are many different nontrivial algebraic theories, and it is not easy to find properties that every algebraic theory must satisfy.
+However, to explore their general structure a little bit, we can show that their variables are distinct, and so every $ T_n $ has at least $ n $ distinct elements.
+Therefore, no nontrivial algebraic theory is `almost trivial', if almost trivial means having some $ N $ such that every $ T_n $ has at most $ N $ elements.
 \begin{lemma}\label{lem:nontrivial-algebraic-theory}
-  Let $ T $ be an algebraic theory, such that $ T_n $ has at least two distinct elements for some $ n $. Then for all $ 1 \leq i, j \leq m $ with $ i \not = j $, we have $ x_{m, i} \not = x_{m, j} $.
+  Let $ T $ be an algebraic theory, such that $ T_n $ has at least two distinct elements for some $ n $. Then for all $ 1 \leq i, j \leq m $ with $ i \not = j $, we have $ x_i \not = x_j $.
 \end{lemma}
 \begin{proof}
-  We can also formulate the statement as: If there exist $ 1 \leq i, j \leq m $ with $ i \not = j $ such that $ x_{m, i} = x_{m, j} $, then all $ L_n $ contain at most one distinct element.
+  We can also formulate the statement as: If there exist $ 1 \leq i, j \leq m $ with $ i \not = j $ such that $ x_i = x_j $, then every $ T_n $ contains at most one distinct element.
 
-  So, suppose that $ x_{m, i} = x_{m, j} $ for some $ i \not = j $. For $ a, b : L_n $, we define $ v : L_n^m $ as
+  So, suppose that $ x_i = x_j $ for some $ i \not = j $. For $ a, b : T_n $, we define $ v : T_n^m $ as
   \[ v_k = \left\{\begin{array}{ll} a & k = i\\ b & k \not = i \end{array}\right., \]
   so in particular, $ v_j = b $. Then we have
-  \[ a = v_i = x_{m, i} \bullet v = x_{m, j} \bullet v = v_j = b, \]
-  so $ L_n $ contains at most one distinct element.
+  \[ a = v_i = x_i \bullet v = x_j \bullet v = v_j = b, \]
+  so every $ T_n $ contains exactly one element, and $ T $ is trivial.
 \end{proof}
+
+Now, there are also a lot of other, equivalent ways to define the objects that we call `algebraic theories' here.
+For a couple of these alternative definitions, see Chapter \ref{ch:alternative-definitions}.
+In particular, an algebraic theory is equivalent to a category $ \L $ with $ \L_0 = \mathbb N $ where the object $ n $ is $ 1^n $, the $ n $-fold product of $ 1 $.
 
@@
 \begin{lemma}[\coqident{AlgebraicTheories.AlgebraCategory}{is_univalent_algebra_cat}]
-  Note that just like with algebraic theories, the category of $ T $-algebras is univalent because its (iso)morphisms preserve $ \bullet $.
+  Just like with algebraic theories, the category of $ T $-algebras is univalent because its (iso)morphisms preserve $ \bullet $.
 \end{lemma}
@@
 For example, consider (binary) products and coproducts of groups.
+
+  Note that this means that any category that does not have all limits or colimits, is not algebraic.
+For example, the category of fields (commutative rings that also have a division operation) is not algebraic: the product $ \mathbb Q \times \mathbb F_p $ does not exist, because there is no (product) field that has morphisms to fields of different characteristic.
 \end{remark}
@@
 
-  First of all, note that for all $ n : \mathbb N $ and $ B : \Alg T $, the following diagram in $ \SET $ commutes:
+  First of all, note that for all $ n : \mathbb N $ and $ A : \Alg T $, the following diagram in $ \SET $ commutes:
   \begin{center}
     \begin{tikzcd}
-      \Alg T(T_n, B) \arrow[r, "f^*"] \arrow[d, "\sim"] & \Alg{T^\prime}(f^* T_n, f^* B) \arrow[d, "\bar f_n \cdot -"]\\
-      B^n \arrow[r, "\sim"] & \Alg{T^\prime}(T^\prime_n, f^* B)
+      \Alg T(T_n, A) \arrow[r, "f^*"] \arrow[d, "\sim"] & \Alg{T^\prime}(f^* T_n, f^* A) \arrow[d, "\bar f_n \cdot -"]\\
+      A^n \arrow[r, "\sim"] & \Alg{T^\prime}(T^\prime_n, f^* A)
     \end{tikzcd}
@@
   with $ \bar f_n: T^\prime_n \to f^* T_n $ the $ T^\prime $-algebra morphism with underlying function $ f_n $.
-Note that $ f^* $ is fully faithful, so the function at the top is a bijection, and so precomposition by $ \bar f_n $ is a bijection as well.
+Note that $ f^* $ is fully faithful, so the function at the top of the diagram is a bijection, and so precomposition by $ \bar f_n $ is a bijection as well.
 Since $ f^* $ is essentially surjective, we have for all $ A : \Alg T^\prime $, some $ B : \Alg T $ and an isomorphism $ h: f^* B \xrightarrow \sim A $, which gives the following commutative diagram:
@@
 Note that besides the categories $ \Alg T $, we can also consider the category of `all' algebraic theory algebras together (\coqident{AlgebraicTheories.AlgebraCategoryCore}{algebra_full_cat}).
-That is, the category $ C $ with $ C_0 = \sum_{T : \AlgTh}, \Alg T $ and $ C((T, A), (T^\prime, A^\prime)) $ consisting of pairs $ (f, f^\prime): \AlgTh(T, T^\prime) \times \SET(A, A^\prime) $ such that for all $ t: T_n $ and $ a: A^n $,
+That is, the category $ \int_T \Alg T $ with $ (\int_T \Alg T)_0 = \sum_{T : \AlgTh}, \Alg T $ and $ (\int_T \Alg T)((S, A), (T, B)) $ consisting of pairs $ (f, f^\prime): \AlgTh(S, T) \times \SET(A, B) $ such that for all $ t: S_n $ and $ a: A^n $,
 \[ f^\prime(t \bullet a) = f(t) \bullet (f^\prime(a_i))_i. \]
-We then have a functor $ P: C \to \AlgTh $, projecting onto the first coordinate.
+We then have a functor $ P: \int \Alg T \to \AlgTh $, projecting onto the first coordinate.
 
@@
 \begin{proof}
-  Given an algebraic theory morphism $ f: \AlgTh(S, T) $ and a $ T $-algebra $ A_T $, Definition \ref{def:algebra-pullback} gives an $ S $-algebra $ A_S $ with underlying set $ A_T $.
-The cartesian morphism is $ (f, \id{A_T}): C((S, A_S), (T, A_T)) $.
+  Given an algebraic theory morphism $ f: \AlgTh(S, T) $ and a $ T $-algebra $ A $, Definition \ref{def:algebra-pullback} gives an $ S $-algebra $ f^* A $ with underlying set $ A $.
+The cartesian morphism is $ (f, \id A): (\int \Alg T)((S, f^* A), (T, A)) $.
 
-  It is cartesian because for $ (R, A_R): C $ and $ (g, g^\prime): C((R, A_R), (T, A_T)) $ and $ h: \AlgTh(R, S) $ with $ h \cdot f = g $, the required morphism $ C((R, A_R), (S, A_S)) $ is given by $ g^\prime: \SET(A_R, A_S) $.
+  It is cartesian because for $ (R, B): \int \Alg T $ and $ (g, g^\prime): (\int \Alg T)((R, B), (T, A)) $ and $ h: \AlgTh(R, S) $ with $ h \cdot f = g $, the required morphism over $ h $ is given by $ g^\prime: \SET(B, A) $.
 \end{proof}
@@
 \begin{definition}[\coqident{AlgebraicTheories.PresheafMorphisms}{presheaf_morphism}]
-  For an algebraic theory $ T $, a \textit{morphism}\index{presheaf!morphism} $ f $ between $ T $-presheaves $ P $ and $ P^\prime $ is a sequence of functions $ f_n: P_n \to P^\prime_n $ such that
+  For an algebraic theory $ T $, a \textit{morphism}\index{presheaf!morphism} $ f $ between $ T $-presheaves $ P $ and $ Q $ is a sequence of functions $ f_n: P_n \to Q_n $ such that
   \[ f_n(t \bullet f) = f_m(t) \bullet f \]
@@
 
+The equivalence between algebraic theories and Lawvere theories gives an equivalence between the presheaf category $ \Pshf T $ of an algebraic theory, and the presheaf category $ P \L_T = [\op{\L_T}, \SET] $ of its associated Lawvere theory (see Lemma \ref{lem:lawvere-presheaf}).
+
 \section{\texorpdfstring{$ \lambda $-}{lambda-}theories}
 
-Let \index{$ \iota_{m, n} $}$ \iota_{m, n} : T_m \to T_{m + n} $ be the function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
+Now we get to the core definition: $ \lambda $-theories. It is what allows us to use algebraic theories to reason about the $ \lambda $-calculus.
+
+Let \index{$ \iota_{m, n} $}$ \iota_{m, n} : T_m \to T_{m + n} $ be the `inflation' function that sends $ f $ to $ f \bullet (x_{m + n, 1}, \dots, x_{m + n, m}) $. Note that
 \[ \iota_{m, n}(f) \bullet g = f \bullet (g_i)_{i \leq m} \quad \text{and} \quad \iota_{m, n}(f \bullet g) = f \bullet (\iota_{m, n}(g_i))_i. \]
-
-For tuples $ x : X^m $ and $ y: X^n $, let $ x + y $ denote the tuple $ (x_1, \dots, x_m, y_1, \dots, y_n) : X^{m + n} $.
 
@@
   for all $ f: L_{m + 1} $, $ g: L_m $ and $ h: L_n^m $.
+\end{definition}
+
+\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{has_β} \coqident{AlgebraicTheories.LambdaTheories}{has_η}]\label{def:beta-equality}
+  We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $.
+We say that is satisfies $ \eta $-equality if $ \lambda_n \circ \rho_n = \id{L_{n + 1}} $ for all $ n $.
 \end{definition}
@@
 
-\begin{definition}[\coqident{AlgebraicTheories.LambdaTheories}{has_β} \coqident{AlgebraicTheories.LambdaTheories}{has_η}]\label{def:beta-equality}
-  We say that a $ \lambda $-theory $ L $ satisfies $ \beta $-equality (or that it is a $ \lambda $-theory with $ \beta $) if $ \rho_n \circ \lambda_n = \id{L_n} $ for all $ n $.
-We say that is satisfies $ \eta $-equality if $ \lambda_n \circ \rho_n = \id{L_{n + 1}} $ for all $ n $.
-\end{definition}
-
-\begin{definition}[\coqident{AlgebraicTheories.LambdaTheoryMorphisms}{lambda_theory_morphism}] \textit{morphism}\index{$ \lambda $-theory!morphism} $ f $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ f $ such that
+\begin{definition}[\coqident{AlgebraicTheories.LambdaTheoryMorphisms}{lambda_theory_morphism}]
+  A \textit{morphism}\index{$ \lambda $-theory!morphism} $ f $ between $ \lambda $-theories $ L $ and $ L^\prime $ is an algebraic theory morphism $ f $ such that
   \begin{align*}
@@
 \subsection{The $ \lambda $-calculus operations}\label{subsec:lambda-calculus-operations}
-Now, for a $ \lambda $-theory $ L $, we have variables $ x_{n, i} : L_n $ and $ \lambda $-abstraction $ f \mapsto \lambda(f) $.
+For a $ \lambda $-theory $ L $, we have variables $ x_{n, i} : L_n $ and $ \lambda $-abstraction $ f \mapsto \lambda(f) $.
 We will sometimes denote $ \lambda(f) $ as $ \lambda x_{n + 1}, f $ for $ f: L_{n + 1} $.
@@
 \end{definition}
-This means that we can interpret all three operations of the $ \lambda $-calculus in $ L $.
+This means that we can interpret all three operations (\texttt{var}, \texttt{app} and \texttt{abs}) of the $ \lambda $-calculus in $ L $.
+
+\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app}]
+  Note that for $ f, g : L_n $,
+  \[
+    \rho(f) \bullet (x_1, \dots, x_n, g)
+    = \rho(x_1) \bullet (\iota_{n, 1}(f), x_{n + 1}) \bullet (x_1, \dots, x_n, g)
+    = \rho(x_1) \bullet (\iota_{n, 1}(f), g),
+  \]
+  so we could also define the application as $ f g = \rho(f) \bullet (x_1, \dots, x_n, g) $, although that is more complicated.
+\end{remark}
 
@@
 
-\begin{remark}[\coqident{AlgebraicTheories.LambdaTheories}{app}]
-  Note that for $ f, g : L_n $,
-  \[
-    \rho(f) \bullet (x_1, \dots, x_n, g)
-    = \rho(x_1) \bullet (\iota_{n, 1}(f), x_{n + 1}) \bullet (x_1, \dots, x_n, g)
-    = \rho(x_1) \bullet (\iota_{n, 1}(f), g),
-  \]
-  so we could also define the application as $ f g = \rho(f) \bullet (x_1, \dots, x_n, g) $, although that is more complicated.
-\end{remark}
-
 \begin{remark}\label{rem:lambda-theory-or-algebra}
@@
 Alternatively, we can try to study the $ \lambda $-calculus-like structures as algebras for some algebraic theory $ \Lambda $.
-However, it is not clear beforehand that this will succeed, because there is no reason why this category should be algebraic.
+However, it is not clear beforehand that this will succeed, because there is no reason why the category of $ \lambda $-calculus-like structures should be algebraic.
 In particular, $ \lambda $-abstraction causes problems, because it is not an algebraic operation.
@@
 
-There is a lot of different examples of algebraic theories and their algebras. Some of these even turn out to be $ \lambda $-theories. In this section, we will discuss a couple of these.
+There are a lot of different examples of algebraic theories and $ \lambda $-theories and their algebras. In this section, we will discuss a couple of these examples.
 
@@
 
-Note that we have a forgetful functor $ (\cdot)_0 $ that sends a morphism of algebraic theories $ g: T \to T^\prime $ to the function $ f_0: T_0 \to T^\prime_0 $.
+Note that we have a forgetful functor $ (\cdot)_0 $ that sends a morphism of algebraic theories $ g: T \to T^\prime $ to the function $ g_0: T_0 \to T^\prime_0 $.
 
@@
 
-The proofs that $ F(S) $ is an algebraic theory and that $ F(f) $ and $ g $ are algebraic theory morphisms is an easy exercise in case distinction.
+The proofs that $ F(S) $ is an algebraic theory and that $ F(f) $ and $ g $ are algebraic theory morphisms are easy exercises in case distinction.
 
@@
 
-  Therefore, the functor $ \Alg{F(S)} \to S \downarrow \SET $ is an adjoint equivalence.
+  Therefore, the functor $ \Alg{F(S)} \to (S \downarrow \SET) $ is an adjoint equivalence.
 
@@
   Note that the category of $ F(\emptyset) $-algebras is equivalent to the coslice-category $ (\emptyset \downarrow \SET) $, which, since $ \emptyset $ is the initial set, is just equivalent to $ \SET $.
+Therefore, $ \SET $ is algebraic.
 \end{remark}
@@
 
-Like with the free algebraic theory, we will construct the free $ \lambda $-theory as the smallest nontrivial $ \lambda $-theory (which is the $ \lambda $-calculus) with some additional constants.
+Like with the free algebraic theory, we will construct the free $ \lambda $-theory as the `pure', inductive $ \lambda $-calculus, with some additional constants.
 
-Let $ S $ be a set. Consider the sequence of inductive types $ (\Lambda(S)_n)_n $ with the following constructors:
+Let $ S $ be a set. Consider the sequence of inductive types $ X_n $ with the following constructors:
 \begin{align*}
-  \mathtt{Var}_n &: \{ 1, \dots, n \} \to \Lambda(S)_n;\\
-  \mathtt{App}_n &: \Lambda(S)_n \to \Lambda(S)_n \to \Lambda(S)_n;\\
-  \mathtt{Abs}_n &: \Lambda(S)_{n + 1} \to \Lambda(S)_n;\\
-  \mathtt{Con}_n &: S \to \Lambda(S)_n.\\
+  \mathtt{Var}_n &: \{ 1, \dots, n \} \to X_n;\\
+  \mathtt{App}_n &: X_n \to X_n \to X_n;\\
+  \mathtt{Abs}_n &: X_{n + 1} \to X_n;\\
+  \mathtt{Con}_n &: S \to X_n.\\
 \end{align*}
 
-Define a substitution operator $ \bullet: \Lambda(S)_m \times \Lambda(S)_n^m \to \Lambda(S)_n $ by induction on the first argument:
+Define a substitution operator $ \bullet: X_m \times X_n^m \to X_n $ by induction on the first argument:
 \begin{align*}
@@
 
-And then quotient $ \Lambda(S) $ by the relation generated by
+And then quotient $ X $ by the relation generated by
 \[ \mathtt{App}_m(\mathtt{Abs}_m(f), g) \sim f \bullet ((x_{n, i})_i + (g)) \]
-for all $ f: \Lambda(S)_{n + 1} $ and $ g: \Lambda(S)_n $.
+for all $ f: X_{n + 1} $ and $ g: X_n $. This gives a sequence of sets $ (\Lambda(S)_n)_n $.
 
 \begin{example}\label{ex:free-lambda-theory}
-  We can give the sequence of sets $ \Lambda(S) $ an algebraic theory structure with variables $ x_{m, i} = \mathtt{Var}_m(i) $ and the substitution operator $ \bullet $ defined above.
+  We can give $ \Lambda(S) $ an algebraic theory structure with variables $ x_{m, i} = \mathtt{Var}_m(i) $ and the substitution operator $ \bullet $ defined above.
 We can give $ \Lambda(S) $ a $ \lambda $-theory structure with $ \beta $-equality by taking
@@
 \begin{example}[\coqident{AlgebraicTheories.Examples.FreeObjectTheory}{free_object_theory}, \coqident{AlgebraicTheories.Examples.FreeObjectTheory}{free_object_algebra_functor}]
-  Take a category $ C $, with a forgetful functor $ G: C \to \SET $ and a free functor $ F: \SET \to C $.
-Let $ \eta: \id \SET \Rightarrow F \bullet G $ be the unit of the adjunction and let $ \varphi: C(F(c), d) \cong \SET(c, G(d)) $ be the natural equivalence of homsets.
+  Take a category $ \C $, with a forgetful functor $ G: \C \to \SET $ and a free functor $ F: \SET \to \C $.
+Let $ \eta: \id \SET \Rightarrow F \bullet G $ be the unit of the adjunction and let $ \varphi: \C(F(X), Y) \cong \SET(X, G(Y)) $ be the natural equivalence of homsets.
 
   We define an algebraic theory $ T $ with $ T_n = G(F(\{ 1, \dots, n \})) $, projections $ x_{n, i} = \eta_{\{1, \dots, n\}}(i) $.
-For the substitution, note that we take $ t_1, \dots, t_m: T_n $, so we have $ t: \{ 1, \dots, m \} \to G(F(\{ 1, \dots, n \})) $.
+For the substitution, note that we can view $ t: T_n^m $ as a function $ t: \{ 1, \dots, m \} \to G(F(\{ 1, \dots, n \})) $.
 We then take
@@
 
-  Now, given an object $ c: C $, we can create a $ T $-algebra $ \alpha(c) $, with set $ G(c) $ and action
+  Now, given an object $ X: \C $, we can give $ G(X) $ a $ T $-algebra structure, with action
   \[ s \bullet t = G(\varphi^{-1}(t))(s). \]
-  Also, given a morphism $ f: C(c, d) $. This gives a morphism $ G(f): \alpha(c) \to \alpha(d) $. Therefore, $ \alpha: C \to \Alg T $ is a functor.
+  Also, for a morphism $ f: \C(X, Y) $, we get a $ T $-algebra morphism $ G(f): G(X) \to G(Y) $. Therefore, we can view $ G $ as a functor $ G: \C \to \Alg T $.
 \end{example}
 
-The proofs that $ T $ is an algebraic theory, that $ G(c) $ is an algebra and that $ G(f) $ is an algebra morphism mainly rely on the fact that $ \varphi $ is natural.
+The proofs that $ T $ is an algebraic theory, that $ G(X) $ is an algebra and that $ G(f) $ is an algebra morphism mainly rely on the fact that $ \varphi $ is natural.
 
-So we have a functor from $ C $ to the category of $ T $-algebras.
-One can wonder whether there also is a functor the other way, or whether $ \alpha $ is even an equivalence.
-If $ \alpha $ is an equivalence, $ C $ is trivially an algebraic category, but the question for which algebraic categories $ \alpha $ is an equivalence is harder to answer.
+So we have a functor from $ \C $ to the category of $ T $-algebras.
+One can wonder whether there also is a functor the other way, or whether $ G: \C \to \Alg T $ is even an equivalence.
+If the latter is true, $ \C $ is trivially an algebraic category, but the question for which algebraic categories $ G $ is an equivalence is harder to answer.
 
-Of course, for many common categories in algebra, where an object of $ C $ is a set with some operations between its elements, one can carefully choose some elements of $ T_0 $, $ T_1 $, $ T_2 $ etc., which act on an algebra like the specified operations, which turns $ \alpha $ into an equivalence.
+Of course, for many common categories in algebra, where an object of $ \C $ is a set with some operations between its elements, one can carefully choose some elements of $ T_0 $, $ T_1 $, $ T_2 $ etc., which act on an algebra like the specified operations, which turns $ G $ into an equivalence.
 
 \begin{example}[\coqident{AlgebraicTheories.Examples.FreeMonoidTheory}{monoid_algebra_equivalence}]\label{ex:free-monoid-theory}
-  For $ C $ the category of monoids, $ \alpha: C \to \Alg T $ is an adjoint equivalence.
+  For $ \C $ the category of monoids, $ G: \C \to \Alg T $ is an adjoint equivalence.
 
   Note that $ T_n $ is the free monoid on $ n $ elements.
-Its elements can be viewed as strings $ (x_1 x_5 x_3 x_{18} \dots x_7) $ with the characters $ x_1, \dots, x_n $, with the $ x_i $ the generators of the monoid, acting as the projections of the algebraic theory.
+Its elements can be viewed as strings with the characters $ x_1, \dots, x_n $ (for example, $ x_1 x_5 x_3 x_{18} \dots x_7 $), with the $ x_i $ the generators of the monoid, acting as the projections of the algebraic theory.
 
@@
   Note that if we take a monoid, turn it into a $ T $-algebra and then into a monoid again, we still have the same underlying set, and it turns out that the monoid operation and unit element are equal to the original monoid operation and unit element.
-Therefore, $ \alpha $ is essentially surjective.
+Therefore, $ G $ is essentially surjective.
 It is also fully faithful, since any $ T $-algebra morphism respects the action of $ T $, which makes it into a monoid morphism.
-Therefore, $ \alpha $ is an adjoint equivalence.
+Therefore, $ G $ is an adjoint equivalence.
 \end{example}
@@
 In other words: the $ T $-algebra structure does not preserve the topological information.
-Therefore, the functor $ \alpha: \mathbf{Top} \to \Alg T $ is not an equivalence.
+Therefore, the functor $ G: \mathbf{Top} \to \Alg T $ is not an equivalence.
 \end{remark}
@@
 \begin{example}[\coqident{AlgebraicTheories.Examples.OnePointTheory}{one_point_theory}]
-  We can create a (somewhat trivial) algebraic theory $ T $ by taking $ T_n = \{ \star \} $, with projections $ x_i = \star $ and substitution $ \star \bullet \star = \star $.
+  We can create the trivial algebraic theory $ T $ by taking $ T_n = \{ \star \} $, with projections $ x_i = \star $ and substitution $ \star \bullet \star = \star $.
 Taking $ \lambda(\star) = \star $ and $ \rho(\star) = \star $, we give it a $ \lambda $-theory structure (with $ \beta $ and $ \eta $-equality).
@@
 
-  Now, given any other algebraic theory $ T^\prime $, there exists a unique function $ T^\prime_n \to T_n $ for every $ n $, sending everything to $ \star $.
-These functions actually constitute an algebraic theory morphism $ T^\prime \to T $.
-If $ T^\prime $ is a $ \lambda $-theory, the algebraic theory morphism is actually a $ \lambda $-theory morphism.
+  Now, given any other algebraic theory $ S $, there exists a unique function $ S_n \to T_n $ for every $ n $, sending everything to $ \star $.
+These functions actually constitute an algebraic theory morphism $ S \to T $.
+If $ S $ is a $ \lambda $-theory, the algebraic theory morphism is actually a $ \lambda $-theory morphism.
 Again, checking this is trivial.
@@
 \begin{proof}
-  Let $ A $ be a $ T $-algebra. First of all, we have an element $ \star_A = \star_T \bullet_{0} () $. Secondly, for all elements $ \star, \star^\prime: A $, we have
-  \[ \star = x_1 \bullet (\star, \star^\prime) = \star \bullet (\star, \star^\prime) = x_2 \bullet (\star, \star^\prime) = \star^\prime. \]
-  Therefore, $ A = \{ \star \} $, which allows exactly one possible $ T $-action:
+  Let $ A $ be a $ T $-algebra. First of all, we have an element $ \star_A = \star_T \bullet_{0} () $. Secondly, for all elements $ a: A $, we have
+  \[ a = x_1 \bullet (a, \star) = \star \bullet (a, \star) = x_2 \bullet (a, \star) = \star. \]
+  Therefore, the set of $ A $ is $ \{ \star \} $, which can have only one $ T $-action:
   \[ \star \bullet (\star, \dots, \star) = \star. \]
@@
 \begin{definition}[\coqident{AlgebraicTheories.Examples.EndomorphismTheory}{endomorphism_algebraic_theory}]\label{def:endomorphism-theory}
-  Suppose that we have a category $ C $ and an object $ X: C $, such that all powers $ X^n $ of $ X $ are also in $ C $.
-  The \iindex{endomorphism theory} $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ f \circ \langle g_i \rangle_i: X^n \to X^m \to X $.
+  Suppose that we have a category $ \C $ and an object $ X: \C $, such that all powers $ X^n $ of $ X $ are also in $ \C $.
+  The \iindex{endomorphism theory} $ E(X) $ of $ X $ is the algebraic theory given by $ E(X)_n = \C(X^n, X) $ with projections as variables $ x_{n, i}: X^n \to X $ and a substitution that sends $ f: X^m \to X $ and $ g_1, \dots, g_m: X^n \to X $ to $ \langle g_i \rangle_i \cdot f: X^n \to X $.
 \end{definition}
@@
 \begin{definition}[\coqident{AlgebraicTheories.Examples.EndomorphismTheory}{endomorphism_lambda_theory}]
-  Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ abs: X^X \to X $ and $ app: X \to X^X $.
-Let, for $ Y: C $, $ \varphi_Y $ be the isomorphism $ C(X \times Y, X) \xrightarrow{\sim} C(Y, X^X) $.
+  Now, suppose that the exponential object $ X^X $ exists, and that we have morphisms back and forth $ \mathrm{abs}: X^X \to X $ and $ \mathrm{app}: X \to X^X $.
+Let $ \varphi_Y $ be the isomorphism $ \C(X \times Y, X) \xrightarrow{\sim} \C(Y, X^X) $ for $ Y: \C $.
   We can give $ E(X) $ a $ \lambda $-theory structure by setting, for $ f: E(X)_{n + 1} $ and $ g: E(X)_n $,
-  \[ \lambda(f) = abs \circ \varphi_{X^n}(f) \qquad \rho(g) = \varphi_{X^n}^{-1}(app \circ g). \]
+  \[ \lambda(f) = \varphi_{X^n}(f) \cdot \mathrm{abs} \qquad \rho(g) = \varphi_{X^n}^{-1}(g \cdot \mathrm{app}). \]
 \end{definition}
+
+\begin{remark}[\coqident{AlgebraicTheories.Examples.EndomorphismTheory}{endomorphism_theory_has_β} \coqident{AlgebraicTheories.Examples.EndomorphismTheory}{endomorphism_theory_has_eta}]
+  From the definition of $ \lambda $ and $ \rho $, it follows immediately that $ E(X) $ has $ \beta $-equality if $ \mathrm{abs} \cdot \mathrm{app} = \id{X^X} $.
+  In the same way, if $ \mathrm{app} \cdot \mathrm{abs} = \id X $, then $ E(X) $ has $ \eta $-equality.
+\end{remark}
 
@@
 \begin{proof}
-  Recall from Lemma \ref{lem:lawvere-algebra} that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $.
+  In Lemma \ref{lem:lawvere-algebra}, it is shown that $ T $-algebras are equivalent to finite-product-preserving $ \SET $-valued functors on the Lawvere theory $ \mathbf L $ associated to $ T $.
 Now, recall from Definition \ref{def:Yoneda-embedding} for any category $ C $, we can embed $ \op C $ inside $ [C, \SET] $, the category of $ \SET $-valued functors on $ C $.
 This embeds $ n: \mathbf L $ as the theory algebra $ T_n $.
-Then the Yoneda Lemma gives a bijection
+Then the Yoneda lemma gives a bijection
   \[ \Alg T(T_n, A) \cong A^n = \SET(\{ 1, \dots, n \}, A) \]
@@
   Take a nonnegative integer $ n $.
-Take an object $ S : \AlgTh $.
-For every object $ T : \AlgTh $, we can take the $ T $-algebra $ T_n $.
+Take $ S : \AlgTh $.
+For every $ T : \AlgTh $, we can take the $ T $-algebra $ T_n $.
 Then every morphism $ f: \AlgTh(S, T) $ gives an $ S $-algebra $ f^* T_n $.
@@
 \begin{proof}
-  Recall from Lemma \ref{lem:lawvere-presheaf} that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $.
+  Lemma \ref{lem:lawvere-presheaf} shows that $ T $-presheaves are equivalent to presheaves on the Lawvere theory $ \mathbf L $ associated to $ T $.
 Now, recall from Definition \ref{def:Yoneda-embedding} that we can embed any category inside its own category of presheaves.
 This embeds $ n: \mathbf L $ as the power $ T^n = (T_m^n)_m $ of the theory presheaf.
-Then the Yoneda Lemma gives a bijection
+Then the Yoneda lemma gives a bijection
   \[ \Pshf T(T^n, Q) \cong Q_n \]
@@
 
-\subsection{The "+l" presheaf}
+\subsection{The ``+\texorpdfstring{$ \ell $}{l}'' presheaf}
 
-\begin{example}[\coqident{AlgebraicTheories.Examples.Plus1Presheaf}{plus_1_presheaf}][The `+l' presheaf]
-  Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, l) $ with $ A(Q, l)_n = Q_{n + l} $ and, for $ q: A(Q, l)_m $ and $ f: T_n^m $, action
-  \[ q \bullet_{A(Q, l)} f = q \bullet_Q ((\iota_{n, l} (f_i))_i + (x_{n + i})_i). \]
+\begin{example}[\coqident{AlgebraicTheories.Examples.Plus1Presheaf}{plus_1_presheaf}]
+  Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, \ell) $ with $ A(Q, \ell)_n = Q_{n + \ell} $ and, for $ q: A(Q, \ell)_m $ and $ f: T_n^m $, action
+  \[ q \bullet_{A(Q, \ell)} f = q \bullet_Q ((\iota_{n, \ell} (f_i))_i + (x_{n + i})_i). \]
 \end{example}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.RepresentationTheorem}{theory_presheaf_exponentiable}]
-  For all $ l $ and $ T $-presheaves $ Q $, $ A(Q, l) $ is the exponential object $ Q^{T^l} $.
+  For all $ m $ and all $ T $-presheaves $ Q $, $ A(Q, m) $ is the exponential object $ Q^{T^m} $.
 \end{lemma}
 \begin{proof}
-  We will show that $ A(-, l) $ constitutes a right adjoint to the functor $ - \times T^l $. We will do this using universal arrows.
+  We will show that $ A(-, m) $ constitutes a right adjoint to the functor $ - \times T^m $. We will do this using universal arrows.
 
-  For $ Q $ a $ T $-presheaf, take the arrow $ \varphi: A(Q, l) \times T^l \to Q $ given by $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $ for $ q: A(Q, l)_n = Q_{n + l} $ and $ t: T^l_n $.
+  For $ Q $ a $ T $-presheaf, take the arrow $ \varphi: A(Q, m) \times T^m \to Q $ given by $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $ for $ q: A(Q, m)_n = Q_{n + m} $ and $ t: T^m_n $.
 
-  Now, given a $ T $-presheaf $ Q^\prime $ and a morphism $ \psi: Q^\prime \times T^l \to Q $.
-Define $ \tilde \psi: Q^\prime_n \to A(Q, l)_n $ by $ \tilde \psi(q) = \psi(\iota_{n, l}(q), (x_{n + i})_i) $.
+  Now, given a $ T $-presheaf $ Q^\prime $ and a morphism $ \psi: Q^\prime \times T^m \to Q $.
+Define $ \tilde \psi: Q^\prime_n \to A(Q, m)_n $ by $ \tilde \psi(q) = \psi(\iota_{n, m}(q), (x_{n + i})_i) $.
 
-  Then $ \psi $ factors as $ \varphi \circ (\tilde \psi \times \id{T^l}) $.
+  Then $ \psi $ factors as $ (\tilde \psi \times \id{T^m}) \cdot \varphi $.
 Also, some equational reasoning shows that $ \tilde \psi $ is unique, which proves that $ \varphi $ indeed is a universal arrow.

### 2024-10-14 910-alternative-definitions.tex
Slightly clean up chapter 4

@@
 This definition is more general than the definition of algebraic theory in Section \ref{sec:algebraic-theories}. To make it equivalent, we have to be more specific about the objects of the category:
-\begin{definition}
+\begin{definition}\label{def:lawvere-theory}
   A \iindex{Lawvere theory}, or \textit{one-sorted algebraic theory} is a category $ L $, with $ L_0 = \{ 0, 1, \dots \} $, such that $ n = 1^n $, the $ n $-fold product.

### 2024-10-14 100-introduction.tex
Slightly improve the introduction after feedback

@@
 However, because the computation part of such a proof involves a lot of code, and computer code tends to contain bugs, accepting a proof by computer involves a certain amount of trust.
-Therefore, both of the theorems mentioned have subsequently also been proved using `computer proof assistants'\autocite{formalized-four-color-theorem}\autocite{formalized-Kepler-conjecture}.
-Such proof assistants, like `rocq', `lean' and `Agda', are computer programs with only a very small `trusted codebase'\footnote{Trusted codebase means the part of the codebase of which we hope that it is correct.
+Therefore, both of the theorems mentioned have subsequently also been proved using `computer proof assistants' \autocite{formalized-four-color-theorem}\autocite{formalized-Kepler-conjecture}.
+Such proof assistants, like `rocq', `lean' and `Agda', are computer programs with only a very small `trusted codebase'\footnote{The trusted codebase is the part of the codebase of which we have to trust that it is correct.
 The rest of the codebase is checked using this trusted core, so if the trusted core is correct, the rest is too.}, that can verify mathematical reasoning.
@@
 Now, much of contemporary mathematics is built on the foundation of set theory, which we will often refer to as \iindex{classical mathematics}.
-Usually, `set theory' refers to ZFC: Zermelo Fraenkel set theory with the axiom of choice, developed in the early 1900s.
+Usually, `set theory' refers to ZFC: Zermelo Fraenkel set theory with the axiom of choice, developed in the early 1900s \autocite{Zermelo-set-theory}.
 On the other hand, most of the formalization in proof assistants is built on the foundation of type theory.
 This is because computers can reason better with types than with sets, as evidenced by the many typed programming languages that are around nowadays.
-However, type theory has been around longer than computers have: it was initially developed by Bertrand Russell in the early 1900s, to create a foundation of mathematics that avoided Russell's paradox\footnote{``Consider the set of all sets that do not contain themself.
-Does this set contain itself?''}.
+However, type theory has been around longer than computers have: it was initially developed by Bertrand Russell in the early 1900s (\autocite{Russell-type-theory}, Appendix B), to create a foundation of mathematics that avoided Russell's paradox\footnote{Russell's paradox is the question ``Consider the set of all sets that do not contain themself.
+Does this set contain itself?'' Answering this question with either `yes' or `no' leads to a contradiction.}.
 
@@
 Every flavour has its advantages and disadvantages, but in this thesis we will work with `univalent foundations', set forth by Vladimir Voevodsky \autocite{voevodsky-univalent-foundations}.
-In univalent foundations, the common mathematical principle that `things with a similar structure\footnote{For example, two sets with a bijection between them have a similar structure.
-Also, two graphs $ G $ and $ H $ have a similar structure when there is a bijection $ f $ between their sets of vertices, such that for every two vertices $ v, w : G $, we have a bijection between the set of edges from $ v $ to $ w $, and the set of edges from $ f(v) $ to $ f(w) $.}, are the same' is made explicit.
-The principle is used often in modern mathematics, and making this explicit in the type theory that we work with, allows us to use the principle when formalizing.
+The advantage of working with univalent foundations is that it makes explicit the common mathematical principle that `things with a similar structure\footnote{For example, two sets with a bijection between them have a similar structure.
+Also, two graphs $ G $ and $ H $ have a similar structure when there is a bijection $ f $ between their sets of vertices, such that for every two vertices $ v, w : G $, we have a bijection between the set of edges from $ v $ to $ w $, and the set of edges from $ f(v) $ to $ f(w) $.} are the same', which allows us to use it when formalizing.
 
-However, note that two objects can often have a similar structure in more than one way.
+Unfortunately, there is a trade-off here: we do not get `similar objects are the same' for free.
+This is because two objects can often have a similar structure in more than one way.
 For example, the set $ \{ \top, \bot \} $ has two bijections to the set $ \{ 0, 1 \} $.
-To accomodate for this, in univalent foundations, two things can sometimes `be the same' in more way than one.
+To accomodate for this, in univalent foundations, two things can sometimes `be the same' in more ways than one.
 For example, we have two equalities between $ \{ \top, \bot \} $ and $ \{ 0, 1 \} $.
-This means that the concept of `sameness' is more intricate to work with in univalent foundations than it is in set theory.
+This means that the concept of `sameness' becomes more complicated to work with in univalent foundations than it is in set theory.
 This is one of the reasons that there are subtleties involved in transferring definitions and proofs from set theory to univalent foundations.
@@
 
-In this thesis, we study the paper `classical lambda calculus in modern dress' through the lens of univalent foundations, work out the details of the proofs and formalize part of the paper and its preliminaries.
-The major contributions are
+In this thesis, we study the paper `classical lambda calculus in modern dress' through the lens of univalent foundations, work out the details of the proofs, and formalize part of the paper and its preliminaries.
+The major contributions are:
 \begin{itemize}
-  \item The category theoretical preliminaries needed to understand the paper (Chapter \ref{ch:category-theory}), as well as the work of Hyland's predecessors that he expands upon (Chapter \ref{ch:previous-work}), and more detailed versions of his definitions and proofs, complemented with some examples (Chapters \ref{ch:algebraic-structures} and \ref{ch:the-paper}).
-This makes Hyland's paper more accessible to computer scientists.
+  \item More detailed versions of Hyland's definitions and proofs, complemented with some examples (Chapters \ref{ch:algebraic-structures} and \ref{ch:the-paper}).
+Also, the work of Hyland's predecessors that he expands upon (Chapter \ref{ch:previous-work}), and most of the category theoretical preliminaries needed to understand the paper (Chapter \ref{ch:category-theory}), to make this thesis reasonably self-contained.
+All this makes Hyland's paper more accessible to computer scientists.
   \item The translation of Hyland's paper and the work of his predecessors to univalent foundations (Chapter \ref{ch:the-paper}).
@@
 % 700-formalization.tex
-Lastly, the formalization of part of the material is discussed in Chapter \ref{ch:the-formalization}.
+Lastly, the formalization of part of the material covered in this thesis is discussed in Chapter \ref{ch:the-formalization}.
 

### 2024-10-14 500-previous-work.tex
Add links back from the conclusion
Slightly improve the introduction after feedback

@@
 
-  During the 1960s, computer scientists sought for nontrivial examples of reflexive objects, there is a quote by Dana Scott that ``Lambda-calculus has no mathematical models!''\autocite{strachey}.
+  During the 1960s, computer scientists sought for nontrivial examples of reflexive objects, there is a quote by Dana Scott that ``Lambda-calculus has no mathematical models!'' \autocite{strachey}.
 However, in 1969, the same Dana Scott discovered that the category of (continuous) lattices with (Scott-)continuous functions between them has a nontrivial reflexive object, with the retraction onto the function spaces being even an isomorphism.
@@
 This brings us to the main theorem of this section (\autocite{taylor}, 5.1.8).
-\begin{theorem}
+\begin{theorem}\label{thm:Taylor}
   If we assume the axiom of choice, $ \R $ is cartesian closed, relative to the given class of display maps.

### 2024-10-14 800-conclusion.tex
Slightly improve the introduction after feedback

@@
 Lastly, we saw how part of the material in this thesis was formalized, and we evaluated the choices that were made in the formalization (Chapter \ref{ch:the-formalization}).
-Unfortunately, due to the very time-consuming nature of formalization, not all of the material could be formalized.
-In future work, it would be interesting to see which version of Hyland's fundamental theorem would lend itself best to formalization.
+For some of the very complicated mathematics with a lot of bookkeeping, like the proofs about the Yoneda embedding or the theory of extensions, this formalization constitutes an additional guarantee that it is correct.
+In some other instances, the process of formalizing contributed to the realization that a lemma should be stated in more generality (see Section \ref{sec:quotients}).
+Unfortunately, due to the very time-consuming nature of formalization, not all of the material in Hyland's paper could be formalized.
+In future work, it would be interesting to see which version of the fundamental theorem would lend itself best to formalization.
 Personally, I would guess it is the most elementary one, exhibited in Section \ref{sec:elementary-fundamental-theorem}.

### 2024-10-22 100-introduction.tex
Process feedback about introduction, conclusion, bibliography and citations

@@
 Later, all kinds of different flavours and extensions of the $ \lambda $-calculus were put forth, with colorful names like `simply typed $ \lambda $-calculus', `System T' and `PCF'.
-Even though the $ \lambda $-calculus was originally a very theoretical tool, it was also the inspiration for function programming languages, and traces of it can be seen in imperative programming languages, where unnamed functions are commonly called `lambda expressions' \autocite{java-lambdas} and are sometimes even written like \texttt{lambda x y : (x - y) * (x + y)} \autocite{python-expressions}.
+Even though the $ \lambda $-calculus was originally a very theoretical tool, it was also the inspiration for functional programming languages, and traces of it can be seen in imperative programming languages, where unnamed functions are commonly called `lambda expressions' \autocite{java-lambdas} and are sometimes even written like \texttt{lambda x y : (x - y) * (x + y)} \autocite{python-expressions}.
 
 Even so, the theoretical study of the $ \lambda $-calculus and its extensions continues to this day.
-For example, in 2017\footnote{Note that the paper has been around since 2012, when it was first published as a preprint on arXiv.}, a paper by Martin Hyland was published with the title `classical lambda calculus in modern dress' \autocite{Hyland}.
+For example, in 2017\footnote{Note that the paper has been around since 2012, when it was first published as a preprint on arXiv.}, a paper by Martin Hyland was published with the title `Classical lambda calculus in modern dress' \autocite{Hyland}.
 In this paper, Hyland approaches the $ \lambda $-calculus from the viewpoint of universal algebra, using algebraic theories, and more generally category theory, to study it.
@@
 All kinds of tools have been created that aid mathematicians in their job.
-Some of these tools help with quick calculations, for formulating or disproving new conjectures.
+Some of these tools help with quick calculations for formulating or disproving new conjectures.
 Other tools help in structurally verifying ideas.
@@
 However, because the computation part of such a proof involves a lot of code, and computer code tends to contain bugs, accepting a proof by computer involves a certain amount of trust.
-Therefore, both of the theorems mentioned have subsequently also been proved using `computer proof assistants' \autocite{formalized-four-color-theorem}\autocite{formalized-Kepler-conjecture}.
+Therefore, both of the theorems mentioned have subsequently also been proved using `computer proof assistants' \autocite{formalized-four-color-theorem, formalized-Kepler-conjecture}.
 Such proof assistants, like `rocq', `lean' and `Agda', are computer programs with only a very small `trusted codebase'\footnote{The trusted codebase is the part of the codebase of which we have to trust that it is correct.
@@
 This is because computers can reason better with types than with sets, as evidenced by the many typed programming languages that are around nowadays.
-However, type theory has been around longer than computers have: it was initially developed by Bertrand Russell in the early 1900s (\autocite{Russell-type-theory}, Appendix B), to create a foundation of mathematics that avoided Russell's paradox\footnote{Russell's paradox is the question ``Consider the set of all sets that do not contain themself.
+However, type theory has been around longer than computers have: it was initially developed by Bertrand Russell in the early 1900s \autocite[][Appendix B]{Russell-type-theory}, to create a foundation of mathematics that avoided Russell's paradox\footnote{Russell's paradox is the question ``Consider the set of all sets that do not contain themself.
 Does this set contain itself?'' Answering this question with either `yes' or `no' leads to a contradiction.}.
@@
 
-In this thesis, we study the paper `classical lambda calculus in modern dress' through the lens of univalent foundations, work out the details of the proofs, and formalize part of the paper and its preliminaries.
+In this thesis, we study the paper `Classical lambda calculus in modern dress' through the lens of univalent foundations, work out the details of the proofs, and formalize part of the paper and its preliminaries.
 The major contributions are:
@@
   \item More detailed versions of Hyland's definitions and proofs, complemented with some examples (Chapters \ref{ch:algebraic-structures} and \ref{ch:the-paper}).
-Also, the work of Hyland's predecessors that he expands upon (Chapter \ref{ch:previous-work}), and most of the category theoretical preliminaries needed to understand the paper (Chapter \ref{ch:category-theory}), to make this thesis reasonably self-contained.
+Also, the work of Dana Scott and Paul Taylor that Hyland expands upon (Chapter \ref{ch:previous-work}), and most of the category theoretical preliminaries needed to understand the paper (Chapter \ref{ch:category-theory}), to make this thesis reasonably self-contained.
 All this makes Hyland's paper more accessible to computer scientists.

### 2024-10-22 200-category-theory.tex
Process feedback about introduction, conclusion, bibliography and citations

@@
 
-An alternative characterization (see \autocite{MacLane}, chapter IV.1, Theorem 2) of an adjunction $ L \dashv R $ is as a natural bijection
+An alternative characterization \autocite[][Chapter IV.1, Theorem 2]{MacLane} of an adjunction $ L \dashv R $ is as a natural bijection
 \[ \varphi: \D(L(X), Y) \xrightarrow{\sim} \C(X, R(Y)). \]
@@
 
-We can embed $ \C $ fully faithfully into $ P \C $ as follows (see \autocite{Kashiwara}, Section 1.4):
+We can embed $ \C $ fully faithfully into $ P \C $ as follows \autocite[][Section 1.4]{Kashiwara}:
 \begin{definition}\label{def:Yoneda-embedding}
@@
 Conversely, it sends an element $ X : P(Y) $ to the natural transformation $ a $ given by $ a_X(f) = P(f)(X) $ for all $ f: \yo(Y)(X) = \C(X, Y) $.
-For more details, see \autocite{Kashiwara}, Proposition 1.4.3.
+For more details, see \autocite[][Proposition 1.4.3]{Kashiwara}.
 \end{proof}
@@
   \[ (F^G)(X) = P\C(\yo(X) \times G, F), \]
-  the natural transformations from the product functor of the Yoneda embedding of $ X $ and $ G $, to $ F $ (see \autocite{MacLane-Moerdijk}, Section I.6, Proposition 1).
+  the natural transformations from the product functor of the Yoneda embedding of $ X $ and $ G $, to $ F $ \autocite[][Section I.6, Proposition 1]{MacLane-Moerdijk}.
 \end{remark}
@@
   To show that $ \eta $ is a natural isomorphism, we have to show that $ \eta_G(Y): G(Y) \Rightarrow \Lan F G(F(Y)) $ is an isomorphism for all $ G: [\A, \C] $ and $ Y: \A $.
-Since a left adjoint is unique up to natural isomorphism (\autocite{CT4P}, Exercise 153), we can assume that $ \Lan F G(F(Y)) $ is given by
+Since a left adjoint is unique up to natural isomorphism \autocite[][Exercise 153]{CT4P}, we can assume that $ \Lan F G(F(Y)) $ is given by
   \[ \text{colim} ((F \downarrow F(Y)) \to \A \xrightarrow G \C). \]

### 2024-10-22 300-univalent-foundations.tex
Process feedback about introduction, conclusion, bibliography and citations

@@
 So if we have types and elements, are types also elements of some type?
-This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system (see \autocite{girard}).
+This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system \autocite{girard}.
 This is just like having a `set of all sets', which results in problematic questions like ``does its subset, containing only the sets which do not contain itself, contain itself?'' This is usually solved by either stating that types do not themselves have a type, or by assuming the existence of \textit{type universes} $ U_1, U_2, \dots $, such that every type is an element of some $ U_i $.
@@
 We construct this using path induction with the function that sends $ \mathrm{refl}: x = x $ to itself.
-For more information, see \autocite{hottbook}, Section 1.12.1.
+For more information, see \autocite[][Section 1.12.1]{hottbook}.
 
@@
 Since bijections are not well-behaved for types that are not sets (see Section \ref{sec:homotopy-props-sets}), because in those cases, a function $ f: S \to T $ can have multiple distinct inverses.
-Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ (see \autocite{hottbook}, Equation 2.4.10).
+Therefore, we define $ S \simeq T := \sum_{f: S \to T} \mathrm{isequiv}(f) $, for some predicate $ \mathrm{isequiv}: (S \to T) \to \TYPE $ \autocite[][Equation 2.4.10]{hottbook}.
 However, intuitively we can still think of these as bijections.
@@
 \begin{definition}
-  For a type $ T $, a type $ \Vert T \Vert $ exists (\autocite{hottbook}, Section 3.7) with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
+  For a type $ T $, a type $ \Vert T \Vert $ exists \autocite[][Section 3.7]{hottbook} with the properties that for all $ t: T $, we have an element $ \vert t \vert : \Vert T \Vert $ and that $ \Vert T \Vert $ is a mere proposition.
 It has a recursion principle stating that for a mere proposition $ B $, a function $ f: T \to B $ induces a function $ \vert f \vert: \Vert T \Vert \to B $ that commutes with $ \vert \cdot \vert $.

### 2024-10-22 500-previous-work.tex
Process feedback about introduction, conclusion, bibliography and citations

@@
 
-Taylor notes (\autocite{taylor}, Section 1.5) that the objects in $ \R $ have very strong properties with respect to fixpoints.
-One of the properties also arises via Lawvere's fixed point theorem (\autocite{lawvere-fixpoints}, page 136): For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint (\coqident{AlgebraicTheories.CategoryOfRetracts}{fixpoint_is_fixpoint}).
+Taylor notes \autocite[][Section 1.5]{taylor} that the objects in $ \R $ have very strong properties with respect to fixpoints.
+One of the properties also arises via Lawvere's fixed point theorem \autocite[][page 136]{lawvere-fixpoints}: For all $ B: \R $, since $ B^U $ is a retract of $ U $, every endomorphism $ f: B \to B $ has a fixpoint (\coqident{AlgebraicTheories.CategoryOfRetracts}{fixpoint_is_fixpoint}).
 That is, there exists $ s: I \to B $ such that $ f \circ s = s $.
@@
 
-From this, Taylor deduces (\autocite{taylor}, \S 1.5.12) that $ \R $ does not have all coproducts if $ L $ is nontrivial, because suppose that $ \R $ has all coproducts.
+From this, Taylor deduces \autocite[][\S 1.5.12]{taylor} that $ \R $ does not have all coproducts if $ L $ is nontrivial, because suppose that $ \R $ has all coproducts.
 Then $ B = I + I $ is a `boolean algebra object': We define $ \bot, \top: I \to B $ to be the injections on the left and right components.
@@
 Since Lambek showed an equivalence between simply typed $ \lambda $-calculi and cartesian closed categories, and since we have a construction for an untyped $ \lambda $-calculus from a cartesian closed category with a reflexive object, we can wonder whether this construction constitutes contitutes an equivalence between untyped $ \lambda $-calculi and some class of categories.
-This question finds a partial answer in the following theorem, originally proved in a very syntactical way by Dana Scott (see \autocite{curry}, page 418).
+This question finds a partial answer in the following theorem, originally proved in a very syntactical way by Dana Scott \autocite[][418]{curry}.
 \begin{theorem}[\coqident{AlgebraicTheories.OriginalRepresentationTheorem}{representation_theorem_iso}]\label{thm:Scott}
@@
   However, note that we have a weak equivalence between strict categories (categories in which the type of objects is a homotopy set) $ \sum_A: \R^A \xrightarrow \sim (\R \downarrow_D A) $.
-If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories (see bullet (ii) in the introduction of Chapter 9 of \autocite{hottbook}) and then our pullback functor is given by
+If we assume the axiom of choice, $ \sum_A $ becomes an equivalence of categories \autocite[][Chapter 9, introduction, bullet (ii)]{hottbook} and then our pullback functor is given by
   \[ \sum_A^{-1} \bullet (\alpha \cdot -) \bullet \sum_B, \]
@@
 
-This brings us to the main theorem of this section (\autocite{taylor}, 5.1.8).
+This brings us to the main theorem of this section \autocite[][\S 5.1.8]{taylor}.
 \begin{theorem}\label{thm:Taylor}

### 2024-10-22 600-paper.tex
Rewrite the introduction, list main contributions
Process feedback about introduction, conclusion, bibliography and citations

@@
 \begin{remark}
-  There is a couple of tricks that we will use in this section.
+  There are a couple of tricks that we will use in this section.
 First of all, note that retractions can be composed.
@@
 Leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $, we have $ \iota_\Lambda(f) (x_i)_i = f $.
-We will do this by structural induction on $ f $.
+We will do this by structural induction on $ f $:
   \begin{itemize}
@@
 
-  Explicitly, we can express the coproduct of algebras, and especially its set, as the following coend (\autocite{Hyland}, Proposition 2.5) (see also Section \ref{sec:coends} for more on coends)
+  Explicitly, we can express the coproduct of algebras, and especially its set, as the following coend \autocite[][Proposition 2.5]{Hyland} (see also Section \ref{sec:coends} for more on coends)
   \[ A + B = \int^{(m, n) : \mathbf L \times \mathbf L} T_{m^\prime + n^\prime} \times A^m \times B^n, \]

### 2024-10-22 700-formalization.tex
Process feedback about introduction, conclusion, bibliography and citations

@@
 \section{Some Numbers}
-The code for this project was written over the course of about 18 months, spread over \href{https://github.com/UniMath/UniMath/pulls?q=is%3Apr+author%3Aarnoudvanderleer+is%3Aclosed}{20 pull requests}: 13 with content about Hyland's paper, adding 23.361 and removing 7.620 lines of code, and 7 with only some missing category theoretical preliminaries, adding 3.291 and removing 816 lines.
+The code for this project was written over the course of about 18 months, spread over \href{https://github.com/UniMath/UniMath/pulls?q=is%3Apr+author%3Aarnoudvanderleer+is%3Aclosed}{20 pull requests}: 13 with content about Hyland's paper, adding 23\,361 and removing 7\,620 lines of code, and 7 with only some missing category theoretical preliminaries, adding 3\,291 and removing 816 lines.
 
@@
 
-The formalized parts of Hyland's paper are collected in a package in the library called \textit{algebraic theories}. This package now consists of over 14.000 lines of code, and contains
+The formalized parts of Hyland's paper are collected in a package in the library called \textit{algebraic theories}. This package now consists of over 14\,000 lines of code, and contains:
 \begin{itemize}
@@
 However, when working with displayed categories, the category of algebraic theories is displayed over the category of algebraic theory data, which is displayed over the category of sequences of sets.
-It turns out that in coq, coercions on categories do not compose very well: If $ X $ is an algebraic theory, and we have coercions from algebraic theories to algebraic theory data, and from algebraic theory data to sequences of sets, we can still only use $ X $ to denote the algebraic theory data, and not the sequence of sets.
+It turns out that in rocq, coercions on categories do not compose very well: If $ X $ is an algebraic theory, and we have coercions from algebraic theories to algebraic theory data, and from algebraic theory data to sequences of sets, we can still only use $ X $ to denote the algebraic theory data, and not the sequence of sets.
 
@@
 \section{Duplication in Definitions}
-One of the adages in software engineering is `DRY': ``Don't Repeat Yourself'': Long expressions and blocks of code that occur multiple times throughout the program should usually be abstracted into a separate function.
+One of the adages in software engineering is `DRY', which stands for ``Don't Repeat Yourself'': Long expressions and blocks of code that occur multiple times throughout the program should usually be abstracted into a separate function.
 One of the reasons for this is that it is easier to change code in this function, than to change every instance of the repeated expression or block of code.
@@
 Therefore, if one uses the constructor for an algebraic theory, the goals become \texttt{var\_ax} and \texttt{subst\_ax}, and these have to be unfolded to see what they mean.
-Also, when coq is asked to state the property of an algebra morphism, it responds with \texttt{mor\_action\_ax}, which is not very informative.
+Also, when rocq is asked to state the property of an algebra morphism, it responds with \texttt{mor\_action\_ax}, which is not very informative.
 This is not a big problem, per se, but it adds some friction when formalizing.
-This friction could be reduced a lot if coq would have some sort of macros, which would immediately be unfolded upon use, and would never be printed.
+This friction could be reduced a lot if rocq would have some sort of macros, which would immediately be unfolded upon use, and would never be printed.
 
@@
 Initially, this was solved by transporting along the equality $ \emptyset = \{ i \mid 1 \leq i \leq 0 \} $.
-However, much further down the line, some proof involved an element of this product over $ \{ i \mid 1 \leq i \leq 0 \} $, and because of the transport, coq was not able to see that this product was just $ \{ \star \} $.
+However, much further down the line, some proof involved an element of this product over $ \{ i \mid 1 \leq i \leq 0 \} $, and because of the transport, rocq was not able to see that this product was just $ \{ \star \} $.
 Therefore, the statement of the lemma about the empty product was changed to ``For a type $ I $ and a family $ X : I \to C $, if we have a function $ f : I \to \emptyset $, the terminal object gives the product $ \prod_{i : I} X_i $''.
@@
 Note that coequalizers of set-valued functions are given pointwise by coequalizers in $ \SET $, which are formalized using quotients.
-Because of this, when simplifying, coq usually reduced the goal to elementary statements about quotients, which somewhat obfuscated the relatively simple nature of the construction.
+Because of this, when simplifying, rocq usually reduced the goal to elementary statements about quotients, which somewhat obfuscated the relatively simple nature of the construction.
 Luckily, the construction could be made agnostic to the specific implementation of coequalizers, by introducing a variable
@@
 Now, in this thesis, it is defined as a quotient of an inductive type.
-However, in the UniMath library, the use of inductive types (other than a handful of basic ones like \texttt{empty}, \texttt{bool}, \texttt{nat} and \texttt{coprod}) is prohibited
-\footnote{This is because allowing inductive types requires a much larger trusted codebase of the proof assistant, and because most of mathematics can be formalized with $ \sum $-types or using initial algebras of functors, instead of inductive and record types.}.
+However, in the UniMath library, the use of inductive types (other than a handful of basic ones like \texttt{empty}, \texttt{bool}, \texttt{nat} and \texttt{coprod}) is prohibited\footnote{This is because allowing inductive types requires a much larger trusted codebase of the proof assistant, and because most of mathematics can be formalized with $ \sum $-types or using initial algebras of functors, instead of inductive and record types.}.
 Also, as we saw in section \ref{sec:quotients}, working with quotients can be somewhat complicated.
@@
 The inductive type approach has a variation, which instead of a quotient uses a higher inductive type to force the required elements to be equal.
-Unfortunately, even if the use of inductive types was allowed, coq does not support higher inductive types.
+Unfortunately, even if the use of inductive types was allowed, rocq does not support higher inductive types.
 
@@
 A class in group theory often starts with laying out a couple of axioms, like: ``We have a set $ G $, with a binary operation $ b $, a unary operation $ u $ and an element $ e $.
-$ b $ is associative, $ u $ is a left and right inverse for $ b $ and $ e $ is a unit for $ b $.'' Afterwards, this structure is usually bundled into the declaration ``Let $ G $ be a group.'' In the same spirit, every section in the formalization that needs the pure $ \lambda $-calculus, starts with ``Let $ L $ be the pure $ \lambda $-calculus with $ \beta $-equality.'' To this end, there is a definition \texttt{lambda\_calculus}, consisting of
+$ b $ is associative, $ u $ is a left and right inverse for $ b $ and $ e $ is a unit for $ b $.'' Afterwards, this structure is usually bundled into the declaration ``Let $ G $ be a group.'' In the same spirit, every section in the formalization that needs the pure $ \lambda $-calculus, starts with ``Let $ L $ be the pure $ \lambda $-calculus with $ \beta $-equality.'' To this end, there is a definition \texttt{lambda\_calculus}, consisting of:
 \begin{itemize}
@@
 \end{lstlisting}
-a call to \texttt{repeat reduce\_lambda} would take about a second, but a call to \texttt{propagate\_subst ()} runs in about $ \frac 1 3 $ of a second and prints
+a call to \texttt{repeat reduce\_lambda} would take about a second, but a call to \texttt{propagate\_subst ()} runs in about $ 330 $ millseconds and prints
 \begin{lstlisting}
@@
 \end{lstlisting}
-Replacing the call to \texttt{propagate\_subst} by these statements, results in the same rewrites, but these only take $ \frac{1}{25} $ of a second.
+Replacing the call to \texttt{propagate\_subst} by these statements, results in the same rewrites, but these only take $ 40 $ milliseconds.
 
@@
 It would be interesting to see whether parts of these tactics can be generalized.
-For example, whether it is possible to create an extensible tactic which shows that some type is a homotopy set, or a mere proposition, and prints the coq statements that can replace the tactic call.
+For example, whether it is possible to create an extensible tactic which shows that some type is a homotopy set, or a mere proposition, and prints the rocq statements that can replace the tactic call.
 Or whether it would be possible to generalize \texttt{generate\_refine} to very quickly generate very fast and precise rewrite statements for large and complicated goals.
@@
 When I start working with a new language, it takes me a couple of minutes to figure things out, and within an hour, I can probably get a small program up and running, with some help from google.
-However, when I started working with coq and UniMath, I kind of had to start from scratch again.
+However, when I started working with rocq and UniMath, I kind of had to start from scratch again.
 As it turns out, the naive or direct approach is often not the right one when working with a proof assistant, and of the code that I wrote in the first months, almost nothing remains.

### 2024-10-22 800-conclusion.tex
Process feedback about introduction, conclusion, bibliography and citations

@@
 For example, one way to construct a cartesian closed category is by taking the Karoubi envelope of a `semi cartesian closed category', and the cartesian closed structure on $ \R $ in Scott's representation theorem can be viewed as a special case of this \autocite{hayashi-1985-semifunctors}.
-In another direction, the category of smooth manifolds can be constructed as the Karoubi envelope of the category $ \C $ of the open subsets of all Euclidean spaces, with smooth maps between them (see \autocite{Lawvere-Karoubi}, page 267).
+In another direction, the category of smooth manifolds can be constructed as the Karoubi envelope of the category $ \C $ of the open subsets of all Euclidean spaces, with smooth maps between them \autocite[][267]{Lawvere-Karoubi}.
 For such classical results about the Karoubi envelope, it would be interesting to study how they hold up in univalent foundations for the different choices $ \overline \C $ and $ \hat \C $ of `the Karoubi envelope'.

### 2024-10-22 910-alternative-definitions.tex
Process feedback about introduction, conclusion, bibliography and citations

@@
 
-In this section, we will denote the finite set $ \llbracket n \rrbracket = \{ 1, \dots, n \} $.
+In this appendix, we will denote the finite set $ \llbracket n \rrbracket = \{ 1, \dots, n \} $.
 
@@
   \[ T(m) \times \prod_i T(n_i) \to T\left(\sum_i n_i\right), \]
-  written $ (f, g_1, \dots, g_m) \mapsto f[g_1, \dots, g_m] $, satisfying some identity, associativity and naturality conditions (see \autocite{lambda-monoid}, Definition 2.1, for more details).
+  written $ (f, g_1, \dots, g_m) \mapsto f[g_1, \dots, g_m] $, satisfying some identity, associativity and naturality conditions. See \autocite[][Definition 2.1]{lambda-monoid} for more details.
 \end{definition}
@@
   Note that for an adjunction $ F \dashv G $, $ F \bullet G $ gives a monad.
-In the same way, there exists a notion of \iindex{relative adjunction}, from which we can obtain a relative monad (see \autocite{monads-endofunctors}, Theorem 2.10).
+In the same way, there exists a notion of \iindex{relative adjunction}, from which we can obtain a relative monad \autocite[][Theorem 2.10]{monads-endofunctors}.
 \end{remark}
@@
 \begin{definition}
-  Given a (skew-)monoidal category $ (C, \otimes, I) $, a \iindex{monoid} in this category is an object $ T : C $, together with a `multiplication' $ \mu: C(T \otimes T, T) $ and a `unit' morphism $ \eta: C(I, T) $ satisfying a couple of laws (see \autocite{MacLane}, Section III.6).
+  Given a (skew-)monoidal category $ (C, \otimes, I) $, a \iindex{monoid} in this category is an object $ T : C $, together with a `multiplication' $ \mu: C(T \otimes T, T) $ and a `unit' morphism $ \eta: C(I, T) $ satisfying a couple of laws \autocite[][Section III.6]{MacLane}.
 \end{definition}

### 2024-10-22 200-category-theory.tex
Improve another couple of citations

@@
 \begin{proof}
-  See \autocite{MacLane}, Chapter III.2, Proposition 1.
+  See \autocite[][Chapter III.2, Proposition 1]{MacLane}.
 \end{proof}
@@
 \begin{proof}
-  See \autocite{MacLane}, Chapter IV.1, Theorem 2 (iv).
+  See \autocite[][Chapter IV.1, Theorem 2 (iv)]{MacLane}.
 \end{proof}
@@
 \begin{proof}
-  See \autocite{borceux}, Volume 1, Proposition 2.15.5 for the full proof, but note that for binary products, we have bijections
+  See \autocite[][Volume 1, Proposition 2.15.5]{borceux} for the full proof, but note that for binary products, we have bijections
   \[ \yo(X \times Y)(Z) \xrightarrow \sim \yo(X)(Z) \times \yo(Y)(Z) \]
@@
 \begin{proof}
-  See \autocite{borceux}, Volume 3, Lemma 5.8.2. This lemma shows this via the following equivalences:
+  See \autocite[][Volume 3, Lemma 5.8.2]{borceux}. There, the following equivalences are used for the proof:
   \begin{align*}

### 2024-10-26 300-univalent-foundations.tex
Improve another couple of citations
Improve one additional citation

@@
 \begin{proof}
-  One construction takes $ D $ to be the full subcategory of the presheaf category $ PC $ of objects that are isomorphic (there \textit{merely exists} an isomorphism) to the Yoneda embedding $ \yo(X) $ of some object $ X : C $.
-See \autocite{univalent-categories}, Theorem 8.5.
+  One construction takes $ D $ to be the full subcategory of the presheaf category $ PC $ of objects that are isomorphic (there \textit{merely exists} an isomorphism) to the Yoneda embedding $ \yo(X) $ of some object $ X : C $ \autocite[][Theorem 8.5]{univalent-categories}.
 \end{proof}
@@
 \begin{proof}
-  See \autocite{univalent-categories}, Lemma 6.8.
+  See \autocite[][Lemma 6.8]{univalent-categories}.
 \end{proof}

### 2024-10-30 500-previous-work.tex
Slightly sharpen the two examples of classes of display maps

@@
   A `maximal' example of a subtype of display maps is, for example, in the category $ \SET $, where we can take our subtype of display maps to equal the full type of all morphisms of $ C $.
+This works in any category that has all limits.
 \end{remark}
 \begin{remark}
-  A `minimal' example of a subtype of display maps is the subtype of (maps isomorphic to) product projections in a category with finite products.
+  A `minimal' example of a subtype of display maps is the subtype of product projections in a univalent category with finite products.
 In this case, all indexed families are constant, and then dependent sums and products become binary products and exponential objects.

### 2024-11-08 200-category-theory.tex
Add chapter introductions

@@
 
-I will assume a familiarity with the category-theoretical concepts presented in \autocite{CT4P}.
+This chapter will introduce most of the category theory that is needed to understand the rest of the thesis.
+The chapter assumes familiarity with the category theoretical concepts presented in \autocite{CT4P}.
 These include categories, functors, isomorphisms, natural transformations, adjunctions, equivalences and limits.
+
+It is probably wise to skim this chapter upon first reading, and periodically come back to it to better understand the material in the other chapters.
 
@@
 This gives us what we need to translate the classical equivalence between the two notions of Karoubi envelope to type theory:
-\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope_is_retract}]\label{lem:karoubi-equivalence}
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_equivalence}]\label{lem:karoubi-equivalence}
   We have an adjoint equivalence $ \overline \C \xrightarrow \sim \tilde \C $.
@@
 
-\begin{remark}
+\begin{remark}\label{rem:karoubi-candidate-choice}
   As we saw in this section, there are multiple candidates for the `Karoubi envelope'.

### 2024-11-08 300-univalent-foundations.tex
Add chapter introductions

@@
 
-\section{Dependent Type Theory}
+Since this thesis is, among other things, a case study in translating mathematics from set theory to univalent foundations, this chapter will give an introduction to univalent foundations and introduce some of the relevant concepts.
+It will also point out some issues that can arise in such a translation, like the difference between existence and mere existence (Section \ref{sec:truncation-mere-existence}).
+
+First, we will introduce dependent type theory (Section \ref{sec:dependent-type-theory}).
+After this, we will talk about the univalence principle (Section \ref{sec:univalence-principle}), and introduce the univalence axiom (Section \ref{sec:univalence-axiom}).
+Then we will discuss how propositions and sets show up in univalent foundations (Section \ref{sec:homotopy-props-sets}) and introduce the related notions of propositional truncation and `mere existence' (Section \ref{sec:truncation-mere-existence}).
+After this, we will discuss the relation between equality and homotopy, which is a central idea in homotpy type theory (Section \ref{sec:equality-homotopy}), and lastly, we will talk about transport over equalities (Section \ref{sec:transports}).
+
+\section{Dependent Type Theory}\label{sec:dependent-type-theory}
 Univalent foundations takes place in a framework of type theory. In this section, we will quickly introduce some topics that we will need in subsequent sections.
@@
 
-\section{The Univalence Axiom}
+\section{The Univalence Axiom}\label{sec:univalence-axiom}
 Now, even for a basic category, like the category of types, it seems impossible to prove that the univalence principle holds.
@@
 
-\section{Truncation and (Mere) Existence}
+\section{Truncation and (Mere) Existence}\label{sec:truncation-mere-existence}
 As mentioned before, if we want to do mathematics in a dependent type theory, we can `encode' propositions as types.
@@
 
-\section{Equality and Homotopy}
+\section{Equality and Homotopy}\label{sec:equality-homotopy}
 Univalent Foundations is often mentioned together with Homotopy Type Theory, because they are related but distinct concepts. Therefore, we will mention it here.
@@
 
-\section{Transport}
+\section{Transport}\label{sec:transports}
 

### 2024-11-08 400-algebraic-structures.tex
Add chapter introductions

@@
 \chapter{Algebraic Structures}\label{ch:algebraic-structures}
+
+In his paper, Hyland uses concepts from universal algebra to study the $ \lambda $-calculus.
+This chapter introduces these concepts: it consecutively introduces algebraic theories (Section \ref{sec:algebraic-theories}), algebras (Section \ref{sec:algebras}), presheaves (Section \ref{sec:presheaves}) and $ \lambda $-theories (Section \ref{sec:lambda-theories}).
+The last part of this chapter, Section \ref{sec:algebraic-theory-examples}, is devoted to examples, so it may be useful to skip back and forth a couple of times to get a better understanding of what the definitions are about.
 
@@
 
-\section{Algebras}
+\section{Algebras}\label{sec:algebras}
 
@@
 
-\section{Presheaves}
+\section{Presheaves}\label{sec:presheaves}
 
@@
 
-\section{\texorpdfstring{$ \lambda $-}{lambda-}theories}
+\section{\texorpdfstring{$ \lambda $-}{lambda-}theories}\label{sec:lambda-theories}
 
@@
 
-\section{Examples}
+\section{Examples}\label{sec:algebraic-theory-examples}
 

### 2024-11-08 500-previous-work.tex
Add chapter introductions

@@
 
-% \begin{tabular}{|c|c|c|}\hline
-%   $ K $ & $ \lambda xy.x $ & constant \\\hline
-%   $ S $ & $ \lambda xyz.xz(yz) $ & \\\hline
-%   $ I $ & $ \lambda x.x = SKK $ & identity \\\hline
-%   $ Y $ & $ \lambda f.(\lambda x.f (xx))(\lambda x.f (xx)) $ & ﬁxpoint \\\hline
-%   $ \bot $ & $ (\lambda x.xx)(\lambda x.xx) = (SII)(SII) = YI $ & bottom \\\hline
-%   $ P $ & $ \lambda f gx.g(f x) = S(K(S(S(KS)K)))K $ & composition \\\hline
-%   $ Q $ & $ \lambda f gax.ga(f ax) $ & ﬁbred composition \\\hline
-%   $ \langle \rangle $ & $ \lambda xyz.zxy $ & pairing \\\hline
-%   $ 0 $ & $ \lambda xy.x = K $ & left projection \\\hline
-%   $ 1 $ & $ \lambda xy.y = KI $ & right projection \\\hline
-% \end{tabular}
+Hyland, like every scientist, stands on the shoulder of giants.
+As we saw in the last chapter, he borrows concepts from universal algebra to study the $ \lambda $-calculus.
+Furthermore, two main theorems in his paper have been proven by others before him, although in a different way.
+This chapter strives to improve the understanding of Hyland's work by expositing the work of those who came before.
+
+To understand what categorical semantics for the untyped $ \lambda $-calculus is about, we first briefly take a look at categorical semantics for the simply typed $ \lambda $-calculus (Section \ref{sec:lambek-correspondence}).
+After this, we provide Scott's result about categorical semantics for the untyped $ \lambda $-calculus (Section \ref{sec:scott}), for which we first study the `category of retracts' (Section \ref{sec:retracts-category}).
+We then discuss Paul Taylor's result about the structure of this category of retracts (Section \ref{sec:taylor}), which says something about its internal logic.
+Lastly, we briefly discuss a result of Peter Selinger (Section \ref{sec:selinger}), which seems to have inspired Hyland's fundamental theorem of the $ \lambda $-calculus.
 
@@
 
-\section{Scott's Representation Theorem}
+\section{Scott's Representation Theorem}\label{sec:scott}
 The correspondence in Section \ref{sec:lambek-correspondence} between simply-typed $ \lambda $-calculi and cartesian closed categories raises a question whether such a correspondence also exists for untyped $ \lambda $-calculi.
@@
 
-\section{The Taylor Fibration}
+\section{The Taylor Fibration}\label{sec:taylor}
 
@@
 
-\section{The \texorpdfstring{$ \lambda $}{lambda}-calculus is Algebraic}
+\section{The \texorpdfstring{$ \lambda $}{lambda}-calculus is Algebraic}\label{sec:selinger}
 As we mentioned in Remark \ref{rem:lambda-theory-or-algebra}, using tools from universal algebra, there are two approaches to study $ \lambda $-calculus-like structures.

### 2024-11-08 600-paper.tex
Add chapter introductions

@@
 
-\section{Scott's Representation Theorem}
+In this chapter, we will cover the main results from Hyland's paper.
+We work out the proofs in more detail, and point out where subtleties arise when translating them from set theory to univalent foundations.
+
+The chapter starts with a new proof for Scott's representation theorem (Section \ref{sec:hyland-scott}).
+The sections after this deal with a lot of different categories and Section \ref{sec:hyland-categories} discusses the relations between these categories.
+Section \ref{sec:relatively-cartesian-closed} gives Hyland's proof of the result by Paul Taylor that was covered in the previous chapter.
+Here, the bifurcation of the Karoubi envelope in univalent foundations, as mentioned in Remark \ref{rem:karoubi-candidate-choice}, means that Hyland's result is about a different category than Taylor's result (Remark \ref{rem:difference-Taylor-Hyland}).
+
+In the last part of this chapter, we cover Hyland's fundamental theorem about the equivalence between $ \lambda $-theories and $ \Lambda $-algebras.
+There are multiple ways to construct a $ \lambda $-theory from a $ \Lambda $-algebra, and these give rise to slightly different proofs.
+We will consecutively cover a very elementary version (Section \ref{sec:elementary-fundamental-theorem}), Hyland's first version, which uses the endomorphism theory (Section \ref{sec:hyland-fundamental-theorem}), and Hyland's second version, which uses the theory of extensions (Section \ref{sec:theory-of-extentions}).
+
+\section{Scott's Representation Theorem}\label{sec:hyland-scott}
 
@@
 
-\section{Relations Between the Categories}
+\section{Relations Between the Categories}\label{sec:hyland-categories}
 
@@
 
-\section{Hyland's Proof}
+\section{Hyland's Proof}\label{sec:hyland-fundamental-theorem}
 
@@
 
-\section{The Theory of Extensions}
+\section{The Theory of Extensions}\label{sec:theory-of-extentions}
 

### 2024-11-08 910-alternative-definitions.tex
Add chapter introductions

@@
 \chapter{Alternative definitions}\label{ch:alternative-definitions}
-The literature, there are many different but equivalent definitions, carrying many different names, for the objects that called `algebraic theories' in Section \ref{sec:algebraic-theories}.
-Also, many of these different names are attached to differently defined objects in different sources.
-This section will showcase some of the various definitions.
+In the literature, there are many different but equivalent definitions, carrying many different names, for the objects that are called `algebraic theories' in Section \ref{sec:algebraic-theories}.
+To make matters even more confusing, the same name can refer to different things in different parts of the literature.
+This appendix will showcase various definitions and give them a name.
+Of particular interest is the Lawvere theory (Section \ref{sec:lawvere-theory}), which is also used in Hyland's paper.
 
-In this appendix, we will denote the finite set $ \llbracket n \rrbracket = \{ 1, \dots, n \} $.
+In this appendix, we will denote the finite set $ \{ 1, \dots, n \} $ as $ \llbracket n \rrbracket $.
 
@@
 
-\section{Lawvere Theory}
+\section{Lawvere Theory}\label{sec:lawvere-theory}
 \begin{definition}

### 2024-11-08 920-weak-cartesian-closed.tex
Add chapter introductions

@@
 However, as it turns out, we do not need all of the properties of a cartesian closed category.
-It suffices to consider a \textit{weak} cartesian closed category.
-In fact, even a `semi cartesian closed category' will suffice, but in this section, we will restrict ourselves to a weak cartesian closed category, as this notion suits our purposes well enough.
+It suffices to consider a \textit{weak} cartesian closed category, which we will discuss in this appendix.
+In fact, even a `semi cartesian closed category' will suffice, but in this appendix, we will restrict ourselves to a weak cartesian closed category, as this notion suits our purposes well enough.
 

### 2024-11-14 200-category-theory.tex
Improve titles, make some sentences active instead of passive

@@
 
-\subsection{Adjoint equivalences}
+\subsection{Adjoint Equivalences}
 An (adjoint) equivalence of categories has two equivalent definitions, that only differ in which notion they take as the base. In this case, we will use the definition that is based on adjunctions:
@@
 
-\subsection{Weak equivalences}
+\subsection{Weak Equivalences}
 There is also the notion of `weak equivalence'. In some cases, this is equivalent to an adjoint equivalence (for example, when its domain is univalent, see Section \ref{sec:univalence-principle}).
@@
 
-\subsection{Exponential objects}
+\subsection{Exponential Objects}
 Note that in the category of sets, for all $ X, Y: \SET $, we have a set of functions $ (X \to Y) $. Also, for all $ X, Y, Z $, there is a (natural) bijection
@@
 
-\subsection{Forgetful functors and free objects}
+\subsection{Forgetful Functors and Free Objects}
 
@@
 
-\subsection{Extension and restriction of scalars}
+\subsection{Extension and Restriction of Scalars}
 

### 2024-11-14 400-algebraic-structures.tex
Improve titles, make some sentences active instead of passive

@@
 
-\section{\texorpdfstring{$ \lambda $-}{lambda-}theories}\label{sec:lambda-theories}
+\section{\texorpdfstring{$ \lambda $-}{lambda-}Theories}\label{sec:lambda-theories}
 
@@
 
-\subsection{The $ \lambda $-calculus operations}\label{subsec:lambda-calculus-operations}
+\subsection{The $ \lambda $-Calculus Operations}\label{subsec:lambda-calculus-operations}
 For a $ \lambda $-theory $ L $, we have variables $ x_{n, i} : L_n $ and $ \lambda $-abstraction $ f \mapsto \lambda(f) $.
@@
 
-\subsection{The free algebraic theory on a set}
+\subsection{The Free Algebraic Theory on a Set}
 \begin{example}[\coqident{AlgebraicTheories.Examples.FreeTheory}{free_functor}]
@@
 
-\subsection{The free \texorpdfstring{$ \lambda $}{lambda}-theory on a set}
+\subsection{The Free \texorpdfstring{$ \lambda $}{lambda}-Theory on a Set}
 
@@
 
-\subsubsection{About $ \Lambda $-algebra morphisms}
+\subsubsection{About $ \Lambda $-Algebra Morphisms}
 
@@
 
-\subsection{The free object algebraic theory}
+\subsection{The Free Object Algebraic Theory}
 
@@
 
-\subsection{The terminal theory}
+\subsection{The Terminal Theory}
 \begin{example}[\coqident{AlgebraicTheories.Examples.OnePointTheory}{one_point_theory}]
@@
 
-\subsection{The endomorphism theory}
+\subsection{The Endomorphism Theory}
 
@@
 
-\subsection{The theory algebra}
+\subsection{The Theory Algebra}
 \begin{example}[\coqident{AlgebraicTheories.Examples.TheoryAlgebra}{theory_algebra}]\label{ex:theory-algebra}
@@
 
-\subsection{The initial presheaf}
+\subsection{The Initial Presheaf}
 \begin{example}
@@
 
-\subsection{The theory presheaf}
+\subsection{The Theory Presheaf}
 \begin{example}[\coqident{AlgebraicTheories.Presheaves}{theory_presheaf}]
@@
 
-\subsection{The ``+\texorpdfstring{$ \ell $}{l}'' presheaf}
+\subsection{The `\texorpdfstring{$ n + p $}{n + p}'-Presheaf}
 
 \begin{example}[\coqident{AlgebraicTheories.Examples.Plus1Presheaf}{plus_1_presheaf}]
-  Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, \ell) $ with $ A(Q, \ell)_n = Q_{n + \ell} $ and, for $ q: A(Q, \ell)_m $ and $ f: T_n^m $, action
-  \[ q \bullet_{A(Q, \ell)} f = q \bullet_Q ((\iota_{n, \ell} (f_i))_i + (x_{n + i})_i). \]
+  Given a $ T $-presheaf $ Q $, we can construct a presheaf $ A(Q, p) $ with $ A(Q, p)_n = Q_{n + p} $ and, for $ q: A(Q, p)_m $ and $ f: T_n^m $, action
+  \[ q \bullet_{A(Q, p)} f = q \bullet_Q ((\iota_{n, p} (f_i))_i + (x_{n + i})_i). \]
 \end{example}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.RepresentationTheorem}{theory_presheaf_exponentiable}]
-  For all $ m $ and all $ T $-presheaves $ Q $, $ A(Q, m) $ is the exponential object $ Q^{T^m} $.
+  For all $ p $ and all $ T $-presheaves $ Q $, $ A(Q, p) $ is the exponential object $ Q^{T^p} $.
 \end{lemma}
 \begin{proof}
-  We will show that $ A(-, m) $ constitutes a right adjoint to the functor $ - \times T^m $. We will do this using universal arrows.
+  We will show that $ A(-, p) $ constitutes a right adjoint to the functor $ - \times T^p $. We will do this using universal arrows.
 
-  For $ Q $ a $ T $-presheaf, take the arrow $ \varphi: A(Q, m) \times T^m \to Q $ given by $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $ for $ q: A(Q, m)_n = Q_{n + m} $ and $ t: T^m_n $.
+  For $ Q $ a $ T $-presheaf, take the arrow $ \varphi: A(Q, p) \times T^p \to Q $ given by $ \varphi(q, t) = q \bullet_Q ((x_{n, i})_i + t) $ for $ q: A(Q, p)_n = Q_{n + p} $ and $ t: T^p_n $.
 
-  Now, given a $ T $-presheaf $ Q^\prime $ and a morphism $ \psi: Q^\prime \times T^m \to Q $.
-Define $ \tilde \psi: Q^\prime_n \to A(Q, m)_n $ by $ \tilde \psi(q) = \psi(\iota_{n, m}(q), (x_{n + i})_i) $.
+  Now, given a $ T $-presheaf $ Q^\prime $ and a morphism $ \psi: Q^\prime \times T^p \to Q $.
+Define $ \tilde \psi: Q^\prime_n \to A(Q, p)_n $ by $ \tilde \psi(q) = \psi(\iota_{n, p}(q), (x_{n + i})_i) $.
 
-  Then $ \psi $ factors as $ (\tilde \psi \times \id{T^m}) \cdot \varphi $.
+  Then $ \psi $ factors as $ (\tilde \psi \times \id{T^p}) \cdot \varphi $.
 Also, some equational reasoning shows that $ \tilde \psi $ is unique, which proves that $ \varphi $ indeed is a universal arrow.

### 2024-11-14 500-previous-work.tex
Improve titles, make some sentences active instead of passive

@@
 
-\subsection{Taylor's proof}
+\subsection{Taylor's Proof}
 
@@
 
-\section{The \texorpdfstring{$ \lambda $}{lambda}-calculus is Algebraic}\label{sec:selinger}
+\section{The \texorpdfstring{$ \lambda $}{lambda}-Calculus is Algebraic}\label{sec:selinger}
 As we mentioned in Remark \ref{rem:lambda-theory-or-algebra}, using tools from universal algebra, there are two approaches to study $ \lambda $-calculus-like structures.

### 2024-11-14 700-formalization.tex
Improve titles, make some sentences active instead of passive

@@
 In addition to the reading, investigating and writing mathematics that lead up to the previous chapters, this thesis project also had a formalization component.
-Parts of Hyland's paper were carefully written out in detail in a proof assistant and added to a library of formalized mathematics with the univalent point of view, called \textit{UniMath}.
+I carefully worked out parts of Hyland's paper in detail using a proof assistant and added the resulting code to a library of formalized mathematics with the univalent point of view, called \textit{UniMath}.
 
-This chapter will give an overview of what was formalized, as well as point out and evaluate a couple of design decisions that were made.
+This chapter will give an overview of the mathematics that I formalized, as well as point out and evaluate a couple of design decisions that I made.
 
 \section{Some Numbers}
-The code for this project was written over the course of about 18 months, spread over \href{https://github.com/UniMath/UniMath/pulls?q=is%3Apr+author%3Aarnoudvanderleer+is%3Aclosed}{20 pull requests}: 13 with content about Hyland's paper, adding 23\,361 and removing 7\,620 lines of code, and 7 with only some missing category theoretical preliminaries, adding 3\,291 and removing 816 lines.
+I wrote the code for this project over the course of about 18 months, spread over \href{https://github.com/UniMath/UniMath/pulls?q=is%3Apr+author%3Aarnoudvanderleer+is%3Aclosed}{20 pull requests}: 13 with content about Hyland's paper, adding 23\,361 and removing 7\,620 lines of code, and 7 with only some missing category theoretical preliminaries, adding 3\,291 and removing 816 lines.
 
 \section{Overview of the Formalized Material}
-The material that was formalized can be subdivided into material that is introduced or described in Hyland's paper, and category theoretical preliminaries that are necessary to make the proofs in Hyland's paper work.
+The material that I formalized can be subdivided into material that is introduced or described in Hyland's paper, and category theoretical preliminaries that are necessary to make the proofs in Hyland's paper work.
 
@@
 \section{Equality, Isomorphisms and Equivalences}
-One of the lessons during this project was that for formalizing, it is always important to choose te right equality for the job.
+One of the lessons that I learned during this project was that for formalizing, it is always important to choose te right equality for the job.
 For example, for two categories $ \C $ and $ \D $, one can aim to prove either that $ \C = \D $ or that we have a functor $ F : \C \to \D $ that has a right and left inverse, or that we have a functor $ F : \C \to \D $ that is an adjoint equivalence.
@@
 
-\subsection{The categories in question}\label{subsec:formalized-categories}
+\subsection{The Categories in Question}\label{subsec:formalized-categories}
 
@@
 Also, we know that a product of univalent categories is univalent again, since its isomorphisms and equalities are equivalent to pairs of isomorphisms and equalities of its factors.
-We already knew that $ \SET $ is univalent, and in this project, the category of sets, indexed over a type, was constructed and shown to be univalent.
+We already knew that $ \SET $ is univalent, and in this project, I constructed the category of families of sets, indexed over a type, and showed this category to be univalent.
 
@@
 
-During this project, a small lemma was added to the library, showing that for a full subcategory $ \int_C D \subseteq C $, where $ D_c $ is a mere proposition for all $ c : C $, if for all $ (X, \bar X), (Y, \bar Y) : \int D $, we have $ D_{X \times Y} $ (the $ C $-product of two objects in $ \int D $ is again in $ \int D $), then $ D $ creates binary products.
-Also, a lemma was added that shows that if a displayed category $ D $ over $ C $, and a displayed category $ E $ over $ D $, both create binary products, then $ \sigma_D E $ also creates binary products.
+During this project, I added a small lemma to the library, showing that for a full subcategory $ \int_C D \subseteq C $, where $ D_c $ is a mere proposition for all $ c : C $, if for all $ (X, \bar X), (Y, \bar Y) : \int D $, we have $ D_{X \times Y} $ (the $ C $-product of two objects in $ \int D $ is again in $ \int D $), then $ D $ creates binary products.
+I also added a lemma showing that if a displayed category $ D $ over $ C $, and a displayed category $ E $ over $ D $, both create binary products, then $ \sigma_D E $ also creates binary products.
 
@@
 For example, if the function $ f $ commutes with the algebra actions on $ \bar C $ and $ \bar A $, and $ g $ commutes with the actions on $ \bar C $ and $ \bar B $, then we need to show that the product morphism $ \langle f, g \rangle $ commutes with the actions on $ \bar C $ and $ \overline{A \times B} $.
-A lemma showing that it suffices to show that we can lift the product morphism was added to the library, and used to show that the `\dots data' displayed categories create binary products.
+I added a lemma showing that it suffices to construct a lift for the product morphism, and used this lemma to show that the `\dots data' displayed categories create binary products.
 
@@
 
-\subsection{Chicken or egg?}
+\subsection{Chicken or Egg?}
 The formalization started with definitions for the objects and morphisms in question: algebraic theories and algebras.
-Using these, the categories were defined directly.
-However, since showing univalence is much easier when working with displayed categories, the definitions of the categories were decoupled from the definitions of the objects and morphisms, and instead were constructed as displayed categories.
+Using these, I defined the categories directly.
+However, since showing univalence is much easier when working with displayed categories, I decoupled the definitions of the categories from the definitions of the objects and morphisms, and instead constructed them as displayed categories.
 This meant that of every definition, a part was duplicated: once for the object (and morphism) types, and once for the objects and morphisms in the displayed categories.
@@
 
-In the end, the solution was to first define the category, and then the object and morphism types as the objects and morphisms of the category.
+In the end, the best solution was to first define the category, and then the object and morphism types as the objects and morphisms of the category.
 The coercions can then be defined on the standalone object and morphism types, which works very well.
 
-\subsection{A product of categories}\label{subsec:displayed-product}
+\subsection{A Product of Categories}\label{subsec:displayed-product}
 Given two categories $ C $ and $ C^\prime $, their product $ C \times C^\prime $ can be viewed as a displayed category over $ C $ (or $ C^\prime $), where the objects over any object are the objects of $ C^\prime $, and the displayed morphisms $ g: c \to_f c^\prime $ are the morphisms $ g: C^\prime(c, c^\prime) $.
@@
 In return, this approach gives cleaner definitions in practice for the identity and composition morphisms of the total category.
-Therefore, halfway during the project, a switch was made from the first to the second approach.
+Therefore, halfway during the project, I switched from the first to the second approach.
 
@@
 
-Therefore, in this project, the type of every one of these components is given a name, ending in \texttt{\_ax}, for `axiom'.
+Therefore, in this project, I gave the type of every one of these components a name, ending in \texttt{\_ax}, for `axiom'.
 For example, there are \texttt{var\_ax} and \texttt{subst\_ax} for algebraic theories, \texttt{mor\_var\_ax} and \texttt{mor\_subst\_ax} for their morphisms, \texttt{action\_ax} for algebras and \texttt{app\_ax} and \texttt{abs\_ax} for $ \lambda $-theories.
@@
 This is because their categories are displayed over the categories of algebraic theories, and the category of $ T $-algebras and $ T $-presheaves are fibers of the full displayed category.
-Therefore, the morphisms of $ T $-algebras are given by displayed morphisms over $ \id T $, so the axiom of an algebra morphism $ g $ is
+Therefore, the morphisms of $ T $-algebras are given by displayed morphisms over $ \id T $, so the axiom of, for example, an algebra morphism $ g $ is
 \[ \mathtt{mor\_action\_ax}: \prod_n \prod_{t : T_n} \prod_{a : A^n} g (t \bullet a) = \id T(t) \bullet (g (a_i))_i, \]
@@
 
-Very early on in the project, a choice was made to use the second approach.
+Very early on in the project, I chose to use the second approach.
 Since many definitions require extending a mapping to a tuple, and since we do not very often need to extend tuples or do induction on a tuple, this proved to be the right choice.
@@
 
-In this case, somewhat of a compromise was made.
-The endomorphism theory was indeed defined using a repeated binary product, and the construction of finite powers from the terminal object and binary products\footnote{Unfortunately, defining the product of a tuple of objects was much harder than defining the finite power of one object.
+In this case, I made somewhat of a compromise.
+I indeed defined the endomorphism theory using a repeated binary product, and the construction of finite powers from the terminal object and binary products\footnote{Unfortunately, defining the product of a tuple of objects was much harder than defining the finite power of one object.
 When generalizing the approach to tuples of objects, some terms suddenly do not have the `correct' type, which has something to do with some equalities like $ ((x_1, \dots, x_n) + (y))_{n + 1} = y $ that do not hold definitionally.
 Even though this specific problem can be solved using transports, the rest of the proof becomes then much harder because the transports get in the way}.
-On the other hand, the Yoneda lemma for $ L $-presheaves does indeed use the `usual' notion of products $ L^n $ where the sets are tuple types.
-Luckily, the library contains a proof that two products are isomorphic, so where the definitions clash, we use the isomorphisms to translate between them.
+On the other hand, for the Yoneda lemma for $ L $-presheaves, I indeed use the `usual' notion of products $ L^n $ where the sets are tuple types.
+Luckily, the library contains a proof that products are unique up to isomorphism, so where the definitions clash, we use the isomorphisms to translate between them.
 Even though this adds friction, in the end it is pretty straightforward.
@@
 However, the repeated binary product construction needed $ \prod_{i : \{ i \mid 1 \leq i \leq 0 \}} X_i $, and $ \emptyset $ is not definitionally equal to $ \{ i \mid 1 \leq i \leq 0 \} $.
-Initially, this was solved by transporting along the equality $ \emptyset = \{ i \mid 1 \leq i \leq 0 \} $.
+Initially, I solved this by transporting along the equality $ \emptyset = \{ i \mid 1 \leq i \leq 0 \} $.
 However, much further down the line, some proof involved an element of this product over $ \{ i \mid 1 \leq i \leq 0 \} $, and because of the transport, rocq was not able to see that this product was just $ \{ \star \} $.
-Therefore, the statement of the lemma about the empty product was changed to ``For a type $ I $ and a family $ X : I \to C $, if we have a function $ f : I \to \emptyset $, the terminal object gives the product $ \prod_{i : I} X_i $''.
+Therefore, I changed the statement of the lemma about the empty product to ``For a type $ I $ and a family $ X : I \to C $, if we have a function $ f : I \to \emptyset $, the terminal object gives the product $ \prod_{i : I} X_i $''.
 Note that having the function $ f $ is equivalent to $ I $ being equivalent (and therefore equal) to the empty type.
@@
 
-\section{The \texorpdfstring{$ n + p $}{n + p}-presheaf}
+\section{The `\texorpdfstring{$ n + p $}{n + p}'-Presheaf}
 Now, the definition of the endomorphism $ \lambda $-theory $ E_{\Pshf L}(L) $ requires that the theory presheaf $ L $ is exponentiable.
 As shown before, $ P^L $ is given by $ A(P, 1) $, the `plus 1' presheaf, where the last variable is ignored in the $ L $-action.
-In fact, one can show that $ P^{L^n} $ is given by $ A(P, n) $ and this was the level of generality at which the statement was formalized.
+In fact, one can show that $ P^{L^n} $ is given by $ A(P, n) $ and this was indeed the level of generality at which I formalized the statement.
 To obtain the action
 \[ \bullet : A(P, p)_m \times L_n^m \to A(P, p)_n, \]
-the equivalence
+I used the equivalence
 \[ \{ 1, \dots, n + p \} \simeq \{ 1, \dots, n \} \sqcup \{ 1, \dots, p \} \]
-from the library was used, which sends the first $ n $ elements to the first set, and the last $ p $ elements to the second, so this could indeed be used to construct elements of tuples $ A^{n + p} $, separating them into first a tuple of $ n $ and then a tuple of $ p $.
+from the library, which sends the first $ n $ elements to the first set, and the last $ p $ elements to the second, so this could indeed be used to construct elements of tuples $ A^{n + p} $, separating them into first a tuple of $ n $ and then a tuple of $ p $.
 After this, it was time to construct the presheaf morphisms for $ \rho $ and $ \lambda $ between $ L $ and $ A(L, 1) $, but this turned out to be much harder than expected, because $ A(L, 1)_n = L_{n + 1} $, whereas $ \rho $ and $ \lambda $ are functions between $ L_n $ and $ L_{S n} $, where $ S n = 1 + n $.
-Unfortunately, $ 1 + n $ is not definitionally equal to $ n + 1 $, and even though we might transport along a proof $ h: 1 + n = n + 1 $, this will give problems down the road.
+Unfortunately, $ 1 + n $ is not definitionally equal to $ n + 1 $, and even though we might transport along a proof $ h: 1 + n = n + 1 $, such a transport will give problems down the road.
 
@@
 However, this equivalence would be somewhat weird, because the order of $ n $ and $ p $ are reversed.
-Also, proving things about these standard finite sets is quite hard, and outside the scope of this project, so this was not attempted in this project, but potentially left for future work.
+Also, proving things about these standard finite sets is quite hard, and outside the scope of this project, so I did not attempted this in this project, but left it for potential future work.
 
@@
 However, the relation given by $ R : (x n, m) \sim (x, f(n) \cdot m) $ for all $ a $, is reflexive and transitive, but not necessarily symmetric.
-Therefore, first the `equivalence closure' $ \bar R $ of $ R $ is taken: the smallest transitive and symmetric relation that contains $ R $.
+Therefore, we first take the `equivalence closure' $ \bar R $ of $ R $: the smallest transitive and symmetric relation that contains $ R $.
 This is then used for the quotient.
-To construct functions from this, like, the right action of the monoid $ M^\prime $, we use the universal property of the quotient: a function from $ X \times M^\prime $ that sends `related' elements $ (x_1, m_1) $ and $ (x_2, m_2) $ to the same element.
+To construct functions from this, like the right action of the monoid $ M^\prime $, we use the universal property of the quotient: a function from $ X \times M^\prime $ that sends `related' elements $ (x_1, m_1) $ and $ (x_2, m_2) $ to the same element gives a function from the quotient $ X \times M^\prime / \sim $.
 However, the quotient is taken over $ \bar R $ instead of $ R $, so it is no longer possible to assume that $ x_2 = x_1 n $ and $ m_1 = f(n) \cdot m_2 $ for some $ n $.
@@
 Since the proofs did not use any elements of the sets in question, it was then trivial to generalize to any category with coequalizers.
-It turned out that the construction was a special version of left Kan extension, which uses general colimits, and using the existing definition of Kan extension, the proof was made considerably shorter.
+It turned out that the construction was a special version of left Kan extension, which uses general colimits, and using the existing definition of Kan extension, I was able to considerably shorten the proof.
 
@@
 Also, for the fundamental theorem we only need the ordinary set-based monoids.
-Therefore, this generalization was not pursued any further.
+Therefore, I did not pursue this generalization any further.
 
-\section{The Formalization of the \texorpdfstring{$ \lambda $}{lambda}-calculus} \label{sec:axiomatic-lambda-calculus}
+\section{The Formalization of the \texorpdfstring{$ \lambda $}{lambda}-Calculus} \label{sec:axiomatic-lambda-calculus}
 One of the important classes of objects in this thesis is the class of $ \Lambda $-algebras: algebras for the initial $ \lambda $-theory $ \Lambda $, corresponding to the `pure' $ \lambda $-calculus.
@@
 
-Instead, a different, more axiomatic approach was taken.
-A class in group theory often starts with laying out a couple of axioms, like: ``We have a set $ G $, with a binary operation $ b $, a unary operation $ u $ and an element $ e $.
-$ b $ is associative, $ u $ is a left and right inverse for $ b $ and $ e $ is a unit for $ b $.'' Afterwards, this structure is usually bundled into the declaration ``Let $ G $ be a group.'' In the same spirit, every section in the formalization that needs the pure $ \lambda $-calculus, starts with ``Let $ L $ be the pure $ \lambda $-calculus with $ \beta $-equality.'' To this end, there is a definition \texttt{lambda\_calculus}, consisting of:
+Instead, I took a different, more axiomatic approach.
+An undergraduate class in group theory often starts with laying out a couple of axioms, like: ``We have a set $ G $, with a binary operation $ b $, a unary operation $ u $ and an element $ e $.
+$ b $ is associative, $ u $ is a left and right inverse for $ b $ and $ e $ is a unit for $ b $.'' Afterwards, this structure is usually bundled into the declaration ``Let $ G $ be a group.'' In the same spirit, every section in the formalization that needs the pure $ \lambda $-calculus, starts with ``Let $ L $ be the pure $ \lambda $-calculus with $ \beta $-equality.'' To this end, I added a definition \texttt{lambda\_calculus}, consisting of:
 \begin{itemize}
@@
 
-\subsection{Propagation of substitution}
+\subsection{Propagation of Substitution}
 Once the pure $ \lambda $-calculus is defined, it is not very hard to give it a $ \lambda $-theory structure, using the induction principle a couple of times to show that some identities are satisfied.
@@
 
-Therefore, a tactic was added to the project. A first version of this tactic was a variation of
+Therefore, I added a tactic to the project. A first version of this tactic was a variation of
 \begin{lstlisting}

### 2024-11-15 200-category-theory.tex
Add a remark about the classical definition of the Karoubi envelope and refer to it from Remark 2.79

@@
 
-\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}]
+\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}]\label{def:karoubi}
   We define the category $ \overline \C $.
@@
 \end{corollary}
+
+\begin{remark}\label{rem:karoubi-classical}
+  The situation in classical mathematics is very similar to the situation above: We can define a category $ \bar \D $ which is defined using idempotents, a category $ \tilde \D $ which consists of presheaves with chosen retractions, and a category $ \hat \D $ which is the image of $ \tilde \D $ under the forgetful functor $ F : \hat \D \to P \C $.
+More specifically, $ \hat \D $ is the full subcategory of $ P \C $, which we get if we only select the presheaves $ F $ such that we can find some $ X : \C $ and some retraction $ (r, s) : F \triangleleft \yo(X) $.
+We again have an adjoint equivalence $ \bar \D \simeq \tilde \D $ and a fully faithful, essentially surjective functor $ F : \tilde \D \to \hat \D $.
+
+  However, in classical mathematics we have something even stronger: unlike in univalent foundations, we can use the axiom of choice to turn the weak equivalence into an adjoint equivalence $ F : \tilde \D \xrightarrow \sim \hat \D $, choosing an object $ X : \C $ and a retraction $ (r, s) : F \triangleleft \yo(X) $ for every $ F : \tilde \D $.
+This means that classically, the different definitions of the Karoubi envelope all coincide.
+\end{remark}
 
@@
 \begin{remark}\label{rem:karoubi-candidate-choice}
-  As we saw in this section, there are multiple candidates for the `Karoubi envelope'.
-Two of these candidates are equivalent to each other, but the third is not.
+  As we saw in this section, there are multiple candidates for the `Karoubi envelope' of a category $ \C $: $ \bar \C $ (Definition \ref{def:karoubi}), $ \tilde \C $ (Definition \ref{def:karoubi'}) and $ \hat \C $ (Definition \ref{def:karoubi''}).
+In classical mathematics, these are all equivalent to each other (Remark \ref{rem:karoubi-classical}), but in univalent foundations $ \hat \C $ is usually not equivalent to $ \bar \C $ and $ \tilde \C $ (Corollary \ref{cor:karoubi-candidates}).
+
   Therefore, we need to be careful which definition we choose, because this choice has consequences.

### 2024-11-15 200-category-theory.tex
Add a remark about univalence of L0, and string the remarks about univalence of the category of retracts together

@@
 
-\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_univalence}]
+\begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_univalence}]\label{rem:karoubi-univalent}
   If $ \overline \C $ is univalent, $ \C $ is univalent as well.
@@
 
-\begin{remark}
+\begin{remark}\label{rem:karoubi-not-univalent}
   Note that the converse does not necessarily hold. Consider the commutative monoid consisting of the three matrices

### 2024-11-15 500-previous-work.tex
Add a remark about univalence of L0, and string the remarks about univalence of the category of retracts together

@@
 \begin{remark}
-  Note that if $ L $ is a nontrivial $ \lambda $-theory, $ \R $ is not a univalent category.
+  As we saw in Remarks \ref{rem:karoubi-univalent} and \ref{rem:karoubi-not-univalent}, the Karoubi envelope can only be univalent if the original category is univalent, and even then it is not always univalent.
+In the case of $ \R $, if $ L $ is a nontrivial $ \lambda $-theory, $ \R $ is not a univalent category.
 To see this, note, for example, that we have an object $ X := \langle \pi_1, \pi_2 \rangle : \R $ (corresponding to the type of `pairs' of $ \lambda $-terms).
@@
 To see that these are indeed different morphisms, note that applying them (or their lifted versions) to $ (x_{2, 1}, x_{2, 2}) $ gives respectively $ x_{2, 1} $ and $ x_{2, 2} $, which are distinct elements by Lemma \ref{lem:nontrivial-algebraic-theory}.
+\end{remark}
+
+\begin{remark}
+  In some cases, we can already conclude that $ \R $ is not univalent because $ L_0 $ is not univalent.
+For example, if $ L_0 $ has $ \eta $-equality, the single object $ \star : L_0 $ has a nontrivial automorphism given by
+  \[ \lambda x_1 x_2 x_3, x_1 x_3 x_2, \]
+  so $ L_0 $ is not univalent, so $ \R $ is not univalent.
+
+  On the other hand, if $ L $ is the pure $ \lambda $-calculus with $ \beta $-equality, I believe we can use structural induction to show that $ \star : L_0 $ has no nontrivial automorphisms, so $ L_0 $ is univalent.
+However, as shown above, $ \R $ is still not univalent.
 \end{remark}

### 2024-11-25 200-category-theory.tex
Sort out simeq and cong

@@
 
+Throughout this thesis, we will use the notation $ A \cong B $ for an isomorphism of objects in a category, or of categories themselves.
+We will use the notation $ A \simeq B $ for an equivalence of types or of categories.
+If $ A $ and $ B $ are sets or univalent categories, $ A \cong B $ is equivalent to $ A \simeq B $.
+We will often, instead of $ A \cong B $ or $ A \simeq B $ just write $ f: A \xrightarrow \sim B $, giving the isomorphism or equivalence a name.
+
 In this thesis, we will often work with `tuples': elements of $ S^n $ for some set $ S $ and some natural number $ n $. We will denote
@@
   Let $ F: \C \to \D $ be a functor and $ X: \D $ an object. An object $ Y: \C $ and an arrow $ f: \D(X, F(Y)) $ form a universal arrow from $ X $ to $ F $ if and only if the function
-  \[ (g \mapsto f \cdot F(g)) : \C(Y, x) \cong \D(X, F(x)) \]
+  \[ (g \mapsto f \cdot F(g)) : \C(Y, x) \to \D(X, F(x)) \]
   is a bijection.
@@
 \begin{lemma}
-  For any $ Y: \C $ and $ F : P \C $, we have an equivalence $ P \C(\yo(Y), F) \simeq F(Y) $, and this equivalence is natural in $ Y $ and $ F $.
+  For any $ Y: \C $ and $ F : P \C $, we have a bijection $ P \C(\yo(Y), F) \cong F(Y) $, and this bijection is natural in $ Y $ and $ F $.
 \end{lemma}
@@
 
-In fact, $ \Delta_X : \C \to (\C \downarrow X) $ is a functor, with $ \Delta_X(f) = \id X \times f $ for $ f: \C(Y, Y^\prime) $. This functor preserves the terminal object, products and pullbacks:
+In fact, $ \Delta_X : \C \to (\C \downarrow X) $ is a functor, with $ \Delta_X(f) = \id X \times f $ for $ f: \C(Y, Y^\prime) $.
+If $ \C $ has a terminal object $ T $ and we identify $ \C $ with $ (\C \downarrow T) $, then $ \Delta_X $ is the pullback functor along $ (\C \downarrow T) \to (\C \downarrow X) $ along the morphism $ !: X \to T $.
+This functor preserves the terminal object, products and pullbacks:
 \begin{lemma}\label{lem:delta-limits}
@@
 \begin{proof}
-  See \autocite[][Volume 3, Lemma 5.8.2]{borceux}. There, the following equivalences are used for the proof:
+  See \autocite[][Volume 3, Lemma 5.8.2]{borceux}. There, the following isomorphisms are used for the proof:
   \begin{align*}
@@
 Note that for the terminal morphism $ f: X \to \{ \star \} $, we have $ (X, \id X) = f^*(\{\star\}, \id{\{\star\}}) $.
-To summarize, we have an equivalence
-\[ (\SET \downarrow X)\left(f^*(\{ \star \}, \id{\{\star\}}), (Y_x)_x \right) \simeq (\SET \downarrow {\{\star\}})\left( (\{\star\}, \id{\{ \star \}}), \left( \prod_{x : X} Y_x, ! \right) \right) \]
+To summarize, we have a bijection
+\[ (\SET \downarrow X)\left(f^*(\{ \star \}, \id{\{\star\}}), (Y_x)_x \right) \cong (\SET \downarrow {\{\star\}})\left( (\{\star\}, \id{\{ \star \}}), \left( \prod_{x : X} Y_x, ! \right) \right) \]
 for $ !
@@
 Now, for an internal indexed family $ f : Y \to X $ and given a family of families $ ((Z_y)_{y : Y_x})_{x : X} $, we can wonder whether we can construct the family of dependent products $ (\prod_{y : Y_x} Z_y)_x $.
-In $ \SET $, this is definitely possible, and from this, we get an equivalence again
-\[ \left(\SET \downarrow \sum_{x : X} Y_x \right)\left(f^*(X, \id X), (Z_y)_{x, y} \right) \simeq (\SET \downarrow X)\left((X, \id X), \left(\prod_{y : Y_x} Z_y\right)_x\right). \]
+In $ \SET $, this is definitely possible, and from this, we get a bijection again
+\[ \left(\SET \downarrow \sum_{x : X} Y_x \right)\left(f^*(X, \id X), (Z_y)_{x, y} \right) \cong (\SET \downarrow X)\left((X, \id X), \left(\prod_{y : Y_x} Z_y\right)_x\right). \]
 with $ p : \sum_{x : X} \sum_{y : Y_x} Z_y \to \sum_{x : X} Y_x $ defined as $ p(x, y, z) = (x, y) $.
-These equivalences suggest an adjunction $ f^* \dashv \prod_{\dots} $.
+These bijections suggest an adjunction $ f^* \dashv \prod_{\dots} $.
 We can use this to define in general
@@
 A family of maps $ g_x : (\sum_{y : Y_x} Z_y)_x \to Y^\prime_x $ consists of maps $ Z_y \to Y^\prime_x $ for all $ y : Y_x $, so these are maps $ g_y : Z_y \to Y^\prime_{f(y)} $.
-This gives an equivalence
-\[ (\SET \downarrow X)\left(\left( \sum_{y : Y_x} Z_y \right)_x, (Y^\prime_x)_x \right) \simeq \left(\SET \downarrow \left(\sum_{x : X} Y_x \right) \right)((Z_y)_y, f^*((Y^\prime_x)_x)). \]
+This gives a bijection
+\[ (\SET \downarrow X)\left(\left( \sum_{y : Y_x} Z_y \right)_x, (Y^\prime_x)_x \right) \cong \left(\SET \downarrow \left(\sum_{x : X} Y_x \right) \right)((Z_y)_y, f^*((Y^\prime_x)_x)). \]
 This, again, suggests an adjunction which we will use as a definition.
@@
   \end{center}
-  gives an equivalence between morphisms $ \varphi: W \to f^* Z $ that commute with $ h $ and $ f^* g $, and morphisms $ \psi: W \to Z $ that commute with $ h $, $ g $ and $ f $. In other words:
-  \[ (\C \downarrow X)(h \cdot f, g) \simeq (\C \downarrow Y)(h, f^*(g)), \]
+  gives a bijection between morphisms $ \varphi: W \to f^* Z $ that commute with $ h $ and $ f^* g $, and morphisms $ \psi: W \to Z $ that commute with $ h $, $ g $ and $ f $. In other words:
+  \[ (\C \downarrow X)(h \cdot f, g) \cong (\C \downarrow Y)(h, f^*(g)), \]
   which shows the adjunction.
@@
 
-  Now, note that if we have a coequalizer $ W $ of $ \id Z $ and $ a $, and an equalizer $ Y $ of $ \id X $ and $ b $ (in particular, if $ W $ and $ Y $ are retracts), the universal properties of these give an equivalence
-  \[ \D(W, Y) \cong \{ f: \D(Z, Y) \mid a \cdot f = f \} \cong \{ f: \D(Z, X) \mid a \cdot f = f = f \cdot b \}. \]
+  Now, note that if we have a coequalizer $ W $ of $ \id Z $ and $ a $, and an equalizer $ Y $ of $ \id X $ and $ b $ (in particular, if $ W $ and $ Y $ are retracts), the universal properties of these give a bijection
+  \[ \D(W, Y) \cong \{ f: \D(Z, Y) \mid a \cdot f = f \} \cong \{ f: \D(Z, X) \mid a \cdot f = f = f \cdot b \}, \]
+  which exactly describes the morphisms in $ \bar C $.
   \begin{center}
@@
   As the category $ \SET $ is cocomplete, we have an equivalence between the category of presheaves on $ \C $ and the category of presheaves on $ \overline \C $:
-  \[ [\op \C, \SET] \cong [\overline{\op \C}, \SET] \cong [\op{\overline \C}, \SET]. \]
+  \[ [\op \C, \SET] \simeq [\overline{\op \C}, \SET] \simeq [\op{\overline \C}, \SET]. \]
 \end{corollary}

### 2024-11-25 300-univalent-foundations.tex
Improve titles, make some sentences active instead of passive
Sort out simeq and cong

@@
 This type comes with an interesting induction principle called \iindex{path induction}: we can show any statement about paths $ p: x = y $ for generic $ x $ and $ y $, if we can show it about the `trivial' path $ \mathrm{refl}: x = x $ for generic $ x $.
+Often, a way to think about this, is that if we have a proof of equality between $ x $ and $ y $, we can replace $ y $ by $ x $ in any statement.
 For example, symmetry of the equality boils down to a function $ \prod_{x y : T} x = y \to y = x $.
@@
 
-In set-theoretic mathematics, there is the concept of a `bijection' $ S \simeq T $ of sets (or an isomorphism in the category $ \SET $), which is often treated as an equivalence.
+In set-theoretic mathematics, there is the concept of a `bijection' $ S \cong T $ of sets (or an isomorphism in the category $ \SET $), which is often treated as an equivalence.
 It consists of functions $ f: S \to T $ and $ g: T \to S $ with $ f \cdot g = \id S $ and $ g \cdot f = \id T $.
@@
 \[ \mathrm{idtoequiv}: \prod_{S, T: \TYPE} (S = T) \to (S \simeq T). \]
-We construct this function using path induction with the identity bijection $ \prod_S \id S: (S \simeq S) $.
-In fact, this is a specific case of the following: for a category $ C $, if we denote the type of isomorphisms between objects $ c $ and $ d $ with $ c \cong d $, we can construct a function
-\[ \mathrm{idtoiso}: \prod_{c, d: C} (c = d) \to (c \cong d), \]
-using path induction with the identity isomorphism $ \prod_{c: C} \id c: (c \cong c) $. We can then formulate the univalence principle for categories as
+We construct this function using path induction with the identity equivalence $ \prod_S \id S: (S \simeq S) $.
+More generally, for a category $ C $, if we denote the type of isomorphisms between objects $ c $ and $ d $ with $ c \cong d $, we can construct a function
+\[ \mathrm{idtoiso}: \prod_{X, Y: C} (X = Y) \to (X \cong Y), \]
+using path induction with the identity isomorphism $ \prod_{X: C} \id X: (X \cong X) $.
+If $ X $ and $ Y $ are sets, then $ \mathrm{idtoequiv} $ and $ \mathrm{idtoiso} $ coincide.
+We can then formulate the univalence principle for categories as
 
@@
   \[ G \bullet G^\prime = \id D \quad \text{and} \quad G^\prime \bullet G = \id{D^\prime}. \]
-  From this, we can construct an equivalence $ D \cong D^\prime $.
+  From this, we can construct an equivalence $ D \simeq D^\prime $.
 Since $ D $ and $ D^\prime $ are univalent, this equivalence gives an equality of categories, and because $ F \bullet G = F^\prime $, we have an equality of pairs
@@
 
-The last structure in this section for which we want to consider the univalence axiom, is the 2-category $ \Cat $ of categories.
+The last structure in this section for which we want to consider the univalence principle, is the 2-category $ \Cat $ of categories.
 In general, we cannot show that this satisfies the univalence principle.
-However, we will restrict our attention to the sub-2-category of univalent categories, which are the categories that we want to study.
+However, we will restrict our attention to the sub-2-category of univalent categories, which are the `well-behaved' categories in some sense.
 Then Theorem 6.8 in \autocite{univalent-categories} shows that for univalent categories $ C $ and $ D $, there is an equivalence between $ C = D $ and $ C \simeq D $, where $ C \simeq D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
@@
 
-\subsection{Caution: `transport hell'}
+\subsection{Caution: `Transport Hell'}
 Now, it seems that we can transport all properties and data along equalities. And of course, that is true, but some caution needs to be taken with this when working with a proof assistant.

### 2024-11-25 400-algebraic-structures.tex
Sort out simeq and cong

@@
 \begin{lemma}[\coqident{AlgebraicTheories.AlgebraicTheoryCategory}{is_univalent_algebraic_theory_cat}]
-  Since an isomorphism of algebraic theories $ S \simeq T $ consists of pointwise isomorphisms $ f_n: S_n \simeq T_n $ that respect the variables and substitution, the category of algebraic theories is univalent.
+  Since an isomorphism of algebraic theories $ S \cong T $ consists of pointwise bijections $ f_n: S_n \cong T_n $ that respect the variables and substitution, the category of algebraic theories is univalent.
 \end{lemma}
@@
 \begin{proof}
-  Let $ T $ be an algebraic theory. We have an equivalence
+  Let $ T $ be an algebraic theory. We have a bijection
   \[ \AlgTh(F(S), T) \cong \SET(S, T_0), \]
@@
 \begin{proof}
-  For $ S = \emptyset $, the equivalence of hom-sets becomes
+  For $ S = \emptyset $, the bijection of hom-sets becomes
   \[ \AlgTh(F(\emptyset), T) \cong \SET(\emptyset, T_0) \]
@@
 \begin{proof}
-  Let $ L $ be a $ \lambda $-theory. We have an equivalence
+  Let $ L $ be a $ \lambda $-theory. We have a bijection
   \[ \LamTh(\Lambda(S), L) \cong \SET(S, L_0), \]
@@
   Take a category $ \C $, with a forgetful functor $ G: \C \to \SET $ and a free functor $ F: \SET \to \C $.
-Let $ \eta: \id \SET \Rightarrow F \bullet G $ be the unit of the adjunction and let $ \varphi: \C(F(X), Y) \cong \SET(X, G(Y)) $ be the natural equivalence of homsets.
+Let $ \eta: \id \SET \Rightarrow F \bullet G $ be the unit of the adjunction and let $ \varphi: \C(F(X), Y) \cong \SET(X, G(Y)) $ be the natural bijection of homsets.
 

### 2024-11-25 500-previous-work.tex
Sort out simeq and cong

@@
 Given a term $ t: B $ with free variables $ x_1: A_1, \dots, x_n: A_n $, the abstraction $ (\lambda x_n, t): A_n \to B $ corresponds to using the adjunction corresponding to the exponential object of $ A_n $:
-\[ C(A_1 \times \dots \times A_{n-1} \times A_n, B) \simeq C(A_1 \times \dots \times A_{n-1}, B^{A_n}). \]
+\[ C(A_1 \times \dots \times A_{n-1} \times A_n, B) \cong C(A_1 \times \dots \times A_{n-1}, B^{A_n}). \]
 
@@
 In particular, for any two objects $ A, A^\prime: \R $, since we have $ A \circ A^\prime : \R(A^\prime, A) $, so $ \R(A^\prime, A) $ is nonempty, we have
-\[ \R(A^\prime, A) \simeq \R(I \times A^\prime, A) \simeq \R(I, A^{A^\prime}) \simeq \{ \star \}, \]
+\[ \R(A^\prime, A) \cong \R(I \times A^\prime, A) \cong \R(I, A^{A^\prime}) \cong \{ \star \}, \]
 so $ \R $ is the trivial category and $ L $ is trivial.
@@
   We have $ U^U = \lambda f, U \circ f \circ U = \lambda x_1 x_2, x_1 x_2 $.
-Using the equivalence $ \R(U^n \times U, U) \simeq \R(U^n, U^U) $ and the retraction $ U^U: U \to U^U $, the abstraction and application $ \lambda $ and $ \rho $ are given by
+Using the bijection $ \R(U^n \times U, U) \cong \R(U^n, U^U) $ and the retraction $ U^U: U \to U^U $, the abstraction and application $ \lambda $ and $ \rho $ are given by
   \[ \lambda(f) = \lambda x_1 x_2, \iota_{0, 2}(f)(x_1, x_2), \quad \rho(g) = \lambda x_1, \iota_{0, 1}(g) (\pi_1 x_1) (\pi_2 x_1). \]
@@
     \end{center}
-    Intuitively, $ \sum_B Y \cong \sum_A Z $ represents
-    \[ \sum_{b: \sum_{a: A} X a} Y b \cong \sum_{a: A} \sum_{x: X a} Y(a, x), \]
-    by the isomorphism that relates $ ((a, x), y) $ to $ (a, (x, y)) $. Therefore, consider
+    Intuitively, the isomorphism $ \sum_B Y \cong \sum_A Z $ represents a bijection
+    \[ \sum_{b: \sum_{a: A} X a} Y b \cong \sum_{a: A} \sum_{x: X a} Y (a, x), \]
+    relating $ ((a, x), y) $ to $ (a, (x, y)) $. Therefore, consider
     \[ Z = \lambda x_1 x_2, (X x_1 (\pi_1 x_2), Y (s^{-1} (x_1, \pi_1 x_2)) (\pi_2 x_2)): \R^A. \]

### 2024-11-25 600-paper.tex
Improve titles, make some sentences active instead of passive
Sort out simeq and cong

@@
   \[ \varphi_n(f) = \iota_{0, n}(f) (x_i)_i. \]
-  Restricting this equivalence to the morphisms to $ A $ yields
+  Restricting this isomorphism to the morphisms to $ A $ yields
   \[ \R(U^n, A) \cong \{ a : L_n \mid A a = a \}. \]
@@
 Now, officially, $ \hat C_{L_0} $ is the full subcategory of $ P C_{L_0} $, consisting of all objects $ X : P C_{L_0} $ such that there merely exists $ X \triangleleft \yo(\star) $.
-However, recall from the previous section that $ P C_{L_0} \cong P C_{L_1} \cong \Pshf L $.
+However, recall from the previous section that $ P C_{L_0} \simeq P C_{L_1} \simeq \Pshf L $.
 Under this equivalence, $ \yo(\star) $ is embedded as the theory presheaf $ L $, and we will work in the full subcategory $ \hat \R \subseteq \Pshf L $ of the objects $ X : \Pshf L $ such that there merely exists $ X \triangleleft L $.
@@
 \end{remark}
-
-% \begin{remark}
-%   Taylor would write $ (\Pshf L \downarrow_D A) $ instead of $ \R(A) $, with $ D(X, A) $ the retracts $ f: X \to A $ of $ \Delta_A L $.
-However, note that $ D $ is not a class of display maps.
-For example, for $ D $ to be a class of display maps, all terminal projections $ !
-: X \to T $ need to be in $ D $.
-Since for any category $ C $ with terminal object $ T $, we have an equivalence $ (C \downarrow T) \cong C $, having all terminal projections in $ D $ is equivalent to every object in $ \Pshf L $ being a retract of $ L $.
-
-%   However, if we take $ X $ to be the initial (empty) presheaf, we see that there are no morphisms $ L \to X $, because the $ L_n $ are nonempty and the $ X_n $ are empty.
-
-%   There also is a more category-theoretical argument: Suppose that every object of $ \Pshf L $ is a retract of $ L $.
-Via the equivalence $ \Pshf L \cong L_1 $, we see that every object of $ P C_{L_1} $ is a retract of $ \yo(\star) $.
-However then the embedding of $ \hat \R $ (Definition \ref{def:karoubi'}) into $ P C_{L_1} $ is an adjoint equivalence.
-Since $ \yo_{\R} \bullet {\op{\iota_{L_1}}}_* : \R \to \hat \R $ and $ {\op{\iota_{L_1}}}_* : P \R \to P C_{L_1} $ are weak equivalences, (Lemma \ref{lem:retracts-rezk}, Corollary \ref{cor:karoubi-presheaf}), $ \yo_\R : \R \to P \R $ is a weak equivalence as well, but the Yoneda embedding is never essentially surjective.
-For any category $ C $, the constant empty presheaf $ E: c \mapsto \emptyset $ is not representable, since for all $ c : C $, $ \id c = \yo(c)(c) $, so $ \yo(c) $ is not isomorphic to $ E $.
-% \end{remark}
 
@@
 
-  Therefore, this only works in $ \hat \R \cong \hat C_{L_0} $.
+  Therefore, this only works in $ \hat \R \simeq \hat C_{L_0} $.
 Suppose that we tried to do this in $ \tilde C_{L_0} $.
@@
 \end{remark}
-
-% \begin{remark}
-%   Now, recall that according to Hyland, Taylor endows the category of retracts $ \R $ with a class of display maps $ D $, such that $ (\R \downarrow_D X) $ consists exactly of the retracts of $ \Delta_X U $.
-
-%   Hyland then claims that the fact that $ \R $ is cartesian closed relative to this class of display maps follows from the theorem above.
-Recall that Taylor already shows relative cartesian closedness directly, which still works in univalent foundations if we assume the axiom of choice.
-
-%   Recall that we have a weak equivalence $ \varphi : \R \xrightarrow \sim \hat \R $ (Lemma \ref{lem:retracts-rezk}) and one can imagine that we can extend this to weak equivalences $ \psi_X : (\R \downarrow_D X) \xrightarrow \sim (\hat \R \downarrow_D \varphi(X)) $.
-Hyland notes that for $ X : \hat \R $, $ \R(\varphi(X)) $ is equivalent to $ (\hat \R \downarrow_D \varphi(X)) $.
-Implicitly, for $ f: \R(X, Y) $, he wants to lift the functors $ \sum_f $, $ f^* $ and $ \prod_f $ along the equivalences $ \psi $:
-%   \begin{center}
-%     \begin{tikzcd}[sep=large]
-%       (\R \downarrow_D X)
-%         \arrow[d, "\psi_X"]
-%         \arrow[r, dashed, bend left, "\sum_f"']
-%         \arrow[r, dashed, bend right, "\prod_f"]
-%       & (\R \downarrow_D Y)
-%         \arrow[d, "\psi_Y"]
-%         \arrow[l, dashed, "f^*" description]\\
-%       \R(\varphi(X))
-%         \arrow[r, bend left, "\sum_{\varphi(f)}"']
-%         \arrow[r, bend right, "\prod_{\varphi(f)}"]
-%       & \R(\varphi(Y))
-%         \arrow[l, "\varphi(f)^*" description]\\
-%     \end{tikzcd}
-%   \end{center}
-%   For this to work, we need to turn the weak equivalences $ \psi_X $ into adjoint equivalences.
-In particular, we know that for every object $ A : \R(\varphi(X)) $, there merely exists a preimage $ \bar A : (\R \downarrow_D X) $ such that $ \psi_X(\bar A) \cong A $, and we need to construct a functor $ \psi_X^{-1}: \R(\varphi(X)) \to (\R \downarrow_D X) $.
-
-%   For Taylor's proof, we did a similar thing when we knew that for every object $ X : (\R \downarrow_D A) $, there existed some $ Y : \R^A $, and we needed to construct a pullback functor $ f^* : (\R \downarrow_D A) \to (\R \downarrow_D B) $.
-We could use the axiom of choice here because the objects of $ \R $ (and therefore also the objects of the relative slices $ (\R \downarrow_D A) $) form a set.
-
-%   However, as mentioned in \autocite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \autocite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.
-
-%   Therefore, in univalent foundations, the relative cartesian closedness is not a corollary of Theorem \ref{thm:restrict-sum-product}.
-% \end{remark}
 
@@
 \begin{remark}
-  Note that if $ A = L_0 $, then the construction of $ \R_A $ and $ \R $ coincide, so we have an almost trivial equivalence $ \R_A \cong \R $, and an isomorphism $ E_{\R}(U) \cong E_{\R_A}(U) $.
+  Note that if $ A = L_0 $, then the construction of $ \R_A $ and $ \R $ coincide, so we have an almost trivial equivalence $ \R_A \simeq \R $, and an isomorphism $ E_{\R}(U) \cong E_{\R_A}(U) $.
 \end{remark}
@@
 
-\subsection{Terms of a \texorpdfstring{$ \Lambda $}{Lambda}-algebra}
+\subsection{Terms of a \texorpdfstring{$ \Lambda $}{Lambda}-Algebra}
 
@@
 
-Recall that we have an equivalence $ [\op{C_{A_1}}, \SET] \cong \RAct{A_1} $.
+Recall that we have an equivalence $ [\op{C_{A_1}}, \SET] \simeq \RAct{A_1} $.
 
@@
 
-\subsection{Constructing a theory from an algebra}
+\subsection{Constructing a Theory From an Algebra}
 
@@
 
-\subsection{Constructing a theory morphism from an algebra morphism}
+\subsection{Constructing a Theory Morphism From an Algebra Morphism}
 
@@
 \begin{remark}
-  The fact that $ \bar F $ preserves the variables and substitution is not very hard, since these are just defined in terms of finite products of $ U_A $ and $ \bar F $ preserves finite products and $ U_A $.
+  The fact that $ \bar F $ preserves the variables and substitution is not very hard to show, since these are just defined in terms of finite products of $ U_A $ and $ \bar F $ preserves finite products and $ U_A $.
 
@@
 
-\subsection{The unit}
+\subsection{The Unit}
 
@@
 
-\subsection{The counit}
+\subsection{The Counit}
 
 \begin{definition}
-  For $ A : \Alg \Lambda $, we define a bijection $ \epsilon_A : E_{\RAct{A_1}}(U_A)_0 \cong A $ as
+  For $ A : \Alg \Lambda $, we define a bijection $ \epsilon_A : E_{\RAct{A_1}}(U_A)_0 \xrightarrow \sim A $ as
   \[ \epsilon_A(s) = x_1 (\lambda x_2, x_2) \bullet (s(\star)) \quad \text{and} \quad \epsilon_A^{-1}(a)(\star) = (\lambda x_2, x_1) \bullet a. \]
@@
 
-\subsection{The equivalence}
+\subsection{The Equivalence}
 
@@
 \begin{theorem}\label{thm:Hyland-fundamental-theorem}
-  There is an adjoint equivalence $ \LamTh \cong \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
+  There is an adjoint equivalence $ \LamTh \simeq \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
 \end{theorem}
@@
 \begin{lemma}[\coqident{AlgebraicTheories.Examples.ExtensionsTheory}{algebra_coslice_equivalence}]\label{lem:extensions-algebra-coslice}
-  For $ T $ an algebraic theory and $ A $ a $ T $-algebra, we have an adjoint equivalence $ \Alg{T_A} \cong (A \downarrow \Alg T) $ between algebras for $ T_A $ and the coslice category under $ A $.
+  For $ T $ an algebraic theory and $ A $ a $ T $-algebra, we have an adjoint equivalence $ \Alg{T_A} \simeq (A \downarrow \Alg T) $ between algebras for $ T_A $ and the coslice category under $ A $.
 \end{lemma}
@@
   The functor that sends a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $ and the functor that sends a $ \Lambda $-algebra $ A $ to the theory of extensions $ \Lambda_A $ form an adjoint equivalence
-  \[ \LamTh \cong \Alg \Lambda. \]
+  \[ \LamTh \simeq \Alg \Lambda. \]
 \end{theorem}

### 2024-11-25 700-formalization.tex
Sort out simeq and cong

@@
 Lastly, note that if we have a displayed category $ D $ over $ C $, and a displayed category $ E $ over $ \int_C D $, then we can form the \iindex{sigma displayed category} $ \sum_D E $ over $ C $, where $ (\sum_D E)_c $ consists of pairs $ (d, e) $ with $ d : D_c $ and $ e : E_{(c, d)} $.
-Of course, the total categories are equivalent: $ \int_{\int_C D} E \cong \int_C (\sum_D E) $, which boils down to rebracketing $ ((c, d), e) $ to $ (c, (d, e)) $.
+Of course, the total categories are equivalent: $ \int_{\int_C D} E \simeq \int_C (\sum_D E) $, which boils down to rebracketing $ ((c, d), e) $ to $ (c, (d, e)) $.
 
@@
 The first approach uses \textit{reindexing}, by taking the unique functor to the unit category $ F : C \to \{ \star \} $, and considering $ C^\prime $ as a displayed category $ D $ over $ \{ \star \} $.
-Then we have the reindexed (pullback) displayed category $ F^* D $, with $ (F^* D)_c = D_{F(c)} $, with $ \int (F^* D) \cong C \times C^\prime $.
+Then we have the reindexed (pullback) displayed category $ F^* D $, with $ (F^* D)_c = D_{F(c)} $, with $ \int (F^* D) \simeq C \times C^\prime $.
 The advantage of this approach is that it uses fairly simple general machinery.
@@
 
-On the other hand, recall that inverse morphism of $ \Pshf L(L^n, L) \cong L_n $ sends $ s: L_n $ to the presheaf morphism that sends $ (t_i)_i : L^n_m $ to $ s \bullet t : L_m $.
+On the other hand, recall that the inverse morphism of $ \Pshf L(L^n, L) \cong L_n $ sends $ s: L_n $ to the presheaf morphism that sends $ (t_i)_i : L^n_m $ to $ s \bullet t : L_m $.
 Here, we would like the sets of $ L^n $ to match the tuple types in the definition of the substitution $ \bullet : L_n \times L_m^n \to L_m $.
@@
 \[ \bullet : A(P, p)_m \times L_n^m \to A(P, p)_n, \]
-I used the equivalence
-\[ \{ 1, \dots, n + p \} \simeq \{ 1, \dots, n \} \sqcup \{ 1, \dots, p \} \]
+I used the bijection
+\[ \{ 1, \dots, n + p \} \cong \{ 1, \dots, n \} \sqcup \{ 1, \dots, p \} \]
 from the library, which sends the first $ n $ elements to the first set, and the last $ p $ elements to the second, so this could indeed be used to construct elements of tuples $ A^{n + p} $, separating them into first a tuple of $ n $ and then a tuple of $ p $.
@@
 
-In this case, the cleanest solution was to only do the construction for the special case $ p = 1 $ and take $ A(P, 1)_n = P_{S n} $, using the equivalence from the library
-\[ s_m: \{ 1, \dots, n + 1 \} \simeq \{ 1, \dots, n \} \sqcup \{ \star \}, \]
+In this case, the cleanest solution was to only do the construction for the special case $ p = 1 $ and take $ A(P, 1)_n = P_{S n} $, using the bijection from the library
+\[ s_m: \{ 1, \dots, n + 1 \} \cong \{ 1, \dots, n \} \sqcup \{ \star \}, \]
 with
@@
 
-It is possible that constructing a new equivalence
-\[ \{ 1, \dots, p + n \} \simeq \{1, \dots, n\} \sqcup \{1, \dots, p\}, \]
+It is possible that constructing a new bijection
+\[ \{ 1, \dots, p + n \} \cong \{1, \dots, n\} \sqcup \{1, \dots, p\}, \]
 makes it possible to generalize the result to general $ p $ again.

### 2024-11-25 100-introduction.tex
Sort out simeq and cong
Minor changes, make the statement about the Karoubi envelope more subtle

@@
 Therefore, both of the theorems mentioned have subsequently also been proved using `computer proof assistants' \autocite{formalized-four-color-theorem, formalized-Kepler-conjecture}.
-Such proof assistants, like `rocq', `lean' and `Agda', are computer programs with only a very small `trusted codebase'\footnote{The trusted codebase is the part of the codebase of which we have to trust that it is correct.
-The rest of the codebase is checked using this trusted core, so if the trusted core is correct, the rest is too.}, that can verify mathematical reasoning.
+Such proof assistants, like `rocq', `lean' and `Agda', are computer programs with only a very small `trusted codebase'\footnote{The trusted core is the part of the codebase of which we have to trust that it is correct.
+Among other things, it verifies the output of every other part of the codebase, so if the trusted core is correct, the rest is too.}, that can verify mathematical reasoning.
 In this way, if we trust the small core of such a proof assistant, and the proof assistant says that a proof is correct, then we can trust that indeed, the proof is correct.
@@
 
-Now, much of contemporary mathematics is built on the foundation of set theory, which we will often refer to as \iindex{classical mathematics}.
+Now, much of contemporary mathematics is built on the foundation of set theory with classical logic, which we will often refer to as \iindex{classical mathematics}.
 Usually, `set theory' refers to ZFC: Zermelo Fraenkel set theory with the axiom of choice, developed in the early 1900s \autocite{Zermelo-set-theory}.
@@
 This shows that his work can be translated to univalent foundations, and contributes to the knowledge about translating classical mathematics to univalent foundations in general.
-  \item A formalization of part of the paper in rocq (Chapter \ref{ch:the-formalization}). This contributes to the knowledge about formalization in general.
+  \item A formalization of part of the paper in rocq (Chapter \ref{ch:the-formalization}).
+Of particular interest here is a tactic for applying $ \beta $-reduction and substitution to $ \lambda $-terms (Section \ref{sec:tactic}).
+This formalization contributes to the knowledge about formalization in general.
   \item A new proof for the fundamental theorem of the $ \lambda $-calculus (Section \ref{sec:elementary-fundamental-theorem}).
@@
   \item An analysis of the behaviour of the Karoubi envelope in univalent foundations in general (Section \ref{sec:karoubi-envelope}), and in the specific case of Paul Taylor's and Martin Hyland's work (Remark \ref{rem:difference-Taylor-Hyland}).
-Here we see an example of two definitions that are equivalent in classical mathematics, but become different in univalent foundations.
-It is interesting to see the differences between the behaviour of the two definitions in univalent foundations.
+It is one of the places where subtleties arise when translating from classical mathematics to univalent foundations.
 \end{itemize}

### 2024-11-25 200-category-theory.tex
Minor changes, make the statement about the Karoubi envelope more subtle

@@
 \begin{definition}
-  A functor $ F: \C \to \D $ is called a \iindex{weak equivalence} if it is essentially surjective and fully faithful.
+  A functor $ F: \C \to \D $ is called a \iindex{weak equivalence} if it is essentially surjective and fully faithful. We will sometimes denote a weak equivalence with
+  \begin{center}
+    \begin{tikzcd}
+      \C \arrow[r, hook, two heads] & \D
+    \end{tikzcd}
+  \end{center}
+  because intuitively it is injective and surjective, up to isomorphism.
 \end{definition}
@@
   Precomposition gives a functor between functor categories $ F_* : [\B, \C] \to [\A, \C] $.
-If $ F_* $ has a left adjoint, we will denote call this adjoint functor the \textit{left Kan extension}\index{Kan extension!left} along $ F $ and denote it $ \mathrm{Lan}_F : [\A, \C] \to [\B, \C] $.
+If $ F_* $ has a left adjoint, we will call this adjoint functor the \textit{left Kan extension}\index{Kan extension!left} along $ F $ and denote it $ \mathrm{Lan}_F : [\A, \C] \to [\B, \C] $.
 
@@
   The situation in classical mathematics is very similar to the situation above: We can define a category $ \bar \D $ which is defined using idempotents, a category $ \tilde \D $ which consists of presheaves with chosen retractions, and a category $ \hat \D $ which is the image of $ \tilde \D $ under the forgetful functor $ F : \hat \D \to P \C $.
-More specifically, $ \hat \D $ is the full subcategory of $ P \C $, which we get if we only select the presheaves $ F $ such that we can find some $ X : \C $ and some retraction $ (r, s) : F \triangleleft \yo(X) $.
+To be more precise, $ \hat \D $ is the full subcategory of $ P \C $, which we get if we only select the presheaves $ F $ such that we can find some $ X : \C $ and some retraction $ (r, s) : F \triangleleft \yo(X) $.
 We again have an adjoint equivalence $ \bar \D \simeq \tilde \D $ and a fully faithful, essentially surjective functor $ F : \tilde \D \to \hat \D $.
@@
 
-For convenience, the lemma below works very abstractly with pointwise left Kan extension using colimits, but one could also prove this using just (co)equalizers (or right Kan extension using limits).
+For convenience, the lemma below works very abstractly with pointwise left Kan extension using colimits, but one could also prove this using just (co)equalizers (or right Kan extension using $ \C $-small limits).
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_pullback_equivalence}]
-  Let $ \D $ be a category with colimits. We have an adjoint equivalence between $ [\C, \D] $ and $ [\overline \C, \D] $.
+  Let $ \D $ be a category with $ \C $-small colimits. We have an adjoint equivalence between $ [\C, \D] $ and $ [\overline \C, \D] $.
 \end{lemma}

### 2024-11-25 500-previous-work.tex
Minor changes, make the statement about the Karoubi envelope more subtle

@@
 
-Types in the $ \lambda $-calculus correspond to objects in the category.
-
-Types $ A \to B $ in the $ \lambda $-calculus correspond to exponential objects $ B^A $ in the category.
-
-Terms in the $ \lambda $-calculus of type $ B $, with free variables $ x_1: A_1, \dots, x_n: A_n $, correspond to morphisms $ A_1 \times \dots \times A_n \to B $.
-
-A free variable $ x_i: A_i $ in a context with free variables $ x_1: A_1, \dots, x_n: A_n $ corresponds to the projection morphism $ \pi_i : A_1 \times \dots \times A_n \to A_i $.
-
-Given a term $ s: B_1 \to B_2 $ and a term $ t: B_1 $, both with free variables $ x_1: A_1, \dots, x_n: A_n $, corresponding to morphisms $ \overline s: A_1 \times \dots \times A_n \to B_2 $ and $ \overline t: A_1 \times \dots \times A_n \to B_1 $, the application $ st: B_2 $ corresponds to the composite of the product morphism with the evaluation morphism $ A_1 \times \dots \times A_n \to B_2^{B_1} \times B_1 \to B_2 $.
+\begin{itemize}
+  \item Types in the $ \lambda $-calculus correspond to objects in the category.
+  \item Types $ A \to B $ in the $ \lambda $-calculus correspond to exponential objects $ B^A $ in the category.
+  \item Terms in the $ \lambda $-calculus of type $ B $, with free variables $ x_1: A_1, \dots, x_n: A_n $, correspond to morphisms $ A_1 \times \dots \times A_n \to B $.
+  \item A free variable $ x_i: A_i $ in a context with free variables $ x_1: A_1, \dots, x_n: A_n $ corresponds to the projection morphism $ \pi_i : A_1 \times \dots \times A_n \to A_i $.
+  \item Given a term $ s: B_1 \to B_2 $ and a term $ t: B_1 $, both with free variables $ x_1: A_1, \dots, x_n: A_n $, corresponding to morphisms $ \overline s: A_1 \times \dots \times A_n \to B_2^{B_1} $ and $ \overline t: A_1 \times \dots \times A_n \to B_1 $, the application $ st: B_2 $ corresponds to the composite of the product morphism with the evaluation morphism $ A_1 \times \dots \times A_n \to B_2^{B_1} \times B_1 \to B_2 $.
     \begin{center}
@@
     \end{center}
-
-Given a term $ t: B $ with free variables $ x_1: A_1, \dots, x_n: A_n $, the abstraction $ (\lambda x_n, t): A_n \to B $ corresponds to using the adjunction corresponding to the exponential object of $ A_n $:
-\[ C(A_1 \times \dots \times A_{n-1} \times A_n, B) \cong C(A_1 \times \dots \times A_{n-1}, B^{A_n}). \]
+  \item Given a term $ t: B $ with free variables $ x_1: A_1, \dots, x_n: A_n $, the abstraction $ (\lambda x_n, t): A_n \to B $ corresponds to using the adjunction corresponding to the exponential object of $ A_n $:
+    \[ \C(A_1 \times \dots \times A_{n-1} \times A_n, B) \cong \C(A_1 \times \dots \times A_{n-1}, B^{A_n}). \]
+\end{itemize}
 
@@
   Note that the set of $ \lambda $-terms without free variables $ L_0 $ has a monoid structure under the composition defined above.
-The category \index{R}$ \R $ is defined as the Karoubi envelope $ \overline C_{L_0} $ of the category $ C_{L_0} $ of this monoid.
+The category \index{R}$ \R $ is defined as the Karoubi envelope $ \overline C_{L_0} $ (Definition \ref{def:karoubi}) of the category $ C_{L_0} $ of this monoid.
 

### 2024-11-25 700-formalization.tex
Minor changes, make the statement about the Karoubi envelope more subtle

@@
 
-\subsection{Propagation of Substitution}
+\subsection{Propagation of Substitution}\label{sec:tactic}
 Once the pure $ \lambda $-calculus is defined, it is not very hard to give it a $ \lambda $-theory structure, using the induction principle a couple of times to show that some identities are satisfied.

### 2024-11-26 200-category-theory.tex
Write about the universal property of the Karoubi envelope

@@
 
-Besides $ \overline \C $, there is also another (classically equivalent) definition of the Karoubi envelope.
+\begin{remark}\label{rem:classical-karoubi-universal}
+  In this section, we have shown a couple of properties which classically are used as a `universal property' to characterize the Karoubi envelope:
+  \begin{itemize}
+    \item In $ \bar \C $, every idempotent splits.
+    \item We have a fully faithful embedding $ \iota_\C : \C \to \bar \C $;
+    \item Every object in $ \bar \C $ is a retract of an object in $ \C $.
+  \end{itemize}
+  Classically, one can show that if two categories $ \D $ and $ \E $ satisfy the three properties above, then we have an adjoint equivalence $ \D \xrightarrow \sim \E $.
+This uses the axiom of choice to select, for every object in $ \D $ and $ \E $, a retraction from an object in $ \C $.
+
+  There is another construction that yields a category with the properties listed above.
 An object in this alternative category is a presheaf $ F : P\C $ that is a retract of the Yoneda embedding $ \yo(X) $ of an object $ X : \C $.
-Note that there are two different ways to translate this to univalent foundations.
+Because it satisfies the universal property, it is classically equivalent to $ \bar \C $.
+\end{remark}
+
+\begin{remark}
+  In classical mathematics, the only structure of a category is that of the objects and morphisms.
+Therefore, the properties in Remark \ref{rem:classical-karoubi-universal} characterize a classical category uniquely up to adjoint equivalence.
+However, in univalent foundations, categories have additional structure, which is given by identities between objects.
+Therefore, there can be structurally different categories which satisfy this universal property and we need an additional constraint to single out the `right' one.
+However, there are actually two branches of category theory in univalent foundations, each giving its own constraint.
+
+  One branch is the theory of setcategories, where every identity type between two objects is a mere proposition.
+For this branch, the universal property of the Karoubi envelope gets the additional constraint that it must be a setcategory.
+Then we have exactly the classical situation: using the axiom of choice, we can show that any two categories satisfying the universal property are equivalent.
+
+  The other branch is the theory of univalent categories, where the identity type between two objects is equivalent to the isomorphism type between them.
+In this branch, the Karoubi envelope must be a univalent category.
+In this case, we can show that any two categories satisfying the universal property are equivalent without using the axiom of choice.
+\end{remark}
+
+Note that there are two different ways to translate the definition at the end of Remark \ref{rem:classical-karoubi-universal} to univalent foundations.
 We can either interpret the existence of the object $ X $ and the retraction $ (r, s) : F \triangleleft \yo(X) $ as additional \textit{structure} on $ F $, or we can treat it as a \textit{property} and ask for \textit{mere existence} (see Definition \ref{def:mere-existence}) of $ X $, $ r $ and $ s $.
@@
 \end{definition}
-
-This gives us what we need to translate the classical equivalence between the two notions of Karoubi envelope to type theory:
+Because it is a full subcategory of a presheaf category (which is univalent), $ \hat \C $ is univalent.
+
+Now classically, $ \bar \C $ is equivalent to $ \tilde \C $ or $ \hat \C $. In general, this does not work for $ \hat \C $, but it does work for $ \tilde \C $:
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_equivalence}]\label{lem:karoubi-equivalence}
@@
 \end{corollary}
-
-\begin{remark}\label{rem:karoubi-classical}
-  The situation in classical mathematics is very similar to the situation above: We can define a category $ \bar \D $ which is defined using idempotents, a category $ \tilde \D $ which consists of presheaves with chosen retractions, and a category $ \hat \D $ which is the image of $ \tilde \D $ under the forgetful functor $ F : \hat \D \to P \C $.
-To be more precise, $ \hat \D $ is the full subcategory of $ P \C $, which we get if we only select the presheaves $ F $ such that we can find some $ X : \C $ and some retraction $ (r, s) : F \triangleleft \yo(X) $.
-We again have an adjoint equivalence $ \bar \D \simeq \tilde \D $ and a fully faithful, essentially surjective functor $ F : \tilde \D \to \hat \D $.
-
-  However, in classical mathematics we have something even stronger: unlike in univalent foundations, we can use the axiom of choice to turn the weak equivalence into an adjoint equivalence $ F : \tilde \D \xrightarrow \sim \hat \D $, choosing an object $ X : \C $ and a retraction $ (r, s) : F \triangleleft \yo(X) $ for every $ F : \tilde \D $.
-This means that classically, the different definitions of the Karoubi envelope all coincide.
-\end{remark}
 
@@
   \[ b \cdot c = c \quad \text{and} \quad c \cdot c = b, \]
-  $ c $ is also an automorphism of $ b $. Therefore, $ \overline \C_M $ is not univalent.
-
-  In a somewhat more complicated way, we can show that $ \tilde \C_M $ is not univalent either: the counterpart of $ b $ in that category has two automorphisms, corresponding to $ b $ and $ c $, but only one equality, which is the identity.
-This is because isomorphisms only have to respect the presheaf structure, whereas equalities also have to respect the section (and retraction).
-Note that presheaves are univalent, so equality of presheaves is equivalent to isomorphism of presheaves.
-
-  Therefore, $ \overline \C $ and $ \tilde \C $ are usually more pathological than $ \C $ itself. On the other hand, since $ \hat \C $ is a full subcategory of $ P\C $, it is univalent.
+  $ c $ is also an automorphism of $ b $. Therefore, $ \overline \C_M $ is not univalent and $ \overline \C $ is usually more pathological than $ \C $ itself.
+\end{remark}
+
+\begin{remark}
+  We will also briefly study the identity types of $ \tilde \C $.
+Take $ P = (F_1, X_1, r_1, s_1) $ and $ Q = (F_2, X_2, r_2, s_2) $ as objects of $ \tilde \C $.
+The identity type $ P = Q $ is equivalent to
+  \[ \prod_{f : F_1 = F_2} \prod_{g: X_1 = X_2} r_1 \cdot \mathrm{idtoiso}(f) = \yo(\mathrm{idtoiso}(g)) \cdot r_2 \land s_1 \cdot \yo(\mathrm{idtoiso}(g)) = \mathrm{idtoiso}(f) \cdot s_2. \]
+  \begin{center}
+    \begin{tikzcd}
+      F_1 \arrow[d, "\mathrm{idtoiso}(f)"'] \arrow[r, "s_1", shift left] & \yo(X_1) \arrow[d, "\yo(\mathrm{idtoiso}(g))"] \arrow[l, "r_1", shift left] \\
+      F_2 \arrow[r, "s_2", shift left] & \yo(X_2) \arrow[l, "r_2", shift left]
+    \end{tikzcd}
+  \end{center}
+  Since $ P \C $ is univalent,
+  \[ f = \mathrm{isotoid}(\mathrm{idtoiso}(f)) = \mathrm{isotoid}(s_1 \cdot \yo(\mathrm{idtoiso}(g)) \cdot r_2). \]
+  Since morphisms in $ \C $ form a set, the identities on the $ r_i $ and $ s_i $ are mere propositions, and the only `structure' of the identity type is the equality $ X_1 = X_2 $.
+Therefore, if $ \C $ is a setcategory, $ \tilde \C $ is a setcategory as well.
+
+  Since $ \tilde \C $ has the same isomorphisms as $ \bar \C $, $ \tilde \C_M $ is not univalent for $ M $ as in the remark above.
 \end{remark}
@@
 \begin{remark}\label{rem:karoubi-candidate-choice}
-  As we saw in this section, there are multiple candidates for the `Karoubi envelope' of a category $ \C $: $ \bar \C $ (Definition \ref{def:karoubi}), $ \tilde \C $ (Definition \ref{def:karoubi'}) and $ \hat \C $ (Definition \ref{def:karoubi''}).
-In classical mathematics, these are all equivalent to each other (Remark \ref{rem:karoubi-classical}), but in univalent foundations $ \hat \C $ is usually not equivalent to $ \bar \C $ and $ \tilde \C $ (Corollary \ref{cor:karoubi-candidates}).
-
-  Therefore, we need to be careful which definition we choose, because this choice has consequences.
+  As mentioned in Remark \ref{rem:classical-karoubi-universal}, in univalent foundations, there are two different Karoubi envelopes: one that is a setcategory and one that is univalent.
+As we have seen above, if $ \C $ is a setcategory, both $ \bar \C $ and $ \tilde \C $ are setcategories, so they are the Karoubi envelopes in the theory of setcategories.
+Also, since $ \hat \C $ is univalent, it is the Karoubi envelope in the theory of univalent categories.
+
+  As mentioned before, in univalent foundations $ \hat \C $ is usually not equivalent to $ \bar \C $ and $ \tilde \C $ (Corollary \ref{cor:karoubi-candidates}), because they are the answer to different questions.
+In practice, we need to be careful which definition we choose, because this choice has consequences.
+
   On one hand, $ \hat \C $ is univalent, but very abstract.
 In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \hat \C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism.
+
   On the other hand, $ \overline \C $ and $ \tilde \C $ are very elementary and concrete, which sometimes helps when doing constructions.

### 2024-11-26 200-category-theory.tex
Minor improvements

@@
 Therefore, the properties in Remark \ref{rem:classical-karoubi-universal} characterize a classical category uniquely up to adjoint equivalence.
-However, in univalent foundations, categories have additional structure, which is given by identities between objects.
+However, in univalent foundations, categories have additional structure in the form of the identity types between objects.
 Therefore, there can be structurally different categories which satisfy this universal property and we need an additional constraint to single out the `right' one.
-However, there are actually two branches of category theory in univalent foundations, each giving its own constraint.
+In fact, there are two branches of category theory in univalent foundations, each giving its own constraint.
 
@@
 
-Note that there are two different ways to translate the definition at the end of Remark \ref{rem:classical-karoubi-universal} to univalent foundations.
+There are two different ways to translate the definition at the end of Remark \ref{rem:classical-karoubi-universal} to univalent foundations.
 We can either interpret the existence of the object $ X $ and the retraction $ (r, s) : F \triangleleft \yo(X) $ as additional \textit{structure} on $ F $, or we can treat it as a \textit{property} and ask for \textit{mere existence} (see Definition \ref{def:mere-existence}) of $ X $, $ r $ and $ s $.

### 2024-11-26 000-abstract.tex
Write an abstract

The $ \lambda $-calculus is a versatile tool both in mathematical logic and computer science. This thesis studies and expands upon Martin Hyland's paper `Classical lambda calculus in modern dress'. It gives examples for the definitions and provides more detailed proofs, as well as one new proof for Hyland's fundamental theorem of the $ \lambda $-calculus. It complements these definitions and proofs with material of previous authors by which Hyland has been inspired.
The thesis translates Hyland's paper from set theory with classical logic to univalent foundations, and showcases where subtleties arise in such a translation. In particular, it discusses the different implementations of the Karoubi envelope in univalent foundations.
Lastly, it discusses the accompanying formalization of parts of Hyland's paper, with in particular a tactic that was developed for applying $ \beta $-reduction and substitution to $ \lambda $-terms.

### 2024-11-27 200-category-theory.tex
Fix a mistake about whether R tilde is a setcategory

@@
 
-\begin{remark}
 We will also briefly study the identity types of $ \tilde \C $.
-Take $ P = (F_1, X_1, r_1, s_1) $ and $ Q = (F_2, X_2, r_2, s_2) $ as objects of $ \tilde \C $.
-The identity type $ P = Q $ is equivalent to
+\begin{lemma}\label{lem:isaset-karoubi'}
+  If $ \C $ is a setcategory, $ \tilde \C $ is a setcategory as well.
+\end{lemma}
+\begin{proof}
+  Take $ P = (F_1, X_1, r_1, s_1) $ and $ Q = (F_2, X_2, r_2, s_2) $ as objects of $ \tilde \C $. The identity type $ P = Q $ is equivalent to
   \[ \prod_{f : F_1 = F_2} \prod_{g: X_1 = X_2} r_1 \cdot \mathrm{idtoiso}(f) = \yo(\mathrm{idtoiso}(g)) \cdot r_2 \land s_1 \cdot \yo(\mathrm{idtoiso}(g)) = \mathrm{idtoiso}(f) \cdot s_2. \]
@@
 Therefore, if $ \C $ is a setcategory, $ \tilde \C $ is a setcategory as well.
-
-  Since $ \tilde \C $ has the same isomorphisms as $ \bar \C $, $ \tilde \C_M $ is not univalent for $ M $ as in the remark above.
-\end{remark}
+\end{proof}
+Since $ \tilde \C $ has the same isomorphisms as $ \bar \C $, $ \tilde \C_M $ is not univalent for $ M $ as in Remark \ref{rem:karoubi-not-univalent}.
 

### 2024-11-27 600-paper.tex
Fix a mistake about whether R tilde is a setcategory

@@
   Therefore, this only works in $ \hat \R \simeq \hat C_{L_0} $.
-Suppose that we tried to do this in $ \tilde C_{L_0} $.
+Suppose that we tried to do this in $ \tilde \R = \tilde C_{L_0} $.
 Note that this category is equivalent to the category with as objects $ X : \Pshf L $, together with some $ (r, s) : X \triangleleft L $.
@@
 To define a pullback, we would need to explicitly construct some retraction $ g^* Y \triangleleft L $, for which we would need a retraction $ Z \triangleleft L $.
-However, we have only mere existence of this retraction, so we would only be able to show mere existence of pullbacks, like in Taylor's proof.
-In Taylor's case, we were able to use the axiom of choice because the objects of $ \R $ form a set.
-However, the objects of $ \tilde \R $ do not form a set, and so we cannot use the axiom of choice here (Lemma 3.8.5 in \autocite{hottbook} shows why the axiom of choice only works for sets).
-
-  Since we have an adjoint equivalence between $ \tilde C_{L_0} $ and $ \overline C_{L_0} = \R $, and since any reasoning about $ \R $ using presheaves would use this equivalence, we would run into the same problems if we tried try to apply Hyland's approach to $ \R $.
-However, note that there we might be able to use the axiom of choice to show mere existence of a pullback functor, like in Taylor's proof.
+However, we have only mere existence of the latter, so we would only be able to show mere existence of pullbacks, like in Taylor's proof.
+For $ \R $, we would be able to use the adjoint equivalence between $ \R $ and $ \tilde \R $ to apply Hyland's reasoning with presheaves to $ \R $.
+Since $ C_{L_0} $ is a setcategory, $ \R $ and $ \tilde \R $ are also setcategories (Lemma \ref{lem:isaset-karoubi'}), so we can use the axiom of choice to show the existence of a pullback functor.
+However, this approach still gives only mere existence.
 \end{remark}

### 2024-12-09 010-preface.tex
Add a preface

\chapter{\label{chap:Preface}Preface}
\addcontentsline{toc}{subsection}{Preface}

With this 136-page document, I will finally complete my second (and hopefully last) master's degree. It took me almost 23 months to complete it, during which some parts of my life changed profoundly. Along the way, many people witnessed this journey, and I would like to name a couple of them.

I would like to thank my parents and my friends, who showed an interest in my thesis topic, and who listened to my long stories about what my thesis was really about.
Maarten \& Maarten, thank you for proofreading the final draft.

I want to thank Niels van der Weide for his help with my code. Niels, you were almost always the first person to answer my messages for help. More than once, you took the time to experiment with my code, to see why it did not work and to work out a solution.

Kobe, thank you for always making time to take a look at the material I was working on, to talk about the things that I got stuck on, or to explain a concept that I struggled to grasp.

Benedikt, thank you for your supervision, your enthousiasm, your ideas, and for involving me in the scientific community via DutchCats and via the Cortona summer school. Thank you for the freedom you gave me in this project, and your patience when I took a bit longer than anticipated.

Elise, my wonderful wife, thank you for listening to my rants about the things that I figured out, or the things that I had trouble figuring out. Thank you for your patience when graduating---{}and by extension, starting to earn an income---{}took a bit longer than we initially planned. Thank you for support me through all this, and for being my buddy.

Finally, and most importantly, I would like to thank the Almighty God, without whom neiter I nor this thesis would not be here. He has blessed me with both the financial and mental means to study, as well as the inspiration for solutions whenever I felt stuck.

\newpage

\thispagestyle{empty}

\vspace*{\fill}
\begin{center}
    Soli Deo gloria
\end{center}
\vspace*{\fill}

### 2024-12-09 200-category-theory.tex
Improve notation and wording

--- 2024-11-26 200-category-theory.tex
@@
 \begin{definition}
-  A morphism $ f: \E(Y, Z) $ is called \iindex{cartesian} if for all $ g: \E(X, Z) $ and $ h: \B(P(X), P(Y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \bar h: \E(X, Y) $ such that $ P(\bar h) = h $ and $ \bar h \cdot f = g $, like illustrated in the following diagram from \autocite{nlab:grothendieck_fibration}
+  A morphism $ f: \E(Y, Z) $ is called \iindex{cartesian} if for all $ g: \E(X, Z) $ and $ h: \B(P(X), P(Y)) $ with $ h \cdot P(f) = P(g) $, there exists $ \overline h: \E(X, Y) $ such that $ P(\overline h) = h $ and $ \overline h \cdot f = g $, like illustrated in the following diagram from \autocite{nlab:grothendieck_fibration}
   \begin{center}
     \begin{tikzcd}[sep=large]
-      \E \arrow[d, "P"] &X \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \bar h"', dashed] & Y \arrow[r, "f"'] & Z\\
+      \E \arrow[d, "P"] &X \arrow[rr, "\forall g", bend left] \arrow[r, "\exists! \overline h"', dashed] & Y \arrow[r, "f"'] & Z\\
       \B & P(X) \arrow[r, "\forall h"'] \arrow[rr, "P(g)", bend left] & P(Y) \arrow[r, "P(f)"'] & P(Z)
@@
 \begin{definition}
-  $ P $ is a \iindex{fibration} if for all $ Y: \E $ and morphisms $ f: \B(X, P(Y)) $, there exist an object $ \bar X: \E $ and a cartesian morphism $ \bar f: \E(\bar X, Y) $ such that $ P(\bar X) = X $ and $ P(\bar f) = f $:
-  \begin{center}
-    \begin{tikzcd}
-      \E \arrow[d, "P"] & \bar X \arrow[r, "\exists \bar f", dashed] & Y\\
+  $ P $ is a \iindex{fibration} if for all $ Y: \E $ and morphisms $ f: \B(X, P(Y)) $, there exist an object $ \overline X: \E $ and a cartesian morphism $ \overline f: \E(\overline X, Y) $ such that $ P(\overline X) = X $ and $ P(\overline f) = f $:
+  \begin{center}
+    \begin{tikzcd}
+      \E \arrow[d, "P"] & \overline X \arrow[r, "\exists \overline f", dashed] & Y\\
       \B & X \arrow[r, "\forall f"] & P(Y)
@@
   \[ \D(W, Y) \cong \{ f: \D(Z, Y) \mid a \cdot f = f \} \cong \{ f: \D(Z, X) \mid a \cdot f = f = f \cdot b \}, \]
-  which exactly describes the morphisms in $ \bar C $.
+  which exactly describes the morphisms in $ \overline C $.
   \begin{center}
@@
   \begin{itemize}
-    \item In $ \bar \C $, every idempotent splits.
-    \item We have a fully faithful embedding $ \iota_\C : \C \to \bar \C $;
-    \item Every object in $ \bar \C $ is a retract of an object in $ \C $.
+    \item In $ \overline \C $, every idempotent splits.
+    \item We have a fully faithful embedding $ \iota_\C : \C \to \overline \C $;
+    \item Every object in $ \overline \C $ is a retract of an object in $ \C $.
   \end{itemize}
@@
 An object in this alternative category is a presheaf $ F : P\C $ that is a retract of the Yoneda embedding $ \yo(X) $ of an object $ X : \C $.
-Because it satisfies the universal property, it is classically equivalent to $ \bar \C $.
+Because it satisfies the universal property, it is classically equivalent to $ \overline \C $.
 \end{remark}
@@
 \begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope'}]\label{def:karoubi'}
-  We define the category $ \tilde \C $ in which every object is a presheaf $ F : P \C $, together with an object $ X : \C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo (X) $.
+  We define the category $ \widetilde \C $ in which every object is a presheaf $ F : P \C $, together with an object $ X : \C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo (X) $.
 The morphisms from $ (F_1, X_1, r_1, s_1) $ to $ (F_2, X_2, r_2, s_2) $ are just the presheaf morphisms $ f: P\C(F_1, F_2) $.
@@
 \begin{definition}\label{def:karoubi''}
-  We define the category $ \hat \C $ as the full subcategory of $ P \C $ consisting of objects $ F : P \C $ such that there merely exist an object $ X: \C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo(X) $, summarized in the following diagram:
+  We define the category $ \widehat \C $ as the full subcategory of $ P \C $ consisting of objects $ F : P \C $ such that there merely exist an object $ X: \C $ and a retraction-section pair $ (r, s) : F \triangleleft \yo(X) $, summarized in the following diagram:
   \begin{center}
@@
 \end{definition}
-Because it is a full subcategory of a presheaf category (which is univalent), $ \hat \C $ is univalent.
-
-Now classically, $ \bar \C $ is equivalent to $ \tilde \C $ or $ \hat \C $. In general, this does not work for $ \hat \C $, but it does work for $ \tilde \C $:
+Because it is a full subcategory of a presheaf category (which is univalent), $ \widehat \C $ is univalent.
+
+Now classically, $ \overline \C $ is equivalent to $ \widetilde \C $ or $ \widehat \C $. In general, this does not work for $ \widehat \C $, but it does work for $ \widetilde \C $:
 \begin{lemma}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_equivalence}]\label{lem:karoubi-equivalence}
-  We have an adjoint equivalence $ \overline \C \xrightarrow \sim \tilde \C $.
+  We have an adjoint equivalence $ \overline \C \xrightarrow \sim \widetilde \C $.
 \end{lemma}
@@
   \[ s_1 \cdot \yo(g) \cdot r_2 : P\C(F_1, F_2). \]
-  Note that this is an equivalence on the morphisms: For any morphism $ \bar g : P\C(F_1, F_2) $, we have
-  \[ r_1 \cdot \bar g \cdot s_2 : P\C(\yo(X_1), \yo(X_2)). \]
+  Note that this is an equivalence on the morphisms: For any morphism $ \overline g : P\C(F_1, F_2) $, we have
+  \[ r_1 \cdot \overline g \cdot s_2 : P\C(\yo(X_1), \yo(X_2)). \]
   By the fully faithfulness of the Yoneda lemma, this corresponds to a morphism $ g : \C(X_1, X_2) $ and we can show that these two maps between $ \C((X_1, f_1), (X_2, f_2)) $ and $ \overline \C(F_1, F_2) $ are inverses of each other.
@@
     \begin{tikzcd}
-      F_1 \arrow[r, shift left, "s_1"] \arrow[d, "\bar g"] & \yo(X_1) \arrow[l, shift left, "r_1"] \arrow[r, shift left, "\id{\yo(X_1)}"] \arrow[r, shift right, "\yo(f_1)"'] \arrow[d, "\yo(g)"] & \yo(X_1)\\
+      F_1 \arrow[r, shift left, "s_1"] \arrow[d, "\overline g"] & \yo(X_1) \arrow[l, shift left, "r_1"] \arrow[r, shift left, "\id{\yo(X_1)}"] \arrow[r, shift right, "\yo(f_1)"'] \arrow[d, "\yo(g)"] & \yo(X_1)\\
       F_2 \arrow[r, shift left, "s_2"] & \yo(X_2) \arrow[l, shift left, "r_2"] \arrow[r, shift left, "\id{\yo(X_2)}"] \arrow[r, shift right, "\yo(f_2)"'] & \yo(X_2)\\
@@
   Now, note that this map is also split essentially surjective.
-For some $ (F, X, r, s) : \tilde \C $, $ r \cdot s $ is an idempotent morphism on $ \yo(X) $, and by fully faithfulness of the Yoneda Lemma, it corresponds to an idempotent morphism $ f $ on $ X $.
+For some $ (F, X, r, s) : \widetilde \C $, $ r \cdot s $ is an idempotent morphism on $ \yo(X) $, and by fully faithfulness of the Yoneda Lemma, it corresponds to an idempotent morphism $ f $ on $ X $.
 We send $ (F, X, r, s) $ to $ (X, f) $.
@@
 \begin{remark}
-  Note that since the morphism types of $ \tilde \C $ and $ \hat \C $ are the same, and since the objects of $ \hat \C $ are just truncated versions of the objects in $ \tilde \C $, we have a fully faithful embedding
-  \[ \tilde \C \hookrightarrow \hat \C, \]
+  Note that since the morphism types of $ \widetilde \C $ and $ \widehat \C $ are the same, and since the objects of $ \widehat \C $ are just truncated versions of the objects in $ \widetilde \C $, we have a fully faithful embedding
+  \[ \widetilde \C \hookrightarrow \widehat \C, \]
   which just forgets the choices for $ X $, $ r $ and $ s $ on the objects.
-Note that this is also essentially surjective: by definition, for any $ (F, H) : \hat \C $, there merely exist $ X $, $ r $ and $ s $ such that $ (X, r, s) $ truncates to $ H $.
-  Therefore, we have a weak equivalence from $ \tilde \C $ to $ \hat \C $. However, as we will see, $ \tilde \C $ is usually not univalent, so this does not give an adjoint equivalence of categories.
+Note that this is also essentially surjective: by definition, for any $ (F, H) : \widehat \C $, there merely exist $ X $, $ r $ and $ s $ such that $ (X, r, s) $ truncates to $ H $.
+  Therefore, we have a weak equivalence from $ \widetilde \C $ to $ \widehat \C $.
+However, as we will see, $ \widetilde \C $ is usually not univalent, so this does not give an adjoint equivalence of categories.
 \end{remark}
@@
     \begin{tikzcd}
-      \C \arrow[r, hook, "\iota_\C"] & \overline \C \arrow[r, "\sim"] & \tilde \C \arrow[r, hook, two heads] & \hat \C \arrow[r, phantom, "\subseteq"] & P\C
-    \end{tikzcd}
-  \end{center}
-  The fact that $ \hat \C $ is univalent, and has weak equivalences from $ \overline \C $ and $ \tilde \C $ exhibits $ \hat \C $ as the Rezk completion of $ \overline \C $ and $ \tilde \C $.
+      \C \arrow[r, hook, "\iota_\C"] & \overline \C \arrow[r, "\sim"] & \widetilde \C \arrow[r, hook, two heads] & \widehat \C \arrow[r, phantom, "\subseteq"] & P\C
+    \end{tikzcd}
+  \end{center}
+  The fact that $ \widehat \C $ is univalent, and has weak equivalences from $ \overline \C $ and $ \widetilde \C $ exhibits $ \widehat \C $ as the Rezk completion of $ \overline \C $ and $ \widetilde \C $.
 \end{corollary}
@@
 
-\begin{remark}
-  We will also briefly study the identity types of $ \tilde \C $.
-Take $ P = (F_1, X_1, r_1, s_1) $ and $ Q = (F_2, X_2, r_2, s_2) $ as objects of $ \tilde \C $.
-The identity type $ P = Q $ is equivalent to
+We will also briefly study the identity types of $ \widetilde \C $.
+\begin{lemma}\label{lem:isaset-karoubi'}
+  If $ \C $ is a setcategory, $ \widetilde \C $ is a setcategory as well.
+\end{lemma}
+\begin{proof}
+  Take $ P = (F_1, X_1, r_1, s_1) $ and $ Q = (F_2, X_2, r_2, s_2) $ as objects of $ \widetilde \C $. The identity type $ P = Q $ is equivalent to
   \[ \prod_{f : F_1 = F_2} \prod_{g: X_1 = X_2} r_1 \cdot \mathrm{idtoiso}(f) = \yo(\mathrm{idtoiso}(g)) \cdot r_2 \land s_1 \cdot \yo(\mathrm{idtoiso}(g)) = \mathrm{idtoiso}(f) \cdot s_2. \]
@@
   Since morphisms in $ \C $ form a set, the identities on the $ r_i $ and $ s_i $ are mere propositions, and the only `structure' of the identity type is the equality $ X_1 = X_2 $.
-Therefore, if $ \C $ is a setcategory, $ \tilde \C $ is a setcategory as well.
-
-  Since $ \tilde \C $ has the same isomorphisms as $ \bar \C $, $ \tilde \C_M $ is not univalent for $ M $ as in the remark above.
-\end{remark}
+Therefore, if $ \C $ is a setcategory, $ \widetilde \C $ is a setcategory as well.
+\end{proof}
+Since $ \widetilde \C $ has the same isomorphisms as $ \overline \C $, $ \widetilde \C_M $ is not univalent for $ M $ as in Remark \ref{rem:karoubi-not-univalent}.
 
@@
   As mentioned in Remark \ref{rem:classical-karoubi-universal}, in univalent foundations, there are two different Karoubi envelopes: one that is a setcategory and one that is univalent.
-As we have seen above, if $ \C $ is a setcategory, both $ \bar \C $ and $ \tilde \C $ are setcategories, so they are the Karoubi envelopes in the theory of setcategories.
-Also, since $ \hat \C $ is univalent, it is the Karoubi envelope in the theory of univalent categories.
-
-  As mentioned before, in univalent foundations $ \hat \C $ is usually not equivalent to $ \bar \C $ and $ \tilde \C $ (Corollary \ref{cor:karoubi-candidates}), because they are the answer to different questions.
+As we have seen above, if $ \C $ is a setcategory, both $ \overline \C $ and $ \widetilde \C $ are setcategories, so they are the Karoubi envelopes in the theory of setcategories.
+Also, since $ \widehat \C $ is univalent, it is the Karoubi envelope in the theory of univalent categories.
+
+  As mentioned before, in univalent foundations $ \widehat \C $ is usually not equivalent to $ \overline \C $ and $ \widetilde \C $ (Corollary \ref{cor:karoubi-candidates}), because they are the answer to different questions.
 In practice, we need to be careful which definition we choose, because this choice has consequences.
 
-  On one hand, $ \hat \C $ is univalent, but very abstract.
-In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \hat \C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism.
-
-  On the other hand, $ \overline \C $ and $ \tilde \C $ are very elementary and concrete, which sometimes helps when doing constructions.
+  On one hand, $ \widehat \C $ is univalent, but very abstract.
+In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \widehat \C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism.
+
+  On the other hand, $ \overline \C $ and $ \widetilde \C $ are very elementary and concrete, which sometimes helps when doing constructions.
 However, they are not univalent, which makes working with them complicated in a different way.

### 2024-12-09 300-univalent-foundations.tex
Improve notation and wording

@@
 We construct this function using path induction with the identity equivalence $ \prod_S \id S: (S \simeq S) $.
-More generally, for a category $ C $, if we denote the type of isomorphisms between objects $ c $ and $ d $ with $ c \cong d $, we can construct a function
-\[ \mathrm{idtoiso}: \prod_{X, Y: C} (X = Y) \to (X \cong Y), \]
-using path induction with the identity isomorphism $ \prod_{X: C} \id X: (X \cong X) $.
+More generally, for a category $ \C $, if we denote the type of isomorphisms between objects $ c $ and $ d $ with $ c \cong d $, we can construct a function
+\[ \mathrm{idtoiso}: \prod_{X, Y: \C} (X = Y) \to (X \cong Y), \]
+using path induction with the identity isomorphism $ \prod_{X: \C} \id X: (X \cong X) $.
 If $ X $ and $ Y $ are sets, then $ \mathrm{idtoequiv} $ and $ \mathrm{idtoiso} $ coincide.
@@
 
-\enquote{For all $ c, d : C $, $ \mathrm{idtoiso}_{c, d}: (c = d) \to (c \cong d) $ is an equivalence.}
+\enquote{For all $ c, d : \C $, $ \mathrm{idtoiso}_{c, d}: (c = d) \to (c \cong d) $ is an equivalence.}
 
@@
 
-Note that if $ B $ is a univalent category and $ A $ is any category, the functor category $ [A, B] = B^A $ is univalent as well.
-In particular, the presheaf category $ P A = [\op A, \SET] $ is univalent.
+Note that if $ \B $ is a univalent category and $ \A $ is any category, the functor category $ [\A, \B] = \B^\A $ is univalent as well \autocite[][Theorem 4.5]{univalent-categories}.
+In particular, the presheaf category $ P \A = [\op \A, \SET] $ is univalent.
 
-Also, if $ A $ is univalent, any full subcategory $ B \subseteq A $ is also univalent, because isomorphisms and equalities of objects in $ B $ can be shown to be the `the same' as their isomorphisms and equalities in $ A $.
+Also, if $ \A $ is univalent, any full subcategory $ \B \subseteq \A $ is also univalent, because isomorphisms and equalities of objects in $ B $ can be shown to be the `the same' as their isomorphisms and equalities in $ A $.
 
 \begin{lemma}
-  For every category $ C $, there exists a univalent category $ D $ with a weak equivalence
-  \[ \iota: C \hookrightarrow D. \]
+  For every category $ \C $, there exists a univalent category $ \D $ with a weak equivalence
+  \[ \iota: \C \hookrightarrow \D. \]
 \end{lemma}
 \begin{proof}
-  One construction takes $ D $ to be the full subcategory of the presheaf category $ PC $ of objects that are isomorphic (there \textit{merely exists} an isomorphism) to the Yoneda embedding $ \yo(X) $ of some object $ X : C $ \autocite[][Theorem 8.5]{univalent-categories}.
+  One construction takes $ \D $ to be the full subcategory of the presheaf category $ P \C $ of objects that are isomorphic (there \textit{merely exists} an isomorphism) to the Yoneda embedding $ \yo(X) $ of some object $ X : \C $ \autocite[][Theorem 8.5]{univalent-categories}.
 \end{proof}
-We call such a univalent category a \iindex{Rezk completion} of $ C $. Actually, we can call it \textit{the} Rezk completion:
+We call such a univalent category a \iindex{Rezk completion} of $ \C $. Actually, we can call it \textit{the} Rezk completion:
 \begin{lemma}[\coqident{Bicategories.RezkCompletions.Uniqueness}{rezk_completion_unique}]
@@
 \begin{proof}
-  Precomposition with the weak equivalence $ \iota: C \hookrightarrow D $ gives an adjoint equivalence on the functor categories $ [D, E] \simeq [C, E] $ for any univalent category $ E $.
-From this, it follows that $ \iota $ is the ``initial functor'' from $ C $: any functor from $ C $ to a univalent category factors uniquely through $ \iota $.
+  Precomposition with the weak equivalence $ \iota: \C \hookrightarrow \D $ gives an adjoint equivalence on the functor categories $ [\D, \E] \simeq [\C, \E] $ for any univalent category $ \E $.
+From this, it follows that $ \iota $ is the ``initial functor'' from $ \C $: any functor from $ \C $ to a univalent category factors uniquely through $ \iota $.
 
-  Now, two initial functors $ F : C \to D $ and $ F^\prime : C \to D^\prime $ factor uniquely through each other:
+  Now, two initial functors $ F : \C \to \D $ and $ F^\prime : \C \to \D^\prime $ factor uniquely through each other:
   \[ F^\prime = F \bullet G \quad \text{and} \quad F = F^\prime \bullet G^\prime \]
   for two functors $ G $ and $ G^\prime $ and since $ F $ and $ F^\prime $ also factor uniquely through themselves, we have
-  \[ G \bullet G^\prime = \id D \quad \text{and} \quad G^\prime \bullet G = \id{D^\prime}. \]
-  From this, we can construct an equivalence $ D \simeq D^\prime $.
-Since $ D $ and $ D^\prime $ are univalent, this equivalence gives an equality of categories, and because $ F \bullet G = F^\prime $, we have an equality of pairs
-  \[ (D, F) = (D^\prime, F^\prime). \]
+  \[ G \bullet G^\prime = \id \D \quad \text{and} \quad G^\prime \bullet G = \id{\D^\prime}. \]
+  From this, we can construct an equivalence $ \D \simeq \D^\prime $.
+Since $ \D $ and $ \D^\prime $ are univalent, this equivalence gives an equality of categories, and because $ F \bullet G = F^\prime $, we have an equality of pairs
+  \[ (\D, F) = (\D^\prime, F^\prime). \]
 \end{proof}
@@
 
-Also, Theorem 4.5 in \autocite{univalent-categories} shows that if a category $ B $ is univalent (in the paper, categories are called `precategories` and univalent categories are just called `categories'), then the functor category $ A \rightarrow B $ is also univalent.
-In particular, the category of (pre)sheaves $ A \to \SET $ is univalent.
-
 Therefore, the univalence axiom is a very powerful axiom, and we usually do not need to assume additional axioms to show that more categories satisfy the univalence principle.
@@
 However, we will restrict our attention to the sub-2-category of univalent categories, which are the `well-behaved' categories in some sense.
-Then Theorem 6.8 in \autocite{univalent-categories} shows that for univalent categories $ C $ and $ D $, there is an equivalence between $ C = D $ and $ C \simeq D $, where $ C \simeq D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
+Then Theorem 6.8 in \autocite{univalent-categories} shows that for univalent categories $ \C $ and $ \D $, there is an equivalence between $ \C = \D $ and $ \C \simeq \D $, where $ \C \simeq \D $ denotes the type of (adjoint) equivalences of categories (see Definition \ref{def:equivalence-of-categories}).
 

### 2024-12-09 400-algebraic-structures.tex
Improve notation and wording

@@
     \begin{tikzcd}
-      \Alg T(T_n, A) \arrow[r, "f^*"] \arrow[d, "\sim"] & \Alg{T^\prime}(f^* T_n, f^* A) \arrow[d, "\bar f_n \cdot -"]\\
+      \Alg T(T_n, A) \arrow[r, "f^*"] \arrow[d, "\sim"] & \Alg{T^\prime}(f^* T_n, f^* A) \arrow[d, "\overline f_n \cdot -"]\\
       A^n \arrow[r, "\sim"] & \Alg{T^\prime}(T^\prime_n, f^* A)
@@
   % \]
-  with $ \bar f_n: T^\prime_n \to f^* T_n $ the $ T^\prime $-algebra morphism with underlying function $ f_n $.
-Note that $ f^* $ is fully faithful, so the function at the top of the diagram is a bijection, and so precomposition by $ \bar f_n $ is a bijection as well.
+  with $ \overline f_n: T^\prime_n \to f^* T_n $ the $ T^\prime $-algebra morphism with underlying function $ f_n $.
+Note that $ f^* $ is fully faithful, so the function at the top of the diagram is a bijection, and so precomposition by $ \overline f_n $ is a bijection as well.
 Since $ f^* $ is essentially surjective, we have for all $ A : \Alg T^\prime $, some $ B : \Alg T $ and an isomorphism $ h: f^* B \xrightarrow \sim A $, which gives the following commutative diagram:
@@
     \begin{tikzcd}
-      \Alg{T^\prime}(f^* T_n, f^* B) \arrow[d, "\bar f_n \cdot -", "\sim"'] \arrow[r, "- \cdot h"', "\sim"] & \Alg{T^\prime}(f^* T_n, A) \arrow[d, "\bar f_n \cdot -"]\\
+      \Alg{T^\prime}(f^* T_n, f^* B) \arrow[d, "\overline f_n \cdot -", "\sim"'] \arrow[r, "- \cdot h"', "\sim"] & \Alg{T^\prime}(f^* T_n, A) \arrow[d, "\overline f_n \cdot -"]\\
       \Alg{T^\prime}(T^\prime_n, f^* B) \arrow[r, "- \cdot h"', "\sim"] & \Alg{T^\prime}(T^\prime_n, A)
@@
   so the arrow on the right is an equivalence as well.
-Taking $ A = T^\prime_n $, there exists some $ g: \Alg{T^\prime}(f^* T_n, T^\prime_n) $ such that $ \bar f_n \cdot g = \id{T^\prime_n} $.
+Taking $ A = T^\prime_n $, there exists some $ g: \Alg{T^\prime}(f^* T_n, T^\prime_n) $ such that $ \overline f_n \cdot g = \id{T^\prime_n} $.
 Also, note that
-  \[ \bar f_n \cdot g \cdot \bar f_n = \bar f_n \cdot \id{f^* T_n} \]
+  \[ \overline f_n \cdot g \cdot \overline f_n = \overline f_n \cdot \id{f^* T_n} \]
   so taking $ A = f^* T_n $, we see that
-  \[ g \cdot \bar f_n = \id{f^* T_n}, \]
-  so $ f_n $, the underlying function of $ \bar f_n $, is a bijection, with inverse $ g $.
+  \[ g \cdot \overline f_n = \id{f^* T_n}, \]
+  so $ f_n $, the underlying function of $ \overline f_n $, is a bijection, with inverse $ g $.
 \end{proof}
@@
   Hyland's proof of this fact is almost the same, but in the last part, he uses some category theory. Instead of explicitly constructing the inverse, he notices that the bijection
-  \[ \Alg{T^\prime}(f^* T_n, A) \xrightarrow[\bar f_n \cdot -] \sim \Alg{T^\prime}(T^\prime_n, A) \]
-  is in fact the image of $ \op{\bar f_n} $ under the Yoneda embedding of $ \op{\Alg{T^\prime}} $ (or of $ \bar f_n $ under the covariant Yoneda embedding of $ \Alg{T^\prime} $) into the functor category $ \Alg{T^\prime} \to \SET $:
-  \[ \yo(\bar f_n): \yo(f^* T_n) \to \yo(T^\prime_n). \]
-  Since the Yoneda embedding is fully faithful, this shows that $ \bar f_n $ is an isomorphism of $ T^\prime $-algebras, so in particular, it is a bijection.
+  \[ \Alg{T^\prime}(f^* T_n, A) \xrightarrow[\overline f_n \cdot -] \sim \Alg{T^\prime}(T^\prime_n, A) \]
+  is in fact the image of $ \op{\overline f_n} $ under the Yoneda embedding of $ \op{\Alg{T^\prime}} $ (or of $ \overline f_n $ under the covariant Yoneda embedding of $ \Alg{T^\prime} $) into the functor category $ \Alg{T^\prime} \to \SET $:
+  \[ \yo(\overline f_n): \yo(f^* T_n) \to \yo(T^\prime_n). \]
+  Since the Yoneda embedding is fully faithful, this shows that $ \overline f_n $ is an isomorphism of $ T^\prime $-algebras, so in particular, it is a bijection.
 \end{remark}
@@
 
-\begin{lemma}[\coqident{AlgebraicTheories.RepresentationTheorem}{theory_presheaf_exponentiable}]
+\begin{lemma}[\coqident{AlgebraicTheories.RepresentationTheorem}{theory_presheaf_exponentiable}]\label{lem:plus-p-presheaf}
   For all $ p $ and all $ T $-presheaves $ Q $, $ A(Q, p) $ is the exponential object $ Q^{T^p} $.
@@
   Now, given a $ T $-presheaf $ Q^\prime $ and a morphism $ \psi: Q^\prime \times T^p \to Q $.
-Define $ \tilde \psi: Q^\prime_n \to A(Q, p)_n $ by $ \tilde \psi(q) = \psi(\iota_{n, p}(q), (x_{n + i})_i) $.
+Define $ \widetilde \psi: Q^\prime_n \to A(Q, p)_n $ by $ \widetilde \psi(q) = \psi(\iota_{n, p}(q), (x_{n + i})_i) $.
 
-  Then $ \psi $ factors as $ (\tilde \psi \times \id{T^p}) \cdot \varphi $.
-Also, some equational reasoning shows that $ \tilde \psi $ is unique, which proves that $ \varphi $ indeed is a universal arrow.
+  Then $ \psi $ factors as $ (\widetilde \psi \times \id{T^p}) \cdot \varphi $.
+Also, some equational reasoning shows that $ \widetilde \psi $ is unique, which proves that $ \varphi $ indeed is a universal arrow.
 \end{proof}

### 2024-12-09 500-previous-work.tex
Improve notation and wording

@@
     \begin{tikzcd}
-      Z \circ \alpha \arrow[rd, "f"'] \arrow[r, "{\hat f \circ \alpha}", dashed] & (\alpha_* Y) \circ \alpha \arrow[d, "{\epsilon_Y}"]\\
+      Z \circ \alpha \arrow[rd, "f"'] \arrow[r, "{\widehat f \circ \alpha}", dashed] & (\alpha_* Y) \circ \alpha \arrow[d, "{\epsilon_Y}"]\\
       & Y
@@
   Now, suppose that we have some $ Z : \R^A $ and some $ f: \R^B(Z \circ \alpha, Y) $. We define
-  \[ \hat f = \lambda x_1 x_2 x_3, f(g^{-1}(x_1, x_3)) (Z x_1 x_2): \R^A(Z, \alpha_* Y) \]
-  and we have $ ((\hat f) \circ \alpha) \cdot \epsilon_Y = f $.
+  \[ \widehat f = \lambda x_1 x_2 x_3, f(g^{-1}(x_1, x_3)) (Z x_1 x_2): \R^A(Z, \alpha_* Y) \]
+  and we have $ ((\widehat f) \circ \alpha) \cdot \epsilon_Y = f $.
   % \begin{align*}
-  %   (((\alpha \cdot -) \hat f) \cdot \epsilon_Y) b z
-  %   &= \epsilon_Y b ((\hat f (\alpha b)) z)\\
+  %   (((\alpha \cdot -) \widehat f) \cdot \epsilon_Y) b z
+  %   &= \epsilon_Y b ((\widehat f (\alpha b)) z)\\
   %   &= \epsilon_Y b (\lambda x_3, f (g^{-1} ((\alpha b), x_3)) (Z (\alpha b) z))\\
@@
   % \end{align*}
-  Now, suppose that we have some (other) $ \hat f^\prime : \R^A(Z, \alpha_*(Y)) $ such that $ (\hat f^\prime \circ \alpha) \cdot \epsilon_Y = f $.
-Then substituting $ (\hat f^\prime \circ \alpha) \cdot \epsilon_Y $ for $ f $ in $ \hat f $ yields
-  \[ \hat f = \lambda x_1, (\alpha_* Y x_1) \circ (\hat f^\prime x_1) = \hat f^\prime, \]
-  so $ \hat f $ is unique and $ (\alpha_* Y, \epsilon_Y) $ is a universal arrow, which concludes the proof that $ (\alpha \cdot -) \dashv \alpha_* $ and we see that $ \R $ is cartesian closed relative to the given class of display maps.
+  Now, suppose that we have some (other) $ \widehat f^\prime : \R^A(Z, \alpha_*(Y)) $ such that $ (\widehat f^\prime \circ \alpha) \cdot \epsilon_Y = f $.
+Then substituting $ (\widehat f^\prime \circ \alpha) \cdot \epsilon_Y $ for $ f $ in $ \widehat f $ yields
+  \[ \widehat f = \lambda x_1, (\alpha_* Y x_1) \circ (\widehat f^\prime x_1) = \widehat f^\prime, \]
+  so $ \widehat f $ is unique and $ (\alpha_* Y, \epsilon_Y) $ is a universal arrow, which concludes the proof that $ (\alpha \cdot -) \dashv \alpha_* $ and we see that $ \R $ is cartesian closed relative to the given class of display maps.
   % \begin{align*}
-  %   \hat f
+  %   \widehat f
   %   &= \lambda x_1 x_2 x_3, f (g^{-1} (x_1, x_3))(Z x_1 x_2)\\
-  %   &= \lambda x_1 x_2 x_3, ((\epsilon_Y (g^{-1} (x_1, x_3))) \circ ((\hat f^\prime \circ \alpha) (g^{-1} (x_1, x_3)))) (Z x_1 x_2)\\
-  %   &= \lambda x_1 x_2 x_3, (\epsilon_Y (g^{-1} (x_1, x_3))) (\hat f^\prime (\alpha (g^{-1} (x_1, x_3))) (Z x_1 x_2))\\
-  %   &= \lambda x_1 x_2 x_3, (\epsilon_Y (g^{-1} (x_1, x_3))) (\hat f^\prime x_1 x_2)\\
-  %   &= \lambda x_1 x_2 x_3, Y (g^{-1} (x_1, x_3)) (\hat f^\prime x_1 x_2 (\pi_2 (g (g^{-1} (x_1, x_3)))))\\
-  %   &= \lambda x_1 x_2 x_3, Y (g^{-1} (x_1, x_3)) (\hat f^\prime x_1 x_2 (X x_1 x_3))\\
-  %   &= \lambda x_1 x_2, \alpha_* Y x_1 (\hat f^\prime x_1 (Z x_1 x_2))\\
-  %   &= \hat f^\prime
+  %   &= \lambda x_1 x_2 x_3, ((\epsilon_Y (g^{-1} (x_1, x_3))) \circ ((\widehat f^\prime \circ \alpha) (g^{-1} (x_1, x_3)))) (Z x_1 x_2)\\
+  %   &= \lambda x_1 x_2 x_3, (\epsilon_Y (g^{-1} (x_1, x_3))) (\widehat f^\prime (\alpha (g^{-1} (x_1, x_3))) (Z x_1 x_2))\\
+  %   &= \lambda x_1 x_2 x_3, (\epsilon_Y (g^{-1} (x_1, x_3))) (\widehat f^\prime x_1 x_2)\\
+  %   &= \lambda x_1 x_2 x_3, Y (g^{-1} (x_1, x_3)) (\widehat f^\prime x_1 x_2 (\pi_2 (g (g^{-1} (x_1, x_3)))))\\
+  %   &= \lambda x_1 x_2 x_3, Y (g^{-1} (x_1, x_3)) (\widehat f^\prime x_1 x_2 (X x_1 x_3))\\
+  %   &= \lambda x_1 x_2, \alpha_* Y x_1 (\widehat f^\prime x_1 (Z x_1 x_2))\\
+  %   &= \widehat f^\prime
   % \end{align*}
@@
 Conversely, if we start with one of Hyland's $ \lambda $-theories $ L $, we can consider $ L_n $ as a subset of $ L_{n + 1} $ by sending $ x_{n, i} $ to $ x_{n + 1, i} $.
-If we take the union $ \bar L = \bigcup_n L_n $ (officially, this is a directed limit), we have a function $ f: \Lambda_{\bar L} \to \bar L $, because the constants of $ \Lambda_{\bar L} $ are exactly the terms of $ \bar L $ and because $ \lambda $-theories in Hyland's sense support the operations of the $ \lambda $-calculus (see Subsection \ref{subsec:lambda-calculus-operations}).
-This gives an equivalence relation on $ \Lambda_{\bar L} $ by taking $ a\ `='\ b $ if $ f(a) = f(b) $.
+If we take the union $ \overline L = \bigcup_n L_n $ (officially, this is a directed limit), we have a function $ f: \Lambda_{\overline L} \to \overline L $, because the constants of $ \Lambda_{\overline L} $ are exactly the terms of $ \overline L $ and because $ \lambda $-theories in Hyland's sense support the operations of the $ \lambda $-calculus (see Subsection \ref{subsec:lambda-calculus-operations}).
+This gives an equivalence relation on $ \Lambda_{\overline L} $ by taking $ a\ `='\ b $ if $ f(a) = f(b) $.
 

### 2024-12-09 600-paper.tex
Improve notation and wording

@@
 \begin{proof}
-  First of all, remember that $ L $ is indeed exponentiable and that $ L^L = A(L, 1) $.
+  First of all, remember that $ L $ is indeed exponentiable and that $ L^L = A(L, 1) $ (Lemma \ref{lem:plus-p-presheaf}).
   Now, since $ L $ is a $ \lambda $-theory, we have sequences of functions back and forth $ \lambda_n: A(L, 1)_n \to L_n $ and $ \rho_n: L_n \to A(L, 1)_n $.
@@
 
-  Remark \ref{rem:presheaf-Yoneda} gives a sequence of bijections $ \varphi_n : \Pshf L(L^n, L) \cong L_n $ for all $ n $, sending $ F: \Pshf L(L^n, L) $ to $ F(x_1, \dots, x_n) $, and conversely sending $ s: L_n $ to $ ((t_1, \dots, t_n) \mapsto s \bullet (t_1, \dots, t_n)) $.
+  Remark \ref{rem:presheaf-Yoneda} gives a sequence of bijections $ \varphi_n : \Pshf L(L^n, L) \cong L_n $ for all $ n $, sending $ f: \Pshf L(L^n, L) $ to $ f(x_1, \dots, x_n) $, and conversely sending $ s: L_n $ to $ ((t_1, \dots, t_n) \mapsto s \bullet (t_1, \dots, t_n)) $.
 It considers $ \lambda $-terms in $ n $ variables as $ n $-ary functions on the $ \lambda $-calculus.
@@
 \begin{remark}
-  Actually, in this thesis we stumbled upon another category with a reflexive object that exhibits $ L $ as its endomorphism theory, provided that $ L $ has $ \beta $-equality: In Appendix \ref{ch:weak-cartesian-closed-categories}, we see that the Lawvere theory $ C $ associated to $ L $ is a weak cartesian closed category, in which $ 1^1 = 1 $.
+  Actually, in this thesis we stumbled upon another category with a reflexive object that exhibits $ L $ as its endomorphism theory, provided that $ L $ has $ \beta $-equality: In Appendix \ref{ch:weak-cartesian-closed-categories}, we see that the Lawvere theory $ \L $ associated to $ L $ is a weak cartesian closed category, in which $ 1^1 = 1 $.
 It is then easy to see that the endomorphism theory that we obtain from this reflexive object $ 1 $ is exactly equal to $ L $.
 
-  Note, however, that this is technically not an answer to Scott's original theorem, because the original formulation asks for a cartesian closed category with a reflexive object, whereas here we only have a reflexive object in a weak cartesian closed category.
-Even so, it is an answer to the core of the question, which is about whether we can represent any $ \lambda $-theory as the sets of morphisms $ C(U^n, U) $ for some $ U : C $.
+  Note, however, that this is technically not an answer to Scott's original question, because the original formulation asks for a cartesian closed category with a reflexive object, whereas here we only have a reflexive object in a weak cartesian closed category.
+Even so, it is an answer to the core of the question, which is about whether we can represent any $ \lambda $-theory as the sets of morphisms $ \C(U^n, U) $ for some $ U : \C $.
 \end{remark}
@@
   \begin{tikzcd}
-    L_1 \arrow[r, hookrightarrow] & \mathbf L \arrow[r, hookrightarrow] & \R \arrow[r, hookrightarrow] & \Pshf L
-  \end{tikzcd}
-\end{center}
-
-Note that the composition of the first two morphisms sends the object of the category $ L_1 $ to $ (\lambda x_1, x_1) : \R $, which is exactly the usual embedding of $ L_1 $ into its Karoubi envelope.
-
-Write $ i: \op{L_1} \hookrightarrow \op{\mathbf L} $ and $ j: \op{\mathbf L} \hookrightarrow \op \R $ for the embeddings on the opposite categories.
+    \C_{L_1} \arrow[r, hookrightarrow] & \mathbf L \arrow[r, hookrightarrow] & \R \arrow[r, hookrightarrow] & \Pshf L
+  \end{tikzcd}
+\end{center}
+
+Note that the composition of the first two morphisms sends the object of the category $ \C_{L_1} $ to $ (\lambda x_1, x_1) : \R $, which is exactly the usual embedding of $ \C_{L_1} $ into its Karoubi envelope.
+
+Write $ i: \op{\C_{L_1}} \hookrightarrow \op{\mathbf L} $ and $ j: \op{\mathbf L} \hookrightarrow \op \R $ for the embeddings on the opposite categories.
 By Corollary \ref{cor:surjective-precomposition}, the first two functors in this sequence essentially yield surjective functors on the presheaf categories:
@@
   \begin{tikzcd}
-    C_{L_1} \arrow[d, "\yo", hook] &
+    \C_{L_1} \arrow[d, "\yo", hook] &
     \mathbf L \arrow[l, "\op i"'] \arrow[d, "yo", hook] &
     \mathbf R \arrow[rd, hook] \arrow[d, "\yo", hook] \arrow[l, "\op j"']\\
-    P C_{L_1} &
+    P \C_{L_1} &
     P \mathbf L \arrow[l, "i_*"', two heads] &
@@
 Recall that in the last chapter, we saw that Paul Taylor shows that the category of retracts $ \R $, studied by Scott, is not only cartesian closed, but also `relatively cartesian closed'.
-To make his proof work in univalent foundations, we need the axiom of choice.
-The category in question is the Karoubi envelope of the category $ C_{L_0} $ associated to the monoid $ (L_0, \circ) $.
-
-Now, recall from Chapter \ref{ch:category-theory}, that in univalent foundations there are three different definitions that we can take for the Karoubi envelope, denoted $ \overline C_{L_0} $, $ \tilde C_{L_0} $ and $ \hat C_{L_0} $.
+The proof uses the axiom of choice, and works for the setcategory version of the Karoubi envelope $ \overline{\C_{L_0}} $.
+Here, $ \C_{L_0} $ is the category associated to the monoid $ (L_0, \circ) $.
+
+Now, recall from Chapter \ref{ch:category-theory}, that in univalent foundations there are three different definitions that we can take for the Karoubi envelope, denoted $ \overline \C_{L_0} $, $ \widetilde \C_{L_0} $ and $ \widehat \C_{L_0} $.
 There is three of them because in classical category theory there are two definitions that are equivalent, and because for one of the definitions we have to choose whether we interpret the `existence' of a retraction as additional structure (the retraction is given explicitly) or as a property (where we demand `mere existence').
@@
   \begin{tikzcd}
-    C \arrow[r, hook, "\iota_C"] & \overline C \arrow[r, "\sim"] & \tilde C \arrow[r, hook, two heads] & \hat C \arrow[r, phantom, "\subseteq"] & PC
-  \end{tikzcd}
-\end{center}
-where $ \overline C_{L_0} $ and $ \tilde C_{L_0} $ are equivalent to each other, but usually not to $ \hat C_{L_0} $.
-We saw that $ \hat C_{L_0} $ is the Rezk completion of $ \overline C_{L_0} $ and $ \tilde C_{L_0} $.
+    \C_{L_0} \arrow[r, hook, "\iota_C"] & \overline \C_{L_0} \arrow[r, "\sim"] & \widetilde \C_{L_0} \arrow[r, hook, two heads] & \widehat \C_{L_0} \arrow[r, phantom, "\subseteq"] & P \C
+  \end{tikzcd}
+\end{center}
+where $ \overline \C_{L_0} $ and $ \widetilde \C_{L_0} $ are equivalent to each other, but usually not to $ \widehat \C_{L_0} $.
+We saw that $ \widehat \C_{L_0} $ is the Rezk completion of $ \overline \C_{L_0} $ and $ \widetilde \C_{L_0} $.
 
@@
 
-The proofs of Scott and Taylor are about $ \overline C_{L_0} $, because they work explicitly with idempotents.
-The question whether it is possible to lift the proofs to $ \tilde C_{L_0} $ or $ \hat C_{L_0} $, is left for future research.
-On the other hand, as we will see, Hyland works with presheaves and in this way, he shows that $ \hat C_{L_0} $ is relatively cartesian closed.
-
-Recall that in this thesis, we use the notation $ \Delta_X $ for the functor $ C \to (C \downarrow X) $, sending $ Y $ to $ p_1 : X \times Y \to X $.
+The proofs of Scott and Taylor are about $ \overline \C_{L_0} $, because they work explicitly with idempotents.
+The question whether it is possible to lift the proofs to $ \widetilde \C_{L_0} $ or $ \widehat \C_{L_0} $, is left for future research.
+On the other hand, as we will see, Hyland works with presheaves and in this way, he shows that $ \widehat \C_{L_0} $ is relatively cartesian closed.
+
+Recall that in this thesis, we use the notation $ \Delta_X $ for the functor $ \C \to (\C \downarrow X) $, sending $ Y $ to $ p_1 : X \times Y \to X $.
 Also, we use the notation $ X \triangleleft Y $ to denote the type of retraction-section pairs $ r: Y \to X $ and $ s: X \to Y $.
@@
 
-Now, officially, $ \hat C_{L_0} $ is the full subcategory of $ P C_{L_0} $, consisting of all objects $ X : P C_{L_0} $ such that there merely exists $ X \triangleleft \yo(\star) $.
-However, recall from the previous section that $ P C_{L_0} \simeq P C_{L_1} \simeq \Pshf L $.
-Under this equivalence, $ \yo(\star) $ is embedded as the theory presheaf $ L $, and we will work in the full subcategory $ \hat \R \subseteq \Pshf L $ of the objects $ X : \Pshf L $ such that there merely exists $ X \triangleleft L $.
-Of course, then $ \hat \R $ is equivalent to $ \hat C_{L_0} $.
+Now, officially, $ \widehat \C_{L_0} $ is the full subcategory of $ P \C_{L_0} $, consisting of all objects $ X : P \C_{L_0} $ such that there merely exists $ X \triangleleft \yo(\star) $.
+However, recall from the previous section that $ P \C_{L_0} \simeq P \C_{L_1} \simeq \Pshf L $.
+Under this equivalence, $ \yo(\star) $ is embedded as the theory presheaf $ L $, and we will work in the full subcategory $ \widehat \R \subseteq \Pshf L $ of the objects $ X : \Pshf L $ such that there merely exists $ X \triangleleft L $.
+Of course, then $ \widehat \R $ is equivalent to $ \widehat \C_{L_0} $.
 
@@
 
-  Also, functors preserve retractions, so if we have a functor $ F : C \to D $ and we have $ (r, s) : X \triangleleft Y $, then we have
+  Also, functors preserve retractions, so if we have a functor $ F : \C \to \D $ and we have $ (r, s) : X \triangleleft Y $, then we have
   \[ (F(r), F(s)) : F(X) \triangleleft F(Y). \]
 
-  Lastly, if we want to show that we can do some construction on some $ X : \hat \R $, we can often borrow the construction from $ \Pshf L $ to get some object $ Y : \Pshf L $.
-For this part, we cannot use the $ (r, s) : X \triangleleft L $.
-To show that $ Y $ is indeed in $ \hat \R $, we must show that there merely exist $ (r^\prime, s^\prime) : Y \triangleleft L $.
+  Lastly, if we want to show that we can do some construction on some $ X : \widehat \R $, we can often borrow the construction from $ \Pshf L $ to get some object $ Y : \Pshf L $ and for this part, we cannot use the $ (r, s) : X \triangleleft L $.
+Then, to show that $ Y $ is indeed in $ \widehat \R $, we must show that there merely exist $ (r^\prime, s^\prime) : Y \triangleleft L $.
 By the recursion principle of the propositional truncation, we can assume that we have a concrete $ (r, s) : X \triangleleft L $ to construct $ r^\prime $ and $ s^\prime $.
@@
 
-Recall that Paul Taylor's display maps for $ \R $ can be characterized as the retracts of $ \Delta_X U $ (the projection $ p_1: X \times U \to X $) in $ (\R \downarrow X) $.
-This idea also works for $ \hat \R $, and Hyland defines $ D(Y, X) \subseteq \hat \R(Y, X) $ to consist of the retracts of $ \Delta_X L $ in $ (\hat \R \downarrow X) $.
-Note that, because $ \hat \R $ is a full subcategory of $ \Pshf L $, $ (\hat \R \downarrow X) $ is equivalent to $ (\Pshf L \downarrow X) $ for $ X : \hat \R $.
+Recall that Paul Taylor's display maps for $ \R $ can be characterized as the retracts of $ \Delta_X U $ in $ (\R \downarrow X) $.
+This idea also works for $ \widehat \R $, and Hyland defines $ D(Y, X) \subseteq \widehat \R(Y, X) $ to consist of the retracts of $ \Delta_X L $ in $ (\widehat \R \downarrow X) $.
+Note that, because $ \widehat \R $ is a full subcategory of $ \Pshf L $, $ (\widehat \R \downarrow X) $ is equivalent to $ (\Pshf L \downarrow X) $ for $ X : \widehat \R $.
 
@@
 
-  Therefore, if we want $ D(Y, X) $ to be a subset of $ \hat \R(Y, X) $, we need to take the propositional truncation of the existence of $ r $ and $ s $.
-\end{remark}
-
-\begin{remark}
-  Recall that for all $ X : \R $, we have $ X \triangleleft U = \lambda x_1, x_1 $, so by the above, for all $ Y $ in the image of the embedding of $ \R $ into $ \Pshf L $, we have $ Y \triangleleft L $.
-In particular, $ Y $ is in $ \hat \R $.
-Actually, we already knew this, because this essentially describes the embedding of $ \R $ into its Rezk completion $ \hat \R $.
+  Therefore, if we want $ D(Y, X) $ to be a subset of $ \widehat \R(Y, X) $, we need to take the propositional truncation of the existence of $ r $ and $ s $.
+\end{remark}
+
+\begin{remark}
+  Recall that for all $ X : \R $, we have $ X \triangleleft U $, where $ U = \lambda x_1, x_1 $, so by the above, for all $ Y $ in the image of the embedding of $ \R $ into $ \Pshf L $, we have $ Y \triangleleft L $.
+In particular, $ Y $ is in $ \widehat \R $.
+Actually, we already knew this, because this essentially describes the embedding of $ \R $ into its Rezk completion $ \widehat \R $.
 
@@
   \[ Y \triangleleft X \times L \triangleleft L \times L \triangleleft L. \]
-  In particular, for any $ X : \hat \R $, if some $ (Y, f) : (\Pshf L \downarrow X) $ is a retract of $ \Delta_X L $, we know that $ Y $ is in $ \hat \R $.
-\end{remark}
-
-Note that $ D $ is indeed a class of display maps:
+  In particular, for any $ X : \widehat \R $, if some $ (Y, f) : (\Pshf L \downarrow X) $ is a retract of $ \Delta_X L $, we know that $ Y $ is in $ \widehat \R $.
+\end{remark}
+
+Now we can show that $ D $ is indeed a class of display maps:
 \begin{enumerate}
-  \item Take $ f : D(Y, X) $ and $ g: \hat \R(Z, X) $.
+  \item Take $ f : D(Y, X) $ and $ g: \widehat \R(Z, X) $.
 We can borrow the pullback from $ \Pshf L $ to get $ g^*(Y, f) : (\Pshf L \downarrow Z) $.
@@
     The isomorphism between $ g^*(\Delta_X L) $ and $ \Delta_Z L $ (Remark \ref{rem:pullback-of-projection}) shows that we have $ (g^*Y, g^*f) \triangleleft \Delta_Z L $.
-From this, it also follows that $ g^* Y $ is in $ \hat \R $.
-
-    Now, $ g^*Y $ is the pullback of $ f $ and $ g $ in $ \Pshf L $, and $ \hat \R $ is a full subcategory of $ \Pshf L $, so $ g^* Y $ is also the pullback of $ f $ and $ g $ in $ \hat \R $.
+From this, it also follows that $ g^* Y $ is in $ \widehat \R $.
+
+    Now, $ g^*Y $ is the pullback of $ f $ and $ g $ in $ \Pshf L $, and $ \widehat \R $ is a full subcategory of $ \Pshf L $, so $ g^* Y $ is also the pullback of $ f $ and $ g $ in $ \widehat \R $.
 
@@
   \item Note that $ \Pshf L $ has a terminal presheaf $ I_n = \{ \star \} $.
-Under the embedding of $ \R $ into $ \Pshf L $, this is (isomorphic to) the image of $ \lambda x_1 x_2, x_2 : \R $, and therefore, it is in $ \hat \R $.
-Now, given $ Y : \hat \R $, we need to show that the terminal projection $ !
+Under the embedding of $ \R $ into $ \Pshf L $, this is (isomorphic to) the image of $ \lambda x_1 x_2, x_2 : \R $, and therefore, it is in $ \widehat \R $.
+Now, given $ Y : \widehat \R $, we need to show that the terminal projection $ !
 $ is in $ D(Y, I) $.
 Note that any morphism trivially commutes with the terminal projections.
-Since $ Y : \hat \R $, we have $ (r, s) : Y \triangleleft L $, and since $ L \cong I \times L $, this means that the terminal projection is indeed in $ D(Y, I) $:
+Since $ Y : \widehat \R $, we have $ (r, s) : Y \triangleleft L $, and since $ L \cong I \times L $, this means that the terminal projection is indeed in $ D(Y, I) $:
     \begin{center}
@@
 \begin{theorem}\label{thm:restrict-sum-product}
-  For $ f : D(Y, X) $, we can restrict $ \sum_f $ and $ \prod_f $ to functors from $ (\hat \R \downarrow_D Y) $ to $ (\hat \R \downarrow_D X) $.
+  For $ f : D(Y, X) $, we can restrict $ \sum_f $ and $ \prod_f $ to functors from $ (\widehat \R \downarrow_D Y) $ to $ (\widehat \R \downarrow_D X) $.
 \end{theorem}
@@
   Given $ (Z, g) : (\Pshf L \downarrow Y) $, for $ \prod_F $ we only have to show that if we have $ (Z, g) \triangleleft \Delta_Y L $, then we have $ \prod_f(Z, g) \triangleleft \Delta_X L $.
-Note that since $ X $ is in $ \hat \R $, this also shows that $ \prod_f Z $ is in $ \hat \R $.
+Note that since $ X $ is in $ \widehat \R $, this also shows that $ \prod_f Z $ is in $ \widehat \R $.
 Because functors preserve retractions, it suffices to show that we have $ \prod_f \Delta_Y L \triangleleft \Delta_X L $.
@@
 But we already saw in Theorem \ref{thm:representation-theorem} that $ L^L \cong A(L, 1) $ is a retract of $ L $.
-This shows that $ \prod_f $ indeed restricts to a functor from $ (\hat \R \downarrow_D Y) $ to $ (\hat \R \downarrow_D X) $.
+This shows that $ \prod_f $ indeed restricts to a functor from $ (\widehat \R \downarrow_D Y) $ to $ (\widehat \R \downarrow_D X) $.
 
@@
   By Lemma \ref{lem:sum-postcomposition}, the functor $ \sum_{p_1} $ is given by postcomposition, so $ \sum_{p_1} \Delta_{X \times L} L \cong \Delta_X (L \times L) $.
-As we saw earlier, we have $ L \triangleleft L \times L $, which completes the proof that $ \sum_f $ restricts to a functor from $ (\hat \R \downarrow_D Y) $ to $ (\hat \R \downarrow_D X) $.
+As we saw earlier, we have $ L \triangleleft L \times L $, which completes the proof that $ \sum_f $ restricts to a functor from $ (\widehat \R \downarrow_D Y) $ to $ (\widehat \R \downarrow_D X) $.
 \end{proof}
@@
 \begin{corollary}\label{cor:relatively-cartesian-closed}
-  Since the $ (\hat \R \downarrow_D X) $ are full subcategories of the $ (\Pshf L \downarrow X) $, so we can restrict the adjunction $ f^* \dashv \prod_f $ to an adjunction $ \bar f^* \dashv \bar \prod_f $ between $ (\hat \R \downarrow_D X) $ and $ (\hat \R \downarrow_D Y) $, which shows that $ \hat \R $ is cartesian closed relative to the class $ D $ of display maps.
+  Since the $ (\widehat \R \downarrow_D X) $ are full subcategories of the $ (\Pshf L \downarrow X) $, so we can restrict the adjunction $ f^* \dashv \prod_f $ to an adjunction $ \overline f^* \dashv \overline \prod_f $ between $ (\widehat \R \downarrow_D X) $ and $ (\widehat \R \downarrow_D Y) $, which shows that $ \widehat \R $ is cartesian closed relative to the class $ D $ of display maps.
 \end{corollary}
@@
 \begin{remark}\label{rem:difference-Taylor-Hyland}
-  Recall that to make sure that $ D(Y, X) $ is a subset of $ \hat \R(Y, X) $, we had no choice but to take the propositional truncation of the $ (Y, f) \triangleleft \Delta_X L $.
-Coincidentally, for $ \hat \R $ we also took the propositional truncation of the $ X \triangleleft L $.
+  Recall that to make sure that $ D(Y, X) $ is a subset of $ \widehat \R(Y, X) $, we had no choice but to take the propositional truncation of the $ (Y, f) \triangleleft \Delta_X L $.
+Coincidentally, for $ \widehat \R $ we also took the propositional truncation of the $ X \triangleleft L $.
 
@@
 
-  Therefore, this only works in $ \hat \R \simeq \hat C_{L_0} $.
-Suppose that we tried to do this in $ \tilde \R = \tilde C_{L_0} $.
+  Therefore, this only works in $ \widehat \R \simeq \widehat \C_{L_0} $.
+Suppose that we tried to do this in $ \widetilde \R = \widetilde \C_{L_0} $.
 Note that this category is equivalent to the category with as objects $ X : \Pshf L $, together with some $ (r, s) : X \triangleleft L $.
@@
 However, we have only mere existence of the latter, so we would only be able to show mere existence of pullbacks, like in Taylor's proof.
-For $ \R $, we would be able to use the adjoint equivalence between $ \R $ and $ \tilde \R $ to apply Hyland's reasoning with presheaves to $ \R $.
-Since $ C_{L_0} $ is a setcategory, $ \R $ and $ \tilde \R $ are also setcategories (Lemma \ref{lem:isaset-karoubi'}), so we can use the axiom of choice to show the existence of a pullback functor.
+For $ \R $, we would be able to use the adjoint equivalence between $ \R $ and $ \widetilde \R $ to apply Hyland's reasoning with presheaves to $ \R $.
+Since $ \C_{L_0} $ is a setcategory, $ \R $ and $ \widetilde \R $ are also setcategories (Lemma \ref{lem:isaset-karoubi'}), so we can use the axiom of choice to show the existence of a pullback functor.
 However, this approach still gives only mere existence.
@@
 \begin{remark}\label{rem:ract-presheaf-equivalence}
-  Note that, like in the last chapter, $ \R_A $ pops up as the Karoubi envelope of the monoid category $ C_{A_1} $, and fits into the following diagram:
-  \begin{center}
-    \begin{tikzcd}
-      & C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
-      \RAct{A_1} & P C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
+  Note that, like in the last chapter, $ \R_A $ pops up as the Karoubi envelope of the monoid category $ \C_{A_1} $, and fits into the following diagram:
+  \begin{center}
+    \begin{tikzcd}
+      & \C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
+      \RAct{A_1} & P \C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
     \end{tikzcd}
@@
       &
-      C_{{L_0}_1} \arrow[dd, "\yo" description, near start, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, near start, hook] \arrow[rd, "\sim" description, no head] & & \\
+      \C_{{L_0}_1} \arrow[dd, "\yo" description, near start, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, near start, hook] \arrow[rd, "\sim" description, no head] & & \\
       &
-      & C_{L_1} \arrow[dd, "\yo" description, near start, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, near start, hook] & & \mathbf R \arrow[dd, "\yo" description, near start, hook] \arrow[rdd, hook] & \\
+      & \C_{L_1} \arrow[dd, "\yo" description, near start, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, near start, hook] & & \mathbf R \arrow[dd, "\yo" description, near start, hook] \arrow[rdd, hook] & \\
       \RAct{{L_0}_1} &
-      P C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] & & & P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] & & \\
+      P \C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] & & & P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] & & \\
       &
-      & P C_{L_1} & P \mathbf L \arrow[l, "\sim" description] & & P \R \arrow[ll, "\sim" description] & \Pshf L \arrow[lll, "\sim" description, bend left]
+      & P \C_{L_1} & P \mathbf L \arrow[l, "\sim" description] & & P \R \arrow[ll, "\sim" description] & \Pshf L \arrow[lll, "\sim" description, bend left]
     \end{tikzcd}
@@
 Note that $ F $ preserves $ \circ $ and the $ \mathbf 1_n $.
-Therefore, it induces a monoid morphism $ A_1 \to B_1 $, which gives a functor $ C_{A_1} \to C_{B_1} $.
+Therefore, it induces a monoid morphism $ A_1 \to B_1 $, which gives a functor $ \C_{A_1} \to \C_{B_1} $.
 Precomposing with this, we get a functor $ \RAct{B_1} \to \RAct{A_1} $.
@@
 
-Hyland gives a very high-level argument why $ F_* $ induces a morphism $ \bar F : \LamTh(E_{\RAct{A_1}}(U_A), E_{\RAct{B_1}}(U_B)) $, which we will discuss a bit more here.
+Hyland gives a very high-level argument why $ F_* $ induces a morphism $ \overline F : \LamTh(E_{\RAct{A_1}}(U_A), E_{\RAct{B_1}}(U_B)) $, which we will discuss a bit more here.
 
@@
   \[ F_*(g): \RAct{A^\prime}(f(U_A^n), f(U_A)) \cong \RAct{A^\prime}((U_{A^\prime})^n, U_{A^\prime}) = E(U_{A^\prime})_n \]
-  so we have a morphism $ \bar F: \LamTh(E(U_A), E(U_{A^\prime})) $.
+  so we have a morphism $ \overline F: \LamTh(E(U_A), E(U_{A^\prime})) $.
 \end{definition}
@@
 \begin{remark}
-  The fact that $ \bar F $ preserves the variables and substitution is not very hard to show, since these are just defined in terms of finite products of $ U_A $ and $ \bar F $ preserves finite products and $ U_A $.
+  The fact that $ \overline F $ preserves the variables and substitution is not very hard to show, since these are just defined in terms of finite products of $ U_A $ and $ \overline F $ preserves finite products and $ U_A $.
 
@@
 
-  \enquote{$ F $ preserves $ \mathbf 1_n $, which determines the function space as a retract of the universal. So $ \bar F $ preserves the retract and the result follows.}
+  \enquote{$ F $ preserves $ \mathbf 1_n $, which determines the function space as a retract of the universal. So $ \overline F $ preserves the retract and the result follows.}
 
@@
     \beta: F_*(U_A) &\xrightarrow{\sim} U_{A^\prime};\\
-    \bar \gamma: F_*(A \times B) &\xrightarrow{\sim} F_*(A) \times F_*(B);\\
+    \overline \gamma: F_*(A \times B) &\xrightarrow{\sim} F_*(A) \times F_*(B);\\
     \gamma_n: F_*(X^n) &\xrightarrow{\sim} F_*(X)^n;\\
@@
   Since we already motivated this in a different way, we will leave it as an exercise for the enthousiastic reader.
-  % with $ \gamma_{n + 1} = \bar{\gamma} \cdot (\gamma_n \times \id X) $.
+  % with $ \gamma_{n + 1} = \overline{\gamma} \cdot (\gamma_n \times \id X) $.
   % Then, for $ s: E(U_A)_{n + 1} $, we have $ \lambda_A(s) = \alpha_A(s) \cdot \delta_A \cdot \pi_A : \RAct{A_1}(U_A^n, U_A) $ for the projection $ \pi_A: A_2 \to U_A $.
@@
   %   &(\beta^{-1})^n \cdot \gamma_n^{-1} \cdot f^*(\alpha_A(s)) \cdot f^*(\delta_A \cdot \pi_A) \cdot \beta\\
-  %   &= (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot \alpha_{A^\prime}((\id X^n \times \beta^{-1}) \cdot \bar{\gamma}^{-1} \cdot f^*(s)) \cdot \beta^{U_A} \cdot \delta_{A^\prime} \cdot \pi_{A^\prime}.
+  %   &= (\beta^{-1})^n \cdot \gamma_n^{-1} \cdot \alpha_{A^\prime}((\id X^n \times \beta^{-1}) \cdot \overline{\gamma}^{-1} \cdot f^*(s)) \cdot \beta^{U_A} \cdot \delta_{A^\prime} \cdot \pi_{A^\prime}.
   % \end{align*}
@@
 \begin{lemma}
-  For $ F = \id A $, we have $ \bar F = \id{E(U_A)} $.
-\end{lemma}
-\begin{proof}
-  By the reasoning set forth in Lemma \ref{lem:elementary-faithful}, we only need to check $ \bar F_0 $. Given $ s : \RAct{A_1}(I, U_A) $, we have
-  \[ \bar F_0(s) = \gamma^{-1} \cdot F_*(s) \cdot \beta: \RAct{A_1}(I, U_A) \]
+  For $ F = \id A $, we have $ \overline F = \id{E(U_A)} $.
+\end{lemma}
+\begin{proof}
+  By the reasoning set forth in Lemma \ref{lem:elementary-faithful}, we only need to check $ \overline F_0 $. Given $ s : \RAct{A_1}(I, U_A) $, we have
+  \[ \overline F_0(s) = \gamma^{-1} \cdot F_*(s) \cdot \beta: \RAct{A_1}(I, U_A) \]
   for $ \gamma: F_*(I) \cong I $ and $ \beta: F_*(U_A) \cong U_A $. Then
   \[
-    \bar{\id A}(s)(\star) = s(\star) \circ ((\lambda x_1 x_2, x_2) \bullet ()) = s(\star \circ ((\lambda x_1 x_2, x_2) \bullet ())),
+    \overline{\id A}(s)(\star) = s(\star) \circ ((\lambda x_1 x_2, x_2) \bullet ()) = s(\star \circ ((\lambda x_1 x_2, x_2) \bullet ())),
   \]
-  so $ \bar{\id A}_0(s) = s $ and we can conclude that $ \bar{\id A} = \id{E(U_A)} $.
+  so $ \overline{\id A}_0(s) = s $ and we can conclude that $ \overline{\id A} = \id{E(U_A)} $.
 \end{proof}
@@
 \begin{lemma}
-  For $ F : \Alg{\Lambda}(A, B) $ and $ G: \Alg{\Lambda}(B, C) $, we have $ \bar F \cdot \bar G = \overline{F \cdot G} $.
+  For $ F : \Alg{\Lambda}(A, B) $ and $ G: \Alg{\Lambda}(B, C) $, we have $ \overline F \cdot \overline G = \overline{F \cdot G} $.
 \end{lemma}
@@
   Again, we only have to check at the terms without free variables. Given $ s : \RAct{A_1}(I, U_A) $, we have
-  \[ (\bar F \cdot \bar G)(s) = \gamma_G^{-1} \cdot G_*(\gamma_F^{-1} \cdot F_*(s) \cdot \beta_F) \cdot \beta_G: \RAct{C_1}(I, U_C) \]
+  \[ (\overline F \cdot \overline G)(s) = \gamma_G^{-1} \cdot G_*(\gamma_F^{-1} \cdot F_*(s) \cdot \beta_F) \cdot \beta_G: \RAct{C_1}(I, U_C) \]
   for $ \gamma: F_*(I) \cong I $ and $ \beta: F_*(U_A) \cong U_A $. Then
   \begin{align*}
-    (\bar F \cdot \bar G)(s)(\star)
+    (\overline F \cdot \overline G)(s)(\star)
     &= G(F(s(\star)) \circ ((\lambda x_1 x_2, x_2) \bullet_B ())) \circ ((\lambda x_1 x_2, x_2) \bullet_C ())\\
@@
   \end{align*}
-  so $ (\bar F \cdot \bar G)_0(s) = (\overline{F \cdot G})_0(s) $ and we can conclude that $ \bar F \cdot \bar G = \overline{F \cdot G} $.
+  so $ (\overline F \cdot \overline G)_0(s) = (\overline{F \cdot G})_0(s) $ and we can conclude that $ \overline F \cdot \overline G = \overline{F \cdot G} $.
 \end{proof}
@@
 \begin{definition}
-  We get a functor from $ \Alg{\Lambda} $ to $ \LamTh $, sending objects $ A $ to $ E_{\RAct{A_1}}(U_A) $ and morphisms $ F: \Alg{\Lambda}(A, B) $ to $ \bar F: E(U_A) \to E(U_B) $.
+  We get a functor from $ \Alg{\Lambda} $ to $ \LamTh $, sending objects $ A $ to $ E_{\RAct{A_1}}(U_A) $ and morphisms $ F: \Alg{\Lambda}(A, B) $ to $ \overline F: E(U_A) \to E(U_B) $.
 \end{definition}
@@
   Since $ F $ preserves all the structure of $ \R_A $, as do the embeddings of $ \R_A $ and $ \R_B $ into $ \RAct{A_1} $ and $ \RAct{B_1} $, one would expect $ F_* $ to preserves the structure of the full subcategory $ \R_A $ of $ \RAct{A_1} $, including $ U_A $, its finite products and their exponentials.
-This is another way to argue that $ \bar F $ is indeed a morphism of $ \lambda $-theories.
+This is another way to argue that $ \overline F $ is indeed a morphism of $ \lambda $-theories.
 \end{remark}
@@
   Recall from Remark \ref{rem:ract-presheaf-equivalence} that we have a chain of equivalences
-  \[ \Pshf L \xrightarrow \sim P \mathbf L \xrightarrow \sim P C_{L_1} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}. \]
+  \[ \Pshf L \xrightarrow \sim P \mathbf L \xrightarrow \sim P \C_{L_1} \xrightarrow \sim P \C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}. \]
   It sends the presheaf $ L^n $ to the set $ L_1^n $ with a right action sending $ s: L_1^n $ and $ t: (L_0)_1 $ to $ (s_i \bullet_L \rho(t))_i : L_1^n $.
@@
   Note that we can do the same with Scott's version of his representation theorem, using the chain of equivalences and an embedding
-  \[ \mathbf R \xrightarrow \sim \mathbf R_{L_0} \xrightarrow{\yo} P \R_{L_0} \xrightarrow \sim P C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}, \]
+  \[ \mathbf R \xrightarrow \sim \mathbf R_{L_0} \xrightarrow{\yo} P \R_{L_0} \xrightarrow \sim P \C_{{L_0}_1} \xrightarrow \sim \RAct{{L_0}_1}, \]
   Here, it is a bit harder to get an explicit formula for $ \eta $, because we need to do a bit more conversion between $ U_A^n $ and the image of $ U^n $ after the embedding $ \varphi: \mathbb R \hookrightarrow \RAct{{L_0}_1} $.
@@
       L \arrow[r, "F"] \arrow[d, "\eta_L"] & L^\prime \arrow[d, "\eta_{L^\prime}"]\\
-      E_{\RAct{{L_0}_1}}(U_{L_0}) \arrow[r, "\bar{F_0}"] & E_{\RAct{{L^\prime_0}_1}}(U_{L^\prime_0})
+      E_{\RAct{{L_0}_1}}(U_{L_0}) \arrow[r, "\overline{F_0}"] & E_{\RAct{{L^\prime_0}_1}}(U_{L^\prime_0})
     \end{tikzcd}
@@
   We must show
-  \[ \eta_L \cdot \bar{F_0} = F \cdot \eta_{L^\prime}. \]
+  \[ \eta_L \cdot \overline{F_0} = F \cdot \eta_{L^\prime}. \]
   Note that for all $ s : L_0 $,
   \begin{align*}
-    \bar{F_0}_0(\eta_L(s))
+    \overline{F_0}_0(\eta_L(s))
     &= \gamma_{F_0}^{-1} \cdot {F_0}_*(\star \mapsto (\lambda x_1, \iota_{0, 1}(s))) \cdot \beta_F\\
@@
     \begin{tikzcd}
-      E(U_A)_0 \arrow[d, "\epsilon_A"] \arrow[r, "\bar F_0"] & E(U_B)_0 \arrow[d, "\epsilon_B"]\\
+      E(U_A)_0 \arrow[d, "\epsilon_A"] \arrow[r, "\overline F_0"] & E(U_B)_0 \arrow[d, "\epsilon_B"]\\
       A \arrow[r, "F"] & B
@@
   \[ \beta(a, b) = F(a) \circ b \quad \text{and} \quad \gamma^{-1}(\star) = (\star, (\lambda x_1 x_2, x_2) \bullet ()). \]
-  Then $ \bar F: \RAct{A_1}(I, U_A) \to \RAct{B_1}(I, U_B) $ is given by
+  Then $ \overline F: \RAct{A_1}(I, U_A) \to \RAct{B_1}(I, U_B) $ is given by
   \[
-    \bar F(s)(\star)
+    \overline F(s)(\star)
     = \gamma^{-1} \cdot (s \times \id{B_1}) \cdot \beta
@@
   \[
-    (\bar F \cdot \epsilon_B)(s)
+    (\overline F \cdot \epsilon_B)(s)
     = (x_1 (\lambda x_2, x_2)) \bullet F(s(\star))
@@
       E(U_{\Lambda_0})_0
-        \arrow[r, "\bar F_0"]
+        \arrow[r, "\overline F_0"]
         \arrow[d, "\epsilon_{\Lambda_0}"]
@@
   Recall that there exists a unique morphism $ \iota_\Lambda: \LamTh(\Lambda, E(U_A)) $, and that for all $ s: \Lambda_0 $, by definition $ s \bullet_{E(U_A)_0} () = \iota_\Lambda(s) \bullet_{E(U_A)} () = \iota_\Lambda(s) $.
-Since we have $ \eta \cdot \bar F : \LamTh(\Lambda, E(U_A)) $, we must have $ \iota_\Lambda = \eta \cdot \bar F $ and
+Since we have $ \eta \cdot \overline F : \LamTh(\Lambda, E(U_A)) $, we must have $ \iota_\Lambda = \eta \cdot \overline F $ and
   \begin{align*}
     \epsilon_A(s \bullet_{E(U_A)} ())
-    &= \epsilon_A(\bar{F_0}(\eta_0(s)))\\
+    &= \epsilon_A(\overline{F_0}(\eta_0(s)))\\
     &= F(\epsilon_{\Lambda_0}(\eta_0(s)))\\
@@
         \arrow[d, "\epsilon_{\iota_\Lambda^* C}", "\sim"']\\
-      B \arrow[r, dashed, "\bar h"] & C
+      B \arrow[r, dashed, "\overline h"] & C
     \end{tikzcd}
@@
   This gives us the lift
-  \[ \bar h = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot (a \mapsto \epsilon_A^{-1}(a) \bullet ())^* h \cdot \epsilon_{\iota_\Lambda^* C} : \Alg{E_{\R_A}(U)}(B, C) \]
+  \[ \overline h = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot (a \mapsto \epsilon_A^{-1}(a) \bullet ())^* h \cdot \epsilon_{\iota_\Lambda^* C} : \Alg{E_{\R_A}(U)}(B, C) \]
 
   Now, when we again pull back this map to
-  \[ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* \bar h : \Alg{\Lambda_A}([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* B, [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* C).
+  \[ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* \overline h : \Alg{\Lambda_A}([a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* B, [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* C).
 \]
   Note that by naturality of $ \epsilon $, we have
-  \[ \bar h = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot h \cdot \epsilon_{\iota_\Lambda^* C} = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot \epsilon_{\iota_\Lambda^* B} \cdot h = h \]
-  as functions, and therefore $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* \bar h = h $, so the pullback is full.
+  \[ \overline h = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot h \cdot \epsilon_{\iota_\Lambda^* C} = \epsilon_{\iota_\Lambda^* B}^{-1} \cdot \epsilon_{\iota_\Lambda^* B} \cdot h = h \]
+  as functions, and therefore $ [a \mapsto \epsilon_A^{-1}(a) \bullet (), \iota_{\Lambda_n}]_n^* \overline h = h $, so the pullback is full.
 \end{proof}

### 2024-12-09 700-formalization.tex
Improve notation and wording

@@
   \item The Sigma displayed category creates limits (\coqident{CategoryTheory.DisplayedCats.Examples.Sigma}{creates_limits_sigma_disp_cat}).
-  \item The definitions $ \overline \C $ (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}) and $ \tilde \C $ (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope'}) for the Karoubi envelope, together with some properties and their equivalence (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_equivalence}).
+  \item The definitions $ \overline \C $ (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}) and $ \widetilde \C $ (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope'}) for the Karoubi envelope, together with some properties and their equivalence (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_equivalence}).
   \item The contents of Section \ref{sec:monoid-category}: The functorial construction of a one-object category from a monoid (\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_to_category}), the equivalence between it's presheaves and sets with a right monoid action (\coqident{CategoryTheory.Categories.MonoidToCategory}{monoid_presheaf_action_equivalence}), properties of the category of sets with a monoid action and restriction and extension of scalars (\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_restriction_functor}, \coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.MonoidActions}{scalar_extension_functor}).
@@
 A displayed category $ D $ over a category $ C $ firstly consists of a type $ D_c $ for every $ c : C $ (corresponding to the type of objects $ F^{-1}(c) $) and a type $ d \to_f d^\prime $ for all $ d: D_c $, $ d^\prime : D_{c^\prime} $ and $ f : C(c, c^\prime) $ (corresponding to $ C^\prime((c, d), (c^\prime, d^\prime)) $).
-A displayed category also consists of an identity `morphism' $ d \to_{\id c} d $ for all $ d : D_c $, and compositions $ \bar f \cdot \bar g : d \to_{f \cdot g} d^{\prime \prime} $ for $ \bar f : d \to_f d^\prime $ and $ \bar g : d^\prime \to_g d^{\prime \prime} $.
+A displayed category also consists of an identity `morphism' $ d \to_{\id c} d $ for all $ d : D_c $, and compositions $ \overline f \cdot \overline g : d \to_{f \cdot g} d^{\prime \prime} $ for $ \overline f : d \to_f d^\prime $ and $ \overline g : d^\prime \to_g d^{\prime \prime} $.
 
@@
 One of the places where displayed categories are conceptually better to work with than forgetful functors, is in the case of fibrations.
-Recall that a functor $ P: C^\prime \to C $ is a fibration if for every $ Y : C^\prime $ and $ f : C(X, P(Y)) $, there exists $ \bar X : C^\prime $ with $ P(\bar X) = X $ (and a cartesian morphism $ \bar f : C^\prime(\bar X, Y) $ with $ P(\bar f) = f $).
-The equality $ P(\bar X) = X $ is on objects in the category, and this violates the \textit{principle of equivalence}: `if something is true for $ A $, and $ A $ is isomorphic to $ B $, then it should also hold for $ B $'.
+Recall that a functor $ P: C^\prime \to C $ is a fibration if for every $ Y : C^\prime $ and $ f : C(X, P(Y)) $, there exists $ \overline X : C^\prime $ with $ P(\overline X) = X $ (and a cartesian morphism $ \overline f : C^\prime(\overline X, Y) $ with $ P(\overline f) = f $).
+The equality $ P(\overline X) = X $ is on objects in the category, and this violates the \textit{principle of equivalence}: `if something is true for $ A $, and $ A $ is isomorphic to $ B $, then it should also hold for $ B $'.
 Of course, if the category is univalent, isomorphism and equality are the same, but definitions that use equality on objects still give a bit of conceptual friction.
@@
 \begin{definition}
-  A displayed category $ D $ over $ C $ is a fibration if for every $ \bar Y : D Y $ and $ f: C(X, Y) $, we have $ \bar X : D X $ and a cartesian morphism $ \bar f : \bar X \to_f \bar Y $.
+  A displayed category $ D $ over $ C $ is a fibration if for every $ \overline Y : D Y $ and $ f: C(X, Y) $, we have $ \overline X : D X $ and a cartesian morphism $ \overline f : \overline X \to_f \overline Y $.
 \end{definition}
@@
 This is all very reminiscent of the way that displayed categories `borrow' information from their base category.
-Now if a category $ C $ has binary products, we say that a displayed category $ D $ over $ C $ \textit{creates binary products}, if for all $ \bar X : D_X $, $ \bar Y : D_Y $, we can `lift' their product.
+Now if a category $ C $ has binary products, we say that a displayed category $ D $ over $ C $ \textit{creates binary products}, if for all $ \overline X : D_X $, $ \overline Y : D_Y $, we can `lift' their product.
 That is, if we can find
-\[ \overline{X \times Y} : D_{X \times Y}, \quad \bar{\pi_1} : \overline{X \times Y} \to_{\pi_1} \bar X \quad \text{and} \quad \bar{\pi_2} : \overline{X \times Y} \to_{\pi_2} \bar Y \]
-and if $ (X \times Y, \overline{X \times Y}) $ with the projections $ (\pi_1, \bar{\pi_1}) $ and $ (\pi_2, \bar{\pi_2}) $ is the product of $ (X, \bar X) $ and $ (Y, \bar Y) $ in $ \int_C D $.
+\[ \overline{X \times Y} : D_{X \times Y}, \quad \overline{\pi_1} : \overline{X \times Y} \to_{\pi_1} \overline X \quad \text{and} \quad \overline{\pi_2} : \overline{X \times Y} \to_{\pi_2} \overline Y \]
+and if $ (X \times Y, \overline{X \times Y}) $ with the projections $ (\pi_1, \overline{\pi_1}) $ and $ (\pi_2, \overline{\pi_2}) $ is the product of $ (X, \overline X) $ and $ (Y, \overline Y) $ in $ \int_C D $.
 By definition, if $ D $ creates binary products, then $ \int_C D $ has binary products.
@@
 
-During this project, I added a small lemma to the library, showing that for a full subcategory $ \int_C D \subseteq C $, where $ D_c $ is a mere proposition for all $ c : C $, if for all $ (X, \bar X), (Y, \bar Y) : \int D $, we have $ D_{X \times Y} $ (the $ C $-product of two objects in $ \int D $ is again in $ \int D $), then $ D $ creates binary products.
+During this project, I added a small lemma to the library, showing that for a full subcategory $ \int_C D \subseteq C $, where $ D_c $ is a mere proposition for all $ c : C $, if for all $ (X, \overline X), (Y, \overline Y) : \int D $, we have $ D_{X \times Y} $ (the $ C $-product of two objects in $ \int D $ is again in $ \int D $), then $ D $ creates binary products.
 I also added a lemma showing that if a displayed category $ D $ over $ C $, and a displayed category $ E $ over $ D $, both create binary products, then $ \sigma_D E $ also creates binary products.
@@
 For example, an algebra morphism is a function that `respects the operation', and respecting the operation is a mere proposition.
-In these categories, it is not necessary to give a full proof that the object $ (X \times Y, \overline{X \times Y}) $ and the morphisms $ (\pi_i, \overline{\pi_i}) $ form a binary product, because it suffices to show that for all $ C, \bar C, f, g $ and all $ \bar f : \bar C \to_f \bar A $ and $ \bar g : \bar C \to_g \bar B $, we can lift the product morphism to
-\[ \overline{\langle f, g \rangle} : \bar C \to_{\langle f, g \rangle} \overline{A \times B} \]
-For example, if the function $ f $ commutes with the algebra actions on $ \bar C $ and $ \bar A $, and $ g $ commutes with the actions on $ \bar C $ and $ \bar B $, then we need to show that the product morphism $ \langle f, g \rangle $ commutes with the actions on $ \bar C $ and $ \overline{A \times B} $.
+In these categories, it is not necessary to give a full proof that the object $ (X \times Y, \overline{X \times Y}) $ and the morphisms $ (\pi_i, \overline{\pi_i}) $ form a binary product, because it suffices to show that for all $ C, \overline C, f, g $ and all $ \overline f : \overline C \to_f \overline A $ and $ \overline g : \overline C \to_g \overline B $, we can lift the product morphism to
+\[ \overline{\langle f, g \rangle} : \overline C \to_{\langle f, g \rangle} \overline{A \times B} \]
+For example, if the function $ f $ commutes with the algebra actions on $ \overline C $ and $ \overline A $, and $ g $ commutes with the actions on $ \overline C $ and $ \overline B $, then we need to show that the product morphism $ \langle f, g \rangle $ commutes with the actions on $ \overline C $ and $ \overline{A \times B} $.
 I added a lemma showing that it suffices to construct a lift for the product morphism, and used this lemma to show that the `\dots data' displayed categories create binary products.
@@
 \begin{proof}
-  Take $ \bar X_1, \bar X_2 : D_X $.
-We have a product $ \bar X_1 \times \bar X_2 : D_{X \times X} $ with projections $ \bar \pi_i : \bar X_1 \times \bar X_2 \to_{\pi_i} \bar X_i $.
-For the diagonal morphism on $ X $, the fibration gives an object $ \bar Y $ and a a cartesian lift:
-  \[ \bar f : \bar Y \to_{\langle \id X, \id X \rangle} \bar X_1 \times \bar X_2, \]
+  Take $ \overline X_1, \overline X_2 : D_X $.
+We have a product $ \overline X_1 \times \overline X_2 : D_{X \times X} $ with projections $ \overline \pi_i : \overline X_1 \times \overline X_2 \to_{\pi_i} \overline X_i $.
+For the diagonal morphism on $ X $, the fibration gives an object $ \overline Y $ and a a cartesian lift:
+  \[ \overline f : \overline Y \to_{\langle \id X, \id X \rangle} \overline X_1 \times \overline X_2, \]
   so we have projections
-  \[ \bar p_i = \bar f \cdot \bar \pi_i : \bar Y \to_{\id X} \bar X_i. \]
+  \[ \overline p_i = \overline f \cdot \overline \pi_i : \overline Y \to_{\id X} \overline X_i. \]
   In the diagram below, the first row is the fiber $ D_X $ and the second row is the fiber $ D_{X \times X} $.
@@
     \begin{tikzcd}
-      \bar X_i & \bar Y \arrow[d, "\bar f" description] \arrow[l, "\bar p_i"] & \bar Z \arrow[ll, "\bar g_i"', bend right] \arrow[l, "\bar h"] \arrow[ld, "{\langle \bar g_1, \bar g_2 \rangle}"] \\
-      & \bar X_1 \times \bar X_2 \arrow[lu, "\bar \pi_i"] &
+      \overline X_i & \overline Y \arrow[d, "\overline f" description] \arrow[l, "\overline p_i"] & \overline Z \arrow[ll, "\overline g_i"', bend right] \arrow[l, "\overline h"] \arrow[ld, "{\langle \overline g_1, \overline g_2 \rangle}"] \\
+      & \overline X_1 \times \overline X_2 \arrow[lu, "\overline \pi_i"] &
     \end{tikzcd}
   \end{center}
-  Now, given some $ \bar g_1: \bar Z \to_{g_1} \bar X_1 $ and $ \bar g_2: \bar Z \to_{g_2} \bar X_2 $, we have
-  \[ \langle \bar g_1, \bar g_2 \rangle : \bar Z \to_{\langle g_1, g_2 \rangle} \bar X_1 \times \bar X_2. \]
-  Because $ \bar f $ is cartesian, we have a unique
-  \[ \bar h: \bar Z \to_{\id X} \bar Y, \]
+  Now, given some $ \overline g_1: \overline Z \to_{g_1} \overline X_1 $ and $ \overline g_2: \overline Z \to_{g_2} \overline X_2 $, we have
+  \[ \langle \overline g_1, \overline g_2 \rangle : \overline Z \to_{\langle g_1, g_2 \rangle} \overline X_1 \times \overline X_2. \]
+  Because $ \overline f $ is cartesian, we have a unique
+  \[ \overline h: \overline Z \to_{\id X} \overline Y, \]
   such that
-  \[ \bar h \cdot \bar f = \langle \bar g_1, \bar g_2 \rangle. \]
+  \[ \overline h \cdot \overline f = \langle \overline g_1, \overline g_2 \rangle. \]
   Therefore,
-  \[ \bar h \cdot \bar p_i = \bar h \cdot \bar f \cdot \bar \pi_i = \langle \bar g_1, \bar g_2 \rangle \cdot \bar \pi_i = \bar g_i, \]
-  which shows that $ \bar Y $ is the product of $ \bar X_1 $ and $ \bar X_2 $ in $ D_X $.
+  \[ \overline h \cdot \overline p_i = \overline h \cdot \overline f \cdot \overline \pi_i = \langle \overline g_1, \overline g_2 \rangle \cdot \overline \pi_i = \overline g_i, \]
+  which shows that $ \overline Y $ is the product of $ \overline X_1 $ and $ \overline X_2 $ in $ D_X $.
 \end{proof}
@@
 However, the relation given by $ R : (x n, m) \sim (x, f(n) \cdot m) $ for all $ a $, is reflexive and transitive, but not necessarily symmetric.
-Therefore, we first take the `equivalence closure' $ \bar R $ of $ R $: the smallest transitive and symmetric relation that contains $ R $.
+Therefore, we first take the `equivalence closure' $ \overline R $ of $ R $: the smallest transitive and symmetric relation that contains $ R $.
 This is then used for the quotient.
 To construct functions from this, like the right action of the monoid $ M^\prime $, we use the universal property of the quotient: a function from $ X \times M^\prime $ that sends `related' elements $ (x_1, m_1) $ and $ (x_2, m_2) $ to the same element gives a function from the quotient $ X \times M^\prime / \sim $.
-However, the quotient is taken over $ \bar R $ instead of $ R $, so it is no longer possible to assume that $ x_2 = x_1 n $ and $ m_1 = f(n) \cdot m_2 $ for some $ n $.
+However, the quotient is taken over $ \overline R $ instead of $ R $, so it is no longer possible to assume that $ x_2 = x_1 n $ and $ m_1 = f(n) \cdot m_2 $ for some $ n $.
 In the case of the right $ M^\prime $-action, it sufficed to add the following lemma to the library
 \begin{lemma}
-  For a relation $ S $ on a set $ A $ and a relation $ T $ on a set $ B $, if for $ f: A \to B $, we have that $ S(a_1, a_2) $ implies $ T(f(a_1), f(a_2)) $ for all $ a_1, a_2 : A $, then $ \bar S(a_1, a_2) $ implies $ \bar T(f(a_1), f(a_2)) $ for all $ a_1, a_2 $.
+  For a relation $ S $ on a set $ A $ and a relation $ T $ on a set $ B $, if for $ f: A \to B $, we have that $ S(a_1, a_2) $ implies $ T(f(a_1), f(a_2)) $ for all $ a_1, a_2 : A $, then $ \overline S(a_1, a_2) $ implies $ \overline T(f(a_1), f(a_2)) $ for all $ a_1, a_2 $.
 \end{lemma}
@@
 The second occurrence of quotients was in the proof of Corollary \ref{cor:karoubi-presheaf}, or the lemma that it is based on.
-Initially, the statement of the lemma was only about $ \SET $, stating that $ \iota_C \bullet - : [\bar C, \SET] \to [C, \SET] $ was an adjoint equivalence.
+Initially, the statement of the lemma was only about $ \SET $, stating that $ \iota_C \bullet - : [\overline C, \SET] \to [C, \SET] $ was an adjoint equivalence.
 The proof used coequalizers of functors, like in Lemma \ref{lem:karoubi-equivalence}.

### 2024-12-09 800-conclusion.tex
Improve notation and wording

@@
 
-Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \bar \C $ and $ \hat \C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \bar \C $, can be made to work on its Rezk completion $ \hat \C $.
+Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \overline \C $ and $ \widehat \C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \overline \C $, can be made to work on its Rezk completion $ \widehat \C $.
 More generally, note that the Karoubi envelope is not specific to the material in this thesis.
@@
 In another direction, the category of smooth manifolds can be constructed as the Karoubi envelope of the category $ \C $ of the open subsets of all Euclidean spaces, with smooth maps between them \autocite[][267]{Lawvere-Karoubi}.
-For such classical results about the Karoubi envelope, it would be interesting to study how they hold up in univalent foundations for the different choices $ \overline \C $ and $ \hat \C $ of `the Karoubi envelope'.
+For such classical results about the Karoubi envelope, it would be interesting to study how they hold up in univalent foundations for the different choices $ \overline \C $ and $ \widehat \C $ of `the Karoubi envelope'.

### 2024-12-09 920-weak-cartesian-closed.tex
Improve notation and wording

@@
 \begin{definition}
-  Let $ C $ be a category with binary products (we will call the projections $ \pi_1 $ and $ \pi_2 $), and take $ A, B : C $.
-A \iindex{semi-exponential object} is an object $ A^B : C $, with a morphism $ \mathrm{ev}: C(A^B \times B \to A) $ and a function
-  \[ \mathrm{cur}_X: C(X \times B \to A) \to C(X, A^B) \]
+  Let $ \C $ be a category with binary products (we will call the projections $ \pi_1 $ and $ \pi_2 $), and take $ A, B : \C $.
+A \iindex{semi-exponential object} is an object $ A^B : \C $, with a morphism $ \mathrm{ev}: \C(A^B \times B \to A) $ and a function
+  \[ \mathrm{cur}_X: \C(X \times B, A) \to \C(X, A^B) \]
   for all $ X $, such that
   \[ \langle g \cdot \mathrm{cur}_X(f), h \rangle \cdot \mathrm{ev} = \langle g, h \rangle \cdot f \quad \text{and} \quad \mathrm{cur}_Y((g \times \id B) \cdot f) = g \cdot \mathrm{cur}_X(f) \]
-  for all $ f: C(X \times B, A) $, $ g : C(Y, X) $ and $ h : C(Y, B) $.
+  for all $ f: \C(X \times B, A) $, $ g : \C(Y, X) $ and $ h : \C(Y, B) $.
 \end{definition}
@@
 \begin{definition}
-  A \textit{weak cartesian closed category}\index{cartesian closed category!weak} is a category $ C $ with a terminal object and binary products, together with a choice for a semi-exponential object $ A^B $ for all $ A, B : C $.
+  A \textit{weak cartesian closed category}\index{cartesian closed category!weak} is a category $ \C $ with a terminal object and binary products, together with a choice for a semi-exponential object $ A^B $ for all $ A, B : \C $.
 \end{definition}
@@
 \begin{definition}
-  A \iindex{reflexive object} in a category $ C $ with binary products is an object $ U $ with an exponential $ U^U $ and morphisms $ f $ and $ g $, forming the following commutative diagram:
+  A \iindex{reflexive object} in a category $ \C $ with binary products is an object $ U $ with a semi-exponential $ U^U $ and morphisms $ f $ and $ g $, forming the following commutative diagram:
   \begin{center}
@@
 \begin{definition}
-  If we have a reflexive object $ (U, f, g) $ in a category $ C $ with finite products, we can endow the endomorphism algebraic theory $ E_C(U) $ (Definition \ref{def:endomorphism-theory}) with a $ \lambda $-theory structure with $ \beta $-equality, with
-  \[ \rho(s) = ((s \cdot g) \times \id U) \cdot \mathrm{ev} : C(U^{n + 1}, U) \]
+  If we have a reflexive object $ (U, f, g) $ in a category $ \C $ with finite products, we can endow the endomorphism algebraic theory $ E_\C(U) $ (Definition \ref{def:endomorphism-theory}) with a $ \lambda $-theory structure with $ \beta $-equality, with
+  \[ \rho(s) = ((s \cdot g) \times \id U) \cdot \mathrm{ev} : \C(U^{n + 1}, U) \]
   and
-  \[ \lambda(t) = \mathrm{cur}_{U^n}(t) \cdot f : C(U^n, U) \]
+  \[ \lambda(t) = \mathrm{cur}_{U^n}(t) \cdot f : \C(U^n, U) \]
   for $ s: E(U)_n $ and $ t: E(U)_{n + 1} $.
@@
 \begin{proof}
-  Note that for morphisms $ f: C(U^{m + 1}, U) $ and $ g: C(U^n, U)^m $,
+  Note that for morphisms $ f: \C(U^{m + 1}, U) $ and $ g: \C(U^n, U)^m $,
   \[ (\langle g_i \rangle_i \times \id U) \cdot f = f \bullet (\iota_{n, 1}(g_1), \dots, \iota_{n, 1}(g_m), x_{n + 1}). \]
@@
   Let $ L $ be an algebraic theory.
-Suppose that its associated Lawvere theory $ C $ is a weak cartesian closed category and suppose that for $ 1 : C $, we have $ 1^1 = 1 $.
+Suppose that its associated Lawvere theory $ \C $ is a weak cartesian closed category and suppose that for $ 1 : \C $, we have $ 1^1 = 1 $.
 Then we can give $ L $ a $ \lambda $-theory structure with $ \beta $-equality, given by
@@
 \begin{remark}
-  Note that in a category $ C $ with a terminal object $ I $, we have exponential objects
+  Note that in a category $ \C $ with a terminal object $ I $, we have exponential objects
   \[ A^I = A \quad \text{and} \quad I^A = I \]
@@
 \begin{lemma}
-  Take $ A, A^\prime, B : C $. If $ A^B $ and $ {A^\prime}^B $ are semi-exponential objects, then $ A^B \times (A^\prime)^B $ is the semi-exponential object $ (A \times A^\prime)^B $.
+  Take $ A, A^\prime, B : \C $. If $ A^B $ and $ {A^\prime}^B $ are semi-exponential objects, then $ A^B \times (A^\prime)^B $ is the semi-exponential object $ (A \times A^\prime)^B $.
 \end{lemma}
@@
   \begin{align*}
-    \mathrm{ev} : C(A^B \times B \to A) \quad &\text{and} \quad \mathrm{ev}^\prime : C({A^\prime}^B \times B \to A^\prime),\\
-    \mathrm{cur}_X: C(X \times B, A) \to C(X, A^B) \quad &\text{and} \quad \mathrm{cur}^\prime_X: C(X \times B, A^\prime) \to C(X, {A^\prime}^B).
+    \mathrm{ev} : \C(A^B \times B, A) \quad &\text{and} \quad \mathrm{ev}^\prime : \C({A^\prime}^B \times B, A^\prime),\\
+    \mathrm{cur}_X: \C(X \times B, A) \to \C(X, A^B) \quad &\text{and} \quad \mathrm{cur}^\prime_X: \C(X \times B, A^\prime) \to \C(X, {A^\prime}^B).
   \end{align*}
   Define
-  \[ \mathrm{ev}^{\prime \prime} = \langle \langle \pi_1 \cdot \pi_1, \pi_2 \rangle \cdot \mathrm{ev}, \langle \pi_1 \cdot \pi_2, \pi_2 \rangle \cdot \mathrm{ev} \rangle : C(A^B \times {A^\prime}^B, A \times A^\prime) \]
-  and for $ f: C(X \times B, A \times A^\prime) $,
-  \[ \mathrm{cur}^{\prime \prime}_X(f) = \langle \mathrm{cur}_X(f \cdot \pi_1), \mathrm{cur}_X(f \cdot \pi_2) \rangle : C(X, A^B \times A^{B^\prime}). \]
+  \[ \mathrm{ev}^{\prime \prime} = \langle \langle \pi_1 \cdot \pi_1, \pi_2 \rangle \cdot \mathrm{ev}, \langle \pi_1 \cdot \pi_2, \pi_2 \rangle \cdot \mathrm{ev} \rangle : \C(A^B \times {A^\prime}^B, A \times A^\prime) \]
+  and for $ f: \C(X \times B, A \times A^\prime) $,
+  \[ \mathrm{cur}^{\prime \prime}_X(f) = \langle \mathrm{cur}_X(f \cdot \pi_1), \mathrm{cur}_X(f \cdot \pi_2) \rangle : \C(X, A^B \times A^{B^\prime}). \]
   These satisfy the required equations.
@@
 \begin{lemma}
-  Take $ A, B, B^\prime : C $. If $ A^B $ and $ (A^B)^{B^\prime} $ are semi-exponential objects, then $ (A^B)^{B^\prime} $ is the semi-exponential object $ A^{B \times B^\prime} $.
+  Take $ A, B, B^\prime : \C $. If $ A^B $ and $ (A^B)^{B^\prime} $ are semi-exponential objects, then $ (A^B)^{B^\prime} $ is the semi-exponential object $ A^{B \times B^\prime} $.
 \end{lemma}
@@
   \begin{align*}
-    \mathrm{ev} : C(A^B \times B \to A) \quad &\text{and} \quad \mathrm{ev}^\prime : : C((A^B)^{B^\prime} \times B^\prime \to A^B),\\
-    \mathrm{cur}_X: C(X \times B, A) \to C(X, A^B) \quad &\text{and} \quad \mathrm{cur}^\prime_X: C(X \times B^\prime, A^B) \to C(X, (A^B)^{B^\prime}).
+    \mathrm{ev} : \C(A^B \times B, A) \quad &\text{and} \quad \mathrm{ev}^\prime : \C((A^B)^{B^\prime} \times B^\prime, A^B),\\
+    \mathrm{cur}_X: \C(X \times B, A) \to \C(X, A^B) \quad &\text{and} \quad \mathrm{cur}^\prime_X: \C(X \times B^\prime, A^B) \to \C(X, (A^B)^{B^\prime}).
   \end{align*}
   Define
-  \[ \mathrm{ev}^{\prime \prime} = \langle (\id {(A^B)^{B^\prime}} \times \pi_2) \cdot \mathrm{ev}^\prime, \pi_2 \cdot \pi_1 \rangle \cdot \mathrm{ev} : C((A^B)^{B^\prime} \times (B \times B^\prime), A) \]
-  and for $ f: C(X \times (B \times B^\prime), A) $,
-  \[ \mathrm{cur}^{\prime \prime}_X(f) = \mathrm{cur}^\prime_X(\mathrm{cur}_{X \times B^\prime}(\langle \pi_1 \cdot \pi_1, \langle \pi_2, \pi_1 \cdot \pi_2 \rangle \rangle \cdot f)) : C(X, (A^B)^{B^\prime}).
+  \[ \mathrm{ev}^{\prime \prime} = \langle (\id {(A^B)^{B^\prime}} \times \pi_2) \cdot \mathrm{ev}^\prime, \pi_2 \cdot \pi_1 \rangle \cdot \mathrm{ev} : \C((A^B)^{B^\prime} \times (B \times B^\prime), A) \]
+  and for $ f: \C(X \times (B \times B^\prime), A) $,
+  \[ \mathrm{cur}^{\prime \prime}_X(f) = \mathrm{cur}^\prime_X(\mathrm{cur}_{X \times B^\prime}(\langle \pi_1 \cdot \pi_1, \langle \pi_2, \pi_1 \cdot \pi_2 \rangle \rangle \cdot f)) : \C(X, (A^B)^{B^\prime}).
 \]
-  Then, for $ f: C(X \times (B \times B^\prime), A) $, $ g: C(Y, X) $ and $ h: C(Y, B \times B^\prime) $,
+  Then, for $ f: \C(X \times (B \times B^\prime), A) $, $ g: \C(Y, X) $ and $ h: \C(Y, B \times B^\prime) $,
   \begin{align*}
@@
 \begin{lemma}
-  Let $ L $ be a $ \lambda $-theory with $ \beta $-equality. Its corresponding Lawvere theory $ C $ is a weak cartesian closed category.
+  Let $ L $ be a $ \lambda $-theory with $ \beta $-equality. Its corresponding Lawvere theory $ \C $ is a weak cartesian closed category.
 \end{lemma}
 \begin{proof}
-  Note that by definition of a Lawvere theory, every $ n: C $ is the $ n $-fold product of $ 1 $.
+  Note that by definition of a Lawvere theory, every $ n: \C $ is the $ n $-fold product of $ 1 $.
 Therefore, binary products are given by addition on the natural numbers, and $ 0 $ is the terminal object.
@@
   Now, we define $ 1^1 = 1 $, with
-  \[ \mathrm{ev} = \rho(x_1) : C(2, 1) \quad \text{and} \quad \mathrm{cur}_n(f) = \lambda(f) : C(n, 1) \]
-  for $ f: C(n + 1, 1) $. The following shows that this is indeed a semi-exponential object:
+  \[ \mathrm{ev} = \rho(x_1) : \C(2, 1) \quad \text{and} \quad \mathrm{cur}_n(f) = \lambda(f) : \C(n, 1) \]
+  for $ f: \C(n + 1, 1) $. The following shows that this is indeed a semi-exponential object:
   \[ \rho(x_1) \bullet (\lambda(f) \bullet g, h) = \rho(x_1 \bullet \lambda(f)) \bullet (g + (h)) = f \bullet (g + (h)) \]
@@
   \[ \lambda(f \bullet ((\iota_{n, 1}(g_i))_i + (x_{n + 1, n + 1}))) = \lambda(f) \bullet g \]
-  Now, by the remark and the lemmas above, we have for $ m, n: C $ (both nonzero),
-  \[ m^n = (1 \times \dots \times 1)^n = 1^n \times \dots \times 1^n \]
+  Now, by the remark and the lemmas above, we have for $ m, n: \C $ (both nonzero),
+  \[ 1^n = 1^{1 \times \dots \times 1} = (((1^1)^1)\dots)^1 = 1 \]
   and
-  \[ 1^n = 1^{1 \times \dots \times 1} = ((1^1)^1\dots)^1 = 1 \]
-  so $ C $ has semi-exponential objects and it is a weak cartesian closed category.
+  \[ m^n = (1 \times \dots \times 1)^n = 1^n \times \dots \times 1^n = m \]
+  so $ \C $ has semi-exponential objects and it is a weak cartesian closed category.
 \end{proof}
@@
   Note that if $ L $ has both $ \beta $- and $ \eta $-equality, then for $ 1^1 $,
-  \[ \mathrm{cur}: C(n + 1, 1) \to C(n, 1), \]
+  \[ \mathrm{cur}: \C(n + 1, 1) \to \C(n, 1), \]
   which is given by $ \lambda $, has an inverse given by $ \rho $.
-Furthermore, since $ \lambda $ and $ \rho $ respect substitution, these constitute a natural isomorphism between $ C(- + 1, 1) $ and $ C(-, 1) $, so the semi-exponential object $ 1^1 = 1 $ is in fact an exponential object.
+Furthermore, since $ \lambda $ and $ \rho $ respect substitution, these constitute a natural isomorphism between $ \C(- + 1, 1) $ and $ \C(-, 1) $, so the semi-exponential object $ 1^1 = 1 $ is in fact an exponential object.
 Then we have for all $ m $ and $ n $, an exponential object
   \[ m^n = (1 \times \dots \times 1)^{1 \times \dots \times 1} = 1^{1 \times \dots \times 1} \times \dots \times 1^{1 \times \dots \times 1} = 1 \times \dots \times 1 = m, \]
-  so $ C $ is cartesian closed.
+  so $ \C $ is cartesian closed.
 \end{remark}

### 2024-12-09 600-paper.tex
Improve the diagram on the front of the thesis

@@
 
-Recall that we have an equivalence $ [\op{C_{A_1}}, \SET] \simeq \RAct{A_1} $.
+Recall that we have an equivalence $ [\op{\C_{A_1}}, \SET] \simeq \RAct{A_1} $.
 
@@
     \begin{tikzcd}
-      & \C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
+      & \C_{A_1} \arrow[d, hookrightarrow, "\yo"] \arrow[r, hookrightarrow, "\iota_{\C_{A_1}}"] & \R_A \arrow[d, hookrightarrow, "\yo"]\\
       \RAct{A_1} & P \C_{A_1} \arrow[l, "\sim"] & P \R_A \arrow[l, "\sim"]
@@
       &
-      \C_{{L_0}_1} \arrow[dd, "\yo" description, near start, hook] \arrow[rrr, "\iota_{C_{{L_0}_1}}" description, hook] \arrow[rd, "\sim" description, no head] & & & \R_{L_0} \arrow[dd, "\yo" description, near start, hook] \arrow[rd, "\sim" description, no head] & & \\
-      &
-      & \C_{L_1} \arrow[dd, "\yo" description, near start, hook] \arrow[r, hook] & \mathbf L \arrow[rr, hook] \arrow[dd, "\yo" description, near start, hook] & & \mathbf R \arrow[dd, "\yo" description, near start, hook] \arrow[rdd, hook] & \\
+      \C_{{L_0}_1}
+        \arrow[dd, "\yo" description, near start, hook]
+        \arrow[rrr, "\iota_{\C_{{L_0}_1}}" description, hook]
+        \arrow[rd, "\sim" description, no head] & & &
+      \R_{L_0}
+        \arrow[dd, "\yo" description, near start, hook]
+        \arrow[rd, "\sim" description, no head] & & \\ & &
+      \C_{L_1}
+        \arrow[r, hook] &
+      \L & &
+      \R
+        \arrow[from=ll, hook, crossing over]
+        \arrow[dd, "\yo" description, near start, hook]
+        \arrow[rdd, hook] & \\
       \RAct{{L_0}_1} &
-      P \C_{{L_0}_1} \arrow[l, "\sim"'] \arrow[rd, "\sim" description, no head] & & & P \R_{L_0} \arrow[lll, "\sim" description] \arrow[rd, "\sim" description, no head] & & \\
-      &
-      & P \C_{L_1} & P \mathbf L \arrow[l, "\sim" description] & & P \R \arrow[ll, "\sim" description] & \Pshf L \arrow[lll, "\sim" description, bend left]
+      P \C_{{L_0}_1}
+        \arrow[l, "\sim"']
+        \arrow[rd, "\sim" description, no head] & & &
+      P \R_{L_0}
+        \arrow[lll, "\sim" description]
+        \arrow[rd, "\sim" description, no head] & & \\ & &
+      P \C_{L_1}
+        \arrow[from=uu, "\yo" description, near start, hook, crossing over] &
+      P \mathbf L
+        \arrow[from=uu, "\yo" description, near start, hook, crossing over]
+        \arrow[l, "\sim" description] & &
+      P \R
+        \arrow[ll, "\sim" description] &
+      \Pshf L
+        \arrow[lll, "\sim" description, bend left]
     \end{tikzcd}
